### 2025-02-12 chapters/LBM_technique.tex
Changes 1. Initialized repo 2. Added current progress with dissertation. Intro, methods, analysis techniques, literature review and some results present

This work uses a multicomponent Lattice Boltzmann Method (LBM) to simulate the hydrodynamics of two partially miscible, incompressible fluids as implemented in LB3D. The LBM solves the Navier-Stokes equation at the incompressible limit, $\rho \frac{d \overrightarrow{u}}{dt} = \eta \Delta \overrightarrow{u} + \frac{\nabla P}{\rho} + F_{body}$, at low Mach and Reynolds numbers, incorporating density $(\rho)$, viscosity $(\eta)$, velocity $(u)$, pressure $(P)$, and body force $(F_{body})$. \cite{qian_lattice_1992, chin_lattice_2002, nourgaliev_lattice_2003} The Shan-Chen pseudopotential model is used to simulate the Cahn-Hilliard equation, $\frac{d c^k}{dt} = M^k\Delta \mu - \nabla u^k c^k$, for the non-ideal mixture model. \cite{shan_lattice_1993, shan_simulation_1994, he_lattice_1997, he_discrete_1998} $c^k$, $M^k$ and $u^k$ is the concentration, mobility and velocity of species $k$ respectively while $\mu$ is the free energy of system. Particle dynamics include Hertzian contact and lubrication forces, tracked with classical Newtonian mechanics, while particle-fluid coupling involves momentum exchange to simulate viscous dissipation. Particle-particle magnetic interactions are modeled using dipole interactions. \cite{davies_interface_2014, xie_direct_2017, xie_controllable_2021} A more detailed description of the model is provided in the following sections

\section{Hydrodynamics}

The lattice boltzmann method works by evolving a population distribution $f_{i}(\mathbf{x}, t)$ on a cubic lattice with timestep $\Delta t$ with lengthscale $\Delta x$. \cite{qian_lattice_1992, succi_lattice_2018, he_theory_1997} The D3Q19 velocity set is used in this work with the indexes $i$ represent each of the 19 velocities and converves mass and momentum conservation to the second order. It can be seen in Figure \ref{fig:d3q19_lattice}. The algorithm is split into the collision step where the populations on each lattice grid cell are relaxed towards an equilibrium, followed by the advection step where populations in each velocity direction are propagated with velocity $\mathbf{c_i}$.

The collision step occurs using a single relaxation time Bhatnagar-Gross-Krook (BGK) collision operator at relaxation rate $\tau$. \cite{bhatnagar_model_1954, qian_lattice_1992} The combined collision and advection LBM is expressed below in equation \ref{eq:LBM_BGK}

\begin{equation}
    f_{i}(\mathbf{x} + \mathbf{c}_{i}\Delta t, t + \Delta t) = f_{i}(\mathbf{x}, t) - \frac{1}{\tau}(f_{i}(\mathbf{x}, t) - f_{i}^{eq}(\mathbf{x}, t))
    \label{eq:LBM_BGK}
\end{equation}

The BGK operator limits simulations to low reynolds number and mach numbers to prevent numerical instabilities. \cite{qian_lattice_1992} The kinematic viscosity if using the BGK operator is defined as $\nu = c_s^2(\tau - \frac{\Delta t}{2})$. The equilibrium distribution is obtained from a discretized expansion of the Maxwell-Boltzmann distribution to the second order. \cite{he_theory_1997, succi_lattice_2018} This is shown in equation \ref{eq:LBM_Feq}.

\begin{equation}
    f_{i}^{eq}(\mathbf{x}, t) = w_i\rho(1 + \frac{\mathbf{c_i} \cdot \mathbf{u}}{c_s^2} + \frac{(\mathbf{c_i} \cdot \mathbf{u})^2}{2c_s^4} + \frac{\mathbf{u} \cdot \mathbf{u}}{2c_s^2} + \frac{(\mathbf{c_i} \cdot \mathbf{u})^3}{6c_s^6} - \frac{(\mathbf{c_i} \cdot \mathbf{u})\mathbf{u}^2}{4c_s^3})
    \label{eq:LBM_Feq}
\end{equation}

\begin{figure}[h]
    \centering
    \includegraphics[scale = 0.7]{figures/methods/d3q19_lattice.jpg}
    \caption{D3Q19 lattice demonstrating the rest, nearest and next nearest direction that correspond to the 19 directions $(i)$ of the lattice with lattice velocity $c_{i}$.}
    \label{fig:d3q19_lattice}
\end{figure}

$\rho$ and $\textbf{u}$ in Equation \ref{eq:LBM_Feq} are defined as the macroscopic parameters for density and velocity and can be calculated from the mass distribution using $\rho = \sum f_i$ and $\rho \mathbf{u} = \sum f_i \mathbf{c}_i$ respectively. Using the Chapman-Enskog expansion, the Navier-Stokes equation at the incompressible limit at low-reynolds numbers can be recovered. \cite{qian_lattice_1992, he_lattice_1997} The regime accessible through this method is suitable for simulations in this work as the $ 1 \leq Re \leq 100 $ and the mach number, $Ma < 0.01$, fulfilling the stability criterion and usage requirements for the presented hydrodynamic model.

\section{Non-ideal mixing}

The SC model mimics Cahn-Hilliard type behaviour through a force applied from the other fluid species $k'$ in adjacent cells $\mathbf{x'}$ on fluid species $k$ at point $\mathbf{x}$. \cite{shan_lattice_1993, shan_simulation_1994, shan_multicomponent_1995, he_discrete_1998, jansen_bijels_2011, chin_lattice_2002} Both fluid species are defined by their own distribution equation defined in Equation \ref{eq:LBM_BGK} The strength of this force is controlled through an interaction parameter, $g_{kk'}$ with no contribution from self interaction of the fluid as these are set to zero. The SC force can then be written out in Equation \ref{eq:sc_model}.

\begin{equation}
F_{k}^{SC}(\mathbf{x}, t) = -\Psi^{k}(\mathbf{x}, t)\sum_{k'}g_{cc'}\sum_{\mathbf{x'}}\Psi_{k'}(\mathbf{x'}, t)(\mathbf{x'} - \mathbf{x})
\label{eq:sc_model}
\end{equation}

An effective mass of each fluid at node $\mathbf{x}$ is used in place of the actual density to scale it between zero and one and is defined as $\psi^{c}(\mathbf{x},t) = \rho_{0}\left[1 - \exp(-\frac{\rho^{k}(\mathbf{x}, t)}{\rho_{0}})\right]$. In this model, the SC force is incorporated into the macroscopic velocities written as $\mathbf{u}_k =  \mathbf{u}_k + \frac{\tau}{\rho} F_{k}$ and finally the equilibrium distribution of each fluid species.

\section{Suspended particle dynamics}

Suspended particles will be coupled to the LB fluid based on the work conducted by Ladd. \cite{ladd_numerical_1994, aidun_direct_1998, ladd_lattice-boltzmann_2001} The particles follow Newtonian mechanics with force $\mathbf{F_p} = m_p\frac{d \mathbf{u_p} }{dt}$ and rotational inertia $\mathbf{D_p} = J_p \frac{d \mathbf{\omega_{p}}}{dt}$. $\mathbf{F_p}$ and $\mathbf{D_p}$ represent the force and torque acting on a particle with mass $m_p$ and moment of inertia $J_p$. $\mathbf{u}_p$ and $\mathbf{\omega_{p}}$ are the linear and angular velocities of the particle. The equations of motion are evolved over time using a leapfrog integrator. \cite{jansen_bijels_2011}

The particles are discretized on the lattice according to the method laid out in Ladd and Aidun \cite{ladd_lattice-boltzmann_2001}. Coupling to the LB fluid is done through momentum exchange with the fluid through modification of the velocity surrounding the fluid. The discretized particles have a no-slip boundary condition implemented as a modified bounce back boundary condition, with momentum exchange between particle and fluid done by changing the post collision population distribution, $f^{*}_{i}(\mathbf{x}, t)$, shown in Eq \ref{eq:md_LBM_mod}

\begin{equation}
    f^{*}_{i'}(\mathbf{x}, t + \Delta t) = f^{*}_{i}(\mathbf{x}, t) - \frac{2 w_{i}}{c_s^2}\rho^k \mathbf{u}_{surf} \cdot \mathbf{c_i}
    \label{eq:md_LBM_mod}
\end{equation}

In this work, $i'$ is defined such that $\mathbf{c_i} = -\mathbf{c_{i'}}$ to satisfy the bounce-back boundary condition. The fluid velocity at the particle surface, $\mathbf{u}_{surf}$, is the sum of the particle's linear and rotational velocities, $\mathbf{u}_{surf} = \mathbf{u_p} + R_i\mathbf{\omega_p}$. Advection of populations occurs after this exchange. The total force and torque on the particle are calculated by summing the total momentum over its surface. As particles move, they cover and uncover fluid grid points. Covered points are removed, while the composition of newly uncovered points in a multiphase fluid is averaged from adjacent grid points.

\subsection{Anisotropic particles}

Under 1 lattice unit additional lubrication forces are required to reduce the likelihood of particle overlap. For spherical particles, this is defined in Equation \ref{eq:sphere_lube}

\begin{equation}
    \mathbf{F}_l = -6\pi \eta \frac{R_{i}^{2} R_{j}^{2}}{(R_i + R_j)^2}(\frac{1}{|\mathbf{r}_{ij}| -R_i - R_j} -\frac{1}{\Delta_c}) \frac{(\mathbf{u}_{ij}\cdot\mathbf{r}_{ij})\mathbf{r}_{ij}}{|\mathbf{r}_{ij}|^2}
    \label{eq:sphere_lube}
\end{equation}

where $R_i$ and $R_j$ are the radii of each particle involved in the interaction, $\mathbf{r}_{ij}$ is the distance vector between the particle centers, $\mathbf{u}_{ij}$ are the relative velocities of the particles and $\Delta_c$ is the cutoff distance when the lubrication force begins to act. A hertzian contact force is also added to ensure that there is no particle overlap, defined in Equation \ref{eq:hertz_def}

\begin{equation}
    \phi_{H} = K_{H}(R_i + R_j - |\mathbf{r}_{ij}|)^{5/2}, r < R_i + R_j
    \label{eq:hertz_def}
\end{equation}

$K_H$ is the force constant used to push particles apart. To correct for the anisotropic particles used in this work, the formulas presented in Eqs \ref{eq:sphere_lube} and \ref{eq:hertz_def} can be generalized using the route followed in Gunther et al. and Davies et al., inspired by Berne and Pechukas. \cite{gunther_timescales_2014, davies_interface_2014} They first begin by rewriting the lubrication and Hertzian contact forces in a dimensionless form below

\begin{equation}
    \phi_{H}(\hat{\mathbf{o_i}}, \hat{\mathbf{o_j}}, \hat{\mathbf{r_{ij}}}) = \epsilon(\hat{\mathbf{o_i}}, \hat{\mathbf{o_j}})\Bar{\phi_{H}}\left( \frac{r_{ij}}{\sigma(\hat{\mathbf{o_i}}, \hat{\mathbf{o_j}}, \hat{\mathbf{r_{ij}}})} \right)
    \label{eq:hertz_anisotropic}
\end{equation}

Equation \ref{eq:hertz_anisotropic} defines the generalization of the Hertz force to allow simulation of ellipsoidal particles inspired by Berne and Pechukas. First, the hertzian force is made a function of orientation through the addition of eccentricity, $\chi = \frac{R_p^2 - R_o^2}{R_p^2 + R_o^2}$ and an orientation dependent forces, where $\epsilon(\hat{\mathbf{o_i}}, \hat{\mathbf{o_j}}) = \frac{\Bar{\epsilon}}{\sqrt{1 - \chi(\hat{\mathbf{o_i}}, \hat{\mathbf{o_j}})^2}}$, and $\sigma = \frac{\Bar{\sigma}}{\sqrt{1 - \frac{\chi}{2}( \frac{(\hat{\mathbf{r_{ij}}}\hat{\mathbf{o_i}} +  \hat{\mathbf{r_{ij}}}\hat{\mathbf{o_j}})^2}{1 + \chi \hat{\mathbf{o_i}}\hat{\mathbf{o_j}}} +  \frac{(\hat{\mathbf{r_{ij}}}\hat{\mathbf{o_i}} -  \hat{\mathbf{r_{ij}}}\hat{\mathbf{o_j}})^2}{1 - \chi \hat{\mathbf{o_i}}\hat{\mathbf{o_j}}})}}$, $\Bar{\sigma} = 2R_{\perp}$. \cite{gunther_lattice_2013, gunther_timescales_2014, davies_assembling_2014}

A similar generalization process is done for the lubrication force, resulting in Equation \ref{eq:md_force} where $\mathbf{\Bar{F}}(r) = \hat{\mathbf{r_{ij}}}(\hat{\mathbf{r_{ij}}}(\mathbf{u}_i - \mathbf{u}_j))\left( \frac{1}{r - 1} - \frac{\sigma}{\Delta_{c}} \right)$.

\begin{equation}
    \mathbf{F_{ij}}(\hat{\mathbf{o_i}}, \hat{\mathbf{o_j}}, \hat{\mathbf{r_{ij}}}) = \epsilon(\hat{\mathbf{o_i}}, \hat{\mathbf{o_j}})\mathbf{\mathbf{F_{ij}}}\left( \frac{r_{ij}}{\sigma(\hat{\mathbf{o_i}}, \hat{\mathbf{o_j}}, \hat{\mathbf{r_{ij}}})} \right)
    \label{eq:md_force}
\end{equation}

\subsection{Magnetic field and particle coupling}

The magnetic dipole potential is defined as

\begin{equation}
    \mathbf{U_{ij}} = \frac{\mu_0 m_i m_j}{4\pi r_{ij}^{3}} \left[ \Hat{\mathbf{o_i}} \cdot \Hat{\mathbf{o_j}} - 3(\Hat{\mathbf{o_i}} \cdot \Hat{\mathbf{r_{ij}}})(\Hat{\mathbf{o_j}} \cdot \Hat{\mathbf{r_{ij}}}) \right]
    \label{eq:magnet_potential}
\end{equation}

Where $\mu_0 = 4\pi \cdot 10^{-7} \frac{H}{m}$,  $\Hat{\mathbf{o_i}}$ is the orientation unit vector of particle $i$, $\Hat{\mathbf{r_{ij}}}$ is the distance vector between particles $i$ and $j$ and $m_i$ is the magnitude the magnetic dipole of particle $i$. From the potential, the force and torque of the dipole force between particles can be found. These expressions are shown in equations \ref{eq:dipole_magnetic_force} and \ref{eq:dipole_magnetic_torque} for the force and torque respectively.

\begin{equation}
    \mathbf{F}_{ij} = \frac{3 \mu_0}{4 \pi} [\frac{5(m_i \cdot \mathbf{r}_{ij})(m_j \cdot \mathbf{r}_{ij})}{|\mathbf{r}_{ij}|^7}\mathbf{r}_{ij} - \frac{(m_i \cdot m_{j})\mathbf{r}_{ij} + (m_i \cdot \mathbf{r}_{ij})m_i + (m_j \cdot \mathbf{r}_{ij})m_j }{|\mathbf{r}_{ij}|^5})]
\label{eq:dipole_magnetic_force}
\end{equation}

\begin{equation}
    \mathbf{T}_{ij} = \frac{\mu_0}{4 \pi}[ \frac{3(m_j \cdot \mathbf{r}_{ij})m_i \times \mathbf{r}_{ij} }{|\mathbf{r}_{ij}|^5} - \frac{m_i \cdot m_j }{|\mathbf{r}_{ij}|^3} ]
    \label{eq:dipole_magnetic_torque}
\end{equation}

Equations \ref{eq:magnet_force} and \ref{eq:magnet_torque} are used to calculate the force and torque that the field exerts on each particle.

\begin{equation}
    \mathbf{F_{j}} = (m_j \Hat{\mathbf{o_j}} \cdot \nabla B_i)
    \label{eq:magnet_force}
\end{equation}

\begin{equation}
    \mathbf{\tau_j} = (m_j \Hat{\mathbf{o_j}} \times B_i)
    \label{eq:magnet_torque}
\end{equation}

The total force and torque exerted on each particle is the sum of the particle dipole interaction and the field dependent contribution.

### 2025-02-12 chapters/analysis_techniques.tex
Changes 1. Initialized repo 2. Added current progress with dissertation. Intro, methods, analysis techniques, literature review and some results present

\section{Analysis techniques}

In this work, the structure factor derived domain size, geometric pore size distribution and tortuosity will be utilized to characterize the microstructure. The nematic order parameter will be used to characterize the particle order to the magnetic field. The average angle to the interface will be utilized to characterize how the particles ordering to the field affect the interface position. Finally, the radial distribution function will be used to probe how differences in ordering change the packing of particles on the interface. The time evolution of viscosity will provide insight into the rheological properties of the bijel, while the aforementioned analysis tools in addition to proportion of particles on the interface will be calculated to provide insight into how the bijel reacts to shear, parallel and perpendicular to the magnetic field. A more detailed description of the implementation of each method is shown in subsequent sections.

\subsection{Particle filling and interface smoothening}
\label{section:filling_routine}

Particles are the cause of bijels but they can also make characterization of domain size, curvature, pore size distribution and tortuosity more difficult as particles may change these parameters. An extrapolation scheme is required to connect the interface one different sides of the particles and to fill in the particles themselves so as to create a more accurate interface for other techniques.

This is accomplished through sequential density averaging and filling of grid points making up the particles from the outside in. The grid cells around a cell of interest are averaged using a D3Q19 like lattice and stepping through all points with a order parameter $\phi = \rho^w - \rho^o$ value of 0.

\subsection{Domain size}

The characteristic length scale at time $t$ of a bijel can be computed from the moments of the structure factor. The structure factor is first calculated from the order parameter of the phases, defined as $\phi = \rho_b - \rho_r$ where $\phi$ is the density order parameter and $\rho_b$ and $\rho_r$ are the densities of the blue and red fluid respectively. Next, the fluctuations of the order parameter $\phi'$ is calculated by subtracting the mean of the order parameter, $\langle \phi \rangle$ from the order parameter, defined as $\phi' = \phi - \langle \phi \rangle$. Next, the fourier transform of the fluctuations of the order parameter $\phi'(\mathbf{k})$ is calculated. Finally, $\phi'(\mathbf{k})$ is squared and made positive and normalized by the volume of the system defined as $S(\mathbf{k}) = \frac{1}{N} |\phi'(\mathbf{k})^2|$.

The first domain size metric used is the domain size derived from the spherically averaged first moment of the structure factor. The spherical averaging is done by averaging the values of the structure factor at the same $\mathbf{k}$ up till the nyquist frequency. The spherically averaged structure factor is defined as $S(k)$ where $k$ represents the wave numbers obtained from the spherical averaging. Next, the first moment $\langle k_1 \rangle$ is calculated as $\langle k_1 \rangle = \frac{\Sigma_{k} k\cdot S(k)}{\Sigma_{k} S(k)}$. Finally, the domain size is calculated as $L_1 = \frac{2 \pi}{\langle k_1 \rangle}$. This domain size is used in past literature \textcolor{blue}{https://doi.org/10.1017/S0022112001004682, https://www.doi.org/10.1103/PhysRevE.67.046304} to calculate the correct scaling regime of a system undergoing spinodal decomposition.

While it cannot be used to correlate physical phenomena the second moment of the structure factor derived domain size is utilized here to discriminate directional length scales. Owing to the spherical averaging done, the first moment moment derived domain size is unable to be used to calculate direction specific length scales. The second moment of the structure factor is first calculated by multiplying $\langle \mathbf{k_2}^2 \rangle = \frac{\Sigma_{\mathbf{k}} \mathbf{k}^2 S(\mathbf{k})}{\Sigma_k S(\mathbf{k})}$ where $\mathbf{k_2}^2$ represents the second moment in each cartesian direction. Next, the domain size in each direction is calculated as $L_2 = \frac{2 \pi}{\sqrt{\mathbf{k_2}^2}}$. \cite{jansen_bijels_2011, gunther_timescales_2014} In the rest of this document, $L_{\parallel}$ and $L_{\perp}$ is defined as the domain size parallel and perpendicular to the applied magnetic field.

\subsection{Tortuosity}

Tortuosity can be defined as the ratio between the path length $(L_{eff})$ of two points and the euclidean distance between two points $L_{0}$, $\tau = L_{eff}/L_{0}$. In practice this is the geometric definition of tortuosity as often the tortuosity of a system is dependent upon other factors. Diffusive tortuosity is what we will use here, defined as $\tau = \frac{D_{eff}}{D_0}$. This metric is also more relevant to the potential applications of bijels which rely on diffusion of mass for their uses.

Simulation techniques such as Lattice Boltzmann or Molecular Dynamics have been used to characterize the tortuosity of porous materials. However, these simulations can be computationally expensive and time consuming to perform, even though they may have great accuracy. Recently, particle diffusion techniques based on a random walk such as pytrax and taufactor or Pore Network Modelling (PNM) based techniques such as PoreSpy have been introduced which offer a tradeoff of accuracy for speed. Taufactor in particular is implemented on GPU's with a periodic boundary condition, allowing for rapid and accurate calculation of the tortuosity.

\textcolor{blue}{https://joss.theoj.org/papers/10.21105/joss.05358, https://doi.org/10.1016/j.softx.2019.100277, https://joss.theoj.org/papers/10.21105/joss.01296}

Before using taufactor, the microstructure is first binarized. This is done by first calculating the order parameter of the system with $\phi = \rho_b - \rho_r$ where $\phi$ is the order parameter and $\rho_b, \rho_r$ are the densities of the blue and red fluid respectively. Next, the interface described with $\phi$ is smoothened using the algorithm detailed in section \ref{section:filling_routine}. In many of the bijels synthesized using small molecule liquids, monomer is introduced into the oil phase and polymerized. Therefore, to perform the binarization step, we select all points where $\phi \leq 0$ and set their value to $0$, and all other values are set to $1$. To taufactor, $1$ represents void spaces and 0's are solid.

\subsection{Nematic order parameter}

The orientational ordering of the particles to one another can be characterized using the nematic order parameter, defined as $S$. This parameter was first used to characterize liquid crystals. However its use has expanded to colloidal systems to characterize the ordering of a system to an average orientation, termed the director. A system is said to have nematic ordering if its components have orientational order to the director but does not require the system to have translational order.

The nematic order parameter is calculated from the orientational alignment tensor, $Q$, which is calculated from the orientation of particles to one another as $\langle Q \rangle = \frac{1}{N} \sum_{i}^{N} \langle \frac{3}{2}u_i u_i - \frac{1}{2}I \rangle$. $u_i$ is the orientation of particle $i$ and $I$ is an identity matrix. \cite{veerman_phase_1992} While there are multiple methods to evaluate the nematic order parameter, the one we have picked is where the largest eigenvector is $S$, with its corresponding eignvector referring to the director of the system. \cite{veerman_phase_1992} \textcolor{blue}{https://doi.org/10.1080/00268978400101951} A system is defined to be ordered nematically, if $S > 0.3$. In this work, the direction of the director will be compared to the direction of the magnetic field. We utilize the implementation in Freud to calculate the nematic order parameter.

\subsection{Radial distribution function}

The radial distribution function (RDF) is used to measure the normalized number density of particles around a reference particle as a function of distance. The normalization factor is the expected density of particles derived from an ideal gas. The general form of the equation to calculate the RDF is $g(r) = \frac{1}{\rho_{ideal}(r) 4\pi r^2} \int_{r}^{r+\Delta r} \delta(r_{i} - r_{j}) dr$ where $\rho_{ideal}(r)$ represents the density expected at distance r from a reference particle in an ideal gas, $\delta(r_{i} - r_{j})$ represents the number of particles within the bin $r + \Delta r$ and integrated to get a volumetric density. As implemented in a numerical method, the integral becomes a sum. After correcting for the periodic boundary condition using the minimum image convention, the RDF can be used to characterize periodic systems. We utilize the implementation in the software package Freud.

\subsection{Average interface angle and proportion of particles on the interface}

One way to differentiate between whether the particles pull the interface or whether the tilt of the particles at the interface causes changes to the jamming point is to characterize the average interface angle. The average interface angle $(\psi)$ is defined as the angle between the orientation of the axis of symmetry of the particle and the interface normal. The former mechanism would show little to no change in the interface angle, while the former mechanism should show large differences. The proportion of particles on the interface can also be calculated using this technique.

The orientation of the particle is obtained from the output files from the simulation. The interface normal needs to be calculated from $\phi$. This is done by taking $\phi$ as calaculated from the red and blue fluid densities, then performing the particle fill routine described in section \ref{section:filling_routine}. Next, a mesh corresponding to the interface is obtained using a marching cubes algorithm at a countour level of 0 with a cube length of 4 lattice units, which corresponds to the thickness of the interface. \textcolor{blue}{https://doi.org/10.7717/peerj.453} The position of the particle and its closest vertex is calculated. If this distance is larger than the first minimum in the radial distribution function, it is considered to be not on the interface and the next step is not performed. The vertex and corresponding normal closest to the position of a particle is used in the dot product, $\cos{\psi} = \frac{n_{int} \cdot o_{i}}{|n_{int}| |o_i|}$ where $n_{int}$ is the normal of the interface and $o_i$ is the orientation of particle i. After looping through all the particles, the average of $\psi$ and the number of particles in the interface is calculated.

\subsection{Shear viscosity}
\label{section:shear_viscosity}

Shear viscosity is a physical parameter measured through the dissipation of applied strain onto a fluid, resulting in an applied shear stress. In an incompressible fluid, the viscosity $(\eta)$ is defined as the ratio between the measured shear stress $(\sigma)$ and the applied strain rate $(\dot{\gamma})$, $\sigma = \eta \dot{\gamma}$. In rheological experiments, the shear viscosity is measured through a viscometer based on Couette or shear viscometry and Poiselle or pressure gradient viscometry. A Couette cell functions by applying a shear velocity to one or more walls, and measuring the shear stress response of the fluid. Common geometries for Couette cells include the cone and plate and concentric cylinder viscometers.

In this work, a shear velocity is imparted in the z direction, across the x-axis. Therefore, the shear stress in the x and z directions, $\sigma_{xz}$, is measured. $\sigma_{xz}$ is output per lattice in the output file, which is then averaged across the entire volume to obtain an average shear stress $\hat{\sigma_{xz}}$. The effective viscosity of the system, $\eta_{eff}$ is calculated using $\eta_{eff} = \frac{\hat{\sigma_{xz}}}{\dot{\gamma}}$ where $\dot{\gamma} = \frac{2 u_{LE}}{L_x}$. $u_{LE}$ is the shear velocity is enforced through the Lees-Edwards boundary condition, as described in section \textcolor{blue}{description of lees edwards BC}.

\subsection{Yield stress and zero shear rate viscosity}

The yield stress of bijels can be calculated using the flow curve, stress ramp or from oscillatory rheological techniques. The flow curve method involves the steady application of shear, followed by measurements of the shear stress response of the material. The plateau of the shear stress response is indicative of the yield stress of the material. The stress ramp method involves the application of a shear stress onto the material, followed by measurements of the strain rate. A perfectly elastic material will have no strain rate, while a perfectly disspitative material will have high strain rate. The yield stress is characterized as the point when a rapid increase in strain rate is observed. The yield stress from oscillatory rheology is defined when the storage modulus is lower than the loss modulus. This work will utilize the flow curve method.

The shear viscosity calculated using the method detailed in Section \ref{section:shear_viscosity} will be plotted as a function of applied shear rate. Rheological models such as the Herschel Buckley, Bingham Plastic or Carreu models can be utilized to fit the shear viscosity as a function of shear rate to calculate the zero shear rate viscosity. In bijel applications, this parameter gives insight into the material stability and processability.

### 2025-02-12 chapters/final_remarks.tex
Changes 1. Initialized repo 2. Added current progress with dissertation. Intro, methods, analysis techniques, literature review and some results present

\section{Conclusion}

\section{Future work}

This work utilized 2 ellipsoidal particle geometries which were not as anisotropic as rods or plates that some particles have naturally, such as cellulose nanocrystals and graphene nanoplates. These particles have also been shown to naturally have nematic ordering at higher volume fractions that correspond to the volume fractions present at bijel interfaces. An investigation into how using rods or plate like particles would be instructive in identifying how onsager theory can be linked to bijel microstructure. \textcolor{blue}{https://doi.org/10.1039/D1SM00367D}

Colloidal systems made with cohesive and soft particles have been shown in the literature to have different glass transition points and rheological behavior from their hard sphere counterparts. In bijels, cohesive particles in particular have been suggested as a means to create "armored" bijels to improve their performance in catalytic materials, allowing higher flow rates to be used. Investigations into soft particles are of interest in biomedical engineering applications, with newly developed nanogels and hydrogels being suggested as drug carriers or vectors for stimuli response through temperature or pH.

Another avenue of exploration would be the use of gradient or rotating magnetic fields in place of the constant magnetic fields used here. One study on bijel microstructure showed that a gradient in the particle volume fraction can be used to create a gradient in the eventual domain size. A gradient field may be able to generate a gradient in the nematic order parameter, affecting the particle packing of the bijel at different heights and varying the pore size as a function of height in the field gradient direction. In a ferrofluid or solution of magnetic colloids, a rotating field can assemble particles into chains or rings. In the context of bijel structural response, this can be used to tune bijel microstructure as this process can control the unjamming and rejamming of the particle monolayer, allowing for greater control over the resulting bijel microstructure than a constant field would have. In these simulations, the frequency of rotation would likely need to be tuned based upon how quickly particles respond to field in the bijel.

\section{Acknowledgments}

The author acknowledges Dr. Ulf Schiller and the members of the Schiller and Kuksenok groups for the discussions on the characterization and computational techniques used in this work. This work is supported by the US National Science Foundation under award numbers DMR-1944942 and OIA-2131996. Any opinions, findings, conclusions, or recommendations expressed in this material are those of the author(s) and do not necessarily reflect those of the National Science Foundation.

Clemson University is acknowledged for generous allotment of compute time on Palmetto cluster. This research used the Delta advanced computing and data resource which is supported by the National Science Foundation (award OAC 2005572) and the State of Illinois. Delta is a joint effort of the University of Illinois Urbana-Champaign and its National Center for Supercomputing Applications.

This work used Delta at the University of Illinois Urbana Champaign through allocation PHY220131 from the Advanced Cyberinfrastructure Coordination Ecosystem: Services $\&$ Support (ACCESS) program, which is supported by National Science Foundation grants 2138259, 2138286, 2138307, 2137603, and 2138296.

### 2025-02-12 chapters/introduction.tex
Changes 1. Initialized repo 2. Added current progress with dissertation. Intro, methods, analysis techniques, literature review and some results present

\begin{itemize}
    \item What is a porous material? 
    \begin{itemize}
        \item What makes them different to non-porous materials?
        \item Why do their differences make them industrially relevant?
        \item What are some synthesis techniques that exist?
        \item What are weaknesses with those synthesis techniques?
    \end{itemize}
    \item What is a particle stabilized emulsion
    \begin{itemize}
        \item Why are they interesting for porous material applications?
        \item What is a bijel?
        \item How are bijels relevant to porous materials?
        \item Fabrication techniques that are proposed which allow large scale bijel fabrication
        \item microstructure control in those applications
    \end{itemize}
    \item Purpose of study
    \begin{itemize}
        \item Three aims of the study 
        \item significance of study
        \item assumptions and limitations of the study
    \end{itemize}
    \item Summary of motivation, purpose and research aims
\end{itemize}

% \textcolor{blue}{
% \begin{itemize}
%   \item Explain what is a porous material and the advantages they have in their applications compared to non-porous materials 
%   \item Detailed description of their applications and why we are interested in stimuli responsive porous materials 
%   \item Overview of porous material synthesis techniques and what are some areas where there is room for improvement (Definition of critical issues)
%   \item Explain what emulsion templating is and the specific advantages it has over other techniques. Recall where it has been used to great effect
%   \item Explain how bijels fit into emulsion templating and how they offer advantages to standard emulsion templates
%   \item Explain how bijels have been manufactured
%   \item Linking stimuli response as a way to add additional functionality to bijels and identifying how to process them more effectively
%   \item Explain why magnetic fields are interesting in this case
%   \item Explain what is a bijel, how they have been synthesized and some hints at past work for controlling their microstructure (literature review)
%   \item Explain how bijels and stimuli response can address the shortcomings addressed in the previous section (Research objectives)
% \end{itemize}
% }

\section{Introduction}

Porous materials are defined as materials that contain pores or voids within their structure where no material is present. Homogeneous materials in contrast have a uniform structure with no pores. These pores vary in shape and distribution, with materials being categorized by pore size per IUPAC as $(L)$ as microporous $(L < 2nm)$, mesoporous $(2nm < L < 50nm)$ and macroporous materials $(50nm < L)$. \textcolor{blue}{https://doi.org/10.1351/pac198557040603} The presence of these pores increases the surface area to volume ratio of porous materials compared to their homogeneous counterparts. A common experimental technique used to estimate the surface area of a porous material derived from Brunauer-Emmett-Teller(BET) theory shows that porous materials can have surface areas more than a hundred times larger than homogenous materials, dependent upon the pore size and pore size distribution. \cite{shimizu_surface_2022}

In addition to the pore size and its distribution within the material, the arrangement of pores within the material contribute to the performance of the synthesized material, commonly measured using the tortuosity. Tortuosity here is defined as the path length between two points divided by the euclidean length between those points. A tortuosity larger than one implies that the path length is longer than the euclidean length, and vice versa if the tortuosity if less than one. Highlighting the confluence of these factors are the large variety of tailored microstructures for various applications. Each of the specified pore length scales have their unique uses, such as microporous materials being used as zeolites and photonic bandgap materials while macroporous materials facilitate greater transport properties, suitable in applications such as battery electrodes and drug delivery systems. \cite{chen_tortuosity_2020, ebner_tortuosity_2014}

These range from Metal Organic Framework(MOF) enhanced gas adsorption, \textcolor{blue}{https://doi.org/10.1002/admi.201400040} This increased surface area to volume ratio enhances the properties of the base material in applications such as catalysis, battery electrodes and drug delivery systems among many more making them valuable microstructures. \cite{cha_bicontinuous_2019, samdani_bicontinuous_2017, thorson_bijel-templated_2019}

\begin{figure}
    \centering
    \includegraphics[scale = 0.5]{figures/introduction/bijel_templating.png}
    \caption{Fabrication of a graphite oxide battery electrode using bijel template. \cite{garcia_scalable_2019}}
    \label{fig:bijel_template}
\end{figure}

Conventionally, porous materials have been synthesized through solvothermal synthesis or pyrolysis used in the synthesis of zeolites and activated carbon respectively. With more targeted applications of porous materials, synthesis techniques such as sol-gel synthesis, freeze drying and various forms of templating have been utilized to synthesize porous materials from length scales of $10^{-9}m$ to $10^{-3}m$. \cite{stein_morphological_2008, ray_comprehensive_2016, cervellere_mesoscopic_2019, garcia-bennett_unique_2020, zhang_emulsion_2019, alves-rosa_design_2013} Industry has also taken up techniques such as electrospinning to generate non woven fibers, used in membrane synthesis. Templating techniques in particular offer access to various pore length scales, bottom up synthesis and functionality through leveraging various physical phenomena. Colloidal templating works through the close packing of particles. Surfactant and polymer templating work through the assembly of macromolecules into their equilibrium configurations. Emulsion templating utilizes the phase separation of partially misicble liquids to form the pore structure of a porous material.

Emulsion templating offers access to a large length scale of tunable pore sizes, continous production through microfluidic junctions or other flow media, functionalization through the addition of additives or stabilizers, scope of accessible microstructures and mild synthesis conditions. It can further be extended to include heirarchical porosity, further enhancing its utility and fabricated material properties. \cite{yang_hierarchically_2017, thompson_hierarchically_2019, wang_morphology_2023} Figure \ref{fig:bijel_template} demonstrates how emulsion templating allows bottom up synthesis of hierarchically porous materials, although other examples do exist. \cite{garcia_scalable_2019, santiago_cordoba_aerobijels_2020, thorson_bijel-templated_2019, lu_controllable_2020, wang_morphology_2023}

\begin{figure}
    \centering
    \includegraphics[scale = 0.3]{figures/introduction/bijel_coarsening.jpg}
    \caption{Initiation and arrest of spinodal decomposition as particles adsorb onto the interface, followed by jamming once the interfacial area matches the cross sectional area of the adsorbed particles\cite{stratford_colloidal_2005}}
    \label{fig:bijel_coarsen}
\end{figure}

One such emulsion microstructure of interest is the bicontinuous interfacially jammed emulsion gel(bijel). \cite{stratford_colloidal_2005, herzig_bicontinuous_2007, lee_bicontinuous_2010} Bijels are made by arresting the spinodal decomposition of partially miscible liquids, caused by particles adsorbing on the interface and jamming as the cross sectional area of the particles match that of the interface, summarized in Figure \ref{fig:bijel_coarsen}. Bijels are of interest due to their co-continuous, tortuous microstructure which represent excellent fits for several porous material applications.

Bijels were discovered in simulations in 2005 and experimentally realized in 2007 when a mixture of water and 2-6-lutidine mixed with surface modified silica nanoparticles underwent thermally induced spinodal decomposition. \cite{stratford_colloidal_2005, herzig_bicontinuous_2007} Since then, multiple other casting mixtures and particle chemistry's have been used to fabricate bijels using Thermally Induced Spinodal Decomposition (TIPS). \cite{lee_bicontinuous_2010, bai_dynamics_2015} More recently, techniques such as Solvent Transfer Induced Phase Separation (STrIPS), Vapor Induced Phase Separation (VIPS), Non-solvent Induced Phase Separation (NIPS), homogenization and liquid in liquid printing have been utilized to fabricate bijels, demonstrating the ability for bijels to be synthesized in a continuous process, suitable for scale up. \cite{haase_continuous_2015, wang_scalable_2020, cai_bijels_2017, yabuno_preparation_2020, wang_bicontinuous_2023, amirfattahi_fabrication_2024} These techniques also offer preparation of bijels in various different shapes and form-factors for various uses such as fibers, coatings and capsules, seen in Figure \ref{fig:strips}. \cite{haase_continuous_2015, boakye-ansah_controlling_2020, kharal_hightensile_2020, wang_bicontinuous_2023}

\begin{figure}[h]
    \centering
    \includegraphics[scale = 2]{figures/literature_review/STRIPPS.jpg}
    \caption{STrIPS in action. Extrusion of the bijel casting mixture into a non-solvent bath, followed by removal of solvent from the casting mixture through diffusion. \cite{haase_continuous_2015}}
    \label{fig:strips}
\end{figure}

However, these techniques all depend upon controlling the rate of phase separation, which involve changing the casting mixture composition to modify the obtained microstructure. In STrIPS, the obtained bijel microstructure is a function of the flow rate and selected co-solvent, selected to change the rate of phase separation. \cite{haase_continuous_2015} This affects material properties such as the mechanical performance of the bijel, important in fields such as catalysis where rigidity of the particle monolayer is crucial in ensuring consistent performance. \cite{reeves_particle-size_2015, haase_situ_2016, boakye-ansah_controlling_2020} Identification of other techniques that can be utilized to modify the microstructure of a bijel would enable bijels to continue using the desired composition of constituents, while also adding other unique properties. Stimuli response offers one such road to microstructure modification.

\textcolor{blue}{ADD IN PICTURE FROM THAM 2021 AND CUI 2013 ON EXAMPLES OF STIMULI RESPONSE IN EMULSIONS}

Stimuli response based on pH, external fields and temperature have been used in past works when looking at modifying the microstructure of emulsion droplets for enhanced oil recovery, pharmaceutical and cell adhesion. \cite{haase_nanoparticle_2011, tham_magnetophoresis_2021, cui_stabilizing_2013, manfredini_limonene--water_2021}  It was shown that external fields can be used to move, control emulsion stability and elongate emulsion droplets. \cite{tham_magnetophoresis_2021, cui_stabilizing_2013} \textcolor{blue}{https://pubs.acs.org/doi/10.1021/la047691n} Bijels stabilized spherical particles under a magnetic field showed no meaningful microstructure changes. \cite{kim_bijels_2010} Bijels stabilized with spherical particles under an electric field showed more promise. \cite{carmack_tuning_2018} However, magnetic fields offer more targeted stimuli response, allowing even weak fields to incite a response. Magnetic fields non-interaction in many situations offer advantages to many of the desired uses of bijels within pharmaceutical or bioengineering applications. \cite{vanoli_bijels_2022, thorson_bijel-templated_2019, thorson_composite_2018} These same applications also have a need for in-situ microstructure modification that would enable tunable drug delivery rates, separations or catalyst efficiency and permeability improvements in the system. Therefore, identifying schemes that allow modification of the pore size and tortuosity  without synthesis of a new material would enhance the use case of bijels.

Anisotropic particles at interfaces have shown self assembly due to the presence of multi-polar pressure fields caused by interface deformation. Self assembly has also been shown for ellipsoidal particles at interfaces under magnetic fields. Ellipsoidal particles have also been shown to exhibit magnetic field controlled orientations at interfaces, as Bresme and Faraudo showed. \cite{bresme_orientational_2007, davies_interface_2014} Under magnetic fields, assemblies of multiple ellipsoidal particles have been shown to have energy minima at unexpected locations. \cite{newton_influence_2014, newton_capillary_2018} Thus ellipsoidal particles at interfaces, whose orientations and packing can be controlled through external fields, offer a potential means to control the microstructure of bijels.

Bijels present a bottom up synthesis strategy for porous material templates for hard and soft material applications in a scalable and continuous method using STrIPS and other techniques. However, the microstructure control these techniques offer are intrinsically linked to the casting mixture composition. Stimuli response offers a way to modify the microstructure of bijels while still maintaining the various form factors these continuous synthesis techniques can output. While stimuli response has been explored in the past using bijels stabilized with spherical particles with little success, anisotropic particles are poised to allow microstructure modification of bijels upon application of an external field. This technique also has the potential to allow for post synthesis microstructure modification. Therefore, this work seeks to identify a means to control the microstructure of a bijel stabilized with magnetically responsive ellipsoidal particles using magnetic fields.

% Bijels have proposed uses in many of these with the microstructure of the material being shown to affect material properties. \cite{cha_bicontinuous_2019, khan_nanostructured_2022, vanoli_bijels_2022}

% Magnetic fields offer several advantages over currently utilized techniques such as electric fields and shear. \cite{cui_stabilizing_2013, mulligan_deformation_2011} These include greater specificity of response as most materials are unresponsive to magnetic stimuli as well as even weak fields being sufficient to incite responses in many cases.

% this adds value to many of the desired uses of bijels within pharmaceutical or bioengineering applications. \cite{vanoli_bijels_2022, thorson_bijel-templated_2019, thorson_composite_2018}

\textcolor{blue}{Add commentary about past results with bijels and why we use anisotropic particles in bijels. Changes this makes} Therefore, identification of a scheme which allows for tunability of the microstructure, independent of the composition of the casting mixture and post synthesis is the goal of this work.

\section{Research objective}

This work seeks to identify means to control the bijel microstructure independent of the casting mixture composition by utilizing magnetic stimuli on bijels stabilized with magnetically responsive ellipsoidal particles. The proposed mechanism of microstructure modification is driven through reorientation of the particles to the applied magnetic field altering how the particles pack on the interface. By changing the interfacial packing of the particles, we change when the particles jam, which in turn changes the jamming point of the bijel. This mechanism is predicted to be effective during and after synthesis. The processability of bijels fabricated using this technique will also be investigated to ascertain how changes in particle packing affect the rheology of the material. An overview of three major research aims will be presented below.

% this work seeks to identify means to control the bijel microstructure independent of the casting mixture composition utilizing magnetic stimuli response of anisotropic particles. The proposed mechanism of microstructure modification is driven through reorientation of the particles to the applied magnetic field altering how the particles pack on the interface.

\subsection{Aim 1: Determination of the degree of microstructure changes expected when applying a constant field during bijel formation}
\label{section:aim1_desc}

The jamming point of a bijel controls the obtained microstructure, as shown by previous work comparing the length scale of bijels synthesized with different particle volume fractions. It has also been shown how magnetic fields can be used to self assemble ansisotropic particles at interfaces and how they can tilt out of the interface. \cite{davies_interface_2014, davies_assembling_2014} On a curved interface with many other particles, it is unknown how multiple particles orienting to a field and having regular structure will affect when and how the bijel will jam. \cite{bresme_orientational_2007, davies_interface_2014}

To assess the obtained microstructure upon application of a field during formation of the bijel, homogenous mixtures containing spherical and ellipsoidal particles will be subjected to field strengths above and below the critical field strength when particle orientations to the interface are controlled by the applied field strength, as calculated by Bresme and Faraudo for the particle used. This selection of fields will allow insight into the controlling mechanisms behind microstructural changes observed, allowing verification of the hypothesis and ascertainment where the most control over the microstructure can be exercised.

The average and directional domain sizes in addition to their relation with tortuosity will provide windows into the microstructural properties of the resulting bijel. The nematic order parameter and average interfacial angle will be used to investigate how the application of the field affects the particle ordering to each other, and to the interface. Finally, the radial distribution function will be used to assess if the orientational changes expected upon field application, affects the packing of the particles on the interface.

\subsection{Aim 2: Microstructure changes and timescales upon application of a magnetic field after formation}
\label{section:aim2_desc}

Particles on the surface of emulsion droplets have been shown to unjam and rejam into new, stable microstructures upon application of stimuli. \cite{cui_stabilizing_2013} Two techniques of microstructure change are proposed. The first technique is that the adsorption energy is so strong that the interface is dragged along with the particles until they rejam in their new location and orientation to the field. The second technique is that the particles tilt in place out of the interface, causing domain coarsening before the particles jam in their new positions and orientations. The mechanism, derived microstructure change and timescales will be assessed in this aim.

The response of bijels to magnetic fields will be assessed through analyzing how model bijels made with no fields respond to field strengths above and below the critical field strength as calculated from Bresme Faraudo theory. The microstructure properties such as the average domain size, particle orientation to the field and interface and the Steinhardt 6 fold bond order parameter to examine the spatial relationship of the particles to their neighbors. These techniques will allow elucidation of which mechanism is present at which magnetic field strength. Additionally, the microstructure changes observed will be characterized and compared to one another to assess how the applied magnetic field changes the final microstructure obtained.

Next, the importance of the initial order of the particle monolayer will also be assessed through increasing the applied field to equal to the surface tension forces on bijel templates simulated under various field strengths. The applied field will also be switched off on bijel templates simulated under the same field strengths. The same analysis metrics mentioned earlier will be used. Additionally, the microstructures with the same difference in applied field,  will be assessed to investigate the reversibility of bijel microstructures.

\subsection{Aim 3: Rheological characterization of bijels formed under and subjected to a magnetic field}
\label{section:aim3_desc}

In many of the fabrication processes described above, the rheology of the bijel casting mixture is essential. \cite{haase_continuous_2015, cai_bijels_2017, amirfattahi_fabrication_2024} Ching showed that rheologically, bijels are colloidal glasses percolating in 3D space. \cite{ching_bijel_2022} First, a shear capillary number is defined as $Ca_s = \frac{\eta_{f} \dot{\gamma} L_{1}}{\sigma}$ where $\dot{\gamma} = \frac{u_{LE}}{L_x}$ is the strain rate and $L_1$ is the average domain size. \cite{frijters_effects_2012, yang_capillary_2022} Lower capillary numbers in the range of $ 10^{-7} \geq Ca_s \leq 10^{-5}$ will be utilized. 
% which corresponds to a $Ma << 0.01$ to accommodate the hydrodynamic model utilized.

For this study, the yield stress and viscosity of the bijels will be explored as a function of the initial microstructure under various $Ca_s$. Four templates with different processing history will be utilized to assess the impact of initial microstructure on the obtained rheology. These are, $\bar{B} = 0$, $\bar{B} = 1$, $\bar{B} = 0 \rightarrow \bar{B} = 1$ and $\bar{B} = 1 \rightarrow \bar{B} = 0$. To explain any observed differences in the the yield stress and viscosity, the time evolution of the domain size, average interface angle, and nematic order parameter will be characterized and compared to the observed yield stress and viscosity. Additionally, the presence of shear banding will be visually confirmed.

### 2025-02-12 chapters/lit_review.tex
Changes 1. Initialized repo 2. Added current progress with dissertation. Intro, methods, analysis techniques, literature review and some results present

\section{Emulsion stability and microstructures}

When two partially miscible fluids are mixed together, they will have the tendency to coalesce into two distinct phases as they attempt to minimize the thermodynamic penalty accrued from the formation of an interface. To prevent this coalescence process, conventionally small molecule surfactants are utilized. The most famous example of this class of material is soap which emulsifies dirt into droplets suspended in water through mechanical action. Surfactants function through reducing the surface tension between the droplet, known as the dispersed phase, and the bulk fluid, known as the continuous phase. Surfactants function through reducing the surface tension between dispersed and continuous phases, reducing the energy penalty owed from formation of an interface.

The existence of particle stabilized emulsions has been known for more than a century now, after Pickering and Ramsden independently identified dispersed droplets of oil within a water matrix after vigorous stirring of an oil, water and particle mixture. \textcolor{blue}{10.1098/rspl.1903.0034, http://pubs.rsc.org/en/content/articlelanding/1907/ct/ct9079102001} Unlike surfactants, particles act as emulsion stabilizers through the reduction of contact between dispersed and continuous phases as they adsorb into the interface between phases. The Pieranski model derived from observations of \textcolor{blue}{insert derivation of pieranski model} and is used to determine the adsorption energy of a particle at an interface. It is defined as $G_{ads} = \sigma A_{rm} (1 - \cos{\theta_c})^2$, where $G_{ads}$ is the free energy reduction from a particle adsorption, $\sigma$ is the surface tension between the partially miscible fluids, $\theta_c$ is the contact angle of the particle. The particles can be considered to be irreversibly adsorb even for nanoparticles, and for particles larger than 100nm, the adsorption energy is so great that thermal fluctuations at the interface can be considered to have no effect. \textcolor{blue}{https://doi.org/10.1063/1.3618553}

After their discovery, interest in particle stabilized emulsions became minimal. However, increased interest in them has resurfaced since the 1980s owing to their applications in food science. One such example is fat crystals stabilizing water droplets in oil to create margarine. Particle stabilization has also been of interest owing to their lower toxicity and greater ease of sustainable sourcing.
It has been shown that chemical surfactants can be toxic to aquatic life, acting as a xeno-hormone and interfering with their reproduction. \textcolor{blue}{https://www.sciencedirect.com/science/article/pii/S0304389420302879, https://www.sciencedirect.com/science/article/pii/S014765131530172X} Additionally, particles based cellulose or chitin can be obtained from renewable sources. \textcolor{blue}{https://www.tandfonline.com/doi/full/10.1080/14686996.2017.1401423, 10.1021/acs.biomac.6b00144, 10.1021/acs.langmuir.7b03959} It has also been shown that particle stabilized emulsions are stable for long periods of time. These development have resulted in particle stabilized emulsions seeing a large increase in interest.

The microstructure properties of particle stabilized emulsions were explored in the early 2000s by Lumsdon and Binks among many others. They observed that the radius of emulsion droplets, $R_e \propto \frac{\phi_w}{\phi_p}$, where $\phi_w$ and $\phi_p$ are volume fractions of water and particles respectively. \cite{binks_pickering_2001} They also identified that there were other techniques to modify the microstructure of a Pickering Emulsion such as concentration of fluids and particle wettability. Neutrally wetting particles do not impart a preferential curvature to the interface. When using non-neutrally wetting particles, bridged droplets, capillary aggregates and other non droplet microstructures can be observed. Bijels, are synthesized in a system using equal volume fraction of fluids and neutrally wetting particles, thus facilitating the formation of tortuous, co-continuous domains.

Bijels themselves are synthesized in systems which have roughly equal fluid volume fractions and neutrally wetting particles so as to not impose preferential curvature on the interface. \cite{stratford_colloidal_2005, herzig_bicontinuous_2007, lee_bicontinuous_2010, jansen_bijels_2011, velankar_non-equilibrium_2015} Reeves et al. demonstrated that bijels stabilized with nanoparticles are more stable than those with microparticles due to better mechanical properties and interface coverage. \cite{reeves_particle-size_2015}  Additionally, research by Jansen, Harting, and Hijnen et al. showed that the bijel domain size $L \propto \frac{1}{\phi_p}$ for both rod-like and spherical particles. Although the pre-factor is dependent upon the particle geometry, this feature has been seen with many other particle shapes as well. \cite{hijnen_bijels_2015, madivala_exploiting_2009, gunther_timescales_2014, daware_emulsions_2015, loudet_capillary_2005, cheng_shape-anisotropic_2013}

% While bijels are a relatively new material class, much work has been conducted to elucidate the underlying mechanisms controlling their stability, microstructure and rheology. Many studies focus on how the particle properties play important roles in tuning the properties of bijels. This section will cover a brief overview and summary of literature on the working principle behind particle surfactants, the effect of size and concentration of particles, anisotropic particles in particle stabilized emulsions, microstructure control in various bijel synthesis techniques, stimuli response in bijels and bijel rheology.

\begin{figure}
    \centering
    \includegraphics[scale = 0.5]{figures/literature_review/interfacial_curvature.png}
    \caption{Quadropolar capillary interactions around prolate ellipsoidal particles caused by interfacial deformations around the particle. \cite{loudet_capillary_2005}}
    \label{fig:anisotropic_particle_interface}
\end{figure}

\section{Particle shape anisotropy and synthesis techniques}

In the past decade, methods to synthesize particles which have anisotropic geometry and chemistry have increased in number and scope. Synthesis techniques vary depending on the type of particle shape desired. Ellipsoids can be easily created by mechanical deformation of polymer spheres. Dumbbell shaped particles can be synthesized using microfluidic devices or emulsion templating. Square particles can be generated using crystallization of material. \cite{morgan_understanding_2013} These variety of techniques mean that particle geometry is no longer as constraint when investigating prospective particle stabilizers of bijels. \textcolor{blue}{https://onlinelibrary.wiley.com/doi/10.1002/smll.201600877}

Anisotropic particles have shape dependent properties owing to their induction of multipolar interactions by deforming the interface to ensure the mean curvature is 0,  fulfilling the Young-Laplace equation shown in Figure \ref{fig:anisotropic_particle_interface}. \cite{loudet_capillary_2005, cheng_shape-anisotropic_2013} Using this property has enabled directed assembly and migration through modified capillary forces. \cite{cavallaro_curvature-driven_2011, read_dimerization_2020, sharifi-mood_curvature_2015}

Anisotropic particles have also been shown to exhibit natural liquid crystal like behaviour as shown using Onsager theory.

When stabilizing bijels, ellipsoidal particles offer greater stability than spherical ones due to their larger cross-sectional area to volume ratio, as shown by Günther et al. and Hijnen et al. \cite{gunther_timescales_2014, hijnen_bijels_2015} This results in additional domain coarsening timescales from particle re-orientation and increased mechanical rigidity, enhancing the stability of emulsions with ellipsoidal particles, as evidenced in rheological studies. \cite{gunther_timescales_2014, daware_emulsions_2015, witt_bijel_2013} 
It has also been shown that particle shape changes how and when jamming occurs. Using graphene plate like particles, it was shown that the plate like particles can have their own elasticity to them, affecting when jamming occurs. \textcolor{blue}{https://doi.org/10.1039/C3MH00047H, https://pubs.acs.org/doi/10.1021/la402436w}

Control over the orientation of ellipsoidal particles at interfaces balances interfacial capillary and magnetic field forces. \cite{bresme_orientational_2007, davies_assembling_2014} Theory and simulations indicate a critical field strength above which particle orientation is dominated by the applied field. \cite{bresme_orientational_2007, davies_assembling_2014} Experiments and simulations have found that steric interactions, influenced by orientation and interfacial arrangements significantly influence the free energy of particle assemblies, highlighting the complex interplay between these forces. \cite{morgan_understanding_2013, newton_influence_2014, newton_capillary_2018}

% The adsorption process is affected by the shape of particles used as they pack differently onto the interface \cite{hijnen_bijels_2015, daware_emulsions_2015,carmack_diverse_2017}. It has also been suggested that adsorption dynamics of ellipsoidal particles at liquid interfaces are driven completely by viscous forces even if the timescales of adsorption are driven by particle properties \cite{Coertjens2017}. Some guiding equations to calculate the interfacial area of an ellipsoidal particle are provided \cite{gunther_timescales_2014, Davies2014}.

\section{Bijel synthesis techniques}

Bijels were first synthesized using Thermally Induced Phase Separation (TIPS). \cite{herzig_bicontinuous_2007, lee_bicontinuous_2010, bai_dynamics_2015} First, a small molecule or polymer blend with a critical point, named the casting mixture, is identified and prepared with a composition corresponding to that of the critical point. Next, the casting mixture is blended with particle surfactants while still in a single phase. Once the particles are distributed homogenously in the casting mixture, phase separation is initiated in the casting mixture through changing the temperature such that it is in the two-phase region. Through ensuring the composition is that of the critical point, the casting mixture undergoes spinodal decomposition without any nucleation and growth.

TIPS allows for batch synthesis of bijels in research labs. However to make bijels industrially relevant, a continuous process which also facilitates the synthesis of multiple form factors of bijels for various applications. Solvent Transfer Induced Phase Separation (STrIPS) was proposed as a means to do just this. A casting mixture composed of two fluids, a co-solvent, particles and a surfactant is prepared. The fluids will constitute the bijel while the co-solvent will diffuse out of the bijel to initiate phase separation. The surfactant is present to ensure that the bijel remains stable against Marangoni pressure. The casting mixture if extruded into a bath of non-solvent that is not miscible with the bijel constituents but is miscible with the co-solvent. Diffusion of co-solvent initiates phase separation and synthesis of the bijel. The concentration of surfactant and the flow rate of the casting mixture control the obtained microstructure.

\textcolor{blue}{Description of VIPS}

\textcolor{blue}{Description of homogenization}

\textcolor{blue}{Description of liquid in liquid printing}

% STrIPS, shown in Figure \ref{fig:strips}, and many other fabrication techniques require fine control over the composition of the casting mixture for the technique to function and to control the obtained microstructure. \cite{haase_continuous_2015, amirfattahi_fabrication_2024, sprockel_fabrication_2023} In homogenization, the applied shear of mixing initiates coalescence of droplets in a controlled way, leading to formation of the bijel. \cite{cai_bijels_2017} In both synthesis strategies, the rheology of a proposed casting mixture is therefore essential to understand to explore what other casting mixtures can be utilized in these fabrication techniques. Microstructure control has also been achieved when using TIPS by controlling the concentration of particles at different heights, creating a gradient of pore sizes in the final bijel. \cite{french_bicontinuous_2022} Looking to the current state of stimuli response in bijels,

% \begin{wrapfigure}{r}{7cm}
% \caption{Schematic of a bijel with hard-sphere particles undergoing shear, demonstrating migration and detachment of particles at the interface. \cite{bonaccorso_shear_2020}}
% \label{wrap-fig:bijel_under_shear}
% \includegraphics[width=7cm]{figures/literature_review/bijel_under_shear.jpeg}
% \end{wrapfigure}

\section{Rheological models and shear response of bijels}

\begin{figure}
    \centering
    \includegraphics[scale = 2]{figures/literature_review/bijel_under_shear.jpeg}
    \caption{Schematic of a bijel with hard-sphere particles undergoing shear, demonstrating migration and detachment of particles at the interface. \cite{bonaccorso_shear_2020}}
    \label{fig:bijel_under_shear}
\end{figure}

Studies into bijel rheology have shown the characteristics of a gel when the
storage modulus exceeds the loss modulus. \cite{lee_making_2013, bai_dynamics_2015} Ching and Mohraz also demonstrated that the rheological behaviour of a bijel most closely resembles a 2D colloidal glass that was percolating in 3D space by comparing the linear visco-elasticity of bijels with colloidal gels made with strongly attractive particles. \cite{ching_bijel_2022} Several key feature of glasses are that they posses a yield stress, viscoelastic behaviour and a glass transition point. \cite{pham_yielding_2008, weeks_introduction_2017} Yield stress is the stress imparted when the particle monolayer is irreversibly changed. \cite{pham_yielding_2008} Viscoelasticity is present when the particle monolayer has solid and a liquid like behaviour, depending upon the timescale of the applied stress. \cite{pham_yielding_2008} The glass transition point is characterized when the dynamics of the monolayer drastically slow down. \cite{weeks_introduction_2017} Figure \ref{fig:bijel_under_shear} demonstrates Bonnacorso et al.'s findings that when subjecting a bijel stabilized with hard-sphere like spherical particles to shear, the particles align to the direction of applied shear before detaching from the interface. \cite{bonaccorso_shear_2020} Looking to how particle alignment affects rheology, past work in suspension rheology has shown that colloidal systems with hard-sphere interparticle interactions undergoing constant shear demonstrate particle ordering (shear banding) in the direction of shear at moderate shear rates, causing shear thinning. \cite{vermant_flow-induced_2005, brader_nonlinear_2010}

\textcolor{blue}{https://www.mdpi.com/2311-5521/5/3/150}

\section{Colloidal glasses}

\begin{itemize}
    \item https://pubs.acs.org/doi/10.1021/acsmacrolett.6b00826
    \item Add stuff on dynamic heterogeneity
    \begin{itemize}
        \item https://pubs.rsc.org/en/content/articlelanding/2012/sm/c2sm25267h
    \end{itemize}
    \item Add stuff on particle jamming
    \begin{itemize}
        \item https://journals.aps.org/rmp/pdf/10.1103/RevModPhys.82.2633
    \end{itemize}
    \item Add stuff on cooperatively rearranging regions
        \begin{itemize}
            \item https://doi.org/10.1038/ncomms4829
            \item https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.110.188301
            \item https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.107.065702
        \end{itemize}
    \item Add stuff on reentrant glass phenomena 
    \begin{itemize}
        \item https://doi.org/10.1209/0295-5075/86/58001
    \end{itemize}
\end{itemize}

\section{Stimuli response in particle stabilized emulsions}

Kim et al. found that strong magnetic fields do not significantly alter the microstructure of a bijel stabilized with spherical particles, as the particles orient to the field without affecting interface ordering. \cite{kim_bijels_2010} In contrast, Carmack and Millet demonstrated that polarizable fluids and particles under an electric field show significant microstructural changes, with particles self-assembling into chains and forming cylindrical domains parallel to the applied field, thus modifying the microstructure. \cite{carmack_tuning_2018}

\section{Lattice Boltzmann Method}

The Lattice Boltzmann Method (LBM) is an evolution of preceding lattice gas automata techniques, which is a discretization of the Boltzmann equation of motion for molecules. This means that unlike traditional CFD techniques such as FDM, VOF or level set methods, LBM is a psuedo-molecule method that tracks the evolution of a particle distribution function within grid cells evolved through a discretized Boltzmann equation of motion. Macroscopic variables such as fluid density and velocity are recovered from the particle distributions through appropriate moment integration, and the Navier Stokes equation at the incompressible limit can be obtained through a Chapman-Enskog expansion of the LBM. The LBM has become an attractive tool for meso-scale CFD simulations due to its ease of algorithm implementation, highly parallelizable nature and ease of boundary condition implementation, allowing coupling to other physically relevant systems such as particles with varieties of potentials, external fields and deformable bodies.

The particle distribution function described earlier is advected on a pre-constructed lattice stencil, commonly denoted as DnQm where n and m represent the number of dimensions and directions in the stencil. Common stencils include the D1Q5, D2Q9 and D3Q19 stencil, all of which recover mass and momentum conservation. For energy conservation, a higher order stencil such as D3Q27 is necessary. The D2Q9 and D3Q19 stencils have 8 and 18 populations respectively that include connections to nearest and next nearest neighbour points, in addition to a central rest point.

The LBM is composed of a collision and advection step. In the advection step, the populations at each grid point are propagated to adjacent points in accordance with the chosen stencil. During the collision step, the particle population distribution is relaxed towards an equilibrium with a collision operator, at a specified relaxation rate. The collision operator can have multiple forms based on how many relaxation rates are used although the most common variant is the Single Relaxation Time (SRT) collision operator, more commonly known as the Bhatnagar-Gross-Krook (BGK) collision operator. Owing to its stability in low Mach and Reynolds numbers and simplicity of implementation, the BGK operator is often used in common particle laden flow and soft matter scenarios. \cite{bhatnagar_model_1954} These limitations are present owing to the implicit link between the fluid properties and the relaxation rate necessitating relaxation rates above 0.5, and to ensure fluid incompressibility from an equation that intrinsically simulates a compressible fluid. To get over these limitations, Two Relaxation Time (TRT) and Multiple Relaxation Time (MRT) operators also exist, expanding the possible application of the LBM to visco-elastic flows and implementation of fluctuating hydrodynamics in the LBM. \textcolor{blue}{https://pubs.acs.org/doi/10.1021/acsomega.3c06663, https://iopscience.iop.org/article/10.1209/epl/i2004-10542-5, https://link.aps.org/doi/10.1103/PhysRevE.82.056714}

Five primary techniques to model multicomponent or multiphase systems exist in the LBM literature. A quick review of the Shan-Chen or interparticle potential model  will be provided here from the perspective of a binary mixture. Additionally, the names and descriptions of other techniques will be described as well. The interparticle potential model or Shan-Chen model that adds a non-local density dependent force between two species, effectively modelling non-ideal mixing and recovering the Cahn-Hilliard equation. To alleviate the standard Shan-Chen implementations weaknesses of not being thermodynamically consistent and reducing the existence of spurious velocities,

In addition to the Shan-Chen model, the color gradient model, free energy model, mean field theory model and interface tracking technique all allow for simulations of various types of multiphase and/or multicomponent flows. The color gradient model proposed by Rothman and Keller and implemented by Gunstensen et al relies upon modelling two particle distributions. These represent a binary fluid mixture with the collision step able to recover the hydrodynamics and non-ideal mixing dynamics. The free energy model utilizes phase field theory and constructs a free energy functional to recover interfacial dynamics and effects in a thermodynamically consistent manner. Often, a square gradient free energy is used for simplicity and ease of implementation. The mean field theory

The non-ideal mixing dynamics are recovered during the "recoloring" step, of which the technique proposed by Latva-Kokko and Rothman is more commonly used for soft matter flows.

\textcolor{blue}{https://pure.tue.nl/ws/files/25832941/1404.7523.pdf}

### 2025-02-12 chapters/model_params.tex
Changes 1. Initialized repo 2. Added current progress with dissertation. Intro, methods, analysis techniques, literature review and some results present

\section{Simulation setup}

Critical parameters in this system include fluid density $\rho_f$, dynamic viscosity $\eta$, surface tension $\sigma$, length scale $L$, and applied magnetic field strength $B$. The dynamic viscosity and surface tension is determined by the relaxation time using the BGK collision operator, $\eta = \rho_f c_s^2(\tau - \frac{1}{2})$ and $g_{kk'}$ respectively. Dimensionless numbers derived from the Buckingham Pi theorem are the Reynolds number($Re = \frac{\rho u L}{\eta}$), Weber number ($We = \frac{\rho u^2 L}{\sigma}$), and magnetic bond number ($\Bar{B} = \frac{Bd}{\sigma A}$). Here, $u$ is velocity, $d$ is the particle's dipole moment, and $A$ is the particle's cross-sectional area. The system's velocity and length scale are set as the domain size and coarsening rate. Parameters for the fluid, particle, and non-ideal mixing model used in the simulations are summarized in Table \ref{table:model_params}.

\begin{table}[h!]
\centering
\begin{tabular}{||c c c c c c c c c c c c c||} 
 \hline
 $t_{sim}$ & $L_x$ & $\rho_f$ & $\tau$ & $\eta_f$ & $g_{cc'}$ & $\sigma$ & $\phi_f$ & $\rho_p$ & $\phi_p$ & $V_p$ & $d_c$ & $K_H$ \\ [0.5ex] 
 \hline\hline
 $10^5$ & 256 & 0.7 & 1 & 0.117 & 0.08 & 0.0267 & 0.5 & 1 & 0.15 & 2000$\pi$ & 2/3 & 100\\ [1ex] 
 \hline
\end{tabular}
\caption{Summary of the fluid, particle and model parameters used in the proposed simulations}
\label{table:model_params}
\end{table}

In these simulations, the aspect ratio is defined as $\alpha = \frac{R_{\parallel}}{R_{\perp}}$ with $\alpha = 0.5, 1, 2$ used in these simulations. All particle geometries are volume matched, based on the spherical particle volume. For the spherical particle, the radius was set at $R_{\parallel} = R_{\perp} = 7.9$ which sets the $\alpha = 0.5$ particles to $R_{\parallel} = 5, R_{\perp} = 10$ and the $\alpha = 2$ particles to $R_{\parallel} = 12.6, R_{\perp} = 6.3$. $R_{\parallel}$ and $R_{\perp}$ is the radius of the particle parallel and perpendicular to the symmetry axis of the particle respectively. These values are identical to what was used in Gunther et al, allowing comparisons to the trends they observed. \cite{gunther_timescales_2014} The particles were randomly placed in the system and an equilibration step was performed to push the particles further away from each after placement. Once equilibration is performed, a constant magnetic field is switched on with dimensionless strengths defined using $Bo_m$.

The initial condition of the system when simulating bijels sets the density of each grid to $0.5\rho_f + \varepsilon$ of each fluid where $\varepsilon = 0.0001N(0,1)$. The model parameters trigger phase separation with a sharp interface at the start of the simulation. Periodic boundary conditions are applied on all sides unless the system is undergoing shear. The shear gradient is applied as a velocity in the z direction across the x axis and implemented as a Lees-Edwards (LE) boundary condition in the yz planes. \cite{wagner_leesedwards_2002, lorenz_lees-edwards_2009, yang_capillary_2022} These boundaries move with velocities $u_{LE}$ and $-u_{LE}$ to conserve momentum, with a shear rate $\dot{\gamma} = \frac{2 u_{LE}}{L_x}$. LE boundaries are preferred over walls to avoid affecting viscosity measurements. \cite{wagner_leesedwards_2002, lorenz_lees-edwards_2009, yang_capillary_2022}

Bijel templates have been synthesized using water/2-6-lutidine for further applications. \cite{lee_making_2013} While intrinsically polymerizable bijels have been prepared using oligomeric polymers, STRIPS and VIPS currently utilize small molecule liquids in their bijel casting mixtures. Therefore, an experimentally viable system using water/2-6-lutidine will be discussed in the context of the work presented here. The critical temperature (UCST) for this system is $T_c = 37 ^{\circ}C$, with many systems heated to $T = 40^{\circ}C$ to form the bijel. At this temperature, the fluid properties are $\sigma = 0.22 mN/m$ and $\eta = 2.38 mPas$. \cite{grattoni_lower_1993} Fei et al. developed a method to synthesize polystyrene microparticles ($(R_p = 2 \mu m)$) with tunable geometries by mechanically stretching or compressing them, then coating them with nickel to create magnetic microparticles with a dipole moment of approximately$\approx 3 \cdot 10^{-14} Am^2$. \cite{fei_active_2017, fei_magneto-capillary_2020} Comparing the physical properties to simulation parameters, the simulations correspond to a box side length of $L \approx 64.5 \mu m$ and a timestep duration of $\Delta t \approx 624 ns$.

\section{Model results}

\subsubsection{Surface tension}

In experiments, Wilhelmy and ring tensionometry are used to measure the surface tension from the force needed to break through the interface. Pendant drop tensionometry is also used by measuring the pressure required to maintain a droplet of analyte at a various sizes and utilizing the Young-Laplace equation to calculate the surface tension of the system. \textcolor{blue}{https://pubs.acs.org/doi/10.1021/la402436w, https://doi.org/10.1016/j.jcis.2015.05.012} Upon extrusion of a droplet from a reservoir, the size of a droplet is determined by the balance between cohesive forces between bubble molecules and geometrical forces that attempt to reduce the curvature of a system by increasing its size. For spherical droplets, the equation simplifies to $\Delta P = \frac{2 \sigma}{R_d}$ where $\Delta P$ is the difference in scalar pressure between the center of the droplet and the ambient pressure, $\sigma$ is the surface tension of the interface and $R_d$ is the radius of the droplet.

\begin{figure}[h]
    \centering
    \includegraphics[scale = 0.5]{figures/model_validation/surface_tension.png}
    \caption{Plot of the surface tension of the multicomponent model in this work calculated using the Young-Laplace equation.}
    \label{fig:young_laplace_valid}
\end{figure}

Using the fluid and non-ideal mixing parameters defined in Table \ref{table:model_params}, a single water in oil droplet, termed blue in red, was initialized in the center system and run till the droplet radii reached steady state. This process was repeated for various droplet diameters, specified between $40$ and $85 \%$ of the system size at $5\%$ increments. The system had a box length of $L = 64$ and was run for $50000$ timesteps with periodic boundary conditions on all sides. Data was dumped every 10000 timesteps with only the last timestep used to calculate the values shown. Due to the diffuse interface present in this method, the density profiles were verified to be at steady state at the end of the simulation before further analysis was performed. \cite{frijters_effects_2012} Past work also showed that the pressures remained constant after 5 lattice units away from the interface. \cite{frijters_effects_2012}

The pressure difference was calculated using the difference in scalar pressure between the center of the droplet and one of the corners of the box. Two techniques exist to calculate the radius of the droplet. The first directly measures the distance between opposite points of the droplet as measured from the density profile at opposite points of the droplet, and the second is based upon the total mass and density of the fluid making up the droplet. The second method offers greater accuracy by avoiding discretization errors that may exist in the first method, and also allows for the correction of particle volume at the interface if the system contained them. First, a local effective mass density $\rho^b_{eff} = \rho^{b}_{d} - \rho^{b}_{m}$ is found by calculating the difference in density between the blue fluid in the droplet and in the matrix. Next, the droplet mass is calculated as $M_d = \sum_{\mathbf{x}}{\rho_{eff}^{b}}$. The radius of the droplet can then be calculated from the mass and density of the droplets as $R_d = \sqrt[3]{\frac{3}{4\pi} \frac{M_d}{\rho^b_d - \rho^b_m}}$. To linearize the plot, the $\Delta P$ was plotted against $\frac{2}{R_d}$ with $\sigma$ being the slope of the fit.

Figure \ref{fig:young_laplace_valid} shows the results of the fit conducted of the Young-Laplace equation demonstrating that under these fluid and mixing parameters, the surface tension is $\sigma = 0.0279$. The fit was performed using \texttt{scipy.optimize.curve\_fit} with the fit function defined as $y = mx$. Droplets with starting sizes $2R_d < 70\%$ of the initial system size disappeared. This occurred due to the initial condition of each fluid set to not contain the other fluid species, meaning once the simulation was initiated diffusion of mass from the droplet to the bulk occurred, causing disappearance of the droplet until the thermodynamically optimal composition was reached. From the fit calculated in Figure \ref{fig:young_laplace_valid}, the fit is linear as long as the initial droplet size is sufficiently large. Alternatively, the composition of the system can be set to near equilibrium in order to allow access to smaller droplet sizes.

\subsubsection{Contact angle}

Contact angle plays a role in particle stabilized emulsions by controlling the free energy reduction that the interface has in addition to the imparting of preferential curvature. LB3D allows for modification of the contact angle of a particle through the addition of a shell of blue or red fluid to the surface of the Ladd particle termed as the particle color $(\Delta \rho)$. \cite{jansen_bijels_2011, gunther_lattice_2013} To ensure that the correct settings are used in these simulations, in addition to gaining understanding into how to change parameters if the need arises, the contact angle as a function of the particle color was calculated.

Experimentally and computationally, the contact angle can be calculated through direct measurement of the angle of a droplet on a substrate. A droplet that preferentially wets a substrate has a lower contact angle relative to that substrate material, physically manifesting as the droplet spreading on the substrate. At a liquid interface, the particle will prefer to be in the particle it wets more. Thus for a spherical particle, the contact angle can be calculated as $\theta_c = \arccos{\frac{h_p - h_i}{R_p}}$ where $h_p - h_i$ defines the distance between the center of the particle after reaching its steady state position and the interface and $R_p$ is the radius of the spherical particle. \cite{gunther_lattice_2013, davies_interface_2014} This has been extended to ellipsoidal particles through assuming that the particle will have its largest cross sectional area flat on the interface and using the radius that is perpendicular to the interface to calculate the contact angle, defined as $\theta_c = \arccos{\frac{h_p - h_i}{R_{\parallel}}}$ and $\theta_c = \arccos{\frac{h_p - h_i}{R_{\perp}}}$ if $\alpha < 1$ and $\alpha \geq 1$ respectively.

The simulation was setup in a box of size $32\cdot32\cdot64$ with an interface lying at $z = 32$, and a single particle placed at the center of the box with periodic boundary conditions on all sides. Fluid and non-ideal mixing properties were the same as those listed in table \ref{table:model_params}. The particle was then placed at the center of the simulation box and run for $30000$ timesteps with data read every 500 timesteps. The contact angles shown are results from triplicate runs, and averages of the final 10 data points.

\begin{figure}[h]
    \centering
    \includegraphics[scale = 0.5]{figures/model_validation/contact_angle_compare.png}
    \caption{Contact angle with respect to the oil phase, $(\theta_c^{oil})$ of the particles plotted against the control parameter in LB3D}
    \label{fig:contact_angle_valid}
\end{figure}

Figure \ref{fig:contact_angle_valid} demonstrates the contact angles of the three particle geometries analyzed, confirming that $\Delta \rho = 0$ will result in neutrally wetting particles for all geometries. Oblate and spherical particles have usable particle colors between $-0.10 \leq \Delta \rho \leq 0.10$ while for prolate ellipsoids this value is $-0.05 \leq \Delta \rho \leq 0.05$. The slope of ellipsoidal particles appears to be lower which may arise from a larger interfacial adsorption energy, making it more difficult for surface energy changes to move particles out of the interface. At $\Delta \rho$ values further from 0, it was observed that the prolate particles tended to leave the interface rather than stay at a slightly off center equilibrium position.

### 2025-02-12 chapters/paper1.tex
Changes 1. Initialized repo 2. Added current progress with dissertation. Intro, methods, analysis techniques, literature review and some results present

Enter some blurb here for a short introduction to content

\subsubsection{Model parameters and simulation setup}\label{sec:parameters}

The dynamics of the binary fluid mixture is governed by inertial,
viscous, and surface tension forces. The relative magnitudes of these
forces at a characteristic length scale \(L\) and characteristic
velocity \(U\) are captured by the capillary number $\mathrm{Ca}=\frac{\eta U}{\sigma}$ and the Weber number
\(\mathrm{We}=\frac{\rho U^2 L}{\sigma}\). Here we are primarily interested in spinodal decomposition of the mixture, where we analyze the dynamics after the initial formation of the interfaces and neglect residual diffusion. Hence the Peclet number \(\mathrm{Pe}=\frac{UL}{\Gamma}\) is of lesser importance and we do not consider it when choosing our simulation parameters.

The equations of motion of our model comprise the relevant materials
properties: the density \(\rho\), viscosity \(\nu\), and surface tension \(\sigma\) of the binary fluid, and the mass \(m_p\), size \(R_p\) and aspect ratio \(\alpha\), and dipole moment \(m\) of the particles. In addition, we can control the particle volume fraction \(\phi_p\) and
magnetic field strength \(B\). These nine quantities involve four unit
dimensions (mass, length, time, and charge), hence we can use five
dimensionless variables to specify the parameters of the system. These
are the particle aspect ratio $\alpha$, particle volume fraction
\(\phi_p\), particle vs.~fluid density ratio
$\xi = \frac{3m_p}{4\pi \rho V_p}$, nominal Weber number $\mathrm{We} = \frac{\rho \sigma V_p^{1/3}}{\eta^2}$, and magnetic Bond
number \(\bar{B} = m B/(\sigma A_p)\), where
\(V_p=(4/3)\pi R_\parallel^3/\alpha^2\) is the particle volume and
\(A_p=\max\left( \pi R_\parallel^2/\alpha, \pi R_\parallel^2/\alpha^2 \right)\)
the area of the larger cross-section of the ellpsoidal particles.

For our simulations, we choose units \(\Delta x\), \(\Delta t\),
\(\Delta m\), and \(\Delta i\) such that \(V_p=\hat{V}_p(\Delta x)^3\),
\(\nu=\hat{\nu}(\Delta x)^2/\Delta t\),
\(\sigma=\hat{\sigma}\Delta m/(\Delta t)^2\), and
\(m=\hat{m}\Delta i(\Delta x)^2\). We used \(V_p=2000\pi/3\),
\(\hat{\nu}=1/6\), \(\hat{\sigma}=0.0267\), \(\hat{m}=1\), and a density
ratio \(\xi=1/\hat{\rho}\). For reference, the values of the model
parameters are listed in table \ref{tab:parameters}. The values of
\(\alpha\) and \(\bar{B}\) are variable and are reported
with the results in section \ref{sec:results}.

%\new{We note that the dynamics of the simulations are determined by
%the dimensionless numbers, and the actual unit values $\Delta x$,
%$\Delta t$, $\Delta m$, and $\Delta j$ are arbitrary and only become
%meaningful when a connection to an experimental system is made (see
%below).}

\begin{table}
\centering
\caption{Summary of the parameters of the numerical model and the values used in the simulations}
\label{tab:parameters}
\begin{tabular}{|c|r|}
\hline
Parameter & Value \\
\hline
$L_V/\Delta x$ & 256 \\
$\rho \cdot (\Delta x)^3/\Delta m$ & 0.7 \\
$\nu \cdot \Delta t/(\Delta x)^2$ & 1/6 \\
$\sigma \cdot (\Delta t)^2/\Delta m$ & 0.0267 \\
$\tau/\Delta t$ & 1 \\
$g \cdot \Delta m(\Delta t)^2/(\Delta x)^5$ & 0.08 \\
$\phi_f$ & 0.5 \\
$\phi_p$ & 0.15 \\
$n_p$ & 1200 \\
$\rho_p \cdot (\Delta x)^3/\Delta m$ & 1 \\
$V_p/(\Delta x)^3$ & $2000\pi/3$ \\
$m/(\Delta i(\Delta x)^2)$ & 1 \\
$d_c/\Delta x$ & 2/3 \\
$K_H\cdot (\Delta x)^{1/2}(\Delta t)^2/\Delta m$ & 100 \\
\hline
\end{tabular}
\end{table}

We performed simulations of a binary fluid using the software package
LB3D \cite{schmieschek_lb3d_2017} that implements the lattice Boltzmann method described in section
\ref{sec:methods}. The multicomponent
lattice Boltzmann model is solved in a cubic box of size
\(L_V=256\Delta x\) with periodic boundary conditions. The simulation
box is filled with equal volume fractions \(\phi_f=0.5\) of two fluids,
initially homogeneously mixed with a density
\(\rho=0.7\Delta m/(\Delta x)^3\). The BGK relaxation time is set to
\(\tau=\Delta t\) and the Shan-Chen interaction strength is set to
\(g_{kk^\star}=0.08(\Delta x)^2/(\Delta m(\Delta t)^2)\). We performed
preliminary simulations of a spherical droplet with these parameters and
fitted the pressure difference inside and outside the droplet to the
Young-Laplace law, which yielded a surface tension
\(\sigma=0.0267\Delta m/(\Delta t)^2\). To study the influence of
anisotropic particle shapes on the bijel formation, we performed
simulations for particles with three different aspect ratios:
\(\alpha=1\) for spherical particles, \(\alpha=2\) for prolate
ellipsoids, and \(\alpha=1/2\) for oblate ellipsoids. To match the
particle volume fraction \(\phi_p\) between the different particle
shapes, we kept the volume of the particles fixed and used the same
number of particles for each aspect ratio. The radius along the symmetry
axis of the particles was calculated from
\(V_p=(4/3)\pi R_\parallel^3/\alpha^2\), yielding
\(R_\parallel=7.9\Delta x\) for spheres, \(R_\parallel=12.6\Delta x\)
for prolate ellipsoids, and \(R_\parallel=5\Delta x\) for oblate
ellipsoids, respectively. Particles were added to the fluid by placing
them randomly inside the box. The lubrication cutoff distance was set to
the value \(d_c=(2/3)\Delta x\) recommended by Ladd
\cite{ladd_lattice-boltzmann_2001}, and the strength of the Hertz
potential was set to \(K_H=100\Delta m/((\Delta x)^{1/2}(\Delta t)^2)\).
We first equilibrated the particle positions and orientations by
evolving only the equations of motion of the particles, while the fluid
remained in its initial configuration, until the minimum particle
distance exceeded \(1.2\cdot\max(R_\parallel,R_\parallel/\alpha)\).
After the equilibration, the magnetic flux density
\(\vec{B}=B\hat{\vec{z}}\) was switched on and the full system was
evolved for \(10^5\) timesteps. In the course of the simulation, the binary mixture undergoes spinodal decomposition. The particles adsorb at the coarsening interface and eventually become jammed, resulting in the bicontinuous phase morphology of the bijel.

It is worth discussing briefly the possible realization of our model in
experiments. A common choice for bijel formation in binary liquids is a
mixture of water and lutidine
\cite{clegg_emulsification_2007,herzig_bicontinuous_2007}. The surface
tension between the phases of a water-lutidine system at
\(40^\circ\mathrm{C}\) is around \(\sigma=0.22\ \mathrm{mN/m}\) and the
dynamic viscosity of the lutidine-rich phase is around
\(\eta=2.38\ \mathrm{mPa\,s}\) \cite{grattoni_lower_1993}. Ellipsoidal
particles with various aspect ratios can be formed by mechanically
stretching spherical particles \cite{trevenen_gradient_2021}. Such
particles can be magnetically functionalized by e-beam deposition of a
Nickel layer. Fei et
al.~\cite{fei_magneto-capillary_2018,fei_magneto-capillary_2020}
fabricated coated \(4\ \mathrm{\mu m}\) polystyrene particles with a
permanent magnetic dipole moment of
\(m\approx3\cdot10^{-14}\ \mathrm{Am^2}\). It was shown that the dipole moment is oriented in the direction parallel to the coated interface \cite{yan_linking_2012,yan_rotating_2014}, i.e., it can be aligned with the axis of ellipsoidal particles.
For the given surface tension, the capillary torque on a particle adsorbed at an interface is approximately
$8.8\cdot10^{-16}\ \mathrm{Nm}$. We thus can estimate that a magnetic
flux density of \(30\ \mathrm{mT}\) is able to exert a magnetic torque
that exceeds the capillary torque.
We note that under these conditions,
the dipole-dipole interaction is on the order of
\(10^{-16}\ \mathrm{J}\) and an order of magnitude smaller than the
particle-interface interaction which is of order
\(10^{-15}\ \mathrm{J}\). %Unlike previous works
%\cite{xie_direct_2017,xie_controllable_2021}, we therefore cannot
%neglect the magnetic dipole-dipole interactions between particles.For these bijel properties and the parameters given in
table \ref{tab:parameters}, the spatial resolution of our
simulations is $\Delta x\approx252\ \mathrm{nm}$, and the time step
is $\Delta t=624\ \mathrm{ns}$. This corresponds to a system side length of $L_V \approx 64.5\ \mathrm{\mu m}$ and a runtime of
$T \approx 62.4\ \mathrm{ms}$.

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{figures/results/paper1/microstructure_viz.png}
\caption{Snapshots of emulsion gels stabilized by prolate ellipsoids after $t=5\cdot10^3$ timesteps (left) and after $10^5$ timesteps (right). The top row shows the structure forming without a magnetic field. The bottom row shows the structure forming in an applied magnetic field of reduced strength $\bar{B}=1.0$. The snapshots are colored according to the order parameter $\phi$.}
\label{fig:microstructure_viz}
\end{figure}

\section{Results}\label{sec:results}

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{figures/results/paper1/structure_factor.png}
\caption{Scaling plot of the dynamic structure factor $S(k,t)$ for different particle shapes $\alpha$ and at different magnetic field strength $\bar{B}$. The structure factor is plotted at four different timesteps for each case. The good data collapse shows that the bijel formation is driven by spinodal decomposition. The decay to the right of the peak is reasonably well described by Porod's law $S(k)\sim k^{-4}$.}
\label{fig:structure_factor}
\end{figure*}

Bijels can be used as emulsion templates for porous materials with
applications including drug delivery, water desalination, and battery
electrodes
\cite{vanoli_bijels_2022, chen_pore-scale_2022, lu_controllable_2020, garcia_scalable_2019}.
The transport properties of porous materials depend on the porosity and
tortuosity of the void space and can be linked to the phase-separated
morphology of the bijel template. Therefore, we study the domain size
and tortuosity of the phase morphology of bijels stabilized by
anisotropic particles. In particular, we investigate the effect of
magnetic particles on the microstructure of bijels that are formed in
external magnetic fields. We simulated bijels with a particle volume
fraction of \(\phi_p=0.15\) and varied the magnetic flux density such
that the Bond numbers varies in the range \(0\le\bar{B}\le1\).
In this work, we use a fixed particle volume fraction and focus on the dependence of the bijel structure on the magnetic field. Bijels with varying particle loading and surface tension and have been studied elsewhere in the literature, e.g., by Hijnen et al.\cite{hijnen_bijels_2015} and Jansen and Harting\cite{jansen_bijels_2011}.

Figure \ref{fig:microstructure_viz} shows snapshots of the bijel
microstructure observed at different times with and without an external
magnetic field. The figure illustrates how anisotropic particles align
with the direction of the magnetic field. As the particles reorient,
they can deform the interface which thus responds by rearrangements
including reorientation and domain coalescence or breakup. This results
in apparently larger domain sizes for bijel formation in magnetic
fields. The quantitative effect on the bijel morphology, and domain size
in particular, is analyzed in the following sections.

\subsection{Structure factor and domain size of magnetically responsive bijels}

In LB simulations of spinodal decomposition
\cite{kendon_3d_1999,kendon_inertial_2001}, a characteristic length
scale can be obtained from the structure factor
%
\begin{equation}
S(\vec{k},t) = \tilde{\phi}(\vec{k},t)\tilde{\phi}(-\vec{k},t) .
\end{equation}
%
where \(\tilde{\phi}(\vec{k},t)\) is the Fourier
transform of the order parameter fluctuations
\(\phi(\vec{x},t)-\left\langle\phi\right\rangle\). A common measure of
domain size uses the spherically averaged structure factor
%
\begin{equation}
S(k,t) = \frac{1}{n_k} \sum_{k-\frac{\Delta}{2}<k<k+\frac{\Delta}{2}} \tilde{\phi}(\vec{k},t)\tilde{\phi}(-\vec{k},t) ,
\end{equation}
%
where \(k=|\vec{k}|\) denotes the modulus of \(\vec{k}\)
and \(n_k\) is the number of lattice sites in a shell of radius \(k\)
and thickness \(\Delta=2\pi/L_V\). The average domain size can then be
defined in terms of the \(n\)-th moment of the structure factor
\cite{laradji_molecular_1996}

\begin{equation}
L_n(t) = 2 \pi (\left( \frac{\sum_k S(k, t)}{\sum_k k^n S(k, t)} )\right)^{\frac{1}{n}}
\end{equation}

It is worth noting that this definition of average domain
size does not necessarily yield values that coincide with the typical
domain size observed visually in snapshots such as those shown in
Fig.~\ref{fig:microstructure_viz}. However, in a dynamic
scaling regime, different measures of domain size are expected to differ
only by a constant ratio. We found that the commonly used measure
\(L_1(t)\) tends to overestimate the observed domain size. Numerically,
the calculation of the spherically averaged structure factor is subject
to poor statistics in the low \(k\)-shells, where the average
\(|\vec{k}|\) of the lattice sites differs from the nominal shell
radius. Additionally, the measurement of \(L(t)\) in simulations with
periodic boundary conditions is subject to finite size effects. More
importantly, in suspensions of anisotropic particles, we cannot expect
that the structure factor is isotropic. Therefore, we also used the 3D
structure factor to calculate a lateral domain size in each Cartesian
direction from the second moments
\cite{jansen_bijels_2011,gunther_timescales_2014}
%
\begin{equation}
L_\beta(t)=2\pi\sqrt{\frac{\sum_{\vec{k}}S(\vec{k},t)}{\sum_{\vec{k}}k_\beta^2 S(\vec{k},t)}} .
\end{equation}
%
This allows us to compute a domain size parallel
(\(L_\parallel=L_z\)) and perpendicular (\(L_\perp=(L_x+L_y)/2\)) to the
direction of \(\vec{B}\) separately. The average domain size \(L_d(t)\)
is computed as \(L_d(t)=\sum_\beta L_\beta(t) / 3\).
%
\begin{equation}
L_d(t)=2\pi\sqrt{\frac{\sum_{\vec{k}}S(\vec{k},t)}{\sum_{\vec{k}}\sum_\beta k_\beta^2 S(\vec{k},t)}} .
\end{equation}
%
%In case the structure factor is isotropic
%\(S(\vec{k},t)=S(k,t)\), this is equivalent to the ratio of the fourth
%and second moments of the spherically averaged structure factor.
%
%\begin{equation}
%\begin{split}
%  L_d(t) &%= \left[\sum_{\beta}\left(\frac{1}{L_\beta(t)}\right)^2\right]^{-\frac{1}{2}}
%  = 2\pi \sqrt{\frac{\sum_{\vec{k}}S(\vec{k},t)}{\sum_{\vec{k}}\sum_\beta k_\beta^2 S(\vec{k},t)}} \\
%L_\perp(t) &%= \left[\left(\frac{1}{L_x(t)}\right)^2+\left(\frac{1}{L_y(t)}\right)^2\right]^{-\frac{1}{2}}
%= 2\pi \sqrt{\frac{\sum_{\vec{k}}S(\vec{k},t)}{\sum_{\vec{k}} \left(k_x^2+k_y^2\right) S(\vec{k},t)}} \\
%L_\parallel(t) &= 2\pi \sqrt{\frac{\sum_{\vec{k}} S(\vec{k},t)}{\sum_{\vec{k}} k_z^2 S(\vec{k},t)}}
%\end{split}
%\end{equation}

Before calculating the structure factor \(S(\vec{k},t)\), we
first filled the lattice sites covered by particles with the average
density at the surrounding lattice sites. We employed an iterative
procedure that fills the particles layer by layer, starting at the
surface layer and using equation \eqref{eq:fill_particles} to
approximate the density at solid nodes that have a least one neighboring
fluid node. This is repeated until all solid nodes have been filled with
fluid. The order parameter \(\phi(\vec{x},t)\) was then calculated for
the filled density fields \(\rho_k(\vec{x},t)\). Filling the lattice
sites covered by particles is crucial to avoid spurious oscillations of
the structure factor at length scales corresponding to the particle
size.

Figure \ref{fig:structure_factor} shows the scaling of the dynamic
structure factor \(S(k,t)\). The data collapse is good, albeit
deviations from dynamic scaling are present at smaller length scales.
The decay to the right of the maximum is reasonably well described by
Porod's law \(S(k)\sim k^{-4}\) indicating scattering off a nearly flat
interface. These results are in line with the scaling results by Kendon
et al.~\cite{kendon_3d_1999, kendon_inertial_2001} for spinodal
decomposition of binary fluids, which suggests that the formation of
bijels is primarily driven by the separation dynamics of the fluids. The
effect of the suspended particles only comes into play once larger
domains have formed and the coarsening interface reduces the accessible
area to the point where the particles start interacting. The onset of
particle interactions and subsequent jamming leads to a fairly sudden
slow-down of domain growth, as can be observed in the time evolution of
the domain size shown in Figure \ref{fig:domain_size}.

The domain size \(L_1\) obtained from the spherically averaged structure
factor initially shows a power law behavior very close to
\(L_1\sim t^{2/3}\). A nonlinear curve fit of the function
\(b(t-t_0)^a\) to the interval \(t\in[0,\ 3\cdot10^5\Delta x]\) yields
the exponents \(a=0.6448\) for spherical particles, \(a=0.6083\) for
oblate particles with aspect ratio \(\alpha=0.5\), and \(a=0.652\) for
prolate ellipsoids with aspect ratio \(\alpha=2\). These values are in
good agreement with the exponent \(a=2/3\) that is expected in an
inertial scaling regime, where the characteristic velocity \(U=dL/dt\)
scales with the characteristic length scale
\(U\sim \sqrt{\sigma/(\rho L)}\), leading to \(L \sim t^{2/3}\). After
around 30,000 to 40,000 time steps, the domain growth starts slowing
down and approaches a plateau at \(L_1\approx 200\Delta x\) for
spherical particles, \(L_1\approx 180\Delta x\) for the prolate
particles, and \(L_1\approx 170\Delta x\) for the oblate particles.
Interestingly, the alternative domain size measure \(L_d\) obtained from
the second moments of the 3D structure factor does not show the same
power law behavior. The rate of increase of \(L_d\) is substantially
smaller than that of \(L_1\), with a fitted exponent in the range of
0.12 to 0.20. The increase of \(L_d\) levels of earlier and reaches a
plateau around \(L_d\approx 70\Delta x\) for all three particle aspect
ratios. While dynamic scaling allows different measures of the
characteristic length scale to vary by a prefactor, the deviation from
the expected power law of both viscous and inertial scaling indicates
that the second moment of the 3D structure factor does not yield a
proper characteristic length scale. %, contrary to what has been assumed in
%previous works \cite{jansen_bijels_2011, gunther_timescales_2014}.
If one interprets the moments of the structure factor as moments of a
probability distribution, then the second moment of the 3D structure
factor is equivalent to the ratio of the fourth and second moments of
the spherically averaged structure factor (due to the factor \(k^2\) in
the volume integral). Hence \(L_d\) is perhaps better interpreted as
describing the shape of the structure factor (similar to kurtosis, but
not exactly the same) rather than a characteristic length scale.
Nevertheless, the second moments \(L_\beta\) provide separate measures
for the three Cartesian directions and can thus reveal anisotropy of the
domain morphology.

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{figures/results/paper1/domain_size.png}
\caption{Time dependence of the average domain size of the bijel for different particles shapes $\alpha$ and at different magnetic field strength $\bar{B}$. $L_1$ denotes the domain size obtained from the first moment of the spherical average structure factor, and $L_d$ denotes the domain size obtained from the second moment of the 3D structure factor. The increase roughly follows a $\sim t^{2/3}$ scaling law indicative of the inertial regime of spinodal decomposition.}
\label{fig:domain_size}
\end{figure*}

\subsection{Effect of magnetic field on bijel formation}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{figures/results/paper1/D2a-vs-B_ss.png}
\caption{Dependence of the average domain size on the magnetic field strength $\bar{B}$. The left plot shows the average domain size $L_1$ obtained from the spherically averaged structure factor. The right plot shows the parallel and perpendicular domain size obtained from the respective second moments of the 3D structure factor. Errorbars indicate the standard deviation taken over three independent simulation runs. For anisotropic particles, the directional domain size becomes more anisotropic with increasing field strength.}
\label{fig:D2a_B}
\end{figure}

At first glance, the time-dependence of the domain size in Fig.
\ref{fig:domain_size} suggests that the domain size is not strongly
affected by the external magnetic field. In Fig.\ref{fig:D2a_B}a) we
plotted the domain size measure \(L_d\) normalized by \(R\), the larger
of the two radii of the ellipsoidal particles. The data points represent
the domain size measured at the final time step and averaged over three
independent simulation runs with the same parameters. The normalization
with the particle radius makes it apparent that the ellipsoidal
particles reduce the domain size of bijels. This observation is in line
with observations by Günther et al.~\cite{gunther_timescales_2014} and
indicates that -- relative to their volume -- ellipsoidal particles
stabilize a larger interface area than spherical particles. This is due
to the larger cross-sectional area of ellipsoidal particles at the same
volume. Furthermore, steric constraints prevent anisotropic particles to
pack less densely in the interface than spherical particles, as we will
discuss in more detail below.

The magnetic field does have an effect on the directional
domain size as shown in Figure \ref{fig:D2a_B} where we plotted the
domain size in the direction parallel and perpendicular to \(\vec{B}\)
separately. We find that for prolate particles, the domain size in the
parallel direction increases with the field strength up to approximately
three particle radii for the largest field, while the perpendicular
domain size stays constant. This trend is reversed for oblate particles
for which the domain size in the parallel direction decreases slightly
with field strength while the perpendicular domain size increases by
approximately four particle radii. Without a field, prolate
particles lead to smaller domain size than both spherical and oblate
particles, whereas they increase the domain size when the bijel forms under the
influence of a magnetic field. The anisotropy is due to the alignment of
ellipsoidal particles which leads to a closer packing within the
interface akin to nematic ordering. The difference between oblate and
prolate particles is caused by the orientation of the magnetic dipole
moment \(\vec{m}\) along the symmetry axis of the particles. In our
model, \(\vec{m}\) is aligned with the larger axis of prolate
ellipsoids, whereas it is aligned with the smaller axis of oblate
ellipsoids. Hence \(\vec{m}\) lies in the plane of the larger
cross-section of prolate particles while \(\vec{m}\) is perpendicular to
the larger cross-section of oblate particles. We thus expect that
alignment of the particles with the magnetic field \(\vec{B}\)
facilitates closer packing perpendicular to the field for prolate
particles, and parallel to the field for oblate particles. The
increase/decrease of domain size levels off at intermediate field
strength and further increases of the field have no additional effect.

\subsection{Tortuosity}

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{figures/results/paper1/tortuosity_compare.png}
\caption{Dependence of the tortuosity on the magnetic field strength $\bar{B}$ for different particle shapes $\alpha$. Different components of the tortuosity tensor show the anisotropy for oblate and prolate particles.}
\label{fig:tau_B}
\end{figure*}

The anisotropy of domain size suggests that the magnetic field
influences the bijel morphology at the microscale. To investigate
whether these structural changes have an effect on macroscopic
transport properties, we also characterized the tortuosity of the
bijels. Various definitions of tortuosity have been proposed in the
literature \cite{dasilva_tortuosity_2022}, including geometric,
diffusional, and hydraulic tortuosity. Here we use the diffusional
tortuosity $\tau= \frac{\epsilon D}{D_{\text{eff}}}$, i.e., the ratio of the 
effective diffusivity $D_{\text{eff}}$ and the intrinsic diffusivity
$D$. Porous structures were generated from the order parameter field
at the last time step of the simulations by binarizing the raw order
parameter data using a threshold of zero. We masked the largest
connected component representing the percolating domain and then used
the Python package \texttt{taufactor}\cite{cooper_taufactor_2016} to
calculate the tortuosity in the three Cartesian coordinate
directions. \texttt{taufactor} determines the tortuosity by comparison
of steady-state diffusive flow through a porous medium with the bulk
diffusive flow in a control volume of the same size, molecular
diffusivity, and driving force \cite{cooper_taufactor_2016}. We used
the \texttt{PeriodicSolver} to employ periodic boundary conditions.

Figure \ref{fig:tau_B} shows the results for the tortuosity as a
function of the applied magnetic flux for the three particle aspect
ratios. In the absence a magnetic field, the three aspect ratios lead to
a similar tortuosity around $\tau\approx 1.5$, slightly larger than
the tortuosity predicted by the Bruggeman relation
\(\tau=\epsilon^{-0.5}=1.41\) for equal volume fractions
\(\epsilon=0.5\) of the phases
\cite{bruggeman1935tortuosity, tjaden_origin_2016}. The observed
tortuosity is consistent with simulations of gyroid structures by Luo et
al., who found diffusive tortuosities in the range from 1.48 to 1.73
\cite{luo_macroscopic_2020}. Figure \ref{fig:tau_B} shows that in an
applied magnetic field, the tortuosity of bijels stabilized by
anisotropic particles (\(\alpha\neq1\)) becomes anisotropic as well.
Oblate particles (\(\alpha=0.5\)) lead to an increase of the tortuosity
\(\tau_\parallel\) in the direction of the magnetic field while the
tortuosity in the direction perpendicular to the magnetic field remains
around \(\tau_\parallel\approx1.5\). Conversely, prolate particles
(\(\alpha=2\)) lead to an increase of the tortuosity in the direction
perpendicular to the magnetic field, while the tortuosity in the
parallel direction slightly decreases with increasing field strength. In
both cases, the changes in tortuosity are consistent with the
anisotropic domain size and the alignment of particles with the magnetic
field. For prolate particles, the longer axis is aligned with the
magnetic moment and induces larger domain size and lower tortuosity in
this direction. The results show that the magnetic field has a
noticeable effect on the tortuosity of the bijel. We observe that the
largest change of tortuosity is measured at intermediate field strength
\(\bar{B}=0.5\). This suggests that the competition of interfacial and
magnetic forces and the resulting alignment of particles and liquid
domains induces morphological changes that are more complex than a
monotonic increase or decrease. We therefore turn to investigate the
microstructural changes within the bijel morphology in more detail.

\subsection{Kinetics of bijel formation in magnetic fields}

To shed light on the mechanisms involved in the coarsening dynamics,
we now turn to the kinetics of bijel formation in more detail. The
coarsening dynamics can be characterized by a coarsening speed. Here,
we use the finite difference of the directional domain size to
calculate the components of the coarsening velocity
%
\begin{equation}
u_{L_\beta}(t) = \frac{L_\beta(t+\Delta t_s)-L_\beta(t-\Delta t_s)}{2\Delta t_s} ,
\end{equation}
%
where \(\Delta t_s\) is the time between simulation
snapshots, and $\beta$ denotes either the direction parallel or perpendicular to the magnetic field.

\begin{figure*}
\includegraphics[width=\textwidth]{figures/results/paper1/coarsening_vel.png}
\caption{Time-dependence of the coarsening velocity $u_L$ for different particles shapes $\alpha$  and at different magnetic field strength $\bar{B}$. The different components of the coarsening velocity show that the jamming time is different in the direction parallel and perpendicular to the magnetic field.}
\label{fig:coarsening_velocity}
\end{figure*}

Figure \ref{fig:coarsening_velocity} shows the coarsening speed in the directions parallel and perpendicular to the applied magnetic field. The data confirms that for spherical particles, domain coarsening remains isotropic. We observe a higher coarsening speed initially which slows at later times when the particles begin to jam. This indicates that the
coarsening is subject to different time scales, as reported previously
by Harting and co-workers \cite{gunther_timescales_2014}. Reeves et
al.~\cite{reeves_particle-size_2015} have pointed out that bijel
formation hinges on the jamming time in relation to the disruption time, i.e., the time scale at which domain pinch-off events can cause bijel break-up through depercolation. In our simulations, however, we have not observed disruption of bijel formation; stable bijels form for all parameters consistent with simulations by Stratford et
al.~\cite{stratford_colloidal_2005} and Jansen et al.~\cite{jansen_bijels_2011}.

For ellipsoidal particles, our data clearly shows that an\-isotropic
domain coarsening arises in magnetic fields.  For oblate particles
(\(\alpha=0.5\)), the coarsening speed in the direction perpendicular
to the field increases with increasing magnetic field strength.
Jamming in this direction appears to be delayed compared with the
direction parallel to the field. The coarsening speed in the parallel
direction remains comparable to the case without an applied magnetic
field. This anisotropic behavior of the coarsening speed reverses for
prolate particles, where the coarsening speed in the direction parallel to the field increases with increasing field strength, and jamming in this direction
is delayed compared with the perpendicular direction. In addition, we observe a shoulder (around \(10^4\Delta t\)) where the coarsening speed decays more slowly before jamming sets in. These results suggest that the coarsening near the jamming time is affected by a mechanism that depends on the applied magnetic field and causes the anisotropic
behavior. This mechanisms involves the re-orientation of anisotropic
particles and their alignment relative to the direction of the
magnetic field. To confirm this hypothesis, we analyze the
orientational order of the particles and their alignment relative to
the magnetic field and the interface, respectively.

\subsection{Particle re-orientation and packing}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{figures/results/paper1/particle_packing_viz.png}
\caption{Snapshots illustrating the particle packing at the interface for different particle shapes $\alpha$ with (left) and without (right) applied magnetic field $\bar{B}$. The right column shows the alignment of the symmetry axis of the oblate (top row) and prolate (bottom row) particles in the direction of the magnetic field indicated by arrows.}
\label{fig:packing_viz}
\end{figure}

The primary effect of the magnetic field is the torque it exerts on the
magnetic dipole of the particles. This torque rotates the particles
towards the direction of the magnetic field. The alignment of the
particles with the field direction can be clearly observed in the
simulation snapshots shown in Figure \ref{fig:packing_viz}. While the
particles are oriented randomly in the interface in the absence of a
magnetic field (\(\bar{B}=0\)), the magnetic field induces orientational
order of the magnetic dipoles (shown for \(\bar{B}=1\)).

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{figures/results/paper1/S-vs-t.png}
\caption{Time-dependence of the nematic order parameter $S$ of oblate ($\alpha=0.5$) and prolate ($\alpha=2$) particles at different field strength $\bar{B}$. Errorbars indicate the standard deviation taken over three independent simulation runs. Nematic order generally increases with applied field strength for all particle geometries. The increase slows down (for prolate particles) or reverses (for oblate particles) around $10^4$ timesteps.}
\label{fig:nematic_time}
\end{figure}

To measure the particle alignment quantitatively, we computed the
nematic order tensor \cite{veerman_phase_1992}
%
\begin{equation}
\tens{Q} = \frac{1}{n_p} \sum_i \left( \frac{3}{2} \hat{\vec{o}}_i \otimes \hat{\vec{o}}_i -\frac{1}{2}\mathsf{1} \right)
\end{equation}
%
where \(\hat{\vec{o}}_i\) is the orientation of the
\(i\)-th particles and \(n_p\) is the number of particles in the system.
The largest eigenvalue of $\tens{Q}$ yields the nematic order
parameter
%
\begin{equation}
S = \left\langle \frac{3}{2}\cos^2 (\theta) - \frac{1}{2} \right\rangle ,
\end{equation}
%
where
\(\theta=\arccos(\hat{\vec{o}}_i\cdot\hat{\vec{n}})\) is the angle
between the particle orientation and the nematic director
\(\hat{\vec{n}}\).

Figure \ref{fig:nematic_time} shows the time evolution of the nematic
order parameter \(S\) for the three different particle aspect ratios
\(\alpha\) and varying magnetic field strength \(\bar{B}\). The onset of
orientational order is nearly instantaneous and increases with
increasing field strength. For magnetic flux densities
\(\bar{B}\ge0.5\), the nematic order parameter saturates at
\(S\approx 1.0\) towards the end of the simulation. For the prolate
particles (\(\alpha=2.0\)), we observe a shoulder at around
\(10^4\Delta t\) and an intermittent plateau. The occurrence of this
plateau coincides with the slowed decay of the coarsening speed in Fig.
\ref{fig:coarsening_velocity}. This change in the orientational ordering
is even more distinct for the oblate particles, where the nematic order
decays intermittently before it increases again. The intermittent decay
for oblate particles, and the plateau for prolate particles, correlate
with the delayed onset of jamming in the direction perpendicular and
parallel to the magnetic field, respectively. These observations can be
interpreted as follows: The magnetic field aligns the particles with the
direction of the magnetic field early during the simulation. Due to this
alignment, the steric constraints between particles adsorbed at the
interface are reduced which allows further coarsening of the interfacial
area. However, during coarsening, the interfaces may re-orient
themselves and cause a capillary torque on the particles that competes
with the magnetic torque. This competition intermittently perturbs the
nematic order of the particles leading to the observed decay and plateau
of the nematic order parameter. Accordingly, the decay of \(S\) is most
pronounced at the weakest magnetic field \(\bar{B}=0.2\).

To further corroborate this mechanism, we quantify the orientational
order of the interfaces. We computed the interfacial orientation tensor
%
\begin{equation}
\tens{Q}_{\text{int}} = \frac{1}{\langle \mathrm{tr}(\tens{A}) \rangle} 
\left\langle \tens{A} - \frac{1}{3} \mathrm{tr}(\tens{A}) \mathsf{1} \right\rangle ,
\end{equation}
%
where the local tensor field $\tens{A}$ is defined by
%
\begin{equation}
\tens{A} = \nabla\phi\otimes\nabla\phi .
\end{equation}
%
The largest eigenvalue of $\tens{Q}$ is taken as the
interface nematic order parameter $S_{\text{int}}$.

\begin{figure}
\includegraphics[width=\columnwidth]{figures/results/paper1/interface_nematic.png}
\caption{Time-dependence of the interface nematic order for oblate ($\alpha=0.5$) and prolate ($\alpha=2$) particles at different magnetic field strength $\bar{B}$. The interface alignment tends to increase with increasing field strength. The rate of increase becomes larger around $10^4$ timesteps, indicating the alignment of the interfaces due to capillary interactions with the particles.}
\label{fig:interface_nematic}
\end{figure}

The results for the interface nematic order parameter $S_{\text{int}}$
are shown in Figure \ref{fig:interface_nematic}. The nematic interface
alignment increases over time and the rate of increase appears to be
higher for larger magnetic field strength $\bar{B}$. In all cases, the
final value of $S_{\text{int}}$ is below 0.5 indicating that the
tortuous structure of the interface is maintained in the presence of
magnetic fields. This confirms that the re-orientation of the particles
does not disrupt the bijel structure but leads to partial alignment of
the interfaces without changing the general topology of the bicontinuous
morphology.

When the particles rotate, the interface exerts a capillary torque on
the particles due to the surface tension and the contact angle. If the
magnetic torque exceeds the interfacial forces, the particles can
potentially overcome the capillary torque and rotate out of the
interface. For prolate particles (\(\alpha=2\)) adsorbed at flat
interfaces, Davies et al. have shown that a transition between the
energetically preferred ``flat'' orientation and a tilted orientation
occurs at a critical field strength of approximately \(\bar{B}=0.2\)
\cite{bresme_orientational_2007,davies_interface_2014,newton_influence_2014}.
In the case of bijels, however, the percolating interfaces are tortuous
and thus more mobile. We therefore posit that, rather than tilting out
of the interface, rotating particles can ``pull'' the interface along
and thereby align the liquid domains. For anisotropic particles, we
expect that the interfaces align along the larger cross-section of the
particles, i.e., perpendicular to the symmetry axis of oblate particles
and parallel to the symmetry axis of prolate particles. The data for the
anisotropic domain size and tortuosity above is consistent with this
assumption. To ascertain that the particles remain indeed in their
energetically preferred orientation with respect to the interface, we
analyzed the angle between the symmetry axis of the particles and the
interface normal. To this end, we generated a mesh of the interface
using a marching cubes algorithm. For each particle we identified the
mesh vertex closest to the particle's position (excluding particles
whose distance to the mesh exceeds the radius of the longer particle
axis) and computed the angle between the particle orientation vector
\(\hat{\vec{o}}_i\) and the interface normal at the closest vertex.
Figure \ref{fig:psi_time} shows the time-dependence of the average angle
\(\psi\) between the particle dipole axis and the nearest interface
normal.

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{figures/results/paper1/psi-vs-t.png}
\caption{Time-dependence of the average angle $\psi$ between the particle axis and the interface normal for oblate ($\alpha=0.5$) and prolate ($\alpha=2$) particles at different magnetic field strength $\bar{B}$. Errorbars indicate the standard deviation taken over three independent simulation runs. The angle between between the particles and the interface normal generally approaches the energetically preferred value ($0^\circ$ for oblate particls, $90^\circ$ for prolate particles). The average angle changes most rapidly around $10^4$ timesteps.}
\label{fig:psi_time}
\end{figure}

For both types of anisotropic particles, the average angle between the
particle dipole and the interface normal is initially around
\(\psi\approx60^\circ\). As the spinodal interface sweeps through the
system, particles attach to the interface and alignment due to the
capillary torque sets in. For oblate particles, the dipole axis aligns
with the interface normal as indicated by the decay of \(\psi\) towards
zero. For prolate particles, the preferential alignment of the dipole
axis is parallel to the interface and hence \(\psi\) increases towards
\(90^\circ\). The main variation of \(\psi\) occur in a time interval
around \(10^4\Delta t\) which coincides with the distinct features of
the coarsening speed and the particle nematic order observed above. The
results thus substantiate the proposed mechanism of particle
re-orientation in the magnetic field and the concomitant local alignment
of the interface. Once the particles start jamming, the shrinking
interfacial area forces some particles out of their preferred alignment
with the interface, leading to an increase of \(\psi\) for oblate
particles and a decrease of \(\psi\) for prolate particles. Figure
\ref{fig:psi_time} suggests that the forced tilting is more pronounced
for oblate particles than for prolate particles. Due to the larger
aspect ratio, the tilting of prolate particles relative to the interface
induces deformations that appear to cause a larger capillary torque than
the tilting of oblate particles. %For oblate particles, the liquid-solid
%contact line is on average further away from the particle center than
%for prolate particles, hence the lever effect of oblate particles is
%weaker and allows larger tilting relative to the the preferred alignment
%with the interface.
Hence the prolate particles remain mostly aligned with the interface
even in the stronger applied magnetic fields.

As hypothesized above, the alignment of the particle dipole axis with
the magnetic field reduces the steric constraints within the interface.
To corroborate this idea, we analyzed the radial distribution function
(RDF) of the particles
%
\begin{equation}
g(r) = \frac{n_p-1}{n_p} V \left\langle\delta\left(r-r_i\right)\right\rangle ,
\end{equation}
%
where \(n_p\) is the number of particles in the volume
\(V\), and \(\langle\cdot\rangle\) denotes an average over all
particles. The radial distribution function was calculated by binning
the distance between all particle pairs and normalizing the shells with
respect to the distribution \(4\pi \rho r^2 \mathrm{d}r\) of an ideal
gas. The time-evolution of the RDFs for the three particle shapes and
varying magnetic flux density is illustrated in Figure \ref{fig:rdf}.

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{figures/results/paper1/rdf_compare_time.png}
\caption{Time-evolution of the radial distribution function $g(r)$ of the particles at different magnetic field strength $\bar{B}$. The radial distribution function is shown at $10^3$, $10^4$, and $10^5$ timesteps. The distance $r$ is normalized by the radius $R=\max(R_\parallel,R_\perp)$ of the larger particle axis. The peaks illustrate the packing of particles in the interface. Dashed lines indicate the side-by-side, tip-to-tip, and side-to-tip configuration of particle pairs. For spherical particles, the three values are identical. The insets show snapshots of the particle arrangement with and without magnetic field at the respective timesteps. The direction of the magnetic field is indicated by arrows.}
\label{fig:rdf}
\end{figure*}

The radial distribution function is shown at time steps
\(t=1000\Delta t,\ 10000\Delta t,\ 100000\Delta t\). For ellipsoidal
particles, the characteristic distances between particles in contact are
\(2R_{\parallel}\), \(2R_{\perp}\), and \(R_{\parallel} + R_{\perp}\).
These distances are marked by dashed lines in Fig. \ref{fig:rdf}. We
observe that the largest peak of the RDF coincides with the distance
\(2R_\perp\) for both oblate and spherical particles, indicating that
oblate particles tend to be in contact at their circumference while
prolate particles preferentially align side-by-side. These arrangements
lead to closer packing of particles in the interface. The peaks are less
pronounced in the early stage of the simulations, where the particles
are more randomly oriented. Notably, there is a dip in the RDF of
prolate particles at \(2R_\parallel\) indicating that initially the
tip-to-tip configuration occurs more rarely. The growth of the peak
height over time shows that the magnetic fields promote this alignment
compared to the case without magnetic field. For oblate particles, a
shoulder develops around \(R_\parallel+R_\perp\), indicating that some
particles tilt out of the interface to reduce the covered interfacial
area. For prolate particles, the dip at \(2R_\parallel\) disappears over
time, indicating that more particles align tip-to-tip. This is
consistent with alignment of prolate particles with respect to the
magnetic field, which facilitates closer packing along both axes of the
particles. It further suggests that particles arrange in layers, which can also be observed in the snapshot in Fig.
\ref{fig:packing_viz}. Together with the analysis of nematic order
above, these results substantiate the proposed mechanisms that influence
the formation of bijels with anisotropic particles in magnetic fields:
The magnetic field aligns the particle dipole axis in the field
direction, and the particle re-orientation couples to interface
alignment due to the capillary interactions. The alignment of particles
reduces the steric constraints within the interface, which allows the
interface to shrink further and facilitates domain coarsening. In terms
of the time-evolution, the rotation of particles due to the magnetic
field occurs during the initial stages of the simulation, followed by
the local re-alignment of interfaces due to capillary interactions. In
the case of prolate particles, we observed the shrinking interface can
force particles to tilt out of their preferential alignment to facilitate
closer packing. Generally, our results show that when bijels stabilized
by anisotropic magnetic particles form under the influence of a magnetic
field, the domain size and tortuosity become anisotropic. Additionally,
we observe that the particle packing in the interface becomes more
ordered due to the alignment effects.

\section{Conclusions}

In this work, we studied the effect of applied magnetic fields on the
formation of bijels stabilized by magnetic ellipsoidal particles. We
considered oblate, spherical, and prolate particles with a permanent
magnetic dipole moment suspended in a symmetric binary liquid. We found
that, while the overall formation of a bijel is not disrupted by
magnetic interactions, bijels stabilized by oblate or prolate ellipsoids
exhibit anisotropic domain size and an anisotropic tortuosity. For
oblate particles, the domain size increases in the direction
perpendicular to the magnetic field while the tortuosity increases in
the parallel direction. Conversely, for prolate particles, the domain
size increases in the direction parallel to the magnetic field while the
tortuosity increases in the perpendicular direction. Compared with
bijels formed in the absence of a magnetic field, we observed changes in
domain size up to \(30\%\) for non-spherical particles. This effect can
be explained by the re-orientation of the particle dipole axis with the
magnetic field, which in turn re-aligns the interfaces in the direction
of the longer axis of the particles. We further corroborated this
mechanisms by analyzing the coarsening speed and the nematic order of
the particles and the interfaces. We found that jamming of particles is
delayed in the direction of the longer ellipsoidal axis leading to
enhanced coarsening in this direction. The timescale of the delayed
jamming coincides with a slow-down of the orientational ordering of the
particles whereas the alignment of the interfaces increases. We also
found that the angle between the particle dipole axis and the interface
normal changes at this stage. Additionally, we analyzed the radial
distribution function of the particles and found that prolate particles
tend to align side by side, while the oblate particles exhibit a less
regular arrangement. Based on these findings, we propose that bijel
formation in magnetic fields is governed by two coupled effects: During
the initial stage, the magnetic torque rotates the particles to align
the magnetic dipole moment with the field, and the orientational order
of the particles facilitates further coarsening. As coarsening proceeds,
the capillary interactions cause the interfaces to align with the longer
particle axis. The shrinking interface compresses the particles into
ordered arrangements. When jamming sets in, some particles can be forced
to tilt out of the interface and this effect is more prominent for
oblate particles.

Our results demonstrate the effects of magnetic fields on the structural
properties of bijels stabilized by ellipsoidal magnetic particles. This
control is desirable in applications where the domain size and
tortuosity affect the transport properties. For example, reduced
tortuosity can increase the diffusive permeability of bone-like
materials \cite{prakoso2023tortuosity}. Similarly, low tortuosity
in lithium electrodes facilitates homogeneous ion transport and
uniform lithium deposition, leading to enhanced cyclability of
batteries\cite{chen_tortuosity_2020, ebner_tortuosity_2014}. Whereas we
have considered one particular regime of spinodal decomposition, the
viscosity and surface tension of the liquids offer additional parameters
that could be leveraged to tune the bijel formation. Moreover, the
particle volume fraction is another parameter that is known to affect
the formation of particle-stabilized emulsions
\cite{jansen_bijels_2011,hijnen_bijels_2015}. With respect to possible
experimental realizations of our simulations, we should emphasize that
we have generally considered micron-size particles and have neglected
thermal fluctuations. At the nanoscale, thermal fluctuations may in
principle play a role, however, Reeves et
al.~\cite{reeves_particle-size_2015} have shown that nanoparticles
benefit from smaller driving forces towards disruptive curvature and
actually lead to more robust bijel formation. Nevertheless, the
stability of magnetically-responsive bijels is a relevant question for
applications that involve shear flows such as crossflow reactors
\cite{khan_nanostructured_2022}. Aside from particle-size and shape
effects, direct interactions between particles are a possible avenue
to tune the formation of particle-stabilized emulsions gels, as the
recent discovery of bicontinuous intraphase jammed emulsion gels
(bipjels) illustrates \cite{kinkead_bicontinuous_2019}. Another
interesting observation arising from our simulations is that the
packing order of particles in the interface appears to increase when
bijels form under the influence of a magnetic field. While such
interfacial ordering effects have been studied on planar interfaces
\cite{toor_self-assembly_2016,shi_nanoparticle_2018,kim_dynamic_2022},
they have hitherto not been reported for particle-stabilized emulsion
gels. It would be interesting to examine the implications of this
ordering on the optical and transport properties of jammed emulsion
gels. In conclusion, our simulations provide relevant insights into the
formation of magnetic particle-stabilized bijels in the presence of
external magnetic fields, and they demonstrate the potential of magnetic
particles for fabrication of emulsion systems with tunable and
anisotropic particle packing and domain structure.

% \section*{Data availability}

% The data and code used to generate the figures in this manuscript are available as an interactive notebook on Code Ocean at https://doi.org/00.0000/00000000. Due to size limitations, the raw simulation data are available for download on request from the authors.

% \section*{Acknowledgements}
% %The Acknowledgements come at the end of an article after Conflicts of interest and before the Notes and references.
% This work was supported by the National Science Foundation under NSF
% Awards DMR-1944942 and OIA-2346036. Any opinions, findings and
% conclusions or recommendations expressed in this material are those of
% the authors and do not necessarily reflect those of the National Science
% Foundation. This work used NCSA Delta at the National Center for
% Supercomputing Applications through allocation PHY220131 from the
% Advanced Cyberinfrastructure Coordination Ecosystem: Services \& Support
% (ACCESS) program, which is supported by National Science Foundation
% grants \#2138259, \#2138286, \#2138307, \#2137603, and \#2138296. We
% wish to thank Jens Harting and Alexander Wagner for insightful
% discussions.

%%%END OF MAIN TEXT%%%

%The \balance command can be used to balance the columns on the final page if desired. It should be placed anywhere within the first column of the last page.

%\balance

%If notes are included in your references you can change the title from 'References' to 'Notes and references' using the following command:
%\renewcommand\refname{Notes and references}

%%%REFERENCES%%%
% \bibliographystyle{rsc} % RSC's .bst file
% \bibliography{bijels}

### 2025-02-12 chapters/paper1_old.tex
Changes 1. Initialized repo 2. Added current progress with dissertation. Intro, methods, analysis techniques, literature review and some results present

The first area of investigation this work seeks to tackle is how constant magnetic fields can be utilized to modify the microstructure of a bijel during formation. To achieve this goal, the extent of microstructure change that constant magnetic fields facilitate and the underlying cause for any observed microstructure change will be probed. This was accomplished through applying constant magnetic fields of strength $\Bar{B} = 0, 0.2, 0.5, 1$ in the z direction on bijels as they were phase separating. The obtained microstructure and particle order are analyzed below.

\begin{figure}[h]
    \centering
    \includegraphics[scale = 0.5]{figures/results/paper1/D2a-vs-B_ss.png}
    \caption{Dimensionless average domain size ($L_1$, left) and perpendicular and parallel to the field direction domain sizes ($L_{\perp}, L_{\parallel}$, right) plotted against dimensionless magnetic field strength. Domain sizes are dimensionless by dividing with the larger radius the particle.}
    \label{fig:P1_D-vs-B-ss}
\end{figure}

Figure \ref{fig:P1_D-vs-B-ss} shows that the average domain size, $L_1$, is not significantly affected by the application of a magnetic field. Ellipsoidal particles result in smaller domain sizes compared to spherical particles, as observed by Gunther et al. This is due to their larger cross-sectional area to volume ratio, increasing interfacial coverage and causing the bijel to jam earlier. Directional domain sizes, however, show significant changes with ellipsoidal particles, varying based on particle aspect ratio. Prolate particles, with magnetic moments parallel to their long axis, show an increase in $L_{\parallel}$ by approximately $\approx 3 L/R$, while $L_{\perp}$ remains unchanged. This trend is inverted for oblate particles, with $L_{\perp}$ increasing by approximately $\approx 4 L/R$.

\begin{figure}
    \centering
    \includegraphics[scale = 0.5]{figures/results/paper1/coarsening_vel.png}
    \caption{Coarsening rates of the bijel under different field strengths over time. A coarsening rate of 0 implies a jammed system. When ellipsoidal particles are used, the jamming points in each direction change when a field is applied, especially apparent at higher field strengths.}
    \label{fig:P1_coarsen}
\end{figure}

% \begin{wrapfigure}{l}{10cm}
% \caption{Coarsening rates of the bijel under different field strengths over time. A coarsening rate of 0 implies a jammed system. When ellipsoidal particles are used, the jamming points in each direction change when a field is applied, especially apparent at higher field strengths.}
% \label{wrap-fig:P1_coarsen}
% \includegraphics[width=10cm]{figures/results/paper1/coarsening_vel.png}
% \end{wrapfigure}

In this system, the microstructure is controlled through particle jamming, with any magnetic field-induced ordering observed as a change in the bijel's jamming point, defined when the coarsening rate is zero. Anisotropy in domain size indicates a divergence between directional coarsening rates. The coarsening rate, defined as the change in domain size over time, is analyzed directionally as $u_{L_{\parallel}}$ and $u_{L_{\perp}}$. Figure \ref{fig:P1_coarsen} shows that bijels stabilized with spherical particles have coarsening rates independent of field strength. However, ellipsoidal particles exhibit different coarsening rates in parallel and perpendicular directions, with the jamming point correlated to domain size. This suggests that magnetic field-driven particle ordering at the interface modifies the bijel's jamming point and microstructure.

\begin{figure}
    \centering
    \includegraphics[scale = 0.5]{figures/results/paper1/S-vs-t.png}
    \caption{Plots of the nematic order $(S)$ of ellipsoidal particles over time. $S = 1$ indicates all particles are aligned with one another. $S \geq 0.3$ indicates an isotropic to nematic transition \cite{veerman_phase_1992}}
    \label{fig:P1_nematic}
\end{figure}

To conclusively link if particle ordering driven by the magnetic field was the cause of the change in coarsening rate, the nematic order parameter $(S)$ was used to calculate the average order of the particles over time, shown in Figure \ref{fig:P1_nematic}. As the spherical particles show no microstructure modification under an applied field, they are omitted from this plot. Figure \ref{fig:P1_nematic} shows that the nematic order of the particles increase as a function of the applied field strength. This links the ordering of the particles being caused by the applied magnetic field. The shape of the nematic ordering over time also changes as a function of the applied field, with a non-monotonic increase being seen for both ellipsoidal particles tested. Davies identified that the tilt of an ellipsoidal particle to the interface was a force balance between the interfacial and magnetic field forces. \cite{davies_interface_2014}

\begin{figure}
    \centering
    \includegraphics[scale = 0.5]{figures/results/paper1/psi-vs-t.png}
    \caption{Plots of the average angle between the particle dipole moment and interface normal $(\psi)$ over time. While there are minor changes in for the oblate particles, these are not as significant as the ordering of particles to the field.}
    \label{fig:P1_particle-angle}
\end{figure}

The non-monotonic changes seen in the nematic order parameter may be driven through a balance between steric and magnetic field forces tilting particles out of the interface to orient to the field or through the interface itself realigning particles during domain coarsening. To identify which of these mechanisms dominate in this system, the angle between the dipole moment and the interface normal $(\psi)$ is plotted. An oblate or prolate ellipsoid lying in its equilibrium orientation on the interface should have $\psi = 0 ^{\circ}$ and $\psi = 90 ^{\circ}$ respectively. From Figure \ref{fig:P1_particle-angle}, even with no field it can be seen that not all particles lie completely flat on the interface. Upon field application, the prolate particles seem to be unaffected while the oblate particles show a slight increase in the angle, demonstrating that they are tilting out of the interface more than at equilibrium. If steric and magnetic field forces dominate $\psi$ should be changing greatly with time as the interface does not remain static to the direction of the field. However, the particle orientations remained pinned to the interface, suggesting that as the particles orient to the field, the particles drag the interface with them.

### 2025-02-12 chapters/paper2.tex
Changes 1. Initialized repo 2. Added current progress with dissertation. Intro, methods, analysis techniques, literature review and some results present

Previous work demonstrated that applying electric fields to silica-stabilized emulsion droplets caused particle stabilizers to unjam and then rejam, locking the emulsion in a new morphology. \cite{cui_stabilizing_2013} Considering the potential applications of an already synthesized porous material with tunable microstructure, the second part of this work will explore using magnetic fields to manipulate bijels after synthesis. \cite{vanoli_bijels_2022, cha_bicontinuous_2019} Bijels simulated under no field had a constant magnetic in the z direction of strength $\Bar{B} = 0, 0.2, 0.5, 1$ with their microstructure and particle order analyzed.

Underlying mechanism being rearrangement of particles on the interface in response to magnetic field, or unjamming and rejamming characterized by a change in the number of bonded neighbors. Explains behaviour seen in differences in the system above and below the isotropic to nematic transition?

\begin{figure}
    \centering
    \includegraphics[scale = 0.5]{figures/results/paper2/domain_size.png}
    \caption{Left plot shows the average domain size $(L_1)$ in markers and the nematic order parameter $(S)$ in lines versus time. Right plot shows the same data rescaled over $t_{iso \rightarrow nematic}$.}
    \label{fig:P2_domain_scaling}
\end{figure}

In this system, the mechanism of microstructure modification after formation is expected to be due to magnetic field driven particle ordering changes. Figure \ref{fig:P2_domain_scaling} demonstrates that the average domain size $(L_1)$ does not change significantly with the applied field, with a slight increase of about $\approx 0.3 L/R$, noted to be within error. However, clues into the underlying mechanics are visible when examining the nematic order parameter lines overlaid on the domain size markers. At $\Bar{B} = 0.2$, the domain size change corresponds with the nematic order parameter change, indicating a direct link between domain size change and particle ordering. At $\Bar{B} > 0.2$, a gap appears between the domain size change and the nematic order parameter change, suggesting steric effects influence the rate of bijel microstructure change. The timescales of these rearrangements may also impact the observed microstructure changes, which can be characterized by the domain size change over time rescaled by a characteristic timescale.

A naive guess as to the dominating timescale of the response would be the isotropic to nematic time of the system or when $S \geq 0.3$. The right plot of Figure \ref{fig:P2_domain_scaling} demonstrates the time evolution of the system when rescaling time with the isotropic to nematic transition time, $t_{iso \rightarrow nematic}$. From this plot, it can be seen that application of the field causes collapse of domain size changes at different field strengths on top of one another, showing that this naive guess is a correct one. The changes in domain size at with no applied field can be attributed to the reordering of particles at the interface, leading to coarsening at long time scales consistent with what Gunther et al. observed. \cite{gunther_timescales_2014}

\begin{figure}
    \centering
    \includegraphics[scale = 0.5]{figures/results/paper2/domain_size_aniso.png}
    \caption{Plots of the perpendicular $(L_{\perp})$ and parallel $(L_{\parallel})$ domain sizes over time rescaled over $t_{iso \rightarrow nematic}$}
    \label{fig:P2_domain_aniso}
\end{figure}

In the previous section, even if the average domain size did not change much, there was domain size anisotropy found upon application of the field. This observation and trends seen remains true when applying the field after formation as can be observed in \ref{fig:P2_domain_aniso}. Time was again rescaled with the isotropic to nematic transition time for each system, demonstrating that the timescale of response is controlled using this timescale, and is independent from field strength. The domain size change observed appears to be about $1 L/R$ less than what can be found when applying the same field size during bijel synthesis as the increase in domain size for $L_{parallel}$ for prolate particles is $\approx 2 L/R$ which is $50 \%$ lower than what was found. This indicates that microstructure control after synthesis is not as effective. This might be due to steric effects being much stronger after synthesis, limiting how much particles can move or tilt before rejamming. Despite this, the domain size change found is well within what has been seen to be effective in the literature, indicating that magnetic field enabled in-situ microstructure modifications can be utilized within bijels. \cite{cha_bicontinuous_2019, khan_nanostructured_2022, vanoli_bijels_2022}

\begin{figure}
    \centering
    \includegraphics[scale = 0.5]{figures/results/paper2/interface_angle.png}
    \caption{Plots of the average angle between the particle dipole moment and interface normal $(\psi)$ over time. While there are minor changes in for the oblate particles, these are not as significant as the ordering of particles to the field.}
    \label{fig:P2_interface_angle}
\end{figure}

To determine if the interface follows the orientation of the particles, the average angle between the particle symmetry axis and the interface normal $(\psi)$ was plotted against time rescaled by $t_{iso \rightarrow nematic}$ in Figure \ref{fig:P2_interface_angle}. From ths plot, it can be observed that upon application of the magnetic field, the particle tilts out of the interface at an equal normalized rate. However, the angle reached before the particles begin returning to their equilibrium configuration is magnetic field strength dependent, suggesting that the degree of microstructure changed observed might be dependent on how much the particle tilts away from its equilibrium position. At non-equilibrium particle tilts, there is more leeway for coarsening to occur before rejamming occurs, resulting in larger microstructural differences.

Future work will more closely examine the role of the particles in observed microstructure changes by calculating the average angle between the particle symmetry axis and the interface normal. In addition, the impact of initial order of the particle monolayer on the degree of microstructure change observed will be characterized. This will be accomplished by using bijels that have been simulated under magnetic fields and changing the applied field. Example conditions would be a bijel being simulated under a field strength of $\Bar{B} = 0.2$ and increasing the applied field to $\Bar{B} = 1$ or switching off the applied field. Based on the findings so far it is predicted that initial particle order and microstructure change are inversely correlated. Additionally, the timescales of these microstructure changes will be investigated. When switching a field on, there are magnetic field, steric and interfacial forces that govern the dynamics. However, when reducing the field strength, the magnetic field derived force isn't present, resulting in steric and interfacial forces playing a significant role. These differences can be examined by investigating the timescales the observed response occurs at, as well as the particle properties over time.

% \textcolor{blue}{Still needs additional explanation of how using templates made under fields and decreasing and increasing field strengths will change results}

### 2025-02-12 chapters/paper3.tex
Changes 1. Initialized repo 2. Added current progress with dissertation. Intro, methods, analysis techniques, literature review and some results present

% Previous work into shearing bijels have demonstrated how particles prefer to move in the direction of shear and if strong enough, even detach from the interface. \cite{bonaccorso_shear_2020} It has also been shown how at curved interfaces, ellipsoidal particles

In many of the manufacturing techniques outlined for continuous bijel production such as STrIPS, the rheological properties are essential in ensuring that the casting mixture remains processable. However, past work with ferrofluids and magnetic emulsions have showed how the rheological properties vary drastically as a function of the field strength. Bijels themselves have complex rheological properties stemming from the removal of particles from the interface if too much shear is applied. Therefore, avenues of exploration here would be how the rheological properties of bijels change under the influence of fields in response to an applied shear. One of the questions that will be investigated in particular will be how shear changes the orientation of the particles on the interface, the interfacial coverage of particles and if there is anisotropy in the viscosity during the application of a field owing to the orientation of particles towards the field.

First, a shear capillary number is defined as $Ca_s = \frac{\eta_{f} \dot{\gamma} L_{1}}{\sigma}$ where $\dot{\gamma} = \frac{u_{LE}}{L_x}$ is the strain rate and $L_1$ is the average domain size. \cite{frijters_effects_2012, yang_capillary_2022} In the literature, $Ca_s$ has been between between 0.04 and 0.16. However, the box size in these simulations were smaller, meaning that these capillary number ranges would exceed the maximum mach number the model allows if this same range were used $(Ma \leq 0.03)$. To accommodate this limitation the largest capillary number used will be $Ca_s = 10^-5$ which correspond to a maximum of $Ma \approx 0.002$. $Ca_s = 10^-6,  10^-7$ will also be used to demonstrate how the bijels respond to shear of varying strengths. As all particles used have only hard-sphere type interactions, it is expected that the behaviour seen should mimic 2D colloidal glasses percolating in 3D space, akin to what Ching and Mohraz saw, with an additional dependence on -the direction of shear. This would predict the discovery of particle monolayer dependent elasticity and yield stress along with shear thinning behaviour as a function of strain rate.

To verify these predictions, bijel microstructure will be defined using four processing histories; The first is of a bijel simulated under a $\Bar{B} = 1$ magnetic field strength, the second is a bijel stimulated under no field, followed by the application of a $\Bar{B} = 1$ field after jamming, the third is a bijel simulated under no field, while the final microstructure is a bijel simulated under $\Bar{B} = 1$ magnetic field, followed by switching the field off after jamming. This gives insight into the impact of processing history on the shear properties of a bijel, in addition to the microstructural and colloidal insights gained. Based on the results in Bonaccorso et al., there should be shear driven and shear rate dependent elongation of the domains in the direction parallel to the applied shear which in this system will be seen as a reduction in $L_{\perp}$ and an increase in $L_{\parallel}$. \cite{bonaccorso_shear_2020} The microstructure anisotropy will also be a factor in the viscosity results, as larger domains are more permeable than smaller ones, meaning that bijels where $L_{\perp} > L_{\parallel}$ should see less of the domain elongation effects shown in Bonaccorso et al. as the permeability of the bijels rises with larger domain size. \cite{bonaccorso_shear_2020}

It is also expected that the effective viscosity will be different between the four microstructures dependent upon the degree of nematic ordering and microstructural anisotropy of the bijel. Nematic ordering of the particles will be mimic shear banding in colloidal suspensions, resulting in a lowered effective viscosity compared to bijels without nematically ordered particles. \cite{xu_relation_2013, vermant_flow-induced_2005} Tracking of the proportion of particles on the interface will also yield insight into how the packing of the particles affects the rate at which particles will get ejected from the interface. Systems with a larger $\eta_{eff}$ are predicted to have the largest domains, largest difference between initial and final particle order and lowest number of particles left on the interface once steady state has been established.

### 2025-02-12 licenses/licenses.tex
Changes 1. Created license folder and added list of licenses currently or to be used 2. Modified gitignore file to ensure that latex make files are not added to git

\section{License numbers}

\begin{itemize}
    \item Continuous Fabrication of Hierarchical and Asymmetric Bijel Microparticles, 
    Fibers, and Membranes by Solvent Transfer‐Induced Phase Separation (STRIPS): 5913140219015
    \item Scalable synthesis of gyroid-inspired freestanding three-dimensional graphene architectures: 1548092-1
    \item State diagram for particle stabilized emulsions. [Soft Matter, 2015,11, 8393-8403]: 1551968-1
    \item Scalable Manufacturing of Hierarchical Biphasic Bicontinuous Structures via Vaporization-Induced 
    Phase Separation (VIPS) [Materials Letters 2020, 2, 5, 524-530]: "Reprinted (adapted) with permission from 
    {COMPLETE REFERENCE CITATION}. Copyright {YEAR} American Chemical Society."
    \item Modulation of Cellulose Nanocrystals Amphiphilic Properties to Stabilize Oil/Water Interface 
    [Biomacromolecules 2016, 17, 5, 1748–1756]: "Reprinted (adapted) with permission from 
    {COMPLETE REFERENCE CITATION}. Copyright {YEAR} American Chemical Society."
    \item Dextran-Based Nanoparticles to Formulate pH-Responsive Pickering Emulsions: A Fully Degradable 
    Vector at a Day Scale [Biomacromolecules 2020, 21, 12, 5358–5368]: "Reprinted (adapted) with permission from 
    {COMPLETE REFERENCE CITATION}. Copyright {YEAR} American Chemical Society."
    \item Stable emulsions with thermally responsive microstructure and rheology using poly(ethylene oxide) star 
    polymers as emulsifiers [Journal of Colloid and Interface Science, 2013, 394, 284-292]: 5921030909190
    \item Magnetophoresis of Magnetic Pickering Emulsions Under Low Field Gradient: Macroscopic and Microscopic 
    Motion [Langmuir 2021, 37, 5, 1811–1822]: "Reprinted (adapted) with permission from 
    {COMPLETE REFERENCE CITATION}. Copyright {YEAR} American Chemical Society."
    \item Influence of magnetic field on the orientation of anisotropic magnetic particles at liquid interfaces 
    [Phys Chem Chem Phys 2014, 16, 47, 26051-26058]: 1551970-1
    \item Pickering Emulsions with Controllable Stability [Langmuir, 2005, 21, 6, 2158-2162]: "Reprinted (adapted) with permission from 
    {COMPLETE REFERENCE CITATION}. Copyright {YEAR} American Chemical Society."
    \item Bijels Containing Magnetic Particles: A Simulation Study [Langmuir, 2010, 26, 11, 7928-7936]: 
    "Reprinted (adapted) with permission from {COMPLETE REFERENCE CITATION}. Copyright {YEAR} 
    American Chemical Society."
    \item Numerical simulations of particulate suspensions via a discretized Boltzmann equation. Part 2. Numerical results
    \item Aerobijels: Ultralight Carbon Monoliths from Cocontinuous Emulsions 
    [Adv. Funct. Mater. 2020, 30, 1908383]: 5921080017718
    \item Hierarchical assemblies of superparamagnetic colloids in 
    time-varying magnetic fields [Soft Matter. 17, 5, 1120-1155]: 1552854-1
\end{itemize}

### 2025-02-12 chapters/paper2.tex
Changes 1. Fixed reference formatting in bib file and added stylesheet for rendering 2. Modified formatting to improve human readability in an IDE
Changes 1. Adding structural response of bijels chapter to dissertation 2. Figures for the aforementioned chapter added

@@
-Previous work demonstrated that applying electric fields to silica-stabilized emulsion droplets caused particle stabilizers to unjam and then rejam, locking the emulsion in a new morphology.
-\cite{cui_stabilizing_2013} Considering the potential applications of an already synthesized porous material with tunable microstructure, the second part of this work will explore using magnetic fields to manipulate bijels after synthesis.
-\cite{vanoli_bijels_2022, cha_bicontinuous_2019} Bijels simulated under no field had a constant magnetic in the z direction of strength $\Bar{B} = 0, 0.2, 0.5, 1$ with their microstructure and particle order analyzed.
+\section{Introduction}
+\section{Results}\label{sec:results_p2}
 
-Underlying mechanism being rearrangement of particles on the interface in response to magnetic field, or unjamming and rejamming characterized by a change in the number of bonded neighbors.
-Explains behaviour seen in differences in the system above and below the isotropic to nematic transition?
+\subsection{Hysteresis curve}
+
+Bijels have proposed applications as soft matter based material templates, drug delivery vectors and separations systems. 
+The materials performance in each application is dependent upon the microstructure of the bijel template. Many of the 
+applications listed above benefit from stimuli response, allowing for in-situ microstructure tuning to modify permeability 
+of the material. We want to understand whether bijels provide access to reversible structural modifications which would 
+allow stimuli responsive bijels to be used in in-situ applications.
+
+We begin our investigation by characterizing the microstructure changes observed on bijels stabilized with prolate 
+ellipsoids with a particle volume fraction of $\phi_p = 0.1$. We apply a constant magnetic field of $\bar{B}_z = 0.2$ 
+onto bijels that were simulated with no magnetic field. Once the microstructure has reached its new state, we ramp up 
+the magnetic field to $\bar{B}_z = 0.5$ and finally $\bar{B}_z = 1$. We then apply the opposite procedure to reduce 
+the applied field strength, resulting in a magnetic field ramp of 
+$\bar{B}_z: 0 \rightarrow 0.2 \rightarrow 0.5 \rightarrow 1 \rightarrow 0.5 \rightarrow 0.2 \rightarrow 0$.
+
+We characterize the microstructure changes observed through calculating a characteristic length scale, 
+called the average domain size. The average domain size is calculated using the first moment of the 3D 
+averaged structure factor. Past work has shown that this method correctly reproduces the scaling expected 
+in phase separating systems. The structure factor is calculated from the fourier transform of the fluctuations 
+in the order parameter. \cite{kendon_inertial_2001}
+
+We identified that this measure of the domain size tended to overestimate the domain size. However, past work has 
+shown that the scaling behavior of the first moment derived domain size is consistent with phase separation expected 
+for spinodal decomposition. Overestimation is caused by a low number of samples at small k values as the bin size is 
+approximately equal to the k value. Furthermore, the structure factor and the length scale calculated in simulations
+ with periodic domains are subject to finite size effects. Nevertherless, trends about the average domain size can be 
+ determined from this measurement.
+
+Before the structure factor was calculated, the location of the particles were filled with the average density of the 
+surrounding lattice sites using Equation \ref{eq:fill_particles} to generate a smooth interface. The particles are 
+iteratively filled from outside in until all lattice points corresponding to the particle are filled with the average 
+density of the fluid surrounding the lattice point. Within the red and blue fluid densities, sites representing the 
+particles are filled before the order parameter is calculated. By filling the particles, we are able to analyze the 
+microstructure without the influence of the particles. We calculate the hysteresis curve by calculating the domain 
+size at the final timestep of each magnetic field change. We then plot these domain sizes against the magnetic field 
+applied to obtain them and split them in the descending and ascending magnetic field directions to demonstrate the 
+differences observed. We plot these results in Figure \ref{fig:hysteresis_curve}
 
@@
     \centering 
-    \includegraphics[scale = 0.5]{figures/results/paper2/domain_size.png}
-    \caption{Left plot shows the average domain size $(L_1)$ in markers and the nematic order parameter $(S)$ in lines versus time.
-Right plot shows the same data rescaled over $t_{iso \rightarrow nematic}$.}
-    \label{fig:P2_domain_scaling}
+    \includegraphics[scale=0.7]{../figures/results/paper2/hysteresis_curve.png} 
+    \caption{Hysteresis curve of bijels stabilized with magnetically responsive ellipsoidal particles.
+The y-axis is the average length scale $\frac{L}{R}$ normalized with the radius of the particle, while the x-axis corresponds to the dimensionless magnetic field strength $\bar{B}$.
+We show that there is domain coarsening upon increase of the field strength, followed by jamming of the structure as the field strength is decreased indicating the path dependence of the bijel microstructure.}
+    \label{fig:hysteresis_curve} 
 \end{figure}
 
-In this system, the mechanism of microstructure modification after formation is expected to be due to magnetic field driven particle ordering changes.
-Figure \ref{fig:P2_domain_scaling} demonstrates that the average domain size $(L_1)$ does not change significantly with the applied field, with a slight increase of about $\approx 0.3 L/R$, noted to be within error.
-However, clues into the underlying mechanics are visible when examining the nematic order parameter lines overlaid on the domain size markers.
-At $\Bar{B} = 0.2$, the domain size change corresponds with the nematic order parameter change, indicating a direct link between domain size change and particle ordering.
-At $\Bar{B} > 0.2$, a gap appears between the domain size change and the nematic order parameter change, suggesting steric effects influence the rate of bijel microstructure change.
-The timescales of these rearrangements may also impact the observed microstructure changes, which can be characterized by the domain size change over time rescaled by a characteristic timescale.
+Figure \ref{fig:hysteresis_curve} illustrates the hysteresis behavior of magnetically responsive bijels. 
+We observe a hysteresis response of the bijel microstructure, characterized by a non-return of the microstructure 
+to the original average domain size value when reducing the applied magnetic field strength. The increase in the 
+average length scale when applying the magnetic field is due to domain coarsening caused by reorientation of particles 
+to the magnetic field strength, reducing the interfacial coverage. When decreasing the magnetic field strength, 
+we observe that the domain size does not return to the original value meaning that that the microstructure of the 
+bijel is unaffected by the reduction in magnetic field. This suggests that the particles at the interface are in a 
+kinetically trapped configuration.
 
-A naive guess as to the dominating timescale of the response would be the isotropic to nematic time of the system or when $S \geq 0.3$.
-The right plot of Figure \ref{fig:P2_domain_scaling} demonstrates the time evolution of the system when rescaling time with the isotropic to nematic transition time, $t_{iso \rightarrow nematic}$.
-From this plot, it can be seen that application of the field causes collapse of domain size changes at different field strengths on top of one another, showing that this naive guess is a correct one.
-The changes in domain size at with no applied field can be attributed to the reordering of particles at the interface, leading to coarsening at long time scales consistent with what Gunther et al.
-observed.
-\cite{gunther_timescales_2014}
+\subsection{Applying a field}
+
+We saw in Figure \ref{fig:hysteresis_curve} that there was hysteresis in the structural response of magnetic bijels 
+to a constant magnetic field. The first facet to investigate would be why there is a large increase in the domain size 
+between $\bar{B}_z: 0.0 \rightarrow 0.2$. In many of the proposed stimuli responsive applications for bijels, the 
+timescales of response is important to characterize and would also provide a mechanistic understanding of the reasons 
+why the microstructure changes. We probe these aspects of structural response of bijels in this section by assessing 
+the response of bijels stabilized by particles with volume fraction of $\phi_p = 0.1$ simulated under no applied field 
+to an applied field in the range $\bar{B} = 0, 0.2, 0.5, 1$. We begin our investigation by visualizing the structure 
+before and after the application of magnetic fields.
 
@@
     \centering 
-    \includegraphics[scale = 0.5]{figures/results/paper2/domain_size_aniso.png}
-    \caption{Plots of the perpendicular $(L_{\perp})$ and parallel $(L_{\parallel})$ domain sizes over time rescaled over $t_{iso \rightarrow nematic}$}
-    \label{fig:P2_domain_aniso}
+    \includegraphics[scale=0.7]{../figures/results/paper2/microstructure_viz-field_on.png} 
+    \caption{Visualizations of bijels simulated under no fields at $t = 0$ (left) and $t = 10^5$ (right). The top 
+            column demonstrates the microstructure evolution if no field is used while the bottom column demonstrates 
+            the microstructure evolution when the system is exposed to a field strength of $\bar{B} = 1$. Particle 
+            reorientation to the direction of the field can be seen, resulting in microstructure changes driven 
+            through domain coarsening until the particles jam.} 
+    \label{fig:microstructure_viz-field_on} 
 \end{figure}
 
-In the previous section, even if the average domain size did not change much, there was domain size anisotropy found upon application of the field.
-This observation and trends seen remains true when applying the field after formation as can be observed in \ref{fig:P2_domain_aniso}.
-Time was again rescaled with the isotropic to nematic transition time for each system, demonstrating that the timescale of response is controlled using this timescale, and is independent from field strength.
-The domain size change observed appears to be about $1 L/R$ less than what can be found when applying the same field size during bijel synthesis as the increase in domain size for $L_{parallel}$ for prolate particles is $\approx 2 L/R$ which is $50 \%$ lower than what was found.
-This indicates that microstructure control after synthesis is not as effective.
-This might be due to steric effects being much stronger after synthesis, limiting how much particles can move or tilt before rejamming.
-Despite this, the domain size change found is well within what has been seen to be effective in the literature, indicating that magnetic field enabled in-situ microstructure modifications can be utilized within bijels.
-\cite{cha_bicontinuous_2019, khan_nanostructured_2022, vanoli_bijels_2022}
+In Figure \ref{fig:microstructure_viz-field_on} we show representative snapshots of the bijel at the initial and 
+final timestep with $\bar{B}_z = 0$ and $\bar{B}_z = 1$. We show that upon application of the field, particles align 
+to the direction of the field. As the particles orient to the field, they disrupt the packing of particles at the 
+interface, causing domain coarsening as the particles rearrange into new positions. The particles then rejam in 
+place once the interfacial area and particle cross sectional area match. Domain coarsening observed in the figure 
+can be explained through the ordering of particles at the interface, causing a reduction in the available area that 
+the particles have for stabilization. To correlate the microstructure evolution to the ordering of the particles, we calculate the 
+nematic order parameter. \cite{cuesta_monte_1990}
 
@@
     \centering 
-    \includegraphics[scale = 0.5]{figures/results/paper2/interface_angle.png}
-    \caption{Plots of the average angle between the particle dipole moment and interface normal $(\psi)$ over time.
-While there are minor changes in for the oblate particles, these are not as significant as the ordering of particles to the field.}
-    \label{fig:P2_interface_angle}
+    \includegraphics[scale=0.7]{../figures/results/paper2/domain_size-field_on.png} 
+    \caption{Plotting the spherically averaged domain size normalized with $R_p$($L/R$) of the 
+             particle at different magnetic field strengths, $\bar{B}$, and the nematic order parameter $S$ in lines.
+             We quantify the domain size and ordering of the particles, and show that the change in both parameters
+            are correlated with the strength of the applied magnetic field.} 
+    \label{fig:domain_size-field_on} 
     \end{figure}
 
-To determine if the interface follows the orientation of the particles, the average angle between the particle symmetry axis and the interface normal $(\psi)$ was plotted against time rescaled by $t_{iso \rightarrow nematic}$ in Figure \ref{fig:P2_interface_angle}.
-From ths plot, it can be observed that upon application of the magnetic field, the particle tilts out of the interface at an equal normalized rate.
-However, the angle reached before the particles begin returning to their equilibrium configuration is magnetic field strength dependent, suggesting that the degree of microstructure changed observed might be dependent on how much the particle tilts away from its equilibrium position.
-At non-equilibrium particle tilts, there is more leeway for coarsening to occur before rejamming occurs, resulting in larger microstructural differences.
+In Figure \ref{fig:domain_size-field_on}, we plot the average domain size change over time normalized by the particle 
+radius parallel to the symmetry axis $R_p$. We see that there is a $\approx 2.4\%$ increase in the average domain size 
+observed when switching on a magnetic field onto a bijel made with no field when comparing the final timestep of each 
+simulation. We also observe that with no applied field, there is a small increase in the domain size. The 
+microstructure change observed with no applied magnetic field is consistent with what Gunther et al. observed 
+in their investigations on the timescales of bijels stabilized with ellipsoidal particles. \cite{gunther_timescales_2014} 
+They concluded that domain size increases at long time scales seen in bijels stabilized with ellipsoidal particles 
+occur due to steric force derived particle reorientation to a closer packed configuration, causing domain coarsening 
+as the stabilized interface area reduces.
 
-Future work will more closely examine the role of the particles in observed microstructure changes by calculating the average angle between the particle symmetry axis and the interface normal.
-In addition, the impact of initial order of the particle monolayer on the degree of microstructure change observed will be characterized.
-This will be accomplished by using bijels that have been simulated under magnetic fields and changing the applied field.
-Example conditions would be a bijel being simulated under a field strength of $\Bar{B} = 0.2$ and increasing the applied field to $\Bar{B} = 1$ or switching off the applied field.
-Based on the findings so far it is predicted that initial particle order and microstructure change are inversely correlated.
-Additionally, the timescales of these microstructure changes will be investigated.
-When switching a field on, there are magnetic field, steric and interfacial forces that govern the dynamics.
-However, when reducing the field strength, the magnetic field derived force isn't present, resulting in steric and interfacial forces playing a significant role.
-These differences can be examined by investigating the timescales the observed response occurs at, as well as the particle properties over time.
+In Figure \ref{fig:domain_size-field_on}, we also plot the nematic order parameter of each respective bijel as 
+lines demonstrating the change in this parameter over time. Firstly, we see the effect of particle reordering due 
+to steric effects at $\bar{B}_z = 0$ from the slight increase $S$ over time. We also see that there is field 
+strength dependence on the rate of ordering and final ordering of the particles to the field. A gap between the 
+time evolution of the nematic order parameter and the domain size can be observed when $\bar{B}_z = 0.5, 1$, 
+that is not present when $\bar{B}_z = 0.2$. It was hypothesized that the time taken for particle reorientation 
+to the field would control the degree and rate of domain size change when the bijel begins with particles with 
+random order. This result suggests that the dynamics of the system at higher magnetic field strengths are 
+dependent upon other factors that vary upon application of the magnetic field.
 
-% \textcolor{blue}{Still needs additional explanation of how using templates made under fields and decreasing and increasing field strengths will change results}
+We have also identified that bijels stabilized with anisotropic particles under magnetic fields form anisotropic 
+structures. Past work has shown that the microstructure, specifically the length scale and tortuosity are critical to 
+the performance of porous materials in applications such as battery electrodes and tissue engineering applications. 
+\cite{zhang_promoting_2019, ebner_tortuosity_2014, hsieh_architected_2021} Characterization of the anisotropic 
+microstructure would allow application specific microstructure design. To quantify the length scales in each cartesian 
+direction, we also calculate the 2nd moment derived structure factor without radial averaging. \cite{jansen_bijels_2011} 
+Once the structure factor is calculated as in Eq \ref{eq:structure_factor_calc}, the second moment of the structure factor 
+in direction $\beta$ is calculated in each cartesian direction. We also calculate the tortuosity of the microstructures. In 
+previous work, we identified that the length scale derived from the second moment of the structure factor is only useful 
+for identifying length scale anisotropy. Therefore, we plot the directional second moment derived length scales and 
+tortuosity in Figure \ref{fig:domain_size_aniso-field_on}.
+
+\begin{figure} 
+    \centering 
+    \includegraphics{../figures/results/paper2/domain_size_aniso-field_on.png} 
+    \caption{Plotting the anisotropic domain size and tortuosities against the applied magnetic field strength on 
+             the left and right respectively for bijels stabilized with magnetically responsive prolate ellipsoids. 
+             We see that upon application of the field, the domain size parallel to the applied field direction, 
+             $L_{\parallel}$ increases while the domain size perpendicular to the applied field, $L_{\perp}$ decreases.
+             These results support the tortuosity data obtained which show that $\tau_{\parallel}$ decreases, 
+             indicating a shorter path length, while $\tau_{\perp}$ increases, indicating a longer path length.} 
+    \label{fig:domain_size_aniso-field_on} 
+\end{figure}
+
+From Figure \ref{fig:domain_size_aniso-field_on}, we see that domain size anisotropy is observed upon application of the field, with $L_{\perp}$ and $L_{\parallel}$ increasing and decreasing by 35 $\%$ and 13 $\%$ respectively.
+The qualitative changes match what has been observed in our past work when applying magnetic fields onto bijels during formation.
+\cite{karthikeyan_formation_2024} This can be explained through understanding the mechanisms of domain size change in both cases.
+During the formation of bijels, the particles are adsorbed onto the interface and oriented to the field when they jam, creating the anisotropic microstructure observed.
+In this case, we see that the particles reorient in response to the field, unjamming and rejamming once the domains have coarsened sufficiently that the interfacial area matches the area covered by the particle monolayer.
+The directionality of particles, causes domain ordering as the particles jam in their ordered states, causing domain size anisotropy in both cases.
+
+In Figure \ref{fig:domain_size_aniso-field_on}, we demonstrate that the application of the magnetic field changes the 
+domain size. The tortuosity of the bijel is initially around $\tau \approx 1.6$, consistent with simulations of the 
+diffusive tortuosities of gyroid structures using Lattice Boltzmann simulations. \cite{luo_macroscopic_2020} 
+Upon application of the field, $\tau_{\perp}$ slightly decreases while $\tau_{\parallel}$ increases. We have seen 
+that an increasing domain size decreases the tortuosity in our past work. \cite{karthikeyan_formation_2024} This 
+observation is in line with the domain size changes observed in Figure \ref{fig:domain_size_aniso-field_on}. The 
+results show that the tortuosity of the bijel is noticeably affected by the application of magnetic fields. 
+Earlier, we observed that the dynamics of structural response were not directly tied to the nematic order 
+parameter upon application of stimuli. To understand this phemomena, we focus more on the dynamics of the 
+particle monolayer. First, we visualize the particle monolayer of the bijels at the initial and final configuration 
+before and after application of a magnetic field.
+
+\begin{figure} 
+    \centering 
+    \includegraphics[scale=0.7]{../figures/results/paper2/particle_viz-field_on.png} 
+    \caption{Visualizations of bijels simulated under no fields at $t = 0$ (left) and $t = 10^5$ (right). 
+            The top column demonstrates the microstructure evolution if no field is used while the bottom column 
+            demonstrates the microstructure evolution when the system is exposed to a field strength of $\bar{B}_z = 1$. 
+            Particle reorientation to the direction of the field can be seen, resulting in coarsening of the domains.} 
+    \label{fig:particle_viz-field_on} 
+\end{figure}
+
+In Figure \ref{fig:particle_viz-field_on}, we see the effect of the application of the magnetic field on the monolayer. 
+The initial configuration of particles at the monolayer show that the orientations are random and that the particles 
+tend to lie flat on the interface. However, upon application of the magnetic field the particles orient to the field 
+direction. The effect that Gunther. et al. observed for bijels stabilized with anisotropic particles can also be 
+observed in these snapshots as the particles can be observed to have more local order in the final state than in 
+the initial state.
+
+Past work by Bresme and Faraudo and Davies investigating the reorientation of particles at interfaces under magnetic 
+fields have shown that a critical magnetic field exists, above which the particle orients to the field and below 
+which the particle orientation is a function of the capillary force and magnetic field derived force. 
+\cite{davies_interface_2014, bresme_orientational_2007} Particle adsorption into the interface with microparticles have 
+also been shown to be irreversible due to the high adsorption energy. Upon particle reorientation, the microstructure 
+change can be driven solely through particle unjamming and re-jamming, or it can be driven through the particles dragging 
+the interface during this process. The mechanism of unjamming and re-jamming can be investigated using the average 
+interfacial angle, $\psi$.
+
+Another factor affected by the application of the magnetic field is the Steinhardt 6 fold order parameter, $Q6$, 
+which characterized the local particle ordering. \cite{steinhardt_bond-orientational_1983} It has been used to 
+characterize crystallization, glass transitions and crystal structures for colloidal and molecular crystals. 
+We utilize the average across all particles on the interface, $\langle Q6 \rangle$ and track this parameter 
+as a function of time. Past work has identified that local crystallization of colloidal crystals takes place 
+at $\langle Q6 \rangle = 0.38$, and that $\langle Q6 \rangle^{HCP} = 0.485$. 
+\cite{steinhardt_bond-orientational_1983, toxvaerd_role_2020, mickel_shortcomings_2013}
+
+From Figure \ref{fig:interface_angle-nint-field_on}, we see that the initial value of $\psi \approx 80 ^{\circ}$ 
+indicating that at the start of the simulation, most of the particles lie flat on the interface. The variance from 
+the expected $\psi = 90 ^{\circ}$ can be expected from the presence of the curved interface, meaning that not all 
+particles will lie completely flat. This can also be seen in the microstructure visualizations in Figures 
+\ref{fig:microstructure_viz-field_on} and \ref{fig:particle_viz-field_on}. Upon application of the field, 
+$\psi$ decreases in all cases indicating that the particles are being oriented out of the interface. 
+However, the energy of adsorption is sufficiently high that the interface moves with the particle as it 
+reorients to the field. This is exhibited by the small change in $\psi$ and recovery to the initial value over time.
+
+We also observe from plotting $\langle Q6 \rangle$ over time that the application of magnetic fields on bijels causes a 
+local crystallization of the particle monolayer, as observed from the increase in $\langle Q6 \rangle > 0.38$ not 
+observed when a magnetic field is not applied. We also observe that for $\bar{B} > 0.2$, $\langle Q6 \rangle$ will 
+end up around $\langle Q6 \rangle = 0.45$ which indicates that they are close to being hexagonal close packed. 
+This is related to the nematic ordering of the particles causing the local arrangement of particles to become 
+more ordered. However, the arrangement of particles will not evolve at the same rate as the nematic order parameter 
+as the local arrangement of particles will experience steric hindrance during rearrangement at the interface.
+
+Figure \ref{fig:domain_size-field_on}, we observed a gap between the growth of the nematic order parameter and an 
+increase in the domain size. To probe why this occurs, we recast $\langle \psi \rangle$, $\langle Q_6 \rangle$ and 
+$S$ in terms of the physical phenomena they represent. The nematic order parameter represents the ordering of 
+particles to an average direction, which in the case of the application of a magnetic field, is the field direction. 
+Therefore, a timescale reliant on the nematic order parameter would represent a timescale of response rate limited 
+to the response to the magnetic field, which indicates a particle-field orientation dependence. We name this 
+timescale $\tau_S$. When applying a field to a bijel system with a randomly oriented particle monolayer, the 
+most significant transition point is the isotropic to nematic transition or when $S \geq 0.3$. We define $\tau_S$ 
+for this section of the analysis by identifying when $S \geq 0.3$.
+
+We can also do the same for $\langle \psi \rangle$ and $\langle Q_6 \rangle$. A timescale derived from 
+$\langle \psi \rangle$ named $\tau_{\langle \psi \rangle}$ represents the capillary timescale between the 
+interface and the particle which is also affected by interparticle interactions. Given the shape of the plot,
+we assign the $\tau_{\langle \psi \rangle}$ to be the time when the first minimum of $\langle \psi \rangle$ is 
+observed. A timescale derived from $\langle Q_6 \rangle$, named $\tau_{\langle Q_6 \rangle}$ is also calculated. 
+This represents the point when local crystallization of the particle monolayer occurs, calculated when 
+$\langle Q_6 \rangle \geq 0.38$. We omit $\bar{B} = 0$ as previous results have identified the domain size 
+changes observed there. We then plot the average domain size $L$ against time rescaled with these three 
+timescales in Figure \ref{fig:domain_size-field_on-scaled}.
+
+\begin{figure} 
+    \centering 
+    \includegraphics{../figures/results/paper2/domain_size-field_on-scaled.png} 
+    \caption{Plots of domain size with different timescales. The figure on the left rescales time with the nematic to 
+            isotropic transition time while the figure on the right rescales time with the time taken till the 1st minimum in 
+            the interface angle is reached. We show that the controlling timescale when applying a magnetic field onto bijels 
+            with disordered particles is the latter timescale, indicating that the dominating effect is steric hindrance as the 
+            interface is dragged along with the particles upon reorientation.} 
+    \label{fig:domain_size-field_on-scaled} 
+\end{figure}
+
+In Figure \ref{fig:domain_size-field_on-scaled}, the left plot plots the average domain size against time rescaled 
+using $\tau_S$. We see that the domain sizes do not collapse onto a single line, which is expected if we want to 
+explain the dynamics using the nematic order parameter. This confirms the observation made above that the dynamics 
+do not only depend on the reorientation of particles to the field. The middle plot demonstrates the average domain 
+size against time rescaled using $\tau_{\langle \psi \rangle}$. We see that there is good agreement between all 
+simulations, although the point when $\frac{t}{\tau_{\langle \psi \rangle}} = 1$ lies when the domain size transition 
+has started. The right plot demonstrates the domain size change after rescaling time with $\tau_{\langle Q_6 \rangle}$ 
+where we see good collapse between all plots while the domain size transition also begins at 
+$\frac{t}{\tau_{\langle Q_6 \rangle}} = 1$. The latter point demonstrates that the dynamics for the 
+structural response of randomly oriented particles are controlled by the local particle rearrangement at the 
+interface rather than the orientation of the particle to the magnetic field.
+
+From the evidence in Figure \ref{fig:domain_size-field_on-scaled}, two types of interfacial behaviors are characterized 
+in addition to that identified by Gunther et al. \cite{gunther_timescales_2014} The first type is what is observed for 
+$\bar{B} = 0.2$, where the interfacial coverage and average orientation of the particle to the field and to the 
+interface change in lock step. This causes the interface to reorient at the same rate as the particles reorienting 
+to the magnetic field. The second is observed for $\bar{B} = 0.5, 1$, where there is a time lag between particle 
+ordering, and the intiation of domain coarsening. In the latter scenario, at early times the particles are jolted 
+out of position before the large adsorption energy of the particles into the interface causes the interface to move 
+to the particle position, causing domain coarsening as the interfacial area reduces.
+
+\subsection{Increasing the applied field strength}
+
+\subsection{Reducing the applied field strength}

### 2025-02-14 chapters/LBM_technique.tex
Changes 1. Made tex files human readable again 2. Added content to paper3 tex file 3. Added licenses to some of the images from other papers

@@
-This work uses a multicomponent Lattice Boltzmann Method (LBM) to simulate the hydrodynamics of two partially miscible, incompressible fluids as implemented in LB3D.
-The LBM solves the Navier-Stokes equation at the incompressible limit, $\rho \frac{d \overrightarrow{u}}{dt} = \eta \Delta \overrightarrow{u} + \frac{\nabla P}{\rho} + F_{body}$, at low Mach and Reynolds numbers, incorporating density $(\rho)$, viscosity $(\eta)$, velocity $(u)$, pressure $(P)$, and body force $(F_{body})$.
-\cite{qian_lattice_1992, chin_lattice_2002, nourgaliev_lattice_2003} The Shan-Chen pseudopotential model is used to simulate the Cahn-Hilliard equation, $\frac{d c^k}{dt} = M^k\Delta \mu - \nabla u^k c^k$, for the non-ideal mixture model.
-\cite{shan_lattice_1993, shan_simulation_1994, he_lattice_1997, he_discrete_1998} $c^k$, $M^k$ and $u^k$ is the concentration, mobility and velocity of species $k$ respectively while $\mu$ is the free energy of system.
-Particle dynamics include Hertzian contact and lubrication forces, tracked with classical Newtonian mechanics, while particle-fluid coupling involves momentum exchange to simulate viscous dissipation.
-Particle-particle magnetic interactions are modeled using dipole interactions.
-\cite{davies_interface_2014, xie_direct_2017, xie_controllable_2021} A more detailed description of the model is provided in the following sections
+This work uses a multicomponent Lattice Boltzmann Method (LBM) to simulate the hydrodynamics of two partially miscible, 
+incompressible fluids as implemented in LB3D. The LBM solves the Navier-Stokes equation at the incompressible limit, 
+$\rho \frac{d \overrightarrow{u}}{dt} = \eta \Delta \overrightarrow{u} + \frac{\nabla P}{\rho} + F_{body}$, at low 
+Mach and Reynolds numbers, incorporating density $(\rho)$, viscosity $(\eta)$, velocity $(u)$, pressure $(P)$, and 
+body force $(F_{body})$. \cite{qian_lattice_1992, chin_lattice_2002, nourgaliev_lattice_2003} The Shan-Chen pseudopotential
+model is used to simulate the Cahn-Hilliard equation, $\frac{d c^k}{dt} = M^k\Delta \mu - \nabla u^k c^k$, for the non-ideal 
+mixture model. \cite{shan_lattice_1993, shan_simulation_1994, he_lattice_1997, he_discrete_1998} $c^k$, $M^k$ and $u^k$ is the 
+concentration, mobility and velocity of species $k$ respectively while $\mu$ is the free energy of system. Particle dynamics 
+include Hertzian contact and lubrication forces, tracked with classical Newtonian mechanics, while particle-fluid coupling 
+involves momentum exchange to simulate viscous dissipation. Particle-particle magnetic interactions are modeled using dipole 
+interactions. \cite{davies_interface_2014, xie_direct_2017, xie_controllable_2021} A more detailed description of the model is 
+provided in the following sections
 
@@
 
-The lattice boltzmann method works by evolving a population distribution $f_{i}(\mathbf{x}, t)$ on a cubic lattice with timestep $\Delta t$ with lengthscale $\Delta x$.
-\cite{qian_lattice_1992, succi_lattice_2018, he_theory_1997} The D3Q19 velocity set is used in this work with the indexes $i$ represent each of the 19 velocities and converves mass and momentum conservation to the second order.
-It can be seen in Figure \ref{fig:d3q19_lattice}.
-The algorithm is split into the collision step where the populations on each lattice grid cell are relaxed towards an equilibrium, followed by the advection step where populations in each velocity direction are propagated with velocity $\mathbf{c_i}$.
+The lattice boltzmann method works by evolving a population distribution $f_{i}(\mathbf{x}, t)$ on a cubic lattice with 
+timestep $\Delta t$ with lengthscale $\Delta x$. \cite{qian_lattice_1992, succi_lattice_2018, he_theory_1997} The D3Q19 
+velocity set is used in this work with the indexes $i$ represent each of the 19 velocities and converves mass and momentum 
+conservation to the second order. It can be seen in Figure \ref{fig:d3q19_lattice}. The algorithm is split into the 
+collision step where the populations on each lattice grid cell are relaxed towards an equilibrium, followed by the 
+advection step where populations in each velocity direction are propagated with velocity $\mathbf{c_i}$.
 
-The collision step occurs using a single relaxation time Bhatnagar-Gross-Krook (BGK) collision operator at relaxation rate $\tau$.
-\cite{bhatnagar_model_1954, qian_lattice_1992} The combined collision and advection LBM is expressed below in equation \ref{eq:LBM_BGK}
+The collision step occurs using a single relaxation time Bhatnagar-Gross-Krook (BGK) collision operator at relaxation 
+rate $\tau$. \cite{bhatnagar_model_1954, qian_lattice_1992} The combined collision and advection LBM is expressed below 
+in equation \ref{eq:LBM_BGK}
 
 \begin{equation}
-    f_{i}(\mathbf{x} + \mathbf{c}_{i}\Delta t, t + \Delta t) = f_{i}(\mathbf{x}, t) - \frac{1}{\tau}(f_{i}(\mathbf{x}, t) - f_{i}^{eq}(\mathbf{x}, t))
+    f_{i}(\mathbf{x} + \mathbf{c}_{i}\Delta t, t + \Delta t) = f_{i}(\mathbf{x}, t) - \frac{1}{\tau}(f_{i}(\mathbf{x}, t) 
+    - f_{i}^{eq}(\mathbf{x}, t))
     \label{eq:LBM_BGK}
@@
 The BGK operator limits simulations to low reynolds number and mach numbers to prevent numerical instabilities. 
-\cite{qian_lattice_1992} The kinematic viscosity if using the BGK operator is defined as $\nu = c_s^2(\tau - \frac{\Delta t}{2})$.
-The equilibrium distribution is obtained from a discretized expansion of the Maxwell-Boltzmann distribution to the second order.
-\cite{he_theory_1997, succi_lattice_2018} This is shown in equation \ref{eq:LBM_Feq}.
+\cite{qian_lattice_1992} The kinematic viscosity if using the BGK operator is defined as 
+$\nu = c_s^2(\tau - \frac{\Delta t}{2})$. The equilibrium distribution is obtained from a discretized expansion of the 
+Maxwell-Boltzmann distribution to the second order. \cite{he_theory_1997, succi_lattice_2018} This is shown in equation 
+\ref{eq:LBM_Feq}.
 
 \begin{equation}
-    f_{i}^{eq}(\mathbf{x}, t) = w_i\rho(1 + \frac{\mathbf{c_i} \cdot \mathbf{u}}{c_s^2} + \frac{(\mathbf{c_i} \cdot \mathbf{u})^2}{2c_s^4} + \frac{\mathbf{u} \cdot \mathbf{u}}{2c_s^2} + \frac{(\mathbf{c_i} \cdot \mathbf{u})^3}{6c_s^6} - \frac{(\mathbf{c_i} \cdot \mathbf{u})\mathbf{u}^2}{4c_s^3})
+    f_{i}^{eq}(\mathbf{x}, t) = w_i\rho(1 + \frac{\mathbf{c_i} \cdot \mathbf{u}}{c_s^2} + \frac{(\mathbf{c_i} \cdot 
+    \mathbf{u})^2}{2c_s^4} + \frac{\mathbf{u} \cdot \mathbf{u}}{2c_s^2} + \frac{(\mathbf{c_i} \cdot 
+    \mathbf{u})^3}{6c_s^6} - \frac{(\mathbf{c_i} \cdot \mathbf{u})\mathbf{u}^2}{4c_s^3})
     \label{eq:LBM_Feq}
@@
     \includegraphics[scale = 0.7]{figures/methods/d3q19_lattice.jpg}
-    \caption{D3Q19 lattice demonstrating the rest, nearest and next nearest direction that correspond to the 19 directions $(i)$ of the lattice with lattice velocity $c_{i}$.}
+    \caption{D3Q19 lattice demonstrating the rest, nearest and next nearest direction that correspond to the 19 
+    directions $(i)$ of the lattice with lattice velocity $c_{i}$. \cite{schmieschek_lb3d_2017} Reproduced from 
+    Schmieschek et al. under the Creative Commons license.}
     \label{fig:d3q19_lattice}
@@
 
-$\rho$ and $\textbf{u}$ in Equation \ref{eq:LBM_Feq} are defined as the macroscopic parameters for density and velocity and can be calculated from the mass distribution using $\rho = \sum f_i$ and $\rho \mathbf{u} = \sum f_i \mathbf{c}_i$ respectively.
-Using the Chapman-Enskog expansion, the Navier-Stokes equation at the incompressible limit at low-reynolds numbers can be recovered.
-\cite{qian_lattice_1992, he_lattice_1997} The regime accessible through this method is suitable for simulations in this work as the $ 1 \leq Re \leq 100 $ and the mach number, $Ma < 0.01$, fulfilling the stability criterion and usage requirements for the presented hydrodynamic model.
+$\rho$ and $\textbf{u}$ in Equation \ref{eq:LBM_Feq} are defined as the macroscopic parameters for density and velocity 
+and can be calculated from the mass distribution using $\rho = \sum f_i$ and $\rho \mathbf{u} = \sum f_i \mathbf{c}_i$ 
+respectively. Using the Chapman-Enskog expansion, the Navier-Stokes equation at the incompressible limit at low-reynolds 
+numbers can be recovered. \cite{qian_lattice_1992, he_lattice_1997} The regime accessible through this method is suitable 
+for simulations in this work as the $ 1 \leq Re \leq 100 $ and the mach number, $Ma < 0.01$, fulfilling the stability 
+criterion and usage requirements for the presented hydrodynamic model.
 
@@
 
-The SC model mimics Cahn-Hilliard type behaviour through a force applied from the other fluid species $k'$ in adjacent cells $\mathbf{x'}$ on fluid species $k$ at point $\mathbf{x}$.
-\cite{shan_lattice_1993, shan_simulation_1994, shan_multicomponent_1995, he_discrete_1998, jansen_bijels_2011, chin_lattice_2002} Both fluid species are defined by their own distribution equation defined in Equation \ref{eq:LBM_BGK} The strength of this force is controlled through an interaction parameter, $g_{kk'}$ with no contribution from self interaction of the fluid as these are set to zero.
-The SC force can then be written out in Equation \ref{eq:sc_model}.
+The SC model mimics Cahn-Hilliard type behaviour through a force applied from the other fluid species $k'$ in adjacent 
+cells $\mathbf{x'}$ on fluid species $k$ at point $\mathbf{x}$. \cite{shan_lattice_1993, shan_simulation_1994, 
+shan_multicomponent_1995, he_discrete_1998, jansen_bijels_2011, chin_lattice_2002} Both fluid species are defined
+ by their own distribution equation defined in Equation \ref{eq:LBM_BGK} The strength of this force is controlled 
+ through an interaction parameter, $g_{kk'}$ with no contribution from self interaction of the fluid as these are 
+ set to zero. The SC force can then be written out in Equation \ref{eq:sc_model}.
 
 \begin{equation}
-F_{k}^{SC}(\mathbf{x}, t) = -\Psi^{k}(\mathbf{x}, t)\sum_{k'}g_{cc'}\sum_{\mathbf{x'}}\Psi_{k'}(\mathbf{x'}, t)(\mathbf{x'} - \mathbf{x})
+F_{k}^{SC}(\mathbf{x}, t) = -\Psi^{k}(\mathbf{x}, t)\sum_{k'}g_{cc'}\sum_{\mathbf{x'}}\Psi_{k'}(\mathbf{x'}, t)(\mathbf{x'} 
+- \mathbf{x})
 \label{eq:sc_model}
@@
 
-An effective mass of each fluid at node $\mathbf{x}$ is used in place of the actual density to scale it between zero and one and is defined as $\psi^{c}(\mathbf{x},t) = \rho_{0}\left[1 - \exp(-\frac{\rho^{k}(\mathbf{x}, t)}{\rho_{0}})\right]$.
-In this model, the SC force is incorporated into the macroscopic velocities written as $\mathbf{u}_k =  \mathbf{u}_k + \frac{\tau}{\rho} F_{k}$ and finally the equilibrium distribution of each fluid species.
+An effective mass of each fluid at node $\mathbf{x}$ is used in place of the actual density to scale it between zero 
+and one and is defined as $\psi^{c}(\mathbf{x},t) = \rho_{0}\left[1 - \exp(-\frac{\rho^{k}(\mathbf{x}, t)}{\rho_{0}})\right]$. 
+In this model, the SC force is incorporated into the macroscopic velocities written as 
+$\mathbf{u}_k =  \mathbf{u}_k + \frac{\tau}{\rho} F_{k}$ and finally the equilibrium distribution of each fluid species.
 
@@
 
-Suspended particles will be coupled to the LB fluid based on the work conducted by Ladd.
-\cite{ladd_numerical_1994, aidun_direct_1998, ladd_lattice-boltzmann_2001} The particles follow Newtonian mechanics with force $\mathbf{F_p} = m_p\frac{d \mathbf{u_p} }{dt}$ and rotational inertia $\mathbf{D_p} = J_p \frac{d \mathbf{\omega_{p}}}{dt}$.
-$\mathbf{F_p}$ and $\mathbf{D_p}$ represent the force and torque acting on a particle with mass $m_p$ and moment of inertia $J_p$.
-$\mathbf{u}_p$ and $\mathbf{\omega_{p}}$ are the linear and angular velocities of the particle.
-The equations of motion are evolved over time using a leapfrog integrator.
-\cite{jansen_bijels_2011}
+Suspended particles will be coupled to the LB fluid based on the work conducted by Ladd. \cite{ladd_numerical_1994, 
+aidun_direct_1998, ladd_lattice-boltzmann_2001} The particles follow Newtonian mechanics with force 
+$\mathbf{F_p} = m_p\frac{d \mathbf{u_p} }{dt}$ and rotational inertia $\mathbf{D_p} = J_p \frac{d \mathbf{\omega_{p}}}{dt}$. 
+$\mathbf{F_p}$ and $\mathbf{D_p}$ represent the force and torque acting on a particle with mass $m_p$ and moment of inertia 
+$J_p$. $\mathbf{u}_p$ and $\mathbf{\omega_{p}}$ are the linear and angular velocities of the particle. The equations of 
+motion are evolved over time using a leapfrog integrator. \cite{jansen_bijels_2011}
 
-The particles are discretized on the lattice according to the method laid out in Ladd and Aidun \cite{ladd_lattice-boltzmann_2001}.
-Coupling to the LB fluid is done through momentum exchange with the fluid through modification of the velocity surrounding the fluid.
-The discretized particles have a no-slip boundary condition implemented as a modified bounce back boundary condition, with momentum exchange between particle and fluid done by changing the post collision population distribution, $f^{*}_{i}(\mathbf{x}, t)$, shown in Eq \ref{eq:md_LBM_mod}
+The particles are discretized on the lattice according to the method laid out in Ladd and Aidun 
+\cite{ladd_lattice-boltzmann_2001}. Coupling to the LB fluid is done through momentum exchange with the 
+fluid through modification of the velocity surrounding the fluid. The discretized particles have a no-slip 
+boundary condition implemented as a modified bounce back boundary condition, with momentum exchange between 
+particle and fluid done by changing the post collision population distribution, $f^{*}_{i}(\mathbf{x}, t)$, 
+shown in Eq \ref{eq:md_LBM_mod}
 
 \begin{equation}
-    f^{*}_{i'}(\mathbf{x}, t + \Delta t) = f^{*}_{i}(\mathbf{x}, t) - \frac{2 w_{i}}{c_s^2}\rho^k \mathbf{u}_{surf} \cdot \mathbf{c_i}
+    f^{*}_{i'}(\mathbf{x}, t + \Delta t) = f^{*}_{i}(\mathbf{x}, t) - \frac{2 w_{i}}{c_s^2}\rho^k \mathbf{u}_{surf} 
+    \cdot \mathbf{c_i}
     \label{eq:md_LBM_mod}
@@
 In this work, $i'$ is defined such that $\mathbf{c_i} = -\mathbf{c_{i'}}$ to satisfy the bounce-back boundary condition. 
-The fluid velocity at the particle surface, $\mathbf{u}_{surf}$, is the sum of the particle's linear and rotational velocities, $\mathbf{u}_{surf} = \mathbf{u_p} + R_i\mathbf{\omega_p}$.
-Advection of populations occurs after this exchange.
-The total force and torque on the particle are calculated by summing the total momentum over its surface.
-As particles move, they cover and uncover fluid grid points.
-Covered points are removed, while the composition of newly uncovered points in a multiphase fluid is averaged from adjacent grid points.
+The fluid velocity at the particle surface, $\mathbf{u}_{surf}$, is the sum of the particle's linear and rotational 
+velocities, $\mathbf{u}_{surf} = \mathbf{u_p} + R_i\mathbf{\omega_p}$. Advection of populations occurs after this exchange. 
+The total force and torque on the particle are calculated by summing the total momentum over its surface. As particles 
+move, they cover and uncover fluid grid points. Covered points are removed, while the composition of newly uncovered 
+points in a multiphase fluid is averaged from adjacent grid points.
 
@@
 
-Under 1 lattice unit additional lubrication forces are required to reduce the likelihood of particle overlap. For spherical particles, this is defined in Equation \ref{eq:sphere_lube}
+Under 1 lattice unit additional lubrication forces are required to reduce the likelihood of particle overlap. For 
+spherical particles, this is defined in Equation \ref{eq:sphere_lube}
 
@@
 
-where $R_i$ and $R_j$ are the radii of each particle involved in the interaction, $\mathbf{r}_{ij}$ is the distance vector between the particle centers, $\mathbf{u}_{ij}$ are the relative velocities of the particles and $\Delta_c$ is the cutoff distance when the lubrication force begins to act.
-A hertzian contact force is also added to ensure that there is no particle overlap, defined in Equation \ref{eq:hertz_def}
+where $R_i$ and $R_j$ are the radii of each particle involved in the interaction, $\mathbf{r}_{ij}$ is the distance
+ vector between the particle centers, $\mathbf{u}_{ij}$ are the relative velocities of the particles and $\Delta_c$ 
+ is the cutoff distance when the lubrication force begins to act. A hertzian contact force is also added to ensure 
+ that there is no particle overlap, defined in Equation \ref{eq:hertz_def}
 
@@
 
-$K_H$ is the force constant used to push particles apart.
-To correct for the anisotropic particles used in this work, the formulas presented in Eqs \ref{eq:sphere_lube} and \ref{eq:hertz_def} can be generalized using the route followed in Gunther et al.
-and Davies et al., inspired by Berne and Pechukas.
-\cite{gunther_timescales_2014, davies_interface_2014} They first begin by rewriting the lubrication and Hertzian contact forces in a dimensionless form below
+$K_H$ is the force constant used to push particles apart. To correct for the anisotropic particles used in this work, 
+the formulas presented in Eqs \ref{eq:sphere_lube} and \ref{eq:hertz_def} can be generalized using the route followed 
+in Gunther et al. and Davies et al., inspired by Berne and Pechukas. \cite{gunther_timescales_2014, davies_interface_2014} 
+They first begin by rewriting the lubrication and Hertzian contact forces in a dimensionless form below
 
 \begin{equation}
-    \phi_{H}(\hat{\mathbf{o_i}}, \hat{\mathbf{o_j}}, \hat{\mathbf{r_{ij}}}) = \epsilon(\hat{\mathbf{o_i}}, \hat{\mathbf{o_j}})\Bar{\phi_{H}}\left( \frac{r_{ij}}{\sigma(\hat{\mathbf{o_i}}, \hat{\mathbf{o_j}}, \hat{\mathbf{r_{ij}}})} \right)
+    \phi_{H}(\hat{\mathbf{o_i}}, \hat{\mathbf{o_j}}, \hat{\mathbf{r_{ij}}}) = \epsilon(\hat{\mathbf{o_i}}, 
+    \hat{\mathbf{o_j}})\Bar{\phi_{H}}\left( \frac{r_{ij}}{\sigma(\hat{\mathbf{o_i}}, \hat{\mathbf{o_j}}, 
+    \hat{\mathbf{r_{ij}}})} \right)
     \label{eq:hertz_anisotropic}
@@
 
-Equation \ref{eq:hertz_anisotropic} defines the generalization of the Hertz force to allow simulation of ellipsoidal particles inspired by Berne and Pechukas.
-First, the hertzian force is made a function of orientation through the addition of eccentricity, $\chi = \frac{R_p^2 - R_o^2}{R_p^2 + R_o^2}$ and an orientation dependent forces, where $\epsilon(\hat{\mathbf{o_i}}, \hat{\mathbf{o_j}}) = \frac{\Bar{\epsilon}}{\sqrt{1 - \chi(\hat{\mathbf{o_i}}, \hat{\mathbf{o_j}})^2}}$, and $\sigma = \frac{\Bar{\sigma}}{\sqrt{1 - \frac{\chi}{2}( \frac{(\hat{\mathbf{r_{ij}}}\hat{\mathbf{o_i}} +  \hat{\mathbf{r_{ij}}}\hat{\mathbf{o_j}})^2}{1 + \chi \hat{\mathbf{o_i}}\hat{\mathbf{o_j}}} +  \frac{(\hat{\mathbf{r_{ij}}}\hat{\mathbf{o_i}} -  \hat{\mathbf{r_{ij}}}\hat{\mathbf{o_j}})^2}{1 - \chi \hat{\mathbf{o_i}}\hat{\mathbf{o_j}}})}}$, $\Bar{\sigma} = 2R_{\perp}$.
-\cite{gunther_lattice_2013, gunther_timescales_2014, davies_assembling_2014}
+Equation \ref{eq:hertz_anisotropic} defines the generalization of the Hertz force to allow simulation of ellipsoidal 
+particles inspired by Berne and Pechukas. First, the hertzian force is made a function of orientation through the 
+addition of eccentricity, $\chi = \frac{R_p^2 - R_o^2}{R_p^2 + R_o^2}$ and an orientation dependent forces, where 
+$\epsilon(\hat{\mathbf{o_i}}, \hat{\mathbf{o_j}}) = \frac{\Bar{\epsilon}}{\sqrt{1 - \chi(\hat{\mathbf{o_i}}, 
+\hat{\mathbf{o_j}})^2}}$, and $\sigma = \frac{\Bar{\sigma}}{\sqrt{1 - \frac{\chi}{2}( 
+\frac{(\hat{\mathbf{r_{ij}}}\hat{\mathbf{o_i}} +  \hat{\mathbf{r_{ij}}}\hat{\mathbf{o_j}})^2}{1 + 
+\chi \hat{\mathbf{o_i}}\hat{\mathbf{o_j}}} +  \frac{(\hat{\mathbf{r_{ij}}}\hat{\mathbf{o_i}} -  
+\hat{\mathbf{r_{ij}}}\hat{\mathbf{o_j}})^2}{1 - \chi \hat{\mathbf{o_i}}\hat{\mathbf{o_j}}})}}$, 
+$\Bar{\sigma} = 2R_{\perp}$. \cite{gunther_lattice_2013, gunther_timescales_2014, davies_assembling_2014}
 
-A similar generalization process is done for the lubrication force, resulting in Equation \ref{eq:md_force} where $\mathbf{\Bar{F}}(r) = \hat{\mathbf{r_{ij}}}(\hat{\mathbf{r_{ij}}}(\mathbf{u}_i - \mathbf{u}_j))\left( \frac{1}{r - 1} - \frac{\sigma}{\Delta_{c}} \right)$.
+A similar generalization process is done for the lubrication force, resulting in Equation \ref{eq:md_force} where 
+$\mathbf{\Bar{F}}(r) = \hat{\mathbf{r_{ij}}}(\hat{\mathbf{r_{ij}}}(\mathbf{u}_i - \mathbf{u}_j))\left( \frac{1}{r - 1} - 
+\frac{\sigma}{\Delta_{c}} \right)$.
 
 \begin{equation}
-    \mathbf{F_{ij}}(\hat{\mathbf{o_i}}, \hat{\mathbf{o_j}}, \hat{\mathbf{r_{ij}}}) = \epsilon(\hat{\mathbf{o_i}}, \hat{\mathbf{o_j}})\mathbf{\mathbf{F_{ij}}}\left( \frac{r_{ij}}{\sigma(\hat{\mathbf{o_i}}, \hat{\mathbf{o_j}}, \hat{\mathbf{r_{ij}}})} \right)
+    \mathbf{F_{ij}}(\hat{\mathbf{o_i}}, \hat{\mathbf{o_j}}, \hat{\mathbf{r_{ij}}}) = \epsilon(\hat{\mathbf{o_i}}, 
+    \hat{\mathbf{o_j}})\mathbf{\mathbf{F_{ij}}}\left( \frac{r_{ij}}{\sigma(\hat{\mathbf{o_i}}, \hat{\mathbf{o_j}}, 
+    \hat{\mathbf{r_{ij}}})} \right)
     \label{eq:md_force}
@@
 \begin{equation}
-    \mathbf{U_{ij}} = \frac{\mu_0 m_i m_j}{4\pi r_{ij}^{3}} \left[ \Hat{\mathbf{o_i}} \cdot \Hat{\mathbf{o_j}} - 3(\Hat{\mathbf{o_i}} \cdot \Hat{\mathbf{r_{ij}}})(\Hat{\mathbf{o_j}} \cdot \Hat{\mathbf{r_{ij}}}) \right]
+    \mathbf{U_{ij}} = \frac{\mu_0 m_i m_j}{4\pi r_{ij}^{3}} \left[ \Hat{\mathbf{o_i}} \cdot \Hat{\mathbf{o_j}} - 
+    3(\Hat{\mathbf{o_i}} \cdot \Hat{\mathbf{r_{ij}}})(\Hat{\mathbf{o_j}} \cdot \Hat{\mathbf{r_{ij}}}) \right]
     \label{eq:magnet_potential}
@@
 
-Where $\mu_0 = 4\pi \cdot 10^{-7} \frac{H}{m}$,  $\Hat{\mathbf{o_i}}$ is the orientation unit vector of particle $i$, $\Hat{\mathbf{r_{ij}}}$ is the distance vector between particles $i$ and $j$ and $m_i$ is the magnitude the magnetic dipole of particle $i$.
-From the potential, the force and torque of the dipole force between particles can be found.
-These expressions are shown in equations \ref{eq:dipole_magnetic_force} and \ref{eq:dipole_magnetic_torque} for the force and torque respectively.
+Where $\mu_0 = 4\pi \cdot 10^{-7} \frac{H}{m}$,  $\Hat{\mathbf{o_i}}$ is the orientation unit vector of particle 
+$i$, $\Hat{\mathbf{r_{ij}}}$ is the distance vector between particles $i$ and $j$ and $m_i$ is the magnitude the 
+magnetic dipole of particle $i$. From the potential, the force and torque of the dipole force between particles 
+can be found. These expressions are shown in equations \ref{eq:dipole_magnetic_force} and \ref{eq:dipole_magnetic_torque} 
+for the force and torque respectively.
 
 \begin{equation}
-    \mathbf{F}_{ij} = \frac{3 \mu_0}{4 \pi} [\frac{5(m_i \cdot \mathbf{r}_{ij})(m_j \cdot \mathbf{r}_{ij})}{|\mathbf{r}_{ij}|^7}\mathbf{r}_{ij} - \frac{(m_i \cdot m_{j})\mathbf{r}_{ij} + (m_i \cdot \mathbf{r}_{ij})m_i + (m_j \cdot \mathbf{r}_{ij})m_j }{|\mathbf{r}_{ij}|^5})]
+    \mathbf{F}_{ij} = \frac{3 \mu_0}{4 \pi} [\frac{5(m_i \cdot \mathbf{r}_{ij})(m_j 
+    \cdot \mathbf{r}_{ij})}{|\mathbf{r}_{ij}|^7}\mathbf{r}_{ij} - \frac{(m_i \cdot m_{j})\mathbf{r}_{ij} + 
+    (m_i \cdot \mathbf{r}_{ij})m_i + (m_j \cdot \mathbf{r}_{ij})m_j }{|\mathbf{r}_{ij}|^5}]
 \label{eq:dipole_magnetic_force}
@@
 \begin{equation}
-    \mathbf{T}_{ij} = \frac{\mu_0}{4 \pi}[ \frac{3(m_j \cdot \mathbf{r}_{ij})m_i \times \mathbf{r}_{ij} }{|\mathbf{r}_{ij}|^5} - \frac{m_i \cdot m_j }{|\mathbf{r}_{ij}|^3} ]
+    \mathbf{T}_{ij} = \frac{\mu_0}{4 \pi}[ \frac{3(m_j \cdot \mathbf{r}_{ij})m_i \times \mathbf{r}_{ij} }
+    {|\mathbf{r}_{ij}|^5} - \frac{m_i \cdot m_j }{|\mathbf{r}_{ij}|^3} ]
     \label{eq:dipole_magnetic_torque}
@@
 
-Equations \ref{eq:magnet_force} and \ref{eq:magnet_torque} are used to calculate the force and torque that the field exerts on each particle.
+Equations \ref{eq:magnet_force} and \ref{eq:magnet_torque} are used to calculate the force and torque that the 
+field exerts on each particle.
 
@@
 
-The total force and torque exerted on each particle is the sum of the particle dipole interaction and the field dependent contribution.
+The total force and torque exerted on each particle is the sum of the particle dipole interaction and the field 
+dependent contribution.

### 2025-02-14 chapters/introduction.tex
Changes 1. Made tex files human readable again 2. Added content to paper3 tex file 3. Added licenses to some of the images from other papers

@@
 Porous materials are defined as materials that contain pores or voids within their structure where no material is present. 
-Homogeneous materials in contrast have a uniform structure with no pores.
-These pores vary in shape and distribution, with materials being categorized by pore size per IUPAC as $(L)$ as microporous $(L < 2nm)$, mesoporous $(2nm < L < 50nm)$ and macroporous materials $(50nm < L)$.
-\textcolor{blue}{https://doi.org/10.1351/pac198557040603} The presence of these pores increases the surface area to volume ratio of porous materials compared to their homogeneous counterparts.
-A common experimental technique used to estimate the surface area of a porous material derived from Brunauer-Emmett-Teller(BET) theory shows that porous materials can have surface areas more than a hundred times larger than homogenous materials, dependent upon the pore size and pore size distribution.
-\cite{shimizu_surface_2022}
+Homogeneous materials in contrast have a uniform structure with no pores. These pores vary in shape and distribution, with materials 
+being categorized by pore size per IUPAC as $(L)$ as microporous $(L < 2nm)$, mesoporous $(2nm < L < 50nm)$ and macroporous materials 
+$(50nm < L)$. \textcolor{blue}{https://doi.org/10.1351/pac198557040603} The presence of these pores increases the surface area to volume 
+ratio of porous materials compared to their homogeneous counterparts. A common experimental technique used to estimate the surface area 
+of a porous material derived from Brunauer-Emmett-Teller(BET) theory shows that porous materials can have surface areas more than a 
+hundred times larger than homogenous materials, dependent upon the pore size and pore size distribution. \cite{shimizu_surface_2022}
 
-In addition to the pore size and its distribution within the material, the arrangement of pores within the material contribute to the performance of the synthesized material, commonly measured using the tortuosity.
-Tortuosity here is defined as the path length between two points divided by the euclidean length between those points.
-A tortuosity larger than one implies that the path length is longer than the euclidean length, and vice versa if the tortuosity if less than one.
-Highlighting the confluence of these factors are the large variety of tailored microstructures for various applications.
-Each of the specified pore length scales have their unique uses, such as microporous materials being used as zeolites and photonic bandgap materials while macroporous materials facilitate greater transport properties, suitable in applications such as battery electrodes and drug delivery systems.
-\cite{chen_tortuosity_2020, ebner_tortuosity_2014}
+In addition to the pore size and its distribution within the material, the arrangement of pores within the material contribute to the 
+performance of the synthesized material, commonly measured using the tortuosity. Tortuosity here is defined as the path length between 
+two points divided by the euclidean length between those points. A tortuosity larger than one implies that the path length is longer 
+than the euclidean length, and vice versa if the tortuosity if less than one. Highlighting the confluence of these factors are the 
+large variety of tailored microstructures for various applications. Each of the specified pore length scales have their unique uses, 
+such as microporous materials being used as zeolites and photonic bandgap materials while macroporous materials facilitate greater 
+transport properties, suitable in applications such as battery electrodes and drug delivery systems. \cite{chen_tortuosity_2020, 
+ebner_tortuosity_2014}
 
-These range from Metal Organic Framework(MOF) enhanced gas adsorption, \textcolor{blue}{https://doi.org/10.1002/admi.201400040} This increased surface area to volume ratio enhances the properties of the base material in applications such as catalysis, battery electrodes and drug delivery systems among many more making them valuable microstructures.
-\cite{cha_bicontinuous_2019, samdani_bicontinuous_2017, thorson_bijel-templated_2019}
+These range from Metal Organic Framework(MOF) enhanced gas adsorption, \textcolor{blue}{https://doi.org/10.1002/admi.201400040} 
+This increased surface area to volume ratio enhances the properties of the base material in applications such as catalysis, 
+battery electrodes and drug delivery systems among many more making them valuable microstructures. \
+cite{cha_bicontinuous_2019, samdani_bicontinuous_2017, thorson_bijel-templated_2019}
 
@@
     \includegraphics[scale = 0.5]{figures/introduction/bijel_templating.png}
-    \caption{Fabrication of a graphite oxide battery electrode using bijel template. \cite{garcia_scalable_2019}}
+    \caption{Fabrication of a graphite oxide battery electrode using bijel template. Reproduced from Garcie et al. under license number 1548092-1. \cite{garcia_scalable_2019}}
     \label{fig:bijel_template}
@@
 
-Conventionally, porous materials have been synthesized through solvothermal synthesis or pyrolysis used in the synthesis of zeolites and activated carbon respectively.
-With more targeted applications of porous materials, synthesis techniques such as sol-gel synthesis, freeze drying and various forms of templating have been utilized to synthesize porous materials from length scales of $10^{-9}m$ to $10^{-3}m$.
-\cite{stein_morphological_2008, ray_comprehensive_2016, cervellere_mesoscopic_2019, garcia-bennett_unique_2020, zhang_emulsion_2019, alves-rosa_design_2013} Industry has also taken up techniques such as electrospinning to generate non woven fibers, used in membrane synthesis.
-Templating techniques in particular offer access to various pore length scales, bottom up synthesis and functionality through leveraging various physical phenomena.
-Colloidal templating works through the close packing of particles.
-Surfactant and polymer templating work through the assembly of macromolecules into their equilibrium configurations.
-Emulsion templating utilizes the phase separation of partially misicble liquids to form the pore structure of a porous material.
+Conventionally, porous materials have been synthesized through solvothermal synthesis or pyrolysis used in the synthesis of zeolites and 
+activated carbon respectively. With more targeted applications of porous materials, synthesis techniques such as sol-gel synthesis, 
+freeze drying and various forms of templating have been utilized to synthesize porous materials from length scales of $10^{-9}m$ to 
+$10^{-3}m$. \cite{stein_morphological_2008, ray_comprehensive_2016, cervellere_mesoscopic_2019, garcia-bennett_unique_2020, zhang_emulsion_2019, 
+alves-rosa_design_2013} Industry has also taken up techniques such as electrospinning to generate non woven fibers, used in membrane synthesis. 
+Templating techniques in particular offer access to various pore length scales, bottom up synthesis and functionality through leveraging various 
+physical phenomena. Colloidal templating works through the close packing of particles. Surfactant and polymer templating work through the 
+assembly of macromolecules into their equilibrium configurations. Emulsion templating utilizes the phase separation of partially miscible 
+liquids to form the pore structure of a porous material.
 
-Emulsion templating offers access to a large length scale of tunable pore sizes, continous production through microfluidic junctions or other flow media, functionalization through the addition of additives or stabilizers, scope of accessible microstructures and mild synthesis conditions.
-It can further be extended to include heirarchical porosity, further enhancing its utility and fabricated material properties.
-\cite{yang_hierarchically_2017, thompson_hierarchically_2019, wang_morphology_2023} Figure \ref{fig:bijel_template} demonstrates how emulsion templating allows bottom up synthesis of hierarchically porous materials, although other examples do exist.
+Emulsion templating offers access to a large length scale of tunable pore sizes, continuous production through microfluidic junctions or 
+other flow media, functionalization through the addition of additives or stabilizers, scope of accessible microstructures and mild synthesis 
+conditions. It can further be extended to include heirarchical porosity, further enhancing its utility and fabricated material properties. 
+\cite{yang_hierarchically_2017, thompson_hierarchically_2019, wang_morphology_2023} Figure \ref{fig:bijel_template} demonstrates how emulsion 
+templating allows bottom up synthesis of hierarchically porous materials, although other examples do exist. 
 \cite{garcia_scalable_2019, santiago_cordoba_aerobijels_2020, thorson_bijel-templated_2019, lu_controllable_2020, wang_morphology_2023}
@@
     \includegraphics[scale = 0.3]{figures/introduction/bijel_coarsening.jpg}
-    \caption{Initiation and arrest of spinodal decomposition as particles adsorb onto the interface, followed by jamming once the interfacial area matches the cross sectional area of the adsorbed particles\cite{stratford_colloidal_2005}}
+    \caption{Initiation and arrest of spinodal decomposition as particles adsorb onto the interface, followed by jamming once the 
+    interfacial area matches the cross sectional area of the adsorbed particles\cite{stratford_colloidal_2005}. Reproduced from Adhikari et al. 
+    under license number 5966820525314.}
     \label{fig:bijel_coarsen}
@@
 One such emulsion microstructure of interest is the bicontinuous interfacially jammed emulsion gel(bijel). 
-\cite{stratford_colloidal_2005, herzig_bicontinuous_2007, lee_bicontinuous_2010} Bijels are made by arresting the spinodal decomposition of partially miscible liquids, caused by particles adsorbing on the interface and jamming as the cross sectional area of the particles match that of the interface, summarized in Figure \ref{fig:bijel_coarsen}.
-Bijels are of interest due to their co-continuous, tortuous microstructure which represent excellent fits for several porous material applications.
+\cite{stratford_colloidal_2005, herzig_bicontinuous_2007, lee_bicontinuous_2010} Bijels are made by arresting the spinodal decomposition of 
+partially miscible liquids, caused by particles adsorbing on the interface and jamming as the cross sectional area of the particles match that 
+of the interface, summarized in Figure \ref{fig:bijel_coarsen}. Bijels are of interest due to their co-continuous, tortuous microstructure which 
+represent excellent fits for several porous material applications.
 
-Bijels were discovered in simulations in 2005 and experimentally realized in 2007 when a mixture of water and 2-6-lutidine mixed with surface modified silica nanoparticles underwent thermally induced spinodal decomposition.
-\cite{stratford_colloidal_2005, herzig_bicontinuous_2007} Since then, multiple other casting mixtures and particle chemistry's have been used to fabricate bijels using Thermally Induced Spinodal Decomposition (TIPS).
-\cite{lee_bicontinuous_2010, bai_dynamics_2015} More recently, techniques such as Solvent Transfer Induced Phase Separation (STrIPS), Vapor Induced Phase Separation (VIPS), Non-solvent Induced Phase Separation (NIPS), homogenization and liquid in liquid printing have been utilized to fabricate bijels, demonstrating the ability for bijels to be synthesized in a continuous process, suitable for scale up.
-\cite{haase_continuous_2015, wang_scalable_2020, cai_bijels_2017, yabuno_preparation_2020, wang_bicontinuous_2023, amirfattahi_fabrication_2024} These techniques also offer preparation of bijels in various different shapes and form-factors for various uses such as fibers, coatings and capsules, seen in Figure \ref{fig:strips}.
-\cite{haase_continuous_2015, boakye-ansah_controlling_2020, kharal_hightensile_2020, wang_bicontinuous_2023}
-
+Bijels were discovered in simulations in 2005 and experimentally realized in 2007 when a mixture of water and 2-6-lutidine mixed with 
+surface modified silica nanoparticles underwent thermally induced spinodal decomposition. \cite{stratford_colloidal_2005, herzig_bicontinuous_2007}
+Since then, multiple other casting mixtures and particle chemistry's have been used to fabricate bijels using Thermally Induced Spinodal 
+Decomposition (TIPS). \cite{lee_bicontinuous_2010, bai_dynamics_2015} More recently, techniques such as Solvent Transfer Induced Phase 
+Separation (STrIPS), Vapor Induced Phase Separation (VIPS), Non-solvent Induced Phase Separation (NIPS), homogenization and liquid in 
+liquid printing have been utilized to fabricate bijels, demonstrating the ability for bijels to be synthesized in a continuous process, 
+suitable for scale up. \cite{haase_continuous_2015, wang_scalable_2020, cai_bijels_2017, yabuno_preparation_2020, wang_bicontinuous_2023, 
+amirfattahi_fabrication_2024} These techniques also offer preparation of bijels in various different shapes and form-factors for various 
+uses such as fibers, coatings and capsules, seen in Figure \ref{fig:strips}. \cite{haase_continuous_2015, boakye-ansah_controlling_2020, 
+kharal_hightensile_2020, wang_bicontinuous_2023}
 \begin{figure}[h]
@@
     \includegraphics[scale = 2]{figures/literature_review/STRIPPS.jpg}
-    \caption{STrIPS in action. Extrusion of the bijel casting mixture into a non-solvent bath, followed by removal of solvent from the casting mixture through diffusion. \cite{haase_continuous_2015}}
+    \caption{STrIPS in action. Extrusion of the bijel casting mixture into a non-solvent bath, followed by removal of solvent from 
+    the casting mixture through diffusion. Reproduced from Haase et al. 2015 under license number 5913140219015. \cite{haase_continuous_2015}}
     \label{fig:strips}
@@
 
-However, these techniques all depend upon controlling the rate of phase separation, which involve changing the casting mixture composition to modify the obtained microstructure.
-In STrIPS, the obtained bijel microstructure is a function of the flow rate and selected co-solvent, selected to change the rate of phase separation.
-\cite{haase_continuous_2015} This affects material properties such as the mechanical performance of the bijel, important in fields such as catalysis where rigidity of the particle monolayer is crucial in ensuring consistent performance.
-\cite{reeves_particle-size_2015, haase_situ_2016, boakye-ansah_controlling_2020} Identification of other techniques that can be utilized to modify the microstructure of a bijel would enable bijels to continue using the desired composition of constituents, while also adding other unique properties.
-Stimuli response offers one such road to microstructure modification.
+However, these techniques all depend upon controlling the rate of phase separation, which involve changing the casting mixture composition to 
+modify the obtained microstructure. In STrIPS, the obtained bijel microstructure is a function of the flow rate and selected co-solvent, 
+selected to change the rate of phase separation. \cite{haase_continuous_2015} This affects material properties such as the mechanical 
+performance of the bijel, important in fields such as catalysis where rigidity of the particle monolayer is crucial in ensuring consistent 
+performance. \cite{reeves_particle-size_2015, haase_situ_2016, boakye-ansah_controlling_2020} Identification of other techniques that can 
+be utilized to modify the microstructure of a bijel would enable bijels to continue using the desired composition of constituents, while 
+also adding other unique properties. Stimuli response offers one such road to microstructure modification.
 
@@
 
-Stimuli response based on pH, external fields and temperature have been used in past works when looking at modifying the microstructure of emulsion droplets for enhanced oil recovery, pharmaceutical and cell adhesion.
-\cite{haase_nanoparticle_2011, tham_magnetophoresis_2021, cui_stabilizing_2013, manfredini_limonene--water_2021}  It was shown that external fields can be used to move, control emulsion stability and elongate emulsion droplets.
-\cite{tham_magnetophoresis_2021, cui_stabilizing_2013} \textcolor{blue}{https://pubs.acs.org/doi/10.1021/la047691n} Bijels stabilized spherical particles under a magnetic field showed no meaningful microstructure changes.
-\cite{kim_bijels_2010} Bijels stabilized with spherical particles under an electric field showed more promise.
-\cite{carmack_tuning_2018} However, magnetic fields offer more targeted stimuli response, allowing even weak fields to incite a response.
-Magnetic fields non-interaction in many situations offer advantages to many of the desired uses of bijels within pharmaceutical or bioengineering applications.
-\cite{vanoli_bijels_2022, thorson_bijel-templated_2019, thorson_composite_2018} These same applications also have a need for in-situ microstructure modification that would enable tunable drug delivery rates, separations or catalyst efficiency and permeability improvements in the system.
-Therefore, identifying schemes that allow modification of the pore size and tortuosity  without synthesis of a new material would enhance the use case of bijels.
+Stimuli response based on pH, external fields and temperature have been used in past works when looking at modifying the microstructure of 
+emulsion droplets for enhanced oil recovery, pharmaceutical and cell adhesion. \cite{haase_nanoparticle_2011, tham_magnetophoresis_2021, 
+cui_stabilizing_2013, manfredini_limonene--water_2021}  It was shown that external fields can be used to move, control emulsion stability 
+and elongate emulsion droplets. \cite{tham_magnetophoresis_2021, cui_stabilizing_2013} 
+\textcolor{blue}{https://pubs.acs.org/doi/10.1021/la047691n} Bijels stabilized spherical particles under a magnetic field showed no 
+meaningful microstructure changes. \cite{kim_bijels_2010} Bijels stabilized with spherical particles under an electric field showed 
+more promise. \cite{carmack_tuning_2018} However, magnetic fields offer more targeted stimuli response, allowing even weak fields to 
+incite a response. Magnetic fields non-interaction in many situations offer advantages to many of the desired uses of bijels within 
+pharmaceutical or bioengineering applications. \cite{vanoli_bijels_2022, thorson_bijel-templated_2019, thorson_composite_2018} These 
+same applications also have a need for in-situ microstructure modification that would enable tunable drug delivery rates, separations or
+ catalyst efficiency and permeability improvements in the system. Therefore, identifying schemes that allow modification of the pore size 
+ and tortuosity  without synthesis of a new material would enhance the use case of bijels.
 
 Anisotropic particles at interfaces have shown self assembly due to the presence of multi-polar pressure fields caused by interface deformation. 
-Self assembly has also been shown for ellipsoidal particles at interfaces under magnetic fields.
-Ellipsoidal particles have also been shown to exhibit magnetic field controlled orientations at interfaces, as Bresme and Faraudo showed.
-\cite{bresme_orientational_2007, davies_interface_2014} Under magnetic fields, assemblies of multiple ellipsoidal particles have been shown to have energy minima at unexpected locations.
-\cite{newton_influence_2014, newton_capillary_2018} Thus ellipsoidal particles at interfaces, whose orientations and packing can be controlled through external fields, offer a potential means to control the microstructure of bijels.
+Self assembly has also been shown for ellipsoidal particles at interfaces under magnetic fields. Ellipsoidal particles have also been shown to 
+exhibit magnetic field controlled orientations at interfaces, as Bresme and Faraudo showed. \cite{bresme_orientational_2007, davies_interface_2014}
+ Under magnetic fields, assemblies of multiple ellipsoidal particles have been shown to have energy minima at unexpected locations. 
+ \cite{newton_influence_2014, newton_capillary_2018} Thus ellipsoidal particles at interfaces, whose orientations and packing can be 
+ controlled through external fields, offer a potential means to control the microstructure of bijels.
 
-Bijels present a bottom up synthesis strategy for porous material templates for hard and soft material applications in a scalable and continuous method using STrIPS and other techniques.
-However, the microstructure control these techniques offer are intrinsically linked to the casting mixture composition.
-Stimuli response offers a way to modify the microstructure of bijels while still maintaining the various form factors these continuous synthesis techniques can output.
-While stimuli response has been explored in the past using bijels stabilized with spherical particles with little success, anisotropic particles are poised to allow microstructure modification of bijels upon application of an external field.
-This technique also has the potential to allow for post synthesis microstructure modification.
-Therefore, this work seeks to identify a means to control the microstructure of a bijel stabilized with magnetically responsive ellipsoidal particles using magnetic fields.
+Bijels present a bottom up synthesis strategy for porous material templates for hard and soft material applications in a scalable and 
+continuous method using STrIPS and other techniques. However, the microstructure control these techniques offer are intrinsically linked 
+to the casting mixture composition. Stimuli response offers a way to modify the microstructure of bijels while still maintaining the 
+various form factors these continuous synthesis techniques can output. While stimuli response has been explored in the past using bijels 
+stabilized with spherical particles with little success, anisotropic particles are poised to allow microstructure modification of bijels 
+upon application of an external field. This technique also has the potential to allow for post synthesis microstructure modification. 
+Therefore, this work seeks to identify a means to control the microstructure of a bijel stabilized with magnetically responsive 
+ellipsoidal particles using magnetic fields.
 
@@
 
-\textcolor{blue}{Add commentary about past results with bijels and why we use anisotropic particles in bijels.
-Changes this makes} Therefore, identification of a scheme which allows for tunability of the microstructure, independent of the composition of the casting mixture and post synthesis is the goal of this work.
+\textcolor{blue}{Add commentary about past results with bijels and why we use anisotropic particles in bijels. Changes this makes} Therefore, 
+identification of a scheme which allows for tunability of the microstructure, independent of the composition of the casting mixture and post 
+synthesis is the goal of this work.
 
@@
 
-This work seeks to identify means to control the bijel microstructure independent of the casting mixture composition by utilizing magnetic stimuli on bijels stabilized with magnetically responsive ellipsoidal particles.
-The proposed mechanism of microstructure modification is driven through reorientation of the particles to the applied magnetic field altering how the particles pack on the interface.
-By changing the interfacial packing of the particles, we change when the particles jam, which in turn changes the jamming point of the bijel.
-This mechanism is predicted to be effective during and after synthesis.
-The processability of bijels fabricated using this technique will also be investigated to ascertain how changes in particle packing affect the rheology of the material.
-An overview of three major research aims will be presented below.
+This work seeks to identify means to control the bijel microstructure independent of the casting mixture composition by utilizing magnetic 
+stimuli on bijels stabilized with magnetically responsive ellipsoidal particles. The proposed mechanism of microstructure modification is 
+driven through reorientation of the particles to the applied magnetic field altering how the particles pack on the interface. By changing the 
+interfacial packing of the particles, we change when the particles jam, which in turn changes the jamming point of the bijel. This mechanism is 
+predicted to be effective during and after synthesis. The processability of bijels fabricated using this technique will also be investigated to 
+ascertain how changes in particle packing affect the rheology of the material. An overview of three major research aims will be presented below.
 
@@
 
-The jamming point of a bijel controls the obtained microstructure, as shown by previous work comparing the length scale of bijels synthesized with different particle volume fractions.
-It has also been shown how magnetic fields can be used to self assemble ansisotropic particles at interfaces and how they can tilt out of the interface.
-\cite{davies_interface_2014, davies_assembling_2014} On a curved interface with many other particles, it is unknown how multiple particles orienting to a field and having regular structure will affect when and how the bijel will jam.
-\cite{bresme_orientational_2007, davies_interface_2014}
+The jamming point of a bijel controls the obtained microstructure, as shown by previous work comparing the length scale of bijels synthesized 
+with different particle volume fractions. It has also been shown how magnetic fields can be used to self assemble ansisotropic particles at 
+interfaces and how they can tilt out of the interface. \cite{davies_interface_2014, davies_assembling_2014} On a curved interface with many 
+other particles, it is unknown how multiple particles orienting to a field and having regular structure will affect when and how the bijel 
+will jam. \cite{bresme_orientational_2007, davies_interface_2014}
 
-To assess the obtained microstructure upon application of a field during formation of the bijel, homogenous mixtures containing spherical and ellipsoidal particles will be subjected to field strengths above and below the critical field strength when particle orientations to the interface are controlled by the applied field strength, as calculated by Bresme and Faraudo for the particle used.
-This selection of fields will allow insight into the controlling mechanisms behind microstructural changes observed, allowing verification of the hypothesis and ascertainment where the most control over the microstructure can be exercised.
+To assess the obtained microstructure upon application of a field during formation of the bijel, homogenous mixtures containing spherical and 
+ellipsoidal particles will be subjected to field strengths above and below the critical field strength when particle orientations to the 
+interface are controlled by the applied field strength, as calculated by Bresme and Faraudo for the particle used. This selection of fields 
+will allow insight into the controlling mechanisms behind microstructural changes observed, allowing verification of the hypothesis and 
+ascertainment where the most control over the microstructure can be exercised.
 
-The average and directional domain sizes in addition to their relation with tortuosity will provide windows into the microstructural properties of the resulting bijel.
-The nematic order parameter and average interfacial angle will be used to investigate how the application of the field affects the particle ordering to each other, and to the interface.
-Finally, the radial distribution function will be used to assess if the orientational changes expected upon field application, affects the packing of the particles on the interface.
+The average and directional domain sizes in addition to their relation with tortuosity will provide windows into the microstructural properties 
+of the resulting bijel. The nematic order parameter and average interfacial angle will be used to investigate how the application of the 
+field affects the particle ordering to each other, and to the interface. Finally, the radial distribution function will be used to assess 
+if the orientational changes expected upon field application, affects the packing of the particles on the interface.
 
@@
 
-Particles on the surface of emulsion droplets have been shown to unjam and rejam into new, stable microstructures upon application of stimuli.
-\cite{cui_stabilizing_2013} Two techniques of microstructure change are proposed.
-The first technique is that the adsorption energy is so strong that the interface is dragged along with the particles until they rejam in their new location and orientation to the field.
-The second technique is that the particles tilt in place out of the interface, causing domain coarsening before the particles jam in their new positions and orientations.
-The mechanism, derived microstructure change and timescales will be assessed in this aim.
+Particles on the surface of emulsion droplets have been shown to unjam and rejam into new, stable microstructures upon application of 
+stimuli. \cite{cui_stabilizing_2013} Two techniques of microstructure change are proposed. The first technique is that the adsorption 
+energy is so strong that the interface is dragged along with the particles until they rejam in their new location and orientation to the 
+field. The second technique is that the particles tilt in place out of the interface, causing domain coarsening before the particles jam 
+in their new positions and orientations. The mechanism, derived microstructure change and timescales will be assessed in this aim.
 
-The response of bijels to magnetic fields will be assessed through analyzing how model bijels made with no fields respond to field strengths above and below the critical field strength as calculated from Bresme Faraudo theory.
-The microstructure properties such as the average domain size, particle orientation to the field and interface and the Steinhardt 6 fold bond order parameter to examine the spatial relationship of the particles to their neighbors.
-These techniques will allow elucidation of which mechanism is present at which magnetic field strength.
-Additionally, the microstructure changes observed will be characterized and compared to one another to assess how the applied magnetic field changes the final microstructure obtained.
+The response of bijels to magnetic fields will be assessed through analyzing how model bijels made with no fields respond to field strengths 
+above and below the critical field strength as calculated from Bresme Faraudo theory. The microstructure properties such as the average domain 
+size, particle orientation to the field and interface and the Steinhardt 6 fold bond order parameter to examine the spatial relationship of 
+the particles to their neighbors. These techniques will allow elucidation of which mechanism is present at which magnetic field strength. 
+Additionally, the microstructure changes observed will be characterized and compared to one another to assess how the applied magnetic field 
+changes the final microstructure obtained.
 
-Next, the importance of the initial order of the particle monolayer will also be assessed through increasing the applied field to equal to the surface tension forces on bijel templates simulated under various field strengths.
-The applied field will also be switched off on bijel templates simulated under the same field strengths.
-The same analysis metrics mentioned earlier will be used.
-Additionally, the microstructures with the same difference in applied field,  will be assessed to investigate the reversibility of bijel microstructures.
+Next, the importance of the initial order of the particle monolayer will also be assessed through increasing the applied field to equal to the 
+surface tension forces on bijel templates simulated under various field strengths. The applied field will also be switched off on bijel templates 
+simulated under the same field strengths. The same analysis metrics mentioned earlier will be used. Additionally, the microstructures with the 
+same difference in applied field,  will be assessed to investigate the reversibility of bijel microstructures.
 
@@
 In many of the fabrication processes described above, the rheology of the bijel casting mixture is essential. 
-\cite{haase_continuous_2015, cai_bijels_2017, amirfattahi_fabrication_2024} Ching showed that rheologically, bijels are colloidal glasses percolating in 3D space.
-\cite{ching_bijel_2022} First, a shear capillary number is defined as $Ca_s = \frac{\eta_{f} \dot{\gamma} L_{1}}{\sigma}$ where $\dot{\gamma} = \frac{u_{LE}}{L_x}$ is the strain rate and $L_1$ is the average domain size.
-\cite{frijters_effects_2012, yang_capillary_2022} Lower capillary numbers in the range of $ 10^{-7} \geq Ca_s \leq 10^{-5}$ will be utilized.
+\cite{haase_continuous_2015, cai_bijels_2017, amirfattahi_fabrication_2024} Ching showed that rheologically, bijels are 
+colloidal glasses percolating in 3D space. \cite{ching_bijel_2022} First, a shear capillary number is defined as 
+$Ca_s = \frac{\eta_{f} \dot{\gamma} L_{1}}{\sigma}$ where $\dot{\gamma} = \frac{u_{LE}}{L_x}$ is the strain rate and 
+$L_1$ is the average domain size. \cite{frijters_effects_2012, yang_capillary_2022} Lower capillary numbers in the range of
+ $ 10^{-7} \geq Ca_s \leq 10^{-5}$ will be utilized. 
 % which corresponds to a $Ma << 0.01$ to accommodate the hydrodynamic model utilized.
 
-For this study, the yield stress and viscosity of the bijels will be explored as a function of the initial microstructure under various $Ca_s$.
-Four templates with different processing history will be utilized to assess the impact of initial microstructure on the obtained rheology.
-These are, $\bar{B} = 0$, $\bar{B} = 1$, $\bar{B} = 0 \rightarrow \bar{B} = 1$ and $\bar{B} = 1 \rightarrow \bar{B} = 0$.
-To explain any observed differences in the the yield stress and viscosity, the time evolution of the domain size, average interface angle, and nematic order parameter will be characterized and compared to the observed yield stress and viscosity.
-Additionally, the presence of shear banding will be visually confirmed.
+For this study, the yield stress and viscosity of the bijels will be explored as a function of the initial microstructure under 
+various $Ca_s$. Four templates with different processing history will be utilized to assess the impact of initial microstructure on 
+the obtained rheology. These are, $\bar{B} = 0$, $\bar{B} = 1$, $\bar{B} = 0 \rightarrow \bar{B} = 1$ and $\bar{B} = 1 \rightarrow \bar{B} = 0$. 
+To explain any observed differences in the the yield stress and viscosity, the time evolution of the domain size, average interface angle, and 
+nematic order parameter will be characterized and compared to the observed yield stress and viscosity. Additionally, the presence of shear 
+banding will be visually confirmed.

### 2025-02-14 chapters/lit_review.tex
Changes 1. Made tex files human readable again 2. Added content to paper3 tex file 3. Added licenses to some of the images from other papers

@@
 
-When two partially miscible fluids are mixed together, they will have the tendency to coalesce into two distinct phases as they attempt to minimize the thermodynamic penalty accrued from the formation of an interface.
-To prevent this coalescence process, conventionally small molecule surfactants are utilized.
-The most famous example of this class of material is soap which emulsifies dirt into droplets suspended in water through mechanical action.
-Surfactants function through reducing the surface tension between the droplet, known as the dispersed phase, and the bulk fluid, known as the continuous phase.
-Surfactants function through reducing the surface tension between dispersed and continuous phases, reducing the energy penalty owed from formation of an interface.
+When two partially miscible fluids are mixed together, they will have the tendency to coalesce into two distinct phases as they attempt to minimize 
+the thermodynamic penalty accrued from the formation of an interface. To prevent this coalescence process, conventionally small molecule surfactants 
+are utilized. The most famous example of this class of material is soap which emulsifies dirt into droplets suspended in water through mechanical action. 
+Surfactants function through reducing the surface tension between the droplet, known as the dispersed phase, and the bulk fluid, known as the continuous 
+phase. Surfactants function through reducing the surface tension between dispersed and continuous phases, reducing the energy penalty owed from formation 
+of an interface.
 
-The existence of particle stabilized emulsions has been known for more than a century now, after Pickering and Ramsden independently identified dispersed droplets of oil within a water matrix after vigorous stirring of an oil, water and particle mixture.
-\textcolor{blue}{10.1098/rspl.1903.0034, http://pubs.rsc.org/en/content/articlelanding/1907/ct/ct9079102001} Unlike surfactants, particles act as emulsion stabilizers through the reduction of contact between dispersed and continuous phases as they adsorb into the interface between phases.
-The Pieranski model derived from observations of \textcolor{blue}{insert derivation of pieranski model} and is used to determine the adsorption energy of a particle at an interface.
-It is defined as $G_{ads} = \sigma A_{rm} (1 - \cos{\theta_c})^2$, where $G_{ads}$ is the free energy reduction from a particle adsorption, $\sigma$ is the surface tension between the partially miscible fluids, $\theta_c$ is the contact angle of the particle.
-The particles can be considered to be irreversibly adsorb even for nanoparticles, and for particles larger than 100nm, the adsorption energy is so great that thermal fluctuations at the interface can be considered to have no effect.
-\textcolor{blue}{https://doi.org/10.1063/1.3618553}
+The existence of particle stabilized emulsions has been known for more than a century now, after Pickering and Ramsden independently identified dispersed 
+droplets of oil within a water matrix after vigorous stirring of an oil, water and particle mixture. 
+\textcolor{blue}{10.1098/rspl.1903.0034, http://pubs.rsc.org/en/content/articlelanding/1907/ct/ct9079102001} Unlike surfactants, 
+particles act as emulsion stabilizers through the reduction of contact between dispersed and continuous phases as they adsorb into 
+the interface between phases. The Pieranski model derived from observations of \textcolor{blue}{insert derivation of pieranski model} 
+and is used to determine the adsorption energy of a particle at an interface. It is defined as $G_{ads} = \sigma A_{rm} (1 - \cos{\theta_c})^2$, where $G_{ads}$ 
+is the free energy reduction from a particle adsorption, $\sigma$ is the surface tension between the partially miscible fluids, $\theta_c$ is the contact angle 
+of the particle. The particles can be considered to be irreversibly adsorb even for nanoparticles, and for particles larger than 100nm, the adsorption energy 
+is so great that thermal fluctuations at the interface can be considered to have no effect. \textcolor{blue}{https://doi.org/10.1063/1.3618553}
 
-After their discovery, interest in particle stabilized emulsions became minimal.
-However, increased interest in them has resurfaced since the 1980s owing to their applications in food science.
-One such example is fat crystals stabilizing water droplets in oil to create margarine.
-Particle stabilization has also been of interest owing to their lower toxicity and greater ease of sustainable sourcing.
-It has been shown that chemical surfactants can be toxic to aquatic life, acting as a xeno-hormone and interfering with their reproduction.
-\textcolor{blue}{https://www.sciencedirect.com/science/article/pii/S0304389420302879, https://www.sciencedirect.com/science/article/pii/S014765131530172X} Additionally, particles based cellulose or chitin can be obtained from renewable sources.
-\textcolor{blue}{https://www.tandfonline.com/doi/full/10.1080/14686996.2017.1401423, 10.1021/acs.biomac.6b00144, 10.1021/acs.langmuir.7b03959} It has also been shown that particle stabilized emulsions are stable for long periods of time.
-These development have resulted in particle stabilized emulsions seeing a large increase in interest.
+After their discovery, interest in particle stabilized emulsions became minimal. However, increased interest in them has resurfaced since the 1980s owing to 
+their applications in food science. One such example is fat crystals stabilizing water droplets in oil to create margarine. Particle stabilization has also 
+been of interest owing to their lower toxicity and greater ease of sustainable sourcing through the usage of cellulose or chitin particles. \
+textcolor{blue}{https://www.tandfonline.com/doi/full/10.1080/14686996.2017.1401423, 10.1021/acs.biomac.6b00144, 10.1021/acs.langmuir.7b03959} 
+Additionally, chemical surfactants can be toxic to aquatic life, acting as a xeno-hormone and interfering with their reproduction. 
+\textcolor{blue}{https://www.sciencedirect.com/science/article/pii/S0304389420302879, https://www.sciencedirect.com/science/article/pii/S014765131530172X}
 
-The microstructure properties of particle stabilized emulsions were explored in the early 2000s by Lumsdon and Binks among many others.
-They observed that the radius of emulsion droplets, $R_e \propto \frac{\phi_w}{\phi_p}$, where $\phi_w$ and $\phi_p$ are volume fractions of water and particles respectively.
-\cite{binks_pickering_2001} They also identified that there were other techniques to modify the microstructure of a Pickering Emulsion such as concentration of fluids and particle wettability.
-Neutrally wetting particles do not impart a preferential curvature to the interface.
-When using non-neutrally wetting particles, bridged droplets, capillary aggregates and other non droplet microstructures can be observed.
-Bijels, are synthesized in a system using equal volume fraction of fluids and neutrally wetting particles, thus facilitating the formation of tortuous, co-continuous domains.
+Compared to emulsions stabilized using surfactants, particle stabilized emulsions offer greater resistance to coarsening, resulting in increased interest in 
+them once again. The microstructure properties of particle stabilized emulsions were explored in the early 2000s by Lumsdon and Binks among many others. They 
+observed that the radius of emulsion droplets, $R_e \propto \frac{\phi_w}{\phi_p}$, where $\phi_w$ and $\phi_p$ are volume fractions of water and particles 
+respectively. \cite{binks_pickering_2001} They also identified that there were other techniques to modify the microstructure of a Pickering Emulsion 
+such as concentration of fluids and particle wettability. Neutrally wetting particles do not impart a preferential curvature to the interface. When 
+using non-neutrally wetting particles, bridged droplets, capillary aggregates and other non droplet microstructures can be observed. Bijels, are synthesized 
+in a system using equal volume fraction of fluids and neutrally wetting particles, thus facilitating the formation of tortuous, co-continuous domains.
 
-Bijels themselves are synthesized in systems which have roughly equal fluid volume fractions and neutrally wetting particles so as to not impose preferential curvature on the interface.
-\cite{stratford_colloidal_2005, herzig_bicontinuous_2007, lee_bicontinuous_2010, jansen_bijels_2011, velankar_non-equilibrium_2015} Reeves et al.
-demonstrated that bijels stabilized with nanoparticles are more stable than those with microparticles due to better mechanical properties and interface coverage.
-\cite{reeves_particle-size_2015}  Additionally, research by Jansen, Harting, and Hijnen et al.
-showed that the bijel domain size $L \propto \frac{1}{\phi_p}$ for both rod-like and spherical particles.
-Although the pre-factor is dependent upon the particle geometry, this feature has been seen with many other particle shapes as well.
-\cite{hijnen_bijels_2015, madivala_exploiting_2009, gunther_timescales_2014, daware_emulsions_2015, loudet_capillary_2005, cheng_shape-anisotropic_2013}
+Bijels are synthesized in systems which have roughly equal fluid volume fractions and neutrally wetting particles so as to not impose preferential 
+curvature on the interface. \cite{stratford_colloidal_2005, herzig_bicontinuous_2007, lee_bicontinuous_2010, jansen_bijels_2011, velankar_non-equilibrium_2015} 
+Reeves et al. demonstrated that bijels stabilized with nanoparticles are more stable than those with microparticles due to better mechanical properties and 
+interface coverage. \cite{reeves_particle-size_2015}  Additionally, research by Jansen, Harting, and Hijnen et al. showed that the bijel domain size 
+$L \propto \frac{1}{\phi_p}$ for both rod-like and spherical particles. Although the pre-factor is dependent upon the particle geometry, this feature 
+has been seen with many other particle shapes as well. \cite{hijnen_bijels_2015, madivala_exploiting_2009, gunther_timescales_2014, daware_emulsions_2015, 
+loudet_capillary_2005, cheng_shape-anisotropic_2013}
 
@@
     \includegraphics[scale = 0.5]{figures/literature_review/interfacial_curvature.png}
-    \caption{Quadropolar capillary interactions around prolate ellipsoidal particles caused by interfacial deformations around the particle. \cite{loudet_capillary_2005}}
+    \caption{Quadropolar capillary interactions around prolate ellipsoidal particles caused by interfacial deformations around the particle. 
+    \cite{loudet_capillary_2005} Reproduced from Loudet et al. with license number RNP/25/FEB/088185}
     \label{fig:anisotropic_particle_interface}
@@
 
-In the past decade, methods to synthesize particles which have anisotropic geometry and chemistry have increased in number and scope.
-Synthesis techniques vary depending on the type of particle shape desired.
-Ellipsoids can be easily created by mechanical deformation of polymer spheres.
-Dumbbell shaped particles can be synthesized using microfluidic devices or emulsion templating.
-Square particles can be generated using crystallization of material.
-\cite{morgan_understanding_2013} These variety of techniques mean that particle geometry is no longer as constraint when investigating prospective particle stabilizers of bijels.
+In the past decade, methods to synthesize particles which have anisotropic geometry and chemistry have increased in number and scope. Synthesis techniques vary 
+depending on the type of particle shape desired. Ellipsoids can be easily created by mechanical deformation of polymer spheres. Dumbbell shaped particles can be 
+synthesized using microfluidic devices or emulsion templating. Square particles can be generated using crystallization of material. \cite{morgan_understanding_2013} 
+These variety of techniques mean that particle geometry is no longer as constraint when investigating prospective particle stabilizers of bijels. 
 \textcolor{blue}{https://onlinelibrary.wiley.com/doi/10.1002/smll.201600877}
 
-Anisotropic particles have shape dependent properties owing to their induction of multipolar interactions by deforming the interface to ensure the mean curvature is 0,  fulfilling the Young-Laplace equation shown in Figure \ref{fig:anisotropic_particle_interface}.
-\cite{loudet_capillary_2005, cheng_shape-anisotropic_2013} Using this property has enabled directed assembly and migration through modified capillary forces.
+Anisotropic particles have shape dependent properties owing to their induction of multipolar interactions by deforming the interface to ensure the mean 
+curvature is 0,  fulfilling the Young-Laplace equation shown in Figure \ref{fig:anisotropic_particle_interface}. \cite{loudet_capillary_2005, 
+cheng_shape-anisotropic_2013} Using this property has enabled directed assembly and migration through modified capillary forces. 
 \cite{cavallaro_curvature-driven_2011, read_dimerization_2020, sharifi-mood_curvature_2015}
@@
 
-When stabilizing bijels, ellipsoidal particles offer greater stability than spherical ones due to their larger cross-sectional area to volume ratio, as shown by Günther et al.
-and Hijnen et al.
-\cite{gunther_timescales_2014, hijnen_bijels_2015} This results in additional domain coarsening timescales from particle re-orientation and increased mechanical rigidity, enhancing the stability of emulsions with ellipsoidal particles, as evidenced in rheological studies.
-\cite{gunther_timescales_2014, daware_emulsions_2015, witt_bijel_2013}
-It has also been shown that particle shape changes how and when jamming occurs.
+When stabilizing bijels, ellipsoidal particles offer greater stability than spherical ones due to their larger cross-sectional area to volume ratio, 
+as shown by Günther et al. and Hijnen et al. \cite{gunther_timescales_2014, hijnen_bijels_2015} This results in additional domain coarsening timescales 
+from particle re-orientation and increased mechanical rigidity, enhancing the stability of emulsions with ellipsoidal particles, as evidenced in rheological 
+studies. \cite{gunther_timescales_2014, daware_emulsions_2015, witt_bijel_2013} It has also been shown that particle shape changes how and when jamming occurs. 
 Using graphene plate like particles, it was shown that the plate like particles can have their own elasticity to them, affecting when jamming occurs. 
@@
 Control over the orientation of ellipsoidal particles at interfaces balances interfacial capillary and magnetic field forces. 
-\cite{bresme_orientational_2007, davies_assembling_2014} Theory and simulations indicate a critical field strength above which particle orientation is dominated by the applied field.
-\cite{bresme_orientational_2007, davies_assembling_2014} Experiments and simulations have found that steric interactions, influenced by orientation and interfacial arrangements significantly influence the free energy of particle assemblies, highlighting the complex interplay between these forces.
-\cite{morgan_understanding_2013, newton_influence_2014, newton_capillary_2018}
+\cite{bresme_orientational_2007, davies_assembling_2014} Theory and simulations indicate a critical field strength above which particle orientation 
+is dominated by the applied field. \cite{bresme_orientational_2007, davies_assembling_2014} Experiments and simulations have found that steric interactions, 
+influenced by orientation and interfacial arrangements significantly influence the free energy of particle assemblies, highlighting the complex interplay 
+between these forces. \cite{morgan_understanding_2013, newton_influence_2014, newton_capillary_2018}
 
@@
 
-Bijels were first synthesized using Thermally Induced Phase Separation (TIPS).
-\cite{herzig_bicontinuous_2007, lee_bicontinuous_2010, bai_dynamics_2015} First, a small molecule or polymer blend with a critical point, named the casting mixture, is identified and prepared with a composition corresponding to that of the critical point.
-Next, the casting mixture is blended with particle surfactants while still in a single phase.
-Once the particles are distributed homogenously in the casting mixture, phase separation is initiated in the casting mixture through changing the temperature such that it is in the two-phase region.
+Bijels were first synthesized using Thermally Induced Phase Separation (TIPS). \cite{herzig_bicontinuous_2007, lee_bicontinuous_2010, bai_dynamics_2015} 
+First, a small molecule or polymer blend with a critical point, named the casting mixture, is identified and prepared with a composition corresponding to 
+that of the critical point. Next, the casting mixture is blended with particle surfactants while still in a single phase. Once the particles are distributed 
+homogenously in the casting mixture, phase separation is initiated in the casting mixture through changing the temperature such that it is in the two-phase region. 
 Through ensuring the composition is that of the critical point, the casting mixture undergoes spinodal decomposition without any nucleation and growth.
 
-TIPS allows for batch synthesis of bijels in research labs.
-However to make bijels industrially relevant, a continuous process which also facilitates the synthesis of multiple form factors of bijels for various applications.
-Solvent Transfer Induced Phase Separation (STrIPS) was proposed as a means to do just this.
-A casting mixture composed of two fluids, a co-solvent, particles and a surfactant is prepared.
-The fluids will constitute the bijel while the co-solvent will diffuse out of the bijel to initiate phase separation.
-The surfactant is present to ensure that the bijel remains stable against Marangoni pressure.
-The casting mixture if extruded into a bath of non-solvent that is not miscible with the bijel constituents but is miscible with the co-solvent.
-Diffusion of co-solvent initiates phase separation and synthesis of the bijel.
-The concentration of surfactant and the flow rate of the casting mixture control the obtained microstructure.
+TIPS allows for batch synthesis of bijels in research labs. However to make bijels industrially relevant, a continuous process which also facilitates the 
+synthesis of multiple form factors of bijels for various applications. Solvent Transfer Induced Phase Separation (STrIPS) was proposed as a means to do just this. 
+A casting mixture composed of two fluids, a co-solvent, particles and a surfactant is prepared. The fluids will constitute the bijel while the co-solvent will 
+diffuse out of the bijel to initiate phase separation. The surfactant is present to ensure that the bijel remains stable against Marangoni pressure. The casting 
+mixture if extruded into a bath of non-solvent that is not miscible with the bijel constituents but is miscible with the co-solvent. Diffusion of co-solvent 
+initiates phase separation and synthesis of the bijel. The concentration of surfactant and the flow rate of the casting mixture control the obtained microstructure.
 
@@
     \includegraphics[scale = 2]{figures/literature_review/bijel_under_shear.jpeg}
-    \caption{Schematic of a bijel with hard-sphere particles undergoing shear, demonstrating migration and detachment of particles at the interface. \cite{bonaccorso_shear_2020}}
+    \caption{Schematic of a bijel with hard-sphere particles undergoing shear, demonstrating migration and detachment of particles at the interface. 
+    \cite{bonaccorso_shear_2020}}
     \label{fig:bijel_under_shear}
@@
 Studies into bijel rheology have shown the characteristics of a gel when the
-storage modulus exceeds the loss modulus.
-\cite{lee_making_2013, bai_dynamics_2015} Ching and Mohraz also demonstrated that the rheological behaviour of a bijel most closely resembles a 2D colloidal glass that was percolating in 3D space by comparing the linear visco-elasticity of bijels with colloidal gels made with strongly attractive particles.
-\cite{ching_bijel_2022} Several key feature of glasses are that they posses a yield stress, viscoelastic behaviour and a glass transition point.
+storage modulus exceeds the loss modulus. \cite{lee_making_2013, bai_dynamics_2015} Ching and Mohraz also demonstrated that the rheological behaviour of a 
+bijel most closely resembles a 2D colloidal glass that was percolating in 3D space by comparing the linear visco-elasticity of bijels with colloidal gels made 
+with strongly attractive particles. \cite{ching_bijel_2022} Several key feature of glasses are that they posses a yield stress, viscoelastic behaviour and a 
+glass transition point.
 \cite{pham_yielding_2008, weeks_introduction_2017} Yield stress is the stress imparted when the particle monolayer is irreversibly changed.
@@
 
-Kim et al.
-found that strong magnetic fields do not significantly alter the microstructure of a bijel stabilized with spherical particles, as the particles orient to the field without affecting interface ordering.
-\cite{kim_bijels_2010} In contrast, Carmack and Millet demonstrated that polarizable fluids and particles under an electric field show significant microstructural changes, with particles self-assembling into chains and forming cylindrical domains parallel to the applied field, thus modifying the microstructure.
-\cite{carmack_tuning_2018}
+Kim et al. found that strong magnetic fields do not significantly alter the microstructure of a bijel stabilized with spherical particles, as the particles orient 
+to the field without affecting interface ordering. \cite{kim_bijels_2010} In contrast, Carmack and Millet demonstrated that polarizable fluids and particles under 
+an electric field show significant microstructural changes, with particles self-assembling into chains and forming cylindrical domains parallel to the applied field, 
+thus modifying the microstructure. \cite{carmack_tuning_2018}
 
@@
 
-The Lattice Boltzmann Method (LBM) is an evolution of preceding lattice gas automata techniques, which is a discretization of the Boltzmann equation of motion for molecules.
-This means that unlike traditional CFD techniques such as FDM, VOF or level set methods, LBM is a psuedo-molecule method that tracks the evolution of a particle distribution function within grid cells evolved through a discretized Boltzmann equation of motion.
-Macroscopic variables such as fluid density and velocity are recovered from the particle distributions through appropriate moment integration, and the Navier Stokes equation at the incompressible limit can be obtained through a Chapman-Enskog expansion of the LBM.
-The LBM has become an attractive tool for meso-scale CFD simulations due to its ease of algorithm implementation, highly parallelizable nature and ease of boundary condition implementation, allowing coupling to other physically relevant systems such as particles with varieties of potentials, external fields and deformable bodies.
+The Lattice Boltzmann Method (LBM) is an evolution of preceding lattice gas automata techniques, which is a discretization of the Boltzmann equation of motion for 
+molecules. This means that unlike traditional CFD techniques such as FDM, VOF or level set methods, LBM is a psuedo-molecule method that tracks the evolution of a 
+particle distribution function within grid cells evolved through a discretized Boltzmann equation of motion. Macroscopic variables such as fluid density and 
+velocity are recovered from the particle distributions through appropriate moment integration, and the Navier Stokes equation at the incompressible limit can be 
+obtained through a Chapman-Enskog expansion of the LBM. The LBM has become an attractive tool for meso-scale CFD simulations due to its ease of algorithm 
+implementation, highly parallelizable nature and ease of boundary condition implementation, allowing coupling to other physically relevant systems such as 
+particles with varieties of potentials, external fields and deformable bodies.
 
-The particle distribution function described earlier is advected on a pre-constructed lattice stencil, commonly denoted as DnQm where n and m represent the number of dimensions and directions in the stencil.
-Common stencils include the D1Q5, D2Q9 and D3Q19 stencil, all of which recover mass and momentum conservation.
-For energy conservation, a higher order stencil such as D3Q27 is necessary.
-The D2Q9 and D3Q19 stencils have 8 and 18 populations respectively that include connections to nearest and next nearest neighbour points, in addition to a central rest point.
+The particle distribution function described earlier is advected on a pre-constructed lattice stencil, commonly denoted as DnQm where n and m represent the 
+number of dimensions and directions in the stencil. Common stencils include the D1Q5, D2Q9 and D3Q19 stencil, all of which recover mass and momentum conservation. 
+For energy conservation, a higher order stencil such as D3Q27 is necessary. The D2Q9 and D3Q19 stencils have 8 and 18 populations respectively that include 
+connections to nearest and next nearest neighbour points, in addition to a central rest point.
 
-The LBM is composed of a collision and advection step.
-In the advection step, the populations at each grid point are propagated to adjacent points in accordance with the chosen stencil.
-During the collision step, the particle population distribution is relaxed towards an equilibrium with a collision operator, at a specified relaxation rate.
-The collision operator can have multiple forms based on how many relaxation rates are used although the most common variant is the Single Relaxation Time (SRT) collision operator, more commonly known as the Bhatnagar-Gross-Krook (BGK) collision operator.
-Owing to its stability in low Mach and Reynolds numbers and simplicity of implementation, the BGK operator is often used in common particle laden flow and soft matter scenarios.
-\cite{bhatnagar_model_1954} These limitations are present owing to the implicit link between the fluid properties and the relaxation rate necessitating relaxation rates above 0.5, and to ensure fluid incompressibility from an equation that intrinsically simulates a compressible fluid.
-To get over these limitations, Two Relaxation Time (TRT) and Multiple Relaxation Time (MRT) operators also exist, expanding the possible application of the LBM to visco-elastic flows and implementation of fluctuating hydrodynamics in the LBM.
+The LBM is composed of a collision and advection step. In the advection step, the populations at each grid point are propagated to adjacent points in accordance 
+with the chosen stencil. During the collision step, the particle population distribution is relaxed towards an equilibrium with a collision operator, at a 
+specified relaxation rate. The collision operator can have multiple forms based on how many relaxation rates are used although the most common variant is the 
+Single Relaxation Time (SRT) collision operator, more commonly known as the Bhatnagar-Gross-Krook (BGK) collision operator. Owing to its stability in low Mach 
+and Reynolds numbers and simplicity of implementation, the BGK operator is often used in common particle laden flow and soft matter scenarios. 
+\cite{bhatnagar_model_1954} These limitations are present owing to the implicit link between the fluid properties and the relaxation rate necessitating 
+relaxation rates above 0.5, and to ensure fluid incompressibility from an equation that intrinsically simulates a compressible fluid. To get over these 
+limitations, Two Relaxation Time (TRT) and Multiple Relaxation Time (MRT) operators also exist, expanding the possible application of the LBM to visco-elastic 
+flows and implementation of fluctuating hydrodynamics in the LBM. 
 \textcolor{blue}{https://pubs.acs.org/doi/10.1021/acsomega.3c06663, https://iopscience.iop.org/article/10.1209/epl/i2004-10542-5, https://link.aps.org/doi/10.1103/PhysRevE.82.056714}
 
-Five primary techniques to model multicomponent or multiphase systems exist in the LBM literature.
-A quick review of the Shan-Chen or interparticle potential model  will be provided here from the perspective of a binary mixture.
-Additionally, the names and descriptions of other techniques will be described as well.
-The interparticle potential model or Shan-Chen model that adds a non-local density dependent force between two species, effectively modelling non-ideal mixing and recovering the Cahn-Hilliard equation.
-To alleviate the standard Shan-Chen implementations weaknesses of not being thermodynamically consistent and reducing the existence of spurious velocities,
+Five primary techniques to model multicomponent or multiphase systems exist in the LBM literature. A quick review of the Shan-Chen or 
+interparticle potential model  will be provided here from the perspective of a binary mixture. Additionally, the names and descriptions of 
+other techniques will be described as well. The interparticle potential model or Shan-Chen model that adds a non-local density dependent force 
+between two species, effectively modelling non-ideal mixing and recovering the Cahn-Hilliard equation. To alleviate the standard Shan-Chen implementations 
+weaknesses of not being thermodynamically consistent and reducing the existence of spurious velocities,
 
-In addition to the Shan-Chen model, the color gradient model, free energy model, mean field theory model and interface tracking technique all allow for simulations of various types of multiphase and/or multicomponent flows.
-The color gradient model proposed by Rothman and Keller and implemented by Gunstensen et al relies upon modelling two particle distributions.
-These represent a binary fluid mixture with the collision step able to recover the hydrodynamics and non-ideal mixing dynamics.
-The free energy model utilizes phase field theory and constructs a free energy functional to recover interfacial dynamics and effects in a thermodynamically consistent manner.
-Often, a square gradient free energy is used for simplicity and ease of implementation.
-The mean field theory
+In addition to the Shan-Chen model, the color gradient model, free energy model, mean field theory model and interface tracking technique all 
+allow for simulations of various types of multiphase and/or multicomponent flows. The color gradient model proposed by Rothman and Keller and 
+implemented by Gunstensen et al relies upon modelling two particle distributions. These represent a binary fluid mixture with the collision step 
+able to recover the hydrodynamics and non-ideal mixing dynamics. The free energy model utilizes phase field theory and constructs a free energy 
+functional to recover interfacial dynamics and effects in a thermodynamically consistent manner. Often, a square gradient free energy is used for 
+simplicity and ease of implementation. The mean field theory
 
-The non-ideal mixing dynamics are recovered during the "recoloring" step, of which the technique proposed by Latva-Kokko and Rothman is more commonly used for soft matter flows.
+The non-ideal mixing dynamics are recovered during the "recoloring" step, of which the technique proposed by Latva-Kokko and Rothman is more commonly 
+used for soft matter flows.
 

### 2025-02-14 chapters/model_params.tex
Changes 1. Made tex files human readable again 2. Added content to paper3 tex file 3. Added licenses to some of the images from other papers

@@
 
-Critical parameters in this system include fluid density $\rho_f$, dynamic viscosity $\eta$, surface tension $\sigma$, length scale $L$, and applied magnetic field strength $B$.
-The dynamic viscosity and surface tension is determined by the relaxation time using the BGK collision operator, $\eta = \rho_f c_s^2(\tau - \frac{1}{2})$ and $g_{kk'}$ respectively.
-Dimensionless numbers derived from the Buckingham Pi theorem are the Reynolds number($Re = \frac{\rho u L}{\eta}$), Weber number ($We = \frac{\rho u^2 L}{\sigma}$), and magnetic bond number ($\Bar{B} = \frac{Bd}{\sigma A}$).
-Here, $u$ is velocity, $d$ is the particle's dipole moment, and $A$ is the particle's cross-sectional area.
-The system's velocity and length scale are set as the domain size and coarsening rate.
-Parameters for the fluid, particle, and non-ideal mixing model used in the simulations are summarized in Table \ref{table:model_params}.
+Critical parameters in this system include fluid density $\rho_f$, dynamic viscosity $\eta$, surface tension $\sigma$, 
+length scale $L$, and applied magnetic field strength $B$. The dynamic viscosity and surface tension is determined 
+by the relaxation time using the BGK collision operator, $\eta = \rho_f c_s^2(\tau - \frac{1}{2})$ and $g_{kk'}$ 
+respectively. Dimensionless numbers derived from the Buckingham Pi theorem are the Reynolds number
+($Re = \frac{\rho u L}{\eta}$), Weber number ($We = \frac{\rho u^2 L}{\sigma}$), and magnetic bond number 
+($\Bar{B} = \frac{Bd}{\sigma A}$). Here, $u$ is velocity, $d$ is the particle's dipole moment, and $A$ is the 
+particle's cross-sectional area. The system's velocity and length scale are set as the domain size and coarsening rate. 
+Parameters for the fluid, particle, and non-ideal mixing model used in the simulations are summarized in Table 
+\ref{table:model_params}.
 
@@
 
-In these simulations, the aspect ratio is defined as $\alpha = \frac{R_{\parallel}}{R_{\perp}}$ with $\alpha = 0.5, 1, 2$ used in these simulations.
-All particle geometries are volume matched, based on the spherical particle volume.
-For the spherical particle, the radius was set at $R_{\parallel} = R_{\perp} = 7.9$ which sets the $\alpha = 0.5$ particles to $R_{\parallel} = 5, R_{\perp} = 10$ and the $\alpha = 2$ particles to $R_{\parallel} = 12.6, R_{\perp} = 6.3$.
-$R_{\parallel}$ and $R_{\perp}$ is the radius of the particle parallel and perpendicular to the symmetry axis of the particle respectively.
-These values are identical to what was used in Gunther et al, allowing comparisons to the trends they observed.
-\cite{gunther_timescales_2014} The particles were randomly placed in the system and an equilibration step was performed to push the particles further away from each after placement.
-Once equilibration is performed, a constant magnetic field is switched on with dimensionless strengths defined using $Bo_m$.
+In these simulations, the aspect ratio is defined as $\alpha = \frac{R_{\parallel}}{R_{\perp}}$ with $\alpha = 0.5, 1, 2$ 
+used in these simulations. All particle geometries are volume matched, based on the spherical particle volume. For the 
+spherical particle, the radius was set at $R_{\parallel} = R_{\perp} = 7.9$ which sets the $\alpha = 0.5$ particles to 
+$R_{\parallel} = 5, R_{\perp} = 10$ and the $\alpha = 2$ particles to $R_{\parallel} = 12.6, R_{\perp} = 6.3$. 
+$R_{\parallel}$ and $R_{\perp}$ is the radius of the particle parallel and perpendicular to the symmetry axis of 
+the particle respectively. These values are identical to what was used in Gunther et al, allowing comparisons to the 
+trends they observed. \cite{gunther_timescales_2014} The particles were randomly placed in the system and an equilibration
+step was performed to push the particles further away from each after placement. Once equilibration is performed, a 
+constant magnetic field is switched on with dimensionless strengths defined using $Bo_m$.
 
-The initial condition of the system when simulating bijels sets the density of each grid to $0.5\rho_f + \varepsilon$ of each fluid where $\varepsilon = 0.0001N(0,1)$.
-The model parameters trigger phase separation with a sharp interface at the start of the simulation.
-Periodic boundary conditions are applied on all sides unless the system is undergoing shear.
-The shear gradient is applied as a velocity in the z direction across the x axis and implemented as a Lees-Edwards (LE) boundary condition in the yz planes.
-\cite{wagner_leesedwards_2002, lorenz_lees-edwards_2009, yang_capillary_2022} These boundaries move with velocities $u_{LE}$ and $-u_{LE}$ to conserve momentum, with a shear rate $\dot{\gamma} = \frac{2 u_{LE}}{L_x}$.
-LE boundaries are preferred over walls to avoid affecting viscosity measurements.
+The initial condition of the system when simulating bijels sets the density of each grid to $0.5\rho_f + \varepsilon$ of 
+each fluid where $\varepsilon = 0.0001N(0,1)$. The model parameters trigger phase separation with a sharp interface at 
+the start of the simulation. Periodic boundary conditions are applied on all sides unless the system is undergoing shear. 
+The shear gradient is applied as a velocity in the z direction across the x axis and implemented as a Lees-Edwards 
+(LE) boundary condition in the yz planes. \cite{wagner_leesedwards_2002, lorenz_lees-edwards_2009, yang_capillary_2022} 
+These boundaries move with velocities $u_{LE}$ and $-u_{LE}$ to conserve momentum, with a shear rate 
+$\dot{\gamma} = \frac{2 u_{LE}}{L_x}$. LE boundaries are preferred over walls to avoid affecting viscosity measurements. 
 \cite{wagner_leesedwards_2002, lorenz_lees-edwards_2009, yang_capillary_2022}
 
-Bijel templates have been synthesized using water/2-6-lutidine for further applications.
-\cite{lee_making_2013} While intrinsically polymerizable bijels have been prepared using oligomeric polymers, STRIPS and VIPS currently utilize small molecule liquids in their bijel casting mixtures.
-Therefore, an experimentally viable system using water/2-6-lutidine will be discussed in the context of the work presented here.
-The critical temperature (UCST) for this system is $T_c = 37 ^{\circ}C$, with many systems heated to $T = 40^{\circ}C$ to form the bijel.
-At this temperature, the fluid properties are $\sigma = 0.22 mN/m$ and $\eta = 2.38 mPas$.
-\cite{grattoni_lower_1993} Fei et al.
-developed a method to synthesize polystyrene microparticles ($(R_p = 2 \mu m)$) with tunable geometries by mechanically stretching or compressing them, then coating them with nickel to create magnetic microparticles with a dipole moment of approximately$\approx 3 \cdot 10^{-14} Am^2$.
-\cite{fei_active_2017, fei_magneto-capillary_2020} Comparing the physical properties to simulation parameters, the simulations correspond to a box side length of $L \approx 64.5 \mu m$ and a timestep duration of $\Delta t \approx 624 ns$.
+Bijel templates have been synthesized using water/2-6-lutidine for further applications. \cite{lee_making_2013} 
+While intrinsically polymerizable bijels have been prepared using oligomeric polymers, STRIPS and VIPS currently 
+utilize small molecule liquids in their bijel casting mixtures. Therefore, an experimentally viable system using 
+water/2-6-lutidine will be discussed in the context of the work presented here. The critical temperature (UCST) 
+for this system is $T_c = 37 ^{\circ}C$, with many systems heated to $T = 40^{\circ}C$ to form the bijel. At this 
+temperature, the fluid properties are $\sigma = 0.22 mN/m$ and $\eta = 2.38 mPas$. \cite{grattoni_lower_1993} 
+Fei et al. developed a method to synthesize polystyrene microparticles ($(R_p = 2 \mu m)$) with tunable geometries 
+by mechanically stretching or compressing them, then coating them with nickel to create magnetic microparticles with 
+a dipole moment of approximately$\approx 3 \cdot 10^{-14} Am^2$. \cite{fei_active_2017, fei_magneto-capillary_2020} 
+Comparing the physical properties to simulation parameters, the simulations correspond to a box side length of 
+$L \approx 64.5 \mu m$ and a timestep duration of $\Delta t \approx 624 ns$.
 
@@
 
-In experiments, Wilhelmy and ring tensionometry are used to measure the surface tension from the force needed to break through the interface.
-Pendant drop tensionometry is also used by measuring the pressure required to maintain a droplet of analyte at a various sizes and utilizing the Young-Laplace equation to calculate the surface tension of the system.
-\textcolor{blue}{https://pubs.acs.org/doi/10.1021/la402436w, https://doi.org/10.1016/j.jcis.2015.05.012} Upon extrusion of a droplet from a reservoir, the size of a droplet is determined by the balance between cohesive forces between bubble molecules and geometrical forces that attempt to reduce the curvature of a system by increasing its size.
-For spherical droplets, the equation simplifies to $\Delta P = \frac{2 \sigma}{R_d}$ where $\Delta P$ is the difference in scalar pressure between the center of the droplet and the ambient pressure, $\sigma$ is the surface tension of the interface and $R_d$ is the radius of the droplet.
+In experiments, Wilhelmy and ring tensionometry are used to measure the surface tension from the force needed 
+to break through the interface. Pendant drop tensionometry is also used by measuring the pressure required to 
+maintain a droplet of analyte at a various sizes and utilizing the Young-Laplace equation to calculate the 
+surface tension of the system. 
+\textcolor{blue}{https://pubs.acs.org/doi/10.1021/la402436w, https://doi.org/10.1016/j.jcis.2015.05.012} 
+Upon extrusion of a droplet from a reservoir, the size of a droplet is determined by the balance between 
+cohesive forces between bubble molecules and geometrical forces that attempt to reduce the curvature of a 
+system by increasing its size. For spherical droplets, the equation simplifies to 
+$\Delta P = \frac{2 \sigma}{R_d}$ where $\Delta P$ is the difference in scalar pressure 
+between the center of the droplet and the ambient pressure, $\sigma$ is the surface tension 
+of the interface and $R_d$ is the radius of the droplet.
 
@@
     \includegraphics[scale = 0.5]{figures/model_validation/surface_tension.png}
-    \caption{Plot of the surface tension of the multicomponent model in this work calculated using the Young-Laplace equation.}
+    \caption{Plot of the surface tension of the multicomponent model in this work calculated using the 
+    Young-Laplace equation.}
     \label{fig:young_laplace_valid}
@@
 
-Using the fluid and non-ideal mixing parameters defined in Table \ref{table:model_params}, a single water in oil droplet, termed blue in red, was initialized in the center system and run till the droplet radii reached steady state.
-This process was repeated for various droplet diameters, specified between $40$ and $85 \%$ of the system size at $5\%$ increments.
-The system had a box length of $L = 64$ and was run for $50000$ timesteps with periodic boundary conditions on all sides.
-Data was dumped every 10000 timesteps with only the last timestep used to calculate the values shown.
-Due to the diffuse interface present in this method, the density profiles were verified to be at steady state at the end of the simulation before further analysis was performed.
-\cite{frijters_effects_2012} Past work also showed that the pressures remained constant after 5 lattice units away from the interface.
-\cite{frijters_effects_2012}
+Using the fluid and non-ideal mixing parameters defined in Table \ref{table:model_params}, a single water in oil 
+droplet, termed blue in red, was initialized in the center system and run till the droplet radii reached steady state. 
+This process was repeated for various droplet diameters, specified between $40$ and $85 \%$ of the system size at $5\%$ 
+increments. The system had a box length of $L = 64$ and was run for $50000$ timesteps with periodic boundary conditions 
+on all sides. Data was dumped every 10000 timesteps with only the last timestep used to calculate the values shown. Due 
+to the diffuse interface present in this method, the density profiles were verified to be at steady state at the end of 
+the simulation before further analysis was performed. \cite{frijters_effects_2012} Past work also showed that the 
+pressures remained constant after 5 lattice units away from the interface. \cite{frijters_effects_2012}
 
-The pressure difference was calculated using the difference in scalar pressure between the center of the droplet and one of the corners of the box.
-Two techniques exist to calculate the radius of the droplet.
-The first directly measures the distance between opposite points of the droplet as measured from the density profile at opposite points of the droplet, and the second is based upon the total mass and density of the fluid making up the droplet.
-The second method offers greater accuracy by avoiding discretization errors that may exist in the first method, and also allows for the correction of particle volume at the interface if the system contained them.
-First, a local effective mass density $\rho^b_{eff} = \rho^{b}_{d} - \rho^{b}_{m}$ is found by calculating the difference in density between the blue fluid in the droplet and in the matrix.
-Next, the droplet mass is calculated as $M_d = \sum_{\mathbf{x}}{\rho_{eff}^{b}}$.
-The radius of the droplet can then be calculated from the mass and density of the droplets as $R_d = \sqrt[3]{\frac{3}{4\pi} \frac{M_d}{\rho^b_d - \rho^b_m}}$.
-To linearize the plot, the $\Delta P$ was plotted against $\frac{2}{R_d}$ with $\sigma$ being the slope of the fit.
+The pressure difference was calculated using the difference in scalar pressure between the center of the droplet and 
+one of the corners of the box. Two techniques exist to calculate the radius of the droplet. The first directly measures 
+the distance between opposite points of the droplet as measured from the density profile at opposite points of the droplet, 
+and the second is based upon the total mass and density of the fluid making up the droplet. The second method offers greater 
+accuracy by avoiding discretization errors that may exist in the first method, and also allows for the correction of 
+particle volume at the interface if the system contained them. First, a local effective mass density 
+$\rho^b_{eff} = \rho^{b}_{d} - \rho^{b}_{m}$ is found by calculating the difference in density between the blue 
+fluid in the droplet and in the matrix. Next, the droplet mass is calculated as $M_d = \sum_{\mathbf{x}}{\rho_{eff}^{b}}$. 
+The radius of the droplet can then be calculated from the mass and density of the droplets as $R_d = \sqrt[3]{\frac{3}{4\pi} 
+\frac{M_d}{\rho^b_d - \rho^b_m}}$. To linearize the plot, the $\Delta P$ was plotted against $\frac{2}{R_d}$ with 
+$\sigma$ being the slope of the fit.
 
-Figure \ref{fig:young_laplace_valid} shows the results of the fit conducted of the Young-Laplace equation demonstrating that under these fluid and mixing parameters, the surface tension is $\sigma = 0.0279$.
-The fit was performed using \texttt{scipy.optimize.curve\_fit} with the fit function defined as $y = mx$.
-Droplets with starting sizes $2R_d < 70\%$ of the initial system size disappeared.
-This occurred due to the initial condition of each fluid set to not contain the other fluid species, meaning once the simulation was initiated diffusion of mass from the droplet to the bulk occurred, causing disappearance of the droplet until the thermodynamically optimal composition was reached.
-From the fit calculated in Figure \ref{fig:young_laplace_valid}, the fit is linear as long as the initial droplet size is sufficiently large.
-Alternatively, the composition of the system can be set to near equilibrium in order to allow access to smaller droplet sizes.
+Figure \ref{fig:young_laplace_valid} shows the results of the fit conducted of the Young-Laplace equation demonstrating 
+that under these fluid and mixing parameters, the surface tension is $\sigma = 0.0279$. The fit was performed using 
+\texttt{scipy.optimize.curve\_fit} with the fit function defined as $y = mx$. Droplets with starting sizes $2R_d < 70\%$ 
+of the initial system size disappeared. This occurred due to the initial condition of each fluid set to not contain the 
+other fluid species, meaning once the simulation was initiated diffusion of mass from the droplet to the bulk occurred, 
+causing disappearance of the droplet until the thermodynamically optimal composition was reached. From the fit calculated 
+in Figure \ref{fig:young_laplace_valid}, the fit is linear as long as the initial droplet size is sufficiently large. 
+Alternatively, the composition of the system can be set to near equilibrium in order to allow access to smaller droplet 
+sizes.
 
@@
 
-Contact angle plays a role in particle stabilized emulsions by controlling the free energy reduction that the interface has in addition to the imparting of preferential curvature.
-LB3D allows for modification of the contact angle of a particle through the addition of a shell of blue or red fluid to the surface of the Ladd particle termed as the particle color $(\Delta \rho)$.
-\cite{jansen_bijels_2011, gunther_lattice_2013} To ensure that the correct settings are used in these simulations, in addition to gaining understanding into how to change parameters if the need arises, the contact angle as a function of the particle color was calculated.
+Contact angle plays a role in particle stabilized emulsions by controlling the free energy reduction that the interface 
+has in addition to the imparting of preferential curvature. LB3D allows for modification of the contact angle of a 
+particle through the addition of a shell of blue or red fluid to the surface of the Ladd particle termed as the particle 
+color $(\Delta \rho)$. \cite{jansen_bijels_2011, gunther_lattice_2013} To ensure that the correct settings are used in 
+these simulations, in addition to gaining understanding into how to change parameters if the need arises, the contact 
+angle as a function of the particle color was calculated.
 
-Experimentally and computationally, the contact angle can be calculated through direct measurement of the angle of a droplet on a substrate.
-A droplet that preferentially wets a substrate has a lower contact angle relative to that substrate material, physically manifesting as the droplet spreading on the substrate.
-At a liquid interface, the particle will prefer to be in the particle it wets more.
-Thus for a spherical particle, the contact angle can be calculated as $\theta_c = \arccos{\frac{h_p - h_i}{R_p}}$ where $h_p - h_i$ defines the distance between the center of the particle after reaching its steady state position and the interface and $R_p$ is the radius of the spherical particle.
-\cite{gunther_lattice_2013, davies_interface_2014} This has been extended to ellipsoidal particles through assuming that the particle will have its largest cross sectional area flat on the interface and using the radius that is perpendicular to the interface to calculate the contact angle, defined as $\theta_c = \arccos{\frac{h_p - h_i}{R_{\parallel}}}$ and $\theta_c = \arccos{\frac{h_p - h_i}{R_{\perp}}}$ if $\alpha < 1$ and $\alpha \geq 1$ respectively.
+Experimentally and computationally, the contact angle can be calculated through direct measurement of the angle of a 
+droplet on a substrate. A droplet that preferentially wets a substrate has a lower contact angle relative to that 
+substrate material, physically manifesting as the droplet spreading on the substrate. At a liquid interface, the particle 
+will prefer to be in the particle it wets more. Thus for a spherical particle, the contact angle can be calculated as 
+$\theta_c = \arccos{\frac{h_p - h_i}{R_p}}$ where $h_p - h_i$ defines the distance between the center of the particle 
+after reaching its steady state position and the interface and $R_p$ is the radius of the spherical particle. 
+\cite{gunther_lattice_2013, davies_interface_2014} This has been extended to ellipsoidal particles through assuming 
+that the particle will have its largest cross sectional area flat on the interface and using the radius that is 
+perpendicular to the interface to calculate the contact angle, defined as $\theta_c = \arccos{\frac{h_p - h_i}{R_{\parallel}}}$ 
+and $\theta_c = \arccos{\frac{h_p - h_i}{R_{\perp}}}$ if $\alpha < 1$ and $\alpha \geq 1$ respectively.
 
-The simulation was setup in a box of size $32\cdot32\cdot64$ with an interface lying at $z = 32$, and a single particle placed at the center of the box with periodic boundary conditions on all sides.
-Fluid and non-ideal mixing properties were the same as those listed in table \ref{table:model_params}.
-The particle was then placed at the center of the simulation box and run for $30000$ timesteps with data read every 500 timesteps.
-The contact angles shown are results from triplicate runs, and averages of the final 10 data points.
+The simulation was setup in a box of size $32\cdot32\cdot64$ with an interface lying at $z = 32$, and a single particle 
+placed at the center of the box with periodic boundary conditions on all sides. Fluid and non-ideal mixing properties were 
+the same as those listed in table \ref{table:model_params}. The particle was then placed at the center of the simulation 
+box and run for $30000$ timesteps with data read every 500 timesteps. The contact angles shown are results from triplicate 
+runs, and averages of the final 10 data points.
 
@@
     \includegraphics[scale = 0.5]{figures/model_validation/contact_angle_compare.png}
-    \caption{Contact angle with respect to the oil phase, $(\theta_c^{oil})$ of the particles plotted against the control parameter in LB3D}
+    \caption{Contact angle with respect to the oil phase, $(\theta_c^{oil})$ of the particles plotted against the 
+    control parameter in LB3D}
     \label{fig:contact_angle_valid}
@@
 
-Figure \ref{fig:contact_angle_valid} demonstrates the contact angles of the three particle geometries analyzed, confirming that $\Delta \rho = 0$ will result in neutrally wetting particles for all geometries.
-Oblate and spherical particles have usable particle colors between $-0.10 \leq \Delta \rho \leq 0.10$ while for prolate ellipsoids this value is $-0.05 \leq \Delta \rho \leq 0.05$.
-The slope of ellipsoidal particles appears to be lower which may arise from a larger interfacial adsorption energy, making it more difficult for surface energy changes to move particles out of the interface.
-At $\Delta \rho$ values further from 0, it was observed that the prolate particles tended to leave the interface rather than stay at a slightly off center equilibrium position.
+Figure \ref{fig:contact_angle_valid} demonstrates the contact angles of the three particle geometries analyzed, 
+confirming that $\Delta \rho = 0$ will result in neutrally wetting particles for all geometries. Oblate and spherical 
+particles have usable particle colors between $-0.10 \leq \Delta \rho \leq 0.10$ while for prolate ellipsoids this 
+value is $-0.05 \leq \Delta \rho \leq 0.05$. The slope of ellipsoidal particles appears to be lower which may arise 
+from a larger interfacial adsorption energy, making it more difficult for surface energy changes to move particles out 
+of the interface. At $\Delta \rho$ values further from 0, it was observed that the prolate particles tended to leave 
+the interface rather than stay at a slightly off center equilibrium position.

### 2025-02-14 chapters/paper3.tex
Changes 1. Made tex files human readable again 2. Added content to paper3 tex file 3. Added licenses to some of the images from other papers

@@
 
-In many of the manufacturing techniques outlined for continuous bijel production such as STrIPS, the rheological properties are essential in ensuring that the casting mixture remains processable.
-However, past work with ferrofluids and magnetic emulsions have showed how the rheological properties vary drastically as a function of the field strength.
-Bijels themselves have complex rheological properties stemming from the removal of particles from the interface if too much shear is applied.
-Therefore, avenues of exploration here would be how the rheological properties of bijels change under the influence of fields in response to an applied shear.
-One of the questions that will be investigated in particular will be how shear changes the orientation of the particles on the interface, the interfacial coverage of particles and if there is anisotropy in the viscosity during the application of a field owing to the orientation of particles towards the field.
+While the microstructure and synthesis techniques for bijels have been explored in earnest, the rheology of bijels
+has only recently seen an uptick in interest. Some interesting phenomena for bijels and shearing include the 
+presence of monogels, made by remixing the phase separated liquid domains of the bijel while the electrostatic
+interactions between particles maintains the structure of the particle monolayer. \textcolor{blue}{https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.103.255502}
+This behavior is system specific, suggesting the fluid system plays a role in this behavior as well. \textcolor{blue}{https://doi.org/10.1002/adfm.201002562} 
+\cite{bai_dynamics_2015} Investigations have identified that confined bijels under shear undergo elongation of
+the domains in the direction of shear succeeded by particle detachment from the interface and eventual failure of the bijel. \cite{bonaccorso_shear_2020}
+More recently, bijels have been identified to be 2D glasses percolating in 3D space, characterized through comparing the complex rheology of bijels against
+colloidal gels made from silica particles with electrostatic interactions. \cite{ching_bijel_2022}
 
-First, a shear capillary number is defined as $Ca_s = \frac{\eta_{f} \dot{\gamma} L_{1}}{\sigma}$ where $\dot{\gamma} = \frac{u_{LE}}{L_x}$ is the strain rate and $L_1$ is the average domain size.
-\cite{frijters_effects_2012, yang_capillary_2022} In the literature, $Ca_s$ has been between between 0.04 and 0.16.
-However, the box size in these simulations were smaller, meaning that these capillary number ranges would exceed the maximum mach number the model allows if this same range were used $(Ma \leq 0.03)$.
-To accommodate this limitation the largest capillary number used will be $Ca_s = 10^-5$ which correspond to a maximum of $Ma \approx 0.002$.
-$Ca_s = 10^-6,  10^-7$ will also be used to demonstrate how the bijels respond to shear of varying strengths.
-As all particles used have only hard-sphere type interactions, it is expected that the behaviour seen should mimic 2D colloidal glasses percolating in 3D space, akin to what Ching and Mohraz saw, with an additional dependence on -the direction of shear.
-This would predict the discovery of particle monolayer dependent elasticity and yield stress along with shear thinning behaviour as a function of strain rate.
+In many of the manufacturing techniques outlined for continuous bijel production such as STrIPS, the rheological properties are essential in ensuring that 
+the casting mixture remains processable. \cite{haase_continuous_2015,haase_situ_2016} While particle stabilized emulsions have been shown to be shear thinning, 
+our investigation into magnetically stimuli responsive bijels will modify the behavior of these systems due to the application of magnetic fields. Past work with 
+ferrofluids and magnetic emulsions have showed how the rheological properties vary drastically as a function of the field strength due to the orientation of the 
+particles. \textcolor{blue}{https://doi.org/10.1016/j.colsurfa.2012.06.026} The orientation of the particle to shear as well as the nematic order of particles 
+can cause shear banding and a smaller effective viscosity owing to a smaller cross sectional area being presented to the direction of shear.
 
-To verify these predictions, bijel microstructure will be defined using four processing histories; The first is of a bijel simulated under a $\Bar{B} = 1$ magnetic field strength, the second is a bijel stimulated under no field, followed by the application of a $\Bar{B} = 1$ field after jamming, the third is a bijel simulated under no field, while the final microstructure is a bijel simulated under $\Bar{B} = 1$ magnetic field, followed by switching the field off after jamming.
-This gives insight into the impact of processing history on the shear properties of a bijel, in addition to the microstructural and colloidal insights gained.
-Based on the results in Bonaccorso et al., there should be shear driven and shear rate dependent elongation of the domains in the direction parallel to the applied shear which in this system will be seen as a reduction in $L_{\perp}$ and an increase in $L_{\parallel}$.
-\cite{bonaccorso_shear_2020} The microstructure anisotropy will also be a factor in the viscosity results, as larger domains are more permeable than smaller ones, meaning that bijels where $L_{\perp} > L_{\parallel}$ should see less of the domain elongation effects shown in Bonaccorso et al.
-as the permeability of the bijels rises with larger domain size.
-\cite{bonaccorso_shear_2020}
+In this chapter, we probe the dynamics of bijels under constant and complex shear to understand how the application of magnetic fields onto bijels stabilized with
+anisotropic particles. We define a shear capillary number $Ca_s = \frac{\eta_{f} \dot{\gamma} L_{1}}{\sigma}$ where $\dot{\gamma} = \frac{2u_{LE}}{L_x}$ is the
+strain rate and $L_1$ is the average domain size. \cite{frijters_effects_2012, yang_capillary_2022} In the literature, $Ca_s$ has been between between 0.04 
+and 0.16. However, the box size in these simulations were smaller, meaning that these capillary number ranges would exceed the 
+maximum mach number the model allows if this same range were used $(Ma \leq 0.03)$. To accommodate this limitation the 
+largest capillary number used will be $Ca_s = 10^-5$ which correspond to a maximum of $Ma \approx 0.002$. $Ca_s = 10^-6,  
+10^-7$ will also be used to demonstrate how the bijels respond to shear of varying strengths. As all particles used 
+have only hard-sphere type interactions, it is expected that the behaviour seen should mimic 2D colloidal glasses 
+percolating in 3D space, akin to what Ching and Mohraz saw, with an additional dependence on -the direction of shear. 
+This would predict the discovery of particle monolayer dependent elasticity and yield stress along with shear thinning 
+behaviour as a function of strain rate.
 
-It is also expected that the effective viscosity will be different between the four microstructures dependent upon the degree of nematic ordering and microstructural anisotropy of the bijel.
-Nematic ordering of the particles will be mimic shear banding in colloidal suspensions, resulting in a lowered effective viscosity compared to bijels without nematically ordered particles.
-\cite{xu_relation_2013, vermant_flow-induced_2005} Tracking of the proportion of particles on the interface will also yield insight into how the packing of the particles affects the rate at which particles will get ejected from the interface.
-Systems with a larger $\eta_{eff}$ are predicted to have the largest domains, largest difference between initial and final particle order and lowest number of particles left on the interface once steady state has been established.
+To verify these predictions, bijel microstructure will be defined using four processing histories; The first is of a 
+bijel simulated under a $\Bar{B} = 1$ magnetic field strength, the second is a bijel stimulated under no field, 
+followed by the application of a $\Bar{B} = 1$ field after jamming, the third is a bijel simulated under no field, 
+while the final microstructure is a bijel simulated under $\Bar{B} = 1$ magnetic field, followed by switching the 
+field off after jamming. This gives insight into the impact of processing history on the shear properties of a bijel, 
+in addition to the microstructural and colloidal insights gained. Based on the results in Bonaccorso et al., there 
+should be shear driven and shear rate dependent elongation of the domains in the direction parallel to the applied 
+shear which in this system will be seen as a reduction in $L_{\perp}$ and an increase in $L_{\parallel}$. 
+\cite{bonaccorso_shear_2020} The microstructure anisotropy will also be a factor in the viscosity results, as 
+larger domains are more permeable than smaller ones, meaning that bijels where $L_{\perp} > L_{\parallel}$ should 
+see less of the domain elongation effects shown in Bonaccorso et al. as the permeability of the bijels rises with 
+larger domain size. \cite{bonaccorso_shear_2020}
+
+It is also expected that the effective viscosity will be different between the four microstructures dependent upon the 
+degree of nematic ordering and microstructural anisotropy of the bijel. Nematic ordering of the particles will be mimic 
+shear banding in colloidal suspensions, resulting in a lowered effective viscosity compared to bijels without nematically 
+ordered particles. \cite{xu_relation_2013, vermant_flow-induced_2005} Tracking of the proportion of particles on the 
+interface will also yield insight into how the packing of the particles affects the rate at which particles will get 
+ejected from the interface. Systems with a larger $\eta_{eff}$ are predicted to have the largest domains, largest 
+difference between initial and final particle order and lowest number of particles left on the interface once steady 
+state has been established.
+
+\textcolor{blue}{https://doi.org/10.1073/pnas.0812519106}
+
+\begin{itemize}
+    \item Shear banding analyzed through looking at change in particle velocity in the x direction
+    \item Shear banding analyzed through looking at change in $Q_6$ in the x direction
+    \item 
+\end{itemize}

### 2025-02-15 chapters/dissertation-tap.tex
Changes 1. Using UD template class for dissertation

% 
% This is the Title and Approval Page file (dissertation-tap.tex) for
% a dissertation.
%
% The order of the commands below is very important.
% You may choose to add or eliminate a \prefacesection 
% in the front material but the order should remain 
% the same especially \maketocloflot followed by 
% \prefacesectiontoc{Abstract}

% Title and author are also used for PDF file properties
% No special character or commands can be used for the PDF definition; 
% use the [options] paramater to specify a different title or author 
% to remove special characters or commands like \\ for example.
\title[First Line of Title Second Line of Title]{Lattice Boltzmann simulations of magnetically responsive\\
anisotropic particle stabilized emulsions}
\author{Nikhil Karthikeyan}
\type{dissertation}
\degree{Doctor of Philosophy}
\majorfieldtrue\majorfield{Materials Science and Engineering}
\degreedate{Spring 2025}
% Optional PDF properties
\keywords{Keyord,Keyword,Keyword}
\subject{Subject}

\maketitlepage % Generates Title Page

\begin{approvalpage}
\chair{Joshua Zide, PhD}{Chair of the Department of Materials Science and Engineering}
\dean{Jamie Phillips, PhD}{Dean of the College of Engineering}
\end{approvalpage}

\begin{signedpage} % Up to 4 signatures
\profmember{Ulf D. Schiller, PhD}
\member{Eric Furst, PhD}
\member{Arthi Jayaraman, PhD}
\member{Darrin Pochan, PhD}
\end{signedpage}

% For additional signatures beyond 4, uncomment and use
% \begin{signedpagecont}
% \member{Xxxx Xxxx, Highest Degree}
% \member{Xxxx Xxxx, Highest Degree}
% \end{signedpagecont}

\begin{front} % Starts front material (Roman style page numbers)

\prefacesection{Acknowledgements}
%\input{acknowl} % This file (acknowl.tex) contains the text
                % for the acknowledgments or type text here.

In the development of this dissertation, I extend my deepest gratitude to Dr Ulf Schiller whose support, motivation and 
opportunities have been indispensible during my PhD. I believe his approach to mentorship, methodical problem solving 
strategies, depth and breadth of knowledge have been invaluable sources of inspiration for this research as well as 
motivating myself to strive towards those ideals. I would also like to thank members of my committee, especially 
Dr Arthi Jayaraman from the University of Delaware and Dr Olga Kuksenok from Clemson University for their mentorship 
and motivation that pushed me to increase my breadth of knowledge and to think outside the box.

Listing everyone I am grateful for who have provided me non-academic support would be too long for this page 
although I shall try to summarize this. I am grateful to my family, with whom I may not be the best at 
discussing my future plans, but they have been an indispensible source of support during my time away from home. 
I am thankful to my lab members especially for adding brief moments of levity during my PhD and giving me the 
opportunity to be a part of their own journey in graduate school. Thank you to everyone who has been with me 
through thick and thin, and to many more celebrations of our achievements.

% Table of Contents is always created, but you
% may set \tablespagefalse and \figurespagefalse 
% if you don't want these generated automatically
% (i.e. List of Tables and List of Figures).
% These are set to true by default (i.e. \tablespagetrue,
% \figurespagetrue).

% Uncomment if you do not want a List of Figures.
%\figurespagefalse

% Uncomment if you do not want a List of Tables.
%\tablespagefalse

\maketocloflot

\prefacesectiontoc{Abstract}
%\input{abstract} % This file (abstract.tex) contains the text
                 % for an abstract or type text here.

Porous materials have found greater importance in applications such as water filtration, catalyst supports, battery 
electrodes and bio engineered materials. To accommodate a greater variety of pore sizes and continuous fabrication 
techniques with minimal waste, bottom up synthesis techniques have been gaining in popularity.

One such bottom up fabrication technique relies on jamming of particle stabilized emulsions into bicontinuous 
interfacially jammed emulsion gels(bijels). However, casting mixture independent microstructure control has not 
been identified, especially applicable in continuous bijel synthesis strategies such as Solvent Transfer Induced 
Phase separation. Stimuli response has been identified as a technique to enable this. This study focuses on utilizing 
stimuli response of bijels stabilized with ellipsoidal microparticles, and the resulting microstructure and rheological 
implications this induces.

We first identify that upon application of a field to a bijel stabilized with ellipsoidal particles during synthesis, 
microstructure change is observed, not present when analyzing bijels stabilized with spherical particles. Upon 
application of the field, particles reorient to the direction of the field, dragging the interface along with 
them. This causes the bijel to have axially dependent jamming, causing anisotropic microstructures to form.

We then identify that bijels stabilized with ellipsoidal particles have tunable microstructures after jamming. 
This process is dependent upon the initial particle order present in the bijel, as well as the difference 
between the initial and final particle order. We also show that the structural response observed is state 
dependent, meaning that the time of magnetic field application affects the microstructure change observed.

\end{front}

### 2025-02-16 chapters/analysis_techniques.tex
Changes 1. Added more analysis to application of magnetic fields during formation chapter 2. Added references to fix some (not all) literature reference issues 3. Added some detail in analysis techniques section

@@
 
-In this work, the structure factor derived domain size, geometric pore size distribution and tortuosity will be utilized to characterize the microstructure.
-The nematic order parameter will be used to characterize the particle order to the magnetic field.
-The average angle to the interface will be utilized to characterize how the particles ordering to the field affect the interface position.
-Finally, the radial distribution function will be used to probe how differences in ordering change the packing of particles on the interface.
-The time evolution of viscosity will provide insight into the rheological properties of the bijel, while the aforementioned analysis tools in addition to proportion of particles on the interface will be calculated to provide insight into how the bijel reacts to shear, parallel and perpendicular to the magnetic field.
-A more detailed description of the implementation of each method is shown in subsequent sections.
+In this work, the structure factor derived domain size, geometric pore size distribution and tortuosity will be 
+utilized to characterize the microstructure. The nematic order parameter will be used to characterize the particle 
+order to the magnetic field. The average angle to the interface will be utilized to characterize how the particles 
+ordering to the field affect the interface position. Finally, the radial distribution function will be used to probe 
+how differences in ordering change the packing of particles on the interface. The time evolution of viscosity will 
+provide insight into the rheological properties of the bijel, while the aforementioned analysis tools in addition to 
+proportion of particles on the interface will be calculated to provide insight into how the bijel reacts to shear, 
+parallel and perpendicular to the magnetic field. A more detailed description of the implementation of each method is 
+shown in subsequent sections.
 
@@
 
-Particles are the cause of bijels but they can also make characterization of domain size, curvature, pore size distribution and tortuosity more difficult as particles may change these parameters.
-An extrapolation scheme is required to connect the interface one different sides of the particles and to fill in the particles themselves so as to create a more accurate interface for other techniques.
+Particles are the cause of bijels but they can also make characterization of domain size, curvature, pore size 
+distribution and tortuosity more difficult as particles may change these parameters. An extrapolation scheme is 
+required to connect the interface one different sides of the particles and to fill in the particles themselves so 
+as to create a more accurate interface for other techniques.
 
-This is accomplished through sequential density averaging and filling of grid points making up the particles from the outside in.
-The grid cells around a cell of interest are averaged using a D3Q19 like lattice and stepping through all points with a order parameter $\phi = \rho^w - \rho^o$ value of 0.
+This is accomplished through sequential density averaging and filling of grid points making up the particles from 
+the outside in. The grid cells around a cell of interest are averaged using a D3Q19 like lattice and stepping through 
+all points with a order parameter $\phi = \rho^w - \rho^o$ value of 0.
 
 \subsection{Domain size}
+\label{section:domain_size}
 
-The characteristic length scale at time $t$ of a bijel can be computed from the moments of the structure factor.
-The structure factor is first calculated from the order parameter of the phases, defined as $\phi = \rho_b - \rho_r$ where $\phi$ is the density order parameter and $\rho_b$ and $\rho_r$ are the densities of the blue and red fluid respectively.
-Next, the fluctuations of the order parameter $\phi'$ is calculated by subtracting the mean of the order parameter, $\langle \phi \rangle$ from the order parameter, defined as $\phi' = \phi - \langle \phi \rangle$.
-Next, the fourier transform of the fluctuations of the order parameter $\phi'(\mathbf{k})$ is calculated.
-Finally, $\phi'(\mathbf{k})$ is squared and made positive and normalized by the volume of the system defined as $S(\mathbf{k}) = \frac{1}{N} |\phi'(\mathbf{k})^2|$.
+The characteristic length scale at time $t$ of a bijel can be computed from the moments of the structure factor. The 
+structure factor is first calculated from the order parameter of the phases, defined as $\phi = \rho_b - \rho_r$ where 
+$\phi$ is the density order parameter and $\rho_b$ and $\rho_r$ are the densities of the blue and red fluid respectively. 
+Next, the fluctuations of the order parameter $\phi'$ is calculated by subtracting the mean of the order parameter, 
+$\langle \phi \rangle$ from the order parameter, defined as $\phi' = \phi - \langle \phi \rangle$. Next, the fourier 
+transform of the fluctuations of the order parameter $\phi'(\mathbf{k})$ is calculated. Finally, $\phi'(\mathbf{k})$ 
+is squared and made positive and normalized by the volume of the system defined as 
+$S(\mathbf{k}) = \frac{1}{N} |\phi'(\mathbf{k})^2|$.
 
-The first domain size metric used is the domain size derived from the spherically averaged first moment of the structure factor.
-The spherical averaging is done by averaging the values of the structure factor at the same $\mathbf{k}$ up till the nyquist frequency.
-The spherically averaged structure factor is defined as $S(k)$ where $k$ represents the wave numbers obtained from the spherical averaging.
-Next, the first moment $\langle k_1 \rangle$ is calculated as $\langle k_1 \rangle = \frac{\Sigma_{k} k\cdot S(k)}{\Sigma_{k} S(k)}$.
-Finally, the domain size is calculated as $L_1 = \frac{2 \pi}{\langle k_1 \rangle}$.
-This domain size is used in past literature \textcolor{blue}{https://doi.org/10.1017/S0022112001004682, https://www.doi.org/10.1103/PhysRevE.67.046304} to calculate the correct scaling regime of a system undergoing spinodal decomposition.
+The first domain size metric used is the domain size derived from the spherically averaged first moment of the structure 
+factor. The spherical averaging is done by averaging the values of the structure factor at the same $\mathbf{k}$ up 
+till the nyquist frequency. The spherically averaged structure factor is defined as $S(k)$ where $k$ represents the 
+wave numbers obtained from the spherical averaging. Next, the first moment $\langle k_1 \rangle$ is calculated as 
+$\langle k_1 \rangle = \frac{\Sigma_{k} k\cdot S(k)}{\Sigma_{k} S(k)}$. Finally, the domain size is calculated as 
+$L_1 = \frac{2 \pi}{\langle k_1 \rangle}$. This domain size is used in past literature 
+\textcolor{blue}{https://doi.org/10.1017/S0022112001004682, https://www.doi.org/10.1103/PhysRevE.67.046304} 
+to calculate the correct scaling regime of a system undergoing spinodal decomposition.
 
-While it cannot be used to correlate physical phenomena the second moment of the structure factor derived domain size is utilized here to discriminate directional length scales.
-Owing to the spherical averaging done, the first moment moment derived domain size is unable to be used to calculate direction specific length scales.
-The second moment of the structure factor is first calculated by multiplying $\langle \mathbf{k_2}^2 \rangle = \frac{\Sigma_{\mathbf{k}} \mathbf{k}^2 S(\mathbf{k})}{\Sigma_k S(\mathbf{k})}$ where $\mathbf{k_2}^2$ represents the second moment in each cartesian direction.
-Next, the domain size in each direction is calculated as $L_2 = \frac{2 \pi}{\sqrt{\mathbf{k_2}^2}}$.
-\cite{jansen_bijels_2011, gunther_timescales_2014} In the rest of this document, $L_{\parallel}$ and $L_{\perp}$ is defined as the domain size parallel and perpendicular to the applied magnetic field.
+While it cannot be used to correlate physical phenomena the second moment of the structure factor derived domain 
+size is utilized here to discriminate directional length scales. Owing to the spherical averaging done, the first 
+moment moment derived domain size is unable to be used to calculate direction specific length scales. The second 
+moment of the structure factor is first calculated by multiplying 
+$\langle \mathbf{k_2}^2 \rangle = \frac{\Sigma_{\mathbf{k}} \mathbf{k}^2 S(\mathbf{k})}{\Sigma_k S(\mathbf{k})}$ 
+where $\mathbf{k_2}^2$ represents the second moment in each cartesian direction. Next, the domain size in each 
+direction is calculated as $L_2 = \frac{2 \pi}{\sqrt{\mathbf{k_2}^2}}$. \cite{jansen_bijels_2011, gunther_timescales_2014} 
+In the rest of this document, $L_{\parallel}$ and $L_{\perp}$ is defined as the domain size parallel and perpendicular to 
+the applied magnetic field.
+
+\subsection{Curvature}
+\label{section:curvature}
+
+The simulation data was first pre-processed by calculating the order parameter of the densities, defined as the difference between the blue and red 
+fluid densities at each grid point. $\phi(\vec{x}) = \rho^b(\vec{x}) - \rho^r(\vec{x})$. We then apply the particle filling algorithm described in 
+section \ref{section:filling_routine} to the $\phi$ distribution, This reduces error from the presence of particles at the interface, 
+resulting in an interface geometry that is more accurate to the bijel interface profile. From the filled order parameter, $\phi$, we calculate the mesh of 
+the iso-surface representing the interface at $\phi = 0$ using a marching cubes method as implemented in scikit-image. We then use pyvista to calculate the 
+gaussian and mean curvatures of the bijel microstructure, in addition to the interface area. The radii of curvature, $R_1, R_2$ are calculated from the 
+mesh through measuring the angles between nearest neighbors and the laplacian of the faces to calculate the Gaussian and mean curvature respectively.
+
+We then limit the values of the calculated Gaussian and mean curvatures to reduce the effect of numerical artefacts created during the meshing process. We 
+limit the Gaussian and mean curvatures to the expected curvatures around $|H| \approx \frac{2}{L}$ and $|K| \approx (\frac{2}{L})^2$. $L$ here is defined 
+as the characteristic length scale obtained from the first moment of the spherically averaged structure factor described in section \ref{section:domain_size}.  
+We then calculate an interface area normalized curvatures to remove the differences in absolute curvature values arising from the change in the characteristic 
+length scale by calculating the surface area to volume ratio, $\Sigma = A_{int}/V$ where $A_{int}$ is the interfacial area and $V$ is the system volume. After 
+dividing the obtained curvatures with $Sigma$, we obtain the discrete quantities, $H \Sigma^{-1}$ and $K \Sigma^{-2}$. For data presented as a time or magnetic 
+field series, we sum each curvature distributions yielding, $\langle H \Sigma^{-1} \rangle$ and $\langle K \Sigma^{-2} \rangle$. For a bijel with volume ratio 
+$50:50$ as used here, we expect $\langle K \Sigma^{-2} \rangle < 0$ and $\langle H \Sigma^{-1} \rangle \approx 0$.
 
 \subsection{Tortuosity}
+\label{section:tortuosity}
 
-Tortuosity can be defined as the ratio between the path length $(L_{eff})$ of two points and the euclidean distance between two points $L_{0}$, $\tau = L_{eff}/L_{0}$.
-In practice this is the geometric definition of tortuosity as often the tortuosity of a system is dependent upon other factors.
-Diffusive tortuosity is what we will use here, defined as $\tau = \frac{D_{eff}}{D_0}$.
-This metric is also more relevant to the potential applications of bijels which rely on diffusion of mass for their uses.
+Tortuosity can be defined as the ratio between the path length $(L_{eff})$ of two points and the euclidean distance 
+between two points $L_{0}$, $\tau = L_{eff}/L_{0}$. In practice this is the geometric definition of tortuosity as 
+often the tortuosity of a system is dependent upon other factors. Diffusive tortuosity is what we will use here, 
+defined as $\tau = \frac{D_{eff}}{D_0}$. This metric is also more relevant to the potential applications of bijels 
+which rely on diffusion of mass for their uses.
 
-Simulation techniques such as Lattice Boltzmann or Molecular Dynamics have been used to characterize the tortuosity of porous materials.
-However, these simulations can be computationally expensive and time consuming to perform, even though they may have great accuracy.
-Recently, particle diffusion techniques based on a random walk such as pytrax and taufactor or Pore Network Modelling (PNM) based techniques such as PoreSpy have been introduced which offer a tradeoff of accuracy for speed.
-Taufactor in particular is implemented on GPU's with a periodic boundary condition, allowing for rapid and accurate calculation of the tortuosity.
+Simulation techniques such as Lattice Boltzmann or Molecular Dynamics have been used to characterize the tortuosity of 
+porous materials. However, these simulations can be computationally expensive and time consuming to perform, even though 
+they may have great accuracy. Recently, particle diffusion techniques based on a random walk such as pytrax and taufactor 
+or Pore Network Modelling (PNM) based techniques such as PoreSpy have been introduced which offer a tradeoff of accuracy 
+for speed. Taufactor in particular is implemented on GPU's with a periodic boundary condition, allowing for rapid and 
+accurate calculation of the tortuosity.
 
@@
 
-Before using taufactor, the microstructure is first binarized.
-This is done by first calculating the order parameter of the system with $\phi = \rho_b - \rho_r$ where $\phi$ is the order parameter and $\rho_b, \rho_r$ are the densities of the blue and red fluid respectively.
-Next, the interface described with $\phi$ is smoothened using the algorithm detailed in section \ref{section:filling_routine}.
-In many of the bijels synthesized using small molecule liquids, monomer is introduced into the oil phase and polymerized.
-Therefore, to perform the binarization step, we select all points where $\phi \leq 0$ and set their value to $0$, and all other values are set to $1$.
-To taufactor, $1$ represents void spaces and 0's are solid.
+Before using taufactor, the microstructure is first binarized. This is done by first calculating the order parameter of 
+the system with $\phi = \rho_b - \rho_r$ where $\phi$ is the order parameter and $\rho_b, \rho_r$ are the densities of 
+the blue and red fluid respectively. Next, the interface described with $\phi$ is smoothened using the algorithm detailed 
+in section \ref{section:filling_routine}. \texttt{taufactor} determines the tortuosity by comparison
+of steady-state diffusive flow through a porous medium with the bulk
+diffusive flow in a control volume of the same size, molecular
+diffusivity, and driving force \cite{cooper_taufactor_2016}. We used
+the \texttt{PeriodicSolver} to employ periodic boundary conditions. In many of the bijels synthesized using small molecule liquids, monomer is 
+introduced into the oil phase and polymerized. Therefore, to perform the binarization step, we select all points where 
+$\phi \leq 0$ and set their value to $0$, and all other values are set to $1$. To taufactor, $1$ represents void spaces 
+and 0's are solid. \cite{cooper_taufactor_2016}
 
 \subsection{Nematic order parameter}
+\label{section:nematic_order_parameter}
 
-The orientational ordering of the particles to one another can be characterized using the nematic order parameter, defined as $S$.
-This parameter was first used to characterize liquid crystals.
-However its use has expanded to colloidal systems to characterize the ordering of a system to an average orientation, termed the director.
-A system is said to have nematic ordering if its components have orientational order to the director but does not require the system to have translational order.
+The orientational ordering of the particles to one another can be characterized using the nematic order parameter, 
+defined as $S$. This parameter was first used to characterize liquid crystals. However its use has expanded to colloidal 
+systems to characterize the ordering of a system to an average orientation, termed the director. A system is said to have 
+nematic ordering if its components have orientational order to the director but does not require the system to have 
+translational order.
 
-The nematic order parameter is calculated from the orientational alignment tensor, $Q$, which is calculated from the orientation of particles to one another as $\langle Q \rangle = \frac{1}{N} \sum_{i}^{N} \langle \frac{3}{2}u_i u_i - \frac{1}{2}I \rangle$.
-$u_i$ is the orientation of particle $i$ and $I$ is an identity matrix.
-\cite{veerman_phase_1992} While there are multiple methods to evaluate the nematic order parameter, the one we have picked is where the largest eigenvector is $S$, with its corresponding eignvector referring to the director of the system.
-\cite{veerman_phase_1992} \textcolor{blue}{https://doi.org/10.1080/00268978400101951} A system is defined to be ordered nematically, if $S > 0.3$.
-In this work, the direction of the director will be compared to the direction of the magnetic field.
-We utilize the implementation in Freud to calculate the nematic order parameter.
+The nematic order parameter is calculated from the orientational alignment tensor, $Q$, which is calculated from the 
+orientation of particles to one another as 
+$\langle Q \rangle = \frac{1}{N} \sum_{i}^{N} \langle \frac{3}{2}u_i u_i - \frac{1}{2}I \rangle$. $u_i$ is the 
+orientation of particle $i$ and $I$ is an identity matrix. \cite{veerman_phase_1992} While there are multiple 
+methods to evaluate the nematic order parameter, the one we have picked is where the largest eigenvector is $S$, 
+with its corresponding eignvector referring to the director of the system. \cite{veerman_phase_1992} 
+\textcolor{blue}{https://doi.org/10.1080/00268978400101951} A system is defined to be ordered nematically, 
+if $S > 0.3$. In this work, the direction of the director will be compared to the direction of the magnetic 
+field. We utilize the implementation in Freud to calculate the nematic order parameter.
 
 \subsection{Radial distribution function}
+\label{section:radial_distribution}
 
-The radial distribution function (RDF) is used to measure the normalized number density of particles around a reference particle as a function of distance.
-The normalization factor is the expected density of particles derived from an ideal gas.
-The general form of the equation to calculate the RDF is $g(r) = \frac{1}{\rho_{ideal}(r) 4\pi r^2} \int_{r}^{r+\Delta r} \delta(r_{i} - r_{j}) dr$ where $\rho_{ideal}(r)$ represents the density expected at distance r from a reference particle in an ideal gas, $\delta(r_{i} - r_{j})$ represents the number of particles within the bin $r + \Delta r$ and integrated to get a volumetric density.
-As implemented in a numerical method, the integral becomes a sum.
-After correcting for the periodic boundary condition using the minimum image convention, the RDF can be used to characterize periodic systems.
-We utilize the implementation in the software package Freud.
+The radial distribution function (RDF) is used to measure the normalized number density of particles around a 
+reference particle as a function of distance. The normalization factor is the expected density of particles derived 
+from an ideal gas. The general form of the equation to calculate the RDF is 
+$g(r) = \frac{1}{\rho_{ideal}(r) 4\pi r^2} \int_{r}^{r+\Delta r} \delta(r_{i} - r_{j}) dr$ where $\rho_{ideal}(r)$ 
+represents the density expected at distance r from a reference particle in an ideal gas, $\delta(r_{i} - r_{j})$ 
+represents the number of particles within the bin $r + \Delta r$ and integrated to get a volumetric density. 
+As implemented in a numerical method, the integral becomes a sum. After correcting for the periodic boundary 
+condition using the minimum image convention, the RDF can be used to characterize periodic systems. We utilize 
+the implementation in the software package Freud. \cite{ramasubramani_freud_2020}
+
+\begin{equation}
+    g(r) = \frac{n_p-1}{n_p} V \left\langle\delta\left(r-r_i\right)\right\rangle ,
+\end{equation}
+
+where \(n_p\) is the number of particles in the volume
+\(V\), and \(\langle\cdot\rangle\) denotes an average over all
+particles. The radial distribution function was calculated by binning
+the distance between all particle pairs and normalizing the shells with
+respect to the distribution \(4\pi \rho r^2 \mathrm{d}r\) of an ideal
+gas.
 
 \subsection{Average interface angle and proportion of particles on the interface}
+\label{section:interface_angle}
 
-One way to differentiate between whether the particles pull the interface or whether the tilt of the particles at the interface causes changes to the jamming point is to characterize the average interface angle.
-The average interface angle $(\psi)$ is defined as the angle between the orientation of the axis of symmetry of the particle and the interface normal.
-The former mechanism would show little to no change in the interface angle, while the former mechanism should show large differences.
-The proportion of particles on the interface can also be calculated using this technique.
+One way to differentiate between whether the particles pull the interface or whether the tilt of the particles at 
+the interface causes changes to the jamming point is to characterize the average interface angle. The average interface 
+angle $(\psi)$ is defined as the angle between the orientation of the axis of symmetry of the particle and the interface 
+normal. The former mechanism would show little to no change in the interface angle, while the former mechanism should 
+show large differences. The proportion of particles on the interface can also be calculated using this technique.
 
-The orientation of the particle is obtained from the output files from the simulation.
-The interface normal needs to be calculated from $\phi$.
-This is done by taking $\phi$ as calaculated from the red and blue fluid densities, then performing the particle fill routine described in section \ref{section:filling_routine}.
-Next, a mesh corresponding to the interface is obtained using a marching cubes algorithm at a countour level of 0 with a cube length of 4 lattice units, which corresponds to the thickness of the interface.
-\textcolor{blue}{https://doi.org/10.7717/peerj.453} The position of the particle and its closest vertex is calculated.
-If this distance is larger than the first minimum in the radial distribution function, it is considered to be not on the interface and the next step is not performed.
-The vertex and corresponding normal closest to the position of a particle is used in the dot product, $\cos{\psi} = \frac{n_{int} \cdot o_{i}}{|n_{int}| |o_i|}$ where $n_{int}$ is the normal of the interface and $o_i$ is the orientation of particle i.
-After looping through all the particles, the average of $\psi$ and the number of particles in the interface is calculated.
+The orientation of the particle is obtained from the output files from the simulation. The interface normal needs to 
+be calculated from $\phi$. This is done by taking $\phi$ as calaculated from the red and blue fluid densities, then 
+performing the particle fill routine described in section \ref{section:filling_routine}. Next, a mesh corresponding 
+to the interface is obtained using a marching cubes algorithm at a countour level of 0 with a cube length of 4 lattice 
+units, which corresponds to the thickness of the interface. \textcolor{blue}{https://doi.org/10.7717/peerj.453} The 
+position of the particle and its closest vertex is calculated. If this distance is larger than the first minimum in 
+the radial distribution function, it is considered to be not on the interface and the next step is not performed. The 
+vertex and corresponding normal closest to the position of a particle is used in the dot product, 
+$\cos{\psi} = \frac{n_{int} \cdot o_{i}}{|n_{int}| |o_i|}$ where $n_{int}$ is the normal of the interface and $o_i$ 
+is the orientation of particle i. After looping through all the particles, the average of $\psi$ and the number of 
+particles in the interface is calculated.
+
+\subsection{Steinhardt order parameter}
+\label{section:steinhardt_order_parameter}
+
+Another factor affected by the application of the magnetic field is the Steinhardt 6 fold order parameter, $Q6$, which characterized the local 
+particle ordering. \cite{steinhardt_bond-orientational_1983} It has been used to characterize crystallization, glass transitions and crystal 
+structures for colloidal and molecular crystals. We utilize the average across all particles on the interface, $\langle Q6 \rangle$ and track 
+this parameter as a function of time. Past work has identified that local crystallization of colloidal crystals takes place at $\langle Q6 \rangle = 0.38$, 
+and that $\langle Q6 \rangle^{HCP} = 0.485$. \cite{steinhardt_bond-orientational_1983, toxvaerd_role_2020, mickel_shortcomings_2013} We utilize a voronoi 
+cell derived definition of the neighbor list of each particle, addressing some of the shortcomings highlighted in the original distance based definition. 
+\cite{steinhardt_bond-orientational_1983, mickel_shortcomings_2013}. We first define a complex orientational vector, $q_{lm}$
+
+\begin{equation}
+q_{lm}(i) = \frac{1}{N_b(i)} \Sigma_{j = 1}^{N_b(i)} Y_{lm}(\vec{R}_{ij})
+\end{equation}
+
+Where $N_b$ is the number of nearest neighbors of particle $i$, $l$ is controls to the degree of spherical harmonic to be calculated, $m$ is an integer 
+defined as $-l \leq m \leq l$ that defines which spherical harmonic is being calculated and $\vec{r}_{ij}$ is the distance between two particle centers. 
+The neighbor list $N_b$ is usually defined by a cutoff distance from the center of particle $i$ to its nearest neighbors $j$. Steinhardt then defined a 
+bond order parameter $q_l$ from $q_{lm}$ as
+
+\begin{equation}
+Q_{l}(i) = \sqrt{\frac{4 \pi}{2l + 1} \Sigma_{m = -l}^{l} |q_{lm}(i)|^2}
+\end{equation}
+
+In the literature, crystal structures can be distinguished from one another by plotting the distribution of two or more $Q_{l}$.
 
@@
 
-Shear viscosity is a physical parameter measured through the dissipation of applied strain onto a fluid, resulting in an applied shear stress.
-In an incompressible fluid, the viscosity $(\eta)$ is defined as the ratio between the measured shear stress $(\sigma)$ and the applied strain rate $(\dot{\gamma})$, $\sigma = \eta \dot{\gamma}$.
-In rheological experiments, the shear viscosity is measured through a viscometer based on Couette or shear viscometry and Poiselle or pressure gradient viscometry.
-A Couette cell functions by applying a shear velocity to one or more walls, and measuring the shear stress response of the fluid.
-Common geometries for Couette cells include the cone and plate and concentric cylinder viscometers.
+Shear viscosity is a physical parameter measured through the dissipation of applied strain onto a fluid, resulting in 
+an applied shear stress. In an incompressible fluid, the viscosity $(\eta)$ is defined as the ratio between the measured 
+shear stress $(\sigma)$ and the applied strain rate $(\dot{\gamma})$, $\sigma = \eta \dot{\gamma}$. In rheological 
+experiments, the shear viscosity is measured through a viscometer based on Couette or shear viscometry and Poiselle or 
+pressure gradient viscometry. A Couette cell functions by applying a shear velocity to one or more walls, and measuring 
+the shear stress response of the fluid. Common geometries for Couette cells include the cone and plate and concentric 
+cylinder viscometers.
 
-In this work, a shear velocity is imparted in the z direction, across the x-axis.
-Therefore, the shear stress in the x and z directions, $\sigma_{xz}$, is measured.
-$\sigma_{xz}$ is output per lattice in the output file, which is then averaged across the entire volume to obtain an average shear stress $\hat{\sigma_{xz}}$.
-The effective viscosity of the system, $\eta_{eff}$ is calculated using $\eta_{eff} = \frac{\hat{\sigma_{xz}}}{\dot{\gamma}}$ where $\dot{\gamma} = \frac{2 u_{LE}}{L_x}$.
-$u_{LE}$ is the shear velocity is enforced through the Lees-Edwards boundary condition, as described in section \textcolor{blue}{description of lees edwards BC}.
+In this work, a shear velocity is imparted in the z direction, across the x-axis. Therefore, the shear stress in the x 
+and z directions, $\sigma_{xz}$, is measured. $\sigma_{xz}$ is output per lattice in the output file, which is then 
+averaged across the entire volume to obtain an average shear stress $\hat{\sigma_{xz}}$. The effective viscosity of the 
+system, $\eta_{eff}$ is calculated using $\eta_{eff} = \frac{\hat{\sigma_{xz}}}{\dot{\gamma}}$ where $\dot{\gamma} = 
+\frac{2 u_{LE}}{L_x}$. $u_{LE}$ is the shear velocity is enforced through the Lees-Edwards boundary condition, as 
+described in section \textcolor{blue}{description of lees edwards BC}.
 
 \subsection{Yield stress and zero shear rate viscosity}
+\label{section:yield_stress}
 
 The yield stress of bijels can be calculated using the flow curve, stress ramp or from oscillatory rheological techniques. 
-The flow curve method involves the steady application of shear, followed by measurements of the shear stress response of the material.
-The plateau of the shear stress response is indicative of the yield stress of the material.
-The stress ramp method involves the application of a shear stress onto the material, followed by measurements of the strain rate.
-A perfectly elastic material will have no strain rate, while a perfectly disspitative material will have high strain rate.
-The yield stress is characterized as the point when a rapid increase in strain rate is observed.
-The yield stress from oscillatory rheology is defined when the storage modulus is lower than the loss modulus.
-This work will utilize the flow curve method.
+The flow curve method involves the steady application of shear, followed by measurements of the shear stress response of 
+the material. The plateau of the shear stress response is indicative of the yield stress of the material. The stress ramp 
+method involves the application of a shear stress onto the material, followed by measurements of the strain rate. A 
+perfectly elastic material will have no strain rate, while a perfectly disspitative material will have high strain rate. 
+The yield stress is characterized as the point when a rapid increase in strain rate is observed. The yield stress from 
+oscillatory rheology is defined when the storage modulus is lower than the loss modulus. This work will utilize the flow 
+curve method.
 
-The shear viscosity calculated using the method detailed in Section \ref{section:shear_viscosity} will be plotted as a function of applied shear rate.
-Rheological models such as the Herschel Buckley, Bingham Plastic or Carreu models can be utilized to fit the shear viscosity as a function of shear rate to calculate the zero shear rate viscosity.
-In bijel applications, this parameter gives insight into the material stability and processability.
+The shear viscosity calculated using the method detailed in Section \ref{section:shear_viscosity} will be plotted as a 
+function of applied shear rate. Rheological models such as the Herschel Buckley, Bingham Plastic or Carreu models can be 
+utilized to fit the shear viscosity as a function of shear rate to calculate the zero shear rate viscosity. In bijel 
+applications, this parameter gives insight into the material stability and processability.
+
+\subsection{Shear banding}
+\label{section:yield_stress}

### 2025-02-16 chapters/paper1.tex
Changes 1. Fixed reference formatting in bib file and added stylesheet for rendering 2. Modified formatting to improve human readability in an IDE
Changes 1. Made tex files human readable again 2. Added content to paper3 tex file 3. Added licenses to some of the images from other papers
Changes 1. Added more analysis to application of magnetic fields during formation chapter 2. Added references to fix some (not all) literature reference issues 3. Added some detail in analysis techniques section

@@
-Enter some blurb here for a short introduction to content
+The addition of microstructure control in bijels can be utilized to improve the performance of porous materials
+or soft matter derived from their co-continuous, tortuous microstructure. The importance of microstructure control
+allows an increase in the charge/discharge rate of batteries through reducing the material tortuosity, or improving the 
+adhesion and growth rate of bone grafts. These properties are imparted during the fabrication step of the bijel. Anisotropic
+particles adsorbed at interfaces induce shape-dependent capillary interactions that have distinct effects on the
+microstructure of emulsions, resulting in migration or rotation of particles at interfaces, in addition to the addition of
+distinct timescales of domain coarsening. \cite{loudet_capillary_2005, cavallaro_curvature-driven_2011, gunther_lattice_2013}
 
-\subsubsection{Model parameters and simulation setup}\label{sec:parameters}
+In bijels, ellipsoidal stabilizers have been demonstrates to result in additional timescales of domain coarsening 
+at long timescales owing to particle re-orientation at the interface due to interparticle capillary interactions 
+at long timescales. \cite{gunther_timescales_2014} In addition to possessing more timescales, property, bijels stabilized 
+with rod-like particles have been shown to result in smaller characteristic length scales, owing to the particles having a
+larger cross sectional area resulting in jamming occurring at larger interfacial areas. \cite{hijnen_bijels_2015}
 
-The dynamics of the binary fluid mixture is governed by inertial,
-viscous, and surface tension forces. The relative magnitudes of these
-forces at a characteristic length scale \(L\) and characteristic
-velocity \(U\) are captured by the capillary number $\mathrm{Ca}=\frac{\eta U}{\sigma}$ and the Weber number
-\(\mathrm{We}=\frac{\rho U^2 L}{\sigma}\).
-Here we are primarily interested in spinodal decomposition of the mixture, where we analyze the dynamics after the initial formation of the interfaces and neglect residual diffusion.
-Hence the Peclet number \(\mathrm{Pe}=\frac{UL}{\Gamma}\) is of lesser importance and we do not consider it when choosing our simulation parameters.
+Magnetic response has been used in particle stabilized emulsions in the past, causing controlled emulsion failure and
+on-demand droplet coalescence for encapsulation and cargo release applications. \cite{melle_pickering_2005,zhou_magnetic_2011}
+Fields also enable self assembly through the control of interface deformation derived capillary forces.
+\cite{morgan_understanding_2012,davies_interface_2014,davies_dipolar_2015} Magnetically responsive spherical particle 
+stabilized bijels have thus far not yielded significant microstructural modifications. \cite{kim_bijels_2010} However, 
+electric fields have been shown to cause percolating cylindrical domains in electrically responsive bijels. \cite{carmack_tuning_2018}
+The electric field causes polar interactions between particles, which causes the formation of chains of particles that
+also function as nucleation sites for phase separation. \cite{carmack_tuning_2018}
 
-The equations of motion of our model comprise the relevant materials
-properties: the density \(\rho\), viscosity \(\nu\), and surface tension \(\sigma\) of the binary fluid, and the mass \(m_p\), size \(R_p\) and aspect ratio \(\alpha\), and dipole moment \(m\) of the particles.
-In addition, we can control the particle volume fraction \(\phi_p\) and
-magnetic field strength \(B\). These nine quantities involve four unit
-dimensions (mass, length, time, and charge), hence we can use five
-dimensionless variables to specify the parameters of the system. These
-are the particle aspect ratio $\alpha$, particle volume fraction
-\(\phi_p\), particle vs.~fluid density ratio
-$\xi = \frac{3m_p}{4\pi \rho V_p}$, nominal Weber number $\mathrm{We} = \frac{\rho \sigma V_p^{1/3}}{\eta^2}$, and magnetic Bond
-number \(\bar{B} = m B/(\sigma A_p)\), where
-\(V_p=(4/3)\pi R_\parallel^3/\alpha^2\) is the particle volume and
-\(A_p=\max\left( \pi R_\parallel^2/\alpha, \pi R_\parallel^2/\alpha^2 \right)\)
-the area of the larger cross-section of the ellpsoidal particles.
+In this chapter, we investigate the effect of external magnetic fields on the formation of bijels stabilized by 
+anisotropic magnetic particles. The microstructure of bijels stabilized with oblate, spherical and prolate particles, 
+namely the characteristic length scale and tortuosity, will be assessed as a function of the applied magnetic field
+strength. We also characterize the underlying mechanisms governing the observed behavior.
 
-For our simulations, we choose units \(\Delta x\), \(\Delta t\),
-\(\Delta m\), and \(\Delta i\) such that \(V_p=\hat{V}_p(\Delta x)^3\),
-\(\nu=\hat{\nu}(\Delta x)^2/\Delta t\),
-\(\sigma=\hat{\sigma}\Delta m/(\Delta t)^2\), and
-\(m=\hat{m}\Delta i(\Delta x)^2\). We used \(V_p=2000\pi/3\),
-\(\hat{\nu}=1/6\), \(\hat{\sigma}=0.0267\), \(\hat{m}=1\), and a density
-ratio \(\xi=1/\hat{\rho}\). For reference, the values of the model
-parameters are listed in table \ref{tab:parameters}. The values of
-\(\alpha\) and \(\bar{B}\) are variable and are reported
-with the results in section \ref{sec:results}.
+% Anisotropic particles, when adsorbed at liquid interfaces, induce
+% shape-dependent capillary interactions that can have a distinct effect
+% on the microstructure of emulsions
+% \cite{loudet_capillary_2005,loudet_self-assembled_2009}. For instance,
+% Madivala et
+% al.~\cite{madivala_exploiting_2009,madivala_self-assembly_2009} found
+% that emulsion stability can be significantly enhanced by ellipsoidal
+% particles. Additionally, capillary interactions can lead to direct
+% assembly of anisotropic particles
+% \cite{bowden_self-assembly_1997,lewandowski_orientation_2010,stebe_oriented_2009,botto_capillary_2012}.
+% Ellipsoidal particles can rotate and migrate on curved surfaces
+% \cite{cavallaro_curvature-driven_2011}, where the interface curvature
+% acts as an external field that controls the orientation and placement
+% of particles \cite{furst_directing_2011}. Anisotropic particles at
+% fluid interfaces were considered in Monte Carlo simulations by Bresme
+% et al. to test the accuracy of thermodynamic models for the free
+% energy as a function of the particle-fluid interactions, particle
+% size, and orientation
+% \cite{bresme_orientational_2007,bresme_computer_2008}. Harting and
+% co-workers \cite{gunther_lattice_2013,gunther_timescales_2014} have
+% performed lattice Boltzmann simulations of anisotropic particles at
+% liquid interfaces and in emulsions. They found that anisotropic
+% particles affect the dynamics of emulsion formation by introducing two
+% additional timescales associated with particle rotation. Following
+% initial adsorption, particles rotate to align their larger
+% cross-section with the interface. When jamming sets in, capillary
+% interactions cause the particle to re-orient in the interface leading
+% to prolonged coarsening at long timescales. Due to the larger aspect
+% ratio, ellipsoidal particles can stabilize a larger interface area
+% leading to smaller domain sizes. Hijnen et
+% al.~\cite{hijnen_bijels_2015} experimentally realized bijels
+% stabilized by colloidal rods and analyzed their effect on the
+% interface and domain morphology. Their experiments confirmed that
+% jamming occurs at lower interface separations than for spherical
+% particles with the same volume fraction. Moreover, they observed that
+% the overall structure remains isotropic and attributed this to the
+% rapid jamming of the rods. Additionally, they found that some rods
+% tilted out of the interface due to the compression induced by domain
+% coarsening.
 
-%\new{We note that the dynamics of the simulations are determined by
-%the dimensionless numbers, and the actual unit values $\Delta x$,
-%$\Delta t$, $\Delta m$, and $\Delta j$ are arbitrary and only become
-%meaningful when a connection to an experimental system is made (see
-%below).}
-
-\begin{table}
-\centering
-\caption{Summary of the parameters of the numerical model and the values used in the simulations}
-\label{tab:parameters}
-\begin{tabular}{|c|r|}
-\hline
-Parameter & Value \\
-\hline
-$L_V/\Delta x$ & 256 \\
-$\rho \cdot (\Delta x)^3/\Delta m$ & 0.7 \\
-$\nu \cdot \Delta t/(\Delta x)^2$ & 1/6 \\
-$\sigma \cdot (\Delta t)^2/\Delta m$ & 0.0267 \\
-$\tau/\Delta t$ & 1 \\
-$g \cdot \Delta m(\Delta t)^2/(\Delta x)^5$ & 0.08 \\
-$\phi_f$ & 0.5 \\
-$\phi_p$ & 0.15 \\
-$n_p$ & 1200 \\
-$\rho_p \cdot (\Delta x)^3/\Delta m$ & 1 \\
-$V_p/(\Delta x)^3$ & $2000\pi/3$ \\
-$m/(\Delta i(\Delta x)^2)$ & 1 \\
-$d_c/\Delta x$ & 2/3 \\
-$K_H\cdot (\Delta x)^{1/2}(\Delta t)^2/\Delta m$ & 100 \\
-\hline
-\end{tabular}
-\end{table}
-
-We performed simulations of a binary fluid using the software package
-LB3D \cite{schmieschek_lb3d_2017} that implements the lattice Boltzmann method described in section
-\ref{sec:methods}. The multicomponent
-lattice Boltzmann model is solved in a cubic box of size
-\(L_V=256\Delta x\) with periodic boundary conditions. The simulation
-box is filled with equal volume fractions \(\phi_f=0.5\) of two fluids,
-initially homogeneously mixed with a density
-\(\rho=0.7\Delta m/(\Delta x)^3\). The BGK relaxation time is set to
-\(\tau=\Delta t\) and the Shan-Chen interaction strength is set to
-\(g_{kk^\star}=0.08(\Delta x)^2/(\Delta m(\Delta t)^2)\). We performed
-preliminary simulations of a spherical droplet with these parameters and
-fitted the pressure difference inside and outside the droplet to the
-Young-Laplace law, which yielded a surface tension
-\(\sigma=0.0267\Delta m/(\Delta t)^2\). To study the influence of
-anisotropic particle shapes on the bijel formation, we performed
-simulations for particles with three different aspect ratios:
-\(\alpha=1\) for spherical particles, \(\alpha=2\) for prolate
-ellipsoids, and \(\alpha=1/2\) for oblate ellipsoids. To match the
-particle volume fraction \(\phi_p\) between the different particle
-shapes, we kept the volume of the particles fixed and used the same
-number of particles for each aspect ratio. The radius along the symmetry
-axis of the particles was calculated from
-\(V_p=(4/3)\pi R_\parallel^3/\alpha^2\), yielding
-\(R_\parallel=7.9\Delta x\) for spheres, \(R_\parallel=12.6\Delta x\)
-for prolate ellipsoids, and \(R_\parallel=5\Delta x\) for oblate
-ellipsoids, respectively. Particles were added to the fluid by placing
-them randomly inside the box. The lubrication cutoff distance was set to
-the value \(d_c=(2/3)\Delta x\) recommended by Ladd
-\cite{ladd_lattice-boltzmann_2001}, and the strength of the Hertz
-potential was set to \(K_H=100\Delta m/((\Delta x)^{1/2}(\Delta t)^2)\).
-We first equilibrated the particle positions and orientations by
-evolving only the equations of motion of the particles, while the fluid
-remained in its initial configuration, until the minimum particle
-distance exceeded \(1.2\cdot\max(R_\parallel,R_\parallel/\alpha)\).
-After the equilibration, the magnetic flux density
-\(\vec{B}=B\hat{\vec{z}}\) was switched on and the full system was
-evolved for \(10^5\) timesteps.
-In the course of the simulation, the binary mixture undergoes spinodal decomposition.
-The particles adsorb at the coarsening interface and eventually become jammed, resulting in the bicontinuous phase morphology of the bijel.
-
-It is worth discussing briefly the possible realization of our model in
-experiments. A common choice for bijel formation in binary liquids is a
-mixture of water and lutidine
-\cite{clegg_emulsification_2007,herzig_bicontinuous_2007}. The surface
-tension between the phases of a water-lutidine system at
-\(40^\circ\mathrm{C}\) is around \(\sigma=0.22\ \mathrm{mN/m}\) and the
-dynamic viscosity of the lutidine-rich phase is around
-\(\eta=2.38\ \mathrm{mPa\,s}\) \cite{grattoni_lower_1993}. Ellipsoidal
-particles with various aspect ratios can be formed by mechanically
-stretching spherical particles \cite{trevenen_gradient_2021}. Such
-particles can be magnetically functionalized by e-beam deposition of a
-Nickel layer. Fei et
-al.~\cite{fei_magneto-capillary_2018,fei_magneto-capillary_2020}
-fabricated coated \(4\ \mathrm{\mu m}\) polystyrene particles with a
-permanent magnetic dipole moment of
-\(m\approx3\cdot10^{-14}\ \mathrm{Am^2}\).
-It was shown that the dipole moment is oriented in the direction parallel to the coated interface \cite{yan_linking_2012,yan_rotating_2014}, i.e., it can be aligned with the axis of ellipsoidal particles.
-For the given surface tension, the capillary torque on a particle adsorbed at an interface is approximately
-$8.8\cdot10^{-16}\ \mathrm{Nm}$. We thus can estimate that a magnetic
-flux density of \(30\ \mathrm{mT}\) is able to exert a magnetic torque
-that exceeds the capillary torque.
-We note that under these conditions,
-the dipole-dipole interaction is on the order of
-\(10^{-16}\ \mathrm{J}\) and an order of magnitude smaller than the
-particle-interface interaction which is of order
-\(10^{-15}\ \mathrm{J}\). %Unlike previous works
-%\cite{xie_direct_2017,xie_controllable_2021}, we therefore cannot
-%neglect the magnetic dipole-dipole interactions between particles.For these bijel properties and the parameters given in
-table \ref{tab:parameters}, the spatial resolution of our
-simulations is $\Delta x\approx252\ \mathrm{nm}$, and the time step
-is $\Delta t=624\ \mathrm{ns}$. This corresponds to a system side length of $L_V \approx 64.5\ \mathrm{\mu m}$ and a runtime of
-$T \approx 62.4\ \mathrm{ms}$.
-
-\begin{figure}
-\centering
-\includegraphics[width=\columnwidth]{figures/results/paper1/microstructure_viz.png}
-\caption{Snapshots of emulsion gels stabilized by prolate ellipsoids after $t=5\cdot10^3$ timesteps (left) and after $10^5$ timesteps (right).
-The top row shows the structure forming without a magnetic field.
-The bottom row shows the structure forming in an applied magnetic field of reduced strength $\bar{B}=1.0$.
-The snapshots are colored according to the order parameter $\phi$.}
-\label{fig:microstructure_viz}
-\end{figure}
+% Particle-stabilized emulsions can be made responsive to external
+% magnetic fields by magnetic particles
+% \cite{melle_pickering_2005,zhou_magnetic_2011}. An external field can
+% then be used to control the stability of the emulsion
+% \cite{melle_pickering_2005} and the self-assembly of particles
+% \cite{dassanayake_structure_2000,leunissen_directing_2009}. The tendency
+% of anisotropic particles to adopt distinct orientations gives rise to an
+% orientation transition when an external field is applied
+% \cite{morgan_understanding_2012,davies_interface_2014,davies_dipolar_2015}.
+% Magnetic fields thus offer a means to control the capillary interactions
+% of ellipsoidal particles at an interface. For bijels stabilized by
+% spherical magnetic particles, simulations by Kim et
+% al.~\cite{kim_bijels_2010} revealed that magnetic fields do not have a
+% significant effect on the microstructure of bijels. In contrast, Carmack
+% and Millett \cite{carmack_tuning_2018} demonstrated that the structure
+% of thin-film bijels stabilized by dielectric particles can change
+% drastically when an external electric field is applied. The dielectric
+% contrast of the particles induces polar interactions that cause liquid
+% domain alignment leading to percolating cylindrical domains in the
+% thin-film bijel. In addition, they found that particle chains can act as
+% nucleation sites for phase separation. This suggests that anisotropic
+% interactions can have a considerable effect on the phase separation and
+% the resulting emulsion morphology and may offer a means to control the
+% size and shape of liquid domains.
 
 \section{Results}\label{sec:results}
-
-\begin{figure*}
-\centering
-\includegraphics[width=\textwidth]{figures/results/paper1/structure_factor.png}
-\caption{Scaling plot of the dynamic structure factor $S(k,t)$ for different particle shapes $\alpha$ and at different magnetic field strength $\bar{B}$.
-The structure factor is plotted at four different timesteps for each case.
-The good data collapse shows that the bijel formation is driven by spinodal decomposition.
-The decay to the right of the peak is reasonably well described by Porod's law $S(k)\sim k^{-4}$.}
-\label{fig:structure_factor}
-\end{figure*}
 
@@
 that the Bond numbers varies in the range \(0\le\bar{B}\le1\).
-In this work, we use a fixed particle volume fraction and focus on the dependence of the bijel structure on the magnetic field.
-Bijels with varying particle loading and surface tension and have been studied elsewhere in the literature, e.g., by Hijnen et al.\cite{hijnen_bijels_2015} and Jansen and Harting\cite{jansen_bijels_2011}.
+In this work, we use a fixed particle volume fraction and focus on the dependence of the 
+bijel structure on the magnetic field. Bijels with varying particle loading and surface tension 
+and have been studied elsewhere in the literature, e.g., by Hijnen et al.\cite{hijnen_bijels_2015} 
+and Jansen and Harting\cite{jansen_bijels_2011}.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\columnwidth]{figures/results/paper1/microstructure_viz.png}
+    \caption{Snapshots of emulsion gels stabilized by prolate ellipsoids after $t=5\cdot10^3$ timesteps (left) and after $10^5$ timesteps (right).
+The top row shows the structure forming without a magnetic field.
+             The bottom row shows the structure forming in an applied magnetic field of reduced strength $\bar{B}=1.0$. The snapshots are colored according to the order parameter $\phi$.}
+    \label{fig:microstructure_viz}
+\end{figure}
 
@@
 
-In LB simulations of spinodal decomposition
-\cite{kendon_3d_1999,kendon_inertial_2001}, a characteristic length
-scale can be obtained from the structure factor
-%
-\begin{equation}
-S(\vec{k},t) = \tilde{\phi}(\vec{k},t)\tilde{\phi}(-\vec{k},t) .
-\end{equation}
-%
-where \(\tilde{\phi}(\vec{k},t)\) is the Fourier
-transform of the order parameter fluctuations
-\(\phi(\vec{x},t)-\left\langle\phi\right\rangle\). A common measure of
-domain size uses the spherically averaged structure factor
-%
-\begin{equation}
-S(k,t) = \frac{1}{n_k} \sum_{k-\frac{\Delta}{2}<k<k+\frac{\Delta}{2}} \tilde{\phi}(\vec{k},t)\tilde{\phi}(-\vec{k},t) ,
-\end{equation}
-%
-where \(k=|\vec{k}|\) denotes the modulus of \(\vec{k}\)
-and \(n_k\) is the number of lattice sites in a shell of radius \(k\)
-and thickness \(\Delta=2\pi/L_V\). The average domain size can then be
-defined in terms of the \(n\)-th moment of the structure factor
-\cite{laradji_molecular_1996}
+In LB simulations of spinodal decomposition, a characteristic length
+scale can be obtained from the structure factor, defined in Section \ref{section:domain_size}. \cite{kendon_3d_1999,kendon_inertial_2001} 
+It is worth noting that this definition of average domain size does not necessarily yield values that coincide with the typical
+domain size observed visually in snapshots such as those shown in Fig.~\ref{fig:microstructure_viz}. However, in a dynamic
+scaling regime, different measures of domain size are expected to differ only by a constant ratio. We found that the commonly 
+used measure \(L_1(t)\) tends to overestimate the observed domain size. Numerically, the calculation of the spherically 
+averaged structure factor is subject to poor statistics in the low \(k\)-shells, where the average \(|\vec{k}|\) of the 
+lattice sites differs from the nominal shell radius. Additionally, the measurement of \(L(t)\) in simulations with
+periodic boundary conditions is subject to finite size effects. More importantly, in suspensions of anisotropic particles, 
+we cannot expect that the structure factor is isotropic. Therefore, we also used the 3D structure factor to calculate a lateral domain 
+size in each Cartesian direction from the second moments also defined in Section \ref{section:domain_size}. 
+\cite{jansen_bijels_2011,gunther_timescales_2014} We add the additional processing calculating a parallel and perpendicular domain size
+from the results in each cartesian direction, defining $L_{\parallel}=L_z$ and $L_{\perp} = \frac{L_x+L_y}{2}$
 
-\begin{equation}
-L_n(t) = 2 \pi (\left( \frac{\sum_k S(k, t)}{\sum_k k^n S(k, t)} )\right)^{\frac{1}{n}}
-\end{equation}
+Before calculating the structure factor \(S(\vec{k},t)\), we first filled the lattice sites covered by particles with the average
+density at the surrounding lattice sites as detailed in Section \ref{section:filling_routine}. We plot the structure factor of the structures in
+Figure \ref{fig:structure_factor}.
 
-It is worth noting that this definition of average domain
-size does not necessarily yield values that coincide with the typical
-domain size observed visually in snapshots such as those shown in
-Fig.~\ref{fig:microstructure_viz}. However, in a dynamic
-scaling regime, different measures of domain size are expected to differ
-only by a constant ratio. We found that the commonly used measure
-\(L_1(t)\) tends to overestimate the observed domain size. Numerically,
-the calculation of the spherically averaged structure factor is subject
-to poor statistics in the low \(k\)-shells, where the average
-\(|\vec{k}|\) of the lattice sites differs from the nominal shell
-radius. Additionally, the measurement of \(L(t)\) in simulations with
-periodic boundary conditions is subject to finite size effects. More
-importantly, in suspensions of anisotropic particles, we cannot expect
-that the structure factor is isotropic. Therefore, we also used the 3D
-structure factor to calculate a lateral domain size in each Cartesian
-direction from the second moments
-\cite{jansen_bijels_2011,gunther_timescales_2014}
-%
-\begin{equation}
-L_\beta(t)=2\pi\sqrt{\frac{\sum_{\vec{k}}S(\vec{k},t)}{\sum_{\vec{k}}k_\beta^2 S(\vec{k},t)}} .
-\end{equation}
-%
-This allows us to compute a domain size parallel
-(\(L_\parallel=L_z\)) and perpendicular (\(L_\perp=(L_x+L_y)/2\)) to the
-direction of \(\vec{B}\) separately. The average domain size \(L_d(t)\)
-is computed as \(L_d(t)=\sum_\beta L_\beta(t) / 3\).
-%
-\begin{equation}
-L_d(t)=2\pi\sqrt{\frac{\sum_{\vec{k}}S(\vec{k},t)}{\sum_{\vec{k}}\sum_\beta k_\beta^2 S(\vec{k},t)}} .
-\end{equation}
-%
-%In case the structure factor is isotropic
-%\(S(\vec{k},t)=S(k,t)\), this is equivalent to the ratio of the fourth
-%and second moments of the spherically averaged structure factor.
-%
-%\begin{equation}
-%\begin{split}
-%  L_d(t) &%= \left[\sum_{\beta}\left(\frac{1}{L_\beta(t)}\right)^2\right]^{-\frac{1}{2}}
-%  = 2\pi \sqrt{\frac{\sum_{\vec{k}}S(\vec{k},t)}{\sum_{\vec{k}}\sum_\beta k_\beta^2 S(\vec{k},t)}} \\
-%L_\perp(t) &%= \left[\left(\frac{1}{L_x(t)}\right)^2+\left(\frac{1}{L_y(t)}\right)^2\right]^{-\frac{1}{2}}
-%= 2\pi \sqrt{\frac{\sum_{\vec{k}}S(\vec{k},t)}{\sum_{\vec{k}} \left(k_x^2+k_y^2\right) S(\vec{k},t)}} \\
-%L_\parallel(t) &= 2\pi \sqrt{\frac{\sum_{\vec{k}} S(\vec{k},t)}{\sum_{\vec{k}} k_z^2 S(\vec{k},t)}}
-%\end{split}
-%\end{equation}
-
-Before calculating the structure factor \(S(\vec{k},t)\), we
-first filled the lattice sites covered by particles with the average
-density at the surrounding lattice sites. We employed an iterative
-procedure that fills the particles layer by layer, starting at the
-surface layer and using equation \eqref{eq:fill_particles} to
-approximate the density at solid nodes that have a least one neighboring
-fluid node. This is repeated until all solid nodes have been filled with
-fluid. The order parameter \(\phi(\vec{x},t)\) was then calculated for
-the filled density fields \(\rho_k(\vec{x},t)\). Filling the lattice
-sites covered by particles is crucial to avoid spurious oscillations of
-the structure factor at length scales corresponding to the particle
-size.
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{figures/results/paper1/structure_factor.png}
+    \caption{Scaling plot of the dynamic structure factor $S(k,t)$ for different particle shapes $\alpha$ and at different 
+            magnetic field strength $\bar{B}$.
+The structure factor is plotted at four different timesteps for each case.
+The good data collapse shows that the bijel formation is driven by spinodal decomposition.
+The decay to the right of the peak is reasonably well described by Porod's law $S(k)\sim k^{-4}$.}
+    \label{fig:structure_factor}
+\end{figure*}
 
@@
 effective diffusivity $D_{\text{eff}}$ and the intrinsic diffusivity
-$D$. Porous structures were generated from the order parameter field
-at the last time step of the simulations by binarizing the raw order
-parameter data using a threshold of zero. We masked the largest
-connected component representing the percolating domain and then used
-the Python package \texttt{taufactor}\cite{cooper_taufactor_2016} to
-calculate the tortuosity in the three Cartesian coordinate
-directions. \texttt{taufactor} determines the tortuosity by comparison
-of steady-state diffusive flow through a porous medium with the bulk
-diffusive flow in a control volume of the same size, molecular
-diffusivity, and driving force \cite{cooper_taufactor_2016}. We used
-the \texttt{PeriodicSolver} to employ periodic boundary conditions.
+$D$. We calculate the tortuosity using the procedure detailed in Section \ref{section:tortuosity}
 
@@
 
+\subsection{Curvature}
+
+Beyond the length scale, curvature analysis offers insights into the
+local topological landscape of the bijel, facilitating further
+microstructure optimization for various applications.
+\cite{reeves_quantitative_2016} We plot the area averaged mean and
+gaussian curvature \(H\Sigma^{-1}\) and \(K\Sigma^{-2}\) for bijels
+stabilized with oblate, spherical and prolate ellipsoids in Figure
+\ref{fig:curvature-vs-B_ss}.
+
+\begin{figure} 
+    \centering 
+    \includegraphics[width=\textwidth]{figures/results/paper1/curvature-vs-B_ss.png} 
+    \caption{Plot of the area averaged mean $\langle H \rangle \Sigma^{-1}$ and Gaussian 
+            $\langle K \rangle \Sigma^{-2}$ curvature in the left and right respectively. Each 
+            plot contains the $\langle H \rangle \Sigma^{-1}$ and $\langle K \rangle \Sigma^{-1}$ 
+            at the final timestep averaged across 3 runs for particles with $\alpha = 0.5, 1, 2$. 
+            We observe that the mean curvature does not demonstrate any trends, while the Gaussian 
+            curvature shows a reduction as the magnetic field strength is increased for 
+            ellipsoidal particles.} 
+    \label{fig:curvature-vs-B_ss}
+\end{figure}
+
+Error bars are represented by the standard
+deviation of the three simulations per parameter set performed. The area
+averaged mean curvature shows little dependence on the applied field
+strength with values around 0 and within error of one another. A value
+near or at 0 is expected as the fluid volume fraction is equal and the
+particles are neutrally wetting, implying the interface should not have
+a preferred direction of curvature. \cite{jinnai_interfacial_2001} For
+ellipsoidal particles, the gaussian curvature becomes more negative as
+larger field strengths are applied. We also see that the gaussian
+curvature becomes more positive as the interfacial area of the particle
+increases. The trend of these results are inverse to the interfacial
+area of each particle, \(A_{rm}\). This is expected behavior and is in
+agreement with experiments that have investigated the effect of particle
+size on the curvature of bijels. \cite{reeves_quantitative_2016}
+
+Reeves and coworkers identified that nanoparticles were better able to
+lock in the spinodal structure of the liquid-liquid phase separation as
+they were less disruptive the the curvature of the interface due to
+their lower interfacial adsorption energy. This effect can be observed
+as a more negative Gaussian curvature as a result of the greater number
+of hyperbolic surfaces, a hallmark of a minimal surface. In our system,
+the oblate and prolate particles have 60\% and 30\% more interfacial
+area than the spherical particles, resulting in the ellipsoidal
+particles being more disruptive to the curvature of the interface,
+observed as a more positive Gaussian curvature. As the magnetic field
+strength is increased, the packing of the particles at the interface
+changes, as observed from the radial distribution function.
+\cite{karthikeyan_formation_2024} These changes in particle packing
+change the way the particles affect the curvature of the interface,
+resulting in the curvature changes observed. To investigate the field
+dependence on the curvature, we plot the area averaged Gaussian
+curvature as a function of time.
+
+\begin{figure} 
+    \centering 
+    \includegraphics[width=\textwidth]{figures/results/paper1/curvature_vs_coverage.png} 
+    \caption{Plots of Gaussian $\langle K \rangle \Sigma^{-2}$ curvature over time averaged across 3 runs. 
+    From left to right, we have particles with $\alpha = 0.5, 1, 2$. We observe that the initial stages of 
+    evolution are unaffected by the applied magnetic field. However, after about 10000 timsteps, we see a 
+    magnetic field dependence on the evolution of the Gaussian curvature. The preservation of this divergence 
+    occurs when ellipsoidal particles are used but not spherical particles.} 
+    \label{fig:curvature_vs_coverage}
+\end{figure}
+
+Given we did not see any noteworthy changes in the mean curvature in
+Figure \ref{fig:curvature-vs-B_ss}, we focused on the Gaussian curvature
+in Figure \ref{fig:curvature_vs_coverage}. We observe that for all
+simulated systems, the Gaussian curvature increases over time until an
+invariance is reached near the end of the simulation, signifying the
+bijel microstructure is locked in place. We also observe that for all
+microstructures the curvature over time does not increase at the same
+rate, characterized with dips at 10 to 20,000 timesteps for all
+particles and a magnetic field dependent change in the curvature
+increase.
+
+However, for the spherical particles this local topology change
+disappears once the spinodal decomposition ceases, observed as a
+convergence of all curvatures. This is not observed for the bijels
+stabilized by ellipsoidal particles. Despite all our curvature
+calculations being normalized with their surface area to volume ratio,
+we still see curvature differences as a function of the applied magnetic
+field. Experiments have identified that curvature changes can occur due
+to the formation of monogels, which are particle networks formed from
+bijels that can withstand the remixing of their constituent liquids.
+\cite{sanz_colloidal_2009, lee_making_2013} This process cannot occur in
+our simulations as we are utilizing repulsive particles. Therefore, the
+change in curvature arises from the differences in local state of the
+colloids at the interface.
+
 \subsection{Kinetics of bijel formation in magnetic fields}
@@
 \includegraphics[width=\textwidth]{figures/results/paper1/coarsening_vel.png}
-\caption{Time-dependence of the coarsening velocity $u_L$ for different particles shapes $\alpha$  and at different magnetic field strength $\bar{B}$.
-The different components of the coarsening velocity show that the jamming time is different in the direction parallel and perpendicular to the magnetic field.}
+\caption{Time-dependence of the coarsening velocity $u_L$ for different particles shapes $\alpha$  
+and at different magnetic field strength $\bar{B}$. The different components of the coarsening velocity 
+show that the jamming time is different in the direction parallel and perpendicular to the magnetic field.}
 \label{fig:coarsening_velocity}
@@
 \centering
-\includegraphics[width=\columnwidth]{figures/results/paper1/particle_packing_viz.png}
-\caption{Snapshots illustrating the particle packing at the interface for different particle shapes $\alpha$ with (left) and without (right) applied magnetic field $\bar{B}$.
-The right column shows the alignment of the symmetry axis of the oblate (top row) and prolate (bottom row) particles in the direction of the magnetic field indicated by arrows.}
+\includegraphics[width=0.5\columnwidth]{figures/results/paper1/particle_packing_viz.png}
+\caption{Snapshots illustrating the particle packing at the interface for different particle shapes $\alpha$ with (left) 
+        and without (right) applied magnetic field $\bar{B}$. The right column shows the alignment of the symmetry axis of 
+        the oblate (top row) and prolate (bottom row) particles in the direction of the magnetic field indicated by arrows.}
 \label{fig:packing_viz}
@@
 \includegraphics[width=\columnwidth]{figures/results/paper1/S-vs-t.png}
-\caption{Time-dependence of the nematic order parameter $S$ of oblate ($\alpha=0.5$) and prolate ($\alpha=2$) particles at different field strength $\bar{B}$.
-Errorbars indicate the standard deviation taken over three independent simulation runs.
-Nematic order generally increases with applied field strength for all particle geometries.
+\caption{Time-dependence of the nematic order parameter $S$ of oblate ($\alpha=0.5$) and prolate ($\alpha=2$) 
+        particles at different field strength $\bar{B}$. Errorbars indicate the standard deviation taken over 
+        three independent simulation runs. Nematic order generally increases with applied field strength for all particle geometries. 
         The increase slows down (for prolate particles) or reverses (for oblate particles) around $10^4$ timesteps.}
@@
 To measure the particle alignment quantitatively, we computed the
-nematic order tensor \cite{veerman_phase_1992}
-%
-\begin{equation}
-\tens{Q} = \frac{1}{n_p} \sum_i \left( \frac{3}{2} \hat{\vec{o}}_i \otimes \hat{\vec{o}}_i -\frac{1}{2}\mathsf{1} \right)
-\end{equation}
-%
-where \(\hat{\vec{o}}_i\) is the orientation of the
-\(i\)-th particles and \(n_p\) is the number of particles in the system.
-The largest eigenvalue of $\tens{Q}$ yields the nematic order
-parameter
-%
-\begin{equation}
-S = \left\langle \frac{3}{2}\cos^2 (\theta) - \frac{1}{2} \right\rangle ,
-\end{equation}
-%
-where
-\(\theta=\arccos(\hat{\vec{o}}_i\cdot\hat{\vec{n}})\) is the angle
-between the particle orientation and the nematic director
-\(\hat{\vec{n}}\).
-
+nematic order tensor using the method detailed in Section \ref{section:nematic_order_parameter} 
 Figure \ref{fig:nematic_time} shows the time evolution of the nematic
@@
 analyzed the angle between the symmetry axis of the particles and the
-interface normal. To this end, we generated a mesh of the interface
-using a marching cubes algorithm. For each particle we identified the
-mesh vertex closest to the particle's position (excluding particles
-whose distance to the mesh exceeds the radius of the longer particle
-axis) and computed the angle between the particle orientation vector
-\(\hat{\vec{o}}_i\) and the interface normal at the closest vertex.
-Figure \ref{fig:psi_time} shows the time-dependence of the average angle
-\(\psi\) between the particle dipole axis and the nearest interface
-normal.
+interface normal calculated using the technique defined in Section 
+\ref{section:interface_angle}. Figure \ref{fig:psi_time} shows the time-dependence of the average angle
+\(\psi\) between the particle dipole axis and the nearest interface normal.
 
@@
 \includegraphics[width=\columnwidth]{figures/results/paper1/psi-vs-t.png}
-\caption{Time-dependence of the average angle $\psi$ between the particle axis and the interface normal for oblate ($\alpha=0.5$) and prolate ($\alpha=2$) particles at different magnetic field strength $\bar{B}$.
-Errorbars indicate the standard deviation taken over three independent simulation runs.
-The angle between between the particles and the interface normal generally approaches the energetically preferred value ($0^\circ$ for oblate particls, $90^\circ$ for prolate particles).
+\caption{Time-dependence of the average angle $\psi$ between the particle axis and the 
+        interface normal for oblate ($\alpha=0.5$) and prolate ($\alpha=2$) particles at different 
+        magnetic field strength $\bar{B}$. Errorbars indicate the standard deviation taken over three 
+        independent simulation runs. The angle between between the particles and the interface normal generally 
+        approaches the energetically preferred value ($0^\circ$ for oblate particls, $90^\circ$ for prolate particles).
         The average angle changes most rapidly around $10^4$ timesteps.}
@@
 
+Information on the average ordering of the particles towards a
+direction can be characterized using the nematic order parameter.
+\cite{veerman_phase_1992, gunther_timescales_2014} However, we would
+like to understand the local ordering of the particles over time. We
+utilize the 6 fold Steinhardt order parameter Q6.
+\cite{steinhardt_bond-orientational_1983, lechner_accurate_2008, mickel_shortcomings_2013} 
+This parameter has been used extensively to characterize nucleation
+rates, glass transitions of colloidal systems and crystal structure
+transitions of ceramics and colloidal crystals.
+\cite{vagberg_glassiness_2011, besseling_three-dimensional_2007, schall_structural_2007}
+The original implementation has been further improved through the use an
+averaged bond order parameter, adding the next nearest neighbor to the
+neighbor list or utilizing voronoi cells to define the neighbor list
+instead of a cutoff distance. The latter provides the more robust
+implementation of the bond order parameter and is implemented in the
+package Freud. \cite{ramasubramani_freud_2020} This method has been used
+to characterize the jamming of discs at interfaces.
+\cite{ozawa_jamming_2012} We select \(Q6\) as the parameter to calculate
+due to the hexagonal ordering seen in the visualizations of the particle
+monolayer. We plot the averaged bond order parameter for each timestep,
+\(\langle Q6 \rangle\) calculated using a neighbor list derived from
+voronoi cells below.
+
+\begin{figure} 
+    \centering 
+    \includegraphics[width=\columnwidth]{figures/results/paper1/Q6_vs_coverage.png} 
+    \caption{Time dependence of the mean six fold symmetry parameter, $\langle Q6 \rangle$ for bijels 
+    stabilized with oblate(left), spherical(middle) and prolate(right) particles. We show that spherical 
+    particles posess the hexagonal close packing structure for particles on interfaces. Ellipsoidal particles 
+    however posess behavior that is magnetic field and particle aspect ratio dependent.} 
+    \label{fig:Q6_coverage} 
+\end{figure}
+
+From Figure \ref{fig:Q6_coverage}, we observe that
+\(\langle Q6 \rangle \approx 0.34\) for all systems before increasing.
+For bijels stabilized with spherical particles, we observe that
+\(\langle Q6 \rangle\) monotonically increases until
+\(\langle Q6 \rangle \approx 0.485\), indicating that the spherical
+particles reach a hexagonally arranged state at the interface upon
+jamming. In contrast, oblate and prolate particles respectively at the
+\(t = 10^5\) timesteps have values \(\langle Q6 \rangle \approx 0.44\)
+and \(\langle Q6 \rangle \approx 0.35\) respectively, indicating that
+the arrangement of colloids on the interface are not hexagonal close
+packed. We can verify these observations in the visualizations in
+Figures \ref{fig:microstructure_viz}
+
+We observe a magnetic field dependent increase in \(\langle Q6 \rangle\)
+for prolate particles to \(\langle Q6 \rangle \approx 0.4\) and decrease
+for oblate particles to \(\langle Q6 \rangle \approx 0.42\). As the
+magnetic field strength is increased, we observed the interface
+possessed a more negative gaussian curvature. Previous work by Cavallaro
+et al.~demonstrated that surfaces with large gaussian curvature
+gradients can be utilized to control particle self assembly at
+interfaces owing to the excess interfacial energy induced by the
+curvature gradient. \cite{cavallaro_curvature-driven_2011} Spherical
+particles have monopolar effects which for the colloid sizes we are
+modelling are negligible. Previous literature has also ascertained
+aspect ratio dependent self-assembly of ellipsoids. We attribute the
+changes in the local ordering to be due to aspect ratio dependent self
+assembly, amplified by the greater curvature gradient present upon
+application of a magnetic field. Next, we analyze how these local
+toplogical changes affect the microstructure of the bijel by analyzing
+the width of the domains in the bijel.
+
 As hypothesized above, the alignment of the particle dipole axis with
@@
 To corroborate this idea, we analyzed the radial distribution function
-(RDF) of the particles
-%
-\begin{equation}
-g(r) = \frac{n_p-1}{n_p} V \left\langle\delta\left(r-r_i\right)\right\rangle ,
-\end{equation}
-%
-where \(n_p\) is the number of particles in the volume
-\(V\), and \(\langle\cdot\rangle\) denotes an average over all
-particles. The radial distribution function was calculated by binning
-the distance between all particle pairs and normalizing the shells with
-respect to the distribution \(4\pi \rho r^2 \mathrm{d}r\) of an ideal
-gas. The time-evolution of the RDFs for the three particle shapes and
+(RDF) of the particles, the calculation of which is detailed in Section
+\ref{section:radial_distribution} The time-evolution of the RDFs for the three particle shapes and
 varying magnetic flux density is illustrated in Figure \ref{fig:rdf}.
@@
 \includegraphics[width=\textwidth]{figures/results/paper1/rdf_compare_time.png}
-\caption{Time-evolution of the radial distribution function $g(r)$ of the particles at different magnetic field strength $\bar{B}$.
-The radial distribution function is shown at $10^3$, $10^4$, and $10^5$ timesteps.
-The distance $r$ is normalized by the radius $R=\max(R_\parallel,R_\perp)$ of the larger particle axis.
-The peaks illustrate the packing of particles in the interface.
-Dashed lines indicate the side-by-side, tip-to-tip, and side-to-tip configuration of particle pairs.
-For spherical particles, the three values are identical.
+\caption{Time-evolution of the radial distribution function $g(r)$ of the particles at different magnetic 
+        field strength $\bar{B}$. The radial distribution function is shown at $10^3$, $10^4$, and $10^5$ timesteps. 
+        The distance $r$ is normalized by the radius $R=\max(R_\parallel,R_\perp)$ of the larger particle axis. The peaks 
+        illustrate the packing of particles in the interface. Dashed lines indicate the side-by-side, tip-to-tip, 
+        and side-to-tip configuration of particle pairs. For spherical particles, the three values are identical. 
         The insets show snapshots of the particle arrangement with and without magnetic field at the respective timesteps. 
@@
 anisotropic particle packing and domain structure.
-
-% \section*{Data availability}
-
-% The data and code used to generate the figures in this manuscript are available as an interactive notebook on Code Ocean at https://doi.org/00.0000/00000000.
-Due to size limitations, the raw simulation data are available for download on request from the authors.
-
-% \section*{Acknowledgements}
-% %The Acknowledgements come at the end of an article after Conflicts of interest and before the Notes and references.
-% This work was supported by the National Science Foundation under NSF
-% Awards DMR-1944942 and OIA-2346036. Any opinions, findings and
-% conclusions or recommendations expressed in this material are those of
-% the authors and do not necessarily reflect those of the National Science
-% Foundation. This work used NCSA Delta at the National Center for
-% Supercomputing Applications through allocation PHY220131 from the
-% Advanced Cyberinfrastructure Coordination Ecosystem: Services \& Support
-% (ACCESS) program, which is supported by National Science Foundation
-% grants \#2138259, \#2138286, \#2138307, \#2137603, and \#2138296. We
-% wish to thank Jens Harting and Alexander Wagner for insightful
-% discussions.
-
-%%%END OF MAIN TEXT%%%
-
-%The \balance command can be used to balance the columns on the final page if desired. It should be placed anywhere within the first column of the last page.
-
-%\balance
-
-%If notes are included in your references you can change the title from 'References' to 'Notes and references' using the following command:
-%\renewcommand\refname{Notes and references}
-
-%%%REFERENCES%%%
-% \bibliographystyle{rsc} % RSC's .bst file
-% \bibliography{bijels}

### 2025-02-16 chapters/paper2.tex
Changes 1. Added more analysis to application of magnetic fields during formation chapter 2. Added references to fix some (not all) literature reference issues 3. Added some detail in analysis techniques section

@@
-\section{Introduction}
 \section{Results}\label{sec:results_p2}
@@
 
-Before the structure factor was calculated, the location of the particles were filled with the average density of the 
-surrounding lattice sites using Equation \ref{eq:fill_particles} to generate a smooth interface. The particles are 
-iteratively filled from outside in until all lattice points corresponding to the particle are filled with the average 
-density of the fluid surrounding the lattice point. Within the red and blue fluid densities, sites representing the 
-particles are filled before the order parameter is calculated. By filling the particles, we are able to analyze the 
+Before the structure factor was calculated, the location of the particles were filled using the procedure detailed in
+Section \ref{section:filling_routine} to generate a smooth interface. By filling the particles, we are able to analyze the 
 microstructure without the influence of the particles. We calculate the hysteresis curve by calculating the domain 
@@
     \centering 
-    \includegraphics[scale=0.7]{../figures/results/paper2/hysteresis_curve.png} 
+    \includegraphics[width=\textwidth]{../figures/results/paper2/hysteresis_curve.png} 
     \caption{Hysteresis curve of bijels stabilized with magnetically responsive ellipsoidal particles.
@@
     \centering 
-    \includegraphics[scale=0.7]{../figures/results/paper2/microstructure_viz-field_on.png} 
+    \includegraphics[width=\columnwidth]{../figures/results/paper2/microstructure_viz-field_on.png} 
     \caption{Visualizations of bijels simulated under no fields at $t = 0$ (left) and $t = 10^5$ (right). The top 
@@
     \centering 
-    \includegraphics[scale=0.7]{../figures/results/paper2/domain_size-field_on.png} 
+    \includegraphics[width=\columnwidth]{../figures/results/paper2/domain_size-field_on.png} 
     \caption{Plotting the spherically averaged domain size normalized with $R_p$($L/R$) of the 
@@
     \centering 
-    \includegraphics{../figures/results/paper2/domain_size_aniso-field_on.png} 
+    \includegraphics[width=\columnwidth]{../figures/results/paper2/domain_size_aniso-field_on.png} 
     \caption{Plotting the anisotropic domain size and tortuosities against the applied magnetic field strength on 
@@
     \centering 
-    \includegraphics[scale=0.7]{../figures/results/paper2/particle_viz-field_on.png} 
+    \includegraphics[width=\columnwidth]{../figures/results/paper2/particle_viz-field_on.png} 
     \caption{Visualizations of bijels simulated under no fields at $t = 0$ (left) and $t = 10^5$ (right). 
@@
     \centering 
-    \includegraphics{../figures/results/paper2/domain_size-field_on-scaled.png} 
+    \includegraphics[width=\columnwidth]{../figures/results/paper2/domain_size-field_on-scaled.png} 
     \caption{Plots of domain size with different timescales. The figure on the left rescales time with the nematic to 

### 2025-02-19 chapters/introduction.tex
Changes 1. Added more analysis to application of magnetic fields during formation chapter 2. Added references to fix some (not all) literature reference issues 3. Added some detail in analysis techniques section
Changes 1. Adjusted introduction for flow and fixed references

@@
-\begin{itemize}
-    \item What is a porous material? 
-    \begin{itemize}
-        \item What makes them different to non-porous materials?
-        \item Why do their differences make them industrially relevant?
-        \item What are some synthesis techniques that exist?
-        \item What are weaknesses with those synthesis techniques?
-    \end{itemize}
-    \item What is a particle stabilized emulsion
-    \begin{itemize}
-        \item Why are they interesting for porous material applications?
-        \item What is a bijel?
-        \item How are bijels relevant to porous materials?
-        \item Fabrication techniques that are proposed which allow large scale bijel fabrication
-        \item microstructure control in those applications
-    \end{itemize}
-    \item Purpose of study
-    \begin{itemize}
-        \item Three aims of the study 
-        \item significance of study
-        \item assumptions and limitations of the study
-    \end{itemize}
-    \item Summary of motivation, purpose and research aims
-\end{itemize}
+% \begin{itemize}
+%     \item What is a porous material? 
+%     \begin{itemize}
+%         \item What makes them different to non-porous materials?
+%         \item Why do their differences make them industrially relevant?
+%         \item What are some synthesis techniques that exist?
+%         \item What are weaknesses with those synthesis techniques?
+%     \end{itemize}
+%     \item What is a particle stabilized emulsion
+%     \begin{itemize}
+%         \item Why are they interesting for porous material applications?
+%         \item What is a bijel?
+%         \item How are bijels relevant to porous materials?
+%         \item Fabrication techniques that are proposed which allow large scale bijel fabrication
+%         \item microstructure control in those applications
+%     \end{itemize}
+%     \item Purpose of study
+%     \begin{itemize}
+%         \item Three aims of the study 
+%         \item significance of study
+%         \item assumptions and limitations of the study
+%     \end{itemize}
+%     \item Summary of motivation, purpose and research aims
+% \end{itemize}
 
@@
 \section{Introduction}
+\label{section:introduction}
 
@@
 being categorized by pore size per IUPAC as $(L)$ as microporous $(L < 2nm)$, mesoporous $(2nm < L < 50nm)$ and macroporous materials 
-$(50nm < L)$. \textcolor{blue}{https://doi.org/10.1351/pac198557040603} The presence of these pores increases the surface area to volume 
+$(50nm < L)$. \cite{sing_reporting_1985} The presence of these pores increases the surface area to volume 
 ratio of porous materials compared to their homogeneous counterparts. A common experimental technique used to estimate the surface area 
@@
 transport properties, suitable in applications such as battery electrodes and drug delivery systems. \cite{chen_tortuosity_2020, 
-ebner_tortuosity_2014}
-
-These range from Metal Organic Framework(MOF) enhanced gas adsorption, \textcolor{blue}{https://doi.org/10.1002/admi.201400040} 
-This increased surface area to volume ratio enhances the properties of the base material in applications such as catalysis, 
-battery electrodes and drug delivery systems among many more making them valuable microstructures. \
-cite{cha_bicontinuous_2019, samdani_bicontinuous_2017, thorson_bijel-templated_2019}
+ebner_tortuosity_2014} This increased surface area to volume ratio enhances the properties of the base material in applications such 
+as catalysis, battery electrodes and drug delivery systems among many more making them valuable microstructures. 
+\cite{cha_bicontinuous_2019, samdani_bicontinuous_2017, thorson_bijel-templated_2019, zhao_highly_2014}
 
@@
 cui_stabilizing_2013, manfredini_limonene--water_2021}  It was shown that external fields can be used to move, control emulsion stability 
-and elongate emulsion droplets. \cite{tham_magnetophoresis_2021, cui_stabilizing_2013} 
-\textcolor{blue}{https://pubs.acs.org/doi/10.1021/la047691n} Bijels stabilized spherical particles under a magnetic field showed no 
-meaningful microstructure changes. \cite{kim_bijels_2010} Bijels stabilized with spherical particles under an electric field showed 
-more promise. \cite{carmack_tuning_2018} However, magnetic fields offer more targeted stimuli response, allowing even weak fields to 
-incite a response. Magnetic fields non-interaction in many situations offer advantages to many of the desired uses of bijels within 
-pharmaceutical or bioengineering applications. \cite{vanoli_bijels_2022, thorson_bijel-templated_2019, thorson_composite_2018} These 
-same applications also have a need for in-situ microstructure modification that would enable tunable drug delivery rates, separations or
+and elongate emulsion droplets. \cite{tham_magnetophoresis_2021, cui_stabilizing_2013, melle_pickering_2005} Bijels stabilized spherical 
+particles under a magnetic field showed no meaningful microstructure changes. \cite{kim_bijels_2010} Bijels stabilized with spherical 
+particles under an electric field showed more promise. \cite{carmack_tuning_2018} However, magnetic fields offer targeted stimuli 
+response, allowing even weak fields to incite a response. Magnetic fields non-interaction in many situations offer advantages to many of 
+the desired uses of bijels within pharmaceutical or bioengineering applications. \cite{vanoli_bijels_2022, thorson_bijel-templated_2019, thorson_composite_2018} 
+These applications can also take advantage of in-situ microstructure modification that would enable tunable drug delivery rates, separations or
 catalyst efficiency and permeability improvements in the system. Therefore, identifying schemes that allow modification of the pore size 
@@
 exhibit magnetic field controlled orientations at interfaces, as Bresme and Faraudo showed. \cite{bresme_orientational_2007, davies_interface_2014}
- Under magnetic fields, assemblies of multiple ellipsoidal particles have been shown to have energy minima at unexpected locations. 
+Under magnetic fields, assemblies of multiple ellipsoidal particles have been shown to have energy minima at orientations different from isolated particles,
+meaning that the interface coverage of interfaces decorated with ellipsoidal particles can be varied using stimuli response. 
 \cite{newton_influence_2014, newton_capillary_2018} Thus ellipsoidal particles at interfaces, whose orientations and packing can be 
@@
 to the casting mixture composition. Stimuli response offers a way to modify the microstructure of bijels while still maintaining the 
-various form factors these continuous synthesis techniques can output. While stimuli response has been explored in the past using bijels 
-stabilized with spherical particles with little success, anisotropic particles are poised to allow microstructure modification of bijels 
-upon application of an external field. This technique also has the potential to allow for post synthesis microstructure modification. 
-Therefore, this work seeks to identify a means to control the microstructure of a bijel stabilized with magnetically responsive 
-ellipsoidal particles using magnetic fields.
+various form factors these continuous synthesis techniques can output. Magnetic stimuli response has been explored in the past using bijels 
+stabilized with spherical particles with little success. \cite{kim_bijels_2010}
 
-% Bijels have proposed uses in many of these with the microstructure of the material being shown to affect material properties.
-\cite{cha_bicontinuous_2019, khan_nanostructured_2022, vanoli_bijels_2022}
-
-% Magnetic fields offer several advantages over currently utilized techniques such as electric fields and shear.
-\cite{cui_stabilizing_2013, mulligan_deformation_2011} These include greater specificity of response as most materials are unresponsive to magnetic stimuli as well as even weak fields being sufficient to incite responses in many cases.
-
-% this adds value to many of the desired uses of bijels within pharmaceutical or bioengineering applications. \cite{vanoli_bijels_2022, thorson_bijel-templated_2019, thorson_composite_2018}
-
-\textcolor{blue}{Add commentary about past results with bijels and why we use anisotropic particles in bijels. Changes this makes} Therefore, 
-identification of a scheme which allows for tunability of the microstructure, independent of the composition of the casting mixture and post 
-synthesis is the goal of this work.
+With this background, we propose anisotropic particles as a technique to enable microstructure modification of bijels 
+upon application of an external field during and after fabrication. This work seeks to identify means to control the bijel microstructure independent 
+of the casting mixture composition by utilizing magnetic stimuli on bijels stabilized with magnetically responsive ellipsoidal particles. 
+The proposed mechanism of microstructure modification is driven through reorientation of the particles to the applied magnetic field altering 
+how the particles pack on the interface. By changing the interfacial packing of the particles, we change when the particles jam, which in turn changes 
+the jamming point of the bijel. This mechanism is predicted to be effective during and after synthesis. The processability of bijels fabricated using 
+this technique will also be investigated to ascertain how changes in particle packing affect the rheology of the material. An overview of three major 
+research aims will be presented below.
 
 \section{Research objective}
-
-This work seeks to identify means to control the bijel microstructure independent of the casting mixture composition by utilizing magnetic 
-stimuli on bijels stabilized with magnetically responsive ellipsoidal particles. The proposed mechanism of microstructure modification is 
-driven through reorientation of the particles to the applied magnetic field altering how the particles pack on the interface. By changing the 
-interfacial packing of the particles, we change when the particles jam, which in turn changes the jamming point of the bijel. This mechanism is 
-predicted to be effective during and after synthesis. The processability of bijels fabricated using this technique will also be investigated to 
-ascertain how changes in particle packing affect the rheology of the material. An overview of three major research aims will be presented below.
 
@@
 The jamming point of a bijel controls the obtained microstructure, as shown by previous work comparing the length scale of bijels synthesized 
-with different particle volume fractions. It has also been shown how magnetic fields can be used to self assemble ansisotropic particles at 
-interfaces and how they can tilt out of the interface. \cite{davies_interface_2014, davies_assembling_2014} On a curved interface with many 
-other particles, it is unknown how multiple particles orienting to a field and having regular structure will affect when and how the bijel 
+with different particle volume fractions and particle sizes. \cite{jansen_bijels_2011, reeves_particle-size_2015} It has also been shown how magnetic fields 
+can be used to enable self assembly of ansisotropic particles at interfaces and control the interfacial angle between the particle axis of symmetry and the interface. 
+\cite{davies_interface_2014, davies_assembling_2014}
+On a curved interface with many other particles, it is unknown how multiple particles orienting to a field and having regular structure will affect when and how the bijel 
 will jam. \cite{bresme_orientational_2007, davies_interface_2014}
@@
 ellipsoidal particles will be subjected to field strengths above and below the critical field strength when particle orientations to the 
-interface are controlled by the applied field strength, as calculated by Bresme and Faraudo for the particle used. This selection of fields 
+interface are controlled by the applied field strength, as calculated by Bresme and Faraudo for the particle aspect ratio.
+\cite{bresme_orientational_2007, davies_interface_201} This selection of fields
 will allow insight into the controlling mechanisms behind microstructural changes observed, allowing verification of the hypothesis and 
@@
 
-The average and directional domain sizes in addition to their relation with tortuosity will provide windows into the microstructural properties 
+The average and directional domain sizes in addition to their relation with tortuosity will allow characterization of the microstructural properties 
 of the resulting bijel. The nematic order parameter and average interfacial angle will be used to investigate how the application of the 
@@
 Particles on the surface of emulsion droplets have been shown to unjam and rejam into new, stable microstructures upon application of 
-stimuli. \cite{cui_stabilizing_2013} Two techniques of microstructure change are proposed. The first technique is that the adsorption 
+stimuli. \cite{cui_stabilizing_2013} Magnetic fields applied to bijels stabilized with ellipsoidal particles will facilitate unjamming and rejamming of
+the particle monolayer, resulting in microstructure modification of the bijel. Due to local changes in the state of the particles, specifically the 
+interfacial ordering in a specific direction and arrangement of particles, we expect that there will be microstructure modification even when the 
+magnetic field is switched off. Two techniques of microstructure change are proposed. The first technique is that the adsorption 
 energy is so strong that the interface is dragged along with the particles until they rejam in their new location and orientation to the 
@@
 \cite{haase_continuous_2015, cai_bijels_2017, amirfattahi_fabrication_2024} Ching showed that rheologically, bijels are 
-colloidal glasses percolating in 3D space. \cite{ching_bijel_2022} First, a shear capillary number is defined as 
-$Ca_s = \frac{\eta_{f} \dot{\gamma} L_{1}}{\sigma}$ where $\dot{\gamma} = \frac{u_{LE}}{L_x}$ is the strain rate and 
-$L_1$ is the average domain size. \cite{frijters_effects_2012, yang_capillary_2022} Lower capillary numbers in the range of
- $ 10^{-7} \geq Ca_s \leq 10^{-5}$ will be utilized. 
+colloidal glasses percolating in 3D space. \cite{ching_bijel_2022} A shear capillary number, $Ca_s$, is defined that correlates the 
+applied strain rate to the capillary forces derived from surface tension. \cite{frijters_effects_2012, yang_capillary_2022} We are interested 
+in identifying the effect of the initial microstructure and an applied field on the rheological properties of the bijel.
+
+% $Ca_s = \frac{\eta_{f} \dot{\gamma} L_{1}}{\sigma}$ where $\dot{\gamma} = \frac{u_{LE}}{L_x}$ is the strain rate and 
+% $L_1$ is the average domain size. \cite{frijters_effects_2012, yang_capillary_2022} Lower capillary numbers in the range of
+%  $ 10^{-7} \geq Ca_s \leq 10^{-5}$ will be utilized. 
 % which corresponds to a $Ma << 0.01$ to accommodate the hydrodynamic model utilized.
@@
 For this study, the yield stress and viscosity of the bijels will be explored as a function of the initial microstructure under 
-various $Ca_s$. Four templates with different processing history will be utilized to assess the impact of initial microstructure on 
-the obtained rheology. These are, $\bar{B} = 0$, $\bar{B} = 1$, $\bar{B} = 0 \rightarrow \bar{B} = 1$ and $\bar{B} = 1 \rightarrow \bar{B} = 0$. 
-To explain any observed differences in the the yield stress and viscosity, the time evolution of the domain size, average interface angle, and 
-nematic order parameter will be characterized and compared to the observed yield stress and viscosity. Additionally, the presence of shear 
-banding will be visually confirmed.
+various $Ca_s$. The initial microstructure will be derived from bijels stabilized with ellipsoidal particles made with no magnetic field 
+and with a field strength equal to the surface tension energy. We then apply constant shear defined with $Ca_s$ to determine the yield stress and non-newtonian
+characteristics of the bijel. Previous investigations have revealed that the ordering of particles in the direction of shear change
+the rheological behavior significantly compared to unordered systems. Additionally, the domains of the bijel may create additional mechanisms for 
+rheological behavior modification which have not been probed in detail yet.
+
+We will then identify the complex rheology of the bijels, calculating the loss and storage modulus of the bijel microstructures detailed earlier
+as a function of the oscillation of shear. The loss and storage modulus detail the viscous and elastic behavior of the bijel respectively, meaning 
+that the gel point of the bijel can be established as the point when the storage modulus exceeds the loss modulus. We will pay special attention to the 
+state of the particles in all simulations, correlating changes in the properties of the particle to observed rheological events. We will also identify if shear banding
+is observed.

### 2025-02-19 chapters/analysis_techniques.tex
Changes 1. Fixed more literature references

@@
 $\langle k_1 \rangle = \frac{\Sigma_{k} k\cdot S(k)}{\Sigma_{k} S(k)}$. Finally, the domain size is calculated as 
-$L_1 = \frac{2 \pi}{\langle k_1 \rangle}$. This domain size is used in past literature 
-\textcolor{blue}{https://doi.org/10.1017/S0022112001004682, https://www.doi.org/10.1103/PhysRevE.67.046304} 
+$L_1 = \frac{2 \pi}{\langle k_1 \rangle}$. \cite{kendon_inertial_2001,kendon_3d_1999} This domain size is used in past literature 
 to calculate the correct scaling regime of a system undergoing spinodal decomposition.
@@
 
-\textcolor{blue}{https://joss.theoj.org/papers/10.21105/joss.05358, https://doi.org/10.1016/j.softx.2019.100277, https://joss.theoj.org/papers/10.21105/joss.01296}
+% \textcolor{blue}{https://joss.theoj.org/papers/10.21105/joss.05358, https://doi.org/10.1016/j.softx.2019.100277, https://joss.theoj.org/papers/10.21105/joss.01296}
 
@@
 diffusive flow in a control volume of the same size, molecular
-diffusivity, and driving force \cite{cooper_taufactor_2016}. We used
+diffusivity, and driving force \cite{cooper_taufactor_2016, kench_taufactor_2023}. We used
 the \texttt{PeriodicSolver} to employ periodic boundary conditions. In many of the bijels synthesized using small molecule liquids, monomer is 
@@
 $\phi \leq 0$ and set their value to $0$, and all other values are set to $1$. To taufactor, $1$ represents void spaces 
-and 0's are solid. \cite{cooper_taufactor_2016}
+and 0's are solid. \cite{cooper_taufactor_2016, kench_taufactor_2023}
 
@@
 to the interface is obtained using a marching cubes algorithm at a countour level of 0 with a cube length of 4 lattice 
-units, which corresponds to the thickness of the interface. \textcolor{blue}{https://doi.org/10.7717/peerj.453} The 
+units, which corresponds to the thickness of the interface. \cite{van_der_walt_scikit-image:_2014} The 
 position of the particle and its closest vertex is calculated. If this distance is larger than the first minimum in 
@@
 \subsection{Shear banding}
-\label{section:yield_stress}
+\label{section:shear_banding}

### 2025-02-19 chapters/lit_review.tex
Changes 1. Fixed more literature references

@@
 The existence of particle stabilized emulsions has been known for more than a century now, after Pickering and Ramsden independently identified dispersed 
-droplets of oil within a water matrix after vigorous stirring of an oil, water and particle mixture. 
-\textcolor{blue}{10.1098/rspl.1903.0034, http://pubs.rsc.org/en/content/articlelanding/1907/ct/ct9079102001} Unlike surfactants, 
-particles act as emulsion stabilizers through the reduction of contact between dispersed and continuous phases as they adsorb into 
+droplets of oil within a water matrix after vigorous stirring of an oil, water and particle mixture. \cite{ramsden_separation_1904, pickering_cxcvi.emulsions_1907} 
+Unlike surfactants, particles act as emulsion stabilizers through the reduction of contact between dispersed and continuous phases as they adsorb into 
 the interface between phases. The Pieranski model derived from observations of \textcolor{blue}{insert derivation of pieranski model} 
@@
 of the particle. The particles can be considered to be irreversibly adsorb even for nanoparticles, and for particles larger than 100nm, the adsorption energy 
-is so great that thermal fluctuations at the interface can be considered to have no effect. \textcolor{blue}{https://doi.org/10.1063/1.3618553}
+is so great that thermal fluctuations at the interface can be considered to have no effect. \cite{cheung_molecular_2011}
 
@@
 their applications in food science. One such example is fat crystals stabilizing water droplets in oil to create margarine. Particle stabilization has also 
-been of interest owing to their lower toxicity and greater ease of sustainable sourcing through the usage of cellulose or chitin particles. \
-textcolor{blue}{https://www.tandfonline.com/doi/full/10.1080/14686996.2017.1401423, 10.1021/acs.biomac.6b00144, 10.1021/acs.langmuir.7b03959} 
+been of interest owing to their lower toxicity and greater ease of sustainable sourcing through the usage of cellulose or chitin particles. 
+\cite{fujisawa_nanocellulose-stabilized_2017, tang_stimuli-responsive_2016, kalliola_carboxymethyl_2018}
 Additionally, chemical surfactants can be toxic to aquatic life, acting as a xeno-hormone and interfering with their reproduction. 
-\textcolor{blue}{https://www.sciencedirect.com/science/article/pii/S0304389420302879, https://www.sciencedirect.com/science/article/pii/S014765131530172X}
+\cite{kaczerewska_environmental_2020, lechuga_acute_2016}
 
@@
 These variety of techniques mean that particle geometry is no longer as constraint when investigating prospective particle stabilizers of bijels. 
-\textcolor{blue}{https://onlinelibrary.wiley.com/doi/10.1002/smll.201600877}
+\cite{wu_recent_2016}
 
@@
 Using graphene plate like particles, it was shown that the plate like particles can have their own elasticity to them, affecting when jamming occurs. 
-\textcolor{blue}{https://doi.org/10.1039/C3MH00047H, https://pubs.acs.org/doi/10.1021/la402436w}
+\cite{imperiali_simple_2014, sun_assembly_2013}
 
@@
 limitations, Two Relaxation Time (TRT) and Multiple Relaxation Time (MRT) operators also exist, expanding the possible application of the LBM to visco-elastic 
-flows and implementation of fluctuating hydrodynamics in the LBM. 
-\textcolor{blue}{https://pubs.acs.org/doi/10.1021/acsomega.3c06663, https://iopscience.iop.org/article/10.1209/epl/i2004-10542-5, https://link.aps.org/doi/10.1103/PhysRevE.82.056714}
+flows and implementation of fluctuating hydrodynamics in the LBM. \cite{liu_simulation_2023, adhikari_fluctuating_2005}
 
@@
 The non-ideal mixing dynamics are recovered during the "recoloring" step, of which the technique proposed by Latva-Kokko and Rothman is more commonly 
-used for soft matter flows.
-
-\textcolor{blue}{https://pure.tue.nl/ws/files/25832941/1404.7523.pdf}
+used for soft matter flows. \cite{liu_multiphase_2016}

### 2025-02-19 chapters/model_params.tex
Changes 1. Added more analysis to application of magnetic fields during formation chapter 2. Added references to fix some (not all) literature reference issues 3. Added some detail in analysis techniques section
Changes 1. Fixed more literature references

@@
 \section{Simulation setup}
+\label{section:sim_setup}
+
+% The dynamics of the binary fluid mixture is governed by inertial,
+% viscous, and surface tension forces. The relative magnitudes of these
+% forces at a characteristic length scale \(L\) and characteristic
+% velocity \(U\) are captured by the capillary number $\mathrm{Ca}=\frac{\eta U}{\sigma}$ and the Weber number
+% \(\mathrm{We}=\frac{\rho U^2 L}{\sigma}\). Here we are primarily interested in spinodal decomposition of the mixture, 
+% where we analyze the dynamics after the initial formation of the interfaces and neglect residual diffusion. Hence the 
+% Peclet number \(\mathrm{Pe}=\frac{UL}{\Gamma}\) is of lesser importance and we do not consider it when choosing our 
+% simulation parameters.
+
+% The equations of motion of our model comprise the relevant materials
+% properties: the density \(\rho\), viscosity \(\nu\), and surface tension \(\sigma\) of the binary fluid, and the mass \(m_p\), size \(R_p\) and aspect ratio \(\alpha\), and dipole moment \(m\) of the particles.
+In addition, we can control the particle volume fraction \(\phi_p\) and
+% magnetic field strength \(B\). These nine quantities involve four unit
+% dimensions (mass, length, time, and charge), hence we can use five
+% dimensionless variables to specify the parameters of the system. These
+% are the particle aspect ratio $\alpha$, particle volume fraction
+% \(\phi_p\), particle vs.~fluid density ratio
+% $\xi = \frac{3m_p}{4\pi \rho V_p}$, nominal Weber number $\mathrm{We} = \frac{\rho \sigma V_p^{1/3}}{\eta^2}$, and magnetic Bond
+% number \(\bar{B} = m B/(\sigma A_p)\), where
+% \(V_p=(4/3)\pi R_\parallel^3/\alpha^2\) is the particle volume and
+% \(A_p=\max\left( \pi R_\parallel^2/\alpha, \pi R_\parallel^2/\alpha^2 \right)\)
+% the area of the larger cross-section of the ellpsoidal particles.
+
+% For our simulations, we choose units \(\Delta x\), \(\Delta t\),
+% \(\Delta m\), and \(\Delta i\) such that \(V_p=\hat{V}_p(\Delta x)^3\),
+% \(\nu=\hat{\nu}(\Delta x)^2/\Delta t\),
+% \(\sigma=\hat{\sigma}\Delta m/(\Delta t)^2\), and
+% \(m=\hat{m}\Delta i(\Delta x)^2\). We used \(V_p=2000\pi/3\),
+% \(\hat{\nu}=1/6\), \(\hat{\sigma}=0.0267\), \(\hat{m}=1\), and a density
+% ratio \(\xi=1/\hat{\rho}\). For reference, the values of the model
+% parameters are listed in table \ref{tab:parameters}. The values of
+% \(\alpha\) and \(\bar{B}\) are variable and are reported
+% with the results in section \ref{sec:results}.
+
+% %\new{We note that the dynamics of the simulations are determined by
+% %the dimensionless numbers, and the actual unit values $\Delta x$,
+% %$\Delta t$, $\Delta m$, and $\Delta j$ are arbitrary and only become
+% %meaningful when a connection to an experimental system is made (see
+% %below).}
+
+% \begin{table}
+% \centering
+% \caption{Summary of the parameters of the numerical model and the values used in the simulations}
+% \label{tab:parameters}
+% \begin{tabular}{|c|r|}
+% \hline
+% Parameter & Value \\
+% \hline
+% $L_V/\Delta x$ & 256 \\
+% $\rho \cdot (\Delta x)^3/\Delta m$ & 0.7 \\
+% $\nu \cdot \Delta t/(\Delta x)^2$ & 1/6 \\
+% $\sigma \cdot (\Delta t)^2/\Delta m$ & 0.0267 \\
+% $\tau/\Delta t$ & 1 \\
+% $g \cdot \Delta m(\Delta t)^2/(\Delta x)^5$ & 0.08 \\
+% $\phi_f$ & 0.5 \\
+% $\phi_p$ & 0.15 \\
+% $n_p$ & 1200 \\
+% $\rho_p \cdot (\Delta x)^3/\Delta m$ & 1 \\
+% $V_p/(\Delta x)^3$ & $2000\pi/3$ \\
+% $m/(\Delta i(\Delta x)^2)$ & 1 \\
+% $d_c/\Delta x$ & 2/3 \\
+% $K_H\cdot (\Delta x)^{1/2}(\Delta t)^2/\Delta m$ & 100 \\
+% \hline
+% \end{tabular}
+% \end{table}
+
+% We performed simulations of a binary fluid using the software package
+% LB3D \cite{schmieschek_lb3d_2017} that implements the lattice Boltzmann method described in section
+% \ref{section:methods}. The multicomponent
+% lattice Boltzmann model is solved in a cubic box of size
+% \(L_V=256\Delta x\) with periodic boundary conditions. The simulation
+% box is filled with equal volume fractions \(\phi_f=0.5\) of two fluids,
+% initially homogeneously mixed with a density
+% \(\rho=0.7\Delta m/(\Delta x)^3\). The BGK relaxation time is set to
+% \(\tau=\Delta t\) and the Shan-Chen interaction strength is set to
+% \(g_{kk^\star}=0.08(\Delta x)^2/(\Delta m(\Delta t)^2)\). We performed
+% preliminary simulations of a spherical droplet with these parameters and
+% fitted the pressure difference inside and outside the droplet to the
+% Young-Laplace law, which yielded a surface tension
+% \(\sigma=0.0267\Delta m/(\Delta t)^2\). To study the influence of
+% anisotropic particle shapes on the bijel formation, we performed
+% simulations for particles with three different aspect ratios:
+% \(\alpha=1\) for spherical particles, \(\alpha=2\) for prolate
+% ellipsoids, and \(\alpha=1/2\) for oblate ellipsoids. To match the
+% particle volume fraction \(\phi_p\) between the different particle
+% shapes, we kept the volume of the particles fixed and used the same
+% number of particles for each aspect ratio. The radius along the symmetry
+% axis of the particles was calculated from
+% \(V_p=(4/3)\pi R_\parallel^3/\alpha^2\), yielding
+% \(R_\parallel=7.9\Delta x\) for spheres, \(R_\parallel=12.6\Delta x\)
+% for prolate ellipsoids, and \(R_\parallel=5\Delta x\) for oblate
+% ellipsoids, respectively. Particles were added to the fluid by placing
+% them randomly inside the box. The lubrication cutoff distance was set to
+% the value \(d_c=(2/3)\Delta x\) recommended by Ladd
+% \cite{ladd_lattice-boltzmann_2001}, and the strength of the Hertz
+% potential was set to \(K_H=100\Delta m/((\Delta x)^{1/2}(\Delta t)^2)\).
+% We first equilibrated the particle positions and orientations by
+% evolving only the equations of motion of the particles, while the fluid
+% remained in its initial configuration, until the minimum particle
+% distance exceeded \(1.2\cdot\max(R_\parallel,R_\parallel/\alpha)\).
+% After the equilibration, the magnetic flux density
+% \(\vec{B}=B\hat{\vec{z}}\) was switched on and the full system was
+% evolved for \(10^5\) timesteps. In the course of the simulation, the binary mixture undergoes spinodal decomposition. 
+% The particles adsorb at the coarsening interface and eventually become jammed, resulting in the bicontinuous phase 
+% morphology of the bijel.
+
+% It is worth discussing briefly the possible realization of our model in
+% experiments. A common choice for bijel formation in binary liquids is a
+% mixture of water and lutidine
+% \cite{clegg_emulsification_2007,herzig_bicontinuous_2007}. The surface
+% tension between the phases of a water-lutidine system at
+% \(40^\circ\mathrm{C}\) is around \(\sigma=0.22\ \mathrm{mN/m}\) and the
+% dynamic viscosity of the lutidine-rich phase is around
+% \(\eta=2.38\ \mathrm{mPa\,s}\) \cite{grattoni_lower_1993}. Ellipsoidal
+% particles with various aspect ratios can be formed by mechanically
+% stretching spherical particles \cite{trevenen_gradient_2021}. Such
+% particles can be magnetically functionalized by e-beam deposition of a
+% Nickel layer. Fei et
+% al.~\cite{fei_magneto-capillary_2018,fei_magneto-capillary_2020}
+% fabricated coated \(4\ \mathrm{\mu m}\) polystyrene particles with a
+% permanent magnetic dipole moment of
+% \(m\approx3\cdot10^{-14}\ \mathrm{Am^2}\).
+It was shown that the dipole moment is oriented in the direction parallel to the coated interface \cite{yan_linking_2012,yan_rotating_2014}, i.e., it can be aligned with the axis of ellipsoidal particles.
+% For the given surface tension, the capillary torque on a particle adsorbed at an interface is approximately
+% $8.8\cdot10^{-16}\ \mathrm{Nm}$. We thus can estimate that a magnetic
+% flux density of \(30\ \mathrm{mT}\) is able to exert a magnetic torque
+% that exceeds the capillary torque.
+% We note that under these conditions,
+% the dipole-dipole interaction is on the order of
+% \(10^{-16}\ \mathrm{J}\) and an order of magnitude smaller than the
+% particle-interface interaction which is of order
+% \(10^{-15}\ \mathrm{J}\). %Unlike previous works
+% %\cite{xie_direct_2017,xie_controllable_2021}, we therefore cannot
+% %neglect the magnetic dipole-dipole interactions between particles.For these bijel properties and the parameters given in
+% table \ref{tab:parameters}, the spatial resolution of our
+% simulations is $\Delta x\approx252\ \mathrm{nm}$, and the time step
+% is $\Delta t=624\ \mathrm{ns}$. This corresponds to a system side length of $L_V \approx 64.5\ \mathrm{\mu m}$ and a runtime of
+% $T \approx 62.4\ \mathrm{ms}$.
 
@@
 \section{Model results}
+\label{section:model_results}
 
-\subsubsection{Surface tension}
+\subsection{Surface tension}
+\label{section:model_surface_tension}
 
@@
 maintain a droplet of analyte at a various sizes and utilizing the Young-Laplace equation to calculate the 
-surface tension of the system. 
-\textcolor{blue}{https://pubs.acs.org/doi/10.1021/la402436w, https://doi.org/10.1016/j.jcis.2015.05.012} 
+surface tension of the system. \cite{sun_assembly_2013, berry_measurement_2015}
 Upon extrusion of a droplet from a reservoir, the size of a droplet is determined by the balance between 
@@
 
-\subsubsection{Contact angle}
+\subsection{Contact angle}
+\label{section:model_contact_angle}
 

### 2025-02-20 chapters/LBM_technique.tex
Changes 1. Added more analysis to application of magnetic fields during formation chapter 2. Added references to fix some (not all) literature reference issues 3. Added some detail in analysis techniques section
Changes 1. Modify method section to flow better

@@
+\label{section:methods}
+
 This work uses a multicomponent Lattice Boltzmann Method (LBM) to simulate the hydrodynamics of two partially miscible, 
-incompressible fluids as implemented in LB3D. The LBM solves the Navier-Stokes equation at the incompressible limit, 
-$\rho \frac{d \overrightarrow{u}}{dt} = \eta \Delta \overrightarrow{u} + \frac{\nabla P}{\rho} + F_{body}$, at low 
-Mach and Reynolds numbers, incorporating density $(\rho)$, viscosity $(\eta)$, velocity $(u)$, pressure $(P)$, and 
+incompressible fluids as implemented in LB3D. The LBM solves the continuity and Navier-Stokes equation at low
+Mach and Reynolds numbers for the fluid, defined as,
+
+\begin{equation}
+    \begin{split}
+    \frac{\partial\rho}{\partial t} + \nabla\cdot\left(\rho\vec{u}\right) &= 0 , \\
+    \frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u} &= - \frac{1}{\rho} \nabla p + \nu \nabla^2 \vec{u} ,
+    \end{split}
+\end{equation}
+
+incorporating density $(\rho)$, viscosity $(\eta)$, velocity $(u)$, pressure $(P)$, and 
 body force $(F_{body})$. \cite{qian_lattice_1992, chin_lattice_2002, nourgaliev_lattice_2003} The Shan-Chen pseudopotential
-model is used to simulate the Cahn-Hilliard equation, $\frac{d c^k}{dt} = M^k\Delta \mu - \nabla u^k c^k$, for the non-ideal 
-mixture model. \cite{shan_lattice_1993, shan_simulation_1994, he_lattice_1997, he_discrete_1998} $c^k$, $M^k$ and $u^k$ is the 
-concentration, mobility and velocity of species $k$ respectively while $\mu$ is the free energy of system. Particle dynamics 
-include Hertzian contact and lubrication forces, tracked with classical Newtonian mechanics, while particle-fluid coupling 
-involves momentum exchange to simulate viscous dissipation. Particle-particle magnetic interactions are modeled using dipole 
+model is used to simulate the Cahn-Hilliard equation, defined below
+
+\begin{equation}
+    \begin{split}
+    \frac{\partial\phi}{\partial t}+\nabla\cdot\left(\phi\vec{u}\right) &= \nabla \cdot \left( \Gamma  \nabla\phi \right)
+    \end{split}
+\end{equation}
+
+where $c^k$, $M^k$ and $u^k$ is the concentration, mobility and velocity of species $k$ respectively while $\mu$ is the free energy of system. 
+\cite{shan_lattice_1993, shan_simulation_1994, he_lattice_1997, he_discrete_1998}
+
+Particle dynamics include Hertzian contact and lubrication forces, tracked with classical Newtonian mechanics, while 
+particle-fluid coupling involves momentum exchange to simulate viscous dissipation. Particle-particle magnetic interactions are modeled using dipole 
 interactions. \cite{davies_interface_2014, xie_direct_2017, xie_controllable_2021} A more detailed description of the model is 
@@
 \section{Hydrodynamics} 
+\label{section:lbm_hydrodynamics}
 
@@
 \cite{qian_lattice_1992} The kinematic viscosity if using the BGK operator is defined as 
-$\nu = c_s^2(\tau - \frac{\Delta t}{2})$. The equilibrium distribution is obtained from a discretized expansion of the 
+$\nu = c_s^2(\tau - \frac{\Delta t}{2})$. The equilibrium distribution is obtained from a taylor expansion of the 
 Maxwell-Boltzmann distribution to the second order. \cite{he_theory_1997, succi_lattice_2018} This is shown in equation 
@@
     f_{i}^{eq}(\mathbf{x}, t) = w_i\rho(1 + \frac{\mathbf{c_i} \cdot \mathbf{u}}{c_s^2} + \frac{(\mathbf{c_i} \cdot 
-    \mathbf{u})^2}{2c_s^4} + \frac{\mathbf{u} \cdot \mathbf{u}}{2c_s^2} + \frac{(\mathbf{c_i} \cdot 
-    \mathbf{u})^3}{6c_s^6} - \frac{(\mathbf{c_i} \cdot \mathbf{u})\mathbf{u}^2}{4c_s^3})
+    \mathbf{u})^2}{2c_s^4} + \frac{\mathbf{u} \cdot \mathbf{u}}{2c_s^2})
     \label{eq:LBM_Feq}
@@
 and can be calculated from the mass distribution using $\rho = \sum f_i$ and $\rho \mathbf{u} = \sum f_i \mathbf{c}_i$ 
-respectively. Using the Chapman-Enskog expansion, the Navier-Stokes equation at the incompressible limit at low-reynolds 
+respectively. Using the Chapman-Enskog expansion, the Navier-Stokes equation at the incompressible limit at low mach
 numbers can be recovered. \cite{qian_lattice_1992, he_lattice_1997} The regime accessible through this method is suitable 
@@
 \section{Non-ideal mixing}
+\label{section:lbm_non_ideal_mixing}
 
@@
 \begin{equation}
-F_{k}^{SC}(\mathbf{x}, t) = -\Psi^{k}(\mathbf{x}, t)\sum_{k'}g_{cc'}\sum_{\mathbf{x'}}\Psi_{k'}(\mathbf{x'}, t)(\mathbf{x'} 
-- \mathbf{x})
+% F_{k}^{SC}(\mathbf{x}, t) = -\Psi^{k}(\mathbf{x}, t)\sum_{k'}g_{cc'}\sum_{\mathbf{x'}}\Psi_{k'}(\mathbf{x'}, t)(\mathbf{x'} 
+% - \mathbf{x})
+\vec{F}_k(\vec{x}) \Delta t = - \sum_{k'} \sum_i \frac{w_i}{c_s^2} g_{kk'} \psi_k(\vec{x})\psi_{k'}(\vec{x}+\vec{c}_i) \vec{c}_i
 \label{eq:sc_model}
@@
 An effective mass of each fluid at node $\mathbf{x}$ is used in place of the actual density to scale it between zero 
-and one and is defined as $\psi^{c}(\mathbf{x},t) = \rho_{0}\left[1 - \exp(-\frac{\rho^{k}(\mathbf{x}, t)}{\rho_{0}})\right]$. 
-In this model, the SC force is incorporated into the macroscopic velocities written as 
-$\mathbf{u}_k =  \mathbf{u}_k + \frac{\tau}{\rho} F_{k}$ and finally the equilibrium distribution of each fluid species.
+and one and is defined as $\psi^{k}(\mathbf{x},t) = \rho_{0}\left[1 - \exp(-\frac{\rho^{k}(\mathbf{x}, t)}{\rho_{0}})\right]$. 
+In this model, the SC force is incorporated into the macroscopic velocities that are then used to calculate the equilibrium
+distribution $f_{i}^{k, eq}$ for fluid $k$, defined as,
+
+\begin{equation}
+\vec{u}_k^{\text{eq}} = \vec{u}' + \frac{\tau_k}{\rho_k} \vec{F}_k
+\end{equation}
+
+Where $\vec{u}'$ is defined as the common grid velocity and is calculated from $f_i^k$ below
+
+\begin{equation}
+    \sum_k \frac{\rho_k}{\tau_k} \vec{u}' = \sum_k \frac{1}{\tau_k}\sum_i f_i^k\vec{c}_i
+\end{equation}
+
+This recasting of the velocity ensures that in the absence of forces, the total momentum of the system is conserved.
 
 \section{Suspended particle dynamics}
+\label{section:lbm_colloids}
 
 Suspended particles will be coupled to the LB fluid based on the work conducted by Ladd. \cite{ladd_numerical_1994, 
-aidun_direct_1998, ladd_lattice-boltzmann_2001} The particles follow Newtonian mechanics with force 
-$\mathbf{F_p} = m_p\frac{d \mathbf{u_p} }{dt}$ and rotational inertia $\mathbf{D_p} = J_p \frac{d \mathbf{\omega_{p}}}{dt}$. 
+aidun_direct_1998, ladd_lattice-boltzmann_2001} The particles follow Newtonian mechanics with the particle force and
+rotational inertia defined using differential equations
+
+\begin{equation}
+    \begin{split}
+    \vec{F_p} = m_p \frac{\vec{u}_p}{dt} , \\
+    \vec{D_p} = \mathbf{J}_p \frac{\vec{\omega}_p}{dt} ,
+    \label{eq:md}
+    \end{split}
+\end{equation}
+
 $\mathbf{F_p}$ and $\mathbf{D_p}$ represent the force and torque acting on a particle with mass $m_p$ and moment of inertia 
-$J_p$. $\mathbf{u}_p$ and $\mathbf{\omega_{p}}$ are the linear and angular velocities of the particle. The equations of 
+$\mathbf{J}_p$. $\mathbf{u}_p$ and $\mathbf{\omega_{p}}$ are the linear and angular velocities of the particle. The equations of 
 motion are evolved over time using a leapfrog integrator. \cite{jansen_bijels_2011}
@@
 The particles are discretized on the lattice according to the method laid out in Ladd and Aidun 
-\cite{ladd_lattice-boltzmann_2001}. Coupling to the LB fluid is done through momentum exchange with the 
-fluid through modification of the velocity surrounding the fluid. The discretized particles have a no-slip 
-boundary condition implemented as a modified bounce back boundary condition, with momentum exchange between 
-particle and fluid done by changing the post collision population distribution, $f^{*}_{i}(\mathbf{x}, t)$, 
-shown in Eq \ref{eq:md_LBM_mod}
+\cite{ladd_lattice-boltzmann_2001}. Nodes representing the particle are marked as solid nodes that replicate
+a no-slip boundary condition through a moving bounce-back boundary. This is implemented into the distribution function
+by reflecting the outgoing populations of $f_i^k$ to the opposite lattice velocity
 
 \begin{equation}
-    f^{*}_{i'}(\mathbf{x}, t + \Delta t) = f^{*}_{i}(\mathbf{x}, t) - \frac{2 w_{i}}{c_s^2}\rho^k \mathbf{u}_{surf} 
-    \cdot \mathbf{c_i}
-    \label{eq:md_LBM_mod}
+    f^k_{i^\star}(\vec{x}, t+\Delta t) = f^{k,\star}_i(\vec{x}, t) - \frac{2w_i}{c_s^2} \rho \vec{u}_i \cdot \vec{c}_i ,
 \end{equation}
 
-In this work, $i'$ is defined such that $\mathbf{c_i} = -\mathbf{c_{i'}}$ to satisfy the bounce-back boundary condition. 
-The fluid velocity at the particle surface, $\mathbf{u}_{surf}$, is the sum of the particle's linear and rotational 
-velocities, $\mathbf{u}_{surf} = \mathbf{u_p} + R_i\mathbf{\omega_p}$. Advection of populations occurs after this exchange. 
-The total force and torque on the particle are calculated by summing the total momentum over its surface. As particles 
-move, they cover and uncover fluid grid points. Covered points are removed, while the composition of newly uncovered 
-points in a multiphase fluid is averaged from adjacent grid points.
+This facilitates momentum exchange between particle and fluid which can be calculated analytically as 
+\(\Delta\vec{p}^k_i \frac{\Delta t}{(\Delta x)^3} = 2 f^{k,\star}_i(\vec{x},t)\vec{c}_i - \frac{2w_i}{c_s^2}\rho(\vec{u}_i\cdot\vec{c}_i)\vec{c}_i\).
+The sum of the momentum change across the surface of the particle is computed to obtain the force and torque on the particle,
+
+\begin{equation}
+    \begin{split}
+    \vec{F}_p &= \sum_{k,i} \frac{\Delta \vec{p}^k_i}{\Delta t} , \\
+    \vec{T}_p &= \sum_{k,i} \frac{\Delta\vec{p}^k_i}{\Delta t} \times \vec{r}_i .
+    \end{split}
+\end{equation}
+
+As the particle moves, the nodes representing the particle are updated, with newly covered grid points marked as solid and 
+uncovered nodes marked as fluid. When a grid point is covered, the momentum contained in that lattice point is added to the 
+total force of the particle,
+
+\begin{equation}
+    \vec{F}_p = -\sum_{k,i} f_i^k(\vec{x},t)\vec{c}_i .
+\end{equation}
+
+Upon uncovering of a grid point, it is assigned a density value that represents the average of all adjacent fluid sites,
+
+\begin{equation}
+    \rho^k(\vec{x},t) = \frac{1}{N_{\text{f}}} \sum_{i_{\text{f}}} \rho^k(\vec{x}+\vec{c}_{i_{\text{f}}n}, t)
+    \label{eq:fill_particles}
+\end{equation}
 
 \subsection{Anisotropic particles}
+\label{section:lbm_colloids_ellipsoids}
 
-Under 1 lattice unit additional lubrication forces are required to reduce the likelihood of particle overlap. For 
+For particles close to contact, meaning with inter-surface distances under 1 lattice unit the hydrodynamics are unresolved as the
+distance is smaller than what the model can resolve. Lubrication forces are added to reduce the likelihood of particle overlap. For 
 spherical particles, this is defined in Equation \ref{eq:sphere_lube}
@@
 \begin{equation}
-    \mathbf{F}_l = -6\pi \eta \frac{R_{i}^{2} R_{j}^{2}}{(R_i + R_j)^2}(\frac{1}{|\mathbf{r}_{ij}| -R_i - R_j} -\frac{1}{\Delta_c}) \frac{(\mathbf{u}_{ij}\cdot\mathbf{r}_{ij})\mathbf{r}_{ij}}{|\mathbf{r}_{ij}|^2}
-    \label{eq:sphere_lube}
+    \vec{F}_l = -6 \pi \eta \frac{R_1^2 R_2^2}{\left(R_1+R_2\right)^2}\left(\frac{1}{|\vec{r}_{ij}|-R_1-R_2}-\frac{1}{d_c}\right) \frac{\left(\vec{u}_{12}\cdot\vec{r}_{12}\right)\vec{r}_{12}}{|\vec{r}_{12}|^2} ,% \qquad d<d_c,
+    \label{eq:lubrication}
 \end{equation}
 
-where $R_i$ and $R_j$ are the radii of each particle involved in the interaction, $\mathbf{r}_{ij}$ is the distance
+where $R_i$ and $R_j$ are the radii of each particle involved in the interaction, $\vec{r}_{ij}$ is the distance
 vector between the particle centers, $\mathbf{u}_{ij}$ are the relative velocities of the particles and $\Delta_c$ 
- is the cutoff distance when the lubrication force begins to act. A hertzian contact force is also added to ensure 
- that there is no particle overlap, defined in Equation \ref{eq:hertz_def}
+is the cutoff distance when the lubrication force begins to act. If particles are able to overcome the lubrication forces, 
+a hertzian contact force is also added to ensure that there is no particle overlap, defined in Equation \ref{eq:hertz_def}
 
@@
     \phi_{H} = K_{H}(R_i + R_j - |\mathbf{r}_{ij}|)^{5/2}, r < R_i + R_j
-    \label{eq:hertz_def}
+    \label{eq:hertz}
 \end{equation}
@@
 $K_H$ is the force constant used to push particles apart. To correct for the anisotropic particles used in this work, 
-the formulas presented in Eqs \ref{eq:sphere_lube} and \ref{eq:hertz_def} can be generalized using the route followed 
+the formulas presented in Eqs \ref{eq:lubrication} and \ref{eq:hertz} can be generalized using the route followed 
 in Gunther et al. and Davies et al., inspired by Berne and Pechukas. \cite{gunther_timescales_2014, davies_interface_2014} 
-They first begin by rewriting the lubrication and Hertzian contact forces in a dimensionless form below
+They first begin by rewriting the lubrication and Hertzian contact forces as a function of the particle orientation and 
+aspect ratio of the particles.
 
 \begin{equation}
-    \phi_{H}(\hat{\mathbf{o_i}}, \hat{\mathbf{o_j}}, \hat{\mathbf{r_{ij}}}) = \epsilon(\hat{\mathbf{o_i}}, 
-    \hat{\mathbf{o_j}})\Bar{\phi_{H}}\left( \frac{r_{ij}}{\sigma(\hat{\mathbf{o_i}}, \hat{\mathbf{o_j}}, 
-    \hat{\mathbf{r_{ij}}})} \right)
-    \label{eq:hertz_anisotropic}
+    \begin{split}
+    \phi(\vec{r}_{ij}) &= {\epsilon} \tilde{\phi}\left(\frac{\vec{r}_{ij}}{{\sigma}}\right) , \\
+    \vec{F}(\vec{r}_{ij}) &= {\epsilon} \tilde{\vec{F}}\left(\frac{\vec{r}_{ij}}{{\sigma}}\right) .
+    \end{split}
 \end{equation}
 
-Equation \ref{eq:hertz_anisotropic} defines the generalization of the Hertz force to allow simulation of ellipsoidal 
-particles inspired by Berne and Pechukas. First, the hertzian force is made a function of orientation through the 
-addition of eccentricity, $\chi = \frac{R_p^2 - R_o^2}{R_p^2 + R_o^2}$ and an orientation dependent forces, where 
-$\epsilon(\hat{\mathbf{o_i}}, \hat{\mathbf{o_j}}) = \frac{\Bar{\epsilon}}{\sqrt{1 - \chi(\hat{\mathbf{o_i}}, 
-\hat{\mathbf{o_j}})^2}}$, and $\sigma = \frac{\Bar{\sigma}}{\sqrt{1 - \frac{\chi}{2}( 
-\frac{(\hat{\mathbf{r_{ij}}}\hat{\mathbf{o_i}} +  \hat{\mathbf{r_{ij}}}\hat{\mathbf{o_j}})^2}{1 + 
-\chi \hat{\mathbf{o_i}}\hat{\mathbf{o_j}}} +  \frac{(\hat{\mathbf{r_{ij}}}\hat{\mathbf{o_i}} -  
-\hat{\mathbf{r_{ij}}}\hat{\mathbf{o_j}})^2}{1 - \chi \hat{\mathbf{o_i}}\hat{\mathbf{o_j}}})}}$, 
-$\Bar{\sigma} = 2R_{\perp}$. \cite{gunther_lattice_2013, gunther_timescales_2014, davies_assembling_2014}
-
-A similar generalization process is done for the lubrication force, resulting in Equation \ref{eq:md_force} where 
-$\mathbf{\Bar{F}}(r) = \hat{\mathbf{r_{ij}}}(\hat{\mathbf{r_{ij}}}(\mathbf{u}_i - \mathbf{u}_j))\left( \frac{1}{r - 1} - 
-\frac{\sigma}{\Delta_{c}} \right)$.
+For the lubrication force \eqref{eq:lubrication}, we choose
+${\sigma}=R_1+R_2$ and ${\epsilon}=\frac{6\pi\eta R_1^2 R_2^2}{{\sigma^3}}$, and for the
+Hertz potential we chose ${\sigma}=R_1+R_2$ and ${\epsilon}=K_H\sigma^{5/2}$. For two identical, rotationally
+symmetric ellipsoidal particles with orientations $\hat{\vec{o}}_i$ and $\hat{\vec{o}}_j$, we then replace $\epsilon$ and $\sigma$ by
+the anisotropic functions
 
 \begin{equation}
-    \mathbf{F_{ij}}(\hat{\mathbf{o_i}}, \hat{\mathbf{o_j}}, \hat{\mathbf{r_{ij}}}) = \epsilon(\hat{\mathbf{o_i}}, 
-    \hat{\mathbf{o_j}})\mathbf{\mathbf{F_{ij}}}\left( \frac{r_{ij}}{\sigma(\hat{\mathbf{o_i}}, \hat{\mathbf{o_j}}, 
-    \hat{\mathbf{r_{ij}}})} \right)
-    \label{eq:md_force}
+    \begin{split}
+    \tilde\epsilon\left(\hat{\vec{o}}_i, \hat{\vec{o}}_j\right) &= \frac{{\epsilon}}{\sqrt{1-\chi^2}} , \\
+    %\qquad \chi = \frac{\left(\alpha^2-1\right)R_\parallel^2}{\left(\alpha^2+1\right)R_\parallel^2}\left(\hat{\vec{o}}_i\hat{\vec{o}}_j\right) , \\
+    \tilde\sigma\left(\vec{r}_{ij}, \hat{\vec{o}}_i, \hat{\vec{o}}_j\right) &= \frac{{\sigma}}{\sqrt{1-\frac{\chi}{2}\left[ \frac{\left(\hat{\vec{r}}_{ij}\cdot\hat{\vec{o}}_i+\hat{\vec{r}}_{ij}\cdot\hat{\vec{o}}_j\right)^2}{1+\chi\left(\hat{\vec{o}}_i\hat{\vec{o}}_j\right)} + \frac{\left(\hat{\vec{r}}_{ij}\cdot\hat{\vec{o}}_i-\hat{\vec{r}}_{ij}\cdot\hat{\vec{o}}_j\right)^2}{1-\chi\left(\hat{\vec{o}}_i\hat{\vec{o}}_j\right)} \right] }} , \\
+    \chi &= \frac{\alpha^2-1}{\alpha^2+1} , \\
+    \end{split}
+\end{equation}
+
+where $R_{\parallel}$ is the particle radius along the
+symmetry axis $\hat{o}$ and $\alpha=\frac{R_{\parallel}}{R_{\perp}}$ the aspect
+ratio of the particle. The anisotropic Hertz potential and lubrication
+force are then defined as
+%
+\begin{equation}
+    \begin{split}
+    \phi\left(\vec{r}_{ij}, \hat{\vec{o}}_i, \hat{\vec{o}}_j\right) &= \epsilon\left(\hat{\vec{o}}_i, \hat{\vec{o}}_j\right) \tilde{\phi}\left(\frac{\vec{r}_{ij}}{\sigma\left(\vec{r}_{ij}, \hat{\vec{o}}_i, \hat{\vec{o}}_j\right)} \right) , \\
+    \vec{F}\left(\vec{r}_{ij}, \hat{\vec{o}}_i, \hat{\vec{o}}_j\right) &= \epsilon\left(\hat{\vec{o}}_i, \hat{\vec{o}}_j\right) \tilde{\vec{F}}\left(\frac{\vec{r}_{ij}}{\sigma\left(\vec{r}_{ij}, \hat{\vec{o}}_i, \hat{\vec{o}}_j\right)} \right) .
+    \end{split}
 \end{equation}
@@
 \subsection{Magnetic field and particle coupling}
+\label{section:lbm_colloids_magnetics}
 

### 2025-03-04 chapters/LBM_technique.tex
Changes 1. Changed chapter 2 content 2. Addeed chapter 1 curvature results

@@
 distance is smaller than what the model can resolve. Lubrication forces are added to reduce the likelihood of particle overlap. For 
-spherical particles, this is defined in Equation \ref{eq:sphere_lube}
+spherical particles, this is defined in Equation \eqref{eq:lubrication}
 
@@
 is the cutoff distance when the lubrication force begins to act. If particles are able to overcome the lubrication forces, 
-a hertzian contact force is also added to ensure that there is no particle overlap, defined in Equation \ref{eq:hertz_def}
+a hertzian contact force is also added to ensure that there is no particle overlap, defined in Equation \eqref{eq:hertz}
 

### 2025-03-04 chapters/paper1.tex
Changes 1. Changed chapter 2 content 2. Addeed chapter 1 curvature results

@@
 
-\section{Results}\label{sec:results}
+\section{Results}\label{sec:results_p1}
 
@@
     \centering 
-    \includegraphics[width=\textwidth]{figures/results/paper1/curvature_vs_coverage.png} 
+    \includegraphics[width=\textwidth]{figures/results/paper1/genus_curvature_vs_coverage.png} 
     \caption{Plots of Gaussian $\langle K \rangle \Sigma^{-2}$ curvature over time averaged across 3 runs. 
@@
     \centering 
-    \includegraphics[width=\columnwidth]{figures/results/paper1/Q6_vs_coverage.png} 
+    \includegraphics[width=\columnwidth]{figures/results/paper1/steinhardt_vs_coverage.png} 
     \caption{Time dependence of the mean six fold symmetry parameter, $\langle Q6 \rangle$ for bijels 

### 2025-03-04 chapters/paper2.tex
Changes 1. Changed chapter 2 content 2. Addeed chapter 1 curvature results

--- 2025-02-12 chapters/paper2.tex
@@
-Previous work demonstrated that applying electric fields to silica-stabilized emulsion droplets caused particle stabilizers to unjam and then rejam, locking the emulsion in a new morphology.
-\cite{cui_stabilizing_2013} Considering the potential applications of an already synthesized porous material with tunable microstructure, the second part of this work will explore using magnetic fields to manipulate bijels after synthesis.
-\cite{vanoli_bijels_2022, cha_bicontinuous_2019} Bijels simulated under no field had a constant magnetic in the z direction of strength $\Bar{B} = 0, 0.2, 0.5, 1$ with their microstructure and particle order analyzed.
+\section{Results}\label{sec:results_p2}
+\subsection{Field strength dependence on domain
+size}\label{field-strength-dependence-on-domain-size}
 
-Underlying mechanism being rearrangement of particles on the interface in response to magnetic field, or unjamming and rejamming characterized by a change in the number of bonded neighbors.
-Explains behaviour seen in differences in the system above and below the isotropic to nematic transition?
+Bijels have proposed applications as soft matter based material
+templates, drug delivery vectors and separations systems. The materials
+performance in each application is dependent upon the microstructure of
+the bijel template. Many of the applications listed above benefit from
+stimuli response, allowing for in-situ microstructure tuning to modify
+permeability of the material. We want to understand whether bijels
+provide access to reversible structural modifications which would allow
+stimuli responsive bijels to be used in in-situ applications.
+Additionally, in many of the proposed stimuli responsive applications
+for bijels, the timescales of response is important to characterize and
+would also provide a mechanistic understanding of the reasons why the
+microstructure changes occur. We probe these aspects of structural
+response of bijels in this section by assessing the response of bijels
+stabilized by particles with volume fraction of \(\phi_p = 0.1\)
+simulated under no applied field to an applied field in the range
+\(\bar{B} = 0, 0.2, 0.5, 1\). We begin our investigation by visualizing
+the structure before and after the application of magnetic fields.
 
@@
 \centering 
-    \includegraphics[scale = 0.5]{figures/results/paper2/domain_size.png}
-    \caption{Left plot shows the average domain size $(L_1)$ in markers and the nematic order parameter $(S)$ in lines versus time.
-Right plot shows the same data rescaled over $t_{iso \rightarrow nematic}$.}
-    \label{fig:P2_domain_scaling}
+\includegraphics[scale=0.4]{../figures/results/paper2/microstructure_viz-field_on.png} 
+\caption{Visualizations of bijels stabilized by oblate and prolate particles simulated under no fields at $t = 0$ (left columns) and $t = 10^5$ (right columns).
+The first and third row detail the microstructure evolution for oblate and prolate particle stabilized bijels with no applied field while the second and fourth rows show bijels stabilized by oblate and prolate particles respectively with a field strength of $\bar{B} = 1$ applied.
+Particle reorientation to the direction of the field can be seen upon application of the magnetic field, resulting in microstructure changes driven through domain coarsening until the particles jam.
+We see similar behavior in bijels stabilized by oblate particles upon application of the magnetic field.}
+\label{fig:microstructure_viz-field_on} 
 \end{figure}
 
-In this system, the mechanism of microstructure modification after formation is expected to be due to magnetic field driven particle ordering changes.
-Figure \ref{fig:P2_domain_scaling} demonstrates that the average domain size $(L_1)$ does not change significantly with the applied field, with a slight increase of about $\approx 0.3 L/R$, noted to be within error.
-However, clues into the underlying mechanics are visible when examining the nematic order parameter lines overlaid on the domain size markers.
-At $\Bar{B} = 0.2$, the domain size change corresponds with the nematic order parameter change, indicating a direct link between domain size change and particle ordering.
-At $\Bar{B} > 0.2$, a gap appears between the domain size change and the nematic order parameter change, suggesting steric effects influence the rate of bijel microstructure change.
-The timescales of these rearrangements may also impact the observed microstructure changes, which can be characterized by the domain size change over time rescaled by a characteristic timescale.
+In Figure \ref{fig:microstructure_viz-field_on} we show representative
+snapshots of the bijel at the initial and final timestep with
+\(\bar{B}_z = 0\) and \(\bar{B}_z = 1\). We show that upon application
+of the field, particles align to the direction of the field. As the
+particles orient to the field, they disrupt the packing of particles at
+the interface, causing domain coarsening as the particles rearrange into
+new positions. The particles then rejam in place once the interfacial
+area and particle cross sectional area match. Domain coarsening observed
+in the figure can be explained through the ordering of particles at the
+interface, causing a reduction in the available area that the particles
+have for stabilization.
 
-A naive guess as to the dominating timescale of the response would be the isotropic to nematic time of the system or when $S \geq 0.3$.
-The right plot of Figure \ref{fig:P2_domain_scaling} demonstrates the time evolution of the system when rescaling time with the isotropic to nematic transition time, $t_{iso \rightarrow nematic}$.
-From this plot, it can be seen that application of the field causes collapse of domain size changes at different field strengths on top of one another, showing that this naive guess is a correct one.
-The changes in domain size at with no applied field can be attributed to the reordering of particles at the interface, leading to coarsening at long time scales consistent with what Gunther et al.
-observed.
-\cite{gunther_timescales_2014}
+We characterize the microstructure changes observed through calculating
+a characteristic length scale, called the average domain size. The
+average domain size is calculated using the first moment of the 3D
+averaged structure factor. Past work has shown that this method
+correctly reproduces the scaling expected in phase separating systems.
+The structure factor is calculated from the fourier transform of the
+fluctuations in the order parameter. \cite{kendon_inertial_2001}
+
+\begin{equation}
+S(\mathbf{k}, t) = \widetilde{\phi}(\mathbf{k}, t)\widetilde{\phi}(\mathbf{-k}, t)
+\end{equation}
+
+\(\mathbf{k}\) represents the wave vector in each direction of each
+lattice grid point. The fluctuations in the order parameter are
+calculated from the order parameter of the bijel defined as
+\(\widetilde{\phi} = \phi - \langle \phi \rangle\). \(\phi\) is
+calculated through subtraction of the red from the blue fluid density,
+\(\phi = \rho^b - \rho^r\). The average domain size is commonly
+calculated using the spherically averaged structure factor where all
+points corresponding to \(k = |\mathbf{k}|\) are binned, where \(k\) is
+the magnitude of \(\mathbf{k}\).
+
+\begin{equation}
+S(k, t) = \frac{1}{n} \sum_{k - \Delta < k < k + \Delta} S(\mathbf{k}, t)
+\label{eq:structure_factor_calc}
+\end{equation}
+
+The average domain size can then be calculated from the spherically
+averaged structure factor after calculating the first moment of the
+structure factor using the following expression.
+
+\begin{equation}
+L(t) = 2\pi \frac{\sum S(k, t) }{ \sum k S(k, t) }
+\end{equation}
+
+We found that this method for determining domain size generally
+overestimated the observed channel diameter. However, previous studies
+have demonstrated that the scaling behavior of the first-moment-derived
+domain size aligns with the expected phase separation in spinodal
+decomposition. The overestimation arises due to the limited number of
+samples at small k values, where the bin size is roughly equivalent to
+the k value. Additionally, in simulations with periodic domains, both
+the structure factor and computed length scale are influenced by
+finite-size effects. Nonetheless, this measurement still provides
+valuable insight into trends in the average domain size.
+
+To correlate the microstructure evolution to the ordering of the
+particle monolayer to the magnetic field, we calculate the nematic order
+parameter. \cite{cuesta_monte_1990} First, the average orientational
+tensor is calculated from the particle orientations in Eq
+\ref{eq:orientational_order_tensor}
+
+\begin{equation}
+Q = \frac{1}{n_p} \sum_{i} (\frac{3}{2}[\hat{\mathbf{o}}_i \otimes \hat{\mathbf{o}}_i] - \frac{1}{2}\mathbf{I})
+\label{eq:orientational_order_tensor}
+\end{equation}
+
+In Eq \ref{eq:orientational_order_tensor}, \(\hat{\mathbf{o}}_i\)
+defines the orientation vector of particle \(i\) and \(\mathbf{I}\) is
+the identity matrix. The nematic director or average particle
+orientation is the eigenvector corresponding to the largest eigenvalue
+of \(Q\) which is the value of the nematic order parameter, \(S\). The
+assembly of particles can be said to have nematic order if
+\(S \geq 0.3\) and is fully aligned to the director if \(S = 1.0\).
+\cite{cuesta_monte_1990}
 
@@
 \centering 
-    \includegraphics[scale = 0.5]{figures/results/paper2/domain_size_aniso.png}
-    \caption{Plots of the perpendicular $(L_{\perp})$ and parallel $(L_{\parallel})$ domain sizes over time rescaled over $t_{iso \rightarrow nematic}$}
-    \label{fig:P2_domain_aniso}
+\includegraphics[scale=0.5]{../figures/results/paper2/domain_size-field_on.png} 
+\caption{Plotting the spherically averaged domain size normalized with $R_p$($L/R$) of the particle at different magnetic field strengths, $\bar{B}$, and the nematic order parameter $S$ in lines.
+We quantify the domain size and ordering of the particles, and show that the change in both parameters are correlated with the strength of the applied magnetic field.}
+\label{fig:domain_size-field_on} 
 \end{figure}
 
-In the previous section, even if the average domain size did not change much, there was domain size anisotropy found upon application of the field.
-This observation and trends seen remains true when applying the field after formation as can be observed in \ref{fig:P2_domain_aniso}.
-Time was again rescaled with the isotropic to nematic transition time for each system, demonstrating that the timescale of response is controlled using this timescale, and is independent from field strength.
-The domain size change observed appears to be about $1 L/R$ less than what can be found when applying the same field size during bijel synthesis as the increase in domain size for $L_{parallel}$ for prolate particles is $\approx 2 L/R$ which is $50 \%$ lower than what was found.
-This indicates that microstructure control after synthesis is not as effective.
-This might be due to steric effects being much stronger after synthesis, limiting how much particles can move or tilt before rejamming.
-Despite this, the domain size change found is well within what has been seen to be effective in the literature, indicating that magnetic field enabled in-situ microstructure modifications can be utilized within bijels.
-\cite{cha_bicontinuous_2019, khan_nanostructured_2022, vanoli_bijels_2022}
+In Figure \ref{fig:domain_size-field_on}, we present the time evolution
+of the normalized average domain size, where normalization is performed
+using the volume-equivalent spherical particle radius \(R = 7.9\). The
+results indicate that upon applying a magnetic field to a bijel
+initially formed without one, the final average domain size increases by
+up to 5.2\% and 2.5\% for oblate- and prolate-particle-stabilized bijels
+respectively. Additionally, in the absence of an external field, domain
+coarsening occurs for both particle morphologies. However, the results
+for oblate particles with a magnetic field is attributed to coalescence
+of domains rather than magnetic field driven ordering of the particles.
+
+In the same figure, the time evolution of the nematic order parameter
+\(S\) is also plotted to illustrate changes in particle alignment.
+Initially, at \(\bar{B}_z = 0\), a gradual increase in \(S\) is
+observed, attributed to steric interactions driving particle reordering.
+This effect contributes to the domain coarsening seen in the absence of
+an applied field, consistent with the findings of Günther et
+al.~\cite{gunther_timescales_2014}. In the case of
+oblate-particle-stabilized bijels without an external field, domain
+coalescence is primarily driven by steric interactions rather than
+field-induced rearrangement. Furthermore, the rate and extent of
+particle alignment to the field exhibit a dependence on field strength,
+as evidenced by the earlier onset of nematic ordering with increasing
+\(\bar{B}\). We also observed between the time evolution of the nematic
+order parameter and domain size, particularly when comparing results for
+\(\bar{B}_z = 0.5, 1\) against those for \(\bar{B}_z = 0.2\). This
+suggests that nematic ordering alone may not fully account for the
+observed changes in domain size.
+
+Previous studies have demonstrated that microstructural properties,
+particularly length scale and tortuosity, play an important role in the
+performance of porous materials across various applications, including
+battery electrodes and tissue engineering. \cite{zhang_promoting_2019}
+\cite{ebner_tortuosity_2014} \cite{hsieh_architected_2021} Specifically,
+lower tortuosity and more ordered ion-conducting domains have been shown
+to enhance charge/discharge rates in battery systems, while controlled
+tortuosity in artificial bone grafts facilitates improved cell growth
+and nutrient transport.
+
+Precise characterization of the anisotropic microstructure is essential
+for the tailored design of application-specific porous materials. To
+quantify the characteristic length scales in each Cartesian direction,
+we compute the second-moment-derived structure factor without radial
+averaging. \cite{jansen_bijels_2011} Following the structure factor
+calculation described in Eq. \ref{eq:structure_factor_calc}, the second
+moment of the structure factor in direction \(\beta\) is determined for
+each Cartesian coordinate axis as
+
+\begin{equation}
+L_{\beta}(t) = 2 \pi \sqrt{\frac{\sum_{\mathbf{k_{\beta}}}  S(\mathbf{k}, t) }{\sum_{\mathbf{k_{\beta}}}  k_{\beta}^2S(\mathbf{k}, t)}}
+\label{eq:second_moment_domain}
+\end{equation}
+
+From Eq \ref{eq:second_moment_domain}, we can calculate the length scale
+in each cartesian direction, \(L_x, L_y, L_z\). Here, we make a further
+refinement simplifying the domain sizes to directions parallel and
+orthogonal to the magnetic field. These result in the length scales and
+their associated calculation, \(L_{\parallel} = L_{z}\) and
+\(L_{\perp} = \frac{L_x + L_y}{2}\). Tortuosity has been defined using
+the geometric, diffusional and hydraulic tortuosities. Here we define
+the diffusional tortuosity, \(\tau = \frac{D}{D_{eff}}\) which
+characterizes the ratio between the free diffusion of a tracer and the
+effective diffusion of a tracer in the material.
+
+To calculate the tortuosities of the structures generated from our
+simulations, we first calculate \(\phi\) of the system over time from
+the filled densities. Many bijels are synthesized from monomer diffused
+into the oil phase, or the oil phase itself is intrinsically
+polymerizable. Our next step is to binarize the order parameter with the
+condition, \(\phi \leq 0 = 0\) and \(\phi > 0 = 1\) which reflects a
+solid red fluid phase and void blue fluid. We then mask all unconnected
+components, using the \texttt{label} function in \texttt{skimage}
+leaving only the percolating domain representing the bijel.
+\cite{van2014scikit} We utilize the python package taufactor which
+solves the diffusion equation for the structure, calculating the time
+taken for a tracer to go from one side of the system to the other.
+\cite{kench_taufactor_2023} We utilize the periodic boundary condition
+solver for this investigation. In previous work, we identified that the
+length scale derived from the second moment of the structure factor is
+only useful for identifying length scale anisotropy. Therefore, we plot
+the directional second moment derived length scales and tortuosity in
+Figure \ref{fig:domain_size_aniso-field_on}.
 
@@
 \centering 
-    \includegraphics[scale = 0.5]{figures/results/paper2/interface_angle.png}
-    \caption{Plots of the average angle between the particle dipole moment and interface normal $(\psi)$ over time.
-While there are minor changes in for the oblate particles, these are not as significant as the ordering of particles to the field.}
-    \label{fig:P2_interface_angle}
+\includegraphics[scale=0.5]{../figures/results/paper2/domain_size_aniso-field_on.png} 
+\caption{Plotting the anisotropic domain size and tortuosities against the applied magnetic field strength on the left and right respectively for bijels stabilized with magnetically responsive oblate and prolate ellipsoids.
+We see that upon application of the field, bijels stabilized with prolate particles experience a domains ize increase in the direction parallel to the applied field direction, $L_{\parallel}$, while the domain size perpendicular to the applied field, $L_{\perp}$ decreases.
+The opposite is true for bijels stabilized with oblate particles.
+The tortuosity data demonstrate that as the domain size increases, the tortuosity decreases and vice versa.}
+\label{fig:domain_size_aniso-field_on} 
 \end{figure}
 
-To determine if the interface follows the orientation of the particles, the average angle between the particle symmetry axis and the interface normal $(\psi)$ was plotted against time rescaled by $t_{iso \rightarrow nematic}$ in Figure \ref{fig:P2_interface_angle}.
-From ths plot, it can be observed that upon application of the magnetic field, the particle tilts out of the interface at an equal normalized rate.
-However, the angle reached before the particles begin returning to their equilibrium configuration is magnetic field strength dependent, suggesting that the degree of microstructure changed observed might be dependent on how much the particle tilts away from its equilibrium position.
-At non-equilibrium particle tilts, there is more leeway for coarsening to occur before rejamming occurs, resulting in larger microstructural differences.
+From Figure \ref{fig:domain_size_aniso-field_on}, we see that domain
+size anisotropy is observed upon application of the field for both
+particle morphologies. We also see some domain anisotropy with no
+applied field, which increases upon application of the magnetic field.
+The directional domain sizes, \(L_{\perp}\) and \(L_{\parallel}\)
+increase by \(73\%\) and \(7\%\) respectively for oblate particles and
+\(10\%\) and \(44\%\) respectively for oblate particles. The axes that
+coarsens the most is consistent with past work, explained through the
+directions particles reorient in response to the applied magnetic field.
+As particles unjam and rejam at the interface due to reorientating to
+the magnetic field, they adopt direction specific surface coverages
+which manifest as anistropic domains upon jamming. In Figure
+\ref{fig:domain_size_aniso-field_on}, we demonstrate that the
+application of the magnetic field changes the domain size. The
+tortuosity of the bijel is initially around \(\tau \approx 1.5\),
+consistent with simulations of the diffusive tortuosities of gyroid
+structures using Lattice Boltzmann simulations.
+\cite{luo_macroscopic_2020} Upon application of the field,
+\(\tau_{\perp}\) slightly decreases while \(\tau_{\parallel}\)
+increases. We have seen that an increasing domain size decreases the
+tortuosity in our past work. \cite{karthikeyan_formation_2024} This
+observation is in line with the domain size changes observed in Figure
+\ref{fig:domain_size_aniso-field_on}. The results show that the
+tortuosity of the bijel is noticeably affected by the application of
+magnetic fields. This data suggests that magnetic fields applied onto
+bijels stabilized with ellipsoidal particles undergo domain anisotropy
+upon application of magnetic fields. However the particle morphology,
+specifically its axis of symmetry, affect the direction that the domain
+anisotropy is characterized.
 
-Future work will more closely examine the role of the particles in observed microstructure changes by calculating the average angle between the particle symmetry axis and the interface normal.
-In addition, the impact of initial order of the particle monolayer on the degree of microstructure change observed will be characterized.
-This will be accomplished by using bijels that have been simulated under magnetic fields and changing the applied field.
-Example conditions would be a bijel being simulated under a field strength of $\Bar{B} = 0.2$ and increasing the applied field to $\Bar{B} = 1$ or switching off the applied field.
-Based on the findings so far it is predicted that initial particle order and microstructure change are inversely correlated.
-Additionally, the timescales of these microstructure changes will be investigated.
-When switching a field on, there are magnetic field, steric and interfacial forces that govern the dynamics.
-However, when reducing the field strength, the magnetic field derived force isn't present, resulting in steric and interfacial forces playing a significant role.
-These differences can be examined by investigating the timescales the observed response occurs at, as well as the particle properties over time.
+Next, we turn to investigate the time gap between the average domain
+size increase and the nematic order parameter. We hypothesized that the
+time taken for particle reorientation to the field would control the
+degree and rate of domain size change when the bijel begins with
+particles with random order. This result suggests that the dynamics of
+the system at higher magnetic field strengths are dependent upon other
+factors that vary upon application of the magnetic field. To understand
+this phenomena, we focus on the dynamics of the particle monolayer.
+First, we visualize the particle monolayer of the bijels stabilized with
+prolate ellipsoids at the initial and final configuration before and
+after application of a magnetic field.
 
-% \textcolor{blue}{Still needs additional explanation of how using templates made under fields and decreasing and increasing field strengths will change results}
+\begin{figure} 
+\centering 
+\includegraphics[scale=0.4]{../figures/results/paper2/particle_viz-field_on.png} 
+\caption{Visualizations of bijels stabilized with oblate and prolate particles simulated at $t = 0$ (left column) and $t = 10^5$ (right column).
+The first and third rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids respectively with no applied field.
+The second and fourth rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids respectively with an applied field of $\bar{B}_z = 1$.
+Particle reorientation to the direction of the field can be seen, resulting in coarsening of the domains.}
+\label{fig:particle_viz-field_on} 
+\end{figure}
+
+In Figure \ref{fig:particle_viz-field_on}, we see the effect of the
+application of the magnetic field on the monolayer. The initial
+configuration of particles at the monolayer show that the orientations
+are random and that the particles tend to lie flat on the interface.
+However, upon application of the magnetic field the particles orient to
+the field direction. The effect that Gunther. et al.~observed for bijels
+stabilized with anisotropic particles can also be observed in these
+snapshots as the particles can be observed to have more local order in
+the final state than in the initial state with no applied field. We
+observe that for bijels stabilized by prolate ellipsoids, we see the
+adoption of more regular arrangements of the colloids on the interface.
+We investigate the effect of local particle ordering next. Past work by
+Bresme and Faraudo and Davies investigating the reorientation of
+particles at interfaces under magnetic fields have shown that a critical
+magnetic field exists, above which the particle orients to the field and
+below which the particle orientation is a function of the capillary
+force and magnetic field derived force. \cite{davies_interface_2014}
+\cite{bresme_orientational_2007} Particle adsorption into the interface
+with microparticles have also been shown to be irreversible due to the
+high adsorption energy. Upon particle reorientation, the microstructure
+change can be driven solely through particle unjamming and re-jamming,
+or it can be driven through the particles dragging the interface during
+this process. The mechanism of unjamming and re-jamming can be
+investigated using the average interfacial angle, \(\psi\).
+
+The interface angle of each particle is defined as
+\(\psi = \arccos{\frac{ \hat{\mathbf{o_i}}\cdot \hat{\mathbf{n_i}}}{|\hat{\mathbf{o_i}}| |\hat{\mathbf{n_i}}|}}\)
+where \(\hat{\mathbf{n_i}}\) is the normal of the interface closest to
+the center of the particle \(i\) and \(\hat{\mathbf{o_i}}\) is the
+orientation of particle \(i\) which follows the symmetry axis of the
+ellipsoid. For prolate particles, they prefer to lie flat on the
+interface, meaning that with no field \(\psi = 90^{\circ}\).
+\(\hat{\mathbf{n_i}}\) is calculated by first using the particle filling
+algorithm described and calculating the order parameter. Next, a mesh of
+the isocontour at \(\phi = 0\) is generated using the marching cubes
+algorithm in scikit-image with a box length of 4. \cite{van2014scikit}
+Next, the vertex closest to the center of particle \(i\) was found.
+\(\hat{\mathbf{n_i}}\) was then obtained from the normal corresponding
+to the vertex identified in the previous step.
+
+Another factor affected by the application of the magnetic field is the
+Steinhardt 6 fold order parameter, \(Q_6\), which characterized the
+local particle ordering. \cite{steinhardt_bond-orientational_1983} It
+has been used to characterize crystallization, glass transitions and
+crystal structures for colloidal and molecular crystals. We utilize the
+average across all particles on the interface, \(\langle Q_6 \rangle\)
+and track this parameter as a function of time. Past work has identified
+that local crystallization of colloidal crystals takes place at
+\(\langle Q_6 \rangle = 0.38\), and that
+\(\langle Q_6 \rangle^{HCP} = 0.485\).
+\cite{steinhardt_bond-orientational_1983} \cite{toxvaerd_role_2020}
+\cite{mickel_shortcomings_2013} We utilize a voronoi cell derived
+definition of the neighbor list of each particle, addressing some of the
+shortcomings highlighted in the original distance based definition.
+\cite{steinhardt_bond-orientational_1983}
+\cite{mickel_shortcomings_2013} We first define a complex orientational
+vector, \(q_{lm}\)
+
+\begin{equation}
+q_{lm}(i) = \frac{1}{N_b(i)} \Sigma_{j = 1}^{N_b(i)} Y_{lm}(\vec{R}_{ij})
+\end{equation}
+
+Where \(N_b\) is the number of nearest neighbors of particle \(i\),
+\(l\) is controls to the degree of spherical harmonic to be calculated,
+\(m\) is an integer defined as \(-l \leq m \leq l\) that defines which
+spherical harmonic is being calculated and \(\vec{r}_{ij}\) is the
+distance between two particle centers. The neighbor list \(N_b\) is
+usually defined by a cutoff distance from the center of particle \(i\)
+to its nearest neighbors \(j\). Steinhardt then defined a bond order
+parameter \(q_l\) from \(q_{lm}\) as
+
+\begin{equation}
+Q_{l}(i) = \sqrt{\frac{4 \pi}{2l + 1} \Sigma_{m = -l}^{l} |q_{lm}(i)|^2}
+\end{equation}
+
+\begin{figure} 
+\centering 
+\includegraphics[scale=0.5]{../figures/results/paper2/interface_angle-nint-field_on.png} 
+\caption{Plots of the interface angle $(\langle \psi \rangle)$ and six fold Steinhardt order parameter $(\langle Q_6 \rangle)$ on the left and right respectively, versus time for bijels stabilized with oblate and prolate ellipsoids on the top and bottom rows respectively.
+We demonstrate that upon application of a magnetic field, the behavior of $(\langle \psi \rangle)$ and $(\langle Q_6 \rangle)$ differ significantly between oblate and prolate ellipsoids indicating that the dynamics for both particle morphologies differ.
+We also observe magnetic field dependence in each property for both particle types, suggesting that these changes are driven primarily through the change in the applied field strength.}
+\label{fig:interface_angle-nint-field_on} 
+\end{figure}
+
+From Figure \ref{fig:interface_angle-nint-field_on}, we identify that
+prolate and oblate particles respond differently at the interface. For
+bijels stabilized by oblate ellipsoids, we characterize an increase in
+\(\langle \psi \rangle\) from an initial value of \(19 ^{\circ}\),
+before it reduces slightly and begins to increase once again. The
+initial starting value of \(\langle \psi \rangle\) indicates the
+particles are lying close to flat on the interface, before they begin to
+tilt out of the interface when the magnetic field is applied. Then,
+\(\langle \psi \rangle\) plateaus as the interface begins to move in
+response to the tilting particle at the interface. This is caused by the
+large adsorption energy of the particles at the interface of the bijel,
+caused by high surface tension. Finally, the particles jam in place,
+locking the interface at an angle to the particle. We see the rate of
+increase in \(\langle \psi \rangle\) at early stages and the time spent
+in the plateau increase with a larger applied magnetic field. The final
+angle at the interface is also dependent upon the applied field
+strength.
+
+When analyzing \(\langle \psi \rangle\) for bijels stabilized by prolate
+particles, this behavior can also be observed. \(\langle \psi \rangle\)
+begins at \(80 ^{circ}\). The difference in the initial
+\(\langle \psi \rangle\) compared to oblate particles is due to the
+direction of the axis of symmetry. In prolate particles, the axis of
+symmetry lies parallel with the interface and \(\langle \psi \rangle\)
+measures the angle between the interface normal and the orientation of
+the axis of symmetry. We see \(\langle \psi \rangle\) decrease slightly,
+before plateauing and slowly increasing again. The rate of decrease in
+\(\langle \psi \rangle\) is field dependent, although given the small
+decrease in \(\langle \psi \rangle\) it is unclear if the final value of
+this parameter is field dependent for bijels stabilized with prolate
+particles. The changes in \(\langle \psi \rangle\) for bijels stabilized
+with prolate particles are small compared to bijels stabilized with
+oblate particles. We believe this is due to local particle effects at
+the interface. We probe this by identifying the local particle ordering
+at the interface characterized by \(\langle Q_6 \rangle\).
+
+We see that for oblate particles, \(\langle Q_6 \rangle\) sees a
+decrease from its initial value. However the dynamics are controlled by
+the applied magnetic field strength. We split the phases of dynamics
+into three sections, similar to \(\langle \psi \rangle\) with the first
+section seeing a decrease in \(\langle Q_6 \rangle\) upon application of
+the magnetic field, followed by a plateau and finally a gradual increase
+before jamming takes place. These results indicate that the ordering of
+the particles is reduced by the applied magnetic field, before a
+restoration of some of the pre-existing order. The final values of
+\(\langle Q_6 \rangle\) are magnetic field dependent, with a stronger
+magnetic field having a lower final \(\langle Q_6 \rangle\) value
+indicating that either the ordering of particles influence the angle at
+the interface or vice versa. We observe that for bijels stabilized by
+oblate particles, the interface ordering of the particles increases as a
+function of the applied field strength. We also observe from plotting
+\(\langle Q_6 \rangle\) that application of a magnetic field creates a
+local crystallization of the colloid monolayer characterized as
+\(\langle Q_6 \rangle > 0.38\). \cite{toxvaerd_role_2020}
+
+Figure \ref{fig:domain_size-field_on}, we observed a gap between the
+growth of the nematic order parameter and an increase in the domain
+size. To probe why this occurs, we recast \(\langle \psi \rangle\),
+\(\langle Q_6 \rangle\) and \(S\) in terms of the physical phenomena
+they represent. The nematic order parameter represents the ordering of
+particles to an average direction, which in the case of the application
+of a magnetic field, is the field direction. Therefore, a timescale
+reliant on the nematic order parameter would represent a timescale of
+response rate limited to the response to the magnetic field, which
+indicates a particle-field orientation dependence. We name this
+timescale \(\tau_S\). When applying a field to a bijel system with a
+randomly oriented particle monolayer, the most significant transition
+point is the isotropic to nematic transition or when \(S \geq 0.3\). We
+define \(\tau_S\) for this section of the analysis by identifying when
+\(S \geq 0.3\).
+
+We can also do the same for \(\langle \psi \rangle\) and
+\(\langle Q_6 \rangle\). A timescale derived from
+\(\langle \psi \rangle\) named \(\tau_{\langle \psi \rangle}\)
+represents the capillary timescale between the interface and the
+particle. Given the shape of the plot, we assign the
+\(\tau_{\langle \psi \rangle}\) to be the time when the first minimum of
+\(\langle \psi \rangle\) is observed for prolate particles and the first
+maximum for oblate particles. A timescale derived from
+\(\langle Q_6 \rangle\), named \(\tau_{\langle Q_6 \rangle}\) is also
+calculated which represents a timescale of local particle rearrangement.
+We define \(\tau_{\langle Q_6 \rangle}\) as the time when
+\(\langle Q_6 \rangle \geq 0.38\) for prolate particles and the global
+minimum of \(\tau_{\langle Q_6 \rangle}\) for the oblate particles. We
+omit \(\bar{B} = 0\) as previous results have identified the domain size
+changes observed there. We then plot the average domain size \(L\)
+against time rescaled with these three timescales in Figure
+\ref{fig:domain_size-field_on-scaled}.
+
+\begin{figure} 
+\centering 
+\includegraphics[scale=0.35]{../figures/results/paper2/domain_size-field_on-scaled.png} 
+\caption{Plots of domain size with different timescales.
+The top and bottom row represent the average domain size for bijels stabilized with oblate and prolate particles respectively.
+The figures on the left plots the domain size against time rescaled with the nematic to isotropic transition time, $\tau_S$.
+The figures in the middle plot the domain size against time rescaled with the interfacial capillary timescale, $\tau_{\langle \psi \rangle}$.
+The figures on the right plot the domain size against time rescaled with the particle rearrangement timescale, $\tau_{\langle Q_6 \rangle}$.
+We show that the controlling timescale when applying a magnetic field onto bijels with disordered particles is the latter timescale, indicating that the dominating effect is steric hindrance of the particles during rearrangment at the interface.}
+\label{fig:domain_size-field_on-scaled} 
+\end{figure}
+
+In Figure \ref{fig:domain_size-field_on-scaled}, the left plot plots the
+average domain size against time rescaled using \(\tau_S\). We see that
+the domain sizes do not collapse onto a single line, which is expected
+if we want to explain the dynamics using the nematic order parameter.
+This confirms the observation made above that the dynamics do not only
+depend on the reorientation of particles to the field. The middle plot
+demonstrates the average domain size against time rescaled using
+\(\tau_{\langle \psi \rangle}\). We see that there is good agreement
+between all simulations for prolate particles, although the point when
+\(\frac{t}{\tau_{\langle \psi \rangle}} = 1\) lies when the domain size
+transition has started. However for oblate particles we see that this
+timescale does not describe the dynamics well.
+
+The right plot demonstrates the domain size change after rescaling time
+with \(\tau_{\langle Q_6 \rangle}\) where we see good collapse between
+all plots while the domain size transition also begins at
+\(\frac{t}{\tau_{\langle Q_6 \rangle}} = 1\). The latter point
+demonstrates that the dynamics for the structural response of randomly
+oriented particles are controlled by the local particle rearrangement at
+the interface rather than the orientation of the particle to the
+magnetic field.We see that before \(\tau_{\langle Q_6 \rangle} = 1\),
+\(\bar{B} = 0.2\) for the oblate particles does not collapse onto the
+other plots, indicating that the dynamics before that point are
+controlled by another phenomena.
+
+From the evidence in Figure \ref{fig:domain_size-field_on-scaled}, two
+types of interfacial behaviors are characterized in addition to that
+identified by Gunther et al.~\cite{gunther_timescales_2014} The first
+type is what is observed for \(\bar{B} = 0.2\), where the interfacial
+coverage and average orientation of the particle to the field and to the
+interface change in lock step. This causes the interface to reorient at
+the same rate as the particles reorienting to the magnetic field. The
+second is observed for \(\bar{B} = 0.5, 1\), where there is a time lag
+between particle ordering, and the intiation of domain coarsening. In
+the latter scenario, at early times the particles are jolted out of
+position before the large adsorption energy of the particles into the
+interface causes the interface to move to the particle position, causing
+domain coarsening as the interfacial area reduces.
+
+\subsection{Increasing the applied
+field}\label{increasing-the-applied-field}
+
+We saw in the hysteresis curve that the microstructure change at higher
+field strengths began to reduce with each subsequent field strength
+jump, suggesting that the ordering of the particles were linked to the
+domain size change observed. In the previous section, we saw that domain
+size changes in bijels after jamming are constrained by magnetic field
+driven local crystallization of the particle monolayer. In this section,
+we explore how pre-existing order in the particles affect the degree of
+domain size change observed. We apply fields of strength
+\(\bar{B}_{template} = 0, 0.2, 0.5, 1\) during phase separation to
+create bijels stabilized with ellipsoidal particles with pre-existing
+particle order. We then apply a field strength of \(\bar{B}_z = 1\) and
+observe the time evolution of the system for \(t = 10^5\) timesteps. We
+simplify our nomenclature here demonstrated with an example.
+\(\bar{B}_z: 0.0 \rightarrow 1.0\) represents a bijel made with no
+field, and a field of \(\bar{B}_z = 1.0\) applied after the structure
+has reached steady state. We begin by visualizing the microstructure
+changes experienced by bijels simulated with pre-existing particle order
+in Figure \ref{fig:microstructure_viz-field_up}.
+
+\begin{figure}
+\centering 
+\includegraphics[scale=0.4]{../figures/results/paper2/microstructure_viz-field_up.png} 
+\caption{Visualizations of bijels stabilized with oblate and prolate particles simulated at $t = 0$ (left column) and $t = 10^5$ (right column).
+The first and third rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids respectively with an applied field of $\bar{B}_z = 0.2$.
+The second and fourth rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids respectively with an applied field of $\bar{B}_z = 1$.
+We increase the applied field to $\bar{B}_z = 1$ in both cases and show that particle reorientation to the field occurs at the $\bar{B}_z = 0.2$ but not in the $\bar{B}_z = 1$ case.}
+\label{fig:microstructure_viz-field_up}
+\end{figure}
+
+In Figure \ref{fig:microstructure_viz-field_up} we show representative
+snapshots of a bijel stabilized with prolate particles at the initial
+and final timestep with field conditions
+\(\bar{B}_z: 0.2 \rightarrow 1.0\) and
+\(\bar{B}_z: 1.0 \rightarrow 1.0\) in the top and bottom rows
+respectively. We show that upon application of the field, the fluid
+domains undergo a field strength dependent microstructrue response, with
+the degree of response dependent upon the difference between the initial
+and final magnetic field. We also observe a qualitative increase in the
+alignment of the particles to the magnetic field for the
+\(\bar{B}_z: 0.2 \rightarrow 1.0\) case. We quantify these observations
+by plotting the average domain size and nematic order parameter in
+Figure \ref{fig:domain_size-field_up}.
+
+\begin{figure} 
+\centering 
+\includegraphics[scale=0.5]{../figures/results/paper2/domain_size-field_up.png} 
+\caption{Plot of the spherically averaged domain size normalized with $Rp(L/R)$ of the particle in markers and the nematic order parameter in lines.
+We show that the domain size change measured is correlated to the change in the particle ordering, characterized using the nematic order parameter.}
+\label{fig:domain_size-field_up} 
+\end{figure}
+
+In Figure \ref{fig:domain_size-field_up}, we define the difference
+between the final and initial magnetic field strengths as
+\(\Delta \bar{B}\). The onset of microstructural response is observed to
+be \(\Delta \bar{B}\)-dependent, indicating that a stronger driving
+force is required to induce structural reorganization. Additionally, the
+extent of microstructural change is also correlated with
+\(\Delta \bar{B}\), where \(\Delta \bar{B} = 1\) results in average
+microstructural variations of 5\% and 2\% for oblate and prolate
+particles, respectively which decreases as \(\Delta \bar{B}\) decreases.
+We further characterize the relationship between \(\Delta \bar{B}\) and
+nematic order, showing that an increase in \(S\) correlates with
+\(\Delta \bar{B}\). This suggests that changes in domain size are
+intrinsically linked to the initial particle ordering within the system.
+These findings indicate that characteristic length scale evolution is
+dependent on both aspect ratio and field strength variation,
+highlighting the role of particle alignment in governing domain
+coarsening dynamics. To further quantify the anisotropic microstructural
+evolution, we define the relative change in domain size as
+\(\Delta L = \frac{L_{f} - L_{i}}{L_{i}}\), where \(L\) represents
+either \(L_{\perp}\) or \(L_{\parallel}\). The same formulation is
+applied to the tortuosity in the respective directional components. We
+do this to characterize the \(\Delta \bar{B}\)-dependent changes
+observed in the domain anisotropy. The results are presented in Figure
+\ref{fig:domain_size_aniso-field_up}.
+
+\begin{figure} 
+\centering 
+\includegraphics[scale = 0.5]{../figures/results/paper2/domain_size_aniso-field_up.png} 
+\caption{Plotting the anisotropic domain sizes and tortuosity at the final timestep on the left and right respectively for bijels stabilized with oblate and prolate ellipsoidal particles starting at different particle orders.
+We plot these results against the change in the applied field strength, $\Delta B$.
+We show that the anisotropic domain size is inversely correlated to the tortuosity.
+We see that $L_{perp}$ changes for a bijel made with $\bar{B} = 1 \rightarrow 1$ and $\bar{B}: 0 \rightarrow 1$ differ, suggesting that the processing history of the bijel is important.}
+\label{fig:domain_size_aniso-field_up} 
+\end{figure}
+
+In Figure \ref{fig:domain_size_aniso-field_up}, we see that an increase
+in the directional domain size corresponds to a decrease in the
+tortuosity of the material. We also observe a magnetic field dependence
+of each parameter, demonstrating that the difference in the initial and
+final magnetic field applied is correlated with the domain size change
+observed. Another insight is that the runs \(\bar{B}: 0 \rightarrow 1\)
+and \(\bar{B}: 1 \rightarrow 1\) have different microstructural
+properties. This suggests that the processing history of a bijel is
+important when deciding what morphology functions ideally in a desired
+application. As in above, we turn to look at the properties of the
+particle monolayer. We begin by visualizing the particle monolayer in
+Figure \ref{fig:particle_viz-field_up}.
+
+From Figure \ref{fig:domain_size_aniso-field_up}, we see that domain
+size anisotropy is observed upon increasing the applied field
+application of the field for both particle morphologies. We also see
+some domain anisotropy with no applied field, which increases upon
+application of the magnetic field. The directional domain sizes,
+\(L_{\perp}\) and \(L_{\parallel}\) increase by \(73\%\) and \(7\%\)
+respectively for oblate particles and \(10\%\) and \(44\%\) respectively
+for prolate particles. The axes that coarsens the most is consistent
+with past work, explained through the directions particles reorient in
+response to the applied magnetic field. In Figure
+\ref{fig:domain_size_aniso-field_on}, we demonstrate that the
+application of the magnetic field changes the domain size. The
+tortuosity of the bijel is initially around \(\tau \approx 1.5\),
+consistent with simulations of the diffusive tortuosities of gyroid
+structures using Lattice Boltzmann simulations.
+\cite{luo_macroscopic_2020} Upon application of the field,
+\(\tau_{\perp}\) slightly decreases while \(\tau_{\parallel}\)
+increases. We have seen that an increasing domain size decreases the
+tortuosity in our past work. \cite{karthikeyan_formation_2024} This
+observation is in line with the domain size changes observed in Figure
+\ref{fig:domain_size_aniso-field_on}. The results show that the
+tortuosity of the bijel is noticeably affected by the application of
+magnetic fields.
+
+As particles unjam and rejam at the interface due to reorientating to
+the magnetic field, they adopt direction specific surface coverages
+which manifest as anistropic domains upon jamming. The direction of the
+anisotropy is different as the oblate particles have an axis of symmetry
+in the short axis of the radius, while for the prolate particles it is
+on the long axis. Thus during reorientation, the long axis of the oblate
+particles will be orthogonal to the applied field and parallel for the
+prolate particles. To characterize how the particle order changes on the
+interface as a function of the magnetic field strength, we visualize the
+particle monolayer of bijels stabilized by prolate particles in Figure
+\ref{fig:particle_viz-field_up}.
+
+\begin{figure} 
+\centering 
+\includegraphics[scale=0.4]{../figures/results/paper2/particle_viz-field_up.png} 
+\caption{Visualizations of bijels stabilized with oblate and prolate particles simulated at $t = 0$ (left column) and $t = 10^5$ (right column).
+The first and third rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids respectively with an applied field of $\bar{B}_z = 0.2$.
+The second and fourth rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids respectively with an applied field of $\bar{B}_z = 1$.
+We increase the applied field to $\bar{B}_z = 1$ in both cases and show that particle reorientation to the field occurs at the $\bar{B}_z = 0.2$ but not in the $\bar{B}_z = 1$ case.}
+\label{fig:particle_viz-field_up} 
+\end{figure}
+
+In Figure \ref{fig:particle_viz-field_up}, we see the effect of the
+application of the magnetic field on the monolayer. The initial
+configuration of particles at the monolayer show that even at initial
+configuration of run \(\bar{B}: 0.2 \rightarrow 1\), most particles are
+oriented towards the field. Upon increasing the field strength to
+\(\bar{B} = 1\), all particles shown can be seen to be ordered to the
+field, matching the results for the nematic order parameter shown in
+Figure \ref{fig:domain_size-field_up}. We also observe the alignment of
+the long axis of the particles to the magnetic field, demonstrating the
+origin of the microstructure anisotropy. To understand how the particle
+reorientation at the interface causes microstructure reorientation we
+quantify the average interface angle, \(\langle \psi \rangle\) and the
+local interface order of the material, \(\langle Q_6 \rangle\) in Figure
+\ref{fig:interface_angle-nint-field_up}.
+
+\begin{figure} 
+\centering 
+\includegraphics[scale=0.5]{../figures/results/paper2/interface_angle-nint-field_up.png} 
+\caption{Plots of the average interfacial angle $\psi$ and the number of particles on the interface $n_{int}$ on the left and right respectively, plotted against time for bijels stabilized with ellipsoidal particles with aspect ratio 2.
+When looking at $\psi$, a change in dynamics can be seen as the initial particle order increases.
+When looking at $n_{int}$, different dynamics are seen above and below the isotropic to nematic transition point.
+Both results suggest that the ordering of particles is linked to the dynamics of domain coarsening.}
+\label{fig:interface_angle-nint-field_up} 
+\end{figure}
+
+From Figure \ref{fig:interface_angle-nint-field_up}, we identify that
+prolate and oblate particles respond differently at the interface. We
+show that there are three time evolution trends for
+\(\langle \psi \rangle\) and \(\langle Q_6 \rangle\) for both oblate and
+prolate particles despite the differences in the initial state of the
+particles. In oblate particles \(\langle \psi \rangle\) begins closer to
+\(0 ^{\circ}\) as the axis of symmetry lies close to the interface
+normal. We see that for bijels experiencing a field strength history of
+\(\bar{B}: 0 \rightarrow 1\) and \(\bar{B}: 0.2 \rightarrow 1\),
+\(\langle \psi \rangle\) increases, plateaus and increases again before
+plateauing again. This is indicative of particles tilting at the
+interface, before interfacial capillary interactions ``pause'' particle
+reorientation before the applied magnetic field begins to cause
+particles to tilt out of the interface. We see similar trends for bijels
+stabilized by prolate particles. \(\langle \psi \rangle\) begins near
+\(80 ^{\circ}\). We see a decrease before reorientation ceases, and
+finally \(\langle \psi \rangle\) increases again.
+
+When looking at \(\langle Q_6 \rangle\) for \(\bar{B}: 0 \rightarrow 1\)
+and \(\bar{B}: 0.2 \rightarrow 1\) for oblate particles, we see that the
+trends are similar with an initial decrease, followed by a plateau and
+increase over time before plateauing again. \(\langle Q_6 \rangle\)
+generally decreases with a large decrease observed for
+\(\bar{B}: 0 \rightarrow 1\) from an initial hexagonally packed system
+to a structure that is locally ordered but not close packed. For prolate
+particles, we see an increase in \(\langle Q_6 \rangle\) with a plateau
+occurring in both systems around 5000 timesteps. The significance of
+this time is unknown for \(\bar{B}: 0.2 \rightarrow 1\) but for
+\(\bar{B}: 1 \rightarrow 1\), this is approximately the local
+crystallization point when \(\langle Q_6 \rangle \geq 0.38\).
+
+For oblate particles, we can conclude that structural response dynamics
+arise from particle tilting on the interface identified as the large
+difference between the initial and final \(\langle \psi \rangle\) with
+an associated decrease in the interface coverage, initiating domain
+coarsening. We see that this interfacial tilting causes a loss in the
+close packing of oblate particles at the interface. For prolate
+particles, we observe a small degree of particle tilting as can be seen
+from \(\langle \psi \rangle\), although the dynamics are primarily
+driven by the change in \(\langle Q_6 \rangle\), indicated as a slight
+dip and plateau before the particles begin reordering and packing more
+tightly, decreasing the interfacial area. Larger domain size response is
+observed for the prolate particles as the interfacial area change from
+particle tilting at the interface is larger than that of particles close
+packing at the interface.
+
+For both particle morphologies we analyze the response of bijels with a
+field history of \(\bar{B}: 0.5 \rightarrow 1\) and
+\(\bar{B}: 1 \rightarrow 1\). We see a decrease in
+\(\langle Q_6 \rangle\) for bijels stabilized with oblate particles with
+field application of \(\bar{B}: 0.5 \rightarrow 1\) compared to an
+increase for \(\bar{B}: 1 \rightarrow 1\). This behavior arises from the
+slight increase in the nematic order for particles in bijels
+experiencing the \(\bar{B}: 0.5 \rightarrow 1\) field application
+history. The \(\langle \psi \rangle\) results indicate that the
+particles rearrange over time to lie flatter on the interface. For
+bijels stabilized with prolate particles, we characterize a difference
+in behavior between \(\bar{B}: 0.5 \rightarrow 1\) and
+\(\bar{B}: 1 \rightarrow 1\). For the \(\bar{B}: 0.5 \rightarrow 1\)
+case, we see a slight increase in \(\langle \psi \rangle\) before a
+decrease and increase compared to the \(\bar{B}: 1 \rightarrow 1\) case
+where we characterize a slight decrease over time. We also characterize
+a slight decrease in \(\langle Q_6 \rangle\) over time for the
+\(\bar{B}: 1 \rightarrow 1\) case while characterizing a larger decrease
+for the \(\bar{B}: 0.5 \rightarrow 1\) case. Similar to the oblate
+particles, these results originate from the slight increase in the
+nematic order for bijels experiencing the \(\bar{B}: 0.5 \rightarrow 1\)
+field history.
+
+\subsection{Decreasing the applied
+field}\label{decreasing-the-applied-field}
+
+Bijels are kinetically stable structures whose properties are dependent
+upon the stability of the particle monolayer. Past work into responsive
+emulsions have demonstrated resilience to microstructure changes after
+application and removal of stimuli even after several months. However,
+in the systems simulated above the particles need not necessarily be in
+thermodynamically stable states when jammed upon removal of stimuli as
+the particles take up a arrangements not observed when no field is
+applied. In this section, we explore how removal of the magnetic field
+changes the microstructure of the bijel as a function of the initial
+particle order. We use bijels simulated under
+\(\bar{B}_{template} = 0, 0.2, 0.5, 1\) during phase separation. Once
+the microstructure has stabilized, we switch off the magnetic field and
+observe the time evolution of the system for \(t = 10^5\) timesteps.
+
+\begin{figure} 
+\centering 
+\includegraphics[scale=0.4]{../figures/results/paper2/microstructure_viz-field_down.png} 
+\caption{Visualizations of bijels stabilized with oblate and prolate particles simulated at $t = 0$ (left column) and $t = 10^5$ (right column).
+The first and third rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids respectively with an applied field of $\bar{B}_z = 0.2$.
+The second and fourth rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids respectively with an applied field of $\bar{B}_z = 1$.
+We switch off the applied field in both cases and show that while particle reorientation occurs, it has little effect on the microstructure of the bijel.}
+\label{fig:microstructure_viz-field_down}
+\end{figure}
+
+In Figure \ref{fig:microstructure_viz-field_down}, we visualize the time
+evolution of the microstructure of bijels with processing history
+\(\bar{B}:0.2 \rightarrow 0\) (top) and \(\bar{B}:1 \rightarrow 0\)
+(bottom). We see that when switching the field off, the microstructure
+remains largely the same, demonstrating the kinetic stability of bijels.
+However, the particle monolayer, while still showing order, appears to
+be slowly losing that order as particles are beginning to become
+randomly oriented. This is especially obvious in the
+\(\bar{B}:1 \rightarrow 0\) process, demonstrating that the dynamics of
+the system is dependent upon the initial order of the particle
+monolayer.
+
+\begin{figure} 
+\centering 
+\includegraphics[scale=0.5]{../figures/results/paper2/domain_size-field_down.png} 
+\caption{Plot of the spherically averaged domain size normalized with $R_p$ of the particle and the nematic order parameter of each bijel over time.
+Each color represents bijel templates made with different field strengths $\bar{B}$.
+We show that there is domain coarsening when the field is switched off, along with a reduction in the ordering of the particles.}
+\label{fig:domain_size-field_down} 
+\end{figure}
+
+From the results in \ref{fig:domain_size-field_down}, we can see that
+the results show, with the exception of \(\bar{B}: 0\rightarrow 0\), all
+domain sizes show a slow coarsening over time. This is reflected clearly
+in the bijels stabilized by prolate particles, showing that that the
+changes in properties of the particle monolayer due to the applied
+magnetic field during bijel template simulation does not play a
+significant role in the dynamics of the bijel. We attribute the large
+increase in the domain size in oblate particle stabilized
+\(\bar{B}: 0\rightarrow 0\) case to be due to coalescence of two
+domains, characterized as a two step process where we see slower long
+timescale domain coarsening initially followed by a rapid jump in the
+domain size.
+
+The nematic order parameter of all runs with prexisting particle order
+show order dependent decreases, arising from interfacial forces causing
+the particles to return to a thermodynamically optimum configuration on
+the interface. To quantify is the coarsening that takes place is
+anisotropic, we define the relative change in domain size as
+\(\Delta L = \frac{L_{f} - L_{i}}{L_{i}}\), where \(L\) represents
+either \(L_{\perp}\) or \(L_{\parallel}\). The same formulation is
+applied to the tortuosity in the respective directional components. We
+do this to characterize the \(\Delta \bar{B}\)-dependent changes
+observed in the domain anisotropy. The results are presented in Figure
+\ref{fig:domain_size_aniso-field_up}.
+
+\begin{figure} 
+\centering 
+\includegraphics[scale = 0.5]{../figures/results/paper2/domain_size_aniso-field_down.png} 
+\caption{Plotting the anisotropic domain sizes and tortuosity at the final timestep on the left and right respectively for bijels stabilized with oblate and prolate ellipsoidal particles starting at different particle orders.
+We plot these results against the change in the applied field strength, $\Delta B$.
+We show that there are only minor differences in the microstructure of stimuli responsive bijels once the magnetic field is switched off.}
+\label{fig:domain_size_aniso-field_down} 
+\end{figure}
+
+In Figure \ref{fig:domain_size_aniso-field_down}, we see that there are
+small \(\Delta \bar{B}\) dependent changes in the anisotropic domain
+size and tortuosity for both particle morphologies. However, there are
+no clear trends that can be developed from these plots, suggesting that
+the changes are overall isotropic and any differences observed arise
+from the arrangement of particles. This suggests that the response of
+the material to the removal of a magnetic field is isotropic and only
+dependent upon the capillary interactions with the particle monolayer.
+We showed earlier that the application of magnetic fields change the
+local state of the particles at the interface. However the results shown
+thus far demonstrate that that these changes do not seem to affect the
+coarsening of the bijel once stimuli is removed. To investigate why this
+is the case, we plot \(\langle \psi \rangle\) and
+\(\langle Q_6 \rangle\) for bijels stabilized with ellipsoidal particles
+below.
+
+\begin{figure} 
+\centering 
+\includegraphics[scale=0.5]{../figures/results/paper2/interface_angle-nint-field_down.png} 
+\caption{Plots of the average interfacial angle $\psi$ and the number of particles on the interface $n_{int}$ on the left and right respectively, plotted against time for bijels stabilized with ellipsoidal particles with aspect ratio 2.
+When looking at $\psi$, the $\bar{B}:1 \rightarrow 1$ case looks distinctly different from the other processes.
+At $\bar{B} = 1$, the particles are totally ordered to the field.
+This suggests that the presence of some particle disorder resists domain coarsening.}
+\label{fig:interface_angle-field_down} 
+\end{figure}
+
+In Figure \ref{fig:interface_angle-field_down}, we plot
+\(\langle \psi \rangle\) and \(\langle Q_6 \rangle\) in the left and
+right columns respectively. While there are minor differences to the
+time when \(\langle \psi \rangle\) and \(\langle Q_6 \rangle\) increase
+and decrease respectively for bijels stabilized by oblate particles the
+trends are identical. This suggests that the differences in particle
+angle, local ordering and nematic order only change when coarsening will
+take place without affecting its dynamics.
+
+For prolate particles, we see that a reduction in
+\(\langle \psi \rangle\) takes place for all runs except for
+\(\bar{B}: 0.5\rightarrow 0\). This is attributed to be due to this
+system being near its preferred interface angle, with changes occurring
+as the particles reorient away from the magnetic field causing
+deviations before returning to that angle. We see that the
+\(\bar{B}: 1\rightarrow 0\) case also reaches approximately the same
+value for \(\langle \psi \rangle\). \(\bar{B}: 0.2\rightarrow 0\) and
+\(\bar{B}: 0\rightarrow 0\) reduce much more slowly than
+\(\bar{B}: 1\rightarrow 0\). This suggests that local reorientation is
+occurring, although its affects manifest as insignificant changes in the
+microstructure of the material.
+
+Looking at \(\langle Q_6 \rangle\), we see that all simulations see a
+decrease over time. We see that contrary to previous trends, the
+\(\bar{B}: 1\rightarrow 0\) simulation has a smaller change in
+\(\langle Q_6 \rangle\) than \(\bar{B}: 0.5\rightarrow 0\) although this
+difference is also a result of the initial particle orientation and
+position, rather than a defining feature of a broader trend. We see that
+the \(\bar{B}: 0.5\rightarrow 0\) case is near the
+\(Q_6^{HCP} \approx 0.485\) boundary, suggesting it is most susceptible
+to lose short range order upon removal of the magnetic field that
+enforces it, resulting in the large decrease in \(\langle Q_6 \rangle\)
+observed.
+
+We see from the microstructure evolution that steric effects are the
+driving force behind microstructure changes in the absence of a magnetic
+field. Even though we observe that the interface angle and Steinhardt
+order parameter show substantial changes from the scenario where no
+field is applied, these are insufficient to change the average steric
+effect driven particle monolayer rearrangement observed, causing
+coarsening of the bijel at long timescales similar what was observed by
+Gunther et al.~\cite{gunther_timescales_2014}

### 2025-03-05 chapters/introduction.tex
Changes 1. Reworded introduction and lit review and addressed grammar and vocab issues 2. Fixed some referencing problems in the document 3. Fleshed out introduction in paper 2 4. Added sections for results in paper 3

@@
 
-Porous materials are defined as materials that contain pores or voids within their structure where no material is present. 
-Homogeneous materials in contrast have a uniform structure with no pores. These pores vary in shape and distribution, with materials 
-being categorized by pore size per IUPAC as $(L)$ as microporous $(L < 2nm)$, mesoporous $(2nm < L < 50nm)$ and macroporous materials 
-$(50nm < L)$. \cite{sing_reporting_1985} The presence of these pores increases the surface area to volume 
-ratio of porous materials compared to their homogeneous counterparts. A common experimental technique used to estimate the surface area 
-of a porous material derived from Brunauer-Emmett-Teller(BET) theory shows that porous materials can have surface areas more than a 
-hundred times larger than homogenous materials, dependent upon the pore size and pore size distribution. \cite{shimizu_surface_2022}
+Porous materials are characterized by the presence of pores or voids within their structure, where no solid material is present. 
+In contrast, homogeneous materials exhibit a uniform structure devoid of pores. The shape and distribution of these pores can vary, 
+and according to the IUPAC classification, materials are categorized based on pore size as microporous ($L < 2$ nm), 
+mesoporous ($2 < L < 50$ nm), or macroporous ($L > 50$ nm) \cite{sing_reporting_1985}. The presence of pores significantly 
+increases the surface area-to-volume ratio of porous materials compared to their homogeneous counterparts. A commonly used experimental 
+technique for estimating the surface area of porous materials, based on Brunauer-Emmett-Teller (BET) theory, has demonstrated that such 
+materials can exhibit surface areas more than a hundred times greater than those of homogeneous materials, depending on pore size and pore 
+size distribution \cite{shimizu_surface_2022}.
 
-In addition to the pore size and its distribution within the material, the arrangement of pores within the material contribute to the 
-performance of the synthesized material, commonly measured using the tortuosity. Tortuosity here is defined as the path length between 
-two points divided by the euclidean length between those points. A tortuosity larger than one implies that the path length is longer 
-than the euclidean length, and vice versa if the tortuosity if less than one. Highlighting the confluence of these factors are the 
-large variety of tailored microstructures for various applications. Each of the specified pore length scales have their unique uses, 
-such as microporous materials being used as zeolites and photonic bandgap materials while macroporous materials facilitate greater 
-transport properties, suitable in applications such as battery electrodes and drug delivery systems. \cite{chen_tortuosity_2020, 
-ebner_tortuosity_2014} This increased surface area to volume ratio enhances the properties of the base material in applications such 
-as catalysis, battery electrodes and drug delivery systems among many more making them valuable microstructures. 
-\cite{cha_bicontinuous_2019, samdani_bicontinuous_2017, thorson_bijel-templated_2019, zhao_highly_2014}
+In addition to pore size and its distribution, the spatial arrangement of pores within a material significantly influences its performance, 
+often quantified by tortuosity. Tortuosity is defined as the ratio of the actual path length between two points to the Euclidean distance 
+between them. A tortuosity greater than one indicates that the path length is longer than the Euclidean distance, whereas a tortuosity less 
+than one suggests a more direct pathway. The interplay of these factors has led to the development of a wide range of tailored microstructures 
+for diverse applications. Each pore size regime serves distinct functions; for example, microporous materials are commonly used in zeolites and 
+photonic bandgap materials, while macroporous materials enhance transport properties, making them suitable for applications such as battery 
+electrodes and drug delivery systems \cite{chen_tortuosity_2020, ebner_tortuosity_2014}. The increased surface area-to-volume ratio of porous 
+materials further enhances the properties of the base material in various applications, including catalysis, energy storage, and biomedical 
+systems, making them important microstructures. \cite{cha_bicontinuous_2019, samdani_bicontinuous_2017, thorson_bijel-templated_2019, zhao_highly_2014}.
 
@@
 
-Conventionally, porous materials have been synthesized through solvothermal synthesis or pyrolysis used in the synthesis of zeolites and 
-activated carbon respectively. With more targeted applications of porous materials, synthesis techniques such as sol-gel synthesis, 
-freeze drying and various forms of templating have been utilized to synthesize porous materials from length scales of $10^{-9}m$ to 
-$10^{-3}m$. \cite{stein_morphological_2008, ray_comprehensive_2016, cervellere_mesoscopic_2019, garcia-bennett_unique_2020, zhang_emulsion_2019, 
-alves-rosa_design_2013} Industry has also taken up techniques such as electrospinning to generate non woven fibers, used in membrane synthesis. 
-Templating techniques in particular offer access to various pore length scales, bottom up synthesis and functionality through leveraging various 
-physical phenomena. Colloidal templating works through the close packing of particles. Surfactant and polymer templating work through the 
-assembly of macromolecules into their equilibrium configurations. Emulsion templating utilizes the phase separation of partially miscible 
-liquids to form the pore structure of a porous material.
+Conventionally, porous materials have been synthesized through methods such as solvothermal synthesis and pyrolysis, which are commonly 
+used for producing zeolites and activated carbon, respectively. With the increasing demand for tailored porous materials, advanced synthesis 
+techniques—including sol-gel synthesis, freeze-drying, and various templating methods—have been developed to fabricate porous structures across 
+length scales ranging from $10^{-9}$ m to $10^{-3}$ m 
+\cite{stein_morphological_2008, ray_comprehensive_2016, cervellere_mesoscopic_2019, garcia-bennett_unique_2020, zhang_emulsion_2019, alves-rosa_design_2013}. 
+Industry has also adopted techniques such as electro-spinning to produce nonwoven fibers, which are widely used in membrane synthesis.  
+Among these approaches, templating techniques provide precise control over pore size, enable bottom-up synthesis, and introduce functionality by 
+leveraging various physical phenomena. Colloidal templating relies on the close packing of particles to define pore structures. Surfactant and 
+polymer templating utilize the self-assembly of macromolecules into their equilibrium configurations to generate porous networks. Emulsion templating, 
+on the other hand, exploits the phase separation of partially miscible liquids to form the pore architecture of the resulting material.
 
-Emulsion templating offers access to a large length scale of tunable pore sizes, continuous production through microfluidic junctions or 
-other flow media, functionalization through the addition of additives or stabilizers, scope of accessible microstructures and mild synthesis 
-conditions. It can further be extended to include heirarchical porosity, further enhancing its utility and fabricated material properties. 
-\cite{yang_hierarchically_2017, thompson_hierarchically_2019, wang_morphology_2023} Figure \ref{fig:bijel_template} demonstrates how emulsion 
-templating allows bottom up synthesis of hierarchically porous materials, although other examples do exist. 
-\cite{garcia_scalable_2019, santiago_cordoba_aerobijels_2020, thorson_bijel-templated_2019, lu_controllable_2020, wang_morphology_2023}
+Emulsion templating enables the fabrication of porous materials with a wide range of tunable pore sizes, continuous production through microfluidic 
+junctions or other flow-based systems, and functionalization through the incorporation of additives or stabilizers. This technique also offers a broad 
+scope of accessible microstructures and benefits from mild synthesis conditions. Additionally, it can be extended to generate hierarchical porosity, 
+further enhancing the functionality and properties of the resulting materials \cite{yang_hierarchically_2017, thompson_hierarchically_2019, wang_morphology_2023}.  
+Figure \ref{fig:bijel_template} illustrates how emulsion templating enables the bottom-up synthesis of hierarchically porous materials, although various 
+alternative approaches also exist 
+\cite{garcia_scalable_2019, santiago_cordoba_aerobijels_2020, thorson_bijel-templated_2019, lu_controllable_2020, wang_morphology_2023}.
 
@@
 
-One such emulsion microstructure of interest is the bicontinuous interfacially jammed emulsion gel(bijel). 
-\cite{stratford_colloidal_2005, herzig_bicontinuous_2007, lee_bicontinuous_2010} Bijels are made by arresting the spinodal decomposition of 
-partially miscible liquids, caused by particles adsorbing on the interface and jamming as the cross sectional area of the particles match that 
-of the interface, summarized in Figure \ref{fig:bijel_coarsen}. Bijels are of interest due to their co-continuous, tortuous microstructure which 
-represent excellent fits for several porous material applications.
+One particularly interesting emulsion-derived microstructure is the bicontinuous interfacially jammed emulsion gel (bijel) 
+\cite{stratford_colloidal_2005, herzig_bicontinuous_2007, lee_bicontinuous_2010}. Bijels are formed by arresting the spinodal decomposition of partially 
+miscible liquids, a process driven by the adsorption of colloidal particles at the interface. As the interfacial area contracts, the particles become 
+jammed, stabilizing the bicontinuous structure, as summarized in Figure \ref{fig:bijel_coarsen}. The resulting co-continuous and tortuous microstructure 
+of bijels makes them highly suitable for various porous material applications.
 
-Bijels were discovered in simulations in 2005 and experimentally realized in 2007 when a mixture of water and 2-6-lutidine mixed with 
-surface modified silica nanoparticles underwent thermally induced spinodal decomposition. \cite{stratford_colloidal_2005, herzig_bicontinuous_2007}
-Since then, multiple other casting mixtures and particle chemistry's have been used to fabricate bijels using Thermally Induced Spinodal 
-Decomposition (TIPS). \cite{lee_bicontinuous_2010, bai_dynamics_2015} More recently, techniques such as Solvent Transfer Induced Phase 
-Separation (STrIPS), Vapor Induced Phase Separation (VIPS), Non-solvent Induced Phase Separation (NIPS), homogenization and liquid in 
-liquid printing have been utilized to fabricate bijels, demonstrating the ability for bijels to be synthesized in a continuous process, 
-suitable for scale up. \cite{haase_continuous_2015, wang_scalable_2020, cai_bijels_2017, yabuno_preparation_2020, wang_bicontinuous_2023, 
-amirfattahi_fabrication_2024} These techniques also offer preparation of bijels in various different shapes and form-factors for various 
-uses such as fibers, coatings and capsules, seen in Figure \ref{fig:strips}. \cite{haase_continuous_2015, boakye-ansah_controlling_2020, 
-kharal_hightensile_2020, wang_bicontinuous_2023}
+Bijels were first predicted in simulations in 2005 and experimentally realized in 2007 when a mixture of water and 2,6-lutidine, combined with 
+surface-modified silica nanoparticles, underwent thermally induced spinodal decomposition \cite{stratford_colloidal_2005, herzig_bicontinuous_2007}. 
+Since then, various casting mixtures and particle chemistries have been explored to fabricate bijels using thermally induced spinodal decomposition (TIPS) 
+\cite{lee_bicontinuous_2010, bai_dynamics_2015}. More recently, alternative fabrication techniques such as solvent transfer-induced phase separation (STrIPS), 
+vapor-induced phase separation (VIPS), non-solvent-induced phase separation (NIPS), homogenization, and liquid-in-liquid printing have been developed. 
+These methods enable the continuous synthesis of bijels, making them more suitable for large-scale production 
+\cite{haase_continuous_2015, wang_scalable_2020, cai_bijels_2017, yabuno_preparation_2020, wang_bicontinuous_2023, amirfattahi_fabrication_2024}. 
+Additionally, these techniques allow for the fabrication of bijels in various shapes and form factors, including fibers, coatings, and capsules, expanding 
+their applicability across different fields, as illustrated in Figure \ref{fig:strips} 
+\cite{haase_continuous_2015, boakye-ansah_controlling_2020, kharal_hightensile_2020, wang_bicontinuous_2023}.
+
 \begin{figure}[h]
@@
 
-However, these techniques all depend upon controlling the rate of phase separation, which involve changing the casting mixture composition to 
-modify the obtained microstructure. In STrIPS, the obtained bijel microstructure is a function of the flow rate and selected co-solvent, 
-selected to change the rate of phase separation. \cite{haase_continuous_2015} This affects material properties such as the mechanical 
-performance of the bijel, important in fields such as catalysis where rigidity of the particle monolayer is crucial in ensuring consistent 
-performance. \cite{reeves_particle-size_2015, haase_situ_2016, boakye-ansah_controlling_2020} Identification of other techniques that can 
-be utilized to modify the microstructure of a bijel would enable bijels to continue using the desired composition of constituents, while 
-also adding other unique properties. Stimuli response offers one such road to microstructure modification.
+However, all of these techniques rely on precisely controlling the rate of phase separation, which typically involves adjusting the composition 
+of the casting mixture to modify the resulting microstructure. In STrIPS, for example, the bijel microstructure is influenced by both the flow rate 
+and the choice of co-solvent, which are selected to regulate the phase separation dynamics \cite{haase_continuous_2015}. These factors directly 
+impact material properties such as the mechanical stability of the bijel, which is particularly important in applications like catalysis, where the 
+rigidity of the particle monolayer is essential for maintaining consistent performance 
+\cite{reeves_particle-size_2015, haase_situ_2016, boakye-ansah_controlling_2020}. Identifying alternative techniques for modifying the microstructure of 
+bijels would allow for greater tunability while maintaining the desired composition of the constituent materials. One promising approach for achieving 
+such control is the use of stimuli-responsive mechanisms.
 
@@
 
-Stimuli response based on pH, external fields and temperature have been used in past works when looking at modifying the microstructure of 
-emulsion droplets for enhanced oil recovery, pharmaceutical and cell adhesion. \cite{haase_nanoparticle_2011, tham_magnetophoresis_2021, 
-cui_stabilizing_2013, manfredini_limonene--water_2021}  It was shown that external fields can be used to move, control emulsion stability 
-and elongate emulsion droplets. \cite{tham_magnetophoresis_2021, cui_stabilizing_2013, melle_pickering_2005} Bijels stabilized spherical 
-particles under a magnetic field showed no meaningful microstructure changes. \cite{kim_bijels_2010} Bijels stabilized with spherical 
-particles under an electric field showed more promise. \cite{carmack_tuning_2018} However, magnetic fields offer targeted stimuli 
-response, allowing even weak fields to incite a response. Magnetic fields non-interaction in many situations offer advantages to many of 
-the desired uses of bijels within pharmaceutical or bioengineering applications. \cite{vanoli_bijels_2022, thorson_bijel-templated_2019, thorson_composite_2018} 
-These applications can also take advantage of in-situ microstructure modification that would enable tunable drug delivery rates, separations or
-catalyst efficiency and permeability improvements in the system. Therefore, identifying schemes that allow modification of the pore size 
-and tortuosity without synthesis of a new material would enhance the use case of bijels.
+Stimuli-responsive mechanisms based on pH, external fields, and temperature have been explored in previous studies to modify the microstructure of emulsion 
+droplets for applications such as enhanced oil recovery, pharmaceuticals, and cell adhesion 
+\cite{haase_nanoparticle_2011, tham_magnetophoresis_2021, cui_stabilizing_2013, manfredini_limonene--water_2021}. External fields have been shown to 
+manipulate emulsion stability, control droplet movement, and induce elongation in emulsion droplets 
+\cite{tham_magnetophoresis_2021, cui_stabilizing_2013, melle_pickering_2005}.  
+In the case of bijels, spherical particle-stabilized systems subjected to a magnetic field exhibited no significant microstructural changes 
+\cite{kim_bijels_2010}. However, bijels stabilized with spherical particles under an electric field demonstrated greater potential for microstructure 
+modification \cite{carmack_tuning_2018}. Despite this, magnetic fields present a promising avenue for targeted stimuli-responsive behavior, as even 
+weak fields can induce a response while remaining non-invasive in many contexts. This property is particularly advantageous for pharmaceutical and 
+bioengineering applications, where external control over material properties is desirable 
+\cite{vanoli_bijels_2022, thorson_bijel-templated_2019, thorson_composite_2018}.  
+Such applications could benefit from in-situ microstructural modifications, enabling tunable drug delivery rates, improved separations, and enhanced catalyst 
+efficiency and permeability. Therefore, developing strategies to modify pore size and tortuosity without requiring the synthesis of a new material would 
+significantly expand the functional versatility of bijels.
 
-Anisotropic particles at interfaces have shown self assembly due to the presence of multi-polar pressure fields caused by interface deformation. 
-Self assembly has also been shown for ellipsoidal particles at interfaces under magnetic fields. Ellipsoidal particles have also been shown to 
-exhibit magnetic field controlled orientations at interfaces, as Bresme and Faraudo showed. \cite{bresme_orientational_2007, davies_interface_2014}
-Under magnetic fields, assemblies of multiple ellipsoidal particles have been shown to have energy minima at orientations different from isolated particles,
-meaning that the interface coverage of interfaces decorated with ellipsoidal particles can be varied using stimuli response. 
-\cite{newton_influence_2014, newton_capillary_2018} Thus ellipsoidal particles at interfaces, whose orientations and packing can be 
-controlled through external fields, offer a potential means to control the microstructure of bijels.
+Anisotropic particles at interfaces have been shown to undergo self-assembly due to the presence of multipolar pressure fields induced by interface 
+deformation. Similarly, self-assembly has been observed for ellipsoidal particles at interfaces under magnetic fields. Additionally, ellipsoidal particles 
+exhibit magnetic field-controlled orientation at interfaces, as demonstrated by Bresme and Faraudo \cite{bresme_orientational_2007, davies_interface_2014}.  
+When subjected to a magnetic field, assemblies of multiple ellipsoidal particles exhibit energy minima at orientations different from those of isolated 
+particles. This suggests that the interfacial coverage of surfaces decorated with ellipsoidal particles can be dynamically tuned using external 
+stimuli \cite{newton_influence_2014, newton_capillary_2018}. Therefore, ellipsoidal particles at interfaces—whose orientation and packing can be externally 
+controlled—present a promising strategy for tailoring the microstructure of bijels.
 
-Bijels present a bottom up synthesis strategy for porous material templates for hard and soft material applications in a scalable and 
-continuous method using STrIPS and other techniques. However, the microstructure control these techniques offer are intrinsically linked 
-to the casting mixture composition. Stimuli response offers a way to modify the microstructure of bijels while still maintaining the 
-various form factors these continuous synthesis techniques can output. Magnetic stimuli response has been explored in the past using bijels 
-stabilized with spherical particles with little success. \cite{kim_bijels_2010}
+Bijels offer a bottom-up synthesis approach for porous material templates, enabling scalable and continuous fabrication for both hard and soft material 
+applications through STrIPS and related techniques. However, the degree of microstructural control provided by these methods is inherently dependent on 
+the composition of the casting mixture. Stimuli-responsive strategies present a means to modify the microstructure of bijels while preserving the 
+diverse form factors achievable through continuous synthesis techniques. Previous attempts to induce magnetic stimuli response in bijels stabilized 
+with spherical particles have shown limited success \cite{kim_bijels_2010}.
 
-With this background, we propose anisotropic particles as a technique to enable microstructure modification of bijels 
-upon application of an external field during and after fabrication. This work seeks to identify means to control the bijel microstructure independent 
-of the casting mixture composition by utilizing magnetic stimuli on bijels stabilized with magnetically responsive ellipsoidal particles. 
-The proposed mechanism of microstructure modification is driven through reorientation of the particles to the applied magnetic field altering 
-how the particles pack on the interface. By changing the interfacial packing of the particles, we change when the particles jam, which in turn changes 
-the jamming point of the bijel. This mechanism is predicted to be effective during and after synthesis. The processability of bijels fabricated using 
-this technique will also be investigated to ascertain how changes in particle packing affect the rheology of the material. An overview of three major 
-research aims will be presented below.
+Building on this background, we propose the use of anisotropic particles as a technique to enable microstructure modification of bijels upon the application 
+of an external field, both during and after fabrication. This work aims to explore methods for controlling the bijel microstructure independently of the casting 
+mixture composition by utilizing magnetic stimuli on bijels stabilized with magnetically responsive ellipsoidal particles.  
+The proposed mechanism of microstructure modification is based on the reorientation of particles in response to the applied magnetic field, which alters the 
+packing arrangement of the particles at the interface. By modifying the interfacial packing, the point at which the particles jam is also altered, thereby 
+affecting the jamming point of the bijel. This mechanism is expected to be effective both during and after the synthesis process. Additionally, the 
+processability of bijels produced using this technique will be examined to assess how changes in particle packing influence the rheological properties of 
+the material.
 
@@
 
-The jamming point of a bijel controls the obtained microstructure, as shown by previous work comparing the length scale of bijels synthesized 
-with different particle volume fractions and particle sizes. \cite{jansen_bijels_2011, reeves_particle-size_2015} It has also been shown how magnetic fields 
-can be used to enable self assembly of ansisotropic particles at interfaces and control the interfacial angle between the particle axis of symmetry and the interface. 
-\cite{davies_interface_2014, davies_assembling_2014}
-On a curved interface with many other particles, it is unknown how multiple particles orienting to a field and having regular structure will affect when and how the bijel 
-will jam. \cite{bresme_orientational_2007, davies_interface_2014}
+The jamming point of a bijel plays a crucial role in determining the resulting microstructure, as demonstrated by previous studies comparing the length scales 
+of bijels synthesized with varying particle volume fractions and sizes \cite{jansen_bijels_2011, reeves_particle-size_2015}. Additionally, it has been shown 
+that magnetic fields can facilitate the self-assembly of anisotropic particles at interfaces and control the interfacial angle between the particle's axis 
+of symmetry and the interface \cite{davies_interface_2014, davies_assembling_2014}. However, on a curved interface with numerous other particles, it remains 
+unclear how the orientation of multiple particles in response to the field and their regular arrangement will influence the jamming behavior of the bijel 
+\cite{bresme_orientational_2007, davies_interface_2014}.
 
-To assess the obtained microstructure upon application of a field during formation of the bijel, homogenous mixtures containing spherical and 
-ellipsoidal particles will be subjected to field strengths above and below the critical field strength when particle orientations to the 
-interface are controlled by the applied field strength, as calculated by Bresme and Faraudo for the particle aspect ratio.
-\cite{bresme_orientational_2007, davies_interface_201} This selection of fields
-will allow insight into the controlling mechanisms behind microstructural changes observed, allowing verification of the hypothesis and 
-ascertainment where the most control over the microstructure can be exercised.
+To evaluate the microstructure obtained upon the application of a field during the formation of the bijel, homogeneous mixtures containing spherical and 
+ellipsoidal particles will be subjected to field strengths both above and below the critical field strength. This critical field strength is the threshold 
+at which particle orientations to the interface are governed by the applied field, as calculated by Bresme and Faraudo for the particle aspect ratio 
+\cite{bresme_orientational_2007, davies_interface_2014}. The range of selected field strengths will provide insight into the mechanisms controlling 
+microstructural changes, enabling verification of the hypothesis and identification of the conditions under which the most control over the microstructure 
+can be achieved.
 
-The average and directional domain sizes in addition to their relation with tortuosity will allow characterization of the microstructural properties 
-of the resulting bijel. The nematic order parameter and average interfacial angle will be used to investigate how the application of the 
-field affects the particle ordering to each other, and to the interface. Finally, the radial distribution function will be used to assess 
-if the orientational changes expected upon field application, affects the packing of the particles on the interface.
+The average and directional domain sizes, along with their relationship to tortuosity, will be used to characterize the microstructural properties of the 
+resulting bijel. The nematic order parameter and the average interfacial angle will provide insight into how the application of the field influences particle 
+ordering, both among the particles and relative to the interface. Finally, the radial distribution function will be employed to assess whether the expected 
+orientational changes upon field application affect the packing of particles at the interface.
 
@@
 
-Particles on the surface of emulsion droplets have been shown to unjam and rejam into new, stable microstructures upon application of 
-stimuli. \cite{cui_stabilizing_2013} Magnetic fields applied to bijels stabilized with ellipsoidal particles will facilitate unjamming and rejamming of
-the particle monolayer, resulting in microstructure modification of the bijel. Due to local changes in the state of the particles, specifically the 
-interfacial ordering in a specific direction and arrangement of particles, we expect that there will be microstructure modification even when the 
-magnetic field is switched off. Two techniques of microstructure change are proposed. The first technique is that the adsorption 
-energy is so strong that the interface is dragged along with the particles until they rejam in their new location and orientation to the 
-field. The second technique is that the particles tilt in place out of the interface, causing domain coarsening before the particles jam 
-in their new positions and orientations. The mechanism, derived microstructure change and timescales will be assessed in this aim.
+Particles at the surface of emulsion droplets have been shown to unjam and rejam into new, stable microstructures upon the application of stimuli 
+\cite{cui_stabilizing_2013}. Magnetic fields applied to bijels stabilized with ellipsoidal particles will promote the unjamming and rejamming of the 
+particle monolayer, leading to modifications in the bijel's microstructure. Due to local changes in the state of the particles—specifically, alterations 
+in the interfacial ordering and the direction and arrangement of particles—we anticipate that microstructure changes will persist even after the magnetic 
+field is turned off. Two mechanisms for microstructure modification are proposed. The first suggests that the adsorption energy is sufficiently strong to 
+cause the interface to move with the particles, allowing them to rejam in new locations and orientations relative to the field. The second mechanism posits 
+that the particles tilt within the interface, leading to domain coarsening before jamming in their new positions and orientations. This study will assess the 
+mechanism, the resulting microstructural changes, and the associated timescales.
 
-The response of bijels to magnetic fields will be assessed through analyzing how model bijels made with no fields respond to field strengths 
-above and below the critical field strength as calculated from Bresme Faraudo theory. The microstructure properties such as the average domain 
-size, particle orientation to the field and interface and the Steinhardt 6 fold bond order parameter to examine the spatial relationship of 
-the particles to their neighbors. These techniques will allow elucidation of which mechanism is present at which magnetic field strength. 
-Additionally, the microstructure changes observed will be characterized and compared to one another to assess how the applied magnetic field 
-changes the final microstructure obtained.
+The response of bijels to magnetic fields will be evaluated by analyzing how model bijels, synthesized without applied fields, respond to field 
+strengths both above and below the critical field strength, as calculated using Bresme and Faraudo's theory. Microstructural properties, including the 
+average domain size, particle orientation relative to the field and interface, and the Steinhardt 6-fold bond order parameter, will be used to examine 
+the spatial relationships between particles and their neighbors. These techniques will enable the identification of the mechanisms active at different 
+magnetic field strengths. Additionally, the observed microstructure changes will be characterized and compared to assess how the applied magnetic field 
+influences the final microstructure.
 
-Next, the importance of the initial order of the particle monolayer will also be assessed through increasing the applied field to equal to the 
-surface tension forces on bijel templates simulated under various field strengths. The applied field will also be switched off on bijel templates 
-simulated under the same field strengths. The same analysis metrics mentioned earlier will be used. Additionally, the microstructures with the 
-same difference in applied field,  will be assessed to investigate the reversibility of bijel microstructures.
+Next, the importance of the initial ordering of the particle monolayer will be assessed by increasing the applied field to levels equal to the surface 
+tension forces on bijel templates simulated under various field strengths. The applied field will also be switched off for bijel templates simulated under 
+the same conditions. The same analysis metrics mentioned previously will be used. Additionally, microstructures with the same difference in applied field 
+will be examined to investigate the reversibility of bijel microstructures.
 
@@
 
-In many of the fabrication processes described above, the rheology of the bijel casting mixture is essential. 
-\cite{haase_continuous_2015, cai_bijels_2017, amirfattahi_fabrication_2024} Ching showed that rheologically, bijels are 
-colloidal glasses percolating in 3D space. \cite{ching_bijel_2022} A shear capillary number, $Ca_s$, is defined that correlates the 
-applied strain rate to the capillary forces derived from surface tension. \cite{frijters_effects_2012, yang_capillary_2022} We are interested 
-in identifying the effect of the initial microstructure and an applied field on the rheological properties of the bijel.
+In many of the fabrication processes described above, the rheology of the bijel casting mixture plays a crucial role 
+\cite{haase_continuous_2015, cai_bijels_2017, amirfattahi_fabrication_2024}. Ching demonstrated that, rheologically, bijels behave as colloidal 
+glasses percolating in 3D space \cite{ching_bijel_2022}. A shear capillary number, \( Ca_s \), is defined to correlate the applied strain rate 
+with the capillary forces derived from surface tension \cite{frijters_effects_2012, yang_capillary_2022}. This study aims to identify the effect 
+of the initial microstructure and applied field on the rheological properties of the bijel.
 
@@
 
-For this study, the yield stress and viscosity of the bijels will be explored as a function of the initial microstructure under 
-various $Ca_s$. The initial microstructure will be derived from bijels stabilized with ellipsoidal particles made with no magnetic field 
-and with a field strength equal to the surface tension energy. We then apply constant shear defined with $Ca_s$ to determine the yield stress and non-newtonian
-characteristics of the bijel. Previous investigations have revealed that the ordering of particles in the direction of shear change
-the rheological behavior significantly compared to unordered systems. Additionally, the domains of the bijel may create additional mechanisms for 
-rheological behavior modification which have not been probed in detail yet.
+In this study, the yield stress and viscosity of the bijels will be examined as a function of the initial microstructure under various $Ca_s$ values. 
+The initial microstructure will be derived from bijels stabilized with ellipsoidal particles, synthesized both without a magnetic field and with a field 
+strength equal to the surface tension energy. Constant shear, defined by $Ca_s$, will be applied to determine the yield stress and non-Newtonian 
+characteristics of the bijel. Previous studies have shown that particle ordering in the direction of shear significantly alters the rheological behavior 
+compared to unordered systems. Additionally, the domains within the bijel may introduce new mechanisms for modifying rheological properties, which have 
+yet to be explored in detail.
 
-We will then identify the complex rheology of the bijels, calculating the loss and storage modulus of the bijel microstructures detailed earlier
-as a function of the oscillation of shear. The loss and storage modulus detail the viscous and elastic behavior of the bijel respectively, meaning 
-that the gel point of the bijel can be established as the point when the storage modulus exceeds the loss modulus. We will pay special attention to the 
-state of the particles in all simulations, correlating changes in the properties of the particle to observed rheological events. We will also identify if shear banding
-is observed.
+We will then investigate the complex rheology of the bijels by calculating the loss and storage moduli of the bijel microstructures described 
+earlier as a function of oscillatory shear. The loss and storage moduli describe the viscous and elastic behavior of the bijel, respectively, 
+allowing the gel point of the bijel to be determined as the point at which the storage modulus exceeds the loss modulus. Special attention will be 
+given to the state of the particles in all simulations, correlating changes in particle properties with observed rheological events. Additionally, 
+we will assess whether shear banding occurs.

### 2025-03-05 chapters/lit_review.tex
Changes 1. Reworded introduction and lit review and addressed grammar and vocab issues 2. Fixed some referencing problems in the document 3. Fleshed out introduction in paper 2 4. Added sections for results in paper 3

@@
 
-When two partially miscible fluids are mixed together, they will have the tendency to coalesce into two distinct phases as they attempt to minimize 
-the thermodynamic penalty accrued from the formation of an interface. To prevent this coalescence process, conventionally small molecule surfactants 
-are utilized. The most famous example of this class of material is soap which emulsifies dirt into droplets suspended in water through mechanical action. 
-Surfactants function through reducing the surface tension between the droplet, known as the dispersed phase, and the bulk fluid, known as the continuous 
-phase. Surfactants function through reducing the surface tension between dispersed and continuous phases, reducing the energy penalty owed from formation 
-of an interface.
+When two partially miscible fluids are mixed, they tend to separate into distinct phases to minimize the thermodynamic penalty associated with interfacial formation. 
+To inhibit this phase separation, small-molecule surfactants are conventionally employed. A well-known example of such a material is soap, which facilitates the 
+emulsification of dirt into droplets suspended in water through mechanical agitation. Surfactants function by reducing the surface tension between the dispersed 
+phase (droplets) and the continuous phase (bulk fluid), thereby lowering the interfacial energy penalty associated with phase formation.
 
-The existence of particle stabilized emulsions has been known for more than a century now, after Pickering and Ramsden independently identified dispersed 
-droplets of oil within a water matrix after vigorous stirring of an oil, water and particle mixture. \cite{ramsden_separation_1904, pickering_cxcvi.emulsions_1907} 
-Unlike surfactants, particles act as emulsion stabilizers through the reduction of contact between dispersed and continuous phases as they adsorb into 
-the interface between phases. The Pieranski model derived from observations of \textcolor{blue}{insert derivation of pieranski model} 
-and is used to determine the adsorption energy of a particle at an interface. It is defined as $G_{ads} = \sigma A_{rm} (1 - \cos{\theta_c})^2$, where $G_{ads}$ 
-is the free energy reduction from a particle adsorption, $\sigma$ is the surface tension between the partially miscible fluids, $\theta_c$ is the contact angle 
-of the particle. The particles can be considered to be irreversibly adsorb even for nanoparticles, and for particles larger than 100nm, the adsorption energy 
-is so great that thermal fluctuations at the interface can be considered to have no effect. \cite{cheung_molecular_2011}
+The existence of particle-stabilized emulsions has been recognized for over a century, following the independent discoveries by Pickering and Ramsden, who observed dispersed 
+oil droplets within a water matrix after vigorous stirring of an oil-water-particle mixture \cite{ramsden_separation_1904, pickering_cxcvi.emulsions_1907}. Unlike surfactants, 
+which stabilize emulsions by reducing interfacial tension, particles act as stabilizers by adsorbing at the interface between the dispersed and continuous phases, thereby 
+preventing direct contact between them. The Pieranski model, derived from \textcolor{blue}{insert derivation of Pieranski model}, is commonly used to determine the adsorption 
+energy of a particle at an interface. It is expressed as $ G_{ads} = \sigma A_{rm} (1 - \cos{\theta_c})^2 $ where $G_{ads}$ represents the free energy reduction upon particle 
+adsorption, $\sigma$ is the surface tension between the partially miscible fluids, and $ \theta_c $ is the contact angle of the particle. Particles at the interface are 
+generally considered irreversibly adsorbed, even at the nanoscale. For particles larger than 100 nm, the adsorption energy is sufficiently high that thermal fluctuations at 
+the interface can be considered negligible \cite{cheung_molecular_2011}.
 
-After their discovery, interest in particle stabilized emulsions became minimal. However, increased interest in them has resurfaced since the 1980s owing to 
-their applications in food science. One such example is fat crystals stabilizing water droplets in oil to create margarine. Particle stabilization has also 
-been of interest owing to their lower toxicity and greater ease of sustainable sourcing through the usage of cellulose or chitin particles. 
-\cite{fujisawa_nanocellulose-stabilized_2017, tang_stimuli-responsive_2016, kalliola_carboxymethyl_2018}
-Additionally, chemical surfactants can be toxic to aquatic life, acting as a xeno-hormone and interfering with their reproduction. 
-\cite{kaczerewska_environmental_2020, lechuga_acute_2016}
+Following their initial discovery, interest in particle-stabilized emulsions waned for several decades. However, since the 1980s, renewed attention has emerged due to 
+their applications in food science. A notable example is the stabilization of water droplets in oil by fat crystals, a process used in margarine production. Particle 
+stabilization has also gained interest due to its lower toxicity and the potential for sustainable sourcing, particularly through the use of cellulose or chitin 
+particles \cite{fujisawa_nanocellulose-stabilized_2017, tang_stimuli-responsive_2016, kalliola_carboxymethyl_2018}. Moreover, conventional chemical surfactants pose 
+environmental concerns, as they can be toxic to aquatic life, acting as xeno-hormones and disrupting reproductive processes 
+\cite{kaczerewska_environmental_2020, lechuga_acute_2016}.
 
-Compared to emulsions stabilized using surfactants, particle stabilized emulsions offer greater resistance to coarsening, resulting in increased interest in 
-them once again. The microstructure properties of particle stabilized emulsions were explored in the early 2000s by Lumsdon and Binks among many others. They 
-observed that the radius of emulsion droplets, $R_e \propto \frac{\phi_w}{\phi_p}$, where $\phi_w$ and $\phi_p$ are volume fractions of water and particles 
-respectively. \cite{binks_pickering_2001} They also identified that there were other techniques to modify the microstructure of a Pickering Emulsion 
-such as concentration of fluids and particle wettability. Neutrally wetting particles do not impart a preferential curvature to the interface. When 
-using non-neutrally wetting particles, bridged droplets, capillary aggregates and other non droplet microstructures can be observed. Bijels, are synthesized 
-in a system using equal volume fraction of fluids and neutrally wetting particles, thus facilitating the formation of tortuous, co-continuous domains.
+Compared to surfactant-stabilized emulsions, particle-stabilized emulsions exhibit greater resistance to coarsening, leading to renewed interest in their applications. 
+The microstructural properties of these emulsions were extensively studied in the early 2000s by Lumsdon, Binks, and others. Their findings indicated that the emulsion 
+droplet radius follows the relationship $R_e \propto \frac{\phi_w}{\phi_p}$, where $\phi_w$ and $\phi_p$ represent the volume fractions of water and particles, 
+respectively \cite{binks_pickering_2001}. Additionally, they identified several factors influencing the microstructure of Pickering emulsions, including fluid concentration 
+and particle wettability. Neutrally wetting particles do not impose a preferential curvature on the interface, whereas non-neutrally wetting particles can lead to the 
+formation of bridged droplets, capillary aggregates, and other non-spherical microstructures. A notable example is bijels, which are synthesized in systems containing equal 
+volume fractions of immiscible fluids and neutrally wetting particles, leading to the formation of tortuous, co-continuous domains.
 
-Bijels are synthesized in systems which have roughly equal fluid volume fractions and neutrally wetting particles so as to not impose preferential 
-curvature on the interface. \cite{stratford_colloidal_2005, herzig_bicontinuous_2007, lee_bicontinuous_2010, jansen_bijels_2011, velankar_non-equilibrium_2015} 
-Reeves et al. demonstrated that bijels stabilized with nanoparticles are more stable than those with microparticles due to better mechanical properties and 
-interface coverage. \cite{reeves_particle-size_2015}  Additionally, research by Jansen, Harting, and Hijnen et al. showed that the bijel domain size 
-$L \propto \frac{1}{\phi_p}$ for both rod-like and spherical particles. Although the pre-factor is dependent upon the particle geometry, this feature 
-has been seen with many other particle shapes as well. \cite{hijnen_bijels_2015, madivala_exploiting_2009, gunther_timescales_2014, daware_emulsions_2015, 
-loudet_capillary_2005, cheng_shape-anisotropic_2013}
+Bijels are synthesized in systems containing approximately equal fluid volume fractions and neutrally wetting particles to prevent the imposition of preferential 
+curvature at the interface \cite{stratford_colloidal_2005, herzig_bicontinuous_2007, lee_bicontinuous_2010, jansen_bijels_2011, velankar_non-equilibrium_2015}. 
+Reeves et al. demonstrated that bijels stabilized with nanoparticles exhibit greater stability than those stabilized with microparticles due to enhanced mechanical 
+properties and improved interfacial coverage \cite{reeves_particle-size_2015}. 
+Furthermore, research by Jansen, Harting, and Hijnen et al. established that the bijel domain size follows the relationship $ L \propto \frac{1}{\phi_p} $ for both 
+rod-like and spherical particles. While the proportionality constant depends on particle geometry, this trend has been observed across various particle shapes 
+\cite{hijnen_bijels_2015, madivala_exploiting_2009, gunther_timescales_2014, daware_emulsions_2015, loudet_capillary_2005, cheng_shape-anisotropic_2013}.
 
@@
 
-In the past decade, methods to synthesize particles which have anisotropic geometry and chemistry have increased in number and scope. Synthesis techniques vary 
-depending on the type of particle shape desired. Ellipsoids can be easily created by mechanical deformation of polymer spheres. Dumbbell shaped particles can be 
-synthesized using microfluidic devices or emulsion templating. Square particles can be generated using crystallization of material. \cite{morgan_understanding_2013} 
-These variety of techniques mean that particle geometry is no longer as constraint when investigating prospective particle stabilizers of bijels. 
-\cite{wu_recent_2016}
+Over the past decade, advancements in synthesis techniques have significantly expanded the ability to fabricate particles with anisotropic geometry and surface chemistry. 
+The choice of synthesis method depends on the desired particle shape. For example, ellipsoidal particles can be readily produced through the mechanical deformation of 
+polymer spheres, while dumbbell-shaped particles can be synthesized using microfluidic devices or emulsion templating. Square-shaped particles, on the other hand, can be 
+generated through controlled crystallization \cite{morgan_understanding_2013}. The increasing variety of synthesis methods has reduced geometric constraints when exploring 
+potential particle stabilizers for bijels \cite{wu_recent_2016}.
 
-Anisotropic particles have shape dependent properties owing to their induction of multipolar interactions by deforming the interface to ensure the mean 
-curvature is 0,  fulfilling the Young-Laplace equation shown in Figure \ref{fig:anisotropic_particle_interface}. \cite{loudet_capillary_2005, 
-cheng_shape-anisotropic_2013} Using this property has enabled directed assembly and migration through modified capillary forces. 
-\cite{cavallaro_curvature-driven_2011, read_dimerization_2020, sharifi-mood_curvature_2015}
+Anisotropic particles exhibit shape-dependent properties due to their ability to induce multipolar interactions by deforming the interface to maintain a mean curvature of 
+zero, thereby satisfying the Young-Laplace equation, as illustrated in Figure \ref{fig:anisotropic_particle_interface} \cite{loudet_capillary_2005, cheng_shape-anisotropic_2013}.
+This property has been leveraged to facilitate directed assembly and migration through modified capillary forces 
+\cite{cavallaro_curvature-driven_2011, read_dimerization_2020, sharifi-mood_curvature_2015}.
 
@@
 
-When stabilizing bijels, ellipsoidal particles offer greater stability than spherical ones due to their larger cross-sectional area to volume ratio, 
-as shown by Günther et al. and Hijnen et al. \cite{gunther_timescales_2014, hijnen_bijels_2015} This results in additional domain coarsening timescales 
-from particle re-orientation and increased mechanical rigidity, enhancing the stability of emulsions with ellipsoidal particles, as evidenced in rheological 
-studies. \cite{gunther_timescales_2014, daware_emulsions_2015, witt_bijel_2013} It has also been shown that particle shape changes how and when jamming occurs. 
-Using graphene plate like particles, it was shown that the plate like particles can have their own elasticity to them, affecting when jamming occurs. 
-\cite{imperiali_simple_2014, sun_assembly_2013}
+When stabilizing bijels, ellipsoidal particles provide greater stability than spherical ones due to their higher cross-sectional area-to-volume ratio, as demonstrated by 
+Günther et al. and Hijnen et al. \cite{gunther_timescales_2014, hijnen_bijels_2015}. This enhanced stability arises from additional domain coarsening timescales associated 
+with particle reorientation and increased mechanical rigidity, as confirmed by rheological studies \cite{gunther_timescales_2014, daware_emulsions_2015, witt_bijel_2013}. 
+Furthermore, particle shape influences both the onset and dynamics of jamming. Studies using graphene plate-like particles have shown that these particles exhibit intrinsic 
+elasticity, which affects the conditions under which jamming occurs \cite{imperiali_simple_2014, sun_assembly_2013}.
 
-Control over the orientation of ellipsoidal particles at interfaces balances interfacial capillary and magnetic field forces. 
-\cite{bresme_orientational_2007, davies_assembling_2014} Theory and simulations indicate a critical field strength above which particle orientation 
-is dominated by the applied field. \cite{bresme_orientational_2007, davies_assembling_2014} Experiments and simulations have found that steric interactions, 
-influenced by orientation and interfacial arrangements significantly influence the free energy of particle assemblies, highlighting the complex interplay 
-between these forces. \cite{morgan_understanding_2013, newton_influence_2014, newton_capillary_2018}
+The orientation of ellipsoidal particles at interfaces is governed by a balance between interfacial capillary forces and external magnetic fields 
+\cite{bresme_orientational_2007, davies_assembling_2014}. Theoretical studies and simulations suggest the existence of a critical field strength beyond which particle 
+orientation is predominantly dictated by the applied field \cite{bresme_orientational_2007, davies_assembling_2014}. Additionally, both experimental and computational 
+studies have shown that steric interactions—modulated by particle orientation and interfacial arrangements—play a significant role in determining the free energy of particle 
+assemblies, underscoring the intricate interplay between these forces \cite{morgan_understanding_2013, newton_influence_2014, newton_capillary_2018}.
 
@@
 
-Bijels were first synthesized using Thermally Induced Phase Separation (TIPS). \cite{herzig_bicontinuous_2007, lee_bicontinuous_2010, bai_dynamics_2015} 
-First, a small molecule or polymer blend with a critical point, named the casting mixture, is identified and prepared with a composition corresponding to 
-that of the critical point. Next, the casting mixture is blended with particle surfactants while still in a single phase. Once the particles are distributed 
-homogenously in the casting mixture, phase separation is initiated in the casting mixture through changing the temperature such that it is in the two-phase region. 
-Through ensuring the composition is that of the critical point, the casting mixture undergoes spinodal decomposition without any nucleation and growth.
+Bijels were first synthesized using Thermally Induced Phase Separation (TIPS) \cite{herzig_bicontinuous_2007, lee_bicontinuous_2010, bai_dynamics_2015}. 
+The process begins by identifying a small-molecule or polymer blend with a critical point, referred to as the casting mixture, and preparing it at a composition 
+corresponding to this critical point. The casting mixture is then combined with particle surfactants while remaining in a single-phase state. Once the particles 
+are homogeneously distributed, phase separation is induced by adjusting the temperature to bring the system into the two-phase region. By ensuring that the 
+composition aligns with the critical point, the casting mixture undergoes spinodal decomposition, preventing nucleation and growth.
 
-TIPS allows for batch synthesis of bijels in research labs. However to make bijels industrially relevant, a continuous process which also facilitates the 
-synthesis of multiple form factors of bijels for various applications. Solvent Transfer Induced Phase Separation (STrIPS) was proposed as a means to do just this. 
-A casting mixture composed of two fluids, a co-solvent, particles and a surfactant is prepared. The fluids will constitute the bijel while the co-solvent will 
-diffuse out of the bijel to initiate phase separation. The surfactant is present to ensure that the bijel remains stable against Marangoni pressure. The casting 
-mixture if extruded into a bath of non-solvent that is not miscible with the bijel constituents but is miscible with the co-solvent. Diffusion of co-solvent 
-initiates phase separation and synthesis of the bijel. The concentration of surfactant and the flow rate of the casting mixture control the obtained microstructure.
+TIPS enables batch synthesis of bijels in research laboratories. However, for bijels to become industrially viable, a continuous fabrication process is required—one 
+that also allows for the production of various bijel form factors suited to different applications. Solvent Transfer Induced Phase Separation (STrIPS) has been proposed 
+as a method to achieve this. In STrIPS, a casting mixture is prepared, consisting of two fluids that form the bijel, a co-solvent, particles, and a surfactant. Phase 
+separation is initiated as the co-solvent diffuses out of the bijel. The surfactant is included to maintain bijel stability against Marangoni forces. The casting mixture 
+is then extruded into a bath of a non-solvent, which is immiscible with the bijel-forming fluids but miscible with the co-solvent. The diffusion of the co-solvent triggers 
+phase separation, leading to bijel formation. The resulting microstructure is influenced by both the surfactant concentration and the flow rate of the casting mixture.
 
@@
 
+Vapor Induced Phase Separation(VIPS) has also been identified as a technique for continuous fabrication of bijels. \cite{wang_scalable_2020} A quarternary casting mixture
+containing particles, solvent and two partially miscible liquids is prepared. The solvent and liquid species are carefully selected to ensure that removal of the
+solvent will cause phase separation of the two partially miscible liquids. One system that has been used is the water/hexanediol-diacrylate solvated by ethanol.
+Selection of the composition of the system facilitates crossing of the binodal through the critical point, causing phase separation through spinodal decomposition.
+This technique has been used to fabricate thin films of bijels blade and spray coated onto substrates.
+
 \textcolor{blue}{Description of homogenization}
+
+Instead of relying upon spinodal decomposition to generate the bijel morphology, homogenization uses shear to join phase separating domains, resulting in a 
+structure that has the properties of a bijel even if not fabricated from fluids undergoing spinodal decomposition. \cite{huang_bicontinuous_2017, cai_bijels_2017} 
+This method is primarily used for nanoparticles under $50$ nm and it has been shown to work for multiple particle geometries. This method relies upon
+shear to cause limited coalescence of droplets. As coarsening occurs, particles adsorb on the interface and when the interfacial area matches the area of the
+adsorbed particles, the microstructure jams. Tuning of the method can be done through modifying the contact angle of the particles at the interface as well as
+the viscosity of the fluids.
 
@@
 
-% STrIPS, shown in Figure \ref{fig:strips}, and many other fabrication techniques require fine control over the composition of the casting mixture for the technique to function and to control the obtained microstructure.
-\cite{haase_continuous_2015, amirfattahi_fabrication_2024, sprockel_fabrication_2023} In homogenization, the applied shear of mixing initiates coalescence of droplets in a controlled way, leading to formation of the bijel.
-\cite{cai_bijels_2017} In both synthesis strategies, the rheology of a proposed casting mixture is therefore essential to understand to explore what other casting mixtures can be utilized in these fabrication techniques.
-Microstructure control has also been achieved when using TIPS by controlling the concentration of particles at different heights, creating a gradient of pore sizes in the final bijel.
-\cite{french_bicontinuous_2022} Looking to the current state of stimuli response in bijels,
-
-% \begin{wrapfigure}{r}{7cm}
-% \caption{Schematic of a bijel with hard-sphere particles undergoing shear, demonstrating migration and detachment of particles at the interface. \cite{bonaccorso_shear_2020}}
-% \label{wrap-fig:bijel_under_shear}
-% \includegraphics[width=7cm]{figures/literature_review/bijel_under_shear.jpeg}
-% \end{wrapfigure}
+Enter something about this method. \cite{amirfattahi_fabrication_2024}
 
 \section{Rheological models and shear response of bijels}
+
+Bijels undergoing constant shear demonstrate shear thinning behavior which at moderate shear rates can be described reasonably well using the Herschel-Buckley
+model. \cite{macmillan_rheological_2019, wang_morphology_2023} At higher shear rates, the bijel microstructure is destroyed and the viscosity becomes newtonian. 
+\cite{cai_bijels_2017,bonaccorso_shear_2020}. Figure \ref{fig:bijel_under_shear} illustrates the findings of Bonnacorso et al., which observed that when a bijel 
+stabilized with hard-sphere-like particles is subjected to shear, the particles initially align with the shear direction before detaching from the interface 
+\cite{bonaccorso_shear_2020}. Investigating the impact of particle alignment on rheology, prior studies in suspension rheology have shown that colloidal systems 
+with hard-sphere interparticle interactions undergoing constant shear exhibit shear banding—where particles order in the shear direction at moderate shear rates—resulting 
+in shear thinning \cite{vermant_flow-induced_2005, brader_nonlinear_2010}.
 
@@
 
-Studies into bijel rheology have shown the characteristics of a gel when the
-storage modulus exceeds the loss modulus. \cite{lee_making_2013, bai_dynamics_2015} Ching and Mohraz also demonstrated that the rheological behaviour of a 
-bijel most closely resembles a 2D colloidal glass that was percolating in 3D space by comparing the linear visco-elasticity of bijels with colloidal gels made 
-with strongly attractive particles. \cite{ching_bijel_2022} Several key feature of glasses are that they posses a yield stress, viscoelastic behaviour and a 
-glass transition point.
-\cite{pham_yielding_2008, weeks_introduction_2017} Yield stress is the stress imparted when the particle monolayer is irreversibly changed.
-\cite{pham_yielding_2008} Viscoelasticity is present when the particle monolayer has solid and a liquid like behaviour, depending upon the timescale of the applied stress.
-\cite{pham_yielding_2008} The glass transition point is characterized when the dynamics of the monolayer drastically slow down.
-\cite{weeks_introduction_2017} Figure \ref{fig:bijel_under_shear} demonstrates Bonnacorso et al.'s findings that when subjecting a bijel stabilized with hard-sphere like spherical particles to shear, the particles align to the direction of applied shear before detaching from the interface.
-\cite{bonaccorso_shear_2020} Looking to how particle alignment affects rheology, past work in suspension rheology has shown that colloidal systems with hard-sphere interparticle interactions undergoing constant shear demonstrate particle ordering (shear banding) in the direction of shear at moderate shear rates, causing shear thinning.
-\cite{vermant_flow-induced_2005, brader_nonlinear_2010}
+Studies on complex bijel rheology have demonstrated gel-like characteristics when the storage modulus exceeds the loss modulus \cite{lee_making_2013, bai_dynamics_2015}. 
+Ching and Mohraz further showed that the rheological behavior of bijels closely resembles that of a 2D colloidal glass percolating in 3D space, based on comparisons of 
+linear viscoelasticity with colloidal gels composed of strongly attractive particles \cite{ching_bijel_2022}. Key characteristics of glasses include the presence of a 
+yield stress, viscoelastic behavior, and a glass transition point \cite{pham_yielding_2008, weeks_introduction_2017}. Yield stress corresponds to the applied stress at 
+which the particle monolayer undergoes irreversible structural changes \cite{pham_yielding_2008}. Viscoelasticity arises when the monolayer exhibits both solid and 
+liquid-like behavior, depending on the timescale of the applied stress \cite{pham_yielding_2008}. The glass transition point is marked by a dramatic slowdown in the 
+monolayer's dynamics \cite{weeks_introduction_2017}.
 
@@
 
-Five primary techniques to model multicomponent or multiphase systems exist in the LBM literature. A quick review of the Shan-Chen or 
+Four primary techniques to model multicomponent or multiphase systems exist in the LBM literature. A quick review of the Shan-Chen or 
 interparticle potential model  will be provided here from the perspective of a binary mixture. Additionally, the names and descriptions of 
@@
 
-In addition to the Shan-Chen model, the color gradient model, free energy model, mean field theory model and interface tracking technique all 
+In addition to the Shan-Chen model, the color gradient model, free energy model and interface tracking technique all 
 allow for simulations of various types of multiphase and/or multicomponent flows. The color gradient model proposed by Rothman and Keller and 

### 2025-03-05 chapters/paper1.tex
Changes 1. Reworded introduction and lit review and addressed grammar and vocab issues 2. Fixed some referencing problems in the document 3. Fleshed out introduction in paper 2 4. Added sections for results in paper 3

@@
 Magnetic response has been used in particle stabilized emulsions in the past, causing controlled emulsion failure and
-on-demand droplet coalescence for encapsulation and cargo release applications. \cite{melle_pickering_2005,zhou_magnetic_2011}
+on-demand droplet coalescence for encapsulation and cargo release applications. \cite{melle_pickering_2005, zhou_magnetic_2011}
 Fields also enable self assembly through the control of interface deformation derived capillary forces.
-\cite{morgan_understanding_2012,davies_interface_2014,davies_dipolar_2015} Magnetically responsive spherical particle 
+\cite{morgan_understanding_2013,davies_interface_2014,davies_dipolar_2015} Magnetically responsive spherical particle 
 stabilized bijels have thus far not yielded significant microstructural modifications. \cite{kim_bijels_2010} However, 

### 2025-03-05 chapters/paper2.tex
Changes 1. Reworded introduction and lit review and addressed grammar and vocab issues 2. Fixed some referencing problems in the document 3. Fleshed out introduction in paper 2 4. Added sections for results in paper 3

@@
+Stimuli responsive emulsions have seen interest for use in fields such
+as enhanced oil recovery, porous material templates, in-situ reaction
+seperation systems and drug delivery scaffolds.
+\cite{tang_stimuli-responsive_2016,} \cite{bago_rodriguez_capsules_2019}
+These applications are enabled through stimuli response driven
+microstructure modification, changing the permeability, sueface area and
+morphology of the emulsion. Leveraging advances in particle synthesis
+techniques and citing concerns over surfactant toxicity and
+environmental concerns, particle stabilized emulsions have made a
+resurgence in popularity after their discovery in 1907 by Ramsden and
+Pickering. \cite{rozynek_opening_2019} \cite{zhou_magnetic_2011} Stimuli
+response has been enabled in particle stabilized emulsions using pH,
+temperature or chemical composition changes.
+\cite{maingret_dextran-based_2020} \cite{lin_ph-responsive_2018}
+\cite{raju_ph-responsive_2018} \cite{zhang_ph_2022}
+
+Owing to its tortuous, co-continuous domain morphology, bicontinuous
+interfacially jammed emulsion gels (bijel) are studied for their
+possible applications to fabricate membranes, catalyst supports, battery
+electrodes and pharmaceutical products. \cite{yabuno_preparation_2020}
+\cite{samdani_bicontinuous_2017} \cite{cha_bicontinuous_2019}
+\cite{garcia_scalable_2019} \cite{santiago_cordoba_aerobijels_2020}
+Bijels are formed through the arresting of spinodal decomposition of
+partially miscible fluids. \cite{stratford_colloidal_2005}
+\cite{herzig_bicontinuous_2007} \cite{tavacoli_novel_2011} Once phase
+separation begins, the incipient interface begins to sweep through the
+system causing particles to begin to adsorbing into it. Once the
+interfacial area matches that of the cross sectional area of the
+adsorbed particles, the structure jams in place.
+\cite{stratford_colloidal_2005} \cite{herzig_bicontinuous_2007}
+\cite{tavacoli_novel_2011} After their discovery in simulations and
+subsequent synthesis in experiments, a rich diversity of bijel
+literature has developed around various fluid systems that allow for
+bijel synthesis, methods to fabricate them at scale and their
+applications.
+
+Bijels stabilized by ellipsoidal particles exhibit distinct domain evolution timescales compared to those stabilized by 
+spherical particles \cite{gunther_timescales_2014}. Unlike spherical particles, ellipsoidal particle reorientation at the 
+interface influences microstructure. After jamming, additional timescales emerge due to capillary interactions that drive 
+particle reorientation and prolonged domain coarsening \cite{gunther_timescales_2014}. Bijels behave as 2D glasses percolating 
+in 3D space, with locally jammed particles as observed by Günther et al. 
+\cite{ching_bijel_2022, torquato_jammed_2010, gunther_timescales_2014}. Studies on jammed suspensions indicate subdiffusive 
+particle movement, further confirming local jamming in bijel monolayers \cite{savelev_diffusion_2006}.
+
+Magnetic fields have gained interest as external stimuli due to their targeted interactions, biocompatibility, and material 
+versatility. The structural response of magnetically responsive hydroxyapatite crystals depends on initial particle orientation
+\cite{nakayama_stimuli-responsive_2018}. Magnetophoresis, where particles move along field lines, has been observed in Pickering 
+emulsions stabilized by magnetic microspheres \cite{tham_magnetophoresis_2021}. Structural deformation and de-emulsification occur due 
+to particle migration or tilting at the interface \cite{yang_rapid_2020, misra_magnetic_2020}. However, how these effects influence 
+bijel microstructure post-jamming remains unclear. Given the locally jammed nature of bijels, magnetic field responses, combined with 
+anisotropic particle stabilization, may offer a means to control bijel microstructure.
+
+This work investigates the structural response of bijels stabilized by anisotropic magnetic particles. Using a Lattice Boltzmann Method 
+coupled with Molecular Dynamics, we simulate a binary fluid system where ellipsoidal particles, modeled as magnetic dipoles along their 
+symmetry axis, stabilize bijel templates. Simulations without an applied field reveal anisotropic bijel formation, with microstructure 
+evolution dependent on particle reordering at the interface, quantified using the six-fold Steinhardt order parameter \(\langle Q_6 \rangle\).
+
+We further assess how initial microstructure influences structural changes, showing that the difference in order between initial and final 
+particle monolayers dictates the extent of microstructure evolution. Additionally, applying and removing a magnetic field results in distinct 
+microstructural properties and timescales, highlighting the importance of processing history. These findings demonstrate how magnetic fields, 
+combined with anisotropic particle-stabilized bijels, enable on-demand microstructure switching for potential applications.
+
 \section{Results}\label{sec:results_p2}
@@
 
-We characterize the microstructure changes observed through calculating
-a characteristic length scale, called the average domain size. The
-average domain size is calculated using the first moment of the 3D
-averaged structure factor. Past work has shown that this method
-correctly reproduces the scaling expected in phase separating systems.
-The structure factor is calculated from the fourier transform of the
-fluctuations in the order parameter. \cite{kendon_inertial_2001}
-
-\begin{equation}
-S(\mathbf{k}, t) = \widetilde{\phi}(\mathbf{k}, t)\widetilde{\phi}(\mathbf{-k}, t)
-\end{equation}
-
-\(\mathbf{k}\) represents the wave vector in each direction of each
-lattice grid point. The fluctuations in the order parameter are
-calculated from the order parameter of the bijel defined as
-\(\widetilde{\phi} = \phi - \langle \phi \rangle\). \(\phi\) is
-calculated through subtraction of the red from the blue fluid density,
-\(\phi = \rho^b - \rho^r\). The average domain size is commonly
-calculated using the spherically averaged structure factor where all
-points corresponding to \(k = |\mathbf{k}|\) are binned, where \(k\) is
-the magnitude of \(\mathbf{k}\).
-
-\begin{equation}
-S(k, t) = \frac{1}{n} \sum_{k - \Delta < k < k + \Delta} S(\mathbf{k}, t)
-\label{eq:structure_factor_calc}
-\end{equation}
-
-The average domain size can then be calculated from the spherically
-averaged structure factor after calculating the first moment of the
-structure factor using the following expression.
-
-\begin{equation}
-L(t) = 2\pi \frac{\sum S(k, t) }{ \sum k S(k, t) }
-\end{equation}
-
-We found that this method for determining domain size generally
-overestimated the observed channel diameter. However, previous studies
-have demonstrated that the scaling behavior of the first-moment-derived
-domain size aligns with the expected phase separation in spinodal
-decomposition. The overestimation arises due to the limited number of
-samples at small k values, where the bin size is roughly equivalent to
-the k value. Additionally, in simulations with periodic domains, both
-the structure factor and computed length scale are influenced by
-finite-size effects. Nonetheless, this measurement still provides
-valuable insight into trends in the average domain size.
-
 To correlate the microstructure evolution to the ordering of the
 particle monolayer to the magnetic field, we calculate the nematic order
-parameter. \cite{cuesta_monte_1990} First, the average orientational
-tensor is calculated from the particle orientations in Eq
-\ref{eq:orientational_order_tensor}
-
-\begin{equation}
-Q = \frac{1}{n_p} \sum_{i} (\frac{3}{2}[\hat{\mathbf{o}}_i \otimes \hat{\mathbf{o}}_i] - \frac{1}{2}\mathbf{I})
-\label{eq:orientational_order_tensor}
-\end{equation}
-
-In Eq \ref{eq:orientational_order_tensor}, \(\hat{\mathbf{o}}_i\)
-defines the orientation vector of particle \(i\) and \(\mathbf{I}\) is
-the identity matrix. The nematic director or average particle
-orientation is the eigenvector corresponding to the largest eigenvalue
-of \(Q\) which is the value of the nematic order parameter, \(S\). The
-assembly of particles can be said to have nematic order if
-\(S \geq 0.3\) and is fully aligned to the director if \(S = 1.0\).
-\cite{cuesta_monte_1990}
+parameter. \cite{veerman_phase_1992}
 
@@
 we compute the second-moment-derived structure factor without radial
-averaging. \cite{jansen_bijels_2011} Following the structure factor
-calculation described in Eq. \ref{eq:structure_factor_calc}, the second
-moment of the structure factor in direction \(\beta\) is determined for
-each Cartesian coordinate axis as
-
-\begin{equation}
-L_{\beta}(t) = 2 \pi \sqrt{\frac{\sum_{\mathbf{k_{\beta}}}  S(\mathbf{k}, t) }{\sum_{\mathbf{k_{\beta}}}  k_{\beta}^2S(\mathbf{k}, t)}}
-\label{eq:second_moment_domain}
-\end{equation}
-
-From Eq \ref{eq:second_moment_domain}, we can calculate the length scale
-in each cartesian direction, \(L_x, L_y, L_z\). Here, we make a further
+averaging. \cite{jansen_bijels_2011} We also calculate the tortuosity 
+in each cartesian direction. Here, we make a further
 refinement simplifying the domain sizes to directions parallel and
@@
 their associated calculation, \(L_{\parallel} = L_{z}\) and
-\(L_{\perp} = \frac{L_x + L_y}{2}\). Tortuosity has been defined using
+\(L_{\perp} = \frac{L_x + L_y}{2}\). We perform the same simplification
+with the directional tortuosities.
+
+Tortuosity has been defined using
 the geometric, diffusional and hydraulic tortuosities. Here we define
@@
 characterizes the ratio between the free diffusion of a tracer and the
-effective diffusion of a tracer in the material.
-
-To calculate the tortuosities of the structures generated from our
-simulations, we first calculate \(\phi\) of the system over time from
-the filled densities. Many bijels are synthesized from monomer diffused
-into the oil phase, or the oil phase itself is intrinsically
-polymerizable. Our next step is to binarize the order parameter with the
-condition, \(\phi \leq 0 = 0\) and \(\phi > 0 = 1\) which reflects a
-solid red fluid phase and void blue fluid. We then mask all unconnected
-components, using the \texttt{label} function in \texttt{skimage}
-leaving only the percolating domain representing the bijel.
-\cite{van2014scikit} We utilize the python package taufactor which
-solves the diffusion equation for the structure, calculating the time
-taken for a tracer to go from one side of the system to the other.
-\cite{kench_taufactor_2023} We utilize the periodic boundary condition
-solver for this investigation. In previous work, we identified that the
-length scale derived from the second moment of the structure factor is
-only useful for identifying length scale anisotropy. Therefore, we plot
+effective diffusion of a tracer in the material. Therefore, we plot
 the directional second moment derived length scales and tortuosity in
@@
 this process. The mechanism of unjamming and re-jamming can be
-investigated using the average interfacial angle, \(\psi\).
-
-The interface angle of each particle is defined as
-\(\psi = \arccos{\frac{ \hat{\mathbf{o_i}}\cdot \hat{\mathbf{n_i}}}{|\hat{\mathbf{o_i}}| |\hat{\mathbf{n_i}}|}}\)
-where \(\hat{\mathbf{n_i}}\) is the normal of the interface closest to
-the center of the particle \(i\) and \(\hat{\mathbf{o_i}}\) is the
-orientation of particle \(i\) which follows the symmetry axis of the
-ellipsoid. For prolate particles, they prefer to lie flat on the
-interface, meaning that with no field \(\psi = 90^{\circ}\).
-\(\hat{\mathbf{n_i}}\) is calculated by first using the particle filling
-algorithm described and calculating the order parameter. Next, a mesh of
-the isocontour at \(\phi = 0\) is generated using the marching cubes
-algorithm in scikit-image with a box length of 4. \cite{van2014scikit}
-Next, the vertex closest to the center of particle \(i\) was found.
-\(\hat{\mathbf{n_i}}\) was then obtained from the normal corresponding
-to the vertex identified in the previous step.
-
-Another factor affected by the application of the magnetic field is the
-Steinhardt 6 fold order parameter, \(Q_6\), which characterized the
-local particle ordering. \cite{steinhardt_bond-orientational_1983} It
-has been used to characterize crystallization, glass transitions and
-crystal structures for colloidal and molecular crystals. We utilize the
-average across all particles on the interface, \(\langle Q_6 \rangle\)
-and track this parameter as a function of time. Past work has identified
-that local crystallization of colloidal crystals takes place at
-\(\langle Q_6 \rangle = 0.38\), and that
-\(\langle Q_6 \rangle^{HCP} = 0.485\).
-\cite{steinhardt_bond-orientational_1983} \cite{toxvaerd_role_2020}
-\cite{mickel_shortcomings_2013} We utilize a voronoi cell derived
-definition of the neighbor list of each particle, addressing some of the
-shortcomings highlighted in the original distance based definition.
-\cite{steinhardt_bond-orientational_1983}
-\cite{mickel_shortcomings_2013} We first define a complex orientational
-vector, \(q_{lm}\)
-
-\begin{equation}
-q_{lm}(i) = \frac{1}{N_b(i)} \Sigma_{j = 1}^{N_b(i)} Y_{lm}(\vec{R}_{ij})
-\end{equation}
-
-Where \(N_b\) is the number of nearest neighbors of particle \(i\),
-\(l\) is controls to the degree of spherical harmonic to be calculated,
-\(m\) is an integer defined as \(-l \leq m \leq l\) that defines which
-spherical harmonic is being calculated and \(\vec{r}_{ij}\) is the
-distance between two particle centers. The neighbor list \(N_b\) is
-usually defined by a cutoff distance from the center of particle \(i\)
-to its nearest neighbors \(j\). Steinhardt then defined a bond order
-parameter \(q_l\) from \(q_{lm}\) as
-
-\begin{equation}
-Q_{l}(i) = \sqrt{\frac{4 \pi}{2l + 1} \Sigma_{m = -l}^{l} |q_{lm}(i)|^2}
-\end{equation}
+investigated using the average interfacial angle, $\langle \psi \rangle$
+and the local ordering of the particles characterized with 
+$\langle Q_6 \rangle$ Past work has identified that local crystallization 
+of colloidal crystals takes place at \(\langle Q_6 \rangle = 0.38\). 
+\cite{toxvaerd_role_2020}
 

### 2025-03-06 chapters/final_remarks.tex
Changes 1. Added more analysis to application of magnetic fields during formation chapter 2. Added references to fix some (not all) literature reference issues 3. Added some detail in analysis techniques section
Changes 1. Added conclusion in final remarks 2. Added hysteresis curve for prolate particles stabilized bijels in aim2 section 3. Added description of synthesis techniques in lit review

@@
 \section{Conclusion}
+
+Owing to their high surface area to volume ratio, porous materials are seeing a surge in popularity in applications
+such as catalysis, battery electrodes and pharmaceuticals. Given their wide variety of applications, identifying 
+fabrication techniques that allow access to the various pore length scales is of interest. One such synthesis technique
+is emulsion templating which offers a wide variety of accessible microstructures, addition of stimuli response and 
+large number of possible systems that can be fabricated. A microstructure that can be fabricated from emulsion templates
+is the bicontinuous interfacially jammed emulsion gel (bijel).
+
+Bijels are normally fabricated using Thermally Induced Phase Separation (TIPS). However, TIPS does not allow for continuous
+fabrication of bijels. More recent fabrication techniques such as Solvent Transfer Induced Phase Separation (STrIPS) and 
+Vapor Induced Phase Separation (VIPS) allow for continuous fabrication and access to various microstructures. Both techniques
+require modifications to the initial emulsion mixture to facilitate microstructure adjustments, which affect the final rheological
+properties of the system. Decoupling the microstructure and the casting mixture of the bijel would allow for greater flexibility
+in the synthesis of the material.
+
+Stimuli response has been used before to modify the microstructure of particle stabilized emulsions. Magnetic fields offer
+targeted material response and low applied field strengths necessary for response. Past work investigating the effect of magnetic
+stimuli on bijels stabilized with spherical particles yielded little microstructure change. However, anisotropic particles have
+also been used to stabilize bijels. Anisotropic particles at interfaces under magnetic fields have been shown to tilt out of 
+interfaces. These effects have yet to be captured in bijels stabilized by ellipsoidal particles under magnetic fields.
+This study addresses this knowledge gap using a hybrid Molecular-Dynamics multicomponent method Lattice Boltzmann Method.
+We split this work into three aims; Aim 1 addressed the microstructure obtained when applying a magnetic field of various strengths 
+onto bijels stabilized by ellipsoidal particles, compared to bijels stabilized wih spherical particles. Aim 2 addressed the 
+structural response of bijels stabilized by ellipsoidal particles and analyzes the effect of initial order of the particle monolayer
+on the structural response observed. Aim 3 addressed the constant shear response of bijels stabilized by ellipsoidal particles
+with pre-existing particle order and under magnetic fields.
+
+In Aim 1, bijels stabilized with spherical particles do not respond to the application of a magnetic field. However, bijels stabilized
+with ellipsoidal particles have an increase in the average domain size by 3 \%. The microstructure also becomes anisotropic, 
+characterized as a change in the directional tortuosity and distribution of channel widths as a function of the distance from the 
+interface. The curvature also becomes more negative as the applied field strength is increased. The microstructure anisotropy is caused
+by direction specific jamming of the particle monolayer originating from particle ordering to the magnetic field.
+
+When investigating the particle monolayer, the orientational order changes as a function of the applied field strength and has particle
+morphology specific time evolution. The interface angle was also characterized and shown to have magnetic field dependence, although
+this was attributed to the orientational ordering of the particles on the interface. When analyzing the ordering of particles on the
+interface, disc-like particles see lowered local ordering as the magnetic field strength is increased while rod-like particles see
+greater local ordering. These properties are attributed to how those particle morphologies prefer to orient themselves at interfaces
+to one another, with disc like particles preferring to stack while rod like particles order side to side or end to end.
+
+In Aim 2
+
+In Aim 3
 
@@
 
-This work utilized 2 ellipsoidal particle geometries which were not as anisotropic as rods or plates that some particles have naturally, such as cellulose nanocrystals and graphene nanoplates.
-These particles have also been shown to naturally have nematic ordering at higher volume fractions that correspond to the volume fractions present at bijel interfaces.
-An investigation into how using rods or plate like particles would be instructive in identifying how onsager theory can be linked to bijel microstructure.
+This work utilized 2 ellipsoidal particle geometries chosen for comparisons to previous literature using this 
+particle geometry. Particles based on cellulose nanocrystals or graphene nanoplates are now in use to fabricate
+particle stabilized emulsions.These particles have also been shown to have capillary bridging and particle stacking,
+not seen in the particles used in this work. These particles in bulk have been shown to have some intrinsic ordering
+that can be predicted using onsager theory. An investigation into how using rods or plate like particles would be 
+instructive in identifying if onsager theory can be used in bijel formation and its link to bijel microstructure. 
 \textcolor{blue}{https://doi.org/10.1039/D1SM00367D}
 
-Colloidal systems made with cohesive and soft particles have been shown in the literature to have different glass transition points and rheological behavior from their hard sphere counterparts.
-In bijels, cohesive particles in particular have been suggested as a means to create "armored" bijels to improve their performance in catalytic materials, allowing higher flow rates to be used.
-Investigations into soft particles are of interest in biomedical engineering applications, with newly developed nanogels and hydrogels being suggested as drug carriers or vectors for stimuli response through temperature or pH.
+Colloidal systems made with cohesive and soft particles have been shown in the literature to have different glass 
+transition points and rheological behavior from their hard sphere counterparts. In bijels, cohesive particles in 
+particular have been suggested as a means to create "armored" bijels to improve their performance in catalytic materials, 
+allowing higher flow rates to be used. Investigations into soft particles are of interest in biomedical engineering 
+applications, with newly developed nanogels and hydrogels being suggested as drug carriers or vectors for stimuli 
+response through temperature or pH. LBM methods that implement the immersed boundary method can be used to model soft
+particles with a DLVO potential used to model electrostatics between particles. \textcolor{blue}{https://doi.org/10.1039/D3SM01648J}
 
-Another avenue of exploration would be the use of gradient or rotating magnetic fields in place of the constant magnetic fields used here.
-One study on bijel microstructure showed that a gradient in the particle volume fraction can be used to create a gradient in the eventual domain size.
-A gradient field may be able to generate a gradient in the nematic order parameter, affecting the particle packing of the bijel at different heights and varying the pore size as a function of height in the field gradient direction.
-In a ferrofluid or solution of magnetic colloids, a rotating field can assemble particles into chains or rings.
-In the context of bijel structural response, this can be used to tune bijel microstructure as this process can control the unjamming and rejamming of the particle monolayer, allowing for greater control over the resulting bijel microstructure than a constant field would have.
-In these simulations, the frequency of rotation would likely need to be tuned based upon how quickly particles respond to field in the bijel.
+Another avenue of exploration would be the use of gradient or rotating magnetic fields in place of the constant magnetic 
+fields used here. One study on bijel microstructure showed that a gradient in the particle volume fraction can be used to 
+create a gradient in the eventual domain size. A gradient field may be able to generate a gradient in the nematic order 
+parameter, affecting the particle packing of the bijel at different heights and varying the pore size as a function of 
+height in the field gradient direction. In a ferrofluid or solution of magnetic colloids, a rotating field can assemble 
+particles into chains or rings. In the context of bijel structural response, this can be used to tune bijel microstructure 
+as this process can control the unjamming and rejamming of the particle monolayer, allowing for greater control over the 
+resulting bijel microstructure than a constant field would have. In these simulations, the frequency of rotation would 
+likely need to be tuned based upon how quickly particles respond to field in the bijel.
+
+% Extensions to this work can be accomplished by investigating the effect of applying a magnetic field on the bijel 
+% while under shear. Ferrofluid models that predict bingham plastic like flows, $\frac{\eta}{eta_{f}} = 1 + \frac{Mn^{*}(\phi_p)}{Mn}$, 
+% have been developed and defined using the Mason number, $Mn = \frac{8\eta_{f} \dot{\gamma}}{\mu_{0} \mu_{f} \beta^{2} H_0^2}$. 
+% \textcolor{blue}{https://doi.org/10.1122/1.4935850, https://linkinghub.elsevier.com/retrieve/pii/S1359029405000385}
 
@@
 
-The author acknowledges Dr.
-Ulf Schiller and the members of the Schiller and Kuksenok groups for the discussions on the characterization and computational techniques used in this work.
-This work is supported by the US National Science Foundation under award numbers DMR-1944942 and OIA-2131996.
-Any opinions, findings, conclusions, or recommendations expressed in this material are those of the author(s) and do not necessarily reflect those of the National Science Foundation.
+The author acknowledges Dr. Ulf Schiller and the members of the Schiller and Kuksenok groups for the discussions on 
+the characterization and computational techniques used in this work. This work is supported by the US National Science 
+Foundation under award numbers DMR-1944942 and OIA-2131996. Any opinions, findings, conclusions, or recommendations 
+expressed in this material are those of the author(s) and do not necessarily reflect those of the National Science 
+Foundation.
 
-Clemson University is acknowledged for generous allotment of compute time on Palmetto cluster.
-This research used the Delta advanced computing and data resource which is supported by the National Science Foundation (award OAC 2005572) and the State of Illinois.
-Delta is a joint effort of the University of Illinois Urbana-Champaign and its National Center for Supercomputing Applications.
+Clemson University is acknowledged for generous allotment of compute time on Palmetto cluster. This research used the 
+Delta advanced computing and data resource which is supported by the National Science Foundation (award OAC 2005572) 
+and the State of Illinois. Delta is a joint effort of the University of Illinois Urbana-Champaign and its National 
+Center for Supercomputing Applications.
 
-This work used Delta at the University of Illinois Urbana Champaign through allocation PHY220131 from the Advanced Cyberinfrastructure Coordination Ecosystem: Services $\&$ Support (ACCESS) program, which is supported by National Science Foundation grants 2138259, 2138286, 2138307, 2137603, and 2138296.
+This work used Delta at the University of Illinois Urbana Champaign through allocation PHY220131 from the Advanced 
+Cyberinfrastructure Coordination Ecosystem: Services $\&$ Support (ACCESS) program, which is supported by National 
+Science Foundation grants 2138259, 2138286, 2138307, 2137603, and 2138296.

### 2025-03-06 chapters/lit_review.tex
Changes 1. Added conclusion in final remarks 2. Added hysteresis curve for prolate particles stabilized bijels in aim2 section 3. Added description of synthesis techniques in lit review

@@
 
-\textcolor{blue}{https://www.mdpi.com/2311-5521/5/3/150}
+% \textcolor{blue}{https://www.mdpi.com/2311-5521/5/3/150}
 
-\section{Colloidal glasses}
+% \section{Colloidal glasses}
 
-\begin{itemize}
-    \item https://pubs.acs.org/doi/10.1021/acsmacrolett.6b00826
-    \item Add stuff on dynamic heterogeneity
-    \begin{itemize}
-        \item https://pubs.rsc.org/en/content/articlelanding/2012/sm/c2sm25267h
-    \end{itemize}
-    \item Add stuff on particle jamming
-    \begin{itemize}
-        \item https://journals.aps.org/rmp/pdf/10.1103/RevModPhys.82.2633
-    \end{itemize}
-    \item Add stuff on cooperatively rearranging regions
-        \begin{itemize}
-            \item https://doi.org/10.1038/ncomms4829
-            \item https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.110.188301
-            \item https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.107.065702
-        \end{itemize}
-    \item Add stuff on reentrant glass phenomena 
-    \begin{itemize}
-        \item https://doi.org/10.1209/0295-5075/86/58001
-    \end{itemize}
-\end{itemize}
+% \begin{itemize}
+%     \item https://pubs.acs.org/doi/10.1021/acsmacrolett.6b00826
+%     \item Add stuff on dynamic heterogeneity
+%     \begin{itemize}
+%         \item https://pubs.rsc.org/en/content/articlelanding/2012/sm/c2sm25267h
+%     \end{itemize}
+%     \item Add stuff on particle jamming
+%     \begin{itemize}
+%         \item https://journals.aps.org/rmp/pdf/10.1103/RevModPhys.82.2633
+%     \end{itemize}
+%     \item Add stuff on cooperatively rearranging regions
+%         \begin{itemize}
+%             \item https://doi.org/10.1038/ncomms4829
+%             \item https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.110.188301
+%             \item https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.107.065702
+%         \end{itemize}
+%     \item Add stuff on reentrant glass phenomena 
+%     \begin{itemize}
+%         \item https://doi.org/10.1209/0295-5075/86/58001
+%     \end{itemize}
+% \end{itemize}
 

### 2025-03-06 chapters/paper2.tex
Changes 1. Added conclusion in final remarks 2. Added hysteresis curve for prolate particles stabilized bijels in aim2 section 3. Added description of synthesis techniques in lit review

@@
-Stimuli responsive emulsions have seen interest for use in fields such
-as enhanced oil recovery, porous material templates, in-situ reaction
-seperation systems and drug delivery scaffolds.
-\cite{tang_stimuli-responsive_2016,} \cite{bago_rodriguez_capsules_2019}
-These applications are enabled through stimuli response driven
-microstructure modification, changing the permeability, sueface area and
-morphology of the emulsion. Leveraging advances in particle synthesis
-techniques and citing concerns over surfactant toxicity and
-environmental concerns, particle stabilized emulsions have made a
-resurgence in popularity after their discovery in 1907 by Ramsden and
-Pickering. \cite{rozynek_opening_2019} \cite{zhou_magnetic_2011} Stimuli
-response has been enabled in particle stabilized emulsions using pH,
-temperature or chemical composition changes.
-\cite{maingret_dextran-based_2020} \cite{lin_ph-responsive_2018}
-\cite{raju_ph-responsive_2018} \cite{zhang_ph_2022}
+Stimuli-responsive emulsions have attracted significant interest for applications in enhanced oil recovery, porous material templating, 
+in-situ reaction separation systems, and drug delivery scaffolds \cite{tang_stimuli-responsive_2016, bago_rodriguez_capsules_2019}. 
+These applications are facilitated by stimuli-induced microstructural modifications, which alter the permeability, surface area, and 
+morphology of the emulsion. Advancements in particle synthesis techniques, along with growing concerns over surfactant toxicity and 
+environmental impact, have contributed to the renewed interest in particle-stabilized emulsions since their initial discovery by Ramsden 
+and Pickering in 1907 \cite{rozynek_opening_2019, zhou_magnetic_2011}. Stimuli-responsive behavior in these emulsions has been achieved 
+through changes in pH, temperature, or chemical composition 
+\cite{maingret_dextran-based_2020, lin_ph-responsive_2018, raju_ph-responsive_2018, zhang_ph_2022}.
 
-Owing to its tortuous, co-continuous domain morphology, bicontinuous
-interfacially jammed emulsion gels (bijel) are studied for their
-possible applications to fabricate membranes, catalyst supports, battery
-electrodes and pharmaceutical products. \cite{yabuno_preparation_2020}
-\cite{samdani_bicontinuous_2017} \cite{cha_bicontinuous_2019}
-\cite{garcia_scalable_2019} \cite{santiago_cordoba_aerobijels_2020}
-Bijels are formed through the arresting of spinodal decomposition of
-partially miscible fluids. \cite{stratford_colloidal_2005}
-\cite{herzig_bicontinuous_2007} \cite{tavacoli_novel_2011} Once phase
-separation begins, the incipient interface begins to sweep through the
-system causing particles to begin to adsorbing into it. Once the
-interfacial area matches that of the cross sectional area of the
-adsorbed particles, the structure jams in place.
-\cite{stratford_colloidal_2005} \cite{herzig_bicontinuous_2007}
-\cite{tavacoli_novel_2011} After their discovery in simulations and
-subsequent synthesis in experiments, a rich diversity of bijel
-literature has developed around various fluid systems that allow for
-bijel synthesis, methods to fabricate them at scale and their
-applications.
+Due to their tortuous, co-continuous domain morphology, bicontinuous interfacially jammed emulsion gels (bijels) have been 
+extensively studied for applications in membrane fabrication, catalyst supports, battery electrodes, and pharmaceutical 
+products \cite{yabuno_preparation_2020, samdani_bicontinuous_2017, cha_bicontinuous_2019, garcia_scalable_2019, santiago_cordoba_aerobijels_2020}.  
+Bijels form through the arrested spinodal decomposition of partially miscible fluids 
+\cite{stratford_colloidal_2005, herzig_bicontinuous_2007, tavacoli_novel_2011}. During phase separation, the emerging interface propagates 
+through the system, driving particle adsorption. Once the available interfacial area matches the total cross-sectional area of the adsorbed 
+particles, the structure becomes jammed in place \cite{stratford_colloidal_2005, herzig_bicontinuous_2007, tavacoli_novel_2011}. Since their 
+initial discovery in simulations and subsequent experimental synthesis, a diverse body of literature has emerged, exploring fluid systems 
+compatible with bijel formation, scalable fabrication techniques, and potential applications.
 
@@
 \section{Results}\label{sec:results_p2}
+\subsection{Hysteresis curve}\label{section:hysteresis_curve}
+
+Bijels have proposed applications as soft matter based material templates, drug delivery vectors and separations systems. The materials 
+performance in each application is dependent upon the microstructure of the bijel template. Many of the applications listed above benefit 
+from stimuli response, allowing for in-situ microstructure tuning to modify permeability of the material. We want to understand whether 
+bijels provide access to reversible structural modifications which would allow stimuli responsive bijels to be used in in-situ applications.
+
+We begin our investigation by characterizing the microstructure changes observed on bijels stabilized with prolate ellipsoids with a 
+particle volume fraction of $\phi_p = 0.1$. We apply a constant magnetic field of $\bar{B}_z = 0.2$ onto bijels that were simulated 
+with no magnetic field. Once the microstructure has reached its new state, we ramp up the magnetic field to $\bar{B}_z = 0.5$ and 
+finally $\bar{B}_z = 1$. We then apply the opposite procedure to reduce the applied field strength, resulting in a magnetic field 
+ramp of $\bar{B}_z: 0 \rightarrow 0.2 \rightarrow 0.5 \rightarrow 1 \rightarrow 0.5 \rightarrow 0.2 \rightarrow 0$.We characterize the 
+microstructure changes observed through calculating a characteristic length scale, called the average domain size. We calculate the hysteresis 
+curve by calculating the domain size at the final timestep of each magnetic field change. We then plot these domain sizes against the magnetic field 
+applied to obtain them and split them in the descending and ascending magnetic field directions to demonstrate the differences observed. We plot 
+these results in Figure \ref{fig:hysteresis_curve}
+
+\begin{figure} 
+    \centering 
+    \includegraphics[scale=0.5]{../figures/results/paper2/hysteresis_curve.png} 
+    \caption{Plot of the hysteresis curve of a bijel stabilized by magnetically responsive prolate particles. We observe that the domain size increases as we increase the applied
+    magnetic field strength. However, upon decrease of the field strength, we see that the microstructure does not return to its previous value.} 
+    \label{fig:hysteresis_curve} 
+\end{figure}
+
+Figure \ref{fig:hysteresis_curve} illustrates the hysteresis behavior of magnetically responsive bijels. We observe a hysteresis response of the 
+bijel microstructure, characterized by a non-return of the microstructure to the original average domain size value when reducing the applied 
+magnetic field strength. The increase in the average length scale when applying the magnetic field is due to domain coarsening caused by 
+reorientation of particles to the magnetic field strength, reducing the interfacial coverage. When decreasing the magnetic field strength, 
+we observe that the domain size does not return to the original value meaning that that the microstructure of the bijel is unaffected by 
+the reduction in magnetic field. This suggests that the particles at the interface are in a kinetically trapped configuration.
+
 \subsection{Field strength dependence on domain
-size}\label{field-strength-dependence-on-domain-size}
+size}\label{section:field-strength-dependence-on-domain-size}
 
@@
 \centering 
-\includegraphics[scale=0.4]{../figures/results/paper2/particle_viz-field_on.png} 
+\includegraphics[scale=0.2]{../figures/results/paper2/particle_viz-field_on.png} 
 \caption{Visualizations of bijels stabilized with oblate and prolate particles simulated at $t = 0$ (left column) and $t = 10^5$ (right column).
@@
 \centering 
-\includegraphics[scale=0.35]{../figures/results/paper2/domain_size-field_on-scaled.png} 
+\includegraphics[scale=0.4]{../figures/results/paper2/domain_size-field_on-scaled.png} 
 \caption{Plots of domain size with different timescales.
@@
 \centering 
-\includegraphics[scale=0.4]{../figures/results/paper2/particle_viz-field_up.png} 
+\includegraphics[scale=0.2]{../figures/results/paper2/particle_viz-field_up.png} 
 \caption{Visualizations of bijels stabilized with oblate and prolate particles simulated at $t = 0$ (left column) and $t = 10^5$ (right column).
@@
 \centering 
-\includegraphics[scale=0.5]{../figures/results/paper2/interface_angle-nint-field_up.png} 
+\includegraphics[scale=0.4]{../figures/results/paper2/interface_angle-nint-field_up.png} 
 \caption{Plots of the average interfacial angle $\psi$ and the number of particles on the interface $n_{int}$ on the left and right respectively, plotted against time for bijels stabilized with ellipsoidal particles with aspect ratio 2.
@@
 \centering 
-\includegraphics[scale=0.5]{../figures/results/paper2/interface_angle-nint-field_down.png} 
+\includegraphics[scale=0.4]{../figures/results/paper2/interface_angle-nint-field_down.png} 
 \caption{Plots of the average interfacial angle $\psi$ and the number of particles on the interface $n_{int}$ on the left and right respectively, plotted against time for bijels stabilized with ellipsoidal particles with aspect ratio 2.

### 2025-03-06 chapters/final_remarks.tex
Changes 1. Completed conclusion except for aim 3

@@
 characterized as a change in the directional tortuosity and distribution of channel widths as a function of the distance from the 
-interface. The curvature also becomes more negative as the applied field strength is increased. The microstructure anisotropy is caused
-by direction specific jamming of the particle monolayer originating from particle ordering to the magnetic field.
+interface. The response characterized was particle morphology specific due to the orientation of the particle magnetic moment with 
+respect to the direction of the long axis of the particle. This causes the particles to arrange differently on the interface. The 
+microstructure anisotropy is caused by direction specific jamming of the particle monolayer originating from particle ordering to 
+the magnetic field. The direction specific jamming originates from the orientation of the particles to the magnetic field. The direction
+specific jamming also reduces the local curvature of the system as the interface location moves with the particle.
 
-When investigating the particle monolayer, the orientational order changes as a function of the applied field strength and has particle
-morphology specific time evolution. The interface angle was also characterized and shown to have magnetic field dependence, although
-this was attributed to the orientational ordering of the particles on the interface. When analyzing the ordering of particles on the
-interface, disc-like particles see lowered local ordering as the magnetic field strength is increased while rod-like particles see
-greater local ordering. These properties are attributed to how those particle morphologies prefer to orient themselves at interfaces
-to one another, with disc like particles preferring to stack while rod like particles order side to side or end to end.
+To investigate the role of the particle monolayer in greater detail, we characterize the orientational order to the magnetic field,
+angle to the interface and local particle ordering at the interface. The orientational order changes as a function of the applied field 
+strength and has particle morphology specific time evolution. When investigating the average interfacial angle of the particles to the 
+interface, it is shown how the capillary interactions with the interface differ, leading to the time evolution differences observed.
+When analyzing the ordering of particles on the interface, disc-like particles see lowered local ordering as the magnetic field strength is 
+increased while rod-like particles see greater local ordering. These properties are attributed to how those particle morphologies prefer 
+to orient themselves at interfaces to one another, with disc like particles preferring to stack while rod like particles order side to side 
+or end to end.
 
-In Aim 2
+In Aim 2, bijels stabilized by ellipsoidal particles demonstrate responses to an applied magnetic field. When applying a magnetic field
+onto a bijel template simulated with no magnetic fields, we see an average microstructure change of up to 5 \%. This microstructure change
+arises from the magnetic field driven re-orientation of particles at the interface. Particle reorientation creates microstructure anisotropy
+arising from the alignment of particles to the magnetic field. When analyzing the particle monolayer, we characterize the alignment of particles
+to the field direction, average interface angle and the local ordering of the particles. We demonstrate that the average interface angle increases
+as the particles reorient to the field before the capillary forces of the interfaces causes the interface to move, until jamming of the monolayer takes
+place. The local particle order during this process decreases for oblate particles and increases for prolate particles. We characterize that the local 
+order of the particles controls the timescales of response.
 
-In Aim 3
+When investigating the effect of pre-existing order of the particle monolayer, we show that the structural response of the bijel is dependent upon the
+difference between the field applied to make the bijel and the applied field when the field is applied in the same direction. We also characterize that the
+local particle monolayer is dependent upon the pre-existing order of the bijel. When switching off the magnetic field onto bijels made with a magnetic field,
+we see that the microstructure remains resilient to the removal of the magnetic field. We characterize that while there are differences in the particle monolayer,
+these differences manifest as when domain coarsening begins. When characterizing the hysteresis curve of the bijels stabilized with prolate particles,
+we see the effect of this.
+
+In Aim 3 we investigate the rheological response of bijels stabilized with ellipsoidal particles under constant shear and show that the application of magnetic
+fields changes the shear thinning properties of bijels.
 

### 2025-03-09 chapters/dissertation-tap.tex
Changes 1. Updated anisotropic microstructure investigation figures for paper 2 2. Updated title of dissertation to better reflect type of particles used

@@
 \title[First Line of Title Second Line of Title]{Lattice Boltzmann simulations of magnetically responsive\\
-anisotropic particle stabilized emulsions}
+ellipsoidal particle stabilized emulsions}
 \author{Nikhil Karthikeyan}

### 2025-03-09 chapters/paper3.tex
Changes 1. Reworded introduction and lit review and addressed grammar and vocab issues 2. Fixed some referencing problems in the document 3. Fleshed out introduction in paper 2 4. Added sections for results in paper 3
Changes 1. Fleshed out Aim 3 section with text and results

@@
 \cite{bonaccorso_shear_2020} It has also been shown how at curved interfaces, ellipsoidal particles
+
+\section{Introduction}
 
@@
 presence of monogels, made by remixing the phase separated liquid domains of the bijel while the electrostatic
-interactions between particles maintains the structure of the particle monolayer. \textcolor{blue}{https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.103.255502}
-This behavior is system specific, suggesting the fluid system plays a role in this behavior as well. \textcolor{blue}{https://doi.org/10.1002/adfm.201002562} 
+interactions between particles maintains the structure of the particle monolayer. \cite{sanz_colloidal_2009} 
+This behavior is system specific, suggesting the fluid system plays a role in this behavior as well. \cite{tavacoli_novel_2011}
 \cite{bai_dynamics_2015} Investigations have identified that confined bijels under shear undergo elongation of
@@
 ferrofluids and magnetic emulsions have showed how the rheological properties vary drastically as a function of the field strength due to the orientation of the 
-particles. \textcolor{blue}{https://doi.org/10.1016/j.colsurfa.2012.06.026} The orientation of the particle to shear as well as the nematic order of particles 
+particles. \cite{qiao_magnetorheological_2012} The orientation of the particle to shear as well as the nematic order of particles 
 can cause shear banding and a smaller effective viscosity owing to a smaller cross sectional area being presented to the direction of shear.
@@
 
-\textcolor{blue}{https://doi.org/10.1073/pnas.0812519106}
+We begin our investigation by analyzing the domain size change over time for bijels stabilized by ellipsoidal particles. We also
+focus our attention on the effect of the initial state of the particle monolayer, in addition to the addition or removal of magnetic
+fields. We perform this analysis on bijels stabilized by oblate and prolate particles. Bijel templates simulated in Aim 1 with no
+field and a field strength of $\bar{B} = 1$ stabilized with a particle volume fraction $\phi_p = 0.15$. We apply a field strength of
+$\bar{B} = 1$ or switch off the applied field. This results in four setups, $\bar{B}:0\rightarrow 0$, $\bar{B}:0\rightarrow 1$,
+$\bar{B}:1\rightarrow 0$ and $\bar{B}:1\rightarrow 1$. We then define a shear capillary number, 
+$Ca_s = \frac{\dot{\gamma} R_{s} \eta_{f}}{\sigma}$ where $\dot{\gamma}$ is the applied strain rate, $R_s$ is the equivalent
+spherical radius of the particles, $R_s = 7.9$, $\eta_f$ is the dynamic viscosity of the fluid and $\sigma$ is the surface tension
+of the interface. We use five shear numbers, $Ca_s = 10^{-4}, 50^{-5}, 10{^-5}, 50^{-6}, 10^{-6}$.
 
-\begin{itemize}
-    \item Shear banding analyzed through looking at change in particle velocity in the x direction
-    \item Shear banding analyzed through looking at change in $Q_6$ in the x direction
-    \item 
-\end{itemize}
+\section{Results}\label{sec:results_p3}
+\subsection{Microstructure change}
+
+First we plot the domain size of each system over time to analyze the effect of application of shear and magnetic fields.
+
+\begin{figure} 
+    \centering 
+    \includegraphics[scale=0.3]{../figures/results/paper3/domain_size-time_compare.png} 
+    \caption{Comparisons of the time evolution of the average domain size for bijels stabilized by ellipsoidal particles undergoing
+             various shear rates under four processes. Initially, the domain size coarsens for all runs under applied shear before
+             reducing in some cases.} 
+    \label{fig:domain_size_time_shear} 
+\end{figure}
+
+From Figure \ref{fig:domain_size_time_shear}, domains generally coarsen with time but the presence of a magnetic field 
+significantly alters the coarsening dynamics due to magnetic field driven particle reordering on the interface. In the 
+$\bar{B}: 1 \to 0$ and $\bar{B}: 1 \to 1$ cases, an initial plateau in domain size is observed, followed by a divergence in 
+growth depending on $Ca$. The shear rate appears to influence domain coarsening, with higher $Ca_s$ leading to delayed or 
+suppressed growth, especially in the presence of a field. The difference between applying $\bar{B}: 0 \to 1$ and 
+removing $\bar{B}: 1 \to 0$ the field demonstrates the stability of the particle monolayer when a field is switched off.
+There is little difference in the qualitative trends of domain size change for bijels stabilized with oblate or prolate particles,
+This analysis highlights how the interplay between shear, capillary effects, and magnetic interactions governs bijel 
+microstructural stability and evolution, offering insights into tunable bijel design for applications requiring controlled 
+domain morphology. Domain coarsening
+
+\begin{figure} 
+    \centering 
+    \includegraphics[scale=0.3]{../figures/results/paper3/gaussian-time_compare.png} 
+    \caption{Plots of the time evolution of the area averaged Gaussian curvature $\langle K \Sigma^{-2} \rangle$ for four 
+             processing histories applied to bijels stabilized with oblate and prolate ellipsoids. We demonstrate that the 
+             magnitude of the gaussian curvature reduces for all systems except for $\bar{B}: 0 \to 1$.} 
+    \label{fig:gaussian_curvature_time_shear} 
+\end{figure}
+
+Figure \ref{fig:gaussian_curvature_time_shear} reveals that the area averaged Gaussian curvature generally decreases in magnitude over time for all cases except 
+$\bar{B}: 0 \to 1$. We also characterize that the curvature evolution of all systems are shear independent. $\bar{B}: 0 \to 1$ is
+unique because particle rearrangements at the interface dominates the dynamics of the microstructure, not observed in all other
+cases. From the time evolution of the curvature, we show that the same mechanism drives domain coarsening in all cases. Domain
+coarsening is driven through a reduction in the interfacial area covered by the particle monolayer. Previous investigates have 
+demonstrated how the orientation and arrangement of particles on the interface affect the domain size. 
+\cite{gunther_timescales_2014} We focus our investigation on this aspect in the following section.
+
+\subsection{Particle properties}
+
+Particles at the interface of bijels stabilized with ellipsoidal particles reorient at the interface to minimize interfacial and
+steric energies. \cite{gunther_timescales_2014} The particles stabilizing bijels in confined systems under shear have been shown to
+orient to the direction of shear and ejected from the interface at sufficiently long times or shear.\cite{bonaccorso_shear_2020} 
+We probe these aspects of the particle monolayer in this section.
+
+\begin{figure} 
+    \centering 
+    \includegraphics[scale=0.3]{../figures/results/paper3/angle_to_cartesian-SS.png} 
+    \caption{Comparisons of the initial and final particle orientations of the particles to each cartesian direction under
+             four processing histories for bijels stabilized with oblate and prolate ellipsoids at multiple shear rates. We show
+             shear dependent ordering of the particle monolayer if the initial particle monolayer begins with particle order.} 
+    \label{fig:particle_orientation_cartesian_shear} 
+\end{figure}
+
+From Figure \ref{fig:particle_orientation_cartesian_shear} we see that with bijel templates simulated under $\bar{B} = 0$, the
+particles adopt a random orientation. Upon application of shear, we see that there is little directional ordering to the 
+shear direction. Upon application of the magnetic field, the particle order to the direction of the magnetic field. When 
+investigating the orientational ordering of a bijel simulated under a field strength of $\bar{B} = 1$, we see that there is
+shear dependent decay of the orientational ordering when the magnetic field is removed. We also characterize similar behavior
+when maintaining the applied field, indicating that two reasons for surface area reduction is present. These mechanisms are attributed
+to reorientation of particles at the interface or ejection of particles from the interface. We can characterize the former mechanism
+using the average interfacial angle between the particle and the interface $\langle \psi \rangle$.
+
+\begin{figure} 
+    \centering 
+    \includegraphics[scale=0.3]{../figures/results/paper3/psi-time_compare.png} 
+    \caption{Comparisons of the interfacial angle of bijels stabilized by ellipsoidal particles as a function of 
+             the applied shear rate at four different processing histories. We show that upon application of shear
+             particles tilt out of the interface reduces the interfacial area stabilized. $\bar{B}: 0 \to 1$ shows 
+             large variations in the interface angle.} 
+    \label{fig:interface_angle_shear} 
+\end{figure}
+
+From Figure \ref{fig:interface_angle_shear}, we demonstrate that there is a slow increase in the interface angle over time for all cases
+except for $\bar{B}: 0 \to 1$. Shear dependent $\langle \psi \rangle$ can be observed for some of the systems, indicating that the mechanism
+of domain coarsening differs.The data for $\bar{B}: 0 \to 1$ is characterized as such due to a particle reorientation at the interface
+in response to the field just after the magnetic field has been applied. To reduce the interfacial energy as the particles tilt from the 
+interface, the interface moves with the particle until it jams in place. We can characterize the impact of the interfacial angle on the 
+particle packing using the radial distribution function (rdf).
+
+\begin{figure} 
+    \centering 
+    \includegraphics[scale=0.3]{../figures/results/paper3/rdf-SS.png} 
+    \caption{Comparisons of the initial and final radial distribution function of the particles of bijels stabilized by ellipsoidal 
+    particles as a function of the applied shear rate at four different processing histories. We show that there are minor differences
+    in the particle ordering at the interface, suggesting that the particle tilting affects the coverage of particles at the interface.} 
+    \label{fig:rdf_shear} 
+\end{figure}
+
+From Figure \ref{fig:rdf_shear}, we show that the change in the packing of the particles on the interface is not correlated to the change 
+in the interfacial angle of the particles on the interface when changing the applied field strength in all cases. We then characterize the proportion 
+of particles on the interface to investigate how the proportion of particles on the interface changes and its impact on the interfacial area.
+
+\begin{figure} 
+    \centering 
+    \includegraphics[scale=0.3]{../figures/results/paper3/n_int-time_compare.png} 
+    \caption{Comparisons of the proportion of particles on the interface of bijels ($n_{int}$) stabilized by ellipsoidal particles as a function of 
+             the applied shear rate at four different processing histories. We show that upon application of shear, many cases have a 
+             reduction in the number of particles on the interface while in others it stays the same. For cases where $n_{int}$ reduces, we can 
+             attribute the domain size coarsening to this effect.} 
+    \label{fig:particles_interface_prop_shear} 
+\end{figure}
+
+We show in Figure \ref{fig:particles_interface_prop_shear} that when the magnetic field is kept the same between the template and during shear, the
+proportion of particles on the interface ($n_{int}$) stays approximately the same. However when changing the applied field strength, $n_{int}$ more 
+sensitive to shear. Here we also characterize that increasing the applied field strength reduces $n_{int}$ more than decreasing it. This is consistent
+with the amount of coarsening observed for each case seen in Figure \ref{fig:domain_size_time_shear} where $\bar{B}:0 \rightarrow 1$ shows the largest
+change. Next, we characterize how the microstructure and particle properties affect the constant rheology properties of the bijels.
+
+\subsection{Viscosity measurement}
+
+The ordering of the particles play an important role in determining the rheology of suspensions as ordered particles can slip over one another
+before the structure breaks. The adsorption of particles on the interface of a bijel could affect how this slip occurs. Previous work investigating
+the rheology of bijels have determined shear thinning behavior characterized with a Herschel-Buckley fit equation. We perform this analysis on the
+structures we have simulated. First, we plot the shear stress over time.
+
+\begin{figure} 
+    \centering 
+    \includegraphics[scale=0.3]{../figures/results/paper3/stress-time_compare.png} 
+    \caption{Time evolution of the shear stress of bijels stabilized with ellipsoidal particles as a function of the applied strain rate as
+             a function of the initial microstructure and applied magnetic field. The observed stress response is difficult to say when a steady
+             state is reached.} 
+    \label{fig:stress_time} 
+\end{figure}
+
+Figure \ref{fig:stress_time} shows that there is no definitive steady state value of the shear stress obtained from the experiments performed. This is
+attributed to the coarsening of the domains and reorientation of particles at the interface. To characterize the viscosity, we identify pseudo-steady
+state regions within each of the shear stress plots and fit the stress identified within this pseudo-steady state region to the strain rate. We fit 
+the stress to the strain using a Herschel-Buckley rheology model, $\sigma_{xz} = \sigma_{y} + K(\dot{\gamma})^{n}$. $\sigma_{xz}$ is the experimental
+shear stress, $\sigma_{y}$ is the yield stress of the bijel, $K$ is the flow consistency index and $n$ is the flow index.
+Where appropriate, we include results corresponding to a shear capillary number of $Ca_s = 10^{-6}$.
+
+\begin{figure} 
+    \centering 
+    \includegraphics[scale=0.4]{../figures/results/paper3/stress_strain-all.png} 
+    \caption{Fitting the experimental shear stress to the strain rate using the Herschel Buckley model. We characterize the bijels are 
+             shear thinning in all cases. We show that the bijels become less shear thinning as the particle order increases. We also
+             demonstrate that the particle ordering affects the yield stress differently for particles stabilized by oblate and 
+             prolate particles.} 
+    \label{fig:stress_strain} 
+\end{figure}
+
+From Figure \ref{fig:stress_strain}, we show that bijels stabilized with ellipsoidal particles are shear thinning regardless of the initial 
+microstructure and the processing applied. We quantify the fit and tabulate the results in Table \ref{tab:rheology_fit}. From Table 
+\ref{tab:rheology_fit}, we can see that as particle order increases, signified by an increase in the initial magnetic field, the flow index 
+of the material increases, indicating more Newtonian fluid like behavior. This is due to the more ordered particles being able to slip
+while undergoing fluid particle interactions without affecting other particles due to orientational ordering imposed from the application 
+of magnetic fields.
+
+\begin{center}
+    \begin{tabular}{||c c c c c||} 
+     \hline
+     Processing & $\alpha$ & $n$ & $K \frac{\Delta m (\Delta t)^{n-2}}{\Delta m} $ & $\sigma_{y} \frac{\Delta m}{\Delta m (\Delta t)^2}$ \\ [0.5ex] 
+     \hline\hline
+     $\bar{B}: 0 \rightarrow 0$ & 0.5 & 0.522 & 1.030 & $1.054 \cdot 10^{-4}$ \\ 
+     \hline
+     $\bar{B}: 0 \rightarrow 1$ & 0.5 & 0.570 & 0.975 & $5.365 \cdot 10^{-5}$ \\
+     \hline
+     $\bar{B}: 1 \rightarrow 0$ & 0.5 & 0.629 & 0.886 & $4.238 \cdot 10^{-5}$ \\
+     \hline
+     $\bar{B}: 1 \rightarrow 1$ & 0.5 & 0.637 & 0.914 & $1.714 \cdot 10^{-5}$ \\
+     \hline
+     $\bar{B}: 0 \rightarrow 0$ & 2 & 0.569 & 0.984 & $5.803 \cdot 10^{-5}$ \\
+     \hline
+     $\bar{B}: 0 \rightarrow 1$ & 2 & 0.609 & 0.944 & $4.101 \cdot 10^{-5}$ \\
+     \hline
+     $\bar{B}: 1 \rightarrow 0$ & 2 & 0.604 & 0.923 & $5.496 \cdot 10^{-5}$ \\
+     \hline
+     $\bar{B}: 1 \rightarrow 1$ & 2 & 0.618 & 0.909 & $7.161 \cdot 10^{-5}$ \\ [1ex] 
+     \hline
+    \end{tabular}
+\label{tab:rheology_fit}
+\end{center}
+
+We characterize that the yield stress of bijels stabilized with oblate particles decrease as particle order increases while decreasing then increasing for 
+prolate particles. This can be attributed to the morphology differences that lead to different interfacial packing, characterized with the rdf in Figure 
+\ref{fig:rdf_shear}. We see that bijels stabilized with oblate particles do not pack as efficiently on the interface when a magnetic field is applied,
+meaning that the interface can buckle more easily. In contrast prolate particles pack more densely which leads to the greater yield stress. The results
+suggest that increasing the magnetic field onto bijels stabilized with prolate particles also causes the particle monolayer to more easily buckle 
+upon application of shear.

### 2025-03-09 chapters/introduction.tex
Changes 1. Added more figures for introduction and literature review 2. Completed introduction and lit review for draft 1 3. Added figures for Aim 3 section

@@
     \centering
-    \includegraphics[scale = 2]{figures/literature_review/STRIPPS.jpg}
+    \includegraphics[scale = 4]{figures/introduction/STrIPS.jpg}
     \caption{STrIPS in action. Extrusion of the bijel casting mixture into a non-solvent bath, followed by removal of solvent from 
@@
 
-\textcolor{blue}{ADD IN PICTURE FROM THAM 2021 AND CUI 2013 ON EXAMPLES OF STIMULI RESPONSE IN EMULSIONS}
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale = 1]{figures/introduction/magnetophoresis_emulsion.jpeg}
+    \caption{Enhanced oil recovery of oil from water using magnetically responsive emulsion stabilizers, allowing for 
+             locomotion and controlled coalescence of cargo from a matrix phase using magnetic fields relevant in 
+             water filtration and oil refining applications. Reproduced from Tham et al. 2021 under the ACS standard license \cite{tham_magnetophoresis_2021}}
+    \label{fig:magnetophoresis_droplet}
+\end{figure}
 
@@
 manipulate emulsion stability, control droplet movement, and induce elongation in emulsion droplets 
-\cite{tham_magnetophoresis_2021, cui_stabilizing_2013, melle_pickering_2005}.  
+\cite{tham_magnetophoresis_2021, cui_stabilizing_2013, melle_pickering_2005}. One such example is shown in Figure \ref{fig:magnetophoresis_droplet}
+where enhanced oil recovery was performed using magnetically responsive particle stabilizers which could capture oil droplets,
+move the droplets away from the matrix and cause controlled coalescence elsewhere.
 In the case of bijels, spherical particle-stabilized systems subjected to a magnetic field exhibited no significant microstructural changes 
@@
 
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale = 0.4]{figures/introduction/anisotropic_particles_assembly.jpg}
+    \caption{Assembly of prolate particles on a flat interface at various interfacial coverages and field strengths,
+             showing the self assembly into chains that ellipsoidal particles can undergo under applied magnetic fields at
+             interfaces. Reproduced from Davies et al. under the Creative Commons CC BY license \cite{davies_assembling_2014}}
+    \label{fig:anisotropic_assembly}
+\end{figure}
+
 Anisotropic particles at interfaces have been shown to undergo self-assembly due to the presence of multipolar pressure fields induced by interface 
-deformation. Similarly, self-assembly has been observed for ellipsoidal particles at interfaces under magnetic fields. Additionally, ellipsoidal particles 
-exhibit magnetic field-controlled orientation at interfaces, as demonstrated by Bresme and Faraudo \cite{bresme_orientational_2007, davies_interface_2014}.  
+deformation caused by magnetic stimuli, visualized in Figure \ref{fig:anisotropic_assembly}. \cite{bresme_orientational_2007, davies_interface_2014}
 When subjected to a magnetic field, assemblies of multiple ellipsoidal particles exhibit energy minima at orientations different from those of isolated 
@@
 In many of the fabrication processes described above, the rheology of the bijel casting mixture plays a crucial role 
-\cite{haase_continuous_2015, cai_bijels_2017, amirfattahi_fabrication_2024}. Ching demonstrated that, rheologically, bijels behave as colloidal 
-glasses percolating in 3D space \cite{ching_bijel_2022}. A shear capillary number, \( Ca_s \), is defined to correlate the applied strain rate 
-with the capillary forces derived from surface tension \cite{frijters_effects_2012, yang_capillary_2022}. This study aims to identify the effect 
-of the initial microstructure and applied field on the rheological properties of the bijel.
+\cite{haase_continuous_2015, cai_bijels_2017, amirfattahi_fabrication_2024}. Furthermore, the mechanical performance of the
+resulting bijel is a key constraint for bijels in cross flow reactors or water filtration applications. \cite{boakye-ansah_controlling_2020}
+Under high shear, the bijel can fail due to particles being ejected from the interface limiting the flow rate and pressure that can
+be used when using bijels as cross flow reactors or water filtration systems. Ching demonstrated that, rheologically, bijels behave 
+as colloidal glasses percolating in 3D space \cite{ching_bijel_2022}. This implies a yield stress above which flow of the material
+will initiate. Bijels are also shear thinning as fluid-particle interactions increase the effective viscosity at lower shear rates.
 
@@
 In this study, the yield stress and viscosity of the bijels will be examined as a function of the initial microstructure under various $Ca_s$ values. 
-The initial microstructure will be derived from bijels stabilized with ellipsoidal particles, synthesized both without a magnetic field and with a field 
+A shear capillary number, $Ca_s$, is defined to correlate the applied strain rate with the capillary forces derived from surface tension 
+\cite{frijters_effects_2012, yang_capillary_2022}. This study aims to identify the effect 
+of the initial microstructure and applied field on the rheological properties of the bijel.The initial microstructure will be 
+derived from bijels stabilized with ellipsoidal particles, synthesized both without a magnetic field and with a field 
 strength equal to the surface tension energy. Constant shear, defined by $Ca_s$, will be applied to determine the yield stress and non-Newtonian 
@@
 
-We will then investigate the complex rheology of the bijels by calculating the loss and storage moduli of the bijel microstructures described 
-earlier as a function of oscillatory shear. The loss and storage moduli describe the viscous and elastic behavior of the bijel, respectively, 
-allowing the gel point of the bijel to be determined as the point at which the storage modulus exceeds the loss modulus. Special attention will be 
-given to the state of the particles in all simulations, correlating changes in particle properties with observed rheological events. Additionally, 
-we will assess whether shear banding occurs.
+% We will then investigate the complex rheology of the bijels by calculating the loss and storage moduli of the bijel microstructures described 
+% earlier as a function of oscillatory shear. The loss and storage moduli describe the viscous and elastic behavior of the bijel, respectively, 
+% allowing the gel point of the bijel to be determined as the point at which the storage modulus exceeds the loss modulus. Special attention will be 
+% given to the state of the particles in all simulations, correlating changes in particle properties with observed rheological events. Additionally, 
+% we will assess whether shear banding occurs.

### 2025-03-09 chapters/lit_review.tex
Changes 1. Added more figures for introduction and literature review 2. Completed introduction and lit review for draft 1 3. Added figures for Aim 3 section

@@
 which stabilize emulsions by reducing interfacial tension, particles act as stabilizers by adsorbing at the interface between the dispersed and continuous phases, thereby 
-preventing direct contact between them. The Pieranski model, derived from \textcolor{blue}{insert derivation of Pieranski model}, is commonly used to determine the adsorption 
+preventing direct contact between them. The Pieranski model is commonly used to determine the adsorption 
 energy of a particle at an interface. It is expressed as $ G_{ads} = \sigma A_{rm} (1 - \cos{\theta_c})^2 $ where $G_{ads}$ represents the free energy reduction upon particle 
@@
 
-Bijels were first synthesized using Thermally Induced Phase Separation (TIPS) \cite{herzig_bicontinuous_2007, lee_bicontinuous_2010, bai_dynamics_2015}. 
+The existence of bijels was first identified computationally using a multicomponent lattice boltzmann method which looked at 
+the jamming of spherical particles in a binary fluid system with equal volume fraction of each fluid. 
+\cite{stratford_colloidal_2005} Once phase separation was initiated, the particles adsorb onto the interface until the interfacial
+area matches the cross sectional area of the particles at the interface, when domain coarsening is ceased. The simulation assumed
+an equal volume fraction of fluid components and neutrally wetting particles to not impart preferential curvature onto the interface.
+Figure \ref{fig:state_diagram_particle_emulsions} demonstrates a schematic derived from experimental results of particle stabilized
+emulsion microstructures that form when changing the volume fraction and particle contact angle.
+
+In experiments, bijels were first synthesized using Thermally Induced Phase Separation (TIPS) \cite{herzig_bicontinuous_2007, lee_bicontinuous_2010, bai_dynamics_2015}. 
 The process begins by identifying a small-molecule or polymer blend with a critical point, referred to as the casting mixture, and preparing it at a composition 
@@
 composition aligns with the critical point, the casting mixture undergoes spinodal decomposition, preventing nucleation and growth.
+
+\begin{figure}
+    \centering
+    \includegraphics[scale = 0.2]{figures/literature_review/state_diagram.jpg}
+    \caption{Formation criteria for a particle stabilized emulsion that can form bijel. 
+            Reproduced from Velankar 2015 using license number 1551968-1. \cite{velankar_non-equilibrium_2015}}
+    \label{fig:state_diagram_particle_emulsions}
+\end{figure}
 
@@
 
-\textcolor{blue}{Description of VIPS}
-
 Vapor Induced Phase Separation(VIPS) has also been identified as a technique for continuous fabrication of bijels. \cite{wang_scalable_2020} A quarternary casting mixture
@@
 This technique has been used to fabricate thin films of bijels blade and spray coated onto substrates.
-
-\textcolor{blue}{Description of homogenization}
 
@@
 
-\textcolor{blue}{Description of liquid in liquid printing}
+% \textcolor{blue}{Description of liquid in liquid printing}
 
-Enter something about this method. \cite{amirfattahi_fabrication_2024}
+% Enter something about this method. \cite{amirfattahi_fabrication_2024}
 
@@
     \caption{Schematic of a bijel with hard-sphere particles undergoing shear, demonstrating migration and detachment of particles at the interface. 
-    \cite{bonaccorso_shear_2020}}
+             Reproduced from Bonaccorso et al. under the Creative Commons CC BY License. \cite{bonaccorso_shear_2020}}
     \label{fig:bijel_under_shear}
@@
 
-\section{Stimuli response in particle stabilized emulsions}
+\section{Microstructure control in bijels}
 
-Kim et al. found that strong magnetic fields do not significantly alter the microstructure of a bijel stabilized with spherical particles, as the particles orient 
-to the field without affecting interface ordering. \cite{kim_bijels_2010} In contrast, Carmack and Millet demonstrated that polarizable fluids and particles under 
-an electric field show significant microstructural changes, with particles self-assembling into chains and forming cylindrical domains parallel to the applied field, 
-thus modifying the microstructure. \cite{carmack_tuning_2018}
+Kim et al. used a free energy based lattice boltzmann method coupled with particles and magnetic fields to investigate the influence of magnetic fields on 
+the microstructure of bijels stabilized with spherical particles. \cite{kim_bijels_2010}
+They observed that applying strong magnetic fields did not significantly alter the bijel microstructure, as the particles aligned with 
+the field without disrupting the interfacial ordering. This finding suggests that spherical particles, due to their isotropic shape, do 
+not induce anisotropic stresses on the interface when subjected to magnetic fields, thereby maintaining the structural integrity of the bijel.
+
+In contrast to the minimal impact of magnetic fields on bijels stabilized with spherical particles, Carmack and Millett investigated the effects of 
+applied electric fields on thin-film bijels using a Cahn-Hilliard coupled with Langevin dynamics computational model. \cite{carmack_tuning_2018} 
+Their study revealed that electric fields can induce significant microstructural changes in bijels, with particles self-assembling into chains and forming 
+cylindrical domains aligned parallel to the applied field, thereby modifying the overall microstructure. Carmack and Millet observed that the dielectric contrast 
+between liquid domains governs liquid domain alignment, and the dielectric contrast between colloidal particles and the liquid matrix induces dipolar particle 
+interactions. By changing the dielectric contrast between particle and fluid, different bijel morphologies could be formed. Additionally, particle chains were found to 
+act as nucleation sites for phase separation, influencing the resultant morphologies in terms of particle attachment to phase interface regions and average 
+channel diameter.
+
+While not strictly stimuli-responsive, microstructure modifications have been achieved by applying a particle volume fraction gradient during the formation of 
+bijels using Thermally Induced Phase Separation (TIPS). \cite{french_bicontinuous_2022} In their study, French et al. allowed particles to partially sediment in the bijel casting mixture
+before initiating thermal quenching. The gradient in particle volume fraction along the height of the reaction vessel caused the jamming point of the bijel
+to vary along the gradient axis, causing a channel size gradients of up to 2.8\% per millimeter, as measured using confocal microscopy.
 
@@
 functional to recover interfacial dynamics and effects in a thermodynamically consistent manner. Often, a square gradient free energy is used for 
-simplicity and ease of implementation. The mean field theory
-
-The non-ideal mixing dynamics are recovered during the "recoloring" step, of which the technique proposed by Latva-Kokko and Rothman is more commonly 
-used for soft matter flows. \cite{liu_multiphase_2016}
+simplicity and ease of implementation. The mean field theory The non-ideal mixing dynamics are recovered during the "recoloring" step, of which the 
+technique proposed by Latva-Kokko and Rothman is more commonly used for soft matter flows. \cite{liu_multiphase_2016}

### 2025-03-09 licenses/licenses.tex
Changes 1. Made tex files human readable again 2. Added content to paper3 tex file 3. Added licenses to some of the images from other papers
Changes 1. Added more figures for introduction and literature review 2. Completed introduction and lit review for draft 1 3. Added figures for Aim 3 section

@@
 \begin{itemize}
-    \item Continuous Fabrication of Hierarchical and Asymmetric Bijel Microparticles, 
-    Fibers, and Membranes by Solvent Transfer‐Induced Phase Separation (STRIPS): 5913140219015
     \item Scalable synthesis of gyroid-inspired freestanding three-dimensional graphene architectures: 1548092-1
+    \item Colloidal Jamming at Interfaces: A Route to Fluid-Bicontinuous Gels [Science, 2005, 309, 5744]: 5966820525314
+    \item Continuous Fabrication of Hierarchical and Asymmetric Bijel Microparticles, Fibers, and Membranes by Solvent Transfer-Induced Phase Separation (STRIPS): 5913140219015
+    \item Magnetophoresis of Magnetic Pickering Emulsions Under Low Field Gradient: Macroscopic and Microscopic 
+    Motion [Langmuir 2021, 37, 5, 1811-1822]: "Reprinted (adapted) with permission from 
+    Langmuir 2021, 37, 5, 1811-1822. Copyright 2025 American Chemical Society."
+    \item Assembling Ellipsoidal Particles at Fluid Interfaces Using Switchable Dipolar Capillary Interactions [Adv. Mater., 26: 6715-6719]: Reproduced under the Creative Commons CC BY License.
+    \item Capillary Interactions Between Anisotropic Colloidal Particles, [Phys. Rev. Lett. 2005, 94, 018301]: RNP/25/FEB/088185
     \item State diagram for particle stabilized emulsions. [Soft Matter, 2015,11, 8393-8403]: 1551968-1
-    \item Scalable Manufacturing of Hierarchical Biphasic Bicontinuous Structures via Vaporization-Induced 
-    Phase Separation (VIPS) [Materials Letters 2020, 2, 5, 524-530]: "Reprinted (adapted) with permission from 
-    {COMPLETE REFERENCE CITATION}. Copyright {YEAR} American Chemical Society."
-    \item Modulation of Cellulose Nanocrystals Amphiphilic Properties to Stabilize Oil/Water Interface 
-    [Biomacromolecules 2016, 17, 5, 1748–1756]: "Reprinted (adapted) with permission from 
-    {COMPLETE REFERENCE CITATION}. Copyright {YEAR} American Chemical Society."
-    \item Dextran-Based Nanoparticles to Formulate pH-Responsive Pickering Emulsions: A Fully Degradable 
-    Vector at a Day Scale [Biomacromolecules 2020, 21, 12, 5358–5368]: "Reprinted (adapted) with permission from 
-    {COMPLETE REFERENCE CITATION}. Copyright {YEAR} American Chemical Society."
-    \item Stable emulsions with thermally responsive microstructure and rheology using poly(ethylene oxide) star 
-    polymers as emulsifiers [Journal of Colloid and Interface Science, 2013, 394, 284-292]: 5921030909190
-    \item Magnetophoresis of Magnetic Pickering Emulsions Under Low Field Gradient: Macroscopic and Microscopic 
-    Motion [Langmuir 2021, 37, 5, 1811–1822]: "Reprinted (adapted) with permission from 
-    {COMPLETE REFERENCE CITATION}. Copyright {YEAR} American Chemical Society."
-    \item Influence of magnetic field on the orientation of anisotropic magnetic particles at liquid interfaces 
-    [Phys Chem Chem Phys 2014, 16, 47, 26051-26058]: 1551970-1
-    \item Pickering Emulsions with Controllable Stability [Langmuir, 2005, 21, 6, 2158-2162]: "Reprinted (adapted) with permission from 
-    {COMPLETE REFERENCE CITATION}. Copyright {YEAR} American Chemical Society."
-    \item Bijels Containing Magnetic Particles: A Simulation Study [Langmuir, 2010, 26, 11, 7928-7936]: 
-    "Reprinted (adapted) with permission from {COMPLETE REFERENCE CITATION}. Copyright {YEAR} 
-    American Chemical Society."
-    \item Numerical simulations of particulate suspensions via a discretized Boltzmann equation. Part 2. Numerical results
-    \item Aerobijels: Ultralight Carbon Monoliths from Cocontinuous Emulsions 
-    [Adv. Funct. Mater. 2020, 30, 1908383]: 5921080017718
-    \item Hierarchical assemblies of superparamagnetic colloids in 
-    time-varying magnetic fields [Soft Matter. 17, 5, 1120-1155]: 1552854-1
+    \item Shear dynamics of confined bijels [AIP Advances 1 September 2020; 10 (9): 095304]: Reproduced under the Creative Commons CC BY License.
+    \item LB3D: A parallel implementation of the Lattice-Boltzmann method for simulation of interacting amphiphilic fluids [Computer Physics Communications 2017, 217, 149--161]: Reproduced under the Creative Commons CC BY License
 \end{itemize}
+
+% \begin{itemize}
+%     \item Continuous Fabrication of Hierarchical and Asymmetric Bijel Microparticles, 
+%     Fibers, and Membranes by Solvent Transfer‐Induced Phase Separation (STRIPS): 5913140219015
+%     \item Scalable synthesis of gyroid-inspired freestanding three-dimensional graphene architectures: 1548092-1
+%     \item State diagram for particle stabilized emulsions. [Soft Matter, 2015,11, 8393-8403]: 1551968-1
+%     \item Scalable Manufacturing of Hierarchical Biphasic Bicontinuous Structures via Vaporization-Induced 
+%     Phase Separation (VIPS) [Materials Letters 2020, 2, 5, 524-530]: "Reprinted (adapted) with permission from 
+%     {COMPLETE REFERENCE CITATION}. Copyright {YEAR} American Chemical Society."
+%     \item Modulation of Cellulose Nanocrystals Amphiphilic Properties to Stabilize Oil/Water Interface 
+%     [Biomacromolecules 2016, 17, 5, 1748–1756]: "Reprinted (adapted) with permission from 
+%     {COMPLETE REFERENCE CITATION}. Copyright {YEAR} American Chemical Society."
+%     \item Dextran-Based Nanoparticles to Formulate pH-Responsive Pickering Emulsions: A Fully Degradable 
+%     Vector at a Day Scale [Biomacromolecules 2020, 21, 12, 5358–5368]: "Reprinted (adapted) with permission from 
+%     {COMPLETE REFERENCE CITATION}. Copyright {YEAR} American Chemical Society."
+%     \item Stable emulsions with thermally responsive microstructure and rheology using poly(ethylene oxide) star 
+%     polymers as emulsifiers [Journal of Colloid and Interface Science, 2013, 394, 284-292]: 5921030909190
+%     \item Magnetophoresis of Magnetic Pickering Emulsions Under Low Field Gradient: Macroscopic and Microscopic 
+%     Motion [Langmuir 2021, 37, 5, 1811–1822]: "Reprinted (adapted) with permission from 
+%     {COMPLETE REFERENCE CITATION}. Copyright {YEAR} American Chemical Society."
+%     \item Influence of magnetic field on the orientation of anisotropic magnetic particles at liquid interfaces 
+%     [Phys Chem Chem Phys 2014, 16, 47, 26051-26058]: 1551970-1
+%     \item Pickering Emulsions with Controllable Stability [Langmuir, 2005, 21, 6, 2158-2162]: "Reprinted (adapted) with permission from 
+%     {COMPLETE REFERENCE CITATION}. Copyright {YEAR} American Chemical Society."
+%     \item Bijels Containing Magnetic Particles: A Simulation Study [Langmuir, 2010, 26, 11, 7928-7936]: 
+%     "Reprinted (adapted) with permission from {COMPLETE REFERENCE CITATION}. Copyright {YEAR} 
+%     American Chemical Society."
+%     \item Numerical simulations of particulate suspensions via a discretized Boltzmann equation. Part 2. Numerical results
+%     \item Aerobijels: Ultralight Carbon Monoliths from Cocontinuous Emulsions 
+%     [Adv. Funct. Mater. 2020, 30, 1908383]: 5921080017718
+%     \item Hierarchical assemblies of superparamagnetic colloids in 
+%     time-varying magnetic fields [Soft Matter. 17, 5, 1120-1155]: 1552854-1
+%     \item Colloidal Jamming at Interfaces: A Route to Fluid-Bicontinuous Gels [Science, 2005, 309, 5744]: 5966820525314
+%     \item Capillary Interactions Between Anisotropic Colloidal Particles, [Phys. Rev. Lett. 2005, 94, 018301]: RNP/25/FEB/088185
+% \end{itemize}

### 2025-03-10 chapters/analysis_techniques.tex
Changes 1. Added conclusion in final remarks 2. Added hysteresis curve for prolate particles stabilized bijels in aim2 section 3. Added description of synthesis techniques in lit review
adding references in shear banding methods section
Changes 1. Refined text in most sections 2. Resized figures for consistency of figure size 3. Removed shear banding analysis and added how shear stress is calculated

@@
 with its corresponding eignvector referring to the director of the system. \cite{veerman_phase_1992} 
-\textcolor{blue}{https://doi.org/10.1080/00268978400101951} A system is defined to be ordered nematically, 
+% \textcolor{blue}{https://doi.org/10.1080/00268978400101951} 
+A system is defined to be ordered nematically, 
 if $S > 0.3$. In this work, the direction of the director will be compared to the direction of the magnetic 
@@
 In the literature, crystal structures can be distinguished from one another by plotting the distribution of two or more $Q_{l}$. 
+\cite{lechner_accurate_2008, mickel_shortcomings_2013} Given that bijels form colloidal glasses, we only expect there to be
+short range order which means conclusions made from this parameter can only be used to guide trends of order, not quantitative 
+calculations of crystal structures.
 
-\subsection{Shear viscosity}
+\subsection{Shear stress}
 \label{section:shear_viscosity}
 
-Shear viscosity is a physical parameter measured through the dissipation of applied strain onto a fluid, resulting in 
-an applied shear stress. In an incompressible fluid, the viscosity $(\eta)$ is defined as the ratio between the measured 
+In an incompressible fluid, the viscosity $(\eta)$ is defined as the ratio between the measured 
 shear stress $(\sigma)$ and the applied strain rate $(\dot{\gamma})$, $\sigma = \eta \dot{\gamma}$. In rheological 
-experiments, the shear viscosity is measured through a viscometer based on Couette or shear viscometry and Poiselle or 
+experiments, the viscosity is measured through a viscometer based on Couette or shear viscometry and Poiselle or 
 pressure gradient viscometry. A Couette cell functions by applying a shear velocity to one or more walls, and measuring 
 the shear stress response of the fluid. Common geometries for Couette cells include the cone and plate and concentric 
-cylinder viscometers.
+cylinder viscometers. In simulations, shear can be applied to walls of the simulation domain through either a shearing 
+wall boundary condition or a Lees Edwards boundary condition. We select the Lees Edwards boundary condition as shearing 
+results are unaffected by finite size effects and wall effects. Finite size effects are observed as a system size
+dependent shear stress at the same shear rate. Wall effects can be seen as stick-slip effects of the particles or 
+unphysical velocity gradients near the wall.
+
+In a lattice boltzmann, the shear stress is measured as the sum of the equilibrium and nonequilibrium contributions.
+\cite{kruger_shear_2009} These terms are defined as,
+
+\begin{equation}
+    \sigma_{\alpha \beta} = \sigma_{\alpha \beta}^{0} + \sigma_{\alpha \beta}^{1}
+\end{equation}
+
+This expression is obtained from the Chapman Enskog expansion of the lattice boltzmann method. The equilibrium and
+non-equilibrium contributions of the stress are defined as
+
+\begin{equation}
+    \begin{split}
+        \sigma_{\alpha \beta}^{0} &= \rho c_s^2 \delta_{\alpha \beta} + \rho u_{\alpha} u_{\beta} \\
+        \sigma_{\alpha \beta}^{1} &= (1 - \frac{1}{2 \tau})\Sigma_{i} (f_{i} - f_{i}^{eq})c_{i \alpha}c_{i \beta} \\
+    \end{split}
+\end{equation}
 
 In this work, a shear velocity is imparted in the z direction, across the x-axis. Therefore, the shear stress in the x 
-and z directions, $\sigma_{xz}$, is measured. $\sigma_{xz}$ is output per lattice in the output file, which is then 
-averaged across the entire volume to obtain an average shear stress $\hat{\sigma_{xz}}$. The effective viscosity of the 
-system, $\eta_{eff}$ is calculated using $\eta_{eff} = \frac{\hat{\sigma_{xz}}}{\dot{\gamma}}$ where $\dot{\gamma} = 
-\frac{2 u_{LE}}{L_x}$. $u_{LE}$ is the shear velocity is enforced through the Lees-Edwards boundary condition, as 
-described in section \textcolor{blue}{description of lees edwards BC}.
+and z directions, $\sigma_{xz}$, is measured. $\sigma_{xz}$ is output as calculated from the simulation for the entire 
+domain after applying this equation to the system.
 
-\subsection{Yield stress and zero shear rate viscosity}
-\label{section:yield_stress}
+% \subsection{Yield stress and zero shear rate viscosity}
+% \label{section:yield_stress}
 
-The yield stress of bijels can be calculated using the flow curve, stress ramp or from oscillatory rheological techniques. 
-The flow curve method involves the steady application of shear, followed by measurements of the shear stress response of 
-the material. The plateau of the shear stress response is indicative of the yield stress of the material. The stress ramp 
-method involves the application of a shear stress onto the material, followed by measurements of the strain rate. A 
-perfectly elastic material will have no strain rate, while a perfectly disspitative material will have high strain rate. 
-The yield stress is characterized as the point when a rapid increase in strain rate is observed. The yield stress from 
-oscillatory rheology is defined when the storage modulus is lower than the loss modulus. This work will utilize the flow 
-curve method.
+% The yield stress of bijels can be calculated using the flow curve, stress ramp or from oscillatory rheological techniques. 
+% The flow curve method involves the steady application of shear, followed by measurements of the shear stress response of 
+% the material. The plateau of the shear stress response is indicative of the steady state stress of the material. The stress ramp 
+% method involves the application of a shear stress onto the material, followed by measurements of the strain rate. A 
+% perfectly elastic material will have no strain rate, while a perfectly dissipative material will have high strain rate. 
+% The yield stress is characterized as the point when a rapid increase in strain rate is observed. The yield stress from 
+% oscillatory rheology is defined when the storage modulus is lower than the loss modulus. This work will utilize the flow 
+% curve method.
 
-The shear viscosity calculated using the method detailed in Section \ref{section:shear_viscosity} will be plotted as a 
-function of applied shear rate. Rheological models such as the Herschel Buckley, Bingham Plastic or Carreu models can be 
-utilized to fit the shear viscosity as a function of shear rate to calculate the zero shear rate viscosity. In bijel 
-applications, this parameter gives insight into the material stability and processability.
+% The shear viscosity calculated using the method detailed in Section \ref{section:shear_stress} will be plotted as a 
+% function of applied shear rate. Rheological models such as the Herschel Buckley, Bingham Plastic or Carreu models can be 
+% utilized to fit the shear viscosity as a function of shear rate to calculate the zero shear rate viscosity. In bijel 
+% applications, this parameter gives insight into the material stability and processability.
 
-\subsection{Shear banding}
-\label{section:shear_banding}
+% \subsection{Shear banding}
+% \label{section:shear_banding}
+
+% \textcolor{blue}{https://doi.org/10.1073/pnas.0812519106}
+
+% \textcolor{blue}{https://doi.org/10.1103/PhysRevX.11.021017}

### 2025-03-10 chapters/dissertation-tap.tex
Changes 1. Added more figures for introduction and literature review 2. Completed introduction and lit review for draft 1 3. Added figures for Aim 3 section
Changes 1. Refined text in most sections 2. Resized figures for consistency of figure size 3. Removed shear banding analysis and added how shear stress is calculated

@@
 \chair{Joshua Zide, PhD}{Chair of the Department of Materials Science and Engineering}
-\dean{Jamie Phillips, PhD}{Dean of the College of Engineering}
+\dean{Pamela M. Norris, PhD}{Dean of the College of Engineering}
 \end{approvalpage}
@@
 In the development of this dissertation, I extend my deepest gratitude to Dr Ulf Schiller whose support, motivation and 
-opportunities have been indispensible during my PhD. I believe his approach to mentorship, methodical problem solving 
-strategies, depth and breadth of knowledge have been invaluable sources of inspiration for this research as well as 
-motivating myself to strive towards those ideals. I would also like to thank members of my committee, especially 
-Dr Arthi Jayaraman from the University of Delaware and Dr Olga Kuksenok from Clemson University for their mentorship 
+opportunities have been indispensible during my PhD. I believe his methodical problem solving strategies, depth and 
+breadth of knowledge have been invaluable sources of inspiration for me as well as 
+motivating myself to strive towards those ideals. I would also like to thank members of my committee, 
+from the University of Delaware and Clemson University for their mentorship 
 and motivation that pushed me to increase my breadth of knowledge and to think outside the box.
@@
 
-Porous materials have found greater importance in applications such as water filtration, catalyst supports, battery 
+Porous materials have found great importance in applications such as water filtration, catalyst supports, battery 
 electrodes and bio engineered materials. To accommodate a greater variety of pore sizes and continuous fabrication 
-techniques with minimal waste, bottom up synthesis techniques have been gaining in popularity.
+techniques with minimal waste, bottom up synthesis techniques have been gaining in popularity. One such technique is
+emulsion templating of a specific microstructure known as a bicontinuous interfacially jammed emulsion gels(bijels).
 
-One such bottom up fabrication technique relies on jamming of particle stabilized emulsions into bicontinuous 
-interfacially jammed emulsion gels(bijels). However, casting mixture independent microstructure control has not 
-been identified, especially applicable in continuous bijel synthesis strategies such as Solvent Transfer Induced 
-Phase separation. Stimuli response has been identified as a technique to enable this. This study focuses on utilizing 
-stimuli response of bijels stabilized with ellipsoidal microparticles, and the resulting microstructure and rheological 
-implications this induces.
+However, casting mixture independent microstructure control is an open issue, especially applicable in continuous 
+bijel synthesis strategies such as Solvent Transfer Induced Phase separation and as in-situ control mechanisms to
+control the microstructure of a bijel to control properties such as separation efficiency. Stimuli response has been identified as a 
+technique to enable this. This study focuses on utilizing stimuli response of bijels stabilized with ellipsoidal microparticles, 
+and the resulting microstructure and rheological implications this induces.
 
@@
 microstructure change is observed, not present when analyzing bijels stabilized with spherical particles. Upon 
-application of the field, particles reorient to the direction of the field, dragging the interface along with 
-them. This causes the bijel to have axially dependent jamming, causing anisotropic microstructures to form.
+application of the field, particles reorient to the direction of the field, causing directional jamming that creates
+microstructure anisotropy.
 
@@
 
+Finally, we characterize that bijels retain their shear thinning behavior when analyzing the rheological response of bijels
+under magnetic fields. We identify that the particle ordering plays a role in the evolution of the microstructure under shear
+and the rheological response.
+
 \end{front}

### 2025-03-10 chapters/model_params.tex
Changes 1. Refined text in most sections 2. Resized figures for consistency of figure size 3. Removed shear banding analysis and added how shear stress is calculated

--- 2025-02-14 chapters/model_params.tex
@@
 \section{Simulation setup}
+\label{section:sim_setup}
 
@@
 step was performed to push the particles further away from each after placement. Once equilibration is performed, a 
-constant magnetic field is switched on with dimensionless strengths defined using $Bo_m$.
+constant magnetic field is switched on with dimensionless strengths defined using $\bar{B}$.
 
@@
 water/2-6-lutidine will be discussed in the context of the work presented here. The critical temperature (UCST) 
-for this system is $T_c = 37 ^{\circ}C$, with many systems heated to $T = 40^{\circ}C$ to form the bijel. At this 
+for this system is $T_c = 34 ^{\circ}C$, with many systems heated to $T = 40^{\circ}C$ to form the bijel. At this 
 temperature, the fluid properties are $\sigma = 0.22 mN/m$ and $\eta = 2.38 mPas$. \cite{grattoni_lower_1993} 
@@
 a dipole moment of approximately$\approx 3 \cdot 10^{-14} Am^2$. \cite{fei_active_2017, fei_magneto-capillary_2020} 
-Comparing the physical properties to simulation parameters, the simulations correspond to a box side length of 
-$L \approx 64.5 \mu m$ and a timestep duration of $\Delta t \approx 624 ns$.
+Comparing the physical properties to simulation parameters, the simulations correspond to a length scale of
+$\Delta x = 252 \cdot 10^{-9} \text{m}$, timescale of $\Delta t = 624 \cdot 10^{-9} \text{s}$, 
+mass scale of $\Delta m = 2.24 \cdot 10^{-15} \text{kg}$ and charge scale of $\Delta q = 2.948 \cdot 10^{-7} \text{C}$.
 
 \section{Model results}
+\label{section:model_results}
 
-\subsubsection{Surface tension}
+\subsection{Surface tension}
+\label{section:model_surface_tension}
 

### 2025-03-10 chapters/paper1.tex
Changes 1. Added more figures for introduction and literature review 2. Completed introduction and lit review for draft 1 3. Added figures for Aim 3 section
Changes 1. Refined text in most sections 2. Resized figures for consistency of figure size 3. Removed shear banding analysis and added how shear stress is calculated

@@
+\section{Introduction}
+
 The addition of microstructure control in bijels can be utilized to improve the performance of porous materials
@@
 \centering
-\includegraphics[width=\columnwidth]{figures/results/paper1/D2a-vs-B_ss.png}
+\includegraphics[scale = 0.4]{figures/results/paper1/D2a-vs-B_ss.png}
 \caption{Dependence of the average domain size on the magnetic field strength $\bar{B}$.
@@
 \centering
-\includegraphics[width=\textwidth]{figures/results/paper1/tortuosity_compare.png}
+\includegraphics[scale = 0.4]{figures/results/paper1/tortuosity_compare.png}
 \caption{Dependence of the tortuosity on the magnetic field strength $\bar{B}$ for different particle shapes $\alpha$. 
@@
     \centering 
-    \includegraphics[width=\textwidth]{figures/results/paper1/curvature-vs-B_ss.png} 
+    \includegraphics[scale = 0.4]{figures/results/paper1/curvature-vs-B_ss.png} 
     \caption{Plot of the area averaged mean $\langle H \rangle \Sigma^{-1}$ and Gaussian 
@@
     \centering 
-    \includegraphics[width=\textwidth]{figures/results/paper1/genus_curvature_vs_coverage.png} 
+    \includegraphics[scale = 0.4]{figures/results/paper1/genus_curvature_vs_coverage.png} 
     \caption{Plots of Gaussian $\langle K \rangle \Sigma^{-2}$ curvature over time averaged across 3 runs. 
@@
 \centering
-\includegraphics[width=\columnwidth]{figures/results/paper1/S-vs-t.png}
+\includegraphics[scale = 0.4]{figures/results/paper1/S-vs-t.png}
 \caption{Time-dependence of the nematic order parameter $S$ of oblate ($\alpha=0.5$) and prolate ($\alpha=2$) 
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{figures/results/paper1/interface_nematic.png}
+\includegraphics[scale = 0.4]{figures/results/paper1/interface_nematic.png}
 \caption{Time-dependence of the interface nematic order for oblate ($\alpha=0.5$) and prolate ($\alpha=2$) particles at different magnetic field strength $\bar{B}$.
@@
 \centering
-\includegraphics[width=\columnwidth]{figures/results/paper1/psi-vs-t.png}
+\includegraphics[scale = 0.4]{figures/results/paper1/psi-vs-t.png}
 \caption{Time-dependence of the average angle $\psi$ between the particle axis and the 
@@
     \includegraphics[width=\columnwidth]{figures/results/paper1/steinhardt_vs_coverage.png} 
-    \caption{Time dependence of the mean six fold symmetry parameter, $\langle Q6 \rangle$ for bijels 
-    stabilized with oblate(left), spherical(middle) and prolate(right) particles. We show that spherical 
-    particles posess the hexagonal close packing structure for particles on interfaces. Ellipsoidal particles 
-    however posess behavior that is magnetic field and particle aspect ratio dependent.} 
+    \caption{Time dependence of the mean two and six fold symmetry parameter, $\langle Q2 \rangle$ and $\langle Q6 \rangle$ 
+    for bijels stabilized with oblate(left), spherical(middle) and prolate(right) particles. We use $\langle Q2 \rangle$ as an
+    indicator of global particle translational order while $\langle Q6 \rangle$ is an indicator of local order.} 
     \label{fig:Q6_coverage} 

### 2025-03-10 chapters/paper2.tex
Changes 1. Added more figures for introduction and literature review 2. Completed introduction and lit review for draft 1 3. Added figures for Aim 3 section
Changes 1. Refined text in most sections 2. Resized figures for consistency of figure size 3. Removed shear banding analysis and added how shear stress is calculated

@@
+\section{Introduction}
+
 Stimuli-responsive emulsions have attracted significant interest for applications in enhanced oil recovery, porous material templating, 
@@
 symmetry axis, stabilize bijel templates. Simulations without an applied field reveal anisotropic bijel formation, with microstructure 
-evolution dependent on particle reordering at the interface, quantified using the six-fold Steinhardt order parameter \(\langle Q_6 \rangle\).
+evolution dependent on particle reordering at the interface, quantified using the six-fold Steinhardt order parameter \(\langle Q6 \rangle\).
 
@@
 and the local ordering of the particles characterized with 
-$\langle Q_6 \rangle$ Past work has identified that local crystallization 
-of colloidal crystals takes place at \(\langle Q_6 \rangle = 0.38\). 
+$\langle Q6 \rangle$ Past work has identified that local crystallization 
+of colloidal crystals takes place at \(\langle Q6 \rangle = 0.38\). 
 \cite{toxvaerd_role_2020}
@@
 \centering 
-\includegraphics[scale=0.5]{../figures/results/paper2/interface_angle-nint-field_on.png} 
-\caption{Plots of the interface angle $(\langle \psi \rangle)$ and six fold Steinhardt order parameter $(\langle Q_6 \rangle)$ on the left and right respectively, versus time for bijels stabilized with oblate and prolate ellipsoids on the top and bottom rows respectively.
-We demonstrate that upon application of a magnetic field, the behavior of $(\langle \psi \rangle)$ and $(\langle Q_6 \rangle)$ differ significantly between oblate and prolate ellipsoids indicating that the dynamics for both particle morphologies differ.
+\includegraphics[scale=0.3]{../figures/results/paper2/interface_angle-nint-field_on.png} 
+\caption{Plots of the interface angle $(\langle \psi \rangle)$ and six fold Steinhardt order parameter 
+         $(\langle Q6 \rangle)$ on the left and right respectively, versus time for bijels stabilized with 
+         oblate and prolate ellipsoids on the top and bottom rows respectively. We demonstrate that upon application 
+         of a magnetic field, the behavior of $(\langle \psi \rangle)$ and $(\langle Q6 \rangle)$ differ significantly 
+         between oblate and prolate ellipsoids indicating that the dynamics for both particle morphologies differ.
 We also observe magnetic field dependence in each property for both particle types, suggesting that these changes are driven primarily through the change in the applied field strength.}
@@
 particles, this behavior can also be observed. \(\langle \psi \rangle\)
-begins at \(80 ^{circ}\). The difference in the initial
+begins at \(80 ^{\circ}\). The difference in the initial
 \(\langle \psi \rangle\) compared to oblate particles is due to the
@@
 the interface. We probe this by identifying the local particle ordering
-at the interface characterized by \(\langle Q_6 \rangle\).
+at the interface characterized by \(\langle Q6 \rangle\).
 
-We see that for oblate particles, \(\langle Q_6 \rangle\) sees a
+We see that for oblate particles, \(\langle Q6 \rangle\) sees a
 decrease from its initial value. However the dynamics are controlled by
@@
 into three sections, similar to \(\langle \psi \rangle\) with the first
-section seeing a decrease in \(\langle Q_6 \rangle\) upon application of
+section seeing a decrease in \(\langle Q6 \rangle\) upon application of
 the magnetic field, followed by a plateau and finally a gradual increase
@@
 restoration of some of the pre-existing order. The final values of
-\(\langle Q_6 \rangle\) are magnetic field dependent, with a stronger
-magnetic field having a lower final \(\langle Q_6 \rangle\) value
+\(\langle Q6 \rangle\) are magnetic field dependent, with a stronger
+magnetic field having a lower final \(\langle Q6 \rangle\) value
 indicating that either the ordering of particles influence the angle at
@@
 function of the applied field strength. We also observe from plotting
-\(\langle Q_6 \rangle\) that application of a magnetic field creates a
+\(\langle Q6 \rangle\) that application of a magnetic field creates a
 local crystallization of the colloid monolayer characterized as
-\(\langle Q_6 \rangle > 0.38\). \cite{toxvaerd_role_2020}
+\(\langle Q6 \rangle > 0.38\). \cite{toxvaerd_role_2020}
 
@@
 size. To probe why this occurs, we recast \(\langle \psi \rangle\),
-\(\langle Q_6 \rangle\) and \(S\) in terms of the physical phenomena
+\(\langle Q6 \rangle\) and \(S\) in terms of the physical phenomena
 they represent. The nematic order parameter represents the ordering of
@@
 We can also do the same for \(\langle \psi \rangle\) and
-\(\langle Q_6 \rangle\). A timescale derived from
+\(\langle Q6 \rangle\). A timescale derived from
 \(\langle \psi \rangle\) named \(\tau_{\langle \psi \rangle}\)
@@
 maximum for oblate particles. A timescale derived from
-\(\langle Q_6 \rangle\), named \(\tau_{\langle Q_6 \rangle}\) is also
+\(\langle Q6 \rangle\), named \(\tau_{\langle Q6 \rangle}\) is also
 calculated which represents a timescale of local particle rearrangement.
-We define \(\tau_{\langle Q_6 \rangle}\) as the time when
-\(\langle Q_6 \rangle \geq 0.38\) for prolate particles and the global
-minimum of \(\tau_{\langle Q_6 \rangle}\) for the oblate particles. We
+We define \(\tau_{\langle Q6 \rangle}\) as the time when
+\(\langle Q6 \rangle \geq 0.38\) for prolate particles and the global
+minimum of \(\tau_{\langle Q6 \rangle}\) for the oblate particles. We
 omit \(\bar{B} = 0\) as previous results have identified the domain size
@@
 The figures in the middle plot the domain size against time rescaled with the interfacial capillary timescale, $\tau_{\langle \psi \rangle}$.
-The figures on the right plot the domain size against time rescaled with the particle rearrangement timescale, $\tau_{\langle Q_6 \rangle}$.
+The figures on the right plot the domain size against time rescaled with the particle rearrangement timescale, $\tau_{\langle Q6 \rangle}$.
 We show that the controlling timescale when applying a magnetic field onto bijels with disordered particles is the latter timescale, indicating that the dominating effect is steric hindrance of the particles during rearrangment at the interface.}
@@
 The right plot demonstrates the domain size change after rescaling time
-with \(\tau_{\langle Q_6 \rangle}\) where we see good collapse between
+with \(\tau_{\langle Q6 \rangle}\) where we see good collapse between
 all plots while the domain size transition also begins at
-\(\frac{t}{\tau_{\langle Q_6 \rangle}} = 1\). The latter point
+\(\frac{t}{\tau_{\langle Q6 \rangle}} = 1\). The latter point
 demonstrates that the dynamics for the structural response of randomly
@@
 the interface rather than the orientation of the particle to the
-magnetic field.We see that before \(\tau_{\langle Q_6 \rangle} = 1\),
+magnetic field.We see that before \(\tau_{\langle Q6 \rangle} = 1\),
 \(\bar{B} = 0.2\) for the oblate particles does not collapse onto the
@@
 quantify the average interface angle, \(\langle \psi \rangle\) and the
-local interface order of the material, \(\langle Q_6 \rangle\) in Figure
+local interface order of the material, \(\langle Q6 \rangle\) in Figure
 \ref{fig:interface_angle-nint-field_up}.
@@
 show that there are three time evolution trends for
-\(\langle \psi \rangle\) and \(\langle Q_6 \rangle\) for both oblate and
+\(\langle \psi \rangle\) and \(\langle Q6 \rangle\) for both oblate and
 prolate particles despite the differences in the initial state of the
@@
 
-When looking at \(\langle Q_6 \rangle\) for \(\bar{B}: 0 \rightarrow 1\)
+When looking at \(\langle Q6 \rangle\) for \(\bar{B}: 0 \rightarrow 1\)
 and \(\bar{B}: 0.2 \rightarrow 1\) for oblate particles, we see that the
 trends are similar with an initial decrease, followed by a plateau and
-increase over time before plateauing again. \(\langle Q_6 \rangle\)
+increase over time before plateauing again. \(\langle Q6 \rangle\)
 generally decreases with a large decrease observed for
@@
 to a structure that is locally ordered but not close packed. For prolate
-particles, we see an increase in \(\langle Q_6 \rangle\) with a plateau
+particles, we see an increase in \(\langle Q6 \rangle\) with a plateau
 occurring in both systems around 5000 timesteps. The significance of
@@
 \(\bar{B}: 1 \rightarrow 1\), this is approximately the local
-crystallization point when \(\langle Q_6 \rangle \geq 0.38\).
+crystallization point when \(\langle Q6 \rangle \geq 0.38\).
 
@@
 from \(\langle \psi \rangle\), although the dynamics are primarily
-driven by the change in \(\langle Q_6 \rangle\), indicated as a slight
+driven by the change in \(\langle Q6 \rangle\), indicated as a slight
 dip and plateau before the particles begin reordering and packing more
@@
 \(\bar{B}: 1 \rightarrow 1\). We see a decrease in
-\(\langle Q_6 \rangle\) for bijels stabilized with oblate particles with
+\(\langle Q6 \rangle\) for bijels stabilized with oblate particles with
 field application of \(\bar{B}: 0.5 \rightarrow 1\) compared to an
@@
 where we characterize a slight decrease over time. We also characterize
-a slight decrease in \(\langle Q_6 \rangle\) over time for the
+a slight decrease in \(\langle Q6 \rangle\) over time for the
 \(\bar{B}: 1 \rightarrow 1\) case while characterizing a larger decrease
@@
 is the case, we plot \(\langle \psi \rangle\) and
-\(\langle Q_6 \rangle\) for bijels stabilized with ellipsoidal particles
+\(\langle Q6 \rangle\) for bijels stabilized with ellipsoidal particles
 below.
@@
 In Figure \ref{fig:interface_angle-field_down}, we plot
-\(\langle \psi \rangle\) and \(\langle Q_6 \rangle\) in the left and
+\(\langle \psi \rangle\) and \(\langle Q6 \rangle\) in the left and
 right columns respectively. While there are minor differences to the
-time when \(\langle \psi \rangle\) and \(\langle Q_6 \rangle\) increase
+time when \(\langle \psi \rangle\) and \(\langle Q6 \rangle\) increase
 and decrease respectively for bijels stabilized by oblate particles the
@@
 
-Looking at \(\langle Q_6 \rangle\), we see that all simulations see a
+Looking at \(\langle Q6 \rangle\), we see that all simulations see a
 decrease over time. We see that contrary to previous trends, the
 \(\bar{B}: 1\rightarrow 0\) simulation has a smaller change in
-\(\langle Q_6 \rangle\) than \(\bar{B}: 0.5\rightarrow 0\) although this
+\(\langle Q6 \rangle\) than \(\bar{B}: 0.5\rightarrow 0\) although this
 difference is also a result of the initial particle orientation and
@@
 the \(\bar{B}: 0.5\rightarrow 0\) case is near the
-\(Q_6^{HCP} \approx 0.485\) boundary, suggesting it is most susceptible
+\(Q6^{HCP} \approx 0.485\) boundary, suggesting it is most susceptible
 to lose short range order upon removal of the magnetic field that
-enforces it, resulting in the large decrease in \(\langle Q_6 \rangle\)
+enforces it, resulting in the large decrease in \(\langle Q6 \rangle\)
 observed.

### 2025-03-10 chapters/paper3.tex
Changes 1. Refined text in most sections 2. Resized figures for consistency of figure size 3. Removed shear banding analysis and added how shear stress is calculated

@@
 From Figure \ref{fig:stress_strain}, we show that bijels stabilized with ellipsoidal particles are shear thinning regardless of the initial 
-microstructure and the processing applied. We quantify the fit and tabulate the results in Table \ref{tab:rheology_fit}. From Table 
-\ref{tab:rheology_fit}, we can see that as particle order increases, signified by an increase in the initial magnetic field, the flow index 
+microstructure and the processing applied. We quantify the fit and tabulate the results in Table \ref{table:rheology_fit}. From Table 
+\ref{table:rheology_fit}, we can see that as particle order increases, signified by an increase in the initial magnetic field, the flow index 
 of the material increases, indicating more Newtonian fluid like behavior. This is due to the more ordered particles being able to slip
@@
 
-\begin{center}
+\begin{table}[h!]
+    \centering
     \begin{tabular}{||c c c c c||} 
      \hline
-     Processing & $\alpha$ & $n$ & $K \frac{\Delta m (\Delta t)^{n-2}}{\Delta m} $ & $\sigma_{y} \frac{\Delta m}{\Delta m (\Delta t)^2}$ \\ [0.5ex] 
+     Processing & $\alpha$ & $n$ & $K \frac{\Delta m (\Delta t)^{n-2}}{\Delta x} $ & $\sigma_{y} \frac{\Delta m}{\Delta x (\Delta t)^2}$ \\ [0.5ex] 
      \hline\hline
@@
     \end{tabular}
-\label{tab:rheology_fit}
-\end{center}
+    \caption{Hershel Buckley fit parameters for different processing conditions applied to bijels stabilized by ellipsoidal particles.}
+    \label{table:rheology_fit}
+\end{table}
+
+% \begin{table}[h!]
+%     \centering
+%     \begin{tabular}{||c c c c c c c c c c c c c||} 
+%      \hline
+%      $t_{sim}$ & $L_x$ & $\rho_f$ & $\tau$ & $\eta_f$ & $g_{cc'}$ & $\sigma$ & $\phi_f$ & $\rho_p$ & $\phi_p$ & $V_p$ & $d_c$ & $K_H$ \\ [0.5ex] 
+%      \hline\hline
+%      $10^5$ & 256 & 0.7 & 1 & 0.117 & 0.08 & 0.0267 & 0.5 & 1 & 0.15 & 2000$\pi$ & 2/3 & 100\\ [1ex] 
+%      \hline
+%     \end{tabular}
+%     \caption{Summary of the fluid, particle and model parameters used in the proposed simulations}
+%     \label{table:model_params}
+%     \end{table}
 

### 2025-03-10 chapters/final_remarks.tex
Changes 1. Revised conclusion and added aim 3 findings

@@
 
-In Aim 3 we investigate the rheological response of bijels stabilized with ellipsoidal particles under constant shear and show that the application of magnetic
-fields changes the shear thinning properties of bijels.
+In Aim 3, we examine the rheological behavior of bijels stabilized by ellipsoidal particles under constant shear and demonstrate that the application of 
+magnetic fields alters their shear-thinning properties and the yield stress of the bijel. This effect arises from variations in particle ordering at the interface, 
+either due to the introduction of a magnetic field or pre-existing order in templated systems. Enhanced particle ordering facilitates smoother particle rearrangement, reducing local disruptions 
+in the interfacial structure. The observed domain coarsening is primarily driven by shear-induced particle tilting or ejection from the interface, further 
+influencing the overall microstructural evolution.
 
@@
 instructive in identifying if onsager theory can be used in bijel formation and its link to bijel microstructure. 
-\textcolor{blue}{https://doi.org/10.1039/D1SM00367D}
+\cite{tan_2d_2021}
 
@@
 response through temperature or pH. LBM methods that implement the immersed boundary method can be used to model soft
-particles with a DLVO potential used to model electrostatics between particles. \textcolor{blue}{https://doi.org/10.1039/D3SM01648J}
+particles with a DLVO potential used to model electrostatics between particles. \cite{silva_lattice_2024}
 

### 2025-03-10 chapters/dissertation-tap.tex
Changes 1. Modified and added correct format for attributions 2. Fixed all citation and referencing issues

@@
 breadth of knowledge have been invaluable sources of inspiration for me as well as 
-motivating myself to strive towards those ideals. I would also like to thank members of my committee, 
+motivation to strive towards those ideals. I would also like to thank members of my committee, 
 from the University of Delaware and Clemson University for their mentorship 
@@
 
-Listing everyone I am grateful for who have provided me non-academic support would be too long for this page 
-although I shall try to summarize this. I am grateful to my family, with whom I may not be the best at 
+Listing everyone I am grateful for who have provided me non-academic support would be too long for this page. 
+I am grateful to my family, with whom I may not be the best at 
 discussing my future plans, but they have been an indispensible source of support during my time away from home. 

### 2025-03-10 chapters/introduction.tex
Changes 1. Modified and added correct format for attributions 2. Fixed all citation and referencing issues

@@
     \includegraphics[scale = 0.5]{figures/introduction/bijel_templating.png}
-    \caption{Fabrication of a graphite oxide battery electrode using bijel template. Reproduced from Garcie et al. under license number 1548092-1. \cite{garcia_scalable_2019}}
+    \caption{Fabrication of a graphite oxide battery electrode using bijel template. Reproduced from Garcia et al. 
+             Nanoscale Adv., 2019,1, 3870-3882 under license number 1548092-1. \cite{garcia_scalable_2019}}
     \label{fig:bijel_template}
@@
     \caption{Initiation and arrest of spinodal decomposition as particles adsorb onto the interface, followed by jamming once the 
-    interfacial area matches the cross sectional area of the adsorbed particles\cite{stratford_colloidal_2005}. Reproduced from Adhikari et al. 
-    under license number 5966820525314.}
+    interfacial area matches the cross sectional area of the adsorbed particles\cite{stratford_colloidal_2005}. 
+    Reproduced from K. Stratford et al., Science 309, 2198-2201(2005) under license number 5966820525314.}
     \label{fig:bijel_coarsen}
@@
     \caption{STrIPS in action. Extrusion of the bijel casting mixture into a non-solvent bath, followed by removal of solvent from 
-    the casting mixture through diffusion. Reproduced from Haase et al. 2015 under license number 5913140219015. \cite{haase_continuous_2015}}
+             the casting mixture through diffusion. \cite{haase_continuous_2015} Reproduced from Haase et al. Adv. Mater., 
+             Volume27, Issue44, 2015, Pages 7065-7071 under license number 5913140219015. }
     \label{fig:strips}
@@
     \caption{Enhanced oil recovery of oil from water using magnetically responsive emulsion stabilizers, allowing for 
-             locomotion and controlled coalescence of cargo from a matrix phase using magnetic fields relevant in 
-             water filtration and oil refining applications. Reproduced from Tham et al. 2021 under the ACS standard license \cite{tham_magnetophoresis_2021}}
+             locomotion and controlled coalescence of cargo from a matrix phase using magnetic fields. \cite{tham_magnetophoresis_2021} 
+             Reproduced from Tham et al. Langmuir 2021, 37, 5, 1811-1822 under the ACS standard license.}
     \label{fig:magnetophoresis_droplet}
@@
              showing the self assembly into chains that ellipsoidal particles can undergo under applied magnetic fields at
-             interfaces. Reproduced from Davies et al. under the Creative Commons CC BY license \cite{davies_assembling_2014}}
+             interfaces. \cite{davies_assembling_2014} Reproduced from Davies et al. Adv. Mater., 26: 6715-6719 under the 
+             Creative Commons CC BY license.}
     \label{fig:anisotropic_assembly}

### 2025-03-10 chapters/lit_review.tex
Changes 1. Modified and added correct format for attributions 2. Fixed all citation and referencing issues

@@
     \includegraphics[scale = 0.5]{figures/literature_review/interfacial_curvature.png}
-    \caption{Quadropolar capillary interactions around prolate ellipsoidal particles caused by interfacial deformations around the particle. 
-    \cite{loudet_capillary_2005} Reproduced from Loudet et al. with license number RNP/25/FEB/088185}
+    \caption{Quadropolar capillary interactions around prolate ellipsoidal particles caused by interfacial deformations 
+             around the particle. \cite{loudet_capillary_2005} Reproduced from Loudet et al. Phys. Rev. Lett. 2005, 94, 018301
+             with license number RNP/25/FEB/088185}
     \label{fig:anisotropic_particle_interface}
@@
 \cite{cavallaro_curvature-driven_2011, read_dimerization_2020, sharifi-mood_curvature_2015}.
-
-Anisotropic particles have also been shown to exhibit natural liquid crystal like behaviour as shown using Onsager theory.
 
@@
     \includegraphics[scale = 0.2]{figures/literature_review/state_diagram.jpg}
-    \caption{Formation criteria for a particle stabilized emulsion that can form bijel. 
-            Reproduced from Velankar 2015 using license number 1551968-1. \cite{velankar_non-equilibrium_2015}}
+    \caption{Formation criteria for a particle stabilized emulsion that can form bijel. \cite{velankar_non-equilibrium_2015}
+            Reproduced from Velankar Soft Matter, 2015,11, 8393-8403 using license number 1551968-1.}
     \label{fig:state_diagram_particle_emulsions}
@@
     \includegraphics[scale = 2]{figures/literature_review/bijel_under_shear.jpeg}
-    \caption{Schematic of a bijel with hard-sphere particles undergoing shear, demonstrating migration and detachment of particles at the interface. 
-             Reproduced from Bonaccorso et al. under the Creative Commons CC BY License. \cite{bonaccorso_shear_2020}}
+    \caption{Schematic of a bijel with hard-sphere particles undergoing shear, demonstrating migration and detachment of 
+             particles at the interface. \cite{bonaccorso_shear_2020} Reproduced from Bonaccorso et al. AIP Advances 1 
+             September 2020; 10 (9): 095304, under the Creative Commons CC BY License.}
     \label{fig:bijel_under_shear}

### 2025-03-10 chapters/paper1.tex
Changes 1. Modified and added correct format for attributions 2. Fixed all citation and referencing issues

@@
 \section{Introduction}
+
+This section is based on work published in the Royal Society of Chemistry's Soft Matter journal and
+work submited to the American Institude of Physics, Physics of Fluids journal. \cite{karthikeyan_formation_2024} 
+It is reproduced from Ref \cite{karthikeyan_formation_2024} with permission from the Royal Society of Chemistry and 
+reproduced from Ref [FULL CITATION], with the permission of AIP Publishing.
 
@@
 \begin{figure}
+\centering
 \includegraphics[scale = 0.4]{figures/results/paper1/interface_nematic.png}

### 2025-03-10 chapters/paper2.tex
Changes 1. Modified and added correct format for attributions 2. Fixed all citation and referencing issues

@@
 
-Stimuli-responsive emulsions have attracted significant interest for applications in enhanced oil recovery, porous material templating, 
-in-situ reaction separation systems, and drug delivery scaffolds \cite{tang_stimuli-responsive_2016, bago_rodriguez_capsules_2019}. 
-These applications are facilitated by stimuli-induced microstructural modifications, which alter the permeability, surface area, and 
-morphology of the emulsion. Advancements in particle synthesis techniques, along with growing concerns over surfactant toxicity and 
-environmental impact, have contributed to the renewed interest in particle-stabilized emulsions since their initial discovery by Ramsden 
-and Pickering in 1907 \cite{rozynek_opening_2019, zhou_magnetic_2011}. Stimuli-responsive behavior in these emulsions has been achieved 
-through changes in pH, temperature, or chemical composition 
-\cite{maingret_dextran-based_2020, lin_ph-responsive_2018, raju_ph-responsive_2018, zhang_ph_2022}.
+Sections of this chapter appear in a manuscript submitted to Springer link.
+[author and/or editor(s) of contribution], [volume and/or contribution title], [year of publication], [publisher (as it appears on our copyright page)] \
+reproduced with permission of Palgrave Springer Nature.
+
+% Stimuli-responsive emulsions have attracted significant interest for applications in enhanced oil recovery, porous material templating, 
+% in-situ reaction separation systems, and drug delivery scaffolds \cite{tang_stimuli-responsive_2016, bago_rodriguez_capsules_2019}. 
+% These applications are facilitated by stimuli-induced microstructural modifications, which alter the permeability, surface area, and 
+% morphology of the emulsion. Advancements in particle synthesis techniques, along with growing concerns over surfactant toxicity and 
+% environmental impact, have contributed to the renewed interest in particle-stabilized emulsions since their initial discovery by Ramsden 
+% and Pickering in 1907 \cite{rozynek_opening_2019, zhou_magnetic_2011}. Stimuli-responsive behavior in these emulsions has been achieved 
+% through changes in pH, temperature, or chemical composition 
+% \cite{maingret_dextran-based_2020, lin_ph-responsive_2018, raju_ph-responsive_2018, zhang_ph_2022}.
 
@@
 coupled with Molecular Dynamics, we simulate a binary fluid system where ellipsoidal particles, modeled as magnetic dipoles along their 
-symmetry axis, stabilize bijel templates. Simulations without an applied field reveal anisotropic bijel formation, with microstructure 
-evolution dependent on particle reordering at the interface, quantified using the six-fold Steinhardt order parameter \(\langle Q6 \rangle\).
+symmetry axis, stabilize bijel templates. Magnetic fields applied to bijels made without a magnetic field reveal anisotropic bijel formation, 
+with microstructure evolution dependent on particle reordering at the interface, quantified using the six-fold 
+Steinhardt order parameter \(\langle Q6 \rangle\).
 
 We further assess how initial microstructure influences structural changes, showing that the difference in order between initial and final 
-particle monolayers dictates the extent of microstructure evolution. Additionally, applying and removing a magnetic field results in distinct 
-microstructural properties and timescales, highlighting the importance of processing history. These findings demonstrate how magnetic fields, 
-combined with anisotropic particle-stabilized bijels, enable on-demand microstructure switching for potential applications.
+particle monolayers dictates the extent of microstructure evolution if the applied field is increased. Additionally, applying and removing a 
+magnetic field results in distinct microstructural properties and timescales, highlighting the importance of processing history. These findings 
+demonstrate how magnetic fields, combined with anisotropic particle-stabilized bijels, enable on-demand microstructure switching for potential applications.
 

### 2025-03-10 licenses/licenses.tex
Changes 1. Modified and added correct format for attributions 2. Fixed all citation and referencing issues

@@
 \begin{itemize}
-    \item Scalable synthesis of gyroid-inspired freestanding three-dimensional graphene architectures: 1548092-1
-    \item Colloidal Jamming at Interfaces: A Route to Fluid-Bicontinuous Gels [Science, 2005, 309, 5744]: 5966820525314
-    \item Continuous Fabrication of Hierarchical and Asymmetric Bijel Microparticles, Fibers, and Membranes by Solvent Transfer-Induced Phase Separation (STRIPS): 5913140219015
-    \item Magnetophoresis of Magnetic Pickering Emulsions Under Low Field Gradient: Macroscopic and Microscopic 
-    Motion [Langmuir 2021, 37, 5, 1811-1822]: "Reprinted (adapted) with permission from 
+    \item E. Garcia, C. S. Wang, R. N. Sanderson, K. M. McDevitt, Y. Zhang, L. Valdevit, D. R.
+    Mumm, A. Mohraz and R. Ragan. Scalable synthesis of gyroid-inspired freestanding three-
+    dimensional graphene architectures. 1, 3870.: 1548092-1
+    \item Stratford, R. Adhikari, I. Pagonabarraga, J.-C. Desplat and M. E. Cates. Colloidal jam-
+    ming at interfaces: A route to fluid-bicontinuous gels. 309, 2198: 5966820525314
+    \item F. Haase, K. J. Stebe and D. Lee. Continuous fabrication of hierarchical and asymmetric
+    bijel microparticles, fibers, and membranes by solvent transfer-induced phase separation
+    (STRIPS). 27, 7065: 5913140219015
+    \item K. Tham, W. M. Ng, S. S. Leong, S. P. Yeap, S. C. Low, H. L. Lee and J. Lim. Mag-
+    netophoresis of magnetic pickering emulsions under low field gradient: Macroscopic and
+    microscopic motion. 37, 1811: "Reprinted (adapted) with permission from 
     Langmuir 2021, 37, 5, 1811-1822. Copyright 2025 American Chemical Society."
-    \item Assembling Ellipsoidal Particles at Fluid Interfaces Using Switchable Dipolar Capillary Interactions [Adv. Mater., 26: 6715-6719]: Reproduced under the Creative Commons CC BY License.
-    \item Capillary Interactions Between Anisotropic Colloidal Particles, [Phys. Rev. Lett. 2005, 94, 018301]: RNP/25/FEB/088185
-    \item State diagram for particle stabilized emulsions. [Soft Matter, 2015,11, 8393-8403]: 1551968-1
-    \item Shear dynamics of confined bijels [AIP Advances 1 September 2020; 10 (9): 095304]: Reproduced under the Creative Commons CC BY License.
-    \item LB3D: A parallel implementation of the Lattice-Boltzmann method for simulation of interacting amphiphilic fluids [Computer Physics Communications 2017, 217, 149--161]: Reproduced under the Creative Commons CC BY License
+    \item G. B. Davies, T. Kr¨uger, P. V. Coveney, J. Harting and F. Bresme. Assembling ellipsoidal
+    particles at fluid interfaces using switchable dipolar capillary interactions. 26, 6715.: Reproduced under the Creative Commons CC BY License.
+    \item C. Loudet, A. M. Alsayed, J. Zhang and A. G. Yodh. Capillary interactions between
+    anisotropic colloidal particles. 94, 018301: RNP/25/FEB/088185
+    \item S. S. Velankar. A non-equilibrium state diagram for liquid/fluid/particle mixtures. 11, 8393: 1551968-1
+    \item Bonaccorso, S. Succi, M. Lauricella, A. Montessori, A. Tiribocchi and K. H. Luo. Shear
+    dynamics of confined bijels. 10, 095304.: Reproduced under the Creative Commons CC BY License.
+    \item S. Schmieschek, L. Shamardin, S. Frijters, T. Kr¨uger, U. D. Schiller, J. Harting and P. V.
+    Coveney. LB3D: A parallel implementation of the Lattice-Boltzmann method for simulation
+    of interacting amphiphilic fluids. Computer Physics Communications 217, 149 (2017).: Reproduced under the Creative Commons CC BY License
 \end{itemize}

### 2025-03-11 chapters/paper1.tex

--- 2025-03-10 chapters/paper1.tex
@@
 \section{Introduction}
+
+This section is based on work published in the Royal Society of Chemistry's Soft Matter journal and
+work submited to the American Institude of Physics, Physics of Fluids journal. \cite{karthikeyan_formation_2024} 
+It is reproduced from Ref \cite{karthikeyan_formation_2024} with permission from the Royal Society of Chemistry and 
+reproduced from submission number \#POF25-AR-DSFD2024-03180, with the permission of AIP Publishing.
 

### 2025-03-11 chapters/paper2.tex

@@
 
-Sections of this chapter appear in a manuscript submitted to Springer link.
-[author and/or editor(s) of contribution], [volume and/or contribution title], [year of publication], [publisher (as it appears on our copyright page)] \
+Sections of this chapter appear in a manuscript submitted to Springer link as part of the International Conference on Computational 
+Science (ICCS) 2025 in the Computing and Data Science for Materials Discovery and Design track, submission number 259 and is
+% [author and/or editor(s) of contribution], [volume and/or contribution title], [year of publication], [publisher (as it appears on our copyright page)] \
 reproduced with permission of Palgrave Springer Nature.

### 2025-03-13 chapters/paper2.tex
Changes 1. Updated text in aim 2 and aim 3 chapters for better flow

@@
 with microstructure evolution dependent on particle reordering at the interface, quantified using the six-fold 
-Steinhardt order parameter \(\langle Q6 \rangle\).
+Steinhardt order parameter $\langle Q6 \rangle$.
 
@@
 performance in each application is dependent upon the microstructure of the bijel template. Many of the applications listed above benefit 
-from stimuli response, allowing for in-situ microstructure tuning to modify permeability of the material. We want to understand whether 
-bijels provide access to reversible structural modifications which would allow stimuli responsive bijels to be used in in-situ applications.
+from stimuli response, allowing for in-situ microstructure tuning to offer reversible modifications of material permeability. In this section, we analyzes
+whether stimuli responsive bijels provide access to reversible structural modifications.
 
 We begin our investigation by characterizing the microstructure changes observed on bijels stabilized with prolate ellipsoids with a 
-particle volume fraction of $\phi_p = 0.1$. We apply a constant magnetic field of $\bar{B}_z = 0.2$ onto bijels that were simulated 
+particle volume fraction of $\phi_p = 0.1$. We only focus on one system here as the mechanism for stimuli response shown in Aim 1 is identical
+for both systems. Therefore we expect that the qualitative trends between prolate and oblate particles will be matched. We select prolate particles
+as they are more readily synthesized in experiments.
+
+We apply a constant magnetic field of $\bar{B}_z = 0.2$ onto bijels that were simulated 
 with no magnetic field. Once the microstructure has reached its new state, we ramp up the magnetic field to $\bar{B}_z = 0.5$ and 
@@
     \includegraphics[scale=0.5]{../figures/results/paper2/hysteresis_curve.png} 
-    \caption{Plot of the hysteresis curve of a bijel stabilized by magnetically responsive prolate particles. We observe that the domain size increases as we increase the applied
-    magnetic field strength. However, upon decrease of the field strength, we see that the microstructure does not return to its previous value.} 
+    \caption{Plot of the hysteresis curve of a bijel stabilized by magnetically responsive prolate particles. We observe that the domain size increases as we 
+    increase the applied magnetic field strength. However, upon decrease of the field strength, we see that the microstructure does not return to its previous value,
+    demonstrating microstructure hysteresis.} 
     \label{fig:hysteresis_curve} 
@@
 
-Figure \ref{fig:hysteresis_curve} illustrates the hysteresis behavior of magnetically responsive bijels. We observe a hysteresis response of the 
-bijel microstructure, characterized by a non-return of the microstructure to the original average domain size value when reducing the applied 
-magnetic field strength. The increase in the average length scale when applying the magnetic field is due to domain coarsening caused by 
+Figure \ref{fig:hysteresis_curve} we observe a hysteresis response of the bijel microstructure, characterized by a difference in the average domain size
+when increasing and decreasing the magnetic field. The increase in the average length scale when applying the magnetic field is due to domain coarsening caused by 
 reorientation of particles to the magnetic field strength, reducing the interfacial coverage. When decreasing the magnetic field strength, 
 we observe that the domain size does not return to the original value meaning that that the microstructure of the bijel is unaffected by 
-the reduction in magnetic field. This suggests that the particles at the interface are in a kinetically trapped configuration.
+the reduction in applied magnetic field.
+
+This behavior is also observed in past work investigating the shape deformation of particle stabilized emulsions under 
+electric fields. \cite{cui_stabilizing_2013} Cui et al. demonstrated that the particles unjammed and rejammed into a new kinetically arrested state resulting in
+the droplet being elongated in the direction of the applied field. This suggests that the particles at the interface of magnetically responsive bijels are also 
+in a kinetically trapped configuration. We observe in Figure \ref{fig:hysteresis_curve} that the response of the bijel is dependent upon the field strength applied.
+In the following sections, we investigate the impact of magnetic field strength and the initial ordering of the particle monolayer on the observed stimuli response.
 
@@
 
-Bijels have proposed applications as soft matter based material
-templates, drug delivery vectors and separations systems. The materials
-performance in each application is dependent upon the microstructure of
-the bijel template. Many of the applications listed above benefit from
-stimuli response, allowing for in-situ microstructure tuning to modify
-permeability of the material. We want to understand whether bijels
-provide access to reversible structural modifications which would allow
-stimuli responsive bijels to be used in in-situ applications.
-Additionally, in many of the proposed stimuli responsive applications
-for bijels, the timescales of response is important to characterize and
-would also provide a mechanistic understanding of the reasons why the
-microstructure changes occur. We probe these aspects of structural
-response of bijels in this section by assessing the response of bijels
-stabilized by particles with volume fraction of \(\phi_p = 0.1\)
-simulated under no applied field to an applied field in the range
-\(\bar{B} = 0, 0.2, 0.5, 1\). We begin our investigation by visualizing
-the structure before and after the application of magnetic fields.
+From the results in Figure \ref{fig:hysteresis_curve}, we show that the domain size change is dependent upon the applied magnetic field. As porous materials templates,
+the microstructure of the material is of interest as it controls the performance of the material. Additionally, in many of the proposed stimuli responsive applications
+for bijels, the timescales of response is important to characterize and would also provide a mechanistic understanding of the reasons why the microstructure changes 
+occur. We probe these aspects of structural response of bijels in this section by assessing the response of bijels stabilized by particles with volume fraction of 
+$\phi_p = 0.1$ simulated under no applied field to an applied field in the range $\bar{B} = 0, 0.2, 0.5, 1$. We begin our investigation by visualizing the structure before 
+and after the application of magnetic fields.
 
@@
 
-In Figure \ref{fig:microstructure_viz-field_on} we show representative
-snapshots of the bijel at the initial and final timestep with
-\(\bar{B}_z = 0\) and \(\bar{B}_z = 1\). We show that upon application
-of the field, particles align to the direction of the field. As the
-particles orient to the field, they disrupt the packing of particles at
-the interface, causing domain coarsening as the particles rearrange into
-new positions. The particles then rejam in place once the interfacial
-area and particle cross sectional area match. Domain coarsening observed
-in the figure can be explained through the ordering of particles at the
-interface, causing a reduction in the available area that the particles
-have for stabilization.
-
-To correlate the microstructure evolution to the ordering of the
-particle monolayer to the magnetic field, we calculate the nematic order
-parameter. \cite{veerman_phase_1992}
+In Figure \ref{fig:microstructure_viz-field_on} we show representative snapshots of the bijel at the initial and final timestep with $\bar{B}_z = 0$ and $\bar{B}_z = 1$. 
+We show that upon application of the field, particles align to the direction of the field. As the particles orient to the field, they disrupt the packing of particles at
+the interface. This caused domain coarsening as the particles rearrange into new positions before rejamming in place once the interfacial
+area and particle cross sectional area match. Domain coarsening observed in the figure can be explained through the ordering of particles at the interface, causing a 
+reduction in the available area that the particles have for stabilization. To characterize the length scale of the microstructure upon application of the magnetic field,
+we calculate the average domain size. To correlate the microstructure evolution to the ordering of the particle monolayer to the magnetic field, we calculate the 
+nematic order parameter. \cite{veerman_phase_1992}
 
@@
 
-In Figure \ref{fig:domain_size-field_on}, we present the time evolution
-of the normalized average domain size, where normalization is performed
-using the volume-equivalent spherical particle radius \(R = 7.9\). The
-results indicate that upon applying a magnetic field to a bijel
-initially formed without one, the final average domain size increases by
-up to 5.2\% and 2.5\% for oblate- and prolate-particle-stabilized bijels
-respectively. Additionally, in the absence of an external field, domain
-coarsening occurs for both particle morphologies. However, the results
-for oblate particles with a magnetic field is attributed to coalescence
-of domains rather than magnetic field driven ordering of the particles.
+In Figure \ref{fig:domain_size-field_on}, we present the time evolution of the normalized average domain size, where normalization is performed
+using the volume-equivalent spherical particle radius $R = 7.9$. The results indicate that upon applying a magnetic field to a bijel
+initially formed without one, the final average domain size increases by up to 5.2\% and 2.5\% for oblate- and prolate-particle-stabilized bijels
+respectively. The domain coarsening is initially slow, before accelerating rapidly and finally reaching a maximum where it plateaus. 
+Additionally, in the absence of an external field, domain coarsening occurs for both particle morphologies. However, the results
+for oblate particles with a magnetic field is attributed to coalescence of domains rather than magnetic field driven ordering of the particles.
 
-In the same figure, the time evolution of the nematic order parameter
-\(S\) is also plotted to illustrate changes in particle alignment.
-Initially, at \(\bar{B}_z = 0\), a gradual increase in \(S\) is
-observed, attributed to steric interactions driving particle reordering.
-This effect contributes to the domain coarsening seen in the absence of
-an applied field, consistent with the findings of Günther et
-al.~\cite{gunther_timescales_2014}. In the case of
-oblate-particle-stabilized bijels without an external field, domain
-coalescence is primarily driven by steric interactions rather than
-field-induced rearrangement. Furthermore, the rate and extent of
-particle alignment to the field exhibit a dependence on field strength,
-as evidenced by the earlier onset of nematic ordering with increasing
-\(\bar{B}\). We also observed between the time evolution of the nematic
-order parameter and domain size, particularly when comparing results for
-\(\bar{B}_z = 0.5, 1\) against those for \(\bar{B}_z = 0.2\). This
-suggests that nematic ordering alone may not fully account for the
+In the same figure, the time evolution of the nematic order parameter $S$ is also plotted to illustrate changes in particle alignment.
+Initially, at $\bar{B}_z = 0$, a gradual increase in $S$ is observed, attributed to steric interactions driving particle reordering.
+This effect contributes to the domain coarsening seen in the absence of an applied field, consistent with the findings of Günther et
+al.~\cite{gunther_timescales_2014}. In the case of oblate-particle-stabilized bijels without an external field, domain
+coalescence is primarily driven by steric interactions rather than field-induced rearrangement. Furthermore, the rate and extent of
+particle alignment to the field exhibit a dependence on field strength, as evidenced by the earlier onset of nematic ordering with increasing
+$\bar{B}$. We also observed between the time evolution of the nematic order parameter and domain size, particularly when comparing results for
+$\bar{B}_z = 0.5, 1$ against those for $\bar{B}_z = 0.2$. This suggests that nematic ordering alone may not fully account for the
 observed changes in domain size.
 
-Previous studies have demonstrated that microstructural properties,
-particularly length scale and tortuosity, play an important role in the
-performance of porous materials across various applications, including
-battery electrodes and tissue engineering. \cite{zhang_promoting_2019}
-\cite{ebner_tortuosity_2014} \cite{hsieh_architected_2021} Specifically,
-lower tortuosity and more ordered ion-conducting domains have been shown
-to enhance charge/discharge rates in battery systems, while controlled
-tortuosity in artificial bone grafts facilitates improved cell growth
+Previous studies have demonstrated that microstructural properties such as the length scale and tortuosity, play an important role in the
+performance of porous materials across various applications, including battery electrodes and tissue engineering. \cite{zhang_promoting_2019}
+\cite{ebner_tortuosity_2014} \cite{hsieh_architected_2021} Specifically, lower tortuosity and more ordered ion-conducting domains have been shown
+to enhance charge/discharge rates in battery systems, while controlled tortuosity in artificial bone grafts facilitates improved cell growth
 and nutrient transport.
 
-Precise characterization of the anisotropic microstructure is essential
-for the tailored design of application-specific porous materials. To
-quantify the characteristic length scales in each Cartesian direction,
-we compute the second-moment-derived structure factor without radial
-averaging. \cite{jansen_bijels_2011} We also calculate the tortuosity 
-in each cartesian direction. Here, we make a further
-refinement simplifying the domain sizes to directions parallel and
-orthogonal to the magnetic field. These result in the length scales and
-their associated calculation, \(L_{\parallel} = L_{z}\) and
-\(L_{\perp} = \frac{L_x + L_y}{2}\). We perform the same simplification
+Precise characterization of the anisotropic microstructure is essential for the tailored design of application-specific porous materials. To
+quantify the characteristic length scales in each Cartesian direction, we compute the second-moment-derived structure factor. \cite{jansen_bijels_2011} 
+We also calculate the tortuosity  in each cartesian direction. Here, we make a further
+refinement simplifying the domain sizes to directions parallel and orthogonal to the magnetic field. These result in the length scales and
+their associated calculation, $L_{\parallel} = L_{z}$ and $L_{\perp} = \frac{L_x + L_y}{2}$. We perform the same simplification
 with the directional tortuosities.
 
-Tortuosity has been defined using
-the geometric, diffusional and hydraulic tortuosities. Here we define
-the diffusional tortuosity, \(\tau = \frac{D}{D_{eff}}\) which
-characterizes the ratio between the free diffusion of a tracer and the
-effective diffusion of a tracer in the material. Therefore, we plot
-the directional second moment derived length scales and tortuosity in
+Tortuosity has been defined using the geometric, diffusional and hydraulic tortuosities. Here we define
+the diffusional tortuosity, $\tau = \frac{D}{D_{eff}}$ which characterizes the ratio between the free diffusion of a tracer and the
+effective diffusion of a tracer in the material. Therefore, we plot the directional second moment derived length scales and tortuosity in
 Figure \ref{fig:domain_size_aniso-field_on}.
@@
 \includegraphics[scale=0.5]{../figures/results/paper2/domain_size_aniso-field_on.png} 
-\caption{Plotting the anisotropic domain size and tortuosities against the applied magnetic field strength on the left and right respectively for bijels stabilized with magnetically responsive oblate and prolate ellipsoids.
-We see that upon application of the field, bijels stabilized with prolate particles experience a domains ize increase in the direction parallel to the applied field direction, $L_{\parallel}$, while the domain size perpendicular to the applied field, $L_{\perp}$ decreases.
-The opposite is true for bijels stabilized with oblate particles.
-The tortuosity data demonstrate that as the domain size increases, the tortuosity decreases and vice versa.}
+\caption{Plotting the anisotropic domain size and tortuosities against the applied magnetic field strength on the left and right respectively for bijels 
+         stabilized with magnetically responsive oblate and prolate ellipsoids. We see that upon application of the field, bijels stabilized with prolate 
+         particles experience a domains ize increase in the direction parallel to the applied field direction, $L_{\parallel}$, while the domain size 
+         perpendicular to the applied field, $L_{\perp}$ decreases. The opposite is true for bijels stabilized with oblate particles. The tortuosity data 
+         demonstrate that as the domain size increases, the tortuosity decreases and vice versa.} 
 \label{fig:domain_size_aniso-field_on} 
@@
 
-From Figure \ref{fig:domain_size_aniso-field_on}, we see that domain
-size anisotropy is observed upon application of the field for both
-particle morphologies. We also see some domain anisotropy with no
-applied field, which increases upon application of the magnetic field.
-The directional domain sizes, \(L_{\perp}\) and \(L_{\parallel}\)
-increase by \(73\%\) and \(7\%\) respectively for oblate particles and
-\(10\%\) and \(44\%\) respectively for oblate particles. The axes that
-coarsens the most is consistent with past work, explained through the
+From Figure \ref{fig:domain_size_aniso-field_on}, we see that domain size anisotropy is observed upon application of the field for both
+particle morphologies. We also see some domain anisotropy with no applied field, which increases upon application of the magnetic field.
+The directional domain sizes, $L_{\perp}$ and $L_{\parallel}$ increase by 73\% and 7\%\ respectively for oblate particles and
+10\% and 44\% respectively for oblate particles. The axes that coarsens the most is consistent with past work, explained through the
 directions particles reorient in response to the applied magnetic field.
-As particles unjam and rejam at the interface due to reorientating to
-the magnetic field, they adopt direction specific surface coverages
-which manifest as anistropic domains upon jamming. In Figure
-\ref{fig:domain_size_aniso-field_on}, we demonstrate that the
-application of the magnetic field changes the domain size. The
-tortuosity of the bijel is initially around \(\tau \approx 1.5\),
-consistent with simulations of the diffusive tortuosities of gyroid
-structures using Lattice Boltzmann simulations.
-\cite{luo_macroscopic_2020} Upon application of the field,
-\(\tau_{\perp}\) slightly decreases while \(\tau_{\parallel}\)
-increases. We have seen that an increasing domain size decreases the
-tortuosity in our past work. \cite{karthikeyan_formation_2024} This
-observation is in line with the domain size changes observed in Figure
-\ref{fig:domain_size_aniso-field_on}. The results show that the
-tortuosity of the bijel is noticeably affected by the application of
-magnetic fields. This data suggests that magnetic fields applied onto
-bijels stabilized with ellipsoidal particles undergo domain anisotropy
-upon application of magnetic fields. However the particle morphology,
-specifically its axis of symmetry, affect the direction that the domain
-anisotropy is characterized.
 
-Next, we turn to investigate the time gap between the average domain
-size increase and the nematic order parameter. We hypothesized that the
-time taken for particle reorientation to the field would control the
-degree and rate of domain size change when the bijel begins with
-particles with random order. This result suggests that the dynamics of
-the system at higher magnetic field strengths are dependent upon other
-factors that vary upon application of the magnetic field. To understand
-this phenomena, we focus on the dynamics of the particle monolayer.
-First, we visualize the particle monolayer of the bijels stabilized with
-prolate ellipsoids at the initial and final configuration before and
-after application of a magnetic field.
+As particles unjam and rejam at the interface due to reorientating to the magnetic field, they adopt direction specific surface coverages
+which manifest as anistropic domains upon jamming. In Figure \ref{fig:domain_size_aniso-field_on}, we demonstrate that the
+application of the magnetic field changes the domain size. The tortuosity of the bijel is initially around $\tau \approx 1.5$,
+consistent with simulations of the diffusive tortuosities of gyroid structures using Lattice Boltzmann simulations.
+\cite{luo_macroscopic_2020} Upon application of the field, $\tau_{\perp}$ slightly decreases while $\tau_{\parallel}$
+increases. We have seen that an increasing domain size decreases the tortuosity in our past work. \cite{karthikeyan_formation_2024} This
+observation is in line with the domain size changes observed in Figure \ref{fig:domain_size_aniso-field_on}. The results show that the
+tortuosity of the bijel is noticeably affected by the application of magnetic fields. This data suggests that magnetic fields applied onto
+bijels stabilized with ellipsoidal particles undergo domain anisotropy upon application of magnetic fields. However the particle morphology,
+specifically its axis of symmetry, affect the direction that the domain anisotropy is characterized.
+
+Next, we return to investigate the time gap between the average domain size increase and the nematic order parameter. This result suggests that the dynamics 
+of the system at higher magnetic field strengths are dependent upon other factors that vary upon application of the magnetic field. In this system, these factors
+would arise from capillary forces with the interface or steric interactions with other particles at the interface, slowing down the dynamics of the system.
+To understand this phenomena, we focus on the dynamics of the particle monolayer. First, we visualize the particle monolayer of the bijels stabilized with prolate 
+ellipsoids at the initial and final configuration before and after application of a magnetic field.
 
@@
 \includegraphics[scale=0.2]{../figures/results/paper2/particle_viz-field_on.png} 
-\caption{Visualizations of bijels stabilized with oblate and prolate particles simulated at $t = 0$ (left column) and $t = 10^5$ (right column).
-The first and third rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids respectively with no applied field.
-The second and fourth rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids respectively with an applied field of $\bar{B}_z = 1$.
-Particle reorientation to the direction of the field can be seen, resulting in coarsening of the domains.}
+\caption{Visualizations of bijels stabilized with oblate and prolate particles simulated at $t = 0$ (left column) and $t = 10^5$ (right column). The first and 
+         third rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids respectively with no applied field. The second and fourth 
+         rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids respectively with an applied field of $\bar{B}_z = 1$. Particle 
+         reorientation to the direction of the field can be seen, resulting in coarsening of the domains.} 
 \label{fig:particle_viz-field_on} 
@@
 
-In Figure \ref{fig:particle_viz-field_on}, we see the effect of the
-application of the magnetic field on the monolayer. The initial
-configuration of particles at the monolayer show that the orientations
-are random and that the particles tend to lie flat on the interface.
-However, upon application of the magnetic field the particles orient to
-the field direction. The effect that Gunther. et al.~observed for bijels
-stabilized with anisotropic particles can also be observed in these
-snapshots as the particles can be observed to have more local order in
-the final state than in the initial state with no applied field. We
-observe that for bijels stabilized by prolate ellipsoids, we see the
-adoption of more regular arrangements of the colloids on the interface.
-We investigate the effect of local particle ordering next. Past work by
-Bresme and Faraudo and Davies investigating the reorientation of
-particles at interfaces under magnetic fields have shown that a critical
-magnetic field exists, above which the particle orients to the field and
-below which the particle orientation is a function of the capillary
-force and magnetic field derived force. \cite{davies_interface_2014}
-\cite{bresme_orientational_2007} Particle adsorption into the interface
-with microparticles have also been shown to be irreversible due to the
-high adsorption energy. Upon particle reorientation, the microstructure
-change can be driven solely through particle unjamming and re-jamming,
-or it can be driven through the particles dragging the interface during
-this process. The mechanism of unjamming and re-jamming can be
-investigated using the average interfacial angle, $\langle \psi \rangle$
-and the local ordering of the particles characterized with 
-$\langle Q6 \rangle$ Past work has identified that local crystallization 
-of colloidal crystals takes place at \(\langle Q6 \rangle = 0.38\). 
-\cite{toxvaerd_role_2020}
+In Figure \ref{fig:particle_viz-field_on}, we see the initial configuration of particles at the monolayer show that the orientations are random and that the 
+particles tend to lie flat on the interface. However, upon application of the magnetic field the particles orient to the field direction. With no applied field,
+we see that the orientations and positions of the particles vary slightly for both ellipsoidal particle morphologies. This effect is due steric effects between particles,
+as identified in Gunther et al. \cite{gunther_timescales_2014} We observe that for bijels stabilized by prolate ellipsoids, we see the adoption of orientational order
+to the magnetic field and qualitatively different particle arrangements on the interface. These indicate that the interfacial capillary forces or steric interactions 
+with other particles differ upon application of the magnetic field. The particles would prefer to lie flat on the interface to minimize the interfacial energy of 
+adsorption onto the interface. Changes in the local arrangement arise from the unjamming and rejamming process upon application of the magnetic field. These differences 
+in the orientational and interfacial ordering can be characterized to understand how each respective interaction force changes as a function of time.
+
+Bresme and Faraudo and Davies investigating the reorientation of particles at interfaces under magnetic fields have shown that a critical magnetic field exists, 
+above which the particle orients to the field and below which the particle orientation is a function of the capillary force and magnetic field derived force. 
+\cite{davies_interface_2014} \cite{bresme_orientational_2007} Particle adsorption into the interface with microparticles have also been shown to be irreversible due 
+to the high adsorption energy. Upon particle reorientation, the microstructure change can be driven solely through particle unjamming and re-jamming, or it can be 
+driven through the particles dragging the interface during this process. The mechanism of unjamming and re-jamming can be investigated using the average interfacial 
+angle, $\langle \psi \rangle$ and the local ordering of the particles characterized with  $\langle Q6 \rangle$ Past work has identified that local crystallization 
+of colloidal crystals takes place at \(\langle Q6 \rangle = 0.38\). \cite{toxvaerd_role_2020}
 
@@
 \includegraphics[scale=0.3]{../figures/results/paper2/interface_angle-nint-field_on.png} 
-\caption{Plots of the interface angle $(\langle \psi \rangle)$ and six fold Steinhardt order parameter 
-         $(\langle Q6 \rangle)$ on the left and right respectively, versus time for bijels stabilized with 
-         oblate and prolate ellipsoids on the top and bottom rows respectively. We demonstrate that upon application 
-         of a magnetic field, the behavior of $(\langle \psi \rangle)$ and $(\langle Q6 \rangle)$ differ significantly 
-         between oblate and prolate ellipsoids indicating that the dynamics for both particle morphologies differ.
-We also observe magnetic field dependence in each property for both particle types, suggesting that these changes are driven primarily through the change in the applied field strength.}
+\caption{Plots of the interface angle $(\langle \psi \rangle)$ and six fold Steinhardt order parameter $(\langle Q6 \rangle)$ on the left and right respectively, 
+         versus time for bijels stabilized with oblate and prolate ellipsoids on the top and bottom rows respectively. We demonstrate that upon application 
+         of a magnetic field, the behavior of $(\langle \psi \rangle)$ and $(\langle Q6 \rangle)$ differ significantly between oblate and prolate ellipsoids 
+         indicating that the dynamics for both particle morphologies differ. We also observe magnetic field dependence in each property for both particle types, 
+         suggesting that these changes are driven primarily through the change in the applied field strength.} 
 \label{fig:interface_angle-nint-field_on} 
@@
 
-From Figure \ref{fig:interface_angle-nint-field_on}, we identify that
-prolate and oblate particles respond differently at the interface. For
-bijels stabilized by oblate ellipsoids, we characterize an increase in
-\(\langle \psi \rangle\) from an initial value of \(19 ^{\circ}\),
-before it reduces slightly and begins to increase once again. The
-initial starting value of \(\langle \psi \rangle\) indicates the
-particles are lying close to flat on the interface, before they begin to
-tilt out of the interface when the magnetic field is applied. Then,
-\(\langle \psi \rangle\) plateaus as the interface begins to move in
-response to the tilting particle at the interface. This is caused by the
-large adsorption energy of the particles at the interface of the bijel,
-caused by high surface tension. Finally, the particles jam in place,
-locking the interface at an angle to the particle. We see the rate of
-increase in \(\langle \psi \rangle\) at early stages and the time spent
-in the plateau increase with a larger applied magnetic field. The final
-angle at the interface is also dependent upon the applied field
+From Figure \ref{fig:interface_angle-nint-field_on}, we identify that prolate and oblate particles respond differently at the interface. For
+bijels stabilized by oblate ellipsoids, we characterize an increase in $\langle \psi \rangle$ from an initial value of \(19 ^{\circ}\),
+before it reduces slightly and begins to increase once again. The initial starting value of $\langle \psi \rangle$ indicates the
+particles are lying close to flat on the interface, before they begin to tilt out of the interface when the magnetic field is applied. Then,
+$\langle \psi \rangle$ plateaus as the interface begins to move in response to the tilting particle at the interface. This is caused by the
+large adsorption energy of the particles at the interface of the bijel, caused by high surface tension. Finally, the particles jam in place,
+locking the interface at an angle to the particle. We see the rate of increase in $\langle \psi \rangle$ at early stages and the time spent
+in the plateau increase with a larger applied magnetic field. The final angle at the interface is also dependent upon the applied field
 strength.
 
-When analyzing \(\langle \psi \rangle\) for bijels stabilized by prolate
-particles, this behavior can also be observed. \(\langle \psi \rangle\)
-begins at \(80 ^{\circ}\). The difference in the initial
-\(\langle \psi \rangle\) compared to oblate particles is due to the
-direction of the axis of symmetry. In prolate particles, the axis of
-symmetry lies parallel with the interface and \(\langle \psi \rangle\)
-measures the angle between the interface normal and the orientation of
-the axis of symmetry. We see \(\langle \psi \rangle\) decrease slightly,
-before plateauing and slowly increasing again. The rate of decrease in
-\(\langle \psi \rangle\) is field dependent, although given the small
-decrease in \(\langle \psi \rangle\) it is unclear if the final value of
-this parameter is field dependent for bijels stabilized with prolate
-particles. The changes in \(\langle \psi \rangle\) for bijels stabilized
-with prolate particles are small compared to bijels stabilized with
-oblate particles. We believe this is due to local particle effects at
-the interface. We probe this by identifying the local particle ordering
-at the interface characterized by \(\langle Q6 \rangle\).
+When analyzing $\langle \psi \rangle$ for bijels stabilized by prolate particles, this behavior can also be observed. $\langle \psi \rangle$
+begins at $10 ^{\circ}$.We see $\langle \psi \rangle$ decrease slightly, before plateauing and slowly increasing again. The rate of decrease in 
+$\langle \psi \rangle$ is field dependent, although given the small decrease in $\langle \psi \rangle$ it is unclear if the final value of this parameter 
+is field dependent for bijels stabilized with prolate particles. The changes in $\langle \psi \rangle$ for bijels stabilized with prolate particles are 
+small compared to bijels stabilized with oblate particles. We believe this is due to local particle effects at the interface. We probe this by identifying 
+the local particle ordering at the interface characterized by $\langle Q6 \rangle$.
 
-We see that for oblate particles, \(\langle Q6 \rangle\) sees a
-decrease from its initial value. However the dynamics are controlled by
-the applied magnetic field strength. We split the phases of dynamics
-into three sections, similar to \(\langle \psi \rangle\) with the first
-section seeing a decrease in \(\langle Q6 \rangle\) upon application of
-the magnetic field, followed by a plateau and finally a gradual increase
-before jamming takes place. These results indicate that the ordering of
-the particles is reduced by the applied magnetic field, before a
-restoration of some of the pre-existing order. The final values of
-\(\langle Q6 \rangle\) are magnetic field dependent, with a stronger
-magnetic field having a lower final \(\langle Q6 \rangle\) value
-indicating that either the ordering of particles influence the angle at
-the interface or vice versa. We observe that for bijels stabilized by
-oblate particles, the interface ordering of the particles increases as a
-function of the applied field strength. We also observe from plotting
-\(\langle Q6 \rangle\) that application of a magnetic field creates a
-local crystallization of the colloid monolayer characterized as
-\(\langle Q6 \rangle > 0.38\). \cite{toxvaerd_role_2020}
+We see that for oblate particles, $\langle Q6 \rangle$ sees a decrease from its initial value. However the dynamics are controlled by
+the applied magnetic field strength. We split the phases of dynamics into three sections, similar to $\langle \psi \rangle$. In the first
+section, we see a decrease in $\langle Q6 \rangle$ upon application of the magnetic field, followed by a plateau and finally a gradual increase
+before jamming takes place. These results indicate that the ordering of the particles is reduced by the applied magnetic field, before a
+restoration of some of the pre-existing order. The final values of $\langle Q6 \rangle$ are magnetic field dependent, with a stronger
+magnetic field having a lower final $\langle Q6 \rangle$ value indicating that either the ordering of particles influence the angle at
+the interface or vice versa. We observe that for bijels stabilized by oblate particles, the interface ordering of the particles increases as a
+function of the applied field strength. We also observe from plotting $\langle Q6 \rangle$ that application of a magnetic field creates a
+local crystallization of the colloid monolayer characterized as $\langle Q6 \rangle > 0.38$. \cite{toxvaerd_role_2020}
 
-Figure \ref{fig:domain_size-field_on}, we observed a gap between the
-growth of the nematic order parameter and an increase in the domain
-size. To probe why this occurs, we recast \(\langle \psi \rangle\),
-\(\langle Q6 \rangle\) and \(S\) in terms of the physical phenomena
-they represent. The nematic order parameter represents the ordering of
+Next, we want to identify which of these forces represent the timescale that controls the dynamics of the system. We can calculate a characteristic
+timescale for each factor from the calculated particle properties.
+The nematic order parameter $S$ represents the ordering of
 particles to an average direction, which in the case of the application
@@
 indicates a particle-field orientation dependence. We name this
-timescale \(\tau_S\). When applying a field to a bijel system with a
+timescale $\tau_S$. When applying a field to a bijel system with a
 randomly oriented particle monolayer, the most significant transition
-point is the isotropic to nematic transition or when \(S \geq 0.3\). We
-define \(\tau_S\) for this section of the analysis by identifying when
-\(S \geq 0.3\).
+point is the isotropic to nematic transition or when $S \geq 0.3$. We
+define $\tau_S$ as the the isotropic to nematic transition point.
 
-We can also do the same for \(\langle \psi \rangle\) and
-\(\langle Q6 \rangle\). A timescale derived from
-\(\langle \psi \rangle\) named \(\tau_{\langle \psi \rangle}\)
+We can also do the same for $\langle \psi \rangle$ and
+$\langle Q6 \rangle$. A timescale derived from
+$\langle \psi \rangle$ named $\tau_{\langle \psi \rangle}$
 represents the capillary timescale between the interface and the
 particle. Given the shape of the plot, we assign the
-\(\tau_{\langle \psi \rangle}\) to be the time when the first minimum of
-\(\langle \psi \rangle\) is observed for prolate particles and the first
+$\tau_{\langle \psi \rangle}$ to be the time when the first minimum of
+$\langle \psi \rangle$ is observed for prolate particles and the first
 maximum for oblate particles. A timescale derived from
-\(\langle Q6 \rangle\), named \(\tau_{\langle Q6 \rangle}\) is also
+$\langle Q6 \rangle$, named $\tau_{\langle Q6 \rangle}$ is also
 calculated which represents a timescale of local particle rearrangement.
-We define \(\tau_{\langle Q6 \rangle}\) as the time when
+We define $\tau_{\langle Q6 \rangle}$ as the time when
 \(\langle Q6 \rangle \geq 0.38\) for prolate particles and the global
-minimum of \(\tau_{\langle Q6 \rangle}\) for the oblate particles. We
+minimum of $\tau_{\langle Q6 \rangle}$ for the oblate particles. We
 omit \(\bar{B} = 0\) as previous results have identified the domain size
@@
 In Figure \ref{fig:domain_size-field_on-scaled}, the left plot plots the
-average domain size against time rescaled using \(\tau_S\). We see that
+average domain size against time rescaled using $\tau_S$. We see that
 the domain sizes do not collapse onto a single line, which is expected
@@
 demonstrates the average domain size against time rescaled using
-\(\tau_{\langle \psi \rangle}\). We see that there is good agreement
+$\tau_{\langle \psi \rangle}$. We see that there is good agreement
 between all simulations for prolate particles, although the point when
-\(\frac{t}{\tau_{\langle \psi \rangle}} = 1\) lies when the domain size
+$\frac{t}{\tau_{\langle \psi \rangle}} = 1$ lies when the domain size
 transition has started. However for oblate particles we see that this
@@
 The right plot demonstrates the domain size change after rescaling time
-with \(\tau_{\langle Q6 \rangle}\) where we see good collapse between
+with $\tau_{\langle Q6 \rangle}$ where we see good collapse between
 all plots while the domain size transition also begins at
-\(\frac{t}{\tau_{\langle Q6 \rangle}} = 1\). The latter point
+$\frac{t}{\tau_{\langle Q6 \rangle}} = 1$. The latter point
 demonstrates that the dynamics for the structural response of randomly
@@
 the interface rather than the orientation of the particle to the
-magnetic field.We see that before \(\tau_{\langle Q6 \rangle} = 1\),
-\(\bar{B} = 0.2\) for the oblate particles does not collapse onto the
-other plots, indicating that the dynamics before that point are
-controlled by another phenomena.
+magnetic field. As the dynamics of both particle morphologies are well described
+using the particle steric effects timescale, denoted by $\tau_{\langle Q6 \rangle}$,
+we conclude that the dynamics of bijels stabilized by ellipsoidal particles are controlled by
+interfacial particle rearrangement at the interface.
 
@@
 identified by Gunther et al.~\cite{gunther_timescales_2014} The first
-type is what is observed for \(\bar{B} = 0.2\), where the interfacial
+type is what is observed for $\bar{B} = 0.2$, where the interfacial
 coverage and average orientation of the particle to the field and to the
@@
 the same rate as the particles reorienting to the magnetic field. The
-second is observed for \(\bar{B} = 0.5, 1\), where there is a time lag
+second is observed for $\bar{B} = 0.5, 1$, where there is a time lag
 between particle ordering, and the intiation of domain coarsening. In
@@
 size changes in bijels after jamming are constrained by magnetic field
-driven local crystallization of the particle monolayer. In this section,
+driven local rearrangement of the particle monolayer. In this section,
 we explore how pre-existing order in the particles affect the degree of
@@
 reorientation at the interface causes microstructure reorientation we
-quantify the average interface angle, \(\langle \psi \rangle\) and the
-local interface order of the material, \(\langle Q6 \rangle\) in Figure
+quantify the average interface angle, $\langle \psi \rangle$ and the
+local interface order of the material, $\langle Q6 \rangle$ in Figure
 \ref{fig:interface_angle-nint-field_up}.
@@
 show that there are three time evolution trends for
-\(\langle \psi \rangle\) and \(\langle Q6 \rangle\) for both oblate and
+$\langle \psi \rangle$ and $\langle Q6 \rangle$ for both oblate and
 prolate particles despite the differences in the initial state of the
-particles. In oblate particles \(\langle \psi \rangle\) begins closer to
+particles. In oblate particles $\langle \psi \rangle$ begins closer to
 \(0 ^{\circ}\) as the axis of symmetry lies close to the interface
@@
 \(\bar{B}: 0 \rightarrow 1\) and \(\bar{B}: 0.2 \rightarrow 1\),
-\(\langle \psi \rangle\) increases, plateaus and increases again before
+$\langle \psi \rangle$ increases, plateaus and increases again before
 plateauing again. This is indicative of particles tilting at the
@@
 particles to tilt out of the interface. We see similar trends for bijels
-stabilized by prolate particles. \(\langle \psi \rangle\) begins near
+stabilized by prolate particles. $\langle \psi \rangle$ begins near
 \(80 ^{\circ}\). We see a decrease before reorientation ceases, and
-finally \(\langle \psi \rangle\) increases again.
+finally $\langle \psi \rangle$ increases again.
 
-When looking at \(\langle Q6 \rangle\) for \(\bar{B}: 0 \rightarrow 1\)
+When looking at $\langle Q6 \rangle$ for \(\bar{B}: 0 \rightarrow 1\)
 and \(\bar{B}: 0.2 \rightarrow 1\) for oblate particles, we see that the
 trends are similar with an initial decrease, followed by a plateau and
-increase over time before plateauing again. \(\langle Q6 \rangle\)
+increase over time before plateauing again. $\langle Q6 \rangle$
 generally decreases with a large decrease observed for
@@
 to a structure that is locally ordered but not close packed. For prolate
-particles, we see an increase in \(\langle Q6 \rangle\) with a plateau
+particles, we see an increase in $\langle Q6 \rangle$ with a plateau
 occurring in both systems around 5000 timesteps. The significance of
@@
 arise from particle tilting on the interface identified as the large
-difference between the initial and final \(\langle \psi \rangle\) with
+difference between the initial and final $\langle \psi \rangle$ with
 an associated decrease in the interface coverage, initiating domain
@@
 particles, we observe a small degree of particle tilting as can be seen
-from \(\langle \psi \rangle\), although the dynamics are primarily
-driven by the change in \(\langle Q6 \rangle\), indicated as a slight
+from $\langle \psi \rangle$, although the dynamics are primarily
+driven by the change in $\langle Q6 \rangle$, indicated as a slight
 dip and plateau before the particles begin reordering and packing more
@@
 \(\bar{B}: 1 \rightarrow 1\). We see a decrease in
-\(\langle Q6 \rangle\) for bijels stabilized with oblate particles with
+$\langle Q6 \rangle$ for bijels stabilized with oblate particles with
 field application of \(\bar{B}: 0.5 \rightarrow 1\) compared to an
@@
 experiencing the \(\bar{B}: 0.5 \rightarrow 1\) field application
-history. The \(\langle \psi \rangle\) results indicate that the
+history. The $\langle \psi \rangle$ results indicate that the
 particles rearrange over time to lie flatter on the interface. For
@@
 \(\bar{B}: 1 \rightarrow 1\). For the \(\bar{B}: 0.5 \rightarrow 1\)
-case, we see a slight increase in \(\langle \psi \rangle\) before a
+case, we see a slight increase in $\langle \psi \rangle$ before a
 decrease and increase compared to the \(\bar{B}: 1 \rightarrow 1\) case
 where we characterize a slight decrease over time. We also characterize
-a slight decrease in \(\langle Q6 \rangle\) over time for the
+a slight decrease in $\langle Q6 \rangle$ over time for the
 \(\bar{B}: 1 \rightarrow 1\) case while characterizing a larger decrease
@@
 coarsening of the bijel once stimuli is removed. To investigate why this
-is the case, we plot \(\langle \psi \rangle\) and
-\(\langle Q6 \rangle\) for bijels stabilized with ellipsoidal particles
+is the case, we plot $\langle \psi \rangle$ and
+$\langle Q6 \rangle$ for bijels stabilized with ellipsoidal particles
 below.
@@
 In Figure \ref{fig:interface_angle-field_down}, we plot
-\(\langle \psi \rangle\) and \(\langle Q6 \rangle\) in the left and
+$\langle \psi \rangle$ and $\langle Q6 \rangle$ in the left and
 right columns respectively. While there are minor differences to the
-time when \(\langle \psi \rangle\) and \(\langle Q6 \rangle\) increase
+time when $\langle \psi \rangle$ and $\langle Q6 \rangle$ increase
 and decrease respectively for bijels stabilized by oblate particles the
@@
 For prolate particles, we see that a reduction in
-\(\langle \psi \rangle\) takes place for all runs except for
+$\langle \psi \rangle$ takes place for all runs except for
 \(\bar{B}: 0.5\rightarrow 0\). This is attributed to be due to this
@@
 \(\bar{B}: 1\rightarrow 0\) case also reaches approximately the same
-value for \(\langle \psi \rangle\). \(\bar{B}: 0.2\rightarrow 0\) and
+value for $\langle \psi \rangle$. \(\bar{B}: 0.2\rightarrow 0\) and
 \(\bar{B}: 0\rightarrow 0\) reduce much more slowly than
@@
 
-Looking at \(\langle Q6 \rangle\), we see that all simulations see a
+Looking at $\langle Q6 \rangle$, we see that all simulations see a
 decrease over time. We see that contrary to previous trends, the
 \(\bar{B}: 1\rightarrow 0\) simulation has a smaller change in
-\(\langle Q6 \rangle\) than \(\bar{B}: 0.5\rightarrow 0\) although this
+$\langle Q6 \rangle$ than \(\bar{B}: 0.5\rightarrow 0\) although this
 difference is also a result of the initial particle orientation and
@@
 to lose short range order upon removal of the magnetic field that
-enforces it, resulting in the large decrease in \(\langle Q6 \rangle\)
+enforces it, resulting in the large decrease in $\langle Q6 \rangle$
 observed.

### 2025-03-13 chapters/paper3.tex
Changes 1. Modified and added correct format for attributions 2. Fixed all citation and referencing issues
updating plot for herschel buckley fit
Changes 1. Updated text in aim 2 and aim 3 chapters for better flow

@@
 It is also expected that the effective viscosity will be different between the four microstructures dependent upon the 
-degree of nematic ordering and microstructural anisotropy of the bijel. Nematic ordering of the particles will be mimic 
-shear banding in colloidal suspensions, resulting in a lowered effective viscosity compared to bijels without nematically 
+degree of nematic ordering and microstructural anisotropy of the bijel. Nematic ordering of the particles will 
+should resulting in a lowered effective viscosity compared to bijels without nematically 
 ordered particles. \cite{xu_relation_2013, vermant_flow-induced_2005} Tracking of the proportion of particles on the 
@@
 
-We begin our investigation by analyzing the domain size change over time for bijels stabilized by ellipsoidal particles. We also
-focus our attention on the effect of the initial state of the particle monolayer, in addition to the addition or removal of magnetic
-fields. We perform this analysis on bijels stabilized by oblate and prolate particles. Bijel templates simulated in Aim 1 with no
-field and a field strength of $\bar{B} = 1$ stabilized with a particle volume fraction $\phi_p = 0.15$. We apply a field strength of
-$\bar{B} = 1$ or switch off the applied field. This results in four setups, $\bar{B}:0\rightarrow 0$, $\bar{B}:0\rightarrow 1$,
-$\bar{B}:1\rightarrow 0$ and $\bar{B}:1\rightarrow 1$. We then define a shear capillary number, 
-$Ca_s = \frac{\dot{\gamma} R_{s} \eta_{f}}{\sigma}$ where $\dot{\gamma}$ is the applied strain rate, $R_s$ is the equivalent
-spherical radius of the particles, $R_s = 7.9$, $\eta_f$ is the dynamic viscosity of the fluid and $\sigma$ is the surface tension
-of the interface. We use five shear numbers, $Ca_s = 10^{-4}, 50^{-5}, 10{^-5}, 50^{-6}, 10^{-6}$.
+\section{Results}\label{sec:results_p3}
 
-\section{Results}\label{sec:results_p3}
-\subsection{Microstructure change}
-
-First we plot the domain size of each system over time to analyze the effect of application of shear and magnetic fields.
-
-\begin{figure} 
-    \centering 
-    \includegraphics[scale=0.3]{../figures/results/paper3/domain_size-time_compare.png} 
-    \caption{Comparisons of the time evolution of the average domain size for bijels stabilized by ellipsoidal particles undergoing
-             various shear rates under four processes. Initially, the domain size coarsens for all runs under applied shear before
-             reducing in some cases.} 
-    \label{fig:domain_size_time_shear} 
-\end{figure}
-
-From Figure \ref{fig:domain_size_time_shear}, domains generally coarsen with time but the presence of a magnetic field 
-significantly alters the coarsening dynamics due to magnetic field driven particle reordering on the interface. In the 
-$\bar{B}: 1 \to 0$ and $\bar{B}: 1 \to 1$ cases, an initial plateau in domain size is observed, followed by a divergence in 
-growth depending on $Ca$. The shear rate appears to influence domain coarsening, with higher $Ca_s$ leading to delayed or 
-suppressed growth, especially in the presence of a field. The difference between applying $\bar{B}: 0 \to 1$ and 
-removing $\bar{B}: 1 \to 0$ the field demonstrates the stability of the particle monolayer when a field is switched off.
-There is little difference in the qualitative trends of domain size change for bijels stabilized with oblate or prolate particles,
-This analysis highlights how the interplay between shear, capillary effects, and magnetic interactions governs bijel 
-microstructural stability and evolution, offering insights into tunable bijel design for applications requiring controlled 
-domain morphology. Domain coarsening
-
-\begin{figure} 
-    \centering 
-    \includegraphics[scale=0.3]{../figures/results/paper3/gaussian-time_compare.png} 
-    \caption{Plots of the time evolution of the area averaged Gaussian curvature $\langle K \Sigma^{-2} \rangle$ for four 
-             processing histories applied to bijels stabilized with oblate and prolate ellipsoids. We demonstrate that the 
-             magnitude of the gaussian curvature reduces for all systems except for $\bar{B}: 0 \to 1$.} 
-    \label{fig:gaussian_curvature_time_shear} 
-\end{figure}
-
-Figure \ref{fig:gaussian_curvature_time_shear} reveals that the area averaged Gaussian curvature generally decreases in magnitude over time for all cases except 
-$\bar{B}: 0 \to 1$. We also characterize that the curvature evolution of all systems are shear independent. $\bar{B}: 0 \to 1$ is
-unique because particle rearrangements at the interface dominates the dynamics of the microstructure, not observed in all other
-cases. From the time evolution of the curvature, we show that the same mechanism drives domain coarsening in all cases. Domain
-coarsening is driven through a reduction in the interfacial area covered by the particle monolayer. Previous investigates have 
-demonstrated how the orientation and arrangement of particles on the interface affect the domain size. 
-\cite{gunther_timescales_2014} We focus our investigation on this aspect in the following section.
-
-\subsection{Particle properties}
-
-Particles at the interface of bijels stabilized with ellipsoidal particles reorient at the interface to minimize interfacial and
-steric energies. \cite{gunther_timescales_2014} The particles stabilizing bijels in confined systems under shear have been shown to
-orient to the direction of shear and ejected from the interface at sufficiently long times or shear.\cite{bonaccorso_shear_2020} 
-We probe these aspects of the particle monolayer in this section.
-
-\begin{figure} 
-    \centering 
-    \includegraphics[scale=0.3]{../figures/results/paper3/angle_to_cartesian-SS.png} 
-    \caption{Comparisons of the initial and final particle orientations of the particles to each cartesian direction under
-             four processing histories for bijels stabilized with oblate and prolate ellipsoids at multiple shear rates. We show
-             shear dependent ordering of the particle monolayer if the initial particle monolayer begins with particle order.} 
-    \label{fig:particle_orientation_cartesian_shear} 
-\end{figure}
-
-From Figure \ref{fig:particle_orientation_cartesian_shear} we see that with bijel templates simulated under $\bar{B} = 0$, the
-particles adopt a random orientation. Upon application of shear, we see that there is little directional ordering to the 
-shear direction. Upon application of the magnetic field, the particle order to the direction of the magnetic field. When 
-investigating the orientational ordering of a bijel simulated under a field strength of $\bar{B} = 1$, we see that there is
-shear dependent decay of the orientational ordering when the magnetic field is removed. We also characterize similar behavior
-when maintaining the applied field, indicating that two reasons for surface area reduction is present. These mechanisms are attributed
-to reorientation of particles at the interface or ejection of particles from the interface. We can characterize the former mechanism
-using the average interfacial angle between the particle and the interface $\langle \psi \rangle$.
-
-\begin{figure} 
-    \centering 
-    \includegraphics[scale=0.3]{../figures/results/paper3/psi-time_compare.png} 
-    \caption{Comparisons of the interfacial angle of bijels stabilized by ellipsoidal particles as a function of 
-             the applied shear rate at four different processing histories. We show that upon application of shear
-             particles tilt out of the interface reduces the interfacial area stabilized. $\bar{B}: 0 \to 1$ shows 
-             large variations in the interface angle.} 
-    \label{fig:interface_angle_shear} 
-\end{figure}
-
-From Figure \ref{fig:interface_angle_shear}, we demonstrate that there is a slow increase in the interface angle over time for all cases
-except for $\bar{B}: 0 \to 1$. Shear dependent $\langle \psi \rangle$ can be observed for some of the systems, indicating that the mechanism
-of domain coarsening differs.The data for $\bar{B}: 0 \to 1$ is characterized as such due to a particle reorientation at the interface
-in response to the field just after the magnetic field has been applied. To reduce the interfacial energy as the particles tilt from the 
-interface, the interface moves with the particle until it jams in place. We can characterize the impact of the interfacial angle on the 
-particle packing using the radial distribution function (rdf).
-
-\begin{figure} 
-    \centering 
-    \includegraphics[scale=0.3]{../figures/results/paper3/rdf-SS.png} 
-    \caption{Comparisons of the initial and final radial distribution function of the particles of bijels stabilized by ellipsoidal 
-    particles as a function of the applied shear rate at four different processing histories. We show that there are minor differences
-    in the particle ordering at the interface, suggesting that the particle tilting affects the coverage of particles at the interface.} 
-    \label{fig:rdf_shear} 
-\end{figure}
-
-From Figure \ref{fig:rdf_shear}, we show that the change in the packing of the particles on the interface is not correlated to the change 
-in the interfacial angle of the particles on the interface when changing the applied field strength in all cases. We then characterize the proportion 
-of particles on the interface to investigate how the proportion of particles on the interface changes and its impact on the interfacial area.
-
-\begin{figure} 
-    \centering 
-    \includegraphics[scale=0.3]{../figures/results/paper3/n_int-time_compare.png} 
-    \caption{Comparisons of the proportion of particles on the interface of bijels ($n_{int}$) stabilized by ellipsoidal particles as a function of 
-             the applied shear rate at four different processing histories. We show that upon application of shear, many cases have a 
-             reduction in the number of particles on the interface while in others it stays the same. For cases where $n_{int}$ reduces, we can 
-             attribute the domain size coarsening to this effect.} 
-    \label{fig:particles_interface_prop_shear} 
-\end{figure}
-
-We show in Figure \ref{fig:particles_interface_prop_shear} that when the magnetic field is kept the same between the template and during shear, the
-proportion of particles on the interface ($n_{int}$) stays approximately the same. However when changing the applied field strength, $n_{int}$ more 
-sensitive to shear. Here we also characterize that increasing the applied field strength reduces $n_{int}$ more than decreasing it. This is consistent
-with the amount of coarsening observed for each case seen in Figure \ref{fig:domain_size_time_shear} where $\bar{B}:0 \rightarrow 1$ shows the largest
-change. Next, we characterize how the microstructure and particle properties affect the constant rheology properties of the bijels.
+We begin our investigation by analyzing the rheological response of bijels stabilized by ellipsoidal particles under constant shear.
+Specifically, we investigate the effect that particle order has on the rheological response characterized. We are also interested in
+identifying the impact that the application of magnetic fields have on the rheological response of the bijel. 
+Bijel templates simulated in Aim 1 with no field and a field strength of $\bar{B} = 1$ stabilized with a prolate and oblate particles with a 
+particle volume fraction $\phi_p = 0.15$ were used as the starting point for these simulations. Next, We apply a field strength of
+$\bar{B} = 1$ or switch off the applied field to all structures. This results in four processing setups; $\bar{B}:0\rightarrow 0$, $\bar{B}:0\rightarrow 1$,
+$\bar{B}:1\rightarrow 0$ and $\bar{B}:1\rightarrow 1$. We then define a shear capillary number,  $Ca_s = \frac{\dot{\gamma} R_{s} \eta_{f}}{\sigma}$ where 
+$\dot{\gamma}$ is the applied strain rate, $R_s$ is the equivalent spherical radius of the particles, $R_s = 7.9$, $\eta_f$ is the dynamic viscosity of the 
+fluid and $\sigma$ is the surface tension of the interface. We use five shear numbers, $Ca_s = 1\cdot10^{-4}, 5\cdot10^{-5}, 1\cdot10^{-5}, 5\cdot10^{-6}, 1\cdot10^{-6}$.
 
@@
 before the structure breaks. The adsorption of particles on the interface of a bijel could affect how this slip occurs. Previous work investigating
-the rheology of bijels have determined shear thinning behavior characterized with a Herschel-Buckley fit equation. We perform this analysis on the
-structures we have simulated. First, we plot the shear stress over time.
+the rheology of bijels have determined shear thinning behavior characterized with a Herschel-Buckley fit equation. \cite{macmillan_rheological_2019} 
+We perform this analysis on the structures we have simulated. First, we plot the shear stress over time.
 
@@
 
-Figure \ref{fig:stress_time} shows that there is no definitive steady state value of the shear stress obtained from the experiments performed. This is
-attributed to the coarsening of the domains and reorientation of particles at the interface. To characterize the viscosity, we identify pseudo-steady
-state regions within each of the shear stress plots and fit the stress identified within this pseudo-steady state region to the strain rate. We fit 
-the stress to the strain using a Herschel-Buckley rheology model, $\sigma_{xz} = \sigma_{y} + K(\dot{\gamma})^{n}$. $\sigma_{xz}$ is the experimental
-shear stress, $\sigma_{y}$ is the yield stress of the bijel, $K$ is the flow consistency index and $n$ is the flow index.
-Where appropriate, we include results corresponding to a shear capillary number of $Ca_s = 10^{-6}$.
+Figure \ref{fig:stress_time} shows that there is no definitive steady state value of the shear stress obtained in the simulations performed. This is
+attributed to the coarsening of the domains and reorientation of particles at the interface. \cite{tavacoli_novel_2011,macmillan_rheological_2019} 
+Tavacoli et al. investigated the rheological response of Ethanediol/Nitromethane bijels and identified that upon placement of a needle to calculate the yield
+stress of the bijel, the structure of the material was irreversibly altered. \cite{tavacoli_novel_2011} Macmillian et al. identified that repeated 
+shearing of a bijel synthesized using direct mixing resulted in degraded mechanical performance. \cite{macmillan_rheological_2019}
+To characterize the viscosity, we identify pseudo-steady state regions within each of the shear stress plots and fit the stress identified within this 
+pseudo-steady state region to the strain rate. Pseudo-steady state regions are identified by measuring where the rate of change of shear stress is 
+smallest for the longest duration. We fit the calculated stress to the applied strain rate using a Herschel-Buckley rheology model defined as
+$\sigma_{xz} = \sigma_{y} + K(\dot{\gamma})^{n}$. $\sigma_{xz}$ is the shear stress calculated from the simulation, $\sigma_{y}$ is the yield stress of the bijel, 
+$K$ is the flow consistency index and $n$ is the flow index.Where appropriate, we include results corresponding to a shear capillary number of 
+$Ca_s = 10^{-6}$ as in many stress responses, we show that $Ca_s = 10^{-6}$ may not always yield usable results.
 
@@
 while undergoing fluid particle interactions without affecting other particles due to orientational ordering imposed from the application 
-of magnetic fields.
+of magnetic fields. From the Hershel Buckley fit, we also identified the flow index, consistency index and the yield stress of the bijels,
+tabulated in Table \ref{table:rheology_fit}.
 
@@
      \hline\hline
-     $\bar{B}: 0 \rightarrow 0$ & 0.5 & 0.522 & 1.030 & $1.054 \cdot 10^{-4}$ \\ 
+     $\bar{B}: 0 \rightarrow 0$ & 0.5 & 0.511 & 0.999 & $7.168 \cdot 10^{-5}$ \\ 
      \hline
-     $\bar{B}: 0 \rightarrow 1$ & 0.5 & 0.570 & 0.975 & $5.365 \cdot 10^{-5}$ \\
+     $\bar{B}: 0 \rightarrow 1$ & 0.5 & 0.579 & 0.944 & $4.008 \cdot 10^{-5}$ \\
      \hline
-     $\bar{B}: 1 \rightarrow 0$ & 0.5 & 0.629 & 0.886 & $4.238 \cdot 10^{-5}$ \\
+     $\bar{B}: 1 \rightarrow 0$ & 0.5 & 0.642 & 0.888 & $4.945 \cdot 10^{-5}$ \\
      \hline
-     $\bar{B}: 1 \rightarrow 1$ & 0.5 & 0.637 & 0.914 & $1.714 \cdot 10^{-5}$ \\
+     $\bar{B}: 1 \rightarrow 1$ & 0.5 & 0.637 & 0.914 & $1.715 \cdot 10^{-5}$ \\
      \hline
-     $\bar{B}: 0 \rightarrow 0$ & 2 & 0.569 & 0.984 & $5.803 \cdot 10^{-5}$ \\
+     $\bar{B}: 0 \rightarrow 0$ & 2 & 0.561 & 0.965 & $4.618 \cdot 10^{-5}$ \\
      \hline
@@
      \hline
-     $\bar{B}: 1 \rightarrow 0$ & 2 & 0.604 & 0.923 & $5.496 \cdot 10^{-5}$ \\
+     $\bar{B}: 1 \rightarrow 0$ & 2 & 0.597 & 0.899 & $5.025 \cdot 10^{-5}$ \\
      \hline
-     $\bar{B}: 1 \rightarrow 1$ & 2 & 0.618 & 0.909 & $7.161 \cdot 10^{-5}$ \\ [1ex] 
+     $\bar{B}: 1 \rightarrow 1$ & 2 & 0.606 & 0.885 & $6.435 \cdot 10^{-5}$ \\ [1ex] 
      \hline
@@
 
-% \begin{table}[h!]
+We show in Table \ref{table:rheology_fit} that the application of magnetic fields makes the bijel rheological behavior more Newtonian for both particle 
+morphologies. We also see that bijel templates with an applied field of $\bar{B} = 1$ have larger flow indices than bijel templates made with no
+applied field. The same trend exists here where the application of a magnetic field makes the bijel more Newtonian. We also characterize that the yield stress 
+of bijels stabilized with oblate particles decrease as the initial order of the particles and the applied field onto the bijel increase. The yield stress of 
+bijels stabilized by prolate particles increases as the initial order of the particles and the applied field onto the bijel increase. In previous aims, we 
+characterized that application of magnetic fields created orientational ordering of the bijels and that the local ordering of the bijels change. We 
+showed that as magnetic fields were applied, oblate particles have lower local ordering on the interface while for prolate particles it increases.
+Past investigations have identified that particle monolayers buckle more easily as local particle ordering decreases. \cite{prakash_buckling_2024} 
+They identified that local ordering can enhance stress distribution among particles, making locally ordered particle monolayers better at withstanding shear.
+In the following sections, we will investigate the magnetic field process and the effect of local particle ordering on the microstructure of the bijel.
+
+\subsection{Microstructure change}
+
+Bonaccorso et al. identified that the spherical particle stabilizers in their bijel simulations oriented to the direction of shear before being
+ejected from the interface. \cite{bonaccorso_shear_2020} This then led to the domains of the bijel to coalesce and eventually destruction of the
+bicontinuous microstructure. \cite{bonaccorso_shear_2020} In our bijels, we have the additional parameter of an applied magnetic field and
+ellipsoidal particles. In this section, we probe the effect of applied shear to the microstructure and particle properties of magnetically
+responsive bijels stabilized by ellipsoidal particles. First we plot the domain size of each system over time to analyze the effect of application of 
+shear and magnetic fields.
+
+\begin{figure} 
+    \centering 
+    \includegraphics[scale=0.3]{../figures/results/paper3/domain_size-time_compare.png} 
+    \caption{Comparisons of the time evolution of the average domain size for bijels stabilized by ellipsoidal particles undergoing
+             various shear rates under four processes. Initially, the domain size coarsens for all runs under applied shear before
+             reducing in some cases.} 
+    \label{fig:domain_size_time_shear} 
+\end{figure}
+
+From Figure \ref{fig:domain_size_time_shear}, domains coarsen with time in all cases. When increasing the applied magnetic field in the case of 
+$\bar{B}:0 \rightarrow 1$, we see shear assisted domain coarsening characterized as a 20 \% and 10 \% increase in the domain size of bijels
+stabilized by oblate and prolate particles respectively. This is approximately 5 times greater than the response observed in Figure \ref{fig:domain_size-field_on}
+In the  $\bar{B}: 1 \to 0$ and $\bar{B}: 1 \to 1$ cases, an initial plateau in domain size is observed, followed by a divergence in 
+growth depending on $Ca$. The shear rate appears to influence domain coarsening, with higher $Ca_s$ leading to delayed or 
+suppressed growth, especially in the presence of a field. The difference between applying $\bar{B}: 0 \to 1$ and 
+removing $\bar{B}: 1 \to 0$ the field demonstrates the stability of the particle monolayer when a field is switched off.
+There is little difference in the qualitative trends of domain size change for bijels stabilized with oblate or prolate particles.
+To characterize whether the domain size coarsening observed arises from different phenomena in each case, the area averaged curvature is plotted.
+
+\begin{figure} 
+    \centering 
+    \includegraphics[scale=0.3]{../figures/results/paper3/gaussian-time_compare.png} 
+    \caption{Plots of the time evolution of the area averaged Gaussian curvature $\langle K \Sigma^{-2} \rangle$ for four 
+             processing histories applied to bijels stabilized with oblate and prolate ellipsoids. We demonstrate that the 
+             magnitude of the gaussian curvature reduces for all systems except for $\bar{B}: 0 \to 1$.} 
+    \label{fig:gaussian_curvature_time_shear} 
+\end{figure}
+
+Figure \ref{fig:gaussian_curvature_time_shear} reveals that the area averaged Gaussian curvature generally decreases in magnitude over time for all cases except 
+$\bar{B}: 0 \to 1$. We also characterize that the curvature evolution of all systems are shear independent. $\bar{B}: 0 \to 1$ is
+unique because particle rearrangements at the interface dominates the dynamics of the microstructure, not observed in all other
+cases. From the time evolution of the curvature, we show that the same mechanism drives domain coarsening in all cases. Domain
+coarsening is driven through a reduction in the interfacial area covered by the particle monolayer. Previous investigations have 
+demonstrated how the orientation and arrangement of particles on the interface affect the domain size. 
+\cite{gunther_timescales_2014} We focus our investigation on this aspect in the following section.
+
+\subsection{Particle properties}
+
+Particles at the interface of bijels stabilized with ellipsoidal particles reorient at the interface to minimize interfacial and
+steric energies. \cite{gunther_timescales_2014} The particles stabilizing bijels in confined systems under shear have been shown to
+orient to the direction of shear and ejected from the interface at sufficiently long times or shear.\cite{bonaccorso_shear_2020} 
+We probe these aspects of the particle monolayer in this section. We plot the orientation of the particle to each cartesian axis 
+to identify if we characterize shear induced ordering.
+
+\begin{figure} 
+    \centering 
+    \includegraphics[scale=0.3]{../figures/results/paper3/angle_to_cartesian-SS.png} 
+    \caption{Comparisons of the initial and final particle orientations of the particles to each cartesian direction under
+             four processing histories for bijels stabilized with oblate and prolate ellipsoids at multiple shear rates. We show
+             shear dependent ordering of the particle monolayer if the initial particle monolayer begins with particle order.} 
+    \label{fig:particle_orientation_cartesian_shear} 
+\end{figure}
+
+From Figure \ref{fig:particle_orientation_cartesian_shear} we see that with bijel templates simulated under $\bar{B} = 0$, the
+particles adopt a random orientation. Upon application of shear, we see that there is little directional ordering to the 
+shear direction in the simulation time observed. Upon application of the magnetic field, the particle order to the direction of the magnetic field. 
+When investigating the orientational ordering of a bijel simulated under a field strength of $\bar{B} = 1$, we see that there is
+shear dependent decay of the orientational ordering when the magnetic field is removed. We also characterize similar behavior
+when maintaining the applied field. The reorientation of particles in the $\bar{B}:1 \rightarrow 1$ indicates shear induced reorientation of the 
+particles at the interface. From the curvature results characterized in Figure \ref{fig:gaussian_curvature_time_shear}, we saw that the coarsening is
+shear independent. This indicates that the surface area of the interface decreases which can occur due to changes in the interfacial orientation of 
+particles at the interface or a reduction in the number of particles at the interface. We can characterize the former mechanism
+using the average interfacial angle between the particle and the interface $\langle \psi \rangle$.
+
+\begin{figure} 
+    \centering 
+    \includegraphics[scale=0.3]{../figures/results/paper3/psi-time_compare.png} 
+    \caption{Comparisons of the interfacial angle of bijels stabilized by ellipsoidal particles as a function of 
+             the applied shear rate at four different processing histories. We show that upon application of shear
+             particles tilt out of the interface reduces the interfacial area stabilized. $\bar{B}: 0 \to 1$ shows 
+             large variations in the interface angle.} 
+    \label{fig:interface_angle_shear} 
+\end{figure}
+
+From Figure \ref{fig:interface_angle_shear}, we demonstrate that there is a slow increase in the interface angle over time for all cases
+except for $\bar{B}: 0 \to 1$. Shear dependent $\langle \psi \rangle$ can be observed for some of the systems, indicating that the mechanism
+of domain coarsening differs. The data for $\bar{B}: 0 \to 1$ is characterized as such due to a particle reorientation at the interface
+in response to the field just after the magnetic field has been applied. To reduce the interfacial energy as the particles tilt from the 
+interface, the interface moves with the particle until it jams in place. We then characterize the proportion 
+of particles on the interface to investigate how the proportion of particles on the interface changes and its impact on the interfacial area.
+
+% We can characterize the impact of the interfacial angle on the 
+% particle packing using the radial distribution function (rdf).
+
+% \begin{figure} 
 %     \centering 
-%     \begin{tabular}{||c c c c c c c c c c c c c||} 
-%      \hline
-%      $t_{sim}$ & $L_x$ & $\rho_f$ & $\tau$ & $\eta_f$ & $g_{cc'}$ & $\sigma$ & $\phi_f$ & $\rho_p$ & $\phi_p$ & $V_p$ & $d_c$ & $K_H$ \\ [0.5ex] 
-%      \hline\hline
-%      $10^5$ & 256 & 0.7 & 1 & 0.117 & 0.08 & 0.0267 & 0.5 & 1 & 0.15 & 2000$\pi$ & 2/3 & 100\\ [1ex] 
-%      \hline
-%     \end{tabular}
-%     \caption{Summary of the fluid, particle and model parameters used in the proposed simulations}
-%     \label{table:model_params}
-%     \end{table}
+%     \includegraphics[scale=0.3]{../figures/results/paper3/rdf-SS.png} 
+%     \caption{Comparisons of the initial and final radial distribution function of the particles of bijels stabilized by ellipsoidal 
+%     particles as a function of the applied shear rate at four different processing histories. We show that there are minor differences
+%     in the particle ordering at the interface, suggesting that the particle tilting affects the coverage of particles at the interface.} 
+%     \label{fig:rdf_shear} 
+% \end{figure}
 
-We characterize that the yield stress of bijels stabilized with oblate particles decrease as particle order increases while decreasing then increasing for 
-prolate particles. This can be attributed to the morphology differences that lead to different interfacial packing, characterized with the rdf in Figure 
-\ref{fig:rdf_shear}. We see that bijels stabilized with oblate particles do not pack as efficiently on the interface when a magnetic field is applied,
-meaning that the interface can buckle more easily. In contrast prolate particles pack more densely which leads to the greater yield stress. The results
-suggest that increasing the magnetic field onto bijels stabilized with prolate particles also causes the particle monolayer to more easily buckle 
-upon application of shear.
+% From Figure \ref{fig:rdf_shear}, we show that the change in the packing of the particles on the interface is not correlated to the change 
+% in the interfacial angle of the particles on the interface when changing the applied field strength in all cases. We then characterize the proportion 
+% of particles on the interface to investigate how the proportion of particles on the interface changes and its impact on the interfacial area.
+
+\begin{figure} 
+    \centering 
+    \includegraphics[scale=0.3]{../figures/results/paper3/n_int-time_compare.png} 
+    \caption{Comparisons of the proportion of particles on the interface of bijels ($n_{int}$) stabilized by ellipsoidal particles as a function of 
+             the applied shear rate at four different processing histories. We show that upon application of shear, many cases have a 
+             reduction in the number of particles on the interface while in others it stays the same. For cases where $n_{int}$ reduces, we can 
+             attribute the domain size coarsening to this effect.} 
+    \label{fig:particles_interface_prop_shear} 
+\end{figure}
+
+We show in Figure \ref{fig:particles_interface_prop_shear} that when the magnetic field is kept the same between the template and during shear, the
+proportion of particles on the interface ($n_{int}$) stays approximately the same. However when changing the applied field strength, $n_{int}$ more 
+sensitive to shear. Here we also characterize that increasing the applied field strength reduces $n_{int}$ more than decreasing it. This is consistent
+with the amount of coarsening observed for each case seen in Figure \ref{fig:domain_size_time_shear} where $\bar{B}:0 \rightarrow 1$ shows the largest
+change.

### 2025-03-14 chapters/analysis_techniques.tex
Changes 1. Added more visualizations of data 2. Added some images of analysis techniques in use 3. Fixed referencing to some images in aims 1,2,3

@@
 and 0's are solid. \cite{cooper_taufactor_2016, kench_taufactor_2023}
+
+\subsection{Interface order}
+\label{section:interface_order}
+
+We can calculate the ordering of the interface from the iso-surface of the interface. The simulation data was first pre-processed by calculating the 
+order parameter of the densities, $\phi$. We then apply the particle filling algorithm described in section \ref{section:filling_routine} 
+to the $\phi$ distribution. We then mesh the filled order parameter at $\phi = 0$ using the marching cubes algorithm and obtain the normals of the
+vertices representing the points of the interface. We then computed the interfacial orientation tensor and plot that 
+%
+\begin{equation}
+\tens{Q}_{\text{int}} = \frac{1}{\langle \mathrm{tr}(\tens{A}) \rangle} 
+\left\langle \tens{A} - \frac{1}{3} \mathrm{tr}(\tens{A}) \mathsf{1} \right\rangle ,
+\end{equation}
+%
+where the local tensor field $\tens{A}$ is defined by
+%
+\begin{equation}
+\tens{A} = \nabla\phi\otimes\nabla\phi .
+\end{equation}
+%
+The largest eigenvalue of $\tens{Q}$ is taken as the
+interface nematic order parameter $S_{\text{int}}$.
+
+\subsection{Channel size distribution}
+\label{section:channel_size_distribution}
+
+We use a method based on that outlined in Chan and Thornton. We create our distance function by performing an Eularian Distance Transform on 
+our order parameter data $\phi$ to obtain $\phi_{edt}$. \cite{chan_channel_2012} We smooth $\phi_{edt}$ using a boxcar algorithm with side length 3. 
+We then normalize the distance from the interface in $\phi_{edt}$ using the characteristic length scale of the system defined as $\Sigma = \frac{V}{A_{int}}$
+to obtain $\bar{\phi}_{edt}$ and a normalized distance from the interface, $\bar{r}$. A schematic of this workflow is demonstrated in Figure \ref{fig:csd_prep_viz}.
+
+\begin{figure}
+    \centering
+    \includegraphics[scale = 0.4]{figures/analysis/csd_prep.png}
+    \caption{Schematics detailing the order of operations of the steps to calculate the channel size distribution.}
+    \label{fig:csd_prep_viz}
+\end{figure}
+
+The number of handles, $h$
+in the iso-surface at different distances from the interface of $\bar{\phi}_{edt}$ is calculated. $h$ is also normalized by $\Sigma$ and the system volume
+to obtain $\bar{h} = \frac{h}{V\Sigma^{-3}}$. The magnitude of the derivative of $\bar{h}$ with respect to $\bar{r}$, $f$, represents the channel size distribution.
+A mean channel size can also be calculated from the first moment of the $f$.
 

### 2025-03-14 chapters/paper1.tex
Changes 1. Added more visualizations of data 2. Added some images of analysis techniques in use 3. Fixed referencing to some images in aims 1,2,3

@@
 change in curvature arises from the differences in local state of the
-colloids at the interface.
+colloids at the interface. From the microstructure results in Figures \ref{fig:D2a_B}
+in addition to the genus differences characterized in Figure \ref{fig:curvature_vs_coverage},
+the connectivity of the microstructure is affected through the application of magnetic fields.
+We can use the channel size distribution to investigate how the connectivity of the microstructure and thus the 
+channel size is affected as a function of the applied magnetic field.
+
+While minor run to run variation is observed, the combined data of the channel size distribution shown in Figure \ref{fig:CSD_B_ss} shows some major differences 
+in the channel size distribution in each bijel stabilized with oblate particles. It was expected that the domain anisotropy obtained using second moment of the 
+structure factor would manifest as two peaks in the channel size distribution. \cite{karthikeyan_formation_2024} This behavior is observed in the channel size 
+distribution for bijels stabilized with oblate and prolate particles with $\bar{B} = 1$, but is more difficult to see when smaller magnetic fields are applied. 
+We see that there is a shift to larger channel sizes upon application of the magnetic field for bijels stabilized by ellipsoids. These differences arise from the 
+particle ordering and local distribution changes observed.
+
+\begin{figure} 
+        \centering 
+        \includegraphics[scale = 0.4]{figures/results/paper1/CSD_ss.png} 
+        \caption{Plots of the channel size distribution for bijels stabilized by oblate, spherical and oblate particles at the final timestep plotted
+                 against the distance from the interface normalized with the characteristic length scale. The channel sizes obtained are averaged over 
+                 three runs. We see that the peak locations are shifted to larger and smaller positions for bijels stabilized with ellipsoidal particles
+                 upon field application} 
+        \label{fig:CSD_B_ss}
+    \end{figure}
 
@@
 of the nematic order parameter. Accordingly, the decay of \(S\) is most
-pronounced at the weakest magnetic field \(\bar{B}=0.2\).
-
-To further corroborate this mechanism, we quantify the orientational
-order of the interfaces. We computed the interfacial orientation tensor
-%
-\begin{equation}
-\tens{Q}_{\text{int}} = \frac{1}{\langle \mathrm{tr}(\tens{A}) \rangle} 
-\left\langle \tens{A} - \frac{1}{3} \mathrm{tr}(\tens{A}) \mathsf{1} \right\rangle ,
-\end{equation}
-%
-where the local tensor field $\tens{A}$ is defined by
-%
-\begin{equation}
-\tens{A} = \nabla\phi\otimes\nabla\phi .
-\end{equation}
-%
-The largest eigenvalue of $\tens{Q}$ is taken as the
-interface nematic order parameter $S_{\text{int}}$.
+pronounced at the weakest magnetic field \(\bar{B}=0.2\). To further corroborate 
+this mechanism, we plot the time evolution of the orientational order of the interfaces.
 
@@
 Hence the prolate particles remain mostly aligned with the interface
-even in the stronger applied magnetic fields.
+even in the stronger applied magnetic fields. We plot the interface angle of bijels
+stabilized by ellipsoidal particles at the final timestep to demonstrate the differences
+that the application of magnetic fields have on the particle monolayer.
 
-Information on the average ordering of the particles towards a
-direction can be characterized using the nematic order parameter.
-\cite{veerman_phase_1992, gunther_timescales_2014} However, we would
-like to understand the local ordering of the particles over time. We
-utilize the 6 fold Steinhardt order parameter Q6.
-\cite{steinhardt_bond-orientational_1983, lechner_accurate_2008, mickel_shortcomings_2013} 
-This parameter has been used extensively to characterize nucleation
-rates, glass transitions of colloidal systems and crystal structure
-transitions of ceramics and colloidal crystals.
-\cite{vagberg_glassiness_2011, besseling_three-dimensional_2007, schall_structural_2007}
-The original implementation has been further improved through the use an
-averaged bond order parameter, adding the next nearest neighbor to the
-neighbor list or utilizing voronoi cells to define the neighbor list
-instead of a cutoff distance. The latter provides the more robust
-implementation of the bond order parameter and is implemented in the
-package Freud. \cite{ramasubramani_freud_2020} This method has been used
-to characterize the jamming of discs at interfaces.
-\cite{ozawa_jamming_2012} We select \(Q6\) as the parameter to calculate
-due to the hexagonal ordering seen in the visualizations of the particle
-monolayer. We plot the averaged bond order parameter for each timestep,
-\(\langle Q6 \rangle\) calculated using a neighbor list derived from
-voronoi cells below.
+\begin{figure}
+        \centering
+        \includegraphics[scale = 0.4]{figures/results/paper1/psi_concat.png}
+        \caption{Visualizations of the particle monolayer at the last timestep shaded with the interface angle of each particle in red. The top and bottom
+                 rows correspond to snapshots of bijels with no field and a field strength of $\bar{B} = 1$ applied. We see that the oblate particles flip
+                 out of the interface into a non energetically favored position while the bijels stabilized with prolate particles tilt out of the interface
+                 but are less likely to flip out.}
+        \label{fig:psi_viz_ss}
+\end{figure}
+
+From Figure \ref{fig:psi_viz_ss} we can see the differences in the particle alignment to the interface characerizing the differences in $\psi$ observed. Oblate
+particles can be seen to tilt out of the interface more readily than prolate particles at the same magnetic field strength. Due to the strong surface tension
+between the fluids, the particles are strongly adsorbed onto the interface. We also see that the arrangement of particles on the interface is modified through the
+application of the magnetic field for both particle morphologies. We can obtain quantitative metrics regarding this ordering using the Steinhardt 2 and 6 fold
+order parameters, $\langle Q2 \rangle$ and $\langle Q6 \rangle$.
+
+This parameter has been used extensively to characterize nucleation rates, glass transitions of colloidal systems and crystal structure transitions of ceramics 
+and colloidal crystals. \cite{vagberg_glassiness_2011, besseling_three-dimensional_2007, schall_structural_2007} The original implementation has been further 
+improved through the use an averaged bond order parameter, adding the next nearest neighbor to the neighbor list or utilizing voronoi cells to define the 
+neighbor list instead of a cutoff distance. The latter provides a more robust definition of the neighbor list, without needing to assume the structure of 
+the particles and is implemented in the package Freud. \cite{ramasubramani_freud_2020} This method has been used to characterize the jamming of discs at 
+interfaces. \cite{ozawa_jamming_2012}
+
+We select $\langle Q6 \rangle$ and $\langle Q2 \rangle$ as the bond order parameters to calculate as we are interested in identifying the point when ordering 
+of the material changes. Kapfer et al. demonstrated that only using $\langle Q6 \rangle$ to identify the ordering of particles in the system can result in 
+false positives when the particles have icosahedral or amorphous structure. \cite{kapfer_jammed_2012} Mickel et al. showed how increasing deviations from 
+$\langle Q2 \rangle = 0$ can be used to characterize increasing disorder in a system. \cite{mickel_shortcomings_2013} By plotting $\langle Q6 \rangle$ and 
+$\langle Q2 \rangle$, we will be able to identify changes in the local ordering of the system even if we cannot directly assess the local structure.
 
@@
     indicator of global particle translational order while $\langle Q6 \rangle$ is an indicator of local order.} 
-    \label{fig:Q6_coverage} 
+    \label{fig:steinhardt_coverage} 
 \end{figure}
 
-From Figure \ref{fig:Q6_coverage}, we observe that
-\(\langle Q6 \rangle \approx 0.34\) for all systems before increasing.
-For bijels stabilized with spherical particles, we observe that
-\(\langle Q6 \rangle\) monotonically increases until
-\(\langle Q6 \rangle \approx 0.485\), indicating that the spherical
-particles reach a hexagonally arranged state at the interface upon
-jamming. In contrast, oblate and prolate particles respectively at the
-\(t = 10^5\) timesteps have values \(\langle Q6 \rangle \approx 0.44\)
-and \(\langle Q6 \rangle \approx 0.35\) respectively, indicating that
-the arrangement of colloids on the interface are not hexagonal close
-packed. We can verify these observations in the visualizations in
-Figures \ref{fig:microstructure_viz}
+From Figure \ref{fig:steinhardt_coverage}, we see an increase in disorder in all the bijel systems characterized as an increase in $\langle Q2 \rangle$. 
+This is a characteristic of how the particles were initialized and move once the simulation is initiated. The particles are initialized to be randomly placed 
+in the simulation domain with roughly equal spacing. As the interface sweeps through the simulation domain, particles irreversibly adsorb onto the interface 
+and move with the interface until the bijel jams. We see that $\langle Q2 \rangle$ is magnetic field dependent for oblate particles but not for the spherical 
+and prolate particles. We also see an aspect ratio dependence on the values characterized as differences in the time evolution of $\langle Q2 \rangle$. This 
+arises due to the differences in the aspect ratio of the particle causing them to arrange differently on the interface as the bijel microstructure evolves.
 
-We observe a magnetic field dependent increase in \(\langle Q6 \rangle\)
-for prolate particles to \(\langle Q6 \rangle \approx 0.4\) and decrease
-for oblate particles to \(\langle Q6 \rangle \approx 0.42\). As the
-magnetic field strength is increased, we observed the interface
-possessed a more negative gaussian curvature. Previous work by Cavallaro
-et al.~demonstrated that surfaces with large gaussian curvature
-gradients can be utilized to control particle self assembly at
-interfaces owing to the excess interfacial energy induced by the
-curvature gradient. \cite{cavallaro_curvature-driven_2011} Spherical
-particles have monopolar effects which for the colloid sizes we are
-modelling are negligible. Previous literature has also ascertained
-aspect ratio dependent self-assembly of ellipsoids. We attribute the
-changes in the local ordering to be due to aspect ratio dependent self
-assembly, amplified by the greater curvature gradient present upon
-application of a magnetic field. Next, we analyze how these local
-toplogical changes affect the microstructure of the bijel by analyzing
-the width of the domains in the bijel.
+An increase in $\langle Q6 \rangle$ can indicate an increase in the number of particles adopting icosahedral symmetry at the interface of the amorphous 
+interface. \cite{kapfer_jammed_2012} However due to the amorphous nature of the arrangement of particles at the particle monolayer, we use this parameter 
+only to gauge changes in local arrangements of particles at the interface and make no commentary on specific interfacial arrangements. For oblate particles, 
+we characterize a reduction in local order as the applied field strength is increased, consistent with the increase in $\langle Q2 \rangle$. For prolate 
+particles, we observe that $\langle Q6 \rangle$ increases with the applied field. This indicates that the application of the field causes particles to have 
+increased local order, even if we see no discernible changes in $\langle Q2 \rangle$.
+
+The application of the magnetic field affects the prolate and oblate particle differently due to their aspect ratio. At interfaces, rod-like particles 
+prefer to orient themselves in an end to end fashion. \cite{eatson_capillary_2023} Disc-like particles have been shown to prefer stacking. \cite{dabat_mesoscale_2018} 
+Application of the magnetic field and the presence of an interface will constrain the rotation of the particles, meaning that naturally rods will pack better at 
+interfaces than discs as the magnetic field causes the particles to align to the field. This better packing at the interface manifests as greater local ordering 
+Next, we analyze how these local toplogical changes affect the microstructure of the bijel by analyzing the channel size distribution of the bijels.
 

### 2025-03-14 chapters/paper2.tex
Changes 1. Added more visualizations of data 2. Added some images of analysis techniques in use 3. Fixed referencing to some images in aims 1,2,3

@@
 When analyzing $\langle \psi \rangle$ for bijels stabilized by prolate particles, this behavior can also be observed. $\langle \psi \rangle$
-begins at $10 ^{\circ}$.We see $\langle \psi \rangle$ decrease slightly, before plateauing and slowly increasing again. The rate of decrease in 
+begins at $10 ^{\circ}$.We see $\langle \psi \rangle$ increases, before plateauing and slowly decreasing. The initial peak height and rate of increase in 
 $\langle \psi \rangle$ is field dependent, although given the small decrease in $\langle \psi \rangle$ it is unclear if the final value of this parameter 
 is field dependent for bijels stabilized with prolate particles. The changes in $\langle \psi \rangle$ for bijels stabilized with prolate particles are 
-small compared to bijels stabilized with oblate particles. We believe this is due to local particle effects at the interface. We probe this by identifying 
+small compared to bijels stabilized with oblate particles. We visualize this process by color coding snapshots of the particle monolayer at the initial
+and final timesteps of bijels stabilized by prolate particles with a field strength of $\bar{B} = 1$ applied.
+
+\begin{figure} 
+    \centering 
+    \includegraphics[scale=0.4]{../figures/results/paper2/psi_concat_startB-0_endB-1.png} 
+    \caption{Visualizations of bijel stabilized by ellipsoidal particles made with no applied field having a field strength of $\bar{B} = 1$ applied. The top and bottom 
+             rows show $\psi$ for each particle at the initial and final timesteps respectively.The intensity
+             of the red color qualitatively indicates the magnitude of the $\psi$ for each particle. Field application causes particles to flip out of the interface for
+             oblate particles, while prolate particles tilt out of the interface. The interface is shaded with the Gaussian curvature.} 
+    \label{fig:psi_field_on_visualize} 
+\end{figure}
+
+From the visualizations in Figure \ref{fig:psi_field_on_visualize}, we see that the particles lie mostly flat on the interface at the initial timestep for bijels
+stabilized with oblate and prolate particles. Upon application of a field strength of $\bar{B} = 1$, we observe that the particles in the snapshot at the final timestep 
+are in different conformations for bijels stabilized with oblate and prolate particles. Oblate particles tend to flip on the interface into a metastable state where
+the interface covered by each particle is done with the $R_p$ and $R_o$ compared to its lowest energy state where it lies flat with radii $R_o$. The particle monolayer
+of bijels stabilized by prolate particles tilt out of the interface with no metastable configurations observed. This effect explains the trends seen in $\langle \psi \rangle$
+at long times for both particle morphologies. This particle flipping on the interface affects the way the particles can arrange on the interface. We probe this by identifying 
 the local particle ordering at the interface characterized by $\langle Q6 \rangle$.

### 2025-03-14 chapters/paper3.tex
Changes 1. Added more visualizations of data 2. Added some images of analysis techniques in use 3. Fixed referencing to some images in aims 1,2,3

@@
 They identified that local ordering can enhance stress distribution among particles, making locally ordered particle monolayers better at withstanding shear.
-In the following sections, we will investigate the magnetic field process and the effect of local particle ordering on the microstructure of the bijel.
+We visualize the ordering of the particles at the interface to the z direction for both particle morphologies at $Ca_s = 10^{-6}$ for the 
+case $\bar{B}: 1 \rightarrow 0$.
+
+\begin{figure} 
+    \centering 
+    \includegraphics[scale=0.4]{../figures/results/paper3/tz_concat_startB-1_endB-0.png} 
+    \caption{Visualization of the particle monolayer of bijels stabilized by prolate and oblate ellipsoidal particles with processing history $\bar{B}: 1 \rightarrow 0$
+             undergoing an applied shear of $Ca_s = 10^{-6}$. Particles with a deeper purple shade have a larger angle to the z axis. The top row shows the initial 
+             configuration of the particles while the bottom row shows the final configuration of the particles. } 
+    \label{fig:particle_viz_tz} 
+\end{figure}
+
+In Figure \ref{fig:particle_viz_tz}, we see that the particle are initially ordered to the direction of the applied magnetic field. Upon application of shear and removal
+of the magnetic field, we see that the particles begin reorienting away from the z direction. We also observe that the reorientation of particles uncovers the interface.
+The reorientation observed is particle morphology specific with prolate particles seeing more reorientation away from the applied shear direction than oblate particles.
+Looking at the images, we see that prolate particles rotate away from the direction of the magnetic field and applied shear towards the direction of the shear gradient,
+while oblate particles reorient towards minimizing area to the applied shear direction.In the following sections, we will investigate the microstructural implications of
+the uncovering of the bijel interface, in addition to understanding more about the particle reorientation at the interface and its effects.
 

### 2025-03-19 chapters/paper3.tex
Changes 1. Refactored chapter for aim 3 2. Added labels for chapters in main doc (dissertation.tex)

--- 2025-03-13 chapters/paper3.tex
@@
 While the microstructure and synthesis techniques for bijels have been explored in earnest, the rheology of bijels
-has only recently seen an uptick in interest. Some interesting phenomena for bijels and shearing include the 
+has remained relatively unexplored. Some interesting phenomena for bijels and shearing include the 
 presence of monogels, made by remixing the phase separated liquid domains of the bijel while the electrostatic
 interactions between particles maintains the structure of the particle monolayer. \cite{sanz_colloidal_2009} 
-This behavior is system specific, suggesting the fluid system plays a role in this behavior as well. \cite{tavacoli_novel_2011}
-\cite{bai_dynamics_2015} Investigations have identified that confined bijels under shear undergo elongation of
+Monogel formation has been observed in lutidine/water and styrene/butadiene oligomer based bijels but not ethane-diol nitromethane based bijels
+\cite{sanz_colloidal_2009, bai_dynamics_2015, tavacoli_novel_2011} Computational Investigations have identified that confined bijels under shear undergo elongation of
 the domains in the direction of shear succeeded by particle detachment from the interface and eventual failure of the bijel. \cite{bonaccorso_shear_2020}
@@
 
-In many of the manufacturing techniques outlined for continuous bijel production such as STrIPS, the rheological properties are essential in ensuring that 
-the casting mixture remains processable. \cite{haase_continuous_2015,haase_situ_2016} While particle stabilized emulsions have been shown to be shear thinning, 
-our investigation into magnetically stimuli responsive bijels will modify the behavior of these systems due to the application of magnetic fields. Past work with 
-ferrofluids and magnetic emulsions have showed how the rheological properties vary drastically as a function of the field strength due to the orientation of the 
-particles. \cite{qiao_magnetorheological_2012} The orientation of the particle to shear as well as the nematic order of particles 
-can cause shear banding and a smaller effective viscosity owing to a smaller cross sectional area being presented to the direction of shear.
+In many of the manufacturing techniques outlined the rheological properties are essential in ensuring that 
+the casting mixture remains processable. \cite{haase_continuous_2015,haase_situ_2016} In STrIPS, the flow rate of the casting mixture and the co-solvent
+control the microstructure of the bijel and the morphology of the resulting bijel material, controlling whether droplets or ropes are synthesized. \cite{haase_continuous_2015}
+When investigating the effect of magnetic fields on the rheological properties of suspensions, it has been shown that the viscosity of ferrofluids increases substantially due
+to the self assembly of particles restricting the flow of fluid, greatly increasing the viscosity of the ferrofluid. cite{qiao_magnetorheological_2012} The application
+of shear onto suspensions can also cause shear banding as interparticle interactions mediate particle fluid interactions, creating localized velocity differences to the bulk.
+\cite{xu_relation_2013} Looking into emulsions, the application of magnetic fields increases the viscosity of emulsions, making them more shear thinning than when no field 
+is applied.
 
-In this chapter, we probe the dynamics of bijels under constant and complex shear to understand how the application of magnetic fields onto bijels stabilized with
-anisotropic particles. We define a shear capillary number $Ca_s = \frac{\eta_{f} \dot{\gamma} L_{1}}{\sigma}$ where $\dot{\gamma} = \frac{2u_{LE}}{L_x}$ is the
-strain rate and $L_1$ is the average domain size. \cite{frijters_effects_2012, yang_capillary_2022} In the literature, $Ca_s$ has been between between 0.04 
+In past chapters, I identified the microstructure and particle arrangement of bijels stabilized by ellipsoidal particles under magnetic fields and demonstrated
+particles morphology specific ordering to the applied magnetic field. I also show that the local ordering of the particles is affected from the application of
+the magnetic field. In this chapter, I probe the dynamics of bijels under constant shear to understand how these microstructural and particle monolayer changes
+affect the rheology of bijels stabilized by ellipsoidal particles under magnetic fields. First, I define a shear capillary number 
+$Ca_s = \frac{\eta_{f} \dot{\gamma} R_s}{\sigma}$ where $\dot{\gamma} = \frac{2u_{LE}}{L_x}$ is the
+strain rate and $R_s$ is the size of equivalent spherical particle. \cite{frijters_effects_2012, yang_capillary_2022} In the literature, $Ca_s$ has been between between 0.04 
 and 0.16. However, the box size in these simulations were smaller, meaning that these capillary number ranges would exceed the 
 maximum mach number the model allows if this same range were used $(Ma \leq 0.03)$. To accommodate this limitation the 
-largest capillary number used will be $Ca_s = 10^-5$ which correspond to a maximum of $Ma \approx 0.002$. $Ca_s = 10^-6,  
-10^-7$ will also be used to demonstrate how the bijels respond to shear of varying strengths. As all particles used 
+largest capillary number used will be $Ca_s = 10^-4$ which correspond to a maximum of $Ma \approx 0.02$. As all particles used 
 have only hard-sphere type interactions, it is expected that the behaviour seen should mimic 2D colloidal glasses 
-percolating in 3D space, akin to what Ching and Mohraz saw, with an additional dependence on -the direction of shear. 
+percolating in 3D space, akin to what Ching and Mohraz saw, with an additional dependence on the direction of shear. 
 This would predict the discovery of particle monolayer dependent elasticity and yield stress along with shear thinning 
-behaviour as a function of strain rate.
+behavior of the bijels.
 
@@
 It is also expected that the effective viscosity will be different between the four microstructures dependent upon the 
-degree of nematic ordering and microstructural anisotropy of the bijel. Nematic ordering of the particles will 
+degree of nematic ordering and microstructural anisotropy of the bijel. Nematic ordering of the particles in the direction of shear
 should resulting in a lowered effective viscosity compared to bijels without nematically 
@@
 interface will also yield insight into how the packing of the particles affects the rate at which particles will get 
-ejected from the interface. Systems with a larger $\eta_{eff}$ are predicted to have the largest domains, largest 
+ejected from the interface. Bonnacorso et al. identified that shear applied onto bijels caused particles to align to the direction of
+shear before being ejected from the interface. Systems with a larger $\eta_{eff}$ are predicted to have the largest domains, largest 
 difference between initial and final particle order and lowest number of particles left on the interface once steady 
@@
 
-We begin our investigation by analyzing the rheological response of bijels stabilized by ellipsoidal particles under constant shear.
-Specifically, we investigate the effect that particle order has on the rheological response characterized. We are also interested in
+I begin this investigation by analyzing the rheological response of bijels stabilized by ellipsoidal particles under constant shear.
+Specifically, I investigate the effect that particle order has on the rheological response characterized. I am also interested in
 identifying the impact that the application of magnetic fields have on the rheological response of the bijel. 
 Bijel templates simulated in Aim 1 with no field and a field strength of $\bar{B} = 1$ stabilized with a prolate and oblate particles with a 
-particle volume fraction $\phi_p = 0.15$ were used as the starting point for these simulations. Next, We apply a field strength of
+particle volume fraction $\phi_p = 0.15$ were used as the starting point for these simulations. Next, I apply a field strength of
 $\bar{B} = 1$ or switch off the applied field to all structures. This results in four processing setups; $\bar{B}:0\rightarrow 0$, $\bar{B}:0\rightarrow 1$,
-$\bar{B}:1\rightarrow 0$ and $\bar{B}:1\rightarrow 1$. We then define a shear capillary number,  $Ca_s = \frac{\dot{\gamma} R_{s} \eta_{f}}{\sigma}$ where 
+$\bar{B}:1\rightarrow 0$ and $\bar{B}:1\rightarrow 1$. I then define a shear capillary number,  $Ca_s = \frac{\dot{\gamma} R_{s} \eta_{f}}{\sigma}$ where 
 $\dot{\gamma}$ is the applied strain rate, $R_s$ is the equivalent spherical radius of the particles, $R_s = 7.9$, $\eta_f$ is the dynamic viscosity of the 
-fluid and $\sigma$ is the surface tension of the interface. We use five shear numbers, $Ca_s = 1\cdot10^{-4}, 5\cdot10^{-5}, 1\cdot10^{-5}, 5\cdot10^{-6}, 1\cdot10^{-6}$.
+fluid and $\sigma$ is the surface tension of the interface. I use five shear numbers, $Ca_s = 1\cdot10^{-4}, 5\cdot10^{-5}, 1\cdot10^{-5}, 5\cdot10^{-6}, 1\cdot10^{-6}$.
 
@@
 the rheology of bijels have determined shear thinning behavior characterized with a Herschel-Buckley fit equation. \cite{macmillan_rheological_2019} 
-We perform this analysis on the structures we have simulated. First, we plot the shear stress over time.
+I perform this analysis on the structures I have simulated. First, I plot the shear stress over time.
 
@@
 shearing of a bijel synthesized using direct mixing resulted in degraded mechanical performance. \cite{macmillan_rheological_2019}
-To characterize the viscosity, we identify pseudo-steady state regions within each of the shear stress plots and fit the stress identified within this 
+To characterize the viscosity, I identify pseudo-steady state regions within each of the shear stress plots and fit the stress identified within this 
 pseudo-steady state region to the strain rate. Pseudo-steady state regions are identified by measuring where the rate of change of shear stress is 
-smallest for the longest duration. We fit the calculated stress to the applied strain rate using a Herschel-Buckley rheology model defined as
+smallest for the longest duration. I fit the calculated stress to the applied strain rate using a Herschel-Buckley rheology model defined as
 $\sigma_{xz} = \sigma_{y} + K(\dot{\gamma})^{n}$. $\sigma_{xz}$ is the shear stress calculated from the simulation, $\sigma_{y}$ is the yield stress of the bijel, 
-$K$ is the flow consistency index and $n$ is the flow index.Where appropriate, we include results corresponding to a shear capillary number of 
-$Ca_s = 10^{-6}$ as in many stress responses, we show that $Ca_s = 10^{-6}$ may not always yield usable results.
+$K$ is the flow consistency index and $n$ is the flow index.Where appropriate, I include results corresponding to a shear capillary number of 
+$Ca_s = 10^{-6}$ as in many stress responses, $Ca_s = 10^{-6}$ may not always yield usable results.
 
@@
     \includegraphics[scale=0.4]{../figures/results/paper3/stress_strain-all.png} 
-    \caption{Fitting the experimental shear stress to the strain rate using the Herschel Buckley model. We characterize the bijels are 
-             shear thinning in all cases. We show that the bijels become less shear thinning as the particle order increases. We also
+    \caption{Fitting the experimental shear stress to the strain rate using the Herschel Buckley model. I characterize the bijels are 
+             shear thinning in all cases. I show that the bijels become less shear thinning as the particle order increases. I also
              demonstrate that the particle ordering affects the yield stress differently for particles stabilized by oblate and 
@@
 
-From Figure \ref{fig:stress_strain}, we show that bijels stabilized with ellipsoidal particles are shear thinning regardless of the initial 
-microstructure and the processing applied. We quantify the fit and tabulate the results in Table \ref{table:rheology_fit}. From Table 
-\ref{table:rheology_fit}, we can see that as particle order increases, signified by an increase in the initial magnetic field, the flow index 
-of the material increases, indicating more Newtonian fluid like behavior. This is due to the more ordered particles being able to slip
-while undergoing fluid particle interactions without affecting other particles due to orientational ordering imposed from the application 
-of magnetic fields. From the Hershel Buckley fit, we also identified the flow index, consistency index and the yield stress of the bijels,
-tabulated in Table \ref{table:rheology_fit}.
+From Figure \ref{fig:stress_strain}, the slopes of the curve indicate a non-linear shear response to the applied strain rate, suggesting that the rheological properties
+are non-Newtonian. Bijels stabilized by prolate and oblate particles also have different shear properties. For bijels stabilized by oblate particles, the stress curves
+are more spread out suggesting that there is a larger variance in the properties arising from the change in the initial microstructure of the bijel. From the plot
+we can see that the increase in particle order reduces the yield stress of the bijel. For bijels stabilized by rod like particles, the stress response of each processing 
+condition is closer together, indicating a smaller variation in the response to the applied magnetic field compared to oblate particles. The shear response upon application
+of the magnetic field also suggest that increased ordering of prolate particles makes the bijel more resistant to shear. I quantify the Herschel-Buckley fit parameters and 
+tabulate the results in Table \ref{table:rheology_fit}.
 
@@
 
-We show in Table \ref{table:rheology_fit} that the application of magnetic fields makes the bijel rheological behavior more Newtonian for both particle 
-morphologies. We also see that bijel templates with an applied field of $\bar{B} = 1$ have larger flow indices than bijel templates made with no
-applied field. The same trend exists here where the application of a magnetic field makes the bijel more Newtonian. We also characterize that the yield stress 
-of bijels stabilized with oblate particles decrease as the initial order of the particles and the applied field onto the bijel increase. The yield stress of 
-bijels stabilized by prolate particles increases as the initial order of the particles and the applied field onto the bijel increase. In previous aims, we 
-characterized that application of magnetic fields created orientational ordering of the bijels and that the local ordering of the bijels change. We 
+The results in Table \ref{table:rheology_fit} show that bijels remain shear thinning regardless of the processing history and particle morphology.
+The particle morphology dependent differences in the shear response characterized in Figure \ref{fig:stress_strain} are quantified in Table \ref{table:rheology_fit}
+where the yield stress differences predicted is clear to see. I also show that bijel templates with an applied field of $\bar{B} = 1$ have larger flow indices \
+than bijel templates made with no applied field. The same trend exists here where the application of a magnetic field makes the bijel more Newtonian. I also 
+characterize that the yield stress of bijels stabilized with oblate particles decrease as the initial order of the particles and the applied field onto the bijel increase. 
+The yield stress of bijels stabilized by prolate particles increases as the initial order of the particles and the applied field onto the bijel increase. In previous aims, I 
+characterized that application of magnetic fields created orientational ordering of the bijels and that the local ordering of the bijels change. I 
 showed that as magnetic fields were applied, oblate particles have lower local ordering on the interface while for prolate particles it increases.
@@
 They identified that local ordering can enhance stress distribution among particles, making locally ordered particle monolayers better at withstanding shear.
-In the following sections, we will investigate the magnetic field process and the effect of local particle ordering on the microstructure of the bijel.
-
-\subsection{Microstructure change}
-
-Bonaccorso et al. identified that the spherical particle stabilizers in their bijel simulations oriented to the direction of shear before being
-ejected from the interface. \cite{bonaccorso_shear_2020} This then led to the domains of the bijel to coalesce and eventually destruction of the
-bicontinuous microstructure. \cite{bonaccorso_shear_2020} In our bijels, we have the additional parameter of an applied magnetic field and
-ellipsoidal particles. In this section, we probe the effect of applied shear to the microstructure and particle properties of magnetically
-responsive bijels stabilized by ellipsoidal particles. First we plot the domain size of each system over time to analyze the effect of application of 
-shear and magnetic fields.
+I visualize the ordering of the particles at the interface to the z direction for both particle morphologies at $Ca_s = 10^{-6}$ for the 
+case $\bar{B}: 1 \rightarrow 0$.
 
@@
     \centering 
-    \includegraphics[scale=0.3]{../figures/results/paper3/domain_size-time_compare.png} 
-    \caption{Comparisons of the time evolution of the average domain size for bijels stabilized by ellipsoidal particles undergoing
-             various shear rates under four processes. Initially, the domain size coarsens for all runs under applied shear before
-             reducing in some cases.} 
-    \label{fig:domain_size_time_shear} 
+    \includegraphics[scale=0.4]{../figures/results/paper3/tz_concat_startB-1_endB-0.png} 
+    \caption{Visualization of the particle monolayer of bijels stabilized by prolate and oblate ellipsoidal particles with processing history $\bar{B}: 1 \rightarrow 0$
+             undergoing an applied shear of $Ca_s = 10^{-6}$. Particles with a deeper purple shade have a larger angle to the z axis. The top row shows the initial 
+             configuration of the particles while the bottom row shows the final configuration of the particles. } 
+    \label{fig:particle_viz_tz} 
 \end{figure}
 
-From Figure \ref{fig:domain_size_time_shear}, domains coarsen with time in all cases. When increasing the applied magnetic field in the case of 
-$\bar{B}:0 \rightarrow 1$, we see shear assisted domain coarsening characterized as a 20 \% and 10 \% increase in the domain size of bijels
-stabilized by oblate and prolate particles respectively. This is approximately 5 times greater than the response observed in Figure \ref{fig:domain_size-field_on}
-In the  $\bar{B}: 1 \to 0$ and $\bar{B}: 1 \to 1$ cases, an initial plateau in domain size is observed, followed by a divergence in 
-growth depending on $Ca$. The shear rate appears to influence domain coarsening, with higher $Ca_s$ leading to delayed or 
-suppressed growth, especially in the presence of a field. The difference between applying $\bar{B}: 0 \to 1$ and 
-removing $\bar{B}: 1 \to 0$ the field demonstrates the stability of the particle monolayer when a field is switched off.
-There is little difference in the qualitative trends of domain size change for bijels stabilized with oblate or prolate particles.
-To characterize whether the domain size coarsening observed arises from different phenomena in each case, the area averaged curvature is plotted.
-
-\begin{figure} 
-    \centering 
-    \includegraphics[scale=0.3]{../figures/results/paper3/gaussian-time_compare.png} 
-    \caption{Plots of the time evolution of the area averaged Gaussian curvature $\langle K \Sigma^{-2} \rangle$ for four 
-             processing histories applied to bijels stabilized with oblate and prolate ellipsoids. We demonstrate that the 
-             magnitude of the gaussian curvature reduces for all systems except for $\bar{B}: 0 \to 1$.} 
-    \label{fig:gaussian_curvature_time_shear} 
-\end{figure}
-
-Figure \ref{fig:gaussian_curvature_time_shear} reveals that the area averaged Gaussian curvature generally decreases in magnitude over time for all cases except 
-$\bar{B}: 0 \to 1$. We also characterize that the curvature evolution of all systems are shear independent. $\bar{B}: 0 \to 1$ is
-unique because particle rearrangements at the interface dominates the dynamics of the microstructure, not observed in all other
-cases. From the time evolution of the curvature, we show that the same mechanism drives domain coarsening in all cases. Domain
-coarsening is driven through a reduction in the interfacial area covered by the particle monolayer. Previous investigations have 
-demonstrated how the orientation and arrangement of particles on the interface affect the domain size. 
-\cite{gunther_timescales_2014} We focus our investigation on this aspect in the following section.
+In Figure \ref{fig:particle_viz_tz}, the particles are initially ordered to the direction of the applied magnetic field. Upon application of shear and removal
+of the magnetic field, I see that the particles begin reorienting away from the z direction. I also observe that the reorientation of particles uncovers the interface.
+The reorientation observed is particle morphology specific with prolate particles seeing more reorientation away from the applied shear direction than oblate particles.
+Looking at the images, I see that prolate particles rotate away from the direction of the magnetic field and applied shear towards the direction of the shear gradient,
+while oblate particles reorient towards minimizing area to the applied shear direction. While these snapshots show the initial and final orientations of the particles at the
+interface, we can characterize the time evolution of the particle monolayer changes to identify its role in the rheological properties characterized.
 
@@
 orient to the direction of shear and ejected from the interface at sufficiently long times or shear.\cite{bonaccorso_shear_2020} 
-We probe these aspects of the particle monolayer in this section. We plot the orientation of the particle to each cartesian axis 
-to identify if we characterize shear induced ordering.
+I probe these aspects of the particle monolayer in this section. I plot the orientation of the particle to each cartesian axis 
+to identify if I characterize shear induced ordering.
 
@@
     \caption{Comparisons of the initial and final particle orientations of the particles to each cartesian direction under
-             four processing histories for bijels stabilized with oblate and prolate ellipsoids at multiple shear rates. We show
+             four processing histories for bijels stabilized with oblate and prolate ellipsoids at multiple shear rates. I show
              shear dependent ordering of the particle monolayer if the initial particle monolayer begins with particle order.} 
@@
 
-From Figure \ref{fig:particle_orientation_cartesian_shear} we see that with bijel templates simulated under $\bar{B} = 0$, the
-particles adopt a random orientation. Upon application of shear, we see that there is little directional ordering to the 
-shear direction in the simulation time observed. Upon application of the magnetic field, the particle order to the direction of the magnetic field. 
-When investigating the orientational ordering of a bijel simulated under a field strength of $\bar{B} = 1$, we see that there is
-shear dependent decay of the orientational ordering when the magnetic field is removed. We also characterize similar behavior
-when maintaining the applied field. The reorientation of particles in the $\bar{B}:1 \rightarrow 1$ indicates shear induced reorientation of the 
-particles at the interface. From the curvature results characterized in Figure \ref{fig:gaussian_curvature_time_shear}, we saw that the coarsening is
-shear independent. This indicates that the surface area of the interface decreases which can occur due to changes in the interfacial orientation of 
-particles at the interface or a reduction in the number of particles at the interface. We can characterize the former mechanism
-using the average interfacial angle between the particle and the interface $\langle \psi \rangle$.
+From Figure \ref{fig:particle_orientation_cartesian_shear} I see that with bijel templates simulated under $\bar{B} = 0$, the
+particles adopt a random orientation. Upon application of shear, I see that there is little directional ordering to the 
+shear direction in the simulation time observed. Upon application of the magnetic field in the $\bar{B}:0 \rightarrow 1$ case, 
+the particles order to the direction of the magnetic field. Here we see that the prolate particles order more readily to the applied
+field than the oblate particles, seen as a larger clustering of particles at the $\theta_z = 0$ corner of the triangle. In the 
+$\bar{B}:1 \rightarrow 0$ case particle morphology dependent partial relaxation of the particles away from the magnetic field direction 
+is observed. Directionality of the particles to the field is still observed, suggesting that the ordering of the particles is not
+immediately removed once the field is switched off. In the processing history of $\bar{B}:1 \rightarrow 1$, particles are locked
+into ordering to the magnetic field direction. However we also see that some particles are reoriented away from the field direction
+due to the applied shear. Prolate particles have a smaller distribution of particle orientations than oblate particles, suggesting that
+the initial orientation and ordering of particles to the shear applied underpin the response observed. As the particles are adsorbed on the 
+interface, the orientation of the particles are influenced by a balance between magnetic forces from the field and capillary forces 
+from the interface. We can qualitatively calculate the time evolution of the capillary interactions using the interfacial angle.
 
@@
     \caption{Comparisons of the interfacial angle of bijels stabilized by ellipsoidal particles as a function of 
-             the applied shear rate at four different processing histories. We show that upon application of shear
+             the applied shear rate at four different processing histories. I show that upon application of shear
              particles tilt out of the interface reduces the interfacial area stabilized. $\bar{B}: 0 \to 1$ shows 
@@
 
-From Figure \ref{fig:interface_angle_shear}, we demonstrate that there is a slow increase in the interface angle over time for all cases
-except for $\bar{B}: 0 \to 1$. Shear dependent $\langle \psi \rangle$ can be observed for some of the systems, indicating that the mechanism
-of domain coarsening differs. The data for $\bar{B}: 0 \to 1$ is characterized as such due to a particle reorientation at the interface
-in response to the field just after the magnetic field has been applied. To reduce the interfacial energy as the particles tilt from the 
-interface, the interface moves with the particle until it jams in place. We then characterize the proportion 
-of particles on the interface to investigate how the proportion of particles on the interface changes and its impact on the interfacial area.
+From Figure \ref{fig:interface_angle_shear}, I demonstrate that there is a slow increase in the interface angle over time for all cases
+except for $\bar{B}: 0 \to 1$. For the $\bar{B}: 0 \to 1$ case, this has been shown in Chapter \ref{chapter:aim2} to be due to particle
+reorientation to the applied magnetic field. For all other cases, we see an average increase in $\langle \psi \rangle$ over time, showing
+that the particles under shear reorient out of the interface. Particles reorienting out of the interface can be due to shear induced interfacial 
+stress, modifying the curvature of the interface and thus the lowest energy particle orientation to the interface or shear induced increases in
+interparticle forces, causing the particle to tilt out of the interface to minimize interparticle forces. We can characterize the latter 
+mechanism through measurements of the number of particles on the interface as increases in interparticle forces result in ejection of
+particles from the interface.
 
@@
 %     \caption{Comparisons of the initial and final radial distribution function of the particles of bijels stabilized by ellipsoidal 
-%     particles as a function of the applied shear rate at four different processing histories. We show that there are minor differences
+%     particles as a function of the applied shear rate at four different processing histories. I show that there are minor differences
 %     in the particle ordering at the interface, suggesting that the particle tilting affects the coverage of particles at the interface.} 
@@
 
-% From Figure \ref{fig:rdf_shear}, we show that the change in the packing of the particles on the interface is not correlated to the change 
-% in the interfacial angle of the particles on the interface when changing the applied field strength in all cases. We then characterize the proportion 
+% From Figure \ref{fig:rdf_shear}, I show that the change in the packing of the particles on the interface is not correlated to the change 
+% in the interfacial angle of the particles on the interface when changing the applied field strength in all cases. I then characterize the proportion 
 % of particles on the interface to investigate how the proportion of particles on the interface changes and its impact on the interfacial area.
@@
     \caption{Comparisons of the proportion of particles on the interface of bijels ($n_{int}$) stabilized by ellipsoidal particles as a function of 
-             the applied shear rate at four different processing histories. We show that upon application of shear, many cases have a 
-             reduction in the number of particles on the interface while in others it stays the same. For cases where $n_{int}$ reduces, we can 
+             the applied shear rate at four different processing histories. I show that upon application of shear, many cases have a 
+             reduction in the number of particles on the interface while in others it stays the same. For cases where $n_{int}$ reduces, I can 
              attribute the domain size coarsening to this effect.} 
@@
 
-We show in Figure \ref{fig:particles_interface_prop_shear} that when the magnetic field is kept the same between the template and during shear, the
+I show in Figure \ref{fig:particles_interface_prop_shear} that when the magnetic field is kept the same between the template and during shear, the
 proportion of particles on the interface ($n_{int}$) stays approximately the same. However when changing the applied field strength, $n_{int}$ more 
-sensitive to shear. Here we also characterize that increasing the applied field strength reduces $n_{int}$ more than decreasing it. This is consistent
-with the amount of coarsening observed for each case seen in Figure \ref{fig:domain_size_time_shear} where $\bar{B}:0 \rightarrow 1$ shows the largest
-change.
+sensitive to shear. Here I also characterize that increasing the applied field strength reduces $n_{int}$ more than decreasing it. To characterize 
+the role of the interface properties and the impact of particle ejection and tilting of particles out of the interface,the next section aims to 
+uncover the microstructural implications of these effects.
+
+% This is consistent
+% with the amount of coarsening observed for each case seen in Figure \ref{fig:domain_size_time_shear} where $\bar{B}:0 \rightarrow 1$ shows the largest
+% change.
+
+\subsection{Microstructure change}
+
+Bonaccorso et al. identified that the spherical particle stabilizers in their bijel simulations oriented to the direction of shear before being
+ejected from the interface. \cite{bonaccorso_shear_2020} This then led to the domains of the bijel to coalesce and eventually destruction of the
+bicontinuous microstructure. \cite{bonaccorso_shear_2020} In our bijels, we also characterize this behavior upon application of shear.
+In this section, I probe the effect of applied shear to the microstructure of magnetically
+responsive bijels stabilized by ellipsoidal particles. To investigate the effect of the particle angle on the interfacial coverage of the bijel,
+I plot the area averaged gaussian curvature over time. This parameter will allow insight into the evolution of the interface, namely the presence of
+domain coarsening, coalscence or break-off events.
+
+\begin{figure} 
+    \centering 
+    \includegraphics[scale=0.3]{../figures/results/paper3/gaussian-time_compare.png} 
+    \caption{Plots of the time evolution of the area averaged Gaussian curvature $\langle K \Sigma^{-2} \rangle$ for four 
+             processing histories applied to bijels stabilized with oblate and prolate ellipsoids. I demonstrate that the 
+             magnitude of the gaussian curvature reduces for all systems except for $\bar{B}: 0 \to 1$.} 
+    \label{fig:gaussian_curvature_time_shear} 
+\end{figure}
+
+Figure \ref{fig:gaussian_curvature_time_shear} reveals that the area averaged Gaussian curvature generally decreases in magnitude over time for all cases except 
+$\bar{B}: 0 \to 1$. I also characterize that the curvature evolution of all systems are shear independent. $\bar{B}: 0 \to 1$ is
+unique because particle rearrangements at the interface dominates the dynamics of the microstructure, not observed in all other
+cases. From the time evolution of the curvature, I show that the same mechanism drives domain coarsening in all cases. Domain
+coarsening is driven through a reduction in the interfacial area covered by the particle monolayer. From the curvature results characterized in 
+Figure \ref{fig:gaussian_curvature_time_shear}, I saw that the coarsening is shear independent. This indicates that the surface area of the interface 
+decreases which can occur due to changes in the interfacial orientation of particles at the interface or a reduction in the number of particles at the interface. 
+I can characterize the former mechanism using the average interfacial angle between the particle and the interface $\langle \psi \rangle$.
+
+% Previous investigations have 
+% demonstrated how the orientation and arrangement of particles on the interface affect the domain size. 
+% \cite{gunther_timescales_2014} I focus our investigation on this aspect in the following plot.
+
+% \begin{figure} 
+%     \centering 
+%     \includegraphics[scale=0.3]{../figures/results/paper3/domain_size-time_compare.png} 
+%     \caption{Comparisons of the time evolution of the average domain size for bijels stabilized by ellipsoidal particles undergoing
+%              various shear rates under four processes. Initially, the domain size coarsens for all runs under applied shear before
+%              reducing in some cases.} 
+%     \label{fig:domain_size_time_shear} 
+% \end{figure}
+
+% From Figure \ref{fig:domain_size_time_shear}, domains coarsen with time in all cases. When increasing the applied magnetic field in the case of 
+% $\bar{B}:0 \rightarrow 1$, I see shear assisted domain coarsening characterized as a 20 \% and 10 \% increase in the domain size of bijels
+% stabilized by oblate and prolate particles respectively. This is approximately 5 times greater than the response observed in Figure \ref{fig:domain_size-field_on}
+% In the  $\bar{B}: 1 \to 0$ and $\bar{B}: 1 \to 1$ cases, an initial plateau in domain size is observed, followed by a divergence in 
+% growth depending on $Ca$. The shear rate appears to influence domain coarsening, with higher $Ca_s$ leading to delayed or 
+% suppressed growth, especially in the presence of a field. The difference between applying $\bar{B}: 0 \to 1$ and 
+% removing $\bar{B}: 1 \to 0$ the field demonstrates the stability of the particle monolayer when a field is switched off.
+% There is little difference in the qualitative trends of domain size change for bijels stabilized with oblate or prolate particles.
+% To characterize whether the domain size coarsening observed arises from different phenomena in each case, the area averaged curvature is plotted.

### 2025-03-19 chapters/paper3.tex
Changes 1. Completed rewrite of aim 3 chapter

@@
 
-I show in Figure \ref{fig:particles_interface_prop_shear} that when the magnetic field is kept the same between the template and during shear, the
-proportion of particles on the interface ($n_{int}$) stays approximately the same. However when changing the applied field strength, $n_{int}$ more 
-sensitive to shear. Here I also characterize that increasing the applied field strength reduces $n_{int}$ more than decreasing it. To characterize 
-the role of the interface properties and the impact of particle ejection and tilting of particles out of the interface,the next section aims to 
-uncover the microstructural implications of these effects.
+From the results in Figure \ref{fig:particles_interface_prop_shear}, the impact of the initial microstructure on the number of particles on the interface
+differs for bijels stabilized by oblate and prolate ellipsoids. We split this analysis on processing history. While keeping the applied magnetic field
+the same, we see little differences in the behavior of $n_{int}$, with their behavior corresponding to changes in $\langle \psi \rangle$. 
+Looking at the case of $\bar{B}:0 \rightarrow 0$, there is little change in the number of particles at the interface upon application of shear. This implies that the 
+particles remain strongly adsorbed on the
+interface. The $\langle \psi \rangle$ results also show this as we see this parameter increasing slowly. This suggests that the particles remain firmly adsorbed
+on the interface. Looking to the $\bar{B}:0 \rightarrow 1$ case, the number of particles at the interface drops while $\langle \psi \rangle$ increases. This
+trend affects both particles which suggests that shear can pull particles out of the interface due to the decreased
+interfacial adsorption energy the particle experiences when rotating out of the interface to orient to the applied field. The $\bar{B}:1 \rightarrow 1$ and 
+$\bar{B}:1 \rightarrow 0$ have strong dependences on particle morphology. While an increase in $\langle \psi \rangle$ can be seen in both processing histories 
+for both particle morphologies, a decrease in $n_{int}$ can be seen for prolate particles with processing history $\bar{B}:1 \rightarrow 0$ and for 
+oblate particles with processing history $\bar{B}:1 \rightarrow 1$. We visualize $\langle \psi \rangle$ at the initial and final timestep for bijels stabilized with
+oblate and prolate particles with processing $\bar{B}:1 \rightarrow 0$.
 
-% This is consistent
-% with the amount of coarsening observed for each case seen in Figure \ref{fig:domain_size_time_shear} where $\bar{B}:0 \rightarrow 1$ shows the largest
-% change.
+\begin{figure} 
+    \centering 
+    \includegraphics[scale=0.4]{../figures/results/paper3/psi_concat_startB-1_endB-0.png} 
+    \caption{Visualization of the particle monolayer of bijels stabilized by prolate and oblate ellipsoidal particles with processing history $\bar{B}: 1 \rightarrow 0$
+             undergoing an applied shear of $Ca_s = 10^{-6}$. Particles with a deeper red shade have a larger angle to the interface. The top and bottom row show the 
+             configuration of the particles at the initial and final timestep respectively.} 
+    \label{fig:particle_viz_psi} 
+\end{figure}
+
+Figure \ref{fig:particle_viz_psi} shows that the increase in $\langle \psi \rangle$ seen in Figure \ref{fig:interface_angle_shear} occurs due to different
+reasons for both particle morphologies. For oblate particles, this is caused by particles orienting such that their symmetry axis is parallel to the interface
+while prolate particles experienced interparticle forces induced by the applied shear, resulting in particles being ejected from the interface when the magnetic 
+field is switched off. When keeping the magnetic field on, the oblate particles are forced to stay in sub-optimal particle orientations to the interface, resuling
+in ejection of particles from the interface. The presence of the magnetic field reduces shear induced interparticle interactions owing to the ordering of
+particles to the applied field, resulting in the mostly unchanged $n_{int}$ values. A increase in $\langle \psi \rangle$ and decrease in $n_{int}$ indicates domain
+can indicate coarsening of the fluid domains as the interfacial area is reduced. In the next section, I investigate the the role of the interface properties and the 
+impact of particle ejection and tilting of particles out of the interface on the microstructure of bijels.
 
@@
 ejected from the interface. \cite{bonaccorso_shear_2020} This then led to the domains of the bijel to coalesce and eventually destruction of the
-bicontinuous microstructure. \cite{bonaccorso_shear_2020} In our bijels, we also characterize this behavior upon application of shear.
+bicontinuous microstructure. \cite{bonaccorso_shear_2020} In our bijels, we characterize particle morphology and initial microstructure specific 
+properties of the particle monolayer upon application of shear. 
 In this section, I probe the effect of applied shear to the microstructure of magnetically
-responsive bijels stabilized by ellipsoidal particles. To investigate the effect of the particle angle on the interfacial coverage of the bijel,
-I plot the area averaged gaussian curvature over time. This parameter will allow insight into the evolution of the interface, namely the presence of
-domain coarsening, coalscence or break-off events.
+responsive bijels stabilized by ellipsoidal particles. To investigate the effect of the particle angle and the interfacial coverage of the bijel on the
+microstructural evolution of the interface, I plot the area averaged gaussian curvature over time. This parameter will allow insight into the evolution 
+of the interface, namely the presence of domain coarsening, coalscence or break-off events.
 
@@
 Figure \ref{fig:gaussian_curvature_time_shear} reveals that the area averaged Gaussian curvature generally decreases in magnitude over time for all cases except 
-$\bar{B}: 0 \to 1$. I also characterize that the curvature evolution of all systems are shear independent. $\bar{B}: 0 \to 1$ is
+$\bar{B}: 0 \to 1$ indicating that the increase in $\langle \psi \rangle$ causes domain coarsening of the bijel. $\bar{B}: 0 \to 1$ is
 unique because particle rearrangements at the interface dominates the dynamics of the microstructure, not observed in all other
-cases. From the time evolution of the curvature, I show that the same mechanism drives domain coarsening in all cases. Domain
-coarsening is driven through a reduction in the interfacial area covered by the particle monolayer. From the curvature results characterized in 
-Figure \ref{fig:gaussian_curvature_time_shear}, I saw that the coarsening is shear independent. This indicates that the surface area of the interface 
-decreases which can occur due to changes in the interfacial orientation of particles at the interface or a reduction in the number of particles at the interface. 
-I can characterize the former mechanism using the average interfacial angle between the particle and the interface $\langle \psi \rangle$.
+cases. From the time evolution of the curvature, the same mechanism drives coarsening in all cases. From the results in Figures \ref{fig:particles_interface_prop_shear} 
+and \ref{fig:interface_angle_shear}, domain coarsening is driven through a reduction in the interfacial area covered by the particle monolayer. 
+From the curvature results characterized in Figure \ref{fig:gaussian_curvature_time_shear}, the area averaged curvature coarsening is shear independent. This is further
+evidence that the mechanism of coarsening is identical in each case.
+
+\begin{figure} 
+    \centering 
+    \includegraphics[scale=0.3]{../figures/results/paper3/anisotropy_compare.png} 
+    \caption{Comparisons of the time evolution of the directional domain sizes that increase upon application of a magnetic field for bijels stabilized 
+             by ellipsoidal particles undergoing various shear rates under four processes. The directional domain size increases in all cases except for when the
+             field is switched off.} 
+    \label{fig:domain_size_aniso_time_shear} 
+\end{figure}
+
+From Figure \ref{fig:domain_size_aniso_time_shear}, the directional domain sizes in the orientations with the maximum change were characterized. For oblate and prolate 
+particles, this was found to be $L_{\perp}$ and $L_{\parallel}$ respectively. In all cases except for $\bar{B}: 1 \to 0$, this length scale increases matching the expected
+trend that increasing $\langle \psi \rangle$ matches domain coarsening. The decrease in these length scales for $\bar{B}: 1 \to 0$ suggest that the shear induced
+reordering of interfacial particles after application of a field affects the evolution of the microstructure. For both particles, this is due to particle mediated
+shear forces causing domains to coarsen more in specific directions. From the snapshots of the particle arrangement in Figure \ref{fig:particle_viz_psi} the particles were
+shown to reorient at the interface. This process did not occur for $\bar{B}: 1 \to 1$ as the presence of magnetic fields acted to keep particles aligned a specific
+direction.
+
+In this chapter, I investigated the rheology of bijels stabilized by ellipsoidal particles under shear, focusing on the influence of initial microstructure and the 
+application of a constant magnetic field on their shear response. The shear behavior was characterized using a Herschel-Bulkley fitting function to extract the flow index, 
+consistency index, and yield stress. My analysis confirmed that the shear-thinning nature of bijels remains robust, regardless of particle morphology or applied magnetic 
+field. However, the flow index and yield stress trends were strongly dependent on these factors.  
+I found that increased particle ordering led to distinct yield stress behaviors: oblate particles resulted in a lower yield stress, while prolate particles exhibited a 
+higher yield stress. When examining the properties of the particle monolayer, I identified a clear impact of particle morphology on interparticle interactions at the 
+interface. In the absence of a magnetic field, both particle monolayers remained adsorbed at the interface. However, when a magnetic field was initially applied, the 
+behavior diverged significantly oblate particles flipped out of the interface to minimize interfacial energy, whereas prolate particles tilted out. These differences 
+directly influenced the shear response, altering how the surrounding fluid flows around the particles and leading to the observed non-Newtonian behavior and yield 
+stress characteristics.  
+Furthermore, I investigated the microstructural effects of shear and magnetic field-induced particle ordering and found that coarsening was the primary driver of 
+domain size evolution in sheared bijels. This coarsening was facilitated by a reduction in interfacial particle coverage. When analyzing the anisotropic domain size evolution, 
+I observed that in most cases, the direction of greatest structural change aligned with expected trends—except when the magnetic field was switched off. This deviation is 
+attributed to differences in particle monolayer evolution, depending on whether the bijel was formed with or without an initially applied field.
 

### 2025-03-19 chapters/final_remarks.tex
Changes 1. Adapted conclusion to new aim 3 text

--- 2025-03-06 chapters/final_remarks.tex
@@
 specific jamming also reduces the local curvature of the system as the interface location moves with the particle.
-
 To investigate the role of the particle monolayer in greater detail, we characterize the orientational order to the magnetic field,
@@
 order of the particles controls the timescales of response.
-
 When investigating the effect of pre-existing order of the particle monolayer, we show that the structural response of the bijel is dependent upon the
@@
 
-In Aim 3 we investigate the rheological response of bijels stabilized with ellipsoidal particles under constant shear and show that the application of magnetic
-fields changes the shear thinning properties of bijels.
+In Aim 3, I investigated the rheology of bijels stabilized by ellipsoidal particles under shear, examining the effects of initial microstructure and a 
+constant magnetic field on their shear response. Using a Herschel-Bulkley fitting, I found that while shear-thinning behavior remains robust, the 
+flow index and yield stress are strongly influenced by particle morphology and magnetic field application. Increased particle ordering led to 
+lower yield stress in oblate-particle-stabilized bijels and higher yield stress in prolate-particle-stabilized bijels, highlighting the role of particle 
+shape in interfacial mechanics. Without a magnetic field, both particle monolayers remained adsorbed at the interface, but when a field was applied, 
+oblate particles flipped out of the interface, whereas prolate particles tilted, altering the flow field and impacting non-Newtonian behavior. Additionally, 
+coarsening driven by reduced interfacial particle coverage emerged as the dominant mechanism behind domain size evolution in sheared bijels. The anisotropic 
+domain growth trends matched expectations in all cases except when the field was removed, indicating that the history of field application significantly influences 
+microstructural evolution. These findings provide insight into the interplay between particle morphology, interfacial coverage, and external fields, contributing 
+to the understanding of magnetically tunable soft materials and structured emulsions.
 

### 2025-03-19 chapters/paper2.tex
Changes 1. Rewrote aim 2 to improve flow and grammar

@@
 
-Due to their tortuous, co-continuous domain morphology, bicontinuous interfacially jammed emulsion gels (bijels) have been 
+Due to their tortuous, co-continuous domain morphology, bijels have been 
 extensively studied for applications in membrane fabrication, catalyst supports, battery electrodes, and pharmaceutical 
@@
 We further assess how initial microstructure influences structural changes, showing that the difference in order between initial and final 
-particle monolayers dictates the extent of microstructure evolution if the applied field is increased. Additionally, applying and removing a 
+configurations of the particle monolayers dictates the extent of microstructure evolution if the applied field is increased in the direction of 
+the existing order. Additionally, applying and removing a 
 magnetic field results in distinct microstructural properties and timescales, highlighting the importance of processing history. These findings 
@@
 performance in each application is dependent upon the microstructure of the bijel template. Many of the applications listed above benefit 
-from stimuli response, allowing for in-situ microstructure tuning to offer reversible modifications of material permeability. In this section, we analyzes
+from stimuli response, allowing for in-situ microstructure tuning to offer reversible modifications of material permeability. In this section, I analyze
 whether stimuli responsive bijels provide access to reversible structural modifications.
@@
 particle volume fraction of $\phi_p = 0.1$. We only focus on one system here as the mechanism for stimuli response shown in Aim 1 is identical
-for both systems. Therefore we expect that the qualitative trends between prolate and oblate particles will be matched. We select prolate particles
-as they are more readily synthesized in experiments.
+for both systems. Therefore we expect that the qualitative trends between prolate and oblate particles will be matched. I select prolate particles
+as they are more readily synthesizable in experiments.
 
-We apply a constant magnetic field of $\bar{B}_z = 0.2$ onto bijels that were simulated 
-with no magnetic field. Once the microstructure has reached its new state, we ramp up the magnetic field to $\bar{B}_z = 0.5$ and 
-finally $\bar{B}_z = 1$. We then apply the opposite procedure to reduce the applied field strength, resulting in a magnetic field 
-ramp of $\bar{B}_z: 0 \rightarrow 0.2 \rightarrow 0.5 \rightarrow 1 \rightarrow 0.5 \rightarrow 0.2 \rightarrow 0$.We characterize the 
-microstructure changes observed through calculating a characteristic length scale, called the average domain size. We calculate the hysteresis 
-curve by calculating the domain size at the final timestep of each magnetic field change. We then plot these domain sizes against the magnetic field 
-applied to obtain them and split them in the descending and ascending magnetic field directions to demonstrate the differences observed. We plot 
+I apply a constant magnetic field of $\bar{B}_z = 0.2$ onto bijels that were simulated 
+with no magnetic field. Once the microstructure has reached its new state, I ramp up the magnetic field to $\bar{B}_z = 0.5$ and 
+finally $\bar{B}_z = 1$. I then apply the opposite procedure to reduce the applied field strength, resulting in a magnetic field 
+ramp of $\bar{B}_z: 0 \rightarrow 0.2 \rightarrow 0.5 \rightarrow 1 \rightarrow 0.5 \rightarrow 0.2 \rightarrow 0$. I characterize the 
+microstructure changes observed through calculating the domain size, defined as the first moment of the spherically averaged structure factor. 
+I calculate the hysteresis 
+curve by selecting the domain size at the final timestep of each magnetic field change. I then plot these domain sizes against the magnetic field 
+applied to obtain them and split them in the descending and ascending magnetic field directions to demonstrate the differences observed. I plot 
 these results in Figure \ref{fig:hysteresis_curve}
@@
     \includegraphics[scale=0.5]{../figures/results/paper2/hysteresis_curve.png} 
-    \caption{Plot of the hysteresis curve of a bijel stabilized by magnetically responsive prolate particles. We observe that the domain size increases as we 
-    increase the applied magnetic field strength. However, upon decrease of the field strength, we see that the microstructure does not return to its previous value,
+    \caption{Plot of the hysteresis curve of a bijel stabilized by magnetically responsive prolate particles. I observe that the domain size increases as we 
+    increase the applied magnetic field strength. However, upon decrease of the applied field strength the microstructure does not return to its previous value,
     demonstrating microstructure hysteresis.} 
@@
 
-Figure \ref{fig:hysteresis_curve} we observe a hysteresis response of the bijel microstructure, characterized by a difference in the average domain size
-when increasing and decreasing the magnetic field. The increase in the average length scale when applying the magnetic field is due to domain coarsening caused by 
+Figure \ref{fig:hysteresis_curve} demonstrates the hysteresis response of the bijel microstructure, characterized by a difference in the average domain size
+when increasing and decreasing the magnetic field. The increase in the average domain size when applying the magnetic field is due to domain coarsening caused by 
 reorientation of particles to the magnetic field strength, reducing the interfacial coverage. When decreasing the magnetic field strength, 
-we observe that the domain size does not return to the original value meaning that that the microstructure of the bijel is unaffected by 
-the reduction in applied magnetic field.
+the domain size does not return to the original value meaning that that the microstructure of the bijel is unaffected by 
+the reduction and eventual removal of the applied magnetic field.
 
@@
 electric fields. \cite{cui_stabilizing_2013} Cui et al. demonstrated that the particles unjammed and rejammed into a new kinetically arrested state resulting in
-the droplet being elongated in the direction of the applied field. This suggests that the particles at the interface of magnetically responsive bijels are also 
-in a kinetically trapped configuration. We observe in Figure \ref{fig:hysteresis_curve} that the response of the bijel is dependent upon the field strength applied.
-In the following sections, we investigate the impact of magnetic field strength and the initial ordering of the particle monolayer on the observed stimuli response.
+the droplet being elongated in the direction of the applied field. This suggests that the particles at the interface of magnetically responsive bijels are in
+in a kinetically trapped configuration. Cui et al. used spherical particles in their emulsion response experiments while we use ellipsoidal particles. Additionally,
+we also observe in Figure \ref{fig:hysteresis_curve} that the response of the bijel is dependent upon the field strength applied.
+In the following sections, I investigate the impact of magnetic field strength and the initial ordering of the particle monolayer on the observed stimuli response.
 
-\subsection{Field strength dependence on domain
-size}\label{section:field-strength-dependence-on-domain-size}
+\subsection{Field strength dependence on domain size}
+\label{section:field-strength-dependence-on-domain-size}
 
-From the results in Figure \ref{fig:hysteresis_curve}, we show that the domain size change is dependent upon the applied magnetic field. As porous materials templates,
+From the results in Figure \ref{fig:hysteresis_curve}, I show that the domain size change is dependent upon the applied magnetic field. As porous materials templates,
 the microstructure of the material is of interest as it controls the performance of the material. Additionally, in many of the proposed stimuli responsive applications
 for bijels, the timescales of response is important to characterize and would also provide a mechanistic understanding of the reasons why the microstructure changes 
-occur. We probe these aspects of structural response of bijels in this section by assessing the response of bijels stabilized by particles with volume fraction of 
-$\phi_p = 0.1$ simulated under no applied field to an applied field in the range $\bar{B} = 0, 0.2, 0.5, 1$. We begin our investigation by visualizing the structure before 
+occur. In this section, I analyze the structural response of bijels by assessing the response of bijels stabilized by particles with volume fraction of 
+$\phi_p = 0.1$ simulated under no applied field to an applied field in the range $\bar{B} = 0, 0.2, 0.5, 1$. I begin my investigation by visualizing the structure before 
 and after the application of magnetic fields.
@@
 
-In Figure \ref{fig:microstructure_viz-field_on} we show representative snapshots of the bijel at the initial and final timestep with $\bar{B}_z = 0$ and $\bar{B}_z = 1$. 
-We show that upon application of the field, particles align to the direction of the field. As the particles orient to the field, they disrupt the packing of particles at
-the interface. This caused domain coarsening as the particles rearrange into new positions before rejamming in place once the interfacial
+In Figure \ref{fig:microstructure_viz-field_on} I show representative snapshots of the bijel at the initial and final timestep with $\bar{B}_z = 0$ and $\bar{B}_z = 1$. 
+Upon application of the field, particles align to the direction of the field. As the particles orient to the field, they disrupt the packing of particles at
+the interface. This causes domain coarsening as the particles rearrange into new positions before rejamming in place once the interfacial
 area and particle cross sectional area match. Domain coarsening observed in the figure can be explained through the ordering of particles at the interface, causing a 
 reduction in the available area that the particles have for stabilization. To characterize the length scale of the microstructure upon application of the magnetic field,
-we calculate the average domain size. To correlate the microstructure evolution to the ordering of the particle monolayer to the magnetic field, we calculate the 
-nematic order parameter. \cite{veerman_phase_1992}
+I calculate the domain size. To correlate the microstructure evolution to the ordering of the particle monolayer to the magnetic field, I overlay the time evolution of the
+nematic order parameter on the domain size. \cite{veerman_phase_1992}
 
@@
 
-In Figure \ref{fig:domain_size-field_on}, we present the time evolution of the normalized average domain size, where normalization is performed
-using the volume-equivalent spherical particle radius $R = 7.9$. The results indicate that upon applying a magnetic field to a bijel
-initially formed without one, the final average domain size increases by up to 5.2\% and 2.5\% for oblate- and prolate-particle-stabilized bijels
-respectively. The domain coarsening is initially slow, before accelerating rapidly and finally reaching a maximum where it plateaus. 
+I normalized the domain size results by the volume equivalent sphere radius, $R = 7.9$ in Figure \ref{fig:domain_size-field_on} The results indicate that upon 
+applying a magnetic field to a bijel initially formed without one, the final average domain size increases by up to 5.2\% and 2.5\% for oblate and 
+prolate particle stabilized bijels respectively. The domain coarsening is initially slow, before accelerating rapidly and finally reaching a maximum where it plateaus. 
 Additionally, in the absence of an external field, domain coarsening occurs for both particle morphologies. However, the results
@@
 This effect contributes to the domain coarsening seen in the absence of an applied field, consistent with the findings of Günther et
-al.~\cite{gunther_timescales_2014}. In the case of oblate-particle-stabilized bijels without an external field, domain
+al. \cite{gunther_timescales_2014}. In the case of oblate particle stabilized bijels without an external field, domain
 coalescence is primarily driven by steric interactions rather than field-induced rearrangement. Furthermore, the rate and extent of
 particle alignment to the field exhibit a dependence on field strength, as evidenced by the earlier onset of nematic ordering with increasing
-$\bar{B}$. We also observed between the time evolution of the nematic order parameter and domain size, particularly when comparing results for
-$\bar{B}_z = 0.5, 1$ against those for $\bar{B}_z = 0.2$. This suggests that nematic ordering alone may not fully account for the
+$\bar{B}$. A time delay between the evolution of the nematic order parameter and domain size, particularly when comparing results for
+$\bar{B}_z = 0.5, 1$ against those for $\bar{B}_z = 0.2$ are seen. This suggests that nematic ordering alone may not fully account for the
 observed changes in domain size.
@@
 Precise characterization of the anisotropic microstructure is essential for the tailored design of application-specific porous materials. To
-quantify the characteristic length scales in each Cartesian direction, we compute the second-moment-derived structure factor. \cite{jansen_bijels_2011} 
-We also calculate the tortuosity  in each cartesian direction. Here, we make a further
+quantify the characteristic length scales in each Cartesian direction, I compute the second-moment-derived structure factor. \cite{jansen_bijels_2011} 
+I also calculate the tortuosity  in each cartesian direction. I make a further
 refinement simplifying the domain sizes to directions parallel and orthogonal to the magnetic field. These result in the length scales and
-their associated calculation, $L_{\parallel} = L_{z}$ and $L_{\perp} = \frac{L_x + L_y}{2}$. We perform the same simplification
-with the directional tortuosities.
+their associated calculation, $L_{\parallel} = L_{z}$ and $L_{\perp} = \frac{L_x + L_y}{2}$. The same simplification
+with the directional tortuosities is also performed.
 
-Tortuosity has been defined using the geometric, diffusional and hydraulic tortuosities. Here we define
+Tortuosity has been defined using the geometric, diffusional and hydraulic tortuosities. The tortuosity calculated here is
 the diffusional tortuosity, $\tau = \frac{D}{D_{eff}}$ which characterizes the ratio between the free diffusion of a tracer and the
-effective diffusion of a tracer in the material. Therefore, we plot the directional second moment derived length scales and tortuosity in
+effective diffusion of a tracer in the material. I plot the directional second moment derived length scales and tortuosity in
 Figure \ref{fig:domain_size_aniso-field_on}.
@@
 
-From Figure \ref{fig:domain_size_aniso-field_on}, we see that domain size anisotropy is observed upon application of the field for both
-particle morphologies. We also see some domain anisotropy with no applied field, which increases upon application of the magnetic field.
+From Figure \ref{fig:domain_size_aniso-field_on}, domain size anisotropy is observed upon application of the field for both
+particle morphologies. I also see some domain anisotropy with no applied field, which increases upon application of the magnetic field.
 The directional domain sizes, $L_{\perp}$ and $L_{\parallel}$ increase by 73\% and 7\%\ respectively for oblate particles and
 10\% and 44\% respectively for oblate particles. The axes that coarsens the most is consistent with past work, explained through the
-directions particles reorient in response to the applied magnetic field.
+directions particles reorient in response to the applied magnetic field. As particles unjam and rejam at the interface due to reorientating 
+to the magnetic field, they adopt direction specific surface coverages which manifest as anistropic domains upon jamming. In Figure 
+\ref{fig:domain_size_aniso-field_on}, we demonstrate that the application of the magnetic field changes the domain size.
 
-As particles unjam and rejam at the interface due to reorientating to the magnetic field, they adopt direction specific surface coverages
-which manifest as anistropic domains upon jamming. In Figure \ref{fig:domain_size_aniso-field_on}, we demonstrate that the
-application of the magnetic field changes the domain size. The tortuosity of the bijel is initially around $\tau \approx 1.5$,
-consistent with simulations of the diffusive tortuosities of gyroid structures using Lattice Boltzmann simulations.
-\cite{luo_macroscopic_2020} Upon application of the field, $\tau_{\perp}$ slightly decreases while $\tau_{\parallel}$
-increases. We have seen that an increasing domain size decreases the tortuosity in our past work. \cite{karthikeyan_formation_2024} This
+The tortuosity of the bijel is initially around $\tau \approx 1.5$, consistent with simulations of the diffusive tortuosities of gyroid structures using 
+Lattice Boltzmann simulations. \cite{luo_macroscopic_2020} Upon application of the field, $\tau_{\perp}$ slightly decreases while $\tau_{\parallel}$
+increases. In Chapter \ref{chapter:aim1}, I characterized that increasing the domain size decreases the tortuosity. \cite{karthikeyan_formation_2024} This
 observation is in line with the domain size changes observed in Figure \ref{fig:domain_size_aniso-field_on}. The results show that the
@@
 
-Next, we return to investigate the time gap between the average domain size increase and the nematic order parameter. This result suggests that the dynamics 
+Next, I return to investigate the time gap between the average domain size increase and the nematic order parameter. This result suggests that the dynamics 
 of the system at higher magnetic field strengths are dependent upon other factors that vary upon application of the magnetic field. In this system, these factors
 would arise from capillary forces with the interface or steric interactions with other particles at the interface, slowing down the dynamics of the system.
-To understand this phenomena, we focus on the dynamics of the particle monolayer. First, we visualize the particle monolayer of the bijels stabilized with prolate 
+To understand this phenomena, I focus on the dynamics of the particle monolayer. First, I visualize the particle monolayer of the bijels stabilized with prolate 
 ellipsoids at the initial and final configuration before and after application of a magnetic field.
@@
 
-In Figure \ref{fig:particle_viz-field_on}, we see the initial configuration of particles at the monolayer show that the orientations are random and that the 
+In Figure \ref{fig:particle_viz-field_on}, I see the initial configuration of particles at the monolayer show that the orientations are random and that the 
 particles tend to lie flat on the interface. However, upon application of the magnetic field the particles orient to the field direction. With no applied field,
-we see that the orientations and positions of the particles vary slightly for both ellipsoidal particle morphologies. This effect is due steric effects between particles,
-as identified in Gunther et al. \cite{gunther_timescales_2014} We observe that for bijels stabilized by prolate ellipsoids, we see the adoption of orientational order
+I see that the orientations and positions of the particles vary slightly for both ellipsoidal particle morphologies. This effect is due steric effects between particles,
+as identified in Gunther et al. \cite{gunther_timescales_2014} I observe that for bijels stabilized by prolate ellipsoids, we see the adoption of orientational order
 to the magnetic field and qualitatively different particle arrangements on the interface. These indicate that the interfacial capillary forces or steric interactions 
@@
 angle, $\langle \psi \rangle$ and the local ordering of the particles characterized with  $\langle Q6 \rangle$ Past work has identified that local crystallization 
-of colloidal crystals takes place at \(\langle Q6 \rangle = 0.38\). \cite{toxvaerd_role_2020}
+of colloidal supercooled fluids takes place at \(\langle Q6 \rangle = 0.38\). \cite{toxvaerd_role_2020} Past investigations into the rheology of bijels have revealed
+that bijels are colloidal glasses percolating in 3D space. \cite{ching_bijel_2022} However, application of a magnetic field results in reorientation of particles on
+the interface that can temporarily reduce the interfacial coverage of the particles on the interface, temporarily making the particle monolayer more liquid-like
+than amorphous. \cite{hunter_physics_2012} Using this approximation, I can use the local crystallization result shown in Toxvaerd.
 
@@
 From Figure \ref{fig:interface_angle-nint-field_on}, we identify that prolate and oblate particles respond differently at the interface. For
-bijels stabilized by oblate ellipsoids, we characterize an increase in $\langle \psi \rangle$ from an initial value of \(19 ^{\circ}\),
+bijels stabilized by oblate ellipsoids, I characterize an increase in $\langle \psi \rangle$ from an initial value of $19 ^{\circ}$,
 before it reduces slightly and begins to increase once again. The initial starting value of $\langle \psi \rangle$ indicates the
@@
 
-From the visualizations in Figure \ref{fig:psi_field_on_visualize}, we see that the particles lie mostly flat on the interface at the initial timestep for bijels
-stabilized with oblate and prolate particles. Upon application of a field strength of $\bar{B} = 1$, we observe that the particles in the snapshot at the final timestep 
-are in different conformations for bijels stabilized with oblate and prolate particles. Oblate particles tend to flip on the interface into a metastable state where
+From the visualizations in Figure \ref{fig:psi_field_on_visualize}, the particles lie mostly flat on the interface at the initial timestep. Upon application of a field 
+strength of $\bar{B} = 1$, the final state of the monolayer is particle morphology dependent. Oblate particles tend to flip on the interface into a metastable state where
 the interface covered by each particle is done with the $R_p$ and $R_o$ compared to its lowest energy state where it lies flat with radii $R_o$. The particle monolayer
 of bijels stabilized by prolate particles tilt out of the interface with no metastable configurations observed. This effect explains the trends seen in $\langle \psi \rangle$
-at long times for both particle morphologies. This particle flipping on the interface affects the way the particles can arrange on the interface. We probe this by identifying 
-the local particle ordering at the interface characterized by $\langle Q6 \rangle$.
+at long times for both particle morphologies. This particle flipping on the interface affects the way the particles can arrange on the interface, like what I 
+characterized In Figure \ref{fig:rdf}. This change in local ordering can be quantified using $\langle Q6 \rangle$.
 
-We see that for oblate particles, $\langle Q6 \rangle$ sees a decrease from its initial value. However the dynamics are controlled by
-the applied magnetic field strength. We split the phases of dynamics into three sections, similar to $\langle \psi \rangle$. In the first
-section, we see a decrease in $\langle Q6 \rangle$ upon application of the magnetic field, followed by a plateau and finally a gradual increase
-before jamming takes place. These results indicate that the ordering of the particles is reduced by the applied magnetic field, before a
+From Figure \ref{fig:interface_angle-nint-field_on} the dynamics of $\langle Q6 \rangle$ are particle morphology specific but can be split into three sections for 
+both particle morphologies. Characterizing the time evolution of $\langle Q6 \rangle$ for oblate particles, I see a decrease upon application of the magnetic field, 
+followed by a plateau and finally a gradual increase before jamming takes place, seen as a significant decrease in the rate of chang to $\langle Q6 \rangle$.
+These results indicate that the ordering of the particles is reduced by the applied magnetic field, before a
 restoration of some of the pre-existing order. The final values of $\langle Q6 \rangle$ are magnetic field dependent, with a stronger
 magnetic field having a lower final $\langle Q6 \rangle$ value indicating that either the ordering of particles influence the angle at
-the interface or vice versa. We observe that for bijels stabilized by oblate particles, the interface ordering of the particles increases as a
-function of the applied field strength. We also observe from plotting $\langle Q6 \rangle$ that application of a magnetic field creates a
-local crystallization of the colloid monolayer characterized as $\langle Q6 \rangle > 0.38$. \cite{toxvaerd_role_2020}
+the interface or vice versa.
 
-Next, we want to identify which of these forces represent the timescale that controls the dynamics of the system. We can calculate a characteristic
-timescale for each factor from the calculated particle properties.
+I observe that for bijels stabilized by prolate particles, the interface ordering of the particles increases as a
+function of the applied field strength. The first phase of the evolution of $\langle Q6 \rangle$ sees some growth in $\langle Q6 \rangle$ before 
+increasing dramatically and plateauing as jamming takes place. The length of time of the initial plateau and growth regions are negatively and
+positively correlated to the applied magnetic field strength. Upon application of the magnetic field, $\langle Q6 \rangle > 0.38$ in all cases. Approximating
+the particle monolayer as a colloidal glass that underwent a glass transition, the monolayer can be said to undergo a local crystallation event when 
+$\langle Q6 \rangle > 0.38$. \cite{toxvaerd_role_2020}
+
+Thus far, three particle based phenomena have been characterized; the orientation of the particle to the magnetic field, the interface and the local 
+arrangement of the particles on the interface. I can calculate a timescale for each factor from the plots of each of these properties.
 The nematic order parameter $S$ represents the ordering of
@@
 response rate limited to the response to the magnetic field, which
-indicates a particle-field orientation dependence. We name this
+indicates a particle-field orientation dependence. I name this
 timescale $\tau_S$. When applying a field to a bijel system with a
@@
 
-We can also do the same for $\langle \psi \rangle$ and
+I can also do the same for $\langle \psi \rangle$ and
 $\langle Q6 \rangle$. A timescale derived from
@@
 \(\langle Q6 \rangle \geq 0.38\) for prolate particles and the global
-minimum of $\tau_{\langle Q6 \rangle}$ for the oblate particles. We
+minimum of $\tau_{\langle Q6 \rangle}$ for the oblate particles. I
 omit \(\bar{B} = 0\) as previous results have identified the domain size
-changes observed there. We then plot the average domain size \(L\)
+changes observed there. I then plot the average domain size $L$
 against time rescaled with these three timescales in Figure
@@
 In Figure \ref{fig:domain_size-field_on-scaled}, the left plot plots the
-average domain size against time rescaled using $\tau_S$. We see that
+average domain size against time rescaled using $\tau_S$. The
 the domain sizes do not collapse onto a single line, which is expected
@@
 demonstrates the average domain size against time rescaled using
-$\tau_{\langle \psi \rangle}$. We see that there is good agreement
+$\tau_{\langle \psi \rangle}$. There is good agreement
 between all simulations for prolate particles, although the point when
 $\frac{t}{\tau_{\langle \psi \rangle}} = 1$ lies when the domain size
-transition has started. However for oblate particles we see that this
+transition has started. However for oblate particles this
 timescale does not describe the dynamics well.
@@
 The right plot demonstrates the domain size change after rescaling time
-with $\tau_{\langle Q6 \rangle}$ where we see good collapse between
-all plots while the domain size transition also begins at
+with $\tau_{\langle Q6 \rangle}$ all plots collapse onto a single line and 
+the domain size transition also begins at
 $\frac{t}{\tau_{\langle Q6 \rangle}} = 1$. The latter point
@@
 using the particle steric effects timescale, denoted by $\tau_{\langle Q6 \rangle}$,
-we conclude that the dynamics of bijels stabilized by ellipsoidal particles are controlled by
+I conclude that the dynamics of bijels stabilized by ellipsoidal particles are controlled by
 interfacial particle rearrangement at the interface.
@@
 type is what is observed for $\bar{B} = 0.2$, where the interfacial
-coverage and average orientation of the particle to the field and to the
+arrangement and orientation of the particle monolayer to the field and to the
 interface change in lock step. This causes the interface to reorient at
@@
 interface causes the interface to move to the particle position, causing
-domain coarsening as the interfacial area reduces.
+domain coarsening as the interfacial area reduces before rejamming reforms the bijel.
 
@@
 
-We saw in the hysteresis curve that the microstructure change at higher
+The hysteresis curve in Figured \ref{fig:hysteresis_curve} shiows that the microstructure change at higher
 field strengths began to reduce with each subsequent field strength
-jump, suggesting that the ordering of the particles were linked to the
-domain size change observed. In the previous section, we saw that domain
+jump, suggesting that the ordering of the particles is linked to the
+domain size change observed. In the previous section, I saw that domain
 size changes in bijels after jamming are constrained by magnetic field
 driven local rearrangement of the particle monolayer. In this section,
-we explore how pre-existing order in the particles affect the degree of
+I explore how pre-existing order in the particles affect the degree of
 domain size change observed. We apply fields of strength
-\(\bar{B}_{template} = 0, 0.2, 0.5, 1\) during phase separation to
+$\bar{B}_{template} = 0, 0.2, 0.5, 1$ during phase separation to
 create bijels stabilized with ellipsoidal particles with pre-existing
-particle order. We then apply a field strength of \(\bar{B}_z = 1\) and
-observe the time evolution of the system for \(t = 10^5\) timesteps. We
-simplify our nomenclature here demonstrated with an example.
-\(\bar{B}_z: 0.0 \rightarrow 1.0\) represents a bijel made with no
-field, and a field of \(\bar{B}_z = 1.0\) applied after the structure
-has reached steady state. We begin by visualizing the microstructure
+particle order. I then apply a field strength of $\bar{B}_z = 1$ and
+observe the time evolution of the system for $t = 10^5$ timesteps. I
+simplify my nomenclature here for brevity. For example,
+$\bar{B}_z: 0.0 \rightarrow 1.0$ represents a bijel made with no
+field, and a field of $\bar{B}_z = 1.0$ applied during the simulations conducted here. 
+I begin by visualizing the microstructure
 changes experienced by bijels simulated with pre-existing particle order
@@
 \caption{Visualizations of bijels stabilized with oblate and prolate particles simulated at $t = 0$ (left column) and $t = 10^5$ (right column). 
-The first and third rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids respectively with an applied field of $\bar{B}_z = 0.2$.
-The second and fourth rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids respectively with an applied field of $\bar{B}_z = 1$.
-We increase the applied field to $\bar{B}_z = 1$ in both cases and show that particle reorientation to the field occurs at the $\bar{B}_z = 0.2$ but not in the $\bar{B}_z = 1$ case.}
+         The first and third rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids respectively with an applied 
+         field of $\bar{B}_z = 0.2$. The second and fourth rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids 
+         respectively with an applied field of $\bar{B}_z = 1$. I increase the applied field to $\bar{B}_z = 1$ in both cases and show that particle 
+         reorientation to the field occurs at the $\bar{B}_z = 0.2$ but not in the $\bar{B}_z = 1$ case.}
 \label{fig:microstructure_viz-field_up}
@@
 
-In Figure \ref{fig:microstructure_viz-field_up} we show representative
+In Figure \ref{fig:microstructure_viz-field_up} I show representative
 snapshots of a bijel stabilized with prolate particles at the initial
 and final timestep with field conditions
-\(\bar{B}_z: 0.2 \rightarrow 1.0\) and
-\(\bar{B}_z: 1.0 \rightarrow 1.0\) in the top and bottom rows
-respectively. We show that upon application of the field, the fluid
+$\bar{B}_z: 0.2 \rightarrow 1.0$ and
+$\bar{B}_z: 1.0 \rightarrow 1.0$ in the top and bottom rows
+respectively. I show that upon application of the field, the fluid
 domains undergo a field strength dependent microstructrue response, with
 the degree of response dependent upon the difference between the initial
-and final magnetic field. We also observe a qualitative increase in the
+and final magnetic field. I also observe a qualitative increase in the
 alignment of the particles to the magnetic field for the
-\(\bar{B}_z: 0.2 \rightarrow 1.0\) case. We quantify these observations
+$\bar{B}_z: 0.2 \rightarrow 1.0$ case. I quantify these observations
 by plotting the average domain size and nematic order parameter in
@@
 \caption{Plot of the spherically averaged domain size normalized with $Rp(L/R)$ of the particle in markers and the nematic order parameter in lines. 
-We show that the domain size change measured is correlated to the change in the particle ordering, characterized using the nematic order parameter.}
+         I show that the domain size change measured is correlated to the change in the particle ordering, characterized using the nematic order parameter.} 
 \label{fig:domain_size-field_up} 
@@
 
-In Figure \ref{fig:domain_size-field_up}, we define the difference
+In Figure \ref{fig:domain_size-field_up}, I define the difference
 between the final and initial magnetic field strengths as
-\(\Delta \bar{B}\). The onset of microstructural response is observed to
-be \(\Delta \bar{B}\)-dependent, indicating that a stronger driving
+$\Delta \bar{B}$. The onset of microstructural response is observed to
+be $\Delta \bar{B}$-dependent, indicating that a stronger driving
 force is required to induce structural reorganization. Additionally, the
 extent of microstructural change is also correlated with
-\(\Delta \bar{B}\), where \(\Delta \bar{B} = 1\) results in average
+$\Delta \bar{B}$, where $\Delta \bar{B} = 1$ results in average
 microstructural variations of 5\% and 2\% for oblate and prolate
-particles, respectively which decreases as \(\Delta \bar{B}\) decreases.
-We further characterize the relationship between \(\Delta \bar{B}\) and
+particles, respectively which decreases as $\Delta \bar{B}$ decreases.
+We further characterize the relationship between $\Delta \bar{B}$ and
 nematic order, showing that an increase in \(S\) correlates with
-\(\Delta \bar{B}\). This suggests that changes in domain size are
+$\Delta \bar{B}$. This suggests that changes in domain size are
 intrinsically linked to the initial particle ordering within the system.
@@
 coarsening dynamics. To further quantify the anisotropic microstructural
-evolution, we define the relative change in domain size as
-\(\Delta L = \frac{L_{f} - L_{i}}{L_{i}}\), where \(L\) represents
-either \(L_{\perp}\) or \(L_{\parallel}\). The same formulation is
-applied to the tortuosity in the respective directional components. We
-do this to characterize the \(\Delta \bar{B}\)-dependent changes
+evolution, I define the relative change in domain size as
+$\Delta L = \frac{L_{f} - L_{i}}{L_{i}}$, where $L$ represents
+either $L_{\perp}$ or $L_{\parallel}$. The same formulation is
+applied to the tortuosity in the respective directional components. I
+do this to characterize the $\Delta \bar{B}$-dependent changes
 observed in the domain anisotropy. The results are presented in Figure
@@
 \includegraphics[scale = 0.5]{../figures/results/paper2/domain_size_aniso-field_up.png} 
-\caption{Plotting the anisotropic domain sizes and tortuosity at the final timestep on the left and right respectively for bijels stabilized with oblate and prolate ellipsoidal particles starting at different particle orders.
-We plot these results against the change in the applied field strength, $\Delta B$.
-We show that the anisotropic domain size is inversely correlated to the tortuosity.
-We see that $L_{perp}$ changes for a bijel made with $\bar{B} = 1 \rightarrow 1$ and $\bar{B}: 0 \rightarrow 1$ differ, suggesting that the processing history of the bijel is important.}
+\caption{Plotting the anisotropic domain sizes and tortuosity at the final timestep on the left and right respectively for bijels stabilized with 
+         oblate and prolate ellipsoidal particles starting at different particle orders. I plot these results against the change in the applied field 
+         strength, $\Delta B$. We show that the anisotropic domain size is inversely correlated to the tortuosity. We see that $L_{perp}$ changes for 
+         a bijel made with $\bar{B} = 1 \rightarrow 1$ and $\bar{B}: 0 \rightarrow 1$ differ, suggesting that the processing history of the bijel is important.} 
 \label{fig:domain_size_aniso-field_up} 
@@
 
-In Figure \ref{fig:domain_size_aniso-field_up}, we see that an increase
-in the directional domain size corresponds to a decrease in the
-tortuosity of the material. We also observe a magnetic field dependence
-of each parameter, demonstrating that the difference in the initial and
-final magnetic field applied is correlated with the domain size change
-observed. Another insight is that the runs \(\bar{B}: 0 \rightarrow 1\)
-and \(\bar{B}: 1 \rightarrow 1\) have different microstructural
-properties. This suggests that the processing history of a bijel is
-important when deciding what morphology functions ideally in a desired
-application. As in above, we turn to look at the properties of the
-particle monolayer. We begin by visualizing the particle monolayer in
-Figure \ref{fig:particle_viz-field_up}.
-
 From Figure \ref{fig:domain_size_aniso-field_up}, we see that domain
 size anisotropy is observed upon increasing the applied field
-application of the field for both particle morphologies. We also see
+application of the field for both particle morphologies. I also see
 some domain anisotropy with no applied field, which increases upon
 application of the magnetic field. The directional domain sizes,
-\(L_{\perp}\) and \(L_{\parallel}\) increase by \(73\%\) and \(7\%\)
-respectively for oblate particles and \(10\%\) and \(44\%\) respectively
+$L_{\perp}$ and $L_{\parallel}$ increase by $73\%$ and $7\%$
+respectively for oblate particles and $10\%$ and $44\%$ respectively
 for prolate particles. The axes that coarsens the most is consistent
 with past work, explained through the directions particles reorient in
-response to the applied magnetic field. In Figure
-\ref{fig:domain_size_aniso-field_on}, we demonstrate that the
-application of the magnetic field changes the domain size. The
-tortuosity of the bijel is initially around \(\tau \approx 1.5\),
+response to the applied magnetic field. The
+tortuosity of the bijel is initially around $\tau \approx 1.5$,
 consistent with simulations of the diffusive tortuosities of gyroid
@@
 \cite{luo_macroscopic_2020} Upon application of the field,
-\(\tau_{\perp}\) slightly decreases while \(\tau_{\parallel}\)
-increases. We have seen that an increasing domain size decreases the
-tortuosity in our past work. \cite{karthikeyan_formation_2024} This
-observation is in line with the domain size changes observed in Figure
-\ref{fig:domain_size_aniso-field_on}. The results show that the
+$\tau_{\perp}$ slightly decreases while $\tau_{\parallel}$
+increases. Consistent with past work, an increase in the domain size sees a decrease in
+tortuosity in that direction. \cite{karthikeyan_formation_2024}. The results show that the
 tortuosity of the bijel is noticeably affected by the application of
@@
 prolate particles. To characterize how the particle order changes on the
-interface as a function of the magnetic field strength, we visualize the
+interface as a function of the magnetic field strength, I visualize the
 particle monolayer of bijels stabilized by prolate particles in Figure
@@
 \caption{Visualizations of bijels stabilized with oblate and prolate particles simulated at $t = 0$ (left column) and $t = 10^5$ (right column). 
-The first and third rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids respectively with an applied field of $\bar{B}_z = 0.2$.
-The second and fourth rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids respectively with an applied field of $\bar{B}_z = 1$.
-We increase the applied field to $\bar{B}_z = 1$ in both cases and show that particle reorientation to the field occurs at the $\bar{B}_z = 0.2$ but not in the $\bar{B}_z = 1$ case.}
+         The first and third rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids respectively with an applied 
+         field of $\bar{B}_z = 0.2$. The second and fourth rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids 
+         respectively with an applied field of $\bar{B}_z = 1$. I increase the applied field to $\bar{B}_z = 1$ in both cases and show that particle 
+         reorientation to the field occurs at the $\bar{B}_z = 0.2$ but not in the $\bar{B}_z = 1$ case.} 
 \label{fig:particle_viz-field_up} 
@@
 
-In Figure \ref{fig:particle_viz-field_up}, we see the effect of the
+In Figure \ref{fig:particle_viz-field_up}, I see the effect of the
 application of the magnetic field on the monolayer. The initial
 configuration of particles at the monolayer show that even at initial
-configuration of run \(\bar{B}: 0.2 \rightarrow 1\), most particles are
+configuration of run $\bar{B}: 0.2 \rightarrow 1$, most particles are
 oriented towards the field. Upon increasing the field strength to
-\(\bar{B} = 1\), all particles shown can be seen to be ordered to the
+$\bar{B} = 1$, all particles shown can be seen to be ordered to the
 field, matching the results for the nematic order parameter shown in
@@
 origin of the microstructure anisotropy. To understand how the particle
-reorientation at the interface causes microstructure reorientation we
+reorientation at the interface causes microstructure reorientation I
 quantify the average interface angle, $\langle \psi \rangle$ and the
@@
 \includegraphics[scale=0.4]{../figures/results/paper2/interface_angle-nint-field_up.png} 
-\caption{Plots of the average interfacial angle $\psi$ and the number of particles on the interface $n_{int}$ on the left and right respectively, plotted against time for bijels stabilized with ellipsoidal particles with aspect ratio 2.
-When looking at $\psi$, a change in dynamics can be seen as the initial particle order increases.
-When looking at $n_{int}$, different dynamics are seen above and below the isotropic to nematic transition point.
+\caption{Plots of the average interfacial angle $\psi$ and the number of particles on the interface $n_{int}$ on the left and right respectively, 
+         plotted against time for bijels stabilized with ellipsoidal particles with aspect ratio 2. When looking at $\psi$, a change in dynamics can be 
+         seen as the initial particle order increases. When looking at $n_{int}$, different dynamics are seen above and below the isotropic to nematic transition point. 
          Both results suggest that the ordering of particles is linked to the dynamics of domain coarsening.} 
@@
 
-From Figure \ref{fig:interface_angle-nint-field_up}, we identify that
-prolate and oblate particles respond differently at the interface. We
+Figure \ref{fig:interface_angle-nint-field_up} shows that
+prolate and oblate particles respond differently at the interface upon application of a magnetic field
+even with pre-existing ordering of the particles. I
 show that there are three time evolution trends for
@@
 particles. In oblate particles $\langle \psi \rangle$ begins closer to
-\(0 ^{\circ}\) as the axis of symmetry lies close to the interface
-normal. We see that for bijels experiencing a field strength history of
-\(\bar{B}: 0 \rightarrow 1\) and \(\bar{B}: 0.2 \rightarrow 1\),
+$20 ^{\circ}$ as the axis of symmetry lies close to the interface
+normal. For bijels experiencing a field strength history of
+$\bar{B}: 0 \rightarrow 1$ and $\bar{B}: 0.2 \rightarrow 1$,
 $\langle \psi \rangle$ increases, plateaus and increases again before
@@
 stabilized by prolate particles. $\langle \psi \rangle$ begins near
-\(80 ^{\circ}\). We see a decrease before reorientation ceases, and
+$11 ^{\circ}$. We see a decrease before reorientation ceases, and
 finally $\langle \psi \rangle$ increases again.
 
-When looking at $\langle Q6 \rangle$ for \(\bar{B}: 0 \rightarrow 1\)
-and \(\bar{B}: 0.2 \rightarrow 1\) for oblate particles, we see that the
+When looking at $\langle Q6 \rangle$ for $\bar{B}: 0 \rightarrow 1$
+and $\bar{B}: 0.2 \rightarrow 1$ for oblate particles, we see that the
 trends are similar with an initial decrease, followed by a plateau and
@@
 \(\bar{B}: 0 \rightarrow 1\) from an initial hexagonally packed system
-to a structure that is locally ordered but not close packed. For prolate
-particles, we see an increase in $\langle Q6 \rangle$ with a plateau
-occurring in both systems around 5000 timesteps. The significance of
-this time is unknown for \(\bar{B}: 0.2 \rightarrow 1\) but for
-\(\bar{B}: 1 \rightarrow 1\), this is approximately the local
-crystallization point when \(\langle Q6 \rangle \geq 0.38\).
+to a structure that is locally ordered but not close packed. $\langle Q6 \rangle$ increases before plateauing 
+in both systems around 5000 timesteps. The significance of
+this time is unknown for $\bar{B}: 0.2 \rightarrow 1$ but for
+$\bar{B}: 1 \rightarrow 1$, this is approximately the local
+crystallization point when $\langle Q6 \rangle \geq 0.38$.
 
-For oblate particles, we can conclude that structural response dynamics
+For oblate particles, structural response dynamics
 arise from particle tilting on the interface identified as the large
@@
 an associated decrease in the interface coverage, initiating domain
-coarsening. We see that this interfacial tilting causes a loss in the
+coarsening. Interfacial tilting causes a loss in the
 close packing of oblate particles at the interface. For prolate
-particles, we observe a small degree of particle tilting as can be seen
-from $\langle \psi \rangle$, although the dynamics are primarily
-driven by the change in $\langle Q6 \rangle$, indicated as a slight
-dip and plateau before the particles begin reordering and packing more
-tightly, decreasing the interfacial area. Larger domain size response is
-observed for the prolate particles as the interfacial area change from
+particles, a small degree of particle tilting can be seen
+from $\langle \psi \rangle$, although an increase in $\langle Q6 \rangle$ is observed
+decreasing the interfacial area. Larger domain size response is
+observed for the oblate particles as the interfacial area change from
 particle tilting at the interface is larger than that of particles close
@@
 
-For both particle morphologies we analyze the response of bijels with a
-field history of \(\bar{B}: 0.5 \rightarrow 1\) and
-\(\bar{B}: 1 \rightarrow 1\). We see a decrease in
+For both particle morphologies I analyze the response of bijels with a
+field history of $\bar{B}: 0.5 \rightarrow 1$ and
+$\bar{B}: 1 \rightarrow 1$. We see a decrease in
 $\langle Q6 \rangle$ for bijels stabilized with oblate particles with
-field application of \(\bar{B}: 0.5 \rightarrow 1\) compared to an
-increase for \(\bar{B}: 1 \rightarrow 1\). This behavior arises from the
+field application of $\bar{B}: 0.5 \rightarrow 1$ compared to an
+increase for $\bar{B}: 1 \rightarrow 1$. This behavior arises from the
 slight increase in the nematic order for particles in bijels
-experiencing the \(\bar{B}: 0.5 \rightarrow 1\) field application
+experiencing the $\bar{B}: 0.5 \rightarrow 1$ field application
 history. The $\langle \psi \rangle$ results indicate that the
 particles rearrange over time to lie flatter on the interface. For
-bijels stabilized with prolate particles, we characterize a difference
-in behavior between \(\bar{B}: 0.5 \rightarrow 1\) and
-\(\bar{B}: 1 \rightarrow 1\). For the \(\bar{B}: 0.5 \rightarrow 1\)
+bijels stabilized with prolate particles, I characterize a difference
+in behavior between $\bar{B}: 0.5 \rightarrow 1$ and
+$\bar{B}: 1 \rightarrow 1$. For the $\bar{B}: 0.5 \rightarrow 1$
 case, we see a slight increase in $\langle \psi \rangle$ before a
-decrease and increase compared to the \(\bar{B}: 1 \rightarrow 1\) case
-where we characterize a slight decrease over time. We also characterize
+decrease and increase compared to the $\bar{B}: 1 \rightarrow 1$ case
+where we characterize a slight decrease over time. I also characterize
 a slight decrease in $\langle Q6 \rangle$ over time for the
-\(\bar{B}: 1 \rightarrow 1\) case while characterizing a larger decrease
-for the \(\bar{B}: 0.5 \rightarrow 1\) case. Similar to the oblate
+$\bar{B}: 1 \rightarrow 1$ case while characterizing a larger decrease
+for the $\bar{B}: 0.5 \rightarrow 1$ case. Similar to the oblate
 particles, these results originate from the slight increase in the
-nematic order for bijels experiencing the \(\bar{B}: 0.5 \rightarrow 1\)
+nematic order for bijels experiencing the $\bar{B}: 0.5 \rightarrow 1$
 field history.
@@
 emulsions have demonstrated resilience to microstructure changes after
-application and removal of stimuli even after several months. However,
+application and removal of stimuli even after several months. \cite{cui_stabilizing_2013} However,
 in the systems simulated above the particles need not necessarily be in
@@
 the particles take up a arrangements not observed when no field is
-applied. In this section, we explore how removal of the magnetic field
+applied. In this section, I explore how removal of the magnetic field
 changes the microstructure of the bijel as a function of the initial
 particle order. We use bijels simulated under
-\(\bar{B}_{template} = 0, 0.2, 0.5, 1\) during phase separation. Once
-the microstructure has stabilized, we switch off the magnetic field and
-observe the time evolution of the system for \(t = 10^5\) timesteps.
+$\bar{B}_{template} = 0, 0.2, 0.5, 1$ during formation of the bijel. Once
+the microstructure has stabilized, I switch off the magnetic field and
+observe the time evolution of the system for $t = 10^5$ timesteps.
 
@@
 \caption{Visualizations of bijels stabilized with oblate and prolate particles simulated at $t = 0$ (left column) and $t = 10^5$ (right column). 
-The first and third rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids respectively with an applied field of $\bar{B}_z = 0.2$.
-The second and fourth rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids respectively with an applied field of $\bar{B}_z = 1$.
-We switch off the applied field in both cases and show that while particle reorientation occurs, it has little effect on the microstructure of the bijel.}
+         The first and third rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids respectively with an applied 
+         field of $\bar{B}_z = 0.2$. The second and fourth rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids 
+         respectively with an applied field of $\bar{B}_z = 1$. I switch off the applied field in both cases and show that while particle reorientation 
+         occurs, it has little effect on the microstructure of the bijel.}
 \label{fig:microstructure_viz-field_down}
@@
 evolution of the microstructure of bijels with processing history
-\(\bar{B}:0.2 \rightarrow 0\) (top) and \(\bar{B}:1 \rightarrow 0\)
+$\bar{B}:0.2 \rightarrow 0$ (top) and $\bar{B}:1 \rightarrow 0$
 (bottom). We see that when switching the field off, the microstructure
@@
 randomly oriented. This is especially obvious in the
-\(\bar{B}:1 \rightarrow 0\) process, demonstrating that the dynamics of
+$\bar{B}:1 \rightarrow 0$ process, demonstrating that the dynamics of
 the system is dependent upon the initial order of the particle
@@
 \caption{Plot of the spherically averaged domain size normalized with $R_p$ of the particle and the nematic order parameter of each bijel over time. 
-Each color represents bijel templates made with different field strengths $\bar{B}$.
-We show that there is domain coarsening when the field is switched off, along with a reduction in the ordering of the particles.}
+         Each color represents bijel templates made with different field strengths $\bar{B}$. We show that there is domain coarsening when the field 
+         is switched off, along with a reduction in the ordering of the particles.} 
 \label{fig:domain_size-field_down} 
@@
 
-From the results in \ref{fig:domain_size-field_down}, we can see that
-the results show, with the exception of \(\bar{B}: 0\rightarrow 0\), all
+The results in \ref{fig:domain_size-field_down}, show with the exception of $\bar{B}:0\rightarrow0$, all
 domain sizes show a slow coarsening over time. This is reflected clearly
@@
 magnetic field during bijel template simulation does not play a
-significant role in the dynamics of the bijel. We attribute the large
+significant role in the dynamics of the bijel. I attribute the large
 increase in the domain size in oblate particle stabilized
-\(\bar{B}: 0\rightarrow 0\) case to be due to coalescence of two
+$\bar{B}:0\rightarrow0$ case to be due to coalescence of two
 domains, characterized as a two step process where we see slower long
@@
 the interface. To quantify is the coarsening that takes place is
-anisotropic, we define the relative change in domain size as
-\(\Delta L = \frac{L_{f} - L_{i}}{L_{i}}\), where \(L\) represents
-either \(L_{\perp}\) or \(L_{\parallel}\). The same formulation is
-applied to the tortuosity in the respective directional components. We
-do this to characterize the \(\Delta \bar{B}\)-dependent changes
+anisotropic, I define the relative change in domain size as
+$\Delta L = \frac{L_{f} - L_{i}}{L_{i}}$, where $L$ represents
+either $L_{\perp}$ or $L_{\parallel}$. The same formulation is
+applied to the tortuosity in the respective directional components. I
+do this to characterize the $\Delta \bar{B}$ dependent changes
 observed in the domain anisotropy. The results are presented in Figure
@@
 \includegraphics[scale = 0.5]{../figures/results/paper2/domain_size_aniso-field_down.png} 
-\caption{Plotting the anisotropic domain sizes and tortuosity at the final timestep on the left and right respectively for bijels stabilized with oblate and prolate ellipsoidal particles starting at different particle orders.
-We plot these results against the change in the applied field strength, $\Delta B$.
-We show that there are only minor differences in the microstructure of stimuli responsive bijels once the magnetic field is switched off.}
+\caption{Plotting the anisotropic domain sizes and tortuosity at the final timestep on the left and right respectively for bijels stabilized with oblate and 
+         prolate ellipsoidal particles starting at different particle orders. We plot these results against the change in the applied field strength, 
+         $\Delta B$. I show that there are only minor differences in the microstructure of stimuli responsive bijels once the magnetic field is switched off.} 
 \label{fig:domain_size_aniso-field_down} 
@@
 
-In Figure \ref{fig:domain_size_aniso-field_down}, we see that there are
-small \(\Delta \bar{B}\) dependent changes in the anisotropic domain
+Figure \ref{fig:domain_size_aniso-field_down}, shows that there are
+small $\Delta \bar{B}$ dependent changes in the anisotropic domain
 size and tortuosity for both particle morphologies. However, there are
@@
 dependent upon the capillary interactions with the particle monolayer.
-We showed earlier that the application of magnetic fields change the
+I showed earlier that the application of magnetic fields change the
 local state of the particles at the interface. However the results shown
@@
 \includegraphics[scale=0.4]{../figures/results/paper2/interface_angle-nint-field_down.png} 
-\caption{Plots of the average interfacial angle $\psi$ and the number of particles on the interface $n_{int}$ on the left and right respectively, plotted against time for bijels stabilized with ellipsoidal particles with aspect ratio 2.
-When looking at $\psi$, the $\bar{B}:1 \rightarrow 1$ case looks distinctly different from the other processes.
-At $\bar{B} = 1$, the particles are totally ordered to the field.
-This suggests that the presence of some particle disorder resists domain coarsening.}
+\caption{Plots of the average interfacial angle $\psi$ and the number of particles on the interface $n_{int}$ on the left and right respectively, 
+         plotted against time for bijels stabilized with ellipsoidal particles with aspect ratio 2. When looking at $\psi$, the $\bar{B}:1 \rightarrow 1$ 
+         case looks distinctly different from the other processes. At $\bar{B} = 1$, the particles are totally ordered to the field. This suggests that 
+         the presence of some particle disorder resists domain coarsening.} 
 \label{fig:interface_angle-field_down} 
@@
 
-In Figure \ref{fig:interface_angle-field_down}, we plot
-$\langle \psi \rangle$ and $\langle Q6 \rangle$ in the left and
-right columns respectively. While there are minor differences to the
-time when $\langle \psi \rangle$ and $\langle Q6 \rangle$ increase
-and decrease respectively for bijels stabilized by oblate particles the
-trends are identical. This suggests that the differences in particle
-angle, local ordering and nematic order only change when coarsening will
-take place without affecting its dynamics.
+From Figure \ref{fig:interface_angle-field_down}, there are minor differences to the time when $\langle \psi \rangle$ and $\langle Q6 \rangle$
+begin to change. I also characerize that $\langle \psi \rangle$ increases for both particle morphologies, even for systems that have initial ordering.
+Similarly, $\langle Q6 \rangle$ decreases for all systems. Thus, the presence of ordering does not greatly affect trends in the evolution of the
+particle monolayer, and thus has an insignificant effect on the microstructure of the bijel.
 
-For prolate particles, we see that a reduction in
-$\langle \psi \rangle$ takes place for all runs except for
-\(\bar{B}: 0.5\rightarrow 0\). This is attributed to be due to this
-system being near its preferred interface angle, with changes occurring
-as the particles reorient away from the magnetic field causing
-deviations before returning to that angle. We see that the
-\(\bar{B}: 1\rightarrow 0\) case also reaches approximately the same
-value for $\langle \psi \rangle$. \(\bar{B}: 0.2\rightarrow 0\) and
-\(\bar{B}: 0\rightarrow 0\) reduce much more slowly than
-\(\bar{B}: 1\rightarrow 0\). This suggests that local reorientation is
-occurring, although its affects manifest as insignificant changes in the
-microstructure of the material.
-
-Looking at $\langle Q6 \rangle$, we see that all simulations see a
-decrease over time. We see that contrary to previous trends, the
-\(\bar{B}: 1\rightarrow 0\) simulation has a smaller change in
-$\langle Q6 \rangle$ than \(\bar{B}: 0.5\rightarrow 0\) although this
-difference is also a result of the initial particle orientation and
-position, rather than a defining feature of a broader trend. We see that
-the \(\bar{B}: 0.5\rightarrow 0\) case is near the
-\(Q6^{HCP} \approx 0.485\) boundary, suggesting it is most susceptible
-to lose short range order upon removal of the magnetic field that
-enforces it, resulting in the large decrease in $\langle Q6 \rangle$
-observed.
-
-We see from the microstructure evolution that steric effects are the
+From the microstructure evolution, steric effects are the
 driving force behind microstructure changes in the absence of a magnetic
-field. Even though we observe that the interface angle and Steinhardt
+field. Even though I observe that the interface angle and Steinhardt
 order parameter show substantial changes from the scenario where no
@@
 effect driven particle monolayer rearrangement observed, causing
-coarsening of the bijel at long timescales similar what was observed by
-Gunther et al.~\cite{gunther_timescales_2014}
+coarsening of the bijel at long timescales to possess trends similar to what was observed by
+Gunther et al. \cite{gunther_timescales_2014}
+
+In this chapter, I identified that bijels stabilized by magnetically responsive particles exhibit microstructural hysteresis upon the application and removal of a 
+magnetic field. This hysteresis is characterized by the ability to alter microstructure when increasing the applied field, but an inability to do so when switching 
+the field off. When examining the effect of an applied magnetic field on domain size evolution in bijels initially lacking particle ordering, I found that domain 
+size changes correlate with field strength and are accompanied by microstructural anisotropy.
+By analyzing response timescales, I determined that the structural evolution arises primarily from particle reorientation at the interface. I then investigated 
+how the initial particle order in the direction of the magnetic field influences the response and found that the magnitude of the observed response depends on 
+the difference between the initial and final states of the particle monolayer. A closer examination of the monolayer revealed that many characteristic behaviors 
+observed in initially disordered systems were absent, indicating a distinct response mechanism.
+Finally, I explored why pre-existing particle order at the interface did not lead to different microstructural behavior upon field removal. I demonstrated that under 
+the given system parameters, the evolution of the particle monolayer was identical in all cases, suggesting that interface dynamics are governed by particle rearrangements 
+aimed at minimizing interfacial energy.

### 2025-03-20 chapters/final_remarks.tex
Changes 1. Updated aim 1 with first person wording 2. Updated aim 2 with first person wording and modified conclusion 3. Updated aim 3 with full size conclusion

@@
 Colloidal systems made with cohesive and soft particles have been shown in the literature to have different glass 
-transition points and rheological behavior from their hard sphere counterparts. In bijels, cohesive particles in 
+transition points and rheological behavior from their hard sphere counterparts. In bijels, attractive particles in 
 particular have been suggested as a means to create "armored" bijels to improve their performance in catalytic materials, 
-allowing higher flow rates to be used. Investigations into soft particles are of interest in biomedical engineering 
+allowing higher flow rates to be used. Investigations into soft particles are of interest in biomedical
 applications, with newly developed nanogels and hydrogels being suggested as drug carriers or vectors for stimuli 

### 2025-03-20 chapters/paper1.tex
Changes 1. Updated aim 1 with first person wording 2. Updated aim 2 with first person wording and modified conclusion 3. Updated aim 3 with full size conclusion

@@
 
-In this chapter, we investigate the effect of external magnetic fields on the formation of bijels stabilized by 
+In this chapter, I investigate the effect of external magnetic fields on the formation of bijels stabilized by 
 anisotropic magnetic particles. The microstructure of bijels stabilized with oblate, spherical and prolate particles, 
 namely the characteristic length scale and tortuosity, will be assessed as a function of the applied magnetic field
-strength. We also characterize the underlying mechanisms governing the observed behavior.
+strength. I also characterize the underlying mechanisms governing the observed behavior.
 
@@
 tortuosity of the void space and can be linked to the phase-separated
-morphology of the bijel template. Therefore, we study the domain size
+morphology of the bijel template. Therefore, I study the domain size
 and tortuosity of the phase morphology of bijels stabilized by
-anisotropic particles. In particular, we investigate the effect of
+anisotropic particles. In particular, I investigate the effect of
 magnetic particles on the microstructure of bijels that are formed in
-external magnetic fields. We simulated bijels with a particle volume
+external magnetic fields. I simulated bijels with a particle volume
 fraction of \(\phi_p=0.15\) and varied the magnetic flux density such
 that the Bond numbers varies in the range \(0\le\bar{B}\le1\).
-In this work, we use a fixed particle volume fraction and focus on the dependence of the 
+In this work, I use a fixed particle volume fraction and focus on the dependence of the 
 bijel structure on the magnetic field. Bijels with varying particle loading and surface tension 
@@
 domain size observed visually in snapshots such as those shown in Fig.~\ref{fig:microstructure_viz}. However, in a dynamic
-scaling regime, different measures of domain size are expected to differ only by a constant ratio. We found that the commonly 
+scaling regime, different measures of domain size are expected to differ only by a constant ratio. I found that the commonly 
 used measure \(L_1(t)\) tends to overestimate the observed domain size. Numerically, the calculation of the spherically 
@@
 periodic boundary conditions is subject to finite size effects. More importantly, in suspensions of anisotropic particles, 
-we cannot expect that the structure factor is isotropic. Therefore, we also used the 3D structure factor to calculate a lateral domain 
+I cannot expect that the structure factor is isotropic. Therefore, I also used the 3D structure factor to calculate a lateral domain 
 size in each Cartesian direction from the second moments also defined in Section \ref{section:domain_size}. 
-\cite{jansen_bijels_2011,gunther_timescales_2014} We add the additional processing calculating a parallel and perpendicular domain size
-from the results in each cartesian direction, defining $L_{\parallel}=L_z$ and $L_{\perp} = \frac{L_x+L_y}{2}$
-
-Before calculating the structure factor \(S(\vec{k},t)\), we first filled the lattice sites covered by particles with the average
-density at the surrounding lattice sites as detailed in Section \ref{section:filling_routine}. We plot the structure factor of the structures in
+\cite{jansen_bijels_2011,gunther_timescales_2014} I add the additional processing calculating a parallel and perpendicular domain size
+from the results in each cartesian direction, defining $L_{\parallel}=L_z$ and $L_{\perp} = \frac{L_x+L_y}{2}$ I plot the structure factor of the structures in
 Figure \ref{fig:structure_factor}.
@@
     \caption{Scaling plot of the dynamic structure factor $S(k,t)$ for different particle shapes $\alpha$ and at different 
-            magnetic field strength $\bar{B}$.
-The structure factor is plotted at four different timesteps for each case.
-The good data collapse shows that the bijel formation is driven by spinodal decomposition.
-The decay to the right of the peak is reasonably well described by Porod's law $S(k)\sim k^{-4}$.}
+            magnetic field strength $\bar{B}$. The structure factor is plotted at four different timesteps for each case. The good data collapse shows that the 
+            bijel formation is driven by spinodal decomposition. The decay to the right of the peak is reasonably well described by Porod's law $S(k)\sim k^{-4}$.}
     \label{fig:structure_factor}
@@
 \includegraphics[width=\textwidth]{figures/results/paper1/domain_size.png}
-\caption{Time dependence of the average domain size of the bijel for different particles shapes $\alpha$ and at different magnetic field strength $\bar{B}$.
-$L_1$ denotes the domain size obtained from the first moment of the spherical average structure factor, and $L_d$ denotes the domain size obtained from the second moment of the 3D structure factor.
-The increase roughly follows a $\sim t^{2/3}$ scaling law indicative of the inertial regime of spinodal decomposition.}
+\caption{Time dependence of the average domain size of the bijel for different particles shapes $\alpha$ and at different magnetic 
+         field strength $\bar{B}$. $L_1$ denotes the domain size obtained from the first moment of the spherical average structure 
+         factor, and $L_d$ denotes the domain size obtained from the second moment of the 3D structure factor. The increase roughly 
+         follows a $\sim t^{2/3}$ scaling law indicative of the inertial regime of spinodal decomposition.}
 \label{fig:domain_size}
@@
 \ref{fig:domain_size} suggests that the domain size is not strongly
-affected by the external magnetic field. In Fig.\ref{fig:D2a_B}a) we
+affected by the external magnetic field. In Fig.\ref{fig:D2a_B}a) I
 plotted the domain size measure \(L_d\) normalized by \(R\), the larger
@@
 volume. Furthermore, steric constraints prevent anisotropic particles to
-pack less densely in the interface than spherical particles, as we will
+pack less densely in the interface than spherical particles, as I will
 discuss in more detail below.
@@
 The magnetic field does have an effect on the directional
-domain size as shown in Figure \ref{fig:D2a_B} where we plotted the
+domain size as shown in Figure \ref{fig:D2a_B} where I plotted the
 domain size in the direction parallel and perpendicular to \(\vec{B}\)
-separately. We find that for prolate particles, the domain size in the
+separately. I find that for prolate particles, the domain size in the
 parallel direction increases with the field strength up to approximately
@@
 cross-section of prolate particles while \(\vec{m}\) is perpendicular to
-the larger cross-section of oblate particles. We thus expect that
+the larger cross-section of oblate particles. I thus expect that
 alignment of the particles with the magnetic field \(\vec{B}\)
@@
 whether these structural changes have an effect on macroscopic
-transport properties, we also characterized the tortuosity of the
+transport properties, I also characterized the tortuosity of the
 bijels. Various definitions of tortuosity have been proposed in the
 literature \cite{dasilva_tortuosity_2022}, including geometric,
-diffusional, and hydraulic tortuosity. Here we use the diffusional
+diffusional, and hydraulic tortuosity. Here I use the diffusional
 tortuosity $\tau= \frac{\epsilon D}{D_{\text{eff}}}$, i.e., the ratio of the 
 effective diffusivity $D_{\text{eff}}$ and the intrinsic diffusivity
-$D$. We calculate the tortuosity using the procedure detailed in Section \ref{section:tortuosity}
+$D$. I calculate the tortuosity using the procedure detailed in Section \ref{section:tortuosity}
 
@@
 this direction. The results show that the magnetic field has a
-noticeable effect on the tortuosity of the bijel. We observe that the
+noticeable effect on the tortuosity of the bijel. I observe that the
 largest change of tortuosity is measured at intermediate field strength
@@
 domains induces morphological changes that are more complex than a
-monotonic increase or decrease. We therefore turn to investigate the
+monotonic increase or decrease. I therefore turn to investigate the
 microstructural changes within the bijel morphology in more detail.
@@
 Beyond the length scale, curvature analysis offers insights into the
-local topological landscape of the bijel, facilitating further
+topological landscape of the bijel, facilitating further
 microstructure optimization for various applications.
-\cite{reeves_quantitative_2016} We plot the area averaged mean and
+\cite{reeves_quantitative_2016} I plot the area averaged mean and
 gaussian curvature \(H\Sigma^{-1}\) and \(K\Sigma^{-2}\) for bijels
-stabilized with oblate, spherical and prolate ellipsoids in Figure
+stabilized with oblate, spherical and prolate ellipsoids at the final timestep in Figure
 \ref{fig:curvature-vs-B_ss}.
@@
             at the final timestep averaged across 3 runs for particles with $\alpha = 0.5, 1, 2$. 
-            We observe that the mean curvature does not demonstrate any trends, while the Gaussian 
+            The mean curvature remains 0 on average, while the Gaussian 
             curvature shows a reduction as the magnetic field strength is increased for 
@@
 ellipsoidal particles, the gaussian curvature becomes more negative as
-larger field strengths are applied. We also see that the gaussian
+larger field strengths are applied. I also see that the gaussian
 curvature becomes more positive as the interfacial area of the particle
@@
 
-Reeves and coworkers identified that nanoparticles were better able to
-lock in the spinodal structure of the liquid-liquid phase separation as
-they were less disruptive the the curvature of the interface due to
-their lower interfacial adsorption energy. This effect can be observed
-as a more negative Gaussian curvature as a result of the greater number
-of hyperbolic surfaces, a hallmark of a minimal surface. In our system,
-the oblate and prolate particles have 60\% and 30\% more interfacial
-area than the spherical particles, resulting in the ellipsoidal
-particles being more disruptive to the curvature of the interface,
-observed as a more positive Gaussian curvature. As the magnetic field
-strength is increased, the packing of the particles at the interface
-changes, as observed from the radial distribution function.
-\cite{karthikeyan_formation_2024} These changes in particle packing
-change the way the particles affect the curvature of the interface,
-resulting in the curvature changes observed. To investigate the field
-dependence on the curvature, we plot the area averaged Gaussian
-curvature as a function of time.
+To explain the reduction in $\langle K\Sigma^{-2} \rangle$ as a function of the applied field strength, two mechanisms are proposed. The first is that 
+the particle alignment to the magnetic field during coarsening changes the topology of the surface, which upon jamming of ellipsoidal particles is locked in. 
+The other proposed mechanism is that the time evolution of spinodal decomposition remains unaffected, but that the interface conforms to the magnetic field 
+driven arrangement of particles upon jamming. While I cannot apply the Gauss Bonnet theorem to characterize the results, I can still relate the coarsening 
+behavior of the bijel through its change in genus to the curvature. The time evolution of the genus serves as a topological technique to characterize the 
+coarsening of the bijel, which alongside the $\langle K\Sigma^{-2} \rangle$, allows us to identify deviations from the coarsening behavior of bijels 
+stabilized with spherical particles, and with magnetic fields. I calculate the genus by extracting the isosurface of the filled order parameter, where 
+$\phi = 0$. It is then meshed using the marching cubes algorithm implemented in scikit-image with a cube size of 1. \cite{van2014scikit} From the vertices(v) 
+and faces(f) generated from the marching cubes algorithm, I calculate the number of edges(e). The Euler Poincare characteristic, $\chi = n + f - e$. The genus is 
+then obtained from the Euler Poincare parameter as $g = 1 - \chi/2$.
 
@@
     \caption{Plots of Gaussian $\langle K \rangle \Sigma^{-2}$ curvature over time averaged across 3 runs. 
-    From left to right, we have particles with $\alpha = 0.5, 1, 2$. We observe that the initial stages of 
-    evolution are unaffected by the applied magnetic field. However, after about 10000 timsteps, we see a 
+    From left to right, I have particles with $\alpha = 0.5, 1, 2$. I observe that the initial stages of 
+    evolution are unaffected by the applied magnetic field. However, after about 10000 timsteps, I see a 
     magnetic field dependence on the evolution of the Gaussian curvature. The preservation of this divergence 
@@
 
-Given we did not see any noteworthy changes in the mean curvature in
-Figure \ref{fig:curvature-vs-B_ss}, we focused on the Gaussian curvature
-in Figure \ref{fig:curvature_vs_coverage}. We observe that for all
-simulated systems, the Gaussian curvature increases over time until an
-invariance is reached near the end of the simulation, signifying the
-bijel microstructure is locked in place. We also observe that for all
-microstructures the curvature over time does not increase at the same
-rate, characterized with dips at 10 to 20,000 timesteps for all
-particles and a magnetic field dependent change in the curvature
-increase.
+The time evolution of $g \Sigma^{-1}$ of bijels stabilized with spherical particles is unaffected by the application of a magnetic field. However, a 
+slight decrease in the genus as a function of the applied field is observed for bijels stabilized with ellipsoidal particles. This suggests that the 
+evolution of the surface corresponding to the interface is changed by the adsorption and orientation of magnetically responsive ellipsoidal particle. 
+I see effects of this change in $\langle G \rangle \Sigma^{-2}$ where I see the evolution of the curvature being delayed, indicated as a rightward 
+shift of the plots as a function of the applied field.
 
-However, for the spherical particles this local topology change
-disappears once the spinodal decomposition ceases, observed as a
-convergence of all curvatures. This is not observed for the bijels
-stabilized by ellipsoidal particles. Despite all our curvature
-calculations being normalized with their surface area to volume ratio,
-we still see curvature differences as a function of the applied magnetic
-field. Experiments have identified that curvature changes can occur due
-to the formation of monogels, which are particle networks formed from
-bijels that can withstand the remixing of their constituent liquids.
-\cite{sanz_colloidal_2009, lee_making_2013} This process cannot occur in
-our simulations as we are utilizing repulsive particles. Therefore, the
-change in curvature arises from the differences in local state of the
-colloids at the interface. From the microstructure results in Figures \ref{fig:D2a_B}
-in addition to the genus differences characterized in Figure \ref{fig:curvature_vs_coverage},
-the connectivity of the microstructure is affected through the application of magnetic fields.
-We can use the channel size distribution to investigate how the connectivity of the microstructure and thus the 
+Despite all our curvature calculations being normalized with their surface area to volume ratio, I still see curvature differences as a function of the applied 
+magnetic field. Experiments have identified that curvature changes can occur due to the formation of monogels, which are particle networks formed from bijels that 
+can withstand the remixing of their constituent liquids. \cite{sanz_colloidal_2009, lee_making_2013} This process cannot occur in our simulations as I am utilizing 
+electrically neutral particles that only interact through contact forces. Therefore, the change in curvature arises from microstructure changes driven by particle 
+alignment to the magnetic field direction. These results provide support for the mechanism of control being due to particle alignment to the magnetic field during 
+coarsening changes the topology of the surface, which upon jamming of ellipsoidal particles is locked in. As our particles only interact through contact forces, 
+the only mechanism present that can change the topology of the interface would be particle interactions upon contact with each other. Particle interactions are 
+controlled through the orientation of particles and the local ordering of particles on the interface. Seeing that there are differences in the gaussian curvature of the bijel,
+the domain anisotropy characterized in Figure \ref{fig:D2a_B} may be able to be characterized as changes in the topology of the surface. Chan and Thornton introduced a 
+topological technique to characterize the connectivity of surface as a function of a distance from the interface to calculate the channel size distribution. 
+\cite{chan_channel_2012} I can use the channel size distribution to investigate how the connectivity of the microstructure and thus the 
 channel size is affected as a function of the applied magnetic field.
-
-While minor run to run variation is observed, the combined data of the channel size distribution shown in Figure \ref{fig:CSD_B_ss} shows some major differences 
-in the channel size distribution in each bijel stabilized with oblate particles. It was expected that the domain anisotropy obtained using second moment of the 
-structure factor would manifest as two peaks in the channel size distribution. \cite{karthikeyan_formation_2024} This behavior is observed in the channel size 
-distribution for bijels stabilized with oblate and prolate particles with $\bar{B} = 1$, but is more difficult to see when smaller magnetic fields are applied. 
-We see that there is a shift to larger channel sizes upon application of the magnetic field for bijels stabilized by ellipsoids. These differences arise from the 
-particle ordering and local distribution changes observed.
 
@@
                  against the distance from the interface normalized with the characteristic length scale. The channel sizes obtained are averaged over 
-                 three runs. We see that the peak locations are shifted to larger and smaller positions for bijels stabilized with ellipsoidal particles
+                 three runs. I see that the peak locations are shifted to larger and smaller positions for bijels stabilized with ellipsoidal particles
                  upon field application} 
@@
 
+While run to run variation is observed, the combined data of the channel size distribution shown in Figure \ref{fig:CSD_B_ss} shows some differences 
+in the channel size distribution in each bijel stabilized with ellipsoidal particles. It was expected that the domain anisotropy obtained using second moment of the 
+structure factor would manifest as two peaks in the channel size distribution. \cite{karthikeyan_formation_2024} This behavior is observed in the channel size 
+distribution for bijels stabilized with ellipsoidal particles with $\bar{B} = 1$, but is more difficult to see when smaller magnetic fields are applied. 
+These differences arise from the particle ordering and local distribution changes observed.
+
 \subsection{Kinetics of bijel formation in magnetic fields}
@@
 To shed light on the mechanisms involved in the coarsening dynamics,
-we now turn to the kinetics of bijel formation in more detail. The
+I now turn to the kinetics of bijel formation in more detail. The
 coarsening dynamics can be characterized by a coarsening speed. Here,
-we use the finite difference of the directional domain size to
+I use the finite difference of the directional domain size to
 calculate the components of the coarsening velocity
@@
 Figure \ref{fig:coarsening_velocity} shows the coarsening speed in the directions parallel and perpendicular to the applied magnetic field. 
-The data confirms that for spherical particles, domain coarsening remains isotropic.
-We observe a higher coarsening speed initially which slows at later times when the particles begin to jam.
-This indicates that the
+The data confirms that for spherical particles, domain coarsening remains isotropic. I observe a higher coarsening speed initially which slows 
+at later times when the particles begin to jam. This indicates that the
 coarsening is subject to different time scales, as reported previously
@@
 al.~\cite{reeves_particle-size_2015} have pointed out that bijel
-formation hinges on the jamming time in relation to the disruption time, i.e., the time scale at which domain pinch-off events can cause bijel break-up through depercolation.
-In our simulations, however, we have not observed disruption of bijel formation; stable bijels form for all parameters consistent with simulations by Stratford et
+formation hinges on the jamming time in relation to the disruption time, i.e., the time scale at which domain pinch-off events can cause bijel break-up through 
+depercolation. In our simulations, however, I have not observed disruption of bijel formation; stable bijels form for all parameters consistent with simulations 
+by Stratford et
 al.~\cite{stratford_colloidal_2005} and Jansen et al.~\cite{jansen_bijels_2011}.
@@
 is delayed compared with the perpendicular direction.
-In addition, we observe a shoulder (around \(10^4\Delta t\)) where the coarsening speed decays more slowly before jamming sets in.
+In addition, I observe a shoulder (around \(10^4\Delta t\)) where the coarsening speed decays more slowly before jamming sets in.
 These results suggest that the coarsening near the jamming time is affected by a mechanism that depends on the applied magnetic field and causes the anisotropic
@@
 particles and their alignment relative to the direction of the
-magnetic field. To confirm this hypothesis, we analyze the
+magnetic field. To confirm this hypothesis, I analyze the
 orientational order of the particles and their alignment relative to
@@
 
-To measure the particle alignment quantitatively, we computed the
+To measure the particle alignment quantitatively, I computed the
 nematic order tensor using the method detailed in Section \ref{section:nematic_order_parameter} 
@@
 \(S\approx 1.0\) towards the end of the simulation. For the prolate
-particles (\(\alpha=2.0\)), we observe a shoulder at around
+particles (\(\alpha=2.0\)), I observe a shoulder at around
 \(10^4\Delta t\) and an intermittent plateau. The occurrence of this
@@
 pronounced at the weakest magnetic field \(\bar{B}=0.2\). To further corroborate 
-this mechanism, we plot the time evolution of the orientational order of the interfaces.
+this mechanism, I plot the time evolution of the orientational order of the interfaces.
 
@@
 In the case of bijels, however, the percolating interfaces are tortuous
-and thus more mobile. We therefore posit that, rather than tilting out
+and thus more mobile. I therefore posit that, rather than tilting out
 of the interface, rotating particles can ``pull'' the interface along
@@
 Hence the prolate particles remain mostly aligned with the interface
-even in the stronger applied magnetic fields. We plot the interface angle of bijels
+even in the stronger applied magnetic fields. I plot the interface angle of bijels
 stabilized by ellipsoidal particles at the final timestep to demonstrate the differences
@@
         \caption{Visualizations of the particle monolayer at the last timestep shaded with the interface angle of each particle in red. The top and bottom
-                 rows correspond to snapshots of bijels with no field and a field strength of $\bar{B} = 1$ applied. We see that the oblate particles flip
+                 rows correspond to snapshots of bijels with no field and a field strength of $\bar{B} = 1$ applied. I see that the oblate particles flip
                  out of the interface into a non energetically favored position while the bijels stabilized with prolate particles tilt out of the interface
@@
 
-From Figure \ref{fig:psi_viz_ss} we can see the differences in the particle alignment to the interface characerizing the differences in $\psi$ observed. Oblate
+From Figure \ref{fig:psi_viz_ss} I can see the differences in the particle alignment to the interface characerizing the differences in $\psi$ observed. Oblate
 particles can be seen to tilt out of the interface more readily than prolate particles at the same magnetic field strength. Due to the strong surface tension
-between the fluids, the particles are strongly adsorbed onto the interface. We also see that the arrangement of particles on the interface is modified through the
-application of the magnetic field for both particle morphologies. We can obtain quantitative metrics regarding this ordering using the Steinhardt 2 and 6 fold
+between the fluids, the particles are strongly adsorbed onto the interface. I also see that the arrangement of particles on the interface is modified through the
+application of the magnetic field for both particle morphologies. I can obtain quantitative metrics regarding this ordering using the Steinhardt 2 and 6 fold
 order parameters, $\langle Q2 \rangle$ and $\langle Q6 \rangle$.
@@
 
-We select $\langle Q6 \rangle$ and $\langle Q2 \rangle$ as the bond order parameters to calculate as we are interested in identifying the point when ordering 
+I select $\langle Q6 \rangle$ and $\langle Q2 \rangle$ as the bond order parameters to calculate as I am interested in identifying the point when ordering 
 of the material changes. Kapfer et al. demonstrated that only using $\langle Q6 \rangle$ to identify the ordering of particles in the system can result in 
@@
 $\langle Q2 \rangle = 0$ can be used to characterize increasing disorder in a system. \cite{mickel_shortcomings_2013} By plotting $\langle Q6 \rangle$ and 
-$\langle Q2 \rangle$, we will be able to identify changes in the local ordering of the system even if we cannot directly assess the local structure.
+$\langle Q2 \rangle$, I will be able to identify changes in the local ordering of the system even if I cannot directly assess the local structure quantitatively.
 
@@
     \caption{Time dependence of the mean two and six fold symmetry parameter, $\langle Q2 \rangle$ and $\langle Q6 \rangle$ 
-    for bijels stabilized with oblate(left), spherical(middle) and prolate(right) particles. We use $\langle Q2 \rangle$ as an
+    for bijels stabilized with oblate(left), spherical(middle) and prolate(right) particles. I use $\langle Q2 \rangle$ as an
     indicator of global particle translational order while $\langle Q6 \rangle$ is an indicator of local order.} 
@@
 
-From Figure \ref{fig:steinhardt_coverage}, we see an increase in disorder in all the bijel systems characterized as an increase in $\langle Q2 \rangle$. 
+From Figure \ref{fig:steinhardt_coverage}, I see an increase in disorder in all the bijel systems characterized as an increase in $\langle Q2 \rangle$. 
 This is a characteristic of how the particles were initialized and move once the simulation is initiated. The particles are initialized to be randomly placed 
 in the simulation domain with roughly equal spacing. As the interface sweeps through the simulation domain, particles irreversibly adsorb onto the interface 
-and move with the interface until the bijel jams. We see that $\langle Q2 \rangle$ is magnetic field dependent for oblate particles but not for the spherical 
-and prolate particles. We also see an aspect ratio dependence on the values characterized as differences in the time evolution of $\langle Q2 \rangle$. This 
+and move with the interface until the bijel jams. I see that $\langle Q2 \rangle$ is magnetic field dependent for oblate particles but not for the spherical 
+and prolate particles. I also see an aspect ratio dependence on the values characterized as differences in the time evolution of $\langle Q2 \rangle$. This 
 arises due to the differences in the aspect ratio of the particle causing them to arrange differently on the interface as the bijel microstructure evolves.
@@
 An increase in $\langle Q6 \rangle$ can indicate an increase in the number of particles adopting icosahedral symmetry at the interface of the amorphous 
-interface. \cite{kapfer_jammed_2012} However due to the amorphous nature of the arrangement of particles at the particle monolayer, we use this parameter 
+interface. \cite{kapfer_jammed_2012} However due to the amorphous nature of the arrangement of particles at the particle monolayer, I use this parameter 
 only to gauge changes in local arrangements of particles at the interface and make no commentary on specific interfacial arrangements. For oblate particles, 
-we characterize a reduction in local order as the applied field strength is increased, consistent with the increase in $\langle Q2 \rangle$. For prolate 
-particles, we observe that $\langle Q6 \rangle$ increases with the applied field. This indicates that the application of the field causes particles to have 
-increased local order, even if we see no discernible changes in $\langle Q2 \rangle$.
+I characterize a reduction in local order as the applied field strength is increased, consistent with the increase in $\langle Q2 \rangle$. For prolate 
+particles, I observe that $\langle Q6 \rangle$ increases with the applied field. This indicates that the application of the field causes particles to have 
+increased local order, even if I see no discernible changes in $\langle Q2 \rangle$.
 
@@
 interfaces than discs as the magnetic field causes the particles to align to the field. This better packing at the interface manifests as greater local ordering 
-Next, we analyze how these local toplogical changes affect the microstructure of the bijel by analyzing the channel size distribution of the bijels.
+Next, I analyze how these local toplogical changes affect the microstructure of the bijel by analyzing the channel size distribution of the bijels.
 
@@
 the magnetic field reduces the steric constraints within the interface.
-To corroborate this idea, we analyzed the radial distribution function
+To corroborate this idea, I analyzed the radial distribution function
 (RDF) of the particles, the calculation of which is detailed in Section
@@
 the local re-alignment of interfaces due to capillary interactions. In
-the case of prolate particles, we observed the shrinking interface can
+the case of prolate particles, I observed the shrinking interface can
 force particles to tilt out of their preferential alignment to facilitate
@@
 field, the domain size and tortuosity become anisotropic. Additionally,
-we observe that the particle packing in the interface becomes more
+I observe that the particle packing in the interface becomes more
 ordered due to the alignment effects.
@@
 
-In this work, we studied the effect of applied magnetic fields on the
+In this work, I studied the effect of applied magnetic fields on the
 formation of bijels stabilized by magnetic ellipsoidal particles. We
 considered oblate, spherical, and prolate particles with a permanent
-magnetic dipole moment suspended in a symmetric binary liquid. We found
+magnetic dipole moment suspended in a symmetric binary liquid. I found
 that, while the overall formation of a bijel is not disrupted by
@@
 tortuosity increases in the perpendicular direction. Compared with
-bijels formed in the absence of a magnetic field, we observed changes in
+bijels formed in the absence of a magnetic field, I observed changes in
 domain size up to \(30\%\) for non-spherical particles. This effect can
@@
 magnetic field, which in turn re-aligns the interfaces in the direction
-of the longer axis of the particles. We further corroborated this
+of the longer axis of the particles. I further corroborated this
 mechanisms by analyzing the coarsening speed and the nematic order of
-the particles and the interfaces. We found that jamming of particles is
+the particles and the interfaces. I found that jamming of particles is
 delayed in the direction of the longer ellipsoidal axis leading to
@@
 jamming coincides with a slow-down of the orientational ordering of the
-particles whereas the alignment of the interfaces increases. We also
+particles whereas the alignment of the interfaces increases. I also
 found that the angle between the particle dipole axis and the interface
-normal changes at this stage. Additionally, we analyzed the radial
+normal changes at this stage. Additionally, I analyzed the radial
 distribution function of the particles and found that prolate particles
 tend to align side by side, while the oblate particles exhibit a less
-regular arrangement. Based on these findings, we propose that bijel
+regular arrangement. Based on these findings, I propose that bijel
 formation in magnetic fields is governed by two coupled effects: During
@@
 \cite{jansen_bijels_2011,hijnen_bijels_2015}. With respect to possible
-experimental realizations of our simulations, we should emphasize that
-we have generally considered micron-size particles and have neglected
+experimental realizations of our simulations, I should emphasize that
+I have generally considered micron-size particles and have neglected
 thermal fluctuations. At the nanoscale, thermal fluctuations may in

### 2025-03-20 chapters/paper2.tex
Changes 1. Updated aim 1 with first person wording 2. Updated aim 2 with first person wording and modified conclusion 3. Updated aim 3 with full size conclusion

@@
 This work investigates the structural response of bijels stabilized by anisotropic magnetic particles. Using a Lattice Boltzmann Method 
-coupled with Molecular Dynamics, we simulate a binary fluid system where ellipsoidal particles, modeled as magnetic dipoles along their 
+coupled with Molecular Dynamics, I simulate a binary fluid system where ellipsoidal particles, modeled as magnetic dipoles along their 
 symmetry axis, stabilize bijel templates. Magnetic fields applied to bijels made without a magnetic field reveal anisotropic bijel formation, 
@@
 
-We further assess how initial microstructure influences structural changes, showing that the difference in order between initial and final 
+I further assess how initial microstructure influences structural changes, showing that the difference in order between initial and final 
 configurations of the particle monolayers dictates the extent of microstructure evolution if the applied field is increased in the direction of 
@@
 
-We begin our investigation by characterizing the microstructure changes observed on bijels stabilized with prolate ellipsoids with a 
-particle volume fraction of $\phi_p = 0.1$. We only focus on one system here as the mechanism for stimuli response shown in Aim 1 is identical
-for both systems. Therefore we expect that the qualitative trends between prolate and oblate particles will be matched. I select prolate particles
+I begin our investigation by characterizing the microstructure changes observed on bijels stabilized with prolate ellipsoids with a 
+particle volume fraction of $\phi_p = 0.1$. I only focus on one system here as the mechanism for stimuli response shown in Aim 1 is identical
+for both systems. Therefore I expect that the qualitative trends between prolate and oblate particles will be matched. I select prolate particles
 as they are more readily synthesizable in experiments.
@@
     \includegraphics[scale=0.5]{../figures/results/paper2/hysteresis_curve.png} 
-    \caption{Plot of the hysteresis curve of a bijel stabilized by magnetically responsive prolate particles. I observe that the domain size increases as we 
+    \caption{Plot of the hysteresis curve of a bijel stabilized by magnetically responsive prolate particles. I observe that the domain size increases as I 
     increase the applied magnetic field strength. However, upon decrease of the applied field strength the microstructure does not return to its previous value,
@@
 the droplet being elongated in the direction of the applied field. This suggests that the particles at the interface of magnetically responsive bijels are in
-in a kinetically trapped configuration. Cui et al. used spherical particles in their emulsion response experiments while we use ellipsoidal particles. Additionally,
-we also observe in Figure \ref{fig:hysteresis_curve} that the response of the bijel is dependent upon the field strength applied.
+in a kinetically trapped configuration. Cui et al. used spherical particles in their emulsion response experiments while I use ellipsoidal particles. Additionally,
+I also observe in Figure \ref{fig:hysteresis_curve} that the response of the bijel is dependent upon the field strength applied.
 In the following sections, I investigate the impact of magnetic field strength and the initial ordering of the particle monolayer on the observed stimuli response.
@@
 \includegraphics[scale=0.4]{../figures/results/paper2/microstructure_viz-field_on.png} 
-\caption{Visualizations of bijels stabilized by oblate and prolate particles simulated under no fields at $t = 0$ (left columns) and $t = 10^5$ (right columns).
-The first and third row detail the microstructure evolution for oblate and prolate particle stabilized bijels with no applied field while the second and fourth rows show bijels stabilized by oblate and prolate particles respectively with a field strength of $\bar{B} = 1$ applied.
-Particle reorientation to the direction of the field can be seen upon application of the magnetic field, resulting in microstructure changes driven through domain coarsening until the particles jam.
-We see similar behavior in bijels stabilized by oblate particles upon application of the magnetic field.}
+\caption{Visualizations of bijels stabilized by oblate and prolate particles simulated under no fields at $t = 0$ (left columns) and $t = 10^5$ (right columns). The first 
+         and third row detail the microstructure evolution for oblate and prolate particle stabilized bijels with no applied field while the second and fourth rows show 
+         bijels stabilized by oblate and prolate particles respectively with a field strength of $\bar{B} = 1$ applied. Particle reorientation to the direction of the 
+         field can be seen upon application of the magnetic field, resulting in microstructure changes driven through domain coarsening until the particles jam. I see 
+         similar behavior in bijels stabilized by oblate particles upon application of the magnetic field.}
 \label{fig:microstructure_viz-field_on} 
@@
 \includegraphics[scale=0.5]{../figures/results/paper2/domain_size-field_on.png} 
-\caption{Plotting the spherically averaged domain size normalized with $R_p$($L/R$) of the particle at different magnetic field strengths, $\bar{B}$, and the nematic order parameter $S$ in lines.
-We quantify the domain size and ordering of the particles, and show that the change in both parameters are correlated with the strength of the applied magnetic field.}
+\caption{Plotting the spherically averaged domain size normalized with $R_p$($L/R$) of the particle at different magnetic field strengths, $\bar{B}$, and the nematic order 
+         parameter $S$ in lines. I quantify the domain size and ordering of the particles, and show that the change in both parameters are correlated with the strength of 
+         the applied magnetic field.} 
 \label{fig:domain_size-field_on} 
@@
 \caption{Plotting the anisotropic domain size and tortuosities against the applied magnetic field strength on the left and right respectively for bijels 
-         stabilized with magnetically responsive oblate and prolate ellipsoids. We see that upon application of the field, bijels stabilized with prolate 
+         stabilized with magnetically responsive oblate and prolate ellipsoids. I see that upon application of the field, bijels stabilized with prolate 
          particles experience a domains ize increase in the direction parallel to the applied field direction, $L_{\parallel}$, while the domain size 
@@
 to the magnetic field, they adopt direction specific surface coverages which manifest as anistropic domains upon jamming. In Figure 
-\ref{fig:domain_size_aniso-field_on}, we demonstrate that the application of the magnetic field changes the domain size.
+\ref{fig:domain_size_aniso-field_on}, I demonstrate that the application of the magnetic field changes the domain size.
 
@@
 I see that the orientations and positions of the particles vary slightly for both ellipsoidal particle morphologies. This effect is due steric effects between particles,
-as identified in Gunther et al. \cite{gunther_timescales_2014} I observe that for bijels stabilized by prolate ellipsoids, we see the adoption of orientational order
+as identified in Gunther et al. \cite{gunther_timescales_2014} I observe that for bijels stabilized by prolate ellipsoids, I see the adoption of orientational order
 to the magnetic field and qualitatively different particle arrangements on the interface. These indicate that the interfacial capillary forces or steric interactions 
@@
 \caption{Plots of the interface angle $(\langle \psi \rangle)$ and six fold Steinhardt order parameter $(\langle Q6 \rangle)$ on the left and right respectively, 
-         versus time for bijels stabilized with oblate and prolate ellipsoids on the top and bottom rows respectively. We demonstrate that upon application 
+         versus time for bijels stabilized with oblate and prolate ellipsoids on the top and bottom rows respectively. I demonstrate that upon application 
          of a magnetic field, the behavior of $(\langle \psi \rangle)$ and $(\langle Q6 \rangle)$ differ significantly between oblate and prolate ellipsoids 
-         indicating that the dynamics for both particle morphologies differ. We also observe magnetic field dependence in each property for both particle types, 
+         indicating that the dynamics for both particle morphologies differ. I also observe magnetic field dependence in each property for both particle types, 
          suggesting that these changes are driven primarily through the change in the applied field strength.} 
@@
 
-From Figure \ref{fig:interface_angle-nint-field_on}, we identify that prolate and oblate particles respond differently at the interface. For
+From Figure \ref{fig:interface_angle-nint-field_on}, I identify that prolate and oblate particles respond differently at the interface. For
 bijels stabilized by oblate ellipsoids, I characterize an increase in $\langle \psi \rangle$ from an initial value of $19 ^{\circ}$,
@@
 large adsorption energy of the particles at the interface of the bijel, caused by high surface tension. Finally, the particles jam in place,
-locking the interface at an angle to the particle. We see the rate of increase in $\langle \psi \rangle$ at early stages and the time spent
+locking the interface at an angle to the particle. I see the rate of increase in $\langle \psi \rangle$ at early stages and the time spent
 in the plateau increase with a larger applied magnetic field. The final angle at the interface is also dependent upon the applied field
@@
 When analyzing $\langle \psi \rangle$ for bijels stabilized by prolate particles, this behavior can also be observed. $\langle \psi \rangle$
-begins at $10 ^{\circ}$.We see $\langle \psi \rangle$ increases, before plateauing and slowly decreasing. The initial peak height and rate of increase in 
+begins at $10 ^{\circ}$. I see $\langle \psi \rangle$ increases, before plateauing and slowly decreasing. The initial peak height and rate of increase in 
 $\langle \psi \rangle$ is field dependent, although given the small decrease in $\langle \psi \rangle$ it is unclear if the final value of this parameter 
 is field dependent for bijels stabilized with prolate particles. The changes in $\langle \psi \rangle$ for bijels stabilized with prolate particles are 
-small compared to bijels stabilized with oblate particles. We visualize this process by color coding snapshots of the particle monolayer at the initial
+small compared to bijels stabilized with oblate particles. I visualize this process by color coding snapshots of the particle monolayer at the initial
 and final timesteps of bijels stabilized by prolate particles with a field strength of $\bar{B} = 1$ applied.
@@
 represents the capillary timescale between the interface and the
-particle. Given the shape of the plot, we assign the
+particle. Given the shape of the plot, I assign the
 $\tau_{\langle \psi \rangle}$ to be the time when the first minimum of
@@
 calculated which represents a timescale of local particle rearrangement.
-We define $\tau_{\langle Q6 \rangle}$ as the time when
+I define $\tau_{\langle Q6 \rangle}$ as the time when
 \(\langle Q6 \rangle \geq 0.38\) for prolate particles and the global
@@
 \includegraphics[scale=0.4]{../figures/results/paper2/domain_size-field_on-scaled.png} 
-\caption{Plots of domain size with different timescales.
-The top and bottom row represent the average domain size for bijels stabilized with oblate and prolate particles respectively.
-The figures on the left plots the domain size against time rescaled with the nematic to isotropic transition time, $\tau_S$.
-The figures in the middle plot the domain size against time rescaled with the interfacial capillary timescale, $\tau_{\langle \psi \rangle}$.
-The figures on the right plot the domain size against time rescaled with the particle rearrangement timescale, $\tau_{\langle Q6 \rangle}$.
-We show that the controlling timescale when applying a magnetic field onto bijels with disordered particles is the latter timescale, indicating that the dominating effect is steric hindrance of the particles during rearrangment at the interface.}
+\caption{Plots of domain size with different timescales. The top and bottom row represent the average domain size for bijels stabilized with oblate and 
+         prolate particles respectively. The figures on the left plots the domain size against time rescaled with the nematic to isotropic transition time, 
+         $\tau_S$. The figures in the middle plot the domain size against time rescaled with the interfacial capillary timescale, $\tau_{\langle \psi \rangle}$. 
+         The figures on the right plot the domain size against time rescaled with the particle rearrangement timescale, $\tau_{\langle Q6 \rangle}$. I show 
+         that the controlling timescale when applying a magnetic field onto bijels with disordered particles is the latter timescale, indicating that the 
+         dominating effect is steric hindrance of the particles during rearrangment at the interface.} 
 \label{fig:domain_size-field_on-scaled} 
@@
 the domain sizes do not collapse onto a single line, which is expected
-if we want to explain the dynamics using the nematic order parameter.
+if I want to explain the dynamics using the nematic order parameter.
 This confirms the observation made above that the dynamics do not only
@@
 I explore how pre-existing order in the particles affect the degree of
-domain size change observed. We apply fields of strength
+domain size change observed. I apply fields of strength
 $\bar{B}_{template} = 0, 0.2, 0.5, 1$ during phase separation to
@@
 particles, respectively which decreases as $\Delta \bar{B}$ decreases.
-We further characterize the relationship between $\Delta \bar{B}$ and
+I further characterize the relationship between $\Delta \bar{B}$ and
 nematic order, showing that an increase in \(S\) correlates with
@@
          oblate and prolate ellipsoidal particles starting at different particle orders. I plot these results against the change in the applied field 
-         strength, $\Delta B$. We show that the anisotropic domain size is inversely correlated to the tortuosity. We see that $L_{perp}$ changes for 
+         strength, $\Delta B$. I show that the anisotropic domain size is inversely correlated to the tortuosity. I see that $L_{perp}$ changes for 
          a bijel made with $\bar{B} = 1 \rightarrow 1$ and $\bar{B}: 0 \rightarrow 1$ differ, suggesting that the processing history of the bijel is important.} 
@@
 
-From Figure \ref{fig:domain_size_aniso-field_up}, we see that domain
+From Figure \ref{fig:domain_size_aniso-field_up}, domain
 size anisotropy is observed upon increasing the applied field
-application of the field for both particle morphologies. I also see
-some domain anisotropy with no applied field, which increases upon
-application of the magnetic field. The directional domain sizes,
+for both particle morphologies. Some domain anisotropy with no applied field can be observed, 
+which increases upon application of the magnetic field. The directional domain sizes,
 $L_{\perp}$ and $L_{\parallel}$ increase by $73\%$ and $7\%$
@@
 field, matching the results for the nematic order parameter shown in
-Figure \ref{fig:domain_size-field_up}. We also observe the alignment of
+Figure \ref{fig:domain_size-field_up}. I also observe the alignment of
 the long axis of the particles to the magnetic field, demonstrating the
@@
 reorientation before the applied magnetic field begins to cause
-particles to tilt out of the interface. We see similar trends for bijels
+particles to tilt out of the interface. I see similar trends for bijels
 stabilized by prolate particles. $\langle \psi \rangle$ begins near
-$11 ^{\circ}$. We see a decrease before reorientation ceases, and
+$11 ^{\circ}$. I see a decrease before reorientation ceases, and
 finally $\langle \psi \rangle$ increases again.
@@
 When looking at $\langle Q6 \rangle$ for $\bar{B}: 0 \rightarrow 1$
-and $\bar{B}: 0.2 \rightarrow 1$ for oblate particles, we see that the
+and $\bar{B}: 0.2 \rightarrow 1$ for oblate particles, I see that the
 trends are similar with an initial decrease, followed by a plateau and
@@
 field history of $\bar{B}: 0.5 \rightarrow 1$ and
-$\bar{B}: 1 \rightarrow 1$. We see a decrease in
+$\bar{B}: 1 \rightarrow 1$. I see a decrease in
 $\langle Q6 \rangle$ for bijels stabilized with oblate particles with
@@
 $\bar{B}: 1 \rightarrow 1$. For the $\bar{B}: 0.5 \rightarrow 1$
-case, we see a slight increase in $\langle \psi \rangle$ before a
+case, I see a slight increase in $\langle \psi \rangle$ before a
 decrease and increase compared to the $\bar{B}: 1 \rightarrow 1$ case
-where we characterize a slight decrease over time. I also characterize
+where I characterize a slight decrease over time. I also characterize
 a slight decrease in $\langle Q6 \rangle$ over time for the
@@
 changes the microstructure of the bijel as a function of the initial
-particle order. We use bijels simulated under
+particle order. I use bijels simulated under
 $\bar{B}_{template} = 0, 0.2, 0.5, 1$ during formation of the bijel. Once
@@
 
-In Figure \ref{fig:microstructure_viz-field_down}, we visualize the time
+In Figure \ref{fig:microstructure_viz-field_down}, I visualize the time
 evolution of the microstructure of bijels with processing history
 $\bar{B}:0.2 \rightarrow 0$ (top) and $\bar{B}:1 \rightarrow 0$
-(bottom). We see that when switching the field off, the microstructure
+(bottom). I see that when switching the field off, the microstructure
 remains largely the same, demonstrating the kinetic stability of bijels.
@@
 \caption{Plot of the spherically averaged domain size normalized with $R_p$ of the particle and the nematic order parameter of each bijel over time. 
-         Each color represents bijel templates made with different field strengths $\bar{B}$. We show that there is domain coarsening when the field 
+         Each color represents bijel templates made with different field strengths $\bar{B}$. I show that there is domain coarsening when the field 
          is switched off, along with a reduction in the ordering of the particles.} 
@@
 $\bar{B}:0\rightarrow0$ case to be due to coalescence of two
-domains, characterized as a two step process where we see slower long
+domains, characterized as a two step process where I see slower long
 timescale domain coarsening initially followed by a rapid jump in the
@@
 \caption{Plotting the anisotropic domain sizes and tortuosity at the final timestep on the left and right respectively for bijels stabilized with oblate and 
-         prolate ellipsoidal particles starting at different particle orders. We plot these results against the change in the applied field strength, 
+         prolate ellipsoidal particles starting at different particle orders. I plot these results against the change in the applied field strength, 
          $\Delta B$. I show that there are only minor differences in the microstructure of stimuli responsive bijels once the magnetic field is switched off.} 
@@
 coarsening of the bijel once stimuli is removed. To investigate why this
-is the case, we plot $\langle \psi \rangle$ and
+is the case, I plot $\langle \psi \rangle$ and
 $\langle Q6 \rangle$ for bijels stabilized with ellipsoidal particles
@@
 
-In this chapter, I identified that bijels stabilized by magnetically responsive particles exhibit microstructural hysteresis upon the application and removal of a 
-magnetic field. This hysteresis is characterized by the ability to alter microstructure when increasing the applied field, but an inability to do so when switching 
-the field off. When examining the effect of an applied magnetic field on domain size evolution in bijels initially lacking particle ordering, I found that domain 
-size changes correlate with field strength and are accompanied by microstructural anisotropy.
-By analyzing response timescales, I determined that the structural evolution arises primarily from particle reorientation at the interface. I then investigated 
-how the initial particle order in the direction of the magnetic field influences the response and found that the magnitude of the observed response depends on 
-the difference between the initial and final states of the particle monolayer. A closer examination of the monolayer revealed that many characteristic behaviors 
-observed in initially disordered systems were absent, indicating a distinct response mechanism.
-Finally, I explored why pre-existing particle order at the interface did not lead to different microstructural behavior upon field removal. I demonstrated that under 
-the given system parameters, the evolution of the particle monolayer was identical in all cases, suggesting that interface dynamics are governed by particle rearrangements 
-aimed at minimizing interfacial energy.
+\section{Conclusions}
+
+Owing to the applicability of bijels in the catalyst support, filtration membrane and drug release spaces, I was interested in identifying how bijels stabilized 
+by magnetically responsive ellipsoidal particles could be used to create active soft matter. In this work, I have studied the effect of the application, increase 
+or removal of magnetic fields on the structural response of bijels stabilized by magnetically responsive ellipsoids using hybrid Lattice Boltzmann-Molecular Dynamics 
+simulations. I first characterized the hysteresis curve of the bijel, identifying that the process history dependence of the bijel microstructure. To identify why 
+I observed the path dependence and the microstructure change observed when applying magnetic fields after synthesis, I considered three starting setups; The first 
+applying a field of varying strength to bijel templates that were simulated with no magnetic field applied. The second involved increasing the applied field 
+strength onto bijel templates that were simulated with increasing field strengths. The final setup involves removing a field from bijel templates that were simulated 
+with various field strengths.
+
+I found that application of magnetic fields onto bijels stabilized by magnetically responsive ellipsoidal particles results in an average microstructure change up to 
+$5\%$ when investigating changes in the average microstructure. I also identified that the structures become anisotropic upon application of the magnetic field for 
+oblate and prolate particles. The anisotropy is particle dependent with bijels stabilized by oblate particles seeing an increase in $L_{\perp}$ of up to $60\%$ and for 
+prolate particles an increase in $L_{\parallel}$ of up to $40\%$ with a corresponding decrease in the tortuosity in that axis. This is caused by the reorientation of the 
+particles to the magnetic field, followed by domain coarsening as the interfacial coverage of the particles decrease, before jamming in place again. I characterize that 
+while particle reorientation to the applied field initiates microstructural response, local rearrangement of the particle monolayer is the controlling mechanism of 
+domain size evolution as characterized by identifying the dominant timescales 
+of response for both particle morphologies. However, their time evolution is different with bijels stabilized by prolate particles undergoing a local crystallization when 
+the average six fold Steinhardt order parameter or $\langle Q_6 \rangle \geq 0.38$. For bijels stabilized by oblate particles, a global minimum of the $\langle Q_6 \rangle$ 
+characterizes the dynamics of the system.
+
+When increasing the applied field strength, I observe that the difference between the final and initial magnetic fields is correlated to the domain size change observed. 
+I observe that the anisotropic domain size changes are also dependent upon this difference, with the largest difference being observed when characterizing a bijel template 
+simulated under no field before having a field strength of $\bar{B} = 1$ applied to it. When looking at the particle monolayer, I characterize three behaviors seen from the 
+average interfacial angle $\langle \psi \rangle$ and $\langle Q_6 \rangle$. These behaviors are further differentiated for each particle morphology. For oblate particles, 
+the first behavior is characterized as a reorientation of the particle on the interface seen as an increase in $\langle \psi \rangle$ over time with a corresponding decrease 
+in $\langle Q_6 \rangle$ as the particles do not close pack anymore. For prolate particles, I see a slight reduction in $\langle \psi \rangle$ and greater ordering of the 
+particles from $\langle Q_6 \rangle$. The second behavior originates from small reorientations of the particles at the monolayer which do not greatly affect the interfacial 
+angle but cause a loss or gain of particle order on the interface. The final behavior is characterized as long timescale domain coarsening as there is no change between the 
+applied magnetic field and the magnetic field used to simulate the template.
+
+Finally, when decreasing the magnetic field strength, I observe little difference between bijel templates made with any field strength and no field. From the average domain 
+size, I see that the bijels coarsen at approximately the same rate. Upon further investigation of the microstructure anisotropy, I identify that the anisotropic structure 
+does not change as well, suggesting coarsening effects are independent of the effect of the local differences at the particle monolayer. After characterizing 
+$\langle \psi \rangle$ and $\langle Q_6 \rangle$, I see differences at the initial state which, while changing the initiation point of the dynamics, does not play a large
+ role otherwise. Thus any domain size change observed when removing a field is due to interfacial capillary interactions.
+
+It has been shown how the domain size and tortuosity can be used to adjust the flow rate, separations efficiency or reaction rate in applications such as cross-flow reactors, 
+drug delivery and liquid-liquid extraction. These results show that the properties of bijels can be tuned in-situ for these applications although it appears that it can only 
+be done once. With the results presented here, I have considered only one set of parameters that control the dynamics. Parameters not changed such as the fluid density, 
+viscosity, surface tension and volume fraction of particles may impact the mechanisms and rate of domain size control. I also do not consider magnetic 
+fields applied in different directions which even in this simple setup may be able to modify the microstructure considerably, or gradient magnetic fields which may allow 
+more effective unjamming and re-jamming dynamics for further microstructure modification than what has been shown here.
+
+Effects such as the steric hindrance between particles may lessen as particle size reduces as particles are more easily able to conform to the curvature of the interface. 
+The impact this may have on the results seen with the micron-sized particles used here is unknown. In many of the applications listed above, it is also unknown how changes 
+in the spacing between particles affect underlying reactivity, selectivity or diffusion rates which have implications past the domain size and tortuosity changes characterized 
+in the literature. Furthermore, it is unknown how additional particle interactions such as chemical cross-linking or charge affect the results seen here. Both strategies are 
+used in bijels to reinforce them against shear to facilitate higher shear rates, useful in cross-flow reactors and separation membranes. In conclusion, our simulations provide 
+qualitative trends into the expected microstructure change and their underlying mechanisms and timescales when applying or removing a field from a bijel stabilized by 
+anisotropic particles by modifying their orientation and packing.

### 2025-03-20 chapters/paper3.tex
Changes 1. Updated aim 1 with first person wording 2. Updated aim 2 with first person wording and modified conclusion 3. Updated aim 3 with full size conclusion

@@
 
-In this chapter, I investigated the rheology of bijels stabilized by ellipsoidal particles under shear, focusing on the influence of initial microstructure and the 
-application of a constant magnetic field on their shear response. The shear behavior was characterized using a Herschel-Bulkley fitting function to extract the flow index, 
-consistency index, and yield stress. My analysis confirmed that the shear-thinning nature of bijels remains robust, regardless of particle morphology or applied magnetic 
-field. However, the flow index and yield stress trends were strongly dependent on these factors.  
-I found that increased particle ordering led to distinct yield stress behaviors: oblate particles resulted in a lower yield stress, while prolate particles exhibited a 
-higher yield stress. When examining the properties of the particle monolayer, I identified a clear impact of particle morphology on interparticle interactions at the 
-interface. In the absence of a magnetic field, both particle monolayers remained adsorbed at the interface. However, when a magnetic field was initially applied, the 
-behavior diverged significantly oblate particles flipped out of the interface to minimize interfacial energy, whereas prolate particles tilted out. These differences 
-directly influenced the shear response, altering how the surrounding fluid flows around the particles and leading to the observed non-Newtonian behavior and yield 
-stress characteristics.  
-Furthermore, I investigated the microstructural effects of shear and magnetic field-induced particle ordering and found that coarsening was the primary driver of 
-domain size evolution in sheared bijels. This coarsening was facilitated by a reduction in interfacial particle coverage. When analyzing the anisotropic domain size evolution, 
-I observed that in most cases, the direction of greatest structural change aligned with expected trends—except when the magnetic field was switched off. This deviation is 
-attributed to differences in particle monolayer evolution, depending on whether the bijel was formed with or without an initially applied field.
-
 % Previous investigations have 
@@
 % To characterize whether the domain size coarsening observed arises from different phenomena in each case, the area averaged curvature is plotted.
+
+\section{Conclusions}
+
+% In this chapter, I investigated the rheology of bijels stabilized by ellipsoidal particles under shear, focusing on the influence of initial microstructure and the 
+% application of a constant magnetic field on their shear response. The shear behavior was characterized using a Herschel-Bulkley fitting function to extract the flow index, 
+% consistency index, and yield stress. My analysis confirmed that the shear-thinning nature of bijels remains robust, regardless of particle morphology or applied magnetic 
+% field. However, the flow index and yield stress trends were strongly dependent on these factors.  
+% I found that increased particle ordering led to distinct yield stress behaviors: oblate particles resulted in a lower yield stress, while prolate particles exhibited a 
+% higher yield stress. When examining the properties of the particle monolayer, I identified a clear impact of particle morphology on interparticle interactions at the 
+% interface. In the absence of a magnetic field, both particle monolayers remained adsorbed at the interface. However, when a magnetic field was initially applied, the 
+% behavior diverged significantly oblate particles flipped out of the interface to minimize interfacial energy, whereas prolate particles tilted out. These differences 
+% directly influenced the shear response, altering how the surrounding fluid flows around the particles and leading to the observed non-Newtonian behavior and yield 
+% stress characteristics.  
+% Furthermore, I investigated the microstructural effects of shear and magnetic field-induced particle ordering and found that coarsening was the primary driver of 
+% domain size evolution in sheared bijels. This coarsening was facilitated by a reduction in interfacial particle coverage. When analyzing the anisotropic domain size evolution, 
+% I observed that in most cases, the direction of greatest structural change aligned with expected trends—except when the magnetic field was switched off. This deviation is 
+% attributed to differences in particle monolayer evolution, depending on whether the bijel was formed with or without an initially applied field.
+
+The rheological properties of bijels are of importance in many fabrication schemes such as STrIPS and homogenization. \cite{haase_continuous_2015,cai_bijels_2017}
+To characterize how magnetically responsive bijels can be used in these synthesis techniques, I studied the effect of particle morphology, initial microstructure and
+applied magnetic fields on the rheology of bijels experiencing a constant shear. Bijel templates made with $\bar{B} = 0$ and $\bar{B} = 1$ were selected, with field strengths
+of $\bar{B} = 0$ and $\bar{B} = 1$ applied to each template. This results in four processing histories per particle morphology namely $\bar{B}:0 \rightarrow 0$,
+$\bar{B}:0 \rightarrow 1$, $\bar{B}:1 \rightarrow 0$ and $\bar{B}:1 \rightarrow 1$. I then apply a constant shear rate onto each bijel.
+
+I first characterized the shear stress imparted by bijels under several strain rates. The shear stress calculated continued to increase in line with expectations
+for colloidal glasses as ageing occurs. Thus a pseudo-steady state was selected to compare the shear properties of the bijel.
+I fit the shear stress data using a Herschel Buckley fit and identify that the flow index of bijels stabilized by ellipsoidal 
+particles under magnetic fields became less shear thinning. The yield stress of bijels stabilized by oblate particles was shown to reduce by 4x while the yield stress
+of bijels stabilized by prolate particles was shown to increase by 2x upon application of magnetic fields.
+
+To characterize these differences, closer attention is paid to the particle monolayer of the bijel. Shear induced reorientation of the ellipsoids can be observed in cases
+where a magnetic field was used observed, characterized as the orientation of particles drift away from the magnetic field direction. When analyzing the effect this reorientation
+has on the particles at the interface, the interface angle in all cases increases as a function of the shear rate. However the quantitative behavior of oblate particles differ
+from prolate particles. Under magnetic fields, oblate particles tend to flip out of the interface while prolate particles tilt out of the interface. The impact that
+the particle tilting and flipping out of the interface can also be seen in the number of particles in the interface, where the differences in the particle morphology 
+can be characterized as differences in the number of particles at the interface in response to the magnetic field.
+
+A reduction in the number of particles at the interface and the particles tilting out of the interface reduces the interfacial coverage. The reduction in interfacial
+coverage manifests as domain coarsening, characterized as a smooth decrease in the magnitude of the area averaged Gaussian curvature. The changes in the particle monolayer
+properties manifest as changes in the evolution of the directional domain size evolution due to shear induced particle reorientation at the interface.
+
+Past literature
+has shown how bijels are susceptible to failure when being used as crossflow reactors due to shear induced domain coarsening resulting in microstructure failure. 
+\cite{boakye-ansah_controlling_2020} The investigations conducted here demonstrate that controlling the orientations of particles at interfaces are crucial to 
+the rheological properties of bijels. Other properties not considered here such as different particle aspect ratios, the effect of surface tension on the shear response of
+bijels and the volume fraction of particles are not considered here. Additionally, complex rheology of the bijels can determine detailed rheological properties such as the
+gel point and phase difference of the bijel which can yield further rheological characterization of bijels stabilized by magnetically responsive ellipsoidal particles.

### 2025-03-20 chapters/paper3.tex
Fixed some first person wording in aim 3

@@
 are more spread out suggesting that there is a larger variance in the properties arising from the change in the initial microstructure of the bijel. From the plot
-we can see that the increase in particle order reduces the yield stress of the bijel. For bijels stabilized by rod like particles, the stress response of each processing 
+the increase in particle order reduces the yield stress of the bijel. For bijels stabilized by rod like particles, the stress response of each processing 
 condition is closer together, indicating a smaller variation in the response to the applied magnetic field compared to oblate particles. The shear response upon application
@@
 while oblate particles reorient towards minimizing area to the applied shear direction. While these snapshots show the initial and final orientations of the particles at the
-interface, we can characterize the time evolution of the particle monolayer changes to identify its role in the rheological properties characterized.
+interface, the time evolution of the particle monolayer changes to identify its role in the rheological properties characterized.
 
@@
 stress, modifying the curvature of the interface and thus the lowest energy particle orientation to the interface or shear induced increases in
-interparticle forces, causing the particle to tilt out of the interface to minimize interparticle forces. We can characterize the latter 
-mechanism through measurements of the number of particles on the interface as increases in interparticle forces result in ejection of
+interparticle forces, causing the particle to tilt out of the interface to minimize interparticle forces. The latter 
+mechanism can be characterized through measurements of the number of particles on the interface as increases in interparticle forces result in ejection of
 particles from the interface.
@@
 From the results in Figure \ref{fig:particles_interface_prop_shear}, the impact of the initial microstructure on the number of particles on the interface
-differs for bijels stabilized by oblate and prolate ellipsoids. We split this analysis on processing history. While keeping the applied magnetic field
-the same, we see little differences in the behavior of $n_{int}$, with their behavior corresponding to changes in $\langle \psi \rangle$. 
+differs for bijels stabilized by oblate and prolate ellipsoids. I split this analysis on processing history. While keeping the applied magnetic field
+the same, little differences in the behavior of $n_{int}$ is observed, with small changes also being characterized for $\langle \psi \rangle$. 
 Looking at the case of $\bar{B}:0 \rightarrow 0$, there is little change in the number of particles at the interface upon application of shear. This implies that the 
 particles remain strongly adsorbed on the
-interface. The $\langle \psi \rangle$ results also show this as we see this parameter increasing slowly. This suggests that the particles remain firmly adsorbed
+interface. The $\langle \psi \rangle$ results also show this as this parameter increases slowly. This suggests that the particles remain firmly adsorbed
 on the interface. Looking to the $\bar{B}:0 \rightarrow 1$ case, the number of particles at the interface drops while $\langle \psi \rangle$ increases. This

### 2025-03-20 chapters/paper1.tex
Updated conclusion section in aim 1 and fixed non ascii characters in references

@@
 bijels formed in the absence of a magnetic field, I observed changes in
-domain size up to \(30\%\) for non-spherical particles. This effect can
+domain size up to \(30\%\) for non-spherical particles. When probing
+the differences in the microstructure, I identify that while the
+connectivity of the microstructure does not change, 
+the time evolution of the area averaged gaussian curvature shows that
+orientational ordering of the particles affects the shape of the
+coarsening interface. These shape differences are then locked into place
+upon jamming, resulting in a more hyperbolic interface in bijels stabilized
+by ellipsoidal particles upon application of magnetic fields. The frequency 
+of the number of channels changes as a function of distance from the interface. I
+characterize this as peak movements closer and further from the interface upon application of magnetic
+field, corroborating the microstructure anisotropy characterized.
+
+This effect can
 be explained by the re-orientation of the particle dipole axis with the
@@
 found that the angle between the particle dipole axis and the interface
-normal changes at this stage. Additionally, I analyzed the radial
+normal changes at this stage. Orientational ordering at the interface was
+observed to reduce for disc like particles and increase for rod like
+particles upon application of the magnetic field. I analyzed the radial
 distribution function of the particles and found that prolate particles

### 2025-03-21 chapters/analysis_techniques.tex
Changes 1. Updated aim 1 with first person wording 2. Updated aim 2 with first person wording and modified conclusion 3. Updated aim 3 with full size conclusion
Changes 1. Addressed some image sizes and phrasing consistency
Draft 1 complete

@@
 
-In this work, the structure factor derived domain size, geometric pore size distribution and tortuosity will be 
-utilized to characterize the microstructure. The nematic order parameter will be used to characterize the particle 
-order to the magnetic field. The average angle to the interface will be utilized to characterize how the particles 
-ordering to the field affect the interface position. Finally, the radial distribution function will be used to probe 
-how differences in ordering change the packing of particles on the interface. The time evolution of viscosity will 
-provide insight into the rheological properties of the bijel, while the aforementioned analysis tools in addition to 
-proportion of particles on the interface will be calculated to provide insight into how the bijel reacts to shear, 
-parallel and perpendicular to the magnetic field. A more detailed description of the implementation of each method is 
-shown in subsequent sections.
+Many techniques used in the bijel literature such as various definitions of the domain size,
+nematic order parameter, radial distribution function and shear stress calculation were used in the characterization
+of bijels in this work. \cite{kendon_inertial_2001, jansen_bijels_2011, gunther_timescales_2014} Other techniques such
+as the curvature and channel size distribution have also been used to characterize the microstructure of bijels. 
+\cite{reeves_quantitative_2016,chan_channel_2012} Additional techniques such as the interfacial angle
+and the Steinhardt order parameters. \cite{karthikeyan_formation_2024,steinhardt_bond-orientational_1983, mickel_shortcomings_2013}
+This section introduces each method and they are calculated. The implementation of each function can be found in my 
+\href{https://github.com/nkarthi95/schiller_lab_tools}{github repository}.
 
@@
 Particles are the cause of bijels but they can also make characterization of domain size, curvature, pore size 
-distribution and tortuosity more difficult as particles may change these parameters. An extrapolation scheme is 
+distribution and tortuosity more difficult as the presence of particles affects measurement of these parameters. 
+An extrapolation scheme is 
 required to connect the interface one different sides of the particles and to fill in the particles themselves so 
@@
 
-We use a method based on that outlined in Chan and Thornton. We create our distance function by performing an Eularian Distance Transform on 
+We use a method based on that outlined in Chan and Thornton. We create our distance function by performing an Eulerian Distance Transform on 
 our order parameter data $\phi$ to obtain $\phi_{edt}$. \cite{chan_channel_2012} We smooth $\phi_{edt}$ using a boxcar algorithm with side length 3. 
@@
     \centering
-    \includegraphics[scale = 0.4]{figures/analysis/csd_prep.png}
+    \includegraphics[scale = 0.5]{figures/analysis/csd_prep.png}
     \caption{Schematics detailing the order of operations of the steps to calculate the channel size distribution.}

### 2025-03-21 chapters/final_remarks.tex
Changes 1. Addressed some image sizes and phrasing consistency
Draft 1 complete

@@
 particle geometry. Particles based on cellulose nanocrystals or graphene nanoplates are now in use to fabricate
-particle stabilized emulsions.These particles have also been shown to have capillary bridging and particle stacking,
+particle stabilized emulsions. These particles have also been shown to have capillary bridging and particle stacking,
 not seen in the particles used in this work. These particles in bulk have been shown to have some intrinsic ordering
@@
 fields used here. One study on bijel microstructure showed that a gradient in the particle volume fraction can be used to 
-create a gradient in the eventual domain size. A gradient field may be able to generate a gradient in the nematic order 
-parameter, affecting the particle packing of the bijel at different heights and varying the pore size as a function of 
+create a gradient in the eventual domain size. A gradient field may be able to generate nematic order 
+parameter gradients, affecting the particle packing of the bijel at different heights and varying the pore size as a function of 
 height in the field gradient direction. In a ferrofluid or solution of magnetic colloids, a rotating field can assemble 
@@
 Science Foundation grants 2138259, 2138286, 2138307, 2137603, and 2138296.
+
+This research was supported in part through the use of DARWIN computing system: DARWIN - A Resource for Computational 
+and Data-intensive Research at the University of Delaware and in the Delaware Region, Rudolf Eigenmann, Benjamin E. 
+Bagozzi, Arthi Jayaraman, William Totten, and Cathy H. Wu, University of Delaware, 2021, URL: https://udspace.udel.edu/handle/19716/29071

### 2025-03-21 chapters/lit_review.tex
Changes 1. Addressed some image sizes and phrasing consistency
Draft 1 complete

@@
     \centering
-    \includegraphics[scale = 0.2]{figures/literature_review/state_diagram.jpg}
+    \includegraphics[scale = 0.3]{figures/literature_review/state_diagram.jpg}
     \caption{Formation criteria for a particle stabilized emulsion that can form bijel. \cite{velankar_non-equilibrium_2015}
@@
     \centering
-    \includegraphics[scale = 2]{figures/literature_review/bijel_under_shear.jpeg}
+    \includegraphics[scale = 3]{figures/literature_review/bijel_under_shear.jpeg}
     \caption{Schematic of a bijel with hard-sphere particles undergoing shear, demonstrating migration and detachment of 

### 2025-03-21 chapters/paper1.tex
Changes 1. Addressed some image sizes and phrasing consistency
Draft 1 complete

@@
 It is worth noting that this definition of average domain size does not necessarily yield values that coincide with the typical
-domain size observed visually in snapshots such as those shown in Fig.~\ref{fig:microstructure_viz}. However, in a dynamic
+domain size observed visually in snapshots such as those shown in Figure~\ref{fig:microstructure_viz}. However, in a dynamic
 scaling regime, different measures of domain size are expected to differ only by a constant ratio. I found that the commonly 
@@
 
-At first glance, the time-dependence of the domain size in Fig.
+At first glance, the time-dependence of the domain size in Figure 
 \ref{fig:domain_size} suggests that the domain size is not strongly
-affected by the external magnetic field. In Fig.\ref{fig:D2a_B}a) I
+affected by the external magnetic field. In Figure \ref{fig:D2a_B}a) I
 plotted the domain size measure \(L_d\) normalized by \(R\), the larger
@@
 \(10^4\Delta t\) and an intermittent plateau. The occurrence of this
-plateau coincides with the slowed decay of the coarsening speed in Fig.
+plateau coincides with the slowed decay of the coarsening speed in Figure
 \ref{fig:coarsening_velocity}. This change in the orientational ordering
@@
 \(2R_{\parallel}\), \(2R_{\perp}\), and \(R_{\parallel} + R_{\perp}\).
-These distances are marked by dashed lines in Fig. \ref{fig:rdf}. We
+These distances are marked by dashed lines in Figure \ref{fig:rdf}. We
 observe that the largest peak of the RDF coincides with the distance
@@
 magnetic field, which facilitates closer packing along both axes of the
-particles. It further suggests that particles arrange in layers, which can also be observed in the snapshot in Fig.
+particles. It further suggests that particles arrange in layers, which can also be observed in the snapshot in Figure
 \ref{fig:packing_viz}. Together with the analysis of nematic order

### 2025-03-21 chapters/final_remarks.tex
refined future work section
Changed I to we in results chapters

@@
 
-In Aim 3, I investigated the rheology of bijels stabilized by ellipsoidal particles under shear, examining the effects of initial microstructure and a 
-constant magnetic field on their shear response. Using a Herschel-Bulkley fitting, I found that while shear-thinning behavior remains robust, the 
+In Aim 3, the rheology of bijels stabilized by ellipsoidal particles under shear was analyzed, specifically examining the effects of initial microstructure and a 
+constant magnetic field on the shear response. Using a Herschel-Bulkley fitting, shear-thinning behavior remains robust although the 
 flow index and yield stress are strongly influenced by particle morphology and magnetic field application. Increased particle ordering led to 
@@
 particle stabilized emulsions. These particles have also been shown to have capillary bridging and particle stacking,
-not seen in the particles used in this work. These particles in bulk have been shown to have some intrinsic ordering
+not seen in the particles used in this work. These particles in bulk have been shown to have intrinsic ordering
 that can be predicted using onsager theory. An investigation into how using rods or plate like particles would be 

### 2025-03-21 chapters/paper1.tex
Changed I to we in results chapters

@@
 
-In this chapter, I investigate the effect of external magnetic fields on the formation of bijels stabilized by 
+In this chapter, We investigate the effect of external magnetic fields on the formation of bijels stabilized by 
 anisotropic magnetic particles. The microstructure of bijels stabilized with oblate, spherical and prolate particles, 
 namely the characteristic length scale and tortuosity, will be assessed as a function of the applied magnetic field
-strength. I also characterize the underlying mechanisms governing the observed behavior.
+strength. We also characterize the underlying mechanisms governing the observed behavior.
 
@@
 tortuosity of the void space and can be linked to the phase-separated
-morphology of the bijel template. Therefore, I study the domain size
+morphology of the bijel template. Therefore, We study the domain size
 and tortuosity of the phase morphology of bijels stabilized by
-anisotropic particles. In particular, I investigate the effect of
+anisotropic particles. In particular, We investigate the effect of
 magnetic particles on the microstructure of bijels that are formed in
-external magnetic fields. I simulated bijels with a particle volume
+external magnetic fields. We simulated bijels with a particle volume
 fraction of \(\phi_p=0.15\) and varied the magnetic flux density such
 that the Bond numbers varies in the range \(0\le\bar{B}\le1\).
-In this work, I use a fixed particle volume fraction and focus on the dependence of the 
+In this work, We use a fixed particle volume fraction and focus on the dependence of the 
 bijel structure on the magnetic field. Bijels with varying particle loading and surface tension 
@@
 domain size observed visually in snapshots such as those shown in Figure~\ref{fig:microstructure_viz}. However, in a dynamic
-scaling regime, different measures of domain size are expected to differ only by a constant ratio. I found that the commonly 
+scaling regime, different measures of domain size are expected to differ only by a constant ratio. We found that the commonly 
 used measure \(L_1(t)\) tends to overestimate the observed domain size. Numerically, the calculation of the spherically 
@@
 periodic boundary conditions is subject to finite size effects. More importantly, in suspensions of anisotropic particles, 
-I cannot expect that the structure factor is isotropic. Therefore, I also used the 3D structure factor to calculate a lateral domain 
+We cannot expect that the structure factor is isotropic. Therefore, we also used the 3D structure factor to calculate a lateral domain 
 size in each Cartesian direction from the second moments also defined in Section \ref{section:domain_size}. 
-\cite{jansen_bijels_2011,gunther_timescales_2014} I add the additional processing calculating a parallel and perpendicular domain size
-from the results in each cartesian direction, defining $L_{\parallel}=L_z$ and $L_{\perp} = \frac{L_x+L_y}{2}$ I plot the structure factor of the structures in
+\cite{jansen_bijels_2011,gunther_timescales_2014} We add the additional processing calculating a parallel and perpendicular domain size
+from the results in each cartesian direction, defining $L_{\parallel}=L_z$ and $L_{\perp} = \frac{L_x+L_y}{2}$ we plot the structure factor of the structures in
 Figure \ref{fig:structure_factor}.
@@
 \ref{fig:domain_size} suggests that the domain size is not strongly
-affected by the external magnetic field. In Figure \ref{fig:D2a_B}a) I
+affected by the external magnetic field. In Figure \ref{fig:D2a_B}a) we
 plotted the domain size measure \(L_d\) normalized by \(R\), the larger
@@
 volume. Furthermore, steric constraints prevent anisotropic particles to
-pack less densely in the interface than spherical particles, as I will
+pack less densely in the interface than spherical particles, as we will
 discuss in more detail below.
@@
 The magnetic field does have an effect on the directional
-domain size as shown in Figure \ref{fig:D2a_B} where I plotted the
+domain size as shown in Figure \ref{fig:D2a_B} where we plotted the
 domain size in the direction parallel and perpendicular to \(\vec{B}\)
-separately. I find that for prolate particles, the domain size in the
+separately. We find that for prolate particles, the domain size in the
 parallel direction increases with the field strength up to approximately
@@
 cross-section of prolate particles while \(\vec{m}\) is perpendicular to
-the larger cross-section of oblate particles. I thus expect that
+the larger cross-section of oblate particles. We thus expect that
 alignment of the particles with the magnetic field \(\vec{B}\)
@@
 whether these structural changes have an effect on macroscopic
-transport properties, I also characterized the tortuosity of the
+transport properties, we also characterized the tortuosity of the
 bijels. Various definitions of tortuosity have been proposed in the
 literature \cite{dasilva_tortuosity_2022}, including geometric,
-diffusional, and hydraulic tortuosity. Here I use the diffusional
+diffusional, and hydraulic tortuosity. Here we use the diffusional
 tortuosity $\tau= \frac{\epsilon D}{D_{\text{eff}}}$, i.e., the ratio of the 
 effective diffusivity $D_{\text{eff}}$ and the intrinsic diffusivity
-$D$. I calculate the tortuosity using the procedure detailed in Section \ref{section:tortuosity}
+$D$. We calculate the tortuosity using the procedure detailed in Section \ref{section:tortuosity}
 
@@
 this direction. The results show that the magnetic field has a
-noticeable effect on the tortuosity of the bijel. I observe that the
+noticeable effect on the tortuosity of the bijel. We observe that the
 largest change of tortuosity is measured at intermediate field strength
@@
 domains induces morphological changes that are more complex than a
-monotonic increase or decrease. I therefore turn to investigate the
+monotonic increase or decrease. We therefore turn to investigate the
 microstructural changes within the bijel morphology in more detail.
@@
 microstructure optimization for various applications.
-\cite{reeves_quantitative_2016} I plot the area averaged mean and
+\cite{reeves_quantitative_2016} We plot the area averaged mean and
 gaussian curvature \(H\Sigma^{-1}\) and \(K\Sigma^{-2}\) for bijels
@@
 ellipsoidal particles, the gaussian curvature becomes more negative as
-larger field strengths are applied. I also see that the gaussian
+larger field strengths are applied. We also see that the gaussian
 curvature becomes more positive as the interfacial area of the particle
@@
 The other proposed mechanism is that the time evolution of spinodal decomposition remains unaffected, but that the interface conforms to the magnetic field 
-driven arrangement of particles upon jamming. While I cannot apply the Gauss Bonnet theorem to characterize the results, I can still relate the coarsening 
+driven arrangement of particles upon jamming. While we cannot apply the Gauss Bonnet theorem to characterize the results, we can still relate the coarsening 
 behavior of the bijel through its change in genus to the curvature. The time evolution of the genus serves as a topological technique to characterize the 
 coarsening of the bijel, which alongside the $\langle K\Sigma^{-2} \rangle$, allows us to identify deviations from the coarsening behavior of bijels 
-stabilized with spherical particles, and with magnetic fields. I calculate the genus by extracting the isosurface of the filled order parameter, where 
+stabilized with spherical particles, and with magnetic fields. We calculate the genus by extracting the isosurface of the filled order parameter, where 
 $\phi = 0$. It is then meshed using the marching cubes algorithm implemented in scikit-image with a cube size of 1. \cite{van2014scikit} From the vertices(v) 
-and faces(f) generated from the marching cubes algorithm, I calculate the number of edges(e). The Euler Poincare characteristic, $\chi = n + f - e$. The genus is 
+and faces(f) generated from the marching cubes algorithm, we calculate the number of edges(e). The Euler Poincare characteristic, $\chi = n + f - e$. The genus is 
 then obtained from the Euler Poincare parameter as $g = 1 - \chi/2$.
@@
     \caption{Plots of Gaussian $\langle K \rangle \Sigma^{-2}$ curvature over time averaged across 3 runs. 
-    From left to right, I have particles with $\alpha = 0.5, 1, 2$. I observe that the initial stages of 
-    evolution are unaffected by the applied magnetic field. However, after about 10000 timsteps, I see a 
+    From left to right, We have particles with $\alpha = 0.5, 1, 2$. We observe that the initial stages of 
+    evolution are unaffected by the applied magnetic field. However, after about 10000 timsteps, We see a 
     magnetic field dependence on the evolution of the Gaussian curvature. The preservation of this divergence 
@@
 evolution of the surface corresponding to the interface is changed by the adsorption and orientation of magnetically responsive ellipsoidal particle. 
-I see effects of this change in $\langle G \rangle \Sigma^{-2}$ where I see the evolution of the curvature being delayed, indicated as a rightward 
+We see effects of this change in $\langle G \rangle \Sigma^{-2}$ where we see the evolution of the curvature being delayed, indicated as a rightward 
 shift of the plots as a function of the applied field.
 
-Despite all our curvature calculations being normalized with their surface area to volume ratio, I still see curvature differences as a function of the applied 
+Despite all our curvature calculations being normalized with their surface area to volume ratio, we still see curvature differences as a function of the applied 
 magnetic field. Experiments have identified that curvature changes can occur due to the formation of monogels, which are particle networks formed from bijels that 
-can withstand the remixing of their constituent liquids. \cite{sanz_colloidal_2009, lee_making_2013} This process cannot occur in our simulations as I am utilizing 
+can withstand the remixing of their constituent liquids. \cite{sanz_colloidal_2009, lee_making_2013} This process cannot occur in our simulations as we am utilizing 
 electrically neutral particles that only interact through contact forces. Therefore, the change in curvature arises from microstructure changes driven by particle 
@@
 topological technique to characterize the connectivity of surface as a function of a distance from the interface to calculate the channel size distribution. 
-\cite{chan_channel_2012} I can use the channel size distribution to investigate how the connectivity of the microstructure and thus the 
+\cite{chan_channel_2012} We can use the channel size distribution to investigate how the connectivity of the microstructure and thus the 
 channel size is affected as a function of the applied magnetic field.
@@
                  against the distance from the interface normalized with the characteristic length scale. The channel sizes obtained are averaged over 
-                 three runs. I see that the peak locations are shifted to larger and smaller positions for bijels stabilized with ellipsoidal particles
+                 three runs. We see that the peak locations are shifted to larger and smaller positions for bijels stabilized with ellipsoidal particles
                  upon field application} 
@@
 To shed light on the mechanisms involved in the coarsening dynamics,
-I now turn to the kinetics of bijel formation in more detail. The
+we now turn to the kinetics of bijel formation in more detail. The
 coarsening dynamics can be characterized by a coarsening speed. Here,
-I use the finite difference of the directional domain size to
+we use the finite difference of the directional domain size to
 calculate the components of the coarsening velocity
@@
 Figure \ref{fig:coarsening_velocity} shows the coarsening speed in the directions parallel and perpendicular to the applied magnetic field. 
-The data confirms that for spherical particles, domain coarsening remains isotropic. I observe a higher coarsening speed initially which slows 
+The data confirms that for spherical particles, domain coarsening remains isotropic. We observe a higher coarsening speed initially which slows 
 at later times when the particles begin to jam. This indicates that the
@@
 formation hinges on the jamming time in relation to the disruption time, i.e., the time scale at which domain pinch-off events can cause bijel break-up through 
-depercolation. In our simulations, however, I have not observed disruption of bijel formation; stable bijels form for all parameters consistent with simulations 
+depercolation. In our simulations, however, we have not observed disruption of bijel formation; stable bijels form for all parameters consistent with simulations 
 by Stratford et
@@
 is delayed compared with the perpendicular direction.
-In addition, I observe a shoulder (around \(10^4\Delta t\)) where the coarsening speed decays more slowly before jamming sets in.
+In addition, we observe a shoulder (around \(10^4\Delta t\)) where the coarsening speed decays more slowly before jamming sets in.
 These results suggest that the coarsening near the jamming time is affected by a mechanism that depends on the applied magnetic field and causes the anisotropic
@@
 particles and their alignment relative to the direction of the
-magnetic field. To confirm this hypothesis, I analyze the
+magnetic field. To confirm this hypothesis, we analyze the
 orientational order of the particles and their alignment relative to
@@
 
-To measure the particle alignment quantitatively, I computed the
+To measure the particle alignment quantitatively, we computed the
 nematic order tensor using the method detailed in Section \ref{section:nematic_order_parameter} 
@@
 \(S\approx 1.0\) towards the end of the simulation. For the prolate
-particles (\(\alpha=2.0\)), I observe a shoulder at around
+particles (\(\alpha=2.0\)), we observe a shoulder at around
 \(10^4\Delta t\) and an intermittent plateau. The occurrence of this
@@
 pronounced at the weakest magnetic field \(\bar{B}=0.2\). To further corroborate 
-this mechanism, I plot the time evolution of the orientational order of the interfaces.
+this mechanism, We plot the time evolution of the orientational order of the interfaces.
 
@@
 In the case of bijels, however, the percolating interfaces are tortuous
-and thus more mobile. I therefore posit that, rather than tilting out
+and thus more mobile. We therefore posit that, rather than tilting out
 of the interface, rotating particles can ``pull'' the interface along
@@
 Hence the prolate particles remain mostly aligned with the interface
-even in the stronger applied magnetic fields. I plot the interface angle of bijels
+even in the stronger applied magnetic fields. We plot the interface angle of bijels
 stabilized by ellipsoidal particles at the final timestep to demonstrate the differences
@@
         \caption{Visualizations of the particle monolayer at the last timestep shaded with the interface angle of each particle in red. The top and bottom
-                 rows correspond to snapshots of bijels with no field and a field strength of $\bar{B} = 1$ applied. I see that the oblate particles flip
+                 rows correspond to snapshots of bijels with no field and a field strength of $\bar{B} = 1$ applied. We see that the oblate particles flip
                  out of the interface into a non energetically favored position while the bijels stabilized with prolate particles tilt out of the interface
@@
 
-From Figure \ref{fig:psi_viz_ss} I can see the differences in the particle alignment to the interface characerizing the differences in $\psi$ observed. Oblate
+From Figure \ref{fig:psi_viz_ss} We can see the differences in the particle alignment to the interface characerizing the differences in $\psi$ observed. Oblate
 particles can be seen to tilt out of the interface more readily than prolate particles at the same magnetic field strength. Due to the strong surface tension
-between the fluids, the particles are strongly adsorbed onto the interface. I also see that the arrangement of particles on the interface is modified through the
-application of the magnetic field for both particle morphologies. I can obtain quantitative metrics regarding this ordering using the Steinhardt 2 and 6 fold
+between the fluids, the particles are strongly adsorbed onto the interface. We also see that the arrangement of particles on the interface is modified through the
+application of the magnetic field for both particle morphologies. We can obtain quantitative metrics regarding this ordering using the Steinhardt 2 and 6 fold
 order parameters, $\langle Q2 \rangle$ and $\langle Q6 \rangle$.
@@
 
-I select $\langle Q6 \rangle$ and $\langle Q2 \rangle$ as the bond order parameters to calculate as I am interested in identifying the point when ordering 
+We select $\langle Q6 \rangle$ and $\langle Q2 \rangle$ as the bond order parameters to calculate as We am interested in identifying the point when ordering 
 of the material changes. Kapfer et al. demonstrated that only using $\langle Q6 \rangle$ to identify the ordering of particles in the system can result in 
@@
 $\langle Q2 \rangle = 0$ can be used to characterize increasing disorder in a system. \cite{mickel_shortcomings_2013} By plotting $\langle Q6 \rangle$ and 
-$\langle Q2 \rangle$, I will be able to identify changes in the local ordering of the system even if I cannot directly assess the local structure quantitatively.
+$\langle Q2 \rangle$, we will be able to identify changes in the local ordering of the system even if We cannot directly assess the local structure quantitatively.
 
@@
     \caption{Time dependence of the mean two and six fold symmetry parameter, $\langle Q2 \rangle$ and $\langle Q6 \rangle$ 
-    for bijels stabilized with oblate(left), spherical(middle) and prolate(right) particles. I use $\langle Q2 \rangle$ as an
+    for bijels stabilized with oblate(left), spherical(middle) and prolate(right) particles. We use $\langle Q2 \rangle$ as an
     indicator of global particle translational order while $\langle Q6 \rangle$ is an indicator of local order.} 
@@
 
-From Figure \ref{fig:steinhardt_coverage}, I see an increase in disorder in all the bijel systems characterized as an increase in $\langle Q2 \rangle$. 
+From Figure \ref{fig:steinhardt_coverage}, we see an increase in disorder in all the bijel systems characterized as an increase in $\langle Q2 \rangle$. 
 This is a characteristic of how the particles were initialized and move once the simulation is initiated. The particles are initialized to be randomly placed 
 in the simulation domain with roughly equal spacing. As the interface sweeps through the simulation domain, particles irreversibly adsorb onto the interface 
-and move with the interface until the bijel jams. I see that $\langle Q2 \rangle$ is magnetic field dependent for oblate particles but not for the spherical 
-and prolate particles. I also see an aspect ratio dependence on the values characterized as differences in the time evolution of $\langle Q2 \rangle$. This 
+and move with the interface until the bijel jams. We see that $\langle Q2 \rangle$ is magnetic field dependent for oblate particles but not for the spherical 
+and prolate particles. We also see an aspect ratio dependence on the values characterized as differences in the time evolution of $\langle Q2 \rangle$. This 
 arises due to the differences in the aspect ratio of the particle causing them to arrange differently on the interface as the bijel microstructure evolves.
@@
 An increase in $\langle Q6 \rangle$ can indicate an increase in the number of particles adopting icosahedral symmetry at the interface of the amorphous 
-interface. \cite{kapfer_jammed_2012} However due to the amorphous nature of the arrangement of particles at the particle monolayer, I use this parameter 
+interface. \cite{kapfer_jammed_2012} However due to the amorphous nature of the arrangement of particles at the particle monolayer, we use this parameter 
 only to gauge changes in local arrangements of particles at the interface and make no commentary on specific interfacial arrangements. For oblate particles, 
-I characterize a reduction in local order as the applied field strength is increased, consistent with the increase in $\langle Q2 \rangle$. For prolate 
-particles, I observe that $\langle Q6 \rangle$ increases with the applied field. This indicates that the application of the field causes particles to have 
-increased local order, even if I see no discernible changes in $\langle Q2 \rangle$.
+we characterize a reduction in local order as the applied field strength is increased, consistent with the increase in $\langle Q2 \rangle$. For prolate 
+particles, we observe that $\langle Q6 \rangle$ increases with the applied field. This indicates that the application of the field causes particles to have 
+increased local order, even if we see no discernible changes in $\langle Q2 \rangle$.
 
@@
 interfaces than discs as the magnetic field causes the particles to align to the field. This better packing at the interface manifests as greater local ordering 
-Next, I analyze how these local toplogical changes affect the microstructure of the bijel by analyzing the channel size distribution of the bijels.
+Next, we analyze how these local toplogical changes affect the microstructure of the bijel by analyzing the channel size distribution of the bijels.
 
@@
 the magnetic field reduces the steric constraints within the interface.
-To corroborate this idea, I analyzed the radial distribution function
+To corroborate this idea, we analyzed the radial distribution function
 (RDF) of the particles, the calculation of which is detailed in Section
@@
 the local re-alignment of interfaces due to capillary interactions. In
-the case of prolate particles, I observed the shrinking interface can
+the case of prolate particles, we observed the shrinking interface can
 force particles to tilt out of their preferential alignment to facilitate
@@
 field, the domain size and tortuosity become anisotropic. Additionally,
-I observe that the particle packing in the interface becomes more
+we observe that the particle packing in the interface becomes more
 ordered due to the alignment effects.
@@
 
-In this work, I studied the effect of applied magnetic fields on the
+In this work, we studied the effect of applied magnetic fields on the
 formation of bijels stabilized by magnetic ellipsoidal particles. We
 considered oblate, spherical, and prolate particles with a permanent
-magnetic dipole moment suspended in a symmetric binary liquid. I found
+magnetic dipole moment suspended in a symmetric binary liquid. We found
 that, while the overall formation of a bijel is not disrupted by
@@
 tortuosity increases in the perpendicular direction. Compared with
-bijels formed in the absence of a magnetic field, I observed changes in
+bijels formed in the absence of a magnetic field, we observed changes in
 domain size up to \(30\%\) for non-spherical particles. When probing
-the differences in the microstructure, I identify that while the
+the differences in the microstructure, we identify that while the
 connectivity of the microstructure does not change, 
@@
 magnetic field, which in turn re-aligns the interfaces in the direction
-of the longer axis of the particles. I further corroborated this
+of the longer axis of the particles. We further corroborated this
 mechanisms by analyzing the coarsening speed and the nematic order of
-the particles and the interfaces. I found that jamming of particles is
+the particles and the interfaces. We found that jamming of particles is
 delayed in the direction of the longer ellipsoidal axis leading to
@@
 jamming coincides with a slow-down of the orientational ordering of the
-particles whereas the alignment of the interfaces increases. I also
+particles whereas the alignment of the interfaces increases. We also
 found that the angle between the particle dipole axis and the interface
@@
 observed to reduce for disc like particles and increase for rod like
-particles upon application of the magnetic field. I analyzed the radial
+particles upon application of the magnetic field. We analyzed the radial
 distribution function of the particles and found that prolate particles
 tend to align side by side, while the oblate particles exhibit a less
-regular arrangement. Based on these findings, I propose that bijel
+regular arrangement. Based on these findings, we propose that bijel
 formation in magnetic fields is governed by two coupled effects: During
@@
 \cite{jansen_bijels_2011,hijnen_bijels_2015}. With respect to possible
-experimental realizations of our simulations, I should emphasize that
-I have generally considered micron-size particles and have neglected
+experimental realizations of our simulations, we should emphasize that
+we have generally considered micron-size particles and have neglected
 thermal fluctuations. At the nanoscale, thermal fluctuations may in

### 2025-03-21 chapters/paper2.tex
Changes 1. Addressed some image sizes and phrasing consistency
Draft 1 complete
Removed some overhang from images in paper2.tex
Changed I to we in results chapters

--- 2025-03-19 chapters/paper2.tex
@@
 performance in each application is dependent upon the microstructure of the bijel template. Many of the applications listed above benefit 
-from stimuli response, allowing for in-situ microstructure tuning to offer reversible modifications of material permeability. In this section, I analyze
+from stimuli response, allowing for in-situ microstructure tuning to offer reversible modifications of material permeability. In this section, we analyze
 whether stimuli responsive bijels provide access to reversible structural modifications.
@@
 particle volume fraction of $\phi_p = 0.1$. We only focus on one system here as the mechanism for stimuli response shown in Aim 1 is identical
-for both systems. Therefore we expect that the qualitative trends between prolate and oblate particles will be matched. I select prolate particles
+for both systems. Therefore We expect that the qualitative trends between prolate and oblate particles will be matched. We select prolate particles
 as they are more readily synthesizable in experiments.
 
-I apply a constant magnetic field of $\bar{B}_z = 0.2$ onto bijels that were simulated 
-with no magnetic field. Once the microstructure has reached its new state, I ramp up the magnetic field to $\bar{B}_z = 0.5$ and 
-finally $\bar{B}_z = 1$. I then apply the opposite procedure to reduce the applied field strength, resulting in a magnetic field 
-ramp of $\bar{B}_z: 0 \rightarrow 0.2 \rightarrow 0.5 \rightarrow 1 \rightarrow 0.5 \rightarrow 0.2 \rightarrow 0$. I characterize the 
+We apply a constant magnetic field of $\bar{B}_z = 0.2$ onto bijels that were simulated 
+with no magnetic field. Once the microstructure has reached its new state, we ramp up the magnetic field to $\bar{B}_z = 0.5$ and 
+finally $\bar{B}_z = 1$. We then apply the opposite procedure to reduce the applied field strength, resulting in a magnetic field 
+ramp of $\bar{B}_z: 0 \rightarrow 0.2 \rightarrow 0.5 \rightarrow 1 \rightarrow 0.5 \rightarrow 0.2 \rightarrow 0$. We characterize the 
 microstructure changes observed through calculating the domain size, defined as the first moment of the spherically averaged structure factor. 
-I calculate the hysteresis 
-curve by selecting the domain size at the final timestep of each magnetic field change. I then plot these domain sizes against the magnetic field 
-applied to obtain them and split them in the descending and ascending magnetic field directions to demonstrate the differences observed. I plot 
+We calculate the hysteresis 
+curve by selecting the domain size at the final timestep of each magnetic field change. We then plot these domain sizes against the magnetic field 
+applied to obtain them and split them in the descending and ascending magnetic field directions to demonstrate the differences observed. We plot 
 these results in Figure \ref{fig:hysteresis_curve}
@@
     \includegraphics[scale=0.5]{../figures/results/paper2/hysteresis_curve.png} 
-    \caption{Plot of the hysteresis curve of a bijel stabilized by magnetically responsive prolate particles. I observe that the domain size increases as we 
+    \caption{Plot of the hysteresis curve of a bijel stabilized by magnetically responsive prolate particles. We observe that the domain size increases as we 
     increase the applied magnetic field strength. However, upon decrease of the applied field strength the microstructure does not return to its previous value,
@@
 in a kinetically trapped configuration. Cui et al. used spherical particles in their emulsion response experiments while we use ellipsoidal particles. Additionally,
-we also observe in Figure \ref{fig:hysteresis_curve} that the response of the bijel is dependent upon the field strength applied.
-In the following sections, I investigate the impact of magnetic field strength and the initial ordering of the particle monolayer on the observed stimuli response.
+Figure \ref{fig:hysteresis_curve} shows that the response of the bijel is dependent upon the field strength applied.
+In the following sections, we investigate the impact of magnetic field strength and the initial ordering of the particle monolayer on the observed stimuli response.
 
@@
 
-From the results in Figure \ref{fig:hysteresis_curve}, I show that the domain size change is dependent upon the applied magnetic field. As porous materials templates,
+From the results in Figure \ref{fig:hysteresis_curve}, we show that the domain size change is dependent upon the applied magnetic field. As porous materials templates,
 the microstructure of the material is of interest as it controls the performance of the material. Additionally, in many of the proposed stimuli responsive applications
 for bijels, the timescales of response is important to characterize and would also provide a mechanistic understanding of the reasons why the microstructure changes 
-occur. In this section, I analyze the structural response of bijels by assessing the response of bijels stabilized by particles with volume fraction of 
-$\phi_p = 0.1$ simulated under no applied field to an applied field in the range $\bar{B} = 0, 0.2, 0.5, 1$. I begin my investigation by visualizing the structure before 
+occur. In this section, we analyze the structural response of bijels by assessing the response of bijels stabilized by particles with volume fraction of 
+$\phi_p = 0.1$ simulated under no applied field to an applied field in the range $\bar{B} = 0, 0.2, 0.5, 1$. We begin our investigation by visualizing the structure before 
 and after the application of magnetic fields.
@@
 \includegraphics[scale=0.4]{../figures/results/paper2/microstructure_viz-field_on.png} 
-\caption{Visualizations of bijels stabilized by oblate and prolate particles simulated under no fields at $t = 0$ (left columns) and $t = 10^5$ (right columns).
-The first and third row detail the microstructure evolution for oblate and prolate particle stabilized bijels with no applied field while the second and fourth rows show bijels stabilized by oblate and prolate particles respectively with a field strength of $\bar{B} = 1$ applied.
-Particle reorientation to the direction of the field can be seen upon application of the magnetic field, resulting in microstructure changes driven through domain coarsening until the particles jam.
-We see similar behavior in bijels stabilized by oblate particles upon application of the magnetic field.}
+\caption{Visualizations of bijels stabilized by oblate and prolate particles simulated under no fields at $t = 0$ (left columns) and $t = 10^5$ (right columns). The first 
+         and third row detail the microstructure evolution for oblate and prolate particle stabilized bijels with no applied field while the second and fourth rows show 
+         bijels stabilized by oblate and prolate particles respectively with a field strength of $\bar{B} = 1$ applied. Particle reorientation to the direction of the 
+         field can be seen upon application of the magnetic field, resulting in microstructure changes driven through domain coarsening until the particles jam. We see 
+         similar behavior in bijels stabilized by oblate particles upon application of the magnetic field.}
 \label{fig:microstructure_viz-field_on} 
@@
 
-In Figure \ref{fig:microstructure_viz-field_on} I show representative snapshots of the bijel at the initial and final timestep with $\bar{B}_z = 0$ and $\bar{B}_z = 1$. 
+In Figure \ref{fig:microstructure_viz-field_on} we show representative snapshots of the bijel at the initial and final timestep with $\bar{B}_z = 0$ and $\bar{B}_z = 1$. 
 Upon application of the field, particles align to the direction of the field. As the particles orient to the field, they disrupt the packing of particles at
@@
 reduction in the available area that the particles have for stabilization. To characterize the length scale of the microstructure upon application of the magnetic field,
-I calculate the domain size. To correlate the microstructure evolution to the ordering of the particle monolayer to the magnetic field, I overlay the time evolution of the
+we calculate the domain size. To correlate the microstructure evolution to the ordering of the particle monolayer to the magnetic field, we overlay the time evolution of the
 nematic order parameter on the domain size. \cite{veerman_phase_1992}
@@
 \includegraphics[scale=0.5]{../figures/results/paper2/domain_size-field_on.png} 
-\caption{Plotting the spherically averaged domain size normalized with $R_p$($L/R$) of the particle at different magnetic field strengths, $\bar{B}$, and the nematic order parameter $S$ in lines.
-We quantify the domain size and ordering of the particles, and show that the change in both parameters are correlated with the strength of the applied magnetic field.}
+\caption{Plotting the spherically averaged domain size normalized with $R_p$($L/R$) of the particle at different magnetic field strengths, $\bar{B}$, and the nematic order 
+         parameter $S$ in lines. We quantify the domain size and ordering of the particles, and show that the change in both parameters are correlated with the strength of 
+         the applied magnetic field.} 
 \label{fig:domain_size-field_on} 
@@
 
-I normalized the domain size results by the volume equivalent sphere radius, $R = 7.9$ in Figure \ref{fig:domain_size-field_on} The results indicate that upon 
+We normalized the domain size results by the volume equivalent sphere radius, $R = 7.9$ in Figure \ref{fig:domain_size-field_on} The results indicate that upon 
 applying a magnetic field to a bijel initially formed without one, the final average domain size increases by up to 5.2\% and 2.5\% for oblate and 
@@
 Precise characterization of the anisotropic microstructure is essential for the tailored design of application-specific porous materials. To
-quantify the characteristic length scales in each Cartesian direction, I compute the second-moment-derived structure factor. \cite{jansen_bijels_2011} 
-I also calculate the tortuosity  in each cartesian direction. I make a further
-refinement simplifying the domain sizes to directions parallel and orthogonal to the magnetic field. These result in the length scales and
+quantify the characteristic length scales in each Cartesian direction, we compute the second-moment-derived structure factor. \cite{jansen_bijels_2011} 
+We make a further refinement simplifying the domain sizes to directions parallel and orthogonal to the magnetic field. These result in the length scales and
 their associated calculation, $L_{\parallel} = L_{z}$ and $L_{\perp} = \frac{L_x + L_y}{2}$. The same simplification
@@
 the diffusional tortuosity, $\tau = \frac{D}{D_{eff}}$ which characterizes the ratio between the free diffusion of a tracer and the
-effective diffusion of a tracer in the material. I plot the directional second moment derived length scales and tortuosity in
+effective diffusion of a tracer in the material. We plot the directional second moment derived length scales and tortuosity in
 Figure \ref{fig:domain_size_aniso-field_on}.
@@
 From Figure \ref{fig:domain_size_aniso-field_on}, domain size anisotropy is observed upon application of the field for both
-particle morphologies. I also see some domain anisotropy with no applied field, which increases upon application of the magnetic field.
+particle morphologies. Some domain anisotropy with no applied field is observed, which increases upon application of the magnetic field.
 The directional domain sizes, $L_{\perp}$ and $L_{\parallel}$ increase by 73\% and 7\%\ respectively for oblate particles and
@@
 Lattice Boltzmann simulations. \cite{luo_macroscopic_2020} Upon application of the field, $\tau_{\perp}$ slightly decreases while $\tau_{\parallel}$
-increases. In Chapter \ref{chapter:aim1}, I characterized that increasing the domain size decreases the tortuosity. \cite{karthikeyan_formation_2024} This
+increases. In Chapter \ref{chapter:aim1}, we characterized that increasing the domain size decreases the tortuosity. \cite{karthikeyan_formation_2024} This
 observation is in line with the domain size changes observed in Figure \ref{fig:domain_size_aniso-field_on}. The results show that the
@@
 
-Next, I return to investigate the time gap between the average domain size increase and the nematic order parameter. This result suggests that the dynamics 
+Next, we investigate the time gap between the average domain size increase and the nematic order parameter. This result suggests that the dynamics 
 of the system at higher magnetic field strengths are dependent upon other factors that vary upon application of the magnetic field. In this system, these factors
 would arise from capillary forces with the interface or steric interactions with other particles at the interface, slowing down the dynamics of the system.
-To understand this phenomena, I focus on the dynamics of the particle monolayer. First, I visualize the particle monolayer of the bijels stabilized with prolate 
+To understand this phenomena, we focus on the dynamics of the particle monolayer. First, we visualize the particle monolayer of the bijels stabilized with prolate 
 ellipsoids at the initial and final configuration before and after application of a magnetic field.
@@
 
-In Figure \ref{fig:particle_viz-field_on}, I see the initial configuration of particles at the monolayer show that the orientations are random and that the 
+In Figure \ref{fig:particle_viz-field_on}, we see the initial configuration of particles at the monolayer show that the orientations are random and that the 
 particles tend to lie flat on the interface. However, upon application of the magnetic field the particles orient to the field direction. With no applied field,
-I see that the orientations and positions of the particles vary slightly for both ellipsoidal particle morphologies. This effect is due steric effects between particles,
-as identified in Gunther et al. \cite{gunther_timescales_2014} I observe that for bijels stabilized by prolate ellipsoids, we see the adoption of orientational order
+the orientations and positions of the particles vary slightly for both ellipsoidal particle morphologies. This effect is due steric effects between particles,
+as identified in Gunther et al. \cite{gunther_timescales_2014} Bijels stabilized by prolate ellipsoids, adopt orientational order
 to the magnetic field and qualitatively different particle arrangements on the interface. These indicate that the interfacial capillary forces or steric interactions 
@@
 the interface that can temporarily reduce the interfacial coverage of the particles on the interface, temporarily making the particle monolayer more liquid-like
-than amorphous. \cite{hunter_physics_2012} Using this approximation, I can use the local crystallization result shown in Toxvaerd.
+than amorphous. \cite{hunter_physics_2012} Using this approximation, we can use the local crystallization result shown in Toxvaerd.
 
@@
 \centering 
-\includegraphics[scale=0.3]{../figures/results/paper2/interface_angle-nint-field_on.png} 
+\includegraphics[scale=0.5]{../figures/results/paper2/interface_angle-nint-field_on.png} 
 \caption{Plots of the interface angle $(\langle \psi \rangle)$ and six fold Steinhardt order parameter $(\langle Q6 \rangle)$ on the left and right respectively, 
-         versus time for bijels stabilized with oblate and prolate ellipsoids on the top and bottom rows respectively. We demonstrate that upon application 
+         versus time for bijels stabilized with oblate and prolate ellipsoids on the top and bottom rows respectively. I demonstrate that upon application 
          of a magnetic field, the behavior of $(\langle \psi \rangle)$ and $(\langle Q6 \rangle)$ differ significantly between oblate and prolate ellipsoids 
-         indicating that the dynamics for both particle morphologies differ. We also observe magnetic field dependence in each property for both particle types, 
+         indicating that the dynamics for both particle morphologies differ. I also observe magnetic field dependence in each property for both particle types, 
          suggesting that these changes are driven primarily through the change in the applied field strength.} 
@@
 From Figure \ref{fig:interface_angle-nint-field_on}, we identify that prolate and oblate particles respond differently at the interface. For
-bijels stabilized by oblate ellipsoids, I characterize an increase in $\langle \psi \rangle$ from an initial value of $19 ^{\circ}$,
+bijels stabilized by oblate ellipsoids, we characterize an increase in $\langle \psi \rangle$ from an initial value of $19 ^{\circ}$,
 before it reduces slightly and begins to increase once again. The initial starting value of $\langle \psi \rangle$ indicates the
@@
 large adsorption energy of the particles at the interface of the bijel, caused by high surface tension. Finally, the particles jam in place,
-locking the interface at an angle to the particle. We see the rate of increase in $\langle \psi \rangle$ at early stages and the time spent
+locking the interface at an angle to the particle. The rate of increase in $\langle \psi \rangle$ at early stages and the time spent
 in the plateau increase with a larger applied magnetic field. The final angle at the interface is also dependent upon the applied field
@@
 When analyzing $\langle \psi \rangle$ for bijels stabilized by prolate particles, this behavior can also be observed. $\langle \psi \rangle$
-begins at $10 ^{\circ}$.We see $\langle \psi \rangle$ increases, before plateauing and slowly decreasing. The initial peak height and rate of increase in 
+begins at $10 ^{\circ}$. $\langle \psi \rangle$ increases, before plateauing and slowly decreasing. The initial peak height and rate of increase in 
 $\langle \psi \rangle$ is field dependent, although given the small decrease in $\langle \psi \rangle$ it is unclear if the final value of this parameter 
@@
 of bijels stabilized by prolate particles tilt out of the interface with no metastable configurations observed. This effect explains the trends seen in $\langle \psi \rangle$
-at long times for both particle morphologies. This particle flipping on the interface affects the way the particles can arrange on the interface, like what I 
+at long times for both particle morphologies. This particle flipping on the interface affects the way the particles can arrange on the interface, like what we 
 characterized In Figure \ref{fig:rdf}. This change in local ordering can be quantified using $\langle Q6 \rangle$.
@@
 From Figure \ref{fig:interface_angle-nint-field_on} the dynamics of $\langle Q6 \rangle$ are particle morphology specific but can be split into three sections for 
-both particle morphologies. Characterizing the time evolution of $\langle Q6 \rangle$ for oblate particles, I see a decrease upon application of the magnetic field, 
+both particle morphologies. Characterizing the time evolution of $\langle Q6 \rangle$ for oblate particles, we see a decrease upon application of the magnetic field, 
 followed by a plateau and finally a gradual increase before jamming takes place, seen as a significant decrease in the rate of chang to $\langle Q6 \rangle$.
@@
 
-I observe that for bijels stabilized by prolate particles, the interface ordering of the particles increases as a
+We observe that for bijels stabilized by prolate particles, the interface ordering of the particles increases as a
 function of the applied field strength. The first phase of the evolution of $\langle Q6 \rangle$ sees some growth in $\langle Q6 \rangle$ before 
@@
 Thus far, three particle based phenomena have been characterized; the orientation of the particle to the magnetic field, the interface and the local 
-arrangement of the particles on the interface. I can calculate a timescale for each factor from the plots of each of these properties.
+arrangement of the particles on the interface. we can calculate a timescale for each factor from the plots of each of these properties.
 The nematic order parameter $S$ represents the ordering of
@@
 response rate limited to the response to the magnetic field, which
-indicates a particle-field orientation dependence. I name this
-timescale $\tau_S$. When applying a field to a bijel system with a
+indicates a particle-field orientation dependence named $\tau_S$. When applying a field to a bijel system with a
 randomly oriented particle monolayer, the most significant transition
@@
 
-I can also do the same for $\langle \psi \rangle$ and
+We can also do the same for $\langle \psi \rangle$ and
 $\langle Q6 \rangle$. A timescale derived from
@@
 represents the capillary timescale between the interface and the
-particle. Given the shape of the plot, we assign the
+particle. Given the shape of the plot, we assign
 $\tau_{\langle \psi \rangle}$ to be the time when the first minimum of
@@
 omit \(\bar{B} = 0\) as previous results have identified the domain size
-changes observed there. I then plot the average domain size $L$
+changes observed there. We then plot the average domain size $L$
 against time rescaled with these three timescales in Figure
@@
 \includegraphics[scale=0.4]{../figures/results/paper2/domain_size-field_on-scaled.png} 
-\caption{Plots of domain size with different timescales.
-The top and bottom row represent the average domain size for bijels stabilized with oblate and prolate particles respectively.
-The figures on the left plots the domain size against time rescaled with the nematic to isotropic transition time, $\tau_S$.
-The figures in the middle plot the domain size against time rescaled with the interfacial capillary timescale, $\tau_{\langle \psi \rangle}$.
-The figures on the right plot the domain size against time rescaled with the particle rearrangement timescale, $\tau_{\langle Q6 \rangle}$.
-We show that the controlling timescale when applying a magnetic field onto bijels with disordered particles is the latter timescale, indicating that the dominating effect is steric hindrance of the particles during rearrangment at the interface.}
+\caption{Plots of domain size with different timescales. The top and bottom row represent the average domain size for bijels stabilized with oblate and 
+         prolate particles respectively. The figures on the left plots the domain size against time rescaled with the nematic to isotropic transition time, 
+         $\tau_S$. The figures in the middle plot the domain size against time rescaled with the interfacial capillary timescale, $\tau_{\langle \psi \rangle}$. 
+         The figures on the right plot the domain size against time rescaled with the particle rearrangement timescale, $\tau_{\langle Q6 \rangle}$. We show 
+         that the controlling timescale when applying a magnetic field onto bijels with disordered particles is the latter timescale, indicating that the 
+         dominating effect is steric hindrance of the particles during rearrangment at the interface.} 
 \label{fig:domain_size-field_on-scaled} 
@@
 using the particle steric effects timescale, denoted by $\tau_{\langle Q6 \rangle}$,
-I conclude that the dynamics of bijels stabilized by ellipsoidal particles are controlled by
+We conclude that the dynamics of bijels stabilized by ellipsoidal particles are controlled by
 interfacial particle rearrangement at the interface.
@@
 jump, suggesting that the ordering of the particles is linked to the
-domain size change observed. In the previous section, I saw that domain
+domain size change observed. In the previous section, We saw that domain
 size changes in bijels after jamming are constrained by magnetic field
 driven local rearrangement of the particle monolayer. In this section,
-I explore how pre-existing order in the particles affect the degree of
+we explore how pre-existing order in the particles affect the degree of
 domain size change observed. We apply fields of strength
@@
 create bijels stabilized with ellipsoidal particles with pre-existing
-particle order. I then apply a field strength of $\bar{B}_z = 1$ and
+particle order. We then apply a field strength of $\bar{B}_z = 1$ and
 observe the time evolution of the system for $t = 10^5$ timesteps. I
@@
 field, and a field of $\bar{B}_z = 1.0$ applied during the simulations conducted here. 
-I begin by visualizing the microstructure
+We begin by visualizing the microstructure
 changes experienced by bijels simulated with pre-existing particle order
@@
          field of $\bar{B}_z = 0.2$. The second and fourth rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids 
-         respectively with an applied field of $\bar{B}_z = 1$. I increase the applied field to $\bar{B}_z = 1$ in both cases and show that particle 
+         respectively with an applied field of $\bar{B}_z = 1$. We increase the applied field to $\bar{B}_z = 1$ in both cases and show that particle 
          reorientation to the field occurs at the $\bar{B}_z = 0.2$ but not in the $\bar{B}_z = 1$ case.}
@@
 
-In Figure \ref{fig:microstructure_viz-field_up} I show representative
+In Figure \ref{fig:microstructure_viz-field_up} We show representative
 snapshots of a bijel stabilized with prolate particles at the initial
@@
 $\bar{B}_z: 1.0 \rightarrow 1.0$ in the top and bottom rows
-respectively. I show that upon application of the field, the fluid
+respectively. We show that upon application of the field, the fluid
 domains undergo a field strength dependent microstructrue response, with
 the degree of response dependent upon the difference between the initial
-and final magnetic field. I also observe a qualitative increase in the
+and final magnetic field. We also observe a qualitative increase in the
 alignment of the particles to the magnetic field for the
-$\bar{B}_z: 0.2 \rightarrow 1.0$ case. I quantify these observations
+$\bar{B}_z: 0.2 \rightarrow 1.0$ case. We quantify these observations
 by plotting the average domain size and nematic order parameter in
@@
 \caption{Plot of the spherically averaged domain size normalized with $Rp(L/R)$ of the particle in markers and the nematic order parameter in lines. 
-         I show that the domain size change measured is correlated to the change in the particle ordering, characterized using the nematic order parameter.} 
+         We show that the domain size change measured is correlated to the change in the particle ordering, characterized using the nematic order parameter.} 
 \label{fig:domain_size-field_up} 
@@
 
-In Figure \ref{fig:domain_size-field_up}, I define the difference
+In Figure \ref{fig:domain_size-field_up}, We define the difference
 between the final and initial magnetic field strengths as
@@
 coarsening dynamics. To further quantify the anisotropic microstructural
-evolution, I define the relative change in domain size as
+evolution, We define the relative change in domain size as
 $\Delta L = \frac{L_{f} - L_{i}}{L_{i}}$, where $L$ represents
@@
 \caption{Plotting the anisotropic domain sizes and tortuosity at the final timestep on the left and right respectively for bijels stabilized with 
-         oblate and prolate ellipsoidal particles starting at different particle orders. I plot these results against the change in the applied field 
-         strength, $\Delta B$. We show that the anisotropic domain size is inversely correlated to the tortuosity. We see that $L_{perp}$ changes for 
+         oblate and prolate ellipsoidal particles starting at different particle orders. We plot these results against the change in the applied field 
+         strength, $\Delta B$. The anisotropic domain size is inversely correlated to the tortuosity and $L_{perp}$ changes for 
          a bijel made with $\bar{B} = 1 \rightarrow 1$ and $\bar{B}: 0 \rightarrow 1$ differ, suggesting that the processing history of the bijel is important.} 
@@
 prolate particles. To characterize how the particle order changes on the
-interface as a function of the magnetic field strength, I visualize the
+interface as a function of the magnetic field strength, we visualize the
 particle monolayer of bijels stabilized by prolate particles in Figure
@@
          field of $\bar{B}_z = 0.2$. The second and fourth rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids 
-         respectively with an applied field of $\bar{B}_z = 1$. I increase the applied field to $\bar{B}_z = 1$ in both cases and show that particle 
+         respectively with an applied field of $\bar{B}_z = 1$. We increase the applied field to $\bar{B}_z = 1$ in both cases and show that particle 
          reorientation to the field occurs at the $\bar{B}_z = 0.2$ but not in the $\bar{B}_z = 1$ case.} 
@@
 
-In Figure \ref{fig:particle_viz-field_up}, I see the effect of the
+In Figure \ref{fig:particle_viz-field_up}, we see the effect of the
 application of the magnetic field on the monolayer. The initial
@@
 origin of the microstructure anisotropy. To understand how the particle
-reorientation at the interface causes microstructure reorientation I
+reorientation at the interface causes microstructure reorientation we
 quantify the average interface angle, $\langle \psi \rangle$ and the
@@
 
-\begin{figure} 
-\centering 
-\includegraphics[scale=0.4]{../figures/results/paper2/interface_angle-nint-field_up.png} 
-\caption{Plots of the average interfacial angle $\psi$ and the number of particles on the interface $n_{int}$ on the left and right respectively, 
-         plotted against time for bijels stabilized with ellipsoidal particles with aspect ratio 2. When looking at $\psi$, a change in dynamics can be 
-         seen as the initial particle order increases. When looking at $n_{int}$, different dynamics are seen above and below the isotropic to nematic transition point. 
-         Both results suggest that the ordering of particles is linked to the dynamics of domain coarsening.} 
-\label{fig:interface_angle-nint-field_up} 
-\end{figure}
-
 Figure \ref{fig:interface_angle-nint-field_up} shows that
 prolate and oblate particles respond differently at the interface upon application of a magnetic field
-even with pre-existing ordering of the particles. I
+even with pre-existing ordering of the particles. We
 show that there are three time evolution trends for
@@
 stabilized by prolate particles. $\langle \psi \rangle$ begins near
-$11 ^{\circ}$. We see a decrease before reorientation ceases, and
-finally $\langle \psi \rangle$ increases again.
+$11 ^{\circ}$ and decrease before reorientation ceases before
+$\langle \psi \rangle$ increases again.
 
@@
 
-For both particle morphologies I analyze the response of bijels with a
+\begin{figure} 
+    \centering 
+    \includegraphics[scale=0.4]{../figures/results/paper2/interface_angle-nint-field_up.png} 
+    \caption{Plots of the average interfacial angle $\psi$ and the number of particles on the interface $n_{int}$ on the left and right respectively, 
+             plotted against time for bijels stabilized with ellipsoidal particles with aspect ratio 2. When looking at $\psi$, a change in dynamics can be 
+             seen as the initial particle order increases. When looking at $n_{int}$, different dynamics are seen above and below the isotropic to nematic transition point. 
+             Both results suggest that the ordering of particles is linked to the dynamics of domain coarsening.} 
+    \label{fig:interface_angle-nint-field_up} 
+\end{figure}
+
+For both particle morphologies we analyze the response of bijels with a
 field history of $\bar{B}: 0.5 \rightarrow 1$ and
-$\bar{B}: 1 \rightarrow 1$. We see a decrease in
-$\langle Q6 \rangle$ for bijels stabilized with oblate particles with
+$\bar{B}: 1 \rightarrow 1$.
+$\langle Q6 \rangle$ decreases for bijels stabilized with oblate particles with
 field application of $\bar{B}: 0.5 \rightarrow 1$ compared to an
@@
 particles rearrange over time to lie flatter on the interface. For
-bijels stabilized with prolate particles, I characterize a difference
+bijels stabilized with prolate particles, We characterize a difference
 in behavior between $\bar{B}: 0.5 \rightarrow 1$ and
 $\bar{B}: 1 \rightarrow 1$. For the $\bar{B}: 0.5 \rightarrow 1$
-case, we see a slight increase in $\langle \psi \rangle$ before a
-decrease and increase compared to the $\bar{B}: 1 \rightarrow 1$ case
-where we characterize a slight decrease over time. I also characterize
+case, a slight increase in $\langle \psi \rangle$ before a
+decrease and increase is seen compared to the $\bar{B}: 1 \rightarrow 1$ case
+where we characterize a slight decrease over time. We also characterize
 a slight decrease in $\langle Q6 \rangle$ over time for the
@@
 the particles take up a arrangements not observed when no field is
-applied. In this section, I explore how removal of the magnetic field
+applied. In this section, we explore how removal of the magnetic field
 changes the microstructure of the bijel as a function of the initial
@@
 $\bar{B}_{template} = 0, 0.2, 0.5, 1$ during formation of the bijel. Once
-the microstructure has stabilized, I switch off the magnetic field and
+the microstructure has stabilized, we switch off the magnetic field and
 observe the time evolution of the system for $t = 10^5$ timesteps.
@@
          field of $\bar{B}_z = 0.2$. The second and fourth rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids 
-         respectively with an applied field of $\bar{B}_z = 1$. I switch off the applied field in both cases and show that while particle reorientation 
+         respectively with an applied field of $\bar{B}_z = 1$. We switch off the applied field in both cases and show that while particle reorientation 
          occurs, it has little effect on the microstructure of the bijel.}
@@
 $\bar{B}:0.2 \rightarrow 0$ (top) and $\bar{B}:1 \rightarrow 0$
-(bottom). We see that when switching the field off, the microstructure
+(bottom). When switching the field off, the microstructure
 remains largely the same, demonstrating the kinetic stability of bijels.
@@
 magnetic field during bijel template simulation does not play a
-significant role in the dynamics of the bijel. I attribute the large
+significant role in the dynamics of the bijel. We attribute the large
 increase in the domain size in oblate particle stabilized
 $\bar{B}:0\rightarrow0$ case to be due to coalescence of two
-domains, characterized as a two step process where we see slower long
-timescale domain coarsening initially followed by a rapid jump in the
-domain size.
+domains, characterized as a two step process where slower long
+timescale domain coarsening initially occurs followed by a rapid jump in the
+domain size when coalscence between domains occur.
 
@@
 the interface. To quantify is the coarsening that takes place is
-anisotropic, I define the relative change in domain size as
+anisotropic, We define the relative change in domain size as
 $\Delta L = \frac{L_{f} - L_{i}}{L_{i}}$, where $L$ represents
 either $L_{\perp}$ or $L_{\parallel}$. The same formulation is
-applied to the tortuosity in the respective directional components. I
+applied to the tortuosity in the respective directional components. We
 do this to characterize the $\Delta \bar{B}$ dependent changes
@@
          prolate ellipsoidal particles starting at different particle orders. We plot these results against the change in the applied field strength, 
-         $\Delta B$. I show that there are only minor differences in the microstructure of stimuli responsive bijels once the magnetic field is switched off.} 
+         $\Delta B$ and show that there are only minor differences in the microstructure of stimuli responsive bijels once the magnetic field is switched off.} 
 \label{fig:domain_size_aniso-field_down} 
@@
 dependent upon the capillary interactions with the particle monolayer.
-I showed earlier that the application of magnetic fields change the
+We showed earlier that the application of magnetic fields change the
 local state of the particles at the interface. However the results shown
@@
 From Figure \ref{fig:interface_angle-field_down}, there are minor differences to the time when $\langle \psi \rangle$ and $\langle Q6 \rangle$
-begin to change. I also characerize that $\langle \psi \rangle$ increases for both particle morphologies, even for systems that have initial ordering.
+begin to change. We also characerize that $\langle \psi \rangle$ increases for both particle morphologies, even for systems that have initial ordering.
 Similarly, $\langle Q6 \rangle$ decreases for all systems. Thus, the presence of ordering does not greatly affect trends in the evolution of the
@@
 driving force behind microstructure changes in the absence of a magnetic
-field. Even though I observe that the interface angle and Steinhardt
+field. Even though we observe that the interface angle and Steinhardt
 order parameter show substantial changes from the scenario where no
@@
 
-In this chapter, I identified that bijels stabilized by magnetically responsive particles exhibit microstructural hysteresis upon the application and removal of a 
-magnetic field. This hysteresis is characterized by the ability to alter microstructure when increasing the applied field, but an inability to do so when switching 
-the field off. When examining the effect of an applied magnetic field on domain size evolution in bijels initially lacking particle ordering, I found that domain 
-size changes correlate with field strength and are accompanied by microstructural anisotropy.
-By analyzing response timescales, I determined that the structural evolution arises primarily from particle reorientation at the interface. I then investigated 
-how the initial particle order in the direction of the magnetic field influences the response and found that the magnitude of the observed response depends on 
-the difference between the initial and final states of the particle monolayer. A closer examination of the monolayer revealed that many characteristic behaviors 
-observed in initially disordered systems were absent, indicating a distinct response mechanism.
-Finally, I explored why pre-existing particle order at the interface did not lead to different microstructural behavior upon field removal. I demonstrated that under 
-the given system parameters, the evolution of the particle monolayer was identical in all cases, suggesting that interface dynamics are governed by particle rearrangements 
-aimed at minimizing interfacial energy.
+\section{Conclusions}
+
+Owing to the applicability of bijels in the catalyst support, filtration membrane and drug release spaces, we were interested in identifying how bijels stabilized 
+by magnetically responsive ellipsoidal particles could be used to create active soft matter. In this work, we have studied the effect of the application, increase 
+or removal of magnetic fields on the structural response of bijels stabilized by magnetically responsive ellipsoids using hybrid Lattice Boltzmann-Molecular Dynamics 
+simulations. We first characterized the hysteresis curve of the bijel, identifying that the process history dependence of the bijel microstructure. To identify why 
+We observed the path dependence and the microstructure change observed when applying magnetic fields after synthesis, we considered three starting setups; The first 
+applying a field of varying strength to bijel templates that were simulated with no magnetic field applied. The second involved increasing the applied field 
+strength onto bijel templates that were simulated with increasing field strengths. The final setup involves removing a field from bijel templates that were simulated 
+with various field strengths.
+
+We found that application of magnetic fields onto bijels stabilized by magnetically responsive ellipsoidal particles results in an average microstructure change up to 
+$5\%$ when investigating changes in the average microstructure. We also identified that the structures become anisotropic upon application of the magnetic field for 
+oblate and prolate particles. The anisotropy is particle dependent with bijels stabilized by oblate particles seeing an increase in $L_{\perp}$ of up to $60\%$ and for 
+prolate particles an increase in $L_{\parallel}$ of up to $40\%$ with a corresponding decrease in the tortuosity in that axis. This is caused by the reorientation of the 
+particles to the magnetic field, followed by domain coarsening as the interfacial coverage of the particles decrease, before jamming in place again. We characterize that 
+while particle reorientation to the applied field initiates microstructural response, local rearrangement of the particle monolayer is the controlling mechanism of 
+domain size evolution as characterized by identifying the dominant timescales 
+of response for both particle morphologies. However, their time evolution is different with bijels stabilized by prolate particles undergoing a local crystallization when 
+the average six fold Steinhardt order parameter or $\langle Q_6 \rangle \geq 0.38$. For bijels stabilized by oblate particles, a global minimum of the $\langle Q_6 \rangle$ 
+characterizes the dynamics of the system.
+
+When increasing the applied field strength, we observe that the difference between the final and initial magnetic fields is correlated to the domain size change observed. 
+We observe that the anisotropic domain size changes are also dependent upon this difference, with the largest difference being observed when characterizing a bijel template 
+simulated under no field before having a field strength of $\bar{B} = 1$ applied to it. When looking at the particle monolayer, we characterize three behaviors seen from the 
+average interfacial angle $\langle \psi \rangle$ and $\langle Q_6 \rangle$. These behaviors are further differentiated for each particle morphology. For oblate particles, 
+the first behavior is characterized as a reorientation of the particle on the interface seen as an increase in $\langle \psi \rangle$ over time with a corresponding decrease 
+in $\langle Q_6 \rangle$ as the particles do not close pack anymore. For prolate particles, we see a slight reduction in $\langle \psi \rangle$ and greater ordering of the 
+particles from $\langle Q_6 \rangle$. The second behavior originates from small reorientations of the particles at the monolayer which do not greatly affect the interfacial 
+angle but cause a loss or gain of particle order on the interface. The final behavior is characterized as long timescale domain coarsening as there is no change between the 
+applied magnetic field and the magnetic field used to simulate the template.
+
+Finally, when decreasing the magnetic field strength, we observe little difference between bijel templates made with any field strength and no field. From the average domain 
+size, we see that the bijels coarsen at approximately the same rate. Upon further investigation of the microstructure anisotropy, we identify that the anisotropic structure 
+does not change as well, suggesting coarsening effects are independent of the effect of the local differences at the particle monolayer. After characterizing 
+$\langle \psi \rangle$ and $\langle Q_6 \rangle$, we see differences at the initial state which, while changing the initiation point of the dynamics, does not play a large
+ role otherwise. Thus any domain size change observed when removing a field is due to interfacial capillary interactions.
+
+It has been shown how the domain size and tortuosity can be used to adjust the flow rate, separations efficiency or reaction rate in applications such as cross-flow reactors, 
+drug delivery and liquid-liquid extraction. These results show that the properties of bijels can be tuned in-situ for these applications although it appears that it can only 
+be done once. With the results presented here, we have considered only one set of parameters that control the dynamics. Parameters not changed such as the fluid density, 
+viscosity, surface tension and volume fraction of particles may impact the mechanisms and rate of domain size control. We also do not consider magnetic 
+fields applied in different directions which even in this simple setup may be able to modify the microstructure considerably, or gradient magnetic fields which may allow 
+more effective unjamming and re-jamming dynamics for further microstructure modification than what has been shown here.
+
+Effects such as the steric hindrance between particles may lessen as particle size reduces as particles are more easily able to conform to the curvature of the interface. 
+The impact this may have on the results seen with the micron-sized particles used here is unknown. In many of the applications listed above, it is also unknown how changes 
+in the spacing between particles affect underlying reactivity, selectivity or diffusion rates which have implications past the domain size and tortuosity changes characterized 
+in the literature. Furthermore, it is unknown how additional particle interactions such as chemical cross-linking or charge affect the results seen here. Both strategies are 
+used in bijels to reinforce them against shear to facilitate higher shear rates, useful in cross-flow reactors and separation membranes. In conclusion, our simulations provide 
+qualitative trends into the expected microstructure change and their underlying mechanisms and timescales when applying or removing a field from a bijel stabilized by 
+anisotropic particles by modifying their orientation and packing.

### 2025-03-21 chapters/paper3.tex
Changes 1. Addressed some image sizes and phrasing consistency
Draft 1 complete
Changed I to we in results chapters

@@
 
-In past chapters, I identified the microstructure and particle arrangement of bijels stabilized by ellipsoidal particles under magnetic fields and demonstrated
-particles morphology specific ordering to the applied magnetic field. I also show that the local ordering of the particles is affected from the application of
-the magnetic field. In this chapter, I probe the dynamics of bijels under constant shear to understand how these microstructural and particle monolayer changes
-affect the rheology of bijels stabilized by ellipsoidal particles under magnetic fields. First, I define a shear capillary number 
-$Ca_s = \frac{\eta_{f} \dot{\gamma} R_s}{\sigma}$ where $\dot{\gamma} = \frac{2u_{LE}}{L_x}$ is the
-strain rate and $R_s$ is the size of equivalent spherical particle. \cite{frijters_effects_2012, yang_capillary_2022} In the literature, $Ca_s$ has been between between 0.04 
-and 0.16. However, the box size in these simulations were smaller, meaning that these capillary number ranges would exceed the 
+In past chapters, we identified the microstructure and particle arrangement of bijels stabilized by ellipsoidal particles under magnetic fields and demonstrated
+particles morphology specific ordering to the applied magnetic field. We also show that the local ordering of the particles is affected from the application of
+the magnetic field. In this chapter, We probe the dynamics of bijels under constant shear to understand how these microstructural and particle monolayer changes
+affect the rheology of bijels stabilized by ellipsoidal particles under magnetic fields. First, we define a shear capillary number, $Ca_s$
+which in the literature lies 0.04 and 0.16. \cite{frijters_effects_2012, yang_capillary_2022}
+However, these capillary number ranges would exceed the 
 maximum mach number the model allows if this same range were used $(Ma \leq 0.03)$. To accommodate this limitation the 
@@
 
-I begin this investigation by analyzing the rheological response of bijels stabilized by ellipsoidal particles under constant shear.
-Specifically, I investigate the effect that particle order has on the rheological response characterized. I am also interested in
+We begin this investigation by analyzing the rheological response of bijels stabilized by ellipsoidal particles under constant shear.
+Specifically, we investigate the effect that particle order has on the rheological response characterized. We are also interested in
 identifying the impact that the application of magnetic fields have on the rheological response of the bijel. 
 Bijel templates simulated in Aim 1 with no field and a field strength of $\bar{B} = 1$ stabilized with a prolate and oblate particles with a 
-particle volume fraction $\phi_p = 0.15$ were used as the starting point for these simulations. Next, I apply a field strength of
+particle volume fraction $\phi_p = 0.15$ were used as the starting point for these simulations. Next, we apply a field strength of
 $\bar{B} = 1$ or switch off the applied field to all structures. This results in four processing setups; $\bar{B}:0\rightarrow 0$, $\bar{B}:0\rightarrow 1$,
-$\bar{B}:1\rightarrow 0$ and $\bar{B}:1\rightarrow 1$. I then define a shear capillary number,  $Ca_s = \frac{\dot{\gamma} R_{s} \eta_{f}}{\sigma}$ where 
+$\bar{B}:1\rightarrow 0$ and $\bar{B}:1\rightarrow 1$. We then define a shear capillary number,  $Ca_s = \frac{\dot{\gamma} R_{s} \eta_{f}}{\sigma}$ where 
 $\dot{\gamma}$ is the applied strain rate, $R_s$ is the equivalent spherical radius of the particles, $R_s = 7.9$, $\eta_f$ is the dynamic viscosity of the 
-fluid and $\sigma$ is the surface tension of the interface. I use five shear numbers, $Ca_s = 1\cdot10^{-4}, 5\cdot10^{-5}, 1\cdot10^{-5}, 5\cdot10^{-6}, 1\cdot10^{-6}$.
+fluid and $\sigma$ is the surface tension of the interface. We use five shear capillary numbers, 
+$Ca_s = 1\cdot10^{-4}, 5\cdot10^{-5}, 1\cdot10^{-5}, 5\cdot10^{-6}, 1\cdot10^{-6}$.
 
@@
 the rheology of bijels have determined shear thinning behavior characterized with a Herschel-Buckley fit equation. \cite{macmillan_rheological_2019} 
-I perform this analysis on the structures I have simulated. First, I plot the shear stress over time.
+After applying shear on the bijel templates, we characterize and plot the time evolution of the the shear stress in Figure \ref{fig:stress_time}.
 
@@
 shearing of a bijel synthesized using direct mixing resulted in degraded mechanical performance. \cite{macmillan_rheological_2019}
-To characterize the viscosity, I identify pseudo-steady state regions within each of the shear stress plots and fit the stress identified within this 
+To characterize the fit, we identify pseudo-steady state regions within each of the shear stress plots and fit the stress identified within this 
 pseudo-steady state region to the strain rate. Pseudo-steady state regions are identified by measuring where the rate of change of shear stress is 
-smallest for the longest duration. I fit the calculated stress to the applied strain rate using a Herschel-Buckley rheology model defined as
+smallest for the longest duration. We fit the calculated stress to the applied strain rate using a Herschel-Buckley rheology model defined as
 $\sigma_{xz} = \sigma_{y} + K(\dot{\gamma})^{n}$. $\sigma_{xz}$ is the shear stress calculated from the simulation, $\sigma_{y}$ is the yield stress of the bijel, 
-$K$ is the flow consistency index and $n$ is the flow index.Where appropriate, I include results corresponding to a shear capillary number of 
+$K$ is the flow consistency index and $n$ is the flow index. Where appropriate, we include results corresponding to a shear capillary number of 
 $Ca_s = 10^{-6}$ as in many stress responses, $Ca_s = 10^{-6}$ may not always yield usable results.
@@
     \includegraphics[scale=0.4]{../figures/results/paper3/stress_strain-all.png} 
-    \caption{Fitting the experimental shear stress to the strain rate using the Herschel Buckley model. I characterize the bijels are 
-             shear thinning in all cases. I show that the bijels become less shear thinning as the particle order increases. I also
+    \caption{Fitting the experimental shear stress to the strain rate using the Herschel Buckley model. We characterize the bijels are 
+             shear thinning in all cases and that the bijels become less shear thinning as the particle order increases. We also
              demonstrate that the particle ordering affects the yield stress differently for particles stabilized by oblate and 
@@
 condition is closer together, indicating a smaller variation in the response to the applied magnetic field compared to oblate particles. The shear response upon application
-of the magnetic field also suggest that increased ordering of prolate particles makes the bijel more resistant to shear. I quantify the Herschel-Buckley fit parameters and 
+of the magnetic field also suggest that increased ordering of prolate particles makes the bijel more resistant to shear. We quantify the Herschel-Buckley fit parameters and 
 tabulate the results in Table \ref{table:rheology_fit}.
@@
     \centering
+    \renewcommand{\arraystretch}{1.5}  % Increases row height
     \begin{tabular}{||c c c c c||} 
@@
 The particle morphology dependent differences in the shear response characterized in Figure \ref{fig:stress_strain} are quantified in Table \ref{table:rheology_fit}
-where the yield stress differences predicted is clear to see. I also show that bijel templates with an applied field of $\bar{B} = 1$ have larger flow indices \
-than bijel templates made with no applied field. The same trend exists here where the application of a magnetic field makes the bijel more Newtonian. I also 
-characterize that the yield stress of bijels stabilized with oblate particles decrease as the initial order of the particles and the applied field onto the bijel increase. 
-The yield stress of bijels stabilized by prolate particles increases as the initial order of the particles and the applied field onto the bijel increase. In previous aims, I 
-characterized that application of magnetic fields created orientational ordering of the bijels and that the local ordering of the bijels change. I 
+where the yield stress differences predicted is clear to see. The bijel templates with an applied field of $\bar{B} = 1$ have larger flow indices
+than bijel templates made with no applied field. The same trend exists here where the application of a magnetic field makes the bijel more Newtonian.
+The yield stress of bijels stabilized with oblate particles decrease as the initial order of the particles and the applied field onto the bijel increase. 
+The yield stress of bijels stabilized by prolate particles increases as the initial order of the particles and the applied field onto the bijel increase. In previous aims, we 
+characterized that application of magnetic fields created orientational ordering of the bijels and that the local ordering of the bijels change. We  
 showed that as magnetic fields were applied, oblate particles have lower local ordering on the interface while for prolate particles it increases.
@@
 They identified that local ordering can enhance stress distribution among particles, making locally ordered particle monolayers better at withstanding shear.
-I visualize the ordering of the particles at the interface to the z direction for both particle morphologies at $Ca_s = 10^{-6}$ for the 
+We visualize the ordering of the particles at the interface to the z direction for both particle morphologies at $Ca_s = 10^{-6}$ for the 
 case $\bar{B}: 1 \rightarrow 0$.
@@
 In Figure \ref{fig:particle_viz_tz}, the particles are initially ordered to the direction of the applied magnetic field. Upon application of shear and removal
-of the magnetic field, I see that the particles begin reorienting away from the z direction. I also observe that the reorientation of particles uncovers the interface.
+of the magnetic field, We see that the particles begin reorienting away from the z direction. We also observe that the reorientation of particles uncovers the interface.
 The reorientation observed is particle morphology specific with prolate particles seeing more reorientation away from the applied shear direction than oblate particles.
-Looking at the images, I see that prolate particles rotate away from the direction of the magnetic field and applied shear towards the direction of the shear gradient,
+Looking at the images, we see that prolate particles rotate away from the direction of the magnetic field and applied shear towards the direction of the shear gradient,
 while oblate particles reorient towards minimizing area to the applied shear direction. While these snapshots show the initial and final orientations of the particles at the
@@
 orient to the direction of shear and ejected from the interface at sufficiently long times or shear.\cite{bonaccorso_shear_2020} 
-I probe these aspects of the particle monolayer in this section. I plot the orientation of the particle to each cartesian axis 
-to identify if I characterize shear induced ordering.
+We probe these aspects of the particle monolayer in this section. First, we plot the orientation of the particle to each cartesian axis 
+to identify if shear induced ordering is present.
 
@@
     \caption{Comparisons of the initial and final particle orientations of the particles to each cartesian direction under
-             four processing histories for bijels stabilized with oblate and prolate ellipsoids at multiple shear rates. I show
+             four processing histories for bijels stabilized with oblate and prolate ellipsoids at multiple shear rates. We show
              shear dependent ordering of the particle monolayer if the initial particle monolayer begins with particle order.} 
@@
 
-From Figure \ref{fig:particle_orientation_cartesian_shear} I see that with bijel templates simulated under $\bar{B} = 0$, the
-particles adopt a random orientation. Upon application of shear, I see that there is little directional ordering to the 
+From Figure \ref{fig:particle_orientation_cartesian_shear} we see that with bijel templates simulated under $\bar{B} = 0$, the
+particles adopt a random orientation. Upon application of shear, we see that there is little directional ordering to the 
 shear direction in the simulation time observed. Upon application of the magnetic field in the $\bar{B}:0 \rightarrow 1$ case, 
@@
     \caption{Comparisons of the interfacial angle of bijels stabilized by ellipsoidal particles as a function of 
-             the applied shear rate at four different processing histories. I show that upon application of shear
+             the applied shear rate at four different processing histories. We show that upon application of shear
              particles tilt out of the interface reduces the interfacial area stabilized. $\bar{B}: 0 \to 1$ shows 
@@
 
-From Figure \ref{fig:interface_angle_shear}, I demonstrate that there is a slow increase in the interface angle over time for all cases
+From Figure \ref{fig:interface_angle_shear}, we demonstrate that there is a slow increase in the interface angle over time for all cases
 except for $\bar{B}: 0 \to 1$. For the $\bar{B}: 0 \to 1$ case, this has been shown in Chapter \ref{chapter:aim2} to be due to particle
@@
     \caption{Comparisons of the proportion of particles on the interface of bijels ($n_{int}$) stabilized by ellipsoidal particles as a function of 
-             the applied shear rate at four different processing histories. I show that upon application of shear, many cases have a 
-             reduction in the number of particles on the interface while in others it stays the same. For cases where $n_{int}$ reduces, I can 
-             attribute the domain size coarsening to this effect.} 
+             the applied shear rate at four different processing histories. We show that upon application of shear, many cases have a 
+             reduction in the number of particles on the interface while in others it stays the same. 
+            %  For cases where $n_{int}$ reduces, I can 
+            %  attribute the domain size coarsening to this effect.
+             } 
     \label{fig:particles_interface_prop_shear} 
@@
 From the results in Figure \ref{fig:particles_interface_prop_shear}, the impact of the initial microstructure on the number of particles on the interface
-differs for bijels stabilized by oblate and prolate ellipsoids. I split this analysis on processing history. While keeping the applied magnetic field
+differs for bijels stabilized by oblate and prolate ellipsoids. We split this analysis on processing history. While keeping the applied magnetic field
 the same, little differences in the behavior of $n_{int}$ is observed, with small changes also being characterized for $\langle \psi \rangle$. 
@@
 particles to the applied field, resulting in the mostly unchanged $n_{int}$ values. A increase in $\langle \psi \rangle$ and decrease in $n_{int}$ indicates domain
-can indicate coarsening of the fluid domains as the interfacial area is reduced. In the next section, I investigate the the role of the interface properties and the 
+can indicate coarsening of the fluid domains as the interfacial area is reduced. In the next section, we investigate the the role of the interface properties and the 
 impact of particle ejection and tilting of particles out of the interface on the microstructure of bijels.
@@
 properties of the particle monolayer upon application of shear. 
-In this section, I probe the effect of applied shear to the microstructure of magnetically
+In this section, we probe the effect of applied shear to the microstructure of magnetically
 responsive bijels stabilized by ellipsoidal particles. To investigate the effect of the particle angle and the interfacial coverage of the bijel on the
-microstructural evolution of the interface, I plot the area averaged gaussian curvature over time. This parameter will allow insight into the evolution 
+microstructural evolution of the interface, we plot the area averaged gaussian curvature over time. This parameter will allow insight into the evolution 
 of the interface, namely the presence of domain coarsening, coalscence or break-off events.
@@
     \caption{Plots of the time evolution of the area averaged Gaussian curvature $\langle K \Sigma^{-2} \rangle$ for four 
-             processing histories applied to bijels stabilized with oblate and prolate ellipsoids. I demonstrate that the 
+             processing histories applied to bijels stabilized with oblate and prolate ellipsoids. We demonstrate that the 
              magnitude of the gaussian curvature reduces for all systems except for $\bar{B}: 0 \to 1$.} 
@@
 The rheological properties of bijels are of importance in many fabrication schemes such as STrIPS and homogenization. \cite{haase_continuous_2015,cai_bijels_2017}
-To characterize how magnetically responsive bijels can be used in these synthesis techniques, I studied the effect of particle morphology, initial microstructure and
+To characterize how magnetically responsive bijels can be used in these synthesis techniques, we studied the effect of particle morphology, initial microstructure and
 applied magnetic fields on the rheology of bijels experiencing a constant shear. Bijel templates made with $\bar{B} = 0$ and $\bar{B} = 1$ were selected, with field strengths
 of $\bar{B} = 0$ and $\bar{B} = 1$ applied to each template. This results in four processing histories per particle morphology namely $\bar{B}:0 \rightarrow 0$,
-$\bar{B}:0 \rightarrow 1$, $\bar{B}:1 \rightarrow 0$ and $\bar{B}:1 \rightarrow 1$. I then apply a constant shear rate onto each bijel.
+$\bar{B}:0 \rightarrow 1$, $\bar{B}:1 \rightarrow 0$ and $\bar{B}:1 \rightarrow 1$. We then apply a constant shear rate onto each bijel.
 
-I first characterized the shear stress imparted by bijels under several strain rates. The shear stress calculated continued to increase in line with expectations
+We first characterized the shear stress imparted by bijels under several strain rates. The shear stress calculated continued to increase in line with expectations
 for colloidal glasses as ageing occurs. Thus a pseudo-steady state was selected to compare the shear properties of the bijel.
-I fit the shear stress data using a Herschel Buckley fit and identify that the flow index of bijels stabilized by ellipsoidal 
+We fit the shear stress data using a Herschel Buckley fit and identify that the flow index of bijels stabilized by ellipsoidal 
 particles under magnetic fields became less shear thinning. The yield stress of bijels stabilized by oblate particles was shown to reduce by 4x while the yield stress

### 2025-03-23 chapters/dissertation-tap.tex
Changes 1. Working on feedback     a. Changed abstrat     b. Cleaned up bibliography for diagnosis if issues were there     c. Fixed reproduction licenses in figure captions

@@
                  % for an abstract or type text here.
+    Porous materials are important in a wide range of applications, including water filtration, 
+    catalyst supports, battery electrodes, and bioengineered materials. To accommodate a broader range of pore 
+    sizes and enable scalable fabrication with minimal waste, bottom-up synthesis techniques have gained 
+    increasing attention. Among these, emulsion templating based on bicontinuous interfacially jammed 
+    emulsion gels (bijels)—has emerged as a promising approach due to its ability to produce complex, 
+    interconnected porous structures.
 
-Porous materials have found great importance in applications such as water filtration, catalyst supports, battery 
-electrodes and bio engineered materials. To accommodate a greater variety of pore sizes and continuous fabrication 
-techniques with minimal waste, bottom up synthesis techniques have been gaining in popularity. One such technique is
-emulsion templating of a specific microstructure known as a bicontinuous interfacially jammed emulsion gels(bijels).
+    Despite these advantages, achieving microstructural control independent of the casting mixture remains a 
+    key challenge, particularly in continuous bijel fabrication methods such as Solvent Transfer Induced Phase 
+    Separation (STrIPS). Additionally, in situ control strategies for tailoring properties such 
+    as separation efficiency can be useful additions to control material performance. 
+    Stimuli-responsive approaches have been identified as a potential route to 
+    overcome these constraints. This study focuses on the magnetic stimuli-response of bijels stabilized by 
+    magnetically responsive ellipsoidal microparticles, examining both the resulting microstructural 
+    modifications and their rheological implications.
 
-However, casting mixture independent microstructure control is an open issue, especially applicable in continuous 
-bijel synthesis strategies such as Solvent Transfer Induced Phase separation and as in-situ control mechanisms to
-control the microstructure of a bijel to control properties such as separation efficiency. Stimuli response has been identified as a 
-technique to enable this. This study focuses on utilizing stimuli response of bijels stabilized with ellipsoidal microparticles, 
-and the resulting microstructure and rheological implications this induces.
+    It is shown that the application of a magnetic field during bijel formation induces microstructural 
+    changes in systems stabilized by ellipsoidal particles—effects not observed in bijels stabilized by 
+    spherical particles. The applied field causes particle reorientation along its direction, leading to 
+    directional jamming and the development of anisotropic microstructures.
 
-We first identify that upon application of a field to a bijel stabilized with ellipsoidal particles during synthesis, 
-microstructure change is observed, not present when analyzing bijels stabilized with spherical particles. Upon 
-application of the field, particles reorient to the direction of the field, causing directional jamming that creates
-microstructure anisotropy.
+    Post-synthesis, bijels stabilized by ellipsoidal particles exhibit tunable microstructure. This responsiveness 
+    is governed by the degree of particle order present prior to field application, as well as the extent of 
+    reordering induced by the field. The system exhibits state-dependent behavior, indicating that the timing of 
+    magnetic field application significantly influences the magnitude of the microstructural response characterized.
 
-We then identify that bijels stabilized with ellipsoidal particles have tunable microstructures after jamming. 
-This process is dependent upon the initial particle order present in the bijel, as well as the difference 
-between the initial and final particle order. We also show that the structural response observed is state 
-dependent, meaning that the time of magnetic field application affects the microstructure change observed.
-
-Finally, we characterize that bijels retain their shear thinning behavior when analyzing the rheological response of bijels
-under magnetic fields. We identify that the particle ordering plays a role in the evolution of the microstructure under shear
-and the rheological response.
-
+    Rheological characterization reveals that bijels retain their shear-thinning behavior under applied magnetic 
+    fields. However, the degree of particle ordering is found to influence both the evolution of the microstructure 
+    under shear and the corresponding rheological response, highlighting the interplay between field-induced 
+    structuring and mechanical performance.
 \end{front}

### 2025-03-23 chapters/introduction.tex
Changes 1. Addressed some image sizes and phrasing consistency
Draft 1 complete
Changes 1. Working on feedback     a. Changed abstrat     b. Cleaned up bibliography for diagnosis if issues were there     c. Fixed reproduction licenses in figure captions

@@
     \includegraphics[scale = 0.5]{figures/introduction/bijel_templating.png}
-    \caption{Fabrication of a graphite oxide battery electrode using bijel template. Reproduced from Garcia et al. 
-             Nanoscale Adv., 2019,1, 3870-3882 under license number 1548092-1. \cite{garcia_scalable_2019}}
+    \caption{Fabrication of a graphite oxide battery electrode using bijel template. Used with permission of 
+    Royal Society of Chemistry, from Scalable synthesis of gyroid-inspired freestanding three-dimensional graphene architectures, 
+    Garcia et al., 1, 10, 2018 permission conveyed through Copyright Clearance Center, Inc}
     \label{fig:bijel_template}
@@
     \centering
-    \includegraphics[scale = 4]{figures/introduction/STrIPS.jpg}
+    \includegraphics[scale = 5]{figures/introduction/STrIPS.jpg}
     \caption{STrIPS in action. Extrusion of the bijel casting mixture into a non-solvent bath, followed by removal of solvent from 
-             the casting mixture through diffusion. \cite{haase_continuous_2015} Reproduced from Haase et al. Adv. Mater., 
-             Volume27, Issue44, 2015, Pages 7065-7071 under license number 5913140219015. }
+             the casting mixture through diffusion. \cite{haase_continuous_2015}. Reproduced with permission from Wiley-VCH Verlag GmbH 
+             \& Co. KGaA from \textit{Continuous Fabrication of Hierarchical and Asymmetric Bijel Microparticles, Fibers, and Membranes by 
+             Solvent Transfer-Induced Phase Separation (STRIPS)}, Haase, M. F., Stebe, K. J., 
+             \& Lee, D., \textit{Advanced Materials}, 27(44), 7065-7071, 2015}
     \label{fig:strips}
@@
     \centering
-    \includegraphics[scale = 1]{figures/introduction/magnetophoresis_emulsion.jpeg}
+    \includegraphics[scale = 1.5]{figures/introduction/magnetophoresis_emulsion.jpeg}
     \caption{Enhanced oil recovery of oil from water using magnetically responsive emulsion stabilizers, allowing for 
              locomotion and controlled coalescence of cargo from a matrix phase using magnetic fields. \cite{tham_magnetophoresis_2021} 
-             Reproduced from Tham et al. Langmuir 2021, 37, 5, 1811-1822 under the ACS standard license.}
+             K. Tham, W. M. Ng, S. S. Leong, S. P. Yeap, S. C. Low, H. L. Lee and J. Lim. Magnetophoresis of magnetic pickering 
+             emulsions under low field gradient: Macroscopic and microscopic motion. 37, 1811: Reprinted (adapted) with permission from 
+             Langmuir 2021, 37, 5, 1811-1822. Copyright 2025 American Chemical Society.}
     \label{fig:magnetophoresis_droplet}
@@
 
-Building on this background, we propose the use of anisotropic particles as a technique to enable microstructure modification of bijels upon the application 
+Building on this background, the use of anisotropic particles, specifically ellipsoidal particles, is proposed as a technique to enable microstructure modification 
+of bijels upon the application 
 of an external field, both during and after fabrication. This work aims to explore methods for controlling the bijel microstructure independently of the casting 
@@
 
-\section{Research objective}
+% \section{Research objective}
 
-% this work seeks to identify means to control the bijel microstructure independent of the casting mixture composition utilizing magnetic stimuli response of anisotropic particles.
+% % this work seeks to identify means to control the bijel microstructure independent of the casting mixture composition utilizing magnetic stimuli response of anisotropic particles.
 The proposed mechanism of microstructure modification is driven through reorientation of the particles to the applied magnetic field altering how the particles pack on the interface.
 
-\subsection{Aim 1: Determination of the degree of microstructure changes expected when applying a constant field during bijel formation}
-\label{section:aim1_desc}
+% \subsection{Aim 1: Determination of the degree of microstructure changes expected when applying a constant field during bijel formation}
+% \label{section:aim1_desc}
 
@@
 of bijels synthesized with varying particle volume fractions and sizes \cite{jansen_bijels_2011, reeves_particle-size_2015}. Additionally, it has been shown 
-that magnetic fields can facilitate the self-assembly of anisotropic particles at interfaces and control the interfacial angle between the particle's axis 
+that magnetic fields can facilitate the self-assembly of ellipsoidal particles at interfaces and control the interfacial angle between the particle's axis 
 of symmetry and the interface \cite{davies_interface_2014, davies_assembling_2014}. However, on a curved interface with numerous other particles, it remains 
 unclear how the orientation of multiple particles in response to the field and their regular arrangement will influence the jamming behavior of the bijel 
-\cite{bresme_orientational_2007, davies_interface_2014}.
+\cite{bresme_orientational_2007, davies_interface_2014}. Therefore the microstructural response of bijels as a function of the applied field will be 
+characterized.
 
-To evaluate the microstructure obtained upon the application of a field during the formation of the bijel, homogeneous mixtures containing spherical and 
-ellipsoidal particles will be subjected to field strengths both above and below the critical field strength. This critical field strength is the threshold 
+A homogeneous mixtures containing spherical and ellipsoidal particles will be subjected to field strengths both above and below the critical field strength. 
+This critical field strength is the threshold 
 at which particle orientations to the interface are governed by the applied field, as calculated by Bresme and Faraudo for the particle aspect ratio 

### 2025-03-23 chapters/lit_review.tex
Changes 1. Working on feedback     a. Changed abstrat     b. Cleaned up bibliography for diagnosis if issues were there     c. Fixed reproduction licenses in figure captions

@@
     \caption{Quadropolar capillary interactions around prolate ellipsoidal particles caused by interfacial deformations 
-             around the particle. \cite{loudet_capillary_2005} Reproduced from Loudet et al. Phys. Rev. Lett. 2005, 94, 018301
-             with license number RNP/25/FEB/088185}
+             around the particle. \cite{loudet_capillary_2005} Reprinted Figure 4 with permission from
+             Loudet et al, Phys. Rev. Letter., 94, 08301, 2003 Copyright 2025 by the American Physical Society.}
     \label{fig:anisotropic_particle_interface}
@@
     \caption{Formation criteria for a particle stabilized emulsion that can form bijel. \cite{velankar_non-equilibrium_2015}
-            Reproduced from Velankar Soft Matter, 2015,11, 8393-8403 using license number 1551968-1.}
+            Used with permission of Royal Society of Chemistry, from A non-equilibrium state diagram for liquid/fluid/particle 
+            mixtures, Velankar, 1, 11, 2015. Permission conveyed through Copyright Clearance Center, Inc}
     \label{fig:state_diagram_particle_emulsions}
@@
     \caption{Schematic of a bijel with hard-sphere particles undergoing shear, demonstrating migration and detachment of 
-             particles at the interface. \cite{bonaccorso_shear_2020} Reproduced from Bonaccorso et al. AIP Advances 1 
-             September 2020; 10 (9): 095304, under the Creative Commons CC BY License.}
+             particles at the interface. \cite{bonaccorso_shear_2020} Reproduced from Shear dynamics of confined bijels
+             ,Bonaccorso et al. AIP Advances 1, September 2020; 10 (9): 095304, under the Creative Commons CC BY License.}
     \label{fig:bijel_under_shear}

### 2025-03-23 chapters/introduction.tex
rewrote introduction

@@
 
-Porous materials are characterized by the presence of pores or voids within their structure, where no solid material is present. 
-In contrast, homogeneous materials exhibit a uniform structure devoid of pores. The shape and distribution of these pores can vary, 
-and according to the IUPAC classification, materials are categorized based on pore size as microporous ($L < 2$ nm), 
-mesoporous ($2 < L < 50$ nm), or macroporous ($L > 50$ nm) \cite{sing_reporting_1985}. The presence of pores significantly 
-increases the surface area-to-volume ratio of porous materials compared to their homogeneous counterparts. A commonly used experimental 
-technique for estimating the surface area of porous materials, based on Brunauer-Emmett-Teller (BET) theory, has demonstrated that such 
-materials can exhibit surface areas more than a hundred times greater than those of homogeneous materials, depending on pore size and pore 
-size distribution \cite{shimizu_surface_2022}.
+Porous materials play a vital role across a range of applications, including water filtration, catalyst supports, battery electrodes, and bioengineered 
+materials. These materials are characterized by a network of pores that significantly increase surface area-to-volume ratio compared to their 
+homogeneous counterparts. According to the IUPAC classification, porous materials are defined by their pore sizes as microporous ($L < 2$ nm), 
+mesoporous ($2 < L < 50$ nm), or macroporous ($L > 50$ nm) \cite{sing_reporting_1985}. Experimental techniques such as BET analysis have shown 
+that porous materials can possess surface areas exceeding those of solid materials by orders of magnitude \cite{shimizu_surface_2022}. The internal 
+structure, including pore distribution and connectivity, also influences material performance and is often quantified by tortuosity 
+\cite{chen_tortuosity_2020, ebner_tortuosity_2014}.
 
-In addition to pore size and its distribution, the spatial arrangement of pores within a material significantly influences its performance, 
-often quantified by tortuosity. Tortuosity is defined as the ratio of the actual path length between two points to the Euclidean distance 
-between them. A tortuosity greater than one indicates that the path length is longer than the Euclidean distance, whereas a tortuosity less 
-than one suggests a more direct pathway. The interplay of these factors has led to the development of a wide range of tailored microstructures 
-for diverse applications. Each pore size regime serves distinct functions; for example, microporous materials are commonly used in zeolites and 
-photonic bandgap materials, while macroporous materials enhance transport properties, making them suitable for applications such as battery 
-electrodes and drug delivery systems \cite{chen_tortuosity_2020, ebner_tortuosity_2014}. The increased surface area-to-volume ratio of porous 
-materials further enhances the properties of the base material in various applications, including catalysis, energy storage, and biomedical 
-systems, making them important microstructures. \cite{cha_bicontinuous_2019, samdani_bicontinuous_2017, thorson_bijel-templated_2019, zhao_highly_2014}.
+To meet increasing demands for tunable porosity, bottom-up synthesis strategies have gained traction. Among them, emulsion templating has emerged as a 
+versatile technique that leverages phase separation to produce complex porous architectures. One particularly promising class of emulsion-templated 
+materials is bicontinuous interfacially jammed emulsion gels (bijels), which form through the arrested spinodal decomposition of partially miscible 
+fluids. Stabilized by colloidal particles that adsorb onto the fluid interface, bijels exhibit a tortuous, co-continuous structure well-suited for 
+applications requiring high surface area and tunable transport properties \cite{stratford_colloidal_2005, herzig_bicontinuous_2007, lee_bicontinuous_2010}. 
+Their bottom-up formation approach enables scalable synthesis of porous templates for a variety of material systems such as battery electrodes, shown in
+Figure \ref{fig:bijel_template} 
+\cite{cha_bicontinuous_2019, samdani_bicontinuous_2017, thorson_bijel-templated_2019}.
 
@@
 
-Conventionally, porous materials have been synthesized through methods such as solvothermal synthesis and pyrolysis, which are commonly 
-used for producing zeolites and activated carbon, respectively. With the increasing demand for tailored porous materials, advanced synthesis 
-techniques—including sol-gel synthesis, freeze-drying, and various templating methods—have been developed to fabricate porous structures across 
-length scales ranging from $10^{-9}$ m to $10^{-3}$ m 
-\cite{stein_morphological_2008, ray_comprehensive_2016, cervellere_mesoscopic_2019, garcia-bennett_unique_2020, zhang_emulsion_2019, alves-rosa_design_2013}. 
-Industry has also adopted techniques such as electro-spinning to produce nonwoven fibers, which are widely used in membrane synthesis.  
-Among these approaches, templating techniques provide precise control over pore size, enable bottom-up synthesis, and introduce functionality by 
-leveraging various physical phenomena. Colloidal templating relies on the close packing of particles to define pore structures. Surfactant and 
-polymer templating utilize the self-assembly of macromolecules into their equilibrium configurations to generate porous networks. Emulsion templating, 
-on the other hand, exploits the phase separation of partially miscible liquids to form the pore architecture of the resulting material.
+Fabrication methods for bijels have evolved from thermally induced spinodal decomposition (TIPS) to include solvent transfer-induced phase separation (STrIPS), 
+vapor-induced phase separation (VIPS), and other advanced techniques \cite{haase_continuous_2015, wang_scalable_2020, amirfattahi_fabrication_2024}. 
+These approaches allow for continuous production and offer access to various material shapes such as fibers, membranes, and capsules 
+\cite{boakye-ansah_controlling_2020, kharal_hightensile_2020}. However, a key limitation is that the microstructure of bijels remains 
+strongly tied to the casting mixture composition and phase separation kinetics. Adjusting the microstructure typically requires tuning 
+component concentrations or altering flow conditions, which may be impractical or undesired in certain applications 
+\cite{haase_continuous_2015, reeves_particle-size_2015}.
 
-Emulsion templating enables the fabrication of porous materials with a wide range of tunable pore sizes, continuous production through microfluidic 
-junctions or other flow-based systems, and functionalization through the incorporation of additives or stabilizers. This technique also offers a broad 
-scope of accessible microstructures and benefits from mild synthesis conditions. Additionally, it can be extended to generate hierarchical porosity, 
-further enhancing the functionality and properties of the resulting materials \cite{yang_hierarchically_2017, thompson_hierarchically_2019, wang_morphology_2023}.  
-Figure \ref{fig:bijel_template} illustrates how emulsion templating enables the bottom-up synthesis of hierarchically porous materials, although various 
-alternative approaches also exist 
-\cite{garcia_scalable_2019, santiago_cordoba_aerobijels_2020, thorson_bijel-templated_2019, lu_controllable_2020, wang_morphology_2023}.
-
-\begin{figure}
-    \centering
-    \includegraphics[scale = 0.3]{figures/introduction/bijel_coarsening.jpg}
-    \caption{Initiation and arrest of spinodal decomposition as particles adsorb onto the interface, followed by jamming once the 
-    interfacial area matches the cross sectional area of the adsorbed particles\cite{stratford_colloidal_2005}. 
-    Reproduced from K. Stratford et al., Science 309, 2198-2201(2005) under license number 5966820525314.}
-    \label{fig:bijel_coarsen}
-\end{figure}
-
-One particularly interesting emulsion-derived microstructure is the bicontinuous interfacially jammed emulsion gel (bijel) 
-\cite{stratford_colloidal_2005, herzig_bicontinuous_2007, lee_bicontinuous_2010}. Bijels are formed by arresting the spinodal decomposition of partially 
-miscible liquids, a process driven by the adsorption of colloidal particles at the interface. As the interfacial area contracts, the particles become 
-jammed, stabilizing the bicontinuous structure, as summarized in Figure \ref{fig:bijel_coarsen}. The resulting co-continuous and tortuous microstructure 
-of bijels makes them highly suitable for various porous material applications.
-
-Bijels were first predicted in simulations in 2005 and experimentally realized in 2007 when a mixture of water and 2,6-lutidine, combined with 
-surface-modified silica nanoparticles, underwent thermally induced spinodal decomposition \cite{stratford_colloidal_2005, herzig_bicontinuous_2007}. 
-Since then, various casting mixtures and particle chemistries have been explored to fabricate bijels using thermally induced spinodal decomposition (TIPS) 
-\cite{lee_bicontinuous_2010, bai_dynamics_2015}. More recently, alternative fabrication techniques such as solvent transfer-induced phase separation (STrIPS), 
-vapor-induced phase separation (VIPS), non-solvent-induced phase separation (NIPS), homogenization, and liquid-in-liquid printing have been developed. 
-These methods enable the continuous synthesis of bijels, making them more suitable for large-scale production 
-\cite{haase_continuous_2015, wang_scalable_2020, cai_bijels_2017, yabuno_preparation_2020, wang_bicontinuous_2023, amirfattahi_fabrication_2024}. 
-Additionally, these techniques allow for the fabrication of bijels in various shapes and form factors, including fibers, coatings, and capsules, expanding 
-their applicability across different fields, as illustrated in Figure \ref{fig:strips} 
-\cite{haase_continuous_2015, boakye-ansah_controlling_2020, kharal_hightensile_2020, wang_bicontinuous_2023}.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale = 5]{figures/introduction/STrIPS.jpg}
-    \caption{STrIPS in action. Extrusion of the bijel casting mixture into a non-solvent bath, followed by removal of solvent from 
-             the casting mixture through diffusion. \cite{haase_continuous_2015}. Reproduced with permission from Wiley-VCH Verlag GmbH 
-             \& Co. KGaA from \textit{Continuous Fabrication of Hierarchical and Asymmetric Bijel Microparticles, Fibers, and Membranes by 
-             Solvent Transfer-Induced Phase Separation (STRIPS)}, Haase, M. F., Stebe, K. J., 
-             \& Lee, D., \textit{Advanced Materials}, 27(44), 7065-7071, 2015}
-    \label{fig:strips}
-\end{figure}
-
-However, all of these techniques rely on precisely controlling the rate of phase separation, which typically involves adjusting the composition 
-of the casting mixture to modify the resulting microstructure. In STrIPS, for example, the bijel microstructure is influenced by both the flow rate 
-and the choice of co-solvent, which are selected to regulate the phase separation dynamics \cite{haase_continuous_2015}. These factors directly 
-impact material properties such as the mechanical stability of the bijel, which is particularly important in applications like catalysis, where the 
-rigidity of the particle monolayer is essential for maintaining consistent performance 
-\cite{reeves_particle-size_2015, haase_situ_2016, boakye-ansah_controlling_2020}. Identifying alternative techniques for modifying the microstructure of 
-bijels would allow for greater tunability while maintaining the desired composition of the constituent materials. One promising approach for achieving 
-such control is the use of stimuli-responsive mechanisms.
+% microstructure modification post synthesis
+Once fabricated, the microstructure of bijels cannot be changed. In many applications proposed for bijels such as water filtration membranes
+or drug release platforms, the microstructure of the material controls the back pressure, selectivity for specific species and transport
+dynamics in the material. \cite{vanoli_bijels_2022, thorson_bijel-templated_2019} Creating a material whose microstructure an be dynamically
+adjusted to the desired output parameters would add additional functionality and use cases for bijels.
 
@@
 
-Stimuli-responsive mechanisms based on pH, external fields, and temperature have been explored in previous studies to modify the microstructure of emulsion 
-droplets for applications such as enhanced oil recovery, pharmaceuticals, and cell adhesion 
-\cite{haase_nanoparticle_2011, tham_magnetophoresis_2021, cui_stabilizing_2013, manfredini_limonene--water_2021}. External fields have been shown to 
-manipulate emulsion stability, control droplet movement, and induce elongation in emulsion droplets 
-\cite{tham_magnetophoresis_2021, cui_stabilizing_2013, melle_pickering_2005}. One such example is shown in Figure \ref{fig:magnetophoresis_droplet}
-where enhanced oil recovery was performed using magnetically responsive particle stabilizers which could capture oil droplets,
-move the droplets away from the matrix and cause controlled coalescence elsewhere.
-In the case of bijels, spherical particle-stabilized systems subjected to a magnetic field exhibited no significant microstructural changes 
-\cite{kim_bijels_2010}. However, bijels stabilized with spherical particles under an electric field demonstrated greater potential for microstructure 
-modification \cite{carmack_tuning_2018}. Despite this, magnetic fields present a promising avenue for targeted stimuli-responsive behavior, as even 
-weak fields can induce a response while remaining non-invasive in many contexts. This property is particularly advantageous for pharmaceutical and 
-bioengineering applications, where external control over material properties is desirable 
-\cite{vanoli_bijels_2022, thorson_bijel-templated_2019, thorson_composite_2018}.  
-Such applications could benefit from in-situ microstructural modifications, enabling tunable drug delivery rates, improved separations, and enhanced catalyst 
-efficiency and permeability. Therefore, developing strategies to modify pore size and tortuosity without requiring the synthesis of a new material would 
-significantly expand the functional versatility of bijels.
+Stimuli-responsive strategies offer an attractive alternative for post-synthetic or in-situ control of bijel microstructures. External fields, 
+pH, and temperature have all been explored to modify emulsion morphologies, particularly in Pickering emulsions 
+\cite{tham_magnetophoresis_2021, cui_stabilizing_2013}. In Pickering emulsions, magnetically responsive particles have enabled droplet
+manipulation, deformation, and coalescence control, shown in Figure \ref{fig:magnetophoresis_droplet}. By contrast, similar stimuli-responsive 
+behaviors in bijels remain underexplored. Prior work with spherical particles under magnetic fields has shown limited microstructural modification 
+\cite{kim_bijels_2010}, while electric fields have demonstrated greater influence \cite{carmack_tuning_2018}.
 
@@
 
-Anisotropic particles at interfaces have been shown to undergo self-assembly due to the presence of multipolar pressure fields induced by interface 
-deformation caused by magnetic stimuli, visualized in Figure \ref{fig:anisotropic_assembly}. \cite{bresme_orientational_2007, davies_interface_2014}
-When subjected to a magnetic field, assemblies of multiple ellipsoidal particles exhibit energy minima at orientations different from those of isolated 
-particles. This suggests that the interfacial coverage of surfaces decorated with ellipsoidal particles can be dynamically tuned using external 
-stimuli \cite{newton_influence_2014, newton_capillary_2018}. Therefore, ellipsoidal particles at interfaces—whose orientation and packing can be externally 
-controlled—present a promising strategy for tailoring the microstructure of bijels.
+Recent advances suggest that anisotropic particles, particularly ellipsoidal particles, may offer enhanced responsiveness due to their shape-dependent 
+interfacial behavior. When subjected to magnetic fields, ellipsoidal particles can align directionally, inducing local anisotropy in the interfacial 
+packing arising from capillary deformation of the interface. This property has been characterized to induce self assembly of particles, 
+shown in Figure \ref{fig:anisotropic_particle_interface} 
+\cite{bresme_orientational_2007, davies_assembling_2014, newton_influence_2014}. By utilizing the magnetic field driven re-orientation and self assembly 
+of particles at interfaces, the microstructure of bijels could be influenced pre and post formation. Therefore, leveraging this behavior offers a 
+pathway to decouple microstructure control from casting mixture composition, expanding the design space for bijel derived porous materials and
+soft matter.
 
-Bijels offer a bottom-up synthesis approach for porous material templates, enabling scalable and continuous fabrication for both hard and soft material 
-applications through STrIPS and related techniques. However, the degree of microstructural control provided by these methods is inherently dependent on 
-the composition of the casting mixture. Stimuli-responsive strategies present a means to modify the microstructure of bijels while preserving the 
-diverse form factors achievable through continuous synthesis techniques. Previous attempts to induce magnetic stimuli response in bijels stabilized 
-with spherical particles have shown limited success \cite{kim_bijels_2010}.
+The rheological properties are also of interest in bijels, owing to their synthesis and applications being tied to their rheology. STrIPS relied upon the
+flow of casting mixture into a solvent bath and the rheological properties of the bijel are needed to ascertain the parameters to operate. 
+\cite{haase_situ_2016, haase_continuous_2015} Additionally,
+the uses of bijels in many applications such as cross-flow reactors are limited by the yielding of the particle monolayer under strain and fluid 
+composition induced shear. \cite{boakye-ansah_controlling_2020} Magnetically responsive fluids have been shown to have significant increases in viscosity
+due to particle ordering to the field increasing the fluids viscosity. When investigating the failure mechanism of bijels stabilized by spherical
+particles under shear, previous investigations have shown that the particles align to the direction of shear before being pulled out of the interface.
+\cite{bonaccorso_shear_2020} Therefore, magnetic fields affecting the orientation of particles at interfaces would be used to modify the rheological 
+properties of bijels.
 
-Building on this background, the use of anisotropic particles, specifically ellipsoidal particles, is proposed as a technique to enable microstructure modification 
-of bijels upon the application 
-of an external field, both during and after fabrication. This work aims to explore methods for controlling the bijel microstructure independently of the casting 
-mixture composition by utilizing magnetic stimuli on bijels stabilized with magnetically responsive ellipsoidal particles.  
-The proposed mechanism of microstructure modification is based on the reorientation of particles in response to the applied magnetic field, which alters the 
-packing arrangement of the particles at the interface. By modifying the interfacial packing, the point at which the particles jam is also altered, thereby 
-affecting the jamming point of the bijel. This mechanism is expected to be effective both during and after the synthesis process. Additionally, the 
-processability of bijels produced using this technique will be examined to assess how changes in particle packing influence the rheological properties of 
-the material.
+This dissertation investigates the potential of magnetically responsive ellipsoidal particles to enable stimuli-responsive control of bijel microstructure. 
+Specifically, it explores whether magnetic fields applied during or after formation can induce meaningful microstructural changes, and how these changes 
+influence the rheological properties of the resulting materials. The central hypothesis is that particle reorientation under magnetic fields alters 
+interfacial packing, modifying the jamming threshold and thus the resulting domain morphology. By quantifying these effects across different processing 
+conditions, this work aims to establish new methods for tunable bijel synthesis.
 
-% \section{Research objective}
-
-% % this work seeks to identify means to control the bijel microstructure independent of the casting mixture composition utilizing magnetic stimuli response of anisotropic particles.
-The proposed mechanism of microstructure modification is driven through reorientation of the particles to the applied magnetic field altering how the particles pack on the interface.
-
-% \subsection{Aim 1: Determination of the degree of microstructure changes expected when applying a constant field during bijel formation}
-% \label{section:aim1_desc}
-
-The jamming point of a bijel plays a crucial role in determining the resulting microstructure, as demonstrated by previous studies comparing the length scales 
-of bijels synthesized with varying particle volume fractions and sizes \cite{jansen_bijels_2011, reeves_particle-size_2015}. Additionally, it has been shown 
-that magnetic fields can facilitate the self-assembly of ellipsoidal particles at interfaces and control the interfacial angle between the particle's axis 
-of symmetry and the interface \cite{davies_interface_2014, davies_assembling_2014}. However, on a curved interface with numerous other particles, it remains 
-unclear how the orientation of multiple particles in response to the field and their regular arrangement will influence the jamming behavior of the bijel 
-\cite{bresme_orientational_2007, davies_interface_2014}. Therefore the microstructural response of bijels as a function of the applied field will be 
-characterized.
-
-A homogeneous mixtures containing spherical and ellipsoidal particles will be subjected to field strengths both above and below the critical field strength. 
-This critical field strength is the threshold 
-at which particle orientations to the interface are governed by the applied field, as calculated by Bresme and Faraudo for the particle aspect ratio 
-\cite{bresme_orientational_2007, davies_interface_2014}. The range of selected field strengths will provide insight into the mechanisms controlling 
-microstructural changes, enabling verification of the hypothesis and identification of the conditions under which the most control over the microstructure 
-can be achieved.
-
-The average and directional domain sizes, along with their relationship to tortuosity, will be used to characterize the microstructural properties of the 
-resulting bijel. The nematic order parameter and the average interfacial angle will provide insight into how the application of the field influences particle 
-ordering, both among the particles and relative to the interface. Finally, the radial distribution function will be employed to assess whether the expected 
-orientational changes upon field application affect the packing of particles at the interface.
-
-\subsection{Aim 2: Microstructure changes and timescales upon application of a magnetic field after formation}
-\label{section:aim2_desc}
-
-Particles at the surface of emulsion droplets have been shown to unjam and rejam into new, stable microstructures upon the application of stimuli 
-\cite{cui_stabilizing_2013}. Magnetic fields applied to bijels stabilized with ellipsoidal particles will promote the unjamming and rejamming of the 
-particle monolayer, leading to modifications in the bijel's microstructure. Due to local changes in the state of the particles—specifically, alterations 
-in the interfacial ordering and the direction and arrangement of particles—we anticipate that microstructure changes will persist even after the magnetic 
-field is turned off. Two mechanisms for microstructure modification are proposed. The first suggests that the adsorption energy is sufficiently strong to 
-cause the interface to move with the particles, allowing them to rejam in new locations and orientations relative to the field. The second mechanism posits 
-that the particles tilt within the interface, leading to domain coarsening before jamming in their new positions and orientations. This study will assess the 
-mechanism, the resulting microstructural changes, and the associated timescales.
-
-The response of bijels to magnetic fields will be evaluated by analyzing how model bijels, synthesized without applied fields, respond to field 
-strengths both above and below the critical field strength, as calculated using Bresme and Faraudo's theory. Microstructural properties, including the 
-average domain size, particle orientation relative to the field and interface, and the Steinhardt 6-fold bond order parameter, will be used to examine 
-the spatial relationships between particles and their neighbors. These techniques will enable the identification of the mechanisms active at different 
-magnetic field strengths. Additionally, the observed microstructure changes will be characterized and compared to assess how the applied magnetic field 
-influences the final microstructure.
-
-Next, the importance of the initial ordering of the particle monolayer will be assessed by increasing the applied field to levels equal to the surface 
-tension forces on bijel templates simulated under various field strengths. The applied field will also be switched off for bijel templates simulated under 
-the same conditions. The same analysis metrics mentioned previously will be used. Additionally, microstructures with the same difference in applied field 
-will be examined to investigate the reversibility of bijel microstructures.
-
-\subsection{Aim 3: Rheological characterization of bijels formed under and subjected to a magnetic field}
-\label{section:aim3_desc}
-
-In many of the fabrication processes described above, the rheology of the bijel casting mixture plays a crucial role 
-\cite{haase_continuous_2015, cai_bijels_2017, amirfattahi_fabrication_2024}. Furthermore, the mechanical performance of the
-resulting bijel is a key constraint for bijels in cross flow reactors or water filtration applications. \cite{boakye-ansah_controlling_2020}
-Under high shear, the bijel can fail due to particles being ejected from the interface limiting the flow rate and pressure that can
-be used when using bijels as cross flow reactors or water filtration systems. Ching demonstrated that, rheologically, bijels behave 
-as colloidal glasses percolating in 3D space \cite{ching_bijel_2022}. This implies a yield stress above which flow of the material
-will initiate. Bijels are also shear thinning as fluid-particle interactions increase the effective viscosity at lower shear rates.
-
-% $Ca_s = \frac{\eta_{f} \dot{\gamma} L_{1}}{\sigma}$ where $\dot{\gamma} = \frac{u_{LE}}{L_x}$ is the strain rate and 
-% $L_1$ is the average domain size. \cite{frijters_effects_2012, yang_capillary_2022} Lower capillary numbers in the range of
-%  $ 10^{-7} \geq Ca_s \leq 10^{-5}$ will be utilized. 
-% which corresponds to a $Ma << 0.01$ to accommodate the hydrodynamic model utilized.
-
-In this study, the yield stress and viscosity of the bijels will be examined as a function of the initial microstructure under various $Ca_s$ values. 
-A shear capillary number, $Ca_s$, is defined to correlate the applied strain rate with the capillary forces derived from surface tension 
-\cite{frijters_effects_2012, yang_capillary_2022}. This study aims to identify the effect 
-of the initial microstructure and applied field on the rheological properties of the bijel.The initial microstructure will be 
-derived from bijels stabilized with ellipsoidal particles, synthesized both without a magnetic field and with a field 
-strength equal to the surface tension energy. Constant shear, defined by $Ca_s$, will be applied to determine the yield stress and non-Newtonian 
-characteristics of the bijel. Previous studies have shown that particle ordering in the direction of shear significantly alters the rheological behavior 
-compared to unordered systems. Additionally, the domains within the bijel may introduce new mechanisms for modifying rheological properties, which have 
-yet to be explored in detail.
-
-% We will then investigate the complex rheology of the bijels by calculating the loss and storage moduli of the bijel microstructures described 
-% earlier as a function of oscillatory shear. The loss and storage moduli describe the viscous and elastic behavior of the bijel, respectively, 
-% allowing the gel point of the bijel to be determined as the point at which the storage modulus exceeds the loss modulus. Special attention will be 
-% given to the state of the particles in all simulations, correlating changes in particle properties with observed rheological events. Additionally, 
-% we will assess whether shear banding occurs.
+The remainder of this dissertation is structured as follows. Chapter 2 provides a review of the literature on the microstructures and factors affecting
+particle stabilized emulsion and bijel formation, synthesis techniques for bijels and rheology of bijels. Chapter 3 outlines the simulation methods 
+employed, including the Lattice Boltzmann approach and magnetic dipole modeling. Chapter 4 examines the impact of magnetic fields applied during bijel 
+formation, characterizing changes in domain structure and particle ordering. Chapter 5 explores post-formation responsiveness by analyzing unjamming 
+and reordering effects. Chapter 6 evaluates the rheological consequences of microstructural modifications, focusing on yield stress and shear-thinning 
+behavior. Finally, Chapter 7 summarizes the findings and discusses their implications for the design of tunable porous materials, as well as some 
+future avenues of exploration uncovered during this investigation.

### 2025-03-24 chapters/LBM_technique.tex
Changes 1. Reworded introduction and lit review and addressed grammar and vocab issues 2. Fixed some referencing problems in the document 3. Fleshed out introduction in paper 2 4. Added sections for results in paper 3
Changes 1. Added conclusion in final remarks 2. Added hysteresis curve for prolate particles stabilized bijels in aim2 section 3. Added description of synthesis techniques in lit review
Changes 1. Refined text in most sections 2. Resized figures for consistency of figure size 3. Removed shear banding analysis and added how shear stress is calculated
Changes 1. Modified and added

@@
-\label{section:methods}
+\section{Methods} \label{section:methods}
 
@@
 provided in the following sections
+
+\section{Lattice Boltzmann Method}
+
+The Lattice Boltzmann Method (LBM) is an evolution of preceding lattice gas automata techniques, which is a discretization of the Boltzmann equation of motion for 
+molecules. This means that unlike traditional CFD techniques such as FDM, VOF or level set methods, LBM is a psuedo-molecule method that tracks the evolution of a 
+particle distribution function within grid cells evolved through a discretized Boltzmann equation of motion. Macroscopic variables such as fluid density and 
+velocity are recovered from the particle distributions through appropriate moment integration, and the Navier Stokes equation at the incompressible limit can be 
+obtained through a Chapman-Enskog expansion of the LBM. The LBM has become an attractive tool for meso-scale CFD simulations due to its ease of algorithm 
+implementation, highly parallelizable nature and ease of boundary condition implementation, allowing coupling to other physically relevant systems such as 
+particles with varieties of potentials, external fields and deformable bodies.
+
+The particle distribution function described earlier is advected on a pre-constructed lattice stencil, commonly denoted as DnQm where n and m represent the 
+number of dimensions and directions in the stencil. Common stencils include the D1Q5, D2Q9 and D3Q19 stencil, all of which recover mass and momentum conservation. 
+For energy conservation, a higher order stencil such as D3Q27 is necessary. The D2Q9 and D3Q19 stencils have 8 and 18 populations respectively that include 
+connections to nearest and next nearest neighbour points, in addition to a central rest point.
+
+The LBM is composed of a collision and advection step. In the advection step, the populations at each grid point are propagated to adjacent points in accordance 
+with the chosen stencil. During the collision step, the particle population distribution is relaxed towards an equilibrium with a collision operator, at a 
+specified relaxation rate. The collision operator can have multiple forms based on how many relaxation rates are used although the most common variant is the 
+Single Relaxation Time (SRT) collision operator, more commonly known as the Bhatnagar-Gross-Krook (BGK) collision operator. Owing to its stability in low Mach 
+and Reynolds numbers and simplicity of implementation, the BGK operator is often used in common particle laden flow and soft matter scenarios. 
+\cite{bhatnagar_model_1954} These limitations are present owing to the implicit link between the fluid properties and the relaxation rate necessitating 
+relaxation rates above 0.5, and to ensure fluid incompressibility from an equation that intrinsically simulates a compressible fluid. To get over these 
+limitations, Two Relaxation Time (TRT) and Multiple Relaxation Time (MRT) operators also exist, expanding the possible application of the LBM to visco-elastic 
+flows and implementation of fluctuating hydrodynamics in the LBM. \cite{liu_simulation_2023, adhikari_fluctuating_2005}
+
+Four primary techniques to model multicomponent or multiphase systems exist in the LBM literature. A quick review of the Shan-Chen or 
+interparticle potential model  will be provided here from the perspective of a binary mixture. Additionally, the names and descriptions of 
+other techniques will be described as well. The interparticle potential model or Shan-Chen model that adds a non-local density dependent force 
+between two species, effectively modelling non-ideal mixing and recovering the Cahn-Hilliard equation. To alleviate the standard Shan-Chen implementations 
+weaknesses of not being thermodynamically consistent and reducing the existence of spurious velocities,
+
+In addition to the Shan-Chen model, the color gradient model, free energy model and interface tracking technique all 
+allow for simulations of various types of multiphase and/or multicomponent flows. The color gradient model proposed by Rothman and Keller and 
+implemented by Gunstensen et al relies upon modelling two particle distributions. These represent a binary fluid mixture with the collision step 
+able to recover the hydrodynamics and non-ideal mixing dynamics. The free energy model utilizes phase field theory and constructs a free energy 
+functional to recover interfacial dynamics and effects in a thermodynamically consistent manner. Often, a square gradient free energy is used for 
+simplicity and ease of implementation. The mean field theory The non-ideal mixing dynamics are recovered during the "recoloring" step, of which the 
+technique proposed by Latva-Kokko and Rothman is more commonly used for soft matter flows. \cite{liu_multiphase_2016}
 
@@
     \centering
-    \includegraphics[scale = 0.7]{figures/methods/d3q19_lattice.jpg}
+    \includegraphics[scale = 1]{figures/methods/d3q19_lattice.jpg}
     \caption{D3Q19 lattice demonstrating the rest, nearest and next nearest direction that correspond to the 19 
     directions $(i)$ of the lattice with lattice velocity $c_{i}$. \cite{schmieschek_lb3d_2017} Reproduced from 
-    Schmieschek et al. under the Creative Commons license.}
+    Schmieschek et al. Computer Physics Communications 2017, 217, 149--161, under the Creative Commons license.}
     \label{fig:d3q19_lattice}
@@
 This recasting of the velocity ensures that in the absence of forces, the total momentum of the system is conserved.
+
+% \textcolor{blue}{https://doi.org/10.1103/PhysRevE.84.046710}
 

### 2025-03-24 chapters/lit_review.tex
Changes 1. Updated lit review text for flow and clarity. Still have work to do here

@@
-\section{Emulsion stability and microstructures}
+\section{Formation of particle stabilized emulsions}
 
-When two partially miscible fluids are mixed, they tend to separate into distinct phases to minimize the thermodynamic penalty associated with interfacial formation. 
+When two partially miscible fluids are mixed, they phase separate into distinct phases to minimize the thermodynamic penalty associated with interfacial formation. 
 To inhibit this phase separation, small-molecule surfactants are conventionally employed. A well-known example of such a material is soap, which facilitates the 
@@
 
-The existence of particle-stabilized emulsions has been recognized for over a century, following the independent discoveries by Pickering and Ramsden, who observed dispersed 
-oil droplets within a water matrix after vigorous stirring of an oil-water-particle mixture \cite{ramsden_separation_1904, pickering_cxcvi.emulsions_1907}. Unlike surfactants, 
-which stabilize emulsions by reducing interfacial tension, particles act as stabilizers by adsorbing at the interface between the dispersed and continuous phases, thereby 
-preventing direct contact between them. The Pieranski model is commonly used to determine the adsorption 
-energy of a particle at an interface. It is expressed as $ G_{ads} = \sigma A_{rm} (1 - \cos{\theta_c})^2 $ where $G_{ads}$ represents the free energy reduction upon particle 
-adsorption, $\sigma$ is the surface tension between the partially miscible fluids, and $ \theta_c $ is the contact angle of the particle. Particles at the interface are 
-generally considered irreversibly adsorbed, even at the nanoscale. For particles larger than 100 nm, the adsorption energy is sufficiently high that thermal fluctuations at 
-the interface can be considered negligible \cite{cheung_molecular_2011}.
+Without the addition of a stabilizer, the dispersed phase will coalescence to reduce the surface area of the interface. To facilitate the stability of small
+droplets in the continuous phase, stabilizers such as surfactants, particles or bio-polymers are added. These additives reduce the interfacial energy between
+phases characterized through the Pieranski model, $ G_{ads} = \sigma A_{rm} (1 - \cos{\theta_c})^2 $, where $G_{ads}$ represents the free energy reduction upon particle 
+adsorption, $\sigma$ is the surface tension between the partially miscible fluids, and $ \theta_c $ is the contact angle of the particle. Surfactants and bio-polymers work
+through reducing the surface tension between the dispersed and continuous phase. Particle stabilizers work to stabilize emulsions through reducing the interfacial area between
+fluids.
 
@@
 Compared to surfactant-stabilized emulsions, particle-stabilized emulsions exhibit greater resistance to coarsening, leading to renewed interest in their applications. 
-The microstructural properties of these emulsions were extensively studied in the early 2000s by Lumsdon, Binks, and others. Their findings indicated that the emulsion 
-droplet radius follows the relationship $R_e \propto \frac{\phi_w}{\phi_p}$, where $\phi_w$ and $\phi_p$ represent the volume fractions of water and particles, 
+The microstructural properties of these emulsions were extensively studied in the early 2000s by Binks and Lumsdon when they investigated the effect of particle size
+on the resulting Pickering emulsion droplet size. \cite{binks_pickering_2001} Their findings 
+indicated that the emulsion droplet radius follows the relationship $R_e \propto \frac{\phi_w}{\phi_p}$, where $\phi_w$ and $\phi_p$ represent the volume fractions of water and particles, 
 respectively \cite{binks_pickering_2001}. Additionally, they identified several factors influencing the microstructure of Pickering emulsions, including fluid concentration 
 and particle wettability. Neutrally wetting particles do not impose a preferential curvature on the interface, whereas non-neutrally wetting particles can lead to the 
-formation of bridged droplets, capillary aggregates, and other non-spherical microstructures. A notable example is bijels, which are synthesized in systems containing equal 
-volume fractions of immiscible fluids and neutrally wetting particles, leading to the formation of tortuous, co-continuous domains.
+formation of bridged droplets, capillary aggregates, and other non-spherical microstructures, shown in Figure \ref{fig:state_diagram_particle_emulsions}
 
-Bijels are synthesized in systems containing approximately equal fluid volume fractions and neutrally wetting particles to prevent the imposition of preferential 
-curvature at the interface \cite{stratford_colloidal_2005, herzig_bicontinuous_2007, lee_bicontinuous_2010, jansen_bijels_2011, velankar_non-equilibrium_2015}. 
-Reeves et al. demonstrated that bijels stabilized with nanoparticles exhibit greater stability than those stabilized with microparticles due to enhanced mechanical 
-properties and improved interfacial coverage \cite{reeves_particle-size_2015}. 
-Furthermore, research by Jansen, Harting, and Hijnen et al. established that the bijel domain size follows the relationship $ L \propto \frac{1}{\phi_p} $ for both 
-rod-like and spherical particles. While the proportionality constant depends on particle geometry, this trend has been observed across various particle shapes 
-\cite{hijnen_bijels_2015, madivala_exploiting_2009, gunther_timescales_2014, daware_emulsions_2015, loudet_capillary_2005, cheng_shape-anisotropic_2013}.
+\begin{figure}
+    \centering
+    \includegraphics[scale = 0.3]{figures/literature_review/state_diagram.jpg}
+    \caption{Formation criteria for a particle stabilized emulsion that can form bijel. \cite{velankar_non-equilibrium_2015}
+            Used with permission of Royal Society of Chemistry, from A non-equilibrium state diagram for liquid/fluid/particle 
+            mixtures, Velankar, 1, 11, 2015. Permission conveyed through Copyright Clearance Center, Inc}
+    \label{fig:state_diagram_particle_emulsions}
+\end{figure}
 
-% While bijels are a relatively new material class, much work has been conducted to elucidate the underlying mechanisms controlling their stability, microstructure and rheology.
-Many studies focus on how the particle properties play important roles in tuning the properties of bijels.
-This section will cover a brief overview and summary of literature on the working principle behind particle surfactants, the effect of size and concentration of particles, anisotropic particles in particle stabilized emulsions, microstructure control in various bijel synthesis techniques, stimuli response in bijels and bijel rheology.
+\section{Bicontinuous interfacially jammed emulsion gels}
+
+From Figure \ref{fig:state_diagram_particle_emulsions}, the formation of bijels is shown to require equal volume fraction of fluids and neutrally wetting particles. This
+microstructure was first identified in 2005 when Stratford et al. used a multicomponent Lattice Boltzmann Method coupled with particles to characterize the microstructure
+and dynamics of particles stabilized emulsions made with equal volume fractions of a binary fluid and suspended particles. \cite{stratford_colloidal_2005} They characterized
+that upon initiation of the simulation, the fluids began to undergo spinodal decomposition. As the interface coarsens, particles adsorb onto it. When the particle surface area
+and cross sectional area of the particles match, coarsening jams in place resulting in a tortuous co-continuous morphology. A visualization of this process is shown in 
+Figure \ref{fig:bijel_coarsen}.
+
+\begin{figure}
+    \centering
+    \includegraphics[scale = 0.3]{figures/introduction/bijel_coarsening.jpg}
+    \caption{Initiation and arrest of spinodal decomposition as particles adsorb onto the interface, followed by jamming once the 
+    interfacial area matches the cross sectional area of the adsorbed particles\cite{stratford_colloidal_2005}. 
+    Reproduced from K. Stratford et al., Science 309, 2198-2201(2005) under license number 5966820525314.}
+    \label{fig:bijel_coarsen}
+\end{figure}
+
+After their discovery in 2005, bijels were realized in experiments in 2007 using a 2-6 lutidine/water system stabilized by surface modified silica particles.
+\cite{herzig_bicontinuous_2007} The 2-6 lutidine/water system has a lower critical solution temperature (LCST) of 34.1$^{\circ}C$ and a critical weight fraction of
+approximately 28 \% lutidine. \cite{herzig_bicontinuous_2007} Herzig et al. began with a fluid mixture at the critical weight fraction and raised the 
+temperature past the LCST, initiating phase separation. \cite{herzig_bicontinuous_2007} This process is known as Thermally Induced Phase Separation (TIPS). 
+The domains of the fluid coarsened until they observed
+gelation of the system. \cite{herzig_bicontinuous_2007} Since then, other systems based on small molecules, oligomers and polymers have been prepared. 
+\cite{tavacoli_novel_2011, lee_bicontinuous_2010, bai_dynamics_2015, ching_rapid_2021} These works have been primarily based on
+thermally induced phase separation although as this literature review will show modern bijel fabrication techniques have moved
+away from this method to induce phase separation.
+
+Computational simulations have investigated the effect of fluid density, surface tension and particle volume fraction.
+\cite{jansen_bijels_2011} Jansen and Harting utilized a multicomponent Lattice Boltzmann method to assess the effect of fluid volume fraction,
+particle volume fraction, surface tension, fluid density and particle contact angle on the microstructure of particle stabilized emulsions.
+They demonstrated that the effect of the surface tension and initial fluid density were small
+compared to the volume fraction of particles by measuring the length scale of the bijels. \cite{jansen_bijels_2011} The length of 
+particles was proportional to the inverse of the particle volume fraction, $L \propto \frac{1}{\phi_p}$. \cite{jansen_bijels_2011} 
+Jansen and Harting also illustrated that the emulsion state obtained, whether a Pickering emulsion or bijel, was most affected by 
+the contact angle of the particle stabilizer and fluid ratio rather than the particle volume fraction. \cite{jansen_bijels_2011}
+
+Further investigations of the bijel microstructure look at calculating the morphology of the bijel through topological, geometric 
+or image analysis techniques. Topological techniques include the quantification of the genus and channel size distribution which
+allow for determination of differences in the interfacial properties. \cite{chan_channel_2012} Chan and Thornton compared the topology
+of bicontinuous systems obtained using the Cahn-Hilliard and Allen-Cahn equations and identified how they differed. \cite{chan_channel_2012}
+Topological techniques have the advantage
+of being able to characterize the microstructure of a bicontinuous material while also providing information about the connectivity of the
+structure.
+
+Geometric techniques such as
+calculating the curvature of the bijel have also been used to identify the impact of particle size and quench rate on the microstructure
+of bijels. Reeves et al. compared the Gaussian curvatures of bijels stabilized with micro and nanoparticles, as well as the effect of quench rate
+on bijels formed using thermally induced phase separation to characterize that reduced particle size resulted in the interface maintaining a more negative
+Gaussian curvature. \cite{reeves_particle-size_2015,reeves_quantitative_2016}
+The interface of bijels are most similar to minimal surfaces, which indicates their mean curvature and Gaussian curvature are 0 and negative respectively. 
+\cite{jinnai_interfacial_2001} Nanoparticles are able to conform to curved surfaces better as they are less disruptive to the curvature of the interface, resulting
+in more effective stabilization of saddle like regions. \cite{reeves_quantitative_2016}
+
+Image analysis techniques have also been used to characterize the microstructure of bijels, providing information on the connectivity, pore size
+distribution, tortuosity and self similarity. \cite{mcdevitt_microstructural_2019,reeves_quantitative_2016} Connectivity can be derived from region
+growing algorithms, labelling algorithms such as Hoshen-Kopelmann and segmentation. \cite{mcdevitt_microstructural_2019,reeves_quantitative_2016}
+The pore size distribution can be obtained from watershed algorithm. \cite{mcdevitt_microstructural_2019}
+
+\section{Bijel synthesis techniques}
+
+TIPS has enabled batch synthesis of bijels in research laboratories. However, for bijels to become industrially viable, a continuous fabrication process is required.
+This technique should also be flexible enough to produce tailored bijel microstructures to different applications. Solvent Transfer Induced Phase Separation (STrIPS) 
+has been shown as a method to achieve this, shown in Figure \ref{fig:strips}. Figure \ref{fig:strips}a) shows the preparation of casting mixture in STrIPS. The casting
+mixture is a ternary fluid system comprised of the fluids making up the bijel and a solvent. Figure \ref{fig:strips}b) demonstrates the removal of solvent from the
+casting mixture, by flowing a co-solvent past the casting mixture, initiating phase separation. A narrow range of compositions can be used to ensure that the composition
+of the phase separating mixture remains within the spinodal line of the demixed region of the phase diagram. Figure \ref{fig:strips} shows how varying the flow rate
+of the casting mixture and the solvent removal medium is necessary to control the morphology of the bijel.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale = 5]{figures/introduction/STrIPS.jpg}
+    \caption{STrIPS in action. Extrusion of the bijel casting mixture into a non-solvent bath, followed by removal of solvent from 
+             the casting mixture through diffusion. \cite{haase_continuous_2015}. Reproduced with permission from Wiley-VCH Verlag GmbH 
+             \& Co. KGaA from \textit{Continuous Fabrication of Hierarchical and Asymmetric Bijel Microparticles, Fibers, and Membranes by 
+             Solvent Transfer-Induced Phase Separation (STRIPS)}, Haase, M. F., Stebe, K. J., 
+             \& Lee, D., \textit{Advanced Materials}, 27(44), 7065-7071, 2015}
+    \label{fig:strips}
+\end{figure}
+
+STrIPS has been used extensively in a variety of systems ranging from bijels for battery electrode templates, to drug delivery medium, liquid in liquid printing and
+intrinsically polymerizable bijels facilitating the production of free standing structures.
+\cite{garcia_scalable_2019,thorson_bijel-templated_2019, amirfattahi_fabrication_2024, ching_rapid_2021} STrIPS is flexible to the casting mixture being used. The
+only requirement a casting mixture used for STrIPS is that the phase diagram for the casting mixture must be well understood so that the solvent transfer step remains
+within the spinodal at all times.
+
+Another technique based on the removal of solvent is Vapor Induced Phase Separation(VIPS). \cite{wang_scalable_2020} A quarternary casting mixture
+containing particles, solvent and two partially miscible liquids is prepared. The solvent and liquid species and compositions are carefully selected to ensure that 
+removal of the solvent will cause phase separation of the two partially miscible liquids through the critical point of the phase diagram. This ensures that phase separation
+only occurs through spinodal decomposition. One system that has been 
+used is the water/hexanediol-diacrylate solvated by ethanol. Removal of ethanol at room temperature is sufficient to facilitate bijel formation, with this bijel
+mixture composition being able to be spray or blade coated. This technique is limited by the temperature dependence of surface tension, meaning that the casting mixtures
+that can be used are limited to solvents that can vaporize at room temperature.
+
+Instead of relying upon spinodal decomposition to generate the bijel morphology, homogenization uses shear to join phase separating domains, resulting in a 
+structure that has the properties of a bijel even if not fabricated from fluids undergoing spinodal decomposition. \cite{huang_bicontinuous_2017, cai_bijels_2017} 
+This method is primarily used for nanoparticles under $50$ nm and it has been shown to work for multiple particle geometries. This method relies upon
+shear to cause limited coalescence of droplets. As coarsening occurs, particles adsorb on the interface and when the interfacial area matches the area of the
+adsorbed particles, the microstructure jams. Microstructure tuning of the method can be done through modifying the contact angle of the particles through addition of
+surfactants or viscosity of the phase separating fluids through the addition of viscosity modified such as oligomers. Thus far, all these synthesis techniques use
+spherical particles to stabilize the bijels that are generated.
+
+\section{Ellipsoidal particles at interfaces}
+
+Over the past decade, advancements in synthesis techniques have significantly expanded the ability to fabricate particles with anisotropic geometry and surface chemistry. 
+The choice of synthesis method depends on the desired particle shape. For example, ellipsoidal particles can be readily produced through the mechanical deformation of 
+polymer spheres, while dumbbell-shaped particles can be synthesized using microfluidic devices or emulsion templating. \cite{fei_magneto-capillary_2020} 
+Square-shaped particles, on the other hand, can be 
+generated through controlled crystallization \cite{morgan_understanding_2013}. The increasing variety of synthesis methods has reduced geometric constraints when exploring 
+potential particle stabilizers for bijels \cite{wu_recent_2016}.
 
@@
 
-\section{Particle shape anisotropy and synthesis techniques}
-
-Over the past decade, advancements in synthesis techniques have significantly expanded the ability to fabricate particles with anisotropic geometry and surface chemistry. 
-The choice of synthesis method depends on the desired particle shape. For example, ellipsoidal particles can be readily produced through the mechanical deformation of 
-polymer spheres, while dumbbell-shaped particles can be synthesized using microfluidic devices or emulsion templating. Square-shaped particles, on the other hand, can be 
-generated through controlled crystallization \cite{morgan_understanding_2013}. The increasing variety of synthesis methods has reduced geometric constraints when exploring 
-potential particle stabilizers for bijels \cite{wu_recent_2016}.
-
 Anisotropic particles exhibit shape-dependent properties due to their ability to induce multipolar interactions by deforming the interface to maintain a mean curvature of 
 zero, thereby satisfying the Young-Laplace equation, as illustrated in Figure \ref{fig:anisotropic_particle_interface} \cite{loudet_capillary_2005, cheng_shape-anisotropic_2013}.
-This property has been leveraged to facilitate directed assembly and migration through modified capillary forces 
+This property has been leveraged to facilitate directed assembly and migration through modified capillary forces imparted through curvature gradients at interfaces.
 \cite{cavallaro_curvature-driven_2011, read_dimerization_2020, sharifi-mood_curvature_2015}.
-
-When stabilizing bijels, ellipsoidal particles provide greater stability than spherical ones due to their higher cross-sectional area-to-volume ratio, as demonstrated by 
-Günther et al. and Hijnen et al. \cite{gunther_timescales_2014, hijnen_bijels_2015}. This enhanced stability arises from additional domain coarsening timescales associated 
-with particle reorientation and increased mechanical rigidity, as confirmed by rheological studies \cite{gunther_timescales_2014, daware_emulsions_2015, witt_bijel_2013}. 
-Furthermore, particle shape influences both the onset and dynamics of jamming. Studies using graphene plate-like particles have shown that these particles exhibit intrinsic 
-elasticity, which affects the conditions under which jamming occurs \cite{imperiali_simple_2014, sun_assembly_2013}.
-
-The orientation of ellipsoidal particles at interfaces is governed by a balance between interfacial capillary forces and external magnetic fields 
-\cite{bresme_orientational_2007, davies_assembling_2014}. Theoretical studies and simulations suggest the existence of a critical field strength beyond which particle 
-orientation is predominantly dictated by the applied field \cite{bresme_orientational_2007, davies_assembling_2014}. Additionally, both experimental and computational 
-studies have shown that steric interactions—modulated by particle orientation and interfacial arrangements—play a significant role in determining the free energy of particle 
-assemblies, underscoring the intricate interplay between these forces \cite{morgan_understanding_2013, newton_influence_2014, newton_capillary_2018}.
-
+Simulations have shown that ellipsoidal particles can adopt metastable orientations depending upon the perturbations
+the particle experiences. \cite{gunther_lattice_2013}
 % The adsorption process is affected by the shape of particles used as they pack differently onto the interface \cite{hijnen_bijels_2015, daware_emulsions_2015,carmack_diverse_2017}.
@@
 
-\section{Bijel synthesis techniques}
+Ellipsoidal particles have been used as stabilizers in bijels, resulting in bijels that have smaller domains than those made with spherical particles
+at the same volume fraction, identified to arise from the  greater surface area to volume ratio of ellipsoidal particles compared to spherical particles. 
+\cite{gunther_timescales_2014} The evolution of the microstructure is also distinct to bijels stabilized with spheres, demonstrating two timescales at
+early and later timesteps. \cite{gunther_timescales_2014} The short timescale is during formation of the bijel, when particles are adsorbed onto the
+interface and rotate to align with the interface. At longer timescales, capillary interactions between particles lead to reordering of particles
+at the interface, leading to a different interfacial configuration and microstructure. \cite{gunther_timescales_2014}
 
-The existence of bijels was first identified computationally using a multicomponent lattice boltzmann method which looked at 
-the jamming of spherical particles in a binary fluid system with equal volume fraction of each fluid. 
-\cite{stratford_colloidal_2005} Once phase separation was initiated, the particles adsorb onto the interface until the interfacial
-area matches the cross sectional area of the particles at the interface, when domain coarsening is ceased. The simulation assumed
-an equal volume fraction of fluid components and neutrally wetting particles to not impart preferential curvature onto the interface.
-Figure \ref{fig:state_diagram_particle_emulsions} demonstrates a schematic derived from experimental results of particle stabilized
-emulsion microstructures that form when changing the volume fraction and particle contact angle.
+Rod like particles have also been used as stabilizers in experiments, identifying that the length scale of the pores of 
+the bijels follows $ L \propto \frac{1}{\phi_p} $ even if the proportionality constant is different. While the proportionality constant depends on 
+particle geometry, this trend has been observed across various particle shapes 
+\cite{hijnen_bijels_2015, madivala_exploiting_2009, gunther_timescales_2014, daware_emulsions_2015, loudet_capillary_2005, cheng_shape-anisotropic_2013}.
+The dynamics of bijels stabilized by ellipsoidal particles are also distinct from bijels stabilized by spheres, caused by reorientation of particle
+stabilizers at the interface.
 
-In experiments, bijels were first synthesized using Thermally Induced Phase Separation (TIPS) \cite{herzig_bicontinuous_2007, lee_bicontinuous_2010, bai_dynamics_2015}. 
-The process begins by identifying a small-molecule or polymer blend with a critical point, referred to as the casting mixture, and preparing it at a composition 
-corresponding to this critical point. The casting mixture is then combined with particle surfactants while remaining in a single-phase state. Once the particles 
-are homogeneously distributed, phase separation is induced by adjusting the temperature to bring the system into the two-phase region. By ensuring that the 
-composition aligns with the critical point, the casting mixture undergoes spinodal decomposition, preventing nucleation and growth.
+\section{Magnetic fields applied to particles at interfaces}
 
-\begin{figure}
-    \centering
-    \includegraphics[scale = 0.3]{figures/literature_review/state_diagram.jpg}
-    \caption{Formation criteria for a particle stabilized emulsion that can form bijel. \cite{velankar_non-equilibrium_2015}
-            Used with permission of Royal Society of Chemistry, from A non-equilibrium state diagram for liquid/fluid/particle 
-            mixtures, Velankar, 1, 11, 2015. Permission conveyed through Copyright Clearance Center, Inc}
-    \label{fig:state_diagram_particle_emulsions}
-\end{figure}
+Magnetic fields offer a non-invasive and targeted method for manipulating the behavior of particles. Magnetic particles can be fabricated from
+coatings applied onto particles through deposition techniques or a core-shell particle that encapsulates a magnetic core with a non-magnetic shell. 
+\cite{fei_magneto-capillary_2020, nakayama_stimuli-responsive_2018} These effects arise due to the interplay between the magnetic torque or force 
+acting on the particles and the capillary interactions that govern their behavior at the interface. One theory developed for neutrally wetting ellipsoidal 
+particles is Bresme-Faraudo theory. \cite{bresme_orientational_2007, davies_interface_2014}
 
-TIPS enables batch synthesis of bijels in research laboratories. However, for bijels to become industrially viable, a continuous fabrication process is required—one 
-that also allows for the production of various bijel form factors suited to different applications. Solvent Transfer Induced Phase Separation (STrIPS) has been proposed 
-as a method to achieve this. In STrIPS, a casting mixture is prepared, consisting of two fluids that form the bijel, a co-solvent, particles, and a surfactant. Phase 
-separation is initiated as the co-solvent diffuses out of the bijel. The surfactant is included to maintain bijel stability against Marangoni forces. The casting mixture 
-is then extruded into a bath of a non-solvent, which is immiscible with the bijel-forming fluids but miscible with the co-solvent. The diffusion of the co-solvent triggers 
-phase separation, leading to bijel formation. The resulting microstructure is influenced by both the surfactant concentration and the flow rate of the casting mixture.
+A wide range of behaviors has been observed when magnetic fields are applied to interfacial particles. Individual particles tend to align their magnetic 
+dipole moments along the direction of the field, causing them to reorient relative to the interface. \cite{kim_bijels_2010}
+For anisotropic particles such as ellipsoids, this results in a tilt or rotation that changes their interfacial footprint and local curvature. 
+\cite{davies_assembling_2014, davies_interface_2014} The orientation of the particle is a function of the capillary interactions with the interface that 
+prefers to keep the particle flat on the interface and the magnetic field that is attempting to rotate the particle out of the interface. The magnetic force
+experienced by the particle is a function of the applied field strength, magnetic susceptibility, size of the particle, shape of the particles 
+and aspect ratio of the particle.
 
-Vapor Induced Phase Separation(VIPS) has also been identified as a technique for continuous fabrication of bijels. \cite{wang_scalable_2020} A quarternary casting mixture
-containing particles, solvent and two partially miscible liquids is prepared. The solvent and liquid species are carefully selected to ensure that removal of the
-solvent will cause phase separation of the two partially miscible liquids. One system that has been used is the water/hexanediol-diacrylate solvated by ethanol.
-Selection of the composition of the system facilitates crossing of the binodal through the critical point, causing phase separation through spinodal decomposition.
-This technique has been used to fabricate thin films of bijels blade and spray coated onto substrates.
+The equilibrium and metastable orientations of non-spherical particles at fluid interfaces are governed by a complex interplay of particle shape, 
+interfacial tension, and external forces such as magnetic fields. Depending upon the surface wettability and aspect ratio of the particle, non-spherical
+particles have been observed to adopt several stable and metastable orientations. \cite{morgan_understanding_2013, newton_influence_2014}
 
-Instead of relying upon spinodal decomposition to generate the bijel morphology, homogenization uses shear to join phase separating domains, resulting in a 
-structure that has the properties of a bijel even if not fabricated from fluids undergoing spinodal decomposition. \cite{huang_bicontinuous_2017, cai_bijels_2017} 
-This method is primarily used for nanoparticles under $50$ nm and it has been shown to work for multiple particle geometries. This method relies upon
-shear to cause limited coalescence of droplets. As coarsening occurs, particles adsorb on the interface and when the interfacial area matches the area of the
-adsorbed particles, the microstructure jams. Tuning of the method can be done through modifying the contact angle of the particles at the interface as well as
-the viscosity of the fluids.
+Studies on superellipsoidal hematite particles have demonstrated that isolated 
+anisotropic particles at the oil–water interface can adopt multiple stable and metastable orientations depending on their aspect ratio and surface 
+wettability. Specifically, particles exhibit orientations where their major or minor axes align either parallel or perpendicular to the interface, 
+with each configuration corresponding to a local or global energy minimum depending on the interfacial energy landscape \cite{1}. Lattice Boltzmann 
+simulations further support these findings, revealing that particle aspect ratio significantly influences the contact angle and immersion depth, 
+which in turn affect the energetic favorability of different orientations \cite{3}. In the presence of a magnetic field, these equilibrium states can 
+shift due to the torque exerted on the particles, aligning their magnetic moments with the field direction. Experimental observations confirm that 
+magnetic anisotropic particles, such as hematite ellipsoids, can be reoriented at the interface by applying a magnetic field, leading to controlled 
+transitions between metastable and stable states \cite{2}. These studies collectively show that the equilibrium orientation of anisotropic particles 
+is not singular, but rather a function of particle geometry, field strength, and interfacial anchoring, with metastable states playing a significant 
+role in the dynamic reconfiguration of interfacial structures.
 
-% \textcolor{blue}{Description of liquid in liquid printing}
+In many particle system, the magnetic field driven interfacial reorientation lead to the formation of linear chains or clusters of particles on flat interfaces. 
+\cite{davies_assembling_2014, davies_interface_2014,newton_influence_2014, newton_capillary_2018} The orientation of particles relative to one another is also
+a function of the number of particles in contact and the applied field strength owing to the magnetic field driven interactions between each particle. 
+\cite{newton_influence_2014, newton_capillary_2018} In Pickering emulsions, this has enabled field-controlled droplet deformation, coalescence, 
+and motility, illustrating the potential for on-demand manipulation of interfacial structures. \cite{melle_pickering_2005, tham_magnetophoresis_2021}
 
-% Enter something about this method. \cite{amirfattahi_fabrication_2024}
+\textcolor{blue}{stuff about how magnetic fields affect rheology in pickering emulsions}
 
-\section{Rheological models and shear response of bijels}
+\section{Rheological models and shear response of particle stabilized emulsions}
 
@@
 monolayer's dynamics \cite{weeks_introduction_2017}.
+
+Ellipsoidal particles influence the rheological properties and stability of Pickering emulsions. When investigating the effect of rod-like particles on the
+rheology of emulsion droplets, Madivala et al. showed that droplets stability under shear increased as the aspect ratio of the rod-like particle increased.
+\cite{madivala_exploiting_2009} This was attributed to the more effective interfacial coverage of particles and interface deformations inducing attractive
+capillary interactions between particles, reinforcing the particle monolayer to applied shear. \cite{madivala_exploiting_2009} Investigations into the rheology of
+Pickering droplets stabilized by graphene nanosheets showed that the dicsc like particles had posessed increased viscosity and viscoelasticity compared to the same 
+system synthesized with spherical particles. \cite{imperiali_simple_2014} The elasticity of the interface has been shown to be a function of the particle stabilizer
+used. \cite{sun_assembly_2013}
+
+Magnetically responsive Pickering emulsions exhibit rheological behavior that can be tuned by external magnetic fields, making them attractive for applications 
+requiring on-demand flow control and structural reconfiguration. \cite{qiao_magnetorheological_2012, melle_pickering_2005} Upon application of a field, particles
+order at the interface. This tunable rheology enables reversible transitions between fluid and gel-like states, which is particularly valuable in 
+applications such as enhanced oil recovery, drug delivery, and soft robotics \cite{tham_magnetophoresis_2021}.
 
@@
 
-\section{Microstructure control in bijels}
+\section{Stimuli response in bijels}
 
@@
 to vary along the gradient axis, causing a channel size gradients of up to 2.8\% per millimeter, as measured using confocal microscopy.
-
-\section{Lattice Boltzmann Method}
-
-The Lattice Boltzmann Method (LBM) is an evolution of preceding lattice gas automata techniques, which is a discretization of the Boltzmann equation of motion for 
-molecules. This means that unlike traditional CFD techniques such as FDM, VOF or level set methods, LBM is a psuedo-molecule method that tracks the evolution of a 
-particle distribution function within grid cells evolved through a discretized Boltzmann equation of motion. Macroscopic variables such as fluid density and 
-velocity are recovered from the particle distributions through appropriate moment integration, and the Navier Stokes equation at the incompressible limit can be 
-obtained through a Chapman-Enskog expansion of the LBM. The LBM has become an attractive tool for meso-scale CFD simulations due to its ease of algorithm 
-implementation, highly parallelizable nature and ease of boundary condition implementation, allowing coupling to other physically relevant systems such as 
-particles with varieties of potentials, external fields and deformable bodies.
-
-The particle distribution function described earlier is advected on a pre-constructed lattice stencil, commonly denoted as DnQm where n and m represent the 
-number of dimensions and directions in the stencil. Common stencils include the D1Q5, D2Q9 and D3Q19 stencil, all of which recover mass and momentum conservation. 
-For energy conservation, a higher order stencil such as D3Q27 is necessary. The D2Q9 and D3Q19 stencils have 8 and 18 populations respectively that include 
-connections to nearest and next nearest neighbour points, in addition to a central rest point.
-
-The LBM is composed of a collision and advection step. In the advection step, the populations at each grid point are propagated to adjacent points in accordance 
-with the chosen stencil. During the collision step, the particle population distribution is relaxed towards an equilibrium with a collision operator, at a 
-specified relaxation rate. The collision operator can have multiple forms based on how many relaxation rates are used although the most common variant is the 
-Single Relaxation Time (SRT) collision operator, more commonly known as the Bhatnagar-Gross-Krook (BGK) collision operator. Owing to its stability in low Mach 
-and Reynolds numbers and simplicity of implementation, the BGK operator is often used in common particle laden flow and soft matter scenarios. 
-\cite{bhatnagar_model_1954} These limitations are present owing to the implicit link between the fluid properties and the relaxation rate necessitating 
-relaxation rates above 0.5, and to ensure fluid incompressibility from an equation that intrinsically simulates a compressible fluid. To get over these 
-limitations, Two Relaxation Time (TRT) and Multiple Relaxation Time (MRT) operators also exist, expanding the possible application of the LBM to visco-elastic 
-flows and implementation of fluctuating hydrodynamics in the LBM. \cite{liu_simulation_2023, adhikari_fluctuating_2005}
-
-Four primary techniques to model multicomponent or multiphase systems exist in the LBM literature. A quick review of the Shan-Chen or 
-interparticle potential model  will be provided here from the perspective of a binary mixture. Additionally, the names and descriptions of 
-other techniques will be described as well. The interparticle potential model or Shan-Chen model that adds a non-local density dependent force 
-between two species, effectively modelling non-ideal mixing and recovering the Cahn-Hilliard equation. To alleviate the standard Shan-Chen implementations 
-weaknesses of not being thermodynamically consistent and reducing the existence of spurious velocities,
-
-In addition to the Shan-Chen model, the color gradient model, free energy model and interface tracking technique all 
-allow for simulations of various types of multiphase and/or multicomponent flows. The color gradient model proposed by Rothman and Keller and 
-implemented by Gunstensen et al relies upon modelling two particle distributions. These represent a binary fluid mixture with the collision step 
-able to recover the hydrodynamics and non-ideal mixing dynamics. The free energy model utilizes phase field theory and constructs a free energy 
-functional to recover interfacial dynamics and effects in a thermodynamically consistent manner. Often, a square gradient free energy is used for 
-simplicity and ease of implementation. The mean field theory The non-ideal mixing dynamics are recovered during the "recoloring" step, of which the 
-technique proposed by Latva-Kokko and Rothman is more commonly used for soft matter flows. \cite{liu_multiphase_2016}

### 2025-03-25 chapters/LBM_technique.tex
Changes 1. Refactoring LBM methods explanation 2. Removing contact angle plots for model validation 3. Changes psi vs t figure in paper 1

--- 2025-03-04 chapters/LBM_technique.tex
@@
+\section{Methods}
 \label{section:methods}
 
-This work uses a multicomponent Lattice Boltzmann Method (LBM) to simulate the hydrodynamics of two partially miscible, 
-incompressible fluids as implemented in LB3D. The LBM solves the continuity and Navier-Stokes equation at low
-Mach and Reynolds numbers for the fluid, defined as,
+Bijels require a multi-scale model to correctly simulate all the physical phenomena occurring at every scale. Within a bijel, fluid flow,
+phase separation, particle-fluid and interparticle interactions are present. The lengthscales present in a bijel imply a model must be able
+to resolve nanometer to micrometer resolutions and must be able to capture the hydrodynamics, non-ideal mixing and interparticle interactions present
+in the system. A review of the physics in the system will be provided.
+
+Mass conservation is established using simple differential equation of a control volume that characterizes the mass flow through the volume. Assuming no
+addition or subtraction of mass, the differential equation is the material derivative of the density, defined as
 
 \begin{equation}
-    \begin{split}
-    \frac{\partial\rho}{\partial t} + \nabla\cdot\left(\rho\vec{u}\right) &= 0 , \\
-    \frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u} &= - \frac{1}{\rho} \nabla p + \nu \nabla^2 \vec{u} ,
-    \end{split}
+    \frac{\partial\rho}{\partial t} + \nabla\cdot\left(\rho\vec{u}\right) = 0
 \end{equation}
 
-incorporating density $(\rho)$, viscosity $(\eta)$, velocity $(u)$, pressure $(P)$, and 
-body force $(F_{body})$. \cite{qian_lattice_1992, chin_lattice_2002, nourgaliev_lattice_2003} The Shan-Chen pseudopotential
+Where $\rho$ is the fluid density and $\vec{u}$ is the fluid velocity vector. The fluid momentum can be derived from the mass conservation equation
+by calculating the material derivative of the momentum of the system. Changes in momentum from addition or subtraction of momentum cannot be ignored,
+with changes arising from pressure gradients, viscous forces and body force terms. If mass is conserved, the momentum equation is defined as
+
+\begin{equation}
+    \rho (\frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u}) = -\nabla p + \nabla \cdot \mathbf{\tau} + \mathbf{f}
+\end{equation}
+
+Where $p$ is the pressure applied to the control volume, $\mathbf{\tau}$ is a general stress tensor and $\mathbf{f}$ is the body force 
+applied on the box such as gravitational forces. $\mathbf{\tau}$ can be defined by assuming the fluid is isotropic, the shear stress depends
+linearly on the dynamic viscosity and the strain rate and net forces are zero at equilibrium.
+
+\begin{equation}
+    \mathbf{\tau} = p\mathbf{I} + \eta(\nabla \mathbf{v} + (\nabla \mathbf{v})^T) - \frac{2}{3}\eta(\nabla \cdot \mathbf{v})\mathbf{I}
+\end{equation}
+
+Where $p = (\lambda + \frac{2}{3}\eta)\nabla \cdot \mathbf{v}$ is defined from the bulk viscosity $\lambda$. After substitution into the momentum equation, the compressible 
+Navier Stokes equation is obtained, defined as
+
+\begin{equation}
+    \rho (\frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u}) = -\nabla p + \eta \Delta \mathbf{v} + \frac{1}{3}\eta \nabla(\nabla \cdot \mathbf{v}) + \mathbf{f}
+\end{equation}
+
+If the fluid being modelled is assumed to be incompressible meaning that the density stays constant and the bulk viscosity is 0, $\nabla \cdot \mathbf{v} = 0$. This simplifies
+the Navier Stokes equation to
+
+\begin{equation}
+    \rho (\frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u}) = -\nabla p + \eta \Delta \mathbf{v} + \mathbf{f}
+\end{equation}
+
+The Navier Stokes equation can be recast into a dimensionless form by rescaling length, time and density into dimensionless forms. These parameters are rescaled as 
+$\bar{l} = \frac{l}{l_0}$, $\bar{t} = \frac{t}{t_0}$ and $\bar{\rho} = \frac{\rho}{\rho_0}$ with barred quantities indicating dimensionless properties. After substituting
+these parameters into the Naver Stokes equation this is obtained
+
+\begin{equation}
+    \frac{\partial \bar{\vec{u}}}{\partial \bar{t}} + (\bar{\vec{u}} \cdot\nabla)\bar{\vec{u}} = -\nabla \bar{p} + \frac{1}{Re} \Delta \mathbf{\bar{v}} + \bar{\mathbf{f}}
+\end{equation}
+
+$Re = \frac{\rho u l}{\eta}$ which defines the ratio between inertial and viscous forces. Another physical phenomenon being described is non-ideal mixing. The free energy of mixing
+is defined as $\Delta G_m = \Delta H_m - T \Delta S_m$. In an ideal solution, $\Delta H_m = 0$. An expression for $\Delta S_m$ for a binary mixture is obtained from statistical mechanical 
+approximations of the configurations that binary mixtures can take, resulting in
+
+\begin{equation}
+    S_m = -k N_\phi k_B T((1 - \phi)\ln{1 - \phi} + \phi ln(\phi)) 
+\end{equation}
+
+In a regular solution, $\Delta H_m \neq 0$. The free energy of mixing is defined as the sum of the ideal and excess contribution, $\Delta G_m = \Delta G_e + \Delta G_i$.
+$\Delta G_i = -TS_m$. $\Delta G_e = \Delta H_e + T \Delta S_e$. The excess entropy of mixing is 0, and the excess enthalpy of mixing is defined
+
+The Shan-Chen pseudopotential
 model is used to simulate the Cahn-Hilliard equation, defined below
@@
 
-Particle dynamics include Hertzian contact and lubrication forces, tracked with classical Newtonian mechanics, while 
-particle-fluid coupling involves momentum exchange to simulate viscous dissipation. Particle-particle magnetic interactions are modeled using dipole 
-interactions. \cite{davies_interface_2014, xie_direct_2017, xie_controllable_2021} A more detailed description of the model is 
-provided in the following sections
+A computational model designed to simulate soft matter systems 
+at the mesoscale must accurately represent both hydrodynamics and non-ideal mixing in order to capture the essential physics of emulsions, colloids, and phase-separating fluids. 
+A hydrodynamic model must be able to recover mass and momentum conservation of a incompressible fluid
+
+Modelling multicomponent dynamics requires incorporating a free energy model between fluids, allowing for the implementation of
+chemical potential driven mass transfer and surface tension. Typically this is done using a Cahn-Hilliard model based on a
+square gradient free energy functional. This captures the demixing characteristics of phase separating fluids and controls interface
+characteristics, providing surface tension and interface width characteristics. This model has been used in past investigations looking 
+into spinodal decomposition, domain growth and coarsening.
+
+To fully capture mesoscale dynamics, the model must also resolve the coupling between hydrodynamic flow and composition gradients. This coupling 
+is essential for simulating phenomena such as Marangoni flows, interfacial instabilities, and anisotropic stress distributions that arise from 
+non-uniform compositions or curvature-dependent surface tension. Moreover, the model must support anisotropic or time-dependent external fields 
+(e.g., magnetic, electric, or shear) that influence mixing behavior. Computational frameworks that can evolve velocity, pressure, and composition 
+fields simultaneously—while ensuring thermodynamic consistency and mechanical stability—are critical for accurately describing the emergent structures 
+and transport properties in non-ideal soft matter systems.
+
+Given the multiscale modeling necessary to correctly simulate the physical system, one approach suggested to tackle this problem is the multicomponent
+Lattice Boltzmann Method. This technique bridges the length and time scales necessary in soft matter modeling through modeling the evolution of a particle
+distribution function. Hydrodynamic parameters are recovered through calculating the moments of the particle distribution function. One of the advantages of
+the Lattice Boltzmann Method its parallelize nature and ease of adding multiple physical phenomena. In the following sections, the implementation of the LBM
+and alternatives to the LBM will be presented.
+
+% This work uses a multicomponent Lattice Boltzmann Method (LBM) to simulate the hydrodynamics of two partially miscible, 
+% incompressible fluids as implemented in LB3D. The LBM solves the continuity and Navier-Stokes equation at low
+% Mach and Reynolds numbers for the fluid, defined as,
+
+% \begin{equation}
+%     \begin{split}
+%     \frac{\partial\rho}{\partial t} + \nabla\cdot\left(\rho\vec{u}\right) &= 0 , \\
+%     \frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u} &= - \frac{1}{\rho} \nabla p + \nu \nabla^2 \vec{u} ,
+%     \end{split}
+% \end{equation}
+
+% incorporating density $(\rho)$, viscosity $(\eta)$, velocity $(u)$, pressure $(P)$, and 
+% body force $(F_{body})$. \cite{qian_lattice_1992, chin_lattice_2002, nourgaliev_lattice_2003} The Shan-Chen pseudopotential
+% model is used to simulate the Cahn-Hilliard equation, defined below
+
+% \begin{equation}
+%     \begin{split}
+%     \frac{\partial\phi}{\partial t}+\nabla\cdot\left(\phi\vec{u}\right) &= \nabla \cdot \left( \Gamma  \nabla\phi \right)
+%     \end{split}
+% \end{equation}
+
+% where $c^k$, $M^k$ and $u^k$ is the concentration, mobility and velocity of species $k$ respectively while $\mu$ is the free energy of system. 
+% \cite{shan_lattice_1993, shan_simulation_1994, he_lattice_1997, he_discrete_1998}
+
+% Particle dynamics include Hertzian contact and lubrication forces, tracked with classical Newtonian mechanics, while 
+% particle-fluid coupling involves momentum exchange to simulate viscous dissipation. Particle-particle magnetic interactions are modeled using dipole 
+% interactions. \cite{davies_interface_2014, xie_direct_2017, xie_controllable_2021} A more detailed description of the model is 
+% provided in the following sections
+
+\section{Lattice Boltzmann Method}
+
+The Lattice Boltzmann Method (LBM) is an evolution of preceding lattice gas automata techniques, which is a discretization of the Boltzmann equation of motion for 
+molecules. This means that unlike traditional CFD techniques such as FDM, VOF or level set methods, LBM tracks the evolution of a 
+particle distribution function within grid cells evolved through a discretized Boltzmann equation of motion. Macroscopic variables such as fluid density and 
+velocity are recovered from the particle distributions through appropriate moment integration, and the Navier Stokes equation at the incompressible limit can be 
+obtained through a Chapman-Enskog expansion of the LBM. The LBM has become an attractive tool for meso-scale CFD simulations due to its ease of algorithm 
+implementation, highly parallelizable nature and ease of boundary condition implementation, allowing coupling to other physically relevant systems such as 
+particles with varieties of potentials, external fields and deformable bodies.
+
+The particle distribution function described earlier is advected on a pre-constructed lattice stencil, commonly denoted as DnQm where n and m represent the 
+number of dimensions and directions in the stencil. Common stencils include the D1Q5, D2Q9 and D3Q19 stencil, all of which recover mass and momentum conservation. 
+For energy conservation, a higher order stencil such as D3Q27 is necessary. The D2Q9 and D3Q19 stencils have 8 and 18 populations respectively that include 
+connections to nearest and next nearest neighbour points, in addition to a central rest point. The D3Q19 stencil is shown in Figure \ref{fig:d3q19_lattice}.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale = 1]{figures/methods/d3q19_lattice.jpg}
+    \caption{D3Q19 lattice demonstrating the rest, nearest and next nearest direction that correspond to the 19 
+    directions $(i)$ of the lattice with lattice velocity $c_{i}$. \cite{schmieschek_lb3d_2017} Reproduced from 
+    Schmieschek et al. Computer Physics Communications 2017, 217, 149--161, under the Creative Commons license.}
+    \label{fig:d3q19_lattice}
+\end{figure}
+
+The LBM is composed of a collision and advection step. In the advection step, the populations at each grid point are propagated to adjacent points in accordance 
+with the chosen stencil. During the collision step, the particle population distribution is relaxed towards an equilibrium with a collision operator, at a 
+specified relaxation rate.
 
@@
 timestep $\Delta t$ with lengthscale $\Delta x$. \cite{qian_lattice_1992, succi_lattice_2018, he_theory_1997} The D3Q19 
-velocity set is used in this work with the indexes $i$ represent each of the 19 velocities and converves mass and momentum 
-conservation to the second order. It can be seen in Figure \ref{fig:d3q19_lattice}. The algorithm is split into the 
-collision step where the populations on each lattice grid cell are relaxed towards an equilibrium, followed by the 
+velocity set is used in this work with the indexes $i$ represent each of the 19 velocities and conserves mass and momentum 
+to the second order. It can be seen in Figure \ref{fig:d3q19_lattice}. The algorithm is split into the 
+collision step where the populations on each lattice grid cell is relaxed towards an equilibrium, followed by the 
 advection step where populations in each velocity direction are propagated with velocity $\mathbf{c_i}$.
 
-The collision step occurs using a single relaxation time Bhatnagar-Gross-Krook (BGK) collision operator at relaxation 
-rate $\tau$. \cite{bhatnagar_model_1954, qian_lattice_1992} The combined collision and advection LBM is expressed below 
-in equation \ref{eq:LBM_BGK}
+% The collision step occurs using a single relaxation time Bhatnagar-Gross-Krook (BGK) collision operator at relaxation 
+% rate $\tau$. \cite{bhatnagar_model_1954, qian_lattice_1992}
+
+% The collision operator can have multiple forms based on how many relaxation rates are used although the most common variant is the 
+% Single Relaxation Time (SRT) collision operator, more commonly known as the Bhatnagar-Gross-Krook (BGK) collision operator. 
+% \cite{bhatnagar_model_1954, qian_lattice_1992} 
+% Owing to its stability in low Mach 
+% and Reynolds numbers and simplicity of implementation, the BGK operator is often used in particle laden flow and soft matter simulations. 
+% \cite{bhatnagar_model_1954} These limitations are present owing to the implicit link between the fluid properties and the relaxation rate, 
+% and to ensure fluid incompressibility from an equation that intrinsically simulates a compressible fluid. To get over these 
+% limitations, Two Relaxation Time (TRT) and Multiple Relaxation Time (MRT) operators also exist, expanding the possible application of the LBM to visco-elastic 
+% flows and implementation of fluctuating hydrodynamics in the LBM. \cite{liu_simulation_2023, adhikari_fluctuating_2005} The combined collision and advection 
+% LBM is expressed below in equation \ref{eq:LBM_BGK}
+
+The collision step in the LBM is performed using the collision operator. It can take multiple forms depending on the number of
+relaxation rates used. The most commonly used variant is the Single Relaxation Time (SRT) operator defined with the Bhatnagar-Gross-Krook (BGK) 
+collision operator \cite{bhatnagar_model_1954, qian_lattice_1992}. The BGK model is easy to implement and works well enough in soft matter and
+particle-laden flow simulations.
+
+However the BGK operator controls all moments at a single relaxation rate which can induce numerical instabilities and inaccuracies
+at higher fluid velocities. \cite{liu_simulation_2023, adhikari_fluctuating_2005} These numerical instabilities can be resolved by using
+a Multiple Relaxation Time (MRT) collision operator. However the relaxation rates used in an MRT collision operator must be tuned carefully
+to ensure that the appropriate fluid properties are modelled. Simpler variants of the MRT collision operator such as the Two Relaxation Time (TRT)
+collision operator have been proposed as a solution that provides some of the benefits of MRT models with the simplicity of SRT models. These 
+have facilitated simulation of a wider range of physical phenomena \cite{adhikari_fluctuating_2005, liu_simulation_2023}. The SRT collision 
+operator is selected due to the additional computational performance needed by MRT not being needed. The combined streaming and 
+collision step in LBM, using the BGK operator, is expressed in Equation \ref{eq:LBM_BGK}.
 
@@
 
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale = 0.7]{figures/methods/d3q19_lattice.jpg}
-    \caption{D3Q19 lattice demonstrating the rest, nearest and next nearest direction that correspond to the 19 
-    directions $(i)$ of the lattice with lattice velocity $c_{i}$. \cite{schmieschek_lb3d_2017} Reproduced from 
-    Schmieschek et al. under the Creative Commons license.}
-    \label{fig:d3q19_lattice}
-\end{figure}
-
 $\rho$ and $\textbf{u}$ in Equation \ref{eq:LBM_Feq} are defined as the macroscopic parameters for density and velocity 
@@
 \label{section:lbm_non_ideal_mixing}
+
+Four primary techniques to model multicomponent or multiphase systems exist in the LBM literature. They are the Shan-Chen (SC) pseudopotential
+model, the free energy (FE) model, the color gradient (CG) model and the interface tracking (IT) model. All techniques are fundamentally different to one
+another in implementation and tradeoff various properties. Each one will be briefly reviewed before a comparing and contrasting their applicability
+to this system.
+
+The SC model introduces fluid interactions via a density-dependent force, enabling spontaneous phase separation 
+and interface formation without explicitly tracking the interface. It is simple to implement and computationally efficient. However the density
+dependence of the fluid interactions implies that the surface tension is controlled by the density of the fluids used and the strength parameter
+controlling interactions.
+
+The FE model derives from the implementation of a modified equilibrium distribution derived from a square gradient free energy functional. Similar to the
+SC model, the FE model enables spontaneous phase separation and interface formation without explicitly tracking the interface. The surface tension and
+interface width are explicitly defined from the bulk free energy, allowing for user defined surface tensions and interface widths. However in its multicomponent
+implementation, it cannot be used to simulate fluids with high density ratios.
+
+The CG model is defined with fluid components with color labels, followed by the application of a recoloring step to sharpen the interface. 
+\cite{liu_multiphase_2016} The recoloring step creates the surface tension present in phase separated multicomponent mixtures. This model
+provides fine control over the surface tension and narrow interface widths. However implementing the recoloring step is computationally complex 
+and requires tuning of the recoloring step to ensure numerical consistency.  
+% technique proposed by Latva-Kokko and Rothman is more commonly used for soft matter flows. \cite{liu_multiphase_2016}
+
+The IT model is defined using a level-set or front-tracking techniques coupled to LBM. This technique explicitly tracks the location of the
+interface by evolving a separate interface indicator. It offers the highest accuracy at capturing the interface. However it is computationally
+expensive and less suited to topological changes like coalescence.
+
+% A quick review of the Shan-Chen (SC) or 
+% pseudopotential model will be provided here from the perspective of a binary mixture. Additionally, the names and descriptions of 
+% other techniques will be described as well. The interparticle potential model or Shan-Chen model that adds a non-local density dependent force 
+% between two species, effectively modelling non-ideal mixing and recovering the Cahn-Hilliard equation. To alleviate the standard Shan-Chen implementations 
+% weaknesses of not being thermodynamically consistent and reducing the existence of spurious velocities, thermodynamically consistent equations of state
+% such as the Van der walls or Carnahan Starling equations of state have been implemented and compared to the Shan-Chen equation of state.
+
+% In addition to the Shan-Chen model, the color gradient model, free energy model and interface tracking technique all 
+% allow for simulations of various types of multiphase and/or multicomponent flows. The color gradient model proposed by Rothman and Keller and 
+% implemented by Gunstensen et al relies upon modelling two particle distributions. These represent a binary fluid mixture with the collision step 
+% able to recover the hydrodynamics and non-ideal mixing dynamics. The free energy model utilizes phase field theory and constructs a free energy 
+% functional to recover interfacial dynamics and effects in a thermodynamically consistent manner. Often, a square gradient free energy is used for 
+% simplicity and ease of implementation. The mean field theory The non-ideal mixing dynamics are 6
+
+Compared to other multicomponent methods, the SC model provides the
 

### 2025-03-25 chapters/model_params.tex
Changes 1. Refactoring LBM methods explanation 2. Removing contact angle plots for model validation 3. Changes psi vs t figure in paper 1

@@
 Figure \ref{fig:young_laplace_valid} shows the results of the fit conducted of the Young-Laplace equation demonstrating 
-that under these fluid and mixing parameters, the surface tension is $\sigma = 0.0279$. The fit was performed using 
+that under these fluid and mixing parameters, the surface tension is $\sigma = 0.0273$. The fit was performed using 
 \texttt{scipy.optimize.curve\_fit} with the fit function defined as $y = mx$. Droplets with starting sizes $2R_d < 70\%$ 
@@
 
-\subsection{Contact angle}
-\label{section:model_contact_angle}
+% \subsection{Contact angle}
+% \label{section:model_contact_angle}
 
-Contact angle plays a role in particle stabilized emulsions by controlling the free energy reduction that the interface 
-has in addition to the imparting of preferential curvature. LB3D allows for modification of the contact angle of a 
-particle through the addition of a shell of blue or red fluid to the surface of the Ladd particle termed as the particle 
-color $(\Delta \rho)$. \cite{jansen_bijels_2011, gunther_lattice_2013} To ensure that the correct settings are used in 
-these simulations, in addition to gaining understanding into how to change parameters if the need arises, the contact 
-angle as a function of the particle color was calculated.
+% Contact angle plays a role in particle stabilized emulsions by controlling the free energy reduction that the interface 
+% has in addition to the imparting of preferential curvature. LB3D allows for modification of the contact angle of a 
+% particle through the addition of a shell of blue or red fluid to the surface of the Ladd particle termed as the particle 
+% color $(\Delta \rho)$. \cite{jansen_bijels_2011, gunther_lattice_2013} To ensure that the correct settings are used in 
+% these simulations, in addition to gaining understanding into how to change parameters if the need arises, the contact 
+% angle as a function of the particle color was calculated.
 
-Experimentally and computationally, the contact angle can be calculated through direct measurement of the angle of a 
-droplet on a substrate. A droplet that preferentially wets a substrate has a lower contact angle relative to that 
-substrate material, physically manifesting as the droplet spreading on the substrate. At a liquid interface, the particle 
-will prefer to be in the particle it wets more. Thus for a spherical particle, the contact angle can be calculated as 
-$\theta_c = \arccos{\frac{h_p - h_i}{R_p}}$ where $h_p - h_i$ defines the distance between the center of the particle 
-after reaching its steady state position and the interface and $R_p$ is the radius of the spherical particle. 
-\cite{gunther_lattice_2013, davies_interface_2014} This has been extended to ellipsoidal particles through assuming 
-that the particle will have its largest cross sectional area flat on the interface and using the radius that is 
-perpendicular to the interface to calculate the contact angle, defined as $\theta_c = \arccos{\frac{h_p - h_i}{R_{\parallel}}}$ 
-and $\theta_c = \arccos{\frac{h_p - h_i}{R_{\perp}}}$ if $\alpha < 1$ and $\alpha \geq 1$ respectively.
+% Experimentally and computationally, the contact angle can be calculated through direct measurement of the angle of a 
+% droplet on a substrate. A droplet that preferentially wets a substrate has a lower contact angle relative to that 
+% substrate material, physically manifesting as the droplet spreading on the substrate. At a liquid interface, the particle 
+% will prefer to be in the particle it wets more. Thus for a spherical particle, the contact angle can be calculated as 
+% $\theta_c = \arccos{\frac{h_p - h_i}{R_p}}$ where $h_p - h_i$ defines the distance between the center of the particle 
+% after reaching its steady state position and the interface and $R_p$ is the radius of the spherical particle. 
+% \cite{gunther_lattice_2013, davies_interface_2014} This has been extended to ellipsoidal particles through assuming 
+% that the particle will have its largest cross sectional area flat on the interface and using the radius that is 
+% perpendicular to the interface to calculate the contact angle, defined as $\theta_c = \arccos{\frac{h_p - h_i}{R_{\parallel}}}$ 
+% and $\theta_c = \arccos{\frac{h_p - h_i}{R_{\perp}}}$ if $\alpha < 1$ and $\alpha \geq 1$ respectively.
 
-The simulation was setup in a box of size $32\cdot32\cdot64$ with an interface lying at $z = 32$, and a single particle 
-placed at the center of the box with periodic boundary conditions on all sides. Fluid and non-ideal mixing properties were 
-the same as those listed in table \ref{table:model_params}. The particle was then placed at the center of the simulation 
-box and run for $30000$ timesteps with data read every 500 timesteps. The contact angles shown are results from triplicate 
-runs, and averages of the final 10 data points.
+% The simulation was setup in a box of size $32\cdot32\cdot64$ with an interface lying at $z = 32$, and a single particle 
+% placed at the center of the box with periodic boundary conditions on all sides. Fluid and non-ideal mixing properties were 
+% the same as those listed in table \ref{table:model_params}. The particle was then placed at the center of the simulation 
+% box and run for $30000$ timesteps with data read every 500 timesteps. The contact angles shown are results from triplicate 
+% runs, and averages of the final 10 data points.
 
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale = 0.5]{figures/model_validation/contact_angle_compare.png}
-    \caption{Contact angle with respect to the oil phase, $(\theta_c^{oil})$ of the particles plotted against the 
-    control parameter in LB3D}
-    \label{fig:contact_angle_valid}
-\end{figure}
+% \begin{figure}[h]
+%     \centering
+%     \includegraphics[scale = 0.5]{figures/model_validation/contact_angle_compare.png}
+%     \caption{Contact angle with respect to the oil phase, $(\theta_c^{oil})$ of the particles plotted against the 
+%     control parameter in LB3D}
+%     \label{fig:contact_angle_valid}
+% \end{figure}
 
-Figure \ref{fig:contact_angle_valid} demonstrates the contact angles of the three particle geometries analyzed, 
-confirming that $\Delta \rho = 0$ will result in neutrally wetting particles for all geometries. Oblate and spherical 
-particles have usable particle colors between $-0.10 \leq \Delta \rho \leq 0.10$ while for prolate ellipsoids this 
-value is $-0.05 \leq \Delta \rho \leq 0.05$. The slope of ellipsoidal particles appears to be lower which may arise 
-from a larger interfacial adsorption energy, making it more difficult for surface energy changes to move particles out 
-of the interface. At $\Delta \rho$ values further from 0, it was observed that the prolate particles tended to leave 
-the interface rather than stay at a slightly off center equilibrium position.
+% Figure \ref{fig:contact_angle_valid} demonstrates the contact angles of the three particle geometries analyzed, 
+% confirming that $\Delta \rho = 0$ will result in neutrally wetting particles for all geometries. Oblate and spherical 
+% particles have usable particle colors between $-0.10 \leq \Delta \rho \leq 0.10$ while for prolate ellipsoids this 
+% value is $-0.05 \leq \Delta \rho \leq 0.05$. The slope of ellipsoidal particles appears to be lower which may arise 
+% from a larger interfacial adsorption energy, making it more difficult for surface energy changes to move particles out 
+% of the interface. At $\Delta \rho$ values further from 0, it was observed that the prolate particles tended to leave 
+% the interface rather than stay at a slightly off center equilibrium position.

### 2025-03-25 chapters/paper1_new.tex
Rewriting paper 1 chapter

--- 2025-03-21 chapters/paper1.tex
@@
 
-% Anisotropic particles, when adsorbed at liquid interfaces, induce
-% shape-dependent capillary interactions that can have a distinct effect
-% on the microstructure of emulsions
-% \cite{loudet_capillary_2005,loudet_self-assembled_2009}. For instance,
-% Madivala et
-% al.~\cite{madivala_exploiting_2009,madivala_self-assembly_2009} found
-% that emulsion stability can be significantly enhanced by ellipsoidal
-% particles. Additionally, capillary interactions can lead to direct
-% assembly of anisotropic particles
-% \cite{bowden_self-assembly_1997,lewandowski_orientation_2010,stebe_oriented_2009,botto_capillary_2012}.
-% Ellipsoidal particles can rotate and migrate on curved surfaces
-% \cite{cavallaro_curvature-driven_2011}, where the interface curvature
-% acts as an external field that controls the orientation and placement
-% of particles \cite{furst_directing_2011}. Anisotropic particles at
-% fluid interfaces were considered in Monte Carlo simulations by Bresme
-% et al. to test the accuracy of thermodynamic models for the free
-% energy as a function of the particle-fluid interactions, particle
-% size, and orientation
-% \cite{bresme_orientational_2007,bresme_computer_2008}. Harting and
-% co-workers \cite{gunther_lattice_2013,gunther_timescales_2014} have
-% performed lattice Boltzmann simulations of anisotropic particles at
-% liquid interfaces and in emulsions. They found that anisotropic
-% particles affect the dynamics of emulsion formation by introducing two
-% additional timescales associated with particle rotation. Following
-% initial adsorption, particles rotate to align their larger
-% cross-section with the interface. When jamming sets in, capillary
-% interactions cause the particle to re-orient in the interface leading
-% to prolonged coarsening at long timescales. Due to the larger aspect
-% ratio, ellipsoidal particles can stabilize a larger interface area
-% leading to smaller domain sizes. Hijnen et
-% al.~\cite{hijnen_bijels_2015} experimentally realized bijels
-% stabilized by colloidal rods and analyzed their effect on the
-% interface and domain morphology. Their experiments confirmed that
-% jamming occurs at lower interface separations than for spherical
-% particles with the same volume fraction. Moreover, they observed that
-% the overall structure remains isotropic and attributed this to the
-% rapid jamming of the rods. Additionally, they found that some rods
-% tilted out of the interface due to the compression induced by domain
-% coarsening.
-
-% Particle-stabilized emulsions can be made responsive to external
-% magnetic fields by magnetic particles
-% \cite{melle_pickering_2005,zhou_magnetic_2011}. An external field can
-% then be used to control the stability of the emulsion
-% \cite{melle_pickering_2005} and the self-assembly of particles
-% \cite{dassanayake_structure_2000,leunissen_directing_2009}. The tendency
-% of anisotropic particles to adopt distinct orientations gives rise to an
-% orientation transition when an external field is applied
-% \cite{morgan_understanding_2012,davies_interface_2014,davies_dipolar_2015}.
-% Magnetic fields thus offer a means to control the capillary interactions
-% of ellipsoidal particles at an interface. For bijels stabilized by
-% spherical magnetic particles, simulations by Kim et
-% al.~\cite{kim_bijels_2010} revealed that magnetic fields do not have a
-% significant effect on the microstructure of bijels. In contrast, Carmack
-% and Millett \cite{carmack_tuning_2018} demonstrated that the structure
-% of thin-film bijels stabilized by dielectric particles can change
-% drastically when an external electric field is applied. The dielectric
-% contrast of the particles induces polar interactions that cause liquid
-% domain alignment leading to percolating cylindrical domains in the
-% thin-film bijel. In addition, they found that particle chains can act as
-% nucleation sites for phase separation. This suggests that anisotropic
-% interactions can have a considerable effect on the phase separation and
-% the resulting emulsion morphology and may offer a means to control the
-% size and shape of liquid domains.
-
 \section{Results}\label{sec:results_p1}
 
-Bijels can be used as emulsion templates for porous materials with
-applications including drug delivery, water desalination, and battery
-electrodes
-\cite{vanoli_bijels_2022, chen_pore-scale_2022, lu_controllable_2020, garcia_scalable_2019}.
-The transport properties of porous materials depend on the porosity and
-tortuosity of the void space and can be linked to the phase-separated
-morphology of the bijel template. Therefore, We study the domain size
-and tortuosity of the phase morphology of bijels stabilized by
-anisotropic particles. In particular, We investigate the effect of
-magnetic particles on the microstructure of bijels that are formed in
-external magnetic fields. We simulated bijels with a particle volume
-fraction of \(\phi_p=0.15\) and varied the magnetic flux density such
-that the Bond numbers varies in the range \(0\le\bar{B}\le1\).
-In this work, We use a fixed particle volume fraction and focus on the dependence of the 
-bijel structure on the magnetic field. Bijels with varying particle loading and surface tension 
-and have been studied elsewhere in the literature, e.g., by Hijnen et al.\cite{hijnen_bijels_2015} 
-and Jansen and Harting\cite{jansen_bijels_2011}.
+Bijels serve as emulsion templates for fabricating porous materials with applications in areas such as drug delivery, water purification, and energy 
+storage devices like battery electrodes \cite{vanoli_bijels_2022, chen_pore-scale_2022, lu_controllable_2020, garcia_scalable_2019}. The performance of
+materials in these applications are influenced by their microstructure. In the following section, the microstructure of magnetically responsive bijels
+are assessed. The bijels in our simulations have a particle volume fraction $\phi_p = 0.15$ with magnetic Bond numbers ranging from 
+$\bar{Bo} = 0, 0.2, 0.5, 1$. Three simulations per particle and per magnetic field strength are performed, allowing for investigations into the effect of
+the initial particle configuration on the obtained microstructure. While properties such as the particle contact angle, fluid ratio, surface tension and
+particle volume fraction are important, this study will focus exclusively on the effect of magnetic fields on bijels. 
+\cite{jansen_bijels_2011, hijnen_bijels_2015}
+
+\subsection{Microstructure evolution of magnetically responsive bijels}
 
@@
     \includegraphics[width=0.5\columnwidth]{figures/results/paper1/microstructure_viz.png}
-    \caption{Snapshots of emulsion gels stabilized by prolate ellipsoids after $t=5\cdot10^3$ timesteps (left) and after $10^5$ timesteps (right).
-The top row shows the structure forming without a magnetic field.
-             The bottom row shows the structure forming in an applied magnetic field of reduced strength $\bar{B}=1.0$. The snapshots are colored according to the order parameter $\phi$.}
+    \caption{Snapshots of emulsion gels stabilized by prolate ellipsoids after $t=5\cdot10^3$ timesteps (left) and after $10^5$ timesteps (right). The top 
+             row shows the structure forming without a magnetic field. The bottom row shows the structure forming in an applied magnetic field of reduced 
+             strength $\bar{B}=1.0$. The snapshots are colored according to the order parameter $\phi$.}
     \label{fig:microstructure_viz}
@@
 
-Figure \ref{fig:microstructure_viz} shows snapshots of the bijel
-microstructure observed at different times with and without an external
-magnetic field. The figure illustrates how anisotropic particles align
-with the direction of the magnetic field. As the particles reorient,
-they can deform the interface which thus responds by rearrangements
-including reorientation and domain coalescence or breakup. This results
-in apparently larger domain sizes for bijel formation in magnetic
-fields. The quantitative effect on the bijel morphology, and domain size
-in particular, is analyzed in the following sections.
+Figure \ref{fig:microstructure_viz} presents snapshots of the bijel microstructure during formation and at the final timestep with and without magnetic fields.
+The figure highlights the alignment of anisotropic particles along the field direction following its application. Particle reorientation leads to apparently larger
+domain sizes in the bijels, characterized through magnetic field driven rearrangement of particles at the interface. Past work has identified how droplet coalescence
+can be induced through application of magnetic fields. \cite{melle_pickering_2005} This behavior can be quantified using the domain size, done in the following section.
 
-\subsection{Structure factor and domain size of magnetically responsive bijels}
-
-In LB simulations of spinodal decomposition, a characteristic length
-scale can be obtained from the structure factor, defined in Section \ref{section:domain_size}. \cite{kendon_3d_1999,kendon_inertial_2001} 
-It is worth noting that this definition of average domain size does not necessarily yield values that coincide with the typical
-domain size observed visually in snapshots such as those shown in Figure~\ref{fig:microstructure_viz}. However, in a dynamic
-scaling regime, different measures of domain size are expected to differ only by a constant ratio. We found that the commonly 
-used measure \(L_1(t)\) tends to overestimate the observed domain size. Numerically, the calculation of the spherically 
-averaged structure factor is subject to poor statistics in the low \(k\)-shells, where the average \(|\vec{k}|\) of the 
-lattice sites differs from the nominal shell radius. Additionally, the measurement of \(L(t)\) in simulations with
-periodic boundary conditions is subject to finite size effects. More importantly, in suspensions of anisotropic particles, 
-We cannot expect that the structure factor is isotropic. Therefore, we also used the 3D structure factor to calculate a lateral domain 
-size in each Cartesian direction from the second moments also defined in Section \ref{section:domain_size}. 
-\cite{jansen_bijels_2011,gunther_timescales_2014} We add the additional processing calculating a parallel and perpendicular domain size
-from the results in each cartesian direction, defining $L_{\parallel}=L_z$ and $L_{\perp} = \frac{L_x+L_y}{2}$ we plot the structure factor of the structures in
-Figure \ref{fig:structure_factor}.
-
-\begin{figure*}
-    \centering
-    \includegraphics[width=\textwidth]{figures/results/paper1/structure_factor.png}
-    \caption{Scaling plot of the dynamic structure factor $S(k,t)$ for different particle shapes $\alpha$ and at different 
-            magnetic field strength $\bar{B}$. The structure factor is plotted at four different timesteps for each case. The good data collapse shows that the 
-            bijel formation is driven by spinodal decomposition. The decay to the right of the peak is reasonably well described by Porod's law $S(k)\sim k^{-4}$.}
-    \label{fig:structure_factor}
-\end{figure*}
-
-Figure \ref{fig:structure_factor} shows the scaling of the dynamic
-structure factor \(S(k,t)\). The data collapse is good, albeit
-deviations from dynamic scaling are present at smaller length scales.
-The decay to the right of the maximum is reasonably well described by
-Porod's law \(S(k)\sim k^{-4}\) indicating scattering off a nearly flat
-interface. These results are in line with the scaling results by Kendon
-et al.~\cite{kendon_3d_1999, kendon_inertial_2001} for spinodal
-decomposition of binary fluids, which suggests that the formation of
-bijels is primarily driven by the separation dynamics of the fluids. The
-effect of the suspended particles only comes into play once larger
-domains have formed and the coarsening interface reduces the accessible
-area to the point where the particles start interacting. The onset of
-particle interactions and subsequent jamming leads to a fairly sudden
-slow-down of domain growth, as can be observed in the time evolution of
-the domain size shown in Figure \ref{fig:domain_size}.
-
-The domain size \(L_1\) obtained from the spherically averaged structure
-factor initially shows a power law behavior very close to
-\(L_1\sim t^{2/3}\). A nonlinear curve fit of the function
-\(b(t-t_0)^a\) to the interval \(t\in[0,\ 3\cdot10^5\Delta x]\) yields
-the exponents \(a=0.6448\) for spherical particles, \(a=0.6083\) for
-oblate particles with aspect ratio \(\alpha=0.5\), and \(a=0.652\) for
-prolate ellipsoids with aspect ratio \(\alpha=2\). These values are in
-good agreement with the exponent \(a=2/3\) that is expected in an
-inertial scaling regime, where the characteristic velocity \(U=dL/dt\)
-scales with the characteristic length scale
-\(U\sim \sqrt{\sigma/(\rho L)}\), leading to \(L \sim t^{2/3}\). After
-around 30,000 to 40,000 time steps, the domain growth starts slowing
-down and approaches a plateau at \(L_1\approx 200\Delta x\) for
-spherical particles, \(L_1\approx 180\Delta x\) for the prolate
-particles, and \(L_1\approx 170\Delta x\) for the oblate particles.
-Interestingly, the alternative domain size measure \(L_d\) obtained from
-the second moments of the 3D structure factor does not show the same
-power law behavior. The rate of increase of \(L_d\) is substantially
-smaller than that of \(L_1\), with a fitted exponent in the range of
-0.12 to 0.20. The increase of \(L_d\) levels of earlier and reaches a
-plateau around \(L_d\approx 70\Delta x\) for all three particle aspect
-ratios. While dynamic scaling allows different measures of the
-characteristic length scale to vary by a prefactor, the deviation from
-the expected power law of both viscous and inertial scaling indicates
-that the second moment of the 3D structure factor does not yield a
-proper characteristic length scale. %, contrary to what has been assumed in
-%previous works \cite{jansen_bijels_2011, gunther_timescales_2014}.
-If one interprets the moments of the structure factor as moments of a
-probability distribution, then the second moment of the 3D structure
-factor is equivalent to the ratio of the fourth and second moments of
-the spherically averaged structure factor (due to the factor \(k^2\) in
-the volume integral). Hence \(L_d\) is perhaps better interpreted as
-describing the shape of the structure factor (similar to kurtosis, but
-not exactly the same) rather than a characteristic length scale.
-Nevertheless, the second moments \(L_\beta\) provide separate measures
-for the three Cartesian directions and can thus reveal anisotropy of the
-domain morphology.
-
-\begin{figure*}
+\begin{figure}
     \centering
@@
              factor, and $L_d$ denotes the domain size obtained from the second moment of the 3D structure factor. The increase roughly 
-         follows a $\sim t^{2/3}$ scaling law indicative of the inertial regime of spinodal decomposition.}
+             follows a $\sim t^{2/3}$ scaling law indicative of the inertial regime of spinodal decomposition. Image courtesy of Ulf D. Schiller}
     \label{fig:domain_size}
-\end{figure*}
+\end{figure}
 
-\subsection{Effect of magnetic field on bijel formation}
+Two methods have been identified to characterize the domain size of bijels from the structure factor. They are the first moment of the spherically averaged structure factor
+named $L_1$ and the second moment of the directional structure factor. The numerical average of the second moment derived structure factor is named $L_d$. Comparing the time
+evolution of both in Figure \ref{fig:domain_size}, the domain size increases before slowing down and finally plateauing. This indicates unhindered spinodal decomposition at
+early times, followed by a slowdown of domain coarsening caused by particle interactions before the bijel microstructure jams. Comparing the characterized domain sizes, 
+$L_d \~ 80$ compared to $L_1 \~ 150$. $L_d$ and $L_1$ also have differing time evolution, with $L_d$ beginning to plateau earlier than $L_1$. To identify which lengthscale 
+should be used to characterize the time evolution of the structure, we invoke dynamical scaling.
+
+From dynamical scaling, spinodal decomposition of binary fluids can be characterized through the inertial regime $L \~ t^{2/3}$, crossover regime $L \~ t^{n}, 2/3 < n < 1$ and 
+the inertial regime $L \~ t$. \cite{kendon_3d_1999,kendon_inertial_2001} These scaling regimes can be obtained from the Navier Stokes equation with additional surface tension 
+forces. The characterized lengthscales should conform to dynamical scaling as it is independent of the method used to characterize the lengthscale. By fitting the first phase
+of the domain size evolution for all particle shapes, the scaling exponent of domain size change characterized with $L_1$ is found to be approximately $L \~ t^{2/3}$. However
+the scaling exponent for $L_d$ is found to be $L \~ t^{0.2}$. Therefore, $L_1$ is selected to characterize the time evolution of the domain size. However the second moment of
+the domain size allows characterization of the domain size in each cartesian direction. The second moment derived domain size will be used to characterize the microstructure
+of the bijel.
+
+\subsection{Effect of magnetic field on bijel microstructure}
+
+% In LB simulations of spinodal decomposition, a characteristic length
+% scale can be obtained from the structure factor, defined in Section \ref{section:domain_size}. \cite{kendon_3d_1999,kendon_inertial_2001} 
+% It is worth noting that this definition of average domain size does not necessarily yield values that coincide with the typical
+% domain size observed visually in snapshots such as those shown in Figure~\ref{fig:microstructure_viz}. However, in a dynamic
+% scaling regime, different measures of domain size are expected to differ only by a constant ratio. We found that the commonly 
+% used measure \(L_1(t)\) tends to overestimate the observed domain size. Numerically, the calculation of the spherically 
+% averaged structure factor is subject to poor statistics in the low \(k\)-shells, where the average \(|\vec{k}|\) of the 
+% lattice sites differs from the nominal shell radius. Additionally, the measurement of \(L(t)\) in simulations with
+% periodic boundary conditions is subject to finite size effects. More importantly, in suspensions of anisotropic particles, 
+% We cannot expect that the structure factor is isotropic. Therefore, we also used the 3D structure factor to calculate a lateral domain 
+% size in each Cartesian direction from the second moments also defined in Section \ref{section:domain_size}. 
+% \cite{jansen_bijels_2011,gunther_timescales_2014} We add the additional processing calculating a parallel and perpendicular domain size
+% from the results in each cartesian direction, defining $L_{\parallel}=L_z$ and $L_{\perp} = \frac{L_x+L_y}{2}$ we plot the structure factor of the structures in
+% Figure \ref{fig:structure_factor}.
 
@@
     \includegraphics[scale = 0.4]{figures/results/paper1/D2a-vs-B_ss.png}
-\caption{Dependence of the average domain size on the magnetic field strength $\bar{B}$.
-The left plot shows the average domain size $L_1$ obtained from the spherically averaged structure factor.
-The right plot shows the parallel and perpendicular domain size obtained from the respective second moments of the 3D structure factor.
-Errorbars indicate the standard deviation taken over three independent simulation runs.
-For anisotropic particles, the directional domain size becomes more anisotropic with increasing field strength.}
+    \caption{Dependence of the average domain size on the magnetic field strength $\bar{B}$. The left plot shows the average domain size $L_1$ obtained from the spherically averaged structure factor. 
+    The right plot shows the parallel and perpendicular domain size obtained from the respective second moments of the 3D structure factor. Errorbars indicate the standard deviation taken over 
+    three independent simulation runs. For anisotropic particles, the directional domain size becomes more anisotropic with increasing field strength.}
     \label{fig:D2a_B}
@@
 
-At first glance, the time-dependence of the domain size in Figure 
-\ref{fig:domain_size} suggests that the domain size is not strongly
-affected by the external magnetic field. In Figure \ref{fig:D2a_B}a) we
-plotted the domain size measure \(L_d\) normalized by \(R\), the larger
-of the two radii of the ellipsoidal particles. The data points represent
-the domain size measured at the final time step and averaged over three
-independent simulation runs with the same parameters. The normalization
-with the particle radius makes it apparent that the ellipsoidal
-particles reduce the domain size of bijels. This observation is in line
-with observations by Günther et al.~\cite{gunther_timescales_2014} and
-indicates that -- relative to their volume -- ellipsoidal particles
-stabilize a larger interface area than spherical particles. This is due
-to the larger cross-sectional area of ellipsoidal particles at the same
-volume. Furthermore, steric constraints prevent anisotropic particles to
-pack less densely in the interface than spherical particles, as we will
-discuss in more detail below.
-
-The magnetic field does have an effect on the directional
-domain size as shown in Figure \ref{fig:D2a_B} where we plotted the
-domain size in the direction parallel and perpendicular to \(\vec{B}\)
-separately. We find that for prolate particles, the domain size in the
-parallel direction increases with the field strength up to approximately
-three particle radii for the largest field, while the perpendicular
-domain size stays constant. This trend is reversed for oblate particles
-for which the domain size in the parallel direction decreases slightly
-with field strength while the perpendicular domain size increases by
-approximately four particle radii. Without a field, prolate
-particles lead to smaller domain size than both spherical and oblate
-particles, whereas they increase the domain size when the bijel forms under the
-influence of a magnetic field. The anisotropy is due to the alignment of
-ellipsoidal particles which leads to a closer packing within the
-interface akin to nematic ordering. The difference between oblate and
-prolate particles is caused by the orientation of the magnetic dipole
-moment \(\vec{m}\) along the symmetry axis of the particles. In our
-model, \(\vec{m}\) is aligned with the larger axis of prolate
-ellipsoids, whereas it is aligned with the smaller axis of oblate
-ellipsoids. Hence \(\vec{m}\) lies in the plane of the larger
-cross-section of prolate particles while \(\vec{m}\) is perpendicular to
-the larger cross-section of oblate particles. We thus expect that
-alignment of the particles with the magnetic field \(\vec{B}\)
-facilitates closer packing perpendicular to the field for prolate
-particles, and parallel to the field for oblate particles. The
-increase/decrease of domain size levels off at intermediate field
-strength and further increases of the field have no additional effect.
-
 \subsection{Tortuosity}
 
-\begin{figure*}
+\begin{figure}
     \centering
@@
     \label{fig:tau_B}
-\end{figure*}
+\end{figure}
 
-The anisotropy of domain size suggests that the magnetic field
-influences the bijel morphology at the microscale. To investigate
-whether these structural changes have an effect on macroscopic
-transport properties, we also characterized the tortuosity of the
-bijels. Various definitions of tortuosity have been proposed in the
-literature \cite{dasilva_tortuosity_2022}, including geometric,
-diffusional, and hydraulic tortuosity. Here we use the diffusional
-tortuosity $\tau= \frac{\epsilon D}{D_{\text{eff}}}$, i.e., the ratio of the 
-effective diffusivity $D_{\text{eff}}$ and the intrinsic diffusivity
-$D$. We calculate the tortuosity using the procedure detailed in Section \ref{section:tortuosity}
-
-Figure \ref{fig:tau_B} shows the results for the tortuosity as a
-function of the applied magnetic flux for the three particle aspect
-ratios. In the absence a magnetic field, the three aspect ratios lead to
-a similar tortuosity around $\tau\approx 1.5$, slightly larger than
-the tortuosity predicted by the Bruggeman relation
-\(\tau=\epsilon^{-0.5}=1.41\) for equal volume fractions
-\(\epsilon=0.5\) of the phases
-\cite{bruggeman1935tortuosity, tjaden_origin_2016}. The observed
-tortuosity is consistent with simulations of gyroid structures by Luo et
-al., who found diffusive tortuosities in the range from 1.48 to 1.73
-\cite{luo_macroscopic_2020}. Figure \ref{fig:tau_B} shows that in an
-applied magnetic field, the tortuosity of bijels stabilized by
-anisotropic particles (\(\alpha\neq1\)) becomes anisotropic as well.
-Oblate particles (\(\alpha=0.5\)) lead to an increase of the tortuosity
-\(\tau_\parallel\) in the direction of the magnetic field while the
-tortuosity in the direction perpendicular to the magnetic field remains
-around \(\tau_\parallel\approx1.5\). Conversely, prolate particles
-(\(\alpha=2\)) lead to an increase of the tortuosity in the direction
-perpendicular to the magnetic field, while the tortuosity in the
-parallel direction slightly decreases with increasing field strength. In
-both cases, the changes in tortuosity are consistent with the
-anisotropic domain size and the alignment of particles with the magnetic
-field. For prolate particles, the longer axis is aligned with the
-magnetic moment and induces larger domain size and lower tortuosity in
-this direction. The results show that the magnetic field has a
-noticeable effect on the tortuosity of the bijel. We observe that the
-largest change of tortuosity is measured at intermediate field strength
-\(\bar{B}=0.5\). This suggests that the competition of interfacial and
-magnetic forces and the resulting alignment of particles and liquid
-domains induces morphological changes that are more complex than a
-monotonic increase or decrease. We therefore turn to investigate the
-microstructural changes within the bijel morphology in more detail.
+\begin{figure} 
+    \centering 
+    \includegraphics[scale = 0.4]{figures/results/paper1/curvature-vs-B_ss.png} 
+    \caption{Plot of the area averaged mean $\langle H \rangle \Sigma^{-1}$ and Gaussian 
+            $\langle K \rangle \Sigma^{-2}$ curvature in the left and right respectively. Each 
+            plot contains the $\langle H \rangle \Sigma^{-1}$ and $\langle K \rangle \Sigma^{-1}$ 
+            at the final timestep averaged across 3 runs for particles with $\alpha = 0.5, 1, 2$. 
+            The mean curvature remains 0 on average, while the Gaussian 
+            curvature shows a reduction as the magnetic field strength is increased for 
+            ellipsoidal particles.} 
+    \label{fig:curvature-vs-B_ss}
+\end{figure}
 
@@
 
-\begin{figure*}
+\begin{figure}
 \includegraphics[width=\textwidth]{figures/results/paper1/coarsening_vel.png}
@@
 and at different magnetic field strength $\bar{B}$. The different components of the coarsening velocity 
-show that the jamming time is different in the direction parallel and perpendicular to the magnetic field.}
+show that the jamming time is different in the direction parallel and perpendicular to the magnetic field. Image provided
+courtesy of Ulf D. Schiller.}
 \label{fig:coarsening_velocity}
-\end{figure*}
+\end{figure}
 
-Figure \ref{fig:coarsening_velocity} shows the coarsening speed in the directions parallel and perpendicular to the applied magnetic field. 
-The data confirms that for spherical particles, domain coarsening remains isotropic. We observe a higher coarsening speed initially which slows 
-at later times when the particles begin to jam. This indicates that the
-coarsening is subject to different time scales, as reported previously
-by Harting and co-workers \cite{gunther_timescales_2014}. Reeves et
-al.~\cite{reeves_particle-size_2015} have pointed out that bijel
-formation hinges on the jamming time in relation to the disruption time, i.e., the time scale at which domain pinch-off events can cause bijel break-up through 
-depercolation. In our simulations, however, we have not observed disruption of bijel formation; stable bijels form for all parameters consistent with simulations 
-by Stratford et
-al.~\cite{stratford_colloidal_2005} and Jansen et al.~\cite{jansen_bijels_2011}.
+% Figure \ref{fig:coarsening_velocity} shows the coarsening speed in the directions parallel and perpendicular to the applied magnetic field. 
+% The data confirms that for spherical particles, domain coarsening remains isotropic. We observe a higher coarsening speed initially which slows 
+% at later times when the particles begin to jam. This indicates that the
+% coarsening is subject to different time scales, as reported previously
+% by Harting and co-workers \cite{gunther_timescales_2014}. Reeves et
+% al.~\cite{reeves_particle-size_2015} have pointed out that bijel
+% formation hinges on the jamming time in relation to the disruption time, i.e., the time scale at which domain pinch-off events can cause bijel break-up through 
+% depercolation. In our simulations, however, we have not observed disruption of bijel formation; stable bijels form for all parameters consistent with simulations 
+% by Stratford et
+% al.~\cite{stratford_colloidal_2005} and Jansen et al.~\cite{jansen_bijels_2011}.
 
-For ellipsoidal particles, our data clearly shows that an\-isotropic
-domain coarsening arises in magnetic fields.  For oblate particles
-(\(\alpha=0.5\)), the coarsening speed in the direction perpendicular
-to the field increases with increasing magnetic field strength.
-Jamming in this direction appears to be delayed compared with the
-direction parallel to the field. The coarsening speed in the parallel
-direction remains comparable to the case without an applied magnetic
-field. This anisotropic behavior of the coarsening speed reverses for
-prolate particles, where the coarsening speed in the direction parallel to the field increases with increasing field strength, and jamming in this direction
-is delayed compared with the perpendicular direction.
+% For ellipsoidal particles, our data clearly shows that an\-isotropic
+% domain coarsening arises in magnetic fields.  For oblate particles
+% (\(\alpha=0.5\)), the coarsening speed in the direction perpendicular
+% to the field increases with increasing magnetic field strength.
+% Jamming in this direction appears to be delayed compared with the
+% direction parallel to the field. The coarsening speed in the parallel
+% direction remains comparable to the case without an applied magnetic
+% field. This anisotropic behavior of the coarsening speed reverses for
+% prolate particles, where the coarsening speed in the direction parallel to the field increases with increasing field strength, and jamming in this direction
+% is delayed compared with the perpendicular direction.
 In addition, we observe a shoulder (around \(10^4\Delta t\)) where the coarsening speed decays more slowly before jamming sets in.
 These results suggest that the coarsening near the jamming time is affected by a mechanism that depends on the applied magnetic field and causes the anisotropic
-behavior. This mechanisms involves the re-orientation of anisotropic
-particles and their alignment relative to the direction of the
-magnetic field. To confirm this hypothesis, we analyze the
-orientational order of the particles and their alignment relative to
-the magnetic field and the interface, respectively.
+% behavior. This mechanisms involves the re-orientation of anisotropic
+% particles and their alignment relative to the direction of the
+% magnetic field. To confirm this hypothesis, we analyze the
+% orientational order of the particles and their alignment relative to
+% the magnetic field and the interface, respectively.
 
@@
 
-The primary effect of the magnetic field is the torque it exerts on the
-magnetic dipole of the particles. This torque rotates the particles
-towards the direction of the magnetic field. The alignment of the
-particles with the field direction can be clearly observed in the
-simulation snapshots shown in Figure \ref{fig:packing_viz}. While the
-particles are oriented randomly in the interface in the absence of a
-magnetic field (\(\bar{B}=0\)), the magnetic field induces orientational
-order of the magnetic dipoles (shown for \(\bar{B}=1\)).
-
 \begin{figure}
@@
 \end{figure}
-
-To measure the particle alignment quantitatively, we computed the
-nematic order tensor using the method detailed in Section \ref{section:nematic_order_parameter} 
-Figure \ref{fig:nematic_time} shows the time evolution of the nematic
-order parameter \(S\) for the three different particle aspect ratios
-\(\alpha\) and varying magnetic field strength \(\bar{B}\). The onset of
-orientational order is nearly instantaneous and increases with
-increasing field strength. For magnetic flux densities
-\(\bar{B}\ge0.5\), the nematic order parameter saturates at
-\(S\approx 1.0\) towards the end of the simulation. For the prolate
-particles (\(\alpha=2.0\)), we observe a shoulder at around
-\(10^4\Delta t\) and an intermittent plateau. The occurrence of this
-plateau coincides with the slowed decay of the coarsening speed in Figure
-\ref{fig:coarsening_velocity}. This change in the orientational ordering
-is even more distinct for the oblate particles, where the nematic order
-decays intermittently before it increases again. The intermittent decay
-for oblate particles, and the plateau for prolate particles, correlate
-with the delayed onset of jamming in the direction perpendicular and
-parallel to the magnetic field, respectively. These observations can be
-interpreted as follows: The magnetic field aligns the particles with the
-direction of the magnetic field early during the simulation. Due to this
-alignment, the steric constraints between particles adsorbed at the
-interface are reduced which allows further coarsening of the interfacial
-area. However, during coarsening, the interfaces may re-orient
-themselves and cause a capillary torque on the particles that competes
-with the magnetic torque. This competition intermittently perturbs the
-nematic order of the particles leading to the observed decay and plateau
-of the nematic order parameter. Accordingly, the decay of \(S\) is most
-pronounced at the weakest magnetic field \(\bar{B}=0.2\). To further corroborate 
-this mechanism, We plot the time evolution of the orientational order of the interfaces.
-
-\begin{figure}
-\centering
-\includegraphics[scale = 0.4]{figures/results/paper1/interface_nematic.png}
-\caption{Time-dependence of the interface nematic order for oblate ($\alpha=0.5$) and prolate ($\alpha=2$) particles at different magnetic field strength $\bar{B}$.
-The interface alignment tends to increase with increasing field strength.
-The rate of increase becomes larger around $10^4$ timesteps, indicating the alignment of the interfaces due to capillary interactions with the particles.}
-\label{fig:interface_nematic}
-\end{figure}
-
-The results for the interface nematic order parameter $S_{\text{int}}$
-are shown in Figure \ref{fig:interface_nematic}. The nematic interface
-alignment increases over time and the rate of increase appears to be
-higher for larger magnetic field strength $\bar{B}$. In all cases, the
-final value of $S_{\text{int}}$ is below 0.5 indicating that the
-tortuous structure of the interface is maintained in the presence of
-magnetic fields. This confirms that the re-orientation of the particles
-does not disrupt the bijel structure but leads to partial alignment of
-the interfaces without changing the general topology of the bicontinuous
-morphology.
-
-When the particles rotate, the interface exerts a capillary torque on
-the particles due to the surface tension and the contact angle. If the
-magnetic torque exceeds the interfacial forces, the particles can
-potentially overcome the capillary torque and rotate out of the
-interface. For prolate particles (\(\alpha=2\)) adsorbed at flat
-interfaces, Davies et al. have shown that a transition between the
-energetically preferred ``flat'' orientation and a tilted orientation
-occurs at a critical field strength of approximately \(\bar{B}=0.2\)
-\cite{bresme_orientational_2007,davies_interface_2014,newton_influence_2014}.
-In the case of bijels, however, the percolating interfaces are tortuous
-and thus more mobile. We therefore posit that, rather than tilting out
-of the interface, rotating particles can ``pull'' the interface along
-and thereby align the liquid domains. For anisotropic particles, we
-expect that the interfaces align along the larger cross-section of the
-particles, i.e., perpendicular to the symmetry axis of oblate particles
-and parallel to the symmetry axis of prolate particles. The data for the
-anisotropic domain size and tortuosity above is consistent with this
-assumption. To ascertain that the particles remain indeed in their
-energetically preferred orientation with respect to the interface, we
-analyzed the angle between the symmetry axis of the particles and the
-interface normal calculated using the technique defined in Section 
-\ref{section:interface_angle}. Figure \ref{fig:psi_time} shows the time-dependence of the average angle
-\(\psi\) between the particle dipole axis and the nearest interface normal.
 
@@
 
-For both types of anisotropic particles, the average angle between the
-particle dipole and the interface normal is initially around
-\(\psi\approx60^\circ\). As the spinodal interface sweeps through the
-system, particles attach to the interface and alignment due to the
-capillary torque sets in. For oblate particles, the dipole axis aligns
-with the interface normal as indicated by the decay of \(\psi\) towards
-zero. For prolate particles, the preferential alignment of the dipole
-axis is parallel to the interface and hence \(\psi\) increases towards
-\(90^\circ\). The main variation of \(\psi\) occur in a time interval
-around \(10^4\Delta t\) which coincides with the distinct features of
-the coarsening speed and the particle nematic order observed above. The
-results thus substantiate the proposed mechanism of particle
-re-orientation in the magnetic field and the concomitant local alignment
-of the interface. Once the particles start jamming, the shrinking
-interfacial area forces some particles out of their preferred alignment
-with the interface, leading to an increase of \(\psi\) for oblate
-particles and a decrease of \(\psi\) for prolate particles. Figure
-\ref{fig:psi_time} suggests that the forced tilting is more pronounced
-for oblate particles than for prolate particles. Due to the larger
-aspect ratio, the tilting of prolate particles relative to the interface
-induces deformations that appear to cause a larger capillary torque than
-the tilting of oblate particles. %For oblate particles, the liquid-solid
-%contact line is on average further away from the particle center than
-%for prolate particles, hence the lever effect of oblate particles is
-%weaker and allows larger tilting relative to the the preferred alignment
-%with the interface.
+Hence the prolate particles remain mostly aligned with the interface
+even in the stronger applied magnetic fields. We plot the interface angle of bijels
+stabilized by ellipsoidal particles at the final timestep to demonstrate the differences
+that the application of magnetic fields have on the particle monolayer.
+
+\begin{figure}
+    \centering
+    \includegraphics[scale = 0.4]{figures/results/paper1/psi_concat.png}
+    \caption{Visualizations of the particle monolayer at the last timestep shaded with the interface angle of each particle in red. The top and bottom
+             rows correspond to snapshots of bijels with no field and a field strength of $\bar{B} = 1$ applied. We see that the oblate particles flip
+             out of the interface into a non energetically favored position while the bijels stabilized with prolate particles tilt out of the interface
+             but are less likely to flip out.}
+    \label{fig:psi_viz_ss}
+\end{figure}
+
 Hence the prolate particles remain mostly aligned with the interface
@@
 
-\begin{figure*}
+\begin{figure}
 \centering
@@
 \label{fig:rdf}
-\end{figure*}
-
-The radial distribution function is shown at time steps
-\(t=1000\Delta t,\ 10000\Delta t,\ 100000\Delta t\). For ellipsoidal
-particles, the characteristic distances between particles in contact are
-\(2R_{\parallel}\), \(2R_{\perp}\), and \(R_{\parallel} + R_{\perp}\).
-These distances are marked by dashed lines in Figure \ref{fig:rdf}. We
-observe that the largest peak of the RDF coincides with the distance
-\(2R_\perp\) for both oblate and spherical particles, indicating that
-oblate particles tend to be in contact at their circumference while
-prolate particles preferentially align side-by-side. These arrangements
-lead to closer packing of particles in the interface. The peaks are less
-pronounced in the early stage of the simulations, where the particles
-are more randomly oriented. Notably, there is a dip in the RDF of
-prolate particles at \(2R_\parallel\) indicating that initially the
-tip-to-tip configuration occurs more rarely. The growth of the peak
-height over time shows that the magnetic fields promote this alignment
-compared to the case without magnetic field. For oblate particles, a
-shoulder develops around \(R_\parallel+R_\perp\), indicating that some
-particles tilt out of the interface to reduce the covered interfacial
-area. For prolate particles, the dip at \(2R_\parallel\) disappears over
-time, indicating that more particles align tip-to-tip. This is
-consistent with alignment of prolate particles with respect to the
-magnetic field, which facilitates closer packing along both axes of the
-particles. It further suggests that particles arrange in layers, which can also be observed in the snapshot in Figure
-\ref{fig:packing_viz}. Together with the analysis of nematic order
-above, these results substantiate the proposed mechanisms that influence
-the formation of bijels with anisotropic particles in magnetic fields:
-The magnetic field aligns the particle dipole axis in the field
-direction, and the particle re-orientation couples to interface
-alignment due to the capillary interactions. The alignment of particles
-reduces the steric constraints within the interface, which allows the
-interface to shrink further and facilitates domain coarsening. In terms
-of the time-evolution, the rotation of particles due to the magnetic
-field occurs during the initial stages of the simulation, followed by
-the local re-alignment of interfaces due to capillary interactions. In
-the case of prolate particles, we observed the shrinking interface can
-force particles to tilt out of their preferential alignment to facilitate
-closer packing. Generally, our results show that when bijels stabilized
-by anisotropic magnetic particles form under the influence of a magnetic
-field, the domain size and tortuosity become anisotropic. Additionally,
-we observe that the particle packing in the interface becomes more
-ordered due to the alignment effects.
-
-\section{Conclusions}
-
-In this work, we studied the effect of applied magnetic fields on the
-formation of bijels stabilized by magnetic ellipsoidal particles. We
-considered oblate, spherical, and prolate particles with a permanent
-magnetic dipole moment suspended in a symmetric binary liquid. We found
-that, while the overall formation of a bijel is not disrupted by
-magnetic interactions, bijels stabilized by oblate or prolate ellipsoids
-exhibit anisotropic domain size and an anisotropic tortuosity. For
-oblate particles, the domain size increases in the direction
-perpendicular to the magnetic field while the tortuosity increases in
-the parallel direction. Conversely, for prolate particles, the domain
-size increases in the direction parallel to the magnetic field while the
-tortuosity increases in the perpendicular direction. Compared with
-bijels formed in the absence of a magnetic field, we observed changes in
-domain size up to \(30\%\) for non-spherical particles. When probing
-the differences in the microstructure, we identify that while the
-connectivity of the microstructure does not change, 
-the time evolution of the area averaged gaussian curvature shows that
-orientational ordering of the particles affects the shape of the
-coarsening interface. These shape differences are then locked into place
-upon jamming, resulting in a more hyperbolic interface in bijels stabilized
-by ellipsoidal particles upon application of magnetic fields. The frequency 
-of the number of channels changes as a function of distance from the interface. I
-characterize this as peak movements closer and further from the interface upon application of magnetic
-field, corroborating the microstructure anisotropy characterized.
-
-This effect can
-be explained by the re-orientation of the particle dipole axis with the
-magnetic field, which in turn re-aligns the interfaces in the direction
-of the longer axis of the particles. We further corroborated this
-mechanisms by analyzing the coarsening speed and the nematic order of
-the particles and the interfaces. We found that jamming of particles is
-delayed in the direction of the longer ellipsoidal axis leading to
-enhanced coarsening in this direction. The timescale of the delayed
-jamming coincides with a slow-down of the orientational ordering of the
-particles whereas the alignment of the interfaces increases. We also
-found that the angle between the particle dipole axis and the interface
-normal changes at this stage. Orientational ordering at the interface was
-observed to reduce for disc like particles and increase for rod like
-particles upon application of the magnetic field. We analyzed the radial
-distribution function of the particles and found that prolate particles
-tend to align side by side, while the oblate particles exhibit a less
-regular arrangement. Based on these findings, we propose that bijel
-formation in magnetic fields is governed by two coupled effects: During
-the initial stage, the magnetic torque rotates the particles to align
-the magnetic dipole moment with the field, and the orientational order
-of the particles facilitates further coarsening. As coarsening proceeds,
-the capillary interactions cause the interfaces to align with the longer
-particle axis. The shrinking interface compresses the particles into
-ordered arrangements. When jamming sets in, some particles can be forced
-to tilt out of the interface and this effect is more prominent for
-oblate particles.
-
-Our results demonstrate the effects of magnetic fields on the structural
-properties of bijels stabilized by ellipsoidal magnetic particles. This
-control is desirable in applications where the domain size and
-tortuosity affect the transport properties. For example, reduced
-tortuosity can increase the diffusive permeability of bone-like
-materials \cite{prakoso2023tortuosity}. Similarly, low tortuosity
-in lithium electrodes facilitates homogeneous ion transport and
-uniform lithium deposition, leading to enhanced cyclability of
-batteries\cite{chen_tortuosity_2020, ebner_tortuosity_2014}. Whereas we
-have considered one particular regime of spinodal decomposition, the
-viscosity and surface tension of the liquids offer additional parameters
-that could be leveraged to tune the bijel formation. Moreover, the
-particle volume fraction is another parameter that is known to affect
-the formation of particle-stabilized emulsions
-\cite{jansen_bijels_2011,hijnen_bijels_2015}. With respect to possible
-experimental realizations of our simulations, we should emphasize that
-we have generally considered micron-size particles and have neglected
-thermal fluctuations. At the nanoscale, thermal fluctuations may in
-principle play a role, however, Reeves et
-al.~\cite{reeves_particle-size_2015} have shown that nanoparticles
-benefit from smaller driving forces towards disruptive curvature and
-actually lead to more robust bijel formation. Nevertheless, the
-stability of magnetically-responsive bijels is a relevant question for
-applications that involve shear flows such as crossflow reactors
-\cite{khan_nanostructured_2022}. Aside from particle-size and shape
-effects, direct interactions between particles are a possible avenue
-to tune the formation of particle-stabilized emulsions gels, as the
-recent discovery of bicontinuous intraphase jammed emulsion gels
-(bipjels) illustrates \cite{kinkead_bicontinuous_2019}. Another
-interesting observation arising from our simulations is that the
-packing order of particles in the interface appears to increase when
-bijels form under the influence of a magnetic field. While such
-interfacial ordering effects have been studied on planar interfaces
-\cite{toor_self-assembly_2016,shi_nanoparticle_2018,kim_dynamic_2022},
-they have hitherto not been reported for particle-stabilized emulsion
-gels. It would be interesting to examine the implications of this
-ordering on the optical and transport properties of jammed emulsion
-gels. In conclusion, our simulations provide relevant insights into the
-formation of magnetic particle-stabilized bijels in the presence of
-external magnetic fields, and they demonstrate the potential of magnetic
-particles for fabrication of emulsion systems with tunable and
-anisotropic particle packing and domain structure.
+\end{figure}

### 2025-04-01 chapters/dissertation-tap.tex
Changes 1. Refactoring LBM methods explanation 2. Removing contact angle plots for model validation 3. Changes psi vs t figure in paper 1
Rewrote abstract

@@
 % to remove special characters or commands like \\ for example.
-\title[First Line of Title Second Line of Title]{Lattice Boltzmann simulations of magnetically responsive\\
-ellipsoidal particle stabilized emulsions}
+\title[First Line of Title Second Line of Title]{Emulsions Stabilized by Magnetic Ellipsoidal Particles: A Lattice Boltzmann Study}
 \author{Nikhil Karthikeyan}
@@
                  % for an abstract or type text here.
-    Porous materials are important in a wide range of applications, including water filtration, 
-    catalyst supports, battery electrodes, and bioengineered materials. To accommodate a broader range of pore 
-    sizes and enable scalable fabrication with minimal waste, bottom-up synthesis techniques have gained 
-    increasing attention. Among these, emulsion templating based on bicontinuous interfacially jammed 
-    emulsion gels (bijels)—has emerged as a promising approach due to its ability to produce complex, 
-    interconnected porous structures.
+    Porous materials are important across a wide range of applications, including water filtration, catalyst supports, 
+    battery electrodes, and bioengineered materials. To accommodate a broader range of pore sizes and enable scalable 
+    fabrication with minimal waste, bottom-up synthesis techniques have gained increasing attention. Emulsion templating 
+    leverages thermodynamically or kinetically arrested structures formed by phase-separating fluids. Among these, bicontinuous 
+    interfacially jammed emulsion gels (bijels) are particularly promising due to their tortuous and co-continuous microstructures.
 
-    Despite these advantages, achieving microstructural control independent of the casting mixture remains a 
-    key challenge, particularly in continuous bijel fabrication methods such as Solvent Transfer Induced Phase 
-    Separation (STrIPS). Additionally, in situ control strategies for tailoring properties such 
-    as separation efficiency can be useful additions to control material performance. 
-    Stimuli-responsive approaches have been identified as a potential route to 
-    overcome these constraints. This study focuses on the magnetic stimuli-response of bijels stabilized by 
-    magnetically responsive ellipsoidal microparticles, examining both the resulting microstructural 
-    modifications and their rheological implications.
+    Bijels form via thermally induced spinodal decomposition of partially miscible fluid mixtures in the presence of neutrally 
+    wetting particles. As the fluid domains coarsen, particles adsorb onto the interface until the interfacial area matches the 
+    total cross-sectional area of the particles, resulting in a jammed monolayer that locks the microstructure in place. Traditional 
+    bijel synthesis via thermal phase separation is not readily scalable. However, newer techniques such as Solvent Transfer Induced 
+    Phase Separation (STrIPS) have been developed to address this limitation, utilizing the removal of solvent from a bijel casting
+    mixture to induce phase separation. However, the microstructure obtained is coupled to the casting mixture composition, 
+    and the flow rate during STrIPS.
 
-    It is shown that the application of a magnetic field during bijel formation induces microstructural 
-    changes in systems stabilized by ellipsoidal particles—effects not observed in bijels stabilized by 
-    spherical particles. The applied field causes particle reorientation along its direction, leading to 
-    directional jamming and the development of anisotropic microstructures.
+    One promising approach to modulate bijel microstructure is through stimulus-responsive systems. Magnetic stimuli, in particular, 
+    offer a non-invasive, controllable, and targeted mechanism. Earlier studies using spherical particles under magnetic fields showed 
+    limited microstructural changes. More recent work, however, has revealed that ellipsoidal particles can respond to magnetic actuation 
+    by tilting, leading to the formation of particle chains or rings at interfaces. This phenomenon opens the door to controllable 
+    modifications in bijel microstructures using magnetic fields.
 
-    Post-synthesis, bijels stabilized by ellipsoidal particles exhibit tunable microstructure. This responsiveness 
-    is governed by the degree of particle order present prior to field application, as well as the extent of 
-    reordering induced by the field. The system exhibits state-dependent behavior, indicating that the timing of 
-    magnetic field application significantly influences the magnitude of the microstructural response characterized.
+    This dissertation investigates whether constant magnetic fields can be used to control the microstructure of bijels stabilized by 
+    magnetically responsive ellipsoidal particles. To explore this, we employ a multicomponent Lattice Boltzmann Method coupled with a 
+    molecular dynamics representation of rigid particles and a dipole-based magnetic field model. The system simulates a water-2,6-lutidine 
+    mixture stabilized by micron-sized nickel-coated polystyrene particles.
 
-    Rheological characterization reveals that bijels retain their shear-thinning behavior under applied magnetic 
-    fields. However, the degree of particle ordering is found to influence both the evolution of the microstructure 
-    under shear and the corresponding rheological response, highlighting the interplay between field-induced 
-    structuring and mechanical performance.
+    We first examine the ability of magnetic fields to influence bijel formation by applying a constant field during spinodal decomposition 
+    of fluid mixtures containing disc-like, spherical, and rod-like particles. While no significant change in domain size is observed for 
+    spherical particles, bijels stabilized by discs and rods show slight increases in domain size and become anisotropic, as measured by 
+    tortuosity and directional domain size.Further analysis reveals that the coarsening rates become direction-specific for ellipsoidal particles, 
+    suggesting that jamming occurs anisotropically due to particle alignment with the magnetic field. This alignment, governed by the 
+    orientation of the magnetic moment relative to the particle's long axis, also affects how particles arrange themselves at the fluid 
+    interface.
+
+    Having established that magnetic fields can influence microstructure during synthesis, we then assess whether similar control can be exerted 
+    after bijel formation. This has implications for applications like crossflow reactors and filtration systems, where reversible control over 
+    permeability and flow resistance is desirable. By incrementally increasing and decreasing the magnetic field on a bijel stabilized with 
+    rod-like particles, we observe that the microstructure can indeed be modified post-synthesis. Domain size increases nonlinearly with 
+    applied field strength and remains altered even after the field is reduced, indicating a saturation threshold and a history-dependent 
+    response.
+
+    To probe this further, we evaluate field-driven coarsening in bijels stabilized with rod and disc-like particles. Upon field application, 
+    particles reorient, leading to anisotropic domains similar to those formed during synthesis under a field. The temporal evolution of 
+    microstructure involves increased particle ordering, interface alignment, and rearrangement, demonstrating a complex interplay of factors. 
+    Notably, the extent of domain size change is negatively correlated with the initial ordering of particles, suggesting a memory effect 
+    rooted in the starting microstructure.
+
+    Given that many magnetically responsive materials exhibit field-dependent rheological behavior (e.g., shear thickening in ferrofluids), 
+    we investigate whether bijels exhibit similar effects. Prior studies have shown that shear can induce domain coarsening and particle 
+    ejection in bijels. Additionally, emulsions stabilized by ellipsoidal particles show viscosity decreases with increased ordering due 
+    to weakened particle-fluid interactions. In this work, we explore how magnetic fields and initial microstructure affect the shear 
+    response of bijels stabilized by ellipsoidal particles.As particle ordering increases, the viscosity and shear-thinning behavior decrease for 
+    bijels stabilized by disc- and rod-like particles. Interestingly, the yield stress decreases with increased order for discs, but increases for 
+    rods due to differences in local particle arrangement and frictional contacts. Under shear, domain coarsening occurs due to shear induced particle 
+    tilting out of the interface.
+
+    In conclusion, this dissertation demonstrates that magnetic fields offer a viable and tunable method for controlling bijel microstructures both 
+    during and after synthesis, and it provides a detailed characterization of the constant shear response of magnetically responsive bijels. These findings 
+    lay the groundwork for developing adaptive, magnetically responsive porous materials through both conventional synthesis techniques and Solvent 
+    Transfer Induced Phase Separation (STrIPS), enabling scalable and application-specific design.
+
 \end{front}

### 2025-04-01 chapters/paper1_new.tex

@@
 
-% In LB simulations of spinodal decomposition, a characteristic length
-% scale can be obtained from the structure factor, defined in Section \ref{section:domain_size}. \cite{kendon_3d_1999,kendon_inertial_2001} 
-% It is worth noting that this definition of average domain size does not necessarily yield values that coincide with the typical
-% domain size observed visually in snapshots such as those shown in Figure~\ref{fig:microstructure_viz}. However, in a dynamic
-% scaling regime, different measures of domain size are expected to differ only by a constant ratio. We found that the commonly 
-% used measure \(L_1(t)\) tends to overestimate the observed domain size. Numerically, the calculation of the spherically 
-% averaged structure factor is subject to poor statistics in the low \(k\)-shells, where the average \(|\vec{k}|\) of the 
-% lattice sites differs from the nominal shell radius. Additionally, the measurement of \(L(t)\) in simulations with
-% periodic boundary conditions is subject to finite size effects. More importantly, in suspensions of anisotropic particles, 
-% We cannot expect that the structure factor is isotropic. Therefore, we also used the 3D structure factor to calculate a lateral domain 
-% size in each Cartesian direction from the second moments also defined in Section \ref{section:domain_size}. 
-% \cite{jansen_bijels_2011,gunther_timescales_2014} We add the additional processing calculating a parallel and perpendicular domain size
-% from the results in each cartesian direction, defining $L_{\parallel}=L_z$ and $L_{\perp} = \frac{L_x+L_y}{2}$ we plot the structure factor of the structures in
-% Figure \ref{fig:structure_factor}.
+From figure \ref{fig:domain_size}, the jamming of the bijels were determined to occur after $\~50000$ timesteps, characterized as a plateauing
+of the domain size. Qualitative differences in the domain size were observed in Figure \ref{fig:microstructure_viz} which originate from particles
+reorienting to the direction of the applied field. To characterize the microstructure at the final timestep, we plot the domain size of the bijels
+stabilized by ellipsoidal particles and compare them to what is obtained with spherical particles. We also compare the results obtained from the
+first and second moment derived structure factors by plotting the directional domain sizes as a function of the applied field to characterize
+domain anisotropy. An additional simplification is made where the domain size parallel to the magnetic field is defined as $L_{\parallel}=L_z$
+and the average of the other domain sizes are defined as $L_{\perp} = \frac{L_x+L_y}{2}$.
 
@@
 
+Figure \ref{fig:D2a_B} demonstrates that the first moment derived structure factor shows little change in the domain size as a function of the applied field for
+all particle aspect ratios. The second moment derived domain sizes demonstrate that the application of magnetic fields create domain anisotropy in the microstructure
+of bijels stabilized by ellipsoidal particles. Domain anisotropy is characterized as a divergence in the parallel and perpendicular domain sizes, seen in bijels
+stabilized by ellipsoidal particles but not in bijels stabilized by spherical particles upon application of a magnetic field. The characteristics of this divergence
+also differ for bijels stabilized by prolate particles and oblate particles. Bijels stabilized by prolate particles see an increase in $L_{\parallel}$ and a decrease in
+$L_{\perp}$ upon application of a magnetic field, while bijels stabilized by prolate particles see the opposite. This response is also dependent on the applied field,
+with the degree of response increasing from $\bar{B} = 0$ to $\bar{B} = 0.5$ before plateauing with field strengths applied above $\bar{B} = 0.5$.
+The particle aspect ratio dependent response arises from the differences in the orientation of
+the magnetic moment in prolate and oblate ellipsoids. In our simulations, the symmetry axis of prolate and oblate particles lies parallel to the long axis 
+and short axis of the particle respectively. In addition to the geometrical constraints imparted by the shape of the particles, this results in the orientation of the
+particles to differ upon application of the magnetic field.
+
 \subsection{Tortuosity}
+
+In Figure \ref{fig:D2a_B}, we quantitifed how the application of constant magnetic fields affects the microstructure of bijels stabilized by ellipsoidal particles
+and demonstrated that microstrucutre anisotropy is generated as a function of the applied field and the particle aspect ratio. Another parameter that controls the
+performance of porous materials is the tortuosity, characterized as the ratio between the parameter of interest in that system and the parameter of interest in
+the bulk system. While multiple definitions exist such as the geometric, hydraulic and diffusive tortuosity exist, we use the diffusive tortuosity due to its
+importance in characterizing porous material performance. A lower diffusive tortuosity in battery materials have been found to improve ion transport, reducing the
+likelihood of Lithium dendrite formation and improving the charging speed and number of cycles before battery degradation. 
+\cite{chen_tortuosity_2020, ebner_tortuosity_2014}. We calculate the using the method described in Section \ref{section:tortuosity}
 
@@
 
-\begin{figure} 
-    \centering 
-    \includegraphics[scale = 0.4]{figures/results/paper1/curvature-vs-B_ss.png} 
-    \caption{Plot of the area averaged mean $\langle H \rangle \Sigma^{-1}$ and Gaussian 
-            $\langle K \rangle \Sigma^{-2}$ curvature in the left and right respectively. Each 
-            plot contains the $\langle H \rangle \Sigma^{-1}$ and $\langle K \rangle \Sigma^{-1}$ 
-            at the final timestep averaged across 3 runs for particles with $\alpha = 0.5, 1, 2$. 
-            The mean curvature remains 0 on average, while the Gaussian 
-            curvature shows a reduction as the magnetic field strength is increased for 
-            ellipsoidal particles.} 
-    \label{fig:curvature-vs-B_ss}
-\end{figure}
+From Figure \ref{fig:tau_B}, the tortuosities calculated for bijels stabilized by spherical particles
 

### 2025-04-05 chapters/LBM_technique.tex
Changes 1. Rewritten literature review and introduction to combine both 2. Beginning to rewrite methods section 3. Finished rewrite of aim 1 - magnetic fields 4. Finished adding structure characterization

@@
 in the system. A review of the physics in the system will be provided.
+
+\section{Hydrodynamics}
 
@@
 
-$Re = \frac{\rho u l}{\eta}$ which defines the ratio between inertial and viscous forces. Another physical phenomenon being described is non-ideal mixing. The free energy of mixing
+$Re = \frac{\rho u l}{\eta}$ which defines the ratio between inertial and viscous forces.
+
+\section{Phase separation}
+
+Another physical phenomenon being described is non-ideal mixing. The free energy of mixing
 is defined as $\Delta G_m = \Delta H_m - T \Delta S_m$. In an ideal solution, $\Delta H_m = 0$. An expression for $\Delta S_m$ for a binary mixture is obtained from statistical mechanical 
@@
 
-The Shan-Chen pseudopotential
-model is used to simulate the Cahn-Hilliard equation, defined below
-
 \begin{equation}
     \begin{split}
-    \frac{\partial\phi}{\partial t}+\nabla\cdot\left(\phi\vec{u}\right) &= \nabla \cdot \left( \Gamma  \nabla\phi \right)
+    \frac{\partial\phi}{\partial t} = \nabla \cdot \left( \Gamma  \nabla\mu_\phi \right)
     \end{split}
@@
 
-where $c^k$, $M^k$ and $u^k$ is the concentration, mobility and velocity of species $k$ respectively while $\mu$ is the free energy of system. 
-\cite{shan_lattice_1993, shan_simulation_1994, he_lattice_1997, he_discrete_1998}
+\section{Particle dynamics}
 
-A computational model designed to simulate soft matter systems 
-at the mesoscale must accurately represent both hydrodynamics and non-ideal mixing in order to capture the essential physics of emulsions, colloids, and phase-separating fluids. 
-A hydrodynamic model must be able to recover mass and momentum conservation of a incompressible fluid
+\section{Magnetic fields and particles}
 
-Modelling multicomponent dynamics requires incorporating a free energy model between fluids, allowing for the implementation of
-chemical potential driven mass transfer and surface tension. Typically this is done using a Cahn-Hilliard model based on a
-square gradient free energy functional. This captures the demixing characteristics of phase separating fluids and controls interface
-characteristics, providing surface tension and interface width characteristics. This model has been used in past investigations looking 
-into spinodal decomposition, domain growth and coarsening.
+% The Shan-Chen pseudopotential
+% model is used to simulate the Cahn-Hilliard equation, defined below
 
-To fully capture mesoscale dynamics, the model must also resolve the coupling between hydrodynamic flow and composition gradients. This coupling 
-is essential for simulating phenomena such as Marangoni flows, interfacial instabilities, and anisotropic stress distributions that arise from 
-non-uniform compositions or curvature-dependent surface tension. Moreover, the model must support anisotropic or time-dependent external fields 
-(e.g., magnetic, electric, or shear) that influence mixing behavior. Computational frameworks that can evolve velocity, pressure, and composition 
-fields simultaneously—while ensuring thermodynamic consistency and mechanical stability—are critical for accurately describing the emergent structures 
-and transport properties in non-ideal soft matter systems.
+% \begin{equation}
+%     \begin{split}
+%     \frac{\partial\phi}{\partial t}+\nabla\cdot\left(\phi\vec{u}\right) &= \nabla \cdot \left( \Gamma  \nabla\phi \right)
+%     \end{split}
+% \end{equation}
 
-Given the multiscale modeling necessary to correctly simulate the physical system, one approach suggested to tackle this problem is the multicomponent
-Lattice Boltzmann Method. This technique bridges the length and time scales necessary in soft matter modeling through modeling the evolution of a particle
-distribution function. Hydrodynamic parameters are recovered through calculating the moments of the particle distribution function. One of the advantages of
-the Lattice Boltzmann Method its parallelize nature and ease of adding multiple physical phenomena. In the following sections, the implementation of the LBM
-and alternatives to the LBM will be presented.
+% where $c^k$, $M^k$ and $u^k$ is the concentration, mobility and velocity of species $k$ respectively while $\mu$ is the free energy of system. 
+% \cite{shan_lattice_1993, shan_simulation_1994, he_lattice_1997, he_discrete_1998}
+
+% A computational model designed to simulate soft matter systems 
+% at the mesoscale must accurately represent both hydrodynamics and non-ideal mixing in order to capture the essential physics of emulsions, colloids, and phase-separating fluids. 
+% A hydrodynamic model must be able to recover mass and momentum conservation of a incompressible fluid
+
+% Modelling multicomponent dynamics requires incorporating a free energy model between fluids, allowing for the implementation of
+% chemical potential driven mass transfer and surface tension. Typically this is done using a Cahn-Hilliard model based on a
+% square gradient free energy functional. This captures the demixing characteristics of phase separating fluids and controls interface
+% characteristics, providing surface tension and interface width characteristics. This model has been used in past investigations looking 
+% into spinodal decomposition, domain growth and coarsening.
+
+% To fully capture mesoscale dynamics, the model must also resolve the coupling between hydrodynamic flow and composition gradients. This coupling 
+% is essential for simulating phenomena such as Marangoni flows, interfacial instabilities, and anisotropic stress distributions that arise from 
+% non-uniform compositions or curvature-dependent surface tension. Moreover, the model must support anisotropic or time-dependent external fields 
+% (e.g., magnetic, electric, or shear) that influence mixing behavior. Computational frameworks that can evolve velocity, pressure, and composition 
+% fields simultaneously—while ensuring thermodynamic consistency and mechanical stability—are critical for accurately describing the emergent structures 
+% and transport properties in non-ideal soft matter systems.
+
+% Given the multiscale modeling necessary to correctly simulate the physical system, one approach suggested to tackle this problem is the multicomponent
+% Lattice Boltzmann Method. This technique bridges the length and time scales necessary in soft matter modeling through modeling the evolution of a particle
+% distribution function. Hydrodynamic parameters are recovered through calculating the moments of the particle distribution function. One of the advantages of
+% the Lattice Boltzmann Method its parallelize nature and ease of adding multiple physical phenomena. In the following sections, the implementation of the LBM
+% and alternatives to the LBM will be presented.
 

### 2025-04-05 chapters/introduction_new.tex
Changes 1. Rewritten literature review and introduction to combine both 2. Beginning to rewrite methods section 3. Finished rewrite of aim 1 - magnetic fields 4. Finished adding structure characterization

When two partially miscible fluids are mixed, they tend to phase separate into distinct domains to minimize the thermodynamic penalty associated with interfacial formation. 
To inhibit this process, stabilizers such as small-molecule surfactants, particles, or biopolymers are commonly introduced. Surfactants, for example, reduce the surface tension 
between the dispersed and continuous phases, thereby lowering the interfacial energy and promoting the stability of emulsions. A familiar example is soap, which facilitates the 
emulsification of dirt into droplets suspended in water through mechanical agitation.
Without such additives, the dispersed phase tends to coalesce in order to reduce interfacial area. The effectiveness of stabilizers can be characterized through the Pieranski 
model, $G_{ads} = \sigma A_{rm} (1 - \cos{\theta_c})^2$, where $G_{ads}$ is the free energy reduction upon particle adsorption, $\sigma$ is the surface tension between the two 
fluids, and $\theta_c$ is the contact angle of the stabilizing particle. While surfactants and biopolymers reduce interfacial tension, particle stabilizers function by adsorbing 
at the interface and effectively reducing the interfacial area between fluid domains.

Compared to surfactant-stabilized emulsions, particle-stabilized emulsions (Pickering emulsions) exhibit enhanced resistance to coalescence and coarsening, prompting renewed interest 
in their use across various applications. This resurgence is further driven by increasing environmental and toxicity concerns associated with small-molecule surfactants 
\cite{kaczerewska_environmental_2020, lechuga_acute_2016}. In contrast, particle stabilizers lower toxicity and improved biocompatibility, in addition to 
sustainable sourcing from particles based on cellulose or chitin. \cite{fujisawa_nanocellulose-stabilized_2017, tang_stimuli-responsive_2016, kalliola_carboxymethyl_2018}.
The microstructure of Pickering emulsions has been extensively studied, notably by Binks and Lumsdon in the early 2000s. Their investigations revealed that the emulsion droplet radius 
follows the relationship $R_e \propto \frac{\phi_w}{\phi_p}$, where $\phi_w$ and $\phi_p$ represent the volume fractions of water and particles, respectively \cite{binks_pickering_2001}. 
They also identified key parameters influencing microstructure, such as fluid composition and particle wettability. Neutrally wetting particles tend to stabilize nearly spherical droplets, 
while non-neutrally wetting particles can induce curvature, leading to the formation of bridged droplets, capillary aggregates, and other anisotropic structures, as illustrated in 
Figure~\ref{fig:state_diagram_particle_emulsions}.

\begin{figure}
    \centering
    \includegraphics[scale = 0.3]{figures/literature_review/state_diagram.jpg}
    \caption{Formation criteria for a particle stabilized emulsion that can form bijel. \cite{velankar_non-equilibrium_2015}
            Used with permission of Royal Society of Chemistry, from A non-equilibrium state diagram for liquid/fluid/particle 
            mixtures, Velankar, 1, 11, 2015. Permission conveyed through Copyright Clearance Center, Inc}
    \label{fig:state_diagram_particle_emulsions}
\end{figure}

As illustrated in Figure~\ref{fig:state_diagram_particle_emulsions}, the formation of bijels typically requires a near-equal volume fraction of two immiscible fluids and neutrally wetting 
particles.

\begin{figure}
    \centering
    \includegraphics[scale = 0.3]{figures/introduction/bijel_coarsening.jpg}
    \caption{Initiation and arrest of spinodal decomposition as particles adsorb onto the interface, followed by jamming once the 
    interfacial area matches the cross sectional area of the adsorbed particles\cite{stratford_colloidal_2005}. 
    Reproduced from K. Stratford et al., Science 309, 2198-2201(2005) under license number 5966820525314.}
    \label{fig:bijel_coarsen}
\end{figure}

This unique microstructure was first identified in 2005 by Stratford et al., who used a multicomponent Lattice Boltzmann method coupled with suspended particles to simulate the 
dynamics of particle-stabilized emulsions under these conditions \cite{stratford_colloidal_2005}. Their simulations revealed that, following the onset of spinodal decomposition, particles 
rapidly adsorb at the evolving fluid-fluid interface. When the available interfacial area becomes comparable to the total cross-sectional area of the particles, coarsening is arrested, 
resulting in a jammed, tortuous, co-continuous morphology characteristic of bijels (see Figure~\ref{fig:bijel_coarsen}).
This computational discovery was experimentally realized in 2007 by Herzig et al., who used a 2,6-lutidine/water system stabilized with surface-modified silica particles \cite{herzig_bicontinuous_2007}. 
This binary fluid system exhibits a lower critical solution temperature (LCST) of 34.1\textdegree C and a critical composition at approximately 28\% lutidine by weight. By preparing the mixture at this 
critical composition and heating it past the LCST, phase separation was thermally induced, a process known as Thermally Induced Phase Separation (TIPS). The system underwent coarsening until gelation 
occurred, forming a bijel. Since then, a variety of small molecule, oligomeric, and polymeric systems have been developed using similar thermally induced methods 
\cite{tavacoli_novel_2011, lee_bicontinuous_2010, bai_dynamics_2015, ching_rapid_2021}.

\begin{figure}
    \centering
    \includegraphics[scale = 5]{figures/introduction/STrIPS.jpg}
    \caption{STrIPS in action. Extrusion of the bijel casting mixture into a non-solvent bath, followed by removal of solvent from 
             the casting mixture through diffusion. \cite{haase_continuous_2015}. Reproduced with permission from Wiley-VCH Verlag GmbH 
             \& Co. KGaA from \textit{Continuous Fabrication of Hierarchical and Asymmetric Bijel Microparticles, Fibers, and Membranes by 
             Solvent Transfer-Induced Phase Separation (STRIPS)}, Haase, M. F., Stebe, K. J., 
             \& Lee, D., \textit{Advanced Materials}, 27(44), 7065-7071, 2015}
    \label{fig:strips}
\end{figure}

TIPS has been widely used in laboratory-scale studies to produce bijels in batch processes. However, industrial applications require continuous, scalable fabrication techniques capable of generating 
tailored microstructures. STrIPS has emerged as a promising solution for this need. As illustrated in Figure~\ref{fig:strips}, STrIPS involves a ternary fluid system composed of two immiscible fluids 
and a solvent. In the initial stage (Figure~\ref{fig:strips}a), a casting mixture is prepared. Phase separation is then triggered by flowing a co-solvent past the mixture to extract the solvent 
(Figure~\ref{fig:strips}b). This solvent transfer must occur within the spinodal region of the ternary phase diagram to ensure spinodal decomposition. By adjusting flow rates of both the casting 
mixture and the solvent removal stream, the resulting bijel morphology can be finely controlled. STrIPS has been successfully employed in applications ranging from battery electrode templating to drug 
delivery systems, liquid-in-liquid printing, and the creation of intrinsically polymerizable bijels for freestanding structures 
\cite{garcia_scalable_2019, thorson_bijel-templated_2019, amirfattahi_fabrication_2024, ching_rapid_2021}. The method is flexible with respect to fluid choice, with 
the only requirement being a well-characterized phase diagram that keeps the system within the spinodal regime throughout the solvent exchange process.

Vapor-induced phase separation (VIPS) offers another solvent-removal-based technique for bijel synthesis \cite{wang_scalable_2020}. In this approach, a quaternary mixture containing particles, a solvent, 
and two partially miscible liquids is prepared. Careful selection of component identities and ratios ensures that evaporation of the solvent drives the system through its critical point, inducing spinodal 
decomposition. A representative system uses water and hexanediol diacrylate, solvated by ethanol. As ethanol evaporates at room temperature, phase separation and bijel formation occur. VIPS is compatible 
with spray or blade coating techniques but is limited by the temperature dependence of surface tension, restricting solvent options to those that vaporize readily at ambient conditions.

In contrast to methods relying on spinodal decomposition, homogenization uses shear to coalesce domains of immiscible fluids, resulting in a bicontinuous structure that mimics a bijel 
\cite{huang_bicontinuous_2017, cai_bijels_2017}. This approach is particularly effective for nanoparticles under 50 nm and supports various particle shapes. Shear promotes limited coalescence 
of droplets; as coarsening proceeds, particles adsorb at the interface. Once the interfacial area is saturated with particles, jamming occurs, locking the microstructure in place. Tuning can be 
achieved by modifying particle contact angles (e.g., via surfactants) or adjusting the viscosity of the fluid phases using additives like oligomers.
Despite these advances, a persistent limitation is that bijel microstructure remains tightly coupled to the composition of the casting mixture and the kinetics of phase separation. Achieving controlled 
morphology often requires fine-tuning of fluid concentrations or external conditions, which may not be feasible for all applications \cite{haase_continuous_2015, reeves_particle-size_2015}.

Once formed, the microstructure of bijels is typically fixed and cannot be modified post-fabrication. However, in many of the proposed applications such as water filtration membranes or drug delivery 
platforms, the morphology of the material plays a critical role in determining key functional properties, including back pressure, species selectivity, and transport dynamics 
\cite{vanoli_bijels_2022, thorson_bijel-templated_2019}. The ability to dynamically tune these structural features would significantly expand the versatility and 
functionality of bijel-based systems.

Stimuli-responsive strategies present a promising avenue for achieving post-synthetic or in situ control over bijel microstructures. External triggers such as magnetic fields, pH, and temperature have 
been extensively studied in the context of Pickering emulsions to modulate droplet behavior and morphology \cite{tham_magnetophoresis_2021, cui_stabilizing_2013}. In these systems, magnetically 
responsive particles have been used to manipulate, deform, and control the coalescence of droplets, as illustrated in Figure~\ref{fig:magnetophoresis_droplet}. Magnetic 
fields offer a non-invasive and targeted method for manipulating the behavior of particles making them of particular interest. 
However the application of such dynamic control strategies to bijels remains relatively underexplored. Prior studies involving magnetic fields applied to bijels stabilized with spherical particles 
have shown limited success in modifying the microstructure \cite{kim_bijels_2010}, due to the isotropic nature of the stabilizing particles. 
% In comparison, electric fields have demonstrated a 
% greater capacity to influence bijel morphology, suggesting that the type of stimulus and particle properties play critical roles in enabling responsive behavior \cite{carmack_tuning_2018}.

\begin{figure}
    \centering
    \includegraphics[scale = 0.5]{figures/literature_review/interfacial_curvature.png}
    \caption{Quadropolar capillary interactions around prolate ellipsoidal particles caused by interfacial deformations 
             around the particle. \cite{loudet_capillary_2005} Reprinted Figure 4 with permission from
             Loudet et al, Phys. Rev. Letter., 94, 08301, 2003 Copyright 2025 by the American Physical Society.}
    \label{fig:anisotropic_particle_interface}
\end{figure}

Anisotropic particles exhibit shape-dependent interfacial behavior due to their ability to deform fluid interfaces while maintaining zero mean curvature, satisfying the Young-Laplace equation 
(Figure~\ref{fig:anisotropic_particle_interface}) \cite{loudet_capillary_2005, cheng_shape-anisotropic_2013}. These deformations generate multipolar capillary interactions, which can be harnessed 
for curvature-guided migration and directed assembly at fluid interfaces \cite{cavallaro_curvature-driven_2011, read_dimerization_2020, sharifi-mood_curvature_2015}. Simulations have shown that 
ellipsoidal particles can adopt multiple metastable orientations depending on external perturbations and interfacial constraints \cite{gunther_lattice_2013}. When used as stabilizers in bijels, 
ellipsoidal particles produce finer domains than spherical particles at equivalent volume fractions, a result of their higher surface area-to-volume ratio and more efficient interfacial coverage 
\cite{gunther_timescales_2014}.

The dynamics of ellipsoid-stabilized bijels are distinct from their spherical counterparts, displaying two characteristic timescales. Initially, particles adsorb and align with the interface, 
followed by a slower reorganization phase driven by capillary interactions between particles \cite{gunther_timescales_2014}. Experimental results confirm that the domain size in rod- and ellipsoid-stabilized 
bijels still follows the scaling law $L \propto \frac{1}{\phi_p}$, though the proportionality constant depends on particle geometry \cite{hijnen_bijels_2015, madivala_exploiting_2009, daware_emulsions_2015}.

The geometry of the stabilizing particles plays a key role in determining rheological behavior. Madivala et al. showed that Pickering emulsions stabilized with rod-like particles had enhanced stability under 
shear, with greater resistance observed as particle aspect ratio increased \cite{madivala_exploiting_2009}. This enhancement was attributed to improved interfacial coverage and capillary interactions induced by 
interface deformations, which reinforced the particle monolayer. Similarly, emulsions stabilized by graphene nanosheets exhibited higher viscosity and viscoelasticity compared to those stabilized by spherical 
particles, underscoring the importance of particle shape \cite{imperiali_simple_2014}. The elasticity of the interface has also been shown to depend on the nature of the particle stabilizer used 
\cite{sun_assembly_2013}.

The rheological properties of bijels are of fundamental importance due to their direct influence on both fabrication and application. For instance, STrIPS fabrication relies on the controlled flow of a 
casting mixture into a solvent bath, necessitating precise knowledge of the material's rheology to optimize processing parameters \cite{haase_situ_2016, haase_continuous_2015}. In applied systems such as 
cross-flow reactors, the mechanical stability of the particle monolayer is critical; failure under shear or compositional gradients can limit performance \cite{boakye-ansah_controlling_2020}. Under constant 
shear, bijels exhibit shear-thinning behavior, which at moderate shear rates is well described by the Herschel-Bulkley model \cite{macmillan_rheological_2019, wang_morphology_2023}. At higher shear rates, the 
internal structure of the bijel is disrupted, leading to a transition toward Newtonian flow behavior \cite{cai_bijels_2017, bonaccorso_shear_2020}.

\begin{figure}
    \centering
    \includegraphics[scale = 1.5]{figures/introduction/magnetophoresis_emulsion.jpeg}
    \caption{Enhanced oil recovery of oil from water using magnetically responsive emulsion stabilizers, allowing for 
             locomotion and controlled coalescence of cargo from a matrix phase using magnetic fields. \cite{tham_magnetophoresis_2021} 
             K. Tham, W. M. Ng, S. S. Leong, S. P. Yeap, S. C. Low, H. L. Lee and J. Lim. Magnetophoresis of magnetic pickering 
             emulsions under low field gradient: Macroscopic and microscopic motion. 37, 1811: Reprinted (adapted) with permission from 
             Langmuir 2021, 37, 5, 1811-1822. Copyright 2025 American Chemical Society.}
    \label{fig:magnetophoresis_droplet}
\end{figure}

Introducing magnetic responsiveness into anisotropic particles offers a non-invasive strategy for controlling their behavior at fluid interfaces. Such particles can be fabricated via surface deposition of 
magnetic materials or synthesized as core-shell structures with magnetic cores and non-magnetic shells \cite{fei_magneto-capillary_2020, nakayama_stimuli-responsive_2018}. The interplay between magnetic 
torque and capillary anchoring governs particle orientation in response to external magnetic fields. According to Bresme-Faraudo theory, a neutrally wetting ellipsoidal particle at an interface experiences 
competing forces: the magnetic field seeks to reorient the particl's magnetic dipole moment, while capillary forces resist deformation away from the interface plane 
\cite{bresme_orientational_2007, davies_interface_2014}.

\begin{figure}
    \centering
    \includegraphics[scale = 0.4]{figures/introduction/anisotropic_particles_assembly.jpg}
    \caption{Assembly of prolate particles on a flat interface at various interfacial coverages and field strengths,
             showing the self assembly into chains that ellipsoidal particles can undergo under applied magnetic fields at
             interfaces. \cite{davies_assembling_2014} Reproduced from Davies et al. Adv. Mater., 26: 6715-6719 under the 
             Creative Commons CC BY license.}
    \label{fig:anisotropic_assembly}
\end{figure}

The equilibrium and metastable orientations adopted by anisotropic particles are functions of particle aspect ratio, surface wettability, and interfacial tension 
\cite{morgan_understanding_2013, newton_influence_2014}. Studies on superellipsoidal hematite particles at oil-water interfaces demonstrate multiple stable and metastable states, where particles align 
their major or minor axes relative to the interface depending on their geometry and energy landscape. Lattice Boltzmann simulations support these observations, showing how shape influences immersion 
depth and contact angle, which in turn affect orientation stability. Magnetic fields can perturb these equilibria by exerting torque on the particles, reorienting them along the field direction. 
Experiments confirm that magnetic ellipsoids can be reconfigured at the interface, enabling controlled switching between metastable and stable configurations.
As more particles interact under a magnetic field, their mutual dipolar interactions lead to the formation of linear chains or clusters on flat interfaces \cite{davies_assembling_2014, newton_capillary_2018}. 
The final arrangement is influenced by particle concentration, field strength, and local capillary geometry. In Pickering emulsions, these effects enable magnetically triggered droplet deformation, coalescence, 
and motility, demonstrating the potential for real-time, field-controlled manipulation of interfacial structures \cite{melle_pickering_2005, tham_magnetophoresis_2021}.

Magnetically responsive Pickering emulsions offer an additional layer of tunability. When a magnetic field is applied, particles reorient and organize at the interface, significantly altering the material's 
rheological response \cite{qiao_magnetorheological_2012, melle_pickering_2005}. This field-induced ordering can lead to reversible transitions between fluid-like and gel-like states, enabling on-demand control 
over flow properties. Such behavior is particularly advantageous for applications in enhanced oil recovery, drug delivery, and soft robotics, where adaptable and reconfigurable materials are essential 
\cite{tham_magnetophoresis_2021}.

This dissertation investigates the potential of magnetically responsive ellipsoidal particles to enable stimuli-responsive control over bijel microstructure. Specifically, it examines whether magnetic fields 
applied during or after bijel formation can induce meaningful structural changes, and how these changes, in turn, influence the rheological behavior of the resulting material. The central hypothesis is that 
particle reorientation under magnetic fields alters interfacial packing, ultimately reshaping domain morphology. 
Moreover, Carmack and Millet identified that the formation of particle chains was shown to play a critical role in phase separation dynamics. These chains acted as nucleation sites, guiding the development of 
fluid domains and influencing average channel diameter and particle localization at interfaces. These findings suggest that external fields, particularly when coupled with anisotropic particles, offer a 
promising route toward responsive and reconfigurable bijel architectures.
The remainder of this dissertation is organized as follows. Chapter 32 details the physics being modeled and the simulation methods used to model these physics, including the Lattice Boltzmann approach 
and magnetic dipole modeling. Chapter 3 investigates the effects of magnetic fields applied during bijel formation, analyzing their influence on domain structure and particle orientation. Chapter 4 explores 
post-formation responsiveness, specifically examining particle unjamming and reordering phenomena. Chapter 5 assesses the rheological implications of these structural changes, with particular attention to 
yield stress and shear-thinning behavior. Finally, Chapter 6 summarizes the key findings, discusses their implications for the design of tunable porous materials, and outlines potential directions for future 
research.

% To explore this possibility, Kim et al. employed a free-energy-based Lattice Boltzmann method coupled with particles and external magnetic fields to study the responsiveness of bijels stabilized by 
% spherical particles \cite{kim_bijels_2010}. Their simulations showed that even under strong magnetic fields, the particles aligned with the field direction but did not meaningfully disrupt the 
% interfacial morphology. This result suggests that the isotropic geometry of spherical particles does not impart anisotropic stresses on the interface, thereby preserving the original structure of 
% the bijel despite external perturbations.

% Further computational work by Jansen and Harting expanded upon these findings by investigating the effects of fluid composition, surface tension, particle volume fraction, and particle contact angle 
% using a Lattice Boltzmann framework \cite{jansen_bijels_2011}. They found that while surface tension and fluid density had only minor effects on the resulting microstructure, the particle 
% volume fraction had a significant impact, with the characteristic length scale of the bijel inversely proportional to the particle concentration ($L \propto \frac{1}{\phi_p}$). Additionally, they 
% demonstrated that the formation of a bijel versus a conventional Pickering emulsion was primarily determined by the contact angle of the stabilizing particles and the relative fluid volumes, rather 
% than particle concentration alone.

% However, as will be shown in the remainder of this review, modern fabrication approaches have increasingly 
% shifted away from TIPS in favor of alternative strategies.

% Further investigations into bijel microstructure have employed topological, geometric, and image analysis techniques to quantitatively characterize their complex morphology. Topological methods
% focus on properties such as genus and channel size distribution, which reveal differences in interfacial connectivity and structural complexity \cite{chan_channel_2012}. For instance, Chan and 
% Thornton compared bicontinuous structures generated using the Cahn-Hilliard and Allen-Cahn equations, highlighting key topological distinctions between these phase-separation models. The main strength 
% of topological approaches lies in their ability to assess both the shape and the interconnectedness of the structure.

% Geometric techniques, such as curvature analysis, offer insights into how factors like particle size and quench rate influence bijel formation. Reeves et al. used Gaussian curvature measurements to 
% compare bijels stabilized with micro- versus nanoparticles, demonstrating that smaller particles promote more negative Gaussian curvature and better approximation of minimal surface structures 
% \cite{reeves_particle-size_2015,reeves_quantitative_2016}. This finding is consistent with the notion that bijel interfaces resemble minimal surfaces, which are characterized by zero mean curvature 
% and negative Gaussian curvature \cite{jinnai_interfacial_2001}. Because nanoparticles more readily conform to curved interfaces without significantly disrupting interfacial geometry, they enhance 
% stabilization in regions with saddle-like curvature \cite{reeves_quantitative_2016}.

% Image analysis techniques have also been instrumental in characterizing features such as pore size distribution, tortuosity, connectivity, and self-similarity of bijel networks 
% \cite{mcdevitt_microstructural_2019,reeves_quantitative_2016}. These methods utilize tools like region-growing and labeling algorithms (e.g., Hoshen-Kopelmann), segmentation techniques, and watershed 
% transforms to extract quantitative metrics from imaging data. For example, pore size distributions can be derived from watershed algorithms, while connectivity is assessed using segmentation-based 
% approaches.

% Recent advances suggest that anisotropic particles, particularly ellipsoidal particles, may offer enhanced responsiveness due to their shape-dependent 
% interfacial behavior. When subjected to magnetic fields, ellipsoidal particles can align directionally, inducing local anisotropy in the interfacial 
% packing arising from capillary deformation of the interface. This property has been characterized to induce self assembly of particles, 
% shown in Figure \ref{fig:anisotropic_particle_interface} 
% \cite{bresme_orientational_2007, davies_assembling_2014, newton_influence_2014}. By utilizing the magnetic field driven re-orientation and self assembly 
% of particles at interfaces, the microstructure of bijels could be influenced pre and post formation. Therefore, leveraging this behavior offers a 
% pathway to decouple microstructure control from casting mixture composition, expanding the design space for bijel derived porous materials and
% soft matter.

% Stimuli-responsive strategies offer an attractive alternative for post-synthetic or in-situ control of bijel microstructures. External fields, 
% pH, and temperature have all been explored to modify emulsion morphologies, particularly in Pickering emulsions 
% \cite{tham_magnetophoresis_2021, cui_stabilizing_2013}. In Pickering emulsions, magnetically responsive particles have enabled droplet
% manipulation, deformation, and coalescence control, shown in Figure \ref{fig:magnetophoresis_droplet}. By contrast, similar stimuli-responsive 
% behaviors in bijels remain underexplored. Prior work with spherical particles under magnetic fields has shown limited microstructural modification 
% \cite{kim_bijels_2010}, while electric fields have demonstrated greater influence \cite{carmack_tuning_2018}.

% Over the past decade, advancements in synthesis techniques have significantly expanded the ability to fabricate particles with anisotropic geometry and surface chemistry. 
% The choice of synthesis method depends on the desired particle shape. For example, ellipsoidal particles can be readily produced through the mechanical deformation of 
% % NOTE: This paragraph introduces a new concept—consider explicitly linking it to the prior paragraph (e.g., 'Beyond traditional surfactants...').
% polymer spheres, while dumbbell-shaped particles can be synthesized using microfluidic devices or emulsion templating. \cite{fei_magneto-capillary_2020} 
% Square-shaped particles, on the other hand, can be 
% generated through controlled crystallization \cite{morgan_understanding_2013}. The increasing variety of synthesis methods has reduced geometric constraints when exploring 
% potential particle stabilizers for bijels \cite{wu_recent_2016}.

% Magnetic fields offer a non-invasive and targeted method for manipulating the behavior of particles. Magnetic particles can be fabricated from
% coatings applied onto particles through deposition techniques or a core-shell particle that encapsulates a magnetic core with a non-magnetic shell. 
% \cite{fei_magneto-capillary_2020, nakayama_stimuli-responsive_2018} These effects arise due to the interplay between the magnetic torque or force 
% acting on the particles and the capillary interactions that govern their behavior at the interface. One theory developed for neutrally wetting ellipsoidal 
% particles is Bresme-Faraudo theory. \cite{bresme_orientational_2007, davies_interface_2014}
% A wide range of behaviors has been observed when magnetic fields are applied to interfacial particles. Individual particles tend to align their magnetic 
% dipole moments along the direction of the field, causing them to reorient relative to the interface. \cite{kim_bijels_2010}
% For anisotropic particles such as ellipsoids, this results in a tilt or rotation that changes their interfacial footprint and local curvature. 
% \cite{davies_assembling_2014, davies_interface_2014} The orientation of the particle is a function of the capillary interactions with the interface that 
% prefers to keep the particle flat on the interface and the magnetic field that is attempting to rotate the particle out of the interface. The magnetic force
% experienced by the particle is a function of the applied field strength, magnetic susceptibility, size of the particle, shape of the particles 
% and aspect ratio of the particle.

% The rheological properties of bijels are of fundamental importance due to their direct influence on both fabrication and application. For instance, STrIPS fabrication relies on the controlled 
% flow of a casting mixture into a solvent bath, necessitating precise knowledge of the material's rheology to optimize processing parameters \cite{haase_situ_2016, haase_continuous_2015}. In 
% applied systems such as cross-flow reactors, the mechanical stability of the particle monolayer is critical; failure under shear or compositional gradients can limit performance 
% \cite{boakye-ansah_controlling_2020}.

% Under constant shear, bijels exhibit shear-thinning behavior, which at moderate shear rates is well described by the Herschel–Bulkley model \cite{macmillan_rheological_2019, wang_morphology_2023}. 
% At higher shear rates, the internal structure of the bijel is disrupted, leading to a transition toward Newtonian flow behavior \cite{cai_bijels_2017, bonaccorso_shear_2020}. 
% Figure~\ref{fig:bijel_under_shear} illustrates this phenomenon, showing that under shear, particles initially align with the flow direction before detaching from the interface 
% \cite{bonaccorso_shear_2020}. This behavior is consistent with findings in colloidal suspensions, where hard-sphere systems undergoing shear exhibit shear banding and particle ordering along 
% the flow direction, resulting in pronounced shear thinning \cite{vermant_flow-induced_2005, brader_nonlinear_2010}.

% Bijels have also been shown to exhibit gel-like behavior, particularly when the storage modulus exceeds the loss modulus, indicating a dominant elastic response \cite{lee_making_2013, bai_dynamics_2015}. 
% Ching and Mohraz proposed that bijels behave similarly to 2D colloidal glasses percolating in 3D space, based on comparisons of their linear viscoelastic responses to those of attractive colloidal gels 
% \cite{ching_bijel_2022}. Hallmarks of colloidal glass behavior include the presence of a yield stress (the point at which irreversible deformation occurs), viscoelasticity (a combination of solid- and 
% liquid-like behavior), and a dramatic slowdown in dynamics at the glass transition point \cite{pham_yielding_2008, weeks_introduction_2017}.

% The geometry of the stabilizing particles plays a key role in determining rheological behavior. Madivala et al. showed that Pickering emulsions stabilized with rod-like particles had enhanced stability 
% under shear, with greater resistance observed as particle aspect ratio increased \cite{madivala_exploiting_2009}. This enhancement was attributed to improved interfacial coverage and capillary interactions 
% induced by interface deformations, which reinforced the particle monolayer. Similarly, emulsions stabilized by graphene nanosheets exhibited higher viscosity and viscoelasticity compared to those stabilized 
% by spherical particles, underscoring the importance of particle shape \cite{imperiali_simple_2014}. The elasticity of the interface has also been shown to depend on the nature of the particle stabilizer 
% used \cite{sun_assembly_2013}.

% Magnetically responsive Pickering emulsions offer an additional layer of tunability. When a magnetic field is applied, particles reorient and organize at the interface, significantly altering the material's 
% rheological response \cite{qiao_magnetorheological_2012, melle_pickering_2005}. This field-induced ordering can lead to reversible transitions between fluid-like and gel-like states, enabling on-demand 
% control over flow properties. Such behavior is particularly advantageous for applications in enhanced oil recovery, drug delivery, and soft robotics, where adaptable and reconfigurable materials are 
% essential \cite{tham_magnetophoresis_2021}.

% While not strictly stimuli-responsive, microstructure modifications have been achieved by applying a particle volume fraction gradient during the formation of 
% bijels using Thermally Induced Phase Separation (TIPS). \cite{french_bicontinuous_2022} In their study, French et al. allowed particles to partially sediment in the bijel casting mixture
% before initiating thermal quenching. The gradient in particle volume fraction along the height of the reaction vessel caused the jamming point of the bijel
% to vary along the gradient axis, causing a channel size gradients of up to 2.8\% per millimeter, as measured using confocal microscopy.

### 2025-04-05 chapters/paper1_5.tex
Changes 1. Rewritten literature review and introduction to combine both 2. Beginning to rewrite methods section 3. Finished rewrite of aim 1 - magnetic fields 4. Finished adding structure characterization

\section{Introduction}

Bicontinuous interfacially jammed emulsion gels (bijels) are a class of particle-stabilized emulsions composed of two interpenetrating, tortuous domains separated by a jammed layer of colloidal particles 
at the interface \cite{stratford_colloidal_2005, herzig_bicontinuous_2007, tavacoli_novel_2011}. Bijels form when neutrally wetting particles are suspended in a binary fluid mixture undergoing spinodal 
decomposition. As the domains coarsen, the particles irreversibly adsorb onto the interface and eventually jam when the available interfacial area matches the total cross-sectional area of the particles. 
This jamming arrests coarsening and locks in the bicontinuous morphology. Owing to their tunable structure, bijels have been proposed as templates for porous materials with potential applications in 
energy storage, filtration, and catalysis \cite{yabuno_preparation_2020, samdani_bicontinuous_2017, cha_bicontinuous_2019, garcia_scalable_2019, santiago_cordoba_aerobijels_2020}.

Stimuli-responsive emulsions have gained increasing attention for use in enhanced oil recovery, porous material templating, in-situ separation processes, and drug delivery systems 
\cite{tang_stimuli-responsive_2016, bago_rodriguez_capsules_2019, nakayama_stimuli-responsive_2018}. These applications exploit the ability of emulsions to undergo structural transformations in response 
to external stimuli, leading to changes in permeability, surface area, and morphology. We recently demonstrated that bijels stabilized by magnetically responsive ellipsoidal particles exhibit anisotropic 
structures when subjected to external magnetic fields \cite{karthikeyan_formation_2024}. Characterization of the domain size and tortuosity revealed significant field-induced anisotropy, indicating that 
magnetic fields can modulate the structural features of the bijel template.

While the characteristic domain size \(L\), often derived from the structure factor as \(L = \frac{2\pi}{q^*}\), is commonly used to quantify emulsion coarsening, this scalar measure alone cannot capture the 
geometrical complexity or topological features of the microstructure \cite{kendon_inertial_2001}. Prior studies have highlighted the relevance of local topology and morphology in determining the performance of 
porous materials \cite{liu_influence_2021, xiong_porosity_2024, shojaei_minimal_2022}. For example, mechanical properties and cell proliferation in bone scaffolds have been shown to depend on local topological 
characteristics \cite{xiong_porosity_2024}, and optimized gas transport in diffusion membranes has been achieved by tuning microstructural connectivity and wettability \cite{shojaei_minimal_2022}.

Within the bijel literature, Reeves et al.~investigated how particle size and quench rate affect bijel formation, showing that nanoparticles enable bijel synthesis under conditions where microparticles fail 
\cite{reeves_particle-size_2015}. In a follow-up study, they quantified interfacial curvature to reveal that smaller particles and faster quenches result in more negative Gaussian curvature, enhancing the 
hyperbolic character of the structure \cite{reeves_quantitative_2016}. While the curvature is an microstructural metric, information about the topology of the interface provides details about the 
connectivity of the surface. \cite{mendoza_evolution_2006,chan_channel_2012} Thornton and co-workers use a topological approach to characterize the channel sizes of co-continuous porous materials, 
by measuring the topological characteristics of a surface contour as a function of distance from the interface. \cite{chan_channel_2012} McDevitt et al.~further characterized bijels by computing the pore 
size distribution using a medial ball algorithm, showing that bijels exhibit narrower and more uniform pore sizes than other emulsion-derived materials due to their co-continuous morphology 
\cite{mcdevitt_microstructural_2019}. The domain anisotropy characterized in Karthikeyan and Schiller was driven through orientations of particles on the interface towards the magnetic field, causing directional
cessation of coarsening, 'locking in' the anisotropic microstructure. Using the radial distribution function, peak shifts were characterized which indicated more ordered arrangements of particles
on the interface. However the impact and degree of greater interfacial order has not been quantified, nor has it been linked to the microstructure of the bijel.

In this study, we conduct a detailed structural investigation of bijels stabilized by magnetic ellipsoidal particles. Leveraging data obtained from hybrid Lattice Boltzmann-Molecular Dynamics simulations of a 
binary fluid containing suspended magnetic ellipsoids, we examine the bond orientational order of the interfacial particle layer throughout the coarsening process and in the jammed state. Although indications 
of local hexagonal ordering emerge at the interface, the overall particle arrangement remains disordered due to the three-dimensional curvature of the interface. We further explore how the mean 
and Gaussian curvatures of the interface, averaged over the structure, respond to variations in applied magnetic field strength. Our findings indicate that magnetic fields may even enhance the 
inherent hyperbolic geometry of the bijel interface. Additionally, we track the topological development of the bijel network during coarsening by quantifying the number of time evolution of the number of channels
over time. This topological analysis enables the calculation of channel size distributions, which we find to align well with other conventional measures of domain size. Overall, our findings offer a comprehensive 
understanding of the structural characteristics of bijels formed with magnetically responsive ellipsoids and provide a foundation for design strategies in applications requiring tailored porous material 
microstructures.

\section{Results}

During spinodal decomposition of a binary liquid containing magnetic ellipsoidal particles, the formation of a bijel is governed by the combined influence of capillary and magnetic torques acting on 
the particles. The applied magnetic field exerts a torque that tends to align the dipole moments of the particles with the field direction. Concurrently, the advancing liquid-liquid interface collects 
particles and applies a capillary torque, favoring alignment of the particles major axis with the interface to minimize interfacial energy. The competition between these torques influences the 
coarsening process and results in an anisotropic domain morphology. This anisotropy manifests as directional variations in domain size, tortuosity, and jamming time relative to the orientation of 
the magnetic field \cite{karthikeyan_formation_2024}. In the present work, we extend this analysis by examining the structural organization of the interfacial particle monolayer and the evolution 
of interfacial curvature. Additionally, we characterize the topology of the bijel through measures such as the channel size distribution, which provides further insight into the underlying coarsening 
mechanisms in magnetically influenced systems.

\begin{figure}
\includegraphics[width=\textwidth]{../figures/results/paper1_5/particle_layer.png}%
\caption{Visualizations of the order parameter $\phi$ for bijels stabilized by oblate (left), spherical (middle) and prolate (right) particles 
         after $10^5$ simulation time steps. The top row shows the structure of bijels formed in the 
         absence of a magnetic field, while the bottom row shows the structure of bijels formed at $\bar{B} = 1$. 
         The direction of the magnetic field is indicated by the arrow.
\label{fig:particle_layer}}%
\end{figure}

We simulated bijel formation following the procedure outlined in Section~\ref{section:sim_setup}, using magnetic particles of varying shape—spherical (\(\alpha = 1\)), oblate (\(\alpha = 0.5\)), 
and prolate (\(\alpha = 2.0\))—at a fixed volume fraction of \(\phi_p = 0.15\). The external magnetic field strength was varied across a range of reduced field values \(\bar{B} = [0, 0.2, 0.5, 1.0]\). 
Snapshots of the final configurations are shown in Fig.~\ref{fig:microstructure_viz}, illustrating the arrangement of particles at the liquid-liquid interface for each shape and field strength. As the 
field strength increases, we observe notable changes in the interfacial particle structure. In particular, the field induces alignment of the particle symmetry axes along the field direction, and this 
orientational ordering appears to promote enhanced local packing within the interfacial monolayer. To quantify this effect, we assess whether the magnetic field leads to increased bond orientational 
order within the particle layer, thereby linking field-induced alignment to changes in monolayer structure.

\subsection{Bond orientational order within the particle layer}

To quantitatively assess the local arrangement of particles at the interface, we compute the ensemble-averaged Steinhardt bond orientational order parameters $q_2$ and $q_6$.
\cite{steinhardt_bond-orientational_1983, lechner_accurate_2008, mickel_shortcomings_2013}. These parameters characterize the local structural ordering by projecting the orientations of neighboring particles 
onto spherical harmonics of degree \(l\), and are defined as

\begin{equation}
q_l(i) = \left( \frac{4\pi}{2l+1} \sum_{m=-l}^{l} \left| \frac{1}{N(i)} \sum_{j=1}^{n(i)} Y_{lm}(\vec{r}_{ij}) \right|^2 \right)^{\frac{1}{2}} ,
\end{equation} 
%\TODO{update formula to the one actually used}

Here, \(n(i)\) denotes the number of nearest neighbors of particle \(i\), \(\vec{r}_{ij}\) is the vector connecting the centers of particles \(i\) and \(j\), and \(m\) is an integer ranging from \(-l\) 
to \(l\) that indexes the spherical harmonic components \(Y_{lm}\). Neighbor lists are typically defined using a fixed cutoff radius around each particle, identifying nearby particles as neighbors. 
We calculate the python package Freud to calculate the bond order parameters and use a Voronoi cell to determine the particle neighborhood rather than the standard distance criterion 
\cite{ramasubramani_freud_2020,mickel_shortcomings_2013}. The Voronoi-based method avoids the need for a predefined cutoff and yields more robust neighbor definitions, particularly in disordered systems. 
Bond orientational order parameters have been widely employed to study structural transitions in colloidal and ceramic systems, including crystallization, nucleation, and glass formation 
\cite{vagberg_glassiness_2011, besseling_three-dimensional_2007, schall_structural_2007, ozawa_jamming_2012}. $q_6$ is most commonly used to identify crystal structures by matching the calculated
values to reference values for specific crystal structures such as fcc or hcp. However, Kapfer et al. pointed out that only using $q_6$ can result in false positives for amorphous systems. \cite{kapfer_jammed_2012}
Mickel et al. identified that $q_2$ vanishes for ordered crystal arrangements and is finite for disordered particle arrangements. \cite{mickel_shortcomings_2013} Therefore we report both to
characterize the particle layer.

\begin{figure}
\includegraphics[width=\textwidth]{../figures/results/paper1_5/steinhardt_time.png}%
\caption{Time dependence of the Steinhardt order parameters $q_2$ and $q_4$ for different particles shapes $\alpha$ and at different magnetic field strengths $\bar{B}$. The filled bands around the lines indicate the standard deviation over three independent simulation runs.}
\label{fig:steinhardt_time}%
\end{figure}

Figure~\ref{fig:steinhardt_time} shows the time evolution of the Steinhardt order parameters \(q_2\) and \(q_6\) for all simulated magnetic field strengths and particle shapes. Both parameters begin 
to rise sharply around \(10^4\) timesteps, aligning with the onset of interfacial jamming and the deceleration of domain coarsening previously reported in \cite{karthikeyan_formation_2024}. This increase 
reflects closer packing of particles at the interface, where enhanced local density amplifies the contributions of neighboring particles to the order parameters. The growth in \(q_6\) indicates a 
rise in six-fold orientational order, as also qualitatively seen in the particle arrangements shown in Fig.~\ref{fig:particle_layer}. However, the persistence of finite \(q_2\) values suggests that the 
monolayers remain disordered. Despite visual indications of local order in the 2D interfacial projections, the three-dimensional curvature of the interface causes angular deviations between neighboring 
particle vectors \(\vec{r}_{ij}\), resulting in non-canceling contributions to the \(Y_{2m}(\vec{r}_{ij})\) terms. These results are consistent with previous findings that characterize bijels as two-dimensional 
colloidal glasses embedded within a curved, three-dimensional structure \cite{ching_bijel_2022}.

\begin{figure}
\includegraphics[width=\textwidth]{../figures/results/paper1_5/steinhardt_field.png}%
\caption{Dependence of the Steinhardt order parameter $q_2$ and $q_4$ on the magnetic field $\bar{B}$. The order parameters were computed for the final 
         bijel microstructure after $10^5$ simulation time steps. Errorbars indicate the standard deviation taken over three independent simulation runs.
\label{fig:steinhardt_field}}%
\end{figure}

Figure~\ref{fig:steinhardt_field} presents the variation of the bond orientational order parameters \(q_2\) and \(q_6\) with magnetic field strength for fully arrested bijel structures at \(10^5\) 
timesteps. The consistently finite values of \(q_2\) across all field strengths indicate that the interfacial particle arrangements lack long-range crystalline order, irrespective of whether a magnetic 
field is applied. Notably, \(q_2\) remains largely unaffected by the strength of the applied field. In contrast, \(q_6\), which reflects the degree of six-fold orientational symmetry, varies with both 
particle shape and magnetic field. For spherical particles, \(q_6\) reaches the highest values, while for ellipsoidal particles, the magnitude of \(q_6\) is generally reduced. In the case of oblate 
(disk-like) ellipsoids, \(q_6\) decreases as the magnetic field increases, whereas for prolate (rod-like) ellipsoids, \(q_6\) grows with increasing field strength, though it remains lower than that 
observed for oblate particles. These results suggest that magnetic alignment promotes six-fold ordering in the interfacial monolayer, with the extent of ordering modulated by particle aspect ratio. 
For prolate particles, the elongated shape imposes geometric constraints that suppress perfect six-fold symmetry. Meanwhile, the reduced \(q_6\) for oblate particles under strong fields may be attributed 
to out-of-plane tilting or stacking effects relative to the interface \cite{dabat_mesoscale_2018}. Overall, while the interfacial layers exhibit some degree of six-fold order in two dimensions, the 
non-zero \(q_2\) values confirm that the particle arrangement remains amorphous in three dimensions due to interfacial curvature. This motivates further exploration of how the trends in \(q_6\) with 
field strength relate to changes in the mean and Gaussian curvature of the interface.

\subsection{Curvature of the interface}

Interfacial curvature provides geometric descriptors that complement other measures of bijel morphology and are directly relevant to understanding transport properties in the resulting porous structure.
\cite{reeves_quantitative_2016} The local principal curvatures \(\kappa_1\) and \(\kappa_2\) are obtained as the inverse of the radii of curvature, \(R_1\) and \(R_2\) and are used to calculate
the area averaged mean $H$ and Gaussian $K$ curvatures.

\begin{align}
\langle H \rangle &= \frac{1}{A}\int_A \frac{\kappa_1+\kappa_2}{2} \mathrm{d}A , \\
\langle K \rangle &= \frac{1}{A}\int_A \kappa_1\kappa_2 \mathrm{d}A .
\end{align}

To compute curvature, we begin by calculating 
the order parameter field \(\phi(\vec{x}) = \rho^{b}(\vec{x}) - \rho^{r}(\vec{x})\), defined as the local density difference between the two fluid components at each lattice site. Since the presence 
of colloidal particles creates voids in the density field, we apply a particle-filling procedure similar to that used in dynamic simulations to fill uncovered grid points. This step iteratively fills 
the lattice nodes occupied by particles using local averaging from surrounding fluid nodes, thereby reconstructing a continuous order parameter field that more accurately represents the interface geometry.
From the completed \(\phi\) field, we extract the bijel interface as the \(\phi = 0\) isosurface using the marching cubes algorithm implemented in the \texttt{scikit-image} library \cite{van2014scikit}. 
We then compute the mean and Gaussian curvatures of the interface using the \texttt{PyVista} package \cite{sullivan2019pyvista}. and are used to compute the Gaussian curvature \(K = \kappa_1 \kappa_2\) and mean curvature \(H = \frac{1}{2}(\kappa_1 + \kappa_2)\) at each mesh vertex.

\begin{figure}
\includegraphics[width=\textwidth]{../figures/results/paper1_5/curvature_field.png}%
\caption{Plot of the area averaged mean $\langle H \rangle \Sigma^{-1}$ and Gaussian $\langle K \rangle \Sigma^{-2}$ curvature in the left and right 
         respectively. Each plot contains the $\langle H \rangle \Sigma^{-1}$ and $\langle K \rangle \Sigma^{-1}$ at the final timestep averaged across 
         3 runs for particles with $\alpha = 0.5, 1, 2$. We observe that the mean curvature does not demonstrate any trends, while the Gaussian curvature 
         shows a reduction as the magnetic field strength is increased for ellipsoidal particles.}
\label{fig:curvature_field}%
\end{figure}

Figure~\ref{fig:curvature-vs-B_ss} shows the dependence of the area-normalized mean and Gaussian curvature,\(\langle H \Sigma^{-1} \rangle\) and \(\langle K \Sigma^{-2} \rangle\) respectively, on the 
applied magnetic field strength. As expected for systems with equal fluid volume fractions and neutrally wetting particles, the mean curvature remains close to zero across all field strengths and shows 
no significant field dependence, reflecting the absence of a preferred direction for interfacial bending \cite{jinnai_interfacial_2001}. In contrast, the Gaussian curvature exhibits a clear trend for 
ellipsoidal particles, becoming increasingly negative with higher magnetic field strength. This indicates that the interface adopts a more pronounced saddle-like geometry as the field strengthens.
Previous work has shown that bijels formed with smaller stabilizing particles, such as nanoparticles, exhibit more negative Gaussian curvature due to their enhanced ability to conform to curved interfacial 
geometries \cite{reeves_quantitative_2016}. This behavior is attributed to their smaller cross-sectional area, which introduces minimal disruption to the hyperbolic character of the interface. Consistent 
with these findings, our zero-field results show that ellipsoidal particles produce less negative Gaussian curvature than spheres. Specifically, the oblate and prolate particles used here have approximately 
60\% and 30\% larger cross-sectional areas, respectively, compared to spheres of the same volume. However, under increasing magnetic field strength, these anisotropic particles align with the field direction, 
effectively reducing their projected area at the interface. This reorientation enables the interface to adopt more negatively curved geometries, explaining the observed decrease in 
\(\langle K \Sigma^{-2} \rangle\) with field strength. These curvature changes suggest corresponding shifts in the topology of the bijel structure, motivating a closer examination of its topological features.

\subsection{Topology of the emulsion microstructure}

Domain size is one of the most widely used metrics for characterizing coarsening in emulsions. Common approaches to determine domain size include calculating the moments or identifying peaks in the structure 
factor, which are often used to detect dynamic scaling regimes \cite{kendon_inertial_2001}. However, these definitions do not always yield an accurate representation of the true domain dimensions 
\cite{karthikeyan_formation_2024}, and domain size alone does not fully capture morphological variations in bijels under different processing conditions \cite{reeves_quantitative_2016}. The Gauss-Bonet
theorem connects the curvature of a surface to its topology through parameters such as the genus($g$) which can be thought of as the number of holes in a surface. Spheres and torii have a genus of 0 and 1 respectively. 
In this context, we also calculate the number of handles($h$) defined as channels through the volume and voids($v$) which characterize the number of disconnected cavities or loops. The relation between genus \(g\), 
number of handles \(h\), and number of voids \(v\) is thus expressed by \cite{chan_channel_2012}

\begin{equation}
g = h - v .
\end{equation}

The genus is related to the Euler-Poincar\'e characteristic \(\chi\) of the surface, i.e.,

\begin{equation}\label{eq:genus}
g = 1 - \frac{\chi}{2} .
\end{equation}

To compute the Euler-Poincaré characteristic, we used the \texttt{skimage.measure.euler\_number} function from the scikit-image library. In this implementation, the Euler characteristic is defined as the 
number of objects plus the number of holes minus the number of loops, effectively incorporating the factor of 1/2 in Eq.~\ref{eq:genus} into the returned value. As a result, the genus \(g\) was determined 
by subtracting the Euler characteristic from the total number of connected objects. The number of voids was calculated using \texttt{skimage.measure.label}, also from scikit-image, by identifying and 
excluding all regions connected to the boundary of the simulation volume. The number of handles was then obtained by applying Eq.~\ref{eq:genus}.

\begin{figure}
\includegraphics[width=\textwidth]{../figures/results/paper1_5/handles_time.png}%
\caption{Time dependence of the number of channels for different particle shapes $\alpha$ and at different magnetic field strength $\bar{B}$. 
         The bands around the lines indicate the standard deviation taken over three independent simulation results. The number of channels roughly 
         follows a power law behavior $\sim t^{-3/2}$ which suggests that it is inversely proportional to the characteristic domain size $L \sim t^{3/2}$.
\label{fig:handles_time}}%
\end{figure}

The temporal evolution of the number of handles—interpretable as the number of continuous channels through the volume—is presented in Fig.~\ref{fig:handles_time}. This measure provides insight 
into coarsening dynamics, particularly the occurrence of coalescence and pinch-off events. Across all simulations, regardless of particle shape or magnetic field strength, the number of channels 
decreases over time following a similar trend. During the coarsening phase, this decrease closely follows a power law relationship \(h \sim t^{-2/3}\), which is consistent with the known scaling 
law for the domain size \(L \sim t^{2/3}\). This inverse relationship suggests that the number of channels is proportional to the inverse of the characteristic domain size. 
Neither particle anisotropy nor magnetic field strength significantly alters this dynamic scaling behavior during the early stages of coarsening. However, once jamming begins, the reduction in the 
number of channels slows down, though it does not stop entirely. This behavior aligns with earlier findings by Harting and collaborators \cite{gunther_timescales_2014}, which identified multiple 
timescales governing bijel formation. Additionally, we observe that higher magnetic field strengths tend to delay the onset of jamming, consistent with previous observations of reduced coarsening 
rates under such conditions \cite{karthikeyan_formation_2024}.
Following jamming, the final number of channels varies with particle shape and magnetic field strength, likely reflecting the specific domain morphology present at the onset of structural arrest. 
Some regions may already be immobilized while others remain dynamic, contributing to the slow, continued reduction in channel number. Nevertheless, our results do not reveal a clear or systematic 
dependence of the final channel count on particle anisotropy or field strength.

%\TODO{need some comments on coarsening kinetics here and literature references, e.g., comparing to number of droplets over time}

To characterize topological changes in the bijel structure, we compute the channel size distribution (CSD) following the method developed by Chan and Thornton \cite{chan_channel_2012}. This approach begins 
with the construction of a signed distance field from the order parameter \(\phi\), which is reinitialized using the level set algorithm described by Sussman et al.~\cite{sussman_level_1994, chan_channel_2012}. 
The resulting distance transform is smoothed using a boxcar-averaging stencil with periodic boundary conditions to reduce numerical artifacts arising from grid discretization \cite{chan_channel_2012}. 
From the smoothed distance field, a series of isosurfaces are extracted at normalized distances \(\bar{r} = r \cdot \Sigma\), where \(\Sigma\) is the specific interfacial area. The number of handles is computed 
for each of these isodistance surfaces. A decrease in the number of handles with increasing distance from the interface reflects the pinch-off of channels, providing insight into the evolving connectivity of the 
microstructure. The channel size distribution is then obtained from the negative derivative of the handle count with respect to \(\bar{r}\), yielding a statistical measure of channel sizes as a function of 
distance from the interface.

\begin{equation}
f(r) = - \frac{d h(r)}{dr} .
\end{equation}

\begin{figure}
\includegraphics[width=\textwidth]{../figures/results/paper1_5/CSD.png}%
\caption{Channel size distribution (CSD) in bijels stabilized by oblate ($\alpha=0.5$), spherical ($\alpha=1.0$), and prolate ($\alpha=2.0$) particles. 
         The channel size distribution was obtained as the negative derivative of the number of handles in isodistance structures of the Euclidean distance 
         transform of the order parameter field. The negative values are due to numerical artifacts when calculating the number of handles as a function of 
         isodistance from the interface.}
\label{fig:CSD}%
\end{figure}

Figure~\ref{fig:CSD} presents the channel size distribution (CSD) for bijels formed with three different particle shapes under varying magnetic field strengths. Minor negative values appear in 
the distribution due to numerical artifacts associated with computing the number of handles as a function of distance from the interface. Overall, we do not observe any consistent or systematic 
trends related to particle shape or field strength. The channel sizes span a broad range, extending up to approximately \(0.6 \cdot \Sigma^{-1}\), which corresponds to about 20\% of the total system 
size. This wide distribution reflects the structural complexity of bijel morphologies, which include both broad channels and narrow regions where opposing interfaces are separated by distances 
comparable to the particle size. Although previous results indicated anisotropic domain sizes, suggesting the possibility of a bimodal channel distribution, such a feature is not evident in the 
present data. It is possible that a larger simulation domain would be required to resolve such effects more clearly, which could be explored in future work.

\begin{figure}
\centering
\includegraphics[width=.5\textwidth]{../figures/results/paper1_5/channel_size_field.png}%
\caption{Average channel size $L_c$ for different particle shapes $\alpha$ and at different magnetic field strength $\bar{B}$. The average channel size was calculated from the channel size distribution shown in Fig.~\ref{fig:CSD}. Errorbars indicate the standard deviation taken over three independent simulation runs.
\label{fig:channel_size_field}}%
\end{figure}

To relate the channel size distribution (CSD) to previous estimates of the characteristic domain size, we calculated the average channel size \(L_c\), shown in Fig.~\ref{fig:channel_size_field}. For 
systems stabilized by spherical particles, we observe relatively large error bars, representing the standard deviation across three independent simulations. This variability is likely due to the 
sensitivity of the final microstructure to the initial particle arrangement, which can influence the timing of jamming and the pathways available for coarsening—as reflected in the time evolution of 
the number of channels. In contrast, for anisotropic particles, the average channel size increases with magnetic field strength. This trend, along with the overall scale of \(L_c\), is in good agreement 
with previous domain size measurements based on structure factor moments (see Fig. 4 in Ref.~\citenum{karthikeyan_formation_2024}). Thus, identifying channel sizes through topological analysis of 
isodistance surfaces offers an alternative and complementary approach to quantifying domain size in bicontinuous emulsions. Moreover, this method reveals additional insights into the coarsening dynamics 
that are not captured by traditional geometric or structural metrics.

\section{Conclusions\label{conclusions}}

We analyzed the structural properties of bijels stabilized by magnetic ellipsoidal particles using data from Lattice Boltzmann–Molecular Dynamics simulations of binary mixtures containing oblate, 
spherical, and prolate magnetic particles across varying magnetic field strengths. Structural characterization included bond orientational order via Steinhardt parameters, interfacial mean and 
Gaussian curvature, and topological features of the emulsion morphology. In the jammed state, particle layers showed evidence of six-fold ordering but lacked crystalline symmetry in 3D due to 
interfacial curvature. We also found that anisotropic particles induce greater Gaussian curvature than spheres, while increasing magnetic field strength reduces Gaussian curvature—suggesting that 
magnetic alignment enhances the hyperbolic nature of interfaces, promoting more robust bijel formation with anisotropic particles.

To track coarsening, we quantified topological evolution through the number of handles, which reflects the count of channels in the bicontinuous structure. This number decreases over time following a 
power-law trend inversely proportional to domain size. The decay rate slows after jamming, consistent with prior findings \cite{gunther_timescales_2014, karthikeyan_formation_2024}. We further 
extracted channel size distributions (CSDs) from isodistance surfaces of the level set reinitialization \cite{chan_channel_2012}, revealing a broad range of channel sizes without systematic 
changes across magnetic field strengths. However, the average channel size from the CSD agrees with previous domain size measurements.

Our results bridge multiple aspects of bijel morphology: interfacial particle packing connects to local curvature, while global topological features relate to coarsening events such as domain 
coalescence and channel pinch-off. This study extends previous curvature analyses by Reeves et al.~\cite{reeves_quantitative_2016} and CSD measurements in Cahn-Hilliard systems by Chan and 
Thornton \cite{chan_channel_2012}, offering a more detailed view than conventional global metrics like domain size. These structural descriptors are also relevant for applications: interfacial 
particle order correlates with yield stress in emulsions \cite{besseling_three-dimensional_2007, schall_structural_2007, madivala_exploiting_2009, vagberg_glassiness_2011, kaganyuk_shear-induced_2020}, 
and interface curvature affects cell adhesion and reaction kinetics in energy systems \cite{xiong_porosity_2024, shojaei_minimal_2022}.
Understanding how these properties depend on formulation and processing conditions is key for bijel design. By analyzing independent simulations with varied initial conditions, we also captured 
statistical variation in features like channel size and its distribution. These insights lay the groundwork for systematic tuning of bijel fabrication. In particular, magnetic ellipsoidal particles 
offer promising avenues for controlled modulation of interfacial structure and domain morphology.

### 2025-04-05 chapters/paper1_new.tex
Changes 1. Rewritten literature review and introduction to combine both 2. Beginning to rewrite methods section 3. Finished rewrite of aim 1 - magnetic fields 4. Finished adding structure characterization

--- 2025-03-25 chapters/paper1_new.tex
@@
 
-This section is based on work published in the Royal Society of Chemistry's Soft Matter journal and
-work submited to the American Institude of Physics, Physics of Fluids journal. \cite{karthikeyan_formation_2024} 
-It is reproduced from Ref \cite{karthikeyan_formation_2024} with permission from the Royal Society of Chemistry and 
-reproduced from submission number \#POF25-AR-DSFD2024-03180, with the permission of AIP Publishing.
+Emulsions formed from mixtures of immiscible liquids are widely used as structural 
+templates for fabricating porous materials. These include a broad array of applications 
+such as porous polymers, ceramics, synthetic nanoparticles, and engineered tissue scaffolds 
+\cite{zhang_emulsion_2019, stubenrauch_emulsion_2018, jones_high-temperature_2009, binks_macroporous_2002, 
+abbadian_chaleshtari_nanoemulsion_2022, aldemir_dikici_basic_2020}. The technique of emulsion templating 
+provides a flexible and efficient approach to controlling key structural features of the final
+material—namely, the domain size, volume fraction, and phase composition—by manipulating the 
+formulation and processing conditions of the emulsion \cite{mudassir_fundamentals_2021}. To ensure 
+thermodynamic and mechanical stability during processing, emulsions are typically stabilized by additives. 
+Among these, particle-stabilized systems—commonly referred to as Pickering emulsions—have emerged as attractive 
+alternatives to traditional surfactant-based emulsions due to their ability to form stable interfaces without 
+relying on potentially harmful chemicals \cite{ramsden_separation_1903, zheng_pickering_2022, menner_particle-stabilized_2007}.
 
-The addition of microstructure control in bijels can be utilized to improve the performance of porous materials
-or soft matter derived from their co-continuous, tortuous microstructure. The importance of microstructure control
-allows an increase in the charge/discharge rate of batteries through reducing the material tortuosity, or improving the 
-adhesion and growth rate of bone grafts. These properties are imparted during the fabrication step of the bijel. Anisotropic
-particles adsorbed at interfaces induce shape-dependent capillary interactions that have distinct effects on the
-microstructure of emulsions, resulting in migration or rotation of particles at interfaces, in addition to the addition of
-distinct timescales of domain coarsening. \cite{loudet_capillary_2005, cavallaro_curvature-driven_2011, gunther_lattice_2013}
+A particularly intriguing subclass of Pickering emulsions is the bicontinuous interfacially jammed emulsion gel, or bijel. 
+Bijels are characterized by a tortuous co-continuous morphology where two fluid phases are separated by a particle-laden 
+interface \cite{cates_bijels_2008}. This structure forms when a binary liquid mixture containing colloidal particles is 
+rapidly quenched into a spinodal decomposition regime. As phase separation proceeds, the particles are swept up by the 
+growing interface. Eventually, particle crowding leads to jamming at the interface, effectively halting further coarsening 
+and locking the structure into a bicontinuous state. Bijels were first observed in simulation studies \cite{stratford_colloidal_2005}, 
+and later successfully fabricated in experimental systems involving water-lutidine mixtures stabilized with silica particles 
+\cite{clegg_emulsification_2007, herzig_bicontinuous_2007}. Since these foundational discoveries, a wide range of bijel 
+formulations and processing techniques have been developed to enable greater scalability and control. Notably, 
+Haase et al.~\cite{haase_continuous_2015} introduced solvent transfer-induced phase separation (STRIPS), a scalable 
+and continuous fabrication method that leverages imposed flow fields to direct droplet and jet formation. As a result 
+of these innovations, bijels have gained widespread interest as structural templates for functional materials, including 
+filtration membranes, electrochemical electrodes, and biocompatible scaffolds \cite{yabuno_preparation_2020, pang_highly_2020, 
+witt_microstructural_2016, thorson_composite_2018}.
 
-In bijels, ellipsoidal stabilizers have been demonstrates to result in additional timescales of domain coarsening 
-at long timescales owing to particle re-orientation at the interface due to interparticle capillary interactions 
-at long timescales. \cite{gunther_timescales_2014} In addition to possessing more timescales, property, bijels stabilized 
-with rod-like particles have been shown to result in smaller characteristic length scales, owing to the particles having a
-larger cross sectional area resulting in jamming occurring at larger interfacial areas. \cite{hijnen_bijels_2015}
+Beyond chemical composition, the geometry of the stabilizing particles plays a critical role in determining 
+the microstructure and stability of emulsions. When anisotropic particles—such as ellipsoids or rods—adsorb at 
+fluid interfaces, they give rise to shape-dependent capillary interactions that are markedly different from those 
+induced by spherical particles \cite{loudet_capillary_2005,madivala_exploiting_2009}. These interactions can 
+significantly enhance emulsion stability, as demonstrated by Madivala et al., and often result in distinct particle 
+arrangements at the interface \cite{madivala_self-assembly_2009}. Moreover, anisotropic particles are capable of 
+self-assembling in response to interface curvature gradients, where the curvature acts as an external field influencing 
+particle orientation and spatial distribution \cite{cavallaro_curvature-driven_2011, furst_directing_2011}. Computational 
+studies, including Monte Carlo and Lattice Boltzmann simulations, have provided insight into how such particles dynamically 
+interact with fluid interfaces \cite{bresme_orientational_2007, bresme_computer_2008, gunther_lattice_2013,gunther_timescales_2014}. 
+These simulations show that anisotropic particles introduce additional timescales during 
+emulsion formation due to their rotational behavior. Initially, they rotate to align their major axes with the interface, 
+and later reorient under capillary forces, contributing to prolonged coarsening and finer domain features. Experimental studies 
+by Hijnen et al.~\cite{hijnen_bijels_2015} confirmed that rod-shaped particles can jam more quickly than spheres at smaller 
+interfacial separations and can even tilt out of the plane due to compression during domain evolution.
 
-Magnetic response has been used in particle stabilized emulsions in the past, causing controlled emulsion failure and
-on-demand droplet coalescence for encapsulation and cargo release applications. \cite{melle_pickering_2005, zhou_magnetic_2011}
-Fields also enable self assembly through the control of interface deformation derived capillary forces.
-\cite{morgan_understanding_2013,davies_interface_2014,davies_dipolar_2015} Magnetically responsive spherical particle 
-stabilized bijels have thus far not yielded significant microstructural modifications. \cite{kim_bijels_2010} However, 
-electric fields have been shown to cause percolating cylindrical domains in electrically responsive bijels. \cite{carmack_tuning_2018}
-The electric field causes polar interactions between particles, which causes the formation of chains of particles that
-also function as nucleation sites for phase separation. \cite{carmack_tuning_2018}
+Incorporating magnetic functionality into particle stabilizers introduces the possibility of externally controlling interfacial 
+behavior using applied magnetic fields \cite{melle_pickering_2005, zhou_magnetic_2011}. Magnetic particles can align or assemble 
+in response to external fields, enabling modulation of both emulsion stability and particle organization at the interface 
+\cite{dassanayake_structure_2000, leunissen_directing_2009}. This is especially pronounced in systems containing anisotropic magnetic 
+particles, where external fields can trigger orientation transitions and alter capillary interactions \cite{morgan_understanding_2012, 
+davies_interface_2014, davies_dipolar_2015}. However, not all particle geometries respond equally. Simulations by Kim et al. revealed 
+that magnetic fields exert minimal influence on the microstructure of bijels stabilized by spherical particles \cite{kim_bijels_2010}. 
+In contrast, Carmack and Millett demonstrated that applying electric fields to bijels stabilized with dielectric particles can induce 
+significant morphological changes, including domain alignment and cylindrical channel formation via field-induced dipolar interactions 
+\cite{carmack_tuning_2018}. These results suggest that the interplay between field direction, particle geometry, and interface dynamics 
+can be exploited to engineer emulsion microstructures in situ.
 
-In this chapter, We investigate the effect of external magnetic fields on the formation of bijels stabilized by 
-anisotropic magnetic particles. The microstructure of bijels stabilized with oblate, spherical and prolate particles, 
-namely the characteristic length scale and tortuosity, will be assessed as a function of the applied magnetic field
-strength. We also characterize the underlying mechanisms governing the observed behavior.
+This chapter investigates how external magnetic fields influence the formation and microstructure of bijels stabilized by anisotropic 
+magnetic particles. Using a hybrid simulation framework combining Lattice Boltzmann and Molecular Dynamics, we model the phase separation 
+of binary fluids containing anisotropic particles with permanent dipole moments aligned along their symmetry axes. By systematically varying 
+magnetic flux density and particle aspect ratio, we assess how these parameters affect domain structure, spacing, and tortuosity. Our 
+findings reveal that, while magnetic fields do not inhibit bijel formation, they significantly impact the resulting morphology. 
+Specifically, anisotropic particles subjected to magnetic torque align during formation, leading to anisotropic domain features and 
+enhanced interfacial order. This reorientation improves packing efficiency and delays the onset of interfacial jamming. Compared to 
+field-free cases, the resulting bijels display a higher degree of structural organization. These results underscore the potential of 
+magnetic anisotropic particles as tools for designing responsive, field-tunable porous materials.
 
-\section{Results}\label{sec:results_p1}
+\section{Results}
 
-Bijels serve as emulsion templates for fabricating porous materials with applications in areas such as drug delivery, water purification, and energy 
-storage devices like battery electrodes \cite{vanoli_bijels_2022, chen_pore-scale_2022, lu_controllable_2020, garcia_scalable_2019}. The performance of
-materials in these applications are influenced by their microstructure. In the following section, the microstructure of magnetically responsive bijels
-are assessed. The bijels in our simulations have a particle volume fraction $\phi_p = 0.15$ with magnetic Bond numbers ranging from 
-$\bar{Bo} = 0, 0.2, 0.5, 1$. Three simulations per particle and per magnetic field strength are performed, allowing for investigations into the effect of
-the initial particle configuration on the obtained microstructure. While properties such as the particle contact angle, fluid ratio, surface tension and
-particle volume fraction are important, this study will focus exclusively on the effect of magnetic fields on bijels. 
-\cite{jansen_bijels_2011, hijnen_bijels_2015}
-
-\subsection{Microstructure evolution of magnetically responsive bijels}
+The transport characteristics of Bijels are closely linked to the morphology of the underlying 
+phase-separated bijel template. In this study, we investigate how domain size and tortuosity evolve in bijels stabilized by anisotropic particles, 
+with a particular focus on the influence of magnetic fields during formation.
+To this end, we simulate bijels composed of ellipsoidal magnetic particles at a fixed particle volume fraction of \(\phi_p = 0.15\), systematically 
+varying the applied magnetic flux density such that the Bond number spans the range \(0 \le \bar{B} \le 1\). Our approach isolates the effects of 
+the magnetic field on microstructure while holding other parameters constant. Prior studies have explored how changes in particle concentration and 
+interfacial tension affect bijel morphology—for example, work by Hijnen et al.~\cite{hijnen_bijels_2015} and Jansen and Harting~\cite{jansen_bijels_2011}.
 
@@
     \centering
-    \includegraphics[width=0.5\columnwidth]{figures/results/paper1/microstructure_viz.png}
-    \caption{Snapshots of emulsion gels stabilized by prolate ellipsoids after $t=5\cdot10^3$ timesteps (left) and after $10^5$ timesteps (right). The top 
-             row shows the structure forming without a magnetic field. The bottom row shows the structure forming in an applied magnetic field of reduced 
-             strength $\bar{B}=1.0$. The snapshots are colored according to the order parameter $\phi$.}
+    \includegraphics[width=\columnwidth]{../figures/results/paper1/microstructure_viz.png}
+    \caption{Snapshots of emulsion gels stabilized by prolate ellipsoids after $t=5\cdot10^3$ timesteps (left) and after $10^5$ timesteps (right). 
+             The top row shows the structure forming without a magnetic field. The bottom row shows the structure forming in an applied magnetic 
+             field of reduced strength $\bar{B}=1.0$. The snapshots are colored according to the order parameter $\phi$.}
     \label{fig:microstructure_viz}
@@
 
-Figure \ref{fig:microstructure_viz} presents snapshots of the bijel microstructure during formation and at the final timestep with and without magnetic fields.
-The figure highlights the alignment of anisotropic particles along the field direction following its application. Particle reorientation leads to apparently larger
-domain sizes in the bijels, characterized through magnetic field driven rearrangement of particles at the interface. Past work has identified how droplet coalescence
-can be induced through application of magnetic fields. \cite{melle_pickering_2005} This behavior can be quantified using the domain size, done in the following section.
+Figure~\ref{fig:microstructure_viz} presents snapshots of bijel structures at various time points, comparing systems formed with and without an applied 
+magnetic field. These images demonstrate how anisotropic particles align along the field direction, causing interfacial deformation and rearrangements 
+such as domain reorientation, coalescence, or breakup. This alignment appears to result in larger characteristic domain sizes when magnetic fields are 
+applied. A detailed, quantitative analysis of the impact of magnetic fields on bijel morphology—particularly domain size—is presented in the following sections.
+
+\subsection{Structure factor and domain size of magnetically responsive bijels}
+
+    In LB simulations of spinodal decomposition
+    \cite{kendon_3d_1999,kendon_inertial_2001}, a characteristic length
+    scale can be obtained from the structure factor
+    %
+    \begin{equation}
+    S(\vec{k},t) = \tilde{\phi}(\vec{k},t)\tilde{\phi}(-\vec{k},t) .
+    \end{equation}
+    %
+    where \(\tilde{\phi}(\vec{k},t)\) is the Fourier
+    transform of the order parameter fluctuations
+    \(\phi(\vec{x},t)-\left\langle\phi\right\rangle\). A common measure of
+    domain size uses the spherically averaged structure factor
+    %
+    \begin{equation}
+    S(k,t) = \frac{1}{n_k} \sum_{k-\frac{\Delta}{2}<k<k+\frac{\Delta}{2}} \tilde{\phi}(\vec{k},t)\tilde{\phi}(-\vec{k},t) ,
+    \end{equation}
+    %
+    where \(k=|\vec{k}|\) denotes the modulus of \(\vec{k}\)
+    and \(n_k\) is the number of lattice sites in a shell of radius \(k\)
+    and thickness \(\Delta=2\pi/L_V\). The average domain size can then be
+    defined in terms of the \(n\)-th moment of the structure factor
+    \cite{laradji_molecular_1996}
+    %
+    \begin{equation}
+        L_n(t) = 2\pi \left( \frac{\sum_k S(k,t)}{\sum_k k^n S(k,t)} \right)^{\frac{1}{n}}
+    \end{equation}
+
+The average domain size defined here may not directly match the visually estimated size seen in snapshots such as Fig.~\ref{fig:microstructure_viz}. 
+However, in the dynamic scaling regime, different domain size metrics typically differ only by a constant factor. We observed that the commonly used 
+measure \(L_1(t)\) tends to overestimate the apparent domain size. This is partly due to poor statistics in the low-\(k\) shells of the spherically 
+averaged structure factor, where the average \(|\vec{k}|\) deviates from the nominal shell radius. Additionally, simulations with periodic boundaries 
+are subject to finite-size effects. In systems with anisotropic particles, the structure factor is generally not isotropic. To account for this, we 
+also computed directional domain sizes along each Cartesian axis from the 3D structure factor using second-moment analysis \cite{jansen_bijels_2011, 
+gunther_timescales_2014}.
+
+    %
+    \begin{equation}
+    L_\beta(t)=2\pi\sqrt{\frac{\sum_{\vec{k}}S(\vec{k},t)}{\sum_{\vec{k}}k_\beta^2 S(\vec{k},t)}} .
+    \end{equation}
+    %
+    This allows us to compute a domain size parallel
+    (\(L_\parallel=L_z\)) and perpendicular (\(L_\perp=(L_x+L_y)/2\)) to the
+    direction of \(\vec{B}\) separately. The average domain size \(L_d(t)\)
+    is computed as \(L_d(t)=\sum_\beta L_\beta(t) / 3\).
+    %
+    \begin{equation}
+    L_d(t)=2\pi\sqrt{\frac{\sum_{\vec{k}}S(\vec{k},t)}{\sum_{\vec{k}}\sum_\beta k_\beta^2 S(\vec{k},t)}} .
+    \end{equation}
+    %
+
+Before computing the structure factor \(S(\vec{k}, t)\), we filled lattice sites occupied by particles with the average density of 
+their neighboring fluid nodes. This was done using an iterative method that applies Eq.~\eqref{eq:fill_particles}, starting from the 
+particle surface and proceeding layer by layer until all solid nodes were filled. The order parameter \(\phi(\vec{x}, t)\) was then 
+computed from the resulting filled density fields \(\rho_k(\vec{x}, t)\). This filling procedure is essential to eliminate spurious 
+oscillations in the structure factor at length scales comparable to the particle size.
+
+    \begin{figure*}
+        \centering
+        \includegraphics[width=\textwidth]{../figures/results/paper1/structure_factor.png}
+        \caption{Scaling plot of the dynamic structure factor $S(k,t)$ for different particle shapes $\alpha$ and at different magnetic field 
+                 strength $\bar{B}$. The structure factor is plotted at four different timesteps for each case. The good data collapse shows 
+                 that the bijel formation is driven by spinodal decomposition. The decay to the right of the peak is reasonably well described 
+                 by Porod's law $S(k)\sim k^{-4}$.}
+    \label{fig:structure_factor}
+    \end{figure*}
+
+Figure~\ref{fig:structure_factor} shows the scaling behavior of the dynamic structure factor \(S(k, t)\). While the data exhibit good overall 
+collapse, deviations from dynamic scaling appear at smaller length scales. The post-peak decay follows Porod's law, \(S(k) \sim k^{-4}\), indicating 
+scattering from relatively flat interfaces. These findings are consistent with results by Kendon et al.~\cite{kendon_3d_1999, kendon_inertial_2001} 
+for spinodal decomposition in binary fluids, supporting the view that bijel formation is initially governed by fluid demixing dynamics. Particle effects 
+become significant only at later stages, when interface coarsening reduces available surface area and triggers particle interactions. This leads to jamming, 
+which is reflected in the abrupt slowing of domain growth, as shown in Figure~\ref{fig:domain_size}.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{../figures/results/paper1/domain_size.png}
+    \caption{Time dependence of the average domain size of the bijel for different particles shapes $\alpha$ and at different magnetic field strength $\bar{B}$.
+$L_1$ denotes the domain size obtained from the first moment of the spherical average structure factor, and $L_d$ denotes the domain size obtained from the second moment of the 3D structure factor.
+The increase roughly follows a $\sim t^{2/3}$ scaling law indicative of the inertial regime of spinodal decomposition.}
+    \label{fig:domain_size}
+\end{figure*}
+
+A nonlinear fit of the domain size with form \(b(t - t_0)^a\) over the time interval \(t \in [0,\ 3 \cdot 10^5 \Delta x]\) yields scaling exponents of \(a = 0.6448\) 
+for spherical particles, \(a = 0.6083\) for oblate particles with aspect ratio \(\alpha = 0.5\), and \(a = 0.652\) for prolate ellipsoids with \(\alpha = 2\). 
+These values are consistent with the theoretical exponent \(a = 2/3\), characteristic of the inertial scaling regime, where the characteristic velocity 
+\(U = dL/dt\) scales as \(U \sim \sqrt{\sigma / (\rho L)}\), resulting in \(L \sim t^{2/3}\).
+Beyond approximately 30,000–40,000 time steps, domain growth slows down and approaches a steady-state value. The plateau values are \(L_1 \approx 200 \Delta x\) 
+for spherical particles, \(L_1 \approx 180 \Delta x\) for prolate particles, and \(L_1 \approx 170 \Delta x\) for oblate particles.
+
+In contrast, an alternative measure of domain size, \(L_d\), obtained from the second moments of the full 3D structure factor, does not exhibit the same 
+power-law growth. Its increase is significantly slower, with fitted exponents ranging from 0.12 to 0.20. Moreover, \(L_d\) saturates earlier and reaches a 
+plateau near \(L_d \approx 70 \Delta x\) for all particle shapes. Although dynamic scaling permits different length scale measures to vary by a constant 
+factor, the deviation of \(L_d\) from both viscous and inertial scaling suggests that it may not serve as a reliable characteristic length scale.
+
+Interpreting the structure factor moments as statistical moments of a probability distribution, the second moment of the 3D structure factor corresponds to 
+the ratio of the fourth and second moments of the spherically averaged structure factor—due to the \(k^2\) weighting in the volume integral. Thus, \(L_d\) 
+may be more appropriately viewed as a descriptor of the structure factor's shape (akin to kurtosis), rather than as a direct measure of domain size.
+Nonetheless, the directional second moments \(L_\beta\) provide independent domain size estimates along each Cartesian axis, making them valuable for 
+identifying anisotropy in the domain morphology.
+
+\subsection{Effect of magnetic field on bijel formation}
 
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/results/paper1/domain_size.png}
-    \caption{Time dependence of the average domain size of the bijel for different particles shapes $\alpha$ and at different magnetic 
-             field strength $\bar{B}$. $L_1$ denotes the domain size obtained from the first moment of the spherical average structure 
-             factor, and $L_d$ denotes the domain size obtained from the second moment of the 3D structure factor. The increase roughly 
-             follows a $\sim t^{2/3}$ scaling law indicative of the inertial regime of spinodal decomposition. Image courtesy of Ulf D. Schiller}
-    \label{fig:domain_size}
-\end{figure}
-
-Two methods have been identified to characterize the domain size of bijels from the structure factor. They are the first moment of the spherically averaged structure factor
-named $L_1$ and the second moment of the directional structure factor. The numerical average of the second moment derived structure factor is named $L_d$. Comparing the time
-evolution of both in Figure \ref{fig:domain_size}, the domain size increases before slowing down and finally plateauing. This indicates unhindered spinodal decomposition at
-early times, followed by a slowdown of domain coarsening caused by particle interactions before the bijel microstructure jams. Comparing the characterized domain sizes, 
-$L_d \~ 80$ compared to $L_1 \~ 150$. $L_d$ and $L_1$ also have differing time evolution, with $L_d$ beginning to plateau earlier than $L_1$. To identify which lengthscale 
-should be used to characterize the time evolution of the structure, we invoke dynamical scaling.
-
-From dynamical scaling, spinodal decomposition of binary fluids can be characterized through the inertial regime $L \~ t^{2/3}$, crossover regime $L \~ t^{n}, 2/3 < n < 1$ and 
-the inertial regime $L \~ t$. \cite{kendon_3d_1999,kendon_inertial_2001} These scaling regimes can be obtained from the Navier Stokes equation with additional surface tension 
-forces. The characterized lengthscales should conform to dynamical scaling as it is independent of the method used to characterize the lengthscale. By fitting the first phase
-of the domain size evolution for all particle shapes, the scaling exponent of domain size change characterized with $L_1$ is found to be approximately $L \~ t^{2/3}$. However
-the scaling exponent for $L_d$ is found to be $L \~ t^{0.2}$. Therefore, $L_1$ is selected to characterize the time evolution of the domain size. However the second moment of
-the domain size allows characterization of the domain size in each cartesian direction. The second moment derived domain size will be used to characterize the microstructure
-of the bijel.
-
-\subsection{Effect of magnetic field on bijel microstructure}
-
-% In LB simulations of spinodal decomposition, a characteristic length
-% scale can be obtained from the structure factor, defined in Section \ref{section:domain_size}. \cite{kendon_3d_1999,kendon_inertial_2001} 
-% It is worth noting that this definition of average domain size does not necessarily yield values that coincide with the typical
-% domain size observed visually in snapshots such as those shown in Figure~\ref{fig:microstructure_viz}. However, in a dynamic
-% scaling regime, different measures of domain size are expected to differ only by a constant ratio. We found that the commonly 
-% used measure \(L_1(t)\) tends to overestimate the observed domain size. Numerically, the calculation of the spherically 
-% averaged structure factor is subject to poor statistics in the low \(k\)-shells, where the average \(|\vec{k}|\) of the 
-% lattice sites differs from the nominal shell radius. Additionally, the measurement of \(L(t)\) in simulations with
-% periodic boundary conditions is subject to finite size effects. More importantly, in suspensions of anisotropic particles, 
-% We cannot expect that the structure factor is isotropic. Therefore, we also used the 3D structure factor to calculate a lateral domain 
-% size in each Cartesian direction from the second moments also defined in Section \ref{section:domain_size}. 
-% \cite{jansen_bijels_2011,gunther_timescales_2014} We add the additional processing calculating a parallel and perpendicular domain size
-% from the results in each cartesian direction, defining $L_{\parallel}=L_z$ and $L_{\perp} = \frac{L_x+L_y}{2}$ we plot the structure factor of the structures in
-% Figure \ref{fig:structure_factor}.
-
-\begin{figure}
-    \centering
-    \includegraphics[scale = 0.4]{figures/results/paper1/D2a-vs-B_ss.png}
-    \caption{Dependence of the average domain size on the magnetic field strength $\bar{B}$. The left plot shows the average domain size $L_1$ obtained from the spherically averaged structure factor. 
-    The right plot shows the parallel and perpendicular domain size obtained from the respective second moments of the 3D structure factor. Errorbars indicate the standard deviation taken over 
-    three independent simulation runs. For anisotropic particles, the directional domain size becomes more anisotropic with increasing field strength.}
+    \includegraphics[width=\columnwidth]{../figures/results/paper1/D2a-vs-B_ss.png}
+    \caption{Dependence of the average domain size on the magnetic field strength $\bar{B}$.
+The left plot shows the average domain size $L_1$ obtained from the spherically averaged structure factor.
+The right plot shows the parallel and perpendicular domain size obtained from the respective second moments of the 3D structure factor.
+Errorbars indicate the standard deviation taken over three independent simulation runs.
+For anisotropic particles, the directional domain size becomes more anisotropic with increasing field strength.}
     \label{fig:D2a_B}
@@
 
+To understand the microstructure changes imparted onto the bijel, we plot the domain size \(L_d\) at the final timestep in 
+Figure~\ref{fig:D2a_B}a, normalized by \(R\), the larger semi-axis of the ellipsoidal particles. Each point 
+represents the final domain size, averaged over three simulations with identical parameters. This normalization highlights that ellipsoidal particles 
+reduce the domain size in bijels, consistent with findings by Günther et al.~\cite{gunther_timescales_2014}. Ellipsoids stabilize a larger interfacial 
+area relative to their volume due to their greater cross-sectional area. Additionally, steric effects limit how densely anisotropic particles can pack, 
+a topic we discuss further below.
+
+Figure~\ref{fig:D2a_B}b displays the domain size components parallel and perpendicular to the applied magnetic field \(\vec{B}\). For prolate particles, 
+the domain size increases by up to three particle radii at the highest field while the perpendicular size remains unchanged. The 
+trend reverses for oblate particles, where the parallel domain size slightly decreases and the perpendicular size increases by about four particle radii.
+Without a magnetic field, prolate particles yield smaller domains than spherical or oblate ones. However, under field influence, they increase domain size. 
+This anisotropy results from particle alignment under the magnetic field. The difference between prolate and oblate behavior 
+stems from the dipole orientation. \(\vec{m}\) aligns with the major axis in prolates (within the larger cross-section plane) and the minor axis in oblates 
+(perpendicular to it). Thus, field-induced alignment encourages tighter packing perpendicular to \(\vec{B}\) for prolates and parallel for oblates. These 
+effects saturate at intermediate field strengths, with little change at higher values.
+
 \subsection{Tortuosity}
 
-\begin{figure}
+    \begin{figure*}
     \centering
-    \includegraphics[scale = 0.4]{figures/results/paper1/tortuosity_compare.png}
+    \includegraphics[width=\textwidth]{../figures/results/paper1/tortuosity_compare.png}
     \caption{Dependence of the tortuosity on the magnetic field strength $\bar{B}$ for different particle shapes $\alpha$.
@@
     \label{fig:tau_B}
-\end{figure}
+    \end{figure*}
 
-\begin{figure} 
-    \centering 
-    \includegraphics[scale = 0.4]{figures/results/paper1/curvature-vs-B_ss.png} 
-    \caption{Plot of the area averaged mean $\langle H \rangle \Sigma^{-1}$ and Gaussian 
-            $\langle K \rangle \Sigma^{-2}$ curvature in the left and right respectively. Each 
-            plot contains the $\langle H \rangle \Sigma^{-1}$ and $\langle K \rangle \Sigma^{-1}$ 
-            at the final timestep averaged across 3 runs for particles with $\alpha = 0.5, 1, 2$. 
-            The mean curvature remains 0 on average, while the Gaussian 
-            curvature shows a reduction as the magnetic field strength is increased for 
-            ellipsoidal particles.} 
-    \label{fig:curvature-vs-B_ss}
-\end{figure}
+The observed anisotropy in domain size suggests that magnetic fields influence bijel morphology at the microscale. To determine whether these structural 
+changes impact macroscopic transport properties, we also analyzed the tortuosity of the bijels. While geometric, 
+diffusional, and hydraulic definitions of the tortuosity exist, we use the diffusional tortuosity, defined as \(\tau = \epsilon D / D_{\text{eff}}\), 
+where \(D_{\text{eff}}\) is the effective diffusivity and \(D\) is the intrinsic molecular diffusivity. \cite{dasilva_tortuosity_2022} Porous structures were 
+extracted by binarizing the final order parameter field using a zero threshold, isolating the largest connected (percolating) domain. We computed tortuosity 
+along each Cartesian direction using the \texttt{taufactor} package \cite{cooper_taufactor_2016}, which compares steady-state diffusion through the porous 
+structure to bulk diffusion in an equivalent volume. Periodic boundary conditions were applied via the \texttt{PeriodicSolver}.
 
-\subsection{Curvature}
+Figure~\ref{fig:tau_B} presents tortuosity as a function of magnetic flux density for the three particle aspect ratios. In the absence of a field, all 
+shapes yield a similar tortuosity around \(\tau \approx 1.5\), slightly exceeding the Bruggeman prediction \(\tau = \epsilon^{-0.5} = 1.41\) for equal 
+phase volume fractions \(\epsilon = 0.5\) \cite{bruggeman_berechnung_1935, tjaden_origin_2016}. These values align with simulations of gyroid structures 
+by Luo et al., who reported tortuosities between 1.48 and 1.73 \cite{luo_macroscopic_2020}.
 
-Beyond the length scale, curvature analysis offers insights into the
-topological landscape of the bijel, facilitating further
-microstructure optimization for various applications.
-\cite{reeves_quantitative_2016} We plot the area averaged mean and
-gaussian curvature \(H\Sigma^{-1}\) and \(K\Sigma^{-2}\) for bijels
-stabilized with oblate, spherical and prolate ellipsoids at the final timestep in Figure
-\ref{fig:curvature-vs-B_ss}.
+Under an applied magnetic field, tortuosity becomes directionally dependent for bijels stabilized by anisotropic particles (\(\alpha \neq 1\)). For oblate 
+particles (\(\alpha = 0.5\)), tortuosity increases in the field-parallel direction, while remaining near \(\tau \approx 1.5\) perpendicular to the field. 
+In contrast, prolate particles (\(\alpha = 2\)) exhibit the opposite trend: tortuosity rises in the perpendicular direction and slightly decreases along 
+the field. These trends align with the anisotropic domain sizes and particle alignment under the field. For prolates, alignment of the major axis with the 
+magnetic moment results in larger domains and reduced tortuosity along the field direction.
 
-\begin{figure} 
-    \centering 
-    \includegraphics[scale = 0.4]{figures/results/paper1/curvature-vs-B_ss.png} 
-    \caption{Plot of the area averaged mean $\langle H \rangle \Sigma^{-1}$ and Gaussian 
-            $\langle K \rangle \Sigma^{-2}$ curvature in the left and right respectively. Each 
-            plot contains the $\langle H \rangle \Sigma^{-1}$ and $\langle K \rangle \Sigma^{-1}$ 
-            at the final timestep averaged across 3 runs for particles with $\alpha = 0.5, 1, 2$. 
-            The mean curvature remains 0 on average, while the Gaussian 
-            curvature shows a reduction as the magnetic field strength is increased for 
-            ellipsoidal particles.} 
-    \label{fig:curvature-vs-B_ss}
-\end{figure}
-
-Error bars are represented by the standard
-deviation of the three simulations per parameter set performed. The area
-averaged mean curvature shows little dependence on the applied field
-strength with values around 0 and within error of one another. A value
-near or at 0 is expected as the fluid volume fraction is equal and the
-particles are neutrally wetting, implying the interface should not have
-a preferred direction of curvature. \cite{jinnai_interfacial_2001} For
-ellipsoidal particles, the gaussian curvature becomes more negative as
-larger field strengths are applied. We also see that the gaussian
-curvature becomes more positive as the interfacial area of the particle
-increases. The trend of these results are inverse to the interfacial
-area of each particle, \(A_{rm}\). This is expected behavior and is in
-agreement with experiments that have investigated the effect of particle
-size on the curvature of bijels. \cite{reeves_quantitative_2016}
-
-To explain the reduction in $\langle K\Sigma^{-2} \rangle$ as a function of the applied field strength, two mechanisms are proposed. The first is that 
-the particle alignment to the magnetic field during coarsening changes the topology of the surface, which upon jamming of ellipsoidal particles is locked in. 
-The other proposed mechanism is that the time evolution of spinodal decomposition remains unaffected, but that the interface conforms to the magnetic field 
-driven arrangement of particles upon jamming. While we cannot apply the Gauss Bonnet theorem to characterize the results, we can still relate the coarsening 
-behavior of the bijel through its change in genus to the curvature. The time evolution of the genus serves as a topological technique to characterize the 
-coarsening of the bijel, which alongside the $\langle K\Sigma^{-2} \rangle$, allows us to identify deviations from the coarsening behavior of bijels 
-stabilized with spherical particles, and with magnetic fields. We calculate the genus by extracting the isosurface of the filled order parameter, where 
-$\phi = 0$. It is then meshed using the marching cubes algorithm implemented in scikit-image with a cube size of 1. \cite{van2014scikit} From the vertices(v) 
-and faces(f) generated from the marching cubes algorithm, we calculate the number of edges(e). The Euler Poincare characteristic, $\chi = n + f - e$. The genus is 
-then obtained from the Euler Poincare parameter as $g = 1 - \chi/2$.
-
-\begin{figure} 
-    \centering 
-    \includegraphics[scale = 0.4]{figures/results/paper1/genus_curvature_vs_coverage.png} 
-    \caption{Plots of Gaussian $\langle K \rangle \Sigma^{-2}$ curvature over time averaged across 3 runs. 
-    From left to right, We have particles with $\alpha = 0.5, 1, 2$. We observe that the initial stages of 
-    evolution are unaffected by the applied magnetic field. However, after about 10000 timsteps, We see a 
-    magnetic field dependence on the evolution of the Gaussian curvature. The preservation of this divergence 
-    occurs when ellipsoidal particles are used but not spherical particles.} 
-    \label{fig:curvature_vs_coverage}
-\end{figure}
-
-The time evolution of $g \Sigma^{-1}$ of bijels stabilized with spherical particles is unaffected by the application of a magnetic field. However, a 
-slight decrease in the genus as a function of the applied field is observed for bijels stabilized with ellipsoidal particles. This suggests that the 
-evolution of the surface corresponding to the interface is changed by the adsorption and orientation of magnetically responsive ellipsoidal particle. 
-We see effects of this change in $\langle G \rangle \Sigma^{-2}$ where we see the evolution of the curvature being delayed, indicated as a rightward 
-shift of the plots as a function of the applied field.
-
-Despite all our curvature calculations being normalized with their surface area to volume ratio, we still see curvature differences as a function of the applied 
-magnetic field. Experiments have identified that curvature changes can occur due to the formation of monogels, which are particle networks formed from bijels that 
-can withstand the remixing of their constituent liquids. \cite{sanz_colloidal_2009, lee_making_2013} This process cannot occur in our simulations as we am utilizing 
-electrically neutral particles that only interact through contact forces. Therefore, the change in curvature arises from microstructure changes driven by particle 
-alignment to the magnetic field direction. These results provide support for the mechanism of control being due to particle alignment to the magnetic field during 
-coarsening changes the topology of the surface, which upon jamming of ellipsoidal particles is locked in. As our particles only interact through contact forces, 
-the only mechanism present that can change the topology of the interface would be particle interactions upon contact with each other. Particle interactions are 
-controlled through the orientation of particles and the local ordering of particles on the interface. Seeing that there are differences in the gaussian curvature of the bijel,
-the domain anisotropy characterized in Figure \ref{fig:D2a_B} may be able to be characterized as changes in the topology of the surface. Chan and Thornton introduced a 
-topological technique to characterize the connectivity of surface as a function of a distance from the interface to calculate the channel size distribution. 
-\cite{chan_channel_2012} We can use the channel size distribution to investigate how the connectivity of the microstructure and thus the 
-channel size is affected as a function of the applied magnetic field.
-
-\begin{figure} 
-        \centering 
-        \includegraphics[scale = 0.4]{figures/results/paper1/CSD_ss.png} 
-        \caption{Plots of the channel size distribution for bijels stabilized by oblate, spherical and oblate particles at the final timestep plotted
-                 against the distance from the interface normalized with the characteristic length scale. The channel sizes obtained are averaged over 
-                 three runs. We see that the peak locations are shifted to larger and smaller positions for bijels stabilized with ellipsoidal particles
-                 upon field application} 
-        \label{fig:CSD_B_ss}
-    \end{figure}
-
-While run to run variation is observed, the combined data of the channel size distribution shown in Figure \ref{fig:CSD_B_ss} shows some differences 
-in the channel size distribution in each bijel stabilized with ellipsoidal particles. It was expected that the domain anisotropy obtained using second moment of the 
-structure factor would manifest as two peaks in the channel size distribution. \cite{karthikeyan_formation_2024} This behavior is observed in the channel size 
-distribution for bijels stabilized with ellipsoidal particles with $\bar{B} = 1$, but is more difficult to see when smaller magnetic fields are applied. 
-These differences arise from the particle ordering and local distribution changes observed.
+Notably, the most pronounced tortuosity changes occur at intermediate field strength (\(\bar{B} = 0.5\)), suggesting a nonlinear interplay between magnetic 
+and interfacial forces. This highlights that field-induced morphological evolution is more complex than a simple monotonic response, prompting a deeper 
+investigation into the bijels microstructural changes.
 
@@
 
-To shed light on the mechanisms involved in the coarsening dynamics,
-we now turn to the kinetics of bijel formation in more detail. The
-coarsening dynamics can be characterized by a coarsening speed. Here,
-we use the finite difference of the directional domain size to
-calculate the components of the coarsening velocity
+To better understand the mechanisms driving coarsening, we now examine the kinetics of bijel formation in greater detail. Coarsening behavior 
+is quantified through a coarsening velocity, which we compute by taking finite differences of the directional domain size to obtain its individual components
     %
@@
 
-\begin{figure}
-\includegraphics[width=\textwidth]{figures/results/paper1/coarsening_vel.png}
-\caption{Time-dependence of the coarsening velocity $u_L$ for different particles shapes $\alpha$  
-and at different magnetic field strength $\bar{B}$. The different components of the coarsening velocity 
-show that the jamming time is different in the direction parallel and perpendicular to the magnetic field. Image provided
-courtesy of Ulf D. Schiller.}
+    \begin{figure*}
+    \includegraphics[width=\textwidth]{../figures/results/paper1/coarsening_vel.png}
+    \caption{Time-dependence of the coarsening velocity $u_L$ for different particles shapes $\alpha$  and at different magnetic 
+    field strength $\bar{B}$. The different components of the coarsening velocity show that the jamming time is different in the 
+    direction parallel and perpendicular to the magnetic field.}
     \label{fig:coarsening_velocity}
-\end{figure}
+    \end{figure*}
 
-% Figure \ref{fig:coarsening_velocity} shows the coarsening speed in the directions parallel and perpendicular to the applied magnetic field. 
-% The data confirms that for spherical particles, domain coarsening remains isotropic. We observe a higher coarsening speed initially which slows 
-% at later times when the particles begin to jam. This indicates that the
-% coarsening is subject to different time scales, as reported previously
-% by Harting and co-workers \cite{gunther_timescales_2014}. Reeves et
-% al.~\cite{reeves_particle-size_2015} have pointed out that bijel
-% formation hinges on the jamming time in relation to the disruption time, i.e., the time scale at which domain pinch-off events can cause bijel break-up through 
-% depercolation. In our simulations, however, we have not observed disruption of bijel formation; stable bijels form for all parameters consistent with simulations 
-% by Stratford et
-% al.~\cite{stratford_colloidal_2005} and Jansen et al.~\cite{jansen_bijels_2011}.
+Figure~\ref{fig:coarsening_velocity} presents the coarsening speed along directions parallel and perpendicular to the applied magnetic field. For 
+spherical particles, coarsening remains isotropic, as expected. The velocity is initially high but slows over time as particles begin to jam. 
+Reeves et al.~\cite{reeves_particle-size_2015} emphasized the importance of the jamming time relative to the disruption time, where domain pinch-off can 
+lead to depercolation and structural failure. However, in our simulations, we observe no such disruption—bijels remain stable across all conditions, in 
+agreement with prior studies by Stratford et al.~\cite{stratford_colloidal_2005} and Jansen et al.~\cite{jansen_bijels_2011}.
 
-% For ellipsoidal particles, our data clearly shows that an\-isotropic
-% domain coarsening arises in magnetic fields.  For oblate particles
-% (\(\alpha=0.5\)), the coarsening speed in the direction perpendicular
-% to the field increases with increasing magnetic field strength.
-% Jamming in this direction appears to be delayed compared with the
-% direction parallel to the field. The coarsening speed in the parallel
-% direction remains comparable to the case without an applied magnetic
-% field. This anisotropic behavior of the coarsening speed reverses for
-% prolate particles, where the coarsening speed in the direction parallel to the field increases with increasing field strength, and jamming in this direction
-% is delayed compared with the perpendicular direction.
-In addition, we observe a shoulder (around \(10^4\Delta t\)) where the coarsening speed decays more slowly before jamming sets in.
-These results suggest that the coarsening near the jamming time is affected by a mechanism that depends on the applied magnetic field and causes the anisotropic
-% behavior. This mechanisms involves the re-orientation of anisotropic
-% particles and their alignment relative to the direction of the
-% magnetic field. To confirm this hypothesis, we analyze the
-% orientational order of the particles and their alignment relative to
-% the magnetic field and the interface, respectively.
+In contrast, simulations with ellipsoidal particles show clear evidence of anisotropic coarsening in the presence of a magnetic field. For oblate 
+particles (\(\alpha = 0.5\)), the coarsening speed increases in the direction perpendicular to the field as its strength grows, while the parallel 
+direction remains largely unaffected. This suggests delayed jamming perpendicular to the field. Prolate particles show the opposite trend with coarsening 
+accelerating along the field direction and jamming delayed relative to the perpendicular direction. Notably, we also observe a shoulder in the coarsening 
+curve near \(10^4 \Delta t\), where the decay in speed slows before jamming occurs.
+
+These findings point to a magnetic field-dependent mechanism influencing coarsening near the jamming threshold. Specifically, the anisotropy appears 
+linked to the reorientation and alignment of anisotropic particles with respect to the magnetic field. To test this hypothesis, we further examine the 
+orientational order of particles and their alignment relative to both the field direction and the fluid interface.
 
@@
     \centering
-    \includegraphics[width=0.5\columnwidth]{figures/results/paper1/particle_packing_viz.png}
+    \includegraphics[width=\columnwidth]{../figures/results/paper1/particle_packing_viz.png}
     \caption{Snapshots illustrating the particle packing at the interface for different particle shapes $\alpha$ with (left)
-            and without (right) applied magnetic field $\bar{B}$. The right column shows the alignment of the symmetry axis of 
-            the oblate (top row) and prolate (bottom row) particles in the direction of the magnetic field indicated by arrows.}
+     and without (right) applied magnetic field $\bar{B}$. The right column shows the alignment of the symmetry axis of the oblate (top row) and prolate (bottom row) 
+     particles in the direction of the magnetic field indicated by arrows.}
     \label{fig:packing_viz}
@@
 
+The dominant influence of the magnetic field is the torque it applies to the particles magnetic dipoles, causing them to rotate and align with the 
+field direction. This field-induced alignment is clearly visible in the simulation snapshots in Figure~\ref{fig:packing_viz}. In the absence of a 
+magnetic field (\(\bar{B} = 0\)), the particles remain randomly oriented at the interface. When a magnetic field is applied (\(\bar{B} = 1\)), the 
+dipoles exhibit pronounced orientational order aligned with the field.
+
     \begin{figure}
     \centering
-    \includegraphics[scale = 0.4]{figures/results/paper1/S-vs-t.png}
-    \caption{Time-dependence of the nematic order parameter $S$ of oblate ($\alpha=0.5$) and prolate ($\alpha=2$) 
-            particles at different field strength $\bar{B}$. Errorbars indicate the standard deviation taken over 
-            three independent simulation runs. Nematic order generally increases with applied field strength for all particle geometries. 
+    \includegraphics[width=\columnwidth]{../figures/results/paper1/S-vs-t.png}
+    \caption{Time-dependence of the nematic order parameter $S$ of oblate ($\alpha=0.5$) and prolate ($\alpha=2$) particles at different field strength $\bar{B}$.
+Errorbars indicate the standard deviation taken over three independent simulation runs.
+Nematic order generally increases with applied field strength for all particle geometries.
 The increase slows down (for prolate particles) or reverses (for oblate particles) around $10^4$ timesteps.}
@@
 
+    To measure the particle alignment quantitatively, we computed the
+    nematic order tensor \cite{veerman_phase_1992}
+    %
+    \begin{equation}
+    \tens{Q} = \frac{1}{n_p} \sum_i \left( \frac{3}{2} \hat{\vec{o}}_i \otimes \hat{\vec{o}}_i -\frac{1}{2}\mathsf{1} \right) ,
+    \end{equation}
+    %
+    where \(\hat{\vec{o}}_i\) is the orientation of the
+    \(i\)-th particles and \(n_p\) is the number of particles in the system.
+    The largest eigenvalue of \(\tens{Q}\) yields the nematic order
+    parameter
+    %
+    \begin{equation}
+    S = \left\langle \frac{3}{2}\cos^2 (\theta) - \frac{1}{2} \right\rangle ,
+    \end{equation}
+    %
+    where
+    \(\theta=\arccos(\hat{\vec{o}}_i\cdot\hat{\vec{n}})\) is the angle
+    between the particle orientation and the nematic director
+    \(\hat{\vec{n}}\).
+
+Figure~\ref{fig:nematic_time} shows how the nematic order parameter \(S\) evolves over time for different particle aspect ratios \(\alpha\) and magnetic 
+field strengths \(\bar{B}\). The onset of orientational order is nearly immediate and increases with field strength. For \(\bar{B} \ge 0.5\), \(S\) 
+approaches saturation at around 1.0 by the end of the simulation. In the case of prolate particles (\(\alpha = 2.0\)), a shoulder appears around 
+\(10^4 \Delta t\), forming a temporary plateau. This behavior coincides with the slower decline in coarsening speed seen in 
+Figure~\ref{fig:coarsening_velocity}. For oblate particles, the effect is even more pronounced—\(S\) exhibits an intermittent drop before rising again.
+
+These fluctuations in orientational order align with the delayed jamming observed in directions perpendicular (oblate) and parallel (prolate) to the 
+magnetic field. The underlying mechanism appears to be the early alignment of particles with the field, which reduces steric hindrance at the interface 
+and allows further coarsening. However, as the interface evolves, reorientation can induce capillary torques that compete with the magnetic torque, 
+temporarily disrupting the nematic alignment. This competition explains the observed dips and plateaus in \(S\), particularly at lower field strength 
+(\(\bar{B} = 0.2\)), where the decay is most pronounced.
+
+To further corroborate this mechanism, we quantify the orientational, order of the interfaces. We computed the interfacial orientation tensor
+    %
+    \begin{equation}
+    \tens{Q}_{\text{int}} = \frac{1}{\langle \mathrm{tr}(\tens{A}) \rangle} \left\langle \tens{A} - \frac{1}{3} \mathrm{tr}(\tens{A}) \mathsf{1} \right\rangle ,
+    \end{equation}
+    %
+where the local tensor field \(\tens{A}\) is defined by
+    %
+    \begin{equation}
+    \tens{A} = \nabla \phi \otimes \nabla \phi .
+    \end{equation}
+    %
+The largest eigenvalue of \(\tens{Q}\) is taken as the interface nematic order parameter $S_{\text{int}}$.
+
+    \begin{figure}
+    \includegraphics[width=\columnwidth]{../figures/results/paper1/interface_nematic.png}
+    \caption{Time-dependence of the interface nematic order for oblate ($\alpha=0.5$) and prolate ($\alpha=2$) particles at different magnetic field strength $\bar{B}$.
+The interface alignment tends to increase with increasing field strength.
+The rate of increase becomes larger around $10^4$ timesteps, indicating the alignment of the interfaces due to capillary interactions with the particles.}
+    \label{fig:interface_nematic}
+    \end{figure}
+
+Figure~\ref{fig:interface_nematic} presents the evolution of the interface nematic order parameter \(S_{\text{int}}\). Interface alignment increases over 
+time, with higher magnetic field strengths \(\bar{B}\) accelerating this process. In all cases, \(S_{\text{int}}\) remains below 0.5 by the end of the 
+simulation, indicating that the interface retains its tortuous, bicontinuous morphology despite the field. This confirms that particle reorientation promotes 
+partial alignment without disrupting the overall bijel structure.
+
+As particles rotate, they experience a capillary torque from the interface due to surface tension and contact angle constraints. If the magnetic torque 
+surpasses this, particles may overcome the capillary barrier and tilt out of the interface. For prolate particles (\(\alpha = 2\)) at flat interfaces, 
+Davies et al. showed that a transition from flat to tilted orientation occurs at a critical field strength of \(\bar{B} \approx 0.2\) 
+\cite{bresme_orientational_2007,davies_interface_2014,newton_influence_2014}. In bijels, however, the interfaces are curved and mobile. We propose that 
+instead of tilting out, particles “drag” the interface as they rotate, guiding alignment of the surrounding liquid domains. For anisotropic particles, 
+we expect this alignment to occur perpendicular to the symmetry axis in oblates and parallel in prolates. The previously discussed domain size and 
+tortuosity data support this assumption.
+
+To verify that particles maintain their preferred orientation relative to the interface, we analyzed the angle between each particles symmetry axis and 
+the local interface normal. We generated a mesh of the interface using the marching cubes algorithm and, for each particle, identified the nearest mesh vertex 
+(excluding those beyond the length of the particle’s long axis). We then calculated the angle \(\psi\) between the particle orientation vector 
+\(\hat{\vec{o}}_i\) and the local surface normal. The time evolution of the average angle \(\psi\) is shown in Figure~\ref{fig:psi_time}.
+
 \begin{figure}
     \centering
-    \includegraphics[scale = 0.4]{figures/results/paper1/psi-vs-t.png}
-    \caption{Time-dependence of the average angle $\psi$ between the particle axis and the 
-            interface normal for oblate ($\alpha=0.5$) and prolate ($\alpha=2$) particles at different 
-            magnetic field strength $\bar{B}$. Errorbars indicate the standard deviation taken over three 
-            independent simulation runs. The angle between between the particles and the interface normal generally 
-            approaches the energetically preferred value ($0^\circ$ for oblate particls, $90^\circ$ for prolate particles).
-            The average angle changes most rapidly around $10^4$ timesteps.}
+    \includegraphics[width=\columnwidth]{../figures/results/paper1/psi-vs-t.png}
+    \caption{Time-dependence of the average angle $\psi$ between the particle axis and the interface normal for oblate ($\alpha=0.5$) and 
+             prolate ($\alpha=2$) particles at different magnetic field strength $\bar{B}$. Errorbars indicate the standard deviation taken over 
+             three independent simulation runs. The angle between between the particles and the interface normal generally approaches the energetically 
+             preferred value ($0^\circ$ for oblate particls, $90^\circ$ for prolate particles). The average angle changes most rapidly around $10^4$ timesteps.}
 \label{fig:psi_time}
@@
 
-Hence the prolate particles remain mostly aligned with the interface
-even in the stronger applied magnetic fields. We plot the interface angle of bijels
-stabilized by ellipsoidal particles at the final timestep to demonstrate the differences
-that the application of magnetic fields have on the particle monolayer.
+For both types of anisotropic particles, the initial angle between the particle dipole and the interface normal is approximately 
+\(\psi \approx 60^\circ\). As the spinodal interface propagates through the system, particles attach and begin aligning due to capillary torque. 
+In oblate particles, this results in alignment of the dipole axis with the interface normal, reflected by a decrease in \(\psi\) toward zero. In 
+contrast, prolate particles preferentially align their dipole axis parallel to the interface, causing \(\psi\) to increase toward \(90^\circ\).
 
-\begin{figure}
-    \centering
-    \includegraphics[scale = 0.4]{figures/results/paper1/psi_concat.png}
-    \caption{Visualizations of the particle monolayer at the last timestep shaded with the interface angle of each particle in red. The top and bottom
-             rows correspond to snapshots of bijels with no field and a field strength of $\bar{B} = 1$ applied. We see that the oblate particles flip
-             out of the interface into a non energetically favored position while the bijels stabilized with prolate particles tilt out of the interface
-             but are less likely to flip out.}
-    \label{fig:psi_viz_ss}
-\end{figure}
+The most significant changes in \(\psi\) occur around \(10^4 \Delta t\), coinciding with notable features in coarsening speed and particle nematic 
+order discussed earlier. These trends support the proposed mechanism of particle reorientation under magnetic fields and the associated local 
+alignment of the interface. As jamming begins and the available interfacial area decreases, some particles are pushed out of their preferred 
+alignment. This leads to an increase in \(\psi\) for oblate particles and a decrease for prolate particles.
 
-Hence the prolate particles remain mostly aligned with the interface
-even in the stronger applied magnetic fields. We plot the interface angle of bijels
-stabilized by ellipsoidal particles at the final timestep to demonstrate the differences
-that the application of magnetic fields have on the particle monolayer.
-
-\begin{figure}
-        \centering
-        \includegraphics[scale = 0.4]{figures/results/paper1/psi_concat.png}
-        \caption{Visualizations of the particle monolayer at the last timestep shaded with the interface angle of each particle in red. The top and bottom
-                 rows correspond to snapshots of bijels with no field and a field strength of $\bar{B} = 1$ applied. We see that the oblate particles flip
-                 out of the interface into a non energetically favored position while the bijels stabilized with prolate particles tilt out of the interface
-                 but are less likely to flip out.}
-        \label{fig:psi_viz_ss}
-\end{figure}
-
-From Figure \ref{fig:psi_viz_ss} We can see the differences in the particle alignment to the interface characerizing the differences in $\psi$ observed. Oblate
-particles can be seen to tilt out of the interface more readily than prolate particles at the same magnetic field strength. Due to the strong surface tension
-between the fluids, the particles are strongly adsorbed onto the interface. We also see that the arrangement of particles on the interface is modified through the
-application of the magnetic field for both particle morphologies. We can obtain quantitative metrics regarding this ordering using the Steinhardt 2 and 6 fold
-order parameters, $\langle Q2 \rangle$ and $\langle Q6 \rangle$.
-
-This parameter has been used extensively to characterize nucleation rates, glass transitions of colloidal systems and crystal structure transitions of ceramics 
-and colloidal crystals. \cite{vagberg_glassiness_2011, besseling_three-dimensional_2007, schall_structural_2007} The original implementation has been further 
-improved through the use an averaged bond order parameter, adding the next nearest neighbor to the neighbor list or utilizing voronoi cells to define the 
-neighbor list instead of a cutoff distance. The latter provides a more robust definition of the neighbor list, without needing to assume the structure of 
-the particles and is implemented in the package Freud. \cite{ramasubramani_freud_2020} This method has been used to characterize the jamming of discs at 
-interfaces. \cite{ozawa_jamming_2012}
-
-We select $\langle Q6 \rangle$ and $\langle Q2 \rangle$ as the bond order parameters to calculate as We am interested in identifying the point when ordering 
-of the material changes. Kapfer et al. demonstrated that only using $\langle Q6 \rangle$ to identify the ordering of particles in the system can result in 
-false positives when the particles have icosahedral or amorphous structure. \cite{kapfer_jammed_2012} Mickel et al. showed how increasing deviations from 
-$\langle Q2 \rangle = 0$ can be used to characterize increasing disorder in a system. \cite{mickel_shortcomings_2013} By plotting $\langle Q6 \rangle$ and 
-$\langle Q2 \rangle$, we will be able to identify changes in the local ordering of the system even if We cannot directly assess the local structure quantitatively.
-
-\begin{figure} 
-    \centering 
-    \includegraphics[width=\columnwidth]{figures/results/paper1/steinhardt_vs_coverage.png} 
-    \caption{Time dependence of the mean two and six fold symmetry parameter, $\langle Q2 \rangle$ and $\langle Q6 \rangle$ 
-    for bijels stabilized with oblate(left), spherical(middle) and prolate(right) particles. We use $\langle Q2 \rangle$ as an
-    indicator of global particle translational order while $\langle Q6 \rangle$ is an indicator of local order.} 
-    \label{fig:steinhardt_coverage} 
-\end{figure}
-
-From Figure \ref{fig:steinhardt_coverage}, we see an increase in disorder in all the bijel systems characterized as an increase in $\langle Q2 \rangle$. 
-This is a characteristic of how the particles were initialized and move once the simulation is initiated. The particles are initialized to be randomly placed 
-in the simulation domain with roughly equal spacing. As the interface sweeps through the simulation domain, particles irreversibly adsorb onto the interface 
-and move with the interface until the bijel jams. We see that $\langle Q2 \rangle$ is magnetic field dependent for oblate particles but not for the spherical 
-and prolate particles. We also see an aspect ratio dependence on the values characterized as differences in the time evolution of $\langle Q2 \rangle$. This 
-arises due to the differences in the aspect ratio of the particle causing them to arrange differently on the interface as the bijel microstructure evolves.
-
-An increase in $\langle Q6 \rangle$ can indicate an increase in the number of particles adopting icosahedral symmetry at the interface of the amorphous 
-interface. \cite{kapfer_jammed_2012} However due to the amorphous nature of the arrangement of particles at the particle monolayer, we use this parameter 
-only to gauge changes in local arrangements of particles at the interface and make no commentary on specific interfacial arrangements. For oblate particles, 
-we characterize a reduction in local order as the applied field strength is increased, consistent with the increase in $\langle Q2 \rangle$. For prolate 
-particles, we observe that $\langle Q6 \rangle$ increases with the applied field. This indicates that the application of the field causes particles to have 
-increased local order, even if we see no discernible changes in $\langle Q2 \rangle$.
-
-The application of the magnetic field affects the prolate and oblate particle differently due to their aspect ratio. At interfaces, rod-like particles 
-prefer to orient themselves in an end to end fashion. \cite{eatson_capillary_2023} Disc-like particles have been shown to prefer stacking. \cite{dabat_mesoscale_2018} 
-Application of the magnetic field and the presence of an interface will constrain the rotation of the particles, meaning that naturally rods will pack better at 
-interfaces than discs as the magnetic field causes the particles to align to the field. This better packing at the interface manifests as greater local ordering 
-Next, we analyze how these local toplogical changes affect the microstructure of the bijel by analyzing the channel size distribution of the bijels.
+Figure~\ref{fig:psi_time} suggests that this forced misalignment is more pronounced for oblate particles. Due to their larger aspect ratio, prolate 
+particles experience stronger capillary torques when tilted, making them more resistant to reorientation. As a result, prolate particles largely 
+maintain alignment with the interface, even under stronger magnetic fields.
 
@@
 To corroborate this idea, we analyzed the radial distribution function
-(RDF) of the particles, the calculation of which is detailed in Section
-\ref{section:radial_distribution} The time-evolution of the RDFs for the three particle shapes and
+(RDF) of the particles
+    %
+    \begin{equation}
+        g(r) = \frac{n_p - 1}{n_p} \cdot V \cdot \left\langle \delta\left(r - r_i\right) \right\rangle
+    \end{equation}
+    %
+where \(n_p\) is the number of particles in the volume
+\(V\), and \(\langle\cdot\rangle\) denotes an average over all
+particles. The radial distribution function was calculated by binning
+the distance between all particle pairs and normalizing the shells with
+respect to the distribution \(4\pi \rho r^2 \mathrm{d}r\) of an ideal
+gas. The time-evolution of the RDFs for the three particle shapes and
 varying magnetic flux density is illustrated in Figure \ref{fig:rdf}.
 
-\begin{figure}
+    \begin{figure*}
     \centering
-\includegraphics[width=\textwidth]{figures/results/paper1/rdf_compare_time.png}
-\caption{Time-evolution of the radial distribution function $g(r)$ of the particles at different magnetic 
-        field strength $\bar{B}$. The radial distribution function is shown at $10^3$, $10^4$, and $10^5$ timesteps. 
-        The distance $r$ is normalized by the radius $R=\max(R_\parallel,R_\perp)$ of the larger particle axis. The peaks 
-        illustrate the packing of particles in the interface. Dashed lines indicate the side-by-side, tip-to-tip, 
-        and side-to-tip configuration of particle pairs. For spherical particles, the three values are identical. 
-        The insets show snapshots of the particle arrangement with and without magnetic field at the respective timesteps. 
-        The direction of the magnetic field is indicated by arrows.}
+    \includegraphics[width=\textwidth]{../figures/results/paper1/rdf_compare_time.png}
+    \caption{Time-evolution of the radial distribution function $g(r)$ of the particles at different magnetic field strength $\bar{B}$. The radial 
+    distribution function is shown at $10^3$, $10^4$, and $10^5$ timesteps. The distance $r$ is normalized by the radius $R=\max(R_\parallel,R_\perp)$ 
+    of the larger particle axis. The peaks illustrate the packing of particles in the interface. Dashed lines indicate the side-by-side, tip-to-tip, and 
+    side-to-tip configuration of particle pairs. For spherical particles, the three values are identical.}
     \label{fig:rdf}
-\end{figure}
+    \end{figure*}
+
+Figure~\ref{fig:rdf} shows the radial distribution function (RDF) at time steps \(t = 1000\Delta t,\ 10000\Delta t,\ 100000\Delta t\). 
+For ellipsoidal particles, characteristic contact distances include \(2R_{\parallel}\), \(2R_{\perp}\), and \(R_{\parallel} + R_{\perp}\), 
+indicated by dashed lines in the figure. The largest RDF peak for both oblate and spherical particles occurs at \(2R_\perp\), suggesting 
+contact around the particle circumference, while prolate particles preferentially align side-by-side. These configurations enable denser 
+packing at the interface.
+
+In the early stages of the simulation, RDF peaks are less distinct due to the more random particle orientations. Notably, for prolate particles, 
+the RDF shows an initial dip at \(2R_\parallel\), indicating that tip-to-tip arrangements are rare. As time progresses, the peak heights increase, 
+particularly under magnetic fields, supporting the idea that magnetic alignment promotes side-by-side and tip-to-tip ordering. For oblate particles, 
+a shoulder emerges near \(R_\parallel + R_\perp\), indicating occasional tilting out of the interface to reduce interfacial coverage. In contrast, 
+for prolate particles, the dip at \(2R_\parallel\) disappears over time, suggesting increased tip-to-tip alignment—consistent with field-driven 
+particle orientation that supports close packing along both particle axes. This layered structure is also visible in the snapshots in 
+Figure~\ref{fig:packing_viz}.
+
+Together with the nematic order analysis, these findings reinforce the proposed mechanism of bijel formation under magnetic fields: the field aligns 
+particle dipoles, particle reorientation couples to interface alignment via capillary interactions, and steric constraints are reduced, allowing further 
+interface shrinkage and domain coarsening. Temporally, particle rotation occurs early in the simulation, followed by gradual re-alignment of interfaces. 
+For prolate particles, shrinking interfaces can even force slight misalignment to accommodate tighter packing. Overall, our results demonstrate that 
+bijels formed under magnetic fields with anisotropic particles develop anisotropic domain sizes and tortuosity, and exhibit more ordered interfacial 
+particle packing due to alignment effects.
+
+\section{Conclusions}
+
+In this work, we investigated how external magnetic fields affect the formation of bijels stabilized by magnetic ellipsoidal particles. We considered 
+oblate, spherical, and prolate particles with permanent magnetic dipoles dispersed in a symmetric binary fluid. While the presence of a magnetic field 
+does not prevent bijel formation, it induces anisotropy in both domain size and tortuosity when using non-spherical particles. For oblates, domain size 
+increases perpendicular to the field, while tortuosity increases along the field direction. In contrast, for prolates, domain growth is enhanced along 
+the field, with increased tortuosity perpendicular to it. Compared to bijels formed without a field, domain size changed by up to 30\% for anisotropic particles.
+
+This behavior is driven by particle reorientation: magnetic dipoles align with the field, which in turn influences interface alignment along the longer axis 
+of the particles. Our analyses of coarsening velocity, nematic ordering, and interfacial structure support this mechanism. We observed that jamming is delayed 
+in the direction aligned with the particles long axis, allowing extended coarsening. This delay correlates with a slowdown in particle alignment and increased 
+interface ordering. We also found that the average angle between particle dipoles and the interface normal evolves during this stage. Radial distribution 
+functions further show that prolate particles tend to align side-by-side, while oblates form less regular arrangements.
+Together, these findings suggest that bijel formation under magnetic fields is governed by two coupled processes: initial magnetic alignment of the particles, 
+which facilitates coarsening, followed by capillary-induced interface alignment. As jamming sets in, interfacial shrinkage compresses particles into ordered 
+structures. Some particles, particularly oblates, may tilt out of the interface to accommodate tighter packing.
+
+Our results highlight how magnetic fields can be used to tune the structural properties of bijels, which is valuable for applications where domain size and 
+tortuosity affect performance. For instance, reduced tortuosity can enhance diffusive transport in bone-like materials \cite{prakoso2023tortuosity} and 
+lithium-ion electrodes \cite{chen2020tortuosity, ebner2014tortuosity}, improving efficiency and cyclability. While we focused on a specific spinodal 
+decomposition regime, further tuning could be achieved by adjusting fluid viscosity, surface tension, or particle volume fraction, known to influence 
+bijel morphology \cite{jansen_bijels_2011, hijnen_bijels_2015}.
+
+Regarding experimental relevance, our simulations consider micron-scale particles and neglect thermal fluctuations, which may become relevant at the 
+nanoscale. However, prior work by Reeves et al.~\cite{reeves_particle-size_2015} shows that nanoparticles can enhance bijel stability by resisting 
+disruptive curvature. The long-term stability of magnetically responsive bijels remains an important consideration for flow-based applications like 
+crossflow reactors \cite{khan_nanostructured_2022}.
+Beyond shape and size effects, interparticle interactions offer another route for tuning bijel formation. Recent work on bicontinuous intraphase jammed 
+emulsion gels (bipjels) underscores this potential \cite{kinkead_bicontinuous_2019}. Notably, our simulations reveal that interfacial particle ordering 
+increases under magnetic fields. While such ordering has been observed at planar interfaces 
+\cite{toor_self-assembly_2016, shi_nanoparticle_2018, kim_dynamic_2022}, it has not yet been reported in bijel systems. Future studies could explore how 
+this ordering impacts the optical and transport properties of jammed emulsion gels.
+In summary, our simulations provide new insights into the role of magnetic fields in guiding the formation and microstructure of bijels. Magnetic particles 
+enable tunable and anisotropic control over particle packing and domain morphology, offering promising opportunities for designing advanced porous materials.

### 2025-04-06 chapters/paper3.tex
Changes 1. Updated text for rheology of bijels section

@@
 
-While the microstructure and synthesis techniques for bijels have been explored in earnest, the rheology of bijels
-has remained relatively unexplored. Some interesting phenomena for bijels and shearing include the 
-presence of monogels, made by remixing the phase separated liquid domains of the bijel while the electrostatic
-interactions between particles maintains the structure of the particle monolayer. \cite{sanz_colloidal_2009} 
-Monogel formation has been observed in lutidine/water and styrene/butadiene oligomer based bijels but not ethane-diol nitromethane based bijels
-\cite{sanz_colloidal_2009, bai_dynamics_2015, tavacoli_novel_2011} Computational Investigations have identified that confined bijels under shear undergo elongation of
-the domains in the direction of shear succeeded by particle detachment from the interface and eventual failure of the bijel. \cite{bonaccorso_shear_2020}
-More recently, bijels have been identified to be 2D glasses percolating in 3D space, characterized through comparing the complex rheology of bijels against
-colloidal gels made from silica particles with electrostatic interactions. \cite{ching_bijel_2022}
+The rheological properties of bijels are critical to their processability and structural fidelity across a variety of manufacturing techniques. In solvent transfer-induced phase separation 
+(STrIPS), for example, the flow rate of the casting mixture and the co-solvent ratio play a key role in controlling the microstructure of the bijel and determining whether droplets or 
+rope-like structures emerge during synthesis \cite{haase_continuous_2015, haase_situ_2016}. Similarly, in volatile-induced phase separation (VIPS), the viscosity of the solvent rich and poor 
+phases determines the extent of phase separation before gelation or jamming occurs, ultimately governing final domain morphology \cite{wang_scalable_2020}. In homogenization-driven methods, 
+the imposed shear rate directly influences the interfacial jamming dynamics and can either assist or disrupt bicontinuous structure formation depending on processing windows 
+\cite{huang_bicontinuous_2017}. Understanding these rheological dependencies is essential for tuning bijel architectures for advanced applications.
 
-In many of the manufacturing techniques outlined the rheological properties are essential in ensuring that 
-the casting mixture remains processable. \cite{haase_continuous_2015,haase_situ_2016} In STrIPS, the flow rate of the casting mixture and the co-solvent
-control the microstructure of the bijel and the morphology of the resulting bijel material, controlling whether droplets or ropes are synthesized. \cite{haase_continuous_2015}
-When investigating the effect of magnetic fields on the rheological properties of suspensions, it has been shown that the viscosity of ferrofluids increases substantially due
-to the self assembly of particles restricting the flow of fluid, greatly increasing the viscosity of the ferrofluid. cite{qiao_magnetorheological_2012} The application
-of shear onto suspensions can also cause shear banding as interparticle interactions mediate particle fluid interactions, creating localized velocity differences to the bulk.
-\cite{xu_relation_2013} Looking into emulsions, the application of magnetic fields increases the viscosity of emulsions, making them more shear thinning than when no field 
-is applied.
+While the microstructure and synthesis of bijels have been extensively investigated, their rheological behaviour remains comparatively underexplored. One intriguing feature is the formation of 
+monogels, in which remixing the liquid phases of a bijel preserves the interfacial particle network due to persistent attractive interactions between particles \cite{sanz_colloidal_2009}. This 
+phenomenon has been observed in bijels composed of lutidine/water and styrene/butadiene oligomer mixtures, but is notably in systems based on ethylene glycol and nitromethane 
+\cite{sanz_colloidal_2009, bai_dynamics_2015, tavacoli_novel_2011}. Rheologically, bijels typically exhibit shear thinning and thixotropic responses under steady shear, indicative of dynamic 
+restructuring and gradual recovery of the internal network \cite{macmillan_rheological_2019}. In confined geometries, computational studies have shown that shear induces elongation 
+of domains followed by particle alignment along the flow direction, detachment from the interface, and eventual collapse of the bicontinuous structure \cite{bonaccorso_shear_2020}. More recently, 
+bijels have been conceptualized as two-dimensional colloidal glasses embedded in a percolating three-dimensional network, exhibiting rheological behaviour that bridges colloidal gels and jammed 
+particle layers \cite{ching_bijel_2022}. However, existing frameworks for bijel rheology focus on bijels stabilized by spherical, non-stimuli responsive particles, and do not yet capture the complex 
+rheology arising from anisotropic particle shapes or magnetic interactions, which are increasingly relevant in functionalized bijel systems.
 
-In past chapters, we identified the microstructure and particle arrangement of bijels stabilized by ellipsoidal particles under magnetic fields and demonstrated
-particles morphology specific ordering to the applied magnetic field. We also show that the local ordering of the particles is affected from the application of
-the magnetic field. In this chapter, We probe the dynamics of bijels under constant shear to understand how these microstructural and particle monolayer changes
-affect the rheology of bijels stabilized by ellipsoidal particles under magnetic fields. First, we define a shear capillary number, $Ca_s$
-which in the literature lies 0.04 and 0.16. \cite{frijters_effects_2012, yang_capillary_2022}
-However, these capillary number ranges would exceed the 
-maximum mach number the model allows if this same range were used $(Ma \leq 0.03)$. To accommodate this limitation the 
-largest capillary number used will be $Ca_s = 10^-4$ which correspond to a maximum of $Ma \approx 0.02$. As all particles used 
-have only hard-sphere type interactions, it is expected that the behaviour seen should mimic 2D colloidal glasses 
-percolating in 3D space, akin to what Ching and Mohraz saw, with an additional dependence on the direction of shear. 
-This would predict the discovery of particle monolayer dependent elasticity and yield stress along with shear thinning 
-behavior of the bijels.
+While the rheology of emulsions stabilized by spherical particles has been extensively characterized, ellipsoidal particles introduce additional complexity through interfacial locking and anisotropic drag,
+which can suppress coalescence and resist flow differently under shear \cite{madivala_self-assembly_2009, daware_emulsions_2015, sun_assembly_2013}. Under shear, ellipsoidal particles 
+can promote shear banding, wherein particle-fluid interactions create localized variations in velocity profiles \cite{xu_relation_2013}. Furthermore, suspensions of magnetically responsive particles, 
+such as ferrofluids, exhibit a pronounced increase in viscosity due to field-induced self-assembly that restricts fluid flow \cite{qiao_magnetorheological_2012}. 
+Theoretical predictions and experimental observations have identified that orientational ordering of anisotropic particles in the direction of shear reduces viscosity by minimizing hydrodynamic drag and interfacial
+disruption, allowing the fluid to flow more easily along the direction of least resistance.\cite{vermant_flow-induced_2005, xu_relation_2013}.
 
-To verify these predictions, bijel microstructure will be defined using four processing histories; The first is of a 
-bijel simulated under a $\Bar{B} = 1$ magnetic field strength, the second is a bijel stimulated under no field, 
-followed by the application of a $\Bar{B} = 1$ field after jamming, the third is a bijel simulated under no field, 
-while the final microstructure is a bijel simulated under $\Bar{B} = 1$ magnetic field, followed by switching the 
-field off after jamming. This gives insight into the impact of processing history on the shear properties of a bijel, 
-in addition to the microstructural and colloidal insights gained. Based on the results in Bonaccorso et al., there 
-should be shear driven and shear rate dependent elongation of the domains in the direction parallel to the applied 
-shear which in this system will be seen as a reduction in $L_{\perp}$ and an increase in $L_{\parallel}$. 
-\cite{bonaccorso_shear_2020} The microstructure anisotropy will also be a factor in the viscosity results, as 
-larger domains are more permeable than smaller ones, meaning that bijels where $L_{\perp} > L_{\parallel}$ should 
-see less of the domain elongation effects shown in Bonaccorso et al. as the permeability of the bijels rises with 
-larger domain size. \cite{bonaccorso_shear_2020}
-
-It is also expected that the effective viscosity will be different between the four microstructures dependent upon the 
-degree of nematic ordering and microstructural anisotropy of the bijel. Nematic ordering of the particles in the direction of shear
-should resulting in a lowered effective viscosity compared to bijels without nematically 
-ordered particles. \cite{xu_relation_2013, vermant_flow-induced_2005} Tracking of the proportion of particles on the 
-interface will also yield insight into how the packing of the particles affects the rate at which particles will get 
-ejected from the interface. Bonnacorso et al. identified that shear applied onto bijels caused particles to align to the direction of
-shear before being ejected from the interface. Systems with a larger $\eta_{eff}$ are predicted to have the largest domains, largest 
-difference between initial and final particle order and lowest number of particles left on the interface once steady 
-state has been established.
+In this study, we investigate the rheological response of bijels stabilized by magnetically responsive ellipsoidal particles subjected to constant shear.
+Using a hybrid Lattice Boltzmann-Molecular Dynamics
+(LBM-MD) simulation framework, we model a binary fluid system containing suspended magnetic ellipsoids, with shear applied via Lees-Edwards boundary conditions along one axis and periodic conditions along
+the remaining boundaries. Our results show that these bijels exhibit Herschel-Bulkley-type rheology, with yield stress and shear-thinning behavior modulated by particle orientation at the interface. 
+Specifically, increasing orientational ordering of ellipsoidal particles under the applied magnetic field reduces hydrodynamic resistance, resulting in lower effective viscosity and a diminished shear-thinning
+response.
+Furthermore, we find that the yield stress is dependent on particle shape and magnetic alignment, as magnetic stimuli alter the number and orientation of frictional contacts within the interfacial
+monolayer.
+These findings highlight the tunability of bijel rheology via particle morphology and magnetic field application, offering potential design pathways for adaptive and reconfigurable soft materials.
 
@@
 
-We begin this investigation by analyzing the rheological response of bijels stabilized by ellipsoidal particles under constant shear.
-Specifically, we investigate the effect that particle order has on the rheological response characterized. We are also interested in
-identifying the impact that the application of magnetic fields have on the rheological response of the bijel. 
-Bijel templates simulated in Aim 1 with no field and a field strength of $\bar{B} = 1$ stabilized with a prolate and oblate particles with a 
-particle volume fraction $\phi_p = 0.15$ were used as the starting point for these simulations. Next, we apply a field strength of
-$\bar{B} = 1$ or switch off the applied field to all structures. This results in four processing setups; $\bar{B}:0\rightarrow 0$, $\bar{B}:0\rightarrow 1$,
-$\bar{B}:1\rightarrow 0$ and $\bar{B}:1\rightarrow 1$. We then define a shear capillary number,  $Ca_s = \frac{\dot{\gamma} R_{s} \eta_{f}}{\sigma}$ where 
-$\dot{\gamma}$ is the applied strain rate, $R_s$ is the equivalent spherical radius of the particles, $R_s = 7.9$, $\eta_f$ is the dynamic viscosity of the 
-fluid and $\sigma$ is the surface tension of the interface. We use five shear capillary numbers, 
-$Ca_s = 1\cdot10^{-4}, 5\cdot10^{-5}, 1\cdot10^{-5}, 5\cdot10^{-6}, 1\cdot10^{-6}$.
+To probe the rheological behavior of bijels stabilized by ellipsoidal particles, we analyze their response under constant shear with particular focus on the influence of interfacial particle ordering 
+and magnetic field application. The initial bijel structures are obtained from previous simulations, consisting of bicontinuous morphologies stabilized by either prolate or oblate magnetic 
+ellipsoids at a particle volume fraction of $\phi_p = 0.15$, generated with and without an applied magnetic field of dimensionless strength $\bar{B} = 1$.
+To evaluate the combined and decoupled effects
+of field history and applied shear, we systematically vary the magnetic field configuration, yielding four distinct processing pathways: 
+$\bar{B}:0 \rightarrow 0$, $\bar{B}:0 \rightarrow 1$, $\bar{B}:1 \rightarrow 0$, and $\bar{B}:1 \rightarrow 1$.
+These setups enable us to isolate the contributions of pre-aligned versus dynamically aligning
+particles during flow.
+Shear is imposed via a range of dimensionless shear capillary numbers, defined as $Ca_s = \frac{\dot{\gamma} R_s \eta_f}{\sigma}$, where $\dot{\gamma}$ is the applied shear rate,
+$R_s = 7.9$ is the equivalent spherical radius of the ellipsoids, $\eta_f$ is the dynamic viscosity of the continuous phase, and $\sigma$ is the interfacial tension. 
+\cite{frijters_effects_2012, yang_capillary_2022} We explore five shear conditions spanning $Ca_s = 1 \times 10^{-4}$ to $1 \times 10^{-6}$, capturing the transition from strong deformation to 
+near-equilibrium interfacial response.
 
@@
 
-The ordering of the particles play an important role in determining the rheology of suspensions as ordered particles can slip over one another
-before the structure breaks. The adsorption of particles on the interface of a bijel could affect how this slip occurs. Previous work investigating
-the rheology of bijels have determined shear thinning behavior characterized with a Herschel-Buckley fit equation. \cite{macmillan_rheological_2019} 
-After applying shear on the bijel templates, we characterize and plot the time evolution of the the shear stress in Figure \ref{fig:stress_time}.
+Particle ordering plays a critical role in determining the rheological behavior of suspensions, as aligned particles can more readily slide past one another 
+under shear, delaying structural breakdown. In bijels, where particles are adsorbed at the fluid-fluid interface, this interfacial confinement may significantly 
+influence the degree of slip and the onset of yielding. Prior studies have shown that bijels exhibit shear-thinning behavior consistent with Herschel-Bulkley rheology, 
+indicating a non-Newtonian response governed by both interfacial structure and particle dynamics \cite{macmillan_rheological_2019}. To investigate these effects in 
+the presence of magnetic fields and varying degrees of particle ordering, we apply constant shear to the bijel templates and plot the resulting time evolution of 
+the shear stress, as shown in Figure~\ref{fig:stress_time}.
 
@@
     \centering 
-    \includegraphics[scale=0.3]{../figures/results/paper3/stress-time_compare.png} 
+    \includegraphics[scale=0.5]{../figures/results/paper3/stress-time_compare.png} 
     \caption{Time evolution of the shear stress of bijels stabilized with ellipsoidal particles as a function of the applied strain rate as
@@
 
-Figure \ref{fig:stress_time} shows that there is no definitive steady state value of the shear stress obtained in the simulations performed. This is
-attributed to the coarsening of the domains and reorientation of particles at the interface. \cite{tavacoli_novel_2011,macmillan_rheological_2019} 
-Tavacoli et al. investigated the rheological response of Ethanediol/Nitromethane bijels and identified that upon placement of a needle to calculate the yield
-stress of the bijel, the structure of the material was irreversibly altered. \cite{tavacoli_novel_2011} Macmillian et al. identified that repeated 
-shearing of a bijel synthesized using direct mixing resulted in degraded mechanical performance. \cite{macmillan_rheological_2019}
-To characterize the fit, we identify pseudo-steady state regions within each of the shear stress plots and fit the stress identified within this 
-pseudo-steady state region to the strain rate. Pseudo-steady state regions are identified by measuring where the rate of change of shear stress is 
-smallest for the longest duration. We fit the calculated stress to the applied strain rate using a Herschel-Buckley rheology model defined as
-$\sigma_{xz} = \sigma_{y} + K(\dot{\gamma})^{n}$. $\sigma_{xz}$ is the shear stress calculated from the simulation, $\sigma_{y}$ is the yield stress of the bijel, 
-$K$ is the flow consistency index and $n$ is the flow index. Where appropriate, we include results corresponding to a shear capillary number of 
-$Ca_s = 10^{-6}$ as in many stress responses, $Ca_s = 10^{-6}$ may not always yield usable results.
+Figure \ref{fig:stress_time} demonstrates that a definitive steady-state shear stress is not reached within the simulated timeframes across all conditions. 
+This absence of steady-state behavior is attributed to the continued coarsening of the bicontinuous domains and the progressive reorientation of interfacial 
+particles under shear \cite{tavacoli_novel_2011, macmillan_rheological_2019}. Tavacoli et al.\ showed that mechanical perturbation of bijels, such as the 
+insertion of a needle to measure yield stress, resulted in irreversible structural deformation, particularly in ethanediol/nitromethane systems 
+\cite{tavacoli_novel_2011}. Similarly, Macmillan et al.\ observed that repeated shearing of bijels synthesized by direct mixing led to degraded mechanical 
+performance over time, suggesting a link between structural evolution and rheological response \cite{macmillan_rheological_2019}. To characterize the rheology 
+of these evolving systems, we identify pseudo-steady-state regions within the stress-time profiles, defined as intervals where the rate of change of shear 
+stress is minimal and persists for the longest continuous duration. Within these regions, the stress response is fitted to the applied shear rate using a 
+Herschel-Bulkley model:
+
+\begin{equation}
+    \sigma_{xz} = \sigma_{y} + K\dot{\gamma}^{n}    
+\end{equation}
+
+In the Herschel-Bulkley model, $\sigma_{xz}$ denotes the computed shear stress, $\sigma_y$ is the yield stress, $K$ represents the flow consistency index, 
+and $n$ is the flow index characterizing the degree of shear thinning. In certain cases, simulations conducted at the lowest shear capillary number 
+($Ca_s = 10^{-6}$) exhibited insufficient stress resolution or high variability, and were excluded from model fitting where appropriate. For each case, 
+$\sigma_{xz}$ is extracted from the pseudo-steady-state region of the stres-time curves, while the corresponding shear rate $\dot{\gamma}$ is derived from 
+the imposed capillary number, $Ca_s$. The resulting fits for the various bijel systems are presented in Figure~\ref{fig:stress_strain}.
 
@@
     \centering 
-    \includegraphics[scale=0.4]{../figures/results/paper3/stress_strain-all.png} 
-    \caption{Fitting the experimental shear stress to the strain rate using the Herschel Buckley model. We characterize the bijels are 
+    \includegraphics[scale=0.5]{../figures/results/paper3/stress_strain-all.png} 
+    \caption{Fitting the experimental shear stress to the strain rate using the Herschel-Bulkley model. We characterize the bijels are 
              shear thinning in all cases and that the bijels become less shear thinning as the particle order increases. We also
@@
 
-From Figure \ref{fig:stress_strain}, the slopes of the curve indicate a non-linear shear response to the applied strain rate, suggesting that the rheological properties
-are non-Newtonian. Bijels stabilized by prolate and oblate particles also have different shear properties. For bijels stabilized by oblate particles, the stress curves
-are more spread out suggesting that there is a larger variance in the properties arising from the change in the initial microstructure of the bijel. From the plot
-the increase in particle order reduces the yield stress of the bijel. For bijels stabilized by rod like particles, the stress response of each processing 
-condition is closer together, indicating a smaller variation in the response to the applied magnetic field compared to oblate particles. The shear response upon application
-of the magnetic field also suggest that increased ordering of prolate particles makes the bijel more resistant to shear. We quantify the Herschel-Buckley fit parameters and 
-tabulate the results in Table \ref{table:rheology_fit}.
+Figure~\ref{fig:stress_strain} presents the shear stress $\sigma_{xz}$ as a function of shear rate $\dot{\gamma}$ for bijels stabilized by oblate ($\alpha = 0.5$) 
+and prolate ($\alpha = 2.0$) ellipsoidal particles, fitted using the Herschel-Bulkley model. In both cases, the curves exhibit nonlinear scaling with $\dot{\gamma}$, 
+confirming a non-Newtonian, shear-thinning response. For bijels stabilized by oblate particles, the stress-strain curves are more widely separated, indicating 
+greater sensitivity to the initial microstructural configuration induced by magnetic field history. Specifically, increased orientational ordering—achieved through 
+magnetic pre-alignment—correlates with a reduced yield stress, as observed by the downward shift of the stress curves. In contrast, bijels stabilized by prolate 
+particles exhibit more closely clustered stress responses across different magnetic conditions, suggesting a reduced dependence on field history. Interestingly, 
+for the prolate case, the stress response under persistent ordering ($\bar{B}:1 \rightarrow 1$) exceeds that of disordered systems, implying that aligned rod-like 
+particles enhance interfacial resistance to shear. These trends highlight the contrasting rheological behaviors imparted by particle shape and the role of 
+field-induced anisotropy in modulating mechanical response. Quantitative fit parameters obtained from the Herschel-Bulkley model are provided in 
+Table~\ref{table:rheology_fit}.
 
@@
     \end{tabular}
-    \caption{Hershel Buckley fit parameters for different processing conditions applied to bijels stabilized by ellipsoidal particles.}
+    \caption{Hershel Bulkley fit parameters for different processing conditions applied to bijels stabilized by ellipsoidal particles.}
     \label{table:rheology_fit}
@@
 
-The results in Table \ref{table:rheology_fit} show that bijels remain shear thinning regardless of the processing history and particle morphology.
-The particle morphology dependent differences in the shear response characterized in Figure \ref{fig:stress_strain} are quantified in Table \ref{table:rheology_fit}
-where the yield stress differences predicted is clear to see. The bijel templates with an applied field of $\bar{B} = 1$ have larger flow indices
-than bijel templates made with no applied field. The same trend exists here where the application of a magnetic field makes the bijel more Newtonian.
-The yield stress of bijels stabilized with oblate particles decrease as the initial order of the particles and the applied field onto the bijel increase. 
-The yield stress of bijels stabilized by prolate particles increases as the initial order of the particles and the applied field onto the bijel increase. In previous aims, we 
-characterized that application of magnetic fields created orientational ordering of the bijels and that the local ordering of the bijels change. We  
-showed that as magnetic fields were applied, oblate particles have lower local ordering on the interface while for prolate particles it increases.
-Past investigations have identified that particle monolayers buckle more easily as local particle ordering decreases. \cite{prakash_buckling_2024} 
-They identified that local ordering can enhance stress distribution among particles, making locally ordered particle monolayers better at withstanding shear.
-We visualize the ordering of the particles at the interface to the z direction for both particle morphologies at $Ca_s = 10^{-6}$ for the 
-case $\bar{B}: 1 \rightarrow 0$.
+The results presented in Table~\ref{table:rheology_fit} confirm that all bijel systems exhibit shear-thinning behavior, regardless of particle morphology or 
+magnetic field history. The particle-shape-dependent differences in shear response observed in Figure~\ref{fig:stress_strain} are quantitatively reflected in 
+the Hersche-Bulkley fit parameters, particularly in the yield stress $\sigma_y$ and flow index $n$. Notably, bijels synthesized with an applied magnetic field 
+($\bar{B} = 1$) exhibit higher flow indices than those without, indicating a shift toward more Newtonian-like behavior under increased particle ordering. This 
+trend is especially pronounced in bijels stabilized by oblate particles, where increased magnetic alignment leads to a progressive reduction in yield stress. 
+In contrast, bijels stabilized by prolate particles show an opposite trend, with yield stress increasing alongside particle alignment and magnetic field 
+application. These findings are consistent with earlier observations from Aim 1, which showed that magnetic fields promote local orientational ordering at the 
+interface—enhancing ordering for prolate particles while reducing it for oblate particles. Prior studies have demonstrated that reduced local order in 
+interfacial monolayers leads to structural buckling and early mechanical failure, whereas increased ordering enables more uniform stress distribution 
+across particles, thereby enhancing resistance to deformation \cite{prakash_buckling_2024}.
+
+\subsection{Shear induced particle rearrangement}
+
+Given that magnetic fields can modify the local arrangement of ellipsoidal particles at fluid interfaces, understanding how this arrangement evolves under 
+different processing conditions is essential for interpreting the mechanical 
+behavior observed. In particular, the contrasting effects seen for prolate and oblate particles, where increased magnetic ordering leads to a larger
+and smaller yield stress respectively. To quantitatively assess the local arrangement of particles at the interface, we compute the ensemble-averaged 
+Steinhardt bond orientational order parameters $q_2$ and $q_6$. 
+\cite{steinhardt_bond-orientational_1983, lechner_accurate_2008, mickel_shortcomings_2013}. These parameters characterize the local structural ordering by 
+projecting the orientations of neighboring particles onto spherical harmonics of degree \(l\), and are defined as
+
+\begin{equation}
+q_l(i) = \left( \frac{4\pi}{2l+1} \sum_{m=-l}^{l} \left| \frac{1}{N(i)} \sum_{j=1}^{n(i)} Y_{lm}(\vec{r}_{ij}) \right|^2 \right)^{\frac{1}{2}} ,
+\end{equation} 
+%\TODO{update formula to the one actually used}
+
+Here, \(n(i)\) denotes the number of nearest neighbors of particle \(i\), \(\vec{r}_{ij}\) is the vector connecting the centers of particles \(i\) and \(j\), 
+and \(m\) is an integer ranging from \(-l\) to \(l\) that indexes the spherical harmonic components \(Y_{lm}\). Neighbor lists are typically defined using a 
+fixed cutoff radius around each particle, identifying nearby particles as neighbors. We calculate the python package Freud to calculate the bond order parameters 
+and use a Voronoi cell to determine the particle neighborhood rather than the standard distance criterion \cite{ramasubramani_freud_2020,mickel_shortcomings_2013}. 
+The Voronoi-based method avoids the need for a predefined cutoff and yields more robust neighbor definitions, particularly in disordered systems. Bond 
+orientational order parameters have been widely employed to study structural transitions in colloidal and ceramic systems, including crystallization, nucleation, 
+and glass formation \cite{vagberg_glassiness_2011, besseling_three-dimensional_2007, schall_structural_2007, ozawa_jamming_2012}. $q_6$ is most commonly used 
+to identify crystal structures by matching the calculated values to reference values for specific crystal structures such as fcc or hcp. We plot the change in 
+$q_6$ of the microstructures as a function of the processing applied in Figure \ref{fig:q6_rheology_init}
 
@@
     \centering 
-    \includegraphics[scale=0.4]{../figures/results/paper3/tz_concat_startB-1_endB-0.png} 
-    \caption{Visualization of the particle monolayer of bijels stabilized by prolate and oblate ellipsoidal particles with processing history $\bar{B}: 1 \rightarrow 0$
-             undergoing an applied shear of $Ca_s = 10^{-6}$. Particles with a deeper purple shade have a larger angle to the z axis. The top row shows the initial 
-             configuration of the particles while the bottom row shows the final configuration of the particles. } 
-    \label{fig:particle_viz_tz} 
+    \includegraphics[scale=0.4]{../figures/results/paper3/Q6-start.png} 
+    \caption{Plot of the relationship between the local particle order $\langle Q6 \rangle$ at the first timestep after initiation of shear and 
+             yield stress ($\sigma_y$) in bijels across magnetic field histories for oblate 
+             ($\alpha = 0.5$) and prolate ($\alpha = 2.0$) particle-stabilized systems.} 
+    \label{fig:q6_rheology_init} 
 \end{figure}
 
-In Figure \ref{fig:particle_viz_tz}, the particles are initially ordered to the direction of the applied magnetic field. Upon application of shear and removal
-of the magnetic field, We see that the particles begin reorienting away from the z direction. We also observe that the reorientation of particles uncovers the interface.
-The reorientation observed is particle morphology specific with prolate particles seeing more reorientation away from the applied shear direction than oblate particles.
-Looking at the images, we see that prolate particles rotate away from the direction of the magnetic field and applied shear towards the direction of the shear gradient,
-while oblate particles reorient towards minimizing area to the applied shear direction. While these snapshots show the initial and final orientations of the particles at the
-interface, the time evolution of the particle monolayer changes to identify its role in the rheological properties characterized.
+Figure~\ref{fig:q6_rheology_init} shows that for oblate particles (left panel), $\langle Q_6 \rangle$ decreases progressively with increasing magnetic alignment, 
+indicating a loss of local hexagonal
+order at the interface. This trend is accompanied by a reduction in yield stress, suggesting that disrupted interfacial packing compromises the bijel's 
+ability to resist deformation. These findings align with prior observations that reduced local order facilitates monolayer buckling and structural failure 
+under shear. In contrast, bijels stabilized by prolate particles display the opposite behavior, characterized as an increase in $\langle Q_6 \rangle$ with
+the particle order field history, signifying enhanced local ordering, and this increase correlates with a substantial rise in yield stress. The positive 
+coupling between local particle order and mechanical strength in prolate systems supports the hypothesis that nematic alignment reinforces the interfacial 
+network, distributing stress more effectively under shear. Together, these results demonstrate a morphology-dependent link between magnetic field-induced 
+ordering and rheological response.
 
-\subsection{Particle properties}
+\subsection{Shear induced reorientation of particles}
 
-Particles at the interface of bijels stabilized with ellipsoidal particles reorient at the interface to minimize interfacial and
-steric energies. \cite{gunther_timescales_2014} The particles stabilizing bijels in confined systems under shear have been shown to
-orient to the direction of shear and ejected from the interface at sufficiently long times or shear.\cite{bonaccorso_shear_2020} 
-We probe these aspects of the particle monolayer in this section. First, we plot the orientation of the particle to each cartesian axis 
-to identify if shear induced ordering is present.
+Bonaccorso et al. identified that the spherical particle stabilizers in their bijel simulations oriented to the direction of shear before being
+ejected from the interface. \cite{bonaccorso_shear_2020} Due to the shape of ellipsoidal particles, they adopt a preferred orientation which
+maximizes the interface covered by the particle. \cite{davies_dipolar_2015, davies_interface_2014} Energy must be imparted to rotate the particles
+out of the interface. Upon application of shear, the orientation of particles on the interface will be a function of the applied shear rate, 
+applied magnetic field and the capillary forces of the interface on the particle. \cite{cao_modeling_2021, chhabra_drag_1999, brenner_stokes_1963, naga_capillary_2021}
+Therefore, the degree of interface angle change observed can shed light onto the rheological 
+differences of bijels stabilized by prolate and oblate particles as the shear stress determined is affected by the particle rotation on the interface.
 
-\begin{figure} 
-    \centering 
-    \includegraphics[scale=0.3]{../figures/results/paper3/angle_to_cartesian-SS.png} 
-    \caption{Comparisons of the initial and final particle orientations of the particles to each cartesian direction under
-             four processing histories for bijels stabilized with oblate and prolate ellipsoids at multiple shear rates. We show
-             shear dependent ordering of the particle monolayer if the initial particle monolayer begins with particle order.} 
-    \label{fig:particle_orientation_cartesian_shear} 
-\end{figure}
-
-From Figure \ref{fig:particle_orientation_cartesian_shear} we see that with bijel templates simulated under $\bar{B} = 0$, the
-particles adopt a random orientation. Upon application of shear, we see that there is little directional ordering to the 
-shear direction in the simulation time observed. Upon application of the magnetic field in the $\bar{B}:0 \rightarrow 1$ case, 
-the particles order to the direction of the magnetic field. Here we see that the prolate particles order more readily to the applied
-field than the oblate particles, seen as a larger clustering of particles at the $\theta_z = 0$ corner of the triangle. In the 
-$\bar{B}:1 \rightarrow 0$ case particle morphology dependent partial relaxation of the particles away from the magnetic field direction 
-is observed. Directionality of the particles to the field is still observed, suggesting that the ordering of the particles is not
-immediately removed once the field is switched off. In the processing history of $\bar{B}:1 \rightarrow 1$, particles are locked
-into ordering to the magnetic field direction. However we also see that some particles are reoriented away from the field direction
-due to the applied shear. Prolate particles have a smaller distribution of particle orientations than oblate particles, suggesting that
-the initial orientation and ordering of particles to the shear applied underpin the response observed. As the particles are adsorbed on the 
-interface, the orientation of the particles are influenced by a balance between magnetic forces from the field and capillary forces 
-from the interface. We can qualitatively calculate the time evolution of the capillary interactions using the interfacial angle.
+We analyzed the angle between each particles symmetry axis and the local interface normal by generating a mesh of the interface using the marching 
+cubes algorithm and, for each particle, identified the nearest mesh vertex (excluding those beyond the length of the particle's long axis). We then calculated 
+the angle $\psi$ between the particle orientation vector \(\hat{\vec{o}}_i\) and the local surface normal. The time evolution of the average interface
+angle of all particles $\langle \psi \rangle$, calculated as a numerical average of $\psi$ for all particles, is shown in Figure~\ref{fig:interface_angle_shear}.
 
@@
 
-From Figure \ref{fig:interface_angle_shear}, we demonstrate that there is a slow increase in the interface angle over time for all cases
-except for $\bar{B}: 0 \to 1$. For the $\bar{B}: 0 \to 1$ case, this has been shown in Chapter \ref{chapter:aim2} to be due to particle
-reorientation to the applied magnetic field. For all other cases, we see an average increase in $\langle \psi \rangle$ over time, showing
-that the particles under shear reorient out of the interface. Particles reorienting out of the interface can be due to shear induced interfacial 
-stress, modifying the curvature of the interface and thus the lowest energy particle orientation to the interface or shear induced increases in
-interparticle forces, causing the particle to tilt out of the interface to minimize interparticle forces. The latter 
-mechanism can be characterized through measurements of the number of particles on the interface as increases in interparticle forces result in ejection of
-particles from the interface.
-
-% We can characterize the impact of the interfacial angle on the 
-% particle packing using the radial distribution function (rdf).
-
-% \begin{figure} 
-%     \centering 
-%     \includegraphics[scale=0.3]{../figures/results/paper3/rdf-SS.png} 
-%     \caption{Comparisons of the initial and final radial distribution function of the particles of bijels stabilized by ellipsoidal 
-%     particles as a function of the applied shear rate at four different processing histories. I show that there are minor differences
-%     in the particle ordering at the interface, suggesting that the particle tilting affects the coverage of particles at the interface.} 
-%     \label{fig:rdf_shear} 
-% \end{figure}
-
-% From Figure \ref{fig:rdf_shear}, I show that the change in the packing of the particles on the interface is not correlated to the change 
-% in the interfacial angle of the particles on the interface when changing the applied field strength in all cases. I then characterize the proportion 
-% of particles on the interface to investigate how the proportion of particles on the interface changes and its impact on the interfacial area.
-
-\begin{figure} 
-    \centering 
-    \includegraphics[scale=0.3]{../figures/results/paper3/n_int-time_compare.png} 
-    \caption{Comparisons of the proportion of particles on the interface of bijels ($n_{int}$) stabilized by ellipsoidal particles as a function of 
-             the applied shear rate at four different processing histories. We show that upon application of shear, many cases have a 
-             reduction in the number of particles on the interface while in others it stays the same. 
-            %  For cases where $n_{int}$ reduces, I can 
-            %  attribute the domain size coarsening to this effect.
-             } 
-    \label{fig:particles_interface_prop_shear} 
-\end{figure}
-
-From the results in Figure \ref{fig:particles_interface_prop_shear}, the impact of the initial microstructure on the number of particles on the interface
-differs for bijels stabilized by oblate and prolate ellipsoids. We split this analysis on processing history. While keeping the applied magnetic field
-the same, little differences in the behavior of $n_{int}$ is observed, with small changes also being characterized for $\langle \psi \rangle$. 
-Looking at the case of $\bar{B}:0 \rightarrow 0$, there is little change in the number of particles at the interface upon application of shear. This implies that the 
-particles remain strongly adsorbed on the
-interface. The $\langle \psi \rangle$ results also show this as this parameter increases slowly. This suggests that the particles remain firmly adsorbed
-on the interface. Looking to the $\bar{B}:0 \rightarrow 1$ case, the number of particles at the interface drops while $\langle \psi \rangle$ increases. This
-trend affects both particles which suggests that shear can pull particles out of the interface due to the decreased
-interfacial adsorption energy the particle experiences when rotating out of the interface to orient to the applied field. The $\bar{B}:1 \rightarrow 1$ and 
-$\bar{B}:1 \rightarrow 0$ have strong dependences on particle morphology. While an increase in $\langle \psi \rangle$ can be seen in both processing histories 
-for both particle morphologies, a decrease in $n_{int}$ can be seen for prolate particles with processing history $\bar{B}:1 \rightarrow 0$ and for 
-oblate particles with processing history $\bar{B}:1 \rightarrow 1$. We visualize $\langle \psi \rangle$ at the initial and final timestep for bijels stabilized with
-oblate and prolate particles with processing $\bar{B}:1 \rightarrow 0$.
-
-\begin{figure} 
-    \centering 
-    \includegraphics[scale=0.4]{../figures/results/paper3/psi_concat_startB-1_endB-0.png} 
-    \caption{Visualization of the particle monolayer of bijels stabilized by prolate and oblate ellipsoidal particles with processing history $\bar{B}: 1 \rightarrow 0$
-             undergoing an applied shear of $Ca_s = 10^{-6}$. Particles with a deeper red shade have a larger angle to the interface. The top and bottom row show the 
-             configuration of the particles at the initial and final timestep respectively.} 
-    \label{fig:particle_viz_psi} 
-\end{figure}
-
-Figure \ref{fig:particle_viz_psi} shows that the increase in $\langle \psi \rangle$ seen in Figure \ref{fig:interface_angle_shear} occurs due to different
-reasons for both particle morphologies. For oblate particles, this is caused by particles orienting such that their symmetry axis is parallel to the interface
-while prolate particles experienced interparticle forces induced by the applied shear, resulting in particles being ejected from the interface when the magnetic 
-field is switched off. When keeping the magnetic field on, the oblate particles are forced to stay in sub-optimal particle orientations to the interface, resuling
-in ejection of particles from the interface. The presence of the magnetic field reduces shear induced interparticle interactions owing to the ordering of
-particles to the applied field, resulting in the mostly unchanged $n_{int}$ values. A increase in $\langle \psi \rangle$ and decrease in $n_{int}$ indicates domain
-can indicate coarsening of the fluid domains as the interfacial area is reduced. In the next section, we investigate the the role of the interface properties and the 
-impact of particle ejection and tilting of particles out of the interface on the microstructure of bijels.
-
-\subsection{Microstructure change}
-
-Bonaccorso et al. identified that the spherical particle stabilizers in their bijel simulations oriented to the direction of shear before being
-ejected from the interface. \cite{bonaccorso_shear_2020} This then led to the domains of the bijel to coalesce and eventually destruction of the
-bicontinuous microstructure. \cite{bonaccorso_shear_2020} In our bijels, we characterize particle morphology and initial microstructure specific 
-properties of the particle monolayer upon application of shear. 
-In this section, we probe the effect of applied shear to the microstructure of magnetically
-responsive bijels stabilized by ellipsoidal particles. To investigate the effect of the particle angle and the interfacial coverage of the bijel on the
-microstructural evolution of the interface, we plot the area averaged gaussian curvature over time. This parameter will allow insight into the evolution 
-of the interface, namely the presence of domain coarsening, coalscence or break-off events.
-
-\begin{figure} 
-    \centering 
-    \includegraphics[scale=0.3]{../figures/results/paper3/gaussian-time_compare.png} 
-    \caption{Plots of the time evolution of the area averaged Gaussian curvature $\langle K \Sigma^{-2} \rangle$ for four 
-             processing histories applied to bijels stabilized with oblate and prolate ellipsoids. We demonstrate that the 
-             magnitude of the gaussian curvature reduces for all systems except for $\bar{B}: 0 \to 1$.} 
-    \label{fig:gaussian_curvature_time_shear} 
-\end{figure}
-
-Figure \ref{fig:gaussian_curvature_time_shear} reveals that the area averaged Gaussian curvature generally decreases in magnitude over time for all cases except 
-$\bar{B}: 0 \to 1$ indicating that the increase in $\langle \psi \rangle$ causes domain coarsening of the bijel. $\bar{B}: 0 \to 1$ is
-unique because particle rearrangements at the interface dominates the dynamics of the microstructure, not observed in all other
-cases. From the time evolution of the curvature, the same mechanism drives coarsening in all cases. From the results in Figures \ref{fig:particles_interface_prop_shear} 
-and \ref{fig:interface_angle_shear}, domain coarsening is driven through a reduction in the interfacial area covered by the particle monolayer. 
-From the curvature results characterized in Figure \ref{fig:gaussian_curvature_time_shear}, the area averaged curvature coarsening is shear independent. This is further
-evidence that the mechanism of coarsening is identical in each case.
-
-\begin{figure} 
-    \centering 
-    \includegraphics[scale=0.3]{../figures/results/paper3/anisotropy_compare.png} 
-    \caption{Comparisons of the time evolution of the directional domain sizes that increase upon application of a magnetic field for bijels stabilized 
-             by ellipsoidal particles undergoing various shear rates under four processes. The directional domain size increases in all cases except for when the
-             field is switched off.} 
-    \label{fig:domain_size_aniso_time_shear} 
-\end{figure}
-
-From Figure \ref{fig:domain_size_aniso_time_shear}, the directional domain sizes in the orientations with the maximum change were characterized. For oblate and prolate 
-particles, this was found to be $L_{\perp}$ and $L_{\parallel}$ respectively. In all cases except for $\bar{B}: 1 \to 0$, this length scale increases matching the expected
-trend that increasing $\langle \psi \rangle$ matches domain coarsening. The decrease in these length scales for $\bar{B}: 1 \to 0$ suggest that the shear induced
-reordering of interfacial particles after application of a field affects the evolution of the microstructure. For both particles, this is due to particle mediated
-shear forces causing domains to coarsen more in specific directions. From the snapshots of the particle arrangement in Figure \ref{fig:particle_viz_psi} the particles were
-shown to reorient at the interface. This process did not occur for $\bar{B}: 1 \to 1$ as the presence of magnetic fields acted to keep particles aligned a specific
-direction.
-
-% Previous investigations have 
-% demonstrated how the orientation and arrangement of particles on the interface affect the domain size. 
-% \cite{gunther_timescales_2014} I focus our investigation on this aspect in the following plot.
-
-% \begin{figure} 
-%     \centering 
-%     \includegraphics[scale=0.3]{../figures/results/paper3/domain_size-time_compare.png} 
-%     \caption{Comparisons of the time evolution of the average domain size for bijels stabilized by ellipsoidal particles undergoing
-%              various shear rates under four processes. Initially, the domain size coarsens for all runs under applied shear before
-%              reducing in some cases.} 
-%     \label{fig:domain_size_time_shear} 
-% \end{figure}
-
-% From Figure \ref{fig:domain_size_time_shear}, domains coarsen with time in all cases. When increasing the applied magnetic field in the case of 
-% $\bar{B}:0 \rightarrow 1$, I see shear assisted domain coarsening characterized as a 20 \% and 10 \% increase in the domain size of bijels
-% stabilized by oblate and prolate particles respectively. This is approximately 5 times greater than the response observed in Figure \ref{fig:domain_size-field_on}
-% In the  $\bar{B}: 1 \to 0$ and $\bar{B}: 1 \to 1$ cases, an initial plateau in domain size is observed, followed by a divergence in 
-% growth depending on $Ca$. The shear rate appears to influence domain coarsening, with higher $Ca_s$ leading to delayed or 
-% suppressed growth, especially in the presence of a field. The difference between applying $\bar{B}: 0 \to 1$ and 
-% removing $\bar{B}: 1 \to 0$ the field demonstrates the stability of the particle monolayer when a field is switched off.
-% There is little difference in the qualitative trends of domain size change for bijels stabilized with oblate or prolate particles.
-% To characterize whether the domain size coarsening observed arises from different phenomena in each case, the area averaged curvature is plotted.
+As shown in Figure~\ref{fig:interface_angle_shear}, the interface angle $\langle \psi \rangle$ generally increases over time across all cases, with the 
+exception of the $\bar{B}: 0 \rightarrow 1$ condition. This indicates shear induced particle reorientation at the interface, indicating that particles are
+being pulled out of the interface. The exception at $\bar{B}: 0 \rightarrow 1$ is consistent with the findings presented in Chapter~\ref{chapter:aim2}, where the 
+observed behavior was attributed to particle reorientation toward the applied magnetic field. In all other cases, the gradual increase in $\langle \psi \rangle$ 
+suggests that particles are progressively reorienting out of the interface under the influence of shear. For oblate particles initialized from bijel templates 
+generated under $\bar{B} = 1$, the average initial interface angle is approximately 40°, indicating a pronounced tilt at the interface. As the tilt angle 
+increases, the energy barrier to rotate a particle further out of the interface decreases, leading to reduced hydrodynamic drag and, consequently, lower 
+effective viscosity. In contrast, the difference in initial interface angle between field- and non-field-aligned bijels stabilized by prolate particles 
+is much smaller—approximately 13.5° and 11.5°, respectively. This smaller variation helps explain the more modest changes in rheological response observed 
+in prolate systems, compared to the more pronounced field-dependent behavior in oblate particle-stabilized bijels.
 
@@
 
-% In this chapter, I investigated the rheology of bijels stabilized by ellipsoidal particles under shear, focusing on the influence of initial microstructure and the 
-% application of a constant magnetic field on their shear response. The shear behavior was characterized using a Herschel-Bulkley fitting function to extract the flow index, 
-% consistency index, and yield stress. My analysis confirmed that the shear-thinning nature of bijels remains robust, regardless of particle morphology or applied magnetic 
-% field. However, the flow index and yield stress trends were strongly dependent on these factors.  
-% I found that increased particle ordering led to distinct yield stress behaviors: oblate particles resulted in a lower yield stress, while prolate particles exhibited a 
-% higher yield stress. When examining the properties of the particle monolayer, I identified a clear impact of particle morphology on interparticle interactions at the 
-% interface. In the absence of a magnetic field, both particle monolayers remained adsorbed at the interface. However, when a magnetic field was initially applied, the 
-% behavior diverged significantly oblate particles flipped out of the interface to minimize interfacial energy, whereas prolate particles tilted out. These differences 
-% directly influenced the shear response, altering how the surrounding fluid flows around the particles and leading to the observed non-Newtonian behavior and yield 
-% stress characteristics.  
-% Furthermore, I investigated the microstructural effects of shear and magnetic field-induced particle ordering and found that coarsening was the primary driver of 
-% domain size evolution in sheared bijels. This coarsening was facilitated by a reduction in interfacial particle coverage. When analyzing the anisotropic domain size evolution, 
-% I observed that in most cases, the direction of greatest structural change aligned with expected trends—except when the magnetic field was switched off. This deviation is 
-% attributed to differences in particle monolayer evolution, depending on whether the bijel was formed with or without an initially applied field.
+In this study, we investigated the rheological behavior of bijels stabilized by magnetically responsive ellipsoidal particles subjected to constant shear. 
+In systems like solvent transfer-induced phase separation (STrIPS) and volatile-induced phase separation (VIPS), rheology plays a key role in determining the
+microstructure and morphology of the bijel. The presence of anisotropic particles and external magnetic fields further complicates this behavior 
+by altering interfacial structure. To systematically probe these effects, we employed a hybrid Lattice Boltzmann-Molecular Dynamics (LBM-MD) simulation 
+framework to evaluate how particle shape, magnetic field history, and interfacial microstructure jointly influence the flow response of bijels. 
+Four magnetic processing pathways were considered—ranging from fully unordered systems to those with persistent particle alignment—across a range of 
+shear capillary numbers. By fitting the resulting stress-strain data to a Herschel-Bulkley model, we characterized the yield stress and degree of shear 
+thinning for each configuration.
 
-The rheological properties of bijels are of importance in many fabrication schemes such as STrIPS and homogenization. \cite{haase_continuous_2015,cai_bijels_2017}
-To characterize how magnetically responsive bijels can be used in these synthesis techniques, we studied the effect of particle morphology, initial microstructure and
-applied magnetic fields on the rheology of bijels experiencing a constant shear. Bijel templates made with $\bar{B} = 0$ and $\bar{B} = 1$ were selected, with field strengths
-of $\bar{B} = 0$ and $\bar{B} = 1$ applied to each template. This results in four processing histories per particle morphology namely $\bar{B}:0 \rightarrow 0$,
-$\bar{B}:0 \rightarrow 1$, $\bar{B}:1 \rightarrow 0$ and $\bar{B}:1 \rightarrow 1$. We then apply a constant shear rate onto each bijel.
+Our results show that bijels exhibit non-Newtonian, shear-thinning behavior regardless of processing history or particle morphology. However, both yield stress 
+and flow index are highly sensitive to the initial degree of particle alignment at the interface. Bijels stabilized by oblate particles demonstrated substantial 
+variation in yield stress across magnetic field histories, with increased ordering correlating with a reduction in stress response. Conversely, bijels stabilized 
+by prolate particles exhibited more consistent rheological behavior, with yield stress increasing in response to magnetic alignment. Systems initialized with 
+fully ordered structures ($\bar{B}:1 \rightarrow 1$) showed the highest resistance to flow for prolate particles, while oblate systems in the same condition 
+yielded more readily.
 
-We first characterized the shear stress imparted by bijels under several strain rates. The shear stress calculated continued to increase in line with expectations
-for colloidal glasses as ageing occurs. Thus a pseudo-steady state was selected to compare the shear properties of the bijel.
-We fit the shear stress data using a Herschel Buckley fit and identify that the flow index of bijels stabilized by ellipsoidal 
-particles under magnetic fields became less shear thinning. The yield stress of bijels stabilized by oblate particles was shown to reduce by 4x while the yield stress
-of bijels stabilized by prolate particles was shown to increase by 2x upon application of magnetic fields.
+To interpret these rheological differences, we analyzed both local structural ordering (via the Steinhardt $Q_6$ parameter) and particle orientation relative to 
+the interface. Increased magnetic alignment in prolate systems led to higher $Q_6$ values and lower interface angles, indicating that particles remained 
+well-anchored to the interface. This ordering enhanced stress distribution, leading to higher yield stress. In contrast, oblate particles 
+tended to tilt further from the interface when aligned, as confirmed by elevated interface angles and decreased $Q_6$, making the monolayer more susceptible to 
+shear-induced buckling and collapse. The increased interface angle of oblate particles after application of a field reduces the torque necessary to rotate particles
+out of the interface, resulting in the larger differences in shear stress calculated for bijels stabilized with oblate particles.
 
-To characterize these differences, closer attention is paid to the particle monolayer of the bijel. Shear induced reorientation of the ellipsoids can be observed in cases
-where a magnetic field was used observed, characterized as the orientation of particles drift away from the magnetic field direction. When analyzing the effect this reorientation
-has on the particles at the interface, the interface angle in all cases increases as a function of the shear rate. However the quantitative behavior of oblate particles differ
-from prolate particles. Under magnetic fields, oblate particles tend to flip out of the interface while prolate particles tilt out of the interface. The impact that
-the particle tilting and flipping out of the interface can also be seen in the number of particles in the interface, where the differences in the particle morphology 
-can be characterized as differences in the number of particles at the interface in response to the magnetic field.
-
-A reduction in the number of particles at the interface and the particles tilting out of the interface reduces the interfacial coverage. The reduction in interfacial
-coverage manifests as domain coarsening, characterized as a smooth decrease in the magnitude of the area averaged Gaussian curvature. The changes in the particle monolayer
-properties manifest as changes in the evolution of the directional domain size evolution due to shear induced particle reorientation at the interface.
-
-Past literature
-has shown how bijels are susceptible to failure when being used as crossflow reactors due to shear induced domain coarsening resulting in microstructure failure. 
-\cite{boakye-ansah_controlling_2020} The investigations conducted here demonstrate that controlling the orientations of particles at interfaces are crucial to 
-the rheological properties of bijels. Other properties not considered here such as different particle aspect ratios, the effect of surface tension on the shear response of
-bijels and the volume fraction of particles are not considered here. Additionally, complex rheology of the bijels can determine detailed rheological properties such as the
-gel point and phase difference of the bijel which can yield further rheological characterization of bijels stabilized by magnetically responsive ellipsoidal particles.
+These findings highlight the interplay between particle anisotropy, interfacial order, and external magnetic fields in tuning the mechanical properties of bijels. 
+By modulating particle alignment through magnetic stimuli, it is possible to tailor the yield stress and flow behavior of these materials—a property of potential 
+interest in fields such as soft robotics, drug delivery, and responsive templating. Moreover, the contrast in behavior between oblate and prolate particles 
+underscores the importance of shape-specific design in engineering structured fluids. In the next chapter, we extend this investigation to consider dynamic or 
+transient shear regimes and explore the reversibility of these structural transitions under cyclic loading and field modulation.

### 2025-04-06 chapters/paper2.tex
Changes 1. Completed rewriting introduction of aim 2

@@
 
-% Stimuli-responsive emulsions have attracted significant interest for applications in enhanced oil recovery, porous material templating, 
-% in-situ reaction separation systems, and drug delivery scaffolds \cite{tang_stimuli-responsive_2016, bago_rodriguez_capsules_2019}. 
-% These applications are facilitated by stimuli-induced microstructural modifications, which alter the permeability, surface area, and 
-% morphology of the emulsion. Advancements in particle synthesis techniques, along with growing concerns over surfactant toxicity and 
-% environmental impact, have contributed to the renewed interest in particle-stabilized emulsions since their initial discovery by Ramsden 
-% and Pickering in 1907 \cite{rozynek_opening_2019, zhou_magnetic_2011}. Stimuli-responsive behavior in these emulsions has been achieved 
-% through changes in pH, temperature, or chemical composition 
-% \cite{maingret_dextran-based_2020, lin_ph-responsive_2018, raju_ph-responsive_2018, zhang_ph_2022}.
+Emulsions can adopt a variety of microstructures depending on fluid volume fractions and the affinity of stabilizing agents for each phase. Among these, bicontinuous 
+interfacially jammed emulsion gels (bijels) are characterized by a tortuous, co-continuous network of immiscible fluid domains stabilized by colloidal particles. This 
+unique architecture lends itself to numerous advanced applications, including membrane fabrication, catalyst supports, battery electrodes, and pharmaceutical delivery 
+systems. Bijels form through the arrest of spinodal decomposition in partially miscible fluid mixtures: as phase separation proceeds, the interface sweeps through the 
+system, adsorbing particles until the interfacial area becomes saturated, resulting in jamming. Microstructural features such as domain size, continuity, and interfacial 
+curvature critically influence material performance, affecting properties like mass transport, mechanical stability, and surface reactivity. Since their discovery via 
+simulation and subsequent experimental realization, research on bijels has expanded significantly, exploring diverse synthesis conditions and scalable processing methods.
 
-Due to their tortuous, co-continuous domain morphology, bijels have been 
-extensively studied for applications in membrane fabrication, catalyst supports, battery electrodes, and pharmaceutical 
-products \cite{yabuno_preparation_2020, samdani_bicontinuous_2017, cha_bicontinuous_2019, garcia_scalable_2019, santiago_cordoba_aerobijels_2020}.  
-Bijels form through the arrested spinodal decomposition of partially miscible fluids 
-\cite{stratford_colloidal_2005, herzig_bicontinuous_2007, tavacoli_novel_2011}. During phase separation, the emerging interface propagates 
-through the system, driving particle adsorption. Once the available interfacial area matches the total cross-sectional area of the adsorbed 
-particles, the structure becomes jammed in place \cite{stratford_colloidal_2005, herzig_bicontinuous_2007, tavacoli_novel_2011}. Since their 
-initial discovery in simulations and subsequent experimental synthesis, a diverse body of literature has emerged, exploring fluid systems 
-compatible with bijel formation, scalable fabrication techniques, and potential applications.
+The functional properties of bijels are inherently linked to their internal structure. For instance, lower tortuosities in the direction of ion transport yield improved 
+charge rates and cycling stability in battery electrodes \cite{ebner_tortuosity_2014, samdani_bicontinuous_2017}. In liquid-liquid extraction, the characteristic pore 
+lengthscale determines molecular selectivity \cite{khan_nanostructured_2022}, while in pharmaceutical applications, domain size influences drug release rates and cellular 
+behavior \cite{vanoli_bijels_2022, thorson_bijel-templated_2019}. Given the sensitivity of these properties to microstructural characteristics, the ability to dynamically 
+modify the morphology of bijels presents a promising strategy to adapt their behavior in situ for targeted performance.
 
-Bijels stabilized by ellipsoidal particles exhibit distinct domain evolution timescales compared to those stabilized by 
-spherical particles \cite{gunther_timescales_2014}. Unlike spherical particles, ellipsoidal particle reorientation at the 
-interface influences microstructure. After jamming, additional timescales emerge due to capillary interactions that drive 
-particle reorientation and prolonged domain coarsening \cite{gunther_timescales_2014}. Bijels behave as 2D glasses percolating 
-in 3D space, with locally jammed particles as observed by Günther et al. 
-\cite{ching_bijel_2022, torquato_jammed_2010, gunther_timescales_2014}. Studies on jammed suspensions indicate subdiffusive 
-particle movement, further confirming local jamming in bijel monolayers \cite{savelev_diffusion_2006}.
+Stimuli-responsive emulsions have garnered increasing interest for applications requiring dynamic control over material properties, including enhanced oil recovery, reaction 
+separation, and therapeutic delivery \cite{tham_magnetophoresis_2021, cui_stabilizing_2013, rozynek_opening_2019, lu_controllable_2020}. These systems operate by using 
+external stimuli to alter interfacial configurations, enabling modulation of permeability, interfacial area, and morphology. For example, in emulsions stabilized by 
+spherical particles, electric fields can induce droplet deformation via particle unjamming and migration before re-establishing interfacial jamming \cite{cui_stabilizing_2013}. 
+Among various external stimuli, magnetic fields are particularly attractive due to their remote addressability, material compatibility, and bio-relevance. 
+Core-shell ferrite-hydroxyapatite nanorods, for instance, exhibit reversible morphological changes depending on initial particle orientation and field direction 
+\cite{nakayama_stimuli-responsive_2018}. In magnetically stabilized Pickering emulsions, magnetophoresis has been shown to drive particle migration and interfacial 
+distortion or collapse \cite{tham_magnetophoresis_2021, yang_rapid_2020, misra_magnetic_2020}. Notably, Karthikeyan and Schiller demonstrated that magnetic fields applied 
+during bijel formation can bias domain coarsening, producing anisotropic microstructures via orientation-specific jamming \cite{karthikeyan_formation_2024}. However, the 
+structural response of bijels to magnetic fields after formation remains poorly understood.
 
-Magnetic fields have gained interest as external stimuli due to their targeted interactions, biocompatibility, and material 
-versatility. The structural response of magnetically responsive hydroxyapatite crystals depends on initial particle orientation
-\cite{nakayama_stimuli-responsive_2018}. Magnetophoresis, where particles move along field lines, has been observed in Pickering 
-emulsions stabilized by magnetic microspheres \cite{tham_magnetophoresis_2021}. Structural deformation and de-emulsification occur due 
-to particle migration or tilting at the interface \cite{yang_rapid_2020, misra_magnetic_2020}. However, how these effects influence 
-bijel microstructure post-jamming remains unclear. Given the locally jammed nature of bijels, magnetic field responses, combined with 
-anisotropic particle stabilization, may offer a means to control bijel microstructure.
+This study investigates the post-formation structural response of bijels stabilized by ellipsoidal magnetic particles under the influence of externally applied magnetic fields. 
+Using a hybrid Lattice Boltzmann Method coupled with Molecular Dynamics, we simulate the formation and evolution of bijel structures stabilized by rod-like particles modeled as 
+magnetic dipoles. We find that increasing the applied magnetic field after formation induces significant microstructural changes, including increased domain anisotropy and 
+coarsening, up to a saturation threshold. In contrast, decreasing or removing the magnetic field results in minimal morphological change, suggesting a strong hysteresis effect. 
+Analysis reveals that particle unjamming, reorientation at the interface, and subsequent re-jamming are responsible for these structural transformations.
 
-This work investigates the structural response of bijels stabilized by anisotropic magnetic particles. Using a Lattice Boltzmann Method 
-coupled with Molecular Dynamics, we simulate a binary fluid system where ellipsoidal particles, modeled as magnetic dipoles along their 
-symmetry axis, stabilize bijel templates. Magnetic fields applied to bijels made without a magnetic field reveal anisotropic bijel formation, 
-with microstructure evolution dependent on particle reordering at the interface, quantified using the six-fold 
-Steinhardt order parameter $\langle Q6 \rangle$.
-
-We further assess how initial microstructure influences structural changes, showing that the difference in order between initial and final 
-configurations of the particle monolayers dictates the extent of microstructure evolution if the applied field is increased in the direction of 
-the existing order. Additionally, applying and removing a 
-magnetic field results in distinct microstructural properties and timescales, highlighting the importance of processing history. These findings 
-demonstrate how magnetic fields, combined with anisotropic particle-stabilized bijels, enable on-demand microstructure switching for potential applications.
+To understand the saturation behavior, we applied magnetic fields of varying strength to bijel templates formed under increasing initial field conditions. We observed that 
+a greater initial nematic order parameter negatively correlated with the extent of microstructure change. Finally, switching off the magnetic field in pre-aligned bijels had little 
+impact on the microstructure, indicating that the jammed interfacial network prevents reversal of anisotropic features. These findings underscore the importance of processing 
+history and demonstrate how magnetic field manipulation, in combination with anisotropic particle stabilization, enables tunable, on-demand microstructure control in bijels, 
+offering new capabilities for adaptive material design.
 

### 2025-04-06 chapters/paper2.tex
Changes 1. Rewrote all of aim 2 except conclusion

@@
 \section{Results}\label{sec:results_p2}
-\subsection{Hysteresis curve}\label{section:hysteresis_curve}
+\subsection{Hysteresis curve}
+\label{section:hysteresis_curve}
 
-Bijels have proposed applications as soft matter based material templates, drug delivery vectors and separations systems. The materials 
-performance in each application is dependent upon the microstructure of the bijel template. Many of the applications listed above benefit 
-from stimuli response, allowing for in-situ microstructure tuning to offer reversible modifications of material permeability. In this section, we analyze
-whether stimuli responsive bijels provide access to reversible structural modifications.
+Bijels have proposed applications as soft-matter-based material templates, drug delivery vectors, and separation systems. In all cases, material performance is 
+tightly coupled to the internal microstructure of the bijel template. Applications that benefit from adaptive permeability or structural tunability would be 
+enhanced by the ability to reversibly modulate microstructure in situ. This section explores whether magnetically responsive bijels can undergo reversible 
+structural changes upon repeated application and removal of an external magnetic field.
 
-We begin our investigation by characterizing the microstructure changes observed on bijels stabilized with prolate ellipsoids with a 
-particle volume fraction of $\phi_p = 0.1$. We only focus on one system here as the mechanism for stimuli response shown in Aim 1 is identical
-for both systems. Therefore We expect that the qualitative trends between prolate and oblate particles will be matched. We select prolate particles
-as they are more readily synthesizable in experiments.
+We begin by analyzing bijels stabilized by prolate ellipsoidal particles at a particle volume fraction of \(\phi_p = 0.1\). This system is selected due to the 
+similar qualitative response mechanisms observed for both prolate and oblate geometries in preliminary simulations (Aim 1), with prolate particles chosen here 
+for their greater experimental accessibility. The bijel is initially formed without a magnetic field. After equilibration, a static magnetic field is applied 
+in the \(z\)-direction and incrementally increased: \(\bar{B}_z = 0 \rightarrow 0.2 \rightarrow 0.5 \rightarrow 1\). This is followed by a symmetric 
+decrement: \(\bar{B}_z = 1 \rightarrow 0.5 \rightarrow 0.2 \rightarrow 0\). At each step, the system is allowed to evolve to a new equilibrium, defined as
+the plateauing of the length scale obtained from the domain size, \(L\), computed from the first moment of the spherically averaged structure factor.
+\cite{kendon_3d_1999,kendon_inertial_2001} The structure factor is calculated from the density fields as,
 
-We apply a constant magnetic field of $\bar{B}_z = 0.2$ onto bijels that were simulated 
-with no magnetic field. Once the microstructure has reached its new state, we ramp up the magnetic field to $\bar{B}_z = 0.5$ and 
-finally $\bar{B}_z = 1$. We then apply the opposite procedure to reduce the applied field strength, resulting in a magnetic field 
-ramp of $\bar{B}_z: 0 \rightarrow 0.2 \rightarrow 0.5 \rightarrow 1 \rightarrow 0.5 \rightarrow 0.2 \rightarrow 0$. We characterize the 
-microstructure changes observed through calculating the domain size, defined as the first moment of the spherically averaged structure factor. 
-We calculate the hysteresis 
-curve by selecting the domain size at the final timestep of each magnetic field change. We then plot these domain sizes against the magnetic field 
-applied to obtain them and split them in the descending and ascending magnetic field directions to demonstrate the differences observed. We plot 
-these results in Figure \ref{fig:hysteresis_curve}
+%
+\begin{equation}
+S(\vec{k},t) = \tilde{\phi}(\vec{k},t)\tilde{\phi}(-\vec{k},t) .
+\end{equation}
+%
+where \(\tilde{\phi}(\vec{k},t)\) is the Fourier
+transform of the order parameter fluctuations
+\(\phi(\vec{x},t)-\left\langle\phi\right\rangle\). Spherical averaging is 
+done by averaging the values of the structure factor where $k = |\vec{k}|$ is in
+the same bin, defined as
+
+%
+\begin{equation}
+S(k,t) = \frac{1}{n_k} \sum_{k-\frac{\Delta}{2}<k<k+\frac{\Delta}{2}} \tilde{\phi}(\vec{k},t)\tilde{\phi}(-\vec{k},t) ,
+\end{equation}
+
+The lengthscale is then defined as
+
+\begin{equation}
+    L = \frac{2 \pi}{\frac{ \sum_k S(k, t)k }{\sum_k S(k, t)}}
+\end{equation}
+
+The hysteresis behavior is shown in Figure~\ref{fig:hysteresis_curve}, which plots the normalized domain size \(L/R\) as a function of the applied magnetic 
+field at the end of the equilibration step.
 
@@
 
-Figure \ref{fig:hysteresis_curve} demonstrates the hysteresis response of the bijel microstructure, characterized by a difference in the average domain size
-when increasing and decreasing the magnetic field. The increase in the average domain size when applying the magnetic field is due to domain coarsening caused by 
-reorientation of particles to the magnetic field strength, reducing the interfacial coverage. When decreasing the magnetic field strength, 
-the domain size does not return to the original value meaning that that the microstructure of the bijel is unaffected by 
-the reduction and eventual removal of the applied magnetic field.
+The hysteresis behavior is shown in Figure~\ref{fig:hysteresis_curve} demonstrates that as the field is increased, domain size increases, indicating coarsening 
+of the fluid domains in the bijel. Karthikeyan and Schiller showed that application of magnetic fields cause reordering of particles at interfaces towards the
+direction of the applied field, making the particle monolayer have nematic ordering. In the case of already formed bijels,
+this reorientation likely reduces the interface area stabilized, facilitating local unjamming and domain growth. In contrast, when the field strength is reduced, 
+the domain size does not revert to its original value, suggesting that the microstructure remains kinetically arrested in the coarsened configuration. This 
+irreversibility confirms a hysteretic response of the bijel structure to magnetic field cycling.
 
-This behavior is also observed in past work investigating the shape deformation of particle stabilized emulsions under 
-electric fields. \cite{cui_stabilizing_2013} Cui et al. demonstrated that the particles unjammed and rejammed into a new kinetically arrested state resulting in
-the droplet being elongated in the direction of the applied field. This suggests that the particles at the interface of magnetically responsive bijels are in
-in a kinetically trapped configuration. Cui et al. used spherical particles in their emulsion response experiments while we use ellipsoidal particles. Additionally,
-Figure \ref{fig:hysteresis_curve} shows that the response of the bijel is dependent upon the field strength applied.
-In the following sections, we investigate the impact of magnetic field strength and the initial ordering of the particle monolayer on the observed stimuli response.
+A similar phenomenon has been reported by Cui et al.~\cite{cui_stabilizing_2013} in studies of particle-stabilized emulsions subjected to electric fields, 
+where spherical particles unjammed and subsequently rejammed in a new configuration, resulting in anisotropic droplet deformation. Our results extend this 
+concept to jammed, bicontinuous systems stabilized by anisotropic particles. Notably, Figure~\ref{fig:hysteresis_curve} also shows that the degree of 
+structural change is field-strength dependent, indicating that stronger fields drive more extensive particle reconfiguration. In the following sections, 
+we investigate how the magnitude of the applied field and the initial degree of particle ordering influence the extent and reversibility of microstructural 
+evolution in magnetically responsive bijels.
 
-\subsection{Field strength dependence on domain size}
+\subsection{Switching a field onto a bijel with disordered particles}
+\subsubsection{Field strength dependence on domain size}
 \label{section:field-strength-dependence-on-domain-size}
 
-From the results in Figure \ref{fig:hysteresis_curve}, we show that the domain size change is dependent upon the applied magnetic field. As porous materials templates,
-the microstructure of the material is of interest as it controls the performance of the material. Additionally, in many of the proposed stimuli responsive applications
-for bijels, the timescales of response is important to characterize and would also provide a mechanistic understanding of the reasons why the microstructure changes 
-occur. In this section, we analyze the structural response of bijels by assessing the response of bijels stabilized by particles with volume fraction of 
-$\phi_p = 0.1$ simulated under no applied field to an applied field in the range $\bar{B} = 0, 0.2, 0.5, 1$. We begin our investigation by visualizing the structure before 
-and after the application of magnetic fields.
+The results presented in Figure~\ref{fig:hysteresis_curve} demonstrate that changes in bijel domain size are dependent on the strength of the applied magnetic 
+field. For applications where bijels serve as porous material templates, microstructural characteristics directly govern performance metrics such as permeability, 
+selectivity, and mechanical stability. Furthermore, in many proposed stimuli-responsive applications, understanding not only the extent but also the mechanism
+of structural response is critical for functionality and control. In this section, we investigate the dynamic structural response of bijels stabilized by randomly 
+oriented ellipsoidal particles with a volume fraction of \(\phi_p = 0.1\), initially formed without a magnetic field. Magnetic fields of varying strengths 
+(\(\bar{B} = 0, 0.2, 0.5, 1\)) are applied to these pre-formed structures to assess how the microstructure evolves under external stimuli. We begin by visualizing 
+the microstructure of bijels stabilized by prolate particles before and after field application.
 
@@
 \includegraphics[scale=0.4]{../figures/results/paper2/microstructure_viz-field_on.png} 
-\caption{Visualizations of bijels stabilized by oblate and prolate particles simulated under no fields at $t = 0$ (left columns) and $t = 10^5$ (right columns). The first 
-         and third row detail the microstructure evolution for oblate and prolate particle stabilized bijels with no applied field while the second and fourth rows show 
-         bijels stabilized by oblate and prolate particles respectively with a field strength of $\bar{B} = 1$ applied. Particle reorientation to the direction of the 
-         field can be seen upon application of the magnetic field, resulting in microstructure changes driven through domain coarsening until the particles jam. We see 
-         similar behavior in bijels stabilized by oblate particles upon application of the magnetic field.}
+\caption{Visualizations of bijels stabilized by prolate particles simulated under no fields at $t = 0$ (left columns) and $t = 10^5$ (right columns). The top 
+         row detail the microstructure evolution for bijels with no applied field while the bottom rows show bijels stabilized by oblate and prolate particles 
+         respectively with a field strength of $\bar{B} = 1$ applied.}
 \label{fig:microstructure_viz-field_on} 
@@
 
-In Figure \ref{fig:microstructure_viz-field_on} we show representative snapshots of the bijel at the initial and final timestep with $\bar{B}_z = 0$ and $\bar{B}_z = 1$. 
-Upon application of the field, particles align to the direction of the field. As the particles orient to the field, they disrupt the packing of particles at
-the interface. This causes domain coarsening as the particles rearrange into new positions before rejamming in place once the interfacial
-area and particle cross sectional area match. Domain coarsening observed in the figure can be explained through the ordering of particles at the interface, causing a 
-reduction in the available area that the particles have for stabilization. To characterize the length scale of the microstructure upon application of the magnetic field,
-we calculate the domain size. To correlate the microstructure evolution to the ordering of the particle monolayer to the magnetic field, we overlay the time evolution of the
-nematic order parameter on the domain size. \cite{veerman_phase_1992}
+Figure~\ref{fig:microstructure_viz-field_on} shows that at zero field, the fluid domains exhibit an isotropic, co-continuous morphology with particles randomly 
+distributed and oriented at the fluid interface. Upon applying a magnetic field (\(\bar{B}_z = 1\)), the particles undergo reorientation along the field direction, 
+which visibly alters the interfacial configuration and the domain morphology. 
+To quantitatively characterize this response, we compute the average domain size as a function of time and magnetic field strength. Additionally, to assess 
+how particle alignment contributes to the structural transition, we overlay the evolution of the nematic order parameter with the domain size. This correlation 
+provides insight into the mechanistic role of particle ordering in driving microstructural transformation under applied magnetic fields \cite{veerman_phase_1992}.
+The nematic order parameter is calculated from the orientations of the particles as
+
+\begin{equation}
+\tens{Q} = \frac{1}{n_p} \sum_i \left( \frac{3}{2} \hat{\vec{o}}_i \otimes \hat{\vec{o}}_i -\frac{1}{2}\mathsf{1} \right) ,
+\end{equation}
+
+where \(\hat{\vec{o}}_i\) is the orientation of the \(i\)-th particles and \(n_p\) is the number of particles in the system. The largest eigenvalue of 
+\(\tens{Q}\) yields the nematic order parameter
+
+\begin{equation}
+S = \left\langle \frac{3}{2}\cos^2 (\theta) - \frac{1}{2} \right\rangle ,
+\end{equation}
+
+where \(\theta=\arccos(\hat{\vec{o}}_i\cdot\hat{\vec{n}})\) is the angle between the particle orientation and the nematic director \(\hat{\vec{n}}\). We plot $S$
+and $L$ over time in Figure \ref{fig:domain_size-field_on}
 
@@
 \includegraphics[scale=0.5]{../figures/results/paper2/domain_size-field_on.png} 
-\caption{Plotting the spherically averaged domain size normalized with $R_p$($L/R$) of the particle at different magnetic field strengths, $\bar{B}$, and the nematic order 
-         parameter $S$ in lines. We quantify the domain size and ordering of the particles, and show that the change in both parameters are correlated with the strength of 
-         the applied magnetic field.} 
+\caption{Plots of the time evolution of the normalized domain size \(L/R\) (markers) and nematic order parameter 
+         \(S\) (lines) for bijels stabilized by oblate (left, \(\alpha = 0.5\)) and prolate (right, \(\alpha = 2.0\)) ellipsoidal particles under varying 
+         magnetic field strengths. Here, \(R = 7.9\) is the volume-equivalent sphere radius.} 
 \label{fig:domain_size-field_on} 
@@
 
-We normalized the domain size results by the volume equivalent sphere radius, $R = 7.9$ in Figure \ref{fig:domain_size-field_on} The results indicate that upon 
-applying a magnetic field to a bijel initially formed without one, the final average domain size increases by up to 5.2\% and 2.5\% for oblate and 
-prolate particle stabilized bijels respectively. The domain coarsening is initially slow, before accelerating rapidly and finally reaching a maximum where it plateaus. 
-Additionally, in the absence of an external field, domain coarsening occurs for both particle morphologies. However, the results
-for oblate particles with a magnetic field is attributed to coalescence of domains rather than magnetic field driven ordering of the particles.
+The results show that applying a magnetic field to bijels 
+initially formed without one induces domain coarsening, with the final domain size increasing by up to 5.2\% for oblate and 2.5\% for 
+prolate particle-stabilized systems.
+In both oblate and prolate systems, domain coarsening follows a characteristic three-stage evolution: an initial slow growth phase, a period of rapid 
+coarsening, and eventual plateauing as the structure reaches a new jammed configuration. Even in the absence of a magnetic field (\(\bar{B}_z = 0\)), 
+domain growth is observed driven by steric rearrangement of interfacial particles, consistent 
+with findings by Günther et al.~\cite{gunther_timescales_2014}. Notably, the initiation of domain coarsening under applied magnetic fields is more rapid 
+for bijels stabilized by oblate particles compared to prolate systems. However, the rejamming process takes longer.
 
-In the same figure, the time evolution of the nematic order parameter $S$ is also plotted to illustrate changes in particle alignment.
-Initially, at $\bar{B}_z = 0$, a gradual increase in $S$ is observed, attributed to steric interactions driving particle reordering.
-This effect contributes to the domain coarsening seen in the absence of an applied field, consistent with the findings of Günther et
-al. \cite{gunther_timescales_2014}. In the case of oblate particle stabilized bijels without an external field, domain
-coalescence is primarily driven by steric interactions rather than field-induced rearrangement. Furthermore, the rate and extent of
-particle alignment to the field exhibit a dependence on field strength, as evidenced by the earlier onset of nematic ordering with increasing
-$\bar{B}$. A time delay between the evolution of the nematic order parameter and domain size, particularly when comparing results for
-$\bar{B}_z = 0.5, 1$ against those for $\bar{B}_z = 0.2$ are seen. This suggests that nematic ordering alone may not fully account for the
-observed changes in domain size.
+In the absence of magnetic fields, a slight increase in $S(t)$ is observed, consistent with the sterically driven reorientation of particles at the interface.
+\cite{gunther_timescales_2014} Upon application of a magnetic field, the curves for \(S(t)\) increase before plateauing, indicating the parameter has reached
+its saturation value. Notably at stronger field strengths, $S(t)$ precedes the increase in domain size for both particle shapes analyzed. This time lag suggests 
+that nematic ordering is a precursor, but not the sole driver, of domain coarsening. Overall, these results confirm that domain coarsening in magnetically 
+responsive bijels occurs as a result of applied magnetic fields, with the degree of change observed dependent on the strength of the applied field.
 
-Previous studies have demonstrated that microstructural properties such as the length scale and tortuosity, play an important role in the
-performance of porous materials across various applications, including battery electrodes and tissue engineering. \cite{zhang_promoting_2019}
-\cite{ebner_tortuosity_2014} \cite{hsieh_architected_2021} Specifically, lower tortuosity and more ordered ion-conducting domains have been shown
-to enhance charge/discharge rates in battery systems, while controlled tortuosity in artificial bone grafts facilitates improved cell growth
-and nutrient transport.
+\subsubsection{Particle reorientation at the interface}
 
-Precise characterization of the anisotropic microstructure is essential for the tailored design of application-specific porous materials. To
-quantify the characteristic length scales in each Cartesian direction, we compute the second-moment-derived structure factor. \cite{jansen_bijels_2011} 
-We make a further refinement simplifying the domain sizes to directions parallel and orthogonal to the magnetic field. These result in the length scales and
-their associated calculation, $L_{\parallel} = L_{z}$ and $L_{\perp} = \frac{L_x + L_y}{2}$. The same simplification
-with the directional tortuosities is also performed.
+Building on the observed time lag between the onset of particle alignment and domain coarsening, we next investigate the underlying dynamics of particles at the 
+interface. While nematic ordering appears to precede structural changes, the delayed increase in domain size at higher magnetic field strengths suggests that 
+additional factors influence the system's response. In this context, capillary interactions between particles and the fluid interface, as well as steric hindrance 
+from neighboring particles, may act to resist or slow particle rearrangement, thereby affecting the timescale of domain evolution. To better understand these 
+phenomena, we focus on the dynamic behavior of the interfacial particle monolayer. As a first step, we visualize the initial and final configurations of bijels 
+stabilized by prolate ellipsoids before and after application of a magnetic field, providing qualitative insight into particle displacement and reorganization 
+at the interface.
 
-Tortuosity has been defined using the geometric, diffusional and hydraulic tortuosities. The tortuosity calculated here is
-the diffusional tortuosity, $\tau = \frac{D}{D_{eff}}$ which characterizes the ratio between the free diffusion of a tracer and the
-effective diffusion of a tracer in the material. We plot the directional second moment derived length scales and tortuosity in
-Figure \ref{fig:domain_size_aniso-field_on}.
+\begin{figure} 
+\centering 
+\includegraphics[scale=0.2]{../figures/results/paper2/particle_viz-field_on.png} 
+\caption{Visualizations of bijels stabilized by prolate ellipsoidal particles at the initial and final timesteps, 
+         both in the absence of a magnetic field (top row) and with a magnetic field applied (\(\bar{B}_z = 1\), bottom row). Particle reorientation to the
+         applied field can be observed.} 
+\label{fig:particle_viz-field_on} 
+\end{figure}
+
+The snapshow shows that in the absence of a magnetic field, minor variations in particle orientation and position occur due to steric interactions, as 
+previously observed by Günther et al.~\cite{gunther_timescales_2014}. However, the application of a magnetic field induces clear orientational ordering of the 
+particle monolayer, with particles aligning along the field direction and reorganizing into distinct interfacial arrangements. These changes suggest that both 
+capillary forces and steric hindrance are modified upon field application. While particles naturally prefer to lie flat at the interface to minimize interfacial 
+adsorption energy, the applied field competes with this tendency, reorienting the particles and disrupting their initial packing.
+
+To quantify the orientation of the particles relative to the interface, we analyzed the angle between each particles symmetry axis and 
+the local interface normal. We generated a mesh of the interface using the marching cubes algorithm and, for each particle, identified the nearest mesh vertex 
+(excluding those beyond the length of the particle's long axis). We then calculated the angle \(\psi\) between the particle orientation vector 
+\(\hat{\vec{o}}_i\) and the local surface normal. We plot the time evolution of $\psi$ in Figure \ref{fig:interface_angle-field_on}.
+
+\begin{figure} 
+    \centering 
+    \includegraphics[scale=0.5]{../figures/results/paper2/psi-field_on.png} 
+    \caption{Plots of the evolution of the average interface angle \(\langle \psi \rangle\) over time for bijels stabilized 
+             by oblate (left) and prolate (right) ellipsoidal particles under varying magnetic field strengths. The response of \(\langle \psi \rangle\) 
+             differs notably between the two particle morphologies.} 
+    \label{fig:interface_angle-field_on} 
+\end{figure}
+
+For bijels stabilized by oblate particles, \(\langle \psi \rangle\) initially increases from approximately \(19^\circ\), indicating that the particles, which begin 
+in an approximately flat configuration at the interface, begin to tilt out of the plane in response to the applied field. After a brief decrease or plateau, the angle 
+resumes increasing before stabilizing. This behavior suggests that particles first reorient under magnetic torque but are temporarily resisted by interfacial tension 
+and capillary constraints. Once the interface begins to deform in response to particle tilt, the system eventually jams in a new configuration, locking the particles 
+at an elevated angle. Both the rate of initial tilt and the duration of the plateau phase increase with field strength, and the final value of 
+\(\langle \psi \rangle\) is positively correlated with the magnitude of the applied field.
+
+For bijels stabilized by prolate particles, a similar but more subtle trend is observed. The initial value of \(\langle \psi \rangle\) starts around \(10^\circ\), 
+gradually increases, and then exhibits a small plateau followed by a slight decline. While the rate and magnitude of the initial increase are field-dependent, 
+the final values converge more closely across different field strengths, suggesting that the field sensitivity of interface tilt is weaker for prolate particles. 
+The overall changes in \(\langle \psi \rangle\) are also smaller in magnitude compared to those in oblate systems, indicating that prolate particles experience 
+less pronounced reorientation at the interface.
+
+While the interface angle \(\langle \psi \rangle\) provides insight into the out-of-plane orientation of particles in response to magnetic field application, 
+it does not capture how particles reorganize at the interface, observed in Figure \ref{fig:microstructure_viz-field_on} Since the evolution of microstructure is 
+influenced not only by tilt but also by the steric effects of interfacial particles, we also assess the Steinhardt bond orientational parameter. 
+We compute the six fold bond orienational parameter $q_6$ which measures the degree of hexagonal arrangement of particles at the interface.
+\cite{steinhardt_bond-orientational_1983, lechner_accurate_2008, mickel_shortcomings_2013} These parameters characterize the local structural ordering by projecting 
+the orientations of neighboring particles onto spherical harmonics of degree \(l\), and are defined as
+
+\begin{equation}
+q_l(i) = \left( \frac{4\pi}{2l+1} \sum_{m=-l}^{l} \left| \frac{1}{N(i)} \sum_{j=1}^{n(i)} Y_{lm}(\vec{r}_{ij}) \right|^2 \right)^{\frac{1}{2}} ,
+\end{equation} 
+%\TODO{update formula to the one actually used}
+
+Here, \(n(i)\) denotes the number of nearest neighbors of particle \(i\), \(\vec{r}_{ij}\) is the vector connecting the centers of particles \(i\) and \(j\), and 
+\(m\) is an integer ranging from \(-l\) to \(l\) that indexes the spherical harmonic components \(Y_{lm}\). Neighbor lists are typically defined using a fixed cutoff 
+radius around each particle, identifying nearby particles as neighbors. We calculate the python package Freud to calculate the bond order parameters and use a Voronoi 
+cell to determine the particle neighborhood rather than the standard distance criterion \cite{ramasubramani_freud_2020,mickel_shortcomings_2013}. The Voronoi-based 
+method avoids the need for a predefined cutoff and yields more robust neighbor definitions, particularly in disordered systems. Bond orientational order parameters 
+have been widely employed to study structural transitions in colloidal and ceramic systems, including crystallization, nucleation, and glass formation 
+\cite{vagberg_glassiness_2011, besseling_three-dimensional_2007, schall_structural_2007, ozawa_jamming_2012} We plot the time evolution of $\psi$ in Figure 
+\ref{fig:Q6-field_on}.
+
+\begin{figure} 
+    \centering 
+    \includegraphics[scale=0.5]{../figures/results/paper2/Q6-field_on.png} 
+    \caption{Plots of the time evolution of the six-fold Steinhardt bond order parameter \(\langle Q_6 \rangle\) for bijels 
+             stabilized by oblate (left) and prolate (right) ellipsoidal particles under varying magnetic field strengths. The dynamics of interfacial ordering differ 
+             significantly between particle morphologies with \(\langle Q_6 \rangle\) decreasing over time for oblate particles and increasing for prolate particles.} 
+    \label{fig:interface_angle-field_on} 
+\end{figure}
+
+From Figure \ref{fig:interface_angle-field_on} the time evolution of \(\langle Q_6 \rangle\) can be qualitatively divided into three regimes;
+an initial transition period, a plateau, and a final reordering or jamming phase.
+For oblate particles, application of the magnetic field initially causes a sharp decrease in \(\langle Q_6 \rangle\), reflecting a disruption of the 
+pre-existing interfacial order as particles begin to tilt and rearrange. This is followed by a plateau, during which ordering is temporarily suppressed 
+as particles continue reorienting. Finally, \(\langle Q_6 \rangle\) begins to increase gradually, indicating partial recovery of local order as the system 
+evolves toward a new jammed state. The rate of change of \(\langle Q_6 \rangle\) significantly decreases toward the end of the simulation, suggesting the onset 
+of kinetic arrest. The final value of \(\langle Q_6 \rangle\) is dependent on the applied magnetic field strength, with higher field strengths 
+resulting in lower final ordering, potentially due to increased variance in the interfacial angle, reducing packing efficiency.
+
+In contrast, for bijels stabilized by prolate particles, \(\langle Q_6 \rangle\) increases monotonically with time after the field is applied. The degree 
+of ordering and the rate of increase both scale positively with magnetic field strength. The early stage is characterized by a modest rise in \(\langle Q_6 \rangle\), 
+followed by a more rapid growth and eventual plateau, indicating progressive in-plane reordering of the particle monolayer as alignment along the field direction 
+becomes dominant. The timing and extent of these regimes are also field-dependent with stronger fields result in earlier onset of ordering and higher final values 
+of \(\langle Q_6 \rangle\). Notably, for all applied fields, the final ordering significantly exceeds that of the zero-field case. These results highlight that the 
+response of interfacial particle order to magnetic fields is morphology-specific as oblate particles undergo a disruption and partial recovery of order, 
+while prolate particles experience continuous enhancement of local ordering.
+
+\subsubsection{Microstructural effects of particle reordering}
+
+Karthikeyan and Schiller identified that the reorientation of particles at the interface due to the application of magnetic fields caused domain size anisotropy
+driven by the directional cessation of domain coarsening. \cite{karthikeyan_formation_2024} In this study, we have established that the mechanism of domain size change
+arises from magnetic field driven rotations of particles at the interface, causing unjamming of the particle monolayer before rejamming and locking in the new
+microstructure. Due to the differences in mechanism, we turn to investigate the anisotropic microstructure of the bijel at the final timestep.
+
+We probe the domain anisotropy using the directional second moment of the structure factor, computed along each Cartesian axis from the full structure factor shown
+below. \cite{jansen_bijels_2011, gunther_timescales_2014}. 
+    %
+    \begin{equation}
+    L_\beta(t)=2\pi\sqrt{\frac{\sum_{\vec{k}}S(\vec{k},t)}{\sum_{\vec{k}}k_\beta^2 S(\vec{k},t)}} .
+    \end{equation}
+    %
+    This allows us to compute a domain size parallel
+    (\(L_\parallel=L_z\)) and perpendicular (\(L_\perp=(L_x+L_y)/2\)) to the
+    direction of \(\vec{B}\) separately. The average domain size \(L_d(t)\)
+    is computed as \(L_d(t)=\sum_\beta L_\beta(t) / 3\).
+    %
+    \begin{equation}
+    L_d(t)=2\pi\sqrt{\frac{\sum_{\vec{k}}S(\vec{k},t)}{\sum_{\vec{k}}\sum_\beta k_\beta^2 S(\vec{k},t)}} .
+    \end{equation}
+    %
+Previous studies have also shown that a domain size increase is usually accompanied by a decrease in
+tortuosity. \cite{karthikeyan_formation_2024} To determine whether these structural 
+changes impact macroscopic transport properties, we also analyzed the tortuosity of the bijels. We utilize the package \texttt{taufactor} that implements
+a periodic boundary condition solver and calculates the diffusive tortuosity of the bijel structures. Porous structures were 
+extracted by binarizing the final order parameter field using a zero threshold, isolating the largest connected (percolating) domain. We plot the results of
+the directional domain size and tortuosity in Figure \ref{fig:domain_size_aniso-field_on}
 
@@
 
-From Figure \ref{fig:domain_size_aniso-field_on}, domain size anisotropy is observed upon application of the field for both
-particle morphologies. Some domain anisotropy with no applied field is observed, which increases upon application of the magnetic field.
-The directional domain sizes, $L_{\perp}$ and $L_{\parallel}$ increase by 73\% and 7\%\ respectively for oblate particles and
-10\% and 44\% respectively for oblate particles. The axes that coarsens the most is consistent with past work, explained through the
-directions particles reorient in response to the applied magnetic field. As particles unjam and rejam at the interface due to reorientating 
-to the magnetic field, they adopt direction specific surface coverages which manifest as anistropic domains upon jamming. In Figure 
-\ref{fig:domain_size_aniso-field_on}, we demonstrate that the application of the magnetic field changes the domain size.
+Figure~\ref{fig:domain_size_aniso-field_on} shows that the application of a magnetic field induces clear domain size anisotropy in bijels stabilized by both oblate 
+and prolate particles. Even at zero field, a small degree of anisotropy is observed, which increases substantially with rising field strength. For oblate particles, 
+the domain sizes perpendicular (\(L_\perp\)) and parallel (\(L_\parallel\)) to the applied field increase by approximately 73\% and 7\%, respectively. In contrast, 
+for prolate particles, \(L_\perp\) increases by 10\%, while \(L_\parallel\) increases by 44\%. These results indicate that the dominant direction of coarsening 
+depends on particle morphology: oblate particles promote greater coarsening perpendicular to the field, while prolate particles favor coarsening parallel to the 
+field. This trend is consistent with previous findings and reflects how particles reorient in response to the applied magnetic field. As particles unjam and rejam 
+at the interface, they adopt morphology- and field-dependent orientations that result in directionally biased surface coverage, manifesting as anisotropic domain 
+growth.
 
-The tortuosity of the bijel is initially around $\tau \approx 1.5$, consistent with simulations of the diffusive tortuosities of gyroid structures using 
-Lattice Boltzmann simulations. \cite{luo_macroscopic_2020} Upon application of the field, $\tau_{\perp}$ slightly decreases while $\tau_{\parallel}$
-increases. In Chapter \ref{chapter:aim1}, we characterized that increasing the domain size decreases the tortuosity. \cite{karthikeyan_formation_2024} This
-observation is in line with the domain size changes observed in Figure \ref{fig:domain_size_aniso-field_on}. The results show that the
-tortuosity of the bijel is noticeably affected by the application of magnetic fields. This data suggests that magnetic fields applied onto
-bijels stabilized with ellipsoidal particles undergo domain anisotropy upon application of magnetic fields. However the particle morphology,
-specifically its axis of symmetry, affect the direction that the domain anisotropy is characterized.
+The right panel of Figure~\ref{fig:domain_size_aniso-field_on} presents the corresponding changes in directional tortuosity. Initially, the tortuosity values 
+for both directions are close to \(\tau \approx 1.5\), aligning with previous simulations of gyroidal and co-continuous structures using Lattice Boltzmann methods 
+\cite{luo_macroscopic_2020}. Upon applying the magnetic field, \(\tau_\perp\) decreases while \(\tau_\parallel\) increases. This inverse relationship between 
+tortuosity and domain size is consistent with prior findings \cite{karthikeyan_formation_2024}, where larger domains exhibited 
+reduced tortuosity. The observed anisotropic response suggests that magnetic fields not only influence interfacial particle orientation but also lead to 
+direction-dependent transport pathways in the bijel. Moreover, the extent and direction of anisotropy are strongly influenced by the particle morphology, 
+particularly the axis of symmetry, which dictates the dominant direction of microstructural reorganization under field application.
 
-Next, we investigate the time gap between the average domain size increase and the nematic order parameter. This result suggests that the dynamics 
-of the system at higher magnetic field strengths are dependent upon other factors that vary upon application of the magnetic field. In this system, these factors
-would arise from capillary forces with the interface or steric interactions with other particles at the interface, slowing down the dynamics of the system.
-To understand this phenomena, we focus on the dynamics of the particle monolayer. First, we visualize the particle monolayer of the bijels stabilized with prolate 
-ellipsoids at the initial and final configuration before and after application of a magnetic field.
+Thus far, three key particle-scale phenomena have been characterized in response to the application of a magnetic field. The first is
+particle alignment to the field direction, where both oblate and prolate ellipsoids reorient their major axes along the magnetic field vector. The second effect is
+changes in particle tilt relative to the fluid interface, reflected in variations of the interface angle \(\langle \psi \rangle\), indicating out of interface 
+reorientation driven by magnetic torque. Third, reorganization of the local particle monolayer, as captured by the evolution of the Steinhardt bond order parameter 
+\(\langle Q_6 \rangle\), which reflects field-dependent disruptions and recoveries in particle ordering at the interface. Together, these processes 
+drive the unjamming of the particle monolayer, causing coarsening of the fluid domains before the interface rejams in place with anisotropy dictated by the orientation
+of particles to the magnetic field.
 
-\begin{figure} 
-\centering 
-\includegraphics[scale=0.2]{../figures/results/paper2/particle_viz-field_on.png} 
-\caption{Visualizations of bijels stabilized with oblate and prolate particles simulated at $t = 0$ (left column) and $t = 10^5$ (right column). The first and 
-         third rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids respectively with no applied field. The second and fourth 
-         rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids respectively with an applied field of $\bar{B}_z = 1$. Particle 
-         reorientation to the direction of the field can be seen, resulting in coarsening of the domains.} 
-\label{fig:particle_viz-field_on} 
-\end{figure}
+\subsection{Increasing the applied field onto a bijel made with a magnetic field}
+\subsubsection{Field strength dependence on domain size}
+\label{section:increasing-the-applied-field}
 
-In Figure \ref{fig:particle_viz-field_on}, we see the initial configuration of particles at the monolayer show that the orientations are random and that the 
-particles tend to lie flat on the interface. However, upon application of the magnetic field the particles orient to the field direction. With no applied field,
-the orientations and positions of the particles vary slightly for both ellipsoidal particle morphologies. This effect is due steric effects between particles,
-as identified in Gunther et al. \cite{gunther_timescales_2014} Bijels stabilized by prolate ellipsoids, adopt orientational order
-to the magnetic field and qualitatively different particle arrangements on the interface. These indicate that the interfacial capillary forces or steric interactions 
-with other particles differ upon application of the magnetic field. The particles would prefer to lie flat on the interface to minimize the interfacial energy of 
-adsorption onto the interface. Changes in the local arrangement arise from the unjamming and rejamming process upon application of the magnetic field. These differences 
-in the orientational and interfacial ordering can be characterized to understand how each respective interaction force changes as a function of time.
+The hysteresis curve presented earlier in Figure~\ref{fig:hysteresis_curve} revealed that microstructural changes—quantified by domain size—diminish 
+with each successive increase in magnetic field strength. This saturation behavior suggests a direct link between the extent of domain coarsening 
+and the evolving order within the interfacial particle monolayer. As demonstrated in the previous section, once the bijel is jammed, further domain 
+growth is constrained by local rearrangements of the particles at the interface, which are themselves influenced by the degree of particle alignment 
+and packing. To investigate this relationship further, we now examine how pre-existing particle order, established during bijel formation, affects 
+the system's responsiveness to a subsequent applied magnetic field.
 
-Bresme and Faraudo and Davies investigating the reorientation of particles at interfaces under magnetic fields have shown that a critical magnetic field exists, 
-above which the particle orients to the field and below which the particle orientation is a function of the capillary force and magnetic field derived force. 
-\cite{davies_interface_2014} \cite{bresme_orientational_2007} Particle adsorption into the interface with microparticles have also been shown to be irreversible due 
-to the high adsorption energy. Upon particle reorientation, the microstructure change can be driven solely through particle unjamming and re-jamming, or it can be 
-driven through the particles dragging the interface during this process. The mechanism of unjamming and re-jamming can be investigated using the average interfacial 
-angle, $\langle \psi \rangle$ and the local ordering of the particles characterized with  $\langle Q6 \rangle$ Past work has identified that local crystallization 
-of colloidal supercooled fluids takes place at \(\langle Q6 \rangle = 0.38\). \cite{toxvaerd_role_2020} Past investigations into the rheology of bijels have revealed
-that bijels are colloidal glasses percolating in 3D space. \cite{ching_bijel_2022} However, application of a magnetic field results in reorientation of particles on
-the interface that can temporarily reduce the interfacial coverage of the particles on the interface, temporarily making the particle monolayer more liquid-like
-than amorphous. \cite{hunter_physics_2012} Using this approximation, we can use the local crystallization result shown in Toxvaerd.
-
-\begin{figure} 
-\centering 
-\includegraphics[scale=0.5]{../figures/results/paper2/interface_angle-nint-field_on.png} 
-\caption{Plots of the interface angle $(\langle \psi \rangle)$ and six fold Steinhardt order parameter $(\langle Q6 \rangle)$ on the left and right respectively, 
-         versus time for bijels stabilized with oblate and prolate ellipsoids on the top and bottom rows respectively. I demonstrate that upon application 
-         of a magnetic field, the behavior of $(\langle \psi \rangle)$ and $(\langle Q6 \rangle)$ differ significantly between oblate and prolate ellipsoids 
-         indicating that the dynamics for both particle morphologies differ. I also observe magnetic field dependence in each property for both particle types, 
-         suggesting that these changes are driven primarily through the change in the applied field strength.} 
-\label{fig:interface_angle-nint-field_on} 
-\end{figure}
-
-From Figure \ref{fig:interface_angle-nint-field_on}, we identify that prolate and oblate particles respond differently at the interface. For
-bijels stabilized by oblate ellipsoids, we characterize an increase in $\langle \psi \rangle$ from an initial value of $19 ^{\circ}$,
-before it reduces slightly and begins to increase once again. The initial starting value of $\langle \psi \rangle$ indicates the
-particles are lying close to flat on the interface, before they begin to tilt out of the interface when the magnetic field is applied. Then,
-$\langle \psi \rangle$ plateaus as the interface begins to move in response to the tilting particle at the interface. This is caused by the
-large adsorption energy of the particles at the interface of the bijel, caused by high surface tension. Finally, the particles jam in place,
-locking the interface at an angle to the particle. The rate of increase in $\langle \psi \rangle$ at early stages and the time spent
-in the plateau increase with a larger applied magnetic field. The final angle at the interface is also dependent upon the applied field
-strength.
-
-When analyzing $\langle \psi \rangle$ for bijels stabilized by prolate particles, this behavior can also be observed. $\langle \psi \rangle$
-begins at $10 ^{\circ}$. $\langle \psi \rangle$ increases, before plateauing and slowly decreasing. The initial peak height and rate of increase in 
-$\langle \psi \rangle$ is field dependent, although given the small decrease in $\langle \psi \rangle$ it is unclear if the final value of this parameter 
-is field dependent for bijels stabilized with prolate particles. The changes in $\langle \psi \rangle$ for bijels stabilized with prolate particles are 
-small compared to bijels stabilized with oblate particles. We visualize this process by color coding snapshots of the particle monolayer at the initial
-and final timesteps of bijels stabilized by prolate particles with a field strength of $\bar{B} = 1$ applied.
-
-\begin{figure} 
-    \centering 
-    \includegraphics[scale=0.4]{../figures/results/paper2/psi_concat_startB-0_endB-1.png} 
-    \caption{Visualizations of bijel stabilized by ellipsoidal particles made with no applied field having a field strength of $\bar{B} = 1$ applied. The top and bottom 
-             rows show $\psi$ for each particle at the initial and final timesteps respectively.The intensity
-             of the red color qualitatively indicates the magnitude of the $\psi$ for each particle. Field application causes particles to flip out of the interface for
-             oblate particles, while prolate particles tilt out of the interface. The interface is shaded with the Gaussian curvature.} 
-    \label{fig:psi_field_on_visualize} 
-\end{figure}
-
-From the visualizations in Figure \ref{fig:psi_field_on_visualize}, the particles lie mostly flat on the interface at the initial timestep. Upon application of a field 
-strength of $\bar{B} = 1$, the final state of the monolayer is particle morphology dependent. Oblate particles tend to flip on the interface into a metastable state where
-the interface covered by each particle is done with the $R_p$ and $R_o$ compared to its lowest energy state where it lies flat with radii $R_o$. The particle monolayer
-of bijels stabilized by prolate particles tilt out of the interface with no metastable configurations observed. This effect explains the trends seen in $\langle \psi \rangle$
-at long times for both particle morphologies. This particle flipping on the interface affects the way the particles can arrange on the interface, like what we 
-characterized In Figure \ref{fig:rdf}. This change in local ordering can be quantified using $\langle Q6 \rangle$.
-
-From Figure \ref{fig:interface_angle-nint-field_on} the dynamics of $\langle Q6 \rangle$ are particle morphology specific but can be split into three sections for 
-both particle morphologies. Characterizing the time evolution of $\langle Q6 \rangle$ for oblate particles, we see a decrease upon application of the magnetic field, 
-followed by a plateau and finally a gradual increase before jamming takes place, seen as a significant decrease in the rate of chang to $\langle Q6 \rangle$.
-These results indicate that the ordering of the particles is reduced by the applied magnetic field, before a
-restoration of some of the pre-existing order. The final values of $\langle Q6 \rangle$ are magnetic field dependent, with a stronger
-magnetic field having a lower final $\langle Q6 \rangle$ value indicating that either the ordering of particles influence the angle at
-the interface or vice versa.
-
-We observe that for bijels stabilized by prolate particles, the interface ordering of the particles increases as a
-function of the applied field strength. The first phase of the evolution of $\langle Q6 \rangle$ sees some growth in $\langle Q6 \rangle$ before 
-increasing dramatically and plateauing as jamming takes place. The length of time of the initial plateau and growth regions are negatively and
-positively correlated to the applied magnetic field strength. Upon application of the magnetic field, $\langle Q6 \rangle > 0.38$ in all cases. Approximating
-the particle monolayer as a colloidal glass that underwent a glass transition, the monolayer can be said to undergo a local crystallation event when 
-$\langle Q6 \rangle > 0.38$. \cite{toxvaerd_role_2020}
-
-Thus far, three particle based phenomena have been characterized; the orientation of the particle to the magnetic field, the interface and the local 
-arrangement of the particles on the interface. we can calculate a timescale for each factor from the plots of each of these properties.
-The nematic order parameter $S$ represents the ordering of
-particles to an average direction, which in the case of the application
-of a magnetic field, is the field direction. Therefore, a timescale
-reliant on the nematic order parameter would represent a timescale of
-response rate limited to the response to the magnetic field, which
-indicates a particle-field orientation dependence named $\tau_S$. When applying a field to a bijel system with a
-randomly oriented particle monolayer, the most significant transition
-point is the isotropic to nematic transition or when $S \geq 0.3$. We
-define $\tau_S$ as the the isotropic to nematic transition point.
-
-We can also do the same for $\langle \psi \rangle$ and
-$\langle Q6 \rangle$. A timescale derived from
-$\langle \psi \rangle$ named $\tau_{\langle \psi \rangle}$
-represents the capillary timescale between the interface and the
-particle. Given the shape of the plot, we assign
-$\tau_{\langle \psi \rangle}$ to be the time when the first minimum of
-$\langle \psi \rangle$ is observed for prolate particles and the first
-maximum for oblate particles. A timescale derived from
-$\langle Q6 \rangle$, named $\tau_{\langle Q6 \rangle}$ is also
-calculated which represents a timescale of local particle rearrangement.
-We define $\tau_{\langle Q6 \rangle}$ as the time when
-\(\langle Q6 \rangle \geq 0.38\) for prolate particles and the global
-minimum of $\tau_{\langle Q6 \rangle}$ for the oblate particles. I
-omit \(\bar{B} = 0\) as previous results have identified the domain size
-changes observed there. We then plot the average domain size $L$
-against time rescaled with these three timescales in Figure
-\ref{fig:domain_size-field_on-scaled}.
-
-\begin{figure} 
-\centering 
-\includegraphics[scale=0.4]{../figures/results/paper2/domain_size-field_on-scaled.png} 
-\caption{Plots of domain size with different timescales. The top and bottom row represent the average domain size for bijels stabilized with oblate and 
-         prolate particles respectively. The figures on the left plots the domain size against time rescaled with the nematic to isotropic transition time, 
-         $\tau_S$. The figures in the middle plot the domain size against time rescaled with the interfacial capillary timescale, $\tau_{\langle \psi \rangle}$. 
-         The figures on the right plot the domain size against time rescaled with the particle rearrangement timescale, $\tau_{\langle Q6 \rangle}$. We show 
-         that the controlling timescale when applying a magnetic field onto bijels with disordered particles is the latter timescale, indicating that the 
-         dominating effect is steric hindrance of the particles during rearrangment at the interface.} 
-\label{fig:domain_size-field_on-scaled} 
-\end{figure}
-
-In Figure \ref{fig:domain_size-field_on-scaled}, the left plot plots the
-average domain size against time rescaled using $\tau_S$. The
-the domain sizes do not collapse onto a single line, which is expected
-if we want to explain the dynamics using the nematic order parameter.
-This confirms the observation made above that the dynamics do not only
-depend on the reorientation of particles to the field. The middle plot
-demonstrates the average domain size against time rescaled using
-$\tau_{\langle \psi \rangle}$. There is good agreement
-between all simulations for prolate particles, although the point when
-$\frac{t}{\tau_{\langle \psi \rangle}} = 1$ lies when the domain size
-transition has started. However for oblate particles this
-timescale does not describe the dynamics well.
-
-The right plot demonstrates the domain size change after rescaling time
-with $\tau_{\langle Q6 \rangle}$ all plots collapse onto a single line and 
-the domain size transition also begins at
-$\frac{t}{\tau_{\langle Q6 \rangle}} = 1$. The latter point
-demonstrates that the dynamics for the structural response of randomly
-oriented particles are controlled by the local particle rearrangement at
-the interface rather than the orientation of the particle to the
-magnetic field. As the dynamics of both particle morphologies are well described
-using the particle steric effects timescale, denoted by $\tau_{\langle Q6 \rangle}$,
-We conclude that the dynamics of bijels stabilized by ellipsoidal particles are controlled by
-interfacial particle rearrangement at the interface.
-
-From the evidence in Figure \ref{fig:domain_size-field_on-scaled}, two
-types of interfacial behaviors are characterized in addition to that
-identified by Gunther et al.~\cite{gunther_timescales_2014} The first
-type is what is observed for $\bar{B} = 0.2$, where the interfacial
-arrangement and orientation of the particle monolayer to the field and to the
-interface change in lock step. This causes the interface to reorient at
-the same rate as the particles reorienting to the magnetic field. The
-second is observed for $\bar{B} = 0.5, 1$, where there is a time lag
-between particle ordering, and the intiation of domain coarsening. In
-the latter scenario, at early times the particles are jolted out of
-position before the large adsorption energy of the particles into the
-interface causes the interface to move to the particle position, causing
-domain coarsening as the interfacial area reduces before rejamming reforms the bijel.
-
-\subsection{Increasing the applied
-field}\label{increasing-the-applied-field}
-
-The hysteresis curve in Figured \ref{fig:hysteresis_curve} shiows that the microstructure change at higher
-field strengths began to reduce with each subsequent field strength
-jump, suggesting that the ordering of the particles is linked to the
-domain size change observed. In the previous section, We saw that domain
-size changes in bijels after jamming are constrained by magnetic field
-driven local rearrangement of the particle monolayer. In this section,
-we explore how pre-existing order in the particles affect the degree of
-domain size change observed. We apply fields of strength
-$\bar{B}_{template} = 0, 0.2, 0.5, 1$ during phase separation to
-create bijels stabilized with ellipsoidal particles with pre-existing
-particle order. We then apply a field strength of $\bar{B}_z = 1$ and
-observe the time evolution of the system for $t = 10^5$ timesteps. I
-simplify my nomenclature here for brevity. For example,
-$\bar{B}_z: 0.0 \rightarrow 1.0$ represents a bijel made with no
-field, and a field of $\bar{B}_z = 1.0$ applied during the simulations conducted here. 
-We begin by visualizing the microstructure
-changes experienced by bijels simulated with pre-existing particle order
-in Figure \ref{fig:microstructure_viz-field_up}.
+Specifically, we prepare bijel templates by applying magnetic fields of strength \(\bar{B}_{\text{template}} = 0, 0.2, 0.5, 1.0\) during the phase separation 
+process, thereby generating structures stabilized by ellipsoidal particles with varying initial degrees of interfacial order. A constant magnetic field of 
+\(\bar{B}_z = 1.0\) is then applied to each system post-jamming, and we monitor the microstructure evolution over a simulation duration of \(t = 10^5\) 
+timesteps. For clarity, we adopt simplified notation in the discussion that follows—for example, \(\bar{B}_z: 0.0 \rightarrow 1.0\) denotes a bijel 
+formed without a field and then subjected to a field of \(\bar{B}_z = 1.0\) during the response phase. We begin by qualitatively assessing the 
+structural changes induced in bijels formed with different levels of initial particle ordering, as shown in Figure~\ref{fig:microstructure_viz-field_up}.
 
@@
 \includegraphics[scale=0.4]{../figures/results/paper2/microstructure_viz-field_up.png} 
-\caption{Visualizations of bijels stabilized with oblate and prolate particles simulated at $t = 0$ (left column) and $t = 10^5$ (right column). 
-         The first and third rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids respectively with an applied 
-         field of $\bar{B}_z = 0.2$. The second and fourth rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids 
-         respectively with an applied field of $\bar{B}_z = 1$. We increase the applied field to $\bar{B}_z = 1$ in both cases and show that particle 
-         reorientation to the field occurs at the $\bar{B}_z = 0.2$ but not in the $\bar{B}_z = 1$ case.}
+\caption{Visualizations of bijels stabilized by prolate ellipsoidal particles at the initial (left column) and final (right column)
+         timepoints for two magnetic field conditions. The top row corresponds to the case where the field is increased from 
+         \(\bar{B}_z = 0.2\) to \(\bar{B}_z = 1.0\), while the bottom row shows a bijel formed and evolved under a constant field of 
+         \(\bar{B}_z = 1.0\). }
 \label{fig:microstructure_viz-field_up}
@@
 
-In Figure \ref{fig:microstructure_viz-field_up} We show representative
-snapshots of a bijel stabilized with prolate particles at the initial
-and final timestep with field conditions
-$\bar{B}_z: 0.2 \rightarrow 1.0$ and
-$\bar{B}_z: 1.0 \rightarrow 1.0$ in the top and bottom rows
-respectively. We show that upon application of the field, the fluid
-domains undergo a field strength dependent microstructrue response, with
-the degree of response dependent upon the difference between the initial
-and final magnetic field. We also observe a qualitative increase in the
-alignment of the particles to the magnetic field for the
-$\bar{B}_z: 0.2 \rightarrow 1.0$ case. We quantify these observations
-by plotting the average domain size and nematic order parameter in
-Figure \ref{fig:domain_size-field_up}.
+Figure \ref{fig:microstructure_viz-field_up} demonstrates a clear initial microstructure dependent structural response, 
+where the extent of domain coarsening and anisotropy is greater 
+in the system that undergoes a field increase. In the \(\bar{B}_z: 0.2 \rightarrow 1.0\) case, fluid domains exhibit more pronounced reorganization and growth 
+compared to the \(\bar{B}_z: 1.0 \rightarrow 1.0\) case, where the structure remains largely unchanged over time.
+Additionally, a qualitative increase in particle alignment with the field direction is observed in the top row, indicating that pre-existing particle order 
+limits the extent of reorientation and structural evolution under further field application. These results suggest that the degree of microstructural change 
+is influenced by the difference between the initial and final magnetic field strengths, and by the capacity of the interfacial particles to reorient at the interface. 
+We quantify these trends in the following section by analyzing the time evolution of domain size and the nematic order parameter in 
+Figure~\ref{fig:domain_size-field_up}.
 
@@
 
-In Figure \ref{fig:domain_size-field_up}, We define the difference
-between the final and initial magnetic field strengths as
-$\Delta \bar{B}$. The onset of microstructural response is observed to
-be $\Delta \bar{B}$-dependent, indicating that a stronger driving
-force is required to induce structural reorganization. Additionally, the
-extent of microstructural change is also correlated with
-$\Delta \bar{B}$, where $\Delta \bar{B} = 1$ results in average
-microstructural variations of 5\% and 2\% for oblate and prolate
-particles, respectively which decreases as $\Delta \bar{B}$ decreases.
-We further characterize the relationship between $\Delta \bar{B}$ and
-nematic order, showing that an increase in \(S\) correlates with
-$\Delta \bar{B}$. This suggests that changes in domain size are
-intrinsically linked to the initial particle ordering within the system.
-These findings indicate that characteristic length scale evolution is
-dependent on both aspect ratio and field strength variation,
-highlighting the role of particle alignment in governing domain
-coarsening dynamics. To further quantify the anisotropic microstructural
-evolution, We define the relative change in domain size as
-$\Delta L = \frac{L_{f} - L_{i}}{L_{i}}$, where $L$ represents
-either $L_{\perp}$ or $L_{\parallel}$. The same formulation is
-applied to the tortuosity in the respective directional components. I
-do this to characterize the $\Delta \bar{B}$-dependent changes
-observed in the domain anisotropy. The results are presented in Figure
-\ref{fig:domain_size_aniso-field_up}.
+Figure~\ref{fig:domain_size-field_up} presents the evolution of domain size \(L/R\) and nematic order parameter \(S\) for bijels stabilized by oblate (left) 
+and prolate (right) particles under various field transition conditions. We define \(\Delta \bar{B}\) as the difference between the final and initial magnetic 
+field strengths. The onset and magnitude of the microstructural response are both observed to be dependent on \(\Delta \bar{B}\), indicating that a stronger 
+magnetic field change provides a greater driving force for structural reorganization. Specifically, when \(\Delta \bar{B} = 1.0\), the resulting domain size 
+increases by approximately 5\% for oblate particles and 2\% for prolate particles. These structural changes diminish progressively as \(\Delta \bar{B}\) decreases.
+
+The accompanying nematic order parameter \(S\) also correlates strongly with \(\Delta \bar{B}\), suggesting that domain size evolution is intrinsically linked 
+to the extent of particle alignment within the system. Higher values of \(\Delta \bar{B}\) induce greater particle reorientation, which facilitates is linked to
+reconfiguration of particles at the interface, thereby enabling domain coarsening. These findings highlight that characteristic length scale evolution is jointly 
+governed by both particle aspect ratio and the magnitude of magnetic field variation. To further quantify anisotropic changes in microstructure, we define the 
+relative change in directional domain size as \(\Delta L = \frac{L_f - L_i}{L_i}\), where \(L\) refers to either \(L_{\perp}\) or \(L_{\parallel}\). 
+The same formulation is applied to the directional tortuosity components. These metrics allow us to isolate and characterize the \(\Delta \bar{B}\)-dependent 
+evolution of anisotropic structural features. The results are presented and analyzed in Figure~\ref{fig:domain_size_aniso-field_up}.
 
@@
 
-From Figure \ref{fig:domain_size_aniso-field_up}, domain
-size anisotropy is observed upon increasing the applied field
-for both particle morphologies. Some domain anisotropy with no applied field can be observed, 
-which increases upon application of the magnetic field. The directional domain sizes,
-$L_{\perp}$ and $L_{\parallel}$ increase by $73\%$ and $7\%$
-respectively for oblate particles and $10\%$ and $44\%$ respectively
-for prolate particles. The axes that coarsens the most is consistent
-with past work, explained through the directions particles reorient in
-response to the applied magnetic field. The
-tortuosity of the bijel is initially around $\tau \approx 1.5$,
-consistent with simulations of the diffusive tortuosities of gyroid
-structures using Lattice Boltzmann simulations.
-\cite{luo_macroscopic_2020} Upon application of the field,
-$\tau_{\perp}$ slightly decreases while $\tau_{\parallel}$
-increases. Consistent with past work, an increase in the domain size sees a decrease in
-tortuosity in that direction. \cite{karthikeyan_formation_2024}. The results show that the
-tortuosity of the bijel is noticeably affected by the application of
-magnetic fields.
+Figure~\ref{fig:domain_size_aniso-field_up} quantifies the directional changes in domain size (\(\Delta L\)) and tortuosity (\(\Delta \tau\)) as a 
+function of magnetic field variation \(\Delta \bar{B}\), for bijels stabilized by oblate (blue) and prolate (red) particles. The results show that 
+increasing the applied magnetic field leads to enhanced domain size anisotropy in both particle systems. Even in the absence of a magnetic field 
+change (\(\Delta \bar{B} = 0\)), a small degree of anisotropy is observed, which becomes more pronounced as \(\Delta \bar{B}\) increases. For oblate 
+particles, the perpendicular and parallel domain sizes increase by approximately 73\% and 7\%, respectively. In contrast, for prolate particles, the 
+increases are 10\% and 44\%, respectively. The direction of dominant coarsening aligns with prior findings and reflects how particles reorient under 
+the influence of the magnetic field—oblate particles tend to reorient and promote coarsening perpendicular to the field, while prolate particles favor 
+coarsening along the field direction.
 
-As particles unjam and rejam at the interface due to reorientating to
-the magnetic field, they adopt direction specific surface coverages
-which manifest as anistropic domains upon jamming. The direction of the
-anisotropy is different as the oblate particles have an axis of symmetry
-in the short axis of the radius, while for the prolate particles it is
-on the long axis. Thus during reorientation, the long axis of the oblate
-particles will be orthogonal to the applied field and parallel for the
-prolate particles. To characterize how the particle order changes on the
-interface as a function of the magnetic field strength, we visualize the
-particle monolayer of bijels stabilized by prolate particles in Figure
-\ref{fig:particle_viz-field_up}.
+The right panel shows the corresponding changes in directional tortuosity. The initial tortuosity is approximately \(\tau \approx 1.5\), consistent with 
+Lattice Boltzmann simulations of gyroid and co-continuous porous structures \cite{luo_macroscopic_2020}. Upon field application, \(\tau_\perp\) 
+generally decreases while \(\tau_\parallel\) increases, in agreement with the observed domain size changes. These trends are consistent with prior 
+work \cite{karthikeyan_formation_2024}, which demonstrated an inverse relationship between domain size and tortuosity. The results confirm that 
+magnetic field-driven domain anisotropy significantly affects the transport properties of the bijel, with particle shape and orientation playing a 
+critical role in determining the direction and magnitude of these structural changes. The shape of the plots indicate that the decrease in structural response
+is correlated strongly to an increase in the ordering of the particles. In the next section, we focus more on the particle monolayer.
+
+\subsubsection{Particle reorientation as a function of initial particle order}
+
+The results presented thus far demonstrate that the extent of microstructural evolution, particularly domain anisotropy and coarsening, decreases sharply 
+as the difference between the initial and final magnetic field strengths (\(\Delta \bar{B}\)) approaches zero. This exponential decay in structural 
+response suggests that beyond a certain threshold, the system becomes increasingly resistant to reorganization. Since domain-scale changes are driven 
+by local particle rearrangements at the interface, this diminishing response points to a progressively reduced capacity of the particle monolayer to 
+unjam and reorient under small field perturbations. To better understand the origin of this resistance to structural change, we now shift our focus to 
+the particle monolayer itself. Specifically, we examine how initial ordering within the interfacial particle layer governs the system's ability to respond 
+to further magnetic stimuli.
 
@@
 \includegraphics[scale=0.2]{../figures/results/paper2/particle_viz-field_up.png} 
-\caption{Visualizations of bijels stabilized with oblate and prolate particles simulated at $t = 0$ (left column) and $t = 10^5$ (right column). 
-         The first and third rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids respectively with an applied 
-         field of $\bar{B}_z = 0.2$. The second and fourth rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids 
-         respectively with an applied field of $\bar{B}_z = 1$. We increase the applied field to $\bar{B}_z = 1$ in both cases and show that particle 
-         reorientation to the field occurs at the $\bar{B}_z = 0.2$ but not in the $\bar{B}_z = 1$ case.} 
+\caption{Snapshots of the structural evolution of the particle monolayer in bijels stabilized by prolate ellipsoids 
+         under different magnetic field conditions. The top row corresponds to a simulation where the field is increased from 
+         \(\bar{B} = 0.2\) to \(\bar{B} = 1.0\), while the bottom row shows a system maintained at a constant field of \(\bar{B} = 1.0\) throughout.} 
 \label{fig:particle_viz-field_up} 
@@
 
-In Figure \ref{fig:particle_viz-field_up}, we see the effect of the
-application of the magnetic field on the monolayer. The initial
-configuration of particles at the monolayer show that even at initial
-configuration of run $\bar{B}: 0.2 \rightarrow 1$, most particles are
-oriented towards the field. Upon increasing the field strength to
-$\bar{B} = 1$, all particles shown can be seen to be ordered to the
-field, matching the results for the nematic order parameter shown in
-Figure \ref{fig:domain_size-field_up}. We also observe the alignment of
-the long axis of the particles to the magnetic field, demonstrating the
-origin of the microstructure anisotropy. To understand how the particle
-reorientation at the interface causes microstructure reorientation we
-quantify the average interface angle, $\langle \psi \rangle$ and the
-local interface order of the material, $\langle Q6 \rangle$ in Figure
-\ref{fig:interface_angle-nint-field_up}.
-
-Figure \ref{fig:interface_angle-nint-field_up} shows that
-prolate and oblate particles respond differently at the interface upon application of a magnetic field
-even with pre-existing ordering of the particles. We
-show that there are three time evolution trends for
-$\langle \psi \rangle$ and $\langle Q6 \rangle$ for both oblate and
-prolate particles despite the differences in the initial state of the
-particles. In oblate particles $\langle \psi \rangle$ begins closer to
-$20 ^{\circ}$ as the axis of symmetry lies close to the interface
-normal. For bijels experiencing a field strength history of
-$\bar{B}: 0 \rightarrow 1$ and $\bar{B}: 0.2 \rightarrow 1$,
-$\langle \psi \rangle$ increases, plateaus and increases again before
-plateauing again. This is indicative of particles tilting at the
-interface, before interfacial capillary interactions ``pause'' particle
-reorientation before the applied magnetic field begins to cause
-particles to tilt out of the interface. We see similar trends for bijels
-stabilized by prolate particles. $\langle \psi \rangle$ begins near
-$11 ^{\circ}$ and decrease before reorientation ceases before
-$\langle \psi \rangle$ increases again.
-
-When looking at $\langle Q6 \rangle$ for $\bar{B}: 0 \rightarrow 1$
-and $\bar{B}: 0.2 \rightarrow 1$ for oblate particles, we see that the
-trends are similar with an initial decrease, followed by a plateau and
-increase over time before plateauing again. $\langle Q6 \rangle$
-generally decreases with a large decrease observed for
-\(\bar{B}: 0 \rightarrow 1\) from an initial hexagonally packed system
-to a structure that is locally ordered but not close packed. $\langle Q6 \rangle$ increases before plateauing 
-in both systems around 5000 timesteps. The significance of
-this time is unknown for $\bar{B}: 0.2 \rightarrow 1$ but for
-$\bar{B}: 1 \rightarrow 1$, this is approximately the local
-crystallization point when $\langle Q6 \rangle \geq 0.38$.
-
-For oblate particles, structural response dynamics
-arise from particle tilting on the interface identified as the large
-difference between the initial and final $\langle \psi \rangle$ with
-an associated decrease in the interface coverage, initiating domain
-coarsening. Interfacial tilting causes a loss in the
-close packing of oblate particles at the interface. For prolate
-particles, a small degree of particle tilting can be seen
-from $\langle \psi \rangle$, although an increase in $\langle Q6 \rangle$ is observed
-decreasing the interfacial area. Larger domain size response is
-observed for the oblate particles as the interfacial area change from
-particle tilting at the interface is larger than that of particles close
-packing at the interface.
+Even at the initial timepoint of the \(\bar{B}: 0.2 \rightarrow 1.0\) run, a majority of particles are already aligned with the field direction. 
+Upon increasing the field strength to \(\bar{B} = 1.0\), nearly all visible particles exhibit strong alignment, consistent with the high nematic order 
+parameter values observed in Figure~\ref{fig:domain_size-field_up}.
+The visual alignment of the particles long axes with the magnetic field highlights the mechanism driving anisotropic domain formation in the bijel. 
+As particle orientation is locked in by magnetic torque, the interfacial arrangement becomes directionally biased, influencing the resulting domain 
+morphology. To quantitatively link this particle-scale reorientation to the observed structural anisotropy, we next evaluate the average interface 
+angle \(\langle \psi \rangle\) in Figure \ref{fig:interface_angle-field_on}
 
@@
     \centering 
-    \includegraphics[scale=0.4]{../figures/results/paper2/interface_angle-nint-field_up.png} 
-    \caption{Plots of the average interfacial angle $\psi$ and the number of particles on the interface $n_{int}$ on the left and right respectively, 
-             plotted against time for bijels stabilized with ellipsoidal particles with aspect ratio 2. When looking at $\psi$, a change in dynamics can be 
-             seen as the initial particle order increases. When looking at $n_{int}$, different dynamics are seen above and below the isotropic to nematic transition point. 
-             Both results suggest that the ordering of particles is linked to the dynamics of domain coarsening.} 
-    \label{fig:interface_angle-nint-field_up} 
+    \includegraphics[scale=0.4]{../figures/results/paper2/psi-field_up.png} 
+    \caption{Plots of the evolution of the average interface angle \(\langle \psi \rangle\) for bijels stabilized 
+             by oblate (left) and prolate (right) particles, as a function of the initial microstructure and subsequent magnetic field application.
+             The dynamics observed can be seen to be a function of the initial microstructure.} 
+    \label{fig:interface_angle-field_up} 
 \end{figure}
 
-For both particle morphologies we analyze the response of bijels with a
-field history of $\bar{B}: 0.5 \rightarrow 1$ and
-$\bar{B}: 1 \rightarrow 1$.
-$\langle Q6 \rangle$ decreases for bijels stabilized with oblate particles with
-field application of $\bar{B}: 0.5 \rightarrow 1$ compared to an
-increase for $\bar{B}: 1 \rightarrow 1$. This behavior arises from the
-slight increase in the nematic order for particles in bijels
-experiencing the $\bar{B}: 0.5 \rightarrow 1$ field application
-history. The $\langle \psi \rangle$ results indicate that the
-particles rearrange over time to lie flatter on the interface. For
-bijels stabilized with prolate particles, We characterize a difference
-in behavior between $\bar{B}: 0.5 \rightarrow 1$ and
-$\bar{B}: 1 \rightarrow 1$. For the $\bar{B}: 0.5 \rightarrow 1$
-case, a slight increase in $\langle \psi \rangle$ before a
-decrease and increase is seen compared to the $\bar{B}: 1 \rightarrow 1$ case
-where we characterize a slight decrease over time. We also characterize
-a slight decrease in $\langle Q6 \rangle$ over time for the
-$\bar{B}: 1 \rightarrow 1$ case while characterizing a larger decrease
-for the $\bar{B}: 0.5 \rightarrow 1$ case. Similar to the oblate
-particles, these results originate from the slight increase in the
-nematic order for bijels experiencing the $\bar{B}: 0.5 \rightarrow 1$
-field history.
+The results show that the initial particle ordering plays a significant role in the interfacial response. As characterized earlier for the case of
+$\bar{B}:0.0 \rightarrow 1.0$ the time evolution of $\langle \psi \rangle$ has three stages characterized as a rapid increase, followed by a plateau
+and finally as jamming sets in, a slow increase or decrease. However when initial ordering is present this behavior is different. At 
+$\bar{B}: 0.2 \rightarrow 1.0$, bijels stabilized by ellipsoidal particles see a gradual increase in $\langle \psi \rangle$ for both particle aspect ratios.
+At stronger magnetic fields, $\bar{B}: 0.5 \rightarrow 1.0$ and $\bar{B}: 1.0 \rightarrow 1.0$, there is little to no change in $\langle \psi \rangle$ indicating
+that the magnetic field has no effect on the particle monolayer. This indicates that the mechanism of structural response if beginning with an ordered particle
+monolayer differs from that of a disordered one. We confirm this by plotting the Steinhardt 6 fold order parameter $\langle Q_6 \rangle$ in Figure \ref{fig:Q6-field_up}
 
-\subsection{Decreasing the applied
-field}\label{decreasing-the-applied-field}
+\begin{figure} 
+    \centering 
+    \includegraphics[scale=0.4]{../figures/results/paper2/Q6-field_up.png} 
+    \caption{Plots of the evolution of the average interface angle \(\langle Q6 \rangle\) for bijels stabilized 
+             by oblate (left) and prolate (right) particles, as a function of the initial microstructure and subsequent magnetic field application.
+             The dynamics observed can be seen to be a function of the initial microstructure.} 
+    \label{fig:Q6-field_up} 
+\end{figure}
 
-Bijels are kinetically stable structures whose properties are dependent
-upon the stability of the particle monolayer. Past work into responsive
-emulsions have demonstrated resilience to microstructure changes after
-application and removal of stimuli even after several months. \cite{cui_stabilizing_2013} However,
-in the systems simulated above the particles need not necessarily be in
-thermodynamically stable states when jammed upon removal of stimuli as
-the particles take up a arrangements not observed when no field is
-applied. In this section, we explore how removal of the magnetic field
-changes the microstructure of the bijel as a function of the initial
-particle order. We use bijels simulated under
-$\bar{B}_{template} = 0, 0.2, 0.5, 1$ during formation of the bijel. Once
-the microstructure has stabilized, we switch off the magnetic field and
-observe the time evolution of the system for $t = 10^5$ timesteps.
+For oblate particles, both the \(\bar{B}: 0.0 \rightarrow 1.0\) and 
+\(\bar{B}: 0.2 \rightarrow 1.0\) cases exhibit a three-phase progression characterized as an initial decline in \(\langle Q_6 \rangle\), followed by a 
+plateau and a subsequent increase that stabilizes over time. The most pronounced decrease is observed in the \(\bar{B}: 0.0 \rightarrow 1.0\) case, where a 
+highly ordered monolayer undergoes significant disruption due to the sudden field-induced reorientation of particles. The recovery of \(\langle Q_6 \rangle\) 
+following this dip reflects the system's gradual reordering as particles adjust to their new orientation and repack at the interface.
+For the \(\bar{B}: 1.0 \rightarrow 1.0\) system, \(\langle Q_6 \rangle\) remains nearly constant, indicating that the monolayer was already aligned and 
+structurally stable at the onset of the simulation. The \(\bar{B}: 0.5 \rightarrow 1.0\) case stands out as an intermediate response, with only minor 
+fluctuations in \(\langle Q_6 \rangle\), suggesting limited capacity for additional structural reorganization due to pre-existing particle alignment.
+
+In the case of prolate particles, the behavior for systems with lower initial field values (\(\bar{B}: 0.0 \rightarrow 1.0\) 
+and \(\bar{B}: 0.2 \rightarrow 1.0\)) show monotonic increases in \(\langle Q_6 \rangle\), indicating a progressive gain in local particle ordering as the 
+field drives further interfacial reorganization. The magnitude and rate of increase are greatest in the \(\bar{B}: 0.0 \rightarrow 1.0\) case, which aligns with 
+the larger structural transformations observed in the microstructure. In contrast, the \(\bar{B}: 1.0 \rightarrow 1.0\) case remains largely unchanged, 
+confirming that the system has already reached its field-aligned state. The $\bar{B}: 0.5 \rightarrow 1.0$ shows some variations, although broadly there are no
+significant changes in the interfacial arrangement.
+
+Taken together, the results reveal two distinct categories of structural response in magnetically responsive bijels, governed by the initial degree of particle 
+ordering. The first category arises when the bijel is stabilized by a disordered particle monolayer. In this case, the application of a magnetic field drives 
+particle rotation and tilting out of the interface, which reduces the available interfacial area stabilized by the particles. This destabilization initiates 
+domain coarsening. As the fluid domains grow, capillary interactions couple with the evolving particle orientations, allowing the interface to deform in concert 
+with the particle dynamics. Ultimately, the microstructure becomes kinetically arrested as the particles rejam in their new field-aligned configurations, leading 
+to a stable, coarsened structure.
+
+The second category corresponds to systems with an initially nematically ordered monolayer, where the director is misaligned with the magnetic field. Here, the 
+applied field reorients the particles within the plane of the interface without inducing unjamming. Because the particle network remains structurally constrained, 
+the interface angle increases gradually as particles rotate, but without triggering large-scale fluid reorganization. Microstructural changes in this regime are 
+instead driven by localized adjustments in interfacial packing, rather than full-scale interface remodeling.
+
+Finally, when the particle monolayer is already well-aligned with the magnetic field direction, minimal reorientation occurs, and no significant structural 
+response is observed. This finding highlights that particle reorientation—particularly when it induces or is coupled with unjamming—is a prerequisite for 
+enabling dynamic microstructural evolution in bijels under magnetic fields. These insights underscore the importance of processing history and interfacial 
+particle configuration in tuning bijel responsiveness for functional applications.
+
+\subsection{Decreasing the applied field}
+\label{decreasing-the-applied-field}
+
+Bijels are kinetically arrested systems whose long-term structural properties are governed by the stability and arrangement 
+of the interfacial particle monolayer. Prior studies on responsive emulsions have shown that even after the removal of external 
+stimuli, the microstructure often remains unchanged for extended periods due to the interfacial 
+jamming of particles \cite{cui_stabilizing_2013}. Similarly, in the hysteresis experiments 
+discussed earlier (Figure~\ref{fig:hysteresis_curve}), we observed that reducing or removing the magnetic field did not 
+lead to a reversal of domain coarsening or particle realignment, suggesting an inherent structural resilience once the bijel 
+has stabilized.
+
+However, bijels are formed through a dynamic arrest during spinodal decomposition, and the 
+particles jam in configurations that may not correspond to a thermodynamic minimum particularly when a magnetic field is 
+applied during formation. Gunther et al. also showed that bijels stabilized by ellipsoidal particles exhibited timescales 
+of response distinct from bijels stabilized by spherical particle due to steric effects between ellipsoidal paticles.
+Therefore, this section will seek to understand to what extent the initial particle order affects the 
+bijel's capacity to relax or restructure upon removal of the field. To explore this, 
+we now examine the post-stimulus structural response of bijels formed under different field conditions 
+\(\bar{B}_{\text{template}} = 0.0, 0.2, 0.5, 1.0\). After allowing each structure to fully stabilize under a 
+constant magnetic field, we abruptly switch off the field and observe the subsequent time evolution of both the 
+microstructure and interfacial particle behavior over a duration of \(t = 10^5 \Delta t\). This analysis aims to 
+clarify the mechanisms that underpin the apparent irreversibility captured in the hysteresis response and further 
+assess the role of processing history in bijel stability.
 
@@
 \includegraphics[scale=0.4]{../figures/results/paper2/microstructure_viz-field_down.png} 
-\caption{Visualizations of bijels stabilized with oblate and prolate particles simulated at $t = 0$ (left column) and $t = 10^5$ (right column). 
-         The first and third rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids respectively with an applied 
-         field of $\bar{B}_z = 0.2$. The second and fourth rows show the particle monolayer of bijels stabilized with oblate and prolate ellipsoids 
-         respectively with an applied field of $\bar{B}_z = 1$. We switch off the applied field in both cases and show that while particle reorientation 
-         occurs, it has little effect on the microstructure of the bijel.}
+\caption{Snapshots of bijels stabilized by prolate ellipsoids at 
+         the initial and final time steps after the removal of an applied magnetic field. The top row corresponds to the case where 
+         the field is reduced from \(\bar{B} = 0.2 \rightarrow 0.0\), and the bottom row from \(\bar{B} = 1.0 \rightarrow 0.0\)}
 \label{fig:microstructure_viz-field_down}
@@
 
-In Figure \ref{fig:microstructure_viz-field_down}, we visualize the time
-evolution of the microstructure of bijels with processing history
-$\bar{B}:0.2 \rightarrow 0$ (top) and $\bar{B}:1 \rightarrow 0$
-(bottom). When switching the field off, the microstructure
-remains largely the same, demonstrating the kinetic stability of bijels.
-However, the particle monolayer, while still showing order, appears to
-be slowly losing that order as particles are beginning to become
-randomly oriented. This is especially obvious in the
-$\bar{B}:1 \rightarrow 0$ process, demonstrating that the dynamics of
-the system is dependent upon the initial order of the particle
-monolayer.
+FIgure \ref{fig:microstructure_viz-field_down} shows that in 
+both cases, the bulk microstructure remains effectively unchanged over the course of the simulation, highlighting the 
+kinetic stability and arrested nature of the bijel once jamming has occurred.
+However, closer inspection of the interfacial particle arrangement reveals subtle but important differences. In the 
+\(\bar{B}: 0.2 \rightarrow 0.0\) case, the particles retain a degree of orientational order, although slight deviations 
+from the field-aligned configuration begin to emerge. In contrast, for \(\bar{B}: 1.0 \rightarrow 0.0\), where the 
+initial nematic order was stronger, the system exhibits more apparent disorganization by the final time step. This 
+suggests that while the jammed interface resists large-scale rearrangement, there is a gradual relaxation of particle 
+orientations in the absence of the aligning field. The extent of this relaxation appears to correlate with the initial 
+alignment strength, indicating that systems formed under stronger magnetic fields exhibit greater reorientation when 
+the field is removed. We probe the effect of these reorientations by calculating the time evolution of the domain size
+and the corresponding nematic order parameter of the particles in Figure \ref{fig:domain_size-field_down}
 
@@
 
-The results in \ref{fig:domain_size-field_down}, show with the exception of $\bar{B}:0\rightarrow0$, all
-domain sizes show a slow coarsening over time. This is reflected clearly
-in the bijels stabilized by prolate particles, showing that that the
-changes in properties of the particle monolayer due to the applied
-magnetic field during bijel template simulation does not play a
-significant role in the dynamics of the bijel. We attribute the large
-increase in the domain size in oblate particle stabilized
-$\bar{B}:0\rightarrow0$ case to be due to coalescence of two
-domains, characterized as a two step process where slower long
-timescale domain coarsening initially occurs followed by a rapid jump in the
-domain size when coalscence between domains occur.
+Figure~\ref{fig:domain_size-field_down} presents the time evolution of the normalized domain size (\(L/R\)) and nematic 
+order parameter (\(S\)) for bijels stabilized by oblate (left) and prolate (right) particles following the removal of an 
+applied magnetic field. For all systems except oblate particle stabilized bijel with \(\bar{B}: 0.0 \rightarrow 0.0\), 
+a modest degree of domain coarsening is observed. This slow, steady increase in domain size indicates that while the 
+global microstructure remains largely intact, minor structural rearrangements may still occur post-stimulus, particularly 
+at long timescales. This behavior is more prominent in prolate particle systems, suggesting that elongated particles 
+may provide greater local flexibility for slight monolayer relaxation without disrupting the overall network.
+A notable exception arises in the oblate \(\bar{B}: 0.0 \rightarrow 0.0\) case, which exhibits a sudden and pronounced 
+increase in domain size at later times. This behavior is attributed not to gradual coarsening but to a domain coalescence 
+event.
 
-The nematic order parameter of all runs with prexisting particle order
-show order dependent decreases, arising from interfacial forces causing
-the particles to return to a thermodynamically optimum configuration on
-the interface. To quantify is the coarsening that takes place is
-anisotropic, We define the relative change in domain size as
-$\Delta L = \frac{L_{f} - L_{i}}{L_{i}}$, where $L$ represents
-either $L_{\perp}$ or $L_{\parallel}$. The same formulation is
-applied to the tortuosity in the respective directional components. We
-do this to characterize the $\Delta \bar{B}$ dependent changes
-observed in the domain anisotropy. The results are presented in Figure
-\ref{fig:domain_size_aniso-field_up}.
+The nematic order parameter \(S\) for all field-removal scenarios demonstrates a consistent, order-dependent decrease over 
+time. This trend suggests that in the absence of an aligning field, particles gradually relax from their field-induced 
+configurations toward thermodynamically preferred orientations governed by interfacial capillary interactions. The 
+magnitude of this decay correlates with the initial degree of ordering: systems formed under higher magnetic fields 
+(\(\bar{B} = 0.5\) and \(1.0\)) show the most significant reduction in \(S\), reflecting a greater degree of reorientation.
+
+These results reinforce the interpretation that bijel microstructure is resilient to field removal, with no meaningful 
+reversal in domain architecture once jamming has occurred. However, the interfacial particle monolayer continues to evolve 
+at the microscale, with orientation relaxation providing a residual mechanism for slow, local structural change. To determine 
+whether this relaxation induces anisotropic coarsening, we next quantify the directional change in domain size and tortuosity 
+using the relative change metric \(\Delta L = \frac{L_f - L_i}{L_i}\), applied separately to \(L_\perp\) and \(L_\parallel\). 
+The same formulation is used to compute directional tortuosity changes, with results summarized in 
+Figure~\ref{fig:domain_size_aniso-field_up}.
 
@@
 \includegraphics[scale = 0.5]{../figures/results/paper2/domain_size_aniso-field_down.png} 
-\caption{Plotting the anisotropic domain sizes and tortuosity at the final timestep on the left and right respectively for bijels stabilized with oblate and 
-         prolate ellipsoidal particles starting at different particle orders. We plot these results against the change in the applied field strength, 
-         $\Delta B$ and show that there are only minor differences in the microstructure of stimuli responsive bijels once the magnetic field is switched off.} 
+\caption{Plots of the anisotropic structural response of bijels after the removal of 
+         magnetic fields, by showing the relative change in directional domain size \((\Delta L)\) and tortuosity \((\Delta \tau)\) 
+         as a function of \(\Delta \bar{B}\), the change in field strength from the templated to final state. Blue curves correspond 
+         to bijels stabilized by oblate particles, and red curves to those stabilized by prolate particles.} 
 \label{fig:domain_size_aniso-field_down} 
@@
 
-Figure \ref{fig:domain_size_aniso-field_down}, shows that there are
-small $\Delta \bar{B}$ dependent changes in the anisotropic domain
-size and tortuosity for both particle morphologies. However, there are
-no clear trends that can be developed from these plots, suggesting that
-the changes are overall isotropic and any differences observed arise
-from the arrangement of particles. This suggests that the response of
-the material to the removal of a magnetic field is isotropic and only
-dependent upon the capillary interactions with the particle monolayer.
-We showed earlier that the application of magnetic fields change the
-local state of the particles at the interface. However the results shown
-thus far demonstrate that that these changes do not seem to affect the
-coarsening of the bijel once stimuli is removed. To investigate why this
-is the case, we plot $\langle \psi \rangle$ and
-$\langle Q6 \rangle$ for bijels stabilized with ellipsoidal particles
-below.
+Overall, only minor anisotropic changes in domain size and tortuosity are observed following field removal, with no consistent 
+or monotonic dependence on \(\Delta \bar{B}\). This suggests that although particles may gradually relax from their field-induced 
+alignment, the resulting structural rearrangements are subtle and largely isotropic at the microstructural scale. The small 
+fluctuations observed in \(\Delta L\) and \(\Delta \tau\) likely reflect localized heterogeneities in the particle monolayer 
+rather than coordinated, directional coarsening. These findings support the notion that once the magnetic field is removed, 
+the dominant force acting on the particles is the interfacial capillary interaction, which seeks to minimize interfacial 
+energy without preference for a particular direction.
+
+Importantly, this contrasts with the structural response observed during the application of a magnetic field, where clear 
+anisotropy emerged as a result of field-driven particle reorientation. Here, despite the monolayer initially being in an 
+anisotropic, ordered state, the system exhibits no significant directional relaxation, underscoring the kinetic resilience 
+of the jammed interface. Thus, the microstructural evolution following stimulus removal appears to be dominated by slow, 
+isotropic relaxation rather than directional restructuring.To further understand the role of the capillary interactions on the 
+particle monolayer, we examine the time evolution of the interface angle \(\langle \psi \rangle\).
 
@@
 \includegraphics[scale=0.4]{../figures/results/paper2/interface_angle-nint-field_down.png} 
-\caption{Plots of the average interfacial angle $\psi$ and the number of particles on the interface $n_{int}$ on the left and right respectively, 
-         plotted against time for bijels stabilized with ellipsoidal particles with aspect ratio 2. When looking at $\psi$, the $\bar{B}:1 \rightarrow 1$ 
-         case looks distinctly different from the other processes. At $\bar{B} = 1$, the particles are totally ordered to the field. This suggests that 
-         the presence of some particle disorder resists domain coarsening.} 
+\caption{Plots of the average interfacial angle $\langle \psi \rangle$  plotted against time for bijels stabilized by oblate and prolate particles
+         on the left and right plots respectively. They show slight increases in $\langle \psi \rangle$ over time indicating that the particles are
+         slowly tilting out of the interface, inducing the domain coarsening observed.} 
 \label{fig:interface_angle-field_down} 
@@
 
-From Figure \ref{fig:interface_angle-field_down}, there are minor differences to the time when $\langle \psi \rangle$ and $\langle Q6 \rangle$
-begin to change. We also characerize that $\langle \psi \rangle$ increases for both particle morphologies, even for systems that have initial ordering.
-Similarly, $\langle Q6 \rangle$ decreases for all systems. Thus, the presence of ordering does not greatly affect trends in the evolution of the
-particle monolayer, and thus has an insignificant effect on the microstructure of the bijel.
+Figure \ref{fig:interface_angle-field_down} shows that the the rate and extent of angular relaxation appear relatively insensitive to the initial degree of 
+order imposed by the templating field. For oblate particles, \(\langle \psi \rangle\) increases steadily regardless of initial alignment strength, indicating that 
+even highly ordered monolayers do not retain their field-imposed orientation indefinitely. Similarly, for prolate particles, although the change in 
+\(\langle \psi \rangle\) is smaller in magnitude, a comparable upward trend is evident.
 
-From the microstructure evolution, steric effects are the
-driving force behind microstructure changes in the absence of a magnetic
-field. Even though we observe that the interface angle and Steinhardt
-order parameter show substantial changes from the scenario where no
-field is applied, these are insufficient to change the average steric
-effect driven particle monolayer rearrangement observed, causing
-coarsening of the bijel at long timescales to possess trends similar to what was observed by
-Gunther et al. \cite{gunther_timescales_2014}
+These results suggest that the particle monolayer continues to evolve post field-removal, driven by interfacial forces seeking to minimize the total interfacial 
+energy. However, since these angular adjustments do not lead to noticeable changes in the bulk microstructure it can be 
+inferred that rotational relaxation alone is insufficient to trigger further domain coarsening once jamming has occurred. This supports the conclusion that 
+structural irreversibility in these systems arises primarily from the kinetic constraints imposed by jamming, rather than any residual orientational stress 
+within the particle layer.
 
@@
 
-Owing to the applicability of bijels in the catalyst support, filtration membrane and drug release spaces, we were interested in identifying how bijels stabilized 
-by magnetically responsive ellipsoidal particles could be used to create active soft matter. In this work, we have studied the effect of the application, increase 
-or removal of magnetic fields on the structural response of bijels stabilized by magnetically responsive ellipsoids using hybrid Lattice Boltzmann-Molecular Dynamics 
-simulations. We first characterized the hysteresis curve of the bijel, identifying that the process history dependence of the bijel microstructure. To identify why 
-We observed the path dependence and the microstructure change observed when applying magnetic fields after synthesis, we considered three starting setups; The first 
-applying a field of varying strength to bijel templates that were simulated with no magnetic field applied. The second involved increasing the applied field 
-strength onto bijel templates that were simulated with increasing field strengths. The final setup involves removing a field from bijel templates that were simulated 
-with various field strengths.
+In this chapter, we investigated the microstructural response of bijels stabilized by anisotropic magnetic ellipsoids under varying magnetic field protocols. 
+By systematically analyzing the evolution of domain size, anisotropy, and particle-level order in response to increasing and decreasing magnetic fields, 
+we uncovered key mechanisms that govern structural adaptability and kinetic stability in these systems.
 
-We found that application of magnetic fields onto bijels stabilized by magnetically responsive ellipsoidal particles results in an average microstructure change up to 
-$5\%$ when investigating changes in the average microstructure. We also identified that the structures become anisotropic upon application of the magnetic field for 
-oblate and prolate particles. The anisotropy is particle dependent with bijels stabilized by oblate particles seeing an increase in $L_{\perp}$ of up to $60\%$ and for 
-prolate particles an increase in $L_{\parallel}$ of up to $40\%$ with a corresponding decrease in the tortuosity in that axis. This is caused by the reorientation of the 
-particles to the magnetic field, followed by domain coarsening as the interfacial coverage of the particles decrease, before jamming in place again. We characterize that 
-while particle reorientation to the applied field initiates microstructural response, local rearrangement of the particle monolayer is the controlling mechanism of 
-domain size evolution as characterized by identifying the dominant timescales 
-of response for both particle morphologies. However, their time evolution is different with bijels stabilized by prolate particles undergoing a local crystallization when 
-the average six fold Steinhardt order parameter or $\langle Q_6 \rangle \geq 0.38$. For bijels stabilized by oblate particles, a global minimum of the $\langle Q_6 \rangle$ 
-characterizes the dynamics of the system.
+We first demonstrated that bijels subjected to increasing magnetic field strength exhibit hysteresis in its structural response, wherein the domain size increases 
+with field application but does not revert upon field removal. This behavior was attributed to particle reorientation at the interface, which induces local 
+unjamming and subsequent domain coarsening. Through visualization and quantitative analysis, we showed that reorientation causes particles to tilt out of the 
+interface, reducing the stabilized interfacial area and driving fluid domain coalescence. Importantly, this microstructure change is constrained by the degree 
+of initial particle disorder with systems containing pre-aligned particles exhibiting diminished structural response, indicating that reorientation, not field strength 
+alone is the primary driver of field-induced structural response.
 
-When increasing the applied field strength, we observe that the difference between the final and initial magnetic fields is correlated to the domain size change observed. 
-We observe that the anisotropic domain size changes are also dependent upon this difference, with the largest difference being observed when characterizing a bijel template 
-simulated under no field before having a field strength of $\bar{B} = 1$ applied to it. When looking at the particle monolayer, we characterize three behaviors seen from the 
-average interfacial angle $\langle \psi \rangle$ and $\langle Q_6 \rangle$. These behaviors are further differentiated for each particle morphology. For oblate particles, 
-the first behavior is characterized as a reorientation of the particle on the interface seen as an increase in $\langle \psi \rangle$ over time with a corresponding decrease 
-in $\langle Q_6 \rangle$ as the particles do not close pack anymore. For prolate particles, we see a slight reduction in $\langle \psi \rangle$ and greater ordering of the 
-particles from $\langle Q_6 \rangle$. The second behavior originates from small reorientations of the particles at the monolayer which do not greatly affect the interfacial 
-angle but cause a loss or gain of particle order on the interface. The final behavior is characterized as long timescale domain coarsening as there is no change between the 
-applied magnetic field and the magnetic field used to simulate the template.
+Two distinct categories of structural response emerged: one in which disordered particle monolayers undergo magnetic reordering that enables large-scale domain 
+coarsening, and a second in which initially ordered systems reorient locally but remain globally jammed, leading to minimal structural adaptation. This transition 
+was further reinforced by the observed saturation in domain growth as a function of particle alignment, highlighting a limit to how much structural change can be 
+achieved post-jamming.
 
-Finally, when decreasing the magnetic field strength, we observe little difference between bijel templates made with any field strength and no field. From the average domain 
-size, we see that the bijels coarsen at approximately the same rate. Upon further investigation of the microstructure anisotropy, we identify that the anisotropic structure 
-does not change as well, suggesting coarsening effects are independent of the effect of the local differences at the particle monolayer. After characterizing 
-$\langle \psi \rangle$ and $\langle Q_6 \rangle$, we see differences at the initial state which, while changing the initiation point of the dynamics, does not play a large
- role otherwise. Thus any domain size change observed when removing a field is due to interfacial capillary interactions.
+Upon magnetic field removal, we found that the bijel microstructure remains largely unchanged, consistent with the kinetic arrest characteristic of these systems. 
+While the particle monolayer exhibited gradual relaxation—evident through changes in interface angle—these dynamics were insufficient to trigger significant domain 
+restructuring. Directional domain size and tortuosity metrics further confirmed that coarsening post field removal was isotropic and minimal, regardless of initial 
+ordering.
 
-It has been shown how the domain size and tortuosity can be used to adjust the flow rate, separations efficiency or reaction rate in applications such as cross-flow reactors, 
-drug delivery and liquid-liquid extraction. These results show that the properties of bijels can be tuned in-situ for these applications although it appears that it can only 
-be done once. With the results presented here, we have considered only one set of parameters that control the dynamics. Parameters not changed such as the fluid density, 
-viscosity, surface tension and volume fraction of particles may impact the mechanisms and rate of domain size control. We also do not consider magnetic 
-fields applied in different directions which even in this simple setup may be able to modify the microstructure considerably, or gradient magnetic fields which may allow 
-more effective unjamming and re-jamming dynamics for further microstructure modification than what has been shown here.
+Collectively, these results elucidate the role of particle-level interactions in dictating the field-responsive behavior of bijels. They reveal that while 
+magnetic fields offer a route to tailor microstructure on demand, the efficacy of this control hinges on the degree of initial disorder and the system’s 
+jamming history. This mechanistic understanding provides design principles for harnessing bijel responsiveness in practical applications—such as tunable 
+porous media, controlled release scaffolds, or adaptive separation systems—where reversibility, anisotropy, and stability must be precisely managed.
 
-Effects such as the steric hindrance between particles may lessen as particle size reduces as particles are more easily able to conform to the curvature of the interface. 
-The impact this may have on the results seen with the micron-sized particles used here is unknown. In many of the applications listed above, it is also unknown how changes 
-in the spacing between particles affect underlying reactivity, selectivity or diffusion rates which have implications past the domain size and tortuosity changes characterized 
-in the literature. Furthermore, it is unknown how additional particle interactions such as chemical cross-linking or charge affect the results seen here. Both strategies are 
-used in bijels to reinforce them against shear to facilitate higher shear rates, useful in cross-flow reactors and separation membranes. In conclusion, our simulations provide 
-qualitative trends into the expected microstructure change and their underlying mechanisms and timescales when applying or removing a field from a bijel stabilized by 
-anisotropic particles by modifying their orientation and packing.
+% Owing to the applicability of bijels in the catalyst support, filtration membrane and drug release spaces, we were interested in identifying how bijels stabilized 
+% by magnetically responsive ellipsoidal particles could be used to create active soft matter. In this work, we have studied the effect of the application, increase 
+% or removal of magnetic fields on the structural response of bijels stabilized by magnetically responsive ellipsoids using hybrid Lattice Boltzmann-Molecular Dynamics 
+% simulations. We first characterized the hysteresis curve of the bijel, identifying that the process history dependence of the bijel microstructure. To identify why 
+% We observed the path dependence and the microstructure change observed when applying magnetic fields after synthesis, we considered three starting setups; The first 
+% applying a field of varying strength to bijel templates that were simulated with no magnetic field applied. The second involved increasing the applied field 
+% strength onto bijel templates that were simulated with increasing field strengths. The final setup involves removing a field from bijel templates that were simulated 
+% with various field strengths.
+
+% We found that application of magnetic fields onto bijels stabilized by magnetically responsive ellipsoidal particles results in an average microstructure change up to 
+% $5\%$ when investigating changes in the average microstructure. We also identified that the structures become anisotropic upon application of the magnetic field for 
+% oblate and prolate particles. The anisotropy is particle dependent with bijels stabilized by oblate particles seeing an increase in $L_{\perp}$ of up to $60\%$ and for 
+% prolate particles an increase in $L_{\parallel}$ of up to $40\%$ with a corresponding decrease in the tortuosity in that axis. This is caused by the reorientation of the 
+% particles to the magnetic field, followed by domain coarsening as the interfacial coverage of the particles decrease, before jamming in place again. We characterize that 
+% while particle reorientation to the applied field initiates microstructural response, local rearrangement of the particle monolayer is the controlling mechanism of 
+% domain size evolution as characterized by identifying the dominant timescales 
+% of response for both particle morphologies. However, their time evolution is different with bijels stabilized by prolate particles undergoing a local crystallization when 
+% the average six fold Steinhardt order parameter or $\langle Q_6 \rangle \geq 0.38$. For bijels stabilized by oblate particles, a global minimum of the $\langle Q_6 \rangle$ 
+% characterizes the dynamics of the system.
+
+% When increasing the applied field strength, we observe that the difference between the final and initial magnetic fields is correlated to the domain size change observed. 
+% We observe that the anisotropic domain size changes are also dependent upon this difference, with the largest difference being observed when characterizing a bijel template 
+% simulated under no field before having a field strength of $\bar{B} = 1$ applied to it. When looking at the particle monolayer, we characterize three behaviors seen from the 
+% average interfacial angle $\langle \psi \rangle$ and $\langle Q_6 \rangle$. These behaviors are further differentiated for each particle morphology. For oblate particles, 
+% the first behavior is characterized as a reorientation of the particle on the interface seen as an increase in $\langle \psi \rangle$ over time with a corresponding decrease 
+% in $\langle Q_6 \rangle$ as the particles do not close pack anymore. For prolate particles, we see a slight reduction in $\langle \psi \rangle$ and greater ordering of the 
+% particles from $\langle Q_6 \rangle$. The second behavior originates from small reorientations of the particles at the monolayer which do not greatly affect the interfacial 
+% angle but cause a loss or gain of particle order on the interface. The final behavior is characterized as long timescale domain coarsening as there is no change between the 
+% applied magnetic field and the magnetic field used to simulate the template.
+
+% Finally, when decreasing the magnetic field strength, we observe little difference between bijel templates made with any field strength and no field. From the average domain 
+% size, we see that the bijels coarsen at approximately the same rate. Upon further investigation of the microstructure anisotropy, we identify that the anisotropic structure 
+% does not change as well, suggesting coarsening effects are independent of the effect of the local differences at the particle monolayer. After characterizing 
+% $\langle \psi \rangle$ and $\langle Q_6 \rangle$, we see differences at the initial state which, while changing the initiation point of the dynamics, does not play a large
+%  role otherwise. Thus any domain size change observed when removing a field is due to interfacial capillary interactions.
+
+% It has been shown how the domain size and tortuosity can be used to adjust the flow rate, separations efficiency or reaction rate in applications such as cross-flow reactors, 
+% drug delivery and liquid-liquid extraction. These results show that the properties of bijels can be tuned in-situ for these applications although it appears that it can only 
+% be done once. With the results presented here, we have considered only one set of parameters that control the dynamics. Parameters not changed such as the fluid density, 
+% viscosity, surface tension and volume fraction of particles may impact the mechanisms and rate of domain size control. We also do not consider magnetic 
+% fields applied in different directions which even in this simple setup may be able to modify the microstructure considerably, or gradient magnetic fields which may allow 
+% more effective unjamming and re-jamming dynamics for further microstructure modification than what has been shown here.
+
+% Effects such as the steric hindrance between particles may lessen as particle size reduces as particles are more easily able to conform to the curvature of the interface. 
+% The impact this may have on the results seen with the micron-sized particles used here is unknown. In many of the applications listed above, it is also unknown how changes 
+% in the spacing between particles affect underlying reactivity, selectivity or diffusion rates which have implications past the domain size and tortuosity changes characterized 
+% in the literature. Furthermore, it is unknown how additional particle interactions such as chemical cross-linking or charge affect the results seen here. Both strategies are 
+% used in bijels to reinforce them against shear to facilitate higher shear rates, useful in cross-flow reactors and separation membranes. In conclusion, our simulations provide 
+% qualitative trends into the expected microstructure change and their underlying mechanisms and timescales when applying or removing a field from a bijel stabilized by 
+% anisotropic particles by modifying their orientation and packing.

### 2025-04-07 chapters/dissertation-tap.tex
Changes 1. Modified conclusion section in final remarks 2. Changes image sized in structural response of bijels 3. modified abstract and introduction to include structural analysis results

@@
     orientation of the magnetic moment relative to the particle's long axis, also affects how particles arrange themselves at the fluid 
-    interface.
+    interface. Particle reorientation affects the curvature of the interface as particles with smaller cross sectional area are less disruptive
+    to the saddle like interface shape that minimal surfaces possess. Topological examinations of the interface surface, 
+    demonstrating that the number of interconnected channels in the system decreased over time and that the average channel sizes obtained follow
+    the same trend as that of the domain size.
 

### 2025-04-07 chapters/final_remarks.tex
Changes 1. Modified conclusion section in final remarks 2. Changes image sized in structural response of bijels 3. modified abstract and introduction to include structural analysis results

@@
 
-Owing to their high surface area to volume ratio, porous materials are seeing a surge in popularity in applications
-such as catalysis, battery electrodes and pharmaceuticals. Given their wide variety of applications, identifying 
-fabrication techniques that allow access to the various pore length scales is of interest. One such synthesis technique
-is emulsion templating which offers a wide variety of accessible microstructures, addition of stimuli response and 
-large number of possible systems that can be fabricated. A microstructure that can be fabricated from emulsion templates
-is the bicontinuous interfacially jammed emulsion gel (bijel).
+Porous materials, owing to their high surface-area-to-volume ratio, have gained significant attention in a wide range of 
+applications including catalysis, battery electrodes, and pharmaceuticals. Their functionality across diverse sectors has 
+driven a growing interest in fabrication techniques capable of accessing and tuning pore structures across multiple length 
+scales. Emulsion templating has emerged as a particularly versatile synthesis route, offering access to a broad spectrum of 
+microstructures, the potential for stimuli-responsive behavior, and compatibility with a wide variety of material systems. 
+Among the structures that can be generated through emulsion templating, the bicontinuous interfacially jammed emulsion gel 
+(bijel) stands out for its unique interconnected morphology and potential for functional material design.
 
-Bijels are normally fabricated using Thermally Induced Phase Separation (TIPS). However, TIPS does not allow for continuous
-fabrication of bijels. More recent fabrication techniques such as Solvent Transfer Induced Phase Separation (STrIPS) and 
-Vapor Induced Phase Separation (VIPS) allow for continuous fabrication and access to various microstructures. Both techniques
-require modifications to the initial emulsion mixture to facilitate microstructure adjustments, which affect the final rheological
-properties of the system. Decoupling the microstructure and the casting mixture of the bijel would allow for greater flexibility
-in the synthesis of the material.
+Traditional bijel fabrication relies on thermally induced phase separation (TIPS), a method that, while effective, does not 
+support continuous production. More recently developed techniques—such as Solvent Transfer Induced Phase Separation (STrIPS) 
+and Vapor Induced Phase Separation (VIPS)—enable continuous fabrication and offer greater control over microstructure. However, 
+these methods typically require modifications to the initial emulsion formulation, coupling the casting mixture to the resulting 
+morphology. Decoupling these parameters would offer significantly greater flexibility in bijel design, allowing for independent 
+tuning of material properties and processing conditions.
 
-Stimuli response has been used before to modify the microstructure of particle stabilized emulsions. Magnetic fields offer
-targeted material response and low applied field strengths necessary for response. Past work investigating the effect of magnetic
-stimuli on bijels stabilized with spherical particles yielded little microstructure change. However, anisotropic particles have
-also been used to stabilize bijels. Anisotropic particles at interfaces under magnetic fields have been shown to tilt out of 
-interfaces. These effects have yet to be captured in bijels stabilized by ellipsoidal particles under magnetic fields.
-This study addresses this knowledge gap using a hybrid Molecular-Dynamics multicomponent method Lattice Boltzmann Method.
-We split this work into three aims; Aim 1 addressed the microstructure obtained when applying a magnetic field of various strengths 
-onto bijels stabilized by ellipsoidal particles, compared to bijels stabilized wih spherical particles. Aim 2 addressed the 
-structural response of bijels stabilized by ellipsoidal particles and analyzes the effect of initial order of the particle monolayer
-on the structural response observed. Aim 3 addressed the constant shear response of bijels stabilized by ellipsoidal particles
-with pre-existing particle order and under magnetic fields.
+External stimuli have been previously employed to modulate the microstructure of particle-stabilized emulsions, with magnetic 
+fields offering particular promise due to their directionality and the relatively low energy required to induce a response. Prior 
+studies have shown that bijels stabilized with spherical particles exhibit limited structural response to magnetic fields. In 
+contrast, anisotropic particles such as ellipsoids have demonstrated the capacity to reorient and tilt out of fluid interfaces 
+under magnetic influence. However, the effect of magnetic fields on bijels stabilized by ellipsoidal particles remains unexplored.
 
-In Aim 1, bijels stabilized with spherical particles do not respond to the application of a magnetic field. However, bijels stabilized
-with ellipsoidal particles have an increase in the average domain size by 3 \%. The microstructure also becomes anisotropic, 
-characterized as a change in the directional tortuosity and distribution of channel widths as a function of the distance from the 
-interface. The response characterized was particle morphology specific due to the orientation of the particle magnetic moment with 
-respect to the direction of the long axis of the particle. This causes the particles to arrange differently on the interface. The 
-microstructure anisotropy is caused by direction specific jamming of the particle monolayer originating from particle ordering to 
-the magnetic field. The direction specific jamming originates from the orientation of the particles to the magnetic field. The direction
-specific jamming also reduces the local curvature of the system as the interface location moves with the particle.
-To investigate the role of the particle monolayer in greater detail, we characterize the orientational order to the magnetic field,
-angle to the interface and local particle ordering at the interface. The orientational order changes as a function of the applied field 
-strength and has particle morphology specific time evolution. When investigating the average interfacial angle of the particles to the 
-interface, it is shown how the capillary interactions with the interface differ, leading to the time evolution differences observed.
-When analyzing the ordering of particles on the interface, disc-like particles see lowered local ordering as the magnetic field strength is 
-increased while rod-like particles see greater local ordering. These properties are attributed to how those particle morphologies prefer 
-to orient themselves at interfaces to one another, with disc like particles preferring to stack while rod like particles order side to side 
-or end to end.
+This study addresses that gap through a series of hybrid simulations using a coupled Molecular Dynamics-Lattice Boltzmann framework. 
+We investigated how magnetic fields influence bijel formation and structure when stabilized by ellipsoidal particles, focusing on 
+three key aspects: the impact of magnetic field strength on microstructure compared to systems stabilized by spherical particles; 
+the structural response of these bijels under post-formation magnetic fields and how this response depends on the initial ordering 
+of the interfacial particle monolayer; and the rheological behavior of such systems under constant shear, particularly in relation 
+to prior magnetic field exposure and pre-existing interfacial particle alignment.
 
-In Aim 2, bijels stabilized by ellipsoidal particles demonstrate responses to an applied magnetic field. When applying a magnetic field
-onto a bijel template simulated with no magnetic fields, we see an average microstructure change of up to 5 \%. This microstructure change
-arises from the magnetic field driven re-orientation of particles at the interface. Particle reorientation creates microstructure anisotropy
-arising from the alignment of particles to the magnetic field. When analyzing the particle monolayer, we characterize the alignment of particles
-to the field direction, average interface angle and the local ordering of the particles. We demonstrate that the average interface angle increases
-as the particles reorient to the field before the capillary forces of the interfaces causes the interface to move, until jamming of the monolayer takes
-place. The local particle order during this process decreases for oblate particles and increases for prolate particles. We characterize that the local 
-order of the particles controls the timescales of response.
-When investigating the effect of pre-existing order of the particle monolayer, we show that the structural response of the bijel is dependent upon the
-difference between the field applied to make the bijel and the applied field when the field is applied in the same direction. We also characterize that the
-local particle monolayer is dependent upon the pre-existing order of the bijel. When switching off the magnetic field onto bijels made with a magnetic field,
-we see that the microstructure remains resilient to the removal of the magnetic field. We characterize that while there are differences in the particle monolayer,
-these differences manifest as when domain coarsening begins. When characterizing the hysteresis curve of the bijels stabilized with prolate particles,
-we see the effect of this.
+We first demonstrated that ellipsoidal particles alter the formation dynamics of bijels when subjected to external magnetic 
+fields during phase separation. We also explored how varying magnetic flux densities and particle aspect ratios affect structural outcomes. 
+In the absence of a magnetic field, ellipsoidal particles 
+aligned with the interface over time due to capillary interactions, contributing to slower coarsening and finer domain features compared 
+to spherical particles. Upon introducing magnetic fields, particles experienced additional torques that promoted alignment along the field 
+direction during formation. This field-induced reorientation improved interfacial packing efficiency and introduced directional cessation
+of coarsening, leading to bijels with domain anisotropy. Importantly, these effects were achieved without preventing the formation of a 
+stable, bicontinuous structure.
 
-In Aim 3, the rheology of bijels stabilized by ellipsoidal particles under shear was analyzed, specifically examining the effects of initial microstructure and a 
-constant magnetic field on the shear response. Using a Herschel-Bulkley fitting, shear-thinning behavior remains robust although the 
-flow index and yield stress are strongly influenced by particle morphology and magnetic field application. Increased particle ordering led to 
-lower yield stress in oblate-particle-stabilized bijels and higher yield stress in prolate-particle-stabilized bijels, highlighting the role of particle 
-shape in interfacial mechanics. Without a magnetic field, both particle monolayers remained adsorbed at the interface, but when a field was applied, 
-oblate particles flipped out of the interface, whereas prolate particles tilted, altering the flow field and impacting non-Newtonian behavior. Additionally, 
-coarsening driven by reduced interfacial particle coverage emerged as the dominant mechanism behind domain size evolution in sheared bijels. The anisotropic 
-domain growth trends matched expectations in all cases except when the field was removed, indicating that the history of field application significantly influences 
-microstructural evolution. These findings provide insight into the interplay between particle morphology, interfacial coverage, and external fields, contributing 
-to the understanding of magnetically tunable soft materials and structured emulsions.
+Structural characterization of bijels stabilized by ellipsoids revealed morphological detail across particle shapes and magnetic field strengths. 
+Six-fold bond orientational order emerged within the interfacial particle layers, but true crystalline order remained suppressed due to the 
+inherent curvature of the interface. Ellipsoidal particles increased the Gaussian curvature of the interface compared 
+to spheres, while increasing field strength tended to reduce this curvature by promoting particle alignment due to reductions in the interface
+deformation of each particle. This reduction in curvature indicated a more hyperbolic interfacial character.
+
+Topological analysis showed that the number of handles, or interconnected channels, decreased over time as coarsening progressed, following 
+a power-law relationship inversely proportional to domain size. After the onset of jamming, this decay slowed considerably. Notably, 
+channel size distributions (CSDs) revealed a wide range of channel dimensions but did not show systematic variation with 
+field strength, suggesting that magnetic field effects manifest more prominently in local structure and domain anisotropy. Still, the 
+average channel size derived from the CSD aligned well with conventional domain measurements, reinforcing the results obtained throughout
+the course of this work.
+
+Upon applying magnetic fields post formation, we observed significant structural rearrangements in bijels depending on the initial particle 
+configuration. Systems with disordered interfacial layers underwent domain coarsening and anisotropic growth due to field-induced unjamming 
+and subsequent re-jamming. Specifically, oblate particles induced perpendicular domain elongation of up to 60\%, while prolate particles led 
+to axial coarsening of up to 40\%. These shape-dependent responses were driven by particle rotation and interface realignment under magnetic 
+torque, and were quantified using average interface angles and Steinhardt $Q_6$ bond orientational order parameters. Importantly, once the 
+magnetic field was removed, the bijel structure largely remained in its field-aligned state. Only minor particle relaxation occurred, 
+indicating that capillary forces alone were insufficient to reverse the structural transformations, revealing a hysteresis-like behavior 
+in the response to magnetic stimuli.
+
+The degree of structural reorganization was closely linked to the initial state of the particle monolayer. We identified two primary 
+response modes. The first is where initially disordered layers unjammed and reorganized under magnetic fields before settling into a new 
+jammed configuration, and another where partially ordered particles reoriented to align with the field, modifying domain structure 
+without full unjamming. Systems with high initial order showed minimal structural change, suggesting that the dynamic response of bijels 
+can be pre-programmed via the interfacial order established during formation.
+
+The rheological behavior of these systems was equally sensitive to particle shape, magnetic field history, and interfacial order. All 
+bijels exhibited shear-thinning behavior, which is characteristic of non-Newtonian fluids. However, yield stress and flow 
+response varied significantly across systems. Prolate particle-stabilized bijels exhibited higher yield stress and more consistent flow 
+behavior with increasing magnetic alignment, attributed to improved interfacial adhesion and stress transfer. Conversely, oblate-stabilized 
+systems showed a decrease in yield stress when subjected to the same field history. This contrast was explained by the tendency of oblate 
+particles to tilt away from the interface under magnetic alignment, making the interfacial layer more susceptible to shear-induced buckling.
+
+Steinhardt $Q_6$ values and interface angle analyses further supported these interpretations. Higher $Q_6$ values in aligned prolate systems 
+indicated robust interfacial ordering and enhanced structural resistance under flow, while oblate systems with elevated interface angles 
+demonstrated weaker anchoring and a greater likelihood of particle dislodgment. The impact of particle geometry on interfacial mechanics 
+and flow resistance highlights the importance of shape-selective design for applications requiring tunable rheological properties, such as 
+drug delivery, 3D printing, or adaptive templating.
+
+This work provides several key insights that significantly advance the current understanding of field-responsive emulsions and structurally 
+tunable soft materials. By integrating ellipsoidal particle design with magnetic field stimuli, we demonstrate a new axis of control over 
+bijel formation and function. 
+Conceptually, our results refine the understanding of interfacial jamming in bijels. The identification of distinct 
+unjamming-rejamming mechanisms, modulated by both field strength and particle ordering, reveals that bijel structures are not passively 
+determined by initial phase separation dynamics. Instead, they are dynamically reconfigurable under external fields, with the extent of 
+reconfiguration governed by the memory of prior structural states. This introduces a paradigm in which bijels can be treated as 
+non-equilibrium materials with tunable hysteresis, offering a controllable blend of stability and adaptability.
+
+Our work also implements structural characterization for describing bijel microstructures. While prior studies have focused heavily on global 
+measures such as domain size or volume fraction, our use of bond orientational order, curvature metrics, and channel topology creates a more 
+nuanced toolkit for evaluating local and global bijel structure. This multiscale perspective provides better predictive capacity for 
+tailoring materials with application-specific structural features, such as tortuosity for mass transport or local ordering for mechanical 
+performance.
+
+The broader impacts of this work span several disciplines. In materials science, our findings inform the design of smart scaffolds and 
+porous networks with tunable permeability or rheology. For instance, magnetic field-tunable tortuosity or anisotropy could 
+be leveraged in filtration membranes that dynamically adjust flow pathways or in tissue scaffolds where curvature-sensitive cell adhesion 
+is critical. In energy systems, the ability to control interfacial curvature and connectivity may influence electrochemical transport and 
+reaction kinetics in battery electrodes or catalytic substrates.
+
+The rheological tunability demonstrated here has direct implications for soft robotics, adaptive damping materials, and controlled release 
+systems. The distinction between oblate and prolate behavior under shear and field stresses provides a foundation for selecting particle 
+geometries based on the desired flow performance of the end-use material. Furthermore, the discovery that certain configurations can resist 
+flow better than others may lead to new materials with programmable viscoelasticity—materials that stiffen or soften in response to field inputs.
 
@@
 and Data-intensive Research at the University of Delaware and in the Delaware Region, Rudolf Eigenmann, Benjamin E. 
-Bagozzi, Arthi Jayaraman, William Totten, and Cathy H. Wu, University of Delaware, 2021, URL: https://udspace.udel.edu/handle/19716/29071
+Bagozzi, Arthi Jayaraman, William Totten, and Cathy H. Wu, University of Delaware, 2021

### 2025-04-07 chapters/introduction_new.tex
Changes 1. Modified conclusion section in final remarks 2. Changes image sized in structural response of bijels 3. modified abstract and introduction to include structural analysis results

@@
 The remainder of this dissertation is organized as follows.
-Chapter 32 details the physics being modeled and the simulation methods used to model these physics, including the Lattice Boltzmann approach
-and magnetic dipole modeling.
-Chapter 3 investigates the effects of magnetic fields applied during bijel formation, analyzing their influence on domain structure and particle orientation.
-Chapter 4 explores
+Chapter 2 details the physics being modeled and the simulation methods used to model these physics, including the Lattice Boltzmann approach
+and magnetic dipole modeling. Chapter 3 investigates the effects of magnetic fields applied during bijel formation, analyzing their influence on domain structure and particle orientation. 
+Chapter 4 investigates the microstructure of bijels stabilized by ellipsoidal particles under magnetic fields in more detail, providing further detail on the influence of the magnetic field on
+the coarsening dynamics of the bijel.
+Chapter 5 explores 
 post-formation responsiveness, specifically examining particle unjamming and reordering phenomena.
-Chapter 5 assesses the rheological implications of these structural changes, with particular attention to
+Chapter 6 assesses the rheological implications of these structural changes, with particular attention to
 yield stress and shear-thinning behavior.
-Finally, Chapter 6 summarizes the key findings, discusses their implications for the design of tunable porous materials, and outlines potential directions for future
+Finally, Chapter 7 summarizes the key findings, discusses their implications for the design of tunable porous materials, and outlines potential directions for future
 research.

### 2025-04-07 chapters/paper2.tex
Changes 1. Modified conclusion section in final remarks 2. Changes image sized in structural response of bijels 3. modified abstract and introduction to include structural analysis results

@@
 \centering 
-\includegraphics[scale=0.4]{../figures/results/paper2/microstructure_viz-field_on.png} 
+\includegraphics[scale=0.6]{../figures/results/paper2/microstructure_viz-field_on.png} 
 \caption{Visualizations of bijels stabilized by prolate particles simulated under no fields at $t = 0$ (left columns) and $t = 10^5$ (right columns). The top 
@@
 \centering 
-\includegraphics[scale=0.5]{../figures/results/paper2/domain_size-field_on.png} 
+\includegraphics[scale=0.6]{../figures/results/paper2/domain_size-field_on.png} 
 \caption{Plots of the time evolution of the normalized domain size \(L/R\) (markers) and nematic order parameter 
@@
 \centering 
-\includegraphics[scale=0.2]{../figures/results/paper2/particle_viz-field_on.png} 
+\includegraphics[scale=0.5]{../figures/results/paper2/particle_viz-field_on.png} 
 \caption{Visualizations of bijels stabilized by prolate ellipsoidal particles at the initial and final timesteps, 
@@
     \centering 
-    \includegraphics[scale=0.5]{../figures/results/paper2/psi-field_on.png} 
+    \includegraphics[scale=0.6]{../figures/results/paper2/psi-field_on.png} 
     \caption{Plots of the evolution of the average interface angle \(\langle \psi \rangle\) over time for bijels stabilized 
@@
     \centering 
-    \includegraphics[scale=0.5]{../figures/results/paper2/Q6-field_on.png} 
+    \includegraphics[scale=0.6]{../figures/results/paper2/Q6-field_on.png} 
     \caption{Plots of the time evolution of the six-fold Steinhardt bond order parameter \(\langle Q_6 \rangle\) for bijels 
@@
              significantly between particle morphologies with \(\langle Q_6 \rangle\) decreasing over time for oblate particles and increasing for prolate particles.} 
-    \label{fig:interface_angle-field_on} 
+    \label{fig:Q6-field_on} 
 \end{figure}
 
-From Figure \ref{fig:interface_angle-field_on} the time evolution of \(\langle Q_6 \rangle\) can be qualitatively divided into three regimes;
+From Figure \ref{fig:Q6-field_on} the time evolution of \(\langle Q_6 \rangle\) can be qualitatively divided into three regimes;
 an initial transition period, a plateau, and a final reordering or jamming phase.
@@
     \centering 
-    \includegraphics[scale=0.5]{../figures/results/paper2/domain_size_aniso-field_on.png} 
+    \includegraphics[scale=0.6]{../figures/results/paper2/domain_size_aniso-field_on.png} 
     \caption{Plotting the anisotropic domain size and tortuosities against the applied magnetic field strength on the left and right respectively for bijels 
@@
 
-The hysteresis curve presented earlier in Figure~\ref{fig:hysteresis_curve} revealed that microstructural changes—quantified by domain size—diminish 
+The hysteresis curve presented earlier in Figure~\ref{fig:hysteresis_curve} revealed that microstructural changes diminish 
 with each successive increase in magnetic field strength. This saturation behavior suggests a direct link between the extent of domain coarsening 
@@
 \centering 
-\includegraphics[scale=0.4]{../figures/results/paper2/microstructure_viz-field_up.png} 
+\includegraphics[scale=0.6]{../figures/results/paper2/microstructure_viz-field_up.png} 
 \caption{Visualizations of bijels stabilized by prolate ellipsoidal particles at the initial (left column) and final (right column)
@@
 \centering 
-\includegraphics[scale=0.5]{../figures/results/paper2/domain_size-field_up.png} 
+\includegraphics[scale=0.6]{../figures/results/paper2/domain_size-field_up.png} 
 \caption{Plot of the spherically averaged domain size normalized with $Rp(L/R)$ of the particle in markers and the nematic order parameter in lines. 
@@
 \centering 
-\includegraphics[scale = 0.5]{../figures/results/paper2/domain_size_aniso-field_up.png} 
+\includegraphics[scale = 0.6]{../figures/results/paper2/domain_size_aniso-field_up.png} 
 \caption{Plotting the anisotropic domain sizes and tortuosity at the final timestep on the left and right respectively for bijels stabilized with 
@@
 \centering 
-\includegraphics[scale=0.2]{../figures/results/paper2/particle_viz-field_up.png} 
+\includegraphics[scale=0.4]{../figures/results/paper2/particle_viz-field_up.png} 
 \caption{Snapshots of the structural evolution of the particle monolayer in bijels stabilized by prolate ellipsoids 
@@
     \centering 
-    \includegraphics[scale=0.4]{../figures/results/paper2/psi-field_up.png} 
+    \includegraphics[scale=0.6]{../figures/results/paper2/psi-field_up.png} 
     \caption{Plots of the evolution of the average interface angle \(\langle \psi \rangle\) for bijels stabilized 
@@
     \centering 
-    \includegraphics[scale=0.4]{../figures/results/paper2/Q6-field_up.png} 
+    \includegraphics[scale=0.6]{../figures/results/paper2/Q6-field_up.png} 
     \caption{Plots of the evolution of the average interface angle \(\langle Q6 \rangle\) for bijels stabilized 
@@
 \centering 
-\includegraphics[scale=0.5]{../figures/results/paper2/domain_size-field_down.png} 
+\includegraphics[scale=0.6]{../figures/results/paper2/domain_size-field_down.png} 
 \caption{Plot of the spherically averaged domain size normalized with $R_p$ of the particle and the nematic order parameter of each bijel over time. 
@@
 \centering 
-\includegraphics[scale = 0.5]{../figures/results/paper2/domain_size_aniso-field_down.png} 
+\includegraphics[scale = 0.6]{../figures/results/paper2/domain_size_aniso-field_down.png} 
 \caption{Plots of the anisotropic structural response of bijels after the removal of 
@@
 \centering 
-\includegraphics[scale=0.4]{../figures/results/paper2/interface_angle-nint-field_down.png} 
+\includegraphics[scale=0.6]{../figures/results/paper2/psi-field_down.png} 
 \caption{Plots of the average interfacial angle $\langle \psi \rangle$  plotted against time for bijels stabilized by oblate and prolate particles
@@
 
-In this chapter, we investigated the microstructural response of bijels stabilized by anisotropic magnetic ellipsoids under varying magnetic field protocols. 
-By systematically analyzing the evolution of domain size, anisotropy, and particle-level order in response to increasing and decreasing magnetic fields, 
-we uncovered key mechanisms that govern structural adaptability and kinetic stability in these systems.
+In this work, we investigated how magnetic fields influence the structure and dynamics of bijels stabilized by magnetically responsive ellipsoidal particles. Motivated 
+by the relevance of bijels in applications such as catalysis, membrane filtration, and drug delivery, we explored how external stimuli can enable in-situ control over 
+microstructure in these systems. Using hybrid Lattice Boltzmann-Molecular Dynamics simulations, we characterized the structural response of formed bijels by investigating
+the effect of applying a magnetic field and the initial microstructure on the structural response characterized. We first demonstrated that bijels subjected to increasing 
+magnetic field strength exhibit hysteresis in its structural response, where the domain size increases with field application but does not revert upon field removal.
 
-We first demonstrated that bijels subjected to increasing magnetic field strength exhibit hysteresis in its structural response, wherein the domain size increases 
-with field application but does not revert upon field removal. This behavior was attributed to particle reorientation at the interface, which induces local 
-unjamming and subsequent domain coarsening. Through visualization and quantitative analysis, we showed that reorientation causes particles to tilt out of the 
-interface, reducing the stabilized interfacial area and driving fluid domain coalescence. Importantly, this microstructure change is constrained by the degree 
-of initial particle disorder with systems containing pre-aligned particles exhibiting diminished structural response, indicating that reorientation, not field strength 
-alone is the primary driver of field-induced structural response.
+When investigating the effect of the application of magnetic fields, our results revealed that applying magnetic fields post-formation induces domain coarsening up to 5\%, with 
+field-induced anisotropy dependent on particle shape. Oblate particles exhibited growth primarily in the perpendicular direction by up to 60\%, while prolate particles showed coarsening 
+along the field direction up to 40\%, 
+both accompanied by a decrease in tortuosity. These changes arise from particle reorientation to the field, followed by local unjamming and interfacial rearrangement before 
+re-jamming occurs, as characterized using the average interface angle of the particles and the Steinhardt bond orientational order parameter.
 
-Two distinct categories of structural response emerged: one in which disordered particle monolayers undergo magnetic reordering that enables large-scale domain 
-coarsening, and a second in which initially ordered systems reorient locally but remain globally jammed, leading to minimal structural adaptation. This transition 
-was further reinforced by the observed saturation in domain growth as a function of particle alignment, highlighting a limit to how much structural change can be 
-achieved post-jamming.
+Importantly, the extent of microstructural change scales with the difference in magnetic field strength before and after application. We found that particle alignment 
+characterized via $\langle \psi \rangle$ and $\langle Q_6 \rangle$ governs domain evolution. Disordered particle layers exhibited strong field responses, while highly ordered 
+templates showed minimal change, highlighting the importance of reordering on the structural response observed. In contrast, removing the magnetic field had little effect 
+on bijel structure. Domain size and anisotropy remained largely unchanged, regardless of initial particle order. While minor relaxation in particle alignment was observed, 
+capillary forces alone were insufficient to drive significant structural reorganization.
 
-Upon magnetic field removal, we found that the bijel microstructure remains largely unchanged, consistent with the kinetic arrest characteristic of these systems. 
-While the particle monolayer exhibited gradual relaxation—evident through changes in interface angle—these dynamics were insufficient to trigger significant domain 
-restructuring. Directional domain size and tortuosity metrics further confirmed that coarsening post field removal was isotropic and minimal, regardless of initial 
-ordering.
+Together, these results identify modes of structural response that depend upon the initial ordering of particles at the interface. The first mechanism identified occurs with
+disordered particle monolayers which upon application of a magnetic field, unjam facilitating domain coarsening before rejamming once the interface area matches the 
+particle cross sectional area. The second mechanism occurs due to particle reorientation to the applied field when particles are nematically ordered but not ordered in the direction
+of the magnetic field.
 
-Collectively, these results elucidate the role of particle-level interactions in dictating the field-responsive behavior of bijels. They reveal that while 
-magnetic fields offer a route to tailor microstructure on demand, the efficacy of this control hinges on the degree of initial disorder and the system’s 
-jamming history. This mechanistic understanding provides design principles for harnessing bijel responsiveness in practical applications—such as tunable 
-porous media, controlled release scaffolds, or adaptive separation systems—where reversibility, anisotropy, and stability must be precisely managed.
-
-% Owing to the applicability of bijels in the catalyst support, filtration membrane and drug release spaces, we were interested in identifying how bijels stabilized 
-% by magnetically responsive ellipsoidal particles could be used to create active soft matter. In this work, we have studied the effect of the application, increase 
-% or removal of magnetic fields on the structural response of bijels stabilized by magnetically responsive ellipsoids using hybrid Lattice Boltzmann-Molecular Dynamics 
-% simulations. We first characterized the hysteresis curve of the bijel, identifying that the process history dependence of the bijel microstructure. To identify why 
-% We observed the path dependence and the microstructure change observed when applying magnetic fields after synthesis, we considered three starting setups; The first 
-% applying a field of varying strength to bijel templates that were simulated with no magnetic field applied. The second involved increasing the applied field 
-% strength onto bijel templates that were simulated with increasing field strengths. The final setup involves removing a field from bijel templates that were simulated 
-% with various field strengths.
-
-% We found that application of magnetic fields onto bijels stabilized by magnetically responsive ellipsoidal particles results in an average microstructure change up to 
-% $5\%$ when investigating changes in the average microstructure. We also identified that the structures become anisotropic upon application of the magnetic field for 
-% oblate and prolate particles. The anisotropy is particle dependent with bijels stabilized by oblate particles seeing an increase in $L_{\perp}$ of up to $60\%$ and for 
-% prolate particles an increase in $L_{\parallel}$ of up to $40\%$ with a corresponding decrease in the tortuosity in that axis. This is caused by the reorientation of the 
-% particles to the magnetic field, followed by domain coarsening as the interfacial coverage of the particles decrease, before jamming in place again. We characterize that 
-% while particle reorientation to the applied field initiates microstructural response, local rearrangement of the particle monolayer is the controlling mechanism of 
-% domain size evolution as characterized by identifying the dominant timescales 
-% of response for both particle morphologies. However, their time evolution is different with bijels stabilized by prolate particles undergoing a local crystallization when 
-% the average six fold Steinhardt order parameter or $\langle Q_6 \rangle \geq 0.38$. For bijels stabilized by oblate particles, a global minimum of the $\langle Q_6 \rangle$ 
-% characterizes the dynamics of the system.
-
-% When increasing the applied field strength, we observe that the difference between the final and initial magnetic fields is correlated to the domain size change observed. 
-% We observe that the anisotropic domain size changes are also dependent upon this difference, with the largest difference being observed when characterizing a bijel template 
-% simulated under no field before having a field strength of $\bar{B} = 1$ applied to it. When looking at the particle monolayer, we characterize three behaviors seen from the 
-% average interfacial angle $\langle \psi \rangle$ and $\langle Q_6 \rangle$. These behaviors are further differentiated for each particle morphology. For oblate particles, 
-% the first behavior is characterized as a reorientation of the particle on the interface seen as an increase in $\langle \psi \rangle$ over time with a corresponding decrease 
-% in $\langle Q_6 \rangle$ as the particles do not close pack anymore. For prolate particles, we see a slight reduction in $\langle \psi \rangle$ and greater ordering of the 
-% particles from $\langle Q_6 \rangle$. The second behavior originates from small reorientations of the particles at the monolayer which do not greatly affect the interfacial 
-% angle but cause a loss or gain of particle order on the interface. The final behavior is characterized as long timescale domain coarsening as there is no change between the 
-% applied magnetic field and the magnetic field used to simulate the template.
-
-% Finally, when decreasing the magnetic field strength, we observe little difference between bijel templates made with any field strength and no field. From the average domain 
-% size, we see that the bijels coarsen at approximately the same rate. Upon further investigation of the microstructure anisotropy, we identify that the anisotropic structure 
-% does not change as well, suggesting coarsening effects are independent of the effect of the local differences at the particle monolayer. After characterizing 
-% $\langle \psi \rangle$ and $\langle Q_6 \rangle$, we see differences at the initial state which, while changing the initiation point of the dynamics, does not play a large
-%  role otherwise. Thus any domain size change observed when removing a field is due to interfacial capillary interactions.
-
-% It has been shown how the domain size and tortuosity can be used to adjust the flow rate, separations efficiency or reaction rate in applications such as cross-flow reactors, 
-% drug delivery and liquid-liquid extraction. These results show that the properties of bijels can be tuned in-situ for these applications although it appears that it can only 
-% be done once. With the results presented here, we have considered only one set of parameters that control the dynamics. Parameters not changed such as the fluid density, 
-% viscosity, surface tension and volume fraction of particles may impact the mechanisms and rate of domain size control. We also do not consider magnetic 
-% fields applied in different directions which even in this simple setup may be able to modify the microstructure considerably, or gradient magnetic fields which may allow 
-% more effective unjamming and re-jamming dynamics for further microstructure modification than what has been shown here.
-
-% Effects such as the steric hindrance between particles may lessen as particle size reduces as particles are more easily able to conform to the curvature of the interface. 
-% The impact this may have on the results seen with the micron-sized particles used here is unknown. In many of the applications listed above, it is also unknown how changes 
-% in the spacing between particles affect underlying reactivity, selectivity or diffusion rates which have implications past the domain size and tortuosity changes characterized 
-% in the literature. Furthermore, it is unknown how additional particle interactions such as chemical cross-linking or charge affect the results seen here. Both strategies are 
-% used in bijels to reinforce them against shear to facilitate higher shear rates, useful in cross-flow reactors and separation membranes. In conclusion, our simulations provide 
-% qualitative trends into the expected microstructure change and their underlying mechanisms and timescales when applying or removing a field from a bijel stabilized by 
-% anisotropic particles by modifying their orientation and packing.
+While our simulations offer valuable insights into the tunability of bijels, they were limited to a single set of fluid and particle parameters. Future work could explore the 
+effects of particle size, volume fraction, interparticle forces, and field orientation or gradients, all of which may unlock additional control over bijel structure.
+Ultimately, this study establishes a foundation for stimuli-responsive bijels, showing how particle-level interactions and monolayer dynamics translate into controllable, 
+application-relevant changes in material microstructure.

### 2025-04-07 chapters/paper1_5.tex
fixed all references in results section

@@
 
-Figure~\ref{fig:curvature-vs-B_ss} shows the dependence of the area-normalized mean and Gaussian curvature,\(\langle H \Sigma^{-1} \rangle\) and \(\langle K \Sigma^{-2} \rangle\) respectively, on the 
+Figure~\ref{fig:curvature_field} shows the dependence of the area-normalized mean and Gaussian curvature,\(\langle H \Sigma^{-1} \rangle\) and \(\langle K \Sigma^{-2} \rangle\) respectively, on the 
 applied magnetic field strength.

### 2025-04-07 chapters/paper1_new.tex
fixed all references in results section

@@
 such as porous polymers, ceramics, synthetic nanoparticles, and engineered tissue scaffolds 
-\cite{zhang_emulsion_2019, stubenrauch_emulsion_2018, jones_high-temperature_2009, binks_macroporous_2002, 
-abbadian_chaleshtari_nanoemulsion_2022, aldemir_dikici_basic_2020}. The technique of emulsion templating 
+\cite{zhang_emulsion_2019, stubenrauch_emulsion_2018, jones_high-temperature_2009, binks_macroporous_2002, aldemir_dikici_basic_2020}. 
+The technique of emulsion templating 
 provides a flexible and efficient approach to controlling key structural features of the final
@@
 alternatives to traditional surfactant-based emulsions due to their ability to form stable interfaces without 
-relying on potentially harmful chemicals \cite{ramsden_separation_1903, zheng_pickering_2022, menner_particle-stabilized_2007}.
+relying on potentially harmful chemicals \cite{ramsden_separation_1904, zheng_pickering_2022, menner_particle-stabilized_2007}.
 
@@
 of these innovations, bijels have gained widespread interest as structural templates for functional materials, including 
-filtration membranes, electrochemical electrodes, and biocompatible scaffolds \cite{yabuno_preparation_2020, pang_highly_2020, 
-witt_microstructural_2016, thorson_composite_2018}.
+filtration membranes, electrochemical electrodes, and biocompatible scaffolds 
+\cite{yabuno_preparation_2020, pang_highly_2020, witt_microstructural_2016, thorson_composite_2018}.
 
@@
 \cite{dassanayake_structure_2000, leunissen_directing_2009}. This is especially pronounced in systems containing anisotropic magnetic 
-particles, where external fields can trigger orientation transitions and alter capillary interactions \cite{morgan_understanding_2012, 
-davies_interface_2014, davies_dipolar_2015}. However, not all particle geometries respond equally. Simulations by Kim et al. revealed 
+particles, where external fields can trigger orientation transitions and alter capillary interactions 
+\cite{morgan_understanding_2013, davies_interface_2014, davies_dipolar_2015}. However, not all particle geometries respond equally. 
+Simulations by Kim et al. revealed 
 that magnetic fields exert minimal influence on the microstructure of bijels stabilized by spherical particles \cite{kim_bijels_2010}. 
@@
 the local interface normal. We generated a mesh of the interface using the marching cubes algorithm and, for each particle, identified the nearest mesh vertex 
-(excluding those beyond the length of the particle’s long axis). We then calculated the angle \(\psi\) between the particle orientation vector 
+(excluding those beyond the length of the particle's long axis). We then calculated the angle \(\psi\) between the particle orientation vector 
 \(\hat{\vec{o}}_i\) and the local surface normal. The time evolution of the average angle \(\psi\) is shown in Figure~\ref{fig:psi_time}.

### 2025-04-08 chapters/LBM_technique.tex
Changes 1. Updatd methods section 2. Changed scale of some plots 3. Updated references with new ones

@@
 
-Bijels require a multi-scale model to correctly simulate all the physical phenomena occurring at every scale. Within a bijel, fluid flow,
-phase separation, particle-fluid and interparticle interactions are present. The lengthscales present in a bijel imply a model must be able
-to resolve nanometer to micrometer resolutions and must be able to capture the hydrodynamics, non-ideal mixing and interparticle interactions present
-in the system. A review of the physics in the system will be provided.
+Bijels require a multiscale modeling approach to accurately capture the rich array of physical phenomena 
+occurring across multiple length and time scales. Within a bijel, one must consider fluid flow, phase separation, particle-fluid coupling, and interparticle 
+interactions. The characteristic length scales span from nanometers to micrometers, demanding a model capable of resolving fine structural details while also 
+capturing mesoscale dynamics. In the following sections, a comprehensive review of the relevant physical processes is provided, laying the foundation for the 
+numerical methods used in this work.
 
@@
 
-Mass conservation is established using simple differential equation of a control volume that characterizes the mass flow through the volume. Assuming no
-addition or subtraction of mass, the differential equation is the material derivative of the density, defined as
+Mass conservation is derived by applying the conservation principle to a differential control volume, which characterizes the mass flux through its boundaries.
+Assuming no sources or sinks of mass, the conservation equation takes the form of the continuity equation:
 
@@
 
-Where $\rho$ is the fluid density and $\vec{u}$ is the fluid velocity vector. The fluid momentum can be derived from the mass conservation equation
-by calculating the material derivative of the momentum of the system. Changes in momentum from addition or subtraction of momentum cannot be ignored,
-with changes arising from pressure gradients, viscous forces and body force terms. If mass is conserved, the momentum equation is defined as
+where $\rho$ is the fluid density and $\vec{u}$ is the velocity vector field.
+Momentum conservation can be obtained by applying Newton's second law to the fluid element. This yields the momentum balance equation, where changes in momentum arise due to pressure gradients, 
+viscous stresses, and body forces. The general form of the momentum equation is:
 
 \begin{equation}
-    \rho (\frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u}) = -\nabla p + \nabla \cdot \mathbf{\tau} + \mathbf{f}
+    \rho \left(\frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u} \right) = -\nabla p + \nabla \cdot \boldsymbol{\tau} + \vec{f}
 \end{equation}
 
-Where $p$ is the pressure applied to the control volume, $\mathbf{\tau}$ is a general stress tensor and $\mathbf{f}$ is the body force 
-applied on the box such as gravitational forces. $\mathbf{\tau}$ can be defined by assuming the fluid is isotropic, the shear stress depends
-linearly on the dynamic viscosity and the strain rate and net forces are zero at equilibrium.
+where $p$ is the pressure field, $\boldsymbol{\tau}$ is the viscous stress tensor, and $\vec{f}$ represents body forces such as gravity or magnetic interactions.
+
+For a Newtonian, isotropic fluid, the viscous stress tensor is defined as:
 
 \begin{equation}
-    \mathbf{\tau} = p\mathbf{I} + \eta(\nabla \mathbf{v} + (\nabla \mathbf{v})^T) - \frac{2}{3}\eta(\nabla \cdot \mathbf{v})\mathbf{I}
+    \boldsymbol{\tau} = p\mathbf{I} + \eta\left( \nabla \vec{u} + (\nabla \vec{u})^T \right) - \frac{2}{3}\eta(\nabla \cdot \vec{u})\mathbf{I}
 \end{equation}
 
-Where $p = (\lambda + \frac{2}{3}\eta)\nabla \cdot \mathbf{v}$ is defined from the bulk viscosity $\lambda$. After substitution into the momentum equation, the compressible 
-Navier Stokes equation is obtained, defined as
+where $\eta$ is the dynamic viscosity. The pressure term can be related to the bulk viscosity $\lambda$ as
 
 \begin{equation}
-    \rho (\frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u}) = -\nabla p + \eta \Delta \mathbf{v} + \frac{1}{3}\eta \nabla(\nabla \cdot \mathbf{v}) + \mathbf{f}
+    p = \left( \lambda + \frac{2}{3}\eta \right) \nabla \cdot \vec{u}
 \end{equation}
 
-If the fluid being modelled is assumed to be incompressible meaning that the density stays constant and the bulk viscosity is 0, $\nabla \cdot \mathbf{v} = 0$. This simplifies
-the Navier Stokes equation to
+Substituting this stress tensor into the momentum equation yields the compressible Navier-Stokes equation,
 
 \begin{equation}
-    \rho (\frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u}) = -\nabla p + \eta \Delta \mathbf{v} + \mathbf{f}
+    \rho \left(\frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u} \right) = -\nabla p + \eta \Delta \vec{u} + \frac{1}{3}\eta \nabla(\nabla \cdot \vec{u}) + \vec{f}
 \end{equation}
 
-The Navier Stokes equation can be recast into a dimensionless form by rescaling length, time and density into dimensionless forms. These parameters are rescaled as 
-$\bar{l} = \frac{l}{l_0}$, $\bar{t} = \frac{t}{t_0}$ and $\bar{\rho} = \frac{\rho}{\rho_0}$ with barred quantities indicating dimensionless properties. After substituting
-these parameters into the Naver Stokes equation this is obtained
+For an incompressible fluid—meaning constant density and negligible bulk viscosity—the condition $\nabla \cdot \vec{u} = 0$ holds. Under this assumption, the Navier-Stokes equation simplifies to,
 
 \begin{equation}
-    \frac{\partial \bar{\vec{u}}}{\partial \bar{t}} + (\bar{\vec{u}} \cdot\nabla)\bar{\vec{u}} = -\nabla \bar{p} + \frac{1}{Re} \Delta \mathbf{\bar{v}} + \bar{\mathbf{f}}
+    \rho \left(\frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u} \right) = -\nabla p + \eta \Delta \vec{u} + \vec{f}
 \end{equation}
 
-$Re = \frac{\rho u l}{\eta}$ which defines the ratio between inertial and viscous forces.
+To facilitate numerical simulation and analysis, it is often useful to express the Navier-Stokes equation in non-dimensional form. Introducing characteristic scales for length 
+$l_0$, time $t_0$, and density $\rho_0$, dimensionless variables are defined as
+
+\begin{equation}
+    \bar{l} = \frac{l}{l_0}, \quad \bar{t} = \frac{t}{t_0}, \quad \bar{\rho} = \frac{\rho}{\rho_0}
+\end{equation}
+
+Substituting these into the incompressible Navier-Stokes equation leads to the dimensionless form:
+
+\begin{equation}
+    \frac{\partial \bar{\vec{u}}}{\partial \bar{t}} + (\bar{\vec{u}} \cdot\nabla)\bar{\vec{u}} = -\nabla \bar{p} + \frac{1}{Re} \Delta \bar{\vec{u}} + \bar{\vec{f}}    
+\end{equation}
+
+where the Reynolds number is defined as $Re = \frac{\rho_0 u_0 l_0}{\eta}$ which characterizes the ratio of inertial to viscous forces in the system.
 
 \section{Phase separation}
-
-Another physical phenomenon being described is non-ideal mixing. The free energy of mixing
-is defined as $\Delta G_m = \Delta H_m - T \Delta S_m$. In an ideal solution, $\Delta H_m = 0$. An expression for $\Delta S_m$ for a binary mixture is obtained from statistical mechanical 
-approximations of the configurations that binary mixtures can take, resulting in
+Another physical phenomenon relevant to bijel formation is non-ideal mixing. The free energy of mixing for a binary fluid is given by the thermodynamic relation
 
 \begin{equation}
-    S_m = -k N_\phi k_B T((1 - \phi)\ln{1 - \phi} + \phi ln(\phi)) 
+    \Delta G_m = \Delta H_m - T \Delta S_m
 \end{equation}
 
-In a regular solution, $\Delta H_m \neq 0$. The free energy of mixing is defined as the sum of the ideal and excess contribution, $\Delta G_m = \Delta G_e + \Delta G_i$.
-$\Delta G_i = -TS_m$. $\Delta G_e = \Delta H_e + T \Delta S_e$. The excess entropy of mixing is 0, and the excess enthalpy of mixing is defined
+In an ideal solution, the enthalpy of mixing is zero, i.e., $\Delta H_m = 0$, and the entropy of mixing $\Delta S_m$ can be derived using statistical mechanical approximations of the 
+configurational states of the binary mixture. For a system with volume fractions $\phi$ and $1 - \phi$, the entropy of mixing becomes
 
 \begin{equation}
-    \begin{split}
-    \frac{\partial\phi}{\partial t} = \nabla \cdot \left( \Gamma  \nabla\mu_\phi \right)
-    \end{split}
+    \Delta S_m = -N_a k_B \left[(1 - \phi)\ln(1 - \phi) + \phi \ln(\phi)\right]
 \end{equation}
 
+In contrast, a regular solution includes non-zero enthalpic interactions. The total free energy of mixing is split into ideal and excess components,
+
+\begin{equation}
+    \Delta G_m = \Delta G_i + \Delta G_e
+\end{equation}
+
+The ideal contribution arises from the entropy of mixing: $\Delta G_i = -T \Delta S_m$. For regular solutions, the excess entropy is assumed to be zero, and the excess enthalpy is given by,
+
+\begin{equation}
+    \Delta H_m = \chi (1 - \phi)\phi
+\end{equation}
+
+where $\chi$ is the interaction parameter quantifying the energetic favorability of mixing. This term originates from mean-field approximations assuming equal-sized molecular species. 
+Combining both contributions, the free energy of mixing becomes:
+
+\begin{equation}
+    \Delta G_m = \chi (1 - \phi)\phi + N_a k_B T \left[(1 - \phi)\ln(1 - \phi) + \phi \ln(\phi)\right]
+\end{equation}
+
+This bulk free energy characterizes the thermodynamic driving forces for phase separation. Alternative forms, such as the Landau-Ginzburg or Flory-Huggins models, may also be used depending on system 
+specifics. In real systems, the interface between two partially miscible fluids is not sharp; rather, the composition transitions smoothly across a finite interface width. To account for this, a 
+gradient energy penalty is added to the free energy functional, penalizing sharp spatial variations in composition. The total free energy functional is written as
+
+\begin{equation}
+    F[\phi] = \int \left( f(\phi) + \frac{\kappa}{2}|\nabla \phi|^2 \right) \, dV
+\end{equation}
+
+where $\kappa$ is the gradient energy coefficient controlling the interface width. Larger \(\kappa\) values correspond to wider interfaces.
+The chemical potential is then defined as the variational derivative of the free energy functional,
+
+\begin{equation}
+    \mu = \frac{\delta F}{\delta \phi} = \frac{df}{d\phi} - \kappa \nabla^2 \phi
+\end{equation}
+
+This chemical potential enters the mass flux expression via a Fickian transport law,
+
+\begin{equation}
+    \vec{J} = -M \nabla \mu
+\end{equation}
+
+where $M$ is the mobility and could potentially be a function of $\phi$. Assuming no advection and applying mass conservation for the order parameter, we obtain,
+
+\begin{equation}
+    \frac{\partial \phi}{\partial t} = -\nabla \cdot \vec{J}
+\end{equation}
+
+Substituting in the expression for \(\vec{J}\) leads to the Cahn-Hilliard equation,
+
+\begin{equation}
+    \frac{\partial \phi}{\partial t} = \nabla \cdot \left( M \nabla \mu \right)
+\end{equation}
+
+This equation describes the diffusive evolution of the conserved field $\phi$ during phase separation. It captures the system's tendency to minimize its total free energy 
+by redistributing the order parameter according to gradients in chemical potential. The Cahn-Hilliard framework naturally incorporates interfacial tension and allows for smooth, 
+continuous transitions between phases, making it highly suitable for modeling non-ideal mixing in systems such as bijels.
+
 \section{Particle dynamics}
+
+In computational studies of particle-laden fluids, particles can be modeled either as point particles or as explicitly resolved rigid bodies. The choice between 
+these approaches depends on the physical fidelity required, the computational cost, and the scales at which particle-fluid and particle-interface interactions must be resolved.
+
+Point particle models treat colloids as infinitesimal entities that influence the surrounding fields through source terms or effective force laws. 
+\cite{mehrabadi_direct_2018, prosperetti_point-particle_2007, frohlich_validation_2018}
+In such models, 
+particles do not occupy physical volume and their influence on the fluid is typically introduced via body forces or perturbations to the chemical potential field. This 
+approach is computationally efficient and particularly useful for systems with a large number of particles or when only large-scale collective behavior is of interest. 
+However, point particles cannot capture rotational dynamics, or hydrodynamic effects such as lubrication forces. Additionally, 
+their interaction with phase interfaces is often prescribed rather than emergent, limiting their accuracy in systems like bijels where particles jam at fluid-fluid interfaces 
+and significantly modify the interface topology.
+
+In contrast, explicit particle models represent colloids as finite-size rigid bodies with well-defined shape, volume, and surface boundary conditions. 
+\cite{ladd_numerical_1994, jansen_bijels_2011,gunther_timescales_2014}
+These particles interact 
+with the surrounding fluid through no-slip or slip boundary conditions, and their motion responds dynamically to hydrodynamic, capillary, and interparticle forces. By resolving 
+particle geometry, these models allow for accurate representation of rotational motion, surface wetting and interfacial adsorption.
+\cite{jansen_bijels_2011, gunther_lattice_2013}
+This is important in bijel systems, where particle-induced jamming depend on particle shape, size, and surface wetting.
+
+An intermediate approach between point particles and explicitly resolved rigid bodies is the immersed boundary method (IBM), which represents extended particles as collections of 
+point markers embedded in the fluid. \cite{peskin_immersed_2002, luo_immersed-boundary_2008, spandan_parallel_2017}
+These markers interact with the fluid through momentum exchange that impose motion onto the surrounding fluid, effectively reconstructing 
+the dynamics of a deformable or rigid object without requiring an explicit boundary mesh. \cite{peskin_immersed_2002, luo_immersed-boundary_2008, spandan_parallel_2017} 
+IBM has been widely used in biological and colloidal systems, to model the dynamics of deformable bodies. \cite{peskin_immersed_2002, luo_immersed-boundary_2008, spandan_parallel_2017}
+
+Ultimately, the choice between point and explicit particle models reflects a trade-off between computational efficiency and physical realism. For systems in which interfacial structure, 
+jamming, or near-field hydrodynamics play a central role as in bijel formation, explicit particle modeling is generally preferred.
 
@@
 
-\section{Lattice Boltzmann Method}
+Magnetically responsive particles can generally be classified as paramagnetic or ferromagnetic, depending on the nature and strength of their magnetization in response to external 
+magnetic fields. Paramagnetic particles do not possess a permanent magnetic moment but acquire a reversible magnetization that aligns with the applied field and 
+vanishes once the field is removed. \cite{sinn_magnetically_2011} Their response is typically linear with field strength and does not involve magnetic hysteresis. 
+In contrast, ferromagnetic particles exhibit strong, permanent magnetization due to the alignment of magnetic domains even in the absence of an external field. These particles can 
+exhibit hysteresis and significantly stronger dipole-dipole interactions. \cite{sinn_magnetically_2011}
+As a result, ferromagnetic particles are more likely to form irreversible aggregates or chains, while paramagnetic particles 
+respond more gently and reversibly, making them preferable in systems where tunability and field-off stability are important. The choice between these types depends on the desired 
+degree of responsiveness, reversibility, and control in applications such as field-directed assembly or responsive emulsions.
 
-The Lattice Boltzmann Method (LBM) is an evolution of preceding lattice gas automata techniques, which is a discretization of the Boltzmann equation of motion for 
-molecules. This means that unlike traditional CFD techniques such as FDM, VOF or level set methods, LBM tracks the evolution of a 
+Magnetic particles are often modeled using the magnetic dipole approximation, which treats each particle as possessing a single point dipole moment \(\vec{m}\) located at its center.
+\cite{davies_assembling_2014}
+The dipole-dipole interaction between two particles separated by a vector \(\vec{r}\) is described by the potential:
+
+\begin{equation}
+    U_{\text{d}} = \frac{\mu_0}{4\pi r^3} \left[ \vec{m}_1 \cdot \vec{m}_2 - 3(\vec{m}_1 \cdot \hat{r})(\vec{m}_2 \cdot \hat{r}) \right]
+\end{equation}
+
+This model captures the long-range, anisotropic nature of magnetic interactions and is commonly used due to its simplicity and computational efficiency. It is especially effective when 
+particles are small, well-separated, and uniformly magnetized, such that higher-order multipole contributions can be neglected. However, the dipole model becomes less accurate when particles 
+aggregate closely or experience strong magnetic fields that cause internal magnetization to deviate from a uniform state.
+
+To address these limitations, the demagnetization tensor method offers a more refined model by considering the particle as a uniformly magnetized ellipsoid and calculating the internal magnetic 
+field using an analytical or numerically tabulated demagnetization tensor. \cite{takahashi_ellipsoids_2017} 
+This method accounts for the effect of particle shape on the distribution of internal magnetization and enables the modeling of induced magnetic dipoles that respond to local fields. 
+The demagnetization field \(\vec{H}_d\) inside a particle is given by
+
+\begin{equation}
+    \vec{H}_d = -\mathbf{N} \cdot \vec{M}
+\end{equation}
+
+where \(\mathbf{N}\) is the demagnetization tensor and \(\vec{M}\) is the magnetization vector. \cite{takahashi_ellipsoids_2017} 
+This approach is particularly useful for modeling spheroidal or ellipsoidal particles and is widely used in magnetorheological systems, chain-forming ferrofluids, and dense suspensions where 
+particle-particle interactions are strongly shape-dependent.
+
+At a higher level of fidelity, micromagnetic continuum models resolve the internal magnetization field \(\vec{M}(\vec{r})\) throughout each particle by minimizing the total magnetic energy, which 
+includes exchange, anisotropy, Zeeman, and magnetostatic contributions. \cite{vivas_toward_2020} 
+The governing equations are typically derived from the Landau-Lifshitz-Gilbert (LLG) equation, which evolves \(\vec{M}(\vec{r}, t)\) over time under the influence of effective magnetic fields. 
+These models capture spatially varying domain structures, vortex states, and other complex magnetic configurations, making them essential for accurately simulating particles with nonuniform or dynamic
+magnetization. However, micromagnetic simulations are computationally expensive and require fine discretization within each particle, often using finite element or finite difference methods.
+
+Since bijel formation and stabilization primarily depend on interfacial 
+jamming and long-range interactions between particles at fluid-fluid interfaces, the magnetic dipole approximation is often sufficient to model key behaviors such as chaining, orientation under external
+fields, and capillary-mediated assembly.
+However, if particle shape anisotropy, proximity effects, or induced magnetization in response to local fields are important, incorporating demagnetization tensors
+may offer improved realism.
+
+\section{Numerical modeling}
+
+\subsection{Multiscale modeling algorithms}
+
+A wide range of numerical methods exist for simulating the physics details in previous sections. The choice of method depends on the specific physical processes to be captured such as 
+interface dynamics, hydrodynamic interactions, and thermal fluctuations—as well as computational efficiency and scalability. Below, we outline several commonly used approaches that have been 
+applied in studies of complex fluids and soft matter systems.
+
+The Volume of Fluid (VOF) method is a sharp-interface technique used to track the evolution of fluid-fluid interfaces within a fixed computational grid.
+\cite{gopala_volume_2008, fleckenstein_volume-fluid-based_2015, deising_direct_2018}
+In VOF, a scalar field (the volume fraction) is defined for each grid cell to indicate the presence of each fluid component, with interface reconstruction algorithms used to localize the boundary 
+between phases. 
+The method conserves mass by construction and handles large interface deformations well, making it suitable for high-Reynolds-number flows and surface tension-driven dynamics. However, 
+VOF methods can struggle with accurately capturing interfacial curvature and do not easily accommodate diffuse interfaces or complex topological changes such as pinch-off or coalescence,
+which limits their applicability for simulating phase separation in bijels.
+
+Phase field methods take a diffuse-interface approach, representing fluid composition or phase identity using a continuous order parameter field and are often governed by the Cahn-Hilliard or 
+Allen-Cahn equations. \cite{mendoza_evolution_2006, carmack_tuning_2018, chan_channel_2012}
+These methods naturally capture smooth transitions between phases, allow for accurate calculation of interfacial forces, and can easily handle topological changes in the interface. 
+Phase field methods are thermodynamically consistent, as they are derived from free energy functionals, and are particularly well-suited for modeling systems undergoing spinodal decomposition 
+or wetting transitions. Their main limitations lie in the need for fine resolution near interfaces to maintain numerical accuracy and stability, and in the computational cost of solving 
+higher-order partial differential equations, especially when coupled with full hydrodynamics.
+
+Brownian dynamics is a particle-based method used to simulate the stochastic motion of colloidal particles in a fluid. 
+\cite{huber_brownian_2019, yip_brownian_2005, elsawy_utility_2025}
+It models the over-damped limit of Langevin dynamics by integrating particle 
+trajectories under the influence of deterministic forces (such as interparticle interactions or external fields) and random thermal forces representing collisions with solvent molecules. Hydrodynamic 
+interactions may be included via approximate mobility tensors or neglected altogether, depending on the level of detail required. Brownian dynamics is ideal for studying self-assembly, aggregation, 
+and diffusion of particles in dilute systems, but lacks the ability to capture bulk fluid motion or interface-mediated interactions unless coupled with continuum solvers.
+As such, it is not well-suited
+for simulating the coupled fluid-particle dynamics characteristic of bijel formation on its own.
+
+The Lattice Boltzmann Method (LBM) is a discretization of the Boltzmann equation of motion for molecules. \cite{qian_lattice_1992, succi_lattice_2018, shan_multicomponent_1995, swift_lattice_1996}
+Unlike traditional CFD techniques such as phase field or VOF methods, LBM tracks the evolution of a 
 particle distribution function within grid cells evolved through a discretized Boltzmann equation of motion. Macroscopic variables such as fluid density and 
 velocity are recovered from the particle distributions through appropriate moment integration, and the Navier Stokes equation at the incompressible limit can be 
-obtained through a Chapman-Enskog expansion of the LBM. The LBM has become an attractive tool for meso-scale CFD simulations due to its ease of algorithm 
+obtained through a Chapman-Enskog expansion of the LBM. \cite{qian_lattice_1992} The LBM has become an attractive tool for meso-scale CFD simulations due to its ease of algorithm 
 implementation, highly parallelizable nature and ease of boundary condition implementation, allowing coupling to other physically relevant systems such as 
@@
 The particle distribution function described earlier is advected on a pre-constructed lattice stencil, commonly denoted as DnQm where n and m represent the 
-number of dimensions and directions in the stencil. Common stencils include the D1Q5, D2Q9 and D3Q19 stencil, all of which recover mass and momentum conservation. 
-For energy conservation, a higher order stencil such as D3Q27 is necessary. The D2Q9 and D3Q19 stencils have 8 and 18 populations respectively that include 
-connections to nearest and next nearest neighbour points, in addition to a central rest point. The D3Q19 stencil is shown in Figure \ref{fig:d3q19_lattice}.
+number of dimensions and directions in the stencil. \cite{succi_lattice_2018, schmieschek_lb3d_2017}
+Common stencils include the D1Q5, D2Q9 and D3Q19 stencil, all of which recover mass and momentum conservation. 
+For energy conservation, a higher order stencil such as D3Q27 is necessary. The D2Q9 and D3Q19 stencils have 9 and 19 populations respectively that include 
+connections to nearest and next nearest neighbour points. The D3Q19 stencil is shown in Figure \ref{fig:d3q19_lattice}.
 
@@
 with the chosen stencil. During the collision step, the particle population distribution is relaxed towards an equilibrium with a collision operator, at a 
-specified relaxation rate.
+specified relaxation rate. Importantly, LBM can be extended to handle multiphase and multicomponent fluids, using either color-gradient models, free energy formulations, 
+or pseudopotential approaches to model non-ideal mixing. It also couples well to particle dynamics through momentum exchange schemes, making it a powerful framework for 
+simulating colloidal suspensions, interfacial phenomena, and structurally complex systems like bijels. Its ability to capture both hydrodynamics and mesoscale thermodynamic 
+behavior makes it particularly suited for the multi-scale requirements of stimuli-responsive emulsions.
 
-\section{Hydrodynamics} 
+In summary, the Volume of Fluid method offers robust interface tracking and mass conservation but lacks the ability to naturally capture interfacial curvature and topological changes. 
+Phase field methods provide thermodynamically consistent, diffuse-interface models ideal for phase separation, though they require fine resolution and are computationally intensive. 
+Brownian dynamics excels at modeling particle-level stochastic motion but cannot resolve bulk fluid dynamics or interface evolution on its own. In contrast, the Lattice Boltzmann Method 
+combines the strengths of mesoscopic fluid modeling with efficient handling of complex interfaces and straightforward coupling to particle dynamics. Its balance between computational 
+efficiency, scalability, and physical fidelity across multiple scales makes LBM the most suitable method for simulating the rich interplay of hydrodynamics, phase separation, and particle 
+interactions in stimuli-responsive emulsions such as bijels.
+
+\subsection{Multicomponent models in the Lattice Boltzmann Method}
+
+Four primary techniques exist in the lattice Boltzmann literature for modeling multicomponent or multiphase systems. These are the Shan-Chen (SC) 
+pseudopotential model, the free energy (FE) model, the color gradient (CG) model, and the interface tracking (IT) model.
+These methods differ fundamentally in their formulation and implementation, each offering unique advantages and trade-offs in terms of accuracy, 
+stability, physical realism, and computational cost. Below, each approach is briefly reviewed, followed by a comparative discussion of their 
+suitability for modeling stimuli-responsive emulsions such as bijels.
+
+The SC model introduces fluid-fluid interactions via a local, density-dependent force, enabling spontaneous phase separation and interface 
+formation without requiring explicit interface tracking. 
+\cite{shan_lattice_1993, shan_simulation_1994, shan_multicomponent_1995, jansen_bijels_2011,gunther_timescales_2014}
+Its simplicity and computational efficiency have made it a widely used method. However,
+in this formulation, surface tension is not an independently controllable parameter. An effective mass defined from the density of each component
+in each lattice point is used in the force calculation, meaning that it indirectly determines the surface tension in addition to the interaction
+strength parameter.
+
+The FE model is derived from a square-gradient free energy functional, which modifies the equilibrium distribution to incorporate thermodynamic 
+forces driving phase separation.
+\cite{swift_lattice_1996, kendon_inertial_2001, briant_lattice_2004} Like the SC model, it naturally produces interfaces and captures interfacial tension.
+Unlike the SC model, however,
+the FE model allows for explicit control of surface tension and interface thickness via the bulk free energy parameters. This thermodynamic 
+consistency makes it attractive for modeling systems with diffuse interfaces. The thermodynamics of the system can also be modified through changing the free energy used.
+\cite{swift_lattice_1996, briant_lattice_2004, kendon_inertial_2001}
+A key limitation, however, is its difficulty handling fluids with high density ratios, which can reduce its applicability in more extreme multiphase scenarios.
+
+The CG model assigns color labels to each fluid component and applies a recoloring step to enforce immiscibility and sharpen the interface 
+between fluids. 
+\cite{mora_optimal_2021, latva-kokko_static_2005, huang_study_2014, liu_multiphase_2016}
+This recoloring step is responsible for generating interfacial tension and enables precise control over interfacial properties such 
+as surface tension and width. The model has demonstrated success in soft matter systems where interfacial control is critical. However, implementing 
+the recoloring algorithm introduces additional complexity and requires careful parameter tuning to ensure stability and numerical consistency. \cite{mora_optimal_2021}
+
+The IT model employs level-set or front-tracking techniques to explicitly track the location of fluid interfaces by evolving a separate indicator 
+function alongside the LB solver. \cite{haghani_hassan_abadi_conservative_2018, liang_lattice_2023}
+This method achieves high accuracy in resolving interface position and curvature, making it ideal for problems 
+involving surface tension-driven flows or sharp interfacial features. However, it is computationally intensive and less well-suited for handling 
+topological changes such as coalescence or pinch-off, which are common in phase-separating systems like bijels.
+
+Given these trade-offs, the Shan-Chen pseudopotential model is chosen for this research due to its balance between physical realism and computational 
+efficiency. \cite{jansen_bijels_2011,gunther_timescales_2014, gunther_lattice_2013, xie_direct_2017}
+Its ability to capture phase separation, interface formation, and emergent domain morphology without requiring explicit interface 
+tracking or complex coupling makes it suitable for simulating the large-scale dynamics of bijels. Moreover, its straightforward coupling to 
+colloidal particles facilitates the inclusion of particle-fluid and particle-interface interactions central to the system being studied.
+
+\section{Implementing the multicomponent Lattice Boltzmann Method} 
 \label{section:lbm_hydrodynamics}
@@
 
-\section{Non-ideal mixing}
+\subsection{Non-ideal mixing}
 \label{section:lbm_non_ideal_mixing}
-
-Four primary techniques to model multicomponent or multiphase systems exist in the LBM literature. They are the Shan-Chen (SC) pseudopotential
-model, the free energy (FE) model, the color gradient (CG) model and the interface tracking (IT) model. All techniques are fundamentally different to one
-another in implementation and tradeoff various properties. Each one will be briefly reviewed before a comparing and contrasting their applicability
-to this system.
-
-The SC model introduces fluid interactions via a density-dependent force, enabling spontaneous phase separation 
-and interface formation without explicitly tracking the interface. It is simple to implement and computationally efficient. However the density
-dependence of the fluid interactions implies that the surface tension is controlled by the density of the fluids used and the strength parameter
-controlling interactions.
-
-The FE model derives from the implementation of a modified equilibrium distribution derived from a square gradient free energy functional. Similar to the
-SC model, the FE model enables spontaneous phase separation and interface formation without explicitly tracking the interface. The surface tension and
-interface width are explicitly defined from the bulk free energy, allowing for user defined surface tensions and interface widths. However in its multicomponent
-implementation, it cannot be used to simulate fluids with high density ratios.
-
-The CG model is defined with fluid components with color labels, followed by the application of a recoloring step to sharpen the interface. 
-\cite{liu_multiphase_2016} The recoloring step creates the surface tension present in phase separated multicomponent mixtures. This model
-provides fine control over the surface tension and narrow interface widths. However implementing the recoloring step is computationally complex 
-and requires tuning of the recoloring step to ensure numerical consistency.  
-% technique proposed by Latva-Kokko and Rothman is more commonly used for soft matter flows. \cite{liu_multiphase_2016}
-
-The IT model is defined using a level-set or front-tracking techniques coupled to LBM. This technique explicitly tracks the location of the
-interface by evolving a separate interface indicator. It offers the highest accuracy at capturing the interface. However it is computationally
-expensive and less suited to topological changes like coalescence.
-
-% A quick review of the Shan-Chen (SC) or 
-% pseudopotential model will be provided here from the perspective of a binary mixture. Additionally, the names and descriptions of 
-% other techniques will be described as well. The interparticle potential model or Shan-Chen model that adds a non-local density dependent force 
-% between two species, effectively modelling non-ideal mixing and recovering the Cahn-Hilliard equation. To alleviate the standard Shan-Chen implementations 
-% weaknesses of not being thermodynamically consistent and reducing the existence of spurious velocities, thermodynamically consistent equations of state
-% such as the Van der walls or Carnahan Starling equations of state have been implemented and compared to the Shan-Chen equation of state.
-
-% In addition to the Shan-Chen model, the color gradient model, free energy model and interface tracking technique all 
-% allow for simulations of various types of multiphase and/or multicomponent flows. The color gradient model proposed by Rothman and Keller and 
-% implemented by Gunstensen et al relies upon modelling two particle distributions. These represent a binary fluid mixture with the collision step 
-% able to recover the hydrodynamics and non-ideal mixing dynamics. The free energy model utilizes phase field theory and constructs a free energy 
-% functional to recover interfacial dynamics and effects in a thermodynamically consistent manner. Often, a square gradient free energy is used for 
-% simplicity and ease of implementation. The mean field theory The non-ideal mixing dynamics are 6
-
-Compared to other multicomponent methods, the SC model provides the
 
@@
 
-\section{Suspended particle dynamics}
+\subsection{Suspended particle dynamics}
 \label{section:lbm_colloids}
@@
 
-\subsection{Anisotropic particles}
+\subsubsection{Anisotropic particles}
 \label{section:lbm_colloids_ellipsoids}

### 2025-04-08 chapters/paper1_5.tex
Changes 1. Updatd methods section 2. Changed scale of some plots 3. Updated references with new ones

@@
 \begin{figure}
-\includegraphics[width=\textwidth]{../figures/results/paper1_5/particle_layer.png}%
+\centering
+\includegraphics[scale = 0.4]{../figures/results/paper1_5/particle_layer.png}%
 \caption{Visualizations of the order parameter $\phi$ for bijels stabilized by oblate (left), spherical (middle) and prolate (right) particles 
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{../figures/results/paper1_5/steinhardt_time.png}%
+\centering
+\includegraphics[scale = 0.38]{../figures/results/paper1_5/steinhardt_time.png}%
 \caption{Time dependence of the Steinhardt order parameters $q_2$ and $q_4$ for different particles shapes $\alpha$ and at different magnetic field strengths $\bar{B}$.
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{../figures/results/paper1_5/steinhardt_field.png}%
+\centering
+\includegraphics[scale=0.45]{../figures/results/paper1_5/steinhardt_field.png}%
 \caption{Dependence of the Steinhardt order parameter $q_2$ and $q_4$ on the magnetic field $\bar{B}$. The order parameters were computed for the final 
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{../figures/results/paper1_5/curvature_field.png}%
+    \centering
+\includegraphics[scale=0.5]{../figures/results/paper1_5/curvature_field.png}%
 \caption{Plot of the area averaged mean $\langle H \rangle \Sigma^{-1}$ and Gaussian $\langle K \rangle \Sigma^{-2}$ curvature in the left and right 
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{../figures/results/paper1_5/handles_time.png}%
+    \centering
+\includegraphics[scale=0.45]{../figures/results/paper1_5/handles_time.png}%
 \caption{Time dependence of the number of channels for different particle shapes $\alpha$ and at different magnetic field strength $\bar{B}$. 
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{../figures/results/paper1_5/CSD.png}%
+    \centering
+\includegraphics[scale = 0.4]{../figures/results/paper1_5/CSD.png}%
 \caption{Channel size distribution (CSD) in bijels stabilized by oblate ($\alpha=0.5$), spherical ($\alpha=1.0$), and prolate ($\alpha=2.0$) particles. 
@@
 \centering
-\includegraphics[width=.5\textwidth]{../figures/results/paper1_5/channel_size_field.png}%
+\includegraphics[scale = 0.6]{../figures/results/paper1_5/channel_size_field.png}%
 \caption{Average channel size $L_c$ for different particle shapes $\alpha$ and at different magnetic field strength $\bar{B}$.

### 2025-04-08 chapters/paper1_new.tex
Changes 1. Updatd methods section 2. Changed scale of some plots 3. Updated references with new ones

@@
     \centering
-    \includegraphics[width=\columnwidth]{../figures/results/paper1/microstructure_viz.png}
+    \includegraphics[scale=0.6]{../figures/results/paper1/microstructure_viz.png}
     \caption{Snapshots of emulsion gels stabilized by prolate ellipsoids after $t=5\cdot10^3$ timesteps (left) and after $10^5$ timesteps (right). 
@@
     \centering
-    \includegraphics[width=\columnwidth]{../figures/results/paper1/particle_packing_viz.png}
+    \includegraphics[scale=0.6]{../figures/results/paper1/particle_packing_viz.png}
     \caption{Snapshots illustrating the particle packing at the interface for different particle shapes $\alpha$ with (left)
@@
     \centering
-    \includegraphics[width=\columnwidth]{../figures/results/paper1/S-vs-t.png}
+    \includegraphics[scale=0.6]{../figures/results/paper1/S-vs-t.png}
     \caption{Time-dependence of the nematic order parameter $S$ of oblate ($\alpha=0.5$) and prolate ($\alpha=2$) particles at different field strength $\bar{B}$.
@@
     \begin{figure}
-    \includegraphics[width=\columnwidth]{../figures/results/paper1/interface_nematic.png}
+        \centering
+    \includegraphics[scale=0.6]{../figures/results/paper1/interface_nematic.png}
     \caption{Time-dependence of the interface nematic order for oblate ($\alpha=0.5$) and prolate ($\alpha=2$) particles at different magnetic field strength $\bar{B}$.
@@
     \centering
-    \includegraphics[width=\columnwidth]{../figures/results/paper1/psi-vs-t.png}
+    \includegraphics[scale=0.6]{../figures/results/paper1/psi-vs-t.png}
     \caption{Time-dependence of the average angle $\psi$ between the particle axis and the interface normal for oblate ($\alpha=0.5$) and 
@@
     \centering
-    \includegraphics[width=\textwidth]{../figures/results/paper1/rdf_compare_time.png}
+    \includegraphics[scale=0.4]{../figures/results/paper1/rdf_compare_time.png}
     \caption{Time-evolution of the radial distribution function $g(r)$ of the particles at different magnetic field strength $\bar{B}$. The radial 

### 2025-04-08 chapters/paper2.tex
Changes 1. Updatd methods section 2. Changed scale of some plots 3. Updated references with new ones

@@
 \centering 
-\includegraphics[scale=0.6]{../figures/results/paper2/microstructure_viz-field_on.png} 
+\includegraphics[scale=0.5]{../figures/results/paper2/microstructure_viz-field_on.png} 
 \caption{Visualizations of bijels stabilized by prolate particles simulated under no fields at $t = 0$ (left columns) and $t = 10^5$ (right columns). The top 
@@
 \centering 
-\includegraphics[scale=0.5]{../figures/results/paper2/particle_viz-field_on.png} 
+\includegraphics[scale=0.4]{../figures/results/paper2/particle_viz-field_on.png} 
 \caption{Visualizations of bijels stabilized by prolate ellipsoidal particles at the initial and final timesteps, 
@@
     \includegraphics[scale=0.6]{../figures/results/paper2/domain_size_aniso-field_on.png} 
-    \caption{Plotting the anisotropic domain size and tortuosities against the applied magnetic field strength on the left and right respectively for bijels 
-             stabilized with magnetically responsive oblate and prolate ellipsoids. We see that upon application of the field, bijels stabilized with prolate 
-             particles experience a domains ize increase in the direction parallel to the applied field direction, $L_{\parallel}$, while the domain size 
-             perpendicular to the applied field, $L_{\perp}$ decreases. The opposite is true for bijels stabilized with oblate particles. The tortuosity data 
-             demonstrate that as the domain size increases, the tortuosity decreases and vice versa.} 
+    \caption{Plots of the anisotropic domain size (left) and tortuosity (right) as a function of magnetic field strength for bijels 
+             stabilized with oblate and prolate ellipsoids when raising the applied magnetic field. Prolate-stabilized bijels 
+             exhibit increased domain size parallel to the field ($L_{\parallel}$) and decreased size perpendicular ($L_{\perp}$), 
+             while the opposite trend is observed for oblate-stabilized systems. Tortuosity inversely correlates with domain size in 
+             both cases.} 
     \label{fig:domain_size_aniso-field_on} 
@@
 \centering 
-\includegraphics[scale=0.4]{../figures/results/paper2/particle_viz-field_up.png} 
+\includegraphics[scale=0.5]{../figures/results/paper2/particle_viz-field_up.png} 
 \caption{Snapshots of the structural evolution of the particle monolayer in bijels stabilized by prolate ellipsoids 
@@
 \centering 
-\includegraphics[scale=0.4]{../figures/results/paper2/microstructure_viz-field_down.png} 
+\includegraphics[scale=0.45]{../figures/results/paper2/microstructure_viz-field_down.png} 
 \caption{Snapshots of bijels stabilized by prolate ellipsoids at 

### 2025-04-08 chapters/LBM_technique.tex
Changes 1. Added new lit review 2. Refined introduction and LBM methods 3. Fixed all references so that they have journals

@@
-\section{Methods}
-\label{section:methods}
-
 Bijels require a multiscale modeling approach to accurately capture the rich array of physical phenomena 
@@
 
-For an incompressible fluid—meaning constant density and negligible bulk viscosity—the condition $\nabla \cdot \vec{u} = 0$ holds. Under this assumption, the Navier-Stokes equation simplifies to,
+For an incompressible fluid, meaning that the constant density and negligible bulk viscosity, the condition $\nabla \cdot \vec{u} = 0$ holds. Under this 
+assumption, the Navier-Stokes equation simplifies to,
 
@@
     \rho \left(\frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u} \right) = -\nabla p + \eta \Delta \vec{u} + \vec{f}
+\end{equation}
+
+As there are no external forces like gravity acting on the fluid and there are is no hydrodynamic pressure being applied to the fluid, $-\nabla p = \vec{f} = 0$ resulting in the
+following form of the incompressible Navier Stokes equation.
+
+\begin{equation}
+    \rho \left(\frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u} \right) = \eta \Delta \vec{u}
 \end{equation}
@@
 \begin{equation}
-    \frac{\partial \bar{\vec{u}}}{\partial \bar{t}} + (\bar{\vec{u}} \cdot\nabla)\bar{\vec{u}} = -\nabla \bar{p} + \frac{1}{Re} \Delta \bar{\vec{u}} + \bar{\vec{f}}    
+    \frac{\partial \bar{\vec{u}}}{\partial \bar{t}} + (\bar{\vec{u}} \cdot\nabla)\bar{\vec{u}} = \frac{1}{Re} \Delta \bar{\vec{u}}
 \end{equation}
@@
 \section{Phase separation}
-Another physical phenomenon relevant to bijel formation is non-ideal mixing. The free energy of mixing for a binary fluid is given by the thermodynamic relation
 
-\begin{equation}
-    \Delta G_m = \Delta H_m - T \Delta S_m
-\end{equation}
-
-In an ideal solution, the enthalpy of mixing is zero, i.e., $\Delta H_m = 0$, and the entropy of mixing $\Delta S_m$ can be derived using statistical mechanical approximations of the 
-configurational states of the binary mixture. For a system with volume fractions $\phi$ and $1 - \phi$, the entropy of mixing becomes
-
-\begin{equation}
-    \Delta S_m = -N_a k_B \left[(1 - \phi)\ln(1 - \phi) + \phi \ln(\phi)\right]
-\end{equation}
-
-In contrast, a regular solution includes non-zero enthalpic interactions. The total free energy of mixing is split into ideal and excess components,
-
-\begin{equation}
-    \Delta G_m = \Delta G_i + \Delta G_e
-\end{equation}
-
-The ideal contribution arises from the entropy of mixing: $\Delta G_i = -T \Delta S_m$. For regular solutions, the excess entropy is assumed to be zero, and the excess enthalpy is given by,
-
-\begin{equation}
-    \Delta H_m = \chi (1 - \phi)\phi
-\end{equation}
-
-where $\chi$ is the interaction parameter quantifying the energetic favorability of mixing. This term originates from mean-field approximations assuming equal-sized molecular species. 
-Combining both contributions, the free energy of mixing becomes:
-
-\begin{equation}
-    \Delta G_m = \chi (1 - \phi)\phi + N_a k_B T \left[(1 - \phi)\ln(1 - \phi) + \phi \ln(\phi)\right]
-\end{equation}
-
-This bulk free energy characterizes the thermodynamic driving forces for phase separation. Alternative forms, such as the Landau-Ginzburg or Flory-Huggins models, may also be used depending on system 
-specifics. In real systems, the interface between two partially miscible fluids is not sharp; rather, the composition transitions smoothly across a finite interface width. To account for this, a 
-gradient energy penalty is added to the free energy functional, penalizing sharp spatial variations in composition. The total free energy functional is written as
-
-\begin{equation}
-    F[\phi] = \int \left( f(\phi) + \frac{\kappa}{2}|\nabla \phi|^2 \right) \, dV
-\end{equation}
-
-where $\kappa$ is the gradient energy coefficient controlling the interface width. Larger \(\kappa\) values correspond to wider interfaces.
-The chemical potential is then defined as the variational derivative of the free energy functional,
-
-\begin{equation}
-    \mu = \frac{\delta F}{\delta \phi} = \frac{df}{d\phi} - \kappa \nabla^2 \phi
-\end{equation}
-
-This chemical potential enters the mass flux expression via a Fickian transport law,
-
-\begin{equation}
-    \vec{J} = -M \nabla \mu
-\end{equation}
-
-where $M$ is the mobility and could potentially be a function of $\phi$. Assuming no advection and applying mass conservation for the order parameter, we obtain,
-
-\begin{equation}
-    \frac{\partial \phi}{\partial t} = -\nabla \cdot \vec{J}
-\end{equation}
-
-Substituting in the expression for \(\vec{J}\) leads to the Cahn-Hilliard equation,
+Bijels form through spinodal decomposition of two partially miscible fluids, a process that can be effectively modeled using the Cahn-Hilliard equation, which describes the diffusive dynamics 
+of a conserved scalar order parameter $\phi$, typically representing the local concentration difference between the two fluid components,
 
@@
 
-This equation describes the diffusive evolution of the conserved field $\phi$ during phase separation. It captures the system's tendency to minimize its total free energy 
-by redistributing the order parameter according to gradients in chemical potential. The Cahn-Hilliard framework naturally incorporates interfacial tension and allows for smooth, 
-continuous transitions between phases, making it highly suitable for modeling non-ideal mixing in systems such as bijels.
+Here, $M$ is the mobility coefficient and $\mu$ is the chemical potential, which is derived from the variation of the free energy functional $F[\phi]$. This formulation allows for the modeling of 
+interfacial tension and the spontaneous formation of bicontinuous domains characteristic of spinodal decomposition.
+To capture not only the diffusive separation of phases but also the resulting fluid motion, the Cahn-Hilliard equation is coupled with the Navie-Stokes equations, leading to the 
+Cahn-Hilliard-Navier-Stokes (CHNS) framework. This coupling is essential in systems like bijels, where hydrodynamic interactions play a significant role in domain coarsening and morphology arrest. 
+The momentum conservation equation in this framework is written as:
+
+\begin{equation}
+    \rho \left(\frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u} \right) = \eta \Delta \vec{u} + \nabla \cdot P_{\text{therm}}
+\end{equation}
+
+Here, $\vec{u}$ is the velocity field, $\rho$ is the fluid density, and $\eta$ is the dynamic viscosity. The term $P_{\text{therm}}$ represents the thermodynamic pressure tensor, which incorporates 
+contributions from gradients in the order parameter and is directly linked to the chemical potential \(\mu\). This tensor encodes the capillary and interfacial forces arising from phase separation 
+and effectively couples the compositional dynamics to the fluid flow.
+The CHNS model enables simulation of complex phase-separating fluid systems, capturing both the interfacial evolution and the momentum transfer within the fluid. In the context of bijels, this 
+model can be used to predict the formation and stabilization of the bicontinuous structure, especially when interfacial jamming by colloidal particles is introduced in more advanced extensions.
 
@@
 
-Ultimately, the choice between point and explicit particle models reflects a trade-off between computational efficiency and physical realism. For systems in which interfacial structure, 
-jamming, or near-field hydrodynamics play a central role as in bijel formation, explicit particle modeling is generally preferred.
+For systems in which interfacial structure, jamming, or near-field hydrodynamics play a central role as in bijel formation, explicit particle modeling 
+is generally preferred as we are able to resolve the interfacial structure and near field hydrodynamics without the complications of IBM.
 
@@
 field using an analytical or numerically tabulated demagnetization tensor. \cite{takahashi_ellipsoids_2017} 
-This method accounts for the effect of particle shape on the distribution of internal magnetization and enables the modeling of induced magnetic dipoles that respond to local fields. 
-The demagnetization field \(\vec{H}_d\) inside a particle is given by
+This method accounts for the effect of particle shape on the distribution of internal magnetization and enables the modeling of induced magnetic 
+dipoles that respond to local fields. The total magnetic field of an ellipsoids can be written,
 
 \begin{equation}
-    \vec{H}_d = -\mathbf{N} \cdot \vec{M}
+    \mathbf{H}(r) = \mathbf{H}_0 + \mathbf{N}(r)\mathbf{K}\mathbf{H}^{\dagger}
 \end{equation}
 
-where \(\mathbf{N}\) is the demagnetization tensor and \(\vec{M}\) is the magnetization vector. \cite{takahashi_ellipsoids_2017} 
-This approach is particularly useful for modeling spheroidal or ellipsoidal particles and is widely used in magnetorheological systems, chain-forming ferrofluids, and dense suspensions where 
-particle-particle interactions are strongly shape-dependent.
-
-At a higher level of fidelity, micromagnetic continuum models resolve the internal magnetization field \(\vec{M}(\vec{r})\) throughout each particle by minimizing the total magnetic energy, which 
-includes exchange, anisotropy, Zeeman, and magnetostatic contributions. \cite{vivas_toward_2020} 
-The governing equations are typically derived from the Landau-Lifshitz-Gilbert (LLG) equation, which evolves \(\vec{M}(\vec{r}, t)\) over time under the influence of effective magnetic fields. 
-These models capture spatially varying domain structures, vortex states, and other complex magnetic configurations, making them essential for accurately simulating particles with nonuniform or dynamic
-magnetization. However, micromagnetic simulations are computationally expensive and require fine discretization within each particle, often using finite element or finite difference methods.
+Where $\mathbf{H}(r)$ is the total magnetic field of the ellipsoids, $\mathbf{H}_0$ is the inducing magnetic field in each direction,
+$\mathbf{K}$ is the susceptibility tensor and $\mathbf{H}^{\dagger}$ is the resultant uniform magnetic field at any point within
+the ellipsoids. \cite{takahashi_ellipsoids_2017}  This approach is particularly useful for modeling spheroidal or ellipsoidal particles and is widely 
+used in magnetorheological systems, chain-forming ferrofluids, and dense suspensions where particle-particle interactions are shape-dependent.
 
@@
 
-The Volume of Fluid (VOF) method is a sharp-interface technique used to track the evolution of fluid-fluid interfaces within a fixed computational grid.
-\cite{gopala_volume_2008, fleckenstein_volume-fluid-based_2015, deising_direct_2018}
-In VOF, a scalar field (the volume fraction) is defined for each grid cell to indicate the presence of each fluid component, with interface reconstruction algorithms used to localize the boundary 
-between phases. 
-The method conserves mass by construction and handles large interface deformations well, making it suitable for high-Reynolds-number flows and surface tension-driven dynamics. However, 
-VOF methods can struggle with accurately capturing interfacial curvature and do not easily accommodate diffuse interfaces or complex topological changes such as pinch-off or coalescence,
-which limits their applicability for simulating phase separation in bijels.
+The Volume of Fluid (VOF) method is a sharp-interface technique used to track the evolution of fluid-fluid interfaces within a fixed computational grid 
+\cite{gopala_volume_2008, fleckenstein_volume-fluid-based_2015, deising_direct_2018}. In VOF, a scalar field representing the volume fraction of one 
+fluid is defined for each grid cell to indicate the local phase composition. Interface reconstruction algorithms are then employed to geometrically 
+localize the boundary between phases. The method is inherently mass-conserving and can handle large interface deformations, making it particularly 
+effective for high-Reynolds-number flows and surface-tension-driven phenomena. However, VOF methods can struggle with accurately capturing interfacial 
+curvature and are not well-suited for diffuse interfaces, which limits their applicability in modeling spinodal decomposition and phase separation 
+processes such as those that form bijels.
 
-Phase field methods take a diffuse-interface approach, representing fluid composition or phase identity using a continuous order parameter field and are often governed by the Cahn-Hilliard or 
-Allen-Cahn equations. \cite{mendoza_evolution_2006, carmack_tuning_2018, chan_channel_2012}
-These methods naturally capture smooth transitions between phases, allow for accurate calculation of interfacial forces, and can easily handle topological changes in the interface. 
-Phase field methods are thermodynamically consistent, as they are derived from free energy functionals, and are particularly well-suited for modeling systems undergoing spinodal decomposition 
-or wetting transitions. Their main limitations lie in the need for fine resolution near interfaces to maintain numerical accuracy and stability, and in the computational cost of solving 
-higher-order partial differential equations, especially when coupled with full hydrodynamics.
+Phase field methods use a diffuse-interface approach to model multiphase systems, representing fluid composition or phase identity through a continuous 
+order parameter field governed by equations such as the Cahn-Hilliard or Allen-Cahn equations 
+\cite{mendoza_evolution_2006, carmack_tuning_2018, chan_channel_2012}. These methods naturally capture smooth transitions between phases, enable
+accurate computation of interfacial forces, and handle topological changes like coalescence and breakup with ease. Derived from variational principles, 
+phase field models are thermodynamically consistent, making them particularly well-suited for simulating spinodal decomposition, wetting phenomena, and 
+interfacial dynamics. However, their main limitations include the need for fine spatial resolution near interfaces to maintain accuracy and the relatively 
+high computational cost of solving fourth-order PDEs, especially when coupled with full hydrodynamic models.
 
-Brownian dynamics is a particle-based method used to simulate the stochastic motion of colloidal particles in a fluid. 
-\cite{huber_brownian_2019, yip_brownian_2005, elsawy_utility_2025}
-It models the over-damped limit of Langevin dynamics by integrating particle 
-trajectories under the influence of deterministic forces (such as interparticle interactions or external fields) and random thermal forces representing collisions with solvent molecules. Hydrodynamic 
-interactions may be included via approximate mobility tensors or neglected altogether, depending on the level of detail required. Brownian dynamics is ideal for studying self-assembly, aggregation, 
-and diffusion of particles in dilute systems, but lacks the ability to capture bulk fluid motion or interface-mediated interactions unless coupled with continuum solvers.
-As such, it is not well-suited
-for simulating the coupled fluid-particle dynamics characteristic of bijel formation on its own.
+Brownian dynamics is a particle-based simulation method used to model the stochastic motion of colloidal particles suspended in a fluid 
+\cite{huber_brownian_2019, yip_brownian_2005, elsawy_utility_2025}. It approximates the over-damped limit of Langevin dynamics by integrating 
+particle trajectories under the influence of both deterministic forces—such as interparticle potentials or external fields—and random thermal 
+forces representing collisions with solvent molecules. Hydrodynamic interactions may be included through approximate mobility tensors or omitted 
+entirely, depending on the desired level of fidelity. Brownian dynamics is particularly well-suited for studying self-assembly, aggregation, and 
+diffusion in dilute suspensions, where particle motion is dominated by thermal fluctuations. However, it does not model the surrounding fluid 
+explicitly, limiting its ability to capture bulk fluid flow or interface-mediated interactions. As a result, Brownian dynamics is not sufficient 
+on its own for simulating the coupled fluid-particle dynamics involved in bijel formation.
 
@@
 
-In summary, the Volume of Fluid method offers robust interface tracking and mass conservation but lacks the ability to naturally capture interfacial curvature and topological changes. 
+In summary, the Volume of Fluid method offers robust interface tracking and mass conservation but lacks the ability to naturally capture interfacial curvature. 
 Phase field methods provide thermodynamically consistent, diffuse-interface models ideal for phase separation, though they require fine resolution and are computationally intensive. 
@@
 The IT model employs level-set or front-tracking techniques to explicitly track the location of fluid interfaces by evolving a separate indicator 
-function alongside the LB solver. \cite{haghani_hassan_abadi_conservative_2018, liang_lattice_2023}
+function, commonly defined using a level set technique, alongside the LB solver. \cite{haghani_hassan_abadi_conservative_2018, liang_lattice_2023}
 This method achieves high accuracy in resolving interface position and curvature, making it ideal for problems 
-involving surface tension-driven flows or sharp interfacial features. However, it is computationally intensive and less well-suited for handling 
-topological changes such as coalescence or pinch-off, which are common in phase-separating systems like bijels.
+involving surface tension-driven flows or sharp interfacial features. However, it is computationally intensive as the indicator function must be implemented alongside
+the LB solver.
 
@@
 criterion and usage requirements for the presented hydrodynamic model.
+
+The density and velocity of the fluid at each grid point is calculated from the zeroth and first moment of the particle density
+distribution,
+
+\begin{equation}
+    \begin{split}
+        \rho &= \sum_i f_i \\
+        \rho\vec{u} &= \sum_i f_i \mathbf{c_i}
+    \end{split}
+\end{equation}
+
+The momentum flux tensor is calculated from the Chapman-Enskog expansion of \ref{eq:LBM_BGK} to the first order yielding,
+
+\begin{equation}
+    \begin{split}
+        \rho\frac{\partial \vec{v}}{\partial t} + \nabla \cdot \Pi &= 0 \\
+        \Pi_{\alpha \beta} &= \sum_i \mathbf{c_i}_\alpha \mathbf{c_i}_\beta (f_i^{eq} + (1 - \frac{1}{2 \tau})f_i^1)
+    \end{split}
+\end{equation}
+
+The momentum flux tensor can be further expressed as a function of macroscopic variables,
+
+\begin{equation}
+    \begin{split}
+        \Pi^{(0)}_{\alpha \beta} &= \sum_i \mathbf{c_i}_\alpha \mathbf{c_i}_\beta f_i^{eq} = p \delta_{\alpha \beta} + \rho \vec{u}_\alpha \vec{u}_\beta \\
+        \Pi^{(1)}_{\alpha \beta} &= (1 - \frac{1}{2 \tau})\sum_i \mathbf{c_i}_\alpha \mathbf{c_i}_\beta f_i^{eq} = \nu (\nabla_{\alpha}(\rho \vec{\beta}) + \nabla_{\beta}(\rho \vec{\alpha}))
+    \end{split}
+\end{equation}
+
+With $p = \rho c_s^2$ and $\delta_{\alpha \beta}$ the kronecker delta.
 

### 2025-04-08 chapters/final_remarks.tex
Changes 1. Added new lit review 2. Refined introduction and LBM methods 3. Fixed all references so that they have journals

@@
 Traditional bijel fabrication relies on thermally induced phase separation (TIPS), a method that, while effective, does not 
-support continuous production. More recently developed techniques—such as Solvent Transfer Induced Phase Separation (STrIPS) 
-and Vapor Induced Phase Separation (VIPS)—enable continuous fabrication and offer greater control over microstructure. However, 
+support continuous production. More recently developed techniques such as Solvent Transfer Induced Phase Separation (STrIPS) 
+and Vapor Induced Phase Separation (VIPS) enable continuous fabrication and offer greater control over microstructure. However, 
 these methods typically require modifications to the initial emulsion formulation, coupling the casting mixture to the resulting 
@@
 
-This work utilized 2 ellipsoidal particle geometries chosen for comparisons to previous literature using this 
-particle geometry. Particles based on cellulose nanocrystals or graphene nanoplates are now in use to fabricate
-particle stabilized emulsions. These particles have also been shown to have capillary bridging and particle stacking,
-not seen in the particles used in this work. These particles in bulk have been shown to have intrinsic ordering
-that can be predicted using onsager theory. An investigation into how using rods or plate like particles would be 
-instructive in identifying if onsager theory can be used in bijel formation and its link to bijel microstructure. 
-\cite{tan_2d_2021}
+Building on the observed coupling between interfacial particle dynamics and bijel microstructure, we propose extending 
+this work by investigating bijels stabilized with non-rigid, cohesive, or attractive particles. Unlike rigid ellipsoids, 
+soft and cohesive particles are known to exhibit distinct glass transition behaviors and rheological responses compared 
+to hard-sphere systems. \cite{weeks_introduction_2017, torquato_jammed_2010} In bijel architectures, attractive interactions have been 
+proposed as a strategy to form “armored” interfaces, potentially enhancing mechanical integrity and enabling higher flow rates in catalytic applications. 
+\cite{boakye-ansah_controlling_2020}
+Similarly, soft particles such as nanogels and hydrogels have attracted interest in biomedical contexts, offering tunable responsiveness 
+to environmental stimuli like temperature and pH—critical features for controlled drug delivery. Incorporating such particles 
+could significantly alter jamming dynamics, interfacial rearrangement, and field-induced responsiveness. These effects may be 
+explored computationally using Lattice Boltzmann Methods integrated with immersed boundary frameworks, incorporating attractive
+particle  interactions to account for electrostatic cohesion and deformability \cite{silva_lattice_2024}. This direction opens opportunities 
+to design bijel systems with enhanced adaptability and function, tailored for application-specific demands.
 
-Colloidal systems made with cohesive and soft particles have been shown in the literature to have different glass 
-transition points and rheological behavior from their hard sphere counterparts. In bijels, attractive particles in 
-particular have been suggested as a means to create "armored" bijels to improve their performance in catalytic materials, 
-allowing higher flow rates to be used. Investigations into soft particles are of interest in biomedical
-applications, with newly developed nanogels and hydrogels being suggested as drug carriers or vectors for stimuli 
-response through temperature or pH. LBM methods that implement the immersed boundary method can be used to model soft
-particles with a DLVO potential used to model electrostatics between particles. \cite{silva_lattice_2024}
+The current simulations, while able to capture structural evolution under external fields, do not fully resolve the complex dynamical landscape of the interfacial 
+particle monolayer. In particular, they lack the resolution to distinguish between fast particle rearrangements and slow collective dynamics near the glass transition, 
+which are known to govern the jamming and unjamming behavior of dense colloidal systems. \cite{weeks_introduction_2017, torquato_jammed_2010} 
+As such, the interplay between interfacial ordering, particle-scale dynamics, and existing order can be characterized more convincingly by investigating the dynamics of
+the particle more systematically by accounting for thermal fluctuations of the fluid. This would involve implementation of a fluctuating Lattice Boltzmann Method
+which would facilitate identification of the glassy dynamics in the system, including the onset of arrest and structural aging characterized with the microstructure
+in Gunther et al. \cite{gunther_timescales_2014}
 
-Another avenue of exploration would be the use of gradient or rotating magnetic fields in place of the constant magnetic 
-fields used here. One study on bijel microstructure showed that a gradient in the particle volume fraction can be used to 
-create a gradient in the eventual domain size. A gradient field may be able to generate nematic order 
-parameter gradients, affecting the particle packing of the bijel at different heights and varying the pore size as a function of 
-height in the field gradient direction. In a ferrofluid or solution of magnetic colloids, a rotating field can assemble 
-particles into chains or rings. In the context of bijel structural response, this can be used to tune bijel microstructure 
-as this process can control the unjamming and rejamming of the particle monolayer, allowing for greater control over the 
-resulting bijel microstructure than a constant field would have. In these simulations, the frequency of rotation would 
-likely need to be tuned based upon how quickly particles respond to field in the bijel.
+Another promising avenue for future investigation involves the use of gradient or rotating magnetic fields in place of constant fields. This
+would impart a force on the particles in addition to the torque that magnetic particles experience under constant fields. \cite{spatafora-salazar_hierarchical_2021, martinezpedrero_collective_2020}
+Prior work has demonstrated that spatial gradients in particle volume fraction can generate domain size gradients in bijels, enabling spatial 
+control over porosity and connectivity \cite{french_bicontinuous_2022}. Analogously, applying a magnetic field gradient may induce vertical 
+gradients in nematic order, influencing local particle packing and yielding position-dependent pore structures across the bijel. This could be 
+particularly useful for creating functionally graded materials with hierarchical transport properties.
 
-% Extensions to this work can be accomplished by investigating the effect of applying a magnetic field on the bijel 
-% while under shear. Ferrofluid models that predict bingham plastic like flows, $\frac{\eta}{eta_{f}} = 1 + \frac{Mn^{*}(\phi_p)}{Mn}$, 
-% have been developed and defined using the Mason number, $Mn = \frac{8\eta_{f} \dot{\gamma}}{\mu_{0} \mu_{f} \beta^{2} H_0^2}$. 
-% \textcolor{blue}{https://doi.org/10.1122/1.4935850, https://linkinghub.elsevier.com/retrieve/pii/S1359029405000385}
+In parallel, rotating magnetic fields offer a dynamic mechanism for restructuring particle arrangements at the interface. 
+\cite{spatafora-salazar_hierarchical_2021, martinezpedrero_collective_2020}
+In ferrofluids and magnetic colloidal suspensions, such fields have been shown to induce chain or ring formation, depending on the rotation frequency and field 
+strength. \cite{spatafora-salazar_hierarchical_2021, martinezpedrero_collective_2020}
+Translating this mechanism to bijels, a rotating field could be used to modulate interfacial jamming behavior, promoting controlled 
+unjamming and reorientation of particles prior to re-jamming. This dynamic control could enable finer tuning of microstructure than static fields, 
+potentially achieving reversible and spatially patterned domain morphologies. Importantly, the effectiveness of this strategy would depend on 
+matching the rotation frequency to the particle relaxation timescales within the bijel, a factor that can be systematically explored in simulation.
 

### 2025-04-08 chapters/introduction_new.tex
Changes 1. Added new lit review 2. Refined introduction and LBM methods 3. Fixed all references so that they have journals

@@
 fluids, and $\theta_c$ is the contact angle of the stabilizing particle. While surfactants and biopolymers reduce interfacial tension, particle stabilizers function by adsorbing 
-at the interface and effectively reducing the interfacial area between fluid domains.
+at the interface and effectively reducing the interfacial area between fluid domains. The free energy associated with the decrease in interfacial area $G_{ads}$ can be orders of magnitude
+larger than the thermal energy of the system $k_b T$ which makes the particle irreversibly adsorbed on the interface. \cite{ngai_particle-stabilized_2015}
 
 Compared to surfactant-stabilized emulsions, particle-stabilized emulsions (Pickering emulsions) exhibit enhanced resistance to coalescence and coarsening, prompting renewed interest 
-in their use across various applications. This resurgence is further driven by increasing environmental and toxicity concerns associated with small-molecule surfactants 
+in their use across various applications. \cite{ngai_particle-stabilized_2015} 
+This resurgence is further driven by increasing environmental and toxicity concerns associated with small-molecule surfactants 
 \cite{kaczerewska_environmental_2020, lechuga_acute_2016}. In contrast, particle stabilizers lower toxicity and improved biocompatibility, in addition to 
@@
 followed by a slower reorganization phase driven by capillary interactions between particles \cite{gunther_timescales_2014}.
-Experimental results confirm that the domain size in rod- and ellipsoid-stabilized
+Experimental results confirm that the domain size in rod and ellipsoid stabilized
 bijels still follows the scaling law $L \propto \frac{1}{\phi_p}$, though the proportionality constant depends on particle geometry \cite{hijnen_bijels_2015, madivala_exploiting_2009, daware_emulsions_2015}.

### 2025-04-08 chapters/lit_review_new.tex
Changes 1. Added new lit review 2. Refined introduction and LBM methods 3. Fixed all references so that they have journals

\section{Solid particles at fluid interfaces}

This strong attachment energy makes particles highly effective at stabilizing emulsions by becoming irreversibly trapped at fluid-fluid interfaces. 
\cite{ngai_particle-stabilized_2015}Once adsorbed, these 
particles reduce interfacial tension and act as physical barriers that prevent the coalescence of droplets, thereby enhancing emulsion stability. Unlike molecular surfactants, 
which are dynamic and can desorb under certain conditions, colloidal particles remain anchored at the interface due to the significant energy required to detach them. 
\cite{ngai_particle-stabilized_2015}This mechanism 
is especially useful in systems such as Pickering emulsions, where the interfacial coverage and wettability of the particles determine the type and stability of the emulsion formed. 
\cite{ngai_particle-stabilized_2015,velankar_non-equilibrium_2015}
As such, understanding particle behavior at interfaces is essential for controlling the structure and longevity of particle-stabilized systems. \cite{ngai_particle-stabilized_2015}
For particles that are smooth and simple and at an interface of oil and water, the attachment energy at the fluid interface can be calculated from a force 
balance between the force imparted from the particle on each fluid and the fluids between one another, known as the Young-Dupre equation.

\begin{equation}
    \cos{\theta_c} = \frac{\sigma_{po} - \sigma_{pw}}{\sigma_{ow}}
\end{equation}

Where $\theta_c$ is the contact angle, $\sigma_{po}$ is the surface tension between particle and oil, $\sigma_{pw}$ is the surface tension between particle and water and
$\sigma_{ow}$ is the surface tension between oil and water. The particle is considered to be preferentially wet by water or hydrophilic if $\theta_c < 90 ^{\circ}$ or 
hydrophobic if $\theta_c > 90 ^{\circ}$. The particle is said to be neutrally wetting if $\theta_c = 90 ^{\circ}$.

\begin{figure}
    \centering
    \includegraphics[scale = 0.5]{../figures/literature_review/particle_at_interface.png }
    \caption{Particle schematic at an interface demonstrating the various quantities of interest. Reprinted Figure 2.1 with permission from
             Particle-Stabilized Emulsions and Colloids: Formation and Applications; Ngai, T., Bon, S. A. F., Eds.; RSC soft matter series; 
             Royal Society of Chemistry, RSC Publishing Cambridge, 2015}
    \label{fig:pieranski_model}
\end{figure}

The energy of the system before and after particle adsorption is different and can be characterized for a simple system with parameters shown in Figure \ref{fig:fig:pieranski_model},

\begin{equation}
    \Delta E_{IW} = E_I - E_w
\end{equation}

Where $\Delta E_{I}$ is the energy of the system when the particle is in the interface and $\Delta E_W$ is the energy of the system when the particle is completely in the water phase.
We define $\Delta E_{I}$ as

\begin{equation}
    E_I = A_w \sigma_{pw} + A_o\sigma_{po} + A_{I_1}\sigma_{ow} + V_w P_w + V_o P_o
\end{equation}

Where $A_w$ and $A_o$ are the surface areas of the particle in the water and oil phases respectively, $V_w$ and $V_o$ are the volumes of water and oil phases respectively and 
$P_w$ and $P_o$ are the pressures of water and oil phases respectively. $A_{I_1}$ is the area of the interface with the particle. 
A similar equation can be written for the energy of the water phase, $E_w$

\begin{equation}
    E_w = (A_w + A_o)\sigma_{pw} + A_{I_2}\sigma_{ow} + (V_w + V_o)P_w
\end{equation}

$A_{I_2}$ is the area of the interface without the particle. The change in the interface energy upon adsorption of the particle can be computed to obtain

\begin{equation}
    \Delta E_{IW} = A_o(\sigma_{po} - \sigma_{pw}) - A_p\sigma_{ow} + V_o(P_o - P_w)
\end{equation}

Substituting the Young-Laplace law for a spherical droplet, $P_w - P_o = \frac{2\sigma_{ow}}{R_d}$ where $R_d$ is the droplet size, for $(P_o - P_w)$ and the Young-Dupre contact angle
expression, the following is obtained

\begin{equation}
    \Delta E_{IW} = \sigma_{ow}(A_o\cos{\theta_c} - A_p - \frac{2 V_o}{R_d})
\end{equation}

A similar construction can be done for the oil phase to obtain

\begin{equation}
    \Delta E_{IW} = -\sigma_{ow}(A_w\cos{\theta_c} + A_p - \frac{2 V_o}{R_d})
\end{equation}

After making appropriate geometrical substitutions for $V_o$ and $A_p$, the Piersanski model is recovered,

\begin{equation}
    \Delta E_{ads} = \pi r^2 \sigma_{ow} (1 - |\cos{\theta_c}|)^2
\end{equation}

From this expression, the adsorption energy can be seen to depend on the contact angle, surface tension and contact area of the particles. This indicates that larger, neutrally wetting
particles adsorbing onto interfaces with high surface tension have a high driving force for adsorption. \cite{ngai_particle-stabilized_2015,reeves_particle-size_2015} This adsorption process 
can be orders of magnitude larger than the thermal energy of the system, calculated as $k_b T$ where $T$ is the temperature of the system and $k_b$ is the Boltzmann constant. This results in 
irreversible adsorption of particles at interfaces. \cite{binks_pickering_2001}

In addition to the adsorption of particles on the interface, the contact angle of the particles determine the dispersed phase of an emulsion and its microstructure. 
\cite{velankar_non-equilibrium_2015}
Hydrophillic particles tend to prefer to form oil in water emulsions while hydrophobic particles prefer to form water in oil emulsions. \cite{ngai_particle-stabilized_2015}
This occurs as the particles preferentially wet one phase over another, causing the interface to bend as the emulsion forms. Neutrally wetting particles are preferred in the formation of 
bijels as no preferential curvature is imparted onto the bijels, fulfilling one of the requirements of a minimal surface in that the mean curvature must be zero. \cite{jinnai_interfacial_2001}

\section{Phase separation}

To understand the formation of bijels, the difference between nucleation and growth and spinodal decomposition must be understood. These processes 
govern how distinct domains emerge and evolve within a binary mixture upon quenching into the two-phase region of the phase diagram. While nucleation and growth involve the formation 
and expansion of isolated domains, spinodal decomposition leads to the spontaneous, interconnected structuring characteristic of bijels. Investigating both mechanisms provides insight 
into how thermodynamic and kinetic pathways influence the resulting microstructure, and why spinodal decomposition is uniquely suited for producing the bicontinuous 
architecture essential to bijels. A schematic free energy and phase diagram is plotted in Figure \ref{fig:phase_diagram}

\begin{figure}
    \centering
    \includegraphics[scale = 0.7]{../figures/literature_review/phase_diagram.png}
    \caption{Schematic of a phase diagram obtained from a free energy curve demonstrating key features of the free energy landscape that correspond
             to the phase diagram. Reprinted Figure 1 from
             Guillen-Chable, F.; Bayona, A.; Rodríguez-Zapata, L. C.; Castano, E. Phase Separation of Intrinsically Disordered 
             Nucleolar Proteins Relate to Localization and Function. IJMS 2021, 22 (23), 13095. with permission under the Creative Common CC BY license.}
    \label{fig:phase_diagram}
\end{figure}

The thermodynamic equilibrium of a binary fluid mixture can be described by its Gibbs free energy, given as \(\Delta G = \Delta H - T \Delta S\), where \(\Delta H\) is the enthalpy change, 
\(T\) is temperature, and \(\Delta S\) is the entropy change. The onset of phase separation occurs at the binodal line, defined where \(\frac{dG}{dx} = 0\), with \(x\) representing the composition. 
Although the system is metastable, it remains uniform until fluctuations give rise to small nuclei. The free energy of each nucleus reflects a 
balance between the bulk free energy gain from phase separation and the interfacial energy penalty, expressed as \(\Delta G = \frac{4}{3}\pi r^3 \Delta g_v + 4 \pi r^2 \sigma\), where \(r\) is 
the nucleus radius, \(\Delta g_v\) is the free energy change per unit volume, and \(\sigma\) is the interfacial tension. 
\cite{thanh_mechanisms_2014}
Nuclei that exceed the critical radius \(r_c = \frac{2\sigma}{|\Delta g_v|}\) will grow, driving the system toward phase separation via nucleation and growth. \cite{thanh_mechanisms_2014}
This transformation process is commonly modeled by the Avrami equation, \(Y = 1 - \exp(-K t^n)\), where \(Y\) is the 
transformed fraction, \(K\) is a rate constant incorporating nucleation and growth kinetics, and \(n\) is the Avrami exponent, which reflects the dimensionality and mechanism of the transformation.
\cite{avrami_kinetics_1939}

At the binodal, the system is still metastable, meaning that unless perturbations are introduced to form nuclei, the mixture remains homogeneous. \cite{thanh_mechanisms_2014}
However, a deeper quench into the two-phase region leads to the spinodal line, defined by the stability criterion \(\frac{d^2G}{dx^2} = 0\). \cite{cahn_free_1958}
Within this region, the system is unstable to even infinitesimal composition fluctuations, and phase 
separation proceeds spontaneously without the need for nucleation. This process, known as spinodal decomposition, is characterized by the continuous and simultaneous growth of interconnected 
domains of both phases. \cite{cahn_free_1958} Unlike nucleation and growth, which relies on localized events, spinodal decomposition 
results in a bicontinuous structure driven by the system's attempt to minimize 
free energy through composition modulation. \cite{cahn_free_1958} The dynamics of spinodal decomposition were characterized by Cahn and Hilliard. \cite{cahn_free_1958} 
We first begin by defining the free energy of a regular solution, known as the bulk free energy.

\begin{equation}
    \Delta G_m = \chi (1 - \phi)\phi + N_a k_B T \left[(1 - \phi)\ln(1 - \phi) + \phi \ln(\phi)\right]
\end{equation}

This bulk free energy characterizes the thermodynamic driving forces for phase separation. Alternative forms, such as the Landau-Ginzburg or Flory-Huggins models, may also be used depending on system 
specifics. In real systems, the interface between two partially miscible fluids is not sharp, meaning that the composition transitions smoothly across a finite interface width. To account for this, a 
gradient energy penalty is added to the free energy functional, penalizing sharp spatial variations in composition. The total free energy functional is written as

\begin{equation}
    F[\phi] = \int \left( f(\phi) + \frac{\kappa}{2}|\nabla \phi|^2 \right) \, dV
\end{equation}

where $\kappa$ is the gradient energy coefficient controlling the interface width. Larger \(\kappa\) values correspond to wider interfaces.
The chemical potential is then defined as the variational derivative of the free energy functional,

\begin{equation}
    \mu = \frac{\delta F}{\delta \phi} = \frac{df}{d\phi} - \kappa \nabla^2 \phi
\end{equation}

This chemical potential enters the mass flux expression via a Fickian transport law,

\begin{equation}
    \vec{J} = -M \nabla \mu
\end{equation}

where $M$ is the mobility and could potentially be a function of $\phi$. Assuming no advection and applying mass conservation for the order parameter, we obtain,

\begin{equation}
    \frac{\partial \phi}{\partial t} = -\nabla \cdot \vec{J}
\end{equation}

Substituting in the expression for \(\vec{J}\) leads to the Cahn-Hilliard equation \cite{cahn_free_1958},

\begin{equation}
    \frac{\partial \phi}{\partial t} = \nabla \cdot \left( M \nabla \mu \right)
\end{equation}

This equation describes the diffusive evolution of the conserved field $\phi$ during phase separation. It captures the system's tendency to minimize its total free energy 
by redistributing the order parameter according to gradients in chemical potential. The Cahn-Hilliard framework naturally incorporates interfacial tension and allows for smooth, 
continuous transitions between phases, making it highly suitable for modeling non-ideal mixing in systems such as bijels.

The most important difference between these two phase separation methods is the morphology of the phase separated structure. While nucleation and growth generates discontinuous droplets,
spinodal decomposition creates continuous domains that have tunable domain sizes and tortuosity which are attractive in many materials applications such as battery electrodes, filtration
membranes and catalyst supports.

\section{Anisotropic particles}

As the library of available particle shapes continues to grow, it becomes increasingly important to understand how these anisotropic particles behave at fluid interfaces.
\cite{wu_recent_2016, cavallaro_curvature-driven_2011}
Unlike spherical particles, anisotropic particles introduce directional interactions and complex rotational dynamics which can significantly 
influence interfacial assembly and emulsion stability. \cite{read_dimerization_2020, davies_dipolar_2015,morgan_understanding_2013}
Their shape can dictate not only their orientation at the interface but also how they interact, and jam, 
ultimately affecting the structure and mechanical properties of the resulting material. \cite{hijnen_bijels_2015}
This is relevant for systems like bijels, where the precise arrangement of particles at the interface affects how the bijel james in place, generating new timescales or 
interfacial phenomena not characterized in bijels made with spheres. \cite{gunther_timescales_2014,hijnen_bijels_2015}

Anisotropic particles exhibit shape-dependent interfacial behavior due to their ability to induce complex multipolar capillary interactions. When adsorbed at a fluid-fluid interface, these 
particles distort the surrounding interface in order to maintain a mean curvature of zero, in accordance with the Young-Laplace equation. This distortion creates curvature gradients around the 
particle that interact with nearby particles or features on the interface, giving rise to anisotropic capillary forces. \cite{loudet_capillary_2005, cheng_shape-anisotropic_2013}. 
Computational simulations further support this complexity, showing that ellipsoidal particles can adopt a variety of metastable orientations 
depending on initial conditions and perturbations encountered during adsorption or rearrangement at the interface \cite{gunther_lattice_2013, newton_influence_2014}.

\begin{figure}
    \centering
    \includegraphics[scale = 0.3]{../figures/literature_review/curvature_driven_assembly.jpeg}
    \caption{Self assembly of particles at points of large curvature gradients. Reproduced from Figure 5 in Cavallaro, M.; Botto, L.; 
             Lewandowski, E. P.; Wang, M.; Stebe, K. J. Curvature-Driven Capillary Migration and Assembly of Rod-like Particles. 
             Proc. Natl. Acad. Sci. U.S.A. 2011, 108 (52), 20923-20928 under the CC-BY license}
    \label{fig:curvature_gradient}
\end{figure}

When looking at arrays of ellipsoidal particles at interfaces, curvature gradients control the dynamics of the system. Figure \ref{fig:curvature_gradient} illustrates the effect that
Cavallaro and co-workers identified. They showed how curvature gradients created at the edges of a 
square rod caused directed assembly of cylinders, with the driving force strong enough to overcome gravity. \cite{cavallaro_curvature-driven_2011} Other works have introduced how these features are 
particle shape dependent with greater control over the curvature gradient providing a means to control particle self assembly. \cite{read_dimerization_2020, sharifi-mood_curvature_2015} Botto et al. 
identified that ellipsoidal particles prefer to arrange side to side state while cylinders prefer to arrange tip to tip with the particle geometric smoothness playing a role in this preference.
\cite{botto_capillary_2012} These differences in particle arrangement could open up new possibilities for tailoring interfacial assemblies and the subsequent differences in microstructure obtained in
a bijel.

Ellipsoidal particles have been used as stabilizers in bijels, resulting in bijels that have smaller domains than those made with spherical particles at the same volume fraction. This was identified to arise 
from the greater surface area to volume ratio of ellipsoidal particles compared to spherical particles. \cite{gunther_timescales_2014} The evolution of the microstructure is also distinct to bijels 
stabilized with spheres, demonstrating two timescales at early and later timesteps. \cite{gunther_timescales_2014} The short timescale is during formation of the bijel, when particles are adsorbed onto the
interface and rotate to align with the interface. At longer timescales, capillary interactions between particles lead to reordering of particles at the interface, leading to a different interfacial 
configuration and microstructure. \cite{gunther_timescales_2014}

\begin{figure}
    \centering
    \includegraphics[scale = 0.3]{../figures/literature_review/rods_bijels.png}
    \caption{Bijels stabilized by rod like particles, demonstrating 'flippers' at the interface, which are particles that flip out of the interface due to stress from adjacent particles. 
             Reproduced from Figure 3 in Hijnen, N.; Cai, D.; Clegg, P. S. Bijels Stabilized Using Rod-like Particles. Soft Matter 2015, 11 (22), 4351-4355 under the CC-BY license}
    \label{fig:rod_bijel_flippers}
\end{figure}

Rod like particles have also been used as stabilizers in experiments, identifying that the length scale of the pores of the bijels follows $ L \propto \frac{1}{\phi_p} $ even if the proportionality constant 
is different. Figure \ref{fig:rod_bijel_flippers} demonstrates bijels stabilized by rod like particles showing that particles flip out of the interface due to steric forces from adjacent particles. This
flipping can increase the resistance to shear due to capillary bridging between adjacent rods.
While the proportionality constant depends on particle geometry, this trend has been observed across various particle shapes 
\cite{hijnen_bijels_2015, madivala_exploiting_2009, gunther_timescales_2014, daware_emulsions_2015, loudet_capillary_2005, cheng_shape-anisotropic_2013}. 
The dynamics of bijels stabilized by ellipsoidal particles are also distinct from bijels stabilized by spheres, caused by reorientation of particle stabilizers at the interface. \cite{gunther_timescales_2014}

\section{Rheology}

Understanding the rheology of emulsions, particularly bijels, is essential because it directly impacts both their fabrication and practical use. \cite{haase_situ_2016}
Previous investigations have characterized that bijels are non-Newtonian fluids with a yield stress and shear thinning behavior. \cite{macmillan_rheological_2019}
A non-Newtonian fluid is one whose viscosity is not constant but varies with the applied shear rate or stress. In Newtonian fluids like water 
or air, there is a linear relationship between shear stress and shear rate, meaning viscosity remains the same regardless of how fast the fluid is sheared. \cite{mezger_rheology_2020} Non-Newtonian fluids, on 
the other hand, deviate from this behavior and may exhibit shear thinning, shear thickening, yield behavior or viscoelasticity with no fluid constrained to one behavior. \cite{mezger_rheology_2020}
Shear thinning and thickening here define that the change in viscosity is sub-linear and super-linear respectively, while yield behavior implies that the viscosity is non-zero when no shear 
is applied. \cite{mezger_rheology_2020} Viscoelasticity appears when the shear response of the fluid is dependent upon the frequency of the applied shear, indicating that the fluid has both liquid and solid like 
characteristics. \cite{mezger_rheology_2020}
These properties often appear in soft matter and multiphase systems where microstructure and particle interactions influence flow behavior.

\begin{figure}
    \centering
    \includegraphics[scale = 0.3]{../figures/literature_review/shear_suspensions.jpeg}
    \caption{Schematic of suspensions under shear demonstrating shear banding and shear aggregates modifying the rheological properties of a suspension. 
             Reproduced from Figure 2 in Wagner, N. J.; Brady, J. F. Shear Thickening in Colloidal Dispersions. Physics Today 2009, 62 (10), 27-32 under the CC-BY license}
    \label{fig:suspension_shear}
\end{figure}

Suspensions and emulsions are examples of non-Newtonian fluids due to the presence of dispersed particles or droplets within a continuous phase. 
\cite{brader_nonlinear_2010, besseling_three-dimensional_2007, xu_relation_2013}  
In suspensions, the interaction  between solid particles—such as hydrodynamic forces, electrostatic repulsion, and steric hindrance—creates microstructural rearrangements under flow, leading to 
non-linear viscosity 
responses. \cite{brader_nonlinear_2010, besseling_three-dimensional_2007} Figure \ref{fig:suspension_shear} demonstrates the shear properties of an example suspension, demonstrating how shear thinning
and shear thickening can occur in suspensions. At low shear, particles may aggregate or form a network that resists deformation, while higher shear rates can break 
down these structures, resulting in shear thinning. In dense systems, particles may experience contact-induced resistance or jamming, causing shear thickening. \cite{brader_nonlinear_2010}

Emulsions behave similarly with droplet deformation, coalescence, and interactions 
among droplets generating time-dependent and non-linear responses to shear. When particles are used to stabilize emulsions (e.g., in Pickering emulsions), their interfacial rigidity 
adds further resistance to flow and deformation, contributing to complex, often viscoelastic, rheological behavior.
Madivala et al. showed that Pickering emulsions stabilized with rod-like particles had enhanced stability under shear, with greater resistance observed as particle aspect ratio increased 
\cite{madivala_exploiting_2009}. They identified this improvement to be due to improved interfacial coverage of ellipsoidal particles at interfaces and the improved elasticity of the interface,
allowing for the droplet to elongate more before failure. These improvements also extend to disc like particles with other investigations into the resistance to shear of emulsions stabilized by
graphene nanosheets, showing that they were able to provide better resistance to shear than spherical particles. \cite{imperiali_simple_2014} This was due to the graphene nanosheets overlapping one
another during shear, creating greater resistance to the applied shear and a higher apparent viscosity. In this case too, the overlap of graphene nanosheets was shown to result in greater interfacial
elasticity inferred through surface tension measurements of droplets with graphene stabilizers. \cite{sun_assembly_2013}

\begin{figure}
    \centering
    \includegraphics[scale = 4]{../figures/literature_review/Flow-curves.png}
    \caption{Schematic of expected shear stress as a function of applied shear rate for various models of fluids on the left and a shear thinning material on the right, demonstrating
             the yield stress at low strain rate followed by shear thinning and the infinite shear rate plateau. Reproduced from Cooke, M. E.; Rosenzweig, D. H. The Rheology of Direct 
             and Suspended Extrusion Bioprinting. APL Bioengineering 2021, 5 (1), 011502 under the CC BY license.}
    \label{fig:shear_theory}
\end{figure}

Several theoretical models have been developed to describe the behavior of non-Newtonian fluids under constant shear. The schematic representation of these models is shown in
Figure \ref{fig:shear_theory}. The power law Model is commonly used to represent shear thinning or 
thickening, with the equation \(\sigma = k \dot{\gamma}^n\), where \(\sigma\) is shear stress, \(\dot{\gamma}\) is shear rate, \(k\) is the consistency index, and \(n\) is the flow index.
\cite{mezger_rheology_2020}
For \(n<1\), the fluid is shear thinning and for \(n>1\), shear thickening. \cite{mezger_rheology_2020}
The Bingham plastic model and Herschel-Bulkley model account for yield stress, with the latter being more general by 
including power-law behavior after yielding, defined as $\sigma = \sigma_y + k \dot{\gamma}^n$. \cite{mezger_rheology_2020}
Shear models that include viscoelasticity have also been developed such as the  Maxwell and Kelvin-Voigt 
models. \cite{mezger_rheology_2020}
They are used when the fluid exhibits both solid- and liquid-like characteristics under stress, incorporating time-dependent strain responses and relaxation phenomena. These models help 
predict and quantify the behavior of complex fluids in real-world applications. \cite{mezger_rheology_2020}

Bicontinuous interfacially jammed emulsion gels (bijels) exhibit highly complex rheological behavior due to their unique microstructure. Bijels typically show yield stress and viscoelasticity, 
behaving like soft solids under low stress and flowing under high stress. \cite{macmillan_rheological_2019, bai_dynamics_2015, lee_making_2013}  The rigidity of the 
particle-laden interface resists deformation, until the applied shear rate is high enough to overcome the frictional contacts keeping particles in place. \cite{boakye-ansah_controlling_2020} 
Experimental studies have reported non-Newtonian behavior such as shear thinning, attributed to the gradual inability of the particles to resist shear. \cite{macmillan_rheological_2019}
Simulation studies using Lattice Boltzman have identified the failure mechanism of bijels stabilized by spherical particles to be due to shear induced ordering to the applied field before
particle ejection from the interface, causing domain coalescence. \cite{bonaccorso_shear_2020} However, the rheology of bijels is still an emerging field, 
with ongoing work focused on understanding how particle properties such as shape, particle size and contact angle affect flow behavior. One important find was that bijels were 
2D colloidal glasses percolating in 3D. \cite{ching_bijel_2022}

Magnetic fields introduce a means of dynamically tuning the rheology of emulsions stabilized by magnetically responsive particles. 
\cite{qiao_magnetorheological_2012} In Pickering emulsions, magnetic fields can induce droplet deformation and change the rigidity of the particle monolayer, thereby changing the flow behavior. 
\cite{qiao_magnetorheological_2012} For bijels incorporating magnetic particles, external fields can affect the stability and 
elasticity of the interfacial particle layer or cause domain reorganization. These effects can lead to tunable yield stress, viscosity, and viscoelastic properties.

\section{Emulsion studies using Lattice Boltzmann}

Understanding the complex interplay between fluid phases and particles in emulsions requires modeling approaches that can capture hydrodynamic interactions, interfacial tension, and particle 
behavior at mesoscopic scales. The multicomponent Lattice Boltzmann method has emerged as a powerful tool for simulating such systems, as it bridges the gap between continuum fluid dynamics 
and molecular-level detail. LB models can naturally incorporate smooth interfaces, phase separation dynamics, and solid-fluid coupling, making them particularly well-suited for studying 
emulsion formation, coarsening, and stabilization mechanisms. This has enabled detailed investigations into how particle properties and flow conditions influence emulsion structure and rheology.

One significant contribution of LB simulations to emulsion research has been the study of dynamical scaling during spinodal decomposition, characterized as the growth of the lengthscale
over time following a power law behavior. \cite{siggia_late_1979, furukawa_role_1994} From the multicomponent Navier Stokes equation, Reynolds number dependent scaling exponents for the 
lengthscale of the system were identified that were termed the viscous limit, where the Reynolds number was low, and the inertial limit, where the Reynolds number is high. \cite{kendon_inertial_2001} 
Multicomponent LB studies definitively demonstrated the ranges of Reynolds number where these scaling laws held and identified a broad crossover region. \cite{kendon_inertial_2001, kendon_3d_1999}

Additionally, the bijel itself was first realized computationally using LB simulations. \cite{stratford_colloidal_2005} A multicomponent LB model with neutrally wetting colloids based on the implementation
by Ladd showed that coarsening interfaces could catch particles irreversibly adsorbing them and arresting coarsening once the interfacial area matched the cross sectional area of particles adsorbed. 
\cite{stratford_colloidal_2005,ladd_numerical_1994} The simulations also showed that these structures were stable over long periods of time, motivating and guiding the experimental realization of 
bijels in 2007. \cite{herzig_bicontinuous_2007} These simulations provided an explanation of the dynamics and mechanistic reasoning behind the formation of bijels, allowing for the prediction of
the microstructure. More recent LB studies have extended these findings by identifying the volume fraction and wetting angle needed to form bijels as opposed to Pickering emulsions. \cite{jansen_bijels_2011} 
The effect of the surface tension, fluid density and volume fraction of particles were also studied, showing that surface tension and fluid density had little effect on the microstructure of bijels 
and that the length scale of the bijel was inversely proportional to the volume fraction of particles. \cite{jansen_bijels_2011}

More recent LB studies by Gunther et al. have extended these findings by incorporating nonspherical particles, such as ellipsoids or rods, to explore how anisotropy influences interfacial behavior 
and emulsion morphology. \cite{gunther_timescales_2014}
These particles introduce directional capillary interactions and exhibit preferred orientations at the interface, which can lead to enhanced jamming and altered domain stabilization with timescales 
of domain size change not observed with spherical particles arising from steric force driven particle reorientation. The orientation of ellipsoidal particles at interfaces was also characterized using
a multicomponent LB, demonstrating the adsorption of ellipsoidal particles at interfaces could result in metastable orientations of particles. \cite{gunther_lattice_2013}

The LB method has also enabled exploration of external field effects, particularly magnetic fields acting on particles at interfaces. Simulations involving magnetic dipolar particles show that 
applying an external field can induce tilting, chaining, or reorientation of particles at the interface. \cite{davies_interface_2014, davies_assembling_2014} This effect was caused by interface deformation
that caused dipolar or quadropolar capillary interactions. This was extended to analyzing the effect of Janus particles at interfaces of evaporating droplets that showed how they preferred to stick together
on curved interfaces. \cite{xie_direct_2017}

These studies demonstrate the effectiveness of multicomponent LB methods in identifying and characterizing mesoscale phenomena relevant to soft matter systems. By capturing 
complex fluid-fluid and fluid-particle interactions, LB models provide a versatile platform for simulating emulsion dynamics, interfacial assembly, and 
microstructural evolution. From revealing the scaling laws of spinodal decomposition to enabling the computational discovery of bijels, LB simulations have offered valuable insights that would be 
difficult to obtain experimentally. Furthermore, the ability to incorporate anisotropic particles and external fields, such as magnetism, highlights the method's adaptability for exploring 
increasingly sophisticated and tunable systems.

### 2025-04-08 chapters/paper1_new.tex
Changes 1. Added new lit review 2. Refined introduction and LBM methods 3. Fixed all references so that they have journals

@@
 \section{Introduction}
+
+This section is based on work published in the Royal Society of Chemistry's Soft Matter journal. \cite{karthikeyan_formation_2024} 
+It is reproduced from Ref \cite{karthikeyan_formation_2024} with permission from the Royal Society of Chemistry.
 
@@
 
-Figure~\ref{fig:rdf} shows the radial distribution function (RDF) at time steps \(t = 1000\Delta t,\ 10000\Delta t,\ 100000\Delta t\). 
+Figure~\ref{fig:rdf} shows the radial distribution function (RDF) at time steps $t = 1000\Delta t, 10000\Delta t, 100000\Delta t$. 
 For ellipsoidal particles, characteristic contact distances include \(2R_{\parallel}\), \(2R_{\perp}\), and \(R_{\parallel} + R_{\perp}\), 
@@
 a shoulder emerges near \(R_\parallel + R_\perp\), indicating occasional tilting out of the interface to reduce interfacial coverage. In contrast, 
-for prolate particles, the dip at \(2R_\parallel\) disappears over time, suggesting increased tip-to-tip alignment—consistent with field-driven 
+for prolate particles, the dip at \(2R_\parallel\) disappears over time, suggesting increased tip-to-tip alignment, consistent with field-driven 
 particle orientation that supports close packing along both particle axes. This layered structure is also visible in the snapshots in 

### 2025-04-08 licenses/licenses.tex
Changes 1. Added new lit review 2. Refined introduction and LBM methods 3. Fixed all references so that they have journals

@@
     Mumm, A. Mohraz and R. Ragan. Scalable synthesis of gyroid-inspired freestanding three-
-    dimensional graphene architectures. 1, 3870.: 1548092-1
+    dimensional graphene architectures. 1, 3870. Reproduced using license number 1548092-1
     \item Stratford, R. Adhikari, I. Pagonabarraga, J.-C. Desplat and M. E. Cates. Colloidal jam-
-    ming at interfaces: A route to fluid-bicontinuous gels. 309, 2198: 5966820525314
+    ming at interfaces: A route to fluid-bicontinuous gels. 309, 2198. Reproduced using license number 5966820525314
     \item F. Haase, K. J. Stebe and D. Lee. Continuous fabrication of hierarchical and asymmetric
     bijel microparticles, fibers, and membranes by solvent transfer-induced phase separation
-    (STRIPS). 27, 7065: 5913140219015
+    (STRIPS). 27, 7065. Reproduced using license number 5913140219015
     \item K. Tham, W. M. Ng, S. S. Leong, S. P. Yeap, S. C. Low, H. L. Lee and J. Lim. Mag-
@@
     \item G. B. Davies, T. Kr¨uger, P. V. Coveney, J. Harting and F. Bresme. Assembling ellipsoidal
-    particles at fluid interfaces using switchable dipolar capillary interactions. 26, 6715.: Reproduced under the Creative Commons CC BY License.
+    particles at fluid interfaces using switchable dipolar capillary interactions. 26, 6715. Reproduced under the Creative Commons CC BY License.
     \item C. Loudet, A. M. Alsayed, J. Zhang and A. G. Yodh. Capillary interactions between
-    anisotropic colloidal particles. 94, 018301: RNP/25/FEB/088185
-    \item S. S. Velankar. A non-equilibrium state diagram for liquid/fluid/particle mixtures. 11, 8393: 1551968-1
+    anisotropic colloidal particles. 94, 018301. Reproduced using license number RNP/25/FEB/088185
+    \item S. S. Velankar. A non-equilibrium state diagram for liquid/fluid/particle mixtures. 11, 8393. Reproduced using license number 1551968-1
     \item Bonaccorso, S. Succi, M. Lauricella, A. Montessori, A. Tiribocchi and K. H. Luo. Shear
     dynamics of confined bijels. 10, 095304.: Reproduced under the Creative Commons CC BY License.
+    \item Particle-Stabilized Emulsions and Colloids: Formation and Applications; Ngai, T., Bon, S. A. F., Eds.; RSC soft matter series; 
+    Royal Society of Chemistry, RSC Publ: Cambridge, 2015: Reproduced under the Royal Society of Chemistry license number 1597404-1
+    \item Particle schematic at an interface demonstrating the various quantities of interest. Reprinted Figure 1 from
+    Guillen-Chable, F.; Bayona, A.; Rodríguez-Zapata, L. C.; Castano, E. Phase Separation of Intrinsically Disordered 
+    Nucleolar Proteins Relate to Localization and Function. IJMS 2021, 22 (23), 13095. with permission under the Creative Common CC BY license.
+    \item Cavallaro, M.; Botto, L.; Lewandowski, E. P.; Wang, M.; Stebe, K. J. Curvature-Driven Capillary Migration and Assembly of Rod-like Particles. 
+    Proc. Natl. Acad. Sci. U.S.A. 2011, 108 (52), 20923-20928. Reproduced under the CC-BY license
+    \item Hijnen, N.; Cai, D.; Clegg, P. S. Bijels Stabilized Using Rod-like Particles. Soft Matter 2015, 11 (22), 4351-4355. Reproduced under the CC-BY license
+    \item Wagner, N. J.; Brady, J. F. Shear Thickening in Colloidal Dispersions. Physics Today 2009, 62 (10), 27-32. Reproduced under the CC-BY license
+    \item Cooke, M. E.; Rosenzweig, D. H. The Rheology of Direct and Suspended Extrusion Bioprinting. APL Bioengineering 2021, 5 (1), 
+          011502. Reproduced under the CC BY license.
     \item S. Schmieschek, L. Shamardin, S. Frijters, T. Kr¨uger, U. D. Schiller, J. Harting and P. V.
     Coveney. LB3D: A parallel implementation of the Lattice-Boltzmann method for simulation
-    of interacting amphiphilic fluids. Computer Physics Communications 217, 149 (2017).: Reproduced under the Creative Commons CC BY License
+    of interacting amphiphilic fluids. Computer Physics Communications 217, 149 (2017). Reproduced under the Creative Commons CC BY License
 \end{itemize}

### 2025-04-08 chapters/lit_review_new.tex
fixed figure ref in lit review

@@
 
-The energy of the system before and after particle adsorption is different and can be characterized for a simple system with parameters shown in Figure \ref{fig:fig:pieranski_model},
+The energy of the system before and after particle adsorption is different and can be characterized for a simple system with parameters shown in Figure \ref{fig:pieranski_model},
 

### 2025-04-11 chapters/LBM_technique.tex
Changes 1. Rearranged introduction, lit review and methods sections

--- 2025-04-05 chapters/LBM_technique.tex
@@
-\section{Methods}
-\label{section:methods}
-
-Bijels require a multi-scale model to correctly simulate all the physical phenomena occurring at every scale. Within a bijel, fluid flow,
-phase separation, particle-fluid and interparticle interactions are present. The lengthscales present in a bijel imply a model must be able
-to resolve nanometer to micrometer resolutions and must be able to capture the hydrodynamics, non-ideal mixing and interparticle interactions present
-in the system. A review of the physics in the system will be provided.
+Bijels require a multiscale modeling approach to accurately capture the rich array of physical phenomena 
+occurring across multiple length and time scales. Within a bijel, one must consider fluid flow, phase separation, particle-fluid coupling, and interparticle 
+interactions. The length scales of interest range in the hundreds of nanometer to  tens of micron scale, demanding a model capable of resolving fine structural details while also 
+capturing mesoscale dynamics. In the following sections, a comprehensive review of the relevant physical processes is provided, laying the foundation for the 
+numerical methods used in this work.
 
@@
 
-Mass conservation is established using simple differential equation of a control volume that characterizes the mass flow through the volume. Assuming no
-addition or subtraction of mass, the differential equation is the material derivative of the density, defined as
+We begin with a restatement of Reynolds Transport Theorem (RTT) which relates the change in a parameter in a volume over time to the change in that quantity in a control volume,
+defined as
+
+\begin{equation}
+    \frac{d}{dt} \int_V f \, dV = \int_V \frac{\partial f}{\partial t} \, dV + \int_{\partial V} f (\vec{v}_{\text{surf}} \cdot \vec{n}) \, dA
+\end{equation}
+
+Where $f$ can be a scalar, vector or tensor, $V$ is the volume of the control element, $t$ is time, $\vec{v}_{surf}$ is the velocity vector of the surface of the volume element,
+$\vec{n}$ is the surface normal unit vector. From the RTT, the continuity equation can be written to analyze the mass flux of a control volume given by,
 
@@
 
-Where $\rho$ is the fluid density and $\vec{u}$ is the fluid velocity vector. The fluid momentum can be derived from the mass conservation equation
-by calculating the material derivative of the momentum of the system. Changes in momentum from addition or subtraction of momentum cannot be ignored,
-with changes arising from pressure gradients, viscous forces and body force terms. If mass is conserved, the momentum equation is defined as
+where $\rho$ is the fluid density and $\vec{u}$ is the fluid velocity. Based on the system being modeled, we assume that the fluid is incompressible, reducing the continuity equation to
+$\nabla\cdot \vec{u} = 0$ The momentum conservation equation can also be written by applying Newton's second law to the fluid element. This yields the Cauchy momentum equation for an
+incompressible fluid, where changes in momentum arise due to pressure gradients, viscous stresses, and body forces. The general form of the momentum equation is given by,
 
 \begin{equation}
-    \rho (\frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u}) = -\nabla p + \nabla \cdot \mathbf{\tau} + \mathbf{f}
+    \rho \left(\frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u} \right) = -\nabla p + \nabla \cdot \boldsymbol{\tau} + \vec{f}
 \end{equation}
 
-Where $p$ is the pressure applied to the control volume, $\mathbf{\tau}$ is a general stress tensor and $\mathbf{f}$ is the body force 
-applied on the box such as gravitational forces. $\mathbf{\tau}$ can be defined by assuming the fluid is isotropic, the shear stress depends
-linearly on the dynamic viscosity and the strain rate and net forces are zero at equilibrium.
+where $p$ is the pressure, $\boldsymbol{\tau}$ is the viscous stress tensor, and $\vec{f}$ represents external forces such as gravity or magnetic interactions.
+
+For a Newtonian, isotropic fluid, the viscous stress tensor is given by
 
 \begin{equation}
-    \mathbf{\tau} = p\mathbf{I} + \eta(\nabla \mathbf{v} + (\nabla \mathbf{v})^T) - \frac{2}{3}\eta(\nabla \cdot \mathbf{v})\mathbf{I}
+    \boldsymbol{\tau} = p\mathbf{I} + \eta\left( \nabla \vec{u} + (\nabla \vec{u})^T \right)
 \end{equation}
 
-Where $p = (\lambda + \frac{2}{3}\eta)\nabla \cdot \mathbf{v}$ is defined from the bulk viscosity $\lambda$. After substitution into the momentum equation, the compressible 
-Navier Stokes equation is obtained, defined as
+Substituting this stress tensor into the momentum equation yields the incompressible Navier-Stokes equation,
 
 \begin{equation}
-    \rho (\frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u}) = -\nabla p + \eta \Delta \mathbf{v} + \frac{1}{3}\eta \nabla(\nabla \cdot \mathbf{v}) + \mathbf{f}
+    \rho \left(\frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u} \right) = -\nabla p + \eta \nabla^2 \vec{u} + \vec{f}
 \end{equation}
 
-If the fluid being modelled is assumed to be incompressible meaning that the density stays constant and the bulk viscosity is 0, $\nabla \cdot \mathbf{v} = 0$. This simplifies
-the Navier Stokes equation to
+In the single component case, $-\nabla p = \vec{f} = 0$ as there are no external forces like gravity acting on the fluid and there are is no hydrodynamic pressure being applied to the 
+fluid resulting in the following form of the incompressible Navier Stokes equation.
 
 \begin{equation}
-    \rho (\frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u}) = -\nabla p + \eta \Delta \mathbf{v} + \mathbf{f}
+    \rho \left(\frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u} \right) = \eta \nabla^2 \vec{u}
 \end{equation}
 
-The Navier Stokes equation can be recast into a dimensionless form by rescaling length, time and density into dimensionless forms. These parameters are rescaled as 
-$\bar{l} = \frac{l}{l_0}$, $\bar{t} = \frac{t}{t_0}$ and $\bar{\rho} = \frac{\rho}{\rho_0}$ with barred quantities indicating dimensionless properties. After substituting
-these parameters into the Naver Stokes equation this is obtained
+To facilitate numerical simulation and analysis, it is often useful to express the Navier-Stokes equation in non-dimensional form. Introducing characteristic scales for length 
+$l_0$, time $t_0$, and density $\rho_0$, dimensionless variables are defined as
 
 \begin{equation}
-    \frac{\partial \bar{\vec{u}}}{\partial \bar{t}} + (\bar{\vec{u}} \cdot\nabla)\bar{\vec{u}} = -\nabla \bar{p} + \frac{1}{Re} \Delta \mathbf{\bar{v}} + \bar{\mathbf{f}}
+    \bar{l} = \frac{l}{l_0}, \quad \bar{t} = \frac{t}{t_0}, \quad \bar{\rho} = \frac{\rho}{\rho_0}
 \end{equation}
 
-$Re = \frac{\rho u l}{\eta}$ which defines the ratio between inertial and viscous forces.
+Substituting these into the incompressible Navier-Stokes equation leads to the dimensionless form:
+
+\begin{equation}
+    \frac{\partial \bar{\vec{u}}}{\partial \bar{t}} + (\bar{\vec{u}} \cdot\nabla)\bar{\vec{u}} = \frac{1}{Re} \nabla^2 \bar{\vec{u}}
+\end{equation}
+
+where the Reynolds number is defined as $Re = \frac{\rho_0 u_0 l_0}{\eta}$ which characterizes the ratio of inertial to viscous forces in the system.
 
@@
 
-Another physical phenomenon being described is non-ideal mixing. The free energy of mixing
-is defined as $\Delta G_m = \Delta H_m - T \Delta S_m$. In an ideal solution, $\Delta H_m = 0$. An expression for $\Delta S_m$ for a binary mixture is obtained from statistical mechanical 
-approximations of the configurations that binary mixtures can take, resulting in
+Bijels form through spinodal decomposition of two partially miscible fluids, a process that can be effectively modeled using the Cahn-Hilliard equation, which describes the diffusive dynamics 
+of a conserved scalar order parameter $\phi$, typically representing the local concentration difference between the two fluid components,
 
 \begin{equation}
-    S_m = -k N_\phi k_B T((1 - \phi)\ln{1 - \phi} + \phi ln(\phi)) 
+    \frac{\partial \phi}{\partial t} = \nabla \cdot \left( M \nabla \mu \right)
 \end{equation}
 
-In a regular solution, $\Delta H_m \neq 0$. The free energy of mixing is defined as the sum of the ideal and excess contribution, $\Delta G_m = \Delta G_e + \Delta G_i$.
-$\Delta G_i = -TS_m$. $\Delta G_e = \Delta H_e + T \Delta S_e$. The excess entropy of mixing is 0, and the excess enthalpy of mixing is defined
+Here, $M$ is the mobility coefficient and $\mu$ is the chemical potential, which is derived from the variation of the free energy functional $F[\phi]$. This formulation allows for the modeling of 
+interfacial tension and the spontaneous formation of bicontinuous domains characteristic of spinodal decomposition.
+To capture not only the diffusive separation of phases but also the resulting fluid motion, the Cahn-Hilliard equation is coupled with the Navie-Stokes equations, leading to the 
+Cahn-Hilliard-Navier-Stokes (CHNS) framework. This coupling is essential in systems like bijels, where advection play a significant role in domain coarsening and morphology arrest. 
+The momentum conservation equation in this framework is written as:
 
 \begin{equation}
-    \begin{split}
-    \frac{\partial\phi}{\partial t} = \nabla \cdot \left( \Gamma  \nabla\mu_\phi \right)
-    \end{split}
+    \rho \left(\frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u} \right) = \eta \nabla^2 \vec{u} - \nabla p - \phi \nabla \mu
 \end{equation}
 
-\section{Particle dynamics}
+% Here, $\vec{u}$ is the velocity field, $\rho$ is the fluid density, and $\eta$ is the dynamic viscosity. The term $P_{\text{therm}}$ represents the thermodynamic pressure tensor, which incorporates 
+% contributions from gradients in the order parameter and is directly linked to the chemical potential \(\mu\). This tensor encodes the capillary and interfacial forces arising from phase separation 
+% and effectively couples the compositional dynamics to the fluid flow.
 
-\section{Magnetic fields and particles}
+The CHNS model enables simulation of complex phase-separating fluid systems, capturing both the interfacial evolution and the momentum transfer within the fluid. In the context of bijels, this 
+model can be used to predict the formation and stabilization of the bicontinuous structure, especially when interfacial jamming by colloidal particles is introduced in more advanced extensions.
 
-% The Shan-Chen pseudopotential
-% model is used to simulate the Cahn-Hilliard equation, defined below
+\section{Implementing the multicomponent Lattice Boltzmann Method} 
+\label{section:lbm_hydrodynamics}
 
-% \begin{equation}
-%     \begin{split}
-%     \frac{\partial\phi}{\partial t}+\nabla\cdot\left(\phi\vec{u}\right) &= \nabla \cdot \left( \Gamma  \nabla\phi \right)
-%     \end{split}
-% \end{equation}
-
-% where $c^k$, $M^k$ and $u^k$ is the concentration, mobility and velocity of species $k$ respectively while $\mu$ is the free energy of system. 
-% \cite{shan_lattice_1993, shan_simulation_1994, he_lattice_1997, he_discrete_1998}
-
-% A computational model designed to simulate soft matter systems 
-% at the mesoscale must accurately represent both hydrodynamics and non-ideal mixing in order to capture the essential physics of emulsions, colloids, and phase-separating fluids. 
-% A hydrodynamic model must be able to recover mass and momentum conservation of a incompressible fluid
-
-% Modelling multicomponent dynamics requires incorporating a free energy model between fluids, allowing for the implementation of
-% chemical potential driven mass transfer and surface tension. Typically this is done using a Cahn-Hilliard model based on a
-% square gradient free energy functional. This captures the demixing characteristics of phase separating fluids and controls interface
-% characteristics, providing surface tension and interface width characteristics. This model has been used in past investigations looking 
-% into spinodal decomposition, domain growth and coarsening.
-
-% To fully capture mesoscale dynamics, the model must also resolve the coupling between hydrodynamic flow and composition gradients. This coupling 
-% is essential for simulating phenomena such as Marangoni flows, interfacial instabilities, and anisotropic stress distributions that arise from 
-% non-uniform compositions or curvature-dependent surface tension. Moreover, the model must support anisotropic or time-dependent external fields 
-% (e.g., magnetic, electric, or shear) that influence mixing behavior. Computational frameworks that can evolve velocity, pressure, and composition 
-% fields simultaneously—while ensuring thermodynamic consistency and mechanical stability—are critical for accurately describing the emergent structures 
-% and transport properties in non-ideal soft matter systems.
-
-% Given the multiscale modeling necessary to correctly simulate the physical system, one approach suggested to tackle this problem is the multicomponent
-% Lattice Boltzmann Method. This technique bridges the length and time scales necessary in soft matter modeling through modeling the evolution of a particle
-% distribution function. Hydrodynamic parameters are recovered through calculating the moments of the particle distribution function. One of the advantages of
-% the Lattice Boltzmann Method its parallelize nature and ease of adding multiple physical phenomena. In the following sections, the implementation of the LBM
-% and alternatives to the LBM will be presented.
-
-% This work uses a multicomponent Lattice Boltzmann Method (LBM) to simulate the hydrodynamics of two partially miscible, 
-% incompressible fluids as implemented in LB3D. The LBM solves the continuity and Navier-Stokes equation at low
-% Mach and Reynolds numbers for the fluid, defined as,
-
-% \begin{equation}
-%     \begin{split}
-%     \frac{\partial\rho}{\partial t} + \nabla\cdot\left(\rho\vec{u}\right) &= 0 , \\
-%     \frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u} &= - \frac{1}{\rho} \nabla p + \nu \nabla^2 \vec{u} ,
-%     \end{split}
-% \end{equation}
-
-% incorporating density $(\rho)$, viscosity $(\eta)$, velocity $(u)$, pressure $(P)$, and 
-% body force $(F_{body})$. \cite{qian_lattice_1992, chin_lattice_2002, nourgaliev_lattice_2003} The Shan-Chen pseudopotential
-% model is used to simulate the Cahn-Hilliard equation, defined below
-
-% \begin{equation}
-%     \begin{split}
-%     \frac{\partial\phi}{\partial t}+\nabla\cdot\left(\phi\vec{u}\right) &= \nabla \cdot \left( \Gamma  \nabla\phi \right)
-%     \end{split}
-% \end{equation}
-
-% where $c^k$, $M^k$ and $u^k$ is the concentration, mobility and velocity of species $k$ respectively while $\mu$ is the free energy of system. 
-% \cite{shan_lattice_1993, shan_simulation_1994, he_lattice_1997, he_discrete_1998}
-
-% Particle dynamics include Hertzian contact and lubrication forces, tracked with classical Newtonian mechanics, while 
-% particle-fluid coupling involves momentum exchange to simulate viscous dissipation. Particle-particle magnetic interactions are modeled using dipole 
-% interactions. \cite{davies_interface_2014, xie_direct_2017, xie_controllable_2021} A more detailed description of the model is 
-% provided in the following sections
-
-\section{Lattice Boltzmann Method}
-
-The Lattice Boltzmann Method (LBM) is an evolution of preceding lattice gas automata techniques, which is a discretization of the Boltzmann equation of motion for 
-molecules. This means that unlike traditional CFD techniques such as FDM, VOF or level set methods, LBM tracks the evolution of a 
-particle distribution function within grid cells evolved through a discretized Boltzmann equation of motion. Macroscopic variables such as fluid density and 
-velocity are recovered from the particle distributions through appropriate moment integration, and the Navier Stokes equation at the incompressible limit can be 
-obtained through a Chapman-Enskog expansion of the LBM. The LBM has become an attractive tool for meso-scale CFD simulations due to its ease of algorithm 
-implementation, highly parallelizable nature and ease of boundary condition implementation, allowing coupling to other physically relevant systems such as 
-particles with varieties of potentials, external fields and deformable bodies.
-
-The particle distribution function described earlier is advected on a pre-constructed lattice stencil, commonly denoted as DnQm where n and m represent the 
-number of dimensions and directions in the stencil. Common stencils include the D1Q5, D2Q9 and D3Q19 stencil, all of which recover mass and momentum conservation. 
-For energy conservation, a higher order stencil such as D3Q27 is necessary. The D2Q9 and D3Q19 stencils have 8 and 18 populations respectively that include 
-connections to nearest and next nearest neighbour points, in addition to a central rest point. The D3Q19 stencil is shown in Figure \ref{fig:d3q19_lattice}.
+The lattice boltzmann method works by evolving a population distribution $f_{i}(\mathbf{x}, t)$ on a cubic lattice with 
+timestep $\Delta t$ with lengthscale $\Delta x$. \cite{qian_lattice_1992, succi_lattice_2018, he_theory_1997} The cubic lattice or stencil is described
+DnQm where n and m represent the number of dimensions and directions in the stencil. \cite{succi_lattice_2018, schmieschek_lb3d_2017}
+Common stencils include the D1Q5, D2Q9 and D3Q19 stencil, all of which recover mass and momentum conservation and are Galilean invariant.
+For energy conservation, a higher order stencil such as D3Q27 is necessary. The D2Q9 and D3Q19 stencils have 9 and 19 populations respectively that include 
+connections to nearest and next nearest neighbour points. The D3Q19 
+velocity set is used in this work with the indexes $i$ represent each of the 19 velocities and conserves mass and momentum 
+to the second order. It can be seen in Figure \ref{fig:d3q19_lattice}.
 
@@
 with the chosen stencil. During the collision step, the particle population distribution is relaxed towards an equilibrium with a collision operator, at a 
-specified relaxation rate.
-
-\section{Hydrodynamics} 
-\label{section:lbm_hydrodynamics}
-
-The lattice boltzmann method works by evolving a population distribution $f_{i}(\mathbf{x}, t)$ on a cubic lattice with 
-timestep $\Delta t$ with lengthscale $\Delta x$. \cite{qian_lattice_1992, succi_lattice_2018, he_theory_1997} The D3Q19 
-velocity set is used in this work with the indexes $i$ represent each of the 19 velocities and conserves mass and momentum 
-to the second order. It can be seen in Figure \ref{fig:d3q19_lattice}. The algorithm is split into the 
-collision step where the populations on each lattice grid cell is relaxed towards an equilibrium, followed by the 
-advection step where populations in each velocity direction are propagated with velocity $\mathbf{c_i}$.
-
-% The collision step occurs using a single relaxation time Bhatnagar-Gross-Krook (BGK) collision operator at relaxation 
-% rate $\tau$. \cite{bhatnagar_model_1954, qian_lattice_1992}
-
-% The collision operator can have multiple forms based on how many relaxation rates are used although the most common variant is the 
-% Single Relaxation Time (SRT) collision operator, more commonly known as the Bhatnagar-Gross-Krook (BGK) collision operator. 
-% \cite{bhatnagar_model_1954, qian_lattice_1992} 
-% Owing to its stability in low Mach 
-% and Reynolds numbers and simplicity of implementation, the BGK operator is often used in particle laden flow and soft matter simulations. 
-% \cite{bhatnagar_model_1954} These limitations are present owing to the implicit link between the fluid properties and the relaxation rate, 
-% and to ensure fluid incompressibility from an equation that intrinsically simulates a compressible fluid. To get over these 
-% limitations, Two Relaxation Time (TRT) and Multiple Relaxation Time (MRT) operators also exist, expanding the possible application of the LBM to visco-elastic 
-% flows and implementation of fluctuating hydrodynamics in the LBM. \cite{liu_simulation_2023, adhikari_fluctuating_2005} The combined collision and advection 
-% LBM is expressed below in equation \ref{eq:LBM_BGK}
-
-The collision step in the LBM is performed using the collision operator. It can take multiple forms depending on the number of
+specified relaxation rate. It can take multiple forms depending on the number of
 relaxation rates used. The most commonly used variant is the Single Relaxation Time (SRT) operator defined with the Bhatnagar-Gross-Krook (BGK) 
@@
 The BGK operator limits simulations to low reynolds number and mach numbers to prevent numerical instabilities. 
-\cite{qian_lattice_1992} The kinematic viscosity if using the BGK operator is defined as 
-$\nu = c_s^2(\tau - \frac{\Delta t}{2})$. The equilibrium distribution is obtained from a taylor expansion of the 
-Maxwell-Boltzmann distribution to the second order. \cite{he_theory_1997, succi_lattice_2018} This is shown in equation 
+\cite{qian_lattice_1992} The kinematic viscosity, if using the BGK operator, is obtained from the Chapman-Enskog expansion of \ref{eq:LBM_BGK}
+as $\nu = c_s^2(\tau - \frac{\Delta t}{2})$. The equilibrium distribution is obtained from a projection of the 
+Maxwell-Boltzmann distribution onto Hermite polynomials. \cite{he_theory_1997, succi_lattice_2018} This is shown in equation 
 \ref{eq:LBM_Feq}.
@@
 \begin{equation}
-    f_{i}^{eq}(\mathbf{x}, t) = w_i\rho(1 + \frac{\mathbf{c_i} \cdot \mathbf{u}}{c_s^2} + \frac{(\mathbf{c_i} \cdot 
-    \mathbf{u})^2}{2c_s^4} + \frac{\mathbf{u} \cdot \mathbf{u}}{2c_s^2})
+    f_{i}^{eq}(\rho, \vec{u}) = w_i\rho(1 + \frac{\mathbf{c_i} \cdot \mathbf{u}}{c_s^2} + \frac{ \vec{u}(c_{i,\alpha}c_{i,\beta}-c_s^2\mathbb{I}) }{2c_s^4})
+    % \frac{(\mathbf{c_i} \cdot \mathbf{u})^2}{2c_s^4} + \frac{\mathbf{u} \cdot \mathbf{u}}{2c_s^2})
     \label{eq:LBM_Feq}
@@
 and can be calculated from the mass distribution using $\rho = \sum f_i$ and $\rho \mathbf{u} = \sum f_i \mathbf{c}_i$ 
-respectively. Using the Chapman-Enskog expansion, the Navier-Stokes equation at the incompressible limit at low mach
+respectively. Using the Chapman-Enskog expansion, the Navier-Stokes equation at the incompressible limit at low Mach
 numbers can be recovered. \cite{qian_lattice_1992, he_lattice_1997} The regime accessible through this method is suitable 
@@
 
-\section{Non-ideal mixing}
+The density and velocity of the fluid at each grid point is calculated from the zeroth and first moment of the particle density
+distribution,
+
+\begin{equation}
+    \begin{split}
+        \rho &= \sum_i f_i \\
+        \rho\vec{u} &= \sum_i f_i \mathbf{c_i}
+    \end{split}
+\end{equation}
+
+The momentum flux tensor is calculated from the Chapman-Enskog expansion of \ref{eq:LBM_BGK} to the first order yielding,
+
+\begin{equation}
+    \begin{split}
+        \rho\frac{\partial \vec{v}}{\partial t} + \nabla \cdot \Pi &= 0 \\
+        \Pi_{\alpha \beta} &= \sum_i \mathbf{c_i}_\alpha \mathbf{c_i}_\beta (f_i^{eq} + (1 - \frac{1}{2 \tau})f_i^1)
+    \end{split}
+\end{equation}
+
+The momentum flux tensor can be further expressed as a function of macroscopic variables,
+
+\begin{equation}
+    \begin{split}
+        \Pi^{(0)}_{\alpha \beta} &= \sum_i \mathbf{c_i}_\alpha \mathbf{c_i}_\beta f_i^{eq} = p \delta_{\alpha \beta} + \rho \vec{u}_\alpha \vec{u}_\beta \\
+        \Pi^{(1)}_{\alpha \beta} &= (1 - \frac{1}{2 \tau})\sum_i \mathbf{c_i}_\alpha \mathbf{c_i}_\beta f_i^{eq} = \nu (\nabla_{\alpha}(\rho \vec{\beta}) + \nabla_{\beta}(\rho \vec{\alpha}))
+    \end{split}
+\end{equation}
+
+With $p = \rho c_s^2$ and $\delta_{\alpha \beta}$ the kronecker delta.
+
+\subsection{Non-ideal mixing}
 \label{section:lbm_non_ideal_mixing}
-
-Four primary techniques to model multicomponent or multiphase systems exist in the LBM literature. They are the Shan-Chen (SC) pseudopotential
-model, the free energy (FE) model, the color gradient (CG) model and the interface tracking (IT) model. All techniques are fundamentally different to one
-another in implementation and tradeoff various properties. Each one will be briefly reviewed before a comparing and contrasting their applicability
-to this system.
-
-The SC model introduces fluid interactions via a density-dependent force, enabling spontaneous phase separation 
-and interface formation without explicitly tracking the interface. It is simple to implement and computationally efficient. However the density
-dependence of the fluid interactions implies that the surface tension is controlled by the density of the fluids used and the strength parameter
-controlling interactions.
-
-The FE model derives from the implementation of a modified equilibrium distribution derived from a square gradient free energy functional. Similar to the
-SC model, the FE model enables spontaneous phase separation and interface formation without explicitly tracking the interface. The surface tension and
-interface width are explicitly defined from the bulk free energy, allowing for user defined surface tensions and interface widths. However in its multicomponent
-implementation, it cannot be used to simulate fluids with high density ratios.
-
-The CG model is defined with fluid components with color labels, followed by the application of a recoloring step to sharpen the interface. 
-\cite{liu_multiphase_2016} The recoloring step creates the surface tension present in phase separated multicomponent mixtures. This model
-provides fine control over the surface tension and narrow interface widths. However implementing the recoloring step is computationally complex 
-and requires tuning of the recoloring step to ensure numerical consistency.  
-% technique proposed by Latva-Kokko and Rothman is more commonly used for soft matter flows. \cite{liu_multiphase_2016}
-
-The IT model is defined using a level-set or front-tracking techniques coupled to LBM. This technique explicitly tracks the location of the
-interface by evolving a separate interface indicator. It offers the highest accuracy at capturing the interface. However it is computationally
-expensive and less suited to topological changes like coalescence.
-
-% A quick review of the Shan-Chen (SC) or 
-% pseudopotential model will be provided here from the perspective of a binary mixture. Additionally, the names and descriptions of 
-% other techniques will be described as well. The interparticle potential model or Shan-Chen model that adds a non-local density dependent force 
-% between two species, effectively modelling non-ideal mixing and recovering the Cahn-Hilliard equation. To alleviate the standard Shan-Chen implementations 
-% weaknesses of not being thermodynamically consistent and reducing the existence of spurious velocities, thermodynamically consistent equations of state
-% such as the Van der walls or Carnahan Starling equations of state have been implemented and compared to the Shan-Chen equation of state.
-
-% In addition to the Shan-Chen model, the color gradient model, free energy model and interface tracking technique all 
-% allow for simulations of various types of multiphase and/or multicomponent flows. The color gradient model proposed by Rothman and Keller and 
-% implemented by Gunstensen et al relies upon modelling two particle distributions. These represent a binary fluid mixture with the collision step 
-% able to recover the hydrodynamics and non-ideal mixing dynamics. The free energy model utilizes phase field theory and constructs a free energy 
-% functional to recover interfacial dynamics and effects in a thermodynamically consistent manner. Often, a square gradient free energy is used for 
-% simplicity and ease of implementation. The mean field theory The non-ideal mixing dynamics are 6
-
-Compared to other multicomponent methods, the SC model provides the
 
@@
 
-The particles are discretized on the lattice according to the method laid out in Ladd and Aidun 
-\cite{ladd_lattice-boltzmann_2001}. Nodes representing the particle are marked as solid nodes that replicate
+The particles are discretized on the lattice according to the method laid out in Ladd 1994 and Aidun 1998
+\cite{ladd_numerical_1994,aidun_direct_1998}. Nodes representing the particle are marked as solid nodes that replicate
 a no-slip boundary condition through a moving bounce-back boundary. This is implemented into the distribution function
@@
 
-\subsection{Anisotropic particles}
-\label{section:lbm_colloids_ellipsoids}
+\subsection{Particles near contact}
+\label{section:particles_near_contact}
 
@@
 
-$K_H$ is the force constant used to push particles apart. To correct for the anisotropic particles used in this work, 
+$K_H$ is the force constant used to push particles apart.
+
+\subsection{ellipsoidal_particles}
+\label{section:ellipsoidal_particles}
+
+To correct for the ellipsoidal particles used in this work, 
 the formulas presented in Eqs \ref{eq:lubrication} and \ref{eq:hertz} can be generalized using the route followed 
@@
 \begin{equation}
-    \mathbf{U_{ij}} = \frac{\mu_0 m_i m_j}{4\pi r_{ij}^{3}} \left[ \Hat{\mathbf{o_i}} \cdot \Hat{\mathbf{o_j}} - 
-    3(\Hat{\mathbf{o_i}} \cdot \Hat{\mathbf{r_{ij}}})(\Hat{\mathbf{o_j}} \cdot \Hat{\mathbf{r_{ij}}}) \right]
+    \mathbf{U_{ij}} = \frac{\mu_0 \vec{m}_i \vec{m}_j}{4\pi |r_{ij}|^{3}} \left[ \vec{o}_i \cdot \vec{o}_j - 
+    3(\vec{o}_i \cdot \vec{r}_{ij})(\vec{o}_j \cdot \vec{r}_{ij}) \right]
     \label{eq:magnet_potential}
@@
 Where $\mu_0 = 4\pi \cdot 10^{-7} \frac{H}{m}$,  $\Hat{\mathbf{o_i}}$ is the orientation unit vector of particle 
-$i$, $\Hat{\mathbf{r_{ij}}}$ is the distance vector between particles $i$ and $j$ and $m_i$ is the magnitude the 
+$i$, $\Hat{\vec{r}_{ij}}$ is the distance vector between particles $i$ and $j$ and $m_i$ is the magnitude the 
 magnetic dipole of particle $i$. From the potential, the force and torque of the dipole force between particles 
@@
 \begin{equation}
-    \mathbf{F}_{ij} = \frac{3 \mu_0}{4 \pi} [\frac{5(m_i \cdot \mathbf{r}_{ij})(m_j 
-    \cdot \mathbf{r}_{ij})}{|\mathbf{r}_{ij}|^7}\mathbf{r}_{ij} - \frac{(m_i \cdot m_{j})\mathbf{r}_{ij} + 
-    (m_i \cdot \mathbf{r}_{ij})m_i + (m_j \cdot \mathbf{r}_{ij})m_j }{|\mathbf{r}_{ij}|^5}]
+    \mathbf{F}_{ij} = \frac{3 \mu_0}{4 \pi} [\frac{5(\vec{m}_i \cdot \vec{r}_{ij} )(\vec{m}_j
+    \cdot \vec{r}_{ij})}{|\vec{r}_{ij}|^7}\vec{r}_{ij} - \frac{(\vec{m}_{i} \cdot \vec{m}_{j})\vec{r}_{ij} + 
+    (\vec{m}_{i} \cdot \vec{r}_{ij})\vec{m}_{i} + (\vec{m}_{j} \cdot \vec{r}_{ij})\vec{m}_{j} }{|\vec{r}_{ij}|^5}]
 \label{eq:dipole_magnetic_force}
@@
 \begin{equation}
-    \mathbf{T}_{ij} = \frac{\mu_0}{4 \pi}[ \frac{3(m_j \cdot \mathbf{r}_{ij})m_i \times \mathbf{r}_{ij} }
-    {|\mathbf{r}_{ij}|^5} - \frac{m_i \cdot m_j }{|\mathbf{r}_{ij}|^3} ]
+    \mathbf{T}_{ij} = \frac{\mu_0}{4 \pi}[ \frac{3(\vec{m}_{j} \cdot \vec{r}_{ij})m_i \times \vec{r}_{ij} }
+    {|\vec{r}_{ij}|^5} - \frac{\vec{m}_{i} \cdot \vec{m}_{j} }{|\vec{r}_{ij}|^3} ]
     \label{eq:dipole_magnetic_torque}
@@
 \begin{equation}
-    \mathbf{F_{j}} = (m_j \Hat{\mathbf{o_j}} \cdot \nabla B_i)
+    \mathbf{F_{j}} = \vec{m}_{j}(\vec{o}_{j} \cdot \nabla \vec{B}_{i})
     \label{eq:magnet_force}
@@
 \begin{equation}
-    \mathbf{\tau_j} = (m_j \Hat{\mathbf{o_j}} \times B_i)
+    \mathbf{\tau_j} = \vec{m}_{j}(\vec{o}_{j} \times \vec{B}_{i})
     \label{eq:magnet_torque}

### 2025-04-11 chapters/introduction_new.tex
Changes 1. Rearranged introduction, lit review and methods sections

@@
-When two partially miscible fluids are mixed, they tend to phase separate into distinct domains to minimize the thermodynamic penalty associated with interfacial formation. 
-To inhibit this process, stabilizers such as small-molecule surfactants, particles, or biopolymers are commonly introduced. Surfactants, for example, reduce the surface tension 
-between the dispersed and continuous phases, thereby lowering the interfacial energy and promoting the stability of emulsions. A familiar example is soap, which facilitates the 
-emulsification of dirt into droplets suspended in water through mechanical agitation.
-Without such additives, the dispersed phase tends to coalesce in order to reduce interfacial area. The effectiveness of stabilizers can be characterized through the Pieranski 
-model, $G_{ads} = \sigma A_{rm} (1 - \cos{\theta_c})^2$, where $G_{ads}$ is the free energy reduction upon particle adsorption, $\sigma$ is the surface tension between the two 
-fluids, and $\theta_c$ is the contact angle of the stabilizing particle. While surfactants and biopolymers reduce interfacial tension, particle stabilizers function by adsorbing 
-at the interface and effectively reducing the interfacial area between fluid domains. The free energy associated with the decrease in interfacial area $G_{ads}$ can be orders of magnitude
-larger than the thermal energy of the system $k_b T$ which makes the particle irreversibly adsorbed on the interface. \cite{ngai_particle-stabilized_2015}
+When two immiscible fluids are mixed, they phase separate into fluid domains to reduce the interfacial energy between them. This phenomena is driven by the free energy
+reduction as the interface area between both fluids decrease. To inhibit this process, stabilizers such as small-molecule surfactants, particles, or biopolymers are commonly introduced. 
+Surfactants, for example, reduce the surface tension between the dispersed and continuous phases, thereby lowering the interfacial energy and promoting the stability of emulsions. 
+A familiar example is soap, which facilitates the emulsification of dirt into droplets suspended in water through mechanical agitation.
+Without such additives, the dispersed phase tends to coalesce in order to reduce interfacial area. While surfactants and biopolymers reduce interfacial tension, particle stabilizers 
+function by adsorbing at the interface and effectively reducing the interfacial area between fluid domains. The free energy associated with the decrease in interfacial area 
+can be orders of magnitude larger than the thermal energy of the system $k_b T$ which makes the particle irreversibly adsorbed on the interface. \cite{ngai_particle-stabilized_2015}
 
-Compared to surfactant-stabilized emulsions, particle-stabilized emulsions (Pickering emulsions) exhibit enhanced resistance to coalescence and coarsening, prompting renewed interest 
-in their use across various applications. \cite{ngai_particle-stabilized_2015} 
-This resurgence is further driven by increasing environmental and toxicity concerns associated with small-molecule surfactants 
+Compared to surfactant-stabilized emulsions, particle-stabilized emulsions (Pickering emulsions) exhibit enhanced resistance to coalescence and coarsening
+due to the irreversibility of particle adsorption at the interface. \cite{ngai_particle-stabilized_2015} 
+Additionally, growing environmental and toxicity concerns associated with small-molecule surfactants have increased interest in the applications of particle-stabilized emulsions.
 \cite{kaczerewska_environmental_2020, lechuga_acute_2016}. In contrast, particle stabilizers lower toxicity and improved biocompatibility, in addition to 
@@
             Used with permission of Royal Society of Chemistry, from A non-equilibrium state diagram for liquid/fluid/particle 
-            mixtures, Velankar, 1, 11, 2015. Permission conveyed through Copyright Clearance Center, Inc}
+            mixtures, Velankar, 1, 11, 2015 under license number 1551968-1}
     \label{fig:state_diagram_particle_emulsions}
@@
 
-As illustrated in Figure~\ref{fig:state_diagram_particle_emulsions}, the formation of bijels typically requires a near-equal volume fraction of two immiscible fluids and neutrally wetting 
-particles.
+One microstructure of interest shown in Figure~\ref{fig:state_diagram_particle_emulsions} is the bicontinuous interfacially jammed emulsion gel (bijel). This unique microstructure was 
+first identified in 2005 by Stratford et al., who used a multicomponent Lattice Boltzmann method coupled with suspended particles to simulate the 
+dynamics of particle-stabilized emulsions under these conditions \cite{stratford_colloidal_2005}. Their simulations revealed that, following the onset of spinodal decomposition, particles 
+rapidly adsorb at the evolving fluid-fluid interface. When the available interfacial area becomes comparable to the total cross-sectional area of the particles, coarsening is arrested, 
+resulting in a jammed, tortuous, co-continuous morphology characteristic of bijels (see Figure~\ref{fig:bijel_coarsen}).
 
@@
 
-This unique microstructure was first identified in 2005 by Stratford et al., who used a multicomponent Lattice Boltzmann method coupled with suspended particles to simulate the 
-dynamics of particle-stabilized emulsions under these conditions \cite{stratford_colloidal_2005}. Their simulations revealed that, following the onset of spinodal decomposition, particles 
-rapidly adsorb at the evolving fluid-fluid interface. When the available interfacial area becomes comparable to the total cross-sectional area of the particles, coarsening is arrested, 
-resulting in a jammed, tortuous, co-continuous morphology characteristic of bijels (see Figure~\ref{fig:bijel_coarsen}).
-This computational discovery was experimentally realized in 2007 by Herzig et al., who used a 2,6-lutidine/water system stabilized with surface-modified silica particles \cite{herzig_bicontinuous_2007}.
+Bijel microstructures are of interest because their bicontinuous, interpenetrating networks enable tunable transport and separation properties. The computational discovery of the technique to 
+synthesize bijels was succeeded by the experimental synthesis of a bijel in 2007 by Herzig et al., who used a 2,6-lutidine/water system stabilized with surface-modified silica particles.
+\cite{herzig_bicontinuous_2007} 
 This binary fluid system exhibits a lower critical solution temperature (LCST) of 34.1\textdegree C and a critical composition at approximately 28\% lutidine by weight.
@@
 critical composition and heating it past the LCST, phase separation was thermally induced, a process known as Thermally Induced Phase Separation (TIPS). The system underwent coarsening until gelation 
-occurred, forming a bijel. Since then, a variety of small molecule, oligomeric, and polymeric systems have been developed using similar thermally induced methods 
+occurred, forming a bijel.
+Since this initial experimental synthesis, TIPS has been widely used in laboratory-scale studies to synthesize a variety of small molecule, oligomeric, and polymeric systems.
 \cite{tavacoli_novel_2011, lee_bicontinuous_2010, bai_dynamics_2015, ching_rapid_2021}.
+
+However, industrial applications require continuous, scalable fabrication techniques capable of generating application specific tailored microstructures. STrIPS has emerged as a promising solution 
+for this need. As illustrated in Figure~\ref{fig:strips}, STrIPS involves a ternary fluid system composed of two immiscible fluids 
+and a solvent. In the initial stage (Figure~\ref{fig:strips}a), a casting mixture is prepared. Phase separation is then triggered by flowing a co-solvent past the mixture to extract the solvent 
+(Figure~\ref{fig:strips}b). This solvent transfer must occur within the spinodal region of the ternary phase diagram to ensure spinodal decomposition. By adjusting flow rates of both the casting 
+mixture and the solvent removal stream, the resulting bijel morphology can be finely controlled.
+STrIPS has been successfully employed in applications ranging from battery electrode templating to drug
+delivery systems, liquid-in-liquid printing, and the creation of intrinsically polymerizable bijels for freestanding structures 
+\cite{garcia_scalable_2019, thorson_bijel-templated_2019, amirfattahi_fabrication_2024, ching_rapid_2021}. The method is flexible with respect to fluid choice, with 
+the only requirement being a well-characterized phase diagram that keeps the system within the spinodal regime throughout the solvent exchange process. Other techniques based on
+induced phase separation such as Vapor Induced Phase Separation(VIPS) and controlled coalescence of droplets to form bijels through shear (homogenization) have also been identified as techniques
+to synthesize bijels. \cite{wang_scalable_2020, huang_bicontinuous_2017}
 
@@
     \includegraphics[scale = 5]{figures/introduction/STrIPS.jpg}
-    \caption{STrIPS in action. Extrusion of the bijel casting mixture into a non-solvent bath, followed by removal of solvent from 
-             the casting mixture through diffusion. \cite{haase_continuous_2015}. Reproduced with permission from Wiley-VCH Verlag GmbH 
+    \caption{Extrusion of the bijel casting mixture into a non-solvent bath, followed by removal of solvent from 
+             the casting mixture through diffusion, demonstrating the working principal of STrIPS. \cite{haase_continuous_2015}. Reproduced with permission from Wiley-VCH Verlag GmbH 
              \& Co. KGaA from \textit{Continuous Fabrication of Hierarchical and Asymmetric Bijel Microparticles, Fibers, and Membranes by 
@@
 
-TIPS has been widely used in laboratory-scale studies to produce bijels in batch processes. However, industrial applications require continuous, scalable fabrication techniques capable of generating 
-tailored microstructures. STrIPS has emerged as a promising solution for this need. As illustrated in Figure~\ref{fig:strips}, STrIPS involves a ternary fluid system composed of two immiscible fluids 
-and a solvent. In the initial stage (Figure~\ref{fig:strips}a), a casting mixture is prepared. Phase separation is then triggered by flowing a co-solvent past the mixture to extract the solvent 
-(Figure~\ref{fig:strips}b). This solvent transfer must occur within the spinodal region of the ternary phase diagram to ensure spinodal decomposition. By adjusting flow rates of both the casting 
-mixture and the solvent removal stream, the resulting bijel morphology can be finely controlled.
-STrIPS has been successfully employed in applications ranging from battery electrode templating to drug
-delivery systems, liquid-in-liquid printing, and the creation of intrinsically polymerizable bijels for freestanding structures 
-\cite{garcia_scalable_2019, thorson_bijel-templated_2019, amirfattahi_fabrication_2024, ching_rapid_2021}. The method is flexible with respect to fluid choice, with 
-the only requirement being a well-characterized phase diagram that keeps the system within the spinodal regime throughout the solvent exchange process.
-
-Vapor-induced phase separation (VIPS) offers another solvent-removal-based technique for bijel synthesis \cite{wang_scalable_2020}.
+% Vapor-induced phase separation (VIPS) offers another solvent-removal-based technique for bijel synthesis \cite{wang_scalable_2020}.
 In this approach, a quaternary mixture containing particles, a solvent,
-and two partially miscible liquids is prepared.
+% and two partially miscible liquids is prepared.
 Careful selection of component identities and ratios ensures that evaporation of the solvent drives the system through its critical point, inducing spinodal
-decomposition.
+% decomposition.
 A representative system uses water and hexanediol diacrylate, solvated by ethanol.
@@
 VIPS is compatible
-with spray or blade coating techniques but is limited by the temperature dependence of surface tension, restricting solvent options to those that vaporize readily at ambient conditions.
+% with spray or blade coating techniques but is limited by the temperature dependence of surface tension, restricting solvent options to those that vaporize readily at ambient conditions.
 
-In contrast to methods relying on spinodal decomposition, homogenization uses shear to coalesce domains of immiscible fluids, resulting in a bicontinuous structure that mimics a bijel 
-\cite{huang_bicontinuous_2017, cai_bijels_2017}. This approach is particularly effective for nanoparticles under 50 nm and supports various particle shapes. Shear promotes limited coalescence 
-of droplets; as coarsening proceeds, particles adsorb at the interface. Once the interfacial area is saturated with particles, jamming occurs, locking the microstructure in place. Tuning can be 
-achieved by modifying particle contact angles (e.g., via surfactants) or adjusting the viscosity of the fluid phases using additives like oligomers.
+% In contrast to methods relying on spinodal decomposition, homogenization uses shear to coalesce domains of immiscible fluids, resulting in a bicontinuous structure that mimics a bijel 
+% \cite{huang_bicontinuous_2017, cai_bijels_2017}. This approach is particularly effective for nanoparticles under 50 nm and supports various particle shapes. Shear promotes limited coalescence 
+% of droplets; as coarsening proceeds, particles adsorb at the interface. Once the interfacial area is saturated with particles, jamming occurs, locking the microstructure in place. Tuning can be 
+% achieved by modifying particle contact angles (e.g., via surfactants) or adjusting the viscosity of the fluid phases using additives like oligomers.
+% Despite these advances, a persistent limitation is that bijel microstructure remains tightly coupled to the composition of the casting mixture and the kinetics of phase separation.
+Achieving controlled
+% morphology often requires fine-tuning of fluid concentrations or external conditions, which may not be feasible for all applications \cite{haase_continuous_2015, reeves_particle-size_2015}.
+
 Despite these advances, a persistent limitation is that bijel microstructure remains tightly coupled to the composition of the casting mixture and the kinetics of phase separation.
 Achieving controlled
-morphology often requires fine-tuning of fluid concentrations or external conditions, which may not be feasible for all applications \cite{haase_continuous_2015, reeves_particle-size_2015}.
-
-Once formed, the microstructure of bijels is typically fixed and cannot be modified post-fabrication. However, in many of the proposed applications such as water filtration membranes or drug delivery 
-platforms, the morphology of the material plays a critical role in determining key functional properties, including back pressure, species selectivity, and transport dynamics 
-\cite{vanoli_bijels_2022, thorson_bijel-templated_2019}. The ability to dynamically tune these structural features would significantly expand the versatility and 
-functionality of bijel-based systems.
+morphology often requires fine-tuning of fluid concentrations or external conditions, which may not be feasible for all applications. \cite{haase_continuous_2015, reeves_particle-size_2015}
+The ability to tune these structural features would significantly expand the versatility and functionality of bijel-based systems.
+In many of the proposed applications such as water filtration membranes or drug delivery 
+platforms, the morphology of the material plays a critical role in determining key functional properties, including back pressure, species selectivity, and transport dynamics.
+\cite{vanoli_bijels_2022, thorson_bijel-templated_2019, khan_nanostructured_2022}
 
@@
 responsive particles have been used to manipulate, deform, and control the coalescence of droplets, as illustrated in Figure~\ref{fig:magnetophoresis_droplet}. Magnetic 
-fields offer a non-invasive and targeted method for manipulating the behavior of particles making them of particular interest. 
+fields offer a targeted method for manipulating the behavior of particles making them of particular interest. 
 However the application of such dynamic control strategies to bijels remains relatively underexplored. Prior studies involving magnetic fields applied to bijels stabilized with spherical particles 
@@
 
-Anisotropic particles exhibit shape-dependent interfacial behavior due to their ability to deform fluid interfaces while maintaining zero mean curvature, satisfying the Young-Laplace equation 
+Anisotropic particles exhibit shape-dependent interfacial behavior due to their ability to deform fluid interfaces while maintaining zero mean curvature, as seen in 
 (Figure~\ref{fig:anisotropic_particle_interface}) \cite{loudet_capillary_2005, cheng_shape-anisotropic_2013}. These deformations generate multipolar capillary interactions, which can be harnessed 
@@
 
-The dynamics of ellipsoid-stabilized bijels are distinct from their spherical counterparts, displaying two characteristic timescales. Initially, particles adsorb and align with the interface, 
+The dynamics of ellipsoid-stabilized bijels display additional dynamics and droplet bridging, not observed in their spherical counterparts.
+\cite{gunther_timescales_2014, witt_bijel_2013} Initially, particles adsorb and align with the interface,
 followed by a slower reorganization phase driven by capillary interactions between particles \cite{gunther_timescales_2014}.
@@
 
-Introducing magnetic responsiveness into anisotropic particles offers a non-invasive strategy for controlling their behavior at fluid interfaces.
-Such particles can be fabricated via surface deposition of
+Introducing magnetic responsiveness into anisotropic particles offers a strategy for controlling their behavior at fluid interfaces. Such particles can be fabricated via surface deposition of 
 magnetic materials or synthesized as core-shell structures with magnetic cores and non-magnetic shells \cite{fei_magneto-capillary_2020, nakayama_stimuli-responsive_2018}.
 The interplay between magnetic
-torque and capillary anchoring governs particle orientation in response to external magnetic fields.
+and capillary interactions governs particle orientation in response to external magnetic fields.
 According to Bresme-Faraudo theory, a neutrally wetting ellipsoidal particle at an interface experiences
-competing forces: the magnetic field seeks to reorient the particl's magnetic dipole moment, while capillary forces resist deformation away from the interface plane 
+competing forces: the magnetic field seeks to reorient the particle's magnetic dipole moment, while capillary forces resist deformation away from the interface plane 
 \cite{bresme_orientational_2007, davies_interface_2014}.
@@
 The equilibrium and metastable orientations adopted by anisotropic particles are functions of particle aspect ratio, surface wettability, and interfacial tension 
-\cite{morgan_understanding_2013, newton_influence_2014}.
-Studies on superellipsoidal hematite particles at oil-water interfaces demonstrate multiple stable and metastable states, where particles align
-their major or minor axes relative to the interface depending on their geometry and energy landscape. Lattice Boltzmann simulations support these observations, showing how shape influences immersion 
-depth and contact angle, which in turn affect orientation stability. Magnetic fields can perturb these equilibria by exerting torque on the particles, reorienting them along the field direction. 
+\cite{morgan_understanding_2013, newton_influence_2014}. Studies on cuboidal hematite particles at oil-water interfaces demonstrate multiple stable and metastable states, where particles align 
+their major or minor axes relative to the interface depending on their geometry and energy landscape. Lattice Boltzmann simulations support these observations, showing how particle shape influences 
+and contact angle affect the energy required to detach a particle from an interface. \cite{davies_detachment_2014}
+Magnetic fields can perturb these equilibria by exerting torque on the particles, reorienting them along the field direction. 
 Experiments confirm that magnetic ellipsoids can be reconfigured at the interface, enabling controlled switching between metastable and stable configurations.
@@
 The final arrangement is influenced by particle concentration, field strength, and local capillary geometry.
-In Pickering emulsions, these effects enable magnetically triggered droplet deformation, coalescence,
-and motility, demonstrating the potential for real-time, field-controlled manipulation of interfacial structures \cite{melle_pickering_2005, tham_magnetophoresis_2021}.
 
-Magnetically responsive Pickering emulsions offer an additional layer of tunability.
-When a magnetic field is applied, particles reorient and organize at the interface, significantly altering the material's
-rheological response \cite{qiao_magnetorheological_2012, melle_pickering_2005}.
-This field-induced ordering can lead to reversible transitions between fluid-like and gel-like states, enabling on-demand control
-over flow properties.
-Such behavior is particularly advantageous for applications in enhanced oil recovery, drug delivery, and soft robotics, where adaptable and reconfigurable materials are essential
-\cite{tham_magnetophoresis_2021}.
+These effects enable magnetic field driven droplet deformation, coalescence and 
+motility of Pickering Emulsions, demonstrating the potential for real-time, field-controlled manipulation of interfacial structures \cite{melle_pickering_2005, tham_magnetophoresis_2021}.
+The applied field can also alter the materials rheological response as the stabilizing particles reorient and reorganize at the interface
+enabling reversible transitions between fluid-like and gel-like states. \cite{qiao_magnetorheological_2012, melle_pickering_2005}. 
+Such behavior is particularly advantageous for applications in enhanced oil recovery, drug delivery, and soft robotics, where adaptable and 
+reconfigurable materials are essential \cite{tham_magnetophoresis_2021}.
 
 This dissertation investigates the potential of magnetically responsive ellipsoidal particles to enable stimuli-responsive control over bijel microstructure.
-Specifically, it examines whether magnetic fields
-applied during or after bijel formation can induce meaningful structural changes, and how these changes, in turn, influence the rheological behavior of the resulting material.
-The central hypothesis is that
-particle reorientation under magnetic fields alters interfacial packing, ultimately reshaping domain morphology. 
-Moreover, Carmack and Millet identified that the formation of particle chains was shown to play a critical role in phase separation dynamics.
-These chains acted as nucleation sites, guiding the development of
-fluid domains and influencing average channel diameter and particle localization at interfaces.
-These findings suggest that external fields, particularly when coupled with anisotropic particles, offer a
-promising route toward responsive and reconfigurable bijel architectures.
-The remainder of this dissertation is organized as follows.
-Chapter 2 details the physics being modeled and the simulation methods used to model these physics, including the Lattice Boltzmann approach
+Specifically, it examines whether magnetic
+fields applied during or after bijel formation can induce meaningful structural changes, and how these changes, in turn, influence the rheological behavior of the resulting material.
+Upon application of
+a constant magnetic field, a torque will be imparted which will rotate the particles at the interface towards the direction of the magnetic field. This reorientation is hypothesized to impart
+structural changes in the bijel. Carmack and Millet identified that the formation of particle chains was shown to play a critical role in phase separation dynamics. These chains acted as 
+nucleation sites, guiding the development of fluid domains and influencing average channel diameter and particle localization at interfaces. These findings suggest that external fields, 
+particularly when coupled with anisotropic particles, offer a promising route toward responsive and reconfigurable bijel architectures.
+
+The remainder of this dissertation is organized as follows. Chapter 2 details the physical model and the simulation methods used to solve these physics, including the Lattice Boltzmann approach 
 and magnetic dipole modeling. Chapter 3 investigates the effects of magnetic fields applied during bijel formation, analyzing their influence on domain structure and particle orientation. 

### 2025-04-11 chapters/lit_review_new.tex
Changes 1. Rearranged introduction, lit review and methods sections

@@
-\section{Solid particles at fluid interfaces}
-
-This strong attachment energy makes particles highly effective at stabilizing emulsions by becoming irreversibly trapped at fluid-fluid interfaces. 
-\cite{ngai_particle-stabilized_2015}Once adsorbed, these 
-particles reduce interfacial tension and act as physical barriers that prevent the coalescence of droplets, thereby enhancing emulsion stability. Unlike molecular surfactants, 
-which are dynamic and can desorb under certain conditions, colloidal particles remain anchored at the interface due to the significant energy required to detach them. 
-\cite{ngai_particle-stabilized_2015}This mechanism 
-is especially useful in systems such as Pickering emulsions, where the interfacial coverage and wettability of the particles determine the type and stability of the emulsion formed. 
-\cite{ngai_particle-stabilized_2015,velankar_non-equilibrium_2015}
-As such, understanding particle behavior at interfaces is essential for controlling the structure and longevity of particle-stabilized systems. \cite{ngai_particle-stabilized_2015}
-For particles that are smooth and simple and at an interface of oil and water, the attachment energy at the fluid interface can be calculated from a force 
-balance between the force imparted from the particle on each fluid and the fluids between one another, known as the Young-Dupre equation.
-
-\begin{equation}
-    \cos{\theta_c} = \frac{\sigma_{po} - \sigma_{pw}}{\sigma_{ow}}
-\end{equation}
-
-Where $\theta_c$ is the contact angle, $\sigma_{po}$ is the surface tension between particle and oil, $\sigma_{pw}$ is the surface tension between particle and water and
-$\sigma_{ow}$ is the surface tension between oil and water. The particle is considered to be preferentially wet by water or hydrophilic if $\theta_c < 90 ^{\circ}$ or 
-hydrophobic if $\theta_c > 90 ^{\circ}$. The particle is said to be neutrally wetting if $\theta_c = 90 ^{\circ}$.
-
-\begin{figure}
-    \centering
-    \includegraphics[scale = 0.5]{../figures/literature_review/particle_at_interface.png }
-    \caption{Particle schematic at an interface demonstrating the various quantities of interest. Reprinted Figure 2.1 with permission from
-             Particle-Stabilized Emulsions and Colloids: Formation and Applications; Ngai, T., Bon, S. A. F., Eds.; RSC soft matter series; 
-             Royal Society of Chemistry, RSC Publishing Cambridge, 2015}
-    \label{fig:pieranski_model}
-\end{figure}
-
-The energy of the system before and after particle adsorption is different and can be characterized for a simple system with parameters shown in Figure \ref{fig:pieranski_model},
-
-\begin{equation}
-    \Delta E_{IW} = E_I - E_w
-\end{equation}
-
-Where $\Delta E_{I}$ is the energy of the system when the particle is in the interface and $\Delta E_W$ is the energy of the system when the particle is completely in the water phase.
-We define $\Delta E_{I}$ as
-
-\begin{equation}
-    E_I = A_w \sigma_{pw} + A_o\sigma_{po} + A_{I_1}\sigma_{ow} + V_w P_w + V_o P_o
-\end{equation}
-
-Where $A_w$ and $A_o$ are the surface areas of the particle in the water and oil phases respectively, $V_w$ and $V_o$ are the volumes of water and oil phases respectively and 
-$P_w$ and $P_o$ are the pressures of water and oil phases respectively. $A_{I_1}$ is the area of the interface with the particle. 
-A similar equation can be written for the energy of the water phase, $E_w$
-
-\begin{equation}
-    E_w = (A_w + A_o)\sigma_{pw} + A_{I_2}\sigma_{ow} + (V_w + V_o)P_w
-\end{equation}
-
-$A_{I_2}$ is the area of the interface without the particle. The change in the interface energy upon adsorption of the particle can be computed to obtain
-
-\begin{equation}
-    \Delta E_{IW} = A_o(\sigma_{po} - \sigma_{pw}) - A_p\sigma_{ow} + V_o(P_o - P_w)
-\end{equation}
-
-Substituting the Young-Laplace law for a spherical droplet, $P_w - P_o = \frac{2\sigma_{ow}}{R_d}$ where $R_d$ is the droplet size, for $(P_o - P_w)$ and the Young-Dupre contact angle
-expression, the following is obtained
-
-\begin{equation}
-    \Delta E_{IW} = \sigma_{ow}(A_o\cos{\theta_c} - A_p - \frac{2 V_o}{R_d})
-\end{equation}
-
-A similar construction can be done for the oil phase to obtain
-
-\begin{equation}
-    \Delta E_{IW} = -\sigma_{ow}(A_w\cos{\theta_c} + A_p - \frac{2 V_o}{R_d})
-\end{equation}
-
-After making appropriate geometrical substitutions for $V_o$ and $A_p$, the Piersanski model is recovered,
-
-\begin{equation}
-    \Delta E_{ads} = \pi r^2 \sigma_{ow} (1 - |\cos{\theta_c}|)^2
-\end{equation}
-
-From this expression, the adsorption energy can be seen to depend on the contact angle, surface tension and contact area of the particles. This indicates that larger, neutrally wetting
-particles adsorbing onto interfaces with high surface tension have a high driving force for adsorption. \cite{ngai_particle-stabilized_2015,reeves_particle-size_2015} This adsorption process 
-can be orders of magnitude larger than the thermal energy of the system, calculated as $k_b T$ where $T$ is the temperature of the system and $k_b$ is the Boltzmann constant. This results in 
-irreversible adsorption of particles at interfaces. \cite{binks_pickering_2001}
-
-In addition to the adsorption of particles on the interface, the contact angle of the particles determine the dispersed phase of an emulsion and its microstructure. 
-\cite{velankar_non-equilibrium_2015}
-Hydrophillic particles tend to prefer to form oil in water emulsions while hydrophobic particles prefer to form water in oil emulsions. \cite{ngai_particle-stabilized_2015}
-This occurs as the particles preferentially wet one phase over another, causing the interface to bend as the emulsion forms. Neutrally wetting particles are preferred in the formation of 
-bijels as no preferential curvature is imparted onto the bijels, fulfilling one of the requirements of a minimal surface in that the mean curvature must be zero. \cite{jinnai_interfacial_2001}
-
 \section{Phase separation}
@@
 
-The thermodynamic equilibrium of a binary fluid mixture can be described by its Gibbs free energy, given as \(\Delta G = \Delta H - T \Delta S\), where \(\Delta H\) is the enthalpy change, 
+The thermodynamic equilibrium of a binary fluid mixture can be described by its Gibbs free energy, given as $G = \Delta H - T \Delta S$, where \(\Delta H\) is the enthalpy change, 
 \(T\) is temperature, and \(\Delta S\) is the entropy change. The onset of phase separation occurs at the binodal line, defined where \(\frac{dG}{dx} = 0\), with \(x\) representing the composition. 
@@
 balance between the bulk free energy gain from phase separation and the interfacial energy penalty, expressed as \(\Delta G = \frac{4}{3}\pi r^3 \Delta g_v + 4 \pi r^2 \sigma\), where \(r\) is 
-the nucleus radius, \(\Delta g_v\) is the free energy change per unit volume, and \(\sigma\) is the interfacial tension. 
-\cite{thanh_mechanisms_2014}
-Nuclei that exceed the critical radius \(r_c = \frac{2\sigma}{|\Delta g_v|}\) will grow, driving the system toward phase separation via nucleation and growth. \cite{thanh_mechanisms_2014}
+the nucleus radius, \(\Delta g_v\) is the free energy change per unit volume, and \(\sigma\) is the interfacial tension \cite{thanh_mechanisms_2014}. 
+Nuclei that exceed the critical radius \(r_c = \frac{2\sigma}{|\Delta g_v|}\) will grow, driving the system toward phase separation via nucleation and growth \cite{thanh_mechanisms_2014}. 
 This transformation process is commonly modeled by the Avrami equation, \(Y = 1 - \exp(-K t^n)\), where \(Y\) is the 
-transformed fraction, \(K\) is a rate constant incorporating nucleation and growth kinetics, and \(n\) is the Avrami exponent, which reflects the dimensionality and mechanism of the transformation.
-\cite{avrami_kinetics_1939}
+transformed fraction, \(K\) is a rate constant incorporating nucleation and growth kinetics, and \(n\) is the Avrami exponent, which reflects the dimensionality and mechanism of the transformation
+\cite{avrami_kinetics_1939} .
 
-At the binodal, the system is still metastable, meaning that unless perturbations are introduced to form nuclei, the mixture remains homogeneous. \cite{thanh_mechanisms_2014}
-However, a deeper quench into the two-phase region leads to the spinodal line, defined by the stability criterion \(\frac{d^2G}{dx^2} = 0\). \cite{cahn_free_1958}
+At the binodal, the system is still metastable, meaning that unless perturbations are introduced to form nuclei, the mixture remains homogeneous \cite{thanh_mechanisms_2014}.
+However, a deeper quench into the two-phase region leads to the spinodal line, defined by the stability criterion \(\frac{d^2G}{dx^2} = 0\) \cite{cahn_free_1958}. 
 Within this region, the system is unstable to even infinitesimal composition fluctuations, and phase 
 separation proceeds spontaneously without the need for nucleation. This process, known as spinodal decomposition, is characterized by the continuous and simultaneous growth of interconnected 
-domains of both phases. \cite{cahn_free_1958} Unlike nucleation and growth, which relies on localized events, spinodal decomposition 
+domains of both phases \cite{cahn_free_1958}. Unlike nucleation and growth, which relies on localized events, spinodal decomposition 
 results in a bicontinuous structure driven by the system's attempt to minimize 
-free energy through composition modulation. \cite{cahn_free_1958} The dynamics of spinodal decomposition were characterized by Cahn and Hilliard. \cite{cahn_free_1958} 
+free energy through composition modulation \cite{cahn_free_1958}. The dynamics of spinodal decomposition were characterized by Cahn and Hilliard \cite{cahn_free_1958} . 
 We first begin by defining the free energy of a regular solution, known as the bulk free energy.
@@
 
+\section{Solid particles at fluid interfaces}
+
+When micron sized particles are adsorbed by interfaces the attachment energy is large enough that they can become irreversibly trapped at fluid-fluid interfaces \cite{ngai_particle-stabilized_2015}. 
+Once adsorbed, these 
+particles reduce interfacial tension and act as physical barriers that prevent the coalescence of droplets, thereby making them highly effective emulsion stabilizers. Unlike molecular surfactants, 
+which are dynamic and can desorb under certain conditions, colloidal particles remain adsorbed at the interface due to the significant energy required to detach them \cite{ngai_particle-stabilized_2015}.
+This mechanism 
+is especially useful in systems such as Pickering emulsions, where the interfacial coverage and wettability of the particles determine the type and stability of the emulsion formed 
+\cite{ngai_particle-stabilized_2015,velankar_non-equilibrium_2015}.
+As such, understanding particle behavior at interfaces is essential for controlling the structure and longevity of particle-stabilized systems \cite{ngai_particle-stabilized_2015}. 
+For particles that are smooth and simple and at an interface of oil and water, the attachment energy at the fluid interface can be calculated the Pieranski model, 
+$E_{ads} = \sigma A_{rm} (1 - \cos{\theta_c})^2$, where $E_{ads}$ is the free energy reduction upon particle adsorption, $\sigma$ is the surface tension between the two 
+fluids, and $\theta_c$ is the contact angle of the stabilizing particle.
+
+This expression is derived from an energy balance between the interactions between the interface and the 
+fluid phases, with a schematic shown in Figure \ref{fig:pieranski_model},
+
+\begin{figure}
+    \centering
+    \includegraphics[scale = 0.5]{../figures/literature_review/particle_at_interface.png }
+    \caption{Particle schematic at an interface demonstrating the various quantities of interest. Reprinted Figure 2.1 from
+             Particle-Stabilized Emulsions and Colloids: Formation and Applications; Ngai, T., Bon, S. A. F., Eds.; RSC soft matter series; 
+             with permission Royal Society of Chemistry, RSC Publishing Cambridge, 2015 under license number 1597404-1}
+    \label{fig:pieranski_model}
+\end{figure}
+
+From the Pieranski model, the adsorption energy can be seen to depend on the contact angle, surface tension and contact area of the particles. This indicates that larger, neutrally wetting
+particles adsorbing onto interfaces with high surface tension have a high driving force for adsorption. \cite{ngai_particle-stabilized_2015,reeves_particle-size_2015} This adsorption process 
+can be orders of magnitude larger than the thermal energy of the system, calculated as $k_b T$ where $T$ is the temperature of the system and $k_b$ is the Boltzmann constant. This results in 
+irreversible adsorption of particles at interfaces \cite{binks_pickering_2001}.
+
+In addition to the adsorption of particles on the interface, the contact angle of the particles determine the dispersed phase of an emulsion and its microstructure through the
+Bancroft rule \cite{velankar_non-equilibrium_2015,ngai_particle-stabilized_2015}. 
+Hydrophillic particles tend to prefer to form oil in water emulsions while hydrophobic particles prefer to form water in oil emulsions \cite{ngai_particle-stabilized_2015}.
+This occurs as the particles preferentially wet one phase over another, causing the interface to bend as the emulsion forms. Neutrally wetting particles are preferred in the formation of 
+bijels as no preferential curvature is imparted onto the bijels, fulfilling one of the requirements of a minimal surface in that the mean curvature must be zero \cite{jinnai_interfacial_2001}.
+
+% from a force 
+% balance between the force imparted from the particle on each fluid and the fluids between one another, known as the Young-Dupre equation.
+
+% \begin{equation}
+%     \cos{\theta_c} = \frac{\sigma_{po} - \sigma_{pw}}{\sigma_{ow}}
+% \end{equation}
+
+% Where $\theta_c$ is the contact angle, $\sigma_{po}$ is the surface tension between particle and oil, $\sigma_{pw}$ is the surface tension between particle and water and
+% $\sigma_{ow}$ is the surface tension between oil and water. The particle is considered to be preferentially wet by water or hydrophilic if $\theta_c < 90 ^{\circ}$ or 
+% hydrophobic if $\theta_c > 90 ^{\circ}$. The particle is said to be neutrally wetting if $\theta_c = 90 ^{\circ}$.
+
+% \begin{figure}
+%     \centering
+%     \includegraphics[scale = 0.5]{../figures/literature_review/particle_at_interface.png }
+%     \caption{Particle schematic at an interface demonstrating the various quantities of interest. Reprinted Figure 2.1 from
+%              Particle-Stabilized Emulsions and Colloids: Formation and Applications; Ngai, T., Bon, S. A. F., Eds.; RSC soft matter series; 
+%              with permission Royal Society of Chemistry, RSC Publishing Cambridge, 2015 under license number 1597404-1}
+%     \label{fig:pieranski_model}
+% \end{figure}
+
+% The energy of the system before and after particle adsorption is different and can be characterized for a simple system with parameters shown in Figure \ref{fig:pieranski_model},
+
+% \begin{equation}
+%     \Delta E_{IW} = E_I - E_w
+% \end{equation}
+
+% Where $\Delta E_{I}$ is the energy of the system when the particle is in the interface and $\Delta E_W$ is the energy of the system when the particle is completely in the water phase.
+% We define $\Delta E_{I}$ as
+
+% \begin{equation}
+%     E_I = A_w \sigma_{pw} + A_o\sigma_{po} + A_{I_1}\sigma_{ow} + V_w P_w + V_o P_o
+% \end{equation}
+
+% Where $A_w$ and $A_o$ are the surface areas of the particle in the water and oil phases respectively, $V_w$ and $V_o$ are the volumes of water and oil phases respectively and 
+% $P_w$ and $P_o$ are the pressures of water and oil phases respectively. $A_{I_1}$ is the area of the interface with the particle. 
+% A similar equation can be written for the energy of the water phase, $E_w$
+
+% \begin{equation}
+%     E_w = (A_w + A_o)\sigma_{pw} + A_{I_2}\sigma_{ow} + (V_w + V_o)P_w
+% \end{equation}
+
+% $A_{I_2}$ is the area of the interface without the particle. The change in the interface energy upon adsorption of the particle can be computed to obtain
+
+% \begin{equation}
+%     \Delta E_{IW} = A_o(\sigma_{po} - \sigma_{pw}) - A_p\sigma_{ow} + V_o(P_o - P_w)
+% \end{equation}
+
+% Substituting the Young-Laplace law for a spherical droplet, $P_w - P_o = \frac{2\sigma_{ow}}{R_d}$ where $R_d$ is the droplet size, for $(P_o - P_w)$ and the Young-Dupre contact angle
+% expression, the following is obtained
+
+% \begin{equation}
+%     \Delta E_{IW} = \sigma_{ow}(A_o\cos{\theta_c} - A_p - \frac{2 V_o}{R_d})
+% \end{equation}
+
+% A similar construction can be done for the oil phase to obtain
+
+% \begin{equation}
+%     \Delta E_{IW} = -\sigma_{ow}(A_w\cos{\theta_c} + A_p - \frac{2 V_o}{R_d})
+% \end{equation}
+
+% After making appropriate geometrical substitutions for $V_o$ and $A_p$, the Piersanski model is recovered,
+
+% \begin{equation}
+%     \Delta E_{ads} = \pi r^2 \sigma_{ow} (1 - |\cos{\theta_c}|)^2
+% \end{equation}
+
+% From this expression, the adsorption energy can be seen to depend on the contact angle, surface tension and contact area of the particles. This indicates that larger, neutrally wetting
+% particles adsorbing onto interfaces with high surface tension have a high driving force for adsorption. \cite{ngai_particle-stabilized_2015,reeves_particle-size_2015} This adsorption process 
+% can be orders of magnitude larger than the thermal energy of the system, calculated as $k_b T$ where $T$ is the temperature of the system and $k_b$ is the Boltzmann constant. This results in 
+% irreversible adsorption of particles at interfaces. \cite{binks_pickering_2001}
+
+% In addition to the adsorption of particles on the interface, the contact angle of the particles determine the dispersed phase of an emulsion and its microstructure. 
+% \cite{velankar_non-equilibrium_2015}
+% Hydrophillic particles tend to prefer to form oil in water emulsions while hydrophobic particles prefer to form water in oil emulsions. \cite{ngai_particle-stabilized_2015}
+% This occurs as the particles preferentially wet one phase over another, causing the interface to bend as the emulsion forms. Neutrally wetting particles are preferred in the formation of 
+% bijels as no preferential curvature is imparted onto the bijels, fulfilling one of the requirements of a minimal surface in that the mean curvature must be zero. \cite{jinnai_interfacial_2001}
+
 \section{Anisotropic particles}
 
-As the library of available particle shapes continues to grow, it becomes increasingly important to understand how these anisotropic particles behave at fluid interfaces.
-\cite{wu_recent_2016, cavallaro_curvature-driven_2011}
+As the library of available particle shapes continues to grow, it becomes increasingly important to understand how these anisotropic particles behave at fluid interfaces
+\cite{wu_recent_2016, cavallaro_curvature-driven_2011}.
 Unlike spherical particles, anisotropic particles introduce directional interactions and complex rotational dynamics which can significantly 
-influence interfacial assembly and emulsion stability. \cite{read_dimerization_2020, davies_dipolar_2015,morgan_understanding_2013}
+influence interfacial assembly and emulsion stability \cite{read_dimerization_2020, davies_dipolar_2015,morgan_understanding_2013}. 
 Their shape can dictate not only their orientation at the interface but also how they interact, and jam, 
-ultimately affecting the structure and mechanical properties of the resulting material. \cite{hijnen_bijels_2015}
-This is relevant for systems like bijels, where the precise arrangement of particles at the interface affects how the bijel james in place, generating new timescales or 
-interfacial phenomena not characterized in bijels made with spheres. \cite{gunther_timescales_2014,hijnen_bijels_2015}
+ultimately affecting the structure and mechanical properties of the resulting material \cite{hijnen_bijels_2015}.
+This is relevant for systems like bijels, where the precise arrangement of particles at the interface affects how the bijel jams in place, generating new timescales or 
+capillary bridging not characterized in bijels made with spheres \cite{gunther_timescales_2014,hijnen_bijels_2015,witt_bijel_2013}.
 
@@
 particles distort the surrounding interface in order to maintain a mean curvature of zero, in accordance with the Young-Laplace equation. This distortion creates curvature gradients around the 
-particle that interact with nearby particles or features on the interface, giving rise to anisotropic capillary forces. \cite{loudet_capillary_2005, cheng_shape-anisotropic_2013}. 
+particle that interact with nearby particles or features on the interface, giving rise to anisotropic capillary forces \cite{loudet_capillary_2005, cheng_shape-anisotropic_2013}. 
 Computational simulations further support this complexity, showing that ellipsoidal particles can adopt a variety of metastable orientations 
@@
 Cavallaro and co-workers identified. They showed how curvature gradients created at the edges of a 
-square rod caused directed assembly of cylinders, with the driving force strong enough to overcome gravity. \cite{cavallaro_curvature-driven_2011} Other works have introduced how these features are 
-particle shape dependent with greater control over the curvature gradient providing a means to control particle self assembly. \cite{read_dimerization_2020, sharifi-mood_curvature_2015} Botto et al. 
-identified that ellipsoidal particles prefer to arrange side to side state while cylinders prefer to arrange tip to tip with the particle geometric smoothness playing a role in this preference.
-\cite{botto_capillary_2012} These differences in particle arrangement could open up new possibilities for tailoring interfacial assemblies and the subsequent differences in microstructure obtained in
-a bijel.
+square rod caused directed assembly of cylinders, with the driving force strong enough to overcome gravity \cite{cavallaro_curvature-driven_2011}. Other works have introduced how these features are 
+particle shape dependent with greater control over the curvature gradient providing a means to control particle self assembly \cite{read_dimerization_2020, sharifi-mood_curvature_2015}.
+Earlier work in the literature identified that ellipsoidal particles prefer to arrange side to side state while cylinders prefer to arrange tip to tip with the particle geometric smoothness playing 
+a role in this preference \cite{botto_capillary_2012}. These differences in particle arrangement could open up new possibilities for tailoring interfacial assemblies and the subsequent differences 
+in microstructure obtained in a bijel.
 
-Ellipsoidal particles have been used as stabilizers in bijels, resulting in bijels that have smaller domains than those made with spherical particles at the same volume fraction.
-This was identified to arise
-from the greater surface area to volume ratio of ellipsoidal particles compared to spherical particles. \cite{gunther_timescales_2014} The evolution of the microstructure is also distinct to bijels 
-stabilized with spheres, demonstrating two timescales at early and later timesteps.
-\cite{gunther_timescales_2014} The short timescale is during formation of the bijel, when particles are adsorbed onto the
-interface and rotate to align with the interface. At longer timescales, capillary interactions between particles lead to reordering of particles at the interface, leading to a different interfacial 
-configuration and microstructure. \cite{gunther_timescales_2014}
+Ellipsoidal particles have been used as stabilizers in bijels, resulting in bijels that have smaller domains than those made with spherical particles at the same volume fraction. This was identified 
+to arise from the greater surface area to volume ratio of ellipsoidal particles compared to spherical particles \cite{gunther_timescales_2014}. The evolution of the microstructure is also distinct 
+to bijels stabilized with spheres, demonstrating two timescales at early and later timesteps \cite{gunther_timescales_2014}. The short timescale is during formation of the bijel, when particles 
+are adsorbed onto the interface and rotate to align with the interface. At longer timescales, capillary interactions between particles lead to reordering of particles at the interface, leading 
+to a different interfacial configuration and microstructure \cite{gunther_timescales_2014}.
 
@@
 
-Rod like particles have also been used as stabilizers in experiments, identifying that the length scale of the pores of the bijels follows $ L \propto \frac{1}{\phi_p} $ even if the proportionality constant
-is different.
-Figure \ref{fig:rod_bijel_flippers} demonstrates bijels stabilized by rod like particles showing that particles flip out of the interface due to steric forces from adjacent particles.
-This
-flipping can increase the resistance to shear due to capillary bridging between adjacent rods.
+Rod like particles have also been used as stabilizers in experiments, identifying that the length scale of the pores of the bijels follows $ L \propto \frac{1}{\phi_p} $ even if the 
+proportionality constant is different. Figure \ref{fig:rod_bijel_flippers} demonstrates bijels stabilized by rod like particles showing that particles flip out of the interface due to steric 
+forces from adjacent particles. This flipping can provide structural support between the domains, providing the bijel with greater mechanical stability.
 While the proportionality constant depends on particle geometry, this trend has been observed across various particle shapes 
 \cite{hijnen_bijels_2015, madivala_exploiting_2009, gunther_timescales_2014, daware_emulsions_2015, loudet_capillary_2005, cheng_shape-anisotropic_2013}.
-The dynamics of bijels stabilized by ellipsoidal particles are also distinct from bijels stabilized by spheres, caused by reorientation of particle stabilizers at the interface.
-\cite{gunther_timescales_2014}
 
@@
 
-Understanding the rheology of emulsions, particularly bijels, is essential because it directly impacts both their fabrication and practical use. \cite{haase_situ_2016}
-Previous investigations have characterized that bijels are non-Newtonian fluids with a yield stress and shear thinning behavior. \cite{macmillan_rheological_2019}
+Understanding the rheology of emulsions, particularly bijels, is essential because it directly impacts both their fabrication and practical use \cite{haase_situ_2016}.
+Previous investigations have characterized that bijels are non-Newtonian fluids with a yield stress and shear thinning behavior \cite{macmillan_rheological_2019}.
 A non-Newtonian fluid is one whose viscosity is not constant but varies with the applied shear rate or stress. In Newtonian fluids like water 
-or air, there is a linear relationship between shear stress and shear rate, meaning viscosity remains the same regardless of how fast the fluid is sheared.
-\cite{mezger_rheology_2020} Non-Newtonian fluids, on
-the other hand, deviate from this behavior and may exhibit shear thinning, shear thickening, yield behavior or viscoelasticity with no fluid constrained to one behavior. \cite{mezger_rheology_2020}
-Shear thinning and thickening here define that the change in viscosity is sub-linear and super-linear respectively, while yield behavior implies that the viscosity is non-zero when no shear 
-is applied.
-\cite{mezger_rheology_2020} Viscoelasticity appears when the shear response of the fluid is dependent upon the frequency of the applied shear, indicating that the fluid has both liquid and solid like
-characteristics. \cite{mezger_rheology_2020}
-These properties often appear in soft matter and multiphase systems where microstructure and particle interactions influence flow behavior.
+or air, there is a linear relationship between shear stress and shear rate, meaning viscosity remains the same regardless of how fast the fluid is sheared \cite{mezger_rheology_2020}. 
+Non-Newtonian fluids, on the other hand, deviate from this behavior and may exhibit shear thinning, shear thickening, yield behavior or viscoelasticity with no fluid constrained to one behavior
+\cite{mezger_rheology_2020}. Shear thinning and thickening here define that the viscosity increases at a slower and more rapid rate than the applied shear rate., while yield behavior implies that 
+the viscosity is non-zero when no shear is applied \cite{mezger_rheology_2020}. Viscoelasticity appears when the shear response of the fluid is dependent upon the frequency of the applied shear, 
+indicating that the fluid has both liquid and solid like characteristics \cite{mezger_rheology_2020}. These properties often appear in soft matter and multiphase systems where microstructure and 
+particle interactions influence flow behavior.
 
@@
 
-Suspensions and emulsions are examples of non-Newtonian fluids due to the presence of dispersed particles or droplets within a continuous phase. 
-\cite{brader_nonlinear_2010, besseling_three-dimensional_2007, xu_relation_2013}  
+Suspensions and emulsions are examples of non-Newtonian fluids due to the presence of dispersed particles or droplets within a continuous phase
+\cite{brader_nonlinear_2010, besseling_three-dimensional_2007, xu_relation_2013}.
 In suspensions, the interaction  between solid particles—such as hydrodynamic forces, electrostatic repulsion, and steric hindrance—creates microstructural rearrangements under flow, leading to 
-non-linear viscosity 
-responses. \cite{brader_nonlinear_2010, besseling_three-dimensional_2007} Figure \ref{fig:suspension_shear} demonstrates the shear properties of an example suspension, demonstrating how shear thinning
-and shear thickening can occur in suspensions. At low shear, particles may aggregate or form a network that resists deformation, while higher shear rates can break 
-down these structures, resulting in shear thinning. In dense systems, particles may experience contact-induced resistance or jamming, causing shear thickening. \cite{brader_nonlinear_2010}
+non-linear viscosity responses \cite{brader_nonlinear_2010, besseling_three-dimensional_2007}. Figure \ref{fig:suspension_shear} demonstrates the shear properties of an example suspension, 
+demonstrating how shear thinning and shear thickening can occur in suspensions. At low shear, particles may aggregate or form a network that resists deformation, while higher shear rates can break 
+down these structures, resulting in shear thinning. In dense systems, particles may experience contact-induced resistance or jamming, causing shear thickening \cite{brader_nonlinear_2010}.
 
 Emulsions behave similarly with droplet deformation, coalescence, and interactions 
-among droplets generating time-dependent and non-linear responses to shear. When particles are used to stabilize emulsions (e.g., in Pickering emulsions), their interfacial rigidity 
+among droplets generating time-dependent and non-linear responses to shear. When particles are used to stabilize emulsions (e.g., in Pickering emulsions), their rigidity 
 adds further resistance to flow and deformation, contributing to complex, often viscoelastic, rheological behavior.
 Madivala et al. showed that Pickering emulsions stabilized with rod-like particles had enhanced stability under shear, with greater resistance observed as particle aspect ratio increased 
-\cite{madivala_exploiting_2009}. They identified this improvement to be due to improved interfacial coverage of ellipsoidal particles at interfaces and the improved elasticity of the interface,
+\cite{madivala_exploiting_2009}. They identified this improvement to be due to improved interfacial coverage of ellipsoidal particles at interfaces and the enhanced elasticity of the interface,
 allowing for the droplet to elongate more before failure. These improvements also extend to disc like particles with other investigations into the resistance to shear of emulsions stabilized by
-graphene nanosheets, showing that they were able to provide better resistance to shear than spherical particles. \cite{imperiali_simple_2014} This was due to the graphene nanosheets overlapping one
+graphene nanosheets, showing that they were able to provide better resistance to shear than spherical particles \cite{imperiali_simple_2014}. This was due to the graphene nanosheets overlapping one
 another during shear, creating greater resistance to the applied shear and a higher apparent viscosity. In this case too, the overlap of graphene nanosheets was shown to result in greater interfacial
-elasticity inferred through surface tension measurements of droplets with graphene stabilizers. \cite{sun_assembly_2013}
+elasticity inferred through surface tension measurements of droplets with graphene stabilizers \cite{sun_assembly_2013}.
 
@@
 Figure \ref{fig:shear_theory}. The power law Model is commonly used to represent shear thinning or 
-thickening, with the equation \(\sigma = k \dot{\gamma}^n\), where \(\sigma\) is shear stress, \(\dot{\gamma}\) is shear rate, \(k\) is the consistency index, and \(n\) is the flow index.
-\cite{mezger_rheology_2020}
-For \(n<1\), the fluid is shear thinning and for \(n>1\), shear thickening. \cite{mezger_rheology_2020}
+thickening, with the equation \(\sigma = k \dot{\gamma}^n\), where \(\sigma\) is shear stress, \(\dot{\gamma}\) is shear rate, \(k\) is the consistency index, and \(n\) is the flow index 
+\cite{mezger_rheology_2020}.
+For \(n<1\), the fluid is shear thinning and for \(n>1\), shear thickening \cite{mezger_rheology_2020}.
 The Bingham plastic model and Herschel-Bulkley model account for yield stress, with the latter being more general by 
-including power-law behavior after yielding, defined as $\sigma = \sigma_y + k \dot{\gamma}^n$. \cite{mezger_rheology_2020}
+including power-law behavior after yielding, defined as $\sigma = \sigma_y + k \dot{\gamma}^n$ \cite{mezger_rheology_2020}.
 Shear models that include viscoelasticity have also been developed such as the  Maxwell and Kelvin-Voigt 
-models. \cite{mezger_rheology_2020}
+models \cite{mezger_rheology_2020}.
 They are used when the fluid exhibits both solid- and liquid-like characteristics under stress, incorporating time-dependent strain responses and relaxation phenomena. These models help 
-predict and quantify the behavior of complex fluids in real-world applications. \cite{mezger_rheology_2020}
+predict and quantify the behavior of complex fluids in real-world applications \cite{mezger_rheology_2020}.
 
 Bicontinuous interfacially jammed emulsion gels (bijels) exhibit highly complex rheological behavior due to their unique microstructure. Bijels typically show yield stress and viscoelasticity, 
-behaving like soft solids under low stress and flowing under high stress. \cite{macmillan_rheological_2019, bai_dynamics_2015, lee_making_2013}  The rigidity of the 
-particle-laden interface resists deformation, until the applied shear rate is high enough to overcome the frictional contacts keeping particles in place. \cite{boakye-ansah_controlling_2020} 
-Experimental studies have reported non-Newtonian behavior such as shear thinning, attributed to the gradual inability of the particles to resist shear. \cite{macmillan_rheological_2019}
+behaving like soft solids under low stress and flowing under high stress \cite{macmillan_rheological_2019, bai_dynamics_2015, lee_making_2013}.  The rigidity of the 
+particle-laden interface resists deformation, until the applied shear rate is high enough to overcome the frictional contacts keeping particles in place \cite{boakye-ansah_controlling_2020}. 
+Experimental studies have reported non-Newtonian behavior such as shear thinning, attributed to the gradual inability of the particles to resist shear \cite{macmillan_rheological_2019}.
 Simulation studies using Lattice Boltzman have identified the failure mechanism of bijels stabilized by spherical particles to be due to shear induced ordering to the applied field before
-particle ejection from the interface, causing domain coalescence. \cite{bonaccorso_shear_2020} However, the rheology of bijels is still an emerging field, 
+particle ejection from the interface, causing domain coalescence \cite{bonaccorso_shear_2020}. However, the rheology of bijels is still an emerging field, 
 with ongoing work focused on understanding how particle properties such as shape, particle size and contact angle affect flow behavior. One important find was that bijels were 
-2D colloidal glasses percolating in 3D. \cite{ching_bijel_2022}
+2D colloidal glasses percolating in 3D \cite{ching_bijel_2022}.
 
-Magnetic fields introduce a means of dynamically tuning the rheology of emulsions stabilized by magnetically responsive particles. 
-\cite{qiao_magnetorheological_2012} In Pickering emulsions, magnetic fields can induce droplet deformation and change the rigidity of the particle monolayer, thereby changing the flow behavior. 
-\cite{qiao_magnetorheological_2012} For bijels incorporating magnetic particles, external fields can affect the stability and 
-elasticity of the interfacial particle layer or cause domain reorganization. These effects can lead to tunable yield stress, viscosity, and viscoelastic properties.
+Magnetic fields introduce a means of dynamically tuning the rheology of emulsions stabilized by magnetically responsive particles \cite{qiao_magnetorheological_2012}. 
+In Pickering emulsions, magnetic fields can induce droplet deformation and change the rigidity of the particle monolayer, thereby changing the flow behavior \cite{qiao_magnetorheological_2012}. 
+For bijels incorporating magnetic particles, external fields can affect the stability and elasticity of the interfacial particle layer or cause domain reorganization. These effects can lead to 
+tunable yield stress, viscosity, and viscoelastic properties.
 
@@
 One significant contribution of LB simulations to emulsion research has been the study of dynamical scaling during spinodal decomposition, characterized as the growth of the lengthscale
-over time following a power law behavior. \cite{siggia_late_1979, furukawa_role_1994} From the multicomponent Navier Stokes equation, Reynolds number dependent scaling exponents for the 
-lengthscale of the system were identified that were termed the viscous limit, where the Reynolds number was low, and the inertial limit, where the Reynolds number is high. \cite{kendon_inertial_2001} 
-Multicomponent LB studies definitively demonstrated the ranges of Reynolds number where these scaling laws held and identified a broad crossover region. \cite{kendon_inertial_2001, kendon_3d_1999}
+over time following a power law behavior \cite{siggia_late_1979, furukawa_role_1994}. From the multicomponent Navier Stokes equation, Reynolds number dependent scaling exponents for the 
+lengthscale of the system were identified that were termed the viscous limit, where the Reynolds number was low, and the inertial limit, where the Reynolds number is high \cite{kendon_inertial_2001}.
+Multicomponent LB studies definitively demonstrated the ranges of Reynolds number where these scaling laws held and identified a broad crossover region \cite{kendon_inertial_2001, kendon_3d_1999}.
 
-Additionally, the bijel itself was first realized computationally using LB simulations.
-\cite{stratford_colloidal_2005} A multicomponent LB model with neutrally wetting colloids based on the implementation
-by Ladd showed that coarsening interfaces could catch particles irreversibly adsorbing them and arresting coarsening once the interfacial area matched the cross sectional area of particles adsorbed. 
-\cite{stratford_colloidal_2005,ladd_numerical_1994} The simulations also showed that these structures were stable over long periods of time, motivating and guiding the experimental realization of 
-bijels in 2007. \cite{herzig_bicontinuous_2007} These simulations provided an explanation of the dynamics and mechanistic reasoning behind the formation of bijels, allowing for the prediction of
-the microstructure.
-More recent LB studies have extended these findings by identifying the volume fraction and wetting angle needed to form bijels as opposed to Pickering emulsions.
-\cite{jansen_bijels_2011}
-The effect of the surface tension, fluid density and volume fraction of particles were also studied, showing that surface tension and fluid density had little effect on the microstructure of bijels 
-and that the length scale of the bijel was inversely proportional to the volume fraction of particles. \cite{jansen_bijels_2011}
+Additionally, the bijel itself was first realized computationally using LB simulations. \cite{stratford_colloidal_2005} A multicomponent LB model with neutrally wetting colloids based on the 
+implementationby Ladd showed that coarsening interfaces could catch particles irreversibly adsorbing them and arresting coarsening once the interfacial area matched the cross sectional area of 
+particles adsorbed \cite{stratford_colloidal_2005,ladd_numerical_1994}. The simulations also showed that these structures were stable over long periods of time, motivating and guiding the 
+experimental realization of bijels in 2007 \cite{herzig_bicontinuous_2007}. These simulations provided an explanation of the dynamics and mechanistic reasoning behind the formation of bijels, 
+allowing for the prediction of the microstructure. More recent LB studies have extended these findings by identifying the volume fraction and wetting angle needed to form bijels as opposed to 
+Pickering emulsions \cite{jansen_bijels_2011}. The effect of the surface tension, fluid density and volume fraction of particles were also studied, showing that surface tension and fluid density 
+had little effect on the microstructure of bijels and that the length scale of the bijel was inversely proportional to the volume fraction of particles \cite{jansen_bijels_2011}.
 
 More recent LB studies by Gunther et al. have extended these findings by incorporating nonspherical particles, such as ellipsoids or rods, to explore how anisotropy influences interfacial behavior 
-and emulsion morphology. \cite{gunther_timescales_2014}
-These particles introduce directional capillary interactions and exhibit preferred orientations at the interface, which can lead to enhanced jamming and altered domain stabilization with timescales 
-of domain size change not observed with spherical particles arising from steric force driven particle reorientation. The orientation of ellipsoidal particles at interfaces was also characterized using
-a multicomponent LB, demonstrating the adsorption of ellipsoidal particles at interfaces could result in metastable orientations of particles. \cite{gunther_lattice_2013}
+and emulsion morphology \cite{gunther_timescales_2014}. These particles introduce directional capillary interactions and exhibit preferred orientations at the interface, which can lead to enhanced 
+jamming and altered domain stabilization with timescales of domain size change not observed with spherical particles arising from steric force driven particle reorientation. The orientation of 
+ellipsoidal particles at interfaces was also characterized using a multicomponent LB, demonstrating the adsorption of ellipsoidal particles at interfaces could result in metastable orientations of 
+particles \cite{gunther_lattice_2013}.
 
 The LB method has also enabled exploration of external field effects, particularly magnetic fields acting on particles at interfaces. Simulations involving magnetic dipolar particles show that 
-applying an external field can induce tilting, chaining, or reorientation of particles at the interface.
-\cite{davies_interface_2014, davies_assembling_2014} This effect was caused by interface deformation
-that caused dipolar or quadropolar capillary interactions.
-This was extended to analyzing the effect of Janus particles at interfaces of evaporating droplets that showed how they preferred to stick together
-on curved interfaces. \cite{xie_direct_2017}
+applying an external field can induce tilting, chaining, or reorientation of particles at the interface \cite{davies_interface_2014, davies_assembling_2014}. This effect was caused by interface 
+deformation that caused dipolar or quadropolar capillary interactions.
+This was extended to analyzing the effect of Janus particles at interfaces of evaporating droplets that showed how they preferred
+to stick together on curved interfaces \cite{xie_direct_2017}.
 
@@
 increasingly sophisticated and tunable systems.
+
+\section{Numerical modeling}
+
+\subsection{Multiscale modeling algorithms}
+
+A wide range of numerical methods exist for simulating the physics details in previous sections. The choice of method depends on the specific physical processes to be captured such as 
+interface dynamics, hydrodynamic interactions, and thermal fluctuations—as well as computational efficiency and scalability. Below, we outline several commonly used approaches that have been 
+applied in studies of complex fluids and soft matter systems.
+
+The Volume of Fluid (VOF) method is a sharp-interface technique used to track the evolution of fluid-fluid interfaces within a fixed computational grid 
+\cite{gopala_volume_2008, fleckenstein_volume-fluid-based_2015, deising_direct_2018}. In VOF, a scalar field representing the volume fraction of one 
+fluid is defined for each grid cell to indicate the local phase composition. Interface reconstruction algorithms are then employed to geometrically 
+localize the boundary between phases. The method is inherently mass-conserving and can handle large interface deformations, making it particularly 
+effective for high-Reynolds-number flows and surface-tension-driven phenomena. However, VOF methods can struggle with accurately capturing interfacial 
+curvature and are not well-suited for diffuse interfaces, which limits their applicability in modeling spinodal decomposition and phase separation 
+processes such as those that form bijels.
+
+Phase field methods use a diffuse-interface approach to model multiphase systems, representing fluid composition or phase identity through a continuous 
+order parameter field governed by equations such as the Cahn-Hilliard or Allen-Cahn equations 
+\cite{mendoza_evolution_2006, carmack_tuning_2018, chan_channel_2012}. These methods naturally capture smooth transitions between phases, enable
+accurate computation of interfacial forces, and handle topological changes like coalescence and breakup with ease. Derived from variational principles, 
+phase field models are thermodynamically consistent, making them particularly well-suited for simulating spinodal decomposition, wetting phenomena, and 
+interfacial dynamics. However, their main limitations include the need for fine spatial resolution near interfaces to maintain accuracy and the relatively 
+high computational cost of solving fourth-order PDEs, especially when coupled with full hydrodynamic models.
+
+Brownian dynamics is a particle-based simulation method used to model the stochastic motion of colloidal particles suspended in a fluid 
+\cite{huber_brownian_2019, yip_brownian_2005, elsawy_utility_2025}. It approximates the over-damped limit of Langevin dynamics by integrating 
+particle trajectories under the influence of both deterministic forces—such as interparticle potentials or external fields—and random thermal 
+forces representing collisions with solvent molecules. Hydrodynamic interactions may be included through approximate mobility tensors or omitted 
+entirely, depending on the desired level of fidelity. Brownian dynamics is particularly well-suited for studying self-assembly, aggregation, and 
+diffusion in dilute suspensions, where particle motion is dominated by thermal fluctuations. However, it does not model the surrounding fluid 
+explicitly, limiting its ability to capture bulk fluid flow or interface-mediated interactions. As a result, Brownian dynamics is not sufficient 
+on its own for simulating the coupled fluid-particle dynamics involved in bijel formation.
+
+The Lattice Boltzmann Method (LBM) is a discretization of the Boltzmann equation of motion for molecules. \cite{qian_lattice_1992, succi_lattice_2018, shan_multicomponent_1995, swift_lattice_1996}
+Unlike traditional CFD techniques such as phase field or VOF methods, LBM tracks the evolution of a 
+particle distribution function within grid cells evolved through a discretized Boltzmann equation of motion. Macroscopic variables such as fluid density and 
+velocity are recovered from the particle distributions through appropriate moment integration, and the Navier Stokes equation at the incompressible limit can be 
+obtained through a Chapman-Enskog expansion of the LBM. \cite{qian_lattice_1992} The LBM has become an attractive tool for meso-scale CFD simulations due to its ease of algorithm 
+implementation, highly parallelizable nature and ease of boundary condition implementation, allowing coupling to other physically relevant systems such as 
+particles with varieties of potentials, external fields and deformable bodies.
+Importantly, LBM can be extended to handle multiphase and multicomponent fluids, using either color-gradient models, free energy formulations,
+or pseudopotential approaches to model non-ideal mixing. It also couples well to particle dynamics through momentum exchange schemes, making it a powerful framework for 
+simulating colloidal suspensions, interfacial phenomena, and structurally complex systems like bijels. Its ability to capture both hydrodynamics and mesoscale thermodynamic 
+behavior makes it particularly suited for the multi-scale requirements of stimuli-responsive emulsions.
+
+In summary, the Volume of Fluid method offers robust interface tracking and mass conservation but lacks the ability to naturally capture interfacial curvature. 
+Phase field methods provide thermodynamically consistent, diffuse-interface models ideal for phase separation, though they require fine resolution and are computationally intensive. 
+Brownian dynamics excels at modeling particle-level stochastic motion but cannot resolve bulk fluid dynamics or interface evolution on its own. In contrast, the Lattice Boltzmann Method 
+combines the strengths of mesoscopic fluid modeling with efficient handling of complex interfaces and straightforward coupling to particle dynamics. Its balance between computational 
+efficiency, scalability, and physical fidelity across multiple scales makes LBM the most suitable method for simulating the rich interplay of hydrodynamics, phase separation, and particle 
+interactions in stimuli-responsive emulsions such as bijels.
+
+\subsection{Multicomponent models in the Lattice Boltzmann Method}
+
+Several techniques exist in the lattice Boltzmann literature for modeling multicomponent or multiphase systems. These are the Shan-Chen (SC) 
+pseudopotential model, the free energy (FE) model, the color gradient (CG) model, and the interface tracking (IT) model.
+These methods differ fundamentally in their formulation and implementation, each offering unique advantages and trade-offs in terms of accuracy, 
+stability, physical realism, and computational cost. Below, each approach is briefly reviewed, followed by a comparative discussion of their 
+suitability for modeling stimuli-responsive emulsions such as bijels.
+
+The SC model introduces fluid-fluid interactions via a local, density-dependent force, enabling spontaneous phase separation and interface 
+formation without requiring explicit interface tracking. 
+\cite{shan_lattice_1993, shan_simulation_1994, shan_multicomponent_1995, jansen_bijels_2011,gunther_timescales_2014}
+Its simplicity and computational efficiency have made it a widely used method. However,
+in this formulation, surface tension is not an independently controllable parameter. An effective mass defined from the density of each component
+in each lattice point is used in the force calculation, meaning that it indirectly determines the surface tension in addition to the interaction
+strength parameter.
+
+The FE model is derived from a square-gradient free energy functional, which modifies the equilibrium distribution to incorporate thermodynamic 
+forces driving phase separation.
+\cite{swift_lattice_1996, kendon_inertial_2001, briant_lattice_2004} Like the SC model, it naturally produces interfaces and captures interfacial tension.
+Unlike the SC model, however,
+the FE model allows for explicit control of surface tension and interface thickness via the bulk free energy parameters. This thermodynamic 
+consistency makes it attractive for modeling systems with diffuse interfaces. The thermodynamics of the system can also be modified through changing the free energy used.
+\cite{swift_lattice_1996, briant_lattice_2004, kendon_inertial_2001}
+A key limitation, however, is its difficulty handling fluids with high density ratios, which can reduce its applicability in more extreme multiphase scenarios.
+
+The CG model assigns color labels to each fluid component and applies a recoloring step to enforce immiscibility and sharpen the interface 
+between fluids. 
+\cite{mora_optimal_2021, latva-kokko_static_2005, huang_study_2014, liu_multiphase_2016}
+This recoloring step is responsible for generating interfacial tension and enables precise control over interfacial properties such 
+as surface tension and width. The model has demonstrated success in soft matter systems where interfacial control is critical. However, implementing 
+the recoloring algorithm introduces additional complexity and requires careful parameter tuning to ensure stability and numerical consistency. \cite{mora_optimal_2021}
+
+The IT model employs level-set or front-tracking techniques to explicitly track the location of fluid interfaces by evolving a separate indicator 
+function, commonly defined using a level set technique, alongside the LB solver. \cite{haghani_hassan_abadi_conservative_2018, liang_lattice_2023}
+This method achieves high accuracy in resolving interface position and curvature, making it ideal for problems 
+involving surface tension-driven flows or sharp interfacial features. However, it is computationally intensive as the indicator function must be implemented alongside
+the LB solver.
+
+Given these trade-offs, the Shan-Chen pseudopotential model is chosen for this research due to its balance between physical realism and computational 
+efficiency. \cite{jansen_bijels_2011,gunther_timescales_2014, gunther_lattice_2013, xie_direct_2017}
+Its ability to capture phase separation, interface formation, and emergent domain morphology without requiring explicit interface 
+tracking or complex coupling makes it suitable for simulating the large-scale dynamics of bijels. Moreover, its straightforward coupling to 
+colloidal particles facilitates the inclusion of particle-fluid and particle-interface interactions central to the system being studied.
+
+\subsection{Particle dynamics}
+
+In computational studies of particle-laden fluids, particles can be modeled either as point particles or as explicitly resolved rigid bodies. The choice between 
+these approaches depends on the physical fidelity required, the computational cost, and the scales at which particle-fluid and particle-interface interactions must be resolved.
+
+Point particle models treat colloids as infinitesimal entities that influence the surrounding fields through source terms or effective force laws. 
+\cite{mehrabadi_direct_2018, prosperetti_point-particle_2007, frohlich_validation_2018}
+In such models, 
+particles do not occupy physical volume and their influence on the fluid is typically introduced via body forces or perturbations to the chemical potential field. This 
+approach is computationally efficient and particularly useful for systems with a large number of particles or when only large-scale collective behavior is of interest. 
+However, point particles cannot capture rotational dynamics, or hydrodynamic effects such as lubrication forces. Additionally, 
+their interaction with phase interfaces is often prescribed rather than emergent, limiting their accuracy in systems like bijels where particles jam at fluid-fluid interfaces 
+and significantly modify the interface topology.
+
+In contrast, explicit particle models represent colloids as finite-size rigid bodies with well-defined shape, volume, and surface boundary conditions. 
+\cite{ladd_numerical_1994, jansen_bijels_2011,gunther_timescales_2014}
+These particles interact 
+with the surrounding fluid through no-slip or slip boundary conditions, and their motion responds dynamically to hydrodynamic, capillary, and interparticle forces. By resolving 
+particle geometry, these models allow for accurate representation of rotational motion, surface wetting and interfacial adsorption.
+\cite{jansen_bijels_2011, gunther_lattice_2013}
+This is important in bijel systems, where particle-induced jamming depend on particle shape, size, and surface wetting.
+
+An intermediate approach between point particles and explicitly resolved rigid bodies is the immersed boundary method (IBM), which represents extended particles as collections of 
+point markers embedded in the fluid. \cite{peskin_immersed_2002, luo_immersed-boundary_2008, spandan_parallel_2017}
+These markers interact with the fluid through momentum exchange that impose motion onto the surrounding fluid, effectively reconstructing 
+the dynamics of a deformable or rigid object without requiring an explicit boundary mesh. \cite{peskin_immersed_2002, luo_immersed-boundary_2008, spandan_parallel_2017} 
+IBM has been widely used in biological and colloidal systems, to model the dynamics of deformable bodies. \cite{peskin_immersed_2002, luo_immersed-boundary_2008, spandan_parallel_2017}
+
+For systems in which interfacial structure, jamming, or near-field hydrodynamics play a central role as in bijel formation, explicit particle modeling 
+is generally preferred as we are able to resolve the interfacial structure and near field hydrodynamics without the complications of IBM.
+
+\subsection{Magnetic fields and particles}
+
+% The Shan-Chen pseudopotential
+% model is used to simulate the Cahn-Hilliard equation, defined below
+
+% \begin{equation}
+%     \begin{split}
+%     \frac{\partial\phi}{\partial t}+\nabla\cdot\left(\phi\vec{u}\right) &= \nabla \cdot \left( \Gamma  \nabla\phi \right)
+%     \end{split}
+% \end{equation}
+
+% where $c^k$, $M^k$ and $u^k$ is the concentration, mobility and velocity of species $k$ respectively while $\mu$ is the free energy of system. 
+% \cite{shan_lattice_1993, shan_simulation_1994, he_lattice_1997, he_discrete_1998}
+
+% A computational model designed to simulate soft matter systems 
+% at the mesoscale must accurately represent both hydrodynamics and non-ideal mixing in order to capture the essential physics of emulsions, colloids, and phase-separating fluids. 
+% A hydrodynamic model must be able to recover mass and momentum conservation of a incompressible fluid
+
+% Modelling multicomponent dynamics requires incorporating a free energy model between fluids, allowing for the implementation of
+% chemical potential driven mass transfer and surface tension. Typically this is done using a Cahn-Hilliard model based on a
+% square gradient free energy functional. This captures the demixing characteristics of phase separating fluids and controls interface
+% characteristics, providing surface tension and interface width characteristics. This model has been used in past investigations looking 
+% into spinodal decomposition, domain growth and coarsening.
+
+% To fully capture mesoscale dynamics, the model must also resolve the coupling between hydrodynamic flow and composition gradients. This coupling 
+% is essential for simulating phenomena such as Marangoni flows, interfacial instabilities, and anisotropic stress distributions that arise from 
+% non-uniform compositions or curvature-dependent surface tension. Moreover, the model must support anisotropic or time-dependent external fields 
+% (e.g., magnetic, electric, or shear) that influence mixing behavior. Computational frameworks that can evolve velocity, pressure, and composition 
+% fields simultaneously—while ensuring thermodynamic consistency and mechanical stability—are critical for accurately describing the emergent structures 
+% and transport properties in non-ideal soft matter systems.
+
+% Given the multiscale modeling necessary to correctly simulate the physical system, one approach suggested to tackle this problem is the multicomponent
+% Lattice Boltzmann Method. This technique bridges the length and time scales necessary in soft matter modeling through modeling the evolution of a particle
+% distribution function. Hydrodynamic parameters are recovered through calculating the moments of the particle distribution function. One of the advantages of
+% the Lattice Boltzmann Method its parallelize nature and ease of adding multiple physical phenomena. In the following sections, the implementation of the LBM
+% and alternatives to the LBM will be presented.
+
+% This work uses a multicomponent Lattice Boltzmann Method (LBM) to simulate the hydrodynamics of two partially miscible, 
+% incompressible fluids as implemented in LB3D. The LBM solves the continuity and Navier-Stokes equation at low
+% Mach and Reynolds numbers for the fluid, defined as,
+
+% \begin{equation}
+%     \begin{split}
+%     \frac{\partial\rho}{\partial t} + \nabla\cdot\left(\rho\vec{u}\right) &= 0 , \\
+%     \frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u} &= - \frac{1}{\rho} \nabla p + \nu \nabla^2 \vec{u} ,
+%     \end{split}
+% \end{equation}
+
+% incorporating density $(\rho)$, viscosity $(\eta)$, velocity $(u)$, pressure $(P)$, and 
+% body force $(F_{body})$. \cite{qian_lattice_1992, chin_lattice_2002, nourgaliev_lattice_2003} The Shan-Chen pseudopotential
+% model is used to simulate the Cahn-Hilliard equation, defined below
+
+% \begin{equation}
+%     \begin{split}
+%     \frac{\partial\phi}{\partial t}+\nabla\cdot\left(\phi\vec{u}\right) &= \nabla \cdot \left( \Gamma  \nabla\phi \right)
+%     \end{split}
+% \end{equation}
+
+% where $c^k$, $M^k$ and $u^k$ is the concentration, mobility and velocity of species $k$ respectively while $\mu$ is the free energy of system. 
+% \cite{shan_lattice_1993, shan_simulation_1994, he_lattice_1997, he_discrete_1998}
+
+% Particle dynamics include Hertzian contact and lubrication forces, tracked with classical Newtonian mechanics, while 
+% particle-fluid coupling involves momentum exchange to simulate viscous dissipation. Particle-particle magnetic interactions are modeled using dipole 
+% interactions. \cite{davies_interface_2014, xie_direct_2017, xie_controllable_2021} A more detailed description of the model is 
+% provided in the following sections
+
+Magnetically responsive particles can generally be classified as paramagnetic or ferromagnetic, depending on the nature and strength of their magnetization in response to external 
+magnetic fields. Paramagnetic particles do not possess a permanent magnetic moment but acquire a reversible magnetization that aligns with the applied field and 
+vanishes once the field is removed. \cite{sinn_magnetically_2011} Their response is typically linear with field strength and does not involve magnetic hysteresis. 
+In contrast, ferromagnetic particles exhibit strong, permanent magnetization due to the alignment of magnetic domains even in the absence of an external field. These particles can 
+exhibit hysteresis and significantly stronger dipole-dipole interactions. \cite{sinn_magnetically_2011}
+As a result, ferromagnetic particles are more likely to form irreversible aggregates or chains, while paramagnetic particles 
+respond more gently and reversibly, making them preferable in systems where tunability and field-off stability are important. The choice between these types depends on the desired 
+degree of responsiveness, reversibility, and control in applications such as field-directed assembly or responsive emulsions.
+
+Magnetic particles are often modeled using the magnetic dipole approximation, which treats each particle as possessing a single point dipole moment \(\vec{m}\) located at its center.
+\cite{davies_assembling_2014}
+The dipole-dipole interaction between two particles separated by a vector \(\vec{r}\) is described by the potential:
+
+\begin{equation}
+    U_{\text{d}} = \frac{\mu_0}{4\pi r^3} \left[ \vec{m}_1 \cdot \vec{m}_2 - 3(\vec{m}_1 \cdot \hat{r})(\vec{m}_2 \cdot \hat{r}) \right]
+\end{equation}
+
+This model captures the long-range, anisotropic nature of magnetic interactions and is commonly used due to its simplicity and computational efficiency. It is especially effective when 
+particles are small, well-separated, and uniformly magnetized, such that higher-order multipole contributions can be neglected. However, the dipole model becomes less accurate when particles 
+aggregate closely or experience strong magnetic fields that cause internal magnetization to deviate from a uniform state.
+
+To address these limitations, the demagnetization tensor method offers a more refined model by considering the particle as a uniformly magnetized ellipsoid and calculating the internal magnetic 
+field using an analytical or numerically tabulated demagnetization tensor. \cite{takahashi_ellipsoids_2017} 
+This method accounts for the effect of particle shape on the distribution of internal magnetization and enables the modeling of induced magnetic 
+dipoles that respond to local fields. The total magnetic field of an ellipsoids can be written,
+
+\begin{equation}
+    \mathbf{H}(r) = \mathbf{H}_0 + \mathbf{N}(r)\mathbf{K}\mathbf{H}^{\dagger}
+\end{equation}
+
+Where $\mathbf{H}(r)$ is the total magnetic field of the ellipsoids, $\mathbf{H}_0$ is the inducing magnetic field in each direction,
+$\mathbf{K}$ is the susceptibility tensor and $\mathbf{H}^{\dagger}$ is the resultant uniform magnetic field at any point within
+the ellipsoids. \cite{takahashi_ellipsoids_2017}  This approach is particularly useful for modeling spheroidal or ellipsoidal particles and is widely 
+used in magnetorheological systems, chain-forming ferrofluids, and dense suspensions where particle-particle interactions are shape-dependent.
+
+Since bijel formation and stabilization primarily depend on interfacial 
+jamming and long-range interactions between particles at fluid-fluid interfaces, the magnetic dipole approximation is often sufficient to model key behaviors such as chaining, orientation under external
+fields, and capillary-mediated assembly.
+However, if particle shape anisotropy, proximity effects, or induced magnetization in response to local fields are important, incorporating demagnetization tensors
+may offer improved realism.

### 2025-04-11 chapters/lit_review_new.tex
adjusted footnote

@@
 continuous transitions between phases, making it highly suitable for modeling non-ideal mixing in systems such as bijels.
+
+\textcolor{blue}{add surface tension calculation}
+
+\textcolor{blue}{add interface width calculation}
 
@@
 Additionally, the bijel itself was first realized computationally using LB simulations. \cite{stratford_colloidal_2005} A multicomponent LB model with neutrally wetting colloids based on the 
-implementationby Ladd showed that coarsening interfaces could catch particles irreversibly adsorbing them and arresting coarsening once the interfacial area matched the cross sectional area of 
+implementation by Ladd showed that coarsening interfaces could catch particles irreversibly adsorbing them and arresting coarsening once the interfacial area matched the cross sectional area of 
 particles adsorbed \cite{stratford_colloidal_2005,ladd_numerical_1994}. The simulations also showed that these structures were stable over long periods of time, motivating and guiding the 

### 2025-04-12 chapters/LBM_technique.tex
Changes 1. Reformatting for intro, lit review and methods complete

@@
 
-We begin with a restatement of Reynolds Transport Theorem (RTT) which relates the change in a parameter in a volume over time to the change in that quantity in a control volume,
-defined as
+We begin with a restatement of Reynolds Transport Theorem (RTT) which relates the accumulation of a parameter within a control volume to the difference between the values
+of the parameter entering and leaving the volume and the generation and consumption within the volume. The derivation from page 135 to 147 in reference \cite{batchelor_introduction_2000}
+is followed. For a non moving and non-deforming volume, the transport equation is given by,
 
 \begin{equation}
-    \frac{d}{dt} \int_V f \, dV = \int_V \frac{\partial f}{\partial t} \, dV + \int_{\partial V} f (\vec{v}_{\text{surf}} \cdot \vec{n}) \, dA
+    \frac{d}{dt} \int \theta \rho \, dV = \int Q \, dV - \int \theta \rho (\vec{v}_{\text{surf}} \cdot \vec{n}) \, dA
 \end{equation}
 
-Where $f$ can be a scalar, vector or tensor, $V$ is the volume of the control element, $t$ is time, $\vec{v}_{surf}$ is the velocity vector of the surface of the volume element,
-$\vec{n}$ is the surface normal unit vector. From the RTT, the continuity equation can be written to analyze the mass flux of a control volume given by,
+Where $\theta$ is an intensive quantity of the system such as mass, momentum or energy, $\rho$ is the density of the fluid in the control volume, $Q$ is an effective density
+of a source, $V$ is the volume of the control element, $t$ is time, $\vec{v}_{surf}$ is the velocity vector 
+of the surface of the volume element and $\vec{n}$ is the surface normal unit vector. \cite{batchelor_introduction_2000} Using the divergence theorem, the expression can be rewritten as
+
+\begin{equation}
+    \int \frac{\partial \theta \rho}{\partial t} \, dV = \int Q \, dV - \int \nabla \cdot (\theta \rho \vec{v}_{\text{surf}}) \, dV
+\end{equation}
+
+If $\theta = 1$ and $Q = 0$ the continuity equation for fluid density can be written to analyze the mass flux of a control volume given by,
 
@@
 \begin{equation}
-    \rho \left(\frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u} \right) = -\nabla p + \nabla \cdot \boldsymbol{\tau} + \vec{f}
+    \rho \left(\frac{\partial u_i}{\partial t} + (u_i\cdot\frac{\partial u_i}{x_i}) \right) = \frac{\partial \sigma_{ij}}{\partial x_j} + f_i
 \end{equation}
 
-where $p$ is the pressure, $\boldsymbol{\tau}$ is the viscous stress tensor, and $\vec{f}$ represents external forces such as gravity or magnetic interactions.
-
-For a Newtonian, isotropic fluid, the viscous stress tensor is given by
+where $f_i$ is the force exerted on the fluid from external forces such as gravity or magnetic interactions and $\sigma_{ij}$ is the stress tensor. For a Newtonian, isotropic fluid, 
+the viscous stress tensor is given by
 
 \begin{equation}
-    \boldsymbol{\tau} = p\mathbf{I} + \eta\left( \nabla \vec{u} + (\nabla \vec{u})^T \right)
+    \sigma_{ij} = -p\delta_{ij} + \eta((\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i}) - \frac{2}{3}(\frac{\partial u_j}{\partial x_i})^2\delta_{ij})
 \end{equation}
 
-Substituting this stress tensor into the momentum equation yields the incompressible Navier-Stokes equation,
+Substituting this stress tensor into the momentum equation and using the relation, $\nabla\cdot \vec{u} = 0$ from the incompressibility constraint, the incompressible 
+Navier-Stokes equation can be derived which in vector notation is given by,
 
@@
 
-Bijels form through spinodal decomposition of two partially miscible fluids, a process that can be effectively modeled using the Cahn-Hilliard equation, which describes the diffusive dynamics 
-of a conserved scalar order parameter $\phi$, typically representing the local concentration difference between the two fluid components,
+Bijels form through spinodal decomposition of two partially miscible fluids, a process that can be effectively modeled using the Cahn-Hilliard equation. \cite{cahn_spinodal_1961} While the
+original equation is written for a concentration of species $c$. For a binary mixture, it can be recast in terms of a conserved scalar order parameter $\phi$, typically representing the 
+local concentration difference between the two fluid components,
 
@@
 
-Here, $M$ is the mobility coefficient and $\mu$ is the chemical potential, which is derived from the variation of the free energy functional $F[\phi]$. This formulation allows for the modeling of 
+Here, $M$ is the mobility coefficient and $\mu$ is the chemical potential, which is derived from the variation of the free energy functional $F[\phi]$ which is the sum of a bulk free energy
+$f(\phi)$ and an interfacial contribution. This formulation allows for the modeling of 
 interfacial tension and the spontaneous formation of bicontinuous domains characteristic of spinodal decomposition.
-To capture not only the diffusive separation of phases but also the resulting fluid motion, the Cahn-Hilliard equation is coupled with the Navie-Stokes equations, leading to the 
+To capture not only the diffusive separation of phases but also the resulting fluid motion, the Cahn-Hilliard equation is coupled with the Navier-Stokes equations, leading to the 
 Cahn-Hilliard-Navier-Stokes (CHNS) framework. This coupling is essential in systems like bijels, where advection play a significant role in domain coarsening and morphology arrest. 
-The momentum conservation equation in this framework is written as:
+The momentum conservation equation in this framework is given by,
 
@@
     directions $(i)$ of the lattice with lattice velocity $c_{i}$. \cite{schmieschek_lb3d_2017} Reproduced from 
-    Schmieschek et al. Computer Physics Communications 2017, 217, 149--161, under the Creative Commons license.}
+    Schmieschek et al. Computer Physics Communications 2017, 217, 149--161, under the CC-BY license.}
     \label{fig:d3q19_lattice}
@@
 
-The momentum flux tensor can be further expressed as a function of macroscopic variables,
+The momentum flux tensor can be further expressed as a sum of the equilibrium and non-equilibrium components of the stress tensor, denoted by 0 and 1 given by,
 
@@
 
-\subsection{ellipsoidal_particles}
+\subsection{Ellipsoidal_particles}
 \label{section:ellipsoidal_particles}

### 2025-04-12 chapters/introduction_new.tex
Changes 1. Reformatting for intro, lit review and methods complete

@@
 function by adsorbing at the interface and effectively reducing the interfacial area between fluid domains. The free energy associated with the decrease in interfacial area 
-can be orders of magnitude larger than the thermal energy of the system $k_b T$ which makes the particle irreversibly adsorbed on the interface. \cite{ngai_particle-stabilized_2015}
+can be orders of magnitude larger than the thermal energy of the system $k_b T$ which makes the particle irreversibly adsorbed on the interface \cite{ngai_particle-stabilized_2015}.
 
 Compared to surfactant-stabilized emulsions, particle-stabilized emulsions (Pickering emulsions) exhibit enhanced resistance to coalescence and coarsening
-due to the irreversibility of particle adsorption at the interface. \cite{ngai_particle-stabilized_2015} 
+due to the irreversibility of particle adsorption at the interface \cite{ngai_particle-stabilized_2015} .
 Additionally, growing environmental and toxicity concerns associated with small-molecule surfactants have increased interest in the applications of particle-stabilized emulsions.
@@
     \includegraphics[scale = 0.3]{figures/literature_review/state_diagram.jpg}
-    \caption{Formation criteria for a particle stabilized emulsion that can form bijel. \cite{velankar_non-equilibrium_2015}
+    \caption{Formation criteria for a particle stabilized emulsion that can form bijel \cite{velankar_non-equilibrium_2015}.
             Used with permission of Royal Society of Chemistry, from A non-equilibrium state diagram for liquid/fluid/particle 
@@
 Bijel microstructures are of interest because their bicontinuous, interpenetrating networks enable tunable transport and separation properties. The computational discovery of the technique to 
-synthesize bijels was succeeded by the experimental synthesis of a bijel in 2007 by Herzig et al., who used a 2,6-lutidine/water system stabilized with surface-modified silica particles.
-\cite{herzig_bicontinuous_2007} 
+synthesize bijels was succeeded by the experimental synthesis of a bijel in 2007 by Herzig et al., who used a 2,6-lutidine/water system stabilized with surface-modified silica particles
+\cite{herzig_bicontinuous_2007}.
 This binary fluid system exhibits a lower critical solution temperature (LCST) of 34.1\textdegree C and a critical composition at approximately 28\% lutidine by weight.
@@
 occurred, forming a bijel.
-Since this initial experimental synthesis, TIPS has been widely used in laboratory-scale studies to synthesize a variety of small molecule, oligomeric, and polymeric systems.
+Since this initial experimental synthesis, TIPS has been widely used in laboratory-scale studies to synthesize a variety of small molecule, oligomeric, and polymeric systems
 \cite{tavacoli_novel_2011, lee_bicontinuous_2010, bai_dynamics_2015, ching_rapid_2021}.
@@
 induced phase separation such as Vapor Induced Phase Separation(VIPS) and controlled coalescence of droplets to form bijels through shear (homogenization) have also been identified as techniques
-to synthesize bijels. \cite{wang_scalable_2020, huang_bicontinuous_2017}
+to synthesize bijels \cite{wang_scalable_2020, huang_bicontinuous_2017}.
 
@@
              Solvent Transfer-Induced Phase Separation (STRIPS)}, Haase, M. F., Stebe, K. J., 
-             \& Lee, D., \textit{Advanced Materials}, 27(44), 7065-7071, 2015}
+             \& Lee, D., \textit{Advanced Materials}, 27(44), 7065-7071, 2015 under license number 5913140219015}
     \label{fig:strips}
@@
 Achieving controlled
-morphology often requires fine-tuning of fluid concentrations or external conditions, which may not be feasible for all applications. \cite{haase_continuous_2015, reeves_particle-size_2015}
+morphology often requires fine-tuning of fluid concentrations or external conditions, which may not be feasible for all applications \cite{haase_continuous_2015, reeves_particle-size_2015}.
 The ability to tune these structural features would significantly expand the versatility and functionality of bijel-based systems.
 In many of the proposed applications such as water filtration membranes or drug delivery 
-platforms, the morphology of the material plays a critical role in determining key functional properties, including back pressure, species selectivity, and transport dynamics.
-\cite{vanoli_bijels_2022, thorson_bijel-templated_2019, khan_nanostructured_2022}
+platforms, the morphology of the material plays a critical role in determining key functional properties, including back pressure, species selectivity, and transport dynamics
+\cite{vanoli_bijels_2022, thorson_bijel-templated_2019, khan_nanostructured_2022}.
 
@@
 However the application of such dynamic control strategies to bijels remains relatively underexplored. Prior studies involving magnetic fields applied to bijels stabilized with spherical particles 
-have shown limited success in modifying the microstructure \cite{kim_bijels_2010}, due to the isotropic nature of the stabilizing particles. 
+have shown limited success in modifying the microstructure, due to the isotropic nature of the stabilizing particles \cite{kim_bijels_2010}. 
 % In comparison, electric fields have demonstrated a 
@@
     \caption{Quadropolar capillary interactions around prolate ellipsoidal particles caused by interfacial deformations 
-             around the particle. \cite{loudet_capillary_2005} Reprinted Figure 4 with permission from
-             Loudet et al, Phys. Rev. Letter., 94, 08301, 2003 Copyright 2025 by the American Physical Society.}
+             around the particle \cite{loudet_capillary_2005}. Reprinted Figure 4 with permission from
+             Loudet et al, Phys. Rev. Letter., 94, 08301, 2003 Copyright 2025 by the American Physical Society under license number RNP/25/FEB/088185}
     \label{fig:anisotropic_particle_interface}
@@
 
-The dynamics of ellipsoid-stabilized bijels display additional dynamics and droplet bridging, not observed in their spherical counterparts.
-\cite{gunther_timescales_2014, witt_bijel_2013} Initially, particles adsorb and align with the interface,
-followed by a slower reorganization phase driven by capillary interactions between particles \cite{gunther_timescales_2014}.
-Experimental results confirm that the domain size in rod and ellipsoid stabilized
-bijels still follows the scaling law $L \propto \frac{1}{\phi_p}$, though the proportionality constant depends on particle geometry \cite{hijnen_bijels_2015, madivala_exploiting_2009, daware_emulsions_2015}.
+The dynamics of ellipsoid-stabilized bijels display additional dynamics and droplet bridging, not observed in their spherical counterparts \cite{gunther_timescales_2014, witt_bijel_2013}. Initially, 
+particles adsorb and align with the interface, followed by a slower reorganization phase driven by capillary interactions between particles \cite{gunther_timescales_2014}. Experimental results 
+confirm that the domain size in rod and ellipsoid stabilized bijels still follows the scaling law $L \propto \frac{1}{\phi_p}$, though the proportionality constant depends on particle geometry 
+\cite{hijnen_bijels_2015, madivala_exploiting_2009, daware_emulsions_2015}.
 
@@
 In applied systems such as
-cross-flow reactors, the mechanical stability of the particle monolayer is critical; failure under shear or compositional gradients can limit performance \cite{boakye-ansah_controlling_2020}.
-Under constant
-shear, bijels exhibit shear-thinning behavior, which at moderate shear rates is well described by the Herschel-Bulkley model \cite{macmillan_rheological_2019, wang_morphology_2023}.
-At higher shear rates, the
-internal structure of the bijel is disrupted, leading to a transition toward Newtonian flow behavior \cite{cai_bijels_2017, bonaccorso_shear_2020}.
+cross-flow reactors, the mechanical stability of the particle monolayer is critical; failure under shear or compositional gradients can limit performance \cite{boakye-ansah_controlling_2020}. Under 
+constant shear, bijels exhibit shear-thinning behavior, which at moderate shear rates is well described by the Herschel-Bulkley model \cite{macmillan_rheological_2019, wang_morphology_2023}.
+At higher
+shear rates, the internal structure of the bijel is disrupted, leading to a transition toward Newtonian flow behavior \cite{cai_bijels_2017, bonaccorso_shear_2020}.
 
@@
     \caption{Enhanced oil recovery of oil from water using magnetically responsive emulsion stabilizers, allowing for 
-             locomotion and controlled coalescence of cargo from a matrix phase using magnetic fields. \cite{tham_magnetophoresis_2021} 
+             locomotion and controlled coalescence of cargo from a matrix phase using magnetic fields \cite{tham_magnetophoresis_2021}. 
              K. Tham, W. M. Ng, S. S. Leong, S. P. Yeap, S. C. Low, H. L. Lee and J. Lim. Magnetophoresis of magnetic pickering 
@@
 their major or minor axes relative to the interface depending on their geometry and energy landscape. Lattice Boltzmann simulations support these observations, showing how particle shape influences 
-and contact angle affect the energy required to detach a particle from an interface. \cite{davies_detachment_2014}
+and contact angle affect the energy required to detach a particle from an interface \cite{davies_detachment_2014}. 
 Magnetic fields can perturb these equilibria by exerting torque on the particles, reorienting them along the field direction. 
 Experiments confirm that magnetic ellipsoids can be reconfigured at the interface, enabling controlled switching between metastable and stable configurations.
-As more particles interact under a magnetic field, their mutual dipolar interactions lead to the formation of linear chains or clusters on flat interfaces \cite{davies_assembling_2014, newton_capillary_2018}.
-The final arrangement is influenced by particle concentration, field strength, and local capillary geometry.
+As more particles interact under a magnetic field, their mutual dipolar interactions lead to the formation of linear chains or clusters on flat interfaces 
+\cite{davies_assembling_2014, newton_capillary_2018}. The final arrangement is influenced by particle concentration, field strength, and local capillary geometry.
 
@@
 
-The remainder of this dissertation is organized as follows. Chapter 2 details the physical model and the simulation methods used to solve these physics, including the Lattice Boltzmann approach 
-and magnetic dipole modeling. Chapter 3 investigates the effects of magnetic fields applied during bijel formation, analyzing their influence on domain structure and particle orientation. 
-Chapter 4 investigates the microstructure of bijels stabilized by ellipsoidal particles under magnetic fields in more detail, providing further detail on the influence of the magnetic field on
-the coarsening dynamics of the bijel.
-Chapter 5 explores 
-post-formation responsiveness, specifically examining particle unjamming and reordering phenomena.
-Chapter 6 assesses the rheological implications of these structural changes, with particular attention to
-yield stress and shear-thinning behavior.
-Finally, Chapter 7 summarizes the key findings, discusses their implications for the design of tunable porous materials, and outlines potential directions for future
-research.
-
-% To explore this possibility, Kim et al. employed a free-energy-based Lattice Boltzmann method coupled with particles and external magnetic fields to study the responsiveness of bijels stabilized by 
-% spherical particles \cite{kim_bijels_2010}. Their simulations showed that even under strong magnetic fields, the particles aligned with the field direction but did not meaningfully disrupt the 
-% interfacial morphology. This result suggests that the isotropic geometry of spherical particles does not impart anisotropic stresses on the interface, thereby preserving the original structure of 
-% the bijel despite external perturbations.
-
-% Further computational work by Jansen and Harting expanded upon these findings by investigating the effects of fluid composition, surface tension, particle volume fraction, and particle contact angle
-% using a Lattice Boltzmann framework \cite{jansen_bijels_2011}. They found that while surface tension and fluid density had only minor effects on the resulting microstructure, the particle 
-% volume fraction had a significant impact, with the characteristic length scale of the bijel inversely proportional to the particle concentration ($L \propto \frac{1}{\phi_p}$). Additionally, they 
-% demonstrated that the formation of a bijel versus a conventional Pickering emulsion was primarily determined by the contact angle of the stabilizing particles and the relative fluid volumes, rather 
-% than particle concentration alone.
-
-% However, as will be shown in the remainder of this review, modern fabrication approaches have increasingly 
-% shifted away from TIPS in favor of alternative strategies.
-
-% Further investigations into bijel microstructure have employed topological, geometric, and image analysis techniques to quantitatively characterize their complex morphology. Topological methods
-% focus on properties such as genus and channel size distribution, which reveal differences in interfacial connectivity and structural complexity \cite{chan_channel_2012}. For instance, Chan and 
-% Thornton compared bicontinuous structures generated using the Cahn-Hilliard and Allen-Cahn equations, highlighting key topological distinctions between these phase-separation models.
-The main strength
-% of topological approaches lies in their ability to assess both the shape and the interconnectedness of the structure.
-
-% Geometric techniques, such as curvature analysis, offer insights into how factors like particle size and quench rate influence bijel formation. Reeves et al. used Gaussian curvature measurements to 
-% compare bijels stabilized with micro- versus nanoparticles, demonstrating that smaller particles promote more negative Gaussian curvature and better approximation of minimal surface structures 
-% \cite{reeves_particle-size_2015,reeves_quantitative_2016}. This finding is consistent with the notion that bijel interfaces resemble minimal surfaces, which are characterized by zero mean curvature 
-% and negative Gaussian curvature \cite{jinnai_interfacial_2001}. Because nanoparticles more readily conform to curved interfaces without significantly disrupting interfacial geometry, they enhance 
-% stabilization in regions with saddle-like curvature \cite{reeves_quantitative_2016}.
-
-% Image analysis techniques have also been instrumental in characterizing features such as pore size distribution, tortuosity, connectivity, and self-similarity of bijel networks 
-% \cite{mcdevitt_microstructural_2019,reeves_quantitative_2016}.
-These methods utilize tools like region-growing and labeling algorithms (e.g., Hoshen-Kopelmann), segmentation techniques, and watershed
-% transforms to extract quantitative metrics from imaging data. For example, pore size distributions can be derived from watershed algorithms, while connectivity is assessed using segmentation-based 
-% approaches.
-
-% Recent advances suggest that anisotropic particles, particularly ellipsoidal particles, may offer enhanced responsiveness due to their shape-dependent 
-% interfacial behavior. When subjected to magnetic fields, ellipsoidal particles can align directionally, inducing local anisotropy in the interfacial 
-% packing arising from capillary deformation of the interface. This property has been characterized to induce self assembly of particles, 
-% shown in Figure \ref{fig:anisotropic_particle_interface} 
-% \cite{bresme_orientational_2007, davies_assembling_2014, newton_influence_2014}. By utilizing the magnetic field driven re-orientation and self assembly 
-% of particles at interfaces, the microstructure of bijels could be influenced pre and post formation. Therefore, leveraging this behavior offers a 
-% pathway to decouple microstructure control from casting mixture composition, expanding the design space for bijel derived porous materials and
-% soft matter.
-
-% Stimuli-responsive strategies offer an attractive alternative for post-synthetic or in-situ control of bijel microstructures. External fields, 
-% pH, and temperature have all been explored to modify emulsion morphologies, particularly in Pickering emulsions 
-% \cite{tham_magnetophoresis_2021, cui_stabilizing_2013}. In Pickering emulsions, magnetically responsive particles have enabled droplet
-% manipulation, deformation, and coalescence control, shown in Figure \ref{fig:magnetophoresis_droplet}. By contrast, similar stimuli-responsive 
-% behaviors in bijels remain underexplored. Prior work with spherical particles under magnetic fields has shown limited microstructural modification 
-% \cite{kim_bijels_2010}, while electric fields have demonstrated greater influence \cite{carmack_tuning_2018}.
-
-% Over the past decade, advancements in synthesis techniques have significantly expanded the ability to fabricate particles with anisotropic geometry and surface chemistry. 
-% The choice of synthesis method depends on the desired particle shape. For example, ellipsoidal particles can be readily produced through the mechanical deformation of 
-% % NOTE: This paragraph introduces a new concept—consider explicitly linking it to the prior paragraph (e.g., 'Beyond traditional surfactants...').
-% polymer spheres, while dumbbell-shaped particles can be synthesized using microfluidic devices or emulsion templating. \cite{fei_magneto-capillary_2020} 
-% Square-shaped particles, on the other hand, can be 
-% generated through controlled crystallization \cite{morgan_understanding_2013}. The increasing variety of synthesis methods has reduced geometric constraints when exploring 
-% potential particle stabilizers for bijels \cite{wu_recent_2016}.
-
-% Magnetic fields offer a non-invasive and targeted method for manipulating the behavior of particles. Magnetic particles can be fabricated from
-% coatings applied onto particles through deposition techniques or a core-shell particle that encapsulates a magnetic core with a non-magnetic shell. 
-% \cite{fei_magneto-capillary_2020, nakayama_stimuli-responsive_2018} These effects arise due to the interplay between the magnetic torque or force 
-% acting on the particles and the capillary interactions that govern their behavior at the interface. One theory developed for neutrally wetting ellipsoidal 
-% particles is Bresme-Faraudo theory. \cite{bresme_orientational_2007, davies_interface_2014}
-% A wide range of behaviors has been observed when magnetic fields are applied to interfacial particles. Individual particles tend to align their magnetic 
-% dipole moments along the direction of the field, causing them to reorient relative to the interface. \cite{kim_bijels_2010}
-% For anisotropic particles such as ellipsoids, this results in a tilt or rotation that changes their interfacial footprint and local curvature. 
-% \cite{davies_assembling_2014, davies_interface_2014} The orientation of the particle is a function of the capillary interactions with the interface that 
-% prefers to keep the particle flat on the interface and the magnetic field that is attempting to rotate the particle out of the interface. The magnetic force
-% experienced by the particle is a function of the applied field strength, magnetic susceptibility, size of the particle, shape of the particles 
-% and aspect ratio of the particle.
-
-% The rheological properties of bijels are of fundamental importance due to their direct influence on both fabrication and application. For instance, STrIPS fabrication relies on the controlled 
-% flow of a casting mixture into a solvent bath, necessitating precise knowledge of the material's rheology to optimize processing parameters \cite{haase_situ_2016, haase_continuous_2015}. In 
-% applied systems such as cross-flow reactors, the mechanical stability of the particle monolayer is critical; failure under shear or compositional gradients can limit performance 
-% \cite{boakye-ansah_controlling_2020}.
-
-% Under constant shear, bijels exhibit shear-thinning behavior, which at moderate shear rates is well described by the Herschel–Bulkley model \cite{macmillan_rheological_2019, wang_morphology_2023}. 
-% At higher shear rates, the internal structure of the bijel is disrupted, leading to a transition toward Newtonian flow behavior \cite{cai_bijels_2017, bonaccorso_shear_2020}. 
-% Figure~\ref{fig:bijel_under_shear} illustrates this phenomenon, showing that under shear, particles initially align with the flow direction before detaching from the interface 
-% \cite{bonaccorso_shear_2020}. This behavior is consistent with findings in colloidal suspensions, where hard-sphere systems undergoing shear exhibit shear banding and particle ordering along 
-% the flow direction, resulting in pronounced shear thinning \cite{vermant_flow-induced_2005, brader_nonlinear_2010}.
-
-% Bijels have also been shown to exhibit gel-like behavior, particularly when the storage modulus exceeds the loss modulus, indicating a dominant elastic response \cite{lee_making_2013, bai_dynamics_2015}.
-% Ching and Mohraz proposed that bijels behave similarly to 2D colloidal glasses percolating in 3D space, based on comparisons of their linear viscoelastic responses to those of attractive colloidal gels
-% \cite{ching_bijel_2022}.
-Hallmarks of colloidal glass behavior include the presence of a yield stress (the point at which irreversible deformation occurs), viscoelasticity (a combination of solid- and
-% liquid-like behavior), and a dramatic slowdown in dynamics at the glass transition point \cite{pham_yielding_2008, weeks_introduction_2017}.
-
-% The geometry of the stabilizing particles plays a key role in determining rheological behavior.
-Madivala et al.
-showed that Pickering emulsions stabilized with rod-like particles had enhanced stability
-% under shear, with greater resistance observed as particle aspect ratio increased \cite{madivala_exploiting_2009}.
-This enhancement was attributed to improved interfacial coverage and capillary interactions
-% induced by interface deformations, which reinforced the particle monolayer.
-Similarly, emulsions stabilized by graphene nanosheets exhibited higher viscosity and viscoelasticity compared to those stabilized
-% by spherical particles, underscoring the importance of particle shape \cite{imperiali_simple_2014}.
-The elasticity of the interface has also been shown to depend on the nature of the particle stabilizer
-% used \cite{sun_assembly_2013}.
-
-% Magnetically responsive Pickering emulsions offer an additional layer of tunability.
-When a magnetic field is applied, particles reorient and organize at the interface, significantly altering the material's
-% rheological response \cite{qiao_magnetorheological_2012, melle_pickering_2005}.
-This field-induced ordering can lead to reversible transitions between fluid-like and gel-like states, enabling on-demand
-% control over flow properties.
-Such behavior is particularly advantageous for applications in enhanced oil recovery, drug delivery, and soft robotics, where adaptable and reconfigurable materials are
-% essential \cite{tham_magnetophoresis_2021}.
-
-% While not strictly stimuli-responsive, microstructure modifications have been achieved by applying a particle volume fraction gradient during the formation of 
-% bijels using Thermally Induced Phase Separation (TIPS). \cite{french_bicontinuous_2022} In their study, French et al. allowed particles to partially sediment in the bijel casting mixture
-% before initiating thermal quenching. The gradient in particle volume fraction along the height of the reaction vessel caused the jamming point of the bijel
-% to vary along the gradient axis, causing a channel size gradients of up to 2.8\% per millimeter, as measured using confocal microscopy.
+The remainder of this dissertation is organized as follows. Chapter 2 reviews important background relevant to bijel formation and simulations of bijels.
+Chapter 3 details the physical model and the simulation methods used to solve these physics, including the Lattice Boltzmann Method implementation. Chapter 4 investigates the effects 
+of magnetic fields applied during bijel formation, analyzing their influence on domain structure and particle orientation.
+Chapter 5 performs quantitative microstructural characterization of the effects
+of magnetic fields on the microstructure of bijels. Chapter 6 explores post-formation responsiveness, examining whether the microstructure of a stimuli responsive bijel can be modified
+post-synthesis. Chapter 7 assesses the rheological implications of these structural changes, with particular attention to yield stress and shear-thinning behavior. Finally, Chapter 8 summarizes 
+key findings, discusses their implications for the design of tunable porous materials, and outlines potential directions for future research.

### 2025-04-12 chapters/lit_review_new.tex
Changes 1. Reformatting for intro, lit review and methods complete

@@
 transformed fraction, \(K\) is a rate constant incorporating nucleation and growth kinetics, and \(n\) is the Avrami exponent, which reflects the dimensionality and mechanism of the transformation
-\cite{avrami_kinetics_1939} .
+\cite{avrami_kinetics_1939}.
 
@@
 results in a bicontinuous structure driven by the system's attempt to minimize 
-free energy through composition modulation \cite{cahn_free_1958}. The dynamics of spinodal decomposition were characterized by Cahn and Hilliard \cite{cahn_free_1958} . 
-We first begin by defining the free energy of a regular solution, known as the bulk free energy.
+free energy through composition modulation \cite{cahn_free_1958}. The dynamics of spinodal decomposition were characterized by Cahn and Hilliard \cite{cahn_spinodal_1961}. 
+We first begin by defining the free energy of a regular solution, known as the bulk free energy given by
 
 \begin{equation}
-    \Delta G_m = \chi (1 - \phi)\phi + N_a k_B T \left[(1 - \phi)\ln(1 - \phi) + \phi \ln(\phi)\right]
+    G_m (c) = \chi (1 - c)c + N_a k_B T \left[(1 - c)\ln(1 - c) + c \ln(c)\right]
 \end{equation}
@@
 \begin{equation}
-    F[\phi] = \int \left( f(\phi) + \frac{\kappa}{2}|\nabla \phi|^2 \right) \, dV
+    F[c] = \int \left( f(c) + \frac{\kappa}{2}|\nabla c|^2 \right) \, dV
 \end{equation}
@@
 \begin{equation}
-    \mu = \frac{\delta F}{\delta \phi} = \frac{df}{d\phi} - \kappa \nabla^2 \phi
+    \mu = \frac{\delta F}{\delta c} = \frac{df}{dc} - \kappa \nabla^2 c
 \end{equation}
@@
 
-where $M$ is the mobility and could potentially be a function of $\phi$. Assuming no advection and applying mass conservation for the order parameter, we obtain,
+where $M$ is the mobility and could potentially be a function of $c$. Assuming no advection and applying mass conservation for the order parameter, we obtain,
 
 \begin{equation}
-    \frac{\partial \phi}{\partial t} = -\nabla \cdot \vec{J}
+    \frac{\partial c}{\partial t} = -\nabla \cdot \vec{J}
 \end{equation}
 
-Substituting in the expression for \(\vec{J}\) leads to the Cahn-Hilliard equation \cite{cahn_free_1958},
+Substituting in the expression for \(\vec{J}\) leads to the Cahn-Hilliard equation 18 in reference \cite{cahn_spinodal_1961},
 
 \begin{equation}
-    \frac{\partial \phi}{\partial t} = \nabla \cdot \left( M \nabla \mu \right)
+    \frac{\partial c}{\partial t} = \nabla \cdot \left( M \nabla \mu \right)
 \end{equation}
 
-This equation describes the diffusive evolution of the conserved field $\phi$ during phase separation. It captures the system's tendency to minimize its total free energy 
+This equation describes the diffusive evolution of the conserved field $c$ during phase separation. It captures the system's tendency to minimize its total free energy 
 by redistributing the order parameter according to gradients in chemical potential. The Cahn-Hilliard framework naturally incorporates interfacial tension and allows for smooth, 
 continuous transitions between phases, making it highly suitable for modeling non-ideal mixing in systems such as bijels.
-
-\textcolor{blue}{add surface tension calculation}
-
-\textcolor{blue}{add interface width calculation}
 
@@
 For particles that are smooth and simple and at an interface of oil and water, the attachment energy at the fluid interface can be calculated the Pieranski model, 
-$E_{ads} = \sigma A_{rm} (1 - \cos{\theta_c})^2$, where $E_{ads}$ is the free energy reduction upon particle adsorption, $\sigma$ is the surface tension between the two 
-fluids, and $\theta_c$ is the contact angle of the stabilizing particle.
-
-This expression is derived from an energy balance between the interactions between the interface and the 
-fluid phases, with a schematic shown in Figure \ref{fig:pieranski_model},
+$G_{ads} = \sigma A_{rm} (1 - \cos{\theta_c})^2$, where $G_{ads}$ is the free energy reduction upon particle adsorption, $\sigma$ is the surface tension between the two 
+fluids, and $\theta_c$ is the contact angle of the stabilizing particle. A schematic of a particle adsorbing at an interface is shown in Figure \ref{fig:pieranski_model},
 
@@
 
-From the Pieranski model, the adsorption energy can be seen to depend on the contact angle, surface tension and contact area of the particles. This indicates that larger, neutrally wetting
+To obtain the Pieranski model, an energy balance between the interactions between the interface and the fluid phases can be written. The energy of the system before and after particle adsorption is 
+different and can be characterized for the particle moving from water into the interface as,
+
+\begin{equation}
+    \Delta E_{IW} = E_I - E_w
+\end{equation}
+
+Where $\Delta E_{I}$ is the energy of the system when the particle is in the interface and $\Delta E_W$ is the energy of the system when the particle is completely in the water phase.
+We define $\Delta E_{I}$ as
+
+\begin{equation}
+    E_I = A_w \sigma_{pw} + A_o\sigma_{po} + A_{I_1}\sigma_{ow} + V_w P_w + V_o P_o
+\end{equation}
+
+Where subscripts $w$, $o$ and $I$ represents the water phase, oil phase and interface respectively. $A_w$ and $A_o$ are the surface areas of the particle in the water and oil phases 
+respectively, $V_w$ and $V_o$ are the volumes of water and oil phases respectively, $P_w$ and $P_o$ are the pressures of water and oil phases respectively. $A_{I_1}$ is the area of the 
+interface with the particle. A similar equation can be written for the energy of the water phase, $E_w$
+
+\begin{equation}
+    E_w = (A_w + A_o)\sigma_{pw} + A_{I_2}\sigma_{ow} + (V_w + V_o)P_w
+\end{equation}
+
+$A_{I_2}$ is the area of the interface without the particle. The change in the interface energy upon adsorption of the particle can be computed to obtain
+
+\begin{equation}
+    \Delta E_{IW} = A_o(\sigma_{po} - \sigma_{pw}) - A_p\sigma_{ow} + V_o(P_o - P_w)
+\end{equation}
+
+A similar construction can be done for the oil phase to obtain
+
+\begin{equation}
+    % \Delta E_{IO} = -\sigma_{ow}(A_w\cos{\theta_c} + A_p - \frac{2 V_o}{R_d})
+    \Delta E_{IO} = A_w(\sigma_{pw} - \sigma_{po}) + A_p\sigma_{ow} - V_o(P_o - P_w)
+\end{equation}
+
+We now use the Young-Dupre equation relating the surface tensions of each component to one another, $\cos{\theta_c} = \frac{\sigma_{po} - \sigma_{pw}}{\sigma_{ow}}$ and the
+Young-Laplace equation for a sphere, relating the pressure difference inside and outside a droplet $\Delta P$ to the radius of the droplet $R_d$, $\Delta P = \frac{2\sigma}{R_d}$
+Substutions for $\sigma_{pw} - \sigma_{po}$ and $P_o - P_w$ are made, resulting in
+
+\begin{equation}
+    \begin{split}
+        \Delta E_{IW} &= \sigma_{ow}(A_o\cos{\theta_c} - A_p - \frac{2 V_o}{R_d}) \\
+        \Delta E_{IO} &= -\sigma_{ow}(A_w\cos{\theta_c} + A_p - \frac{2 V_o}{R_d})
+    \end{split}
+\end{equation}
+
+From this the Pieranski model, the adsorption energy can be seen to depend on the contact angle, surface tension and contact area of the particles. This indicates that larger, neutrally wetting
 particles adsorbing onto interfaces with high surface tension have a high driving force for adsorption. \cite{ngai_particle-stabilized_2015,reeves_particle-size_2015} This adsorption process 
 can be orders of magnitude larger than the thermal energy of the system, calculated as $k_b T$ where $T$ is the temperature of the system and $k_b$ is the Boltzmann constant. This results in 
-irreversible adsorption of particles at interfaces \cite{binks_pickering_2001}.
+irreversible adsorption of particles at interfaces. \cite{binks_pickering_2001}
 
-In addition to the adsorption of particles on the interface, the contact angle of the particles determine the dispersed phase of an emulsion and its microstructure through the
-Bancroft rule \cite{velankar_non-equilibrium_2015,ngai_particle-stabilized_2015}. 
-Hydrophillic particles tend to prefer to form oil in water emulsions while hydrophobic particles prefer to form water in oil emulsions \cite{ngai_particle-stabilized_2015}.
+In addition to the adsorption of particles on the interface, the contact angle of the particles determine the dispersed phase of an emulsion and its microstructure.
+\cite{velankar_non-equilibrium_2015}
+Hydrophillic particles tend to prefer to form oil in water emulsions while hydrophobic particles prefer to form water in oil emulsions. \cite{ngai_particle-stabilized_2015}
 This occurs as the particles preferentially wet one phase over another, causing the interface to bend as the emulsion forms. Neutrally wetting particles are preferred in the formation of 
-bijels as no preferential curvature is imparted onto the bijels, fulfilling one of the requirements of a minimal surface in that the mean curvature must be zero \cite{jinnai_interfacial_2001}.
-
-% from a force 
-% balance between the force imparted from the particle on each fluid and the fluids between one another, known as the Young-Dupre equation.
-
-% \begin{equation}
-%     \cos{\theta_c} = \frac{\sigma_{po} - \sigma_{pw}}{\sigma_{ow}}
-% \end{equation}
-
-% Where $\theta_c$ is the contact angle, $\sigma_{po}$ is the surface tension between particle and oil, $\sigma_{pw}$ is the surface tension between particle and water and
-% $\sigma_{ow}$ is the surface tension between oil and water. The particle is considered to be preferentially wet by water or hydrophilic if $\theta_c < 90 ^{\circ}$ or 
-% hydrophobic if $\theta_c > 90 ^{\circ}$. The particle is said to be neutrally wetting if $\theta_c = 90 ^{\circ}$.
-
-% \begin{figure}
-%     \centering
-%     \includegraphics[scale = 0.5]{../figures/literature_review/particle_at_interface.png }
-%     \caption{Particle schematic at an interface demonstrating the various quantities of interest. Reprinted Figure 2.1 from
-%              Particle-Stabilized Emulsions and Colloids: Formation and Applications; Ngai, T., Bon, S. A. F., Eds.; RSC soft matter series; 
-%              with permission Royal Society of Chemistry, RSC Publishing Cambridge, 2015 under license number 1597404-1}
-%     \label{fig:pieranski_model}
-% \end{figure}
-
-% The energy of the system before and after particle adsorption is different and can be characterized for a simple system with parameters shown in Figure \ref{fig:pieranski_model},
-
-% \begin{equation}
-%     \Delta E_{IW} = E_I - E_w
-% \end{equation}
-
-% Where $\Delta E_{I}$ is the energy of the system when the particle is in the interface and $\Delta E_W$ is the energy of the system when the particle is completely in the water phase.
-% We define $\Delta E_{I}$ as
-
-% \begin{equation}
-%     E_I = A_w \sigma_{pw} + A_o\sigma_{po} + A_{I_1}\sigma_{ow} + V_w P_w + V_o P_o
-% \end{equation}
-
-% Where $A_w$ and $A_o$ are the surface areas of the particle in the water and oil phases respectively, $V_w$ and $V_o$ are the volumes of water and oil phases respectively and 
-% $P_w$ and $P_o$ are the pressures of water and oil phases respectively. $A_{I_1}$ is the area of the interface with the particle. 
-% A similar equation can be written for the energy of the water phase, $E_w$
-
-% \begin{equation}
-%     E_w = (A_w + A_o)\sigma_{pw} + A_{I_2}\sigma_{ow} + (V_w + V_o)P_w
-% \end{equation}
-
-% $A_{I_2}$ is the area of the interface without the particle. The change in the interface energy upon adsorption of the particle can be computed to obtain
-
-% \begin{equation}
-%     \Delta E_{IW} = A_o(\sigma_{po} - \sigma_{pw}) - A_p\sigma_{ow} + V_o(P_o - P_w)
-% \end{equation}
-
-% Substituting the Young-Laplace law for a spherical droplet, $P_w - P_o = \frac{2\sigma_{ow}}{R_d}$ where $R_d$ is the droplet size, for $(P_o - P_w)$ and the Young-Dupre contact angle
-% expression, the following is obtained
-
-% \begin{equation}
-%     \Delta E_{IW} = \sigma_{ow}(A_o\cos{\theta_c} - A_p - \frac{2 V_o}{R_d})
-% \end{equation}
-
-% A similar construction can be done for the oil phase to obtain
-
-% \begin{equation}
-%     \Delta E_{IW} = -\sigma_{ow}(A_w\cos{\theta_c} + A_p - \frac{2 V_o}{R_d})
-% \end{equation}
-
-% After making appropriate geometrical substitutions for $V_o$ and $A_p$, the Piersanski model is recovered,
-
-% \begin{equation}
-%     \Delta E_{ads} = \pi r^2 \sigma_{ow} (1 - |\cos{\theta_c}|)^2
-% \end{equation}
-
-% From this expression, the adsorption energy can be seen to depend on the contact angle, surface tension and contact area of the particles. This indicates that larger, neutrally wetting
-% particles adsorbing onto interfaces with high surface tension have a high driving force for adsorption. \cite{ngai_particle-stabilized_2015,reeves_particle-size_2015} This adsorption process 
-% can be orders of magnitude larger than the thermal energy of the system, calculated as $k_b T$ where $T$ is the temperature of the system and $k_b$ is the Boltzmann constant. This results in 
-% irreversible adsorption of particles at interfaces. \cite{binks_pickering_2001}
-
-% In addition to the adsorption of particles on the interface, the contact angle of the particles determine the dispersed phase of an emulsion and its microstructure. 
-% \cite{velankar_non-equilibrium_2015}
-% Hydrophillic particles tend to prefer to form oil in water emulsions while hydrophobic particles prefer to form water in oil emulsions. \cite{ngai_particle-stabilized_2015}
-% This occurs as the particles preferentially wet one phase over another, causing the interface to bend as the emulsion forms. Neutrally wetting particles are preferred in the formation of 
-% bijels as no preferential curvature is imparted onto the bijels, fulfilling one of the requirements of a minimal surface in that the mean curvature must be zero. \cite{jinnai_interfacial_2001}
+bijels as no preferential curvature is imparted onto the bijels, fulfilling one of the requirements of a minimal surface in that the mean curvature must be zero. \cite{jinnai_interfacial_2001}
 
@@
 \cite{mehrabadi_direct_2018, prosperetti_point-particle_2007, frohlich_validation_2018}
-In such models, 
-particles do not occupy physical volume and their influence on the fluid is typically introduced via body forces or perturbations to the chemical potential field. This 
-approach is computationally efficient and particularly useful for systems with a large number of particles or when only large-scale collective behavior is of interest. 
+In such models, particles do not occupy physical volume and their influence on the fluid is typically introduced via body forces or perturbations to the chemical potential field. 
+This approach is computationally efficient and particularly useful for systems with a large number of particles or when only large-scale collective behavior is of interest. 
 However, point particles cannot capture rotational dynamics, or hydrodynamic effects such as lubrication forces. Additionally, 
@@
 
-In contrast, explicit particle models represent colloids as finite-size rigid bodies with well-defined shape, volume, and surface boundary conditions. 
-\cite{ladd_numerical_1994, jansen_bijels_2011,gunther_timescales_2014}
-These particles interact 
+In contrast, explicit particle models represent colloids as finite-size rigid bodies with well-defined shape, volume, and surface boundary conditions
+\cite{ladd_numerical_1994, jansen_bijels_2011,gunther_timescales_2014}. These particles interact 
 with the surrounding fluid through no-slip or slip boundary conditions, and their motion responds dynamically to hydrodynamic, capillary, and interparticle forces. By resolving 
-particle geometry, these models allow for accurate representation of rotational motion, surface wetting and interfacial adsorption.
-\cite{jansen_bijels_2011, gunther_lattice_2013}
+particle geometry, these models allow for accurate representation of rotational motion, surface wetting and interfacial adsorption
+\cite{jansen_bijels_2011, gunther_lattice_2013}.
 This is important in bijel systems, where particle-induced jamming depend on particle shape, size, and surface wetting.
@@
 An intermediate approach between point particles and explicitly resolved rigid bodies is the immersed boundary method (IBM), which represents extended particles as collections of 
-point markers embedded in the fluid. \cite{peskin_immersed_2002, luo_immersed-boundary_2008, spandan_parallel_2017}
+point markers embedded in the fluid \cite{peskin_immersed_2002, luo_immersed-boundary_2008, spandan_parallel_2017}.
 These markers interact with the fluid through momentum exchange that impose motion onto the surrounding fluid, effectively reconstructing 
-the dynamics of a deformable or rigid object without requiring an explicit boundary mesh. \cite{peskin_immersed_2002, luo_immersed-boundary_2008, spandan_parallel_2017} 
-IBM has been widely used in biological and colloidal systems, to model the dynamics of deformable bodies. \cite{peskin_immersed_2002, luo_immersed-boundary_2008, spandan_parallel_2017}
+the dynamics of a deformable or rigid object without requiring an explicit boundary mesh \cite{peskin_immersed_2002, luo_immersed-boundary_2008, spandan_parallel_2017}.
+IBM has been widely used in biological and colloidal systems, to model the dynamics of deformable bodies \cite{peskin_immersed_2002, luo_immersed-boundary_2008, spandan_parallel_2017}.
 
-For systems in which interfacial structure, jamming, or near-field hydrodynamics play a central role as in bijel formation, explicit particle modeling 
-is generally preferred as we are able to resolve the interfacial structure and near field hydrodynamics without the complications of IBM.
+For systems in which interfacial structure, jamming, or near-field hydrodynamics of rigid bodies play a central role as in bijel formation, explicit particle modeling 
+is generally preferred as we are able to resolve the interfacial structure and near field hydrodynamics without the complications of IBM. This technique has been used in simulations of
+bijels based on the Lattice Boltzmann Method and phase field techniques demonstrating its effectiveness in modeling
+phenomena relevant to bijels \cite{jansen_bijels_2011,gunther_timescales_2014,carmack_tuning_2018}.
 
@@
 magnetic fields. Paramagnetic particles do not possess a permanent magnetic moment but acquire a reversible magnetization that aligns with the applied field and 
-vanishes once the field is removed. \cite{sinn_magnetically_2011} Their response is typically linear with field strength and does not involve magnetic hysteresis. 
+vanishes once the field is removed \cite{sinn_magnetically_2011}. Their response is typically linear with field strength and does not involve magnetic hysteresis. 
 In contrast, ferromagnetic particles exhibit strong, permanent magnetization due to the alignment of magnetic domains even in the absence of an external field. These particles can 
-exhibit hysteresis and significantly stronger dipole-dipole interactions. \cite{sinn_magnetically_2011}
+exhibit hysteresis and significantly stronger dipole-dipole interactions \cite{sinn_magnetically_2011}.
 As a result, ferromagnetic particles are more likely to form irreversible aggregates or chains, while paramagnetic particles 
@@
 
-Magnetic particles are often modeled using the magnetic dipole approximation, which treats each particle as possessing a single point dipole moment \(\vec{m}\) located at its center.
-\cite{davies_assembling_2014}
-The dipole-dipole interaction between two particles separated by a vector \(\vec{r}\) is described by the potential:
+% Magnetic particles can be modeled using the magnetic dipole approximation, which treats each particle as possessing a single point dipole moment \(\vec{m}\) located at its center
+% \cite{davies_assembling_2014}.
 
-\begin{equation}
-    U_{\text{d}} = \frac{\mu_0}{4\pi r^3} \left[ \vec{m}_1 \cdot \vec{m}_2 - 3(\vec{m}_1 \cdot \hat{r})(\vec{m}_2 \cdot \hat{r}) \right]
-\end{equation}
+% The dipole-dipole interaction between two particles separated by a vector \(\vec{r}\) is described by the potential:
 
+% \begin{equation}
+%     U_{\text{d}} = \frac{\mu_0}{4\pi |\vec{r}|^3} \left[ \vec{m}_1 \cdot \vec{m}_2 - 3(\vec{m}_1 \cdot \vec{r})(\vec{m}_2 \cdot \vec{r}) \right]
+% \end{equation}
+Magnetic particles can be modeled using the magnetic dipole approximation, which treats each particle as possessing a single point dipole moment \(\vec{m}\) located at its center
+\cite{davies_assembling_2014}. 
 This model captures the long-range, anisotropic nature of magnetic interactions and is commonly used due to its simplicity and computational efficiency. It is especially effective when 
@@
 To address these limitations, the demagnetization tensor method offers a more refined model by considering the particle as a uniformly magnetized ellipsoid and calculating the internal magnetic 
-field using an analytical or numerically tabulated demagnetization tensor. \cite{takahashi_ellipsoids_2017} 
+field using an analytical or numerically tabulated demagnetization tensor \cite{takahashi_ellipsoids_2017}. 
 This method accounts for the effect of particle shape on the distribution of internal magnetization and enables the modeling of induced magnetic 
-dipoles that respond to local fields. The total magnetic field of an ellipsoids can be written,
-
-\begin{equation}
-    \mathbf{H}(r) = \mathbf{H}_0 + \mathbf{N}(r)\mathbf{K}\mathbf{H}^{\dagger}
-\end{equation}
-
-Where $\mathbf{H}(r)$ is the total magnetic field of the ellipsoids, $\mathbf{H}_0$ is the inducing magnetic field in each direction,
-$\mathbf{K}$ is the susceptibility tensor and $\mathbf{H}^{\dagger}$ is the resultant uniform magnetic field at any point within
-the ellipsoids. \cite{takahashi_ellipsoids_2017}  This approach is particularly useful for modeling spheroidal or ellipsoidal particles and is widely 
+dipoles that respond to local fields. This approach is particularly useful for modeling spheroidal or ellipsoidal particles and is widely 
 used in magnetorheological systems, chain-forming ferrofluids, and dense suspensions where particle-particle interactions are shape-dependent.
 
-Since bijel formation and stabilization primarily depend on interfacial 
-jamming and long-range interactions between particles at fluid-fluid interfaces, the magnetic dipole approximation is often sufficient to model key behaviors such as chaining, orientation under external
-fields, and capillary-mediated assembly.
-However, if particle shape anisotropy, proximity effects, or induced magnetization in response to local fields are important, incorporating demagnetization tensors
-may offer improved realism.
+% The total magnetic field of an ellipsoids can be written,
+
+% \begin{equation}
+%     \mathbf{H}(r) = \mathbf{H}_0 + \mathbf{N}(r)\mathbf{K}\mathbf{H}^{\dagger}
+% \end{equation}
+
+% Where $\mathbf{H}(r)$ is the total magnetic field of the ellipsoids, $\mathbf{H}_0$ is the inducing magnetic field in each direction,
+% $\mathbf{K}$ is the susceptibility tensor and $\mathbf{H}^{\dagger}$ is the resultant uniform magnetic field at any point within
+% the ellipsoids. \cite{takahashi_ellipsoids_2017}  This approach is particularly useful for modeling spheroidal or ellipsoidal particles and is widely 
+% used in magnetorheological systems, chain-forming ferrofluids, and dense suspensions where particle-particle interactions are shape-dependent.
+
+Since bijel formation and stabilization primarily depend on interfacial jamming and long-range interactions between particles at fluid-fluid interfaces, the magnetic dipole approximation 
+is often sufficient to model key behaviors such as chaining, orientation under external fields, and capillary-mediated assembly. However, if incoroprating the effect of particle shape anisotropy, 
+proximity effects, or induced magnetization in response to local fields are important, incorporating demagnetization tensors may offer improved realism. Investigations of particle reorientation at
+interfaces has been conducted using the magnetic dipole model, showing that a rich variety of interfacial phenomena can be captured by this model such as the balance between capillary interactions
+and magnetic field induced torque and capillary self assembly of microparticles at interfaces. \cite{xie_direct_2017,davies_interface_2014,davies_assembling_2014}

### 2025-04-12 chapters/paper3.tex
Changes 1. Modified conclusion section in final remarks 2. Changes image sized in structural response of bijels 3. modified abstract and introduction to include structural analysis results
Changes 1. Modified rheology of bijels chapter

@@
     \centering 
-    \includegraphics[scale=0.5]{../figures/results/paper3/stress-time_compare.png} 
+    \includegraphics[scale=0.3]{../figures/results/paper3/stress-time_compare.png} 
     \caption{Time evolution of the shear stress of bijels stabilized with ellipsoidal particles as a function of the applied strain rate as
@@
 Therefore, the degree of interface angle change observed can shed light onto the rheological 
-differences of bijels stabilized by prolate and oblate particles as the shear stress determined is affected by the particle rotation on the interface.
+differences of bijels stabilized by prolate and oblate particles as the shear stress determined is affected by the particle rotation on the interface. We focus on
+the effect of particle alignment to the shear direction to isolate the effect of shear driven particle realignment at the interface.
 
-We analyzed the angle between each particles symmetry axis and the local interface normal by generating a mesh of the interface using the marching 
+To assess the particle alignment to the applied shear, we calculate the average angle to the direction of shear, $\langle \theta_z \rangle$. This is calculated
+by calculating the angle between the orientation vector $\vec{o}$ and the z axis $\vec{r_z}$ given by 
+$\theta_z = \arccos(\frac{ \vec{o} \cdot \vec{r_z} }{ |\vec{o}| |\vec{r_z}| })$. This is done for all particles with $\langle \theta_z \rangle$ calculated from
+by taking the numerical average of $\theta_z$ for all particles. The results are plotted in Figure \ref{fig:theta_z_specific}.
+
+\begin{figure} 
+    \centering 
+    \includegraphics[scale=0.3]{../figures/results/paper3/theta_z-time_compare-specific.png} 
+    \caption{Comparisons of the interfacial angle of bijels stabilized by ellipsoidal particles as a function of 
+             the applied shear rate at four different processing histories. We show that upon application of shear
+             particles tilt out of the interface reduces the interfacial area stabilized. $\bar{B}: 0 \to 1$ shows 
+             large variations in the interface angle.} 
+    \label{fig:theta_z_specific} 
+\end{figure}
+
+From Figure \ref{fig:theta_z_specific}, the effect of the aspect ratio of the particle stabilizer and the ordering of particles to the magnetic field. For oblate 
+particles, the change in $\langle \theta_z \rangle$ over time can be seen to stay approximately the same at shear rates below $Ca = 1e-4$ However at higher shear rates,
+$\langle \theta_z \rangle$ increases rapidly. When comparing this to the results when beginning with magnetic field ordering, $\langle \theta_z \rangle$ can be seen to
+stay approximately the same only at $Ca = 1e-6$. This indicates shear driven reorientation of particles at the interface occurs at higher shear rates in bijels stabilized
+with disordered particles and matching the trend observed in the yield stress. The results for the prolate particles show that particle order increases the applied shear
+necessary to cause particle reorientation on the interface. When taking the $\langle Q6 \rangle$ results into context from Figure \ref{fig:q6_rheology_init}, 
+the effect of magnetic field driven ordering of particles can be seen.
+
+As the particles are adsorbed onto the interface, there is an open question whether the reorientation of particles to the shear also causes the interface to move with the
+particles. To analyze this effect, we analyzed the angle between each particles symmetry axis and the local interface normal by generating a mesh of the interface using the marching 
 cubes algorithm and, for each particle, identified the nearest mesh vertex (excluding those beyond the length of the particle's long axis). We then calculated 
@@
     \centering 
-    \includegraphics[scale=0.3]{../figures/results/paper3/psi-time_compare.png} 
+    \includegraphics[scale=0.3]{../figures/results/paper3/psi-time_compare-specific.png} 
     \caption{Comparisons of the interfacial angle of bijels stabilized by ellipsoidal particles as a function of 
              the applied shear rate at four different processing histories. We show that upon application of shear
-             particles tilt out of the interface reduces the interfacial area stabilized. $\bar{B}: 0 \to 1$ shows 
-             large variations in the interface angle.} 
+             particles tilt out of the interface reduces the interfacial area stabilized.} 
     \label{fig:interface_angle_shear} 
@@
 
-As shown in Figure~\ref{fig:interface_angle_shear}, the interface angle $\langle \psi \rangle$ generally increases over time across all cases, with the 
-exception of the $\bar{B}: 0 \rightarrow 1$ condition. This indicates shear induced particle reorientation at the interface, indicating that particles are
-being pulled out of the interface. The exception at $\bar{B}: 0 \rightarrow 1$ is consistent with the findings presented in Chapter~\ref{chapter:aim2}, where the 
-observed behavior was attributed to particle reorientation toward the applied magnetic field. In all other cases, the gradual increase in $\langle \psi \rangle$ 
-suggests that particles are progressively reorienting out of the interface under the influence of shear. For oblate particles initialized from bijel templates 
-generated under $\bar{B} = 1$, the average initial interface angle is approximately 40°, indicating a pronounced tilt at the interface. As the tilt angle 
-increases, the energy barrier to rotate a particle further out of the interface decreases, leading to reduced hydrodynamic drag and, consequently, lower 
-effective viscosity. In contrast, the difference in initial interface angle between field- and non-field-aligned bijels stabilized by prolate particles 
-is much smaller—approximately 13.5° and 11.5°, respectively. This smaller variation helps explain the more modest changes in rheological response observed 
-in prolate systems, compared to the more pronounced field-dependent behavior in oblate particle-stabilized bijels.
+The interfacial angle results reveal how particle orientation relative to the local interface evolves under varying shear conditions, highlighting the interplay between particle shape, 
+initial ordering, and shear rate. For disc-like particles, $\langle \psi \rangle$ increases steadily with time, especially at higher shear rates, indicating that shear 
+flow drives discs to tilt further away from the interface normal. This effect is strengthened when the particles are initially ordered as the particles are easier to rotate out of the
+interface when they are tilted. In contrast, rod-like particles exhibit more modest changes in $\langle \psi \rangle$ as the particles are closer to lying flat on the interface, meaning
+that higher shear rates are needed to tilt them out of the interface. This effect can be seen more clearly when comparing the results for ordered disc and rod like particles, with
+rod like particles demonstrating smaller average interfacial tilting than disc like particles.
+
+Comparing the trends in $\langle \psi \rangle$ and $\langle \theta_z \rangle$ reveals a complementary view of how shear flow governs particle reorientation in bijels. For systems 
+stabilized with oblate particles under no magnetic field and prolate particles subjected to a magnetic field, the results show that at low shear rates, particles largely resist 
+reorientation due to interfacial jamming and anchoring forces. However, as the shear rate increases, both $\langle \psi \rangle$ and $\langle \theta_z \rangle$ rise, indicating that 
+particles begin to tilt away from both the interface normal and the shear direction. This suggests that while the particles remain adsorbed at the interface, the imposed shear is strong 
+enough to overcome local resistance and drive reorientation. The resulting changes in local packing and alignment are reflected in variations in the bond-orientational order parameter 
+$\langle Q6 \rangle$, particularly under conditions where the bijel retains structural integrity and resists complete flow-induced breakdown.
 
@@
 In this study, we investigated the rheological behavior of bijels stabilized by magnetically responsive ellipsoidal particles subjected to constant shear. 
-In systems like solvent transfer-induced phase separation (STrIPS) and volatile-induced phase separation (VIPS), rheology plays a key role in determining the
+In systems like Solvent Transfer Induced Phase Separation (STrIPS) and Vapor-Induced Phase Separation (VIPS), rheology plays a key role in determining the
 microstructure and morphology of the bijel. The presence of anisotropic particles and external magnetic fields further complicates this behavior 
@@
 
-To interpret these rheological differences, we analyzed both local structural ordering (via the Steinhardt $Q_6$ parameter) and particle orientation relative to 
-the interface. Increased magnetic alignment in prolate systems led to higher $Q_6$ values and lower interface angles, indicating that particles remained 
-well-anchored to the interface. This ordering enhanced stress distribution, leading to higher yield stress. In contrast, oblate particles 
-tended to tilt further from the interface when aligned, as confirmed by elevated interface angles and decreased $Q_6$, making the monolayer more susceptible to 
-shear-induced buckling and collapse. The increased interface angle of oblate particles after application of a field reduces the torque necessary to rotate particles
-out of the interface, resulting in the larger differences in shear stress calculated for bijels stabilized with oblate particles.
+To interpret these rheological differences, we analyzed the local structural ordering via the Steinhardt $Q_6$ parameter, and showed that increased magnetic alignment in 
+prolate systems led to higher $Q_6$ values which corresponds to greater friction between particles, which manifests as a greater yield stress. The opposite trend was
+characterized for oblate particles which explains the yield stress decrease as the particle order increases. To understand the effect of particle ordering 
+on the yielding behavior of the bijel better, we focused on the $\bar{B}:0 \rightarrow 0$ $\bar{B}:1 \rightarrow 1$. We showed from the angle of the particles to the applied
+shear, that bijels with greater local ordering resist shear better, as characterized by the lack of changes seen at lower shear rates compared to those with lower local
+particle order. At higher shear rates, the angle to the applied shear changes. The interface angle provides a complementary view of the interfacial dynamics of the particle 
+under shear, providing further evidence that the orientation of particles under shear corresponds to the local particle ordering. We also show that when the particles begin
+to reorient to the applied shear, the interface moves as well.
 
 These findings highlight the interplay between particle anisotropy, interfacial order, and external magnetic fields in tuning the mechanical properties of bijels. 
-By modulating particle alignment through magnetic stimuli, it is possible to tailor the yield stress and flow behavior of these materials—a property of potential 
-interest in fields such as soft robotics, drug delivery, and responsive templating. Moreover, the contrast in behavior between oblate and prolate particles 
-underscores the importance of shape-specific design in engineering structured fluids. In the next chapter, we extend this investigation to consider dynamic or 
-transient shear regimes and explore the reversibility of these structural transitions under cyclic loading and field modulation.
+By modulating particle alignment through magnetic stimuli, it is possible to tailor the yield stress and flow behavior of these materials relevant in fields such as soft 
+robotics, drug delivery, and responsive templating. Moreover, the contrast in behavior between oblate and prolate particles 
+underscores the importance of particles in engineering the structure of bijels.

### 2025-04-12 chapters/paper3.tex
Fixed caption for new images and fixed rheology property table

@@
              a function of the initial microstructure and applied magnetic field. The observed stress response is difficult to say when a steady
-             state is reached.} 
+             state is reached, with pseudo-steady states being obtained from the regions with the circular markers.} 
     \label{fig:stress_time} 
@@
      \hline\hline
-     $\bar{B}: 0 \rightarrow 0$ & 0.5 & 0.511 & 0.999 & $7.168 \cdot 10^{-5}$ \\ 
+     $\bar{B}: 0 \rightarrow 0$ & 0.5 & 0.570 & 0.946 & $9.818 \cdot 10^{-5}$ \\ 
      \hline
-     $\bar{B}: 0 \rightarrow 1$ & 0.5 & 0.579 & 0.944 & $4.008 \cdot 10^{-5}$ \\
+     $\bar{B}: 0 \rightarrow 1$ & 0.5 & 0.5601 & 0.920 & $4.591 \cdot 10^{-5}$ \\
      \hline
-     $\bar{B}: 1 \rightarrow 0$ & 0.5 & 0.642 & 0.888 & $4.945 \cdot 10^{-5}$ \\
+     $\bar{B}: 1 \rightarrow 0$ & 0.5 & 0.608 & 0.920 & $1.937 \cdot 10^{-5}$ \\
      \hline
-     $\bar{B}: 1 \rightarrow 1$ & 0.5 & 0.637 & 0.914 & $1.715 \cdot 10^{-5}$ \\
+     $\bar{B}: 1 \rightarrow 1$ & 0.5 & 0.630 & 0.922 & $1.188 \cdot 10^{-5}$ \\
      \hline
-     $\bar{B}: 0 \rightarrow 0$ & 2 & 0.561 & 0.965 & $4.618 \cdot 10^{-5}$ \\
+     $\bar{B}: 0 \rightarrow 0$ & 2 & 0.559 & 0.946 & $4.057 \cdot 10^{-5}$ \\
      \hline
-     $\bar{B}: 0 \rightarrow 1$ & 2 & 0.609 & 0.944 & $4.101 \cdot 10^{-5}$ \\
+     $\bar{B}: 0 \rightarrow 1$ & 2 & 0.602 & 0.939 & $4.360 \cdot 10^{-5}$ \\
      \hline
-     $\bar{B}: 1 \rightarrow 0$ & 2 & 0.597 & 0.899 & $5.025 \cdot 10^{-5}$ \\
+     $\bar{B}: 1 \rightarrow 0$ & 2 & 0.583 & 0.921 & $3.914 \cdot 10^{-5}$ \\
      \hline
-     $\bar{B}: 1 \rightarrow 1$ & 2 & 0.606 & 0.885 & $6.435 \cdot 10^{-5}$ \\ [1ex] 
+     $\bar{B}: 1 \rightarrow 1$ & 2 & 0.605 & 0.868 & $6.153 \cdot 10^{-5}$ \\ [1ex] 
      \hline
@@
     \includegraphics[scale=0.3]{../figures/results/paper3/theta_z-time_compare-specific.png} 
-    \caption{Comparisons of the interfacial angle of bijels stabilized by ellipsoidal particles as a function of 
-             the applied shear rate at four different processing histories. We show that upon application of shear
-             particles tilt out of the interface reduces the interfacial area stabilized. $\bar{B}: 0 \to 1$ shows 
-             large variations in the interface angle.} 
+    \caption{Comparisons of the average orientation of particles to the direction of the applied shear for bijels stabilized by
+             ellipsoidal particles as a function of the applied shear rate for bijels made with no field and a field strength of $\bar{B} = 1$,
+             keeping the field strength the same. We show that the orientation of particles to the applied shear is dependent on the
+             applied shear rate, particle ordering to the field and the particle shape.} 
     \label{fig:theta_z_specific} 
@@
     \includegraphics[scale=0.3]{../figures/results/paper3/psi-time_compare-specific.png} 
-    \caption{Comparisons of the interfacial angle of bijels stabilized by ellipsoidal particles as a function of 
-             the applied shear rate at four different processing histories. We show that upon application of shear
-             particles tilt out of the interface reduces the interfacial area stabilized.} 
+    \caption{Comparisons of the average orientation of particles to the interface for bijels stabilized by
+             ellipsoidal particles as a function of the applied shear rate for bijels made with no field and a field strength of $\bar{B} = 1$,
+             keeping the field strength the same. We show that the particles tilt out of the interface upon application of shear with the degree of
+             interfacial tilting a function of the initial particle order and particle shape.} 
     \label{fig:interface_angle_shear} 

### 2025-04-13 chapters/paper2.tex
Changes 1. Updating some refereces of analysis to link previous sections which do the same analysis to prevent repetition 2. Updating paper 2 to remove junk results

@@
 
-Sections of this chapter appear in a manuscript submitted to Springer link as part of the International Conference on Computational 
+Sections of this chapter appear in a manuscript submitted to Springerlink as part of the International Conference on Computational 
 Science (ICCS) 2025 in the Computing and Data Science for Materials Discovery and Design track, submission number 259 and is
@@
 
-The functional properties of bijels are inherently linked to their internal structure. For instance, lower tortuosities in the direction of ion transport yield improved 
-charge rates and cycling stability in battery electrodes \cite{ebner_tortuosity_2014, samdani_bicontinuous_2017}. In liquid-liquid extraction, the characteristic pore 
-lengthscale determines molecular selectivity \cite{khan_nanostructured_2022}, while in pharmaceutical applications, domain size influences drug release rates and cellular 
-behavior \cite{vanoli_bijels_2022, thorson_bijel-templated_2019}. Given the sensitivity of these properties to microstructural characteristics, the ability to dynamically 
-modify the morphology of bijels presents a promising strategy to adapt their behavior in situ for targeted performance.
+The functional properties of bijels are inherently linked to their internal structure. For instance, lower tortuosities in the direction of ion transport yield improved charge 
+rates and cycling stability in battery electrodes \cite{ebner_tortuosity_2014, samdani_bicontinuous_2017}. In liquid-liquid extraction, the characteristic pore length-scale governs 
+molecular selectivity \cite{khan_nanostructured_2022}, while in pharmaceutical applications, domain size influences drug release rates and cellular behavior 
+\cite{vanoli_bijels_2022, thorson_bijel-templated_2019}. Given the sensitivity of these properties to microstructural characteristics, the ability to dynamically modify bijel 
+morphology presents a promising strategy to adapt their behavior in situ for targeted performance. In this context, stimuli-responsive emulsions have garnered increasing interest 
+for applications requiring dynamic control over material properties, such as enhanced oil recovery, reaction separation, and therapeutic delivery 
+\cite{tham_magnetophoresis_2021, cui_stabilizing_2013, rozynek_opening_2019, lu_controllable_2020}.
 
-Stimuli-responsive emulsions have garnered increasing interest for applications requiring dynamic control over material properties, including enhanced oil recovery, reaction 
-separation, and therapeutic delivery \cite{tham_magnetophoresis_2021, cui_stabilizing_2013, rozynek_opening_2019, lu_controllable_2020}. These systems operate by using 
-external stimuli to alter interfacial configurations, enabling modulation of permeability, interfacial area, and morphology. For example, in emulsions stabilized by 
-spherical particles, electric fields can induce droplet deformation via particle unjamming and migration before re-establishing interfacial jamming \cite{cui_stabilizing_2013}. 
-Among various external stimuli, magnetic fields are particularly attractive due to their remote addressability, material compatibility, and bio-relevance. 
-Core-shell ferrite-hydroxyapatite nanorods, for instance, exhibit reversible morphological changes depending on initial particle orientation and field direction 
-\cite{nakayama_stimuli-responsive_2018}. In magnetically stabilized Pickering emulsions, magnetophoresis has been shown to drive particle migration and interfacial 
-distortion or collapse \cite{tham_magnetophoresis_2021, yang_rapid_2020, misra_magnetic_2020}. Notably, Karthikeyan and Schiller demonstrated that magnetic fields applied 
-during bijel formation can bias domain coarsening, producing anisotropic microstructures via orientation-specific jamming \cite{karthikeyan_formation_2024}. However, the 
-structural response of bijels to magnetic fields after formation remains poorly understood.
+These systems can be operated by using external stimuli to alter interfacial configurations, 
+enabling modulation of permeability, interfacial area, and morphology. For example, in emulsions stabilized by spherical particles, electric fields can induce droplet deformation via 
+particle unjamming and migration before re-establishing interfacial jamming \cite{cui_stabilizing_2013}. Among various stimuli, magnetic fields are particularly attractive due to their 
+remote addressability, material compatibility, and bio-relevance. Core-shell ferrite-hydroxyapatite nanorods, for instance, exhibit reversible morphological changes depending on initial 
+particle orientation and field direction \cite{nakayama_stimuli-responsive_2018}. In magnetically stabilized Pickering emulsions, magnetophoresis has been shown to drive particle migration 
+and interfacial distortion or collapse \cite{tham_magnetophoresis_2021, yang_rapid_2020, misra_magnetic_2020}. Chapter 4 demonstrated that magnetic fields applied during bijel formation can 
+bias domain coarsening, producing anisotropic microstructures via orientation-specific jamming \cite{karthikeyan_formation_2024}. However, the structural response of bijels to magnetic fields 
+after formation remains poorly understood, presenting an opportunity to explore how external fields may be used to dynamically reconfigure established bijel architectures.
 
@@
 Using a hybrid Lattice Boltzmann Method coupled with Molecular Dynamics, we simulate the formation and evolution of bijel structures stabilized by rod-like particles modeled as 
-magnetic dipoles. We find that increasing the applied magnetic field after formation induces significant microstructural changes, including increased domain anisotropy and 
-coarsening, up to a saturation threshold. In contrast, decreasing or removing the magnetic field results in minimal morphological change, suggesting a strong hysteresis effect. 
-Analysis reveals that particle unjamming, reorientation at the interface, and subsequent re-jamming are responsible for these structural transformations.
+magnetic dipoles. We find that increasing the applied magnetic field after formation induces microstructural changes characterized by increased domain anisotropy and 
+coarsening, up to a saturation threshold. In contrast, decreasing or removing the magnetic field results in minimal morphological change, suggesting that the structure is
+resilient to removal of stimuli. Analysis reveals that particle unjamming, reorientation at the interface, and subsequent re-jamming are responsible for these structural transformations.
 
@@
 the plateauing of the length scale obtained from the domain size, \(L\), computed from the first moment of the spherically averaged structure factor.
-\cite{kendon_3d_1999,kendon_inertial_2001} The structure factor is calculated from the density fields as,
-
-%
-\begin{equation}
-S(\vec{k},t) = \tilde{\phi}(\vec{k},t)\tilde{\phi}(-\vec{k},t) .
-\end{equation}
-%
-where \(\tilde{\phi}(\vec{k},t)\) is the Fourier
-transform of the order parameter fluctuations
-\(\phi(\vec{x},t)-\left\langle\phi\right\rangle\). Spherical averaging is 
-done by averaging the values of the structure factor where $k = |\vec{k}|$ is in
-the same bin, defined as
-
-%
-\begin{equation}
-S(k,t) = \frac{1}{n_k} \sum_{k-\frac{\Delta}{2}<k<k+\frac{\Delta}{2}} \tilde{\phi}(\vec{k},t)\tilde{\phi}(-\vec{k},t) ,
-\end{equation}
-
-The lengthscale is then defined as
-
-\begin{equation}
-    L = \frac{2 \pi}{\frac{ \sum_k S(k, t)k }{\sum_k S(k, t)}}
-\end{equation}
+\cite{kendon_3d_1999,kendon_inertial_2001} The procedure for the domain size can be found in Equation \ref{eq:spherically_averaged_structure_factor}.
 
@@
     \includegraphics[scale=0.5]{../figures/results/paper2/hysteresis_curve.png} 
-    \caption{Plot of the hysteresis curve of a bijel stabilized by magnetically responsive prolate particles. We observe that the domain size increases as we 
+    \caption{Plot of the domain size of a bijel stabilized by magnetically responsive prolate particles. We observe that the domain size increases as we 
     increase the applied magnetic field strength. However, upon decrease of the applied field strength the microstructure does not return to its previous value,
-    demonstrating microstructure hysteresis.} 
+    demonstrating kinetic arrest.} 
     \label{fig:hysteresis_curve} 
@@
 
-The hysteresis behavior is shown in Figure~\ref{fig:hysteresis_curve} demonstrates that as the field is increased, domain size increases, indicating coarsening 
-of the fluid domains in the bijel. Karthikeyan and Schiller showed that application of magnetic fields cause reordering of particles at interfaces towards the
+The domain sizes characterized in Figure~\ref{fig:hysteresis_curve} demonstrates that as the field is increased, domain size increases, indicating coarsening 
+of the fluid domains in the bijel. Chapter 4 showed that application of magnetic fields cause reordering of particles at interfaces towards the
 direction of the applied field, making the particle monolayer have nematic ordering. In the case of already formed bijels,
-this reorientation likely reduces the interface area stabilized, facilitating local unjamming and domain growth. In contrast, when the field strength is reduced, 
-the domain size does not revert to its original value, suggesting that the microstructure remains kinetically arrested in the coarsened configuration. This 
-irreversibility confirms a hysteretic response of the bijel structure to magnetic field cycling.
+this reorientation reduces the interface area stabilized, facilitating local unjamming and domain growth. In contrast, when the field strength is reduced, 
+the domain size does not revert to its original value, suggesting that the microstructure remains kinetically arrested in the coarsened configuration.
 
@@
 The results presented in Figure~\ref{fig:hysteresis_curve} demonstrate that changes in bijel domain size are dependent on the strength of the applied magnetic 
-field. For applications where bijels serve as porous material templates, microstructural characteristics directly govern performance metrics such as permeability, 
-selectivity, and mechanical stability. Furthermore, in many proposed stimuli-responsive applications, understanding not only the extent but also the mechanism
+field. in many proposed stimuli-responsive applications, understanding not only the extent but also the mechanism
 of structural response is critical for functionality and control. In this section, we investigate the dynamic structural response of bijels stabilized by randomly 
@@
 which visibly alters the interfacial configuration and the domain morphology. 
-To quantitatively characterize this response, we compute the average domain size as a function of time and magnetic field strength. Additionally, to assess 
-how particle alignment contributes to the structural transition, we overlay the evolution of the nematic order parameter with the domain size. This correlation 
-provides insight into the mechanistic role of particle ordering in driving microstructural transformation under applied magnetic fields \cite{veerman_phase_1992}.
-The nematic order parameter is calculated from the orientations of the particles as
-
-\begin{equation}
-\tens{Q} = \frac{1}{n_p} \sum_i \left( \frac{3}{2} \hat{\vec{o}}_i \otimes \hat{\vec{o}}_i -\frac{1}{2}\mathsf{1} \right) ,
-\end{equation}
-
-where \(\hat{\vec{o}}_i\) is the orientation of the \(i\)-th particles and \(n_p\) is the number of particles in the system. The largest eigenvalue of 
-\(\tens{Q}\) yields the nematic order parameter
-
-\begin{equation}
-S = \left\langle \frac{3}{2}\cos^2 (\theta) - \frac{1}{2} \right\rangle ,
-\end{equation}
-
-where \(\theta=\arccos(\hat{\vec{o}}_i\cdot\hat{\vec{n}})\) is the angle between the particle orientation and the nematic director \(\hat{\vec{n}}\). We plot $S$
-and $L$ over time in Figure \ref{fig:domain_size-field_on}
+To quantitatively characterize this response, we compute the average domain size as a function of time and magnetic field strength.
 
@@
 \cite{gunther_timescales_2014} Upon application of a magnetic field, the curves for \(S(t)\) increase before plateauing, indicating the parameter has reached
-its saturation value. Notably at stronger field strengths, $S(t)$ precedes the increase in domain size for both particle shapes analyzed. This time lag suggests 
-that nematic ordering is a precursor, but not the sole driver, of domain coarsening. Overall, these results confirm that domain coarsening in magnetically 
-responsive bijels occurs as a result of applied magnetic fields, with the degree of change observed dependent on the strength of the applied field.
+its saturation value. Notably at stronger field strengths, $S(t)$ precedes the increase in domain size for both particle shapes analyzed. Overall, these results 
+confirm that domain coarsening in magnetically responsive bijels occurs as a result of applied magnetic fields, with the degree of change observed dependent 
+on the strength of the applied field.
+
+In Chapter 4, it was identified that the microstructure became anisotropic upon application of magnetic fields. To characterize if the same is observed
+when applying a magnetic field onto a formed bijel, we plot the anisotropic domain size and tortuosity as a function of the applied magnetic field. The
+directional domain size is calculated using the technique outlined in Equation \ref{eq:directional_structure_factor} and the tortuosity is calculated
+using the technique used to generate the data for Figure \ref{fig:tau_B}.
+
+\begin{figure} 
+    \centering 
+    \includegraphics[scale=0.6]{../figures/results/paper2/domain_size_aniso-field_on.png} 
+    \caption{Plots of the anisotropic domain size (left) and tortuosity (right) as a function of magnetic field strength for bijels 
+             stabilized with oblate and prolate ellipsoids when raising the applied magnetic field. Prolate-stabilized bijels 
+             exhibit increased domain size parallel to the field ($L_{\parallel}$) and decreased size perpendicular ($L_{\perp}$), 
+             while the opposite trend is observed for oblate-stabilized systems. Tortuosity inversely correlates with domain size in 
+             both cases.} 
+    \label{fig:domain_size_aniso-field_on} 
+\end{figure}
+
+Figure~\ref{fig:domain_size_aniso-field_on} shows that the application of a magnetic field induces clear domain size anisotropy in bijels stabilized by both oblate 
+and prolate particles. Even at zero field, a small degree of anisotropy is observed, which increases substantially with rising field strength. For oblate particles, 
+the domain sizes perpendicular (\(L_\perp\)) and parallel (\(L_\parallel\)) to the applied field increase by approximately 73\% and 7\%, respectively. In contrast, 
+for prolate particles, \(L_\perp\) increases by 10\%, while \(L_\parallel\) increases by 44\%. These results indicate that the dominant direction of coarsening 
+depends on particle morphology: oblate particles promote greater coarsening perpendicular to the field, while prolate particles favor coarsening parallel to the 
+field. This trend reflects how particles reorient in response to the applied magnetic field. As particles unjam and rejam 
+at the interface, they adopt morphology- and field-dependent orientations that result in directionally biased surface coverage, manifesting as anisotropic domain 
+growth.
+
+The right panel of Figure~\ref{fig:domain_size_aniso-field_on} presents the corresponding changes in directional tortuosity. Initially, the tortuosity values 
+for both directions are close to \(\tau \approx 1.5\), aligning with previous simulations of gyroidal and co-continuous structures using Lattice Boltzmann methods 
+\cite{luo_macroscopic_2020}. Upon applying the magnetic field, \(\tau_\perp\) decreases while \(\tau_\parallel\) increases. This inverse relationship between 
+tortuosity and domain size is consistent with prior findings \cite{karthikeyan_formation_2024}, where larger domains exhibited 
+reduced tortuosity. The observed anisotropic response suggests that magnetic fields not only influence interfacial particle orientation but also lead to 
+direction-dependent transport pathways in the bijel. Moreover, the extent and direction of anisotropy are strongly influenced by the particle morphology, 
+particularly the axis of symmetry, which dictates the dominant direction of microstructural reorganization under field application. The time dependence of
+the reorientation of particles at the interface is characterized next.
 
@@
 
-Building on the observed time lag between the onset of particle alignment and domain coarsening, we next investigate the underlying dynamics of particles at the 
-interface. While nematic ordering appears to precede structural changes, the delayed increase in domain size at higher magnetic field strengths suggests that 
-additional factors influence the system's response. In this context, capillary interactions between particles and the fluid interface, as well as steric hindrance 
-from neighboring particles, may act to resist or slow particle rearrangement, thereby affecting the timescale of domain evolution. To better understand these 
-phenomena, we focus on the dynamic behavior of the interfacial particle monolayer. As a first step, we visualize the initial and final configurations of bijels 
-stabilized by prolate ellipsoids before and after application of a magnetic field, providing qualitative insight into particle displacement and reorganization 
-at the interface.
+The primary effect of the magnetic field is the torque it exerts on the particles' magnetic dipoles, driving them to rotate and align with the field direction. 
+This field-induced alignment is clearly evident in the simulation snapshots shown in Figure~\ref{fig:particle_viz-field_on}. In the absence of a magnetic field 
+(\(\bar{B} = 0\)), the particles exhibit random orientations at the interface. However, when the field is applied (\(\bar{B} = 1\)), the dipoles display a strong 
+degree of orientational order aligned with the field direction.
 
@@
 
-The snapshow shows that in the absence of a magnetic field, minor variations in particle orientation and position occur due to steric interactions, as 
-previously observed by Günther et al.~\cite{gunther_timescales_2014}. However, the application of a magnetic field induces clear orientational ordering of the 
-particle monolayer, with particles aligning along the field direction and reorganizing into distinct interfacial arrangements. These changes suggest that both 
-capillary forces and steric hindrance are modified upon field application. While particles naturally prefer to lie flat at the interface to minimize interfacial 
-adsorption energy, the applied field competes with this tendency, reorienting the particles and disrupting their initial packing.
+To analyze the reorientation of particles to the magnetic field over time, the nematic order parameter of the particle monolayer is calculated. This is done
+in the same technique used for Figure \ref{fig:nematic_time}.
 
-To quantify the orientation of the particles relative to the interface, we analyzed the angle between each particles symmetry axis and 
-the local interface normal. We generated a mesh of the interface using the marching cubes algorithm and, for each particle, identified the nearest mesh vertex 
-(excluding those beyond the length of the particle's long axis). We then calculated the angle \(\psi\) between the particle orientation vector 
-\(\hat{\vec{o}}_i\) and the local surface normal. We plot the time evolution of $\psi$ in Figure \ref{fig:interface_angle-field_on}.
+\begin{figure} 
+    \centering 
+    \includegraphics[scale=0.4]{../figures/results/paper2/nematic-field_on.png} 
+    \caption{Evolution of the nematic order parameter \( S \) over time for bijels stabilized with disc-like particles (left) and rod-like particles (right), 
+             after the application of varying magnetic field strengths.} 
+    \label{fig:nematic-field_on} 
+\end{figure}
+
+From Figure \ref{fig:nematic-field_on}, as field strength increases, particles exhibit earlier and more pronounced alignment, with \( S \) approaching unity 
+for \( \bar{B} = 1.0 \), indicating strong global nematic order. In contrast, systems with no applied field (\( \bar{B} = 0 \)) remain disordered throughout, 
+with low \( S \) values. The time-dependent development of nematic ordering reflects the interplay between magnetic torque and interfacial mechanics. 
+The increase in \( S \) suggests a process of unjamming and re-jamming at the fluid-fluid interface caused by the magnetic field inducing rotational 
+motion of the dipolar particles, overcoming initial interfacial jamming and allowing particles to realign to the field. As alignment 
+progresses, the particles re-jam. In Chapters 4 and 5, the application of the magnetic field modified the angle of the particle to the interface and the
+local packing of the particles. This was caused by orientational of the particles to the magnetic field causing direction dependent cessation of coarsening.
+To understand how the rotation of particles affects the particle monolayer, the interfacial angle $\langle \psi \rangle$ is analyzed to understand
+how the nematic transition takes place at the interface. $\langle \psi \rangle$ is calculated in the same method as that used to generate Figure \ref{fig:psi_time} 
+in Chapter 4, with the results presented in Figure \ref{fig:interface_angle-field_on}.
+
+% `To understand the interfacial dynamics, the interface angle and the lo This interpretation motivates complementary measurements of the interfacial angle \( \langle \psi \rangle \) and local 
+% packing order \( \langle Q_6 \rangle \), which together provide deeper insight into how the transition from disordered to ordered interfacial states is governed by 
+% field strength and particle anisotropy.
+
+% The snapshot shows that in the absence of a magnetic field, minor variations in particle orientation and position occur as the bijel is not jammed, as 
+% previously observed by Günther et al.~\cite{gunther_timescales_2014}. However, the application of a magnetic field induces clear orientational ordering of the 
+% particle monolayer, with particles aligning along the field direction and reorganizing into distinct interfacial arrangements. Newton et al. showed that
+% the lowest energy state of arrays of ellipsoidal particles are not at the same orientations to one another when tilted by a magnetic field at an interface.
+% \cite{newton_capillary_2018} These changes suggest that both 
+% capillary forces and steric hindrance are modified upon field application. While particles naturally prefer to lie flat at the interface to minimize interfacial 
+% adsorption energy, the applied field competes with this tendency, reorienting the particles and disrupting their initial packing. The angle of the particle to the
+% interface can be used to characterize the reorientation of particles to the magnetic field. The calculation is done in the same way as what is done in Figure
+% \ref{fig:psi_time} in Chapter 4.'
 
@@
 
-For bijels stabilized by prolate particles, a similar but more subtle trend is observed. The initial value of \(\langle \psi \rangle\) starts around \(10^\circ\), 
-gradually increases, and then exhibits a small plateau followed by a slight decline. While the rate and magnitude of the initial increase are field-dependent, 
-the final values converge more closely across different field strengths, suggesting that the field sensitivity of interface tilt is weaker for prolate particles. 
-The overall changes in \(\langle \psi \rangle\) are also smaller in magnitude compared to those in oblate systems, indicating that prolate particles experience 
-less pronounced reorientation at the interface.
+For bijels stabilized by prolate particles, a similar trend is observed. The initial value of \(\langle \psi \rangle\) starts around \(10^\circ\), gradually increases, 
+and then exhibits a plateau followed by a slight decline. While the rate and magnitude of the initial increase are field-dependent, the final values converge more 
+closely across different field strengths, suggesting that the field sensitivity of interface tilt is weaker for prolate particles. The overall changes in \(\langle \psi \rangle\) 
+are also smaller in magnitude compared to those in oblate systems, indicating that prolate particles experience less pronounced reorientation at the interface. This is due to 
+the smaller effective lever arm for magnetic torque in prolate particles, which limits their rotational response to the field.
 
@@
 it does not capture how particles reorganize at the interface, observed in Figure \ref{fig:microstructure_viz-field_on} Since the evolution of microstructure is 
-influenced not only by tilt but also by the steric effects of interfacial particles, we also assess the Steinhardt bond orientational parameter. 
-We compute the six fold bond orienational parameter $q_6$ which measures the degree of hexagonal arrangement of particles at the interface.
-\cite{steinhardt_bond-orientational_1983, lechner_accurate_2008, mickel_shortcomings_2013} These parameters characterize the local structural ordering by projecting 
-the orientations of neighboring particles onto spherical harmonics of degree \(l\), and are defined as
-
-\begin{equation}
-q_l(i) = \left( \frac{4\pi}{2l+1} \sum_{m=-l}^{l} \left| \frac{1}{N(i)} \sum_{j=1}^{n(i)} Y_{lm}(\vec{r}_{ij}) \right|^2 \right)^{\frac{1}{2}} ,
-\end{equation} 
-%\TODO{update formula to the one actually used}
-
-Here, \(n(i)\) denotes the number of nearest neighbors of particle \(i\), \(\vec{r}_{ij}\) is the vector connecting the centers of particles \(i\) and \(j\), and 
-\(m\) is an integer ranging from \(-l\) to \(l\) that indexes the spherical harmonic components \(Y_{lm}\). Neighbor lists are typically defined using a fixed cutoff 
-radius around each particle, identifying nearby particles as neighbors. We calculate the python package Freud to calculate the bond order parameters and use a Voronoi 
-cell to determine the particle neighborhood rather than the standard distance criterion \cite{ramasubramani_freud_2020,mickel_shortcomings_2013}. The Voronoi-based 
-method avoids the need for a predefined cutoff and yields more robust neighbor definitions, particularly in disordered systems. Bond orientational order parameters 
-have been widely employed to study structural transitions in colloidal and ceramic systems, including crystallization, nucleation, and glass formation 
-\cite{vagberg_glassiness_2011, besseling_three-dimensional_2007, schall_structural_2007, ozawa_jamming_2012} We plot the time evolution of $\psi$ in Figure 
-\ref{fig:Q6-field_on}.
+influenced not only by tilt but also by the steric effects of interfacial particles, we also assess the Steinhardt bond orientational parameter. The Steinhardt
+bond orientational parameter is calculated using the Freud package using the same technique described in Equation \ref{eq:steinhardt_definition}. The results
+are plotted in Figure \ref{fig:Q6-field_on}.
 
@@
 evolves toward a new jammed state. The rate of change of \(\langle Q_6 \rangle\) significantly decreases toward the end of the simulation, suggesting the onset 
-of kinetic arrest. The final value of \(\langle Q_6 \rangle\) is dependent on the applied magnetic field strength, with higher field strengths 
-resulting in lower final ordering, potentially due to increased variance in the interfacial angle, reducing packing efficiency.
-
-In contrast, for bijels stabilized by prolate particles, \(\langle Q_6 \rangle\) increases monotonically with time after the field is applied. The degree 
+of kinetic arrest. In contrast, for bijels stabilized by prolate particles, \(\langle Q_6 \rangle\) increases monotonically with time after the field is applied. The degree 
 of ordering and the rate of increase both scale positively with magnetic field strength. The early stage is characterized by a modest rise in \(\langle Q_6 \rangle\), 
@@
 becomes dominant. The timing and extent of these regimes are also field-dependent with stronger fields result in earlier onset of ordering and higher final values 
-of \(\langle Q_6 \rangle\). Notably, for all applied fields, the final ordering significantly exceeds that of the zero-field case. These results highlight that the 
-response of interfacial particle order to magnetic fields is morphology-specific as oblate particles undergo a disruption and partial recovery of order, 
-while prolate particles experience continuous enhancement of local ordering.
+of \(\langle Q_6 \rangle\).
 
-\subsubsection{Microstructural effects of particle reordering}
-
-Karthikeyan and Schiller identified that the reorientation of particles at the interface due to the application of magnetic fields caused domain size anisotropy
-driven by the directional cessation of domain coarsening. \cite{karthikeyan_formation_2024} In this study, we have established that the mechanism of domain size change
-arises from magnetic field driven rotations of particles at the interface, causing unjamming of the particle monolayer before rejamming and locking in the new
-microstructure. Due to the differences in mechanism, we turn to investigate the anisotropic microstructure of the bijel at the final timestep.
-
-We probe the domain anisotropy using the directional second moment of the structure factor, computed along each Cartesian axis from the full structure factor shown
-below. \cite{jansen_bijels_2011, gunther_timescales_2014}. 
-    %
-    \begin{equation}
-    L_\beta(t)=2\pi\sqrt{\frac{\sum_{\vec{k}}S(\vec{k},t)}{\sum_{\vec{k}}k_\beta^2 S(\vec{k},t)}} .
-    \end{equation}
-    %
-    This allows us to compute a domain size parallel
-    (\(L_\parallel=L_z\)) and perpendicular (\(L_\perp=(L_x+L_y)/2\)) to the
-    direction of \(\vec{B}\) separately. The average domain size \(L_d(t)\)
-    is computed as \(L_d(t)=\sum_\beta L_\beta(t) / 3\).
-    %
-    \begin{equation}
-    L_d(t)=2\pi\sqrt{\frac{\sum_{\vec{k}}S(\vec{k},t)}{\sum_{\vec{k}}\sum_\beta k_\beta^2 S(\vec{k},t)}} .
-    \end{equation}
-    %
-Previous studies have also shown that a domain size increase is usually accompanied by a decrease in
-tortuosity. \cite{karthikeyan_formation_2024} To determine whether these structural 
-changes impact macroscopic transport properties, we also analyzed the tortuosity of the bijels. We utilize the package \texttt{taufactor} that implements
-a periodic boundary condition solver and calculates the diffusive tortuosity of the bijel structures. Porous structures were 
-extracted by binarizing the final order parameter field using a zero threshold, isolating the largest connected (percolating) domain. We plot the results of
-the directional domain size and tortuosity in Figure \ref{fig:domain_size_aniso-field_on}
-
-\begin{figure} 
-    \centering 
-    \includegraphics[scale=0.6]{../figures/results/paper2/domain_size_aniso-field_on.png} 
-    \caption{Plots of the anisotropic domain size (left) and tortuosity (right) as a function of magnetic field strength for bijels 
-             stabilized with oblate and prolate ellipsoids when raising the applied magnetic field. Prolate-stabilized bijels 
-             exhibit increased domain size parallel to the field ($L_{\parallel}$) and decreased size perpendicular ($L_{\perp}$), 
-             while the opposite trend is observed for oblate-stabilized systems. Tortuosity inversely correlates with domain size in 
-             both cases.} 
-    \label{fig:domain_size_aniso-field_on} 
-\end{figure}
-
-Figure~\ref{fig:domain_size_aniso-field_on} shows that the application of a magnetic field induces clear domain size anisotropy in bijels stabilized by both oblate 
-and prolate particles. Even at zero field, a small degree of anisotropy is observed, which increases substantially with rising field strength. For oblate particles, 
-the domain sizes perpendicular (\(L_\perp\)) and parallel (\(L_\parallel\)) to the applied field increase by approximately 73\% and 7\%, respectively. In contrast, 
-for prolate particles, \(L_\perp\) increases by 10\%, while \(L_\parallel\) increases by 44\%. These results indicate that the dominant direction of coarsening 
-depends on particle morphology: oblate particles promote greater coarsening perpendicular to the field, while prolate particles favor coarsening parallel to the 
-field. This trend is consistent with previous findings and reflects how particles reorient in response to the applied magnetic field. As particles unjam and rejam 
-at the interface, they adopt morphology- and field-dependent orientations that result in directionally biased surface coverage, manifesting as anisotropic domain 
-growth.
-
-The right panel of Figure~\ref{fig:domain_size_aniso-field_on} presents the corresponding changes in directional tortuosity. Initially, the tortuosity values 
-for both directions are close to \(\tau \approx 1.5\), aligning with previous simulations of gyroidal and co-continuous structures using Lattice Boltzmann methods 
-\cite{luo_macroscopic_2020}. Upon applying the magnetic field, \(\tau_\perp\) decreases while \(\tau_\parallel\) increases. This inverse relationship between 
-tortuosity and domain size is consistent with prior findings \cite{karthikeyan_formation_2024}, where larger domains exhibited 
-reduced tortuosity. The observed anisotropic response suggests that magnetic fields not only influence interfacial particle orientation but also lead to 
-direction-dependent transport pathways in the bijel. Moreover, the extent and direction of anisotropy are strongly influenced by the particle morphology, 
-particularly the axis of symmetry, which dictates the dominant direction of microstructural reorganization under field application.
+The final value of \(\langle Q_6 \rangle\) is dependent on the applied magnetic field strength with oblate and prolate particles being affected by the field in
+different ways. The trends match that characterized in Chapter 5, with oblate particles having lower hexagonal ordering upon application of a magnetic field
+and prolate particles having a greater magnetic field. This was found to be due to oblate particles preferring to stack when magnetic fields are applied while
+prolate particles order end to end ot side to side \cite{dabat_mesoscale_2018, eatson_capillary_2023}. This reordering can also explain why oblate particles
+tilt out of the interface more than prolate particles.
 

### 2025-04-13 chapters/paper2.tex
removed increasing applied field for suspected errors in data collection

@@
 
-\subsection{Increasing the applied field onto a bijel made with a magnetic field}
-\subsubsection{Field strength dependence on domain size}
-\label{section:increasing-the-applied-field}
-
-The hysteresis curve presented earlier in Figure~\ref{fig:hysteresis_curve} revealed that microstructural changes diminish 
-with each successive increase in magnetic field strength. This saturation behavior suggests a direct link between the extent of domain coarsening 
-and the evolving order within the interfacial particle monolayer. As demonstrated in the previous section, once the bijel is jammed, further domain 
-growth is constrained by local rearrangements of the particles at the interface, which are themselves influenced by the degree of particle alignment 
-and packing. To investigate this relationship further, we now examine how pre-existing particle order, established during bijel formation, affects 
-the system's responsiveness to a subsequent applied magnetic field.
-
-Specifically, we prepare bijel templates by applying magnetic fields of strength \(\bar{B}_{\text{template}} = 0, 0.2, 0.5, 1.0\) during the phase separation 
-process, thereby generating structures stabilized by ellipsoidal particles with varying initial degrees of interfacial order. A constant magnetic field of 
-\(\bar{B}_z = 1.0\) is then applied to each system post-jamming, and we monitor the microstructure evolution over a simulation duration of \(t = 10^5\) 
-timesteps. For clarity, we adopt simplified notation in the discussion that follows—for example, \(\bar{B}_z: 0.0 \rightarrow 1.0\) denotes a bijel 
-formed without a field and then subjected to a field of \(\bar{B}_z = 1.0\) during the response phase. We begin by qualitatively assessing the 
-structural changes induced in bijels formed with different levels of initial particle ordering, as shown in Figure~\ref{fig:microstructure_viz-field_up}.
-
-\begin{figure}
-\centering 
-\includegraphics[scale=0.6]{../figures/results/paper2/microstructure_viz-field_up.png} 
-\caption{Visualizations of bijels stabilized by prolate ellipsoidal particles at the initial (left column) and final (right column)
-         timepoints for two magnetic field conditions. The top row corresponds to the case where the field is increased from 
-         \(\bar{B}_z = 0.2\) to \(\bar{B}_z = 1.0\), while the bottom row shows a bijel formed and evolved under a constant field of 
-         \(\bar{B}_z = 1.0\). }
-\label{fig:microstructure_viz-field_up}
-\end{figure}
-
-Figure \ref{fig:microstructure_viz-field_up} demonstrates a clear initial microstructure dependent structural response, 
-where the extent of domain coarsening and anisotropy is greater 
-in the system that undergoes a field increase. In the \(\bar{B}_z: 0.2 \rightarrow 1.0\) case, fluid domains exhibit more pronounced reorganization and growth 
-compared to the \(\bar{B}_z: 1.0 \rightarrow 1.0\) case, where the structure remains largely unchanged over time.
-Additionally, a qualitative increase in particle alignment with the field direction is observed in the top row, indicating that pre-existing particle order 
-limits the extent of reorientation and structural evolution under further field application. These results suggest that the degree of microstructural change 
-is influenced by the difference between the initial and final magnetic field strengths, and by the capacity of the interfacial particles to reorient at the interface. 
-We quantify these trends in the following section by analyzing the time evolution of domain size and the nematic order parameter in 
-Figure~\ref{fig:domain_size-field_up}.
-
-\begin{figure} 
-\centering 
-\includegraphics[scale=0.6]{../figures/results/paper2/domain_size-field_up.png} 
-\caption{Plot of the spherically averaged domain size normalized with $Rp(L/R)$ of the particle in markers and the nematic order parameter in lines. 
-         We show that the domain size change measured is correlated to the change in the particle ordering, characterized using the nematic order parameter.} 
-\label{fig:domain_size-field_up} 
-\end{figure}
-
-Figure~\ref{fig:domain_size-field_up} presents the evolution of domain size \(L/R\) and nematic order parameter \(S\) for bijels stabilized by oblate (left) 
-and prolate (right) particles under various field transition conditions. We define \(\Delta \bar{B}\) as the difference between the final and initial magnetic 
-field strengths. The onset and magnitude of the microstructural response are both observed to be dependent on \(\Delta \bar{B}\), indicating that a stronger 
-magnetic field change provides a greater driving force for structural reorganization. Specifically, when \(\Delta \bar{B} = 1.0\), the resulting domain size 
-increases by approximately 5\% for oblate particles and 2\% for prolate particles. These structural changes diminish progressively as \(\Delta \bar{B}\) decreases.
-
-The accompanying nematic order parameter \(S\) also correlates strongly with \(\Delta \bar{B}\), suggesting that domain size evolution is intrinsically linked 
-to the extent of particle alignment within the system. Higher values of \(\Delta \bar{B}\) induce greater particle reorientation, which facilitates is linked to
-reconfiguration of particles at the interface, thereby enabling domain coarsening. These findings highlight that characteristic length scale evolution is jointly 
-governed by both particle aspect ratio and the magnitude of magnetic field variation. To further quantify anisotropic changes in microstructure, we define the 
-relative change in directional domain size as \(\Delta L = \frac{L_f - L_i}{L_i}\), where \(L\) refers to either \(L_{\perp}\) or \(L_{\parallel}\). 
-The same formulation is applied to the directional tortuosity components. These metrics allow us to isolate and characterize the \(\Delta \bar{B}\)-dependent 
-evolution of anisotropic structural features. The results are presented and analyzed in Figure~\ref{fig:domain_size_aniso-field_up}.
-
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.6]{../figures/results/paper2/domain_size_aniso-field_up.png} 
-\caption{Plotting the anisotropic domain sizes and tortuosity at the final timestep on the left and right respectively for bijels stabilized with 
-         oblate and prolate ellipsoidal particles starting at different particle orders. We plot these results against the change in the applied field 
-         strength, $\Delta B$. The anisotropic domain size is inversely correlated to the tortuosity and $L_{perp}$ changes for 
-         a bijel made with $\bar{B} = 1 \rightarrow 1$ and $\bar{B}: 0 \rightarrow 1$ differ, suggesting that the processing history of the bijel is important.} 
-\label{fig:domain_size_aniso-field_up} 
-\end{figure}
-
-Figure~\ref{fig:domain_size_aniso-field_up} quantifies the directional changes in domain size (\(\Delta L\)) and tortuosity (\(\Delta \tau\)) as a 
-function of magnetic field variation \(\Delta \bar{B}\), for bijels stabilized by oblate (blue) and prolate (red) particles. The results show that 
-increasing the applied magnetic field leads to enhanced domain size anisotropy in both particle systems. Even in the absence of a magnetic field 
-change (\(\Delta \bar{B} = 0\)), a small degree of anisotropy is observed, which becomes more pronounced as \(\Delta \bar{B}\) increases. For oblate 
-particles, the perpendicular and parallel domain sizes increase by approximately 73\% and 7\%, respectively. In contrast, for prolate particles, the 
-increases are 10\% and 44\%, respectively. The direction of dominant coarsening aligns with prior findings and reflects how particles reorient under 
-the influence of the magnetic field—oblate particles tend to reorient and promote coarsening perpendicular to the field, while prolate particles favor 
-coarsening along the field direction.
-
-The right panel shows the corresponding changes in directional tortuosity. The initial tortuosity is approximately \(\tau \approx 1.5\), consistent with 
-Lattice Boltzmann simulations of gyroid and co-continuous porous structures \cite{luo_macroscopic_2020}. Upon field application, \(\tau_\perp\) 
-generally decreases while \(\tau_\parallel\) increases, in agreement with the observed domain size changes. These trends are consistent with prior 
-work \cite{karthikeyan_formation_2024}, which demonstrated an inverse relationship between domain size and tortuosity. The results confirm that 
-magnetic field-driven domain anisotropy significantly affects the transport properties of the bijel, with particle shape and orientation playing a 
-critical role in determining the direction and magnitude of these structural changes. The shape of the plots indicate that the decrease in structural response
-is correlated strongly to an increase in the ordering of the particles. In the next section, we focus more on the particle monolayer.
-
-\subsubsection{Particle reorientation as a function of initial particle order}
-
-The results presented thus far demonstrate that the extent of microstructural evolution, particularly domain anisotropy and coarsening, decreases sharply 
-as the difference between the initial and final magnetic field strengths (\(\Delta \bar{B}\)) approaches zero. This exponential decay in structural 
-response suggests that beyond a certain threshold, the system becomes increasingly resistant to reorganization. Since domain-scale changes are driven 
-by local particle rearrangements at the interface, this diminishing response points to a progressively reduced capacity of the particle monolayer to 
-unjam and reorient under small field perturbations. To better understand the origin of this resistance to structural change, we now shift our focus to 
-the particle monolayer itself. Specifically, we examine how initial ordering within the interfacial particle layer governs the system's ability to respond 
-to further magnetic stimuli.
-
-\begin{figure} 
-\centering 
-\includegraphics[scale=0.5]{../figures/results/paper2/particle_viz-field_up.png} 
-\caption{Snapshots of the structural evolution of the particle monolayer in bijels stabilized by prolate ellipsoids 
-         under different magnetic field conditions. The top row corresponds to a simulation where the field is increased from 
-         \(\bar{B} = 0.2\) to \(\bar{B} = 1.0\), while the bottom row shows a system maintained at a constant field of \(\bar{B} = 1.0\) throughout.} 
-\label{fig:particle_viz-field_up} 
-\end{figure}
-
-Even at the initial timepoint of the \(\bar{B}: 0.2 \rightarrow 1.0\) run, a majority of particles are already aligned with the field direction. 
-Upon increasing the field strength to \(\bar{B} = 1.0\), nearly all visible particles exhibit strong alignment, consistent with the high nematic order 
-parameter values observed in Figure~\ref{fig:domain_size-field_up}.
-The visual alignment of the particles long axes with the magnetic field highlights the mechanism driving anisotropic domain formation in the bijel. 
-As particle orientation is locked in by magnetic torque, the interfacial arrangement becomes directionally biased, influencing the resulting domain 
-morphology. To quantitatively link this particle-scale reorientation to the observed structural anisotropy, we next evaluate the average interface 
-angle \(\langle \psi \rangle\) in Figure \ref{fig:interface_angle-field_on}
-
-\begin{figure} 
-    \centering 
-    \includegraphics[scale=0.6]{../figures/results/paper2/psi-field_up.png} 
-    \caption{Plots of the evolution of the average interface angle \(\langle \psi \rangle\) for bijels stabilized 
-             by oblate (left) and prolate (right) particles, as a function of the initial microstructure and subsequent magnetic field application.
-             The dynamics observed can be seen to be a function of the initial microstructure.} 
-    \label{fig:interface_angle-field_up} 
-\end{figure}
-
-The results show that the initial particle ordering plays a significant role in the interfacial response. As characterized earlier for the case of
-$\bar{B}:0.0 \rightarrow 1.0$ the time evolution of $\langle \psi \rangle$ has three stages characterized as a rapid increase, followed by a plateau
-and finally as jamming sets in, a slow increase or decrease. However when initial ordering is present this behavior is different. At 
-$\bar{B}: 0.2 \rightarrow 1.0$, bijels stabilized by ellipsoidal particles see a gradual increase in $\langle \psi \rangle$ for both particle aspect ratios.
-At stronger magnetic fields, $\bar{B}: 0.5 \rightarrow 1.0$ and $\bar{B}: 1.0 \rightarrow 1.0$, there is little to no change in $\langle \psi \rangle$ indicating
-that the magnetic field has no effect on the particle monolayer. This indicates that the mechanism of structural response if beginning with an ordered particle
-monolayer differs from that of a disordered one. We confirm this by plotting the Steinhardt 6 fold order parameter $\langle Q_6 \rangle$ in Figure \ref{fig:Q6-field_up}
-
-\begin{figure} 
-    \centering 
-    \includegraphics[scale=0.6]{../figures/results/paper2/Q6-field_up.png} 
-    \caption{Plots of the evolution of the average interface angle \(\langle Q6 \rangle\) for bijels stabilized 
-             by oblate (left) and prolate (right) particles, as a function of the initial microstructure and subsequent magnetic field application.
-             The dynamics observed can be seen to be a function of the initial microstructure.} 
-    \label{fig:Q6-field_up} 
-\end{figure}
-
-For oblate particles, both the \(\bar{B}: 0.0 \rightarrow 1.0\) and 
-\(\bar{B}: 0.2 \rightarrow 1.0\) cases exhibit a three-phase progression characterized as an initial decline in \(\langle Q_6 \rangle\), followed by a 
-plateau and a subsequent increase that stabilizes over time. The most pronounced decrease is observed in the \(\bar{B}: 0.0 \rightarrow 1.0\) case, where a 
-highly ordered monolayer undergoes significant disruption due to the sudden field-induced reorientation of particles. The recovery of \(\langle Q_6 \rangle\) 
-following this dip reflects the system's gradual reordering as particles adjust to their new orientation and repack at the interface.
-For the \(\bar{B}: 1.0 \rightarrow 1.0\) system, \(\langle Q_6 \rangle\) remains nearly constant, indicating that the monolayer was already aligned and 
-structurally stable at the onset of the simulation. The \(\bar{B}: 0.5 \rightarrow 1.0\) case stands out as an intermediate response, with only minor 
-fluctuations in \(\langle Q_6 \rangle\), suggesting limited capacity for additional structural reorganization due to pre-existing particle alignment.
-
-In the case of prolate particles, the behavior for systems with lower initial field values (\(\bar{B}: 0.0 \rightarrow 1.0\) 
-and \(\bar{B}: 0.2 \rightarrow 1.0\)) show monotonic increases in \(\langle Q_6 \rangle\), indicating a progressive gain in local particle ordering as the 
-field drives further interfacial reorganization. The magnitude and rate of increase are greatest in the \(\bar{B}: 0.0 \rightarrow 1.0\) case, which aligns with 
-the larger structural transformations observed in the microstructure. In contrast, the \(\bar{B}: 1.0 \rightarrow 1.0\) case remains largely unchanged, 
-confirming that the system has already reached its field-aligned state. The $\bar{B}: 0.5 \rightarrow 1.0$ shows some variations, although broadly there are no
-significant changes in the interfacial arrangement.
-
-Taken together, the results reveal two distinct categories of structural response in magnetically responsive bijels, governed by the initial degree of particle 
-ordering. The first category arises when the bijel is stabilized by a disordered particle monolayer. In this case, the application of a magnetic field drives 
-particle rotation and tilting out of the interface, which reduces the available interfacial area stabilized by the particles. This destabilization initiates 
-domain coarsening. As the fluid domains grow, capillary interactions couple with the evolving particle orientations, allowing the interface to deform in concert 
-with the particle dynamics. Ultimately, the microstructure becomes kinetically arrested as the particles rejam in their new field-aligned configurations, leading 
-to a stable, coarsened structure.
-
-The second category corresponds to systems with an initially nematically ordered monolayer, where the director is misaligned with the magnetic field. Here, the 
-applied field reorients the particles within the plane of the interface without inducing unjamming. Because the particle network remains structurally constrained, 
-the interface angle increases gradually as particles rotate, but without triggering large-scale fluid reorganization. Microstructural changes in this regime are 
-instead driven by localized adjustments in interfacial packing, rather than full-scale interface remodeling.
-
-Finally, when the particle monolayer is already well-aligned with the magnetic field direction, minimal reorientation occurs, and no significant structural 
-response is observed. This finding highlights that particle reorientation—particularly when it induces or is coupled with unjamming—is a prerequisite for 
-enabling dynamic microstructural evolution in bijels under magnetic fields. These insights underscore the importance of processing history and interfacial 
-particle configuration in tuning bijel responsiveness for functional applications.
-
 \subsection{Decreasing the applied field}

### 2025-04-13 chapters/paper1_5.tex
Changes 1. Added new lit review 2. Refined introduction and LBM methods 3. Fixed all references so that they have journals
Changes 1. Updating some refereces of analysis to link previous sections which do the same analysis to prevent repetition 2. Updating paper 2 to remove junk results
Changes 1. removed repeated analysis definitions 2. updated steinhardt definition for voronoi version 3. Increased size of some figures

@@
 \section{Introduction}
+
+This section is based on work submited to the American Institude of Physics, Physics of Fluids journal.
+It is reproduced from submission number \#POF25-AR-DSFD2024-03180, with the permission of AIP Publishing.
 
@@
 \begin{equation}
-q_l(i) = \left( \frac{4\pi}{2l+1} \sum_{m=-l}^{l} \left| \frac{1}{N(i)} \sum_{j=1}^{n(i)} Y_{lm}(\vec{r}_{ij}) \right|^2 \right)^{\frac{1}{2}} ,
+% q_l(i) = \left( \frac{4\pi}{2l+1} \sum_{m=-l}^{l} \left| \frac{1}{N(i)} \sum_{j=1}^{n(i)} Y_{lm}(\vec{r}_{ij}) \right|^2 \right)^{\frac{1}{2}} ,
+q_l(i) = \sqrt{ \frac{4 \pi}{2l + 1} \Sigma_{m = -l}^{l} | \Sigma_{f} \frac{A(f)}{A}, Y_{lm}(\theta_f, \phi_f) |^2 }
+\label{eq:steinhardt_definition}
 \end{equation}
-%\TODO{update formula to the one actually used}
 
-Here, \(n(i)\) denotes the number of nearest neighbors of particle \(i\), \(\vec{r}_{ij}\) is the vector connecting the centers of particles \(i\) and \(j\), and \(m\) is an integer ranging from \(-l\)
-to \(l\) that indexes the spherical harmonic components \(Y_{lm}\). Neighbor lists are typically defined using a fixed cutoff radius around each particle, identifying nearby particles as neighbors. 
+Here $A(f)$ denotes the area of face f of the Voronoi cell around a reference particle, $A$ is the surface area of the Voronoi cell, 
+$\theta_f$ and $\phi_f$ are the polar and azimuth angles of the outer normal vector connecting the reference particle to the vertex representing
+an adjacent particle and $Y_{lm}$ is the spherical harmonic component. 
+Neighbor lists are typically defined using a fixed cutoff radius around each particle, identifying nearby particles as neighbors. 
 We calculate the python package Freud to calculate the bond order parameters and use a Voronoi cell to determine the particle neighborhood rather than the standard distance criterion 

### 2025-04-13 chapters/paper2.tex
Changes 1. removed repeated analysis definitions 2. updated steinhardt definition for voronoi version 3. Increased size of some figures

@@
 \section{Results}\label{sec:results_p2}
-\subsection{Hysteresis curve}
+\subsection{Kinetic arrest}
 \label{section:hysteresis_curve}
@@
 stimuli, the microstructure often remains unchanged for extended periods due to the interfacial 
-jamming of particles \cite{cui_stabilizing_2013}. Similarly, in the hysteresis experiments 
-discussed earlier (Figure~\ref{fig:hysteresis_curve}), we observed that reducing or removing the magnetic field did not 
+jamming of particles \cite{cui_stabilizing_2013}. Similarly, when assessing the kinetic arrest of bijels shown 
+in Figure~\ref{fig:hysteresis_curve}, we observed that reducing or removing the magnetic field did not 
 lead to a reversal of domain coarsening or particle realignment, suggesting an inherent structural resilience once the bijel 
@@
 
-However, bijels are formed through a dynamic arrest during spinodal decomposition, and the 
-particles jam in configurations that may not correspond to a thermodynamic minimum particularly when a magnetic field is 
-applied during formation. Gunther et al. also showed that bijels stabilized by ellipsoidal particles exhibited timescales 
-of response distinct from bijels stabilized by spherical particle due to steric effects between ellipsoidal paticles.
+Gunther et al. also showed that bijels stabilized by ellipsoidal particles exhibited timescales 
+of response distinct from bijels stabilized by spherical particle due to steric effects between ellipsoidal particles.
 Therefore, this section will seek to understand to what extent the initial particle order affects the 
@@
 \(\bar{B}_{\text{template}} = 0.0, 0.2, 0.5, 1.0\). After allowing each structure to fully stabilize under a 
-constant magnetic field, we abruptly switch off the field and observe the subsequent time evolution of both the 
+constant magnetic field, we switch off the field and observe the subsequent time evolution of both the 
 microstructure and interfacial particle behavior over a duration of \(t = 10^5 \Delta t\). This analysis aims to 
@@
 
-FIgure \ref{fig:microstructure_viz-field_down} shows that in 
+Figure \ref{fig:microstructure_viz-field_down} shows that in 
 both cases, the bulk microstructure remains effectively unchanged over the course of the simulation, highlighting the 
-kinetic stability and arrested nature of the bijel once jamming has occurred.
-However, closer inspection of the interfacial particle arrangement reveals subtle but important differences. In the 
+kinetic stability and arrested nature of the bijel.
+However, closer inspection of the interfacial particle arrangement reveals that in the
 \(\bar{B}: 0.2 \rightarrow 0.0\) case, the particles retain a degree of orientational order, although slight deviations 
@@
 suggests that while the jammed interface resists large-scale rearrangement, there is a gradual relaxation of particle 
-orientations in the absence of the aligning field. The extent of this relaxation appears to correlate with the initial 
-alignment strength, indicating that systems formed under stronger magnetic fields exhibit greater reorientation when 
+orientations in the absence of the aligning field. The extent of this relaxation correlates with the initial field strength when 
 the field is removed. We probe the effect of these reorientations by calculating the time evolution of the domain size
-and the corresponding nematic order parameter of the particles in Figure \ref{fig:domain_size-field_down}
+in Figure \ref{fig:domain_size-field_down}
 
@@
 
-Figure~\ref{fig:domain_size-field_down} presents the time evolution of the normalized domain size (\(L/R\)) and nematic 
-order parameter (\(S\)) for bijels stabilized by oblate (left) and prolate (right) particles following the removal of an 
-applied magnetic field. For all systems except oblate particle stabilized bijel with \(\bar{B}: 0.0 \rightarrow 0.0\), 
-a modest degree of domain coarsening is observed. This slow, steady increase in domain size indicates that while the 
-global microstructure remains largely intact, minor structural rearrangements may still occur post-stimulus, particularly 
+Figure~\ref{fig:domain_size-field_down} presents the time evolution of the normalized domain size (\(L/R\)) for bijels stabilized by oblate 
+(left) and prolate (right) particles following the removal of an applied magnetic field. For all systems except oblate particle stabilized 
+bijel with \(\bar{B}: 0.0 \rightarrow 0.0\), a modest degree of domain coarsening is observed. This slow, steady increase in domain size 
+indicates that while the global microstructure remains largely intact, minor structural rearrangements may still occur post-stimulus, particularly 
 at long timescales. This behavior is more prominent in prolate particle systems, suggesting that elongated particles 
 may provide greater local flexibility for slight monolayer relaxation without disrupting the overall network.
-A notable exception arises in the oblate \(\bar{B}: 0.0 \rightarrow 0.0\) case, which exhibits a sudden and pronounced 
-increase in domain size at later times. This behavior is attributed not to gradual coarsening but to a domain coalescence 
-event.
-
-The nematic order parameter \(S\) for all field-removal scenarios demonstrates a consistent, order-dependent decrease over 
-time. This trend suggests that in the absence of an aligning field, particles gradually relax from their field-induced 
-configurations toward thermodynamically preferred orientations governed by interfacial capillary interactions. The 
-magnitude of this decay correlates with the initial degree of ordering: systems formed under higher magnetic fields 
-(\(\bar{B} = 0.5\) and \(1.0\)) show the most significant reduction in \(S\), reflecting a greater degree of reorientation.
-
-These results reinforce the interpretation that bijel microstructure is resilient to field removal, with no meaningful 
-reversal in domain architecture once jamming has occurred. However, the interfacial particle monolayer continues to evolve 
-at the microscale, with orientation relaxation providing a residual mechanism for slow, local structural change. To determine 
-whether this relaxation induces anisotropic coarsening, we next quantify the directional change in domain size and tortuosity 
-using the relative change metric \(\Delta L = \frac{L_f - L_i}{L_i}\), applied separately to \(L_\perp\) and \(L_\parallel\). 
-The same formulation is used to compute directional tortuosity changes, with results summarized in 
-Figure~\ref{fig:domain_size_aniso-field_up}.
-
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.6]{../figures/results/paper2/domain_size_aniso-field_down.png} 
-\caption{Plots of the anisotropic structural response of bijels after the removal of 
-         magnetic fields, by showing the relative change in directional domain size \((\Delta L)\) and tortuosity \((\Delta \tau)\) 
-         as a function of \(\Delta \bar{B}\), the change in field strength from the templated to final state. Blue curves correspond 
-         to bijels stabilized by oblate particles, and red curves to those stabilized by prolate particles.} 
-\label{fig:domain_size_aniso-field_down} 
-\end{figure}
-
-Overall, only minor anisotropic changes in domain size and tortuosity are observed following field removal, with no consistent 
-or monotonic dependence on \(\Delta \bar{B}\). This suggests that although particles may gradually relax from their field-induced 
-alignment, the resulting structural rearrangements are subtle and largely isotropic at the microstructural scale. The small 
-fluctuations observed in \(\Delta L\) and \(\Delta \tau\) likely reflect localized heterogeneities in the particle monolayer 
-rather than coordinated, directional coarsening. These findings support the notion that once the magnetic field is removed, 
-the dominant force acting on the particles is the interfacial capillary interaction, which seeks to minimize interfacial 
-energy without preference for a particular direction.
-
-Importantly, this contrasts with the structural response observed during the application of a magnetic field, where clear 
-anisotropy emerged as a result of field-driven particle reorientation. Here, despite the monolayer initially being in an 
-anisotropic, ordered state, the system exhibits no significant directional relaxation, underscoring the kinetic resilience 
-of the jammed interface. Thus, the microstructural evolution following stimulus removal appears to be dominated by slow, 
-isotropic relaxation rather than directional restructuring.To further understand the role of the capillary interactions on the 
-particle monolayer, we examine the time evolution of the interface angle \(\langle \psi \rangle\).
-
-\begin{figure} 
-\centering 
-\includegraphics[scale=0.6]{../figures/results/paper2/psi-field_down.png} 
-\caption{Plots of the average interfacial angle $\langle \psi \rangle$  plotted against time for bijels stabilized by oblate and prolate particles
-         on the left and right plots respectively. They show slight increases in $\langle \psi \rangle$ over time indicating that the particles are
-         slowly tilting out of the interface, inducing the domain coarsening observed.} 
-\label{fig:interface_angle-field_down} 
-\end{figure}
-
-Figure \ref{fig:interface_angle-field_down} shows that the the rate and extent of angular relaxation appear relatively insensitive to the initial degree of 
-order imposed by the templating field. For oblate particles, \(\langle \psi \rangle\) increases steadily regardless of initial alignment strength, indicating that 
-even highly ordered monolayers do not retain their field-imposed orientation indefinitely. Similarly, for prolate particles, although the change in 
-\(\langle \psi \rangle\) is smaller in magnitude, a comparable upward trend is evident.
-
-These results suggest that the particle monolayer continues to evolve post field-removal, driven by interfacial forces seeking to minimize the total interfacial 
-energy. However, since these angular adjustments do not lead to noticeable changes in the bulk microstructure it can be 
-inferred that rotational relaxation alone is insufficient to trigger further domain coarsening once jamming has occurred. This supports the conclusion that 
-structural irreversibility in these systems arises primarily from the kinetic constraints imposed by jamming, rather than any residual orientational stress 
-within the particle layer.
+A notable exception arises in the oblate \(\bar{B}: 0.0 \rightarrow 0.0\) case, which exhibits a pronounced 
+increase in domain size at later times. These results reinforce the interpretation that bijel microstructure 
+is resilient to field removal, with no meaningful reversal in the fluid once jamming has occurred even though local particle reorientation occurs.
 
@@
 the effect of applying a magnetic field and the initial microstructure on the structural response characterized. We first demonstrated that bijels subjected to increasing 
-magnetic field strength exhibit hysteresis in its structural response, where the domain size increases with field application but does not revert upon field removal.
+magnetic field strength exhibit kinetic arrest in its structural response, where the domain size increases with field application but does not revert upon field removal.
 
 When investigating the effect of the application of magnetic fields, our results revealed that applying magnetic fields post-formation induces domain coarsening up to 5\%, with 
-field-induced anisotropy dependent on particle shape. Oblate particles exhibited growth primarily in the perpendicular direction by up to 60\%, while prolate particles showed coarsening 
-along the field direction up to 40\%, 
-both accompanied by a decrease in tortuosity. These changes arise from particle reorientation to the field, followed by local unjamming and interfacial rearrangement before 
-re-jamming occurs, as characterized using the average interface angle of the particles and the Steinhardt bond orientational order parameter.
-
-Importantly, the extent of microstructural change scales with the difference in magnetic field strength before and after application. We found that particle alignment 
-characterized via $\langle \psi \rangle$ and $\langle Q_6 \rangle$ governs domain evolution. Disordered particle layers exhibited strong field responses, while highly ordered 
-templates showed minimal change, highlighting the importance of reordering on the structural response observed. In contrast, removing the magnetic field had little effect 
+field-induced anisotropy dependent on particle shape. Oblate particles exhibited growth primarily in the perpendicular direction by up to 60\%, while prolate particles showed 
+coarsening along the field direction up to 40\%, both accompanied by a decrease in tortuosity. These changes arise from particle reorientation to the field, followed by 
+local unjamming and interfacial rearrangement before re-jamming occurs, as characterized using the average interface angle of the particles and the 
+Steinhardt bond orientational order parameter. In contrast, removing the magnetic field had little effect 
 on bijel structure. Domain size and anisotropy remained largely unchanged, regardless of initial particle order. While minor relaxation in particle alignment was observed, 
@@
 
-Together, these results identify modes of structural response that depend upon the initial ordering of particles at the interface. The first mechanism identified occurs with
-disordered particle monolayers which upon application of a magnetic field, unjam facilitating domain coarsening before rejamming once the interface area matches the 
-particle cross sectional area. The second mechanism occurs due to particle reorientation to the applied field when particles are nematically ordered but not ordered in the direction
-of the magnetic field.
+These results show that rapid reorientation of the particle stabilizers is necessary to induce structural response in bijels. This is illustrated through structural response
+of bijels occurring upon application of the field, causing rapid realignment of particles to the applied field direction while slow realignment of particles away from
+the field when switching the field off generated no meaningful changes in the microstructure.
 

### 2025-04-13 chapters/paper3.tex
Changes 1. removed repeated analysis definitions 2. updated steinhardt definition for voronoi version 3. Increased size of some figures

@@
 Steinhardt bond orientational order parameters $q_2$ and $q_6$. 
-\cite{steinhardt_bond-orientational_1983, lechner_accurate_2008, mickel_shortcomings_2013}. These parameters characterize the local structural ordering by 
-projecting the orientations of neighboring particles onto spherical harmonics of degree \(l\), and are defined as
-
-\begin{equation}
-q_l(i) = \left( \frac{4\pi}{2l+1} \sum_{m=-l}^{l} \left| \frac{1}{N(i)} \sum_{j=1}^{n(i)} Y_{lm}(\vec{r}_{ij}) \right|^2 \right)^{\frac{1}{2}} ,
-\end{equation} 
-%\TODO{update formula to the one actually used}
-
-Here, \(n(i)\) denotes the number of nearest neighbors of particle \(i\), \(\vec{r}_{ij}\) is the vector connecting the centers of particles \(i\) and \(j\), 
-and \(m\) is an integer ranging from \(-l\) to \(l\) that indexes the spherical harmonic components \(Y_{lm}\). Neighbor lists are typically defined using a 
-fixed cutoff radius around each particle, identifying nearby particles as neighbors. We calculate the python package Freud to calculate the bond order parameters 
-and use a Voronoi cell to determine the particle neighborhood rather than the standard distance criterion \cite{ramasubramani_freud_2020,mickel_shortcomings_2013}. 
-The Voronoi-based method avoids the need for a predefined cutoff and yields more robust neighbor definitions, particularly in disordered systems. Bond 
-orientational order parameters have been widely employed to study structural transitions in colloidal and ceramic systems, including crystallization, nucleation, 
-and glass formation \cite{vagberg_glassiness_2011, besseling_three-dimensional_2007, schall_structural_2007, ozawa_jamming_2012}. $q_6$ is most commonly used 
-to identify crystal structures by matching the calculated values to reference values for specific crystal structures such as fcc or hcp. We plot the change in 
-$q_6$ of the microstructures as a function of the processing applied in Figure \ref{fig:q6_rheology_init}
+\cite{steinhardt_bond-orientational_1983, lechner_accurate_2008, mickel_shortcomings_2013}. The technique to calculate this parameter is provided in
+Equation \ref{eq:steinhardt_definition} We plot the change in 
+$\langle Q6 \rangle$ of the microstructures as a function of the processing applied in Figure \ref{fig:q6_rheology_init}
 
@@
     \centering 
-    \includegraphics[scale=0.3]{../figures/results/paper3/theta_z-time_compare-specific.png} 
+    \includegraphics[scale=0.5]{../figures/results/paper3/theta_z-time_compare-specific.png} 
     \caption{Comparisons of the average orientation of particles to the direction of the applied shear for bijels stabilized by
@@
 As the particles are adsorbed onto the interface, there is an open question whether the reorientation of particles to the shear also causes the interface to move with the
-particles. To analyze this effect, we analyzed the angle between each particles symmetry axis and the local interface normal by generating a mesh of the interface using the marching 
-cubes algorithm and, for each particle, identified the nearest mesh vertex (excluding those beyond the length of the particle's long axis). We then calculated 
-the angle $\psi$ between the particle orientation vector \(\hat{\vec{o}}_i\) and the local surface normal. The time evolution of the average interface
-angle of all particles $\langle \psi \rangle$, calculated as a numerical average of $\psi$ for all particles, is shown in Figure~\ref{fig:interface_angle_shear}.
+particles. To analyze this effect, we analyzed the angle between each particles symmetry axis and the local interface, calculated in the technique described in Chapter 4.
+The time evolution of the average interface angle of all particles $\langle \psi \rangle$, calculated as a numerical average of $\psi$ for all particles, is shown in 
+Figure~\ref{fig:interface_angle_shear}.
 
@@
     \centering 
-    \includegraphics[scale=0.3]{../figures/results/paper3/psi-time_compare-specific.png} 
+    \includegraphics[scale=0.5]{../figures/results/paper3/psi-time_compare-specific.png} 
     \caption{Comparisons of the average orientation of particles to the interface for bijels stabilized by

### 2025-04-13 chapters/dissertation-tap.tex
Changes 1. Added new lit review 2. Refined introduction and LBM methods 3. Fixed all references so that they have journals
Updated abstract

--- 2025-04-01 chapters/dissertation-tap.tex
@@
 \profmember{Ulf D. Schiller, PhD}
-\member{Eric Furst, PhD}
+\member{Eric M. Furst, PhD}
 \member{Arthi Jayaraman, PhD}
@@
     fabrication with minimal waste, bottom-up synthesis techniques have gained increasing attention. Emulsion templating 
-    leverages thermodynamically or kinetically arrested structures formed by phase-separating fluids. Among these, bicontinuous 
-    interfacially jammed emulsion gels (bijels) are particularly promising due to their tortuous and co-continuous microstructures.
+    leverages thermodynamic or kinetically arrested structures formed by phase-separating fluids. Among these, bicontinuous 
+    interfacially jammed emulsion gels (bijels) are particularly interesting due to their tortuous and co-continuous microstructures.
 
-    Bijels form via thermally induced spinodal decomposition of partially miscible fluid mixtures in the presence of neutrally 
+    Bijels were first formed via thermally induced spinodal decomposition of partially miscible fluid mixtures in the presence of neutrally 
     wetting particles. As the fluid domains coarsen, particles adsorb onto the interface until the interfacial area matches the 
     total cross-sectional area of the particles, resulting in a jammed monolayer that locks the microstructure in place. Traditional 
-    bijel synthesis via thermal phase separation is not readily scalable. However, newer techniques such as Solvent Transfer Induced 
-    Phase Separation (STrIPS) have been developed to address this limitation, utilizing the removal of solvent from a bijel casting
-    mixture to induce phase separation. However, the microstructure obtained is coupled to the casting mixture composition, 
-    and the flow rate during STrIPS.
+    bijel synthesis via thermal phase separation is not readily scalable as the cooling rate cannot be uniformly controlled, which
+    reduces uniformity of the structure. However, newer techniques such as Solvent Transfer Induced Phase Separation (STrIPS) have been 
+    developed to address the scale up limitation/ utilizing the removal of solvent from a bijel casting
+    mixture to induce phase separation. STrIPS allows for the decoupling of spinodal decomposition from temperature, allowing for greater
+    material compatibility and tunable bijel shapes and microstructure through controlling the solvent exchange rate. However, the 
+    microstructure obtained is coupled to the casting mixture composition, and the flow rate during STrIPS.
 
     One promising approach to modulate bijel microstructure is through stimulus-responsive systems. Magnetic stimuli, in particular, 
-    offer a non-invasive, controllable, and targeted mechanism. Earlier studies using spherical particles under magnetic fields showed 
-    limited microstructural changes. More recent work, however, has revealed that ellipsoidal particles can respond to magnetic actuation 
-    by tilting, leading to the formation of particle chains or rings at interfaces. This phenomenon opens the door to controllable 
-    modifications in bijel microstructures using magnetic fields.
+    offer a controllable and targeted mechanism. Earlier studies using spherical particles under magnetic fields showed 
+    limited microstructural changes. However, ellipsoidal particles can respond to magnetic actuation 
+    by tilting, leading to the multipolar capillary interactions between particles facilitating formation of particle chains or rings at 
+    interfaces. This phenomenon opens the door to controllable modifications in bijel microstructures using magnetic fields.
 
@@
     magnetically responsive ellipsoidal particles. To explore this, we employ a multicomponent Lattice Boltzmann Method coupled with a 
-    molecular dynamics representation of rigid particles and a dipole-based magnetic field model. The system simulates a water-2,6-lutidine 
-    mixture stabilized by micron-sized nickel-coated polystyrene particles.
-
+    molecular dynamics representation of rigid particles and a dipole-based magnetic field model. The system is modelled on a water-2,6-lutidine 
+    bijel casting mixture stabilized by micron-sized nickel-coated polystyrene particles.
     We first examine the ability of magnetic fields to influence bijel formation by applying a constant field during spinodal decomposition
@@
     spherical particles, bijels stabilized by discs and rods show slight increases in domain size and become anisotropic, as measured by 
-    tortuosity and directional domain size.Further analysis reveals that the coarsening rates become direction-specific for ellipsoidal particles, 
+    tortuosity and directional domain size.
+
+    Further analysis reveals that the coarsening rates become direction-specific for ellipsoidal particles, 
     suggesting that jamming occurs anisotropically due to particle alignment with the magnetic field. This alignment, governed by the 
     orientation of the magnetic moment relative to the particle's long axis, also affects how particles arrange themselves at the fluid 
-    interface.
+    interface. Particle alignment to the magnetic field affects the curvature of the interface as particles with smaller cross sectional area 
+    are less disruptive to the hyperbolic interface shape. Topological examinations of the morphology, 
+    demonstrating that the number of interconnected channels in the system decreased over time and that the average channel sizes obtained follow
+    the same trend as that of the domain size. These results highlight how particle shape and magnetic field interactions can be leveraged to 
+    guide bijel formation in a directional and controllable manner.
 
-    Having established that magnetic fields can influence microstructure during synthesis, we then assess whether similar control can be exerted 
-    after bijel formation. This has implications for applications like crossflow reactors and filtration systems, where reversible control over 
+    Next, we examine the ability of bijels to undergo microstructure modification post formation.
+    This has implications for applications like crossflow reactors and filtration systems, where reversible control over 
     permeability and flow resistance is desirable. By incrementally increasing and decreasing the magnetic field on a bijel stabilized with 
-    rod-like particles, we observe that the microstructure can indeed be modified post-synthesis. Domain size increases nonlinearly with 
-    applied field strength and remains altered even after the field is reduced, indicating a saturation threshold and a history-dependent 
-    response.
-
-    To probe this further, we evaluate field-driven coarsening in bijels stabilized with rod and disc-like particles. Upon field application, 
+    rod-like particles, we observe that the microstructure can be modified post-synthesis. Domain size increases nonlinearly with 
+    applied field strength and remains altered even after the field is reduced, indicating that the structure remains in a kinetically arrested
+    state.To probe this further, we evaluate field-driven coarsening in bijels stabilized with rod and disc-like particles. Upon field application, 
     particles reorient, leading to anisotropic domains similar to those formed during synthesis under a field. The temporal evolution of 
     microstructure involves increased particle ordering, interface alignment, and rearrangement, demonstrating a complex interplay of factors. 
-    Notably, the extent of domain size change is negatively correlated with the initial ordering of particles, suggesting a memory effect 
-    rooted in the starting microstructure.
+    Notably, the extent of domain size change is negatively correlated with the initial ordering of particles.
 
@@
     we investigate whether bijels exhibit similar effects. Prior studies have shown that shear can induce domain coarsening and particle 
-    ejection in bijels. Additionally, emulsions stabilized by ellipsoidal particles show viscosity decreases with increased ordering due 
-    to weakened particle-fluid interactions. In this work, we explore how magnetic fields and initial microstructure affect the shear 
-    response of bijels stabilized by ellipsoidal particles.As particle ordering increases, the viscosity and shear-thinning behavior decrease for 
-    bijels stabilized by disc- and rod-like particles. Interestingly, the yield stress decreases with increased order for discs, but increases for 
-    rods due to differences in local particle arrangement and frictional contacts. Under shear, domain coarsening occurs due to shear induced particle 
-    tilting out of the interface.
+    ejection in bijels. Additionally, emulsions stabilized by ellipsoidal particles exhibit reduced viscosity with increased particle ordering because 
+    aligned particles create less resistance to flow. In this work, we explore how magnetic fields and initial microstructure affect the shear 
+    response of bijels stabilized by ellipsoidal particles. As particle ordering increases, the viscosity and shear-thinning behavior decrease for 
+    bijels stabilized by disc- and rod-like particles. We also characterize that the yield stress is dependent upon the friction between particles
+    that is a function of the arrangement of particles on the interface, affected by the application of magnetic fields. These results suggest 
+    that magnetic field-driven particle ordering can be used to tailor the rheological behavior of bijels, offering a strategy to reduce viscosity 
+    and modulate shear-thinning by controlling interfacial microstructure.
 
-    In conclusion, this dissertation demonstrates that magnetic fields offer a viable and tunable method for controlling bijel microstructures both 
-    during and after synthesis, and it provides a detailed characterization of the constant shear response of magnetically responsive bijels. These findings 
-    lay the groundwork for developing adaptive, magnetically responsive porous materials through both conventional synthesis techniques and Solvent 
-    Transfer Induced Phase Separation (STrIPS), enabling scalable and application-specific design.
+    In conclusion, this dissertation demonstrates that magnetic fields offer a viable and tunable method for controlling bijel microstructures 
+    both during and after synthesis, and it characterizes the constant shear response of magnetically responsive bijels. These findings 
+    lay the groundwork for developing adaptive, magnetically responsive bijels suitable for porous material templates or as a soft matter 
+    system for use in drug release or bioengineering applications.
 

### 2025-04-13 chapters/final_remarks.tex
Changes 1. Updated abstract and conclusion

@@
 
-This study addresses that gap through a series of hybrid simulations using a coupled Molecular Dynamics-Lattice Boltzmann framework. 
+This study addresses that gap through a series of hybrid simulations using a coupled Lattice Boltzmann-Molecular Dynamics framework. 
 We investigated how magnetic fields influence bijel formation and structure when stabilized by ellipsoidal particles, focusing on 
@@
 
-We first demonstrated that ellipsoidal particles alter the formation dynamics of bijels when subjected to external magnetic 
-fields during phase separation. We also explored how varying magnetic flux densities and particle aspect ratios affect structural outcomes. 
-In the absence of a magnetic field, ellipsoidal particles 
-aligned with the interface over time due to capillary interactions, contributing to slower coarsening and finer domain features compared 
-to spherical particles. Upon introducing magnetic fields, particles experienced additional torques that promoted alignment along the field 
-direction during formation. This field-induced reorientation improved interfacial packing efficiency and introduced directional cessation
-of coarsening, leading to bijels with domain anisotropy. Importantly, these effects were achieved without preventing the formation of a 
-stable, bicontinuous structure.
+We first demonstrated that ellipsoidal particles can be used to modify the microstructure of bijels during synthesis of bijels.
+We also explored how varying magnetic flux densities and particle aspect ratios affect structural outcomes. 
+In the absence of a magnetic field, ellipsoidal particles aligned with the interface over time due to capillary interactions, contributing to 
+anisotropic coarsening rates and finer domain features compared to spherical particles. Upon introducing magnetic fields, particles experienced 
+additional torques that promoted alignment along the field direction during formation. This field-induced reorientation improved interfacial 
+packing efficiency and introduced directional cessation of coarsening, leading to bijels with domain anisotropy.
 
@@
 channel size distributions (CSDs) revealed a wide range of channel dimensions but did not show systematic variation with 
-field strength, suggesting that magnetic field effects manifest more prominently in local structure and domain anisotropy. Still, the 
+field strength, suggesting that magnetic field effects manifest more prominently in local structure and domain anisotropy. The 
 average channel size derived from the CSD aligned well with conventional domain measurements, reinforcing the results obtained throughout
@@
 
-Upon applying magnetic fields post formation, we observed significant structural rearrangements in bijels depending on the initial particle 
+Upon applying magnetic fields post formation, we observed structural rearrangements in bijels depending on the initial particle 
 configuration. Systems with disordered interfacial layers underwent domain coarsening and anisotropic growth due to field-induced unjamming 
@@
 magnetic field was removed, the bijel structure largely remained in its field-aligned state. Only minor particle relaxation occurred, 
-indicating that capillary forces alone were insufficient to reverse the structural transformations, revealing a hysteresis-like behavior 
-in the response to magnetic stimuli.
-
-The degree of structural reorganization was closely linked to the initial state of the particle monolayer. We identified two primary 
-response modes. The first is where initially disordered layers unjammed and reorganized under magnetic fields before settling into a new 
-jammed configuration, and another where partially ordered particles reoriented to align with the field, modifying domain structure 
-without full unjamming. Systems with high initial order showed minimal structural change, suggesting that the dynamic response of bijels 
-can be pre-programmed via the interfacial order established during formation.
+indicating that capillary forces alone were insufficient to reverse the structural transformations, revealing a that the particle monolayer
+was kinetically arrested.
 
@@
 tunable soft materials. By integrating ellipsoidal particle design with magnetic field stimuli, we demonstrate a new axis of control over 
-bijel formation and function. 
-Conceptually, our results refine the understanding of interfacial jamming in bijels. The identification of distinct 
+bijel formation and function. Conceptually, our results refine the understanding of interfacial jamming in bijels. The identification of
 unjamming-rejamming mechanisms, modulated by both field strength and particle ordering, reveals that bijel structures are not passively 
 determined by initial phase separation dynamics. Instead, they are dynamically reconfigurable under external fields, with the extent of 
-reconfiguration governed by the memory of prior structural states. This introduces a paradigm in which bijels can be treated as 
-non-equilibrium materials with tunable hysteresis, offering a controllable blend of stability and adaptability.
+reconfiguration governed by prior structural states.
 
-Our work also implements structural characterization for describing bijel microstructures. While prior studies have focused heavily on global 
-measures such as domain size or volume fraction, our use of bond orientational order, curvature metrics, and channel topology creates a more 
-nuanced toolkit for evaluating local and global bijel structure. This multiscale perspective provides better predictive capacity for 
-tailoring materials with application-specific structural features, such as tortuosity for mass transport or local ordering for mechanical 
-performance.
+While prior studies have focused heavily on global measures such as domain size or volume fraction, our use of implemented bond orientational order, 
+curvature metrics, and channel topology creates a more nuanced toolkit for evaluating local and global bijel structure. This multiscale 
+perspective provides better predictive capacity for tailoring materials with application-specific structural features, such as tortuosity 
+for mass transport or local ordering for mechanical performance.
 
-The broader impacts of this work span several disciplines. In materials science, our findings inform the design of smart scaffolds and 
-porous networks with tunable permeability or rheology. For instance, magnetic field-tunable tortuosity or anisotropy could 
-be leveraged in filtration membranes that dynamically adjust flow pathways or in tissue scaffolds where curvature-sensitive cell adhesion 
-is critical. In energy systems, the ability to control interfacial curvature and connectivity may influence electrochemical transport and 
-reaction kinetics in battery electrodes or catalytic substrates.
-
-The rheological tunability demonstrated here has direct implications for soft robotics, adaptive damping materials, and controlled release 
-systems. The distinction between oblate and prolate behavior under shear and field stresses provides a foundation for selecting particle 
-geometries based on the desired flow performance of the end-use material. Furthermore, the discovery that certain configurations can resist 
-flow better than others may lead to new materials with programmable viscoelasticity—materials that stiffen or soften in response to field inputs.
+The broader impacts of this work span several disciplines. In materials science, our findings inform the design of smart scaffolds and porous 
+networks with tunable permeability or rheology. For instance, magnetic field-tunable tortuosity or anisotropy could be leveraged in filtration 
+membranes that dynamically adjust flow pathways or in tissue scaffolds where curvature-sensitive cell adhesion is critical. In energy systems, 
+the ability to control interfacial curvature and connectivity may influence electrochemical transport and reaction kinetics in battery electrodes 
+or catalytic substrates. Additionally, the demonstrated control over yield stress and flow behavior through particle shape and magnetic history 
+opens new pathways for engineering responsive soft materials in applications such as injectable therapeutics, adaptive 3D printing inks, or 
+magnetorheological fluids.
 
@@
 soft and cohesive particles are known to exhibit distinct glass transition behaviors and rheological responses compared 
-to hard-sphere systems. \cite{weeks_introduction_2017, torquato_jammed_2010} In bijel architectures, attractive interactions have been 
-proposed as a strategy to form “armored” interfaces, potentially enhancing mechanical integrity and enabling higher flow rates in catalytic applications. 
-\cite{boakye-ansah_controlling_2020}
+to hard-sphere systems \cite{weeks_introduction_2017, torquato_jammed_2010}. In bijel architectures, attractive interactions have been 
+proposed as a strategy to form “armored” interfaces, potentially enhancing mechanical integrity and enabling higher flow rates in catalytic 
+applications \cite{boakye-ansah_controlling_2020}. 
 Similarly, soft particles such as nanogels and hydrogels have attracted interest in biomedical contexts, offering tunable responsiveness 
@@
 
-The current simulations, while able to capture structural evolution under external fields, do not fully resolve the complex dynamical landscape of the interfacial 
-particle monolayer. In particular, they lack the resolution to distinguish between fast particle rearrangements and slow collective dynamics near the glass transition, 
-which are known to govern the jamming and unjamming behavior of dense colloidal systems. \cite{weeks_introduction_2017, torquato_jammed_2010} 
-As such, the interplay between interfacial ordering, particle-scale dynamics, and existing order can be characterized more convincingly by investigating the dynamics of
-the particle more systematically by accounting for thermal fluctuations of the fluid. This would involve implementation of a fluctuating Lattice Boltzmann Method
-which would facilitate identification of the glassy dynamics in the system, including the onset of arrest and structural aging characterized with the microstructure
-in Gunther et al. \cite{gunther_timescales_2014}
+The current simulations, while able to capture structural evolution under external fields, do not fully resolve the complex dynamical 
+landscape of the interfacial particle monolayer. In particular, they lack the resolution to distinguish between fast particle rearrangements 
+and slow collective dynamics near the glass transition, which are known to govern the jamming and unjamming behavior of dense 
+colloidal systems \cite{weeks_introduction_2017, torquato_jammed_2010}. 
+As such, the interplay between interfacial ordering, particle-scale dynamics, and existing order can be characterized more convincingly by 
+investigating the dynamics of the particle more systematically by accounting for thermal fluctuations of the fluid. This would involve 
+implementation of a fluctuating Lattice Boltzmann Method which would facilitate identification of the glassy dynamics in the system, 
+including the onset of arrest and structural aging characterized with the microstructure in Gunther et al \cite{gunther_timescales_2014}.
 
 Another promising avenue for future investigation involves the use of gradient or rotating magnetic fields in place of constant fields. This
-would impart a force on the particles in addition to the torque that magnetic particles experience under constant fields. \cite{spatafora-salazar_hierarchical_2021, martinezpedrero_collective_2020}
+would impart a force on the particles in addition to the torque that magnetic particles experience under 
+constant fields \cite{spatafora-salazar_hierarchical_2021, martinezpedrero_collective_2020}.
 Prior work has demonstrated that spatial gradients in particle volume fraction can generate domain size gradients in bijels, enabling spatial 
@@
 
-In parallel, rotating magnetic fields offer a dynamic mechanism for restructuring particle arrangements at the interface. 
-\cite{spatafora-salazar_hierarchical_2021, martinezpedrero_collective_2020}
+In parallel, rotating magnetic fields offer a dynamic mechanism for restructuring particle arrangements 
+at the interface \cite{spatafora-salazar_hierarchical_2021, martinezpedrero_collective_2020}. 
 In ferrofluids and magnetic colloidal suspensions, such fields have been shown to induce chain or ring formation, depending on the rotation frequency and field 
-strength. \cite{spatafora-salazar_hierarchical_2021, martinezpedrero_collective_2020}
+strength \cite{spatafora-salazar_hierarchical_2021, martinezpedrero_collective_2020}. 
 Translating this mechanism to bijels, a rotating field could be used to modulate interfacial jamming behavior, promoting controlled 
@@
 
-Clemson University is acknowledged for generous allotment of compute time on Palmetto cluster. This research used the 
-Delta advanced computing and data resource which is supported by the National Science Foundation (award OAC 2005572) 
-and the State of Illinois. Delta is a joint effort of the University of Illinois Urbana-Champaign and its National 
-Center for Supercomputing Applications.
+This research was supported in part through the use of DARWIN computing system: DARWIN - A Resource for Computational 
+and Data-intensive Research at the University of Delaware and in the Delaware Region, Rudolf Eigenmann, Benjamin E. 
+Bagozzi, Arthi Jayaraman, William Totten, and Cathy H. Wu, University of Delaware, 2021
 
@@
 
-This research was supported in part through the use of DARWIN computing system: DARWIN - A Resource for Computational 
-and Data-intensive Research at the University of Delaware and in the Delaware Region, Rudolf Eigenmann, Benjamin E. 
-Bagozzi, Arthi Jayaraman, William Totten, and Cathy H. Wu, University of Delaware, 2021
+Clemson University is acknowledged for generous allotment of compute time on Palmetto cluster. This research used the 
+Delta advanced computing and data resource which is supported by the National Science Foundation (award OAC 2005572) 
+and the State of Illinois. Delta is a joint effort of the University of Illinois Urbana-Champaign and its National 
+Center for Supercomputing Applications.

### 2025-04-13 chapters/lit_review_new.tex
tidied up lit review section

@@
 To understand the formation of bijels, the difference between nucleation and growth and spinodal decomposition must be understood. These processes 
-govern how distinct domains emerge and evolve within a binary mixture upon quenching into the two-phase region of the phase diagram. While nucleation and growth involve the formation 
+govern how distinct domains emerge and evolve within a binary mixture upon quenching into the demixing region of the phase diagram. While nucleation and growth involves the formation 
 and expansion of isolated domains, spinodal decomposition leads to the spontaneous, interconnected structuring characteristic of bijels. Investigating both mechanisms provides insight 
-into how thermodynamic and kinetic pathways influence the resulting microstructure, and why spinodal decomposition is uniquely suited for producing the bicontinuous 
-architecture essential to bijels. A schematic free energy and phase diagram is plotted in Figure \ref{fig:phase_diagram}
+into how phase separation can be leveraged to generate microstructures for porous materials and why spinodal decomposition specifically underpins bijel formation. A schematic free 
+energy and phase diagram is shown in Figure \ref{fig:phase_diagram}
 
@@
 free energy through composition modulation \cite{cahn_free_1958}. The dynamics of spinodal decomposition were characterized by Cahn and Hilliard \cite{cahn_spinodal_1961}. 
-We first begin by defining the free energy of a regular solution, known as the bulk free energy given by
+We first begin by defining the free energy of a regular solution given by,
 
@@
 
-This bulk free energy characterizes the thermodynamic driving forces for phase separation. Alternative forms, such as the Landau-Ginzburg or Flory-Huggins models, may also be used depending on system 
-specifics. In real systems, the interface between two partially miscible fluids is not sharp, meaning that the composition transitions smoothly across a finite interface width. To account for this, a 
-gradient energy penalty is added to the free energy functional, penalizing sharp spatial variations in composition. The total free energy functional is written as
+This bulk free energy characterizes the thermodynamic driving forces for phase separation. Alternative forms of the free energy can be defined based on the double well potential or
+Flory-Huggins theory based on the desired objectives of the model. In real systems, the interface between two partially miscible fluids is diffuse, meaning that the composition 
+transitions smoothly across a finite interface width. To account for this, a gradient energy penalty is added to the free energy to penalize sharp spatial variations in 
+composition, yielding the free energy functional of the system. The total free energy functional is given by,
 
@@
 
-This chemical potential enters the mass flux expression via a Fickian transport law,
+The chemical potential enters the mass flux expression via a Fickian transport law,
 
@@
 
-Substituting in the expression for \(\vec{J}\) leads to the Cahn-Hilliard equation 18 in reference \cite{cahn_spinodal_1961},
+Substituting in the expression for \(\vec{J}\) leads to the Cahn-Hilliard equation, shown in Equation 18 in reference \cite{cahn_spinodal_1961},
 
@@
 
-This equation describes the diffusive evolution of the conserved field $c$ during phase separation. It captures the system's tendency to minimize its total free energy 
+The Cahn-Hilliard equation describes the diffusive evolution of the conserved field $c$ during phase separation. It captures the system's tendency to minimize its total free energy 
 by redistributing the order parameter according to gradients in chemical potential. The Cahn-Hilliard framework naturally incorporates interfacial tension and allows for smooth, 
@@
 
-When micron sized particles are adsorbed by interfaces the attachment energy is large enough that they can become irreversibly trapped at fluid-fluid interfaces \cite{ngai_particle-stabilized_2015}. 
-Once adsorbed, these 
-particles reduce interfacial tension and act as physical barriers that prevent the coalescence of droplets, thereby making them highly effective emulsion stabilizers. Unlike molecular surfactants, 
-which are dynamic and can desorb under certain conditions, colloidal particles remain adsorbed at the interface due to the significant energy required to detach them \cite{ngai_particle-stabilized_2015}.
-This mechanism 
-is especially useful in systems such as Pickering emulsions, where the interfacial coverage and wettability of the particles determine the type and stability of the emulsion formed 
-\cite{ngai_particle-stabilized_2015,velankar_non-equilibrium_2015}.
-As such, understanding particle behavior at interfaces is essential for controlling the structure and longevity of particle-stabilized systems \cite{ngai_particle-stabilized_2015}. 
-For particles that are smooth and simple and at an interface of oil and water, the attachment energy at the fluid interface can be calculated the Pieranski model, 
-$G_{ads} = \sigma A_{rm} (1 - \cos{\theta_c})^2$, where $G_{ads}$ is the free energy reduction upon particle adsorption, $\sigma$ is the surface tension between the two 
-fluids, and $\theta_c$ is the contact angle of the stabilizing particle. A schematic of a particle adsorbing at an interface is shown in Figure \ref{fig:pieranski_model},
+When micron sized particles are adsorbed by interfaces the attachment energy is large enough that they can become irreversibly trapped at fluid-fluid interfaces 
+\cite{ngai_particle-stabilized_2015}. Once adsorbed, these particles act as physical barriers that prevent the coalescence of droplets, thereby making them highly effective 
+emulsion stabilizers. Unlike molecular surfactants, which are dynamic and can desorb under certain conditions, colloidal particles remain adsorbed at the interface due to the 
+significant energy required to detach them \cite{ngai_particle-stabilized_2015}. The microstructure of the resultant particle stabilized emulsion is dependant upon the wettability 
+of the particles \cite{ngai_particle-stabilized_2015,velankar_non-equilibrium_2015}.
+As such, understanding particle behavior at interfaces is essential for controlling the structure of particle-stabilized systems \cite{ngai_particle-stabilized_2015}. 
+For particles that are smooth and simple and at an interface of oil and water, the attachment energy at the fluid interface can be calculated based on the schematic shown in 
+Figure \ref{fig:pieranski_model},
 
@@
 
-To obtain the Pieranski model, an energy balance between the interactions between the interface and the fluid phases can be written. The energy of the system before and after particle adsorption is 
+Am energy balance between the interactions between the interface and the fluid phases can be written. The energy of the system before and after particle adsorption is 
 different and can be characterized for the particle moving from water into the interface as,
@@
 
+After applying geometric constrains, the Pieranski model is given by
+
+\begin{equation}
+    E_{ads} = \sigma A_{rm} (1 - \cos{\theta_c})^2
+\end{equation}
+
+where $E_{ads}$ is the free energy reduction upon particle adsorption, $\sigma$ is the surface tension between the two fluids, and $\theta_c$ is the contact angle of the stabilizing particle. 
 From this the Pieranski model, the adsorption energy can be seen to depend on the contact angle, surface tension and contact area of the particles. This indicates that larger, neutrally wetting
-particles adsorbing onto interfaces with high surface tension have a high driving force for adsorption. \cite{ngai_particle-stabilized_2015,reeves_particle-size_2015} This adsorption process 
+particles adsorbing onto interfaces with high surface tension have a high driving force for adsorption \cite{ngai_particle-stabilized_2015,reeves_particle-size_2015}. This adsorption process 
 can be orders of magnitude larger than the thermal energy of the system, calculated as $k_b T$ where $T$ is the temperature of the system and $k_b$ is the Boltzmann constant. This results in 
-irreversible adsorption of particles at interfaces. \cite{binks_pickering_2001}
+irreversible adsorption of particles at interfaces \cite{binks_pickering_2001}.
 
-In addition to the adsorption of particles on the interface, the contact angle of the particles determine the dispersed phase of an emulsion and its microstructure.
-\cite{velankar_non-equilibrium_2015}
-Hydrophillic particles tend to prefer to form oil in water emulsions while hydrophobic particles prefer to form water in oil emulsions. \cite{ngai_particle-stabilized_2015}
-This occurs as the particles preferentially wet one phase over another, causing the interface to bend as the emulsion forms. Neutrally wetting particles are preferred in the formation of 
-bijels as no preferential curvature is imparted onto the bijels, fulfilling one of the requirements of a minimal surface in that the mean curvature must be zero. \cite{jinnai_interfacial_2001}
+In addition to the adsorption of particles on the interface, the contact angle of the particles determine the dispersed phase of an emulsion and its 
+microstructure \cite{velankar_non-equilibrium_2015}.
+This occurs as the particles preferentially wet one phase over another, causing the interface to bend as the emulsion forms. This bending causes hydrophillic and hydrophobic particles preferentially 
+forming oil in water and water in oil emulsions respectively in an empirical observation named the Bancroft rule \cite{ngai_particle-stabilized_2015}.
+Neutrally wetting particles are preferred in the formation of bijels as no preferential curvature is imparted onto the bijels, fulfilling one of the requirements of a saddle shaped interface
+in that the mean curvature must be zero. \cite{jinnai_interfacial_2001}
 
@@
 \cite{brader_nonlinear_2010, besseling_three-dimensional_2007, xu_relation_2013}.
-In suspensions, the interaction  between solid particles—such as hydrodynamic forces, electrostatic repulsion, and steric hindrance—creates microstructural rearrangements under flow, leading to 
+In suspensions, the interaction  between solid particles such as hydrodynamic forces, electrostatic repulsion, and steric hindrance creates microstructural rearrangements under flow, leading to 
 non-linear viscosity responses \cite{brader_nonlinear_2010, besseling_three-dimensional_2007}. Figure \ref{fig:suspension_shear} demonstrates the shear properties of an example suspension, 
@@
 
-\section{Emulsion studies using Lattice Boltzmann}
-
-Understanding the complex interplay between fluid phases and particles in emulsions requires modeling approaches that can capture hydrodynamic interactions, interfacial tension, and particle 
-behavior at mesoscopic scales. The multicomponent Lattice Boltzmann method has emerged as a powerful tool for simulating such systems, as it bridges the gap between continuum fluid dynamics 
-and molecular-level detail. LB models can naturally incorporate smooth interfaces, phase separation dynamics, and solid-fluid coupling, making them particularly well-suited for studying 
-emulsion formation, coarsening, and stabilization mechanisms. This has enabled detailed investigations into how particle properties and flow conditions influence emulsion structure and rheology.
-
-One significant contribution of LB simulations to emulsion research has been the study of dynamical scaling during spinodal decomposition, characterized as the growth of the lengthscale
-over time following a power law behavior \cite{siggia_late_1979, furukawa_role_1994}. From the multicomponent Navier Stokes equation, Reynolds number dependent scaling exponents for the 
-lengthscale of the system were identified that were termed the viscous limit, where the Reynolds number was low, and the inertial limit, where the Reynolds number is high \cite{kendon_inertial_2001}.
-Multicomponent LB studies definitively demonstrated the ranges of Reynolds number where these scaling laws held and identified a broad crossover region \cite{kendon_inertial_2001, kendon_3d_1999}.
-
-Additionally, the bijel itself was first realized computationally using LB simulations. \cite{stratford_colloidal_2005} A multicomponent LB model with neutrally wetting colloids based on the 
-implementation by Ladd showed that coarsening interfaces could catch particles irreversibly adsorbing them and arresting coarsening once the interfacial area matched the cross sectional area of 
-particles adsorbed \cite{stratford_colloidal_2005,ladd_numerical_1994}. The simulations also showed that these structures were stable over long periods of time, motivating and guiding the 
-experimental realization of bijels in 2007 \cite{herzig_bicontinuous_2007}. These simulations provided an explanation of the dynamics and mechanistic reasoning behind the formation of bijels, 
-allowing for the prediction of the microstructure. More recent LB studies have extended these findings by identifying the volume fraction and wetting angle needed to form bijels as opposed to 
-Pickering emulsions \cite{jansen_bijels_2011}. The effect of the surface tension, fluid density and volume fraction of particles were also studied, showing that surface tension and fluid density 
-had little effect on the microstructure of bijels and that the length scale of the bijel was inversely proportional to the volume fraction of particles \cite{jansen_bijels_2011}.
-
-More recent LB studies by Gunther et al. have extended these findings by incorporating nonspherical particles, such as ellipsoids or rods, to explore how anisotropy influences interfacial behavior 
-and emulsion morphology \cite{gunther_timescales_2014}. These particles introduce directional capillary interactions and exhibit preferred orientations at the interface, which can lead to enhanced 
-jamming and altered domain stabilization with timescales of domain size change not observed with spherical particles arising from steric force driven particle reorientation. The orientation of 
-ellipsoidal particles at interfaces was also characterized using a multicomponent LB, demonstrating the adsorption of ellipsoidal particles at interfaces could result in metastable orientations of 
-particles \cite{gunther_lattice_2013}.
-
-The LB method has also enabled exploration of external field effects, particularly magnetic fields acting on particles at interfaces. Simulations involving magnetic dipolar particles show that 
-applying an external field can induce tilting, chaining, or reorientation of particles at the interface \cite{davies_interface_2014, davies_assembling_2014}. This effect was caused by interface 
-deformation that caused dipolar or quadropolar capillary interactions.
-This was extended to analyzing the effect of Janus particles at interfaces of evaporating droplets that showed how they preferred
-to stick together on curved interfaces \cite{xie_direct_2017}.
-
-These studies demonstrate the effectiveness of multicomponent LB methods in identifying and characterizing mesoscale phenomena relevant to soft matter systems. By capturing 
-complex fluid-fluid and fluid-particle interactions, LB models provide a versatile platform for simulating emulsion dynamics, interfacial assembly, and 
-microstructural evolution. From revealing the scaling laws of spinodal decomposition to enabling the computational discovery of bijels, LB simulations have offered valuable insights that would be 
-difficult to obtain experimentally. Furthermore, the ability to incorporate anisotropic particles and external fields, such as magnetism, highlights the method's adaptability for exploring 
-increasingly sophisticated and tunable systems.
-
 \section{Numerical modeling}
@@
 \cite{huber_brownian_2019, yip_brownian_2005, elsawy_utility_2025}. It approximates the over-damped limit of Langevin dynamics by integrating 
-particle trajectories under the influence of both deterministic forces—such as interparticle potentials or external fields—and random thermal 
+particle trajectories under the influence of both deterministic forces such as interparticle potentials or external field and random thermal 
 forces representing collisions with solvent molecules. Hydrodynamic interactions may be included through approximate mobility tensors or omitted 
@@
 diffusion in dilute suspensions, where particle motion is dominated by thermal fluctuations. However, it does not model the surrounding fluid 
-explicitly, limiting its ability to capture bulk fluid flow or interface-mediated interactions. As a result, Brownian dynamics is not sufficient 
+explicitly, limiting its ability to capture the effect of multicomponent flow. As a result, Brownian dynamics is not sufficient 
 on its own for simulating the coupled fluid-particle dynamics involved in bijel formation.
@@
 obtained through a Chapman-Enskog expansion of the LBM. \cite{qian_lattice_1992} The LBM has become an attractive tool for meso-scale CFD simulations due to its ease of algorithm 
-implementation, highly parallelizable nature and ease of boundary condition implementation, allowing coupling to other physically relevant systems such as 
-particles with varieties of potentials, external fields and deformable bodies.
-Importantly, LBM can be extended to handle multiphase and multicomponent fluids, using either color-gradient models, free energy formulations,
-or pseudopotential approaches to model non-ideal mixing. It also couples well to particle dynamics through momentum exchange schemes, making it a powerful framework for 
+implementation, highly parallelizable nature and ease of implemeting boundary conditions, allowing coupling to other physically relevant systems such as 
+particles with varieties of potentials, external fields and deformable bodies. Importantly, LBM can be extended to handle multiphase and multicomponent fluids through a variety of methods.
+It also can be coupled to particle dynamics through momentum exchange schemes, making it a powerful framework for 
 simulating colloidal suspensions, interfacial phenomena, and structurally complex systems like bijels. Its ability to capture both hydrodynamics and mesoscale thermodynamic 
@@
 Phase field methods provide thermodynamically consistent, diffuse-interface models ideal for phase separation, though they require fine resolution and are computationally intensive. 
-Brownian dynamics excels at modeling particle-level stochastic motion but cannot resolve bulk fluid dynamics or interface evolution on its own. In contrast, the Lattice Boltzmann Method 
+Brownian dynamics excels at modeling particle-level stochastic motion but cannot resolve interface evolution on its own. In contrast, the Lattice Boltzmann Method 
 combines the strengths of mesoscopic fluid modeling with efficient handling of complex interfaces and straightforward coupling to particle dynamics. Its balance between computational 
-efficiency, scalability, and physical fidelity across multiple scales makes LBM the most suitable method for simulating the rich interplay of hydrodynamics, phase separation, and particle 
+efficiency, scalability, and physical fidelity across multiple scales makes the LBM the most suitable method for simulating the rich interplay of hydrodynamics, phase separation, and particle 
 interactions in stimuli-responsive emulsions such as bijels.
+
+\subsection{Emulsion studies using Lattice Boltzmann}
+
+Understanding the complex interplay between fluid phases and particles in emulsions requires modeling approaches that can capture hydrodynamic interactions, interfacial tension, and particle 
+behavior at mesoscopic scales. The multicomponent LBM has emerged as a powerful tool for simulating such systems, as it bridges the gap between continuum fluid dynamics 
+and molecular-level detail. LB models can naturally incorporate smooth interfaces, phase separation dynamics, and solid-fluid coupling, making them particularly well-suited for studying 
+emulsion formation, coarsening, and stabilization mechanisms. This has enabled detailed investigations into how particle properties and flow conditions influence emulsion structure and rheology.
+
+Dynamical scaling provides a basis for the characterization of the driving force for phase separation in a binary system. It posits that, at late times, the system's 
+morphology becomes self-similar, characterized by a single length scale \( l(t) \) that grows over time following a power-law behavior defined as $l(t) \propto t^{\alpha}$ where $\alpha$ is
+the scaling exponent characterizing phase separation \cite{siggia_late_1979, furukawa_role_1994}.
+The regimes identified from previous investigations were the diffusive regime where $\alpha = 1/3$, inertial scaling where $\alpha = 2/3$ and the viscous regime where $\alpha = 1$.
+Kendon et al. characterized the transition between viscous to inertial scaling using a free energy based LBM \cite{kendon_inertial_2001, kendon_3d_1999}. They obtained a master 
+curve for systems undergoing spinodal decomposition which showed the transition from viscous to inertially driven spinodal decomposition, characterized using a length and timescales 
+derived from the surface tension, viscosity and fluid density and the Reynolds number \cite{kendon_inertial_2001, kendon_3d_1999}.
+
+Additionally, the bijel itself was first realized computationally using LB simulations \cite{stratford_colloidal_2005}. A multicomponent LB model with neutrally wetting colloids based on the 
+implementation by Ladd showed that coarsening interfaces could catch particles irreversibly adsorbing them and arresting coarsening once the interfacial area matched the cross sectional area of 
+particles adsorbed \cite{stratford_colloidal_2005,ladd_numerical_1994}. The simulations also showed that these structures were stable over long periods of time, motivating and guiding the 
+experimental realization of bijels in 2007 \cite{herzig_bicontinuous_2007}. These simulations provided an explanation of the dynamics and mechanistic reasoning behind the formation of bijels, 
+allowing for the prediction of the microstructure. More recent LB studies have extended these findings by identifying the volume fraction and wetting angle needed to form bijels as opposed to 
+Pickering emulsions \cite{jansen_bijels_2011}. The effect of the surface tension, fluid density and volume fraction of particles were also studied, showing that surface tension and fluid density 
+had little effect on the microstructure of bijels and that the length scale of the bijel was inversely proportional to the volume fraction of particles \cite{jansen_bijels_2011}.
+
+More recent LB studies by Gunther et al. have extended these findings by incorporating nonspherical particles, such as ellipsoids or rods, to explore how anisotropy influences interfacial behavior 
+and emulsion morphology \cite{gunther_timescales_2014}. These particles introduce directional capillary interactions and exhibit preferred orientations at the interface, which can lead to enhanced 
+jamming and altered domain stabilization with timescales of domain size change not observed with spherical particles arising from steric force driven particle reorientation. The orientation of 
+ellipsoidal particles at interfaces was also characterized using a multicomponent LB, demonstrating the adsorption of ellipsoidal particles at interfaces could result in metastable orientations of 
+particles \cite{gunther_lattice_2013}.
+
+The LB method has also enabled exploration of external field effects, particularly magnetic fields acting on particles at interfaces. Simulations involving magnetic dipolar particles show that 
+applying an external field can induce tilting, chaining, or reorientation of particles at the interface \cite{davies_interface_2014, davies_assembling_2014}. This effect was caused by interface 
+deformation that caused dipolar or quadropolar capillary interactions.
+This was extended to analyzing the effect of Janus particles at interfaces of evaporating droplets that showed how they preferred
+to stick together on curved interfaces \cite{xie_direct_2017}.
+
+These studies demonstrate the effectiveness of multicomponent LB methods in identifying and characterizing mesoscale phenomena relevant to soft matter systems. By capturing 
+complex fluid-fluid and fluid-particle interactions, LB models provide a versatile platform for simulating emulsion dynamics, interfacial assembly, and 
+microstructural evolution. From revealing the scaling laws of spinodal decomposition to enabling the computational discovery of bijels, LB simulations have offered valuable insights that would be 
+difficult to obtain experimentally. Furthermore, the ability to incorporate anisotropic particles and external fields, such as magnetism, highlights the method's adaptability for exploring 
+increasingly sophisticated and tunable systems.
 
@@
 
-Point particle models treat colloids as infinitesimal entities that influence the surrounding fields through source terms or effective force laws. 
-\cite{mehrabadi_direct_2018, prosperetti_point-particle_2007, frohlich_validation_2018}
+Point particle models treat colloids as infinitesimal entities that influence the surrounding fields through source terms or effective force laws
+\cite{mehrabadi_direct_2018, prosperetti_point-particle_2007, frohlich_validation_2018}.
 In such models, particles do not occupy physical volume and their influence on the fluid is typically introduced via body forces or perturbations to the chemical potential field. 
@@
 interfaces has been conducted using the magnetic dipole model, showing that a rich variety of interfacial phenomena can be captured by this model such as the balance between capillary interactions
-and magnetic field induced torque and capillary self assembly of microparticles at interfaces. \cite{xie_direct_2017,davies_interface_2014,davies_assembling_2014}
+and magnetic field induced torque and capillary self assembly of microparticles at interfaces \cite{xie_direct_2017,davies_interface_2014,davies_assembling_2014}.
+
+In this chapter, a survey of why spinodal decomposition is important in the formation of bijels, how particle stabilizes work, dynamics of anisotropic particles at interfaces 
+and numerical methods that can be selected to model the dynamics of the system were shown. In the next chapter, we elaborate on the specific physics being modelled, explain the implementation 
+of the simulation technique and present a model experimental system that we are simulating.

### 2025-04-13 chapters/LBM_technique.tex
Changes 1. Added correct copyright statements to reused images 2. Cleaned up text in introduction, lit review and methods sections

@@
     \caption{D3Q19 lattice demonstrating the rest, nearest and next nearest direction that correspond to the 19 
-    directions $(i)$ of the lattice with lattice velocity $c_{i}$. \cite{schmieschek_lb3d_2017} Reproduced from 
-    Schmieschek et al. Computer Physics Communications 2017, 217, 149--161, under the CC-BY license.}
+    directions $(i)$ of the lattice with lattice velocity $c_{i}$. Reprint of Figure 1 from
+    \textit{Schmieschek, S.; Shamardin, L.; Frijters, S.; Krüger, T.; Schiller, U.
+D.; Harting, J.; Coveney, P.
+V.
+LB3D: A Parallel Implementation of the Lattice-Boltzmann Method for Simulation of Interacting Amphiphilic Fluids.
+Computer Physics Communications 2017, 217, 149-161}
+    with permission from Elsevier under the CC-BY license.}
     \label{fig:d3q19_lattice}

### 2025-04-13 chapters/introduction_new.tex
Changes 1. Added correct copyright statements to reused images 2. Cleaned up text in introduction, lit review and methods sections

@@
 due to the irreversibility of particle adsorption at the interface \cite{ngai_particle-stabilized_2015} .
-Additionally, growing environmental and toxicity concerns associated with small-molecule surfactants have increased interest in the applications of particle-stabilized emulsions.
-\cite{kaczerewska_environmental_2020, lechuga_acute_2016}. In contrast, particle stabilizers lower toxicity and improved biocompatibility, in addition to 
-sustainable sourcing from particles based on cellulose or chitin. \cite{fujisawa_nanocellulose-stabilized_2017, tang_stimuli-responsive_2016, kalliola_carboxymethyl_2018}.
+Additionally, growing environmental and toxicity concerns surrounding small-molecule surfactants have increased interest in particle-stabilized emulsions, due to their lower toxicity, 
+enhanced biocompatibility, and potential for sustainable sourcing from renewable materials such as chitin and cellulose.
+\cite{kaczerewska_environmental_2020, lechuga_acute_2016, fujisawa_nanocellulose-stabilized_2017, tang_stimuli-responsive_2016, kalliola_carboxymethyl_2018}.
 The microstructure of Pickering emulsions has been extensively studied, notably by Binks and Lumsdon in the early 2000s. Their investigations revealed that the emulsion droplet radius 
-follows the relationship $R_e \propto \frac{\phi_w}{\phi_p}$, where $\phi_w$ and $\phi_p$ represent the volume fractions of water and particles, respectively \cite{binks_pickering_2001}. 
+follows the relationship $R_e \propto \frac{1}{\phi_p}$, where $\phi_p$ represent the volume fractions of particles \cite{binks_pickering_2001}. 
 They also identified key parameters influencing microstructure, such as fluid composition and particle wettability. Neutrally wetting particles tend to stabilize nearly spherical droplets, 
@@
     \includegraphics[scale = 0.3]{figures/literature_review/state_diagram.jpg}
-    \caption{Formation criteria for a particle stabilized emulsion that can form bijel \cite{velankar_non-equilibrium_2015}.
-            Used with permission of Royal Society of Chemistry, from A non-equilibrium state diagram for liquid/fluid/particle 
-            mixtures, Velankar, 1, 11, 2015 under license number 1551968-1}
+    \caption{Formation criteria for a particle stabilized emulsion that can form bijel. Reprinted Figure 3 with permission from the Royal Society of Chemistry from 
+             \textit{Velankar, S. S. A Non-Equilibrium State Diagram for Liquid/Fluid/Particle Mixtures. Soft Matter 2015, 11 (43), 8393-8403}
+             with permission from the Royal Society of Chemistry under license number 1551968-1; Permission conveyed through Copyright Clearence Center}
     \label{fig:state_diagram_particle_emulsions}
@@
     \caption{Initiation and arrest of spinodal decomposition as particles adsorb onto the interface, followed by jamming once the 
-    interfacial area matches the cross sectional area of the adsorbed particles\cite{stratford_colloidal_2005}. 
-    Reproduced from K. Stratford et al., Science 309, 2198-2201(2005) under license number 5966820525314.}
+            interfacial area matches the cross sectional area of the adsorbed particles. Reprint of Figure 1 from
+            \textit{Stratford, K.; Adhikari, R.; Pagonabarraga, I.; Desplat, J.-C.; Cates, M.
+E.
+Colloidal Jamming at Interfaces: A Route to Fluid-Bicontinuous Gels.
+Science 2005, 309 (5744), 2198-2201}
+            Reprinted with permission from AAAS under license number 5966820525314.}
     \label{fig:bijel_coarsen}
@@
 By preparing the mixture at this
-critical composition and heating it past the LCST, phase separation was thermally induced, a process known as Thermally Induced Phase Separation (TIPS). The system underwent coarsening until gelation 
-occurred, forming a bijel.
-Since this initial experimental synthesis, TIPS has been widely used in laboratory-scale studies to synthesize a variety of small molecule, oligomeric, and polymeric systems
+critical composition and heating it past the LCST, phase separation was induced in a process known as Thermally Induced Phase Separation (TIPS). The system underwent coarsening until particle
+interactions at the interface jammed the microstructure in place, once the cross-sectional area of the particles matched the interfacial area, forming a bijel. Since this initial 
+experimental synthesis, TIPS has been widely used in laboratory-scale studies to synthesize a variety of small molecule, oligomeric, and polymeric systems 
 \cite{tavacoli_novel_2011, lee_bicontinuous_2010, bai_dynamics_2015, ching_rapid_2021}.
 
-However, industrial applications require continuous, scalable fabrication techniques capable of generating application specific tailored microstructures. STrIPS has emerged as a promising solution 
-for this need. As illustrated in Figure~\ref{fig:strips}, STrIPS involves a ternary fluid system composed of two immiscible fluids 
+However, industrial applications require continuous, scalable fabrication techniques capable of generating application specific tailored microstructures. The thermal induction of phase separation
+does not permit easy scale up due to limitations of suitable systems that forms bijels and the need to have constant cooling rates to ensure consistent microstructures through the entire reaction
+vessel. Solvent Transfer Induced Phase Separation (STrIPS) has emerged as a promising solution to address these issues.
+As illustrated in Figure~\ref{fig:strips}, STrIPS involves a ternary fluid system composed of two immiscible fluids 
 and a solvent. In the initial stage (Figure~\ref{fig:strips}a), a casting mixture is prepared. Phase separation is then triggered by flowing a co-solvent past the mixture to extract the solvent 
@@
 induced phase separation such as Vapor Induced Phase Separation(VIPS) and controlled coalescence of droplets to form bijels through shear (homogenization) have also been identified as techniques
-to synthesize bijels \cite{wang_scalable_2020, huang_bicontinuous_2017}.
+to synthesize bijels \cite{wang_scalable_2020, huang_bicontinuous_2017, cai_bijels_2017}.
 
@@
     \caption{Extrusion of the bijel casting mixture into a non-solvent bath, followed by removal of solvent from 
-             the casting mixture through diffusion, demonstrating the working principal of STrIPS. \cite{haase_continuous_2015}. Reproduced with permission from Wiley-VCH Verlag GmbH 
-             \& Co. KGaA from \textit{Continuous Fabrication of Hierarchical and Asymmetric Bijel Microparticles, Fibers, and Membranes by 
-             Solvent Transfer-Induced Phase Separation (STRIPS)}, Haase, M. F., Stebe, K. J., 
-             \& Lee, D., \textit{Advanced Materials}, 27(44), 7065-7071, 2015 under license number 5913140219015}
+             the casting mixture through diffusion, demonstrating the working principal of STrIPS. \cite{haase_continuous_2015}. 
+             Reprint of Figure 2 from 
+             \textit{Haase, M.
+F.; Stebe, K.
+J.; Lee, D.
+Continuous Fabrication of Hierarchical and Asymmetric Bijel Microparticles, Fibers, and Membranes by Solvent Transfer-Induced Phase Separation (STRIPS).
+Advanced Materials 2015, 27 (44), 7065-7071}
+             with permission from Wiley-VCH Verlag GmbH \& Co. KGaA under license number 5913140219015}
     \label{fig:strips}
@@
 
-Despite these advances, a persistent limitation is that bijel microstructure remains tightly coupled to the composition of the casting mixture and the kinetics of phase separation.
-Achieving controlled
+Despite these advances, a limitation is that bijel microstructure remains tightly coupled to the composition of the casting mixture and the kinetics of phase separation. Achieving controlled 
 morphology often requires fine-tuning of fluid concentrations or external conditions, which may not be feasible for all applications \cite{haase_continuous_2015, reeves_particle-size_2015}.
@@
     \caption{Quadropolar capillary interactions around prolate ellipsoidal particles caused by interfacial deformations 
-             around the particle \cite{loudet_capillary_2005}. Reprinted Figure 4 with permission from
-             Loudet et al, Phys. Rev. Letter., 94, 08301, 2003 Copyright 2025 by the American Physical Society under license number RNP/25/FEB/088185}
+             around the particle. Reprinted Figure 4 with permission from
+             \textit{Loudet, J. C.; Alsayed, A. M.; Zhang, J.; Yodh, A. G. Capillary Interactions Between Anisotropic Colloidal Particles. Phys. Rev. Lett. 2005, 94 (1), 018301}
+             Copyright 2025 by the American Physical Society.}
     \label{fig:anisotropic_particle_interface}
@@
 
-The geometry of the stabilizing particles plays a key role in determining rheological behavior.
-Madivala et al.
-showed that Pickering emulsions stabilized with rod-like particles had enhanced stability under
-shear, with greater resistance observed as particle aspect ratio increased \cite{madivala_exploiting_2009}.
-This enhancement was attributed to improved interfacial coverage and capillary interactions induced by
-interface deformations, which reinforced the particle monolayer.
-Similarly, emulsions stabilized by graphene nanosheets exhibited higher viscosity and viscoelasticity compared to those stabilized by spherical
-particles, underscoring the importance of particle shape \cite{imperiali_simple_2014}. The elasticity of the interface has also been shown to depend on the nature of the particle stabilizer used 
-\cite{sun_assembly_2013}.
+The geometry of the stabilizing particles plays a key role in determining rheological behavior. Madivala et al. showed that Pickering emulsions stabilized with rod-like particles had enhanced 
+stability under shear, with greater resistance observed as particle aspect ratio increased \cite{madivala_exploiting_2009}. This enhancement was attributed to improved interfacial coverage 
+and capillary interactions induced by interface deformations, which reinforced the particle monolayer. Similarly, emulsions stabilized by graphene nanosheets exhibited higher viscosity and 
+viscoelasticity compared to those stabilized by spherical particles, underscoring the importance of particle shape \cite{imperiali_simple_2014}. The elasticity of the interface has also been 
+shown to depend on the nature of the particle stabilizer used \cite{sun_assembly_2013}.
 
-The rheological properties of bijels are of fundamental importance due to their direct influence on both fabrication and application.
-For instance, STrIPS fabrication relies on the controlled flow of a
-casting mixture into a solvent bath, necessitating precise knowledge of the material's rheology to optimize processing parameters \cite{haase_situ_2016, haase_continuous_2015}.
-In applied systems such as
-cross-flow reactors, the mechanical stability of the particle monolayer is critical; failure under shear or compositional gradients can limit performance \cite{boakye-ansah_controlling_2020}. Under 
-constant shear, bijels exhibit shear-thinning behavior, which at moderate shear rates is well described by the Herschel-Bulkley model \cite{macmillan_rheological_2019, wang_morphology_2023}.
-At higher
-shear rates, the internal structure of the bijel is disrupted, leading to a transition toward Newtonian flow behavior \cite{cai_bijels_2017, bonaccorso_shear_2020}.
+The rheological properties of bijels are of fundamental importance due to their direct influence on both fabrication and application. For instance, STrIPS fabrication relies on the controlled 
+flow of a casting mixture into a solvent bath, necessitating precise knowledge of the material's rheology to optimize processing parameters \cite{haase_situ_2016, haase_continuous_2015}. 
+In applied systems such as cross-flow reactors, the mechanical stability of the particle monolayer is critical; failure under shear or compositional gradients can limit performance 
+\cite{boakye-ansah_controlling_2020}. Under constant shear, bijels exhibit shear-thinning behavior, which at moderate shear rates is well described by the Herschel-Bulkley model 
+\cite{macmillan_rheological_2019, wang_morphology_2023}. At higher shear rates, the internal structure of the bijel is disrupted, leading to a transition toward Newtonian 
+flow behavior \cite{cai_bijels_2017, bonaccorso_shear_2020}.
 
@@
     \caption{Enhanced oil recovery of oil from water using magnetically responsive emulsion stabilizers, allowing for 
-             locomotion and controlled coalescence of cargo from a matrix phase using magnetic fields \cite{tham_magnetophoresis_2021}. 
-             K. Tham, W. M. Ng, S. S. Leong, S. P. Yeap, S. C. Low, H. L. Lee and J. Lim. Magnetophoresis of magnetic pickering 
-             emulsions under low field gradient: Macroscopic and microscopic motion. 37, 1811: Reprinted (adapted) with permission from 
-             Langmuir 2021, 37, 5, 1811-1822. Copyright 2025 American Chemical Society.}
+             locomotion and controlled coalescence of cargo from a matrix phase using magnetic fields. Reprint of the graphical abstract from
+             \textit{Tham, F.
+K.; Ng, W.
+M.; Leong, S.
+S.; Yeap, S.
+P.; Low, S.
+C.; Lee, H.
+L.; Lim, J.
+Magnetophoresis of Magnetic Pickering Emulsions Under Low Field Gradient: Macroscopic and Microscopic Motion.
+Langmuir 2021, 37 (5), 1811-1822}
+             Reprinted (adapted) with permission from Langmuir 2021, 37, 5, 1811-1822. Copyright 2025 American Chemical Society.}
     \label{fig:magnetophoresis_droplet}
@@
 Introducing magnetic responsiveness into anisotropic particles offers a strategy for controlling their behavior at fluid interfaces. Such particles can be fabricated via surface deposition of 
-magnetic materials or synthesized as core-shell structures with magnetic cores and non-magnetic shells \cite{fei_magneto-capillary_2020, nakayama_stimuli-responsive_2018}.
-The interplay between magnetic
-and capillary interactions governs particle orientation in response to external magnetic fields.
-According to Bresme-Faraudo theory, a neutrally wetting ellipsoidal particle at an interface experiences
-competing forces: the magnetic field seeks to reorient the particle's magnetic dipole moment, while capillary forces resist deformation away from the interface plane 
+magnetic materials or synthesized as core-shell structures with magnetic cores and non-magnetic shells \cite{fei_magneto-capillary_2020, nakayama_stimuli-responsive_2018}. The interplay between 
+magnetic and capillary interactions governs particle orientation in response to external magnetic fields. According to Bresme-Faraudo theory, a neutrally wetting ellipsoidal particle at an 
+interface experiences competing forces: the magnetic field seeks to reorient the particle's magnetic dipole moment, while capillary forces resist deformation away from the interface plane 
 \cite{bresme_orientational_2007, davies_interface_2014}.
@@
              showing the self assembly into chains that ellipsoidal particles can undergo under applied magnetic fields at
-             interfaces. \cite{davies_assembling_2014} Reproduced from Davies et al. Adv. Mater., 26: 6715-6719 under the 
-             Creative Commons CC BY license.}
+             interfaces. Reprint of Figure 3 from
+             \textit{Davies, G.
+B.; Krüger, T.; Coveney, P.
+V.; Harting, J.; Bresme, F.
+Assembling Ellipsoidal Particles at Fluid Interfaces Using Switchable Dipolar Capillary Interactions.
+Advanced Materials 2014, 26 (39), 6715-6719}
+             with permission from Wiley-VCH Verlag GmbH \& Co. KGaA under the Creative Commons CC BY license.}
     \label{fig:anisotropic_assembly}

### 2025-04-13 chapters/lit_review_new.tex
Changes 1. Added correct copyright statements to reused images 2. Cleaned up text in introduction, lit review and methods sections

@@
     \caption{Schematic of a phase diagram obtained from a free energy curve demonstrating key features of the free energy landscape that correspond
-             to the phase diagram. Reprinted Figure 1 from
-             Guillen-Chable, F.; Bayona, A.; Rodríguez-Zapata, L. C.; Castano, E. Phase Separation of Intrinsically Disordered 
-             Nucleolar Proteins Relate to Localization and Function. IJMS 2021, 22 (23), 13095. with permission under the Creative Common CC BY license.}
+             to the phase diagram. Reprint of Figure 1 from 
+             \textit{Guillen-Chable, F.; Bayona, A.; Rodríguez-Zapata, L. C.; Castano, E. Phase Separation of Intrinsically Disordered 
+             Nucleolar Proteins Relate to Localization and Function. IJMS 2021, 22 (23), 13095.}
+             with permission from MDPI under the Creative Common CC BY license.}
     \label{fig:phase_diagram}
@@
     \includegraphics[scale = 0.5]{../figures/literature_review/particle_at_interface.png }
-    \caption{Particle schematic at an interface demonstrating the various quantities of interest. Reprinted Figure 2.1 from
-             Particle-Stabilized Emulsions and Colloids: Formation and Applications; Ngai, T., Bon, S. A. F., Eds.; RSC soft matter series; 
-             with permission Royal Society of Chemistry, RSC Publishing Cambridge, 2015 under license number 1597404-1}
+    \caption{Particle schematic at an interface demonstrating the various quantities of interest. Used with permission of the Royal Society of Chemistry from 
+             Figure 2.1 in \textit{Particle-Stabilized Emulsions and Colloids: Formation and Applications; Ngai, T., Bon, S. A. F., Eds.; RSC soft matter series;};
+             Permission conveyed through Copyright Clearence Center, Inc. under license number 1597404-1.}
     \label{fig:pieranski_model}
@@
     \includegraphics[scale = 0.3]{../figures/literature_review/curvature_driven_assembly.jpeg}
-    \caption{Self assembly of particles at points of large curvature gradients. Reproduced from Figure 5 in Cavallaro, M.; Botto, L.; 
-             Lewandowski, E. P.; Wang, M.; Stebe, K. J. Curvature-Driven Capillary Migration and Assembly of Rod-like Particles. 
-             Proc. Natl. Acad. Sci. U.S.A. 2011, 108 (52), 20923-20928 under the CC-BY license}
+    \caption{Self assembly of particles at points of large curvature gradients. Reprint of Figure 5 in 
+             \textit{Cavallaro, M.; Botto, L.; Lewandowski, E.
+P.; Wang, M.; Stebe, K.
+J.
+Curvature-Driven Capillary Migration and Assembly of Rod-like Particles.
+Proc.
+Natl.
+Acad.
+Sci.
+U.S.A.
+2011, 108 (52), 20923-20928}
+             with permission from The National Academy of Sciences under the CC-BY license}
     \label{fig:curvature_gradient}
@@
     \caption{Bijels stabilized by rod like particles, demonstrating 'flippers' at the interface, which are particles that flip out of the interface due to stress from adjacent particles. 
-             Reproduced from Figure 3 in Hijnen, N.; Cai, D.; Clegg, P. S. Bijels Stabilized Using Rod-like Particles. Soft Matter 2015, 11 (22), 4351-4355 under the CC-BY license}
+             Reprint of Figure 3 in 
+             \textit{Hijnen, N.; Cai, D.; Clegg, P. S. Bijels Stabilized Using Rod-like Particles. Soft Matter 2015, 11 (22), 4351-4355} 
+             with permission from the Royal Society of Chemistry under the CC-BY license.}
     \label{fig:rod_bijel_flippers}
@@
     \caption{Schematic of suspensions under shear demonstrating shear banding and shear aggregates modifying the rheological properties of a suspension. 
-             Reproduced from Figure 2 in Wagner, N. J.; Brady, J. F. Shear Thickening in Colloidal Dispersions. Physics Today 2009, 62 (10), 27-32 under the CC-BY license}
+             Reprint of Figure 2 in \textit{Wagner, N. J.; Brady, J. F. Shear Thickening in Colloidal Dispersions. Physics Today 2009, 62 (10), 27-32}
+             with permission from the American Institute of Physics under the CC-BY license}
     \label{fig:suspension_shear}
@@
     \caption{Schematic of expected shear stress as a function of applied shear rate for various models of fluids on the left and a shear thinning material on the right, demonstrating
-             the yield stress at low strain rate followed by shear thinning and the infinite shear rate plateau. Reproduced from Cooke, M. E.; Rosenzweig, D. H. The Rheology of Direct 
-             and Suspended Extrusion Bioprinting. APL Bioengineering 2021, 5 (1), 011502 under the CC BY license.}
+             the yield stress at low strain rate followed by shear thinning and the infinite shear rate plateau. Reprint of Figure 2 from
+             \textit{Cooke, M. E.; Rosenzweig, D. H. The Rheology of Direct and Suspended Extrusion Bioprinting. APL Bioengineering 2021, 5 (1), 011502} 
+             with permission from the American Institute of Physics under the CC BY license.}
     \label{fig:shear_theory}

### 2025-04-13 chapters/LBM_technique.tex
Changes 1. Added paper attribution as footnotes 2. Fixed some language in lit review

@@
 dependent contribution.
+
+\section{Simulation setup}
+\label{section:sim_setup}
+
+Critical parameters in this system include fluid density $\rho_f$, dynamic viscosity $\eta$, surface tension $\sigma$, 
+length scale $L$, and applied magnetic field strength $B$. The dynamic viscosity and surface tension is determined 
+by the relaxation time using the BGK collision operator, $\eta = \rho_f c_s^2(\tau - \frac{1}{2})$ and $g_{kk'}$ 
+respectively. Dimensionless numbers derived from the Buckingham Pi theorem are the Reynolds number
+($Re = \frac{\rho u L}{\eta}$), Weber number ($We = \frac{\rho u^2 L}{\sigma}$), and magnetic bond number 
+($\Bar{B} = \frac{Bd}{\sigma A}$). Here, $u$ is velocity, $d$ is the particle's dipole moment, and $A$ is the 
+particle's cross-sectional area. The system's velocity and length scale are set as the domain size and coarsening rate. 
+Parameters for the fluid, particle, and non-ideal mixing model used in the simulations are summarized in Table 
+\ref{table:model_params}.
+
+\begin{table}[h!]
+\centering
+\begin{tabular}{||c c c c c c c c c c c c c||} 
+ \hline
+ $t_{sim}$ & $L_x$ & $\rho_f$ & $\tau$ & $\eta_f$ & $g_{cc'}$ & $\sigma$ & $\phi_f$ & $\rho_p$ & $\phi_p$ & $V_p$ & $d_c$ & $K_H$ \\ [0.5ex] 
+ \hline\hline
+ $10^5$ & 256 & 0.7 & 1 & 0.117 & 0.08 & 0.0267 & 0.5 & 1 & 0.15 & 2000$\pi$ & 2/3 & 100\\ [1ex] 
+ \hline
+\end{tabular}
+\caption{Summary of the fluid, particle and model parameters used in the proposed simulations}
+\label{table:model_params}
+\end{table}
+
+In these simulations, the aspect ratio is defined as $\alpha = \frac{R_{\parallel}}{R_{\perp}}$ with $\alpha = 0.5, 1, 2$ 
+used in these simulations. All particle geometries are volume matched, based on the spherical particle volume. For the 
+spherical particle, the radius was set at $R_{\parallel} = R_{\perp} = 7.9$ which sets the $\alpha = 0.5$ particles to 
+$R_{\parallel} = 5, R_{\perp} = 10$ and the $\alpha = 2$ particles to $R_{\parallel} = 12.6, R_{\perp} = 6.3$. 
+$R_{\parallel}$ and $R_{\perp}$ is the radius of the particle parallel and perpendicular to the symmetry axis of 
+the particle respectively. These values are identical to what was used in Gunther et al, allowing comparisons to the 
+trends they observed. \cite{gunther_timescales_2014} The particles were randomly placed in the system and an equilibration
+step was performed to push the particles further away from each after placement. Once equilibration is performed, a 
+constant magnetic field is switched on with dimensionless strengths defined using $\bar{B}$.
+
+The initial condition of the system when simulating bijels sets the density of each grid to $0.5\rho_f + \varepsilon$ of 
+each fluid where $\varepsilon = 0.0001N(0,1)$. The model parameters trigger phase separation with a sharp interface at 
+the start of the simulation. Periodic boundary conditions are applied on all sides unless the system is undergoing shear. 
+The shear gradient is applied as a velocity in the z direction across the x axis and implemented as a Lees-Edwards 
+(LE) boundary condition in the yz planes. \cite{wagner_leesedwards_2002, lorenz_lees-edwards_2009, yang_capillary_2022} 
+These boundaries move with velocities $u_{LE}$ and $-u_{LE}$ to conserve momentum, with a shear rate 
+$\dot{\gamma} = \frac{2 u_{LE}}{L_x}$. LE boundaries are preferred over walls to avoid affecting viscosity measurements. 
+\cite{wagner_leesedwards_2002, lorenz_lees-edwards_2009, yang_capillary_2022}
+
+Bijel templates have been synthesized using water/2-6-lutidine for further applications. \cite{lee_making_2013} 
+While intrinsically polymerizable bijels have been prepared using oligomeric polymers, STRIPS and VIPS currently 
+utilize small molecule liquids in their bijel casting mixtures. Therefore, an experimentally viable system using 
+water/2-6-lutidine will be discussed in the context of the work presented here. The critical temperature (UCST) 
+for this system is $T_c = 34 ^{\circ}C$, with many systems heated to $T = 40^{\circ}C$ to form the bijel. At this 
+temperature, the fluid properties are $\sigma = 0.22 mN/m$ and $\eta = 2.38 mPas$. \cite{grattoni_lower_1993} 
+Fei et al. developed a method to synthesize polystyrene microparticles ($(R_p = 2 \mu m)$) with tunable geometries 
+by mechanically stretching or compressing them, then coating them with nickel to create magnetic microparticles with 
+a dipole moment of approximately$\approx 3 \cdot 10^{-14} Am^2$. \cite{fei_active_2017, fei_magneto-capillary_2020} 
+Comparing the physical properties to simulation parameters, the simulations correspond to a length scale of
+$\Delta x = 252 \cdot 10^{-9} \text{m}$, timescale of $\Delta t = 624 \cdot 10^{-9} \text{s}$, 
+mass scale of $\Delta m = 2.24 \cdot 10^{-15} \text{kg}$ and charge scale of $\Delta q = 2.948 \cdot 10^{-7} \text{C}$.
+
+\section{Model results}
+\label{section:model_results}
+
+\subsection{Surface tension}
+\label{section:model_surface_tension}
+
+In experiments, Wilhelmy and ring tensionometry are used to measure the surface tension from the force needed 
+to break through the interface. Pendant drop tensionometry is also used by measuring the pressure required to 
+maintain a droplet of analyte at a various sizes and utilizing the Young-Laplace equation to calculate the 
+surface tension of the system. \cite{sun_assembly_2013, berry_measurement_2015}
+Upon extrusion of a droplet from a reservoir, the size of a droplet is determined by the balance between 
+cohesive forces between bubble molecules and geometrical forces that attempt to reduce the curvature of a 
+system by increasing its size. For spherical droplets, the equation simplifies to 
+$\Delta P = \frac{2 \sigma}{R_d}$ where $\Delta P$ is the difference in scalar pressure 
+between the center of the droplet and the ambient pressure, $\sigma$ is the surface tension 
+of the interface and $R_d$ is the radius of the droplet.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale = 0.5]{figures/model_validation/surface_tension.png}
+    \caption{Plot of the surface tension of the multicomponent model in this work calculated using the 
+    Young-Laplace equation.}
+    \label{fig:young_laplace_valid}
+\end{figure}
+
+Using the fluid and non-ideal mixing parameters defined in Table \ref{table:model_params}, a single water in oil 
+droplet, was initialized in the center of the system and run till the droplet radii reached steady state. 
+This process was repeated for various droplet diameters, specified between $70$ and $85 \%$ of the system size at $5\%$ 
+increments. The system had a box length of $L = 64$ and was run for $50000$ timesteps with periodic boundary conditions 
+on all sides. Data was dumped every 10000 timesteps with only the last timestep used to calculate the values shown. Due 
+to the diffuse interface present in this method, the density profiles were verified to be at steady state at the end of 
+the simulation before further analysis was performed. \cite{frijters_effects_2012} Past work also showed that the 
+pressures remained constant after 5 lattice units away from the interface. \cite{frijters_effects_2012}
+
+The pressure difference was calculated using the difference in scalar pressure between the center of the droplet and 
+one of the corners of the box. Two techniques exist to calculate the radius of the droplet. The first directly measures 
+the distance between opposite points of the droplet as measured from the density profile at opposite points of the droplet, 
+and the second is based upon the total mass and density of the fluid making up the droplet. The second method offers greater 
+accuracy by avoiding discretization errors that may exist in the first method, and also allows for the correction of 
+particle volume at the interface if the system contained them. First, a local effective mass density 
+$\rho^b_{eff} = \rho^{b}_{d} - \rho^{b}_{m}$ is found by calculating the difference in density between the blue 
+fluid in the droplet and in the matrix. Next, the droplet mass is calculated as $M_d = \sum_{\mathbf{x}}{\rho_{eff}^{b}}$. 
+The radius of the droplet can then be calculated from the mass and density of the droplets as $R_d = \sqrt[3]{\frac{3}{4\pi} 
+\frac{M_d}{\rho^b_d - \rho^b_m}}$. To linearize the plot, the $\Delta P$ was plotted against $\frac{2}{R_d}$ with 
+$\sigma$ being the slope of the fit.
+
+Figure \ref{fig:young_laplace_valid} shows the results of the fit conducted of the Young-Laplace equation demonstrating 
+that under these fluid and mixing parameters, the surface tension is $\sigma = 0.0267$. The fit was performed using 
+\texttt{scipy.optimize.curve\_fit} with the fit function defined as $y = mx$.

### 2025-04-13 chapters/lit_review_new.tex
Changes 1. Added paper attribution as footnotes 2. Fixed some language in lit review

@@
 free energy through composition modulation \cite{cahn_free_1958}. The dynamics of spinodal decomposition were characterized by Cahn and Hilliard \cite{cahn_spinodal_1961}. 
-We first begin by defining the free energy of a regular solution given by,
+We first begin by defining the free energy of a regular binary solution given by,
 
 \begin{equation}
-    G_m (c) = \chi (1 - c)c + N_a k_B T \left[(1 - c)\ln(1 - c) + c \ln(c)\right]
+    \Delta G_m (c) = \chi (1 - c)c + N_a k_B T \left[(1 - c)\ln(1 - c) + c \ln(c)\right]
 \end{equation}
 
-This bulk free energy characterizes the thermodynamic driving forces for phase separation. Alternative forms of the free energy can be defined based on the double well potential or
-Flory-Huggins theory based on the desired objectives of the model. In real systems, the interface between two partially miscible fluids is diffuse, meaning that the composition 
-transitions smoothly across a finite interface width. To account for this, a gradient energy penalty is added to the free energy to penalize sharp spatial variations in 
-composition, yielding the free energy functional of the system. The total free energy functional is given by,
+When $\chi = 0$ the free energy of an ideal solution is recovered. When $\chi > 0$ repulsive interactions between the components 
+causes the system to phase separate. Alternative forms of the free energy can be defined based on the double well potential or
+Flory-Huggins theory based on the desired objectives of the model. In real systems, the interface between two partially miscible fluids is 
+diffuse, meaning that the composition transitions smoothly across a finite interface width. To account for this, a gradient energy penalty is 
+added to the free energy to penalize sharp spatial variations in composition, yielding the free energy functional of the system. 
+The total free energy functional is given by,
 
@@
 where $\kappa$ is the gradient energy coefficient controlling the interface width. Larger \(\kappa\) values correspond to wider interfaces.
+$f(c)$ is obtained from $\Delta G_m (c)$.
 The chemical potential is then defined as the variational derivative of the free energy functional,

### 2025-04-13 chapters/paper1_5.tex
Changes 1. Added paper attribution as footnotes 2. Fixed some language in lit review

@@
-\section{Introduction}
-
-This section is based on work submited to the American Institude of Physics, Physics of Fluids journal.
-It is reproduced from submission number \#POF25-AR-DSFD2024-03180, with the permission of AIP Publishing.
+\section[Introduction]{Introduction\protect\footnote{This section is based on work submited to the American Institude of Physics, Physics of Fluids journal.
+                        It is reproduced from submission number \#POF25-AR-DSFD2024-03180, with the permission of AIP Publishing.}}
 
@@
 \section{Results}
+% \section[Results]{Results\protect\footnote{This section is based on work submited to the American Institude of Physics, Physics of Fluids journal.
+%                     It is reproduced from submission number \#POF25-AR-DSFD2024-03180, with the permission of AIP Publishing.}}
 
@@
 
-\section{Conclusions\label{conclusions}}
+\section{Conclusion}
+% \section[Conclusion]{Conclusions\protect\footnote{This section is based on work submited to the American Institude of Physics, Physics of Fluids journal.
+% It is reproduced from submission number \#POF25-AR-DSFD2024-03180, with the permission of AIP Publishing.}}
 

### 2025-04-13 chapters/paper1_new.tex
adjusted footnote
Changes 1. Updating some refereces of analysis to link previous sections which do the same analysis to prevent repetition 2. Updating paper 2 to remove junk results
Changes 1. Added paper attribution as footnotes 2. Fixed some language in lit review

@@
-\section{Introduction}
+% \section{Introduction}
 
-This section is based on work published in the Royal Society of Chemistry's Soft Matter journal. \cite{karthikeyan_formation_2024} 
-It is reproduced from Ref \cite{karthikeyan_formation_2024} with permission from the Royal Society of Chemistry.
+% This section is based on work published in the Royal Society of Chemistry's Soft Matter journal.
+% It is reproduced from Ref \cite{karthikeyan_formation_2024} with permission from the Royal Society of Chemistry.
+
+\section[Introduction]{Introduction\protect\footnote{This section is based on work published in the Royal Society of Chemistry's Soft Matter journal.
+It is reproduced from Ref.~\cite{karthikeyan_formation_2024} with permission from the Royal Society of Chemistry.}}
 
@@
 
+% \section[Results]{Results\protect\footnote{This section is based on work published in the Royal Society of Chemistry's Soft Matter journal.
+It is reproduced from Ref.~\cite{karthikeyan_formation_2024} with permission from the Royal Society of Chemistry.}}
 \section{Results}
@@
         L_n(t) = 2\pi \left( \frac{\sum_k S(k,t)}{\sum_k k^n S(k,t)} \right)^{\frac{1}{n}}
+        \label{eq:spherically_averaged_structure_factor}
     \end{equation}
@@
     L_d(t)=2\pi\sqrt{\frac{\sum_{\vec{k}}S(\vec{k},t)}{\sum_{\vec{k}}\sum_\beta k_\beta^2 S(\vec{k},t)}} .
+    \label{eq:directional_structure_factor}
     \end{equation}
@@
 
+% \section[Conclusions]{Conclusions\protect\footnote{This section is based on work published in the Royal Society of Chemistry's Soft Matter journal.
+It is reproduced from Ref.~\cite{karthikeyan_formation_2024} with permission from the Royal Society of Chemistry.}}
 \section{Conclusions}

### 2025-04-13 chapters/paper2.tex
Changes 1. Added paper attribution as footnotes 2. Fixed some language in lit review

@@
-\section{Introduction}
+\section[Introduction]{Introduction\protect\footnote{Sections of this chapter appear in a manuscript submitted to Springerlink as part of the International Conference on Computational 
+Science (ICCS) 2025 in the Computing and Data Science for Materials Discovery and Design track, submission number 259 and is
+reproduced with permission of Palgrave Springer Nature.}}
 
-Sections of this chapter appear in a manuscript submitted to Springerlink as part of the International Conference on Computational 
-Science (ICCS) 2025 in the Computing and Data Science for Materials Discovery and Design track, submission number 259 and is
 % [author and/or editor(s) of contribution], [volume and/or contribution title], [year of publication], [publisher (as it appears on our copyright page)] \
-reproduced with permission of Palgrave Springer Nature.
 
@@
 
-\section{Results}\label{sec:results_p2}
+\section{Results}
+% \section[Results]{Introduction\protect\footnote{Sections of this chapter appear in a manuscript submitted to Springerlink as part of the International Conference on Computational 
+% Science (ICCS) 2025 in the Computing and Data Science for Materials Discovery and Design track, submission number 259 and is
+% reproduced with permission of Palgrave Springer Nature.}}
+% \label{sec:results_p2}
+
 \subsection{Kinetic arrest}
@@
 of the fluid domains in the bijel. Chapter 4 showed that application of magnetic fields cause reordering of particles at interfaces towards the
-direction of the applied field, making the particle monolayer have nematic ordering. In the case of already formed bijels,
+direction of the applied field, enforcing nematic order in the particle monolayer. In the case of already formed bijels,
 this reorientation reduces the interface area stabilized, facilitating local unjamming and domain growth. In contrast, when the field strength is reduced, 
@@
 
-\subsection{Switching a field onto a bijel with disordered particles}
+\subsection{Applying a field onto a bijel with disordered particles}
 \subsubsection{Field strength dependence on domain size}
@@
     \includegraphics[scale=0.6]{../figures/results/paper2/domain_size-field_on.png} 
-    \caption{Plots of the time evolution of the normalized domain size \(L/R\) (markers) and nematic order parameter 
-             \(S\) (lines) for bijels stabilized by oblate (left, \(\alpha = 0.5\)) and prolate (right, \(\alpha = 2.0\)) ellipsoidal particles under varying 
-             magnetic field strengths. Here, \(R = 7.9\) is the volume-equivalent sphere radius.} 
+    \caption{Plots of the time evolution of the normalized domain size \(L/R\) (markers) for bijels stabilized by oblate (left, \(\alpha = 0.5\)) 
+             and prolate (right, \(\alpha = 2.0\)) ellipsoidal particles under varying magnetic field strengths. Here, \(R = 7.9\) is the volume-equivalent sphere radius.} 
     \label{fig:domain_size-field_on} 
@@
 domain growth is observed driven by steric rearrangement of interfacial particles, consistent 
-with findings by Günther et al.~\cite{gunther_timescales_2014}. Notably, the initiation of domain coarsening under applied magnetic fields is more rapid 
-for bijels stabilized by oblate particles compared to prolate systems. However, the rejamming process takes longer.
-
-In the absence of magnetic fields, a slight increase in $S(t)$ is observed, consistent with the sterically driven reorientation of particles at the interface.
-\cite{gunther_timescales_2014} Upon application of a magnetic field, the curves for \(S(t)\) increase before plateauing, indicating the parameter has reached
-its saturation value. Notably at stronger field strengths, $S(t)$ precedes the increase in domain size for both particle shapes analyzed. Overall, these results 
-confirm that domain coarsening in magnetically responsive bijels occurs as a result of applied magnetic fields, with the degree of change observed dependent 
-on the strength of the applied field.
+with findings by Günther et al.~\cite{gunther_timescales_2014}.
 
@@
 
-Figure~\ref{fig:domain_size_aniso-field_on} shows that the application of a magnetic field induces clear domain size anisotropy in bijels stabilized by both oblate 
+Figure~\ref{fig:domain_size_aniso-field_on} shows that the application of a magnetic field induces domain size anisotropy in bijels stabilized by both oblate 
 and prolate particles. Even at zero field, a small degree of anisotropy is observed, which increases substantially with rising field strength. For oblate particles, 
@@
 with low \( S \) values. The time-dependent development of nematic ordering reflects the interplay between magnetic torque and interfacial mechanics. 
-The increase in \( S \) suggests a process of unjamming and re-jamming at the fluid-fluid interface caused by the magnetic field inducing rotational 
-motion of the dipolar particles, overcoming initial interfacial jamming and allowing particles to realign to the field. As alignment 
+The increase in \( S \) demonstrates the application of a constant magnetic field causes particle to rotate at the interface to align with the magnetic field.
+Linking the alignment of the particles to the domain size change showed in Figure \ref{fig:domain_size-field_on}, the rotation of particles to the magnetic field 
+overcomes the initial interfacial jamming. allowing particles to realign to the field. As alignment 
 progresses, the particles re-jam. In Chapters 4 and 5, the application of the magnetic field modified the angle of the particle to the interface and the
@@
 
-\subsection{Decreasing the applied field}
+\subsection{Switching off an applied field}
 \label{decreasing-the-applied-field}
@@
 clarify the mechanisms that underpin the apparent irreversibility captured in the hysteresis response and further 
-assess the role of processing history in bijel stability.
+assess the role of the particles in bijel stability.
 
@@
 from the field-aligned configuration begin to emerge. In contrast, for \(\bar{B}: 1.0 \rightarrow 0.0\), where the 
-initial nematic order was stronger, the system exhibits more apparent disorganization by the final time step. This 
+initial nematic order was stronger, the particles exhibits more apparent disorganization by the final time step. This 
 suggests that while the jammed interface resists large-scale rearrangement, there is a gradual relaxation of particle 
@@
 
-\section{Conclusions}
+\section{Conclusion}
+% \section[Conclusion]{Conclusion\protect\footnote{Sections of this chapter appear in a manuscript submitted to Springerlink as part of the International Conference on Computational 
+% Science (ICCS) 2025 in the Computing and Data Science for Materials Discovery and Design track, submission number 259 and is
+% reproduced with permission of Palgrave Springer Nature.}}
 
@@
 When investigating the effect of the application of magnetic fields, our results revealed that applying magnetic fields post-formation induces domain coarsening up to 5\%, with 
-field-induced anisotropy dependent on particle shape. Oblate particles exhibited growth primarily in the perpendicular direction by up to 60\%, while prolate particles showed 
-coarsening along the field direction up to 40\%, both accompanied by a decrease in tortuosity. These changes arise from particle reorientation to the field, followed by 
+field-induced anisotropy dependent on particle shape. These changes arise from particle reorientation to the field, followed by 
 local unjamming and interfacial rearrangement before re-jamming occurs, as characterized using the average interface angle of the particles and the 
@@
 
-These results show that rapid reorientation of the particle stabilizers is necessary to induce structural response in bijels. This is illustrated through structural response
+These results show that rapid coordinated reorientation of the particle stabilizers is necessary to induce structural response in bijels. This is illustrated through structural response
 of bijels occurring upon application of the field, causing rapid realignment of particles to the applied field direction while slow realignment of particles away from
@@
 
-While our simulations offer valuable insights into the tunability of bijels, they were limited to a single set of fluid and particle parameters. Future work could explore the 
+While our simulations offer insights into the tunability of bijels, they were limited to a single set of fluid and particle parameters. Future work could explore the 
 effects of particle size, volume fraction, interparticle forces, and field orientation or gradients, all of which may unlock additional control over bijel structure.

### 2025-04-13 chapters/paper3.tex
Changes 1. Added paper attribution as footnotes 2. Fixed some language in lit review

@@
              a function of the initial microstructure and applied magnetic field. The observed stress response is difficult to say when a steady
-             state is reached, with pseudo-steady states being obtained from the regions with the circular markers.} 
+             state is reached, with pseudo-steady states being obtained from the regions demarcated with the circular markers.} 
     \label{fig:stress_time} 
@@
 This absence of steady-state behavior is attributed to the continued coarsening of the bicontinuous domains and the progressive reorientation of interfacial 
-particles under shear \cite{tavacoli_novel_2011, macmillan_rheological_2019}. Tavacoli et al.\ showed that mechanical perturbation of bijels, such as the 
+particles under shear \cite{tavacoli_novel_2011, macmillan_rheological_2019}. Tavacoli et al. showed that mechanical perturbation of bijels, such as the 
 insertion of a needle to measure yield stress, resulted in irreversible structural deformation, particularly in ethanediol/nitromethane systems 
-\cite{tavacoli_novel_2011}. Similarly, Macmillan et al.\ observed that repeated shearing of bijels synthesized by direct mixing led to degraded mechanical 
+\cite{tavacoli_novel_2011}. Similarly, Macmillan et al. observed that repeated shearing of bijels synthesized by direct mixing led to degraded mechanical 
 performance over time, suggesting a link between structural evolution and rheological response \cite{macmillan_rheological_2019}. To characterize the rheology 
@@
 \begin{equation}
-    \sigma_{xz} = \sigma_{y} + K\dot{\gamma}^{n}    
+    \sigma = \sigma_{y} + K\dot{\gamma}^{n}    
 \end{equation}
 
-In the Herschel-Bulkley model, $\sigma_{xz}$ denotes the computed shear stress, $\sigma_y$ is the yield stress, $K$ represents the flow consistency index, 
+In the Herschel-Bulkley model, $\sigma$ denotes the computed shear stress, $\sigma_y$ is the yield stress, $K$ represents the flow consistency index, 
 and $n$ is the flow index characterizing the degree of shear thinning. In certain cases, simulations conducted at the lowest shear capillary number 
 ($Ca_s = 10^{-6}$) exhibited insufficient stress resolution or high variability, and were excluded from model fitting where appropriate. For each case, 
-$\sigma_{xz}$ is extracted from the pseudo-steady-state region of the stres-time curves, while the corresponding shear rate $\dot{\gamma}$ is derived from 
+$\sigma$ is extracted from the pseudo-steady-state region of the stress-time curves, while the corresponding shear rate $\dot{\gamma}$ is derived from 
 the imposed capillary number, $Ca_s$. The resulting fits for the various bijel systems are presented in Figure~\ref{fig:stress_strain}.
@@
 Figure~\ref{fig:stress_strain} presents the shear stress $\sigma_{xz}$ as a function of shear rate $\dot{\gamma}$ for bijels stabilized by oblate ($\alpha = 0.5$) 
-and prolate ($\alpha = 2.0$) ellipsoidal particles, fitted using the Herschel-Bulkley model. In both cases, the curves exhibit nonlinear scaling with $\dot{\gamma}$, 
+and prolate ($\alpha = 2.0$) ellipsoidal particles, fitted using the Herschel-Bulkley model. In both cases, the curves exhibit sublinear scaling with $\dot{\gamma}$, 
 confirming a non-Newtonian, shear-thinning response. For bijels stabilized by oblate particles, the stress-strain curves are more widely separated, indicating 

### 2025-04-13 chapters/final_remarks.tex
Removed hyperbole from final remarks

@@
 
-This work provides several key insights that significantly advance the current understanding of field-responsive emulsions and structurally 
-tunable soft materials. By integrating ellipsoidal particle design with magnetic field stimuli, we demonstrate a new axis of control over 
+This work provides several insights that advance the current understanding of field-responsive emulsions and structurally 
+tunable soft materials. By integrating ellipsoidal particles with magnetic field stimuli, we demonstrate a new axis of control over 
 bijel formation and function. Conceptually, our results refine the understanding of interfacial jamming in bijels. The identification of
 unjamming-rejamming mechanisms, modulated by both field strength and particle ordering, reveals that bijel structures are not passively 
-determined by initial phase separation dynamics. Instead, they are dynamically reconfigurable under external fields, with the extent of 
-reconfiguration governed by prior structural states.
+determined by initial phase separation dynamics. Instead, they are dynamically reconfigurable under external fields
 
@@
 perspective provides better predictive capacity for tailoring materials with application-specific structural features, such as tortuosity 
-for mass transport or local ordering for mechanical performance.
+for transport limited applications or local ordering for mechanical performance.
 
@@
 to environmental stimuli like temperature and pH—critical features for controlled drug delivery. Incorporating such particles 
-could significantly alter jamming dynamics, interfacial rearrangement, and field-induced responsiveness. These effects may be 
-explored computationally using Lattice Boltzmann Methods integrated with immersed boundary frameworks, incorporating attractive
-particle  interactions to account for electrostatic cohesion and deformability \cite{silva_lattice_2024}. This direction opens opportunities 
+could alter jamming dynamics, interfacial rearrangement, and field-induced responsiveness. These effects may be 
+explored computationally using Lattice Boltzmann Methods integrated with immersed boundary method based frameworks to account for
+particle deformation or attractive particle interactions to account for electrostatic cohesion \cite{silva_lattice_2024}. This direction opens opportunities 
 to design bijel systems with enhanced adaptability and function, tailored for application-specific demands.
@@
 As such, the interplay between interfacial ordering, particle-scale dynamics, and existing order can be characterized more convincingly by 
-investigating the dynamics of the particle more systematically by accounting for thermal fluctuations of the fluid. This would involve 
+investigating the dynamics of the particle monolayer more convincingly by accounting for thermal fluctuations of the fluid. This would involve 
 implementation of a fluctuating Lattice Boltzmann Method which would facilitate identification of the glassy dynamics in the system, 
-including the onset of arrest and structural aging characterized with the microstructure in Gunther et al \cite{gunther_timescales_2014}.
+including the onset of arrest and structural aging characteristic of colloidal glasses \cite{weeks_introduction_2017, torquato_jammed_2010}.
 
-Another promising avenue for future investigation involves the use of gradient or rotating magnetic fields in place of constant fields. This
+Another avenue for future investigation involves the use of gradient or rotating magnetic fields in place of constant fields. This
 would impart a force on the particles in addition to the torque that magnetic particles experience under 
@@
 particularly useful for creating functionally graded materials with hierarchical transport properties.
-
-In parallel, rotating magnetic fields offer a dynamic mechanism for restructuring particle arrangements 
-at the interface \cite{spatafora-salazar_hierarchical_2021, martinezpedrero_collective_2020}. 
-In ferrofluids and magnetic colloidal suspensions, such fields have been shown to induce chain or ring formation, depending on the rotation frequency and field 
-strength \cite{spatafora-salazar_hierarchical_2021, martinezpedrero_collective_2020}. 
-Translating this mechanism to bijels, a rotating field could be used to modulate interfacial jamming behavior, promoting controlled 
-unjamming and reorientation of particles prior to re-jamming. This dynamic control could enable finer tuning of microstructure than static fields, 
-potentially achieving reversible and spatially patterned domain morphologies. Importantly, the effectiveness of this strategy would depend on 
-matching the rotation frequency to the particle relaxation timescales within the bijel, a factor that can be systematically explored in simulation.
 
@@
 and Data-intensive Research at the University of Delaware and in the Delaware Region, Rudolf Eigenmann, Benjamin E. 
-Bagozzi, Arthi Jayaraman, William Totten, and Cathy H. Wu, University of Delaware, 2021
+Bagozzi, Arthi Jayaraman, William Totten, and Cathy H. Wu, University of Delaware, 2021.
 

### 2025-04-13 chapters/paper2.tex
Streamlined introduction

@@
 resilient to removal of stimuli. Analysis reveals that particle unjamming, reorientation at the interface, and subsequent re-jamming are responsible for these structural transformations.
+These findings demonstrate how magnetic field manipulation, in combination with ellipsoidal particle stabilization, enables tunable, on-demand microstructure 
+control in bijels, offering new capabilities for adaptive material design.
 
-To understand the saturation behavior, we applied magnetic fields of varying strength to bijel templates formed under increasing initial field conditions. We observed that 
-a greater initial nematic order parameter negatively correlated with the extent of microstructure change. Finally, switching off the magnetic field in pre-aligned bijels had little 
-impact on the microstructure, indicating that the jammed interfacial network prevents reversal of anisotropic features. These findings underscore the importance of processing 
-history and demonstrate how magnetic field manipulation, in combination with anisotropic particle stabilization, enables tunable, on-demand microstructure control in bijels, 
-offering new capabilities for adaptive material design.
+% To understand the saturation behavior, we applied magnetic fields of varying strength to bijel templates formed under increasing initial field conditions. We observed that 
+% a greater initial nematic order parameter negatively correlated with the extent of microstructure change. Finally, switching off the magnetic field in pre-aligned bijels had little 
+% impact on the microstructure, indicating that the jammed interfacial network prevents reversal of anisotropic features.
 

### 2025-04-14 chapters/final_remarks.tex
Fixed some captions for figures

@@
 soft and cohesive particles are known to exhibit distinct glass transition behaviors and rheological responses compared 
-to hard-sphere systems \cite{weeks_introduction_2017, torquato_jammed_2010}. In bijel architectures, attractive interactions have been 
+to rigid-sphere systems \cite{weeks_introduction_2017, torquato_jammed_2010}. In bijel architectures, attractive interactions have been 
 proposed as a strategy to form “armored” interfaces, potentially enhancing mechanical integrity and enabling higher flow rates in catalytic 
@@
 Similarly, soft particles such as nanogels and hydrogels have attracted interest in biomedical contexts, offering tunable responsiveness 
-to environmental stimuli like temperature and pH—critical features for controlled drug delivery. Incorporating such particles 
+to environmental stimuli like temperature and pH for controlled drug release applications for example \cite{thorson_bijel-templated_2019, vanoli_bijels_2022}. 
+Incorporating such particles 
 could alter jamming dynamics, interfacial rearrangement, and field-induced responsiveness. These effects may be 

### 2025-04-14 chapters/paper2.tex
Fixed some captions for figures

@@
     \centering 
-    \includegraphics[scale=0.4]{../figures/results/paper2/nematic-field_on.png} 
+    \includegraphics[scale=0.6]{../figures/results/paper2/nematic-field_on.png} 
     \caption{Evolution of the nematic order parameter \( S \) over time for bijels stabilized with disc-like particles (left) and rod-like particles (right), 
@@
 \includegraphics[scale=0.6]{../figures/results/paper2/domain_size-field_down.png} 
-\caption{Plot of the spherically averaged domain size normalized with $R_p$ of the particle and the nematic order parameter of each bijel over time. 
+\caption{Plot of the spherically averaged domain size normalized with $R_p$ of the particle plotted over time. 
          Each color represents bijel templates made with different field strengths $\bar{B}$. We show that there is domain coarsening when the field 
-         is switched off, along with a reduction in the ordering of the particles.} 
+         is switched off.} 
 \label{fig:domain_size-field_down} 

### 2025-04-14 chapters/paper3.tex
Fixed some captions for figures

@@
 
-Particle ordering plays a critical role in determining the rheological behavior of suspensions, as aligned particles can more readily slide past one another 
-under shear, delaying structural breakdown. In bijels, where particles are adsorbed at the fluid-fluid interface, this interfacial confinement may significantly 
-influence the degree of slip and the onset of yielding. Prior studies have shown that bijels exhibit shear-thinning behavior consistent with Herschel-Bulkley rheology, 
+Particle ordering is one factor that affects the rheological behavior of suspensions, as aligned particles reduce particle-fluid interactions, reducing the
+induced shear stress. In bijels, where particles are adsorbed at the fluid-fluid interface, interfacial confinement may significantly 
+influence the degree of slip and the onset of yielding. Prior studies have shown that bijels exhibit shear-thinning behavior consistent with the Herschel-Bulkley fluid model, 
 indicating a non-Newtonian response governed by both interfacial structure and particle dynamics \cite{macmillan_rheological_2019}. To investigate these effects in 
@@
     \includegraphics[scale=0.5]{../figures/results/paper3/stress_strain-all.png} 
-    \caption{Fitting the experimental shear stress to the strain rate using the Herschel-Bulkley model. We characterize the bijels are 
-             shear thinning in all cases and that the bijels become less shear thinning as the particle order increases. We also
-             demonstrate that the particle ordering affects the yield stress differently for particles stabilized by oblate and 
-             prolate particles.} 
+    \caption{Fitting the experimental shear stress to the strain rate using the Herschel-Bulkley model for bijels stabilized by
+             ellipsoidal particles with no magnetic field applied $\bar{B} = 0$ and an applied field of $\bar{B} = 1$ when starting at different
+             initial microstructures.} 
     \label{fig:stress_strain} 
@@
              ellipsoidal particles as a function of the applied shear rate for bijels made with no field and a field strength of $\bar{B} = 1$,
-             keeping the field strength the same. We show that the orientation of particles to the applied shear is dependent on the
-             applied shear rate, particle ordering to the field and the particle shape.} 
+             keeping the field strength the same.} 
     \label{fig:theta_z_specific} 
@@
              ellipsoidal particles as a function of the applied shear rate for bijels made with no field and a field strength of $\bar{B} = 1$,
-             keeping the field strength the same. We show that the particles tilt out of the interface upon application of shear with the degree of
-             interfacial tilting a function of the initial particle order and particle shape.} 
+             keeping the field strength the same during shear.} 
     \label{fig:interface_angle_shear} 
@@
 enough to overcome local resistance and drive reorientation. The resulting changes in local packing and alignment are reflected in variations in the bond-orientational order parameter 
-$\langle Q6 \rangle$, particularly under conditions where the bijel retains structural integrity and resists complete flow-induced breakdown.
+$\langle Q6 \rangle$.
 

### 2025-04-14 chapters/paper3.tex
Removed some repetition in chapter 7

@@
 
-While the rheology of emulsions stabilized by spherical particles has been extensively characterized, ellipsoidal particles introduce additional complexity through interfacial locking and anisotropic drag,
-which can suppress coalescence and resist flow differently under shear \cite{madivala_self-assembly_2009, daware_emulsions_2015, sun_assembly_2013}. Under shear, ellipsoidal particles 
-can promote shear banding, wherein particle-fluid interactions create localized variations in velocity profiles \cite{xu_relation_2013}. Furthermore, suspensions of magnetically responsive particles, 
+Suspensions made with spherical particle have non-Newtonian behavior, originating from particle-particle interactions and particle-fluid interactions
+affecting the shear shear stress. \cite{xu_relation_2013}
+Ellipsoidal particles introduce additional complexity through interfacial locking and anisotropic drag, 
+which can suppress coalescence and resist deformation under shear \cite{madivala_self-assembly_2009, daware_emulsions_2015, sun_assembly_2013}.
+Furthermore, suspensions of magnetically responsive particles,
 such as ferrofluids, exhibit a pronounced increase in viscosity due to field-induced self-assembly that restricts fluid flow \cite{qiao_magnetorheological_2012}. 
@@
 particles during flow.
-Shear is imposed via a range of dimensionless shear capillary numbers, defined as $Ca_s = \frac{\dot{\gamma} R_s \eta_f}{\sigma}$, where $\dot{\gamma}$ is the applied shear rate,
+Shear is imposed via a range of dimensionless shear capillary numbers, defined as $\text{Ca_s}  = \frac{\dot{\gamma} R_s \eta_f}{\sigma}$, where $\dot{\gamma}$ is the applied shear rate,
 $R_s = 7.9$ is the equivalent spherical radius of the ellipsoids, $\eta_f$ is the dynamic viscosity of the continuous phase, and $\sigma$ is the interfacial tension. 
-\cite{frijters_effects_2012, yang_capillary_2022} We explore five shear conditions spanning $Ca_s = 1 \times 10^{-4}$ to $1 \times 10^{-6}$, capturing the transition from strong deformation to 
+\cite{frijters_effects_2012, yang_capillary_2022} We explore five shear conditions spanning $\text{Ca_s} = 1 \times 10^{-4}$ to $1 \times 10^{-6}$, capturing the transition from strong deformation to 
 near-equilibrium interfacial response.
@@
 induced shear stress. In bijels, where particles are adsorbed at the fluid-fluid interface, interfacial confinement may significantly 
-influence the degree of slip and the onset of yielding. Prior studies have shown that bijels exhibit shear-thinning behavior consistent with the Herschel-Bulkley fluid model, 
-indicating a non-Newtonian response governed by both interfacial structure and particle dynamics \cite{macmillan_rheological_2019}. To investigate these effects in 
-the presence of magnetic fields and varying degrees of particle ordering, we apply constant shear to the bijel templates and plot the resulting time evolution of 
+influence the degree of slip and the onset of yielding. Prior studies have shown that bijels exhibit shear-thinning behavior consistent 
+with the Herschel-Bulkley fluid model \cite{macmillan_rheological_2019}. To investigate the particle ordering and reorientation effects of magnetic fields
+applied onto bijels, we apply constant shear to the bijel templates and plot the resulting time evolution of 
 the shear stress, as shown in Figure~\ref{fig:stress_time}.
@@
 Figure \ref{fig:stress_time} demonstrates that a definitive steady-state shear stress is not reached within the simulated timeframes across all conditions. 
-This absence of steady-state behavior is attributed to the continued coarsening of the bicontinuous domains and the progressive reorientation of interfacial 
+This is attributed to the continued coarsening of the bicontinuous domains and the progressive reorientation of interfacial 
 particles under shear \cite{tavacoli_novel_2011, macmillan_rheological_2019}. Tavacoli et al. showed that mechanical perturbation of bijels, such as the 
 insertion of a needle to measure yield stress, resulted in irreversible structural deformation, particularly in ethanediol/nitromethane systems 
-\cite{tavacoli_novel_2011}. Similarly, Macmillan et al. observed that repeated shearing of bijels synthesized by direct mixing led to degraded mechanical 
-performance over time, suggesting a link between structural evolution and rheological response \cite{macmillan_rheological_2019}. To characterize the rheology 
+\cite{tavacoli_novel_2011}. Similarly, Macmillan et al. observed that shearing of bijels synthesized by direct mixing led to degraded mechanical performance 
+over time, as the applied shear progressively disrupted the bijel structure \cite{macmillan_rheological_2019}. To characterize the rheology 
 of these evolving systems, we identify pseudo-steady-state regions within the stress-time profiles, defined as intervals where the rate of change of shear 
-stress is minimal and persists for the longest continuous duration. Within these regions, the stress response is fitted to the applied shear rate using a 
+stress is minimal and persists for the longest continuous duration. Within these regions, the stress response is fit to the applied shear rate using a 
 Herschel-Bulkley model:
@@
 
-In the Herschel-Bulkley model, $\sigma$ denotes the computed shear stress, $\sigma_y$ is the yield stress, $K$ represents the flow consistency index, 
+where $\sigma$ denotes the computed shear stress, $\sigma_y$ is the yield stress, $K$ represents the consistency index, 
 and $n$ is the flow index characterizing the degree of shear thinning. In certain cases, simulations conducted at the lowest shear capillary number 
-($Ca_s = 10^{-6}$) exhibited insufficient stress resolution or high variability, and were excluded from model fitting where appropriate. For each case, 
+($ \text{Ca_s} = 10^{-6}$) exhibited insufficient stress resolution or high variability, and were excluded from model fitting where appropriate. For each case, 
 $\sigma$ is extracted from the pseudo-steady-state region of the stress-time curves, while the corresponding shear rate $\dot{\gamma}$ is derived from 
-the imposed capillary number, $Ca_s$. The resulting fits for the various bijel systems are presented in Figure~\ref{fig:stress_strain}.
+the imposed capillary number, $\text{Ca_s}$. The resulting fits for the various bijel systems are presented in Figure~\ref{fig:stress_strain}.
 
@@
     \end{tabular}
-    \caption{Hershel Bulkley fit parameters for different processing conditions applied to bijels stabilized by ellipsoidal particles.}
+    \caption{Fit parameters for different processing conditions applied to bijels stabilized by ellipsoidal particles.}
     \label{table:rheology_fit}
@@
 
-\subsection{Shear induced particle rearrangement}
+\subsection{Effect of local particle rearrangement on shear properties}
 
@@
 and smaller yield stress respectively. To quantitatively assess the local arrangement of particles at the interface, we compute the ensemble-averaged 
-Steinhardt bond orientational order parameters $q_2$ and $q_6$. 
+Steinhardt bond orientational order parameter $Q6$. 
 \cite{steinhardt_bond-orientational_1983, lechner_accurate_2008, mickel_shortcomings_2013}. The technique to calculate this parameter is provided in
-Equation \ref{eq:steinhardt_definition} We plot the change in 
+Equation \ref{eq:steinhardt_definition}. We plot the change in the ensemble average
 $\langle Q6 \rangle$ of the microstructures as a function of the processing applied in Figure \ref{fig:q6_rheology_init}
@@
 Bonaccorso et al. identified that the spherical particle stabilizers in their bijel simulations oriented to the direction of shear before being
-ejected from the interface. \cite{bonaccorso_shear_2020} Due to the shape of ellipsoidal particles, they adopt a preferred orientation which
-maximizes the interface covered by the particle. \cite{davies_dipolar_2015, davies_interface_2014} Energy must be imparted to rotate the particles
+ejected from the interface \cite{bonaccorso_shear_2020}. Due to the shape of ellipsoidal particles, they adopt a preferred orientation which
+maximizes the interface covered by the particle \cite{davies_dipolar_2015, davies_interface_2014}. Energy must be imparted to rotate the particles
 out of the interface. Upon application of shear, the orientation of particles on the interface will be a function of the applied shear rate, 
-applied magnetic field and the capillary forces of the interface on the particle. \cite{cao_modeling_2021, chhabra_drag_1999, brenner_stokes_1963, naga_capillary_2021}
-Therefore, the degree of interface angle change observed can shed light onto the rheological 
+applied magnetic field and the capillary forces of the interface on the particle \cite{cao_modeling_2021, chhabra_drag_1999, brenner_stokes_1963, naga_capillary_2021}.
+Therefore, the degree of orientational realignment observed can shed light onto the rheological 
 differences of bijels stabilized by prolate and oblate particles as the shear stress determined is affected by the particle rotation on the interface. We focus on
@@
 
-To assess the particle alignment to the applied shear, we calculate the average angle to the direction of shear, $\langle \theta_z \rangle$. This is calculated
-by calculating the angle between the orientation vector $\vec{o}$ and the z axis $\vec{r_z}$ given by 
-$\theta_z = \arccos(\frac{ \vec{o} \cdot \vec{r_z} }{ |\vec{o}| |\vec{r_z}| })$. This is done for all particles with $\langle \theta_z \rangle$ calculated from
-by taking the numerical average of $\theta_z$ for all particles. The results are plotted in Figure \ref{fig:theta_z_specific}.
+To assess the particle alignment to the applied shear, we calculate the average angle to the direction of shear, $\langle \theta_z \rangle$ by calculating the angle 
+between the orientation vector $\vec{o}$ and the z axis $\vec{r_z}$ given by $\theta_z = \arccos(\frac{ \vec{o} \cdot \vec{r_z} }{ |\vec{o}| |\vec{r_z}| })$. 
+This is done for all particles with the numerical mean of all particles, $\langle \theta_z \rangle$, plotted in Figure \ref{fig:theta_z_specific}.
 
@@
 
-From Figure \ref{fig:theta_z_specific}, the effect of the aspect ratio of the particle stabilizer and the ordering of particles to the magnetic field. For oblate 
-particles, the change in $\langle \theta_z \rangle$ over time can be seen to stay approximately the same at shear rates below $Ca = 1e-4$ However at higher shear rates,
-$\langle \theta_z \rangle$ increases rapidly. When comparing this to the results when beginning with magnetic field ordering, $\langle \theta_z \rangle$ can be seen to
-stay approximately the same only at $Ca = 1e-6$. This indicates shear driven reorientation of particles at the interface occurs at higher shear rates in bijels stabilized
-with disordered particles and matching the trend observed in the yield stress. The results for the prolate particles show that particle order increases the applied shear
-necessary to cause particle reorientation on the interface. When taking the $\langle Q6 \rangle$ results into context from Figure \ref{fig:q6_rheology_init}, 
-the effect of magnetic field driven ordering of particles can be seen.
+From Figure \ref{fig:theta_z_specific}, the effect of the aspect ratio of the particle stabilizer and the ordering of particles to the magnetic field can be seen. For oblate 
+particles, $\langle \theta_z \rangle$ stays approximately the same at shear rates below $\text{Ca_s} = 10^{-4}$. However at higher shear rates,
+$\langle \theta_z \rangle$ increases rapidly, indicating that the particle monolayer is reorienting due to the applied shear. When comparing this to the results when beginning with 
+magnetic field ordering, $\langle \theta_z \rangle$ can be seen to stay unaffected by shear only at $\text{Ca_s} = 10^{-6}$. This indicates shear driven reorientation of particles at the interface 
+occurs at higher shear rates in bijels stabilized with disc-like particles with orientational disorder. matching the trend observed in the yield stress. The results for the prolate particles show 
+that particle order increases the applied shear necessary to cause particle reorientation on the interface.
 
@@
 
-The interfacial angle results reveal how particle orientation relative to the local interface evolves under varying shear conditions, highlighting the interplay between particle shape, 
-initial ordering, and shear rate. For disc-like particles, $\langle \psi \rangle$ increases steadily with time, especially at higher shear rates, indicating that shear 
-flow drives discs to tilt further away from the interface normal. This effect is strengthened when the particles are initially ordered as the particles are easier to rotate out of the
+For disc-like particles, $\langle \psi \rangle$ increases steadily with time, especially at higher shear rates, indicating that shear 
+flow drives discs to tilt further away from the interface. This effect is strengthened when the particles are initially ordered as the particles are easier to rotate out of the
 interface when they are tilted. In contrast, rod-like particles exhibit more modest changes in $\langle \psi \rangle$ as the particles are closer to lying flat on the interface, meaning
@@
 stabilized with oblate particles under no magnetic field and prolate particles subjected to a magnetic field, the results show that at low shear rates, particles largely resist 
-reorientation due to interfacial jamming and anchoring forces. However, as the shear rate increases, both $\langle \psi \rangle$ and $\langle \theta_z \rangle$ rise, indicating that 
-particles begin to tilt away from both the interface normal and the shear direction. This suggests that while the particles remain adsorbed at the interface, the imposed shear is strong 
-enough to overcome local resistance and drive reorientation. The resulting changes in local packing and alignment are reflected in variations in the bond-orientational order parameter 
-$\langle Q6 \rangle$.
+reorientation due to interfacial jamming, strengthened through a greater number of particle contacts. However, as the shear rate increases, both $\langle \psi \rangle$ and 
+$\langle \theta_z \rangle$ rise, indicating that particles begin to tilt away from the interface and the shear direction. This suggests that while the particles remain adsorbed 
+at the interface, the imposed shear is strong enough to overcome local resistance and drive reorientation.
 
@@
 In this study, we investigated the rheological behavior of bijels stabilized by magnetically responsive ellipsoidal particles subjected to constant shear. 
-In systems like Solvent Transfer Induced Phase Separation (STrIPS) and Vapor-Induced Phase Separation (VIPS), rheology plays a key role in determining the
+In systems like STrIPS and VIPS, rheology plays a key role in determining the
 microstructure and morphology of the bijel. The presence of anisotropic particles and external magnetic fields further complicates this behavior 

### 2025-04-15 chapters/LBM_technique.tex
Making notation consistent

@@
-Bijels require a multiscale modeling approach to accurately capture the rich array of physical phenomena 
+Bijels require a multiphysics modeling approach to accurately capture the rich array of physical phenomena 
 occurring across multiple length and time scales. Within a bijel, one must consider fluid flow, phase separation, particle-fluid coupling, and interparticle 
@@
 where $\rho$ is the fluid density and $\vec{u}$ is the fluid velocity. Based on the system being modeled, we assume that the fluid is incompressible, reducing the continuity equation to
-$\nabla\cdot \vec{u} = 0$ The momentum conservation equation can also be written by applying Newton's second law to the fluid element. This yields the Cauchy momentum equation for an
-incompressible fluid, where changes in momentum arise due to pressure gradients, viscous stresses, and body forces. The general form of the momentum equation is given by,
+$\nabla\cdot \vec{u} = 0$ The momentum conservation equation can also be written by applying Newton's second law to the fluid element. This yields the Cauchy momentum equation, 
+where changes in momentum arise due to pressure gradients, viscous stresses, and body forces. The general form of the momentum equation is given by,
+
+% \begin{equation}
+    % \rho \left(\frac{\partial u_i}{\partial t} + (u_i\cdot\frac{\partial u_i}{x_i}) \right) = \frac{\partial \sigma_{ij}}{\partial x_j} + f_i
+% \end{equation}
 
 \begin{equation}
-    \rho \left(\frac{\partial u_i}{\partial t} + (u_i\cdot\frac{\partial u_i}{x_i}) \right) = \frac{\partial \sigma_{ij}}{\partial x_j} + f_i
+    \rho \left( \frac{\partial \vec{u}}{\partial t} + (\vec{u}\cdot \nabla \vec{u})  \right) = \nabla \cdot \sigma + \vec{f}
 \end{equation}
 
-where $f_i$ is the force exerted on the fluid from external forces such as gravity or magnetic interactions and $\sigma_{ij}$ is the stress tensor. For a Newtonian, isotropic fluid, 
+where $\vec{f}$ is the force exerted on the fluid from external forces such as gravity or magnetic interactions and $\sigma$ is the stress tensor. For a Newtonian, isotropic fluid, 
 the viscous stress tensor is given by
 
+% \begin{equation}
+%     \sigma_{ij} = -p\delta_{ij} + \eta((\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i}) - \frac{2}{3}(\frac{\partial u_j}{\partial x_i})^2\delta_{ij})
+% \end{equation}
+
 \begin{equation}
-    \sigma_{ij} = -p\delta_{ij} + \eta((\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i}) - \frac{2}{3}(\frac{\partial u_j}{\partial x_i})^2\delta_{ij})
+    \sigma = -p\mathbb{I} + \eta\left( \nabla \vec{u} + (\nabla \vec{u})^T -\frac{2}{3}(\nabla \vec{u})\mathbb{I} \right)
 \end{equation}
@@
 
-In the single component case, $-\nabla p = \vec{f} = 0$ as there are no external forces like gravity acting on the fluid and there are is no hydrodynamic pressure being applied to the 
-fluid resulting in the following form of the incompressible Navier Stokes equation.
-
-\begin{equation}
-    \rho \left(\frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u} \right) = \eta \nabla^2 \vec{u}
-\end{equation}
-
 To facilitate numerical simulation and analysis, it is often useful to express the Navier-Stokes equation in non-dimensional form. Introducing characteristic scales for length 
@@
 \begin{equation}
-    \bar{l} = \frac{l}{l_0}, \quad \bar{t} = \frac{t}{t_0}, \quad \bar{\rho} = \frac{\rho}{\rho_0}
+    \bar{l} = \frac{l}{l_0}, \quad \bar{t} = \frac{t}{t_0}, \quad \bar{\rho} = \frac{\rho}{\rho_0}, \quad \bar{\vec{u}} = \frac{\bar{l}}{\bar{t}}, 
 \end{equation}
@@
 \begin{equation}
-    \frac{\partial \bar{\vec{u}}}{\partial \bar{t}} + (\bar{\vec{u}} \cdot\nabla)\bar{\vec{u}} = \frac{1}{Re} \nabla^2 \bar{\vec{u}}
+    \frac{\partial \bar{\vec{u}}}{\partial \bar{t}} + (\bar{\vec{u}} \cdot\nabla)\bar{\vec{u}} = \frac{1}{Re} \nabla^2 \bar{p} = \frac{p}{\rho \vec{u}^2} - \nabla\bar{p}
 \end{equation}
@@
 original equation is written for a concentration of species $c$. For a binary mixture, it can be recast in terms of a conserved scalar order parameter $\phi$, typically representing the 
-local concentration difference between the two fluid components,
+local concentration difference between the two fluid components. As we are also accounting for the effect of hydrodynamics on the flow of mass, the advection term
+from the mass flux $\vec{J}$ cannot be set to 0. Therefore the Cahn-Hilliard equation is given by,
 
 \begin{equation}
-    \frac{\partial \phi}{\partial t} = \nabla \cdot \left( M \nabla \mu \right)
+    \begin{split}
+        \nabla \cdot \vec{J} &= \nabla \cdot \vec{u} - M \nabla \mu \\
+        \frac{\partial \phi}{\partial t} + \nabla \cdot \vec{J} &= 0 \\
+        \frac{\partial \phi}{\partial t} + \nabla \cdot \phi \vec{u} &= \nabla \cdot \left( M \nabla \mu \right)
+    \end{split}
 \end{equation}
@@
 Here, $M$ is the mobility coefficient and $\mu$ is the chemical potential, which is derived from the variation of the free energy functional $F[\phi]$ which is the sum of a bulk free energy
-$f(\phi)$ and an interfacial contribution. This formulation allows for the modeling of 
-interfacial tension and the spontaneous formation of bicontinuous domains characteristic of spinodal decomposition.
-To capture not only the diffusive separation of phases but also the resulting fluid motion, the Cahn-Hilliard equation is coupled with the Navier-Stokes equations, leading to the 
-Cahn-Hilliard-Navier-Stokes (CHNS) framework. This coupling is essential in systems like bijels, where advection play a significant role in domain coarsening and morphology arrest. 
-The momentum conservation equation in this framework is given by,
+$f(\phi)$ and an interfacial contribution.
+This formulation allows for the modeling of interfacial tension and the spontaneous formation of bicontinuous domains characteristic of spinodal decomposition.
+To capture not only the diffusive separation of phases but also the resulting fluid motion, the Cahn-Hilliard equation is coupled with the Navier-Stokes equation. This is done
+through the pressure which is expressed as the sum of the mechanical $p$ and chemical pressure $p_{chem}$ contributions to yield $p_{tot} = p + p_{chem}$. For a binary system, $p_{chem}$ 
+can be written as a function of $\phi$ given by,
+
+\begin{equation}
+    p_{chem} = \left[ \phi \mu - f(\phi) - \kappa(\phi \nabla^2 \phi + \frac{1}{2}|\nabla \phi |^2 )\right] \mathbb{I} + \kappa \nabla \phi \otimes \nabla \phi
+\end{equation}
+
+The divergence of the above expression is found to be $\nabla \cdot p_{chem} = -\phi \nabla \mu$. Substituting the $p_{tot}$ for $p$ in the Navier Stokes equation,
+the Cahn-Hilliard-Navier-Stokes (CHNS) framework is obtained. This coupling is essential in systems like bijels, where advection play a significant role in domain 
+coarsening and morphology arrest. The momentum conservation equation in this framework is given by,
 
@@
 \begin{equation}
-    f_{i}^{eq}(\rho, \vec{u}) = w_i\rho(1 + \frac{\mathbf{c_i} \cdot \mathbf{u}}{c_s^2} + \frac{ \vec{u}(c_{i,\alpha}c_{i,\beta}-c_s^2\mathbb{I}) }{2c_s^4})
-    % \frac{(\mathbf{c_i} \cdot \mathbf{u})^2}{2c_s^4} + \frac{\mathbf{u} \cdot \mathbf{u}}{2c_s^2})
+    f_i^{\text{eq}}(\rho, \vec{u}) = w_i \rho \left( 1 + \frac{\vec{c}_i \cdot \vec{u}}{c_s^2} + \frac{(\vec{c}_i \otimes \vec{c}_i - c_s^2 \mathbb{I}) : (\vec{u} \otimes \vec{u})}{2c_s^4} \right)
     \label{eq:LBM_Feq}
@@
 
-The momentum flux tensor is calculated from the Chapman-Enskog expansion of \ref{eq:LBM_BGK} to the first order yielding,
+The momentum flux tensor is calculated from the Chapman-Enskog expansion of \ref{eq:LBM_BGK} to the second order yielding,
 
@@
     \begin{split}
-        \rho\frac{\partial \vec{v}}{\partial t} + \nabla \cdot \Pi &= 0 \\
-        \Pi_{\alpha \beta} &= \sum_i \mathbf{c_i}_\alpha \mathbf{c_i}_\beta (f_i^{eq} + (1 - \frac{1}{2 \tau})f_i^1)
+        \rho\frac{\partial \vec{u}}{\partial t} + \nabla \cdot \Pi &= 0 \\
     \end{split}
@@
     \begin{split}
-        \Pi^{(0)}_{\alpha \beta} &= \sum_i \mathbf{c_i}_\alpha \mathbf{c_i}_\beta f_i^{eq} = p \delta_{\alpha \beta} + \rho \vec{u}_\alpha \vec{u}_\beta \\
-        \Pi^{(1)}_{\alpha \beta} &= (1 - \frac{1}{2 \tau})\sum_i \mathbf{c_i}_\alpha \mathbf{c_i}_\beta f_i^{eq} = \nu (\nabla_{\alpha}(\rho \vec{\beta}) + \nabla_{\beta}(\rho \vec{\alpha}))
+        % \Pi^{(0)}_{\alpha \beta} &= \sum_i \mathbf{c_i}_\alpha \mathbf{c_i}_\beta f_i^{eq} = p \delta_{\alpha \beta} + \rho \vec{u}_\alpha \vec{u}_\beta \\
+        % \Pi^{(1)}_{\alpha \beta} &= (1 - \frac{1}{2 \tau})\sum_i \mathbf{c_i}_\alpha \mathbf{c_i}_\beta f_i^{eq} = \nu (\nabla_{\alpha}(\rho \vec{\beta}) + \nabla_{\beta}(\rho \vec{\alpha}))
+        \Pi^{(0)} &= \sum_i f_i^{eq} \vec{c}_i \otimes \vec{c}_i = p\mathbb{I} + \rho \vec{u} \otimes \vec{u} \\
+        \Pi^{(1)} &= (1 - \frac{1}{2 \tau})\sum_i f_i^{neq} \vec{c}_i \otimes \vec{c}_i = -\eta (\nabla \vec{u} + (\nabla \vec{u})^T)
     \end{split}
@@
 
-With $p = \rho c_s^2$ and $\delta_{\alpha \beta}$ the kronecker delta.
+With $p = \rho c_s^2$.
 
@@
 \begin{equation}
-    \mathbf{U_{ij}} = \frac{\mu_0 \vec{m}_i \vec{m}_j}{4\pi |r_{ij}|^{3}} \left[ \vec{o}_i \cdot \vec{o}_j - 
+    U_{ij} = \frac{\mu_0 \vec{m}_i \vec{m}_j}{4\pi |r_{ij}|^{3}} \left[ \vec{o}_i \cdot \vec{o}_j - 
     3(\vec{o}_i \cdot \vec{r}_{ij})(\vec{o}_j \cdot \vec{r}_{ij}) \right]
@@
 \begin{equation}
-    \mathbf{F}_{ij} = \frac{3 \mu_0}{4 \pi} [\frac{5(\vec{m}_i \cdot \vec{r}_{ij} )(\vec{m}_j
+    \vec{F}_{ij} = \frac{3 \mu_0}{4 \pi} [\frac{5(\vec{m}_i \cdot \vec{r}_{ij} )(\vec{m}_j
     \cdot \vec{r}_{ij})}{|\vec{r}_{ij}|^7}\vec{r}_{ij} - \frac{(\vec{m}_{i} \cdot \vec{m}_{j})\vec{r}_{ij} + 
@@
 \begin{equation}
-    \mathbf{T}_{ij} = \frac{\mu_0}{4 \pi}[ \frac{3(\vec{m}_{j} \cdot \vec{r}_{ij})m_i \times \vec{r}_{ij} }
+    \vec{T}_{ij} = \frac{\mu_0}{4 \pi}[ \frac{3(\vec{m}_{j} \cdot \vec{r}_{ij})m_i \times \vec{r}_{ij} }
     {|\vec{r}_{ij}|^5} - \frac{\vec{m}_{i} \cdot \vec{m}_{j} }{|\vec{r}_{ij}|^3} ]
@@
 \begin{equation}
-    \mathbf{F_{j}} = \vec{m}_{j}(\vec{o}_{j} \cdot \nabla \vec{B}_{i})
+    \vec{F}_{j} = \vec{m}_{j}(\vec{o}_{j} \cdot \nabla \vec{B}_{i})
     \label{eq:magnet_force}
@@
 \begin{equation}
-    \mathbf{\tau_j} = \vec{m}_{j}(\vec{o}_{j} \times \vec{B}_{i})
+    \vec{T}_{j} = \vec{m}_{j}(\vec{o}_{j} \times \vec{B}_{i})
     \label{eq:magnet_torque}
@@
  \hline
- $t_{sim}$ & $L_x$ & $\rho_f$ & $\tau$ & $\eta_f$ & $g_{cc'}$ & $\sigma$ & $\phi_f$ & $\rho_p$ & $\phi_p$ & $V_p$ & $d_c$ & $K_H$ \\ [0.5ex] 
+ $t_{sim}$ & $L_x$ & $\rho_f $ & $\tau$ & $\eta_f $ & $g_{cc'} \Delta m(\Delta t)^2/(\Delta x)^5$ & $\sigma$ & $\phi_f$ & $\rho_p$ & $\phi_p$ & $V_p (\Delta x)^3$ & $d_c \Delta x$ & $K_H$ \\ [0.5ex] 
  \hline\hline
- $10^5$ & 256 & 0.7 & 1 & 0.117 & 0.08 & 0.0267 & 0.5 & 1 & 0.15 & 2000$\pi$ & 2/3 & 100\\ [1ex] 
+ $10^5 \Delta t$ & 256$\Delta x$ & 0.7 $\frac{\Delta m}{(\Delta x)^3}$ & 1$\Delta t$ & 0.117 $\frac{\Delta m}{\Delta x \Delta t}$ & 0.08 & 0.0267 $\frac{\Delta m}{(\Delta t)^2}$ & 0.5 & 1 $\frac{\Delta m}{(\Delta x)^3}$ & 0.15 & 2000$\pi (\Delta x)^3$ & 2/3 $\Delta x$& 100 $(\Delta x)^{1/2}(\Delta t)^2/\Delta m$\\ [1ex]
  \hline

### 2025-04-15 chapters/lit_review_new.tex
Making notation consistent

@@
 
-The thermodynamic equilibrium of a binary fluid mixture can be described by its Gibbs free energy, given as $G = \Delta H - T \Delta S$, where \(\Delta H\) is the enthalpy change, 
+The thermodynamic equilibrium of a binary fluid mixture can be described by its Gibbs free energy, given as $\Delta G = \Delta H - T \Delta S$, where \(\Delta H\) is the enthalpy change, 
 \(T\) is temperature, and \(\Delta S\) is the entropy change. The onset of phase separation occurs at the binodal line, defined where \(\frac{dG}{dx} = 0\), with \(x\) representing the composition. 
@@
 results in a bicontinuous structure driven by the system's attempt to minimize 
-free energy through composition modulation \cite{cahn_free_1958}. The dynamics of spinodal decomposition were characterized by Cahn and Hilliard \cite{cahn_spinodal_1961}. 
+free energy through composition modulation \cite{cahn_free_1958}. The dynamics of spinodal decomposition were characterized by Cahn \cite{cahn_spinodal_1961}. 
 We first begin by defining the free energy of a regular binary solution given by,
@@
 The most important difference between these two phase separation methods is the morphology of the phase separated structure. While nucleation and growth generates discontinuous droplets,
-spinodal decomposition creates continuous domains that have tunable domain sizes and tortuosity which are attractive in many materials applications such as battery electrodes, filtration
-membranes and catalyst supports.
+spinodal decomposition creates continuous domains which are attractive in many materials applications such as battery electrodes, filtration membranes and catalyst supports.
 

### 2025-04-15 chapters/model_params.tex
Making notation consistent

@@
 
-\begin{table}[h!]
+% \begin{table}[h!]
+% \centering
+% \begin{tabular}{||c c c c c c c c c c c c c||} 
+%  \hline
+%  $t_{sim}$ & $L_x$ & $\rho_f$ & $\tau$ & $\eta_f$ & $g_{cc'}$ & $\sigma$ & $\phi_f$ & $\rho_p$ & $\phi_p$ & $V_p$ & $d_c$ & $K_H$ \\ [0.5ex] 
+%  \hline\hline
+%  $10^5$ & 256 & 0.7 & 1 & 0.117 & 0.08 & 0.0267 & 0.5 & 1 & 0.15 & 2000$\pi$ & 2/3 & 100\\ [1ex] 
+%  \hline
+% \end{tabular}
+% \caption{Summary of the fluid, particle and model parameters used in the proposed simulations}
+% \label{table:model_params}
+% \end{table}
+
+\begin{table}
     \centering
-\begin{tabular}{||c c c c c c c c c c c c c||} 
+    \caption{Summary of the parameters corresponding to the fluid, particle and model used in the simulations}
+    \label{table:model_params}
+    \begin{tabular}{|c|r|}
     \hline
- $t_{sim}$ & $L_x$ & $\rho_f$ & $\tau$ & $\eta_f$ & $g_{cc'}$ & $\sigma$ & $\phi_f$ & $\rho_p$ & $\phi_p$ & $V_p$ & $d_c$ & $K_H$ \\ [0.5ex] 
- \hline\hline
- $10^5$ & 256 & 0.7 & 1 & 0.117 & 0.08 & 0.0267 & 0.5 & 1 & 0.15 & 2000$\pi$ & 2/3 & 100\\ [1ex] 
+    % Parameter & Value \\
+    % \hline
+    $L_V/\Delta x$ & 256 \\
+    $\rho \cdot (\Delta x)^3/\Delta m$ & 0.7 \\
+    $\nu \cdot \Delta t/(\Delta x)^2$ & 1/6 \\
+    $\sigma \cdot (\Delta t)^2/\Delta m$ & 0.0267 \\
+    $\tau/\Delta t$ & 1 \\
+    $g \cdot \Delta m(\Delta t)^2/(\Delta x)^5$ & 0.08 \\
+    $\phi_f$ & 0.5 \\
+    $\phi_p$ & 0.15 \\
+    $n_p$ & 1200 \\
+    $\rho_p \cdot (\Delta x)^3/\Delta m$ & 1 \\
+    $V_p/(\Delta x)^3$ & $2000\pi/3$ \\
+    $m/(\Delta i(\Delta x)^2)$ & 1 \\
+    $d_c/\Delta x$ & 2/3 \\
+    $K_H\cdot (\Delta x)^{1/2}(\Delta t)^2/\Delta m$ & 100 \\
     \hline
     \end{tabular}
-\caption{Summary of the fluid, particle and model parameters used in the proposed simulations}
-\label{table:model_params}
 \end{table}
@@
 used in these simulations. All particle geometries are volume matched, based on the spherical particle volume. For the 
-spherical particle, the radius was set at $R_{\parallel} = R_{\perp} = 7.9$ which sets the $\alpha = 0.5$ particles to 
-$R_{\parallel} = 5, R_{\perp} = 10$ and the $\alpha = 2$ particles to $R_{\parallel} = 12.6, R_{\perp} = 6.3$. 
+spherical particle, the radius was set at $R_{\parallel} = R_{\perp} = 7.9 \Delta x$ which sets the $\alpha = 0.5$ particles to 
+$R_{\parallel} = 5 \Delta x, R_{\perp} = 10 \Delta x$ and the $\alpha = 2$ particles to $R_{\parallel} = 12.6, R_{\perp} = 6.3 \Delta x$. 
 $R_{\parallel}$ and $R_{\perp}$ is the radius of the particle parallel and perpendicular to the symmetry axis of 
@@
 water/2-6-lutidine will be discussed in the context of the work presented here. The critical temperature (UCST) 
-for this system is $T_c = 34 ^{\circ}C$, with many systems heated to $T = 40^{\circ}C$ to form the bijel. At this 
-temperature, the fluid properties are $\sigma = 0.22 mN/m$ and $\eta = 2.38 mPas$. \cite{grattoni_lower_1993} 
-Fei et al. developed a method to synthesize polystyrene microparticles ($(R_p = 2 \mu m)$) with tunable geometries 
+for this system is $T_c = 34 ^{\circ}\text{C}$, with many systems heated to $T = 40^{\circ}\text{C}$ to form the bijel. At this 
+temperature, the fluid properties are $\sigma = 0.22 \text{mN/m}$ and $\eta = 2.38 \text{mPas}$. \cite{grattoni_lower_1993} 
+Fei et al. developed a method to synthesize polystyrene microparticles ($(R_p = 2 \text{\mu m})$) with tunable geometries 
 by mechanically stretching or compressing them, then coating them with nickel to create magnetic microparticles with 
-a dipole moment of approximately$\approx 3 \cdot 10^{-14} Am^2$. \cite{fei_active_2017, fei_magneto-capillary_2020} 
+a dipole moment of approximately$\approx 3 \cdot 10^{-14} \text{Am^2}$. \cite{fei_active_2017, fei_magneto-capillary_2020} 
 Comparing the physical properties to simulation parameters, the simulations correspond to a length scale of

### 2025-04-15 chapters/paper1_5.tex
Making notation consistent

@@
-\section[Introduction]{Introduction\protect\footnote{This section is based on work submited to the American Institude of Physics, Physics of Fluids journal.
+\section[Introduction]{Introduction\protect\footnote{This chapter is based on work submited to the American Institude of Physics, Physics of Fluids journal.
                         It is reproduced from submission number \#POF25-AR-DSFD2024-03180, with the permission of AIP Publishing.}}

### 2025-04-15 chapters/LBM_technique.tex
addressed notation and made font size larger in stress-time curve

@@
 
-The lattice boltzmann method works by evolving a population distribution $f_{i}(\mathbf{x}, t)$ on a cubic lattice with 
+The lattice boltzmann method works by evolving a population distribution $f_{i}(\vec{x}, t)$ on a cubic lattice with 
 timestep $\Delta t$ with lengthscale $\Delta x$. \cite{qian_lattice_1992, succi_lattice_2018, he_theory_1997} The cubic lattice or stencil is described
@@
 \begin{equation}
-    f_{i}(\mathbf{x} + \mathbf{c}_{i}\Delta t, t + \Delta t) = f_{i}(\mathbf{x}, t) - \frac{1}{\tau}(f_{i}(\mathbf{x}, t) 
-    - f_{i}^{eq}(\mathbf{x}, t))
+    f_{i}(\vec{x} + \vec{c}_{i}\Delta t, t + \Delta t) = f_{i}(\vec{x}, t) - \frac{1}{\tau}(f_{i}(\vec{x}, t) 
+    - f_{i}^{eq}(\rho, \vec{u}))
     \label{eq:LBM_BGK}
@@
 $\rho$ and $\textbf{u}$ in Equation \ref{eq:LBM_Feq} are defined as the macroscopic parameters for density and velocity 
-and can be calculated from the mass distribution using $\rho = \sum f_i$ and $\rho \mathbf{u} = \sum f_i \mathbf{c}_i$ 
+and can be calculated from the mass distribution using $\rho = \sum f_i$ and $\rho \vec{u} = \sum f_i \vec{c}_i$ 
 respectively. Using the Chapman-Enskog expansion, the Navier-Stokes equation at the incompressible limit at low Mach
@@
         \rho &= \sum_i f_i \\
-        \rho\vec{u} &= \sum_i f_i \mathbf{c_i}
+        \rho\vec{u} &= \sum_i f_i \vec{c}_i
     \end{split}
@@
     \begin{split}
-        % \Pi^{(0)}_{\alpha \beta} &= \sum_i \mathbf{c_i}_\alpha \mathbf{c_i}_\beta f_i^{eq} = p \delta_{\alpha \beta} + \rho \vec{u}_\alpha \vec{u}_\beta \\
-        % \Pi^{(1)}_{\alpha \beta} &= (1 - \frac{1}{2 \tau})\sum_i \mathbf{c_i}_\alpha \mathbf{c_i}_\beta f_i^{eq} = \nu (\nabla_{\alpha}(\rho \vec{\beta}) + \nabla_{\beta}(\rho \vec{\alpha}))
         \Pi^{(0)} &= \sum_i f_i^{eq} \vec{c}_i \otimes \vec{c}_i = p\mathbb{I} + \rho \vec{u} \otimes \vec{u} \\
@@
 The SC model mimics Cahn-Hilliard type behaviour through a force applied from the other fluid species $k'$ in adjacent 
-cells $\mathbf{x'}$ on fluid species $k$ at point $\mathbf{x}$. \cite{shan_lattice_1993, shan_simulation_1994, 
+cells $\vec{x'}$ on fluid species $k$ at point $\vec{x}$. \cite{shan_lattice_1993, shan_simulation_1994, 
 shan_multicomponent_1995, he_discrete_1998, jansen_bijels_2011, chin_lattice_2002} Both fluid species are defined
@@
 \begin{equation}
-% F_{k}^{SC}(\mathbf{x}, t) = -\Psi^{k}(\mathbf{x}, t)\sum_{k'}g_{cc'}\sum_{\mathbf{x'}}\Psi_{k'}(\mathbf{x'}, t)(\mathbf{x'} 
-% - \mathbf{x})
 \vec{F}_k(\vec{x}) \Delta t = - \sum_{k'} \sum_i \frac{w_i}{c_s^2} g_{kk'} \psi_k(\vec{x})\psi_{k'}(\vec{x}+\vec{c}_i) \vec{c}_i
@@
 
-An effective mass of each fluid at node $\mathbf{x}$ is used in place of the actual density to scale it between zero 
-and one and is defined as $\psi^{k}(\mathbf{x},t) = \rho_{0}\left[1 - \exp(-\frac{\rho^{k}(\mathbf{x}, t)}{\rho_{0}})\right]$. 
+An effective mass of each fluid at node $\vec{x}$ is used in place of the actual density to scale it between zero 
+and one and is defined as $\psi^{k}(\vec{x},t) = \rho_{0}\left[1 - \exp(-\frac{\rho^{k}(\vec{x}, t)}{\rho_{0}})\right]$. 
 In this model, the SC force is incorporated into the macroscopic velocities that are then used to calculate the equilibrium
@@
     \vec{F_p} = m_p \frac{\vec{u}_p}{dt} , \\
-    \vec{D_p} = \mathbf{J}_p \frac{\vec{\omega}_p}{dt} ,
+    \vec{D_p} = \vec{J}_p \frac{\vec{\omega}_p}{dt} ,
     \label{eq:md}
@@
 
-$\mathbf{F_p}$ and $\mathbf{D_p}$ represent the force and torque acting on a particle with mass $m_p$ and moment of inertia 
-$\mathbf{J}_p$. $\mathbf{u}_p$ and $\mathbf{\omega_{p}}$ are the linear and angular velocities of the particle. The equations of 
+$\vec{F_p}$ and $\vec{D_p}$ represent the force and torque acting on a particle with mass $m_p$ and moment of inertia 
+$\vec{J}_p$. $\vec{u}_p$ and $\vec{\omega_{p}}$ are the linear and angular velocities of the particle. The equations of 
 motion are evolved over time using a leapfrog integrator. \cite{jansen_bijels_2011}
@@
 where $R_i$ and $R_j$ are the radii of each particle involved in the interaction, $\vec{r}_{ij}$ is the distance
-vector between the particle centers, $\mathbf{u}_{ij}$ are the relative velocities of the particles and $\Delta_c$ 
+vector between the particle centers, $\vec{u}_{ij}$ are the relative velocities of the particles and $\Delta_c$ 
 is the cutoff distance when the lubrication force begins to act. If particles are able to overcome the lubrication forces, 
@@
 \begin{equation}
-    \phi_{H} = K_{H}(R_i + R_j - |\mathbf{r}_{ij}|)^{5/2}, r < R_i + R_j
+    \phi_{H} = K_{H}(R_i + R_j - |\vec{r}_{ij}|)^{5/2}, r < R_i + R_j
     \label{eq:hertz}
@@
 
-Where $\mu_0 = 4\pi \cdot 10^{-7} \frac{H}{m}$,  $\Hat{\mathbf{o_i}}$ is the orientation unit vector of particle 
+Where $\mu_0 = 4\pi \cdot 10^{-7} \frac{H}{m}$,  $\Hat{\vec{o_i}}$ is the orientation unit vector of particle 
 $i$, $\Hat{\vec{r}_{ij}}$ is the distance vector between particles $i$ and $j$ and $m_i$ is the magnitude the 
@@
 
-\begin{table}[h!]
+% \begin{table}[h!]
+% \centering
+% \begin{tabular}{||c c c c c c c c c c c c c||} 
+%  \hline
+%  $t_{sim}$ & $L_x$ & $\rho_f $ & $\tau$ & $\eta_f $ & $g_{cc'} \Delta m(\Delta t)^2/(\Delta x)^5$ & $\sigma$ & $\phi_f$ & $\rho_p$ & $\phi_p$ & $V_p (\Delta x)^3$ & $d_c \Delta x$ & $K_H$ \\ [0.5ex]
+%  \hline\hline
+%  $10^5 \Delta t$ & 256$\Delta x$ & 0.7 $\frac{\Delta m}{(\Delta x)^3}$ & 1$\Delta t$ & 0.117 $\frac{\Delta m}{\Delta x \Delta t}$ & 0.08 & 0.0267 $\frac{\Delta m}{(\Delta t)^2}$ & 0.5 & 1 $\frac{\Delta m}{(\Delta x)^3}$ & 0.15 & 2000$\pi (\Delta x)^3$ & 2/3 $\Delta x$& 100 $(\Delta x)^{1/2}(\Delta t)^2/\Delta m$\\ [1ex]
+%  \hline
+% \end{tabular}
+% \caption{Summary of the fluid, particle and model parameters used in the proposed simulations}
+% \label{table:model_params}
+% \end{table}
+
+\begin{table}
     \centering
-\begin{tabular}{||c c c c c c c c c c c c c||} 
+    \caption{Summary of the parameters corresponding to the fluid, particle and model used in the simulations}
+    \label{table:model_params}
+    \begin{tabular}{|c|r|}
     \hline
- $t_{sim}$ & $L_x$ & $\rho_f $ & $\tau$ & $\eta_f $ & $g_{cc'} \Delta m(\Delta t)^2/(\Delta x)^5$ & $\sigma$ & $\phi_f$ & $\rho_p$ & $\phi_p$ & $V_p (\Delta x)^3$ & $d_c \Delta x$ & $K_H$ \\ [0.5ex] 
- \hline\hline
- $10^5 \Delta t$ & 256$\Delta x$ & 0.7 $\frac{\Delta m}{(\Delta x)^3}$ & 1$\Delta t$ & 0.117 $\frac{\Delta m}{\Delta x \Delta t}$ & 0.08 & 0.0267 $\frac{\Delta m}{(\Delta t)^2}$ & 0.5 & 1 $\frac{\Delta m}{(\Delta x)^3}$ & 0.15 & 2000$\pi (\Delta x)^3$ & 2/3 $\Delta x$& 100 $(\Delta x)^{1/2}(\Delta t)^2/\Delta m$\\ [1ex]
+    % Parameter & Value \\
+    % \hline
+    $L_x$ & 256 $\Delta x$ \\
+    $\rho_f$ & 0.7 $ \frac{\Delta m}{(\Delta x)^3}$\\
+    $\nu_f$ & 1/6 $\frac{\Delta x}{(\Delta t)^2}$ \\
+    $\sigma $ & 0.0267 $\frac{\Delta m}{(\Delta t)^2}$ \\
+    $\tau$ & 1 $\Delta t$\\
+    $g_{kk'}$ & 0.08 $\frac{(\Delta x)^5}{\Delta m(\Delta t)^2}$\\
+    $\phi_f$ & 0.5 \\
+    $\phi_p$ & 0.15 \\
+    $n_p$ & 1200 \\
+    $\rho_p$ & 1 $ \frac{\Delta m}{(\Delta x)^3}$\\
+    $V_p$ & $2000\pi/3 (\Delta x)^3$ \\
+    $m$ & 1 $\frac{\Delta q}{\Delta t(\Delta x)^2}$\\
+    $d_c$ & 2/3 $\Delta x$ \\
+    $K_H$ & 100 $\frac{\Delta m}{(\Delta x)^{1/2}(\Delta t)^2} $\\
     \hline
     \end{tabular}
-\caption{Summary of the fluid, particle and model parameters used in the proposed simulations}
-\label{table:model_params}
 \end{table}
@@
 water/2-6-lutidine will be discussed in the context of the work presented here. The critical temperature (UCST) 
-for this system is $T_c = 34 ^{\circ}C$, with many systems heated to $T = 40^{\circ}C$ to form the bijel. At this 
-temperature, the fluid properties are $\sigma = 0.22 mN/m$ and $\eta = 2.38 mPas$. \cite{grattoni_lower_1993} 
-Fei et al. developed a method to synthesize polystyrene microparticles ($(R_p = 2 \mu m)$) with tunable geometries 
+for this system is $T_c = 34 ^{\circ}\text{C}$, with many systems heated to $T = 40^{\circ}\text{C}$ to form the bijel. At this 
+temperature, the fluid properties are $\sigma = 0.22 \text{mN/m}$ and $\eta = 2.38 \text{mPas}$. \cite{grattoni_lower_1993} 
+Fei et al. developed a method to synthesize polystyrene microparticles ($R_p = 2\,\mu\text{m}$) with tunable geometries 
 by mechanically stretching or compressing them, then coating them with nickel to create magnetic microparticles with 
-a dipole moment of approximately$\approx 3 \cdot 10^{-14} Am^2$. \cite{fei_active_2017, fei_magneto-capillary_2020} 
+a dipole moment of approximately$\approx 3 \cdot 10^{-14} \text{Am}^2$. \cite{fei_active_2017, fei_magneto-capillary_2020} 
 Comparing the physical properties to simulation parameters, the simulations correspond to a length scale of
@@
 droplet, was initialized in the center of the system and run till the droplet radii reached steady state. 
-This process was repeated for various droplet diameters, specified between $70$ and $85 \%$ of the system size at $5\%$ 
-increments. The system had a box length of $L = 64$ and was run for $50000$ timesteps with periodic boundary conditions 
+This process was repeated for various droplet diameters, specified between 70 and 85 \% of the system size at 5\% 
+increments. The system had a box length of $L = 64 \Delta x$ and was run for 50000 timesteps with periodic boundary conditions 
 on all sides. Data was dumped every 10000 timesteps with only the last timestep used to calculate the values shown. Due 
@@
 $\rho^b_{eff} = \rho^{b}_{d} - \rho^{b}_{m}$ is found by calculating the difference in density between the blue 
-fluid in the droplet and in the matrix. Next, the droplet mass is calculated as $M_d = \sum_{\mathbf{x}}{\rho_{eff}^{b}}$. 
+fluid in the droplet and in the matrix. Next, the droplet mass is calculated as $M_d = \sum_{\vec{x}}{\rho_{eff}^{b}}$. 
 The radius of the droplet can then be calculated from the mass and density of the droplets as $R_d = \sqrt[3]{\frac{3}{4\pi} 

### 2025-04-15 chapters/paper1_new.tex
Making notation consistent
addressed notation and made font size larger in stress-time curve

@@
 
-\section[Introduction]{Introduction\protect\footnote{This section is based on work published in the Royal Society of Chemistry's Soft Matter journal.
+\section[Introduction]{Introduction\protect\footnote{This chapter is based on work published in the Royal Society of Chemistry's Soft Matter journal.
 It is reproduced from Ref.~\cite{karthikeyan_formation_2024} with permission from the Royal Society of Chemistry.}}
@@
 provides a flexible and efficient approach to controlling key structural features of the final
-material—namely, the domain size, volume fraction, and phase composition—by manipulating the 
+material such as the domain size, volume fraction, and phase composition—by manipulating the 
 formulation and processing conditions of the emulsion \cite{mudassir_fundamentals_2021}. To ensure 
 thermodynamic and mechanical stability during processing, emulsions are typically stabilized by additives. 
-Among these, particle-stabilized systems—commonly referred to as Pickering emulsions—have emerged as attractive 
+Among these, particle-stabilized systems or Pickering emulsions have emerged as attractive 
 alternatives to traditional surfactant-based emulsions due to their ability to form stable interfaces without 
@@
 Beyond chemical composition, the geometry of the stabilizing particles plays a critical role in determining 
-the microstructure and stability of emulsions. When anisotropic particles—such as ellipsoids or rods—adsorb at 
+the microstructure and stability of emulsions. When anisotropic particles such as ellipsoids adsorb at 
 fluid interfaces, they give rise to shape-dependent capillary interactions that are markedly different from those 

### 2025-04-15 chapters/paper3.tex
addressed notation and made font size larger in stress-time curve

@@
 (STrIPS), for example, the flow rate of the casting mixture and the co-solvent ratio play a key role in controlling the microstructure of the bijel and determining whether droplets or 
-rope-like structures emerge during synthesis \cite{haase_continuous_2015, haase_situ_2016}. Similarly, in volatile-induced phase separation (VIPS), the viscosity of the solvent rich and poor 
+rope-like structures emerge during synthesis \cite{haase_continuous_2015, haase_situ_2016}. Similarly, in vapor-induced phase separation (VIPS), the viscosity of the solvent rich and poor 
 phases determines the extent of phase separation before gelation or jamming occurs, ultimately governing final domain morphology \cite{wang_scalable_2020}. In homogenization-driven methods, 

### 2025-04-15 chapters/LBM_technique.tex
Addressed some typesetting and more notational issues in methods section

@@
 \begin{equation}
-    \sigma = -p\mathbb{I} + \eta\left( \nabla \vec{u} + (\nabla \vec{u})^T -\frac{2}{3}(\nabla \vec{u})\mathbb{I} \right)
+    \sigma = -P\mathbb{I} + \eta\left( \nabla \vec{u} + (\nabla \vec{u})^T -\frac{2}{3}(\nabla \vec{u})\mathbb{I} \right)
 \end{equation}
@@
 Substituting this stress tensor into the momentum equation and using the relation, $\nabla\cdot \vec{u} = 0$ from the incompressibility constraint, the incompressible 
-Navier-Stokes equation can be derived which in vector notation is given by,
+Navier-Stokes equation can be derived given by,
 
 \begin{equation}
-    \rho \left(\frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u} \right) = -\nabla p + \eta \nabla^2 \vec{u} + \vec{f}
+    \rho \left(\frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u} \right) = -\nabla P + \eta \nabla^2 \vec{u} + \vec{f}
 \end{equation}
@@
 To facilitate numerical simulation and analysis, it is often useful to express the Navier-Stokes equation in non-dimensional form. Introducing characteristic scales for length 
-$l_0$, time $t_0$, and density $\rho_0$, dimensionless variables are defined as
+$l_0$, velocity $u_0$, and density $\rho_0$, dimensionless variables are defined as
 
 \begin{equation}
-    \bar{l} = \frac{l}{l_0}, \quad \bar{t} = \frac{t}{t_0}, \quad \bar{\rho} = \frac{\rho}{\rho_0}, \quad \bar{\vec{u}} = \frac{\bar{l}}{\bar{t}}, 
+    \bar{l} = \frac{l}{l_0}, \quad \bar{u} = \frac{u}{u_0}, \quad \bar{t} = \frac{u_0 t}{l_0} \quad \bar{\rho} = \frac{\rho}{\rho_0}, \quad \bar{P} = \frac{P}{\rho u^2}, 
 \end{equation}
 
-Substituting these into the incompressible Navier-Stokes equation leads to the dimensionless form:
+The form of the dimensionless pressure $\bar{P}$ is not unique and depends on whether inertial or viscous effects dominate. The expression shown is 
+relevant to an inertial regime. Substituting these into the incompressible Navier-Stokes equation and approximating that no external forces are present 
+leads to the dimensionless form:
 
 \begin{equation}
-    \frac{\partial \bar{\vec{u}}}{\partial \bar{t}} + (\bar{\vec{u}} \cdot\nabla)\bar{\vec{u}} = \frac{1}{Re} \nabla^2 \bar{p} = \frac{p}{\rho \vec{u}^2} - \nabla\bar{p}
+    \frac{\partial \bar{\vec{u}}}{\partial \bar{t}} + (\bar{\vec{u}} \cdot\nabla)\bar{\vec{u}} = \frac{1}{Re} \nabla^2 \bar{\vec{u}} - \nabla\bar{P}
 \end{equation}
 
-where the Reynolds number is defined as $Re = \frac{\rho_0 u_0 l_0}{\eta}$ which characterizes the ratio of inertial to viscous forces in the system.
+where the Reynolds number is defined as $Re = \frac{\rho_0 u_0 l_0}{\eta}$ which characterizes the ratio of inertial to viscous forces in the system. For a system
+where viscous effects dominate, $Re << 1$ the dimensionless pressure is defined as $\bar{P} = \frac{P l_0}{\eta u_0}$. This yields the alterate form,
+
+\begin{equation}
+    Re\left( \frac{\partial \bar{\vec{u}}}{\partial \bar{t}} + (\bar{\vec{u}} \cdot\nabla)\bar{\vec{u}}  \right) = \nabla^2 \bar{\vec{u}} - \nabla\bar{P}
+\end{equation}
+
+When substituting the value of $Re$ into the above, the Stokes equation is recovered.
 
@@
 local concentration difference between the two fluid components. As we are also accounting for the effect of hydrodynamics on the flow of mass, the advection term
-from the mass flux $\vec{J}$ cannot be set to 0. Therefore the Cahn-Hilliard equation is given by,
+from the mass flux $\vec{J}$ cannot be set to 0. Therefore the advective Cahn-Hilliard equation of an incompressible fluid ($\nabla \cdot \vec{v} = 0$) is given by,
 
@@
     \begin{split}
-        \nabla \cdot \vec{J} &= \nabla \cdot \vec{u} - M \nabla \mu \\
+        \nabla \cdot \vec{J} &= \nabla \cdot \phi\vec{u} - M \nabla \mu \\
         \frac{\partial \phi}{\partial t} + \nabla \cdot \vec{J} &= 0 \\
-        \frac{\partial \phi}{\partial t} + \nabla \cdot \phi \vec{u} &= \nabla \cdot \left( M \nabla \mu \right)
+        \frac{\partial \phi}{\partial t} + \vec{u}\nabla \cdot \phi &= \nabla \cdot \left( M \nabla \mu \right)
     \end{split}
@@
 
-Here, $M$ is the mobility coefficient and $\mu$ is the chemical potential, which is derived from the variation of the free energy functional $F[\phi]$ which is the sum of a bulk free energy
+Here, $M$ is the mobility coefficient and $\mu$ is the chemical potential derived from the variation of the free energy functional $F[\phi]$ which is the sum of a bulk free energy
 $f(\phi)$ and an interfacial contribution.
@@
 To capture not only the diffusive separation of phases but also the resulting fluid motion, the Cahn-Hilliard equation is coupled with the Navier-Stokes equation. This is done
-through the pressure which is expressed as the sum of the mechanical $p$ and chemical pressure $p_{chem}$ contributions to yield $p_{tot} = p + p_{chem}$. For a binary system, $p_{chem}$ 
+through the pressure which is expressed as the sum of the mechanical $P$ and chemical pressure $P_{chem}$ contributions to yield $P_{tot} = P + P_{chem}$. For a binary system, $P_{chem}$ 
 can be written as a function of $\phi$ given by,
@@
 \begin{equation}
-    p_{chem} = \left[ \phi \mu - f(\phi) - \kappa(\phi \nabla^2 \phi + \frac{1}{2}|\nabla \phi |^2 )\right] \mathbb{I} + \kappa \nabla \phi \otimes \nabla \phi
+    P_{chem} = \left[ \phi \mu - f(\phi) - \kappa(\phi \nabla^2 \phi + \frac{1}{2}|\nabla \phi |^2 )\right] \mathbb{I} + \kappa \nabla \phi \otimes \nabla \phi
 \end{equation}
 
-The divergence of the above expression is found to be $\nabla \cdot p_{chem} = -\phi \nabla \mu$. Substituting the $p_{tot}$ for $p$ in the Navier Stokes equation,
-the Cahn-Hilliard-Navier-Stokes (CHNS) framework is obtained. This coupling is essential in systems like bijels, where advection play a significant role in domain 
-coarsening and morphology arrest. The momentum conservation equation in this framework is given by,
+The divergence of the above expression is found to be $\nabla \cdot P_{chem} = \phi \nabla \mu$. Substituting $P_{tot}$ for $P$ in the Navier Stokes equation,
+the Cahn-Hilliard-Navier-Stokes (CHNS) framework is obtained. This coupling is essential in systems like bijels, where advection plays a role in domain 
+coarsening. The momentum conservation equation in this framework is given by,
 
 \begin{equation}
-    \rho \left(\frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u} \right) = \eta \nabla^2 \vec{u} - \nabla p - \phi \nabla \mu
+    \rho \left(\frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u} \right) = \eta \nabla^2 \vec{u} - \nabla P - \phi \nabla \mu
 \end{equation}
@@
 collision operator have been proposed as a solution that provides some of the benefits of MRT models with the simplicity of SRT models. These 
-have facilitated simulation of a wider range of physical phenomena \cite{adhikari_fluctuating_2005, liu_simulation_2023}. The SRT collision 
-operator is selected due to the additional computational performance needed by MRT not being needed. The combined streaming and 
+have facilitated simulation of a wider range of physical phenomena \cite{adhikari_fluctuating_2005, liu_simulation_2023}. The regimes that the simulations 
+performed here will take place will be at relatively small Reynolds numbers, mitigating many of the weaknesses of the SRT model while being computatinally
+more efficient. Therefore, the SRT collision operator is selected. The combined streaming and 
 collision step in LBM, using the BGK operator, is expressed in Equation \ref{eq:LBM_BGK}.
@@
 
-$\rho$ and $\textbf{u}$ in Equation \ref{eq:LBM_Feq} are defined as the macroscopic parameters for density and velocity 
-and can be calculated from the mass distribution using $\rho = \sum f_i$ and $\rho \vec{u} = \sum f_i \vec{c}_i$ 
-respectively. Using the Chapman-Enskog expansion, the Navier-Stokes equation at the incompressible limit at low Mach
-numbers can be recovered. \cite{qian_lattice_1992, he_lattice_1997} The regime accessible through this method is suitable 
-for simulations in this work as the $ 1 \leq Re \leq 100 $ and the mach number, $Ma < 0.01$, fulfilling the stability 
-criterion and usage requirements for the presented hydrodynamic model.
-
-The density and velocity of the fluid at each grid point is calculated from the zeroth and first moment of the particle density
-distribution,
+where $w_i$ and $\vec{c}_i$ correspond to the weights and lattice velocity vector of each direction in the D3Q19 lattice shown in Figure \ref{fig:d3q19_lattice}, $\rho$ and $\vec{u}$ are the fluid density
+and velocity at each lattice point, and $c_s$ is the speed of sound of the lattice, set to $c_s = \frac{1}{\sqrt{3}}$. $\rho$ and $\vec{u}$ can be calculated from the zeroth and first moment of the 
+mass distribution $f_i$, given by
 
@@
 
+Using the Chapman-Enskog expansion, the Navier-Stokes equation at the incompressible limit at low Mach
+numbers can be recovered. \cite{qian_lattice_1992, he_lattice_1997} The regime accessible through this method is suitable 
+for simulations in this work as the $ 1 \leq Re \leq 100 $ and the mach number, $Ma < 0.01$, fulfilling the stability 
+criterion and usage requirements for the presented hydrodynamic model.
 The momentum flux tensor is calculated from the Chapman-Enskog expansion of \ref{eq:LBM_BGK} to the second order yielding,
@@
 
-The momentum flux tensor can be further expressed as a sum of the equilibrium and non-equilibrium components of the stress tensor, denoted by 0 and 1 given by,
+The momentum flux tensor can be expressed as a sum of the equilibrium and non-equilibrium components of the stress tensor, denoted by 0 and 1 respectively given by,
 
@@
 
-An effective mass of each fluid at node $\vec{x}$ is used in place of the actual density to scale it between zero 
-and one and is defined as $\psi^{k}(\vec{x},t) = \rho_{0}\left[1 - \exp(-\frac{\rho^{k}(\vec{x}, t)}{\rho_{0}})\right]$. 
+An effective mass of each fluid at node $\vec{x}$ is used in place of the density to scale it between zero 
+and one and is defined as $\psi^{k}(\vec{x},t) = \rho_{0}\left[1 - \exp(-\frac{\rho^{k}(\vec{x}, t)}{\rho_{0}})\right]$ where
+$\rho_0$ is the reference density and is set to $\rho_0 = 1 \frac{\Delta m}{\Delta x^3}$. 
 In this model, the SC force is incorporated into the macroscopic velocities that are then used to calculate the equilibrium
@@
 a no-slip boundary condition through a moving bounce-back boundary. This is implemented into the distribution function
-by reflecting the outgoing populations of $f_i^k$ to the opposite lattice velocity
+by reflecting the outgoing populations of $f_i^k$ to the opposite lattice velocity $f^k_{i^\star}$ given by
 
@@
 
+where $\vec{u}_i = \vec{u}_p + \vec{omega}\times \vec{r_i}$ which represents the difference between the particle velocity and the 
+velocity of the particle surface. The location of the particle surface $r_i$ is calculated as $r_i = \vec{x} + \frac{\Delta t}{2}\vec{c}_i - \vec{x}_{cm}$ 
+where $\vec{x}_{cm}$ is the center of mass of the particle.
 This facilitates momentum exchange between particle and fluid which can be calculated analytically as 
-\(\Delta\vec{p}^k_i \frac{\Delta t}{(\Delta x)^3} = 2 f^{k,\star}_i(\vec{x},t)\vec{c}_i - \frac{2w_i}{c_s^2}\rho(\vec{u}_i\cdot\vec{c}_i)\vec{c}_i\).
+\(\Delta\vec{p}^k_i = 2 f^{k,\star}_i(\vec{x},t)\vec{c}_i - \frac{2w_i}{c_s^2}\rho(\vec{u}_i\cdot\vec{c}_i)\vec{c}_i\).
 The sum of the momentum change across the surface of the particle is computed to obtain the force and torque on the particle,
@@
 
+where $N_{\text{f}}$ is the number of fluid nodes around the node being uncovered and $\vec{c}_{i_{\text{f}}n}$ is the direction of the lattice velocity 
+in the grid point being uncovered that points to a surrounding fluid node.
+
 \subsection{Particles near contact}
@@
 where $R_i$ and $R_j$ are the radii of each particle involved in the interaction, $\vec{r}_{ij}$ is the distance
-vector between the particle centers, $\vec{u}_{ij}$ are the relative velocities of the particles and $\Delta_c$ 
+vector between the particle centers, $\vec{u}_{ij}$ are the relative velocities of the particles and $d_c$ 
 is the cutoff distance when the lubrication force begins to act. If particles are able to overcome the lubrication forces, 
@@
     \begin{split}
-    \phi(\vec{r}_{ij}) &= {\epsilon} \tilde{\phi}\left(\frac{\vec{r}_{ij}}{{\sigma}}\right) , \\
-    \vec{F}(\vec{r}_{ij}) &= {\epsilon} \tilde{\vec{F}}\left(\frac{\vec{r}_{ij}}{{\sigma}}\right) .
+    \phi(\vec{r}_{ij}) &= {\epsilon} \tilde{\phi}\left(\frac{\vec{r}_{ij}}{{\gamma}}\right) , \\
+    \vec{F}(\vec{r}_{ij}) &= {\epsilon} \tilde{\vec{F}}\left(\frac{\vec{r}_{ij}}{{\gamma}}\right) .
     \end{split}
@@
 For the lubrication force \eqref{eq:lubrication}, we choose
-${\sigma}=R_1+R_2$ and ${\epsilon}=\frac{6\pi\eta R_1^2 R_2^2}{{\sigma^3}}$, and for the
-Hertz potential we chose ${\sigma}=R_1+R_2$ and ${\epsilon}=K_H\sigma^{5/2}$. For two identical, rotationally
-symmetric ellipsoidal particles with orientations $\hat{\vec{o}}_i$ and $\hat{\vec{o}}_j$, we then replace $\epsilon$ and $\sigma$ by
+${\gamma}=R_1+R_2$ and ${\epsilon}=\frac{6\pi\eta R_1^2 R_2^2}{{\gamma^3}}$, and for the
+Hertz potential we chose ${\gamma}=R_1+R_2$ and ${\epsilon}=K_H\gamma^{5/2}$. For two identical, rotationally
+symmetric ellipsoidal particles with unit orientation vectors $\hat{\vec{o}}_i$ and $\hat{\vec{o}}_j$, we then replace $\epsilon$ and $\gamma$ by
 the anisotropic functions
@@
     %\qquad \chi = \frac{\left(\alpha^2-1\right)R_\parallel^2}{\left(\alpha^2+1\right)R_\parallel^2}\left(\hat{\vec{o}}_i\hat{\vec{o}}_j\right) , \\
-    \tilde\sigma\left(\vec{r}_{ij}, \hat{\vec{o}}_i, \hat{\vec{o}}_j\right) &= \frac{{\sigma}}{\sqrt{1-\frac{\chi}{2}\left[ \frac{\left(\hat{\vec{r}}_{ij}\cdot\hat{\vec{o}}_i+\hat{\vec{r}}_{ij}\cdot\hat{\vec{o}}_j\right)^2}{1+\chi\left(\hat{\vec{o}}_i\hat{\vec{o}}_j\right)} + \frac{\left(\hat{\vec{r}}_{ij}\cdot\hat{\vec{o}}_i-\hat{\vec{r}}_{ij}\cdot\hat{\vec{o}}_j\right)^2}{1-\chi\left(\hat{\vec{o}}_i\hat{\vec{o}}_j\right)} \right] }} , \\
+    \tilde\gamma\left(\vec{r}_{ij}, \hat{\vec{o}}_i, \hat{\vec{o}}_j\right) &= \frac{{\gamma}}{\sqrt{1-\frac{\chi}{2}\left[ \frac{\left(\hat{\vec{r}}_{ij}\cdot\hat{\vec{o}}_i+\hat{\vec{r}}_{ij}\cdot\hat{\vec{o}}_j\right)^2}{1+\chi\left(\hat{\vec{o}}_i\hat{\vec{o}}_j\right)} + \frac{\left(\hat{\vec{r}}_{ij}\cdot\hat{\vec{o}}_i-\hat{\vec{r}}_{ij}\cdot\hat{\vec{o}}_j\right)^2}{1-\chi\left(\hat{\vec{o}}_i\hat{\vec{o}}_j\right)} \right] }} , \\
     \chi &= \frac{\alpha^2-1}{\alpha^2+1} , \\
@@
 where $R_{\parallel}$ is the particle radius along the
-symmetry axis $\hat{o}$ and $\alpha=\frac{R_{\parallel}}{R_{\perp}}$ the aspect
+symmetry axis and $\alpha=\frac{R_{\parallel}}{R_{\perp}}$ the aspect
 ratio of the particle. The anisotropic Hertz potential and lubrication
@@
     \begin{split}
-    \phi\left(\vec{r}_{ij}, \hat{\vec{o}}_i, \hat{\vec{o}}_j\right) &= \epsilon\left(\hat{\vec{o}}_i, \hat{\vec{o}}_j\right) \tilde{\phi}\left(\frac{\vec{r}_{ij}}{\sigma\left(\vec{r}_{ij}, \hat{\vec{o}}_i, \hat{\vec{o}}_j\right)} \right) , \\
-    \vec{F}\left(\vec{r}_{ij}, \hat{\vec{o}}_i, \hat{\vec{o}}_j\right) &= \epsilon\left(\hat{\vec{o}}_i, \hat{\vec{o}}_j\right) \tilde{\vec{F}}\left(\frac{\vec{r}_{ij}}{\sigma\left(\vec{r}_{ij}, \hat{\vec{o}}_i, \hat{\vec{o}}_j\right)} \right) .
+    \phi\left(\vec{r}_{ij}, \hat{\vec{o}}_i, \hat{\vec{o}}_j\right) &= \epsilon\left(\hat{\vec{o}}_i, \hat{\vec{o}}_j\right) \tilde{\phi}\left(\frac{\vec{r}_{ij}}{\gamma\left(\vec{r}_{ij}, \hat{\vec{o}}_i, \hat{\vec{o}}_j\right)} \right) , \\
+    \vec{F}\left(\vec{r}_{ij}, \hat{\vec{o}}_i, \hat{\vec{o}}_j\right) &= \epsilon\left(\hat{\vec{o}}_i, \hat{\vec{o}}_j\right) \tilde{\vec{F}}\left(\frac{\vec{r}_{ij}}{\gamma\left(\vec{r}_{ij}, \hat{\vec{o}}_i, \hat{\vec{o}}_j\right)} \right) .
     \end{split}
@@
 \begin{equation}
-    U_{ij} = \frac{\mu_0 \vec{m}_i \vec{m}_j}{4\pi |r_{ij}|^{3}} \left[ \vec{o}_i \cdot \vec{o}_j - 
-    3(\vec{o}_i \cdot \vec{r}_{ij})(\vec{o}_j \cdot \vec{r}_{ij}) \right]
+    U_{ij} = \frac{\mu_0 m_i m_j}{4\pi |r_{ij}|^{3}} \left[ \Hat{\vec{o_i}}\cdot \Hat{\vec{o_j}} - 
+    3(\Hat{\vec{o_i}} \cdot \Hat{\vec{r_{ij}}})(\Hat{\vec{o_j}} \cdot \Hat{\vec{r_{ij}}}) \right]
     \label{eq:magnet_potential}
@@
 Where $\mu_0 = 4\pi \cdot 10^{-7} \frac{H}{m}$,  $\Hat{\vec{o_i}}$ is the orientation unit vector of particle 
-$i$, $\Hat{\vec{r}_{ij}}$ is the distance vector between particles $i$ and $j$ and $m_i$ is the magnitude the 
+$i$, $\Hat{\vec{r_{ij}}}$ is the unit distance vector between particles $i$ and $j$ and $m_i$ is the magnitude the 
 magnetic dipole of particle $i$. From the potential, the force and torque of the dipole force between particles 
@@
 \begin{equation}
-    \vec{F}_{ij} = \frac{3 \mu_0}{4 \pi} [\frac{5(\vec{m}_i \cdot \vec{r}_{ij} )(\vec{m}_j
-    \cdot \vec{r}_{ij})}{|\vec{r}_{ij}|^7}\vec{r}_{ij} - \frac{(\vec{m}_{i} \cdot \vec{m}_{j})\vec{r}_{ij} + 
-    (\vec{m}_{i} \cdot \vec{r}_{ij})\vec{m}_{i} + (\vec{m}_{j} \cdot \vec{r}_{ij})\vec{m}_{j} }{|\vec{r}_{ij}|^5}]
+    \vec{F}_{ij} = \frac{3 \mu_0 m_i m_j}{4 \pi} [\frac{5( \Hat{\vec{o_i}} \cdot \Hat{\vec{r_{ij}}} )(\Hat{\vec{o_j}}
+    \cdot \Hat{\vec{r_{ij}}})}{|\vec{r_{ij}}^4|}\Hat{\vec{r_{ij}}} - \frac{(\Hat{\vec{o_i}} \cdot \Hat{\vec{o_j}})\Hat{\vec{r_{ij}}} + 
+    (\Hat{\vec{o_i}} \cdot \Hat{\vec{r_{ij}}})\Hat{\vec{o_j}} + (\Hat{\vec{o_j}} \cdot \Hat{\vec{r_{ij}}})\Hat{\vec{o_j}} }{|\vec{r_{ij}}|^4}]
 \label{eq:dipole_magnetic_force}
@@
 \begin{equation}
-    \vec{T}_{ij} = \frac{\mu_0}{4 \pi}[ \frac{3(\vec{m}_{j} \cdot \vec{r}_{ij})m_i \times \vec{r}_{ij} }
-    {|\vec{r}_{ij}|^5} - \frac{\vec{m}_{i} \cdot \vec{m}_{j} }{|\vec{r}_{ij}|^3} ]
+    \vec{T}_{ij} = \frac{\mu_0 m_i m_j}{4 \pi}[ \frac{3(\Hat{\vec{o_j}} \cdot \Hat{\vec{r_{ij}}})\Hat{\vec{o_i}} \times \Hat{\vec{r_{ij}}} }
+    {|\vec{r}_{ij}|^3} - \frac{\Hat{\vec{o_i}} \cdot \Hat{\vec{o_j}} }{|\vec{r}_{ij}|^3} ]
     \label{eq:dipole_magnetic_torque}
@@
 \begin{equation}
-    \vec{F}_{j} = \vec{m}_{j}(\vec{o}_{j} \cdot \nabla \vec{B}_{i})
+    \vec{F}_{j} = m_j(\Hat{\vec{o_j}} \cdot \nabla \vec{B}_{i})
     \label{eq:magnet_force}
@@
 \begin{equation}
-    \vec{T}_{j} = \vec{m}_{j}(\vec{o}_{j} \times \vec{B}_{i})
+    \vec{T}_{j} = m_j(\Hat{\vec{o_j}} \times \vec{B}_{i})
     \label{eq:magnet_torque}
@@
 
-% \begin{table}[h!]
-% \centering
-% \begin{tabular}{||c c c c c c c c c c c c c||} 
-%  \hline
-%  $t_{sim}$ & $L_x$ & $\rho_f $ & $\tau$ & $\eta_f $ & $g_{cc'} \Delta m(\Delta t)^2/(\Delta x)^5$ & $\sigma$ & $\phi_f$ & $\rho_p$ & $\phi_p$ & $V_p (\Delta x)^3$ & $d_c \Delta x$ & $K_H$ \\ [0.5ex]
-%  \hline\hline
-%  $10^5 \Delta t$ & 256$\Delta x$ & 0.7 $\frac{\Delta m}{(\Delta x)^3}$ & 1$\Delta t$ & 0.117 $\frac{\Delta m}{\Delta x \Delta t}$ & 0.08 & 0.0267 $\frac{\Delta m}{(\Delta t)^2}$ & 0.5 & 1 $\frac{\Delta m}{(\Delta x)^3}$ & 0.15 & 2000$\pi (\Delta x)^3$ & 2/3 $\Delta x$& 100 $(\Delta x)^{1/2}(\Delta t)^2/\Delta m$\\ [1ex]
-%  \hline
-% \end{tabular}
-% \caption{Summary of the fluid, particle and model parameters used in the proposed simulations}
-% \label{table:model_params}
-% \end{table}
-
 \begin{table}
     \centering
-    \caption{Summary of the parameters corresponding to the fluid, particle and model used in the simulations}
+    \caption{Summary of the parameters corresponding to the fluid, particle and model used in the simulations. 
+             LB parameters can be converted to their real world equivalents using the unit conversions provided.}
     \label{table:model_params}
-    \begin{tabular}{|c|r|}
+    \begin{tabular}{|c|c|}
     \hline
-    % Parameter & Value \\
-    % \hline
+    Parameter & Value \\ [0.5ex] 
+    \hline\hline
     $L_x$ & 256 $\Delta x$ \\
@@
 spherical particle, the radius was set at $R_{\parallel} = R_{\perp} = 7.9 \Delta x$ which sets the $\alpha = 0.5$ particles to 
-$R_{\parallel} = 5 \Delta x, R_{\perp} = 10 \Delta x$ and the $\alpha = 2$ particles to $R_{\parallel} = 12.6, R_{\perp} = 6.3 \Delta x$. 
+$R_{\parallel} = 5 \Delta x, R_{\perp} = 10 \Delta x$ and the $\alpha = 2$ particles to $R_{\parallel} = 12.6 \Delta x, R_{\perp} = 6.3 \Delta x$. 
 $R_{\parallel}$ and $R_{\perp}$ is the radius of the particle parallel and perpendicular to the symmetry axis of 
@@
 This process was repeated for various droplet diameters, specified between 70 and 85 \% of the system size at 5\% 
-increments. The system had a box length of $L = 64 \Delta x$ and was run for 50000 timesteps with periodic boundary conditions 
-on all sides. Data was dumped every 10000 timesteps with only the last timestep used to calculate the values shown. Due 
+increments. The system had a box length of $L = 64 \Delta x$ and was run for $50000 \Delta t$ timesteps with periodic boundary conditions 
+on all sides. Data was saved every 10000 timesteps with only the last timestep used to calculate the values shown. Due 
 to the diffuse interface present in this method, the density profiles were verified to be at steady state at the end of 

### 2025-04-15 chapters/LBM_technique.tex
further refinements to notation and typos

@@
 
-% \begin{equation}
-    % \rho \left(\frac{\partial u_i}{\partial t} + (u_i\cdot\frac{\partial u_i}{x_i}) \right) = \frac{\partial \sigma_{ij}}{\partial x_j} + f_i
-% \end{equation}
+\begin{equation}
+    \rho \left( \frac{\partial \vec{u}}{\partial t} + (\vec{u}\cdot \nabla \vec{u})  \right) = \nabla \cdot \vec{\vec{\sigma}} + \vec{f}
+\end{equation}
+
+where $\vec{f}$ is the force exerted on the fluid from external forces such as gravity or magnetic interactions and $\vec{\vec{\sigma}}$ is the stress tensor. 
+For a Newtonian, isotropic fluid, the viscous stress tensor is given by
 
 \begin{equation}
-    \rho \left( \frac{\partial \vec{u}}{\partial t} + (\vec{u}\cdot \nabla \vec{u})  \right) = \nabla \cdot \sigma + \vec{f}
+    \vec{\vec{\sigma}} = -P\mathbb{I} + \eta\left( \nabla \vec{u} + (\nabla \vec{u})^T\right) - \frac{2}{3}(\nabla \cdot \vec{u})\mathbb{I} 
 \end{equation}
 
-where $\vec{f}$ is the force exerted on the fluid from external forces such as gravity or magnetic interactions and $\sigma$ is the stress tensor. For a Newtonian, isotropic fluid, 
-the viscous stress tensor is given by
-
-% \begin{equation}
-%     \sigma_{ij} = -p\delta_{ij} + \eta((\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i}) - \frac{2}{3}(\frac{\partial u_j}{\partial x_i})^2\delta_{ij})
-% \end{equation}
-
-\begin{equation}
-    \sigma = -P\mathbb{I} + \eta\left( \nabla \vec{u} + (\nabla \vec{u})^T -\frac{2}{3}(\nabla \vec{u})\mathbb{I} \right)
-\end{equation}
-
-Substituting this stress tensor into the momentum equation and using the relation, $\nabla\cdot \vec{u} = 0$ from the incompressibility constraint, the incompressible 
-Navier-Stokes equation can be derived given by,
+An additional approximation is made that that bulk and dynamic viscosities are related by $\lambda = -\frac{2}{3} \eta$. Substituting this stress tensor into the momentum equation 
+and using the relation, $\nabla\cdot \vec{u} = 0$ from the incompressibility constraint, the incompressible Navier-Stokes equation can be derived given by,
 
@@
 
-When substituting the value of $Re$ into the above, the Stokes equation is recovered.
+When substituting the value of $Re$ into the above and approximating the LHS to 0, the Stokes equation is recovered.
 
@@
 The CHNS model enables simulation of complex phase-separating fluid systems, capturing both the interfacial evolution and the momentum transfer within the fluid. In the context of bijels, this 
-model can be used to predict the formation and stabilization of the bicontinuous structure, especially when interfacial jamming by colloidal particles is introduced in more advanced extensions.
+model can be used to predict the formation and stabilization of the bicontinuous structure, especially when interfacial jamming by colloidal particles is introduced.
 
@@
 \cite{qian_lattice_1992} The kinematic viscosity, if using the BGK operator, is obtained from the Chapman-Enskog expansion of \ref{eq:LBM_BGK}
-as $\nu = c_s^2(\tau - \frac{\Delta t}{2})$. The equilibrium distribution is obtained from a projection of the 
+as $\nu = c_s^2(\tau - \frac{\Delta t}{2})$. $c_s$ is the speed of sound of the lattice and is set to $c_s = \frac{1}{\sqrt{3}}$ in the D3Q19 velocity set. 
+The equilibrium distribution is obtained from a projection of the 
 Maxwell-Boltzmann distribution onto Hermite polynomials. \cite{he_theory_1997, succi_lattice_2018} This is shown in equation 
@@
 
-where $w_i$ and $\vec{c}_i$ correspond to the weights and lattice velocity vector of each direction in the D3Q19 lattice shown in Figure \ref{fig:d3q19_lattice}, $\rho$ and $\vec{u}$ are the fluid density
-and velocity at each lattice point, and $c_s$ is the speed of sound of the lattice, set to $c_s = \frac{1}{\sqrt{3}}$. $\rho$ and $\vec{u}$ can be calculated from the zeroth and first moment of the 
-mass distribution $f_i$, given by
+where $w_i$ and $\vec{c}_i$ correspond to the weights and lattice velocity vector of each direction in the D3Q19 lattice and $\rho$ and $\vec{u}$ are the fluid density
+and velocity at each lattice point. $\rho$ and $\vec{u}$ can be calculated from the zeroth and first moment of the mass distribution $f_i$, given by
 
@@
 numbers can be recovered. \cite{qian_lattice_1992, he_lattice_1997} The regime accessible through this method is suitable 
-for simulations in this work as the $ 1 \leq Re \leq 100 $ and the mach number, $Ma < 0.01$, fulfilling the stability 
+for simulations in this work given that $Re < 100$ and $Ma < 0.01$, fulfilling the stability 
 criterion and usage requirements for the presented hydrodynamic model.
@@
 
-where $N_{\text{f}}$ is the number of fluid nodes around the node being uncovered and $\vec{c}_{i_{\text{f}}n}$ is the direction of the lattice velocity 
-in the grid point being uncovered that points to a surrounding fluid node.
+where $N_{\text{f}}$ is the number of fluid nodes around the uncovered node and $\vec{c}_{i_{\text{f}}n}$ is the lattice velocity 
+in the uncovered grid point that points to a surrounding fluid node.
 
@@
 symmetric ellipsoidal particles with unit orientation vectors $\hat{\vec{o}}_i$ and $\hat{\vec{o}}_j$, we then replace $\epsilon$ and $\gamma$ by
-the anisotropic functions
+the functions
 

### 2025-04-15 chapters/LBM_technique.tex
resolved some other notation issues

@@
 
-where $\vec{f}$ is the force exerted on the fluid from external forces such as gravity or magnetic interactions and $\vec{\vec{\sigma}}$ is the stress tensor. 
-For a Newtonian, isotropic fluid, the viscous stress tensor is given by
+where $\vec{f}$ is the force exerted on the fluid from external forces such as gravity and $\vec{\vec{\sigma}}$ is the stress tensor. 
+For a Newtonian, isotropic fluid, the stress tensor is given by
 
 \begin{equation}
-    \vec{\vec{\sigma}} = -P\mathbb{I} + \eta\left( \nabla \vec{u} + (\nabla \vec{u})^T\right) - \frac{2}{3}(\nabla \cdot \vec{u})\mathbb{I} 
+    \vec{\vec{\sigma}} = -P\mathbb{I} + \eta\left( \nabla \vec{u} + (\nabla \vec{u})^T - \frac{2}{3}(\nabla \cdot \vec{u})\mathbb{I} \right)
 \end{equation}
@@
     \begin{split}
-    \vec{F_p} = m_p \frac{\vec{u}_p}{dt} , \\
-    \vec{D_p} = \vec{J}_p \frac{\vec{\omega}_p}{dt} ,
+    \vec{F_p} = m_p \frac{d \vec{u}_p}{dt} , \\
+    \vec{D_p} = \vec{J}_p \frac{d \vec{\omega}_p}{dt} ,
     \label{eq:md}
@@
 \begin{equation}
-    \vec{F}_{ij} = \frac{3 \mu_0 m_i m_j}{4 \pi} [\frac{5( \Hat{\vec{o_i}} \cdot \Hat{\vec{r_{ij}}} )(\Hat{\vec{o_j}}
+    \vec{F}_{ij} = \frac{3 \mu_0 m_i m_j}{4 \pi} \left[ \frac{5( \Hat{\vec{o_i}} \cdot \Hat{\vec{r_{ij}}} )(\Hat{\vec{o_j}}
     \cdot \Hat{\vec{r_{ij}}})}{|\vec{r_{ij}}^4|}\Hat{\vec{r_{ij}}} - \frac{(\Hat{\vec{o_i}} \cdot \Hat{\vec{o_j}})\Hat{\vec{r_{ij}}} + 
-    (\Hat{\vec{o_i}} \cdot \Hat{\vec{r_{ij}}})\Hat{\vec{o_j}} + (\Hat{\vec{o_j}} \cdot \Hat{\vec{r_{ij}}})\Hat{\vec{o_j}} }{|\vec{r_{ij}}|^4}]
+    (\Hat{\vec{o_i}} \cdot \Hat{\vec{r_{ij}}})\Hat{\vec{o_j}} + (\Hat{\vec{o_j}} \cdot \Hat{\vec{r_{ij}}})\Hat{\vec{o_j}} }{|\vec{r_{ij}}|^4} \right]
 \label{eq:dipole_magnetic_force}
@@
 \begin{equation}
-    \vec{T}_{ij} = \frac{\mu_0 m_i m_j}{4 \pi}[ \frac{3(\Hat{\vec{o_j}} \cdot \Hat{\vec{r_{ij}}})\Hat{\vec{o_i}} \times \Hat{\vec{r_{ij}}} }
-    {|\vec{r}_{ij}|^3} - \frac{\Hat{\vec{o_i}} \cdot \Hat{\vec{o_j}} }{|\vec{r}_{ij}|^3} ]
+    \vec{T}_{ij} = \frac{\mu_0 m_i m_j}{4 \pi}\left[ \frac{3(\Hat{\vec{o_j}} \cdot \Hat{\vec{r_{ij}}})\Hat{\vec{o_i}} \times \Hat{\vec{r_{ij}}} }
+    {|\vec{r}_{ij}|^3} - \frac{\Hat{\vec{o_i}} \cdot \Hat{\vec{o_j}} }{|\vec{r}_{ij}|^3}\right]
     \label{eq:dipole_magnetic_torque}
